### 2017-06-07 paper/appendix-cueValidity.Rmd
paper and appendices

```{r echo = F}
library(langcog)
library(tidyverse)
library(ggthemes)
library(jsonlite)
theme_set(theme_few())
project.path <- "~/Documents/research/communicating-generalizations/"
data.path <- "data/generics/endorsement/"
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
```

# Appendix B: Measuring cue validity

In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
Here, the prevalence of the feature, or $P(f \mid k)$, is the important quantity.
Quantifiers can be described as conditions on prevalence: $\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}$.
The question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice.

Some (who?) have noted, however, that the inverse probability, the probability of the kind $k$ given the feature $f$ --- $P(k \mid f)$ --- might be able to save statistical-based approaches [@Leslie2007].
This inverse probability, referred to as *cue validity*, encodes the diagnosticity of the feature for the kind.
For example, after learning that an entity *carries malaria*, the probability that the entity is a *mosquito* is very high.

An approach based only on cue-validity would be insufficient because of cases like *Dogs have four legs*. 
Tons of animals have four legs, and so the diagnositicity of having four legs for a dog is very low. 
However, one could argue for some integration of the two probabilities --- prevalence and cue validity.
This is often tested by measuring prevalence and cue validity and using both measurements as predictors of generic endorsement in a logistic-regression [@Khemlani2012; @Prasada2013].

As noted in the main text, cue validity can be derived from a prevalence prior composed of a finite number of kinds.
This relationship follows from Bayes' Rule:

$$
P(x \in k | x \in f) = \frac{P(x \in f \mid x \in k) \cdot P(x \in k)}{\sum_{k'}P(x \in f \mid x \in k') \cdot P(x \in k')}
$$

where $x$ is an arbitrary entity, $k$ is a kind represented as a collection of entities in the kind, and $f$ is a feature represented as a collection of entities with the feature.
However, in a generative model composed of a potentially infinite number of kinds, the cue validity of a feature for a particular kind is 0. 
In our mixture model formulation of the prevalence prior, we explicitly represent the prevalence prior as a generative model with a potentially infinite number of kinds (see Appendix A for more details).
In this formulation, there is a mixture parameter $\phi$ that we consider the *potential of the property to be present in a kind*. 
This is generalization of cue validity to the case of an infinite number of kinds.

## Cue validity is a special case of the prevalence prior structure

## Measuring cue validity

Measuring cue validity involves collecting participants' judgments that rely upon the probability of the kind given the feature.
There are at least two conceivable ways of trying to measure cue validity.
One way is ask participants directly about the probability (or likelihood, odds, etc...) of the kind given the feature, using a likert scale or slider.
This is the paradigm used by @Khemlani2012 and @Prasada2013.
We'll call this approach the "direct question" approach.
Another way is to supply participants with the feature alone and have them generate the kind.
We'll call this approach the "free production" approach.

What criteria can we use to validate one measurement over the other?
We propose three boundary cases *a priori* that the measurement should be able to satisfy.
\begin{enumerate}
\item{Completely diagnostic features: We contend there are a number of features that only one (or very small) of categories contain. Examples include: \emph{carrying malaria} (mosquitos), \emph{carrying Lyme disease} (ticks), \emph{having manes} (lions), \emph{having pouches} (kangaroos). The cue validity of these features for the corresponding categories should be very high (close to 1).}
\item{Completely absent features: For features that are completely absent in a kind, the cue validity should be extremely low or 0. There are many examples of these kinds of pairings; for example, \emph{having wings} (leopards), \emph{laying eggs} (lions).}
\item{Completely undiagnostic features: We contend there are a number of features that almost every category contains. Examples include: \emph{being female / male}, \emph{being juvenile}. The cue validity of these features for particular categories should be extremely low or 0. Learning that an entity is female tells you almost nothing about what kind of animal it is.}
\end{enumerate}

We collected cue validity ratings by running both a direct question and a free production experiment.
For the free production experiment, the cue validity is the proportion of responses of the target category (e.g., "mosquitos") for the property (e.g., "carries malaria").
Of primary interest is the measurement for the boundary conditions described above.

## Experimental materials

Materials were the same for both experiments.
They were a collection of familiar properties and animal categories used in Expt. X (endorsement of generalizations about categories) described in the main text.
There were twenty-one properties in total.

## Direct question experiment

### Method
#### Participants

We recruited 40 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
The experiment took on average 5 minutes and participants were compensated \$0.75 for their work.

#### Procedure

Following the procedure in @Khemlani2012 and @Prasada2013, participants were presented with prompts of the following form:

\begin{quotation}
Imagine you come across a thing that \textsc{f}.
What are the odds that it is a \textsc{k}?
\end{quotation}

Participants responded using a slider bar with endpoints labeled "unlikely" and "likely". 
The slider appeared with no handle present; participants had to click on the slider for the slider handle to appear.
The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/generics/speaker_familiar-kinds/cue-validity-1.html}

Participants completed the thirty target trials (corresponding to the thirty generic statements used in Expt. X) in addition to ten filler trials (total number of trials = 40).
The filler trials were made up of random category -- property pairings.
All trials were presented in a randomized order.

## Free production experiment

### Method
#### Participants

We recruited 50 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
The experiment took on average 3 minutes and participants were compensated \$0.40 for their work.

#### Procedure

On each trial, participants were presented with prompts of the following form:

\begin{quotation}
Imagine you come across a thing (animal or insect) that \textsc{f}.
What do you think it is?
\end{quotation}

Participants responded by filling in a text box with their response.
There were twenty-one trials in total, one for each property.
Trials were presented in a randomized order.
The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/generics/speaker_familiar-kinds/cue-validity-2-freeProduction.html}

## Results

To process the free production, we forced all characters to lower case, removed spaces, and made all terms into singular terms (e.g., "lions" --> "lion").
As well, "mosquito" was a commonly mispelled label; we counted anything that started with "mosqu", "mesqu", "misqu", "mosiq" as "mosquito".

```{r directQuestion, echo = F}
d.cv.dq <- read.csv(paste(project.path, data.path, "cue-validity-1-trials.csv", sep = ""))

diagnostic.props <- data.frame(
  item = c("kangaroo has a pouch", "lion has a mane", 
           "mosquito carries malaria", "tick carries Lyme disease"),
  type = "diagnostic"
)

undiagnostic.props <- data.frame(
  item = c("kangaroo is juvenile", "lion is male", "robin is female", "leopard is full-grown"),
  type = "undiagnostic"
)

false.props <- data.frame(
  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
  type = "false"
)

target.items <- bind_rows(diagnostic.props, undiagnostic.props, false.props)

d.cv.targets <- left_join(
  d.cv.dq %>%
    mutate(property = gsub("&quotechar", "'", property), 
         item = paste(category, property)),
  target.items) %>%
  filter(!is.na(type)) %>%
  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))

d.cv.summary <- d.cv.targets %>%
  group_by(item, type) %>%
  multi_boot_standard(column = "response")

ggplot(d.cv.summary, aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~type, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 90))+
  xlab("")+
  ylab("Probability rating of cue validity")+
  ggtitle("Direct question paradigm")

```

```{r freeProduction, echo = F}
d.cv.fp <- read.csv(paste(project.path, 
                          data.path, "cue-validity-2-freeProduction-trials.csv", sep = ""))

mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")

d.cv.fp <- left_join(
  d.cv.fp %>%
 # rename(property = category) %>%
  mutate(response = tolower(response),
         response = gsub(" ", "", response),
         response = ifelse(substr(response, 1, 5) %in% mosquito.mispellings, "mosquito", response),
         response = ifelse(response == "deertick", "tick", response),
         response = ifelse(substrRight(response, 1) == "s",
                           substr(response, 1, nchar(response)-1), response),
         property = gsub("&quotechar", "'", property),
         item = paste(response, property)),
    target.items)

d.cv.fp.summary <- left_join(
  target.items,
  d.cv.fp %>%
    rename(category = response) %>%
    group_by(property) %>%
    mutate(n = n()) %>%
    filter(!(is.na(type))) %>%
    group_by(category, property, item) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials)
  ) %>%
  mutate(prop = ifelse(is.na(prop), 0.01, prop)) %>%
  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))

ggplot(d.cv.fp.summary, aes ( x = item, y = prop))+
  geom_bar(stat = 'identity', position = position_dodge())+
  facet_wrap(~type, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 90))+
  xlab("")+
  ylab("Proportion produced target category")+
  ggtitle("Free production paradigm")

```

```{r dq.histogram, fig.height = 4, eval = F}
ggplot(d.cv.targets, aes( x = response ))+
  geom_histogram() + 
  facet_wrap(~type) + 
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

### 2017-06-07 paper/appendix-prevalencePrior.Rmd
paper and appendices

# Appendix A: Structure in the prevalence prior

## Extended Analysis of Priors: Conceptual Structure

The pragmatics model only has a prevalence-based semantics yet it is able to explain the flexibility in truth judgments for a diverse range of generic statements.
Conceptual accounts of generic statements have looked beyond prevalence, to structured knowledge representations as the critical factor in generic meaning [@Leslie2007; @Prasada2013]. 
We can interrogate our formal model to see what is driving its predictions, and, in particular, we ask whether structured representations might effect our model after all.

For a given property,  the prior distribution on prevalence $P(x)$ is a single distribution.
However, the distribution may be structured as the result of deeper conceptual knowledge. 
For instance, if participants believe that some kinds have a causal mechanism that \emph{could} give rise to the property, while kinds others do not, then we would expect $P(x)$ to be structured as a mixture distribution [cf., @Griffiths2005].
We know that prior knowledge plays a fundamental role in leading the pragmatics model to endorse or reject generics. 
We now explore the hypothesis that this is at least partly because these priors are structured into two components: kinds that \emph{can} have the property and other kinds that \emph{cannot}.
We explore this possibility by formulating a mixture model for the prevalence priors, and exploring how well it fits the prior data elicited in Expt.~1a.

### Data analysis

If a kind can have the property, we assume the prevalence follows a Beta distribution with mean $\gamma$ and concentration $\xi$. 
If a kind cannot, we assume the prevalence is a Delta distribution, with all probability mass at 0\%. ^[There are other ways to formulate the second component ("the kind doesn't have a causal mechanism that would give rise to  the property") of the prior. 
It could reflect accidental causes of the property, in which case, the prevalence could be a distribution that allows for non-zero prevalence. 
While an interesting possibility, its full consideration is beyond the scope of this article.
]
The relative contribution of these two components is governed by mixture parameter $\phi$, inferred from the data.^[This is similar in spirit to Hurdle Models of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., adverse events to vaccines; @hurdleModels])]
We think of $\phi$ the \emph{potential of a property to be present in a kind} and $\gamma$ is the \emph{mean prevalence of the property among the kinds with the potential to have it}.\footnote{
We note that $\phi$ is not what other authors have described as \emph{cue validity} [@Beach1964; Khemlani2012], or $P(K \mid F)$. 
 $\phi$ is a mixture component in the prior distribution over prevalence: $P(F\mid K$). 
Cue validity and prevalence are related via Bayes Rule': $P(K \mid F) \propto P(F \mid K) \cdot P(K)$. 
}
If this model is correct, the prevalences given by participants would then be distributed as: $P(d) = \phi \cdot \text{Beta}(d \mid \gamma,\xi)+ (1 - \phi) \cdot \delta_{d=0}$.

We performed Bayesian inference over this model, given the observed prevalence data, to examine how well the model's posterior predictive distribution reconstructs the prevalence prior data.
We put uninformative priors over all the parameters, $\phi \sim \text{Uniform}(0,1)$, 
$\gamma \sim \text{Uniform}(0,1)$, $\xi \sim \text{Uniform}(0, 50)$, 
and performed Bayesian inference separately for each property using the Metropolis-Hastings algorithm 
collecting 50,000 samples removing the first 25,000 iterations for burn-in.

### Results

Estimates of the mixture parameter $\phi$ and the mean of the "has the potential" component $\gamma$ for each property are shown in Figure \ref{fig:commongenerics}a.
We see significant diversity among our properties in both parameters, corresponding to priors over prevalence with dramatically different shapes (insets).

Again, we look to the posterior predictive distribution to validate the structured prior model.
Using the model with its inferred parameters, we generate prevalence judgments for different properties and compare that to the empirical counts. 
We discretize the prevalence values of both the model and the data to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$.
This statistical model reproduces the prior elicitation data very well ($r^2 = 0.94$), while a model that assumes just a single generative component fails ($r^2 = 0.14$). This is strong evidence in support of a structured prior.

The other test of this hypothesis is to re-examine the truth judgments from Expt.~1b using the pragmatics model with the inferred structured priors (as opposed to bootstrapping the raw empirical counts). 
We find the same correspondence to the empirical truth judgments data ($r^2 = 0.98$).
This provides further evidence that the prior distribution over prevalence $P(x)$ is structured.
The implication of this finding is that conceptual structure may indeed find its way into generic judgments, but via the prevalence prior, rather than directly in the semantics of the generic. We return to this idea in the General Discussion.

\begin{figure}
\centering
    \includegraphics[width=0.6\columnwidth]{figs/postPred-priorModel.pdf}
    \caption{Posterior predictive distribution of the structured, statistical model thought to give rise to the human data in the prior elicitation task. The close alignment between model and data suggests the assumption of a structured prior is warranted.}
  \label{fig:pp-priorModel}
\end{figure}

### 2017-06-07 paper/gelman2007expt.Rmd
paper and appendices

# Prevalence is a Predictive Probability

So far, we have shown that property prevalence is sufficient to formalize the semantics of generic statements as an underspecified scalar denotation.
But what is property prevalence?
If generic language is truly conveying generalizations, it would be useful for it to reflect expectations, not just the current statistics in the world.
The current frequency of a property is often a good indicator of future frequency, yet statistics can be distorted by spurious events.
The causal history of a property may be more or less important for implying the property will be present in future situations.
Does generic language communicate prevalence in terms of past frequency or future expectations?

To answer this, we adopt an experimental paradigm used by @Gelman2007 to show that generic language is sensitive to theory-based considerations.
In the original paradigm, participants are told a story about a novel creature (e.g. \emph{dobles}) and a property of that kind (e.g., \emph{having claws}).
Participants are then either told that the creature was born with the property or that it acquired the property through extrinsic means (e.g., by finding claws and putting them on). 
Then, participants are told about an event that either causes the property to disappear (e.g., they drank a chemical and their claws fell off) or that leaves the property intact, and are asked whether or not the generic (e.g. \emph{Dobles have claws}) applies.
The original finding was that adult judgments were sensitive to the origins of the property (i.e., born vs. acquired), and insensitive to the outcome of the event (i.e., property maintained vs. lost): Participants fully-endorsed the generic when it was inborn, and rejected it when it was acquired, regardless of the current prevalence of the property.

In Experiment 3a, we use the same basic paradigm to measure \emph{predictive prevalence}: participants' expectations about future instances of the kind.
We explore the predictions of our truth judgments model, assuming that \emph{predictive prevalence} is what is being communicated.
In Experiment 3b, we use a truth judgment task similar to @Gelman2007 and compare participants' judgments to the model's predicted endorsements.

## Experiment 3a: Predictive Prevalence Elicitation

The design of this experiment is based on a study reported in @Gelman2007 with some slight modification.
%The original study was done on 14 undergraduates.

### Method

#### Participants
We recruited 80 participants over MTurk.  
The experiment took about 3 minutes and participants were compensated \$0.35.

#### Procedure and materials

On each trial, participants read a vignette about a novel creature. For instance,
\begin{quote}
These are dobles. [picture of 10 dobles with claws] Here is how they grew. They grew up with claws. First they were born, then they got bigger, then they were full size. [picture of a doble with claws, getting bigger and bigger; in some vignettes, the animal was first shown hatching out of an egg with the relevant property already visible] Then one day they drank a bad chemical. They got very sick and this is how they looked. [picture of 10 dobles without claws]
\end{quote}
The trial proceeded by participants reading the text, and clicking a button to continue to the next part of the story (at which time, the images changed according to the example above).

Participants saw 4 trials: 2 in which the creatures are born with the property (\textbf{intrinsic origins}), and 2 in which the creatures are shown discovering and acquiring the property (\textbf{extrinsic origins} e.g., painting themselves brown).
This was crossed with either the creatures drinking a "bad chemical" and losing the feature, or drinking a "yummy drink" and maintaining the feature.
The outcome of this event determined the final presentation of images that the participant saw (e.g., either 10 dobles with claws or 10 without).

While this final screen was present, we measured \emph{predictive prevalence} by telling participants: "A new doble was born today. When it becomes full grown, how likely is it that it would have claws?"
Participants responded using sliders ranging from "very unlikely" to "very likely".

We used 2 different types of properties: colors (e.g. \emph{Lorches are green.}) and body parts (e.g. \emph{Dobles have claws}).
For each type of property, there were approximately 8 different exemplars (different colors or different body parts for different creatures).
The creatures were either birds, bugs, or fish, with randomly sampled physical dimensions (e.g., sizes of body or tail).
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/generics/experiments/predictive/predictive-elicitation-1-elicitation.html}.

### Results and truth judgment predictions

The average predicted prevalences for the 4 experimental conditions are shown in Table \ref{tab:predictive}.
We observe a main effect of origins, such that when participants read that the creatures had the property from birth, future creatures  are much more likely to have the property as compared to when the property is acquired.
We see that, in our paradigm, participants are also sensitive to the outcome of the event. %This is surprising because @Gelman2007 observed no effect of the event outcome on generic endorsement.
When participants observe a creature who loses the property by drinking a chemical, they report future members of the category are less likely to have the property.
This inference may be driven by inferences about the property (e.g., that the property could be an unstable property, if you can lose it simply by drinking something) or by inferences about the event (e.g., participants may believe this "chemical drinking" event is a relatively normal event, and thus it could happen in the future).

\begin{table}
\centering
\begin{tabular}{l|l|r|r|r}
\hline
Origins & Event Outcome & Collapsed Mean [95\% CI]  & Color  [95\% CI] & Body Part [95\% CI] \\
\hline
Extrinsic & Lost  & 0.15 [0.10, 0.21]& 0.13 [0.07, 0.21] & 0.17 [0.09, 0.26] \\
\hline
Extrinsic & Maintained & 0.32 [0.24, 0.39] & 0.24 [0.16, 0.35] & 0.38 [0.27, 0.50] \\
\hline
Intrinsic & Lost  & 0.69 [0.62, 0.76] & 0.73 [0.63, 0.83] & 0.66 [0.56, 0.75] \\
\hline
Intrinsic & Maintained  &0.95 [0.94, 0.97] & 0.96 [0.94, 0.98] & 0.94 [0.91, 0.97] \\
\hline
\end{tabular}
\caption{Predicted prevalence for the four experimental conditions of Expt.~3a. Right two columns show the summaries broken down by the two types of properties used in the experiment.}
\label{tab:predictive}
\end{table}

We use these predicted probabilities as the prevalence $x$ that the speaker model is trying to communicate: $S_2(u\mid x)$, and examine the model's predicted truth judgments.
We explore the model's predictions for each origin and event outcome, as well as when the data is split by property type (color vs. body parts). 
For priors $P(x)$, we use the body part and color priors elicited in Expt.~2a.
We see that the model predictions track closely the predicted prevalence (Figure \ref{fig:dobles}a, top, compare with predicted prevalence in Table \ref{tab:predictive}).
This is because both color and body part priors are relatively broad, and hence when the property is (predicted to be) more prevalent, the generic has a higher probability of applying (see schematic predictions from Figure \ref{fig:schematic-unif} "have wings" for comparison).
We also see that the model predicts a subtle by-item difference, such that the influence of the event outcome (lost or maintained) on generic endorsement is predicted to be stronger for body parts than for color terms (Figure \ref{fig:dobles}a, bottom).
This prediction is mostly due to the predicted prevalence for the conflict conditions (intrinsic-lost and extrinsic-maintained) being subtly different (Table \ref{tab:predictive}, right-most columns).

<!--
%\footnote{Note that our model's predictions do not deviate substantially from the predicted prevalence because there are only two different priors being used, and the shapes of those distributions do not vary appreciably (see Figure \ref{fig:prior2}). \ndg{huh? two priors does not explain why the model tracks predicted prevalence. instead it's that the priors are broad and unimodal or something right?}
%}.
-->

Our model thus makes two novel predictions for generic endorsement in the paradigm by @Gelman2007.
We predict that in addition to the main effect of origins, we should see a second main effect of event outcome.
Second, we predict that this effect should be slightly stronger in the case of color properties than in the case of body part properties.

## Experiment 3b: Truth Judgment Task

In this experiment, we test the predictions of our model using a truth judgment measure in the same paradigm.

### Method

#### Participants
We recruited 80 participants over MTurk.  
The experiment took about 3 minutes and participants were compensated \$0.35.
None of the participants completed Experiment 3a as well.

#### Procedure and materials
The procedure and materials are exactly the same as in Expt.~3a, with the exception of the dependent measure.
After reading each vignette, participants were asked: "Do you agree or disagree that: \textsc{generic statement} (e.g. Dobles have claws)".
Participants responded by choosing one of two radio buttons corresponding to agree or disagree.

### Results and discussion

<!--
%                                         Estimate Std. Error z value        Pr(>|z|)    
%(Intercept)                               -2.9444     0.5130  -5.740 0.0000000094624 ***
%event_outcomemaintained                    2.6931     0.5603   4.807 0.0000015342262 ***
%originsintrinsic                           3.6753     0.5658   6.496 0.0000000000824 ***
%event_outcomemaintained:originsintrinsic   0.2396     0.9400   0.255           0.799    
-->

Our pragmatics model with the elicited predicted prevalence from Expt.~3a made two novel predictions for this experiment: (1) in addition to a main effect of origins, we would find a main effect of event outcome; (2) this effect would be stronger for body part properties than for color properties.
As predicted, we found two main effects (Figure \ref{fig:dobles}b, top).
The main effect of property origins replicated ($\beta=3.6, SE=0.57, z=6.5, p<1\text{e}10$): participants were more likely to endorse the generic when it was about a property that the creature was born with.
In addition, we find a second main effect of event outcome 
 ($\beta = 2.69, SE = 0.56, z=4.8, p<1\text{e}5$): participants were more likely to endorse the generic when the property was maintained than when it was lost.\footnote{The fact that we find a second main effect of event outcome in addition to origins, whereas the original only found a main effect of origins, makes it worth noting the differences between our paradigm and the original study by Gelman \& Bloom.
In the original study, the first sentence of each vignette used the possessive "my": "These are my dobles.".
At the end of each vignette, the original study had participants judge two statements in counterbalanced order: "Do my dobles have claws?" and "Do dobles have claws?"
Finally, the original sample size was 14; ours was 80. 
}

When we break down the results by item, we see that this effect is  stronger for body part properties than for color properties (Figure \ref{fig:dobles}b, bottom).
The endorsement of a generic for color properties (e.g. \emph{Lorches are green}) seems to be less sensitive to the outcome of the event (i.e. Lorches losing their color as a result of drinking a chemical).
This may be due to participants' intuitive theories of properties and their stability (skin color is more stable than body parts like feathers).
Indeed this difference is apparent in the predictive prevalence task (Expt.~3a).
For the 8 data points of generic endorsement based on origins, outcome, and property type, our model's predictions match the data well ($r^2(8) = 0.96$).
We, thus, elaborate our theory:
The semantics of generics can be understood as a threshold on property prevalence, and this prevalence is a speaker's subjective belief about what is likely to be the case in the future.

\begin{figure*}
\begin{tabular}{l l}
(a) $S_2$ model predictions & (b) Human endorsement of generic statements \\
\\
\centering
    \includegraphics[width=0.5\columnwidth]{figs/dobles-model.pdf} & 
        \includegraphics[width=0.5\columnwidth]{figs/dobles-results.pdf} \\
      \includegraphics[width=0.5\columnwidth]{figs/dobles-model-byItem.pdf} & 
      \includegraphics[width=0.5\columnwidth]{figs/dobles-byItem-results.pdf} \\

\end{tabular}
    \caption{
    Prevalence is a predictive probability.
    (a) Truth judgment model predictions given the predicted prevalence elicited in Expt.~3a.
    (b) Average endorsement of the generic statement in Expt.~3b (replication of Gelman and Bloom, 2007).  
    Bottom row shows data and predictions broken down by property type.
  }
  \label{fig:dobles}
\end{figure*}

### 2017-06-07 paper/generics-paper.Rmd
paper and appendices

---
title             : "Communicating generalizations about categories, events, and causes"
shorttitle        : "Communicating generalizations"

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"

header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}

author_note: >
  Enter author note here.

abstract: > 
    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    One major issue in formalizing *genericity* is that such language is extremely flexible in its usage. 
    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about events (i.e., *habitual language*, e.g., *John runs*), causes (i.e., *causal language*, e.g., *The block makes the machine play music.*), and categories (i.e., *generic language*, e.g., *Birds fly*), and find that the model, and not simpler models, explains full spectra of endorsements of generalizations in language.
    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

keywords          : "genericity, generalizations, generics, pragmatics, semantics, bayesian modeling"
wordcount         : "X"

bibliography      : ["generics.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}
<!-- \newcommand{\ndg}[1]{\textcolor{Green}{$[ndg: #1 ]$}} -->
<!-- \newcommand{\mht}[1]{\textcolor{Blue}{$[mht: #1 ]$}} -->
<!-- \newcommand{\red}[1]{\textcolor{Red}{$#1$}} -->

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)

```

```{r include = FALSE}
library("papaja")
```

```{r libraries}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(tidyr)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "~/Documents/research/comgen-paper/"
options("scipen"=10) 
```

# Introduction

Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge for a cognitive agent.
We learn such *generalizations* early in life by observing instances and drawing inductive inferences [@Dewar2010].
Social learning---relying upon the human capacity to infer others' intentions---faciliates this process [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, her mind gains access to a new, human-unique source of data: language.

<!-- give rise to the productivity of human thought and form of foundations of cultural knowledge. -->
<!-- They allow us to understand the complex world around us and dream up how possible future situations might unfold. -->
<!-- It's been suggested that were psychology to have *general laws* akin to Newtonian laws in physics, the first general law in psychology would be of generalizations [Shepard1987]. -->
<!-- Generalizations are central to human understanding.  -->
<!-- Even before birth, human and non-human animals alike gather statistical information and form generalizations to predict what will come next. -->
<!-- The human learner, perhaps uniquely in the animal kingdom, displays striking sensitivity to the intentional and pedagogical actions of others, leading to distinct and often stronger inferences from data than would otherwise be warranted from random observations. -->

Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Graham2004; @Markman1989].
But language also has the ability to refer to *generalization itself*.
At around the age of two and a half, children begin to understand that *generic language* (e.g., "Dogs bark") refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].
It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are central to the growth of conceptual knowledge [#Gelman2004] 
Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].

Computational models of learning formalize the inferences derived from observations, focusing on the question of how children and adults generalize from sparse data [@Tenenbaum2011]. 
They showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000].
Probabilistic models have recently made progress in describing pragmatic language understanding in precise terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
These models of rational communication describe inferences one can draw from language about *particular* situations: utterances that convey information about a specific entity or event.
The language of generalizations --- statements that extend beyond the here-and-now --- has heretofore eluded precise formalization.

The major issue in formalizing generic language is determining what makes a generic statement true or false. 
When we hear *Dogs bark*, we may feel it's a universal statment as in *All* dogs bark.
We may then realize that, among others, exquisitely well-trained dogs do not bark, which means the generic should signal something weaker like *Most* dogs bark.
Indeed, many generic statements seem to have the quantificational force of *most*. 
But most mosquitos do not carry malaria, while the statement *Mosquitos carry malaria* is intuitively true.
So the generic must in some way be compatible with *some* (e.g., *some mosquitos carry malaria*).
But equating the generic with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
Perhaps properties that only apply to one gender are an exception, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.

Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization.
*Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general (e.g., *You never know what will happen on a blind date*), specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious. 
Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.

In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to define the truth conditions of generalizations in language. 
By formalizing such a hypothesis in a probabilistic language understanding model, we derive predictions for endorsements of such statements by specifying relevant prior knowledge.
Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
We do this in three domains: generalizations about categories, events, and causes. 
In each domain, we define a scale that corresponds to the relevant metric by which a learner should generalize. 
We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fail.

The rest of this paper is organized as follows. 
In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in different domains. 
In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this uncertain semantics into a general framework for pragmatic language understanding -- the Rational Speech Act framework.

To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate. 
In Section 3, we describe experiments the measure both (i) and (ii) and relate it to the endorsements of generalizations about categories, or *generic language*. 
In Section 4, we describe experiments that measure (i) and manipulate (ii) to predict endorsements of generalizations about events, or *habitual language*.
In Section 5, we describe experiments that manipulate both (i) and (ii) to predict endorsements of generalizations about causes, or *causal language*. 
Across all of our experimental settings, we find a very strong agreement of our model's predictions to human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literature on *genericity*.
Our theory also opens up a number of new directions for understanding generic language and building models that learn and think like people.

<!-- ALTERNATIVE INTRO -->

<!-- Yet, generalizations can be hard to acquire. -->
<!-- Consider what it would take to learn that under certain conditions (e.g., when eaten raw) a plant is poisonous, while under other conditions (e.g., when processed appropriately) the plant is nutritious.  -->
<!-- This is a common ecological problem and historical examples suggest that humans are not particularly good at learning such generalizations [e.g., the Australian explorers case; @Henrich2015]. -->
<!-- In this domain, the relationship to be learned (i.e., between different ways of food processing and the poisonousness of the plant) is non-obvious and trial-and-error learning is costly (negative examples entail death). -->

<!-- Crucially, once acquired, such hard-won generalizations can be communicated among humans, something which other animals struggle to accomplish [cite tomasello apes something]. -->
<!-- Generalizable knowledge can be inferred through demonstration, or in pedagogical contexts when ostensive cues are present [@Csibra].  -->
<!-- By and large, however, language provides the most flexible and generative way to communicate generalizations.  -->

<!-- A generalization provides a relation between a category and a property: It tells us to predict that property of future instances of the category [@HumeTHN]. -->
<!-- Generalization can be described as a probability and inductive inference as a probabilistic model [@Tenenbaum2011]. -->
<!-- From a very young age, children make strong inductive inferences from their experience in a way consistent with the Bayesian probability calculus [@Dewar2010; @Gelman1986; @Markman1989]. -->

<!-- If generalizations can be described by predictive probabilities, it would stand to reason that the most direct way to communicate a generalization would be to convey probability.  -->
<!-- Ironically, humans are very bad at describing and interpreting probabilities explicitly [@Tversky1974]. -->
<!-- Rather than be a deficiency, however, the difficulty we have in understanding numerical descriptions of probability might reflect the flexible adaptivity of natural language to make vague or ambiguous that which shared context can be relied upon to guide interpretation [@Piantadosi2012]. -->
<!-- If language has evolved in a way to make efficient the kinds of inductive inferences that are central to human cognition, we would expect the language of generalizations to be simple [c.f., @Leslie2008]. -->

<!-- Indeed, generalizations in language (e.g., *Dogs are friendly*, *Mary smokes cigarettes*, *Yeast makes bread rise*) are among the simplest forms of compositional expressions.  -->
<!-- Generalizations do not come in just one syntactic form: "*Dogs* are friendly", "*A library book* should be treated with respect", "*The contemporary foodie* seeks culinary experinces in menu-less restaurants and grandmothers' kitchens" [@Carlson1995; @NickelBlackwell; @sepGenerics]. -->
<!-- Each of these statements has in common the fact that they predicate a property of a category and the properties themselves apply to instances of the category (unlike, e.g., *Dinosaurs are extinct* because being extinct is not a property that can be true of a particular dinosaur).  -->
<!-- In this way, these statements exhibit *genericity*, or put another way, they convey generalizations. -->

<!-- In this paper, we formalize the language of generalizations with the interest is deciding what makes a generalization in language *true or false*. -->
<!-- How speakers convey generalizations and how listeners interpret them. -->

<!-- We examine three case studies of generalizations in language: Generalizations about agents, objects, and events.  -->
<!-- In Section 1, we introduce an information-theoric communicative theory of how generalizations are conveyed in language and flesh out the model's predictions alongside alternative models. -->
<!-- In order to do so, we provide a unified mathematical framework for dealing with agents, objects, and events, casting each as a category over which generalization can occur. -->
<!-- Our model predicts the endorsements of generalizations should vary with the (A) the probability of an instances having the property and (B) the prior distribution over the property probability (e.g., how likely instances of other categories are to have the property). -->
<!-- In Section 2, we introduce our empirical paradigm which we use to measure endorsement and interpretation of linguisitic generalizations, examining generalizations about *agents* in what is known as *habitual language* (e.g., "Mary smokes cigarettes.").  -->
<!-- In Section 3, we extend our paradigm to generalizations about *events* (i.e., *causal language* e.g., "Yeast makes bread rise.") and experimentally manipulate participants' background knowledge, showing that prior beliefs about probabilities are causally related to endorsement and interpretation of generalizations. -->
<!-- In Section 4, we use our paradigm to address long-standing theoretical and empirical puzzles regarding generalizations about *objects*, so-called *generic language*.  -->
<!-- We show our how model explains three known psychological puzzles surrounding generic language.  -->
<!-- In all case studies, we provide formal comparison to simpler models and in all cases, find that only our communicative theory explains the patterns of empirical data. -->
<!-- We conclude with a general discussion about the relationship of our theory to extant theories in the psychology, linguistics, and philosophy of genericity, and highlight the implications for modeling language acquisition, conceptual development, and other avenues of research that this framework opens. -->

<!-- the truth conditions of generalizations of events (so called *habitual language*) by manipulating the target propensity (A) while surveying a wide variety of events (which should induce variability in B). -->
<!-- In Section 3, we manipulate both (A) and (B) while testing the model on generalizations about causes (*causal language*). -->
<!-- If our theory is truly a theory about communicating generalizations, it should be able to explain the known psychological puzzles surrounding *generic language* (generalizations about categories).  -->

<!-- In stark constrast, a computational understanding of communicating generalizations is not well understood at all.  -->

<!-- Gathering data and observing evidence, however, is costly.  -->
<!-- The human problem of induction even displays a complex sensitivity to not only the type of data, but how the data was generated [@Gweon2010; @Shafto2012]. -->
<!-- A learner cannot form all of her abstract knowledge through direct experience, however. -->
<!-- Life is only so long, and you can only be in one place at a time. -->

<!-- In this paper, we introduce a formal model for understanding the language of generalizations. -->
<!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning. --> -->
<!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning). -->
<!-- We extend a rational model of communication --- the Rational Speech Act theory --- to be able to understand general statements that extend beyond the here-and-now. -->
<!-- We provide a number of stringest tests of this theory to explain generalizations about categories, events, and causal forces.  -->

<!-- How can generalizations in language have such flexible truth conditions while simultaneously carrying intuitive and, at times, very strong implications? -->
<!-- This question has been investigated by psychologists, linguists, and philosophers since @Carlson1977. -->
<!-- Here, we provide a unified formal theory of generalizations conveyed in language. -->
<!-- We test theory on the preeminent case study of linguistic generalizations: generic language, or generalizations about categories. -->
<!--  -->
<!-- To be precise, we develop a computational model that describes pragmatic reasoning about the propensity required to assert the generaization.   -->
<!-- We find that this formalism resolves known philosophical and empirical puzzles. -->
<!--We also provide the first set of experimental results about linguistic generalizations about events and causal forces, so called *habitual* and *causal statements*.-->

<!-- and find extreme flexibility in usage, which our model predicts.  -->

<!-- In Section 2, we conduct a set of experiments to test the *truth conditions* of familiar generalizations about categories (generic statements), and find our model predicts key patterns in human judgments -->
<!-- In Section 3, we conduct a set of experiments to test *interpretations* of novel generic sentences, again finding our model predicts human judgments with high quantitative accuracy. -->
<!-- In Section 4, we begin to test the generality of the theory, examining the *truth conditions* of generalizations about events. -->
<!-- In Section 5, we further probe our theory's generality, investing the *truth conditions* and *interpretations* of novel generalizations about causal forces.  -->
<!-- In all cases, we provide formal comparison to simpler models and in all cases, find that only our communicative theory with an underspecified meaning function explains the pattern of human data. -->
<!-- We also find that the prior beliefs used in our model reflect conceptual structure, and this provides an understanding of the conceptual implications of generics. -->
<!-- Finally, we investigate the underlying semantic scale in more detail, and find that the core meaning of generalizations in language depends in a crucial way on subjective beliefs, not mere frequency. -->

<!--
Most would agree that \emph{Swans are white}, but certainly not every swan is.
This type of utterance conveys a generalization about a category (i.e. \textsc{swans}) and is known as a generic utterance [@Carlson1977; @Leslie2008].
Communicating generically about categories is useful because categories themselves are unobservable [@Markman1989].
Knowledge about categories, while central to human reasoning, is tricky to acquire because categories themselves are unobservable [Markman1989}.
It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are essential to the growth of conceptual knowledge [@Gelman2004] and how kinds are represented in the mind [@Leslie2008].
Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and children as young as two or three understand that generics refer to categories and support generalization [@Cimpian2008].
and though English and many other languages do not possess an unambiguous form devoted to generic meaning [@Behrens2000, @AlMalki2014].
Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@GelmanEtAl2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010motivation].
Despite their psychological centrality, apparent simplicity, and ubiquity, a formal account of generic meaning remains elusive.

How can generics have such flexible truth conditions while simultaneously carrying strong implications?
In this paper, we explore the idea that the core meaning of a generic statement is simple, but underspecified, and that general principles of communication may be used to resolve precise meaning in context. 
In particular, we develop a mathematical model that describes pragmatic reasoning about the degree of prevalence required to assert the generic.  
We find that this formalism resolves the philosophical and empirical puzzles.
-->

# The Bayesian Framework for Generalizations

Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
The linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
We call this kind of statement a *particular*.

```{r table-generalization, results="asis"}
df.tab <- data.frame(
  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
  "Generalization over" = c("Category", "Event", "Cause"),
  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
) #%>% xtable(., 
 #        caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
  #       label = c("tab:genpart"))

apa_table(df.tab, 
          caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
          escape = TRUE, small = TRUE
)

#print(df.tab,  type = "latex", tabular.environment = "tabularx", width = "\\textwidth",  include.rownames = FALSE, comment = F)
```

We can make particular statements about objects, events, and causes.
We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must say exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
In the study of categories and properties, $x$ is an object.
For a behavior exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
In this case, $x$ is a instance of an agent.
Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$: $h = P(x \in e \mid x \in c)$.
We refer to this probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the friendliness of dogs.

$$
P(h \mid d) = \frac{P(d \mid h) \cdot P(h)}{\int_{h'}P(d \mid h') \cdot P(h')}
$$

Our ability to use this updated belief $P(h \mid d)$ in order to make predictions about unobserved instances is a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011].

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent [@Goodman2009].
Quantitative modeling has been crucial in explaining how the subtleties of experience relate to subtleties in generalization [@Tenenbaum2006; @Kemp2008].

Studying generalizations from observational evidence can only take us so far in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

# Communicating Generalizations with a Formal Model

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the formalization described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs (not exactly *most robins*). 
If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.

These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.

The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a dangerous world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which has been empirically verified [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relations can also be expressed like *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations, the statistics can influence generic endorsement.
How do we make sense of this panoply of conditions?
Is there some more general, unified principle that explains what makes generic statements true or false?

Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
The basic currency of inference in these models is probability.
In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement.

\begin{eqnarray}
L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed}
\end{eqnarray}

Equation \ref{eq:L0fixed} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
For an utterance conveying a generalization $u_{gen}$, we adopt a simple threshold semantics:

\begin{eqnarray}
\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
&\propto  &
\begin{cases}
1 & \text{if } h > \theta \\
0 & \text{otherwise}
\end{cases}
\end{eqnarray}

The $\delta_{\denote{u}(h, \theta)}$ likelihood is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?
We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
We assume this prior is uninformed: $\theta \sim \text{Uniform}(0, 1)$.

\begin{eqnarray}
L(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
\end{eqnarray}

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
"Some" rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
If the threshold is very high, only the highest $h$ would pass the threshold.
If the threshold is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold takes on lower and lower values, more and more probabilities would surpass it.
When the threshold is very low, almost all probabilities are consistent with it (akin to "Some").
When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

In this paper, we are interested in explaining the variable endorsements of generalizations based on some known or believed probability $h$.
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).
\begin{equation} 
S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
\label{eq:S1}
\end{equation}

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model generic endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

\begin{equation*}
\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
1 &\text{for all h}\ 
\end{cases}
\end{equation*}

Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[
A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate.
Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind. 
In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution: 
$U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
]

<!-- This decision is based on whether or not the generalization would accurately convey the $h$ -->
<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq. \ref{eq:L0}).  -->

<!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } -->

<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.  -->
<!-- \begin{equation} -->
<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
<!-- \label{eq:utilS1marginalization} -->
<!-- \end{equation} -->
<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
<!-- ] -->
<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->

<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g., *Mosquitos carry malaria*; *Robins lay eggs* v. *Robins are female*). -->

<!-- Abstract mental representations, then, may thus be influencing generic endorsement via its influence on subjective probability. -->

<!-- To understand how generalizations are conveyed in language, we start by considering general purpose language understanding principles. -->
<!-- Foremost, understanding language depends upon assumptions interlocutors make about each other and can exhibit a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000]. -->
<!-- Though once viewed as a wastebasket in which to dump unexplained loose ends in service of more rigorous formal analysis, *pragmatics* --- or language understanding in context --- has seen an emergence of formal frameworks that connect closely with behavioral data [@Franke2015]. -->

<!-- One dominant framework --- the Rational Speech Act theory --- has had considerable success in providing a formal account of pragmatic language phenomena [i.e., interactions between language and context; @Goodman2016]. -->
<!-- This framework has been used to explain, in precise mathematical terms, how it is that utterances like "some of the kids failed the test" are interpreted to mean "some (but not all) of the kids failed the test" [@Goodman2013], how "I waited a million years to get a table" is interpreted as "I waited an obnoxiously long time to get a table" [@Kao2014], how "John is tall" can mean John is 5'4" is John if a 12-year-old but means John is 6'2" if he is 24-years-old [@Lassiter2015], and how "Your talk was fine" can be a polite way of saying your talk was less than fine [@Yoon2016].  -->
<!-- Computational modeling has pushed our understanding of these complex linguistic phenomena, but so far, rational models of language use have focused on *specific* statements: utterances that convey information about a particular entity or situation.  -->
<!-- A formal theory of statements that convey generalizations about entities or situations ---  statements that extend beyond the here-and-now --- has remained elusive. -->

<!-- Formalizing the meaning of linguistic expressions requires specifying *truth conditions*, or the states of the world in which the expression is true vs. false. -->
<!-- Using the tools of formal semantics, we specify a *truth function*: A function from states of the world to truth-values.  -->
<!-- A simple truth function for a generalization could be a threshold on an agent's posterior probability: $\denote{u_{generalization}}(h, \theta): \{ h: h > \theta\}$, where $\denote{u_{generalization}}$ represents a function from a state of the world $h$ and a threshold variable $\theta$ to the set of the states of the world where $h > \theta$.  -->
<!-- Applying this function to a set of worlds returns a set of worlds that are consistent with $h > \theta$. -->

<!-- Though intuitively appealing and simple, this threshold-based truth function for a generalization is problematic. -->
<!-- <!-- fixed value of $\theta$ seems unlikely. --> -->
<!-- The generalization *Mary smokes cigarettes* suggests a daily-habit (e.g., $h > \text{once a day}$), while *Bill writes poems* implies something much weaker, perhaps a poem every few weeks (e.g., $h > \text{once a month}$. -->
<!-- *Drinking moonshine makes you go blind* and so does *staring at the sun*, but neither causal statement tells you to precisely the increased relative risk. -->
<!-- *Mosquitos carry malaria* is a true statement despite the prevalence of carrying malaria among mosquitos being a just a fraction of 1\%, while *Ducks are female* might seem like a weird thing to say, even though the rate is much higher than the malaria-carrying mosquitos. -->
<!-- Finally, *Ducks lay eggs* is a good generalization, though the rate is the same as *Ducks are female*. -->
<!-- The meaning of generalizations, it seems, cannot reduce to a single, precise quantitative statement; this is the major stumbling block to providing a formal account of genericity [@Carlson1977; @Leslie2008; @NickelBlackwell]. -->

<!-- We hypothesize the simple threshold-based truth function for lingusitic generalizations can be rescued by positing an *underspecified* meaning.  -->
<!-- That is, we adopt a threshold semantics as described above, but imagine that $\theta$ is not a fixed property of language but rather is drawn from a prior probability distribution. -->
<!-- In this formulation, listeners infer thresholds along with speakers' intended meanings in context. -->
<!-- We formalize this hypothesis with a "literal listener" model from the Rational Speech Act framework [@Frank2012; @Goodman2013; @Goodman2016]. -->

<!-- *Bills writes poems* might true if Bill does it a few times a year, while we might be hesitant to say *Mary smokes cigarettes* if she only does it once every few months. -->
<!-- *Ducks lay eggs* is true despite only the female ducks laying eggs, while *Ducks are female* is strange to say (even though only the females are female). -->

<!-- The language of generalizations is so simple that it appears everywhere in human conversation (*Movie theaters are cold.*), pedagogy (*The blicket makes the machine play music.*), political and scientific discourse (*The President peddles falsehoods.*, *Psychology experiments don’t replicate.*), stereotypes (*Boys are good at math*), motivation (*Big girls eat their broccoli!*), emotion-regulation  (*Accidents happen.*), child-directed (*Mommy works late*) and child-produced speech (*Slides aren't for grown-ups!*), and many other facets of experience [@GelmanEtAl2004; @Gelman2008; @Cimpian2010motivation; @Rhodes2012]. -->

<!-- Though the language of generalizations is found everywhere and in every language [@Behrens2005; @Carlson1995], the meaning of such linguistic expressions is philosophically puzzling and has resisted precise formalization. -->
<!-- Intuitively, generalizations should convey something about the probability of an instance of the category to have a property, but exactly what is conveyed is unclear. -->

<!-- What if we leave the $\theta$ underspecified in the semantics? -->
<!-- That is, what would a listener believe if she drew $\theta$ from an uninformed prior belief distribution: $P(\theta)$?^[ -->
<!-- Previous attempts have been made to salvage this threshold semantics, using a semantic a technique called "domain restriction", wherein the scope of generalization is restricted to a smaller subset of entities or instances [e.g., "only female ducks"; @Cohen1999].  -->
<!-- Though effective at dealing with at least some of these semantic puzzles, this approach leaves unresolved why the domain should be restricted in some cases and not others. -->
<!-- We return to this more fully in the General Discussion. -->
<!-- ] -->

<!-- [MHT: talk about soft semantics here?] -->

<!-- \begin{eqnarray} -->
<!-- L_{0}(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0} -->
<!-- \end{eqnarray} -->

<!-- The threshold $\theta$ is assumed to be drawn by an uninformative prior distribution, defined on the same scale as the probability $h$: $\theta \sim \text{Uniform}(0, 1)$.^[ -->
<!-- Though it's plausible that different thresholds could be learned for different domains, we assume an uninformed prior distribution in our model to show how background knowledge about how the world works drives inferences. -->
<!-- ] -->
<!-- Finally, the prior distribution $P(h)$ is a distribution over the degrees of probability. -->
<!-- The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenabum2006; @Kemp2008]. -->
<!-- This is a simple Bayesian model of interpreting a statement conveying a generalization. -->

```{r simluationsModel, eval = T, cache = T}

l0.model <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaPrior = Infer({model: function(){
 return uniformDraw([
   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 ])}
});

var bins = [
  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}

var mixture = data.prior.mix[0];
var priorParams = data.prior.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});

var listener0 = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var state_prior = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }})}, 10000)

var continuousListener0 = function(utterance) {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
//    var theta = uniform(0,1)
    factor(
    (utterance == "generic") ? 
      Math.log(state) : 
    (state > 0.017) ? 0 : -Infinity
    )
    return {
      state_Posterior: state, 
      state_Prior: state_prior
  }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}

//var out = {generic: listener0("generic"), some: listener0("some")}
//out
continuousListener0(data.utt[0])
'

priorNames <- c(
  "uniform", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria"#,
 # "areSick"
  )
priorShapes <- list(
  uniform =  list(params = data.frame(a = 1, b = 1), mix = 1), 
  #uniformRare =  list(params = data.frame(a = 1, b = 1), mix = 0.4), 
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  #eatsFood =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  #areSick =  list(params = data.frame(a = 1, b = 5), mix = 1), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

all.simulations <- data.frame()
for (p in priorNames){
  for (u in c("generic", "some")){

    inputData = list(prior = priorShapes[[p]], utt = u)
    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")

    # all.simulations <- bind_rows(all.simulations,
    #                         bind_rows(
    #                           data.frame(l0.rs$generic) %>%
    #                             gather(key, val, -probs) %>%
    #                              group_by(key, val) %>%
    #                              summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                               mutate(key = gsub("support.", "", key)) %>%
    #                              separate(key, into = c("Parameter","Distribution")) %>%
    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
    #                           data.frame(l0.rs$some) %>%
    #                             gather(key, val, -probs) %>%
    #                             group_by(key, val) %>%
    #                             summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                             mutate(key = gsub("support.", "", key)) %>%
    #                             separate(key, into = c("Parameter","Distribution")) %>%
    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
    #                             filter(Distribution != "Prior"),
    #                           data.frame(l0.rs$most) %>%
    #                             gather(key, val, -probs) %>%
    #                             group_by(key, val) %>%
    #                             summarize(prob = sum(probs)) %>%
    #                             ungroup() %>%
    #                             mutate(key = gsub("support.", "", key)) %>%
    #                             separate(key, into = c("Parameter","Distribution")) %>%
    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
    #                             filter(Distribution != "Prior")
    #                         ) %>%
    #                           mutate(PriorShape = p)
    # )
      all.simulations <- bind_rows(all.simulations,
                                   l0.rs %>%
                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
                                  %>%
                              mutate(PriorShape = p, utterance = u)
    )
  }
  #print(p)
}
```

```{r simulations, fig.width = 8, fig.height=5}
all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
  mutate(Distribution = factor(Distribution, levels = 
                             c("Prior_some", "Posterior_Generalization_some", "Posterior_Generalization_generic"),
                                labels = c("Prior/Silence", "Some", "Generalization")),
         PriorShape = fct_relevel(PriorShape, "uniform", "barks","laysEggs","carriesMalaria","isFemale"
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         ) %>%
  ggplot(., aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = Distribution, fill = Distribution))+
    geom_density(#stat= 'identity', 
                aes(y = ..scaled..),
                 size = 0.6, alpha = 0.7, adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    #scale_color_solarized()+
    #scale_fill_solarized()+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   scale_fill_manual(values = c("#636363", "#2b83ba","#d7191c"))+
    scale_color_manual(values = c("#636363","#2b83ba", "#d7191c"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    xlab("Degree of propensity (probability)") +
    ylab("Probability density") +
  facet_grid(PriorShape~Distribution, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq. \ref{eq:L0}).  -->

<!-- <!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } --> 
<!-- \begin{equation}  -->
<!-- S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h)  } -->
<!-- \label{eq:S1} -->
<!-- \end{equation} -->

<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda$. -->
<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.  -->
<!-- \begin{equation} -->
<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
<!-- \label{eq:utilS1marginalization} -->
<!-- \end{equation} -->
<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
<!-- ] -->
<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->

## Alternative formulation

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold meaning for a generalization. 
The Rational Speech Act framework defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
For the most basic formulation of an RSA model, the level of recursion for a model can be unidentifiable from the 
"speaker optimality" model parameter in Eq. \ref{eq:S1} [@FrankEtAlUnderReview].
For our model, with an uncertain threshold variable, theoretically meaningful different models can be formulated in the pragmatic framework.

For example, @Lassiter2013 modeled vagueness and the context-sensitivity of gradable adjectives using a similar underspecified threshold semantics. 
In that work, the authors argued that understanding adjectives required a "pragmatic listener" [i.e., a listener who thinks about a speaker who thinks about a listener; @Lassiter2015]. 
In their model, the threshold variable was "pragmatically lifted", meaning the uncertainty over the threshold variable was resolved using pragmatic reasoning [a so-called uRSA model; @Goodman2016].
In the case of our model of generalizations, we can compare the simple model we described above to a more sophisticated model that resolves the threshold using pragmatic principles.

### Listener models

Eq. \ref{eq:L0} describes how a naive Bayesian agent should update her beliefs about the probability after hearing an utterance conveying a generalization. 
This listener model is not pragmatic because it doesn't reason about the generative process of the utterance (i.e., it doesn't reason about a speaker). 
Eq. \ref{eq:L1u} extends this model adding a level of recursion, modeling a pragmatic listener who reasons about the Gricean speaker in Eq. \ref{eq:S1} who reasons about the literal listener in Eq. \ref{eq:L0}.

\begin{eqnarray}
L_{1}(h \mid u) &\propto& S_{1}(u \mid h) \cdot P(h) \label{eq:L1u}
\end{eqnarray}

This $L_1$ model reasons about the conditions under which the speaker $S_1$ would produce one or another speech act (here, the generalization or staying silent), described above.
Still, the threshold variable gets resolved by $L_0$ (and marginalized out by $S_1$): The posterior distribution over thresholds is arrived at by $L_0$ trying to make the generalization true.
<!-- \mht{How does this posterior on states differ?} -->

Truthfulness is not the only process that could help set $\theta$.
If the listener were to reason about what threshold was likely to be *used by the speaker*, informativity would also help set $\theta$.
This can be modeled by a pragmatic listener who reasons about the threshold, but assumes the speaker had a particular threshold in mind (Eq. \ref{eq:S1l}).

\begin{eqnarray}
L_{1}(h, \theta \mid u) &\propto& S_{1}(u \mid h, \theta) \cdot P(h) \cdot P(\theta) \label{eq:L1l} \\
S_{1}(u \mid h) &\propto &\exp{(\lambda \cdot U(u; h; \theta)  } \label{eq:S1l} \\
U(u; h; \theta)& =& \ln{  L_0(h \mid u, \theta) } - C(u) \label{eq:utilS1nomarginalization} \\
L_{0}(h \mid u, \theta) &\propto& {\delta_{\denote{u}(h, \theta)}} \cdot P(h) \label{eq:L0l}
\end{eqnarray}

Eq. \ref{eq:L1} is mathematically equivalent to the gradable adjectives model of @Lassiter2013, with the modification that states of the world are defined with respect to the probability $h$ under discussion.
In this model, the listener's posterior distribution on thresholds is arrived at by trying to make the utterance conveying the generalization to be both truthful and informative. That is, the listener must believe the threshold used by the speaker is both true and informative; very low thresholds could only be informative in contexts when the listener believes most probabilities are all very low *a priori*.

These alternative pragmatic listener $L_1$ models give rise to corresponding alternative pragmatic speaker models.

### Speaker models

We can define two speaker models who reason about the two different pragmatic listeners.

The speaker who reasons about the pragmatic listener in Eq. \ref{eq:L1u} is defined by a utility function similar to Eq. \ref{eq:utilS1nomarginalization}, but with informativity computed with respect to $L_1$'s posterior distribution rather than $L_0$.

\begin{eqnarray}
S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h; \theta)  } \label{eq:S1li} \\
U(u; h; \theta) = \ln{  L_1(h \mid u) } - C(u) \label{eq:utilS2nomarginalization} \\
\end{eqnarray}

The model who reasons about the pragmatic listener in Eq. \ref{eq:L1l} marginalizes over $L_1$'s posterior distribution on the threshold $\theta$ in order to decide which utterance to produce (similar to \ref{eq:utilS1marginalization}).

\begin{eqnarray}
S_{2}(u \mid k) \propto \exp{(\lambda_2 \cdot U_{S_2}(u; k)  } \\ 
U_{S_2}(u; h) = \ln{ \int_{\theta} L_1(h, \theta \mid u)}  \diff \theta - C(u) \label{eq:S2l}
\end{eqnarray}

All models were implemented in the probabilisitic programming language WebPPL [@dippl], and a complete, runable versions of the models in the following section can be found at \url{http://forestdb.org/models/generics.html}

## Model simulations

All of the RSA models defined in the previous section predict that the interpretation and endorsement of a generalization depends listener's *a priori* beliefs about the probabilty in question $P(h)$.
Qualitatively, the predictions of the different formulations of the RSA models for understanding generalizations are not appreciably different (though their quantitative predictive flexibility is).
For purposes of illustration, we present present predictions of the simplest model with an underspecified threshold and a model where the threshold is fixed to 0 (corresponding intuitively to *some* statements).

Before, we described how an underspecified threshold interacts with a uniformly uncertain belief about the probability.
Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
Our model of endorsements is a model of speaker who decides whether or not to say the generic or stay silent. 
Thus, qualitatively model predictions for endorsement can be gleaned by comparing the prior distribution over the probability $h$ (which is the same as posterior upon hearing "silence") with the posterior distribution over $h$ upon hearing the generalization.

In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
Here, we show the prior is bimodal with peaks at 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have 0\% prevalence) and for those that do have members that bark, many of them bark (i.e., have some high prevalence value).
The fact that "those that do not bark" is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who does not usually bark (say, a cat) could somehow have the feature (e.g., due to some transient or accidental state).
We see that the quantifier "Some" (middle row) struggles to differentiate those that accidentally do have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.
Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.

The strength of a listener's inference (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over the prevalence of the feature.
Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than with "barks" prior: The listener thinks that about 50% of robins lay eggs.
Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
The intuitive differences in the endorsements of these statements comes from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content.

Finally, we look at how a listener would interpret the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
Indeed, we see that for the prior over "carries malaria", which *a priori* assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread, the listener's posterior upon hearing the generalization is similar to what she learns about hearing "Some mosquitos carry malaria". 
Thus, a speaker who believes "some but very few" mosquitos carry malaria will still endorse the generalization.

In the rest of this paper, we examine the validity and generality of this theory of communicating generalizations through three case studies: generalizations about categories, events, and causes.

<!-- Consider how an uniformly underspecified threshold would interact with a uniformly uncertain belief about a probability (recall the thresholds defines what probabilities or states of the world should be ruled out).  -->
<!-- If the threshold is very high, only the highest probabilities would be left (i.e., pass the threshold). -->
<!-- If the threshold is slightly lower but still high, the highest probabilities would still pass the threshold, as would some that are slightly lower. -->
<!-- As the threshold takes on lower and lower values, more and more probabilities would surpass it. -->
<!-- When the threshold is very low, almost all probabilities are consistent with it. -->
<!-- But since we don't know *a priori* what the threshold is likely to be, each of theses situations is plausible. -->
<!-- The posterior distribution on probabilities or states of the world will favor higher probabilities (because they pass more thresholds), but will still include probabilities that are quite low [though they are *a posteriori* unlikely; see Figure \ref{fig:simluations} ].  -->
<!-- Speakers, thus, will produce generalizations with some probability in each state of the world, though the speaker will say the generalization more often when the propensities associated with the states of the world are higher [see Figure \ref{fig:simluations}]. -->

<!-- - Figure -->
  <!-- - Subfigure 1 [width = 0.2] (Uniform priors) [two rows, left subfigure] -->
  <!--   -- Basic L0 posteriors on degrees for uncertain, fixed at 0 and fixed at 0.5 -->
  <!--   -- Basic S1 posteriors on utterances, for prevalence 0 - 1 (and for fixed thresholds) -->
  <!-- - Subfigure 2 [width = 0.8] (L0 vs. L1 lifted vs. L1 unlifted x 4 priors x {speaker, listener} ) [model as color, lty; priors as columns x {speaker, listeners} as rows]  -->
  <!--   -- priors = [uniform, n-shaped, u-shaped, mixture model / maybe put more in appendix: rare, accidental, female, eggs] -->

<!--
mht: is it possible to construct priors in causals that would reflect the qualitative prediction shown here?
-->

<!-- $P(x)$ is a distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across animal categories.  -->
<!-- In Figure \ref{fig:schematic-unif}, are $L_1$ (Eq.~\ref{eq:L1}) posterior prevalence distributions on $x$ (red solid line) for several example prior prevalence distributions $P(x)$ (blue dashed line), as well as the $S_2$ generic endorsement probability for different levels of prevalence. -->
<!-- We name these example prior distributions to suggest properties that might be associated with such priors.  -->
<!-- (Later, we will empirically measure these priors for properties of interest.) -->
<!-- First, we explore generic interpretation and endorsement for priors of three different shapes (left column).  -->
<!-- For each of these, the $L_1$ posterior distribution (red solid) over prevalence is heavily driven by the prior (blue dashed). -->
<!-- $S_2$ endorsement probabilities for the generic (black solid) increase as a function of prevalence, and what counts as "true" (in terms of the prevalence) depends on the prior.  -->

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/schematics_s2.pdf} -->
<!--     \caption{Schematic prior distributions for prevalence $x$ (blue dashed), the pragmatic listener $L_1$ model's posterior distribution over prevalence upon hearing a generic utterance (red), and speaker $S_2$ model's endorsement of a generic utterance for different levels of prevalence (black). -->
<!--     The names given to these priors are meant to be suggestive of what kinds of properties these distributions might correspond to. -->
<!--     The left column uses prevalence priors modeled as Beta(15,15), Beta(4,1), and Beta(4,16) distributions. -->
<!--       The right column uses a prior distribution that is a mixture of the distribution to the left of it with a second component, modeled as Beta(0.5, 4.5), reflecting categories with 0\% property prevalence. -->
<!--     Horizontal dashed line at 0.5 is for convenience of comparing the point at which an utterance becomes judged as more true than false for $S_2$. -->
<!-- 	Note that the prior distribution over prevalence will be the same as $L_1$'s posterior distribution upon hearing the "null" utterance. -->
<!--     } -->
<!--   \label{fig:schematic-unif} -->
<!-- \end{figure} -->

<!-- To take one example, consider the distribution over what might be the property "are female" (top-left facet). -->
<!-- The \emph{a priori} prevalence is centered around 0.5. -->
<!-- Because of pragmatics, the pressure to be \emph{truthful} will drive likely threshold values below 0.5 (lower values are more likely to be true).  -->
<!-- At the same time, the pressure to be \emph{informative} will drive the threshold values up: Higher values are more likely to be informative.  -->
<!-- The result is a posterior over prevalence that is only marginally greater than the prior, making higher prevalence values more likely after hearing the generic.  -->
<!-- But the relative information gain is very little (the posterior is not very different from the prior), and thus the $S_2$ model is reluctant to endorse the generic unless the property is exceedingly prevalent.  -->
<!-- The same basic phenomenon can be observed for the other two example priors (left column): The posterior over prevalence heavily depends upon the prior, but is also not very different from the prior. -->

<!-- We now imagine what would happen if there were some kinds where the property was completely absent, while being present at some rate in other kinds. -->
<!-- Figure \ref{fig:schematic-unif} (right column) shows this possibility: mixing the distribution to the left of it with a second component at 0\% prevalence. -->
<!-- Consider the schematic prior over "lay eggs". -->
<!-- We see the pragmatic listener $L_1$'s posterior prevalence distribution is not very different from the interpretation that doesn't include the second component in the prior (here, "are female"), but it is dramatically different from the prior with two components (compare red with blue dashed line for the right column). -->
<!-- This suggests that when many categories have 0\% prevalence, lower thresholds are informative.  -->
<!-- Indeed, the $S_2$ model predicts that the generic becomes felicitous at lower prevalence levels (compare black line of left v. right column). -->
<!-- For "lay eggs", when the property is prevalent in 50\% of the kind (e.g., 50\% of birds lay eggs), endorsement of the generic (e.g., \emph{Birds lay eggs}) by the $S_2$ is roughly 0.85; for "are female", with the same prevalence (50\% of birds are female), endorsement for \emph{Birds are female} is only 0.50: It is judged to be neither true nor false.  -->
<!-- The important result is the asymmetry: the first generic can be endorsed more strongly than the second, at the same prevalence level; the exact endorsement rates depend on quantitative aspects of the priors, which must be determined empirically. -->

<!-- The model thus predicts differences in truth judgments depending on the prevalence prior.  -->
<!-- The first test of our theory, then, will be to see if these predictions correspond to human truth judgments of familiar generic sentences.  -->

<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
<!-- \begin{eqnarray} -->
<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
<!-- \end{eqnarray} -->
<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->

<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->
<!-- In this model, a threshold $\theta$ is established in context by a Bayesian listener reasoning about what threshold would make this utterance true? -->

<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
<!-- \begin{eqnarray} -->
<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
<!-- \end{eqnarray} -->
<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->

<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise. -->
<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->

<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
<!-- \begin{eqnarray} -->
<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
<!-- \end{eqnarray} -->
<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->

<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the propensity: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
<!-- The prior distribution $P(h)$ is a distribution over likely degrees of propensity.  -->
<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->

<!-- Life is only so long, however, and a person can only be in one place at a time. -->
<!-- The amount of data we can gather about any particular category, event, or causal force is extremely limited by these physical constraints. -->
<!-- Thus, it would be useful if language provided a simple way to communicate these generalizations to one another. -->

<!-- # A Formal Theory of Generalizations in Language -->

<!-- We find both the statistical and conceptual accounts compelling, but an important perspective is missing. -->
<!-- Linguistic generalizations are not unique in their flexibility. -->
<!-- Understanding language in general depends upon assumptions interlocutors make about each other and what content is under discussion.  -->
<!-- Viewing language understanding as a social reasoning process reveals that utterances carry a mosaic of interpretations with a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000].  -->
<!-- Can the puzzles of generic language be understood as effects of pragmatic reasoning? -->
<!-- If so, we may be able to get away with a relatively simple, statistical,  semantic theory. -->
<!-- Abstract mental representations, then, may be the conceptual backdrop against which generic language is interpreted.  -->

<!-- We pursue such a line of inquiry, assuming the simplest truth-conditional meaning: a threshold on prevalence $P(F\mid K)>\theta$ [c.f., @Cohen1999]. -->
<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g. \emph{Mosquitos carry malaria}; \emph{Robins lay eggs} v. \emph{Robins are female}),  -->
<!-- so instead we allow this threshold to be established in context through pragmatic reasoning. -->
<!-- Such an inference would depend on background knowledge about properties and categories---potentially structured, conceptual knowledge. -->
<!-- This inference, nonetheless, is a general mechanism of understanding language, not specific to interpreting generic statements. -->
<!-- We formalize this hypothesis in the Rational Speech Act (RSA) theory---a formal, probabilistic theory of language understanding. -->
<!-- RSA is derived from social reasoning, formalized as recursive Bayesian inference between speaker and listener [@Frank2012; @Goodman2013; @Goodman2016; see also, @Franke2009; @Franke2015]. -->
<!-- @Goodman2016 provides a good introduction to the RSA framework and Appendix A presents a brief tutorial on RSA for the reader unfamiliar. -->

<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
<!-- \begin{eqnarray} -->
<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
<!-- \end{eqnarray} -->
<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
<!-- The prior distribution $P(x)$ is a distribution over likely states of the world.  -->
<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->
<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise. -->
<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->

<!-- To understand how language is interpreted pragmatically, we model a pragmatic listener $L_1$ who updates her prior beliefs $P(x)$ by reasoning about the generative process of the utterance, the speaker model $S_1$. -->
<!-- \begin{eqnarray} -->
<!-- L_{1}(x , \theta \mid u) &\propto& S_{1}(u \mid x, \theta) \cdot P(x) \cdot P(\theta) \label{eq:L1} -->
<!-- \end{eqnarray} -->
<!-- Following @Lassiter2013, we model the pragmatic listener as having uncertainty about the threshold: $P(\theta)$. -->
<!-- Though the listener doesn't know the threshold *a priori*, she resolves the threshold (i.e., the meaning) in context by integrating her prior beliefs $P(x)$ with the basic principles of communication to be truthful and informative, instantiated in her model of the speaker $S_1$ [@Lassiter2015; @GoodmanLassiter]. -->
<!-- In principle, thresholds could be learned over time for different contexts, but here we assume the listener has no informative knowledge about the semantic variable $P(\theta) = \text{Uniform([0, 1])}$. -->
<!-- The pragmatic listener $L_1$ (Eq. \ref{eq:L1}) is thus a model of *generic interpretation*: Upon hearing a generic, how should a listener update her beliefs? -->

# Case Study 1: Generic Language

Generalizations about categories (i.e., *generic language*) have received substantial interest in psychology for their role in concept formation [@Gelman2004] and stereotype propogation [@Rhodes2012].
Generic language (e.g., *Birds fly.*) exhibits substantial flexibility in meaning and truth conditions as described above.
<!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
<!-- Unlike universals, however, generics are resilient to counter-examples (e.g., *Birds fly* seems true even in the face of flightless birds like kiwis or penguins). -->
<!-- *Most* birds fly seems more reasonable, and yet most mosquitos *do not* carry malaria while *Mosquitos carry malaria* seems like a true statement. -->
<!-- Finally, the probability of a bird being female is much higher than the probability of a mosquito carrying malaria, but *Birds are female* seems weird to say. -->
<!-- *Birds lay eggs*, however, is fine, even though the rate is the same as *are female* (only females lay eggs). -->

<!-- Empirical work done on category generalizations has elucidated another puzzling phenomenon. -->
<!-- Generic statements often imply the property is widespread in the category [e.g., *Swans have hollow bones* implies something much stronger than *Some swans have hollow bones*; @Gelman2002; @Cimpian2010; @Brandone2014]. -->
<!-- This characteristically strong interpretation interacts with the indeterminacy in truth conditions, resulting in an *asymmetry* between endorsement and interpretation. -->
<!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->

As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties and show how it systematically predicts endorsements of familiar generic statements (Expt. 1).
In Experiment 3, we replicate and extend a paradigm used by @Cimpian2010 to demonstrate the asymmetry between endorsements and interpretations and find that a similar pattern is predicted by our model.

We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data.
Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.

<!-- Interpreting the generic as meaning "most" (i.e. \emph{Most swans are white}) captures many cases, but cannot explain why \emph{Robins lay eggs} and \emph{Mosquitos carry malaria} are so intuitively compelling: Only adult female robins lay eggs and a very tiny fraction of mosquitos actually carry malaria. -->
<!-- Indeed, it appears that any \emph{truth condition} stated in terms of how common the property is within the kind violates intuitions. -->
<!-- Consider the birds: for a bird, being female practically implies you will lay eggs (the properties are present in the same proportion), yet we say things like \emph{Birds lay eggs} and we do not say things like \emph{Birds are female}. -->

<!-- One case study in the language of generalizations is about category generalizations. -->
<!-- Category generalizations, called *generic statement*, has been studied extensively in cognitive and developmental psychology: *generic* statements, or generalizations about categories. -->

<!-- These *strong implications* might underly stereotype formation in social categories [@Rhodes2012]. -->
<!-- In addition to the flexibility in truth conditions, two phenomena have been noted.  -->
<!-- The case of *Mosquitos carry malaria* suggests the utterance must in some way be analogous to the quantifier "some" (e.g., *Some mosquitos carry malaria*).  -->
<!-- Generic language, however, is often interpreted as implying the property is widespread: *Swans have hollow bones* means something different than *Some swans have hollow bones* [@Gelman2002]. -->

<!-- These three phenomena---flexible truth, strong interpretations, and evidence exaggeration---have confounded all formal models aimed to capture the meaning of generalizations in language. -->
<!-- Informal theories have argued that the nature of concepts and their relations are inextricably tied to their linguistic expression [@Leslie2007; @Prasada2013]. -->
<!-- Formal theories have limited themselves to a measurable quantitative degree (e.g., how prevalent a property is in a category), which, in isolation, is difficult to reconcile with the extreme flexibility of generic language. -->
<!-- Here, we present a theory formalizing the inuition that the core meaning of a linguistic generalization is simple, but underspecified, and that general principles of communication may be used to resolve the precise meaning in context.  -->
<!-- This theory inherently relies upon measurable quantities (i.e., prevalence) but situates it within a Bayesian agent with potentially structured prior knowledge, providing a bridge to conceptual theories.  -->
<!-- We find that this formalism (and not simpler ones) explains all three empirical puzzles. -->

<!-- When interpretations are compared directly against truth conditions (i.e., how prevalent a property would need to be for the generic to be true),  -->

<!-- Three empirical phenomena make generalizations in language difficult to formalize. -->
<!-- The conditions under which a generalizations becomes "true" are variable: -->

<!-- Existing work in both adults and children suggests that choosing to communicate a generalization can be used to exagerate evidence [@Cimpian2010; @Brandone2014]. -->

<!-- In addition to having manifold interpretations, what makes linguistic generalizations true or false (i.e., their truth conditions) is also a mystery. -->
<!-- The statement *Birds lay eggs* is true even though only about half of them do (namely, the females). -->
<!-- Half of birds are also female, and yet *Birds are female* sounds like a strange thing to say. -->
<!--  while *Canadians are right-handed* is also weird, even though the vast majority of them are.  -->

## Experiment 1: Endorsing generalizations about categories

Any theory of generic language must explain their puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g. \emph{Ducks have wings.}), minority (e.g. \emph{Robins lay eggs.}), striking (e.g. \emph{Mosquitos carry malaria.}), false generalization (e.g. \emph{Robins are female.}), and false (e.g. \emph{Lions lay eggs.}).
In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we first measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that this prior distribution encodes probabilities associated with deeper conceptual knowledge [e.g., of the kind discussed by @Prasada2013].
This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada; @Gelman; @Leslie].
If, indeed, there are such things as different types of kind--property relations (e.g., *principled* v. *accidental relations*), we would expect the prevalence prior data to follow a multi-modal, mixture distribution where different modes or components of the prior are the results of the different types of relations.
As a simple of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

After exploring the prevalence prior, we move on to the issue of primary theoretical interest: How well our *simple but underspecified* hypothesis accounts for endorsements of generic sentences (Expt. 1b).

### Experiment 1a: Measuring the Prevalence Prior for Categories

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, imagine your favorite kind of animal.
Then answer, "what percentage of that kind of animal is female?".
The answer is probably 50\%. 
Then ask yourself, "what percentage of that kind of animal lays eggs?".
Depending on what animal you thought of, the answer is probably either 50\% or 0\% (e.g., lions, tigers, and bears each have 0\% egg-laying members).

This decomposition of the prevalence prior $P(h)$ into a kind prior $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
We then ask whether a structured, prior model accounts better for this data than an unstructured model.

#### Method

##### Participants

We recruited 60 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
3 participants were accidentally allowed to complete the experiment for a second time; we excluded their second responses (resulting in $n=57$).
2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
The experiment took about 10 minutes and participants were compensated \$1.00.

##### Procedure and materials

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories (randomly sampled from a set corresponding to the generic sentences used in Expt. 1b (e.g. \textsc{robins, mosquitos}) and asked to generate five of their own.

A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix).
The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.

### Bayesian analysis

We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge
We formalize this hypothesis using a simple, Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two distinct components, for example, if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not [@Griffiths2005].
In this task, participants give responses in the form of numbers between 0 and 100 (or, rescaled to be between 0 - 1).
The canonical prior for generating numbers between 0 - 1 is the Beta distribution.

We then assume the data, for each item independently, was generated from one of two distributions: a distribution corresponds to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ as we explicitly posit a left-skewed "transient" distribution.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with some weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \alpha, \beta) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.

We put priors over the latent parameters of this model and infer their credible values by way of Bayesian infernence.

\begin{eqnarray}
\theta & \sim & \text{Uniform}(0, 1) \\
\alpha & \sim & \text{Uniform}(0, 100) \\
\beta & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

To see how well this data-analytic model fits the prevalence prior data, we can use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.

```{r generic-endorsement-priors, eval = F}
d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

genericEndorsementPriorModel <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)

var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  //var a = uniformDrift({a:0, b: 100, width:5});
  //var b = uniformDrift({a:0, b: 100, width:5});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })

  var marginalPrevalence = sample(flip(phi) ? stableComponent : transientComponent)
  return {g, d,phi, marginalPrevalence}
}
'
marginal.prevalence <- data.frame()
m.gen.endorse.priors.summary <- data.frame()

for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
  m.gen.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
         model_var = "model", inference_opts = list(method = "MCMC", samples = 1000, burn = 500, verbose = T))

  marginal.prevalence <- bind_rows(marginal.prevalence, 
                                   m.gen.endorse.priors %>% 
                                     filter(Parameter == "marginalPrevalence") %>%
                                     mutate(Property = p))

  m.gen.endorse.priors.summary <- bind_rows(m.gen.endorse.priors.summary,
                                            m.gen.endorse.priors %>% 
                                              mutate(Property = p) %>%
                                              group_by(Property, Parameter) %>%
                                              summarize(MAP = estimate_mode(value),
                                                        cred_upper = hdi_upper(value),
                                                        cred_lower = hdi_lower(value))
                                              )
  #print(p)
}

```
```{r, eval = F}

ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")

```

### Results

The prevalence prior data is indeed structure.

We also see tremendous variability in the shapes of these prevalence distributions.

<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.  -->
<!-- Do a BDA to describe the data in a more compact form. -->
<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq. \ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).  -->
<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content. -->
<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.  -->
<!-- Some properties have priors that are unimodal with low variance (e.g. \textsc{is female}); these properties are present in every kind in almost exactly the same proportion. The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.  -->
<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->

### Experiment 1b: Endorsing generic statements

Having measured the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) in addition to target-category prevalence (e.g., how many robins lay eggs; Expt. 1a), our speaker model (Eq. \ref{eq:S1}) can predict endorsements for the corresponding generic statements (e.g., Robins lay eggs).
To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].

#### Method

```{r generic-endorsement}
d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments_catch-trials.csv", sep = ""))

d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments.csv", sep = ""))

d.gen.endorse.summary <- left_join(
  d.gen.endorse, 
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(sentence) %>%
  multi_boot_standard(column = "response") %>%
  ungroup() %>%
  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))

d.gen.endorse.bayes <- left_join(
  d.gen.endorse, 
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(sentence) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup() %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))

# d.gen.endorse.summary %>%
#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
generics.endorsement.spectrum <- d.gen.endorse.bayes %>%
  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5))+
  geom_bar(stat = 'identity', position = position_dodge(),fill = 'grey')+
  geom_linerange(position = position_dodge())+
  #geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Proportion Endorsement")+
  xlab("")+
  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))#+
  #geom_hline(yintercept = -0.25, lty = 3)+
  #geom_hline(yintercept = 0.25, lty = 3)
```

##### Participants

We recruited 100 participants over MTurk. 
4 participants were excluded for failing to pass a catch trial.
5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
The experiment took about 3 minutes and participants were compensated \$0.35.

##### Procedure and materials

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.

As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
4 participants were excluded for failing this trial.

#### Data and model analysis

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
This was a significant predictor of the empirical truth judgments: true generics were significantly more likely to be agreed with than the indeterminate generics ($\beta = 3.14; SE = 0.15; z = 21.5$), as revealed by a mixed-effect logistic regression with random by-participant effects of intercept.
Indeterminate generics were agreed with \emph{less} likely than chance ($\beta = -0.49; SE = 0.09; z = -5.3$) but significantly more than false generics ($\beta = 2.09; SE = 0.14; z = 14.5$).

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
This argues against any simple theory that only predicts whether or not a generic statement is true or false. 
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.

To try to understand this endorsement data, we articulate alternative models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.

Our underspecified threshold model has access to the full prior distribution on prevalence $P(h)$, from which it infers likely thresholds for the generic. 
The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
There are thus three unique components of this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
As a control model, we use the same infrastructure but assign the semantics of "Some" to the utterance (i.e., a fixed-threshold which only rules out the lowest possible degree). 
This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
This provides a strict test of our *simple but underspecified* hypothesis.

##### Prevalence baseline

From the prevalence prior data (Expt. 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*). 
However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $ 20\% < prevalence < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).

##### Prevalence and cue validity

<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though a strong version of cue validity has been argued against on *a priori* grounds [@Leslie2007; @Leslie2008].

For a prevalence distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the prevalence prior distribution (i.e., it is a summary statistic of this distribution).
In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
To measure cue validity, we employed a free production paradigm, following @Cree2006.
Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix.

A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(30) = 0.79$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.

These highlight a shortcoming of cue validity, which is in fact a point-summary statistic based on the prevalence distribution (see Appendix more details).
"Lays eggs" is a somewhat diagnostic features for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
A single metric like cue validity is too blunt to capture this subtlety.
Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the learned regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high.

##### Fixed threshold RSA model

The RSA model we propose for generic endorsement is a speaker model who decides whether or not to say the generic to a naive listener, who has access to the full prior distribution on prevalence $P(h)$.
As a strong alternative model, we retain the specification of the speaker reasoning about a listener with this prior distribution, but remove the uncertainty about the generic threshold. 
For this model, we set $\theta = 0$, and thus the generic statement corresponds to the quantified statement "Some".

<!-- Our pragmatic speaker model, $S_1$ in Eq. \ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$). -->
We use the empirically estimated within-kind target prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt. 1a as the listener's prevalence prior $P(h)$.^[
Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. This corresponds to the more general form of the model described in **Alternative Formulations** section. With these data, the predictions of these two models are nearly identical.
]
The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
We infer this parameter, as well as the values of target prevalence $h$, and parameters of the prevalence priors $P(h)$ (assuming the structured model validated in Expt. 1a) using Bayesian data analysis [@LW2014].
For the prevalence parameters, we use the same priors described in Expt. 1a; for the speaker optimality parameter, we use an informative prior, with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
We learn about the \emph{a posteriori} credible values of our model parameters by collecting samples from MCMC chains of 10,000 iterations removing the first 5,000 iterations, using the Metropolis-Hastings algorithm.

We compare the "Some" model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
(The posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
In accord with intuition, assigning a fixed semantics corresponding to "Some" is too lenient a specification. 
Even for patently false generics (e.g., "Mosquitos don't carry malaria"), the speaker model is unable to prefer staying silent than producing the generic (with a "some" semantics).
It also doesn't strongly prefer producing the generic, possibly because the information content is so small.

##### Uncertain threshold RSA model with diverse priors

Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0.5$, it has *a priori* uncertainty over the threshold.
We perform the same Bayesian data analysis as the "Some" model.
As we see in Figure \ref{fig:commongenerics}b, the pragmatic speaker model $S_2$, using empirically measured priors, explains nearly all of the variance in human truth judgments ($r^2=0.98$; MSE=0.003; Figure \ref{fig:commongenerics}b).

```{r generic-regression-models}
d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
  mutate(sentence = paste(category, property))

### Preprocessing
# - Force all responses to lower case. 
# - Remove spaces.
# - Fix mosquito mispellings.
# - Count "deertick" as "tick".
# - Remove plural "s".
# 
# Mark if the produced animal matches the generic of interest.

mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
  mutate(
    property = gsub("'", "", property),
    Property = gsub("'", "", Property),
    sentence = paste(Category, Property),
    item = paste(category, property))

d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
                       "naturalGenerics-prior-trials-n57.csv", sep = ""))

d.prev.summary <- d.prev %>%
  mutate(item = paste(Category, Property)) %>%
  filter(item %in% d.target.items$sentence) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property, item) %>%
  multi_boot_standard(column = "prevalence")

# need to filter by items specified with endorsement
d.gen.cv.summary <- left_join(
  d.target.items %>% select(-sentence),
  d.cv %>%
    rename(category = response) %>%
    group_by(property) %>%
    mutate(n = n(),
           item = paste(category, property)) %>%
    filter(item %in% d.target.items$item) %>%
    group_by(category, property) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials)
  ) %>%
  mutate(prop = ifelse(is.na(prop), 0.01, prop))

d.gen.endorse.prev.cue <- left_join(
  left_join(
    left_join(
      d.gen.endorse, 
      d.gen.endorse.catch %>% select(workerid, pass)
      ) %>%
      filter(pass == 1) %>%
    rowwise() %>%
    mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence),
          sentence = gsub('[.]', '', sentence)
    ),
    d.prev.summary %>% 
      rename(prevalence = mean,
             sentence = item) %>% 
      select(-ci_lower, -ci_upper)
    ),
  d.gen.cv.summary %>% select(-item))

glm.gen.endorse.prev <- glm(response ~ prevalence, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

glm.gen.endorse.prev.cv <- glm(response ~ prevalence + prop, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

d.gen.endorse.regression.prevalence <- left_join(
  d.gen.endorse.bayes,
  unique(select(
    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
  )) %>%
    mutate(prediction = predict(glm.gen.endorse.prev, ., type = "response")) %>%
    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
) %>% mutate(sqErr = (mean - prediction) ^ 2,
             cuevalidity = prop)

d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
  d.gen.endorse.bayes,
   unique(select(
    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
    )) %>% 
    mutate(prediction = predict(glm.gen.endorse.prev.cv, ., type = "response"),
           sentence = paste(Category, " ", Property, ".", sep = ""))
) %>% mutate(sqErr = (mean - prediction) ^ 2,
             cuevalidity = prop)

d.gen.endorse.regression <- bind_rows(
  d.gen.endorse.regression.prevalence.cuevalidity %>%
    mutate(src = "regression_Prev_Cuevalidity"),
  d.gen.endorse.regression.prevalence %>% 
    mutate(src = "regression_Prev")
  )
# ggplot(d.gen.endorse.regression, 
#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
#   geom_errorbar(alpha = 0.3)+
#   geom_abline(intercept = 0, slope = 1, lty = 3)+
#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
#   #                   rename(cuevalidity = prop) %>% 
#   #                   filter(sqErr > 0.05), 
#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
#   geom_point()+
#   xlim(0,1)+
#   ylim(0,1)+
#   coord_fixed()+
#   xlab("Logistic model prediction")+
#   ylab("Human generic endorsement")+
#   facet_wrap(~src)
```

```{r generic-fullmodel, fig.width = 8}
n_chains <- 1
n_samples <- 50000
burn <- n_samples

model_prefix <- "results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-"

m.samp <- data.frame()
for (i in seq(1, n_chains)){
  mi <- fread(paste(project.path,  "models/generics/results/", model_prefix, 
                    n_samples, "_burn", burn, "_chain", i, ".csv", sep = ""))
  m.samp.i <- mi %>% mutate(chain = i)
  m.samp <- bind_rows(m.samp, m.samp.i)
  #print(i)
}

m.gen.somemodel.endorsement <- fread(
  paste(project.path,"models/generics/results/", 
        #"results-fullModel-s1-smtncssome-20000_burn10000_chain1.csv", 
        "results-fullModel-s1-lowestTheta-smtncssome-1000_burn500_lag10_chain1.csv",
        sep = "")
  ) %>% mutate(chain = 1) %>%
  filter(type == 'predictive') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.fullmodel.endorsement <- m.samp %>%
  filter(type == 'predictive') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

generics.endorsement.models <- bind_rows(
  d.gen.endorse.regression %>% 
  mutate(prediction_lower = prediction,
         prediction_upper = prediction),
  left_join(
    m.gen.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.gen.endorse.regression %>% 
    select(sentence, Property, Category, prevalence, cuevalidity)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "generics_model",
                                      "some_model",
                                      "regression_Prev", 
                                      "regression_Prev_Cuevalidity"
                                     ),
                      labels = c(
                                 "Speaker model - uncertain semantics",
                                 "Speaker model - fixed semantics",
                                 "Prevalence alone", "Prevalence & Cue validity"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prevalence ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")

```

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")

example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

m.gen.fullmodel.prior.parameters <- m.samp %>%
  filter(type == "prior", property %in% example.generics.properties) %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

# use MAP estimates to generate L(h | generic) & L(h | silence) predictions

m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
  ungroup() %>%
  select(param, property, category, MAP) %>%
  mutate(param = paste(param, category, sep = "_")) %>%
  select(-category) %>%
  spread(param, MAP) %>%
  rename(mix = isPresent_na, 
         stable_mean = prevalenceGivenPresent_mean, 
         stable_concentration = prevalenceGivenPresent_sampleSize) %>%
  mutate( a = stable_mean * stable_concentration, 
          b = (1 - stable_mean) * stable_concentration)

gen.listener.predictions <- data.frame()

for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
   )
}

m.gen.fullmodel.target.prevalence <- m.samp %>%
  filter(type == "withinKind") %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.speakerBeliefs <- m.samp %>%
  filter(type == "withinKind") %>%
  mutate(Sentence = paste(category, property)) %>%
  filter(Sentence %in% example.generics)

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.gen.speakerBeliefs %>%
    select(-type, -param, -chain, -Sentence) %>%
    rename(value = val) %>%
    mutate(Parameter = "speakerBeliefs")
)

category.text.labels <- data.frame(property = c("dont eat people", 
                      "carry malaria", "lay eggs",  "are female", "have spots"),
             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
            y = c(0.45, 0.5, 0.45, 0.5, 0.26))

generics.endorsement.insets <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Listener Prior (Posterior given Silence)", 
                                       "Listener Posterior given Generic", 
                                       "Speaker Beliefs")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") ) %>%
  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_text_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

```

```{r generics-endorsement-figure, fig.width=7, fig.height=5}
grid.arrange(generics.endorsement.spectrum, 
             generics.endorsement.models,
             generics.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

<!-- The above analysis provides a single estimate for model predictions, but it is based on noisy empirical measurements of $P(x)$. In order to estimate the impact of this empirical noise on our model predictions, we resampled the prior data (with replacement) for 57 participants worth of data, discretizing and binning as we did above and then inferring parameters. -->
<!-- This procedure (re-sample prior, discretize and bin, infer parameters) was repeated 500 times to bootstrap the model predictions. -->
<!-- The Maximum A-Posteriori (MAP) estimate and 95\% Highest Probability Density (HPD) interval for $\lambda_1$ is 0.5 [0.004, 12.7] and $\lambda_2$ is 1.7 [1.3, 2.1]. -->
<!-- ^[ -->
<!-- The fact that $\lambda_1$ is credibly less than 1 suggests that the generic utterance may be more costly than "staying silent" (our model assumes equal cost). -->
<!-- We maintain using only the two $\lambda$ parameters in the model for simplicity. -->
<!-- ] -->

<!-- This is akin to fitting the parameters and is the critical step in model validation: It shows what data is actually predicted by the model.)  -->

Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g. \emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false.
\emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model.
This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context.

<!-- basic communicative principles (\emph{be truthful}, \emph{be informative}) operating over diverse prior beliefs about the properties, all of which are at play in understanding language.  -->

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-prevalence-tj.pdf} -->
<!--     \caption{Endorsing familiar generics. (a)  -->
<!--     Prevalence prior distributions empirically elicited for twenty-one animal properties. -->
<!--     Prior distributions summarized by two parameters of a structured Bayesian model: $\phi$----a property's potential to be present in a category----and $\gamma$----the mean prevalence when it is possible for the property to be present in a category. -->
<!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a target category. -->
<!--     (b) -->
<!--     Human acceptability judgments compared with model predictions (left) and the target-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
<!--     Color denotes target-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
<!--      Error bars denote 95\% Bayesian credible intervals. -->
<!--     } -->
<!--   \label{fig:commongenerics} -->

<!-- \end{figure} -->

## Discussion

Generic language is the premier case study for generalizations in language. 
Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v. *are female*; *Mosquitos carry malaria*) have stifled the development of formal models.

By measuring listeners' prior beliefs about the prevalence of the property across kinds and the prevalence of the target kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
The key theoretical claim is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.

In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the target category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
Thus, we have shown how these measurements are related to generic endorsement via our model. 
Yet, this evidence is still correlational in nature.
We do not yet know if the variables that we are measuring are causally related to endorsement.
In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the target propensity that the speaker aims to communicate.

<!-- In addition, why generics often imply the property is widespread has also been puzzling [@Gelman2004]. -->
<!-- We show that this is the result of the shape of listener's prior knowledge and that when that shape differs, the implied prevalence is much weaker (e.g., with accidental properties). -->
<!-- Even more puzzling has been the basic asymmetry between endorsements and interpretations [@Cimpian2010]. -->
<!-- We show that this asymmetry arises from the underspecified-threshold interacting with diverse prior beliefs.  -->
<!-- While implied prevalences vary wildly for different kinds of properties under discussion, the endorsements are relatively less sensitive to these distinctions. -->
<!-- Thus, the basic asymmetry is largely being driven by the listener's interpretation of a generic. -->

# Case Study 2: Habitual Language

*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
In this case study, we focus on a particular class of events: people doing actions.
We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).

Habituals about people are of particularly importance because they are likely central to intuitive theories of personality and behavior. 
@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as ``Tell us about your school / family''. 
A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g. ``My brother works part-time at the restaurant.''). 
Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
Habitual language may be a more conservative form of trait language (e.g. \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].

Habituals are a particularly amenable domain to manipulating the target propensity that a speaker aims to communicate.
People are often in the situation of being introduced to new people and learning new information about them.
In addition, the propensity information can be expressed in an easily-interpretable frequency with which a person does an action (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
While target probability can be manipulated for generalizations about categories (generic language) (e.g., by stating the prevalence of feature in a kind), this may interact with domain knowledge in complex ways (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
]
In our first experiment concerning habitual language, we manipulate the target frequency as well as the kind of event (Expt. 2b), creating a data set of endorsements that is three times as large as the data from Expt. 1b (generic endorsement). 
To measure participants' latent prior belief distribution over the frequencies of people doing various actions (e.g., how often people *run*; Expt. 2a), we take advantage of the structured representation discovered in Expt. 1a, and learn about the prior by asking questions about the parameters of this model.
In addition to directly manipulating the target propensity, these experiments provide the first test of the generality of our theory, that it can apply to generalizations about events as well as categories.

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect expectations, not merely observations. 
Up to this point, we have been relatively agnostic as to the interpretation of $h$, the target propensity that the speaker aims to convey.
In our first investigation of the degree scale, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive probability that this event will occur in the near future (e.g., how likely it is that Mary will smoke next week)? 
In Expts. 3a \& 3b, we show that $h$, the target of communication, is a speaker’s prediction about the future frequency of action, and not past frequency, tying the phenomenon of *genericity* even more to subjective beliefs.

<!-- This set of experiments is organized as follows. -->
<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
<!-- In the **Endorsing Habitual Language** experiment (Expt. 2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*). -->
<!-- In the **Interpreting Habitual Language** experiment (Expt. 3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*). -->

<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately. -->
<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated. -->

<!-- The internal structure of particular events can differ in substantial ways. -->
<!-- For example, events differ in their expected duration. -->
<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->

<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
<!-- The computational model described in Eq. \ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events. -->
<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->

## Experiment 2: Endorsing generalizations about events

We follow the same general experimental structure as in Experiment 1. 
First, we measure the prior distribution over the frequency of events, for different kinds of events.
Then, we test endorsements of habitual sentences, manipulating the actual frequency with which a person does an action.

### Experiment 2a: Measuring the propensity prior for event knowledge

In this experiment we elicit the prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements.
For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with a different frequency.
To better understand what frequencies should be expected for different actions, we took advantage of the 
structured representation of the prior discovered in Expt. 1.

In Expt. 1a, we discovered that prior distribution over the prevalence of a feature across different categories can be modeled by a mixture model with two components.
The first component (the "stable cause" component) represents the normal, stable frequencies of the property, among those that normally have the property.
The second component (the "unstable" or "transient cause" component) represents the frequencies of the property among those categories who do not typically have the property. This second component will usually result in frequencies of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero frequencies (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).

For the case of background knowledge over the frequency with which people do actions, we consider again two components.
To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
The second component represents the frequencies of the event among the people who have not done the action before. 
We will assume for these experiments, that those people who have never done the action before will almost never do the action (expected frequency: once every hundred years). 
In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.^[
In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
We assume here a simple structure so as to not make the specification of the prior overly complex.
]

#### Method

##### Participants

We recruited 40 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.

##### Materials

We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
hobbies (e.g. \emph{runs}, \emph{hikes}). 
Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g. \emph{eating} caviar vs. peanut butter).

##### Procedure

For each event, participants were asked two questions, with associated dependent measures:

\begin{enumerate}
\item ``How many \{men, women\} have \textsc{done action} before?'' \\

Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).

\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\

Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
\end{enumerate}

For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''

We anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders. Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/priors-2.html}.

<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->

<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
<!-- The first blank was a text box where participants could enter a number. -->
<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
<!-- They completed this task for each of their eight listed friends or family members. -->
<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->

<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".  -->
<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->

<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->

\begin{figure*}[t]
\centering
  \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3}
  \caption{
  Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency). 
  Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions. 
  Actual frequency noted on x-axis for examples (left).
  Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions. 
  Error bars suppressed and points jittered on left facet for visual clarity.
  }
  \label{fig:tjScatters}
\end{figure*}

<!-- #### Data preprocessing -->

```{r habituals-prior}
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

d.hab.priors <- read.csv(paste(project.path,
                           "data/habituals/priors/friends-and-family-2-trials.csv",
                           sep= ""))

d.hab.priors.tidy <- d.hab.priors %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times,
         never = ifelse(annualRate == 0, 1, 0),
         action = as.character(action),
         action = ifelse(action == "sell things on eBay", "sells things on eBay", action))

d.hab.priors.distinctiveness <- d.hab.priors.tidy %>%
  group_by(action) %>%
  multi_boot_standard(column = 'never') %>%
  ungroup() %>%
  rename(distinctiveness = mean, 
         distinct_low = ci_lower, distinct_high = ci_upper)
#d.hab.priors
#d.hab.priors.distinctiveness
# 
# 
# df.out <- df.tidy %>%
#   mutate(annualRate = ifelse(annualRate == 0, 0.15, annualRate),
#          lograte = log(annualRate),
#          binned_lograte = round(lograte*2)/2) %>%
#   group_by(action, binned_lograte) %>%
#   summarize(counts = n())
# 
# 
# # make sure 0s are represented
# df.out2 <- left_join(
#   expand.grid(action = levels(df.out$action), binned_lograte = levels(factor(df.out$binned_lograte))),
#   df.out %>% mutate(binned_lograte = factor(binned_lograte))) 
# 
# df.out2[is.na(df.out2)] <- 0
# df.out2 <- df.out2 %>%
#   mutate(binned_lograte = as.numeric(binned_lograte))
#   
# ggplot(df.out2, aes( x = binned_lograte, y = counts))+
#   #geom_histogram()+
#   geom_bar(stat = 'identity', position = position_dodge())+
#   #geom_density()+
#   facet_wrap(~action, scales = 'free')+
#   xlim(-3.5, 8.5)
# d.hab.priors.tidy
```

<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
<!-- An empirical distribution can be found by making a histogram of these responses.  -->
<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).  -->
<!-- We thus log-transformed the empirical data.  -->
<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->

<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->

#### Data analysis and results

We built a Bayesian data analysis model for this prior elicitation task.
In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
(1) It smooths effects that are clearly results of the response format. For example, a very common rating for certain events is \emph{1 time per year}. Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
(2) It better captures the tails of the prior distribution (e.g., the probability of a rate of going to the movies two times every five years) which have relatively little data and need to be regularized by the analysis.

Question 1 elicits the proportion of people who have done an action before. 
This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
Question 2 elicits the rate, or relative frequency, with which a person does the action.
This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
Each item was modeled independently for each gender.

We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.

The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).  
We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often). 
This diversity is relevant because the speaker model (Eq.~\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs. the ballet.}) contingent on the shape of the prior distribution.

From the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
That is, $P(h)$ was constructed by sampling $\lambda$ as follows:

\begin{align}
\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
\ln h & \sim \begin{cases}
		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
		\end{cases}
\end{align}

We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before. This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).

Figure \ref{fig:priorScatter} (right) shows example inferred priors.

Some items show substantial differences between the genders (e.g. \emph{wears a bra}) and some show subtle differences (e.g. \emph{watches professional football}). 
%It is \emph{a priori} unclear whether or not $P(x)$ in Eqs.~\ref{eq:L1}, \ref{eq:L0} is the distribution over frequency of action with respect to \emph{all people}, or if it is restricted to be gender specific.
%For example, are the frequency conditions by which a man would qualify to ``wear a bra'' (habitually) different than those by which a woman would qualify to ``wear a bra''?
We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender.
%In order to explore this possibility, we will select items with priors that differ by gender to explore more closely in Experiment 2.

<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->

<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.  -->
<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
<!-- For $a \rightarrow 0$, all bins become equiprobable. -->

<!-- \begin{eqnarray} -->
<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
<!-- a & \sim & \text{Gamma}(2,1) \\ -->
<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
<!-- \end{eqnarray} -->

<!-- VIZ (as before)? -->

<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
<!-- We put a Dirichlet-prior over this probability vector. -->

<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
<!-- Question 1 elicits the proportion of people who have done an action before.  -->
<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
<!-- Each item was modeled independently for each gender. -->
<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin. -->

<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).   -->
<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g. \emph{wears socks}) and visa-versa (e.g. \emph{steals cars}), though there are notable exceptions (e.g. \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).  -->
<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g. \emph{Sam goes to the movies vs. the ballet.}) contingent on the shape of the prior distribution.  -->

<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.  -->
<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->

<!-- \begin{align} -->
<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
<!-- \ln \lambda & \sim \begin{cases} -->
<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
<!-- 		\end{cases} -->
<!-- \end{align} -->

<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
<!-- For example, a very common rating is *1 time per year*. Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure. -->
<!-- ] -->
<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->

<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->

## Experiment 2b: Endorsing generalizations about events

We next explore the endorsements of habituals from the items whose priors were measured the prior elicitation task.

### Method

#### Participants

We recruited 150 participants from MTurk.
To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.

#### Procedure and materials

On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq. \ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
The items were the same as in the prior elicitation task.

Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
Participants completed 37 trials, which were composed of the 27 items from the prior elicitation task and 4 additional filler items not in the prior elicitation task randomly paired with either a male or female character name.
6 of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who watched professional football).
These were used for an exploratory analysis on gender differences.
The 4 filler items were not used in the prior elicitation because they described illegal activities (e.g., "doing cocaine", "stealing cars").
The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-2.html}.

### Results

```{r habituals-endorsement}
d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement-catch_trials.csv", sep = ""))

d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement.csv", sep = ""))

d.hab.endorsement <- left_join(
  left_join(d.hab.endorsement, 
           d.hab.endorsement.catch %>% 
             select(workerid, pass)
           ) %>%
  filter(pass == 1),
  d.hab.priors.distinctiveness %>% rename(habitual = action)) %>%
  mutate(response = as.character(response),
         response = ifelse(response == "agree-key", 1, 0),
         roundedFreq = round(log_times * 2) / 2)

d.hab.endorsement.bayes <- d.hab.endorsement %>% 
  group_by(habitual, time_period, log_times, roundedFreq) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

ggplot(d.hab.endorsement.bayes, aes( x = roundedFreq, y = MAP_h, ymin = low, ymax = high, fill = roundedFreq))+
  geom_jitter(width = 0.1, shape = 21)

#d.hab.endorsement.bayes
```

```{r habituals-regression-models}

glm.hab.endorse.freq <- glm(response ~ log_times, 
              data = d.hab.endorsement, family = 'binomial')

glm.hab.endorse.freq.distinct <- glm(response ~ log_times + distinctiveness, 
              data = d.hab.endorsement, family = 'binomial')

d.hab.endorse.regression <- left_join(
  d.hab.endorsement.bayes,
  unique(select(
    d.hab.endorsement, habitual, log_times, roundedFreq, distinctiveness
  )) %>%
    mutate(regression_freq = predict(glm.hab.endorse.freq, ., type = "response"), 
           regression_freq_distinct = predict(glm.hab.endorse.freq.distinct, ., type = "response"))
) %>%
  gather(src, prediction, regression_freq, regression_freq_distinct) %>%
  mutate(sqErr = (MAP_h-prediction)^2)

ggplot(d.hab.endorse.regression,
       aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = distinctiveness))+
  geom_errorbar(alpha = 0.1)+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
  #                   filter(sqErr > 0.1),
  #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
  geom_point()+
  xlim(0,1)+
  ylim(0,1)+
  coord_fixed()+
  xlab("Logistic model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src)

# with(d.hab.endorse.regression %>%
#        filter(src == "regression_freq"), 
#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
# 
# with(d.hab.endorse.regression %>%
#        filter(src == "regression_freq_distinct"), 
#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
```

```{r habituals-fullmodel}
n_chains <- 1
n_samples <- 10000
burn <- n_samples / 2
lag <- 5
i <- 2
model_prefix <- "results-habituals-S1-ffPrior2-3components-normalPrior-silenceAlt-"

m.samp <- data.frame()
for (i in seq(1, n_chains)){
  mi <- fread(paste(project.path,  "models/habituals/results/", model_prefix, 
                    n_samples, "_burn", burn, "_lag", lag, "_chain", i, ".csv", sep = ""))
  m.samp.i <- mi %>% mutate(chain = i) %>% rename(habitual = item, time_period = param)
  m.samp <- bind_rows(m.samp, m.samp.i)
  #print(i)
}

m.hab.somemodel.endorsement <- fread(
  paste(project.path,"models/habituals/results/", 
        "results-habituals-fixedThreshold-S1-ffPrior2HyperStructured-silenceAlt-10000_burn5000_lag5_chain1.csv",
        sep = "")
  ) %>% mutate(chain = 1) %>% rename(habitual = item, time_period = param) %>%
  filter(type == 'predictive') %>%
  group_by(type, habitual, time_period, cat, gender) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.fullmodel.endorsement <- m.samp %>%
  filter(type == 'predictive') %>%
  group_by(type, habitual, time_period, cat, gender) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.endorse.rsa <- bind_rows(
  left_join(
    d.hab.endorsement.bayes,
    m.hab.fullmodel.endorsement
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.hab.endorsement.bayes,
    m.hab.somemodel.endorsement
  ) %>%
    mutate(src = "some_model")
)

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression %>% 
  mutate(prediction_lower = prediction,
         prediction_upper = prediction),
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, log_times, distinctiveness)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "generics_model",
                                      "some_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - uncertain semantics",
                                 "Speaker model - fixed semantics",
                                 "Frequency alone", "Frequency + Distinctiveness"
                                 ))) %>%
  filter(src == "Speaker model - uncertain semantics") %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = log_times ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")

# with(m.hab.endorse.rsa %>% 
#   filter(src == "generics_model"), cor(MAP_h, MAP, use='pairwise.complete.obs'))^2

habituals.endorsement.models
```

```{r fig.height = 8, eval = F}

m.samp %>% filter(type == "param") %>%
  ggplot(., aes( x = val))+geom_histogram()+
  facet_wrap(~habitual)

m.samp %>% filter(type == "prior") %>%
  ggplot(., aes( x = val, fill = time_period))+geom_histogram() + facet_grid(habitual~cat, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))

#tail(m.samp)
```

#### Behavioral results

On each trial of the experiment, the participant was told a person did a particular action 3 times during some time window. 
A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one. 
Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements.
A more sophisticated alternative hypothesis is that the degree to which the habitual statement is good is the frequency itself. 
<!-- Our computational model predicts that the the degree to which the habitual statement is good is the frequency of event, normalized by the alternative possible frequencies under the prior. -->
<!-- [MHT: SENTENCE ABOVE IS THE SOFT-SEMANTICS INTERPRETATION] -->

Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:tjScatters} (left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence. 
First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency.
It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (log frequency $\sim$ -1; 3 times in a 5-year interval; e.g. \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
We see in addition that even when actions are done relatively frequently (e.g. 3 times in a one month interval; log frequency $\sim$ 5), some habitual sentences receive less than full endorsement (e.g. \emph{wears socks}, \emph{drinks coffee}). 
In our data, actions completed with a high frequency (3 times in a one week interval; log frequency $\sim$ 6.5) receive at a minimum 75\% endorsement, though there is still variability among them (e.g. between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
Overall, the raw (log) frequency of action predicts only a fraction of the variability in responses ($r^2(93) = 0.33$).
For actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(50) = 0.07$)

We observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.

We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$. 
This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women). 
Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.

\begin{figure*}[t]
\centering
  \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf}
  \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity).
  Middle: Human endorsements of habitual sentences (Expt. 3b) vs. Predicted log frequency (Expt. 3a), with data for corresponding items from Expt. 2 (assumed to have the same predictive log frequency as baseline). 
  Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).}
  \label{fig:tj3}
  \vspace{-7pt}
\end{figure*}

#### Model criticism and comparison

We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.~1) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
The model has two free parameters---the speaker optimality parameters, $\alpha_i$, in Eqs.~\ref{eq:S2} \& \ref{eq:S1}. 
We use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.~2.
To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6].
%The MAP and HPD interval for the data-analytic guessing parameter is 0.004 [0.0003, 0.03], suggesting that there is not a substantial amount of the data that is better explained by a model of random guessing than by our pragmatic speaker model.

As shown in Figure \ref{fig:tjScatters}, right, the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(93) = 0.94$), including actions done on the time scale of years or more  ($r^2(50) = 0.92$).
The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.

As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.

Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data.

## Experiment 3: Communicating predictive propensities

In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?

While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
Does habitual language communicate propensity in terms of past frequency or future expectations?
On one hand, speakers can only *know* about what has happened in the past.
On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.

In this pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
In Expt. 3a, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
In Expt. 3b, we examine felicity judgments of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.

### Experiment 3a: Prediction elicitation

#### Methods

We recruited 120 participants from MTurk, using the same criterion as Expt. 2b.
The experiment took 4 minutes on average and participants were compensated \$0.40.

The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
The final third of trials had no additional evidence and were identical to Expt. 2b.

Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
To increase expected variability, participants saw only the frequencies that led to most intermediate endorsement of the habitual in Expt. 2b. 
In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.

Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/predictive-1.html}.

#### Results

Figure \ref{fig:tj3} (left) shows the predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g. participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month). 
This means that our model makes identical predictions for Expt. 2 whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:tj3} left; blue and green dots).

+ MHT: Add some regression analysis here

### Experiment 3b: Felicity judgments

#### Methods

We recruited 150 participants from MTurk, using the same criterion as Expt. 2b.
The experiment took 4 minutes on average on participants were compensated \$0.40 for their work.
None of the participants had completed Expt. 3a.
%\subsubsection{Procedure and materials}
The only difference from Expt. 3a is the dependent measure. 
On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2).
The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
#### Results

There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:tj3}, middle; blue points).
When collapsing across items and subjecting the data to a generalized mixed-effects model with random by-participant effects of intercept and random by-item effects of intercept and conditions, we find evidence for a small effect of \emph{enabling} conditions on endorsements (M =  0.89; 95\% Bootstrapped CI [0.88, 0.91]) as compared to baseline (M = 0.85 [0.83, 0.87]) [$\beta = 0.42; SE = 0.15; z = 2.8$]
, and a large effect of \emph{preventative} conditions on endorsements (M = 0.29 [0.26, 0.31]) [$\beta = -3.22; SE = 0.21; z = -15.2$]. 
<!-- %\mht{should I add points from Expt. 2 to left-most scatter, or maybe there is a better plot?} -->

We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b.
We infer the two model parameters using the same analysis approach in Expt. 2. 
The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right).
The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$).
These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past.

Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points). 
This may be due, in part, to an effect of the experimental context on participants: 
in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt. 2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
Future investigation into this issue is warranted.

## Discussion

Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt. 2a). 
We have seen that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context that people exhibit (Expt. 2b).
In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Experiment 3, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt. 3a) and using that, with the model, to predict the felicity of habitual sentences (Expt. 3b). 
To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.
In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while measuring the propensity priors.
Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlational associated with generic endorsement but not directly causally related.
In our final case study, we extend our theory to communicating generlizations about causes, and test experimentally whether the propensity prior is indeed causally related to generic endorsement.

# Case Study 3: Causal Language

Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality (CITE noah's and kemp's causality and causal models papers?).
Communicating generalizations about causally related events is potentially highly useful because no one individual can run all the experiments that she wants to run in a life time. 
The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.

Our framework for communicating generalizations makes predictions about statements conveying genericty about a category of causal events. 
In this domain, an instance of the category is a single causal event (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough at a particular time of the day). 
@Gerstenberg
The study of *elemental causal induction* is itself very subtle, depending on an observer's background theory of causality. [@Griffiths2005; @Schulz].

We design this last experiment with the goal of testing whether background knowledge that gives rise to the prevalence priors is causally related to the endorsement of causal statements.
Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.

In Experiment 4a, we manipulate participants' beliefs about a causal system and measure their updated beliefs about system, serving a manipulation check.
In Experiment 4b, we test whether these manipulated priors give rise to different endorsements of causal statements.

## Experiment 4a: Manipulating the Prevalence Prior for Causes

People have theories about how different casusal systems work. 
Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force. 
If the experiment is repeated exactly, we would expect the same results.
In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't. 
Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.

In this experiment, we examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present.
We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains.

### Method

#### Participants

We recruited N participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
The experiment took on average N minutes and participants were compensated \$N.NN for their work.

<!-- The different kinds of system are described in more detail below. -->
<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->

The experiment is a single-trial experiment with 2 phases to the trial.
In the first phase, participants are given a story about a causal domain in question.
In the second phase, participants are asked to make a judgment corresponding to the between-subjects condition they are assigned (prior, endorsement, interpretation).

#### Procedure

Participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (e.g., how to make a certain kind of animal more alert). They are told:

\begin{quotation}
You are an astronaut-scientist exploring a distant planet. 
On this planet, there are animals called  (e.g., daiths) and your team of scientists wants to figure out what makes daiths's hair turn brown. 
Your team runs experiments trying to make daiths's hair turn brown with different chemical compounds. 
The results are shown below:
\end{quotation}

Participants then must click a button to show the results of the experiments.
Experiment results appear one at a time (upon a click), and are described verbally (e.g., The team tested Food A on 100 daiths. 30 of them were made more alert.) as well as put into a table showing the number of successes per number of attempts (always 100 per experiment). 
Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 6).
After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.

Upon proceeding to phase 2, the results of the "experiments" are removed and participants are told more experiments were conducted.
Participants were asked to predict the results of the next 4 experiments.
Participants were given 4 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., foods M, N, P, and Q).

#### Materials

The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model.
Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.

A second dimension of manipulation corresponds to the extent to which *determinism* is expected in the domain. 
For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.

### Results

...

## Experiment 4b: Endorsing Causal Language

In this experiment, we tested whether the manipulated priors of Expt. 4a are causally related to the endorsement of causal statements.

### Method

Most of the experiment was identical to that of Experiment 4a.

#### Participants

We recruited N participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
None of the participants had participated in Experiment 4a. 
The experiment took on average N minutes and participants were compensated \$N.NN for their work.

#### Procedure and materials

The materials were the same as in Experiment 4a.
Phase 1 of the experiment was identical to that of Experiment 4a.
In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
Participants were then asked to judge the causal sentence: "Treatment X makes the effect happen". 
Partipants responded by either clicking "Yes" or "No".

Participants saw 1 of 3 frequencies: 20\%, 50\%, or 80\%.

### Results

```{r causals-endorsement}
d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
                                       "data/causals/endorsement/",
                                       "causals-8-20-catch_trials.csv", sep = ""))

d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
                                       "data/causals/endorsement/",
                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )

d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)

d.caus.endorse.catch <- d.caus.endorse.catch %>% 
  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))

d.caus.endorse.20 <- read.csv(paste(project.path, 
                                "data/causals/endorsement/",
                                "causals-8-20-trials.csv", sep = ""))

d.caus.endorse.70 <- read.csv(paste(project.path, 
                                "data/causals/endorsement/",
                                "causals-8-70-trials.csv", sep = "")) %>%
  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))

d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)

d.caus.endorse.summary <- left_join(
  d.caus.endorse, 
  d.caus.endorse.catch %>% select(workerid, passBoth)
  ) %>%
  filter(passBoth == 1) %>%
  group_by(distribution, frequency) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
                        group = distribution))+
  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
  theme(axis.text.x = element_text(angle = 0))+
  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
  scale_fill_solarized()+
  xlab("Frequency")+
  ylab("Proportion Causal Endorsement")
```

## Discussion

# General Discussion

It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
Generalizations in language (e.g., *John runs.*, *Dogs are friendly.*, *The block makes the machine play music*) are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data.

It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *propensity*, or probability (Expts. 1, 3, \& 4).
This scale is defined by a subjective, predictive probability, not mere frequency (Expt. 2).
We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
Finally, our framework naturally accounts for a number of well-documented examples from linguistics of generalizations about categories, or *generic language* (Expt. 1).
In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.

The theory we present here has a number of desirable features that go beyond alternative accounts.
The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Pelletier; @Cohen1999; @Nickel].
As @Nickel2013 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.

Our separation of world knowledge from the semantics of generics allows a way for conceptual structure to influence generic production and comprehension, without having to posit conceptual structure and semantics are one in the same.
This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for influence on generic language [c.f., @Leslie2008].

<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation. -->
<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->

In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
We conclude by sketching out arguments for other known philosophical puzzles in genericity.

## The Comparison Class and the Question Under Discussion

In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
We constructed the prior belief distribution for the propensity of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
These other kinds, people, and causes form *comparison classes* against which the target is evaluated. 
$P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.

The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language to the study of *vague language*.

In this work, we made the design decision to construct the comparison class with respect to other kinds, people, or causes.
In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
In the minimal contexts employed in our experiments, this is a reasonable assumption.
There is a different assumption we could have made, however: Another clear way to construct the comparison class, with respect to other features. 
This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*

Statements of genericity can be used to address either QUD, and this difference can even be observed the same sentence.
"Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; say, in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., said sardonically).
We chose to focus in this work on the category-wise comparison class for methodological convenience. 
In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
*Feature-wise* comparison classes are likely to be modulated by the feature itself.
Future work should address the property-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.

<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}. -->
<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices. -->

<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding. -->
<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant. -->

## Structured prior knowledge and Implications for Conceptual Structure

<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->

Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008]. 
Prasada has argued for a distinction between \emph{characteristic} properties (e.g.~\emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g.~\emph{Diapers are white.}).
Leslie suggests information that is striking (e.g.~\emph{Tigers eat people.}) is useful and thus permitted to be a generic.
Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
Where in the prevalence-based semantics could such conceptual distinctions come into play?

Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different prevalence priors. 
In Expt. 4 we showed that these prevalence distributions are causally related to endorsement.

It is natural to ask how subjective probabilities might reflect conceptual knowledge.
We found that empirical prevalence distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations. 
It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective prevalence.

## Communicating Predictive Probabilities

It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
Indeed, we elucidated in Expt.~3 that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.

The focus on subjective, predictive probability casts new light on puzzles surrounding accidentally-true situations.
To take a thought-experiment from the linguistics litearature, imagine that currently every Supreme Court justice's social security number is an even number. 
Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
Our explanation is this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*. 
Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive prevalence would not be any different for Supreme Court Justices than any other profession.
This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic. 
For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.

This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
This has been taken to imply that people are bad with probabilties.

We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.

<!-- ### The Problems with Communicating Generalizations -->

<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*. -->
<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->

<!-- Generalizations can be made about almost anything. -->
<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers. -->
<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->

<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs). -->
<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}). -->

<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false. -->
<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->

<!-- ### Statistical Accounts of Generics -->

<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
<!-- Let's first introduce some notation: -->

<!-- ### Conceptual Accounts of Generics -->

## Acquiring the Language of Generalizations

The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
Generic language is one of the earliest emerging forms of complex, compositional language (CITE).
Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
More on development.

What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
If generics convey something about the prevalence of feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
Rehash linguistic puzzles.
The extreme flexibility of generic meaning stands in stark contrast to its early emergence in development.
In fact, quantified statements, whose formal meaning is much more straight-forward, emerge much *later* in development.
This has led some to conclude that the normal tools for describing the semantics of quantified utterances (namely, a truth-functional threshold) will not work for generic language [@Leslie2008].

This may be throwing out the baby with the bathwater.
When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance: (1) that the meaning is a threshold-function (i.e., $\denote{u}(p, \theta) = \{p :p > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
If there is no fixed value of the threshold, then a uniform prior over the threshold in the truth-functional threshold semantics is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is *the degree itself*, normalized by the prior distribution over the degree (i.e., the comparison class).

$$
\int_{0}^{1} \delta_{p > \theta} \diff \theta =  p
$$

Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early.
The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* sematnics.
This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).

## Relationship to Other Theories

To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.

Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]

### Statistical Accounts

Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
Similar to our formulation, Cohen looks to *prevalence* as a metric against which generics get evaluated.
For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
"Absolute generics" have a meaning with a fixed threshold on prevalence and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.

There are two main points of deviation of our theory from Cohen's.
First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.

It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the prevalence of *laying eggs* among *robins*?).
These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.

In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.

Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.

Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
Indeed, we have shown in Expt. 3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
Prevalence or propensity in our theory is a posterior predictive probability, which incorporates background knowledge in order to make predictions about the future. 
The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].

### Conceptual Accounts

Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.

Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
For Leslie, generics are tied to the cognitive system's "default mode of generalization".
The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
Generics are much less reasonable when positive counter-instances exist. Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.

@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
Statistical information takes a backseat to the conceptual structure.

Generics can arbitrary relationships too: *Barns are red* because most barns are red.
If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.

In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
In this paper, we take a minimalist approach in modeling conceptual structure in our prior on prevalence $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence of properties across different categories.
This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.

The key point divergence between their and our view concerns the core meaning of a generic statement.
For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.

<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories. -->

<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->

<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->

<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.  -->
<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->

<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013]. -->
<!-- In these experiments, the prevalence considered is only the prevalence of the property for the target category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.  -->
<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance. -->
<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior. -->

<!-- ## Generic Identification -->

<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
<!-- The bare plural construction can also indicate a specific plural predication. -->
<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues. -->

<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process. -->
<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->

## Other philosophical puzzles

In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.

1. Books are paperbacks.
2. Mary handles the mail from Antarctica.
3. Elephants live in Africa and Asia.
4. Women are submissive.

(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
This is not an isolated example.
The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
We posit that the weirdness of these examples is the result of a failure of the comparison class.
If the comparison class can be derived with respect to the property [c.f., @Keil1979], one would expect the entities in the class to

(2) is often used to argue that no actual instances need have occurred to make a generalization true. 
In this thought experiment, part (or perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
Thus, it is not the case that Mary has handled the mail from Antarctica in the past.
Our framework takes the fundamental currency of a generalizatoin in language to be a subjective predictive probability. 
In Expt. 3, we manipulate predictive probability and saw the endorsements for habitual language were affected. 
This example bears similarity to the *enabling* condition of that experiment, wherein causal events increased the propensity of the event in the future, and also resulted in an increase in endorsements of habitual language.

(3) shows a subtle interaction of generic language with another linguistic device: conjunction. 
(3) sounds true but if one takes the conjunction to apply to the properties, it is not true.
That is, we don't think there to be international elephants (i.e., individual elephants who live in Africa part time and Asia part time).
Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008]. 
This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia."
Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.

With reasonable assumptions about the prior (e.g., assuming international elephants are unlikely), upon the hearing "Elephants live in Africa", the moddel infers that most elephants live in Africa.
When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
This is a nice feature of the uncertain threshold semantics: flexibility in accomodating new evidence that might otherwise contradict previous statements.

Finally, (4) is used to argue that even if the property is widespread (perhaps in a soft sense, as in our model, relative to other kinds or groups), we might find it avervise to actually assert the generic.
That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive, we might still not want to say *Women are submissive* [@Haslanger]. 
In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth [cf., @Cimpian2010].
The current formulation of the model is relatively ambivalent the deviations of the listener's beliefs from the speaker's beliefa.
Other models in the RSA framework have identified states of the world with different subjective values (e.g., how good of a job a listener did on a task), and speakers with utilities that extend beyond conveying information can produce qualitatively different patterns of utterances [e.g., polite speech; @Yoon2016; @Yoon2017].
If our model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.

In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity. 
The precise implementation of these hypotheses we leave for future work.

<!-- -- Books are paperbacks. (failure of the constrast class) -->
<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->

# Conclusion

It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
Shouldn't speakers and teachers want to express their ideas as crisply as possible?
To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
which would otherwise be difficult or costly information to learn through direct experience.

The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.  
Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the target prevalence, the prior distributions on prevalence, or the comparison class.
<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
For example, there is considerable disagreement as to whether or not "Humans cause global warming".
Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
This is a promising area for future research.

Categories are inherently unobservable. 
You cannot see the category \textsc{dog}, only some number of instances of it.
Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
The theory presented here gives one explanation of how we do so, providing a computational perspective on how category generalizations are conveyed and how beliefs play a central role in understanding language.

# References

<!-- \setlength{\parindent}{-0.1in}  -->
<!-- \setlength{\leftskip}{0.125in} -->
<!-- \noindent -->

<div id = 'refs'></div>

```{r child = 'appendix-prevalencePrior.Rmd'}
```

```{r child = 'appendix-cueValidity.Rmd'}
```

### 2017-06-07 paper/listener-tasks.Rmd
paper and appendices

## Experiment 2: Interpreting generalizations about categories

One of the most important roles for generic language is to provide learners information about new or poorly understood categories. 
This role depends on how unfamiliar generic sentences are interpreted [e.g., @Gelman2002; @Cimpian2010].
Interpretating generic language has been shown to impact how kinds are represented in the mind [@Cimpian2009; @Cimpian2010], how essentialism develops [@Rhodes2012], and individual motivation [@Cimpian2007; Cimpian2010].
In this rich space of conveyed content, our theory posits that the mediating force in these cases is probability.
The theory we present includes the most basic model of generic comprehension: the listener model (Eq. \ref{eq:L0}) describes interpretation of a generic utterance---\emph{Kind \textsc{has property}}---without previously knowing the prevalence of the property within the kind.

Classic work in generalization suggests beliefs about the prevalence of properties differ by type of property, including relatively fine distinctions among properties that are all biological in nature [@Nisbett1983]. 
We harness these diverse expectations, using properties that explore a wide range of \emph{a priori} beliefs about prevalence. 
We test the impact of generic language on prevalence [following @Gelman2002; @Cimpian2010].

Measuring *a priori* beliefs when the kinds are unknown is subtle.
We cannot, as before, have participants fill out a table with rows corresponding to different novel animal kinds and columns corresponding to different properties:  Nothing would distinguish the rows.
Instead, we build our finding in Expt. 1a that the prevalence prior is structured (i.e., it is implicitly representing two or more primitive distributions: a null distribution and a present distribution).
We assume the null distribution is a transient cause of the property and follows a $Beta(1, 100)$ distribution.
We assume the "present" distribution is a Beta distribution whose mean and variance parameters we wish to measure for different properties. 
We also will measure the relative weighting of these two distributions (i.e., the mixture component) in the prior task (Expt. 2a).

By measuring these two aspects of the prior, we build a Bayesian data analysis model to reconstruct the marginal distribution on prevalence $P(h)$ from these measurements.
We then test the predictions of the underspecified-threshold listener model $L_0$ using these empirically derived priors against human interpretations of novel generic sentences (Expt. 2b).

### Experiment 2a: Measuring the prevalence prior with unfamiliar kinds

##### Participants

We recruited 40 participants over MTurk.  
All participants were native English speakers. 
The experiment took about 5-7 minutes and participants were compensated \$0.75.

##### Procedure and materials

We constructed forty different properties to explore a wide range of \emph{a priori} beliefs about prevalence, building on a stimulus set from @Cimpian2010. 
These items make up four sub-categories of properties concerning body-parts: without modification (e.g. \textsc{has claws}), of a particular color (e.g. \textsc{has green feathers}), 
described vaguely (e.g. \textsc{has small wings}), or in accidental or disease states (e.g. \textsc{has wet fur}, \textsc{has swollen ears}).
Because pilot testing revealed more variability for items in the accidental category relative to the other types of properties, we used twice as many exemplars of accidental properties to yield a data set with more item-wise variability. 
We used 8 exemplars of each of the three non-accidental properties ("parts", "colored parts", "vague parts"), and 16 exemplars of accidental properties.
All materials are shown in Table 3 in the Appendix.

In the task, participants were introduced to a "data-collection robot" that was tasked with learning about properties of animals. 
Participants were told the robot randomly sampled an animal to ask the participant about (e.g. The robot says: "We recently discovered animals called feps."). 
We then used a two-stage elicitation procedure, aimed to measure two relevant components of the structured prior model: (i) the *potential* of the property to be present in a kind and (ii) the *expected prevalence* when present.
The former relates to the distinctiveness of the feature and the latter corresponds to the prevalence among those animals with the capacity to have the feature.
To get at (i), the robot asked how likely it was that "there was \emph{a} fep with \textsc{property}" (potential to be present), to which participants reported on a scale from "unlikely" to "likely".
For example, it is very likely that there is a fep that *is female*, less likely that there is a fep that *has wings*, and even less likely that there is a fep that *has purple wings*. 
To get at (ii), the robot asked, "Suppose there is a fep that has wings. What percentage of feps do you think have wings?" (expected prevalence when present). 
Participants completed a practice trial to make sure they understood the meanings of these two questions.

#### Data analysis and results

We used the same structured, data analysis model from Expt. 1a.
The only difference analytically is that this experiment measures different components of the prior. (In Expt. 1a., our experimental data came asking about particular samples from the prior, i.e., particular familiar categories).

The two measurements in this experiment are slider bar ratings ranging from 0 to 1 in increments of 0.01.
The canonical prior for generating numbers between 0 - 1 is the Beta distribution.
We assume these two measurements follow Beta distributions ($d_{potential} \sim \text{Beta}(\gamma_{1}, \xi_{1})$; $d_{expected} \sim \text{Beta}(\gamma_{2}, \xi_{2})$). 
The posterior predictive of $d_{potential}$ corresponds to the relative weighting of the "present" component in the prior. 
In our Bayesian data analysis model, we then flip a coin weighted by a posterior predictive sample $\phi$ of $\text{Beta}(\gamma_{1}, \xi_{1})$.
If it comes up heads, we then sample from the "present" component: $\text{Beta}(\gamma_{2}, \xi_{2})$.
If it comes up tails, we sample from the "null" component: $\text{Beta}(1, 100)$.
Thus, we construct single prevalence distributions, $P(h)$, by sampling from the posterior predictive distribution of prevalence as we did before: $$P(h) = \int [ \phi\cdot \text{Beta} (x \mid \gamma_{2}, \xi_{2}) + (1 -  \phi) \cdot \text{Beta}(1, 100)] \cdot \text{Beta}(\phi \mid \gamma_{1}, \xi_{1}) d\phi$$.
We used the same uninformative priors over parameters $\phi, \gamma_{i}, \xi_{i}$ as in Expt. 1a.

Figure \ref{fig:prior2}a shows a summary of the elicited priors, in terms of the diversity of $d_{potential}$ and $d_{expected}$.
Biological properties are expected to be \emph{a priori} more prevalent within a kind when present than accidental properties, with additional fine-grained differences within biological and accidental properties.
Like the priors elicited using familiar categories, these priors elicited using unfamiliar categories have diverse shapes (see insets). 
Biological properties ("biological", "vague", and "color" body parts) have prevalence distributions that are bimodal with peaks at 0\% and near-100\% prevalence. 
Interpretations of generics about these properties ($L_0$ model, Eq. \ref{eq:L0}) update these distributions to concave posteriors peaked at 100\% (Figure \ref{fig:prior2}a; red, blue and green insets); the model predicts these novel generics will be interpreted as implying the property is widespread in the category.
By contrast, accidental properties (both "rare" and "common") follow unimodal prior distributions and update to convex posterior distributions, predicting weaker and more variable interpretations of novel generics for these properties.

\begin{figure*}
\centering
    \includegraphics[width=\columnwidth]{figs/prevalence-implied-wPriors}
    \caption{Understanding novel generics. (a) Prevalence prior distributions empirically elicited for 40 animal properties.
    Parameters of the structured statistical model---$\phi$ and $\gamma$---reveal quantitative differences in beliefs about the prevalence of conceptually different types of properties (scatterplot). 
    Inset plots show differences in shapes between biological properties (red, green, blue; bimodal) and accidental properties (orange, purple; unimodal).   
  These differences in the prior (darker shade) give rise to the variability of $L_1$ interpretations of generic utterances (lighter shade).
  (b)
  Human interpretation of prevalence upon hearing a generic compared with the $L_1$ model posterior predictive. 
    Participants and the model interpret generics differently for different property types: Generics of biological properties (red, blue, green) have  strong interpretations while generics of accidental properties (purple, orange) are weaker. 
      Error bars denote Bayesian 95\% credible intervals.
  }
  \label{fig:prior2}
\end{figure*}

### Experiment 2b: Interpreting novel generic statements

Our model of generic interpretation, the listener model $L_0$ (Eq. \ref{eq:L0}), predicts that the implied prevalence of generics should vary as a function of the prevalence prior.
Here, we test the degree to which the predictions based on the empirically elicited prevalence priors for 40 items (from Expt. 2a) match human judgments of how the widespread the property is upon hearing a generic.

### Method

#### Participants

We recruited 40 participants over MTurk to determine how widespread different properties are believed to be upon hearing a novel generic.  
The experimental design is very similar to @Cimpian2010, and we chose to have a sample size at least twice as large as the original study (original n=15). 
All participants were native English speakers. 
The experiment took about 5 minutes and participants were compensated \$0.60.

#### Procedure and materials

In order to get participants motivated to reason about novel kinds, they were told they were the resident zoologist of a team of scientists on a recently discovered island with many unknown animals; their task was to provide their expert opinion on questions about these animals.
Participants were supplied with the generic (e.g., "Feps have yellow fur.") and asked to judge prevalence: "What percentage of feps do you think have yellow fur?". 
Participants completed in randomized order 25 trials: 5 for each of the biological properties and 10 for the accidental (described in Expt. 2a).
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/generics/experiments/asymmetry/asymmetry-2.html}.

### Analysis and results

The underspecified-threshold listener $L_0$ model provides posterior beliefs about prevalence, given prior beliefs and a generic utterance.
This model has zero parameters and its predictions are derived by marginalizing out the uniform prior on threshold $P(\theta)$.

NEED TO REWRITE

We look at the posterior predictive distribution of $L_0$, integrating out the model parameter.
We first explore two important trends predicted by the pragmatic listener model.
In Figure \ref{fig:exp2b} (solid lines) we see the implied prevalence judgments are predicted (at the property class level) to vary linearly with the \emph{a proiri} expected prevalence. 
A mixed-effects linear model with random by-participant effects of intercept and slope indeed reveals the more prevalent a property is expected to be \emph{a priori}, the stronger the implications of a generic statement ($\beta = 0.57; SE = 0.08; t(39) = 7.12; p < 0.001$).
The prevalence implied by a generic is also predicted to be greater than the \emph{a proiri} expected prevalence (i.e., greater than the prevalence expected among the kinds with the potential to have the property).
A mixed-effects linear model with random by-participant effects of intercept and random by-item effects of intercept and condition reveals implied prevalence after hearing a generic is significantly greater than the \emph{a priori} prevalence ($\beta = 0.17; SE = 0.018; t(39) = 9.7; d = 0.64; p < 0.001$).
As for the quantitative accuracy of the model, on a by-item level, the pragmatic listener model predictions closely align with the human judgments of prevalence for novel generics ($r^2(40)=0.94$, MSE=0.002).
Human participants and our model display the same sensitivity of generic interpretation to details of the property (Figure \ref{fig:prior2}b). 
We now have strong support for both of the major predictive components of our model: generic endorsement, modeled as a speaker $S_2$, and generic interpretation, modeled as a listener $L_1$.

## Experiment 3: The Asymmetry Between Endorsements and Interpretations

There is a surprising d\'{e}colage between the truth conditions and interpretations of generic language: Interpretations are often strong while truth conditions are flexible. 
@Cimpian2010 found that upon reading a generic (e.g., \emph{Glippets have yellow fur.}), participants infer (in an \emph{implied prevalence} task; Expt. 2b) that the property is widespread (e.g., almost all glippets have yellow fur).
By contrast, participants endorse generics (in an endorsement task) for a wide range of prevalence levels (e.g., even when "30\% of glippets have yellow fur."), thus highlighting an asymmetry between endorsements  and implied prevalence. 
This mismatch is not found for the behavior of quantified statements involving "all" or "most," and is significantly reduced or disappears for generics of accidental properties  (e.g., \emph{Glippets have wet fur.}).

Below, we measure endorsements using the same stimuli as Expt. 2b. 
We replicate the basic asymmetry findings of @Cimpian2010 and reveal even more variability in the mismatch between *endorsements* and \emph{implied prevalence} using the expanded stimulus set from Expt. 2.
In addition, we now test both our models (generic endorsement [speaker $S_1$] and generic interpretation [listener $L_0$]) in the same experimental paradigm.

### Method

We re-analyze the data from Expt. 2b as the \emph{implied prevalence} data.
The following paradigm is to measure the corresponding \emph{endorsements}.

#### Participants

We recruited 40 participants over MTurk.  
All participants were native English speakers. 
None of the participants completed Expt. 2b (interpretations of novel generics).
The experiment took about 5 minutes and participants were compensated \$0.60.

#### Procedure and materials

The cover story and materials were the same as in Expt. 2b.
On each trial, participants were given a statement about a property's prevalence within a novel kind (e.g., \emph{50\% of feps have yellow fur.}).
Participants were then asked whether or not they agreed or disagreed with the corresponding generic sentence (e.g., \emph{Feps have yellow fur.}).
Prevalence varied between 10, 30, 50, 70, and 90\%.

The experiment consisted of 25 trials: 5 trials for each of 5 types of properties measured in Expt. 2a (part, color part, vague part, common accidental, rare accidental). 
Each prevalence level appeared once for each property type (5 prevalence levels x 5 property types).

### Analysis and results

For both behavioral data and model predictions (Eq. \ref{eq:S1}) we computed the average prevalence that led to an assenting judgment (the \emph{average prevalence score}), for each property type and participant, following the procedure used by @Cimpian2010.
For example, if a participant endorsed the generic whenever the prevalence was 70\% or 90\% and disagreed at the other prevalence levels, that participant received an \emph{average prevalence score} of 80\%.
If a participant didn't endorse the generic at any prevalence level, their \emph{average prevalence score} was 100\% because presumably they would only endorse the generic if the property was universal.

RE-DO

For our pair of models, there are two parameters (the two speaker optimality parameters).
We infer them using the same Bayesian data analytic approach as before. 
The MAP and 95\% HPD intervals for $\lambda_1$ is $19.5 [10.5, 19.9]$ and $\lambda_2$ is $0.4 [0.34, 0.49]$.
We then subjected the generic endorsement model to the same procedure as the human data. % subjected our model to the same procedure. 
The speaker model $S_2$ returns a posterior probability of producing the generic, for each level of prevalence. 
We sample a response (\emph{agree} / \emph{disagree}) from this posterior distribution for each prevalence level, simulating a single subject's data.
As with the human data, we took the trials where the model agreed with the generic, and took the mean of the prevalence levels corresponding to those trials, giving us the average prevalence at which the model assented to the generic.
We repeated this for each type of property 40 times to simulate a sample of 40 participants. 
We repeated this procedure 1000 times to bootstrap 95\% confidence intervals.

The generic endorsement model (speaker $S_2$) predicted that \emph{average truth conditions} should not vary appreciably across the different types of properties, consistent with the fact that generics are acceptable for broad range of prevalence levels for all property types.
A similar absence of a gradient was observed in the human data ($\beta = 2.82; SE = 4.02; t(39) = 0.70; p = 0.49$; Figure \ref{fig:exp2b}, dotted lines). 
Interpretations of generic utterances are stronger than their average truth conditions for the biological properties but not for the accidental properties (Figure \ref{fig:exp2b}) with both human data, replicating @Cimpian2010, and the model; the extent of the difference is governed by prior property knowledge (mean prevalence when present $\gamma$, from Expt.~2a).
The listener and speaker pair of models predicts human endorsements and interpretations of novel generic utterances well ($r^2(10) = 0.87$, MSE = 0.008).
Thus, our model predicts that the asymmetry between truth conditions and implied prevalence should hold, but only for properties with the most extreme prior beliefs.

\begin{figure*}
\centering
    \includegraphics[width=\columnwidth]{figs/unfamiliar-asymmetry-predictive-data.pdf}
    \caption{The asymmetry between truth conditions and interpretations. Human judgments and model predictions of prevalence implied by novel generic utterances (implied prevalence task; solid line) and average prevalence that leads to an acceptable generic utterance (truth conditions task; dotted line) as it relates to the \emph{a priori} mean prevalence when present $\gamma$.
    Expectations of prevalence are higher after hearing a generic than before hearing it (solid line compared to $y=x$ line; both for human data and model).
    Generic statements about biological properties, imply that the property is widespread in the category, for both human participants and the model (solid line: red, blue and green). 
    Generics about accidental properties do not result in such a high implied prevalence (solid line: purple and orange).  
	While the implications of generic utterances are highly variable across the different types of properties, the average prevalence that leads to an acceptable generic does not vary, for participants nor the model.
}
  \label{fig:exp2b}
\end{figure*}

## Experiment 4c: Interpreting generalizations about events

The RSA models described in their paper make predictions both about how generalizations in language will be endorsed as well as how they will be interpreted.
In this experiment, we explore participants' inferences about the likely rate of action upon hearing a habitual statement.

### Method

#### Participants

We recruited 50 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.

#### Procedure and materials

The materials in this experiment are the same as used in Expts. 4a & 4b.
On each trial, participants were supplied a habitual statement (e.g., "John runs") made by randomly pairing the event (e.g., *runs*) with either a male or female character name.
Participants were then asked how often they believed the person did the action (e.g., "How often do you think John runs?").
The dependent measure was the same as in the Event Prior Elicitation experiment (Expt. 1): A text box and a drop-down menu to rate the number of times (text box) the person did the action in some time window (drop-down menu).

### Results

#### Behavioral results

#### Model criticism and comparison

+ [Compare L0 to some adhoc model (maybe, mean of the distribution, or mean of the non-zero distribution?).]

## Jointly modeling endorsement and interpretation

+ [RSA model criticisms and comparisons on joint data set.]

## Experiment 7c: Interpreting Causal Language

In this experiment, we tested whether the manipulated priors of Expt. 5 are causally related to the interpretation of casusal statements.

### Method
Most of the experiment was identical to that of Experiments 5 \& 6.

#### Participants

We recruited N participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
None of the participants had participated in either Experiment 5 or Experiment 6.
The experiment took on average N minutes and participants were compensated \$N.NN for their work.

#### Procedure and materials

The materials were the same as in Experiments 5 \& 6.
Phase 1 of the experiment was identical to that of Experiments 5 \& 6.
In phase 2 of the endorsement task, the table and story were removed from the screen and the participant is told that the results of the "lost experiment" were found and that their colleague has reported to them about the results using the causal: "Treatment X makes the effect happen". 
Participants were then asked to guess how many out of the 100 of the attempts were successful.
Partipants responded using a slider bar that ranged from 0 - 100.

### Results

### 2017-06-07 paper/outline.Rmd
paper and appendices

---
title: "comgen-outline"
author: "M. H. Tessler"
date: "5/24/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

# The Bayesian Framework for Generlizations

# Communicating Generalizations with a Formal Model

- **Figure 1: L0(h|"silence") & L0(h|"generic") for uniform, are female, lays eggs, and has wings priors**

# Case Study 1: Generic Language

## Experiment 1: Endorsing generalizations about categories
### 1a: Measuring the prevalence prior with familiar kinds
### 1b: Endorsements

- **Figure 2: Endorsements vs. Prevalence, Prevalence + Cue Validity, Underspecified-threshold Model**
--- **include insets for L0 priors and posteriors**

## Experiment 2: Interpreting generalizations about categories
### 2a: Measuring the prevalence prior with unfamiliar kinds
### 2b: Interpretations

## Experiment 3: The asymmetry between truth conditions and interpretations (Replication and Extension of Cimpian et al., 2010)

## Discussion
  - Conceptual structure

# Case Study 2: Habitual Language

## Experiment 4: Endorsing and interpreting generalizations about events
### 4a: Measuring the propensity prior for event knowledge
### 4b: Endorsing generalizations about events
### 4c: Interpreting generalizations about events

## Experiment 5: Communcaiting predictive propensity

## Discussion
  - Predictive probabilities

# Case Study 3: Causal Language

## Experiment 6: 
### 6a: Prior elicitation / manipulation check
### 6b: Endorsement
### 6c: Interpretation

## Discussion

  - Prevalence prior is causally related to endorsement and interpretation

# General Discussion

## Comparison class
## Acquisition
## Conceptual structure
  -- Dangerousness
## Predictive propensities
## Relationship to extant theories
## Solutions to other philosophical puzzles

# Conclusion

### 2017-06-08 paper/appendix-alternativeRSAmodels.Rmd
create alt models appendix; begin full posterior appendix

--- 2017-06-07 paper/generics-paper.Rmd
@@
----
-title             : "Communicating generalizations about categories, events, and causes"
-shorttitle        : "Communicating generalizations"
+# Appendix A: Alternative Rational Speech Act (RSA) models
 
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
+The pair of speaker-listener models presented in the main text correspond to the simplest possible communicative models with an underspecified threshold meaning for a generalization. 
+The Rational Speech Act framework defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
 
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-
-author_note: >
-  Enter author note here.
-
-abstract: > 
-    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
-    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
-    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    One major issue in formalizing *genericity* is that such language is extremely flexible in its usage. 
-    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about events (i.e., *habitual language*, e.g., *John runs*), causes (i.e., *causal language*, e.g., *The block makes the machine play music.*), and categories (i.e., *generic language*, e.g., *Birds fly*), and find that the model, and not simpler models, explains full spectra of endorsements of generalizations in language.
-    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
-
-keywords          : "genericity, generalizations, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "X"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-<!-- \newcommand{\ndg}[1]{\textcolor{Green}{$[ndg: #1 ]$}} -->
-<!-- \newcommand{\mht}[1]{\textcolor{Blue}{$[mht: #1 ]$}} -->
-<!-- \newcommand{\red}[1]{\textcolor{Red}{$#1$}} -->
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
-
-```
-
-```{r include = FALSE}
-library("papaja")
-```
-
-```{r libraries}
-library(rwebppl)
-library(xtable)
-library(tidyverse)
-library(forcats)
-library(langcog)
-# library(tidyr)
-# library(dplyr)
-library(data.table)
-library(coda)
-library(ggthemes)
-library(ggrepel)
-library(jsonlite)
-theme_set(theme_few())
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-project.path <- "~/Documents/research/comgen-paper/"
-options("scipen"=10) 
-```
-
-# Introduction
-
-Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge for a cognitive agent.
-We learn such *generalizations* early in life by observing instances and drawing inductive inferences [@Dewar2010].
-Social learning---relying upon the human capacity to infer others' intentions---faciliates this process [@Csibra2009; @Tomasello1999; @Butler2012].
-At around a child's first birthday, her mind gains access to a new, human-unique source of data: language.
-
-<!-- give rise to the productivity of human thought and form of foundations of cultural knowledge. -->
-<!-- They allow us to understand the complex world around us and dream up how possible future situations might unfold. -->
-<!-- It's been suggested that were psychology to have *general laws* akin to Newtonian laws in physics, the first general law in psychology would be of generalizations [Shepard1987]. -->
-<!-- Generalizations are central to human understanding.  -->
-<!-- Even before birth, human and non-human animals alike gather statistical information and form generalizations to predict what will come next. -->
-<!-- The human learner, perhaps uniquely in the animal kingdom, displays striking sensitivity to the intentional and pedagogical actions of others, leading to distinct and often stronger inferences from data than would otherwise be warranted from random observations.
--->
-
-Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Graham2004; @Markman1989].
-But language also has the ability to refer to *generalization itself*.
-At around the age of two and a half, children begin to understand that *generic language* (e.g., "Dogs bark") refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are central to the growth of conceptual knowledge [#Gelman2004] 
-Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
-It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].
-
-Computational models of learning formalize the inferences derived from observations, focusing on the question of how children and adults generalize from sparse data [@Tenenbaum2011]. 
-They showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
-Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000].
-Probabilistic models have recently made progress in describing pragmatic language understanding in precise terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
-These models of rational communication describe inferences one can draw from language about *particular* situations: utterances that convey information about a specific entity or event.
-The language of generalizations --- statements that extend beyond the here-and-now --- has heretofore eluded precise formalization.
-
-The major issue in formalizing generic language is determining what makes a generic statement true or false. 
-When we hear *Dogs bark*, we may feel it's a universal statment as in *All* dogs bark.
-We may then realize that, among others, exquisitely well-trained dogs do not bark, which means the generic should signal something weaker like *Most* dogs bark.
-Indeed, many generic statements seem to have the quantificational force of *most*. 
-But most mosquitos do not carry malaria, while the statement *Mosquitos carry malaria* is intuitively true.
-So the generic must in some way be compatible with *some* (e.g., *some mosquitos carry malaria*).
-But equating the generic with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
-Perhaps properties that only apply to one gender are an exception, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
-
-Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization.
-*Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general (e.g., *You never know what will happen on a blind date*), specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
-Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious. 
-Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.
-
-In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to define the truth conditions of generalizations in language. 
-By formalizing such a hypothesis in a probabilistic language understanding model, we derive predictions for endorsements of such statements by specifying relevant prior knowledge.
-Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-We do this in three domains: generalizations about categories, events, and causes. 
-In each domain, we define a scale that corresponds to the relevant metric by which a learner should generalize. 
-We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fail.
-
-The rest of this paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in different domains. 
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this uncertain semantics into a general framework for pragmatic language understanding -- the Rational Speech Act framework.
-
-To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
-Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments the measure both (i) and (ii) and relate it to the endorsements of generalizations about categories, or *generic language*. 
-In Section 4, we describe experiments that measure (i) and manipulate (ii) to predict endorsements of generalizations about events, or *habitual language*.
-In Section 5, we describe experiments that manipulate both (i) and (ii) to predict endorsements of generalizations about causes, or *causal language*. 
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
-In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literature on *genericity*.
-Our theory also opens up a number of new directions for understanding generic language and building models that learn and think like people.
-
-<!-- ALTERNATIVE INTRO -->
-
-<!-- Yet, generalizations can be hard to acquire. -->
-<!-- Consider what it would take to learn that under certain conditions (e.g., when eaten raw) a plant is poisonous, while under other conditions (e.g., when processed appropriately) the plant is nutritious.
--->
-<!-- This is a common ecological problem and historical examples suggest that humans are not particularly good at learning such generalizations [e.g., the Australian explorers case; @Henrich2015]. -->
-<!-- In this domain, the relationship to be learned (i.e., between different ways of food processing and the poisonousness of the plant) is non-obvious and trial-and-error learning is costly (negative examples entail death).
--->
-
-<!-- Crucially, once acquired, such hard-won generalizations can be communicated among humans, something which other animals struggle to accomplish [cite tomasello apes something]. -->
-<!-- Generalizable knowledge can be inferred through demonstration, or in pedagogical contexts when ostensive cues are present [@Csibra].  -->
-<!-- By and large, however, language provides the most flexible and generative way to communicate generalizations.  -->
-
-<!-- A generalization provides a relation between a category and a property: It tells us to predict that property of future instances of the category [@HumeTHN]. -->
-<!-- Generalization can be described as a probability and inductive inference as a probabilistic model [@Tenenbaum2011]. -->
-<!-- From a very young age, children make strong inductive inferences from their experience in a way consistent with the Bayesian probability calculus [@Dewar2010; @Gelman1986; @Markman1989]. -->
-
-<!-- If generalizations can be described by predictive probabilities, it would stand to reason that the most direct way to communicate a generalization would be to convey probability.  -->
-<!-- Ironically, humans are very bad at describing and interpreting probabilities explicitly [@Tversky1974]. -->
-<!-- Rather than be a deficiency, however, the difficulty we have in understanding numerical descriptions of probability might reflect the flexible adaptivity of natural language to make vague or ambiguous that which shared context can be relied upon to guide interpretation [@Piantadosi2012].
--->
-<!-- If language has evolved in a way to make efficient the kinds of inductive inferences that are central to human cognition, we would expect the language of generalizations to be simple [c.f., @Leslie2008].
--->
-
-<!-- Indeed, generalizations in language (e.g., *Dogs are friendly*, *Mary smokes cigarettes*, *Yeast makes bread rise*) are among the simplest forms of compositional expressions.  -->
-<!-- Generalizations do not come in just one syntactic form: "*Dogs* are friendly", "*A library book* should be treated with respect", "*The contemporary foodie* seeks culinary experinces in menu-less restaurants and grandmothers' kitchens" [@Carlson1995; @NickelBlackwell; @sepGenerics].
--->
-<!-- Each of these statements has in common the fact that they predicate a property of a category and the properties themselves apply to instances of the category (unlike, e.g., *Dinosaurs are extinct* because being extinct is not a property that can be true of a particular dinosaur).
--->
-<!-- In this way, these statements exhibit *genericity*, or put another way, they convey generalizations. -->
-
-<!-- In this paper, we formalize the language of generalizations with the interest is deciding what makes a generalization in language *true or false*. -->
-<!-- How speakers convey generalizations and how listeners interpret them. -->
-
-<!-- We examine three case studies of generalizations in language: Generalizations about agents, objects, and events.  -->
-<!-- In Section 1, we introduce an information-theoric communicative theory of how generalizations are conveyed in language and flesh out the model's predictions alongside alternative models. -->
-<!-- In order to do so, we provide a unified mathematical framework for dealing with agents, objects, and events, casting each as a category over which generalization can occur. -->
-<!-- Our model predicts the endorsements of generalizations should vary with the (A) the probability of an instances having the property and (B) the prior distribution over the property probability (e.g., how likely instances of other categories are to have the property).
--->
-<!-- In Section 2, we introduce our empirical paradigm which we use to measure endorsement and interpretation of linguisitic generalizations, examining generalizations about *agents* in what is known as *habitual language* (e.g., "Mary smokes cigarettes.").
--->
-<!-- In Section 3, we extend our paradigm to generalizations about *events* (i.e., *causal language* e.g., "Yeast makes bread rise.") and experimentally manipulate participants' background knowledge, showing that prior beliefs about probabilities are causally related to endorsement and interpretation of generalizations.
--->
-<!-- In Section 4, we use our paradigm to address long-standing theoretical and empirical puzzles regarding generalizations about *objects*, so-called *generic language*.  -->
-<!-- We show our how model explains three known psychological puzzles surrounding generic language.  -->
-<!-- In all case studies, we provide formal comparison to simpler models and in all cases, find that only our communicative theory explains the patterns of empirical data. -->
-<!-- We conclude with a general discussion about the relationship of our theory to extant theories in the psychology, linguistics, and philosophy of genericity, and highlight the implications for modeling language acquisition, conceptual development, and other avenues of research that this framework opens.
--->
-
-<!-- the truth conditions of generalizations of events (so called *habitual language*) by manipulating the target propensity (A) while surveying a wide variety of events (which should induce variability in B).
--->
-<!-- In Section 3, we manipulate both (A) and (B) while testing the model on generalizations about causes (*causal language*). -->
-<!-- If our theory is truly a theory about communicating generalizations, it should be able to explain the known psychological puzzles surrounding *generic language* (generalizations about categories).
--->
-
-<!-- In stark constrast, a computational understanding of communicating generalizations is not well understood at all.  -->
-
-<!-- Gathering data and observing evidence, however, is costly.  -->
-<!-- The human problem of induction even displays a complex sensitivity to not only the type of data, but how the data was generated [@Gweon2010; @Shafto2012]. -->
-<!-- A learner cannot form all of her abstract knowledge through direct experience, however. -->
-<!-- Life is only so long, and you can only be in one place at a time. -->
-
-<!-- In this paper, we introduce a formal model for understanding the language of generalizations. -->
-<!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning.
---> -->
-<!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning).
--->
-<!-- We extend a rational model of communication --- the Rational Speech Act theory --- to be able to understand general statements that extend beyond the here-and-now. -->
-<!-- We provide a number of stringest tests of this theory to explain generalizations about categories, events, and causal forces.  -->
-
-<!-- How can generalizations in language have such flexible truth conditions while simultaneously carrying intuitive and, at times, very strong implications? -->
-<!-- This question has been investigated by psychologists, linguists, and philosophers since @Carlson1977. -->
-<!-- Here, we provide a unified formal theory of generalizations conveyed in language. -->
-<!-- We test theory on the preeminent case study of linguistic generalizations: generic language, or generalizations about categories. -->
-<!--  -->
-<!-- To be precise, we develop a computational model that describes pragmatic reasoning about the propensity required to assert the generaization.   -->
-<!-- We find that this formalism resolves known philosophical and empirical puzzles. -->
-<!--We also provide the first set of experimental results about linguistic generalizations about events and causal forces, so called *habitual* and *causal statements*.-->
-
-<!-- and find extreme flexibility in usage, which our model predicts.  -->
-
-<!-- In Section 2, we conduct a set of experiments to test the *truth conditions* of familiar generalizations about categories (generic statements), and find our model predicts key patterns in human judgments -->
-<!-- In Section 3, we conduct a set of experiments to test *interpretations* of novel generic sentences, again finding our model predicts human judgments with high quantitative accuracy. -->
-<!-- In Section 4, we begin to test the generality of the theory, examining the *truth conditions* of generalizations about events. -->
-<!-- In Section 5, we further probe our theory's generality, investing the *truth conditions* and *interpretations* of novel generalizations about causal forces.  -->
-<!-- In all cases, we provide formal comparison to simpler models and in all cases, find that only our communicative theory with an underspecified meaning function explains the pattern of human data.
--->
-<!-- We also find that the prior beliefs used in our model reflect conceptual structure, and this provides an understanding of the conceptual implications of generics. -->
-<!-- Finally, we investigate the underlying semantic scale in more detail, and find that the core meaning of generalizations in language depends in a crucial way on subjective beliefs, not mere frequency.
--->
-
-<!--
-Most would agree that \emph{Swans are white}, but certainly not every swan is.
-This type of utterance conveys a generalization about a category (i.e. \textsc{swans}) and is known as a generic utterance [@Carlson1977; @Leslie2008].
-Communicating generically about categories is useful because categories themselves are unobservable [@Markman1989].
-Knowledge about categories, while central to human reasoning, is tricky to acquire because categories themselves are unobservable [Markman1989}.
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are essential to the growth of conceptual knowledge [@Gelman2004] and how kinds are represented in the mind [@Leslie2008].
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and children as young as two or three understand that generics refer to categories and support generalization [@Cimpian2008].
-and though English and many other languages do not possess an unambiguous form devoted to generic meaning [@Behrens2000, @AlMalki2014].
-Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@GelmanEtAl2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010motivation].
-Despite their psychological centrality, apparent simplicity, and ubiquity, a formal account of generic meaning remains elusive.
-
-How can generics have such flexible truth conditions while simultaneously carrying strong implications?
-In this paper, we explore the idea that the core meaning of a generic statement is simple, but underspecified, and that general principles of communication may be used to resolve precise meaning in context.
-In particular, we develop a mathematical model that describes pragmatic reasoning about the degree of prevalence required to assert the generic.  
-We find that this formalism resolves the philosophical and empirical puzzles.
--->
-
-# The Bayesian Framework for Generalizations
-
-Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
-From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
-To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
-The linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
-To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
-That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
-We call this kind of statement a *particular*.
-
-```{r table-generalization, results="asis"}
-df.tab <- data.frame(
-  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
-  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
-  "Generalization over" = c("Category", "Event", "Cause"),
-  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
-  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
-  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
-  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
-) #%>% xtable(., 
- #        caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
-  #       label = c("tab:genpart"))
-
-apa_table(df.tab, 
-          caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
-          escape = TRUE, small = TRUE
-)
-
-#print(df.tab,  type = "latex", tabular.environment = "tabularx", width = "\\textwidth",  include.rownames = FALSE, comment = F)
-```
-
-We can make particular statements about objects, events, and causes.
-We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
-To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must say exactly how the particular relates to the generalization.
-We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
-Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).
-
-Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
-For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
-With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
-].
-In the study of categories and properties, $x$ is an object.
-For a behavior exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
-In this case, $x$ is a instance of an agent.
-Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$: $h = P(x \in e \mid x \in c)$.
-We refer to this probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
-<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->
-
-<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
-Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
-As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the friendliness of dogs.
-
-$$
-P(h \mid d) = \frac{P(d \mid h) \cdot P(h)}{\int_{h'}P(d \mid h') \cdot P(h')}
-$$
-
-Our ability to use this updated belief $P(h \mid d)$ in order to make predictions about unobserved instances is a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011].
-
-The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
-Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
-For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
-Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent [@Goodman2009].
-Quantitative modeling has been crucial in explaining how the subtleties of experience relate to subtleties in generalization [@Tenenbaum2006; @Kemp2008].
-
-Studying generalizations from observational evidence can only take us so far in understanding how the mind understands the world or culture accumulates across generations.
-Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
-For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
-
-# Communicating Generalizations with a Formal Model
-
-We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the formalization described in the previous section.
-Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly").
-Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .
-
-Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
-At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
-*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs (not exactly *most robins*). 
-If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
-Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
-It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.
-
-These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
-The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.
-
-The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
-*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a dangerous world.
-This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which has been empirically verified [@Cimpian2010; @Prasada2013].
-Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].
-
-Yet, generics are not limited to conveying rich relations. 
-Arbitrary relations can also be expressed like *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
-The *generics as default* view must then be supplemented with the principle that, in certain situations, the statistics can influence generic endorsement.
-How do we make sense of this panoply of conditions?
-Is there some more general, unified principle that explains what makes generic statements true or false?
-
-Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
-The basic currency of inference in these models is probability.
-In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
-If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement.
-
-\begin{eqnarray}
-L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed}
-\end{eqnarray}
-
-Equation \ref{eq:L0fixed} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
-$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
-The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
-We term this prior distribution the *prevalence prior*.
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
-For an utterance conveying a generalization $u_{gen}$, we adopt a simple threshold semantics:
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
-&\propto  &
-\begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}
-\end{eqnarray}
-
-The $\delta_{\denote{u}(h, \theta)}$ likelihood is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
-Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
-What threshold $\theta$ should be used for the generic generalization?
-We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
-In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
-We assume this prior is uninformed: $\theta \sim \text{Uniform}(0, 1)$.
-
-\begin{eqnarray}
-L(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (a threshold function) but underspecified.
-Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq.
-\ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
-The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
-"Some" rules out only the lowest possible state and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.
-
-The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
-If the threshold is very high, only the highest $h$ would pass the threshold.
-If the threshold is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
-As the threshold takes on lower and lower values, more and more probabilities would surpass it.
-When the threshold is very low, almost all probabilities are consistent with it (akin to "Some").
-When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.
-
-In this paper, we are interested in explaining the variable endorsements of generalizations based on some known or believed probability $h$.
-Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).
-\begin{equation} 
-S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
-\label{eq:S1}
-\end{equation}
-
-In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
-Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
-The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
-To model generic endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
-with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
-Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
-This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]:
-
-\begin{equation*}
-\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
-1 &\text{for all h}\ 
-\end{cases}
-\end{equation*}
-
-Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[
-A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate.
-Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind. 
-In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution: 
-$U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
-]
-
-<!-- This decision is based on whether or not the generalization would accurately convey the $h$ -->
-<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
-\ref{eq:L0}).
--->
-
-<!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } -->
-
-<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
-<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
--->
-<!-- \begin{equation} -->
-<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
-<!-- \label{eq:utilS1marginalization} -->
-<!-- \end{equation} -->
-<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
-<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
-<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
-<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
-<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
-<!-- ] -->
-<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
-
-<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g., *Mosquitos carry malaria*; *Robins lay eggs* v. *Robins are female*). -->
-
-<!-- Abstract mental representations, then, may thus be influencing generic endorsement via its influence on subjective probability. -->
-
-<!-- To understand how generalizations are conveyed in language, we start by considering general purpose language understanding principles. -->
-<!-- Foremost, understanding language depends upon assumptions interlocutors make about each other and can exhibit a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000]. -->
-<!-- Though once viewed as a wastebasket in which to dump unexplained loose ends in service of more rigorous formal analysis, *pragmatics* --- or language understanding in context --- has seen an emergence of formal frameworks that connect closely with behavioral data [@Franke2015].
--->
-
-<!-- One dominant framework --- the Rational Speech Act theory --- has had considerable success in providing a formal account of pragmatic language phenomena [i.e., interactions between language and context; @Goodman2016].
--->
-<!-- This framework has been used to explain, in precise mathematical terms, how it is that utterances like "some of the kids failed the test" are interpreted to mean "some (but not all) of the kids failed the test" [@Goodman2013], how "I waited a million years to get a table" is interpreted as "I waited an obnoxiously long time to get a table" [@Kao2014], how "John is tall" can mean John is 5'4" is John if a 12-year-old but means John is 6'2" if he is 24-years-old [@Lassiter2015], and how "Your talk was fine" can be a polite way of saying your talk was less than fine [@Yoon2016].
--->
-<!-- Computational modeling has pushed our understanding of these complex linguistic phenomena, but so far, rational models of language use have focused on *specific* statements: utterances that convey information about a particular entity or situation.
--->
-<!-- A formal theory of statements that convey generalizations about entities or situations ---  statements that extend beyond the here-and-now --- has remained elusive. -->
-
-<!-- Formalizing the meaning of linguistic expressions requires specifying *truth conditions*, or the states of the world in which the expression is true vs. false. -->
-<!-- Using the tools of formal semantics, we specify a *truth function*: A function from states of the world to truth-values.  -->
-<!-- A simple truth function for a generalization could be a threshold on an agent's posterior probability: $\denote{u_{generalization}}(h, \theta): \{ h: h > \theta\}$, where $\denote{u_{generalization}}$ represents a function from a state of the world $h$ and a threshold variable $\theta$ to the set of the states of the world where $h > \theta$.
--->
-<!-- Applying this function to a set of worlds returns a set of worlds that are consistent with $h > \theta$. -->
-
-<!-- Though intuitively appealing and simple, this threshold-based truth function for a generalization is problematic. -->
-<!-- <!-- fixed value of $\theta$ seems unlikely. --> -->
-<!-- The generalization *Mary smokes cigarettes* suggests a daily-habit (e.g., $h > \text{once a day}$), while *Bill writes poems* implies something much weaker, perhaps a poem every few weeks (e.g., $h > \text{once a month}$.
--->
-<!-- *Drinking moonshine makes you go blind* and so does *staring at the sun*, but neither causal statement tells you to precisely the increased relative risk. -->
-<!-- *Mosquitos carry malaria* is a true statement despite the prevalence of carrying malaria among mosquitos being a just a fraction of 1\%, while *Ducks are female* might seem like a weird thing to say, even though the rate is much higher than the malaria-carrying mosquitos.
--->
-<!-- Finally, *Ducks lay eggs* is a good generalization, though the rate is the same as *Ducks are female*. -->
-<!-- The meaning of generalizations, it seems, cannot reduce to a single, precise quantitative statement; this is the major stumbling block to providing a formal account of genericity [@Carlson1977; @Leslie2008; @NickelBlackwell].
--->
-
-<!-- We hypothesize the simple threshold-based truth function for lingusitic generalizations can be rescued by positing an *underspecified* meaning.  -->
-<!-- That is, we adopt a threshold semantics as described above, but imagine that $\theta$ is not a fixed property of language but rather is drawn from a prior probability distribution. -->
-<!-- In this formulation, listeners infer thresholds along with speakers' intended meanings in context. -->
-<!-- We formalize this hypothesis with a "literal listener" model from the Rational Speech Act framework [@Frank2012; @Goodman2013; @Goodman2016]. -->
-
-<!-- *Bills writes poems* might true if Bill does it a few times a year, while we might be hesitant to say *Mary smokes cigarettes* if she only does it once every few months. -->
-<!-- *Ducks lay eggs* is true despite only the female ducks laying eggs, while *Ducks are female* is strange to say (even though only the females are female). -->
-
-<!-- The language of generalizations is so simple that it appears everywhere in human conversation (*Movie theaters are cold.*), pedagogy (*The blicket makes the machine play music.*), political and scientific discourse (*The President peddles falsehoods.*, *Psychology experiments don’t replicate.*), stereotypes (*Boys are good at math*), motivation (*Big girls eat their broccoli!*), emotion-regulation  (*Accidents happen.*), child-directed (*Mommy works late*) and child-produced speech (*Slides aren't for grown-ups!*), and many other facets of experience [@GelmanEtAl2004; @Gelman2008; @Cimpian2010motivation; @Rhodes2012].
--->
-
-<!-- Though the language of generalizations is found everywhere and in every language [@Behrens2005; @Carlson1995], the meaning of such linguistic expressions is philosophically puzzling and has resisted precise formalization.
--->
-<!-- Intuitively, generalizations should convey something about the probability of an instance of the category to have a property, but exactly what is conveyed is unclear. -->
-
-<!-- What if we leave the $\theta$ underspecified in the semantics? -->
-<!-- That is, what would a listener believe if she drew $\theta$ from an uninformed prior belief distribution: $P(\theta)$?^[ -->
-<!-- Previous attempts have been made to salvage this threshold semantics, using a semantic a technique called "domain restriction", wherein the scope of generalization is restricted to a smaller subset of entities or instances [e.g., "only female ducks"; @Cohen1999].
--->
-<!-- Though effective at dealing with at least some of these semantic puzzles, this approach leaves unresolved why the domain should be restricted in some cases and not others. -->
-<!-- We return to this more fully in the General Discussion. -->
-<!-- ] -->
-
-<!-- [MHT: talk about soft semantics here?] -->
-
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-
-<!-- The threshold $\theta$ is assumed to be drawn by an uninformative prior distribution, defined on the same scale as the probability $h$: $\theta \sim \text{Uniform}(0, 1)$.^[ -->
-<!-- Though it's plausible that different thresholds could be learned for different domains, we assume an uninformed prior distribution in our model to show how background knowledge about how the world works drives inferences.
--->
-<!-- ] -->
-<!-- Finally, the prior distribution $P(h)$ is a distribution over the degrees of probability. -->
-<!-- The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenabum2006; @Kemp2008].
--->
-<!-- This is a simple Bayesian model of interpreting a statement conveying a generalization. -->
-
-```{r simluationsModel, eval = T, cache = T}
-
-l0.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
-'
-
-priorNames <- c(
-  "uniform", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria"#,
- # "areSick"
-  )
-priorShapes <- list(
-  uniform =  list(params = data.frame(a = 1, b = 1), mix = 1), 
-  #uniformRare =  list(params = data.frame(a = 1, b = 1), mix = 0.4), 
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  #eatsFood =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  #areSick =  list(params = data.frame(a = 1, b = 5), mix = 1), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-all.simulations <- data.frame()
-for (p in priorNames){
-  for (u in c("generic", "some")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
-    )
-  }
-  #print(p)
-}
-```
-
-```{r simulations, fig.width = 8, fig.height=5}
-all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                             c("Prior_some", "Posterior_Generalization_some", "Posterior_Generalization_generic"),
-                                labels = c("Prior/Silence", "Some", "Generalization")),
-         PriorShape = fct_relevel(PriorShape, "uniform", "barks","laysEggs","carriesMalaria","isFemale"
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         ) %>%
-  ggplot(., aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = Distribution, fill = Distribution))+
-    geom_density(#stat= 'identity', 
-                aes(y = ..scaled..),
-                 size = 0.6, alpha = 0.7, adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    #scale_color_solarized()+
-    #scale_fill_solarized()+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   scale_fill_manual(values = c("#636363", "#2b83ba","#d7191c"))+
-    scale_color_manual(values = c("#636363","#2b83ba", "#d7191c"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    xlab("Degree of propensity (probability)") +
-    ylab("Probability density") +
-  facet_grid(PriorShape~Distribution, scales = 'free')+
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
-\ref{eq:L0}).
--->
-
-<!-- <!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } --> 
-<!-- \begin{equation}  -->
-<!-- S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h)  } -->
-<!-- \label{eq:S1} -->
-<!-- \end{equation} -->
-
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda$. -->
-<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
-<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
--->
-<!-- \begin{equation} -->
-<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
-<!-- \label{eq:utilS1marginalization} -->
-<!-- \end{equation} -->
-<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
-<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
-<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
-<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
-<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
-<!-- ] -->
-<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
-
-## Alternative formulation
-
-The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold meaning for a generalization. 
-The Rational Speech Act framework defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-For the most basic formulation of an RSA model, the level of recursion for a model can be unidentifiable from the 
+Note that for the for the intial, simplest formulation of an RSA model, the level of recursion for a model can be unidentifiable from the 
 "speaker optimality" model parameter in Eq. \ref{eq:S1} [@FrankEtAlUnderReview].
-For our model, with an uncertain threshold variable, theoretically meaningful different models can be formulated in the pragmatic framework.
+For our model, however, with an uncertain threshold variable, theoretically meaningful different models can be formulated in the pragmatic framework.
 
@@
 In that work, the authors argued that understanding adjectives required a "pragmatic listener" [i.e., a listener who thinks about a speaker who thinks about a listener; @Lassiter2015]. 
-In their model, the threshold variable was "pragmatically lifted", meaning the uncertainty over the threshold variable was resolved using pragmatic reasoning [a so-called uRSA model; @Goodman2016].
+In their model, the threshold variable was "pragmatically lifted": The uncertainty over the threshold variable was resolved using pragmatic reasoning [a so-called uRSA model; @Goodman2016].
 In the case of our model of generalizations, we can compare the simple model we described above to a more sophisticated model that resolves the threshold using pragmatic principles.
 
-### Listener models
+## Listener models
 
@@
 
-### Speaker models
+## Speaker models
 
@@
 \end{eqnarray}
-
-All models were implemented in the probabilisitic programming language WebPPL [@dippl], and a complete, runable versions of the models in the following section can be found at \url{http://forestdb.org/models/generics.html}
-
-## Model simulations
-
-All of the RSA models defined in the previous section predict that the interpretation and endorsement of a generalization depends listener's *a priori* beliefs about the probabilty in question $P(h)$.
-Qualitatively, the predictions of the different formulations of the RSA models for understanding generalizations are not appreciably different (though their quantitative predictive flexibility is).
-For purposes of illustration, we present present predictions of the simplest model with an underspecified threshold and a model where the threshold is fixed to 0 (corresponding intuitively to *some* statements).
-
-Before, we described how an underspecified threshold interacts with a uniformly uncertain belief about the probability.
-Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
-Our model of endorsements is a model of speaker who decides whether or not to say the generic or stay silent. 
-Thus, qualitatively model predictions for endorsement can be gleaned by comparing the prior distribution over the probability $h$ (which is the same as posterior upon hearing "silence") with the posterior distribution over $h$ upon hearing the generalization.
-
-In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
-Here, we show the prior is bimodal with peaks at 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have 0\% prevalence) and for those that do have members that bark, many of them bark (i.e., have some high prevalence value).
-The fact that "those that do not bark" is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who does not usually bark (say, a cat) could somehow have the feature (e.g., due to some transient or accidental state).
-We see that the quantifier "Some" (middle row) struggles to differentiate those that accidentally do have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.
-Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.
-
-The strength of a listener's inference (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over the prevalence of the feature.
-Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
-The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than with "barks" prior: The listener thinks that about 50% of robins lay eggs.
-Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
-The intuitive differences in the endorsements of these statements comes from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
-In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content.
-
-Finally, we look at how a listener would interpret the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-Indeed, we see that for the prior over "carries malaria", which *a priori* assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread, the listener's posterior upon hearing the generalization is similar to what she learns about hearing "Some mosquitos carry malaria".
-Thus, a speaker who believes "some but very few" mosquitos carry malaria will still endorse the generalization.
-
-In the rest of this paper, we examine the validity and generality of this theory of communicating generalizations through three case studies: generalizations about categories, events, and causes.
-
-<!-- Consider how an uniformly underspecified threshold would interact with a uniformly uncertain belief about a probability (recall the thresholds defines what probabilities or states of the world should be ruled out).
--->
-<!-- If the threshold is very high, only the highest probabilities would be left (i.e., pass the threshold). -->
-<!-- If the threshold is slightly lower but still high, the highest probabilities would still pass the threshold, as would some that are slightly lower. -->
-<!-- As the threshold takes on lower and lower values, more and more probabilities would surpass it. -->
-<!-- When the threshold is very low, almost all probabilities are consistent with it. -->
-<!-- But since we don't know *a priori* what the threshold is likely to be, each of theses situations is plausible. -->
-<!-- The posterior distribution on probabilities or states of the world will favor higher probabilities (because they pass more thresholds), but will still include probabilities that are quite low [though they are *a posteriori* unlikely; see Figure \ref{fig:simluations} ].
--->
-<!-- Speakers, thus, will produce generalizations with some probability in each state of the world, though the speaker will say the generalization more often when the propensities associated with the states of the world are higher [see Figure \ref{fig:simluations}].
--->
-
-<!-- - Figure -->
-  <!-- - Subfigure 1 [width = 0.2] (Uniform priors) [two rows, left subfigure] -->
-  <!--   -- Basic L0 posteriors on degrees for uncertain, fixed at 0 and fixed at 0.5 -->
-  <!--   -- Basic S1 posteriors on utterances, for prevalence 0 - 1 (and for fixed thresholds) -->
-  <!-- - Subfigure 2 [width = 0.8] (L0 vs. L1 lifted vs. L1 unlifted x 4 priors x {speaker, listener} ) [model as color, lty; priors as columns x {speaker, listeners} as rows]  -->
-  <!--   -- priors = [uniform, n-shaped, u-shaped, mixture model / maybe put more in appendix: rare, accidental, female, eggs] -->
-
-<!--
-mht: is it possible to construct priors in causals that would reflect the qualitative prediction shown here?
--->
-
-<!-- $P(x)$ is a distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across animal categories.  -->
-<!-- In Figure \ref{fig:schematic-unif}, are $L_1$ (Eq.~\ref{eq:L1}) posterior prevalence distributions on $x$ (red solid line) for several example prior prevalence distributions $P(x)$ (blue dashed line), as well as the $S_2$ generic endorsement probability for different levels of prevalence.
--->
-<!-- We name these example prior distributions to suggest properties that might be associated with such priors.  -->
-<!-- (Later, we will empirically measure these priors for properties of interest.) -->
-<!-- First, we explore generic interpretation and endorsement for priors of three different shapes (left column).  -->
-<!-- For each of these, the $L_1$ posterior distribution (red solid) over prevalence is heavily driven by the prior (blue dashed). -->
-<!-- $S_2$ endorsement probabilities for the generic (black solid) increase as a function of prevalence, and what counts as "true" (in terms of the prevalence) depends on the prior.  -->
-
-<!-- \begin{figure} -->
-<!-- \centering -->
-<!--     \includegraphics[width=\columnwidth]{figs/schematics_s2.pdf} -->
-<!--     \caption{Schematic prior distributions for prevalence $x$ (blue dashed), the pragmatic listener $L_1$ model's posterior distribution over prevalence upon hearing a generic utterance (red), and speaker $S_2$ model's endorsement of a generic utterance for different levels of prevalence (black).
--->
-<!--     The names given to these priors are meant to be suggestive of what kinds of properties these distributions might correspond to. -->
-<!--     The left column uses prevalence priors modeled as Beta(15,15), Beta(4,1), and Beta(4,16) distributions. -->
-<!--       The right column uses a prior distribution that is a mixture of the distribution to the left of it with a second component, modeled as Beta(0.5, 4.5), reflecting categories with 0\% property prevalence.
--->
-<!--     Horizontal dashed line at 0.5 is for convenience of comparing the point at which an utterance becomes judged as more true than false for $S_2$. -->
-<!-- 	Note that the prior distribution over prevalence will be the same as $L_1$'s posterior distribution upon hearing the "null" utterance. -->
-<!--     } -->
-<!--   \label{fig:schematic-unif} -->
-<!-- \end{figure} -->
-
-<!-- To take one example, consider the distribution over what might be the property "are female" (top-left facet). -->
-<!-- The \emph{a priori} prevalence is centered around 0.5. -->
-<!-- Because of pragmatics, the pressure to be \emph{truthful} will drive likely threshold values below 0.5 (lower values are more likely to be true).  -->
-<!-- At the same time, the pressure to be \emph{informative} will drive the threshold values up: Higher values are more likely to be informative.  -->
-<!-- The result is a posterior over prevalence that is only marginally greater than the prior, making higher prevalence values more likely after hearing the generic.  -->
-<!-- But the relative information gain is very little (the posterior is not very different from the prior), and thus the $S_2$ model is reluctant to endorse the generic unless the property is exceedingly prevalent.
--->
-<!-- The same basic phenomenon can be observed for the other two example priors (left column): The posterior over prevalence heavily depends upon the prior, but is also not very different from the prior.
--->
-
-<!-- We now imagine what would happen if there were some kinds where the property was completely absent, while being present at some rate in other kinds. -->
-<!-- Figure \ref{fig:schematic-unif} (right column) shows this possibility: mixing the distribution to the left of it with a second component at 0\% prevalence. -->
-<!-- Consider the schematic prior over "lay eggs". -->
-<!-- We see the pragmatic listener $L_1$'s posterior prevalence distribution is not very different from the interpretation that doesn't include the second component in the prior (here, "are female"), but it is dramatically different from the prior with two components (compare red with blue dashed line for the right column).
--->
-<!-- This suggests that when many categories have 0\% prevalence, lower thresholds are informative.  -->
-<!-- Indeed, the $S_2$ model predicts that the generic becomes felicitous at lower prevalence levels (compare black line of left v. right column). -->
-<!-- For "lay eggs", when the property is prevalent in 50\% of the kind (e.g., 50\% of birds lay eggs), endorsement of the generic (e.g., \emph{Birds lay eggs}) by the $S_2$ is roughly 0.85; for "are female", with the same prevalence (50\% of birds are female), endorsement for \emph{Birds are female} is only 0.50: It is judged to be neither true nor false.
--->
-<!-- The important result is the asymmetry: the first generic can be endorsed more strongly than the second, at the same prevalence level; the exact endorsement rates depend on quantitative aspects of the priors, which must be determined empirically.
--->
-
-<!-- The model thus predicts differences in truth judgments depending on the prevalence prior.  -->
-<!-- The first test of our theory, then, will be to see if these predictions correspond to human truth judgments of familiar generic sentences.  -->
-
-<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
-<!-- \begin{eqnarray} -->
-<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
-<!-- \end{eqnarray} -->
-<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->
-
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-<!-- In this model, a threshold $\theta$ is established in context by a Bayesian listener reasoning about what threshold would make this utterance true? -->
-
-<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-
-<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise.
--->
-<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->
-
-<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
-<!-- \begin{eqnarray} -->
-<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
-<!-- \end{eqnarray} -->
-<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->
-
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the propensity: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-<!-- The prior distribution $P(h)$ is a distribution over likely degrees of propensity.  -->
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-
-<!-- Life is only so long, however, and a person can only be in one place at a time. -->
-<!-- The amount of data we can gather about any particular category, event, or causal force is extremely limited by these physical constraints. -->
-<!-- Thus, it would be useful if language provided a simple way to communicate these generalizations to one another. -->
-
-<!-- # A Formal Theory of Generalizations in Language -->
-
-<!-- We find both the statistical and conceptual accounts compelling, but an important perspective is missing. -->
-<!-- Linguistic generalizations are not unique in their flexibility. -->
-<!-- Understanding language in general depends upon assumptions interlocutors make about each other and what content is under discussion.  -->
-<!-- Viewing language understanding as a social reasoning process reveals that utterances carry a mosaic of interpretations with a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000].
--->
-<!-- Can the puzzles of generic language be understood as effects of pragmatic reasoning? -->
-<!-- If so, we may be able to get away with a relatively simple, statistical,  semantic theory. -->
-<!-- Abstract mental representations, then, may be the conceptual backdrop against which generic language is interpreted.  -->
-
-<!-- We pursue such a line of inquiry, assuming the simplest truth-conditional meaning: a threshold on prevalence $P(F\mid K)>\theta$ [c.f., @Cohen1999]. -->
-<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g. \emph{Mosquitos carry malaria}; \emph{Robins lay eggs} v. \emph{Robins are female}),  -->
-<!-- so instead we allow this threshold to be established in context through pragmatic reasoning. -->
-<!-- Such an inference would depend on background knowledge about properties and categories---potentially structured, conceptual knowledge. -->
-<!-- This inference, nonetheless, is a general mechanism of understanding language, not specific to interpreting generic statements. -->
-<!-- We formalize this hypothesis in the Rational Speech Act (RSA) theory---a formal, probabilistic theory of language understanding. -->
-<!-- RSA is derived from social reasoning, formalized as recursive Bayesian inference between speaker and listener [@Frank2012; @Goodman2013; @Goodman2016; see also, @Franke2009; @Franke2015]. -->
-<!-- @Goodman2016 provides a good introduction to the RSA framework and Appendix A presents a brief tutorial on RSA for the reader unfamiliar. -->
-
-<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-<!-- The prior distribution $P(x)$ is a distribution over likely states of the world.  -->
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise.
--->
-<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->
-
-<!-- To understand how language is interpreted pragmatically, we model a pragmatic listener $L_1$ who updates her prior beliefs $P(x)$ by reasoning about the generative process of the utterance, the speaker model $S_1$.
--->
-<!-- \begin{eqnarray} -->
-<!-- L_{1}(x , \theta \mid u) &\propto& S_{1}(u \mid x, \theta) \cdot P(x) \cdot P(\theta) \label{eq:L1} -->
-<!-- \end{eqnarray} -->
-<!-- Following @Lassiter2013, we model the pragmatic listener as having uncertainty about the threshold: $P(\theta)$. -->
-<!-- Though the listener doesn't know the threshold *a priori*, she resolves the threshold (i.e., the meaning) in context by integrating her prior beliefs $P(x)$ with the basic principles of communication to be truthful and informative, instantiated in her model of the speaker $S_1$ [@Lassiter2015; @GoodmanLassiter].
--->
-<!-- In principle, thresholds could be learned over time for different contexts, but here we assume the listener has no informative knowledge about the semantic variable $P(\theta) = \text{Uniform([0, 1])}$.
--->
-<!-- The pragmatic listener $L_1$ (Eq. \ref{eq:L1}) is thus a model of *generic interpretation*: Upon hearing a generic, how should a listener update her beliefs? -->
-
-# Case Study 1: Generic Language
-
-Generalizations about categories (i.e., *generic language*) have received substantial interest in psychology for their role in concept formation [@Gelman2004] and stereotype propogation [@Rhodes2012].
-Generic language (e.g., *Birds fly.*) exhibits substantial flexibility in meaning and truth conditions as described above.
-<!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
-<!-- Unlike universals, however, generics are resilient to counter-examples (e.g., *Birds fly* seems true even in the face of flightless birds like kiwis or penguins). -->
-<!-- *Most* birds fly seems more reasonable, and yet most mosquitos *do not* carry malaria while *Mosquitos carry malaria* seems like a true statement. -->
-<!-- Finally, the probability of a bird being female is much higher than the probability of a mosquito carrying malaria, but *Birds are female* seems weird to say. -->
-<!-- *Birds lay eggs*, however, is fine, even though the rate is the same as *are female* (only females lay eggs). -->
-
-<!-- Empirical work done on category generalizations has elucidated another puzzling phenomenon. -->
-<!-- Generic statements often imply the property is widespread in the category [e.g., *Swans have hollow bones* implies something much stronger than *Some swans have hollow bones*; @Gelman2002; @Cimpian2010; @Brandone2014].
--->
-<!-- This characteristically strong interpretation interacts with the indeterminacy in truth conditions, resulting in an *asymmetry* between endorsement and interpretation. -->
-<!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->
-
-As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties and show how it systematically predicts endorsements of familiar generic statements (Expt.
-1).
-In Experiment 3, we replicate and extend a paradigm used by @Cimpian2010 to demonstrate the asymmetry between endorsements and interpretations and find that a similar pattern is predicted by our model.
-
-We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data.
-Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
-After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.
-
-<!-- Interpreting the generic as meaning "most" (i.e.
-\emph{Most swans are white}) captures many cases, but cannot explain why \emph{Robins lay eggs} and \emph{Mosquitos carry malaria} are so intuitively compelling: Only adult female robins lay eggs and a very tiny fraction of mosquitos actually carry malaria.
--->
-<!-- Indeed, it appears that any \emph{truth condition} stated in terms of how common the property is within the kind violates intuitions. -->
-<!-- Consider the birds: for a bird, being female practically implies you will lay eggs (the properties are present in the same proportion), yet we say things like \emph{Birds lay eggs} and we do not say things like \emph{Birds are female}.
--->
-
-<!-- One case study in the language of generalizations is about category generalizations. -->
-<!-- Category generalizations, called *generic statement*, has been studied extensively in cognitive and developmental psychology: *generic* statements, or generalizations about categories. -->
-
-<!-- These *strong implications* might underly stereotype formation in social categories [@Rhodes2012]. -->
-<!-- In addition to the flexibility in truth conditions, two phenomena have been noted.  -->
-<!-- The case of *Mosquitos carry malaria* suggests the utterance must in some way be analogous to the quantifier "some" (e.g., *Some mosquitos carry malaria*).  -->
-<!-- Generic language, however, is often interpreted as implying the property is widespread: *Swans have hollow bones* means something different than *Some swans have hollow bones* [@Gelman2002]. -->
-
-<!-- These three phenomena---flexible truth, strong interpretations, and evidence exaggeration---have confounded all formal models aimed to capture the meaning of generalizations in language. -->
-<!-- Informal theories have argued that the nature of concepts and their relations are inextricably tied to their linguistic expression [@Leslie2007; @Prasada2013]. -->
-<!-- Formal theories have limited themselves to a measurable quantitative degree (e.g., how prevalent a property is in a category), which, in isolation, is difficult to reconcile with the extreme flexibility of generic language.
--->
-<!-- Here, we present a theory formalizing the inuition that the core meaning of a linguistic generalization is simple, but underspecified, and that general principles of communication may be used to resolve the precise meaning in context.
--->
-<!-- This theory inherently relies upon measurable quantities (i.e., prevalence) but situates it within a Bayesian agent with potentially structured prior knowledge, providing a bridge to conceptual theories.
--->
-<!-- We find that this formalism (and not simpler ones) explains all three empirical puzzles. -->
-
-<!-- When interpretations are compared directly against truth conditions (i.e., how prevalent a property would need to be for the generic to be true),  -->
-
-<!-- Three empirical phenomena make generalizations in language difficult to formalize. -->
-<!-- The conditions under which a generalizations becomes "true" are variable: -->
-
-<!-- Existing work in both adults and children suggests that choosing to communicate a generalization can be used to exagerate evidence [@Cimpian2010; @Brandone2014]. -->
-
-<!-- In addition to having manifold interpretations, what makes linguistic generalizations true or false (i.e., their truth conditions) is also a mystery. -->
-<!-- The statement *Birds lay eggs* is true even though only about half of them do (namely, the females). -->
-<!-- Half of birds are also female, and yet *Birds are female* sounds like a strange thing to say. -->
-<!--  while *Canadians are right-handed* is also weird, even though the vast majority of them are.  -->
-
-## Experiment 1: Endorsing generalizations about categories
-
-Any theory of generic language must explain their puzzling flexibility of usage with respect to prevalence.
-That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
-<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
-We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g.
-\emph{Ducks have wings.}), minority (e.g.
-\emph{Robins lay eggs.}), striking (e.g.
-\emph{Mosquitos carry malaria.}), false generalization (e.g.
-\emph{Robins are female.}), and false (e.g.
-\emph{Lions lay eggs.}).
-In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.
-
-To compare the model to empirical truth judgments, we first measure the prior distribution over prevalence of these properties (Expt. 1a).
-We hypothesize that this prior distribution encodes probabilities associated with deeper conceptual knowledge [e.g., of the kind discussed by @Prasada2013].
-This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada; @Gelman; @Leslie].
-If, indeed, there are such things as different types of kind--property relations (e.g., *principled* v.
-*accidental relations*), we would expect the prevalence prior data to follow a multi-modal, mixture distribution where different modes or components of the prior are the results of the different types of relations.
-As a simple of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
-
-After exploring the prevalence prior, we move on to the issue of primary theoretical interest: How well our *simple but underspecified* hypothesis accounts for endorsements of generic sentences (Expt.
-1b).
-
-### Experiment 1a: Measuring the Prevalence Prior for Categories
-
-The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, imagine your favorite kind of animal.
-Then answer, "what percentage of that kind of animal is female?".
-The answer is probably 50\%. 
-Then ask yourself, "what percentage of that kind of animal lays eggs?".
-Depending on what animal you thought of, the answer is probably either 50\% or 0\% (e.g., lions, tigers, and bears each have 0\% egg-laying members).
-
-This decomposition of the prevalence prior $P(h)$ into a kind prior $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
-We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
-We then ask whether a structured, prior model accounts better for this data than an unstructured model.
-
-#### Method
-
-##### Participants
-
-We recruited 60 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-3 participants were accidentally allowed to complete the experiment for a second time; we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-##### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories (randomly sampled from a set corresponding to the generic sentences used in Expt.
-1b (e.g.
-\textsc{robins, mosquitos}) and asked to generate five of their own.
-
-A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
-Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
-In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
-For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix).
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.
-
-### Bayesian analysis
-
-We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge
-We formalize this hypothesis using a simple, Bayesian mixture model. 
-We test the simplest "structural" hypothesis, where there are two distinct components, for example, if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not [@Griffiths2005].
-In this task, participants give responses in the form of numbers between 0 and 100 (or, rescaled to be between 0 - 1).
-The canonical prior for generating numbers between 0 - 1 is the Beta distribution.
-
-We then assume the data, for each item independently, was generated from one of two distributions: a distribution corresponds to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
-The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
-We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
-The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
-Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$.
-This problem does not appear for 0 being adjusted to $\epsilon$ as we explicitly posit a left-skewed "transient" distribution.
-Similar results can be obtained by rounding 0 to 0.01. 
-Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
-]
-Finally, we assume that these two components combine with some weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \alpha, \beta) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.
-
-We put priors over the latent parameters of this model and infer their credible values by way of Bayesian infernence.
-
-\begin{eqnarray}
-\theta & \sim & \text{Uniform}(0, 1) \\
-\alpha & \sim & \text{Uniform}(0, 100) \\
-\beta & \sim & \text{Uniform}(0, 100) \\
-\end{eqnarray}
-
-To see how well this data-analytic model fits the prevalence prior data, we can use the inferred parameters to generate new data.
-This is called the *posterior predictive distribution* and is an important step in model validation. 
-If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
-We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
-If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
-If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
-]
-
-We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
-To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
-
-```{r generic-endorsement-priors, eval = F}
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  //var a = uniformDrift({a:0, b: 100, width:5});
-  //var b = uniformDrift({a:0, b: 100, width:5});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-
-  var marginalPrevalence = sample(flip(phi) ? stableComponent : transientComponent)
-  return {g, d,phi, marginalPrevalence}
-}
-'
-marginal.prevalence <- data.frame()
-m.gen.endorse.priors.summary <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-  m.gen.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 1000, burn = 500, verbose = T))
-
-  marginal.prevalence <- bind_rows(marginal.prevalence, 
-                                   m.gen.endorse.priors %>% 
-                                     filter(Parameter == "marginalPrevalence") %>%
-                                     mutate(Property = p))
-
-  m.gen.endorse.priors.summary <- bind_rows(m.gen.endorse.priors.summary,
-                                            m.gen.endorse.priors %>% 
-                                              mutate(Property = p) %>%
-                                              group_by(Property, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-  #print(p)
-}
-
-```
-```{r, eval = F}
-
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-
-```
-
-### Results
-
-The prevalence prior data is indeed structure.
-
-We also see tremendous variability in the shapes of these prevalence distributions.
-
-<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
--->
-<!-- Do a BDA to describe the data in a more compact form. -->
-<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq.
-\ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).
--->
-<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content.
--->
-<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
-<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
-<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.
--->
-<!-- Some properties have priors that are unimodal with low variance (e.g.
-\textsc{is female}); these properties are present in every kind in almost exactly the same proportion.
-The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.
--->
-<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->
-
-### Experiment 1b: Endorsing generic statements
-
-Having measured the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) in addition to target-category prevalence (e.g., how many robins lay eggs; Expt.
-1a), our speaker model (Eq.
-\ref{eq:S1}) can predict endorsements for the corresponding generic statements (e.g., Robins lay eggs).
-To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
-
-#### Method
-
-```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(column = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- d.gen.endorse.bayes %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5))+
-  geom_bar(stat = 'identity', position = position_dodge(),fill = 'grey')+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("Proportion Endorsement")+
-  xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))#+
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
-```
-
-##### Participants
-
-We recruited 100 participants over MTurk. 
-4 participants were excluded for failing to pass a catch trial.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
-The experiment took about 3 minutes and participants were compensated \$0.35.
-
-##### Procedure and materials
-
-Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
-As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
-
-#### Data and model analysis
-
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-This was a significant predictor of the empirical truth judgments: true generics were significantly more likely to be agreed with than the indeterminate generics ($\beta = 3.14; SE = 0.15; z = 21.5$), as revealed by a mixed-effect logistic regression with random by-participant effects of intercept.
-Indeterminate generics were agreed with \emph{less} likely than chance ($\beta = -0.49; SE = 0.09; z = -5.3$) but significantly more than false generics ($\beta = 2.09; SE = 0.14; z = 14.5$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
-This argues against any simple theory that only predicts whether or not a generic statement is true or false. 
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-To try to understand this endorsement data, we articulate alternative models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
-As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
-
-Our underspecified threshold model has access to the full prior distribution on prevalence $P(h)$, from which it infers likely thresholds for the generic. 
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
-There are thus three unique components of this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
-As a control model, we use the same infrastructure but assign the semantics of "Some" to the utterance (i.e., a fixed-threshold which only rules out the lowest possible degree). 
-This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
-This provides a strict test of our *simple but underspecified* hypothesis.
-
-##### Prevalence baseline
-
-From the prevalence prior data (Expt.
-1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
-We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
-This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
-However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $ 20\% < prevalence < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).
-
-##### Prevalence and cue validity
-
-<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
-If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though a strong version of cue validity has been argued against on *a priori* grounds [@Leslie2007; @Leslie2008].
-
-For a prevalence distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the prevalence prior distribution (i.e., it is a summary statistic of this distribution).
-In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
-To measure cue validity, we employed a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix.
-
-A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(30) = 0.79$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of cue validity, which is in fact a point-summary statistic based on the prevalence distribution (see Appendix more details).
-"Lays eggs" is a somewhat diagnostic features for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A single metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the learned regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high.
-
-##### Fixed threshold RSA model
-
-The RSA model we propose for generic endorsement is a speaker model who decides whether or not to say the generic to a naive listener, who has access to the full prior distribution on prevalence $P(h)$.
-As a strong alternative model, we retain the specification of the speaker reasoning about a listener with this prior distribution, but remove the uncertainty about the generic threshold. 
-For this model, we set $\theta = 0$, and thus the generic statement corresponds to the quantified statement "Some".
-
-<!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
--->
-We use the empirically estimated within-kind target prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
-1a as the listener's prevalence prior $P(h)$.^[
-Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener.
-This corresponds to the more general form of the model described in **Alternative Formulations** section.
-With these data, the predictions of these two models are nearly identical.
-]
-The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-We infer this parameter, as well as the values of target prevalence $h$, and parameters of the prevalence priors $P(h)$ (assuming the structured model validated in Expt.
-1a) using Bayesian data analysis [@LW2014].
-For the prevalence parameters, we use the same priors described in Expt.
-1a; for the speaker optimality parameter, we use an informative prior, with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of our model parameters by collecting samples from MCMC chains of 10,000 iterations removing the first 5,000 iterations, using the Metropolis-Hastings algorithm.
-
-We compare the "Some" model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(The posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
-In accord with intuition, assigning a fixed semantics corresponding to "Some" is too lenient a specification. 
-Even for patently false generics (e.g., "Mosquitos don't carry malaria"), the speaker model is unable to prefer staying silent than producing the generic (with a "some" semantics).
-It also doesn't strongly prefer producing the generic, possibly because the information content is so small.
-
-##### Uncertain threshold RSA model with diverse priors
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0.5$, it has *a priori* uncertainty over the threshold.
-We perform the same Bayesian data analysis as the "Some" model.
-As we see in Figure \ref{fig:commongenerics}b, the pragmatic speaker model $S_2$, using empirically measured priors, explains nearly all of the variance in human truth judgments ($r^2=0.98$; MSE=0.003; Figure \ref{fig:commongenerics}b).
-
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, Property)) %>%
-  filter(item %in% d.target.items$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(column = "prevalence")
-
-# need to filter by items specified with endorsement
-d.gen.cv.summary <- left_join(
-  d.target.items %>% select(-sentence),
-  d.cv %>%
-    rename(category = response) %>%
-    group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials)
-  ) %>%
-  mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prevalence = mean,
-             sentence = item) %>% 
-      select(-ci_lower, -ci_upper)
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prevalence, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prevalence + prop, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
-  )) %>%
-    mutate(prediction = predict(glm.gen.endorse.prev, ., type = "response")) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(sqErr = (mean - prediction) ^ 2,
-             cuevalidity = prop)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-   unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
-    )) %>% 
-    mutate(prediction = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-           sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(sqErr = (mean - prediction) ^ 2,
-             cuevalidity = prop)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
-```
-
-```{r generic-fullmodel, fig.width = 8}
-n_chains <- 1
-n_samples <- 50000
-burn <- n_samples
-
-model_prefix <- "results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-"
-
-m.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/generics/results/", model_prefix, 
-                    n_samples, "_burn", burn, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i)
-  m.samp <- bind_rows(m.samp, m.samp.i)
-  #print(i)
-}
-
-m.gen.somemodel.endorsement <- fread(
-  paste(project.path,"models/generics/results/", 
-        #"results-fullModel-s1-smtncssome-20000_burn10000_chain1.csv", 
-        "results-fullModel-s1-lowestTheta-smtncssome-1000_burn500_lag10_chain1.csv",
-        sep = "")
-  ) %>% mutate(chain = 1) %>%
-  filter(type == 'predictive') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression %>% 
-  mutate(prediction_lower = prediction,
-         prediction_upper = prediction),
-  left_join(
-    m.gen.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-    select(sentence, Property, Category, prevalence, cuevalidity)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "generics_model",
-                                      "some_model",
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c(
-                                 "Speaker model - uncertain semantics",
-                                 "Speaker model - fixed semantics",
-                                 "Prevalence alone", "Prevalence & Cue validity"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prevalence ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human generic endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")
-
-```
-
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = isPresent_na, 
-         stable_mean = prevalenceGivenPresent_mean, 
-         stable_concentration = prevalenceGivenPresent_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "withinKind") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "withinKind") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(-type, -param, -chain, -Sentence) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_text_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence") +
-    ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generics-endorsement-figure, fig.width=7, fig.height=5}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-<!-- The above analysis provides a single estimate for model predictions, but it is based on noisy empirical measurements of $P(x)$.
-In order to estimate the impact of this empirical noise on our model predictions, we resampled the prior data (with replacement) for 57 participants worth of data, discretizing and binning as we did above and then inferring parameters.
--->
-<!-- This procedure (re-sample prior, discretize and bin, infer parameters) was repeated 500 times to bootstrap the model predictions. -->
-<!-- The Maximum A-Posteriori (MAP) estimate and 95\% Highest Probability Density (HPD) interval for $\lambda_1$ is 0.5 [0.004, 12.7] and $\lambda_2$ is 1.7 [1.3, 2.1]. -->
-<!-- ^[ -->
-<!-- The fact that $\lambda_1$ is credibly less than 1 suggests that the generic utterance may be more costly than "staying silent" (our model assumes equal cost). -->
-<!-- We maintain using only the two $\lambda$ parameters in the model for simplicity. -->
-<!-- ] -->
-
-<!-- This is akin to fitting the parameters and is the critical step in model validation: It shows what data is actually predicted by the model.)  -->
-
-Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g.
-\emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
-We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false.
-\emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model.
-This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context.
-
-<!-- basic communicative principles (\emph{be truthful}, \emph{be informative}) operating over diverse prior beliefs about the properties, all of which are at play in understanding language.  -->
-
-<!-- \begin{figure} -->
-<!-- \centering -->
-<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-prevalence-tj.pdf} -->
-<!--     \caption{Endorsing familiar generics. (a)  -->
-<!--     Prevalence prior distributions empirically elicited for twenty-one animal properties. -->
-<!--     Prior distributions summarized by two parameters of a structured Bayesian model: $\phi$----a property's potential to be present in a category----and $\gamma$----the mean prevalence when it is possible for the property to be present in a category.
--->
-<!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
-<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a target category. -->
-<!--     (b) -->
-<!--     Human acceptability judgments compared with model predictions (left) and the target-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
-<!--     Color denotes target-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
-<!--      Error bars denote 95\% Bayesian credible intervals. -->
-<!--     } -->
-<!--   \label{fig:commongenerics} -->
-
-<!-- \end{figure} -->
-
-## Discussion
-
-Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the prevalence of the property across kinds and the prevalence of the target kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical claim is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the target category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-Yet, this evidence is still correlational in nature.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the target propensity that the speaker aims to communicate.
-
-<!-- In addition, why generics often imply the property is widespread has also been puzzling [@Gelman2004]. -->
-<!-- We show that this is the result of the shape of listener's prior knowledge and that when that shape differs, the implied prevalence is much weaker (e.g., with accidental properties). -->
-<!-- Even more puzzling has been the basic asymmetry between endorsements and interpretations [@Cimpian2010]. -->
-<!-- We show that this asymmetry arises from the underspecified-threshold interacting with diverse prior beliefs.  -->
-<!-- While implied prevalences vary wildly for different kinds of properties under discussion, the endorsements are relatively less sensitive to these distinctions. -->
-<!-- Thus, the basic asymmetry is largely being driven by the listener's interpretation of a generic. -->
-
-# Case Study 2: Habitual Language
-
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particularly importance because they are likely central to intuitive theories of personality and behavior. 
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as ``Tell us about your school / family''. 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g.
-``My brother works part-time at the restaurant.'').
-Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
-Habitual language may be a more conservative form of trait language (e.g. \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-Habituals are a particularly amenable domain to manipulating the target propensity that a speaker aims to communicate.
-People are often in the situation of being introduced to new people and learning new information about them.
-In addition, the propensity information can be expressed in an easily-interpretable frequency with which a person does an action (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-While target probability can be manipulated for generalizations about categories (generic language) (e.g., by stating the prevalence of feature in a kind), this may interact with domain knowledge in complex ways (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-In our first experiment concerning habitual language, we manipulate the target frequency as well as the kind of event (Expt.
-2b), creating a data set of endorsements that is three times as large as the data from Expt.
-1b (generic endorsement).
-To measure participants' latent prior belief distribution over the frequencies of people doing various actions (e.g., how often people *run*; Expt.
-2a), we take advantage of the structured representation discovered in Expt.
-1a, and learn about the prior by asking questions about the parameters of this model.
-In addition to directly manipulating the target propensity, these experiments provide the first test of the generality of our theory, that it can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect expectations, not merely observations. 
-Up to this point, we have been relatively agnostic as to the interpretation of $h$, the target propensity that the speaker aims to convey.
-In our first investigation of the degree scale, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive probability that this event will occur in the near future (e.g., how likely it is that Mary will smoke next week)?
-In Expts.
-3a \& 3b, we show that $h$, the target of communication, is a speaker’s prediction about the future frequency of action, and not past frequency, tying the phenomenon of *genericity* even more to subjective beliefs.
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
-## Experiment 2: Endorsing generalizations about events
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the frequency of events, for different kinds of events.
-Then, we test endorsements of habitual sentences, manipulating the actual frequency with which a person does an action.
-
-### Experiment 2a: Measuring the propensity prior for event knowledge
-
-In this experiment we elicit the prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements.
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with a different frequency.
-To better understand what frequencies should be expected for different actions, we took advantage of the 
-structured representation of the prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that prior distribution over the prevalence of a feature across different categories can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable frequencies of the property, among those that normally have the property.
-The second component (the "unstable" or "transient cause" component) represents the frequencies of the property among those categories who do not typically have the property.
-This second component will usually result in frequencies of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero frequencies (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the frequency with which people do actions, we consider again two components.
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action (expected frequency: once every hundred years). 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-
-#### Method
-
-##### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-##### Materials
-
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
-
-##### Procedure
-
-For each event, participants were asked two questions, with associated dependent measures:
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
-\end{enumerate}
-
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-We anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/priors-2.html}.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-\begin{figure*}[t]
-\centering
-  \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3}
-  \caption{
-  Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency). 
-  Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions. 
-  Actual frequency noted on x-axis for examples (left).
-  Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions. 
-  Error bars suppressed and points jittered on left facet for visual clarity.
-  }
-  \label{fig:tjScatters}
-\end{figure*}
-
-<!-- #### Data preprocessing -->
-
-```{r habituals-prior}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path,
-                           "data/habituals/priors/friends-and-family-2-trials.csv",
-                           sep= ""))
-
-d.hab.priors.tidy <- d.hab.priors %>%
-  rowwise() %>%
-  mutate(annualRate = annualRates[[as.character(interval)]]*n_times,
-         never = ifelse(annualRate == 0, 1, 0),
-         action = as.character(action),
-         action = ifelse(action == "sell things on eBay", "sells things on eBay", action))
-
-d.hab.priors.distinctiveness <- d.hab.priors.tidy %>%
-  group_by(action) %>%
-  multi_boot_standard(column = 'never') %>%
-  ungroup() %>%
-  rename(distinctiveness = mean, 
-         distinct_low = ci_lower, distinct_high = ci_upper)
-#d.hab.priors
-#d.hab.priors.distinctiveness
-# 
-# 
-# df.out <- df.tidy %>%
-#   mutate(annualRate = ifelse(annualRate == 0, 0.15, annualRate),
-#          lograte = log(annualRate),
-#          binned_lograte = round(lograte*2)/2) %>%
-#   group_by(action, binned_lograte) %>%
-#   summarize(counts = n())
-# 
-# 
-# # make sure 0s are represented
-# df.out2 <- left_join(
-#   expand.grid(action = levels(df.out$action), binned_lograte = levels(factor(df.out$binned_lograte))),
-#   df.out %>% mutate(binned_lograte = factor(binned_lograte))) 
-# 
-# df.out2[is.na(df.out2)] <- 0
-# df.out2 <- df.out2 %>%
-#   mutate(binned_lograte = as.numeric(binned_lograte))
-#   
-# ggplot(df.out2, aes( x = binned_lograte, y = counts))+
-#   #geom_histogram()+
-#   geom_bar(stat = 'identity', position = position_dodge())+
-#   #geom_density()+
-#   facet_wrap(~action, scales = 'free')+
-#   xlim(-3.5, 8.5)
-# d.hab.priors.tidy
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-#### Data analysis and results
-
-We built a Bayesian data analysis model for this prior elicitation task.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-(1) It smooths effects that are clearly results of the response format.
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-(2) It better captures the tails of the prior distribution (e.g., the probability of a rate of going to the movies two times every five years) which have relatively little data and need to be regularized by the analysis.
-
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate, or relative frequency, with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-
-We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.~\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-From the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-
-Figure \ref{fig:priorScatter} (right) shows example inferred priors.
-
-Some items show substantial differences between the genders (e.g. \emph{wears a bra}) and some show subtle differences (e.g. \emph{watches professional football}). 
-%It is \emph{a priori} unclear whether or not $P(x)$ in Eqs.~\ref{eq:L1}, \ref{eq:L0} is the distribution over frequency of action with respect to \emph{all people}, or if it is restricted to be gender specific.
-%For example, are the frequency conditions by which a man would qualify to ``wear a bra'' (habitually) different than those by which a woman would qualify to ``wear a bra''?
-We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender.
-%In order to explore this possibility, we will select items with priors that differ by gender to explore more closely in Experiment 2.
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-## Experiment 2b: Endorsing generalizations about events
-
-We next explore the endorsements of habituals from the items whose priors were measured the prior elicitation task.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Procedure and materials
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed 37 trials, which were composed of the 27 items from the prior elicitation task and 4 additional filler items not in the prior elicitation task randomly paired with either a male or female character name.
-6 of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who watched professional football).
-These were used for an exploratory analysis on gender differences.
-The 4 filler items were not used in the prior elicitation because they described illegal activities (e.g., "doing cocaine", "stealing cars").
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-2.html}.
-
-### Results
-
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.distinctiveness %>% rename(habitual = action)) %>%
-  mutate(response = as.character(response),
-         response = ifelse(response == "agree-key", 1, 0),
-         roundedFreq = round(log_times * 2) / 2)
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, time_period, log_times, roundedFreq) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-ggplot(d.hab.endorsement.bayes, aes( x = roundedFreq, y = MAP_h, ymin = low, ymax = high, fill = roundedFreq))+
-  geom_jitter(width = 0.1, shape = 21)
-
-#d.hab.endorsement.bayes
-```
-
-```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ log_times, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ log_times + distinctiveness, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.regression <- left_join(
-  d.hab.endorsement.bayes,
-  unique(select(
-    d.hab.endorsement, habitual, log_times, roundedFreq, distinctiveness
-  )) %>%
-    mutate(regression_freq = predict(glm.hab.endorse.freq, ., type = "response"), 
-           regression_freq_distinct = predict(glm.hab.endorse.freq.distinct, ., type = "response"))
-) %>%
-  gather(src, prediction, regression_freq, regression_freq_distinct) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-ggplot(d.hab.endorse.regression,
-       aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = distinctiveness))+
-  geom_errorbar(alpha = 0.1)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-  #                   filter(sqErr > 0.1),
-  #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-  geom_point()+
-  xlim(0,1)+
-  ylim(0,1)+
-  coord_fixed()+
-  xlab("Logistic model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel}
-n_chains <- 1
-n_samples <- 10000
-burn <- n_samples / 2
-lag <- 5
-i <- 2
-model_prefix <- "results-habituals-S1-ffPrior2-3components-normalPrior-silenceAlt-"
-
-m.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/habituals/results/", model_prefix, 
-                    n_samples, "_burn", burn, "_lag", lag, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i) %>% rename(habitual = item, time_period = param)
-  m.samp <- bind_rows(m.samp, m.samp.i)
-  #print(i)
-}
-
-m.hab.somemodel.endorsement <- fread(
-  paste(project.path,"models/habituals/results/", 
-        "results-habituals-fixedThreshold-S1-ffPrior2HyperStructured-silenceAlt-10000_burn5000_lag5_chain1.csv",
-        sep = "")
-  ) %>% mutate(chain = 1) %>% rename(habitual = item, time_period = param) %>%
-  filter(type == 'predictive') %>%
-  group_by(type, habitual, time_period, cat, gender) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(type, habitual, time_period, cat, gender) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
-habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression %>% 
-  mutate(prediction_lower = prediction,
-         prediction_upper = prediction),
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, log_times, distinctiveness)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "generics_model",
-                                      "some_model",
-                                      "regression_freq", 
-                                      "regression_freq_distinct"
-                                     ),
-                      labels = c(
-                                 "Speaker model - uncertain semantics",
-                                 "Speaker model - fixed semantics",
-                                 "Frequency alone", "Frequency + Distinctiveness"
-                                 ))) %>%
-  filter(src == "Speaker model - uncertain semantics") %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = log_times ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")
-
-# with(m.hab.endorse.rsa %>% 
-#   filter(src == "generics_model"), cor(MAP_h, MAP, use='pairwise.complete.obs'))^2
-
-habituals.endorsement.models
-```
-
-```{r fig.height = 8, eval = F}
-
-m.samp %>% filter(type == "param") %>%
-  ggplot(., aes( x = val))+geom_histogram()+
-  facet_wrap(~habitual)
-
-m.samp %>% filter(type == "prior") %>%
-  ggplot(., aes( x = val, fill = time_period))+geom_histogram() + facet_grid(habitual~cat, scales = 'free')+
-  theme(strip.text.y = element_text(angle = 0))
-
-#tail(m.samp)
-```
-
-#### Behavioral results
-
-On each trial of the experiment, the participant was told a person did a particular action 3 times during some time window. 
-A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one. 
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements.
-A more sophisticated alternative hypothesis is that the degree to which the habitual statement is good is the frequency itself. 
-<!-- Our computational model predicts that the the degree to which the habitual statement is good is the frequency of event, normalized by the alternative possible frequencies under the prior. -->
-<!-- [MHT: SENTENCE ABOVE IS THE SOFT-SEMANTICS INTERPRETATION] -->
-
-Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:tjScatters} (left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency.
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (log frequency $\sim$ -1; 3 times in a 5-year interval; e.g.
-\emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g.
-3 times in a one month interval; log frequency $\sim$ 5), some habitual sentences receive less than full endorsement (e.g.
-\emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval; log frequency $\sim$ 6.5) receive at a minimum 75\% endorsement, though there is still variability among them (e.g.
-between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the raw (log) frequency of action predicts only a fraction of the variability in responses ($r^2(93) = 0.33$).
-For actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(50) = 0.07$)
-
-We observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$. 
-This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women). 
-Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
-
-\begin{figure*}[t]
-\centering
-  \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf}
-  \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity).
-  Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
-  Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).}
-  \label{fig:tj3}
-  \vspace{-7pt}
-\end{figure*}
-
-#### Model criticism and comparison
-
-We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.~1) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
-The model has two free parameters---the speaker optimality parameters, $\alpha_i$, in Eqs.~\ref{eq:S2} \& \ref{eq:S1}. 
-We use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.~2.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6].
-%The MAP and HPD interval for the data-analytic guessing parameter is 0.004 [0.0003, 0.03], suggesting that there is not a substantial amount of the data that is better explained by a model of random guessing than by our pragmatic speaker model.
-
-As shown in Figure \ref{fig:tjScatters}, right, the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(93) = 0.94$), including actions done on the time scale of years or more  ($r^2(50) = 0.92$).
-The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.
-
-As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
-
-Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data.
-
-## Experiment 3: Communicating predictive propensities
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate propensity in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In this pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 3a, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 3b, we examine felicity judgments of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-### Experiment 3a: Prediction elicitation
-
-#### Methods
-
-We recruited 120 participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took 4 minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/predictive-1.html}.
-
-#### Results
-
-Figure \ref{fig:tj3} (left) shows the predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g.
-participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2 whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:tj3} left; blue and green dots).
-
-+ MHT: Add some regression analysis here
-
-### Experiment 3b: Felicity judgments
-
-#### Methods
-
-We recruited 150 participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took 4 minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 3a.
-%\subsubsection{Procedure and materials}
-The only difference from Expt. 3a is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2).
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
-#### Results
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:tj3}, middle; blue points).
-When collapsing across items and subjecting the data to a generalized mixed-effects model with random by-participant effects of intercept and random by-item effects of intercept and conditions, we find evidence for a small effect of \emph{enabling} conditions on endorsements (M =  0.89; 95\% Bootstrapped CI [0.88, 0.91]) as compared to baseline (M = 0.85 [0.83, 0.87]) [$\beta = 0.42; SE = 0.15; z = 2.8$]
-, and a large effect of \emph{preventative} conditions on endorsements (M = 0.29 [0.26, 0.31]) [$\beta = -3.22; SE = 0.21; z = -15.2$]. 
-<!-- %\mht{should I add points from Expt. 2 to left-most scatter, or maybe there is a better plot?} -->
-
-We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b.
-We infer the two model parameters using the same analysis approach in Expt. 2. 
-The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right).
-The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$).
-These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past.
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points). 
-This may be due, in part, to an effect of the experimental context on participants: 
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
-## Discussion
-
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
-2a).
-We have seen that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiment 3, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-3a) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-3b).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while measuring the propensity priors.
-Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlational associated with generic endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and test experimentally whether the propensity prior is indeed causally related to generic endorsement.
-
-# Case Study 3: Causal Language
-
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality (CITE noah's and kemp's causality and causal models papers?).
-Communicating generalizations about causally related events is potentially highly useful because no one individual can run all the experiments that she wants to run in a life time. 
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
-
-Our framework for communicating generalizations makes predictions about statements conveying genericty about a category of causal events. 
-In this domain, an instance of the category is a single causal event (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough at a particular time of the day). 
-@Gerstenberg
-The study of *elemental causal induction* is itself very subtle, depending on an observer's background theory of causality. [@Griffiths2005; @Schulz].
-
-We design this last experiment with the goal of testing whether background knowledge that gives rise to the prevalence priors is causally related to the endorsement of causal statements.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
-
-In Experiment 4a, we manipulate participants' beliefs about a causal system and measure their updated beliefs about system, serving a manipulation check.
-In Experiment 4b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 4a: Manipulating the Prevalence Prior for Causes
-
-People have theories about how different casusal systems work. 
-Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force. 
-If the experiment is repeated exactly, we would expect the same results.
-In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't. 
-Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
-
-In this experiment, we examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present.
-We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains.
-
-### Method
-
-#### Participants
-
-We recruited N participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average N minutes and participants were compensated \$N.NN for their work.
-
-<!-- The different kinds of system are described in more detail below. -->
-<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->
-
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain in question.
-In the second phase, participants are asked to make a judgment corresponding to the between-subjects condition they are assigned (prior, endorsement, interpretation).
-
-#### Procedure
-
-Participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (e.g., how to make a certain kind of animal more alert). They are told:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called  (e.g., daiths) and your team of scientists wants to figure out what makes daiths's hair turn brown. 
-Your team runs experiments trying to make daiths's hair turn brown with different chemical compounds. 
-The results are shown below:
-\end{quotation}
-
-Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., The team tested Food A on 100 daiths.
-30 of them were made more alert.) as well as put into a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 6).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
-
-Upon proceeding to phase 2, the results of the "experiments" are removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 4 experiments.
-Participants were given 4 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., foods M, N, P, and Q).
-
-#### Materials
-
-The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model.
-Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
-So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.
-
-A second dimension of manipulation corresponds to the extent to which *determinism* is expected in the domain. 
-For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.
-
-### Results
-
-...
-
-## Experiment 4b: Endorsing Causal Language
-
-In this experiment, we tested whether the manipulated priors of Expt. 4a are causally related to the endorsement of causal statements.
-
-### Method
-
-Most of the experiment was identical to that of Experiment 4a.
-
-#### Participants
-
-We recruited N participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 4a. 
-The experiment took on average N minutes and participants were compensated \$N.NN for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 4a.
-Phase 1 of the experiment was identical to that of Experiment 4a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants were then asked to judge the causal sentence: "Treatment X makes the effect happen". 
-Partipants responded by either clicking "Yes" or "No".
-
-Participants saw 1 of 3 frequencies: 20\%, 50\%, or 80\%.
-
-### Results
-
-```{r causals-endorsement}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-## Discussion
-
-# General Discussion
-
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., *John runs.*, *Dogs are friendly.*, *The block makes the machine play music*) are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data.
-
-It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *propensity*, or probability (Expts. 1, 3, \& 4).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expt. 2).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Pelletier; @Cohen1999; @Nickel].
-As @Nickel2013 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics allows a way for conceptual structure to influence generic production and comprehension, without having to posit conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for influence on generic language [c.f., @Leslie2008].
-
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
-
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the propensity of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the target is evaluated. 
-$P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language to the study of *vague language*.
-
-In this work, we made the design decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class, with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed the same sentence.
-"Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; say, in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the property-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge and Implications for Conceptual Structure
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008]. 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g.~\emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g.~\emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g.~\emph{Tigers eat people.}) is useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the prevalence-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different prevalence priors. 
-In Expt. 4 we showed that these prevalence distributions are causally related to endorsement.
-
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical prevalence distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective prevalence.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expt.~3 that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
-
-The focus on subjective, predictive probability casts new light on puzzles surrounding accidentally-true situations.
-To take a thought-experiment from the linguistics litearature, imagine that currently every Supreme Court justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation is this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive prevalence would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the Language of Generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language (CITE).
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-More on development.
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the prevalence of feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-Rehash linguistic puzzles.
-The extreme flexibility of generic meaning stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward, emerge much *later* in development.
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (namely, a truth-functional threshold) will not work for generic language [@Leslie2008].
-
-This may be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance: (1) that the meaning is a threshold-function (i.e., $\denote{u}(p, \theta) = \{p :p > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-If there is no fixed value of the threshold, then a uniform prior over the threshold in the truth-functional threshold semantics is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is *the degree itself*, normalized by the prior distribution over the degree (i.e., the comparison class).
-
-$$
-\int_{0}^{1} \delta_{p > \theta} \diff \theta =  p
-$$
-
-Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early.
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* sematnics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
-
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical Accounts
-
-Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to *prevalence* as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on prevalence and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the prevalence of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Prevalence or propensity in our theory is a posterior predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
-
-### Conceptual Accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on prevalence $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence of properties across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the target category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-If the comparison class can be derived with respect to the property [c.f., @Keil1979], one would expect the entities in the class to
-
-(2) is often used to argue that no actual instances need have occurred to make a generalization true. 
-In this thought experiment, part (or perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary has handled the mail from Antarctica in the past.
-Our framework takes the fundamental currency of a generalizatoin in language to be a subjective predictive probability. 
-In Expt. 3, we manipulate predictive probability and saw the endorsements for habitual language were affected. 
-This example bears similarity to the *enabling* condition of that experiment, wherein causal events increased the propensity of the event in the future, and also resulted in an increase in endorsements of habitual language.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. 
-(3) sounds true but if one takes the conjunction to apply to the properties, it is not true.
-That is, we don't think there to be international elephants (i.e., individual elephants who live in Africa part time and Asia part time).
-Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
-This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia."
-Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.
-
-With reasonable assumptions about the prior (e.g., assuming international elephants are unlikely), upon the hearing "Elephants live in Africa", the moddel infers that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is a nice feature of the uncertain threshold semantics: flexibility in accomodating new evidence that might otherwise contradict previous statements.
-
-Finally, (4) is used to argue that even if the property is widespread (perhaps in a soft sense, as in our model, relative to other kinds or groups), we might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive, we might still not want to say *Women are submissive* [@Haslanger]. 
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth [cf., @Cimpian2010].
-The current formulation of the model is relatively ambivalent the deviations of the listener's beliefs from the speaker's beliefa.
-Other models in the RSA framework have identified states of the world with different subjective values (e.g., how good of a job a listener did on a task), and speakers with utilities that extend beyond conveying information can produce qualitatively different patterns of utterances [e.g., polite speech; @Yoon2016; @Yoon2017].
-If our model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the target prevalence, the prior distributions on prevalence, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how category generalizations are conveyed and how beliefs play a central role in understanding language.
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-```{r child = 'appendix-prevalencePrior.Rmd'}
-```
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```

### 2017-06-08 paper/appendix-fullModelPosteriors.Rmd
create alt models appendix; begin full posterior appendix

# Appendix C: Full model posteriors

```{r libraries}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "~/Documents/research/comgen-paper/"
data.path <- "data/generics/endorsement/"
model.path <- "models/generics/results/"
options("scipen"=10) 
```

## Case Study 1: Generic language

### Uncertain threshold RSA

```{r}
m.samp <- fread(
  paste(project.path,"models/generics/results/", 
        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain1.csv",
        sep = "")
  ) %>% mutate(chain = 1)
```

### Parameter posteriors

#### Speaker optimality parameter

```{r}
m.samp %>% 
  filter(type == "param") %>%
  ggplot(., aes(x = val, fill = factor(chain)))+
  geom_histogram(position = position_dodge())+
  facet_wrap(~param + property, scales = 'free')
```

#### Posterior predictive distribution on target prevalence

```{r}
d.prior <- read.csv(paste(project.path, data.path, 
                    "naturalGenerics-prior-trials-n57.csv", sep = ""))

full_sentences <- mutate(md, sentence = paste(category, property, sep = "_"))$sentence

d.prior.summary <- d.prior %>% 
  mutate(sentence = paste(Category, Property, sep = "_")) %>%
  filter(sentence %in% full_sentences) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property) %>%
  multi_boot_standard(column = "prevalence")
```

#### Posterior predictive distribution on prevalance priors

Forward sample from posterior on parameters
```{r}

m.samp.prior.params <- m.samp %>%
    filter(type == "prior") %>%
    mutate(parameter = paste(param, category, sep = "_")) %>%
    select(-param, -category, -chain, -type) %>%
    mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(item) %>%
    mutate(iteration = ave(item==item, item, FUN=cumsum)) %>%
    ungroup() %>%
    select(-item)

  m.samp.prevalence.prior <- m.samp.prior.params %>%
                              group_by(parameter, property, iteration) %>%
                              spread(parameter, val) %>%
                              rowwise() %>%
                              mutate(isPresent = rbinom(1, 1, prob = isPresent_na),
                                     prevalence = ifelse(isPresent == 1, 
                                                         rbeta(n = 1, 
                                                               shape1 = prevalenceGivenPresent_mean* prevalenceGivenPresent_sampleSize,
                                                               shape2 = (1-prevalenceGivenPresent_mean)*prevalenceGivenPresent_sampleSize),
                                                         rbeta(n = 1,
                                                               shape1 = 1,
                                                               shape2 = 100))) %>%
                              ungroup() %>%
                              select(property, prevalence)
```

Marginal distributions on prevalence
```{r}

```

CDFs

```{r}

  bind_rows(
    d.prior %>% 
    mutate(prevalence = prevalence / 100) %>%
    rename(property = Property) %>% 
    select(property, prevalence) %>%
    mutate(src = 'data'),
     m.samp.prevalence.prior %>%
      mutate(src = 'model')
  ) %>% ggplot(., aes( x = prevalence, color = src))+
    stat_ecdf()+
    facet_wrap(~property)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))
```

```{r}
m.gen.somemodel.endorsement <- fread(
  paste(project.path,"models/generics/results/", 
        #"results-fullModel-s1-smtncssome-20000_burn10000_chain1.csv", 
        "results-fullModel-s1-lowestTheta-smtncssome-1000_burn500_lag10_chain1.csv",
        sep = "")
  ) %>% mutate(chain = 1) %>%
  filter(type == 'predictive') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```

### 2017-06-08 paper/generics-paper.Rmd
create alt models appendix; begin full posterior appendix

@@
 
-This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (a threshold function) but underspecified.
+This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
 Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq.
@@
 
-## Alternative formulation
-
-The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold meaning for a generalization. 
-The Rational Speech Act framework defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-For the most basic formulation of an RSA model, the level of recursion for a model can be unidentifiable from the 
-"speaker optimality" model parameter in Eq. \ref{eq:S1} [@FrankEtAlUnderReview].
-For our model, with an uncertain threshold variable, theoretically meaningful different models can be formulated in the pragmatic framework.
-
-For example, @Lassiter2013 modeled vagueness and the context-sensitivity of gradable adjectives using a similar underspecified threshold semantics. 
-In that work, the authors argued that understanding adjectives required a "pragmatic listener" [i.e., a listener who thinks about a speaker who thinks about a listener; @Lassiter2015]. 
-In their model, the threshold variable was "pragmatically lifted", meaning the uncertainty over the threshold variable was resolved using pragmatic reasoning [a so-called uRSA model; @Goodman2016].
-In the case of our model of generalizations, we can compare the simple model we described above to a more sophisticated model that resolves the threshold using pragmatic principles.
-
-### Listener models
-
-Eq. \ref{eq:L0} describes how a naive Bayesian agent should update her beliefs about the probability after hearing an utterance conveying a generalization. 
-This listener model is not pragmatic because it doesn't reason about the generative process of the utterance (i.e., it doesn't reason about a speaker). 
-Eq.
-\ref{eq:L1u} extends this model adding a level of recursion, modeling a pragmatic listener who reasons about the Gricean speaker in Eq.
-\ref{eq:S1} who reasons about the literal listener in Eq.
-\ref{eq:L0}.
-
-\begin{eqnarray}
-L_{1}(h \mid u) &\propto& S_{1}(u \mid h) \cdot P(h) \label{eq:L1u}
-\end{eqnarray}
-
-This $L_1$ model reasons about the conditions under which the speaker $S_1$ would produce one or another speech act (here, the generalization or staying silent), described above.
-Still, the threshold variable gets resolved by $L_0$ (and marginalized out by $S_1$): The posterior distribution over thresholds is arrived at by $L_0$ trying to make the generalization true.
-<!-- \mht{How does this posterior on states differ?} -->
-
-Truthfulness is not the only process that could help set $\theta$.
-If the listener were to reason about what threshold was likely to be *used by the speaker*, informativity would also help set $\theta$.
-This can be modeled by a pragmatic listener who reasons about the threshold, but assumes the speaker had a particular threshold in mind (Eq. \ref{eq:S1l}).
-
-\begin{eqnarray}
-L_{1}(h, \theta \mid u) &\propto& S_{1}(u \mid h, \theta) \cdot P(h) \cdot P(\theta) \label{eq:L1l} \\
-S_{1}(u \mid h) &\propto &\exp{(\lambda \cdot U(u; h; \theta)  } \label{eq:S1l} \\
-U(u; h; \theta)& =& \ln{  L_0(h \mid u, \theta) } - C(u) \label{eq:utilS1nomarginalization} \\
-L_{0}(h \mid u, \theta) &\propto& {\delta_{\denote{u}(h, \theta)}} \cdot P(h) \label{eq:L0l}
-\end{eqnarray}
-
-Eq.
-\ref{eq:L1} is mathematically equivalent to the gradable adjectives model of @Lassiter2013, with the modification that states of the world are defined with respect to the probability $h$ under discussion.
-In this model, the listener's posterior distribution on thresholds is arrived at by trying to make the utterance conveying the generalization to be both truthful and informative.
-That is, the listener must believe the threshold used by the speaker is both true and informative; very low thresholds could only be informative in contexts when the listener believes most probabilities are all very low *a priori*.
-
-These alternative pragmatic listener $L_1$ models give rise to corresponding alternative pragmatic speaker models.
-
-### Speaker models
-
-We can define two speaker models who reason about the two different pragmatic listeners.
-
-The speaker who reasons about the pragmatic listener in Eq.
-\ref{eq:L1u} is defined by a utility function similar to Eq.
-\ref{eq:utilS1nomarginalization}, but with informativity computed with respect to $L_1$'s posterior distribution rather than $L_0$.
-
-\begin{eqnarray}
-S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h; \theta)  } \label{eq:S1li} \\
-U(u; h; \theta) = \ln{  L_1(h \mid u) } - C(u) \label{eq:utilS2nomarginalization} \\
-\end{eqnarray}
-
-The model who reasons about the pragmatic listener in Eq.
-\ref{eq:L1l} marginalizes over $L_1$'s posterior distribution on the threshold $\theta$ in order to decide which utterance to produce (similar to \ref{eq:utilS1marginalization}).
-
-\begin{eqnarray}
-S_{2}(u \mid k) \propto \exp{(\lambda_2 \cdot U_{S_2}(u; k)  } \\ 
-U_{S_2}(u; h) = \ln{ \int_{\theta} L_1(h, \theta \mid u)}  \diff \theta - C(u) \label{eq:S2l}
-\end{eqnarray}
+## Model simulations
 
 All models were implemented in the probabilisitic programming language WebPPL [@dippl], and a complete, runable versions of the models in the following section can be found at \url{http://forestdb.org/models/generics.html}
-
-## Model simulations
 
@@
 ```{r generic-fullmodel, fig.width = 8}
-n_chains <- 1
-n_samples <- 50000
-burn <- n_samples
-
-model_prefix <- "results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-"
-
-m.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/generics/results/", model_prefix, 
-                    n_samples, "_burn", burn, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i)
-  m.samp <- bind_rows(m.samp, m.samp.i)
-  #print(i)
-}
+# n_chains <- 1
+# n_samples <- 50000
+# burn <- n_samples
+# 
+# model_prefix <- "results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-"
+# 
+# m.samp <- data.frame()
+# for (i in seq(1, n_chains)){
+#   mi <- fread(paste(project.path,  "models/generics/results/", model_prefix, 
+#                     n_samples, "_burn", burn, "_chain", i, ".csv", sep = ""))
+#   m.samp.i <- mi %>% mutate(chain = i)
+#   m.samp <- bind_rows(m.samp, m.samp.i)
+#   #print(i)
+# }
+
+m.samp <- fread(
+  paste(project.path,"models/generics/results/", 
+        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain1.csv",
+        sep = "")
+  ) %>% mutate(chain = 1)
 
@@
 
-```{r child = 'appendix-prevalencePrior.Rmd'}
+```{r child = 'appendix-alternativeRSAmodels.Rmd'}
 ```

### 2017-06-08 paper/generics-paper.Rmd
edits to intro, abstract

@@
     Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    One major issue in formalizing *genericity* is that such language is extremely flexible in its usage. 
+    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible in communicating generalizations.
     Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about events (i.e., *habitual language*, e.g., *John runs*), causes (i.e., *causal language*, e.g., *The block makes the machine play music.*), and categories (i.e., *generic language*, e.g., *Birds fly*), and find that the model, and not simpler models, explains full spectra of endorsements of generalizations in language.
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (i.e., *generic language*, e.g., *Birds fly*), events (i.e., *habitual language*, e.g., *John runs*), and causes (i.e., *causal language*, e.g., *The block makes the machine play music.*).
+Across these divesre domains, we find that our model, and not simpler models, explains the full spectra of endorsements of generalizations in language.
     The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
@@
 
-Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge for a cognitive agent.
-We learn such *generalizations* early in life by observing instances and drawing inductive inferences [@Dewar2010].
-Social learning---relying upon the human capacity to infer others' intentions---faciliates this process [@Csibra2009; @Tomasello1999; @Butler2012].
-At around a child's first birthday, her mind gains access to a new, human-unique source of data: language.
+Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
+We acquire such *generalizations* early in life, simply by observing instances and drawing inductive inferences [@Xu2008; @Dewar2010].
+Once learners have the capacity to infer the intention of others, social learning can dramatically faciliate inductive reasoning [@Csibra2009; @Tomasello1999; @Butler2012].
+At around the first birthday, a child's mind gains access to a new, human-unique source of data: language.
 
@@
 -->
-
-Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Graham2004; @Markman1989].
+Learning from language is helpful because many properties are costly to directly observe (e.g., being poisonous) or events statistically unlikely (e.g., observing lightning).
+Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
 But language also has the ability to refer to *generalization itself*.
 At around the age of two and a half, children begin to understand that *generic language* (e.g., "Dogs bark") refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
+<!-- *Causal language*, expressing generalization beyond an individual causal event (e.g., "The block *makes* it [the machine] go."), faciliates more abstract forms of causal reasoning [@Bonawitz2010].
+-->
 Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are central to the growth of conceptual knowledge [#Gelman2004] 
 Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
+
+Generic meaning, or *genericity*, can be observed in seemingly disparate kinds of linguistic devices [@Carlson1977; @Carlson1995].
+Speakers can talk about individual people in generalizations (*habitual language*; e.g., "Mary swims after work."), individual causal events in generalizations (*causal language*; e.g., "Drinking moonshine makes you go blind."), and people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that such languge is central to the growth of conceptual knowledge [@Gelman2004] 
 It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].
 
-Computational models of learning formalize the inferences derived from observations, focusing on the question of how children and adults generalize from sparse data [@Tenenbaum2011]. 
-They showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
+<!-- Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization. -->
+<!-- *Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general , specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
+-->
+<!-- Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious.  -->
+<!-- Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.  -->
+
+Computational models of learning formalize the inferences derived from observations, explaining how children and adults generalize from sparse data [@Tenenbaum2011]. 
+Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
 Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000].
@@
 
-The major issue in formalizing generic language is determining what makes a generic statement true or false. 
-When we hear *Dogs bark*, we may feel it's a universal statment as in *All* dogs bark.
-We may then realize that, among others, exquisitely well-trained dogs do not bark, which means the generic should signal something weaker like *Most* dogs bark.
-Indeed, many generic statements seem to have the quantificational force of *most*. 
-But most mosquitos do not carry malaria, while the statement *Mosquitos carry malaria* is intuitively true.
-So the generic must in some way be compatible with *some* (e.g., *some mosquitos carry malaria*).
-But equating the generic with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
-Perhaps properties that only apply to one gender are an exception, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
-
-Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization.
-*Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general (e.g., *You never know what will happen on a blind date*), specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
-Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious. 
-Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.
+The major issue in formalizing genericity is determining what makes statements that convey generalizations true or false. 
+When we hear "Dogs bark", we may feel it's a universal statment as in *All* dogs bark.
+Yet, exquisitely well-trained dogs, among others, do not bark; the statement should signal something weaker like *Most* dogs bark.
+Indeed, many generalizations seem to have the quantificational force of *most*. 
+But most mosquitos do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
+The only quantifier that would permit such a generalization would be "Some" (e.g., *some mosquitos carry malaria*).
+But equating the generalization with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
+Perhaps we should make exceptions for properties that only apply to one gender, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
 
 In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to define the truth conditions of generalizations in language. 
-By formalizing such a hypothesis in a probabilistic language understanding model, we derive predictions for endorsements of such statements by specifying relevant prior knowledge.
+By formalizing such a hypothesis in a probabilistic language understanding model, we can derive predictions for endorsements of such statements by specifying relevant prior knowledge in the model.
 Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
@@
 In each domain, we define a scale that corresponds to the relevant metric by which a learner should generalize. 
-We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fail.
+We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fall short.
 
 The rest of this paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in different domains. 
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this uncertain semantics into a general framework for pragmatic language understanding -- the Rational Speech Act framework.
+In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in our three domains. 
+In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a general framework for pragmatic language understanding -- the Rational Speech Act framework.
 
@@
 Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments the measure both (i) and (ii) and relate it to the endorsements of generalizations about categories, or *generic language*. 
+In Section 3, we describe experiments the measure both (i) and (ii) and relate them to the endorsements of generalizations about categories, or *generic language*. 
 In Section 4, we describe experiments that measure (i) and manipulate (ii) to predict endorsements of generalizations about events, or *habitual language*.
 In Section 5, we describe experiments that manipulate both (i) and (ii) to predict endorsements of generalizations about causes, or *causal language*. 
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
-In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literature on *genericity*.
-Our theory also opens up a number of new directions for understanding generic language and building models that learn and think like people.
+Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
+In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
+Our theory also opens up a number of new directions for understanding generic language and building models that learn from language like people.
 

### 2017-06-08 paper/generics-paper.Rmd
edits throughout model sections, adjust fig 1

@@
 
-We can make particular statements about objects, events, and causes.
+Particular statements can be made about objects, events, and causes.
 We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
-To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must say exactly how the particular relates to the generalization.
+To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
 We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
@@
 ].
-In the study of categories and properties, $x$ is an object.
-For a behavior exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
-In this case, $x$ is a instance of an agent.
-Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$: $h = P(x \in e \mid x \in c)$.
-We refer to this probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
+<!-- In the study of categories and properties, $x$ is an object. -->
+For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
+<!-- In this case, $x$ is a instance of an agent. -->
+Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$, known as causal power: $h = P(x \in e \mid x \in c)$.
+Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
 <!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->
@@
 For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
-Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent [@Goodman2009].
-Quantitative modeling has been crucial in explaining how the subtleties of experience relate to subtleties in generalization [@Tenenbaum2006; @Kemp2008].
-
-Studying generalizations from observational evidence can only take us so far in understanding how the mind understands the world or culture accumulates across generations.
+This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
+Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent, which is predicted assuming the data-generating process (i.e., the likelihood function) is another agent [@Goodman2009].
+
+Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
 Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
@@
 
-We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the formalization described in the previous section.
+We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
 Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly").
@@
 At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
-*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs (not exactly *most robins*). 
+*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs, which is debatable whether or not that counts as *most robins*. 
 If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
@@
 The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
-*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a dangerous world.
-This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which has been empirically verified [@Cimpian2010; @Prasada2013].
+*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
+This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which was empirically corroborated [@Cimpian2010; @Prasada2013].
 Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].
@@
 Yet, generics are not limited to conveying rich relations. 
-Arbitrary relations can also be expressed like *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
-The *generics as default* view must then be supplemented with the principle that, in certain situations, the statistics can influence generic endorsement.
+Arbitrary relations can also be expressed such as *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
+The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
 How do we make sense of this panoply of conditions?
@@
 In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
-If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement.
-
-\begin{eqnarray}
-L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed}
-\end{eqnarray}
-
-Equation \ref{eq:L0fixed} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
-$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
-The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
-We term this prior distribution the *prevalence prior*.
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
-For an utterance conveying a generalization $u_{gen}$, we adopt a simple threshold semantics:
+If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
 
@@
 
-The $\delta_{\denote{u}(h, \theta)}$ likelihood is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
+$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
 Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
@@
 In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
-We assume this prior is uninformed: $\theta \sim \text{Uniform}(0, 1)$.
+We assume this prior is uninformed: $P(\theta) = \text{Uniform}(0, 1)$.
 
@@
 \end{eqnarray}
+
+Equation \ref{eq:L0} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
+$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
+The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
+We term this prior distribution the *prevalence prior*.
+$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
+
+<!-- \begin{eqnarray} -->
+<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
+<!-- \end{eqnarray} -->
 
@@
 The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
-"Some" rules out only the lowest possible state and returns a posterior very similar to the prior.
+The fixed threshold model rules out only the lowest possible state and returns a posterior very similar to the prior.
 The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.
@@
 The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
-If the threshold is very high, only the highest $h$ would pass the threshold.
-If the threshold is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
-As the threshold takes on lower and lower values, more and more probabilities would surpass it.
-When the threshold is very low, almost all probabilities are consistent with it (akin to "Some").
+If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
+If the threshold $\theta$  is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
+As the threshold $\theta$  takes on lower and lower values, more and more $h$ probabilities would surpass it.
+When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
 When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.
@@
 The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
-To model generic endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
+To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
 with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
@@
 ]
+
+The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
+This *simple but underspecified* hypothesis defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
+We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix A.
 
@@
   mutate(Distribution = factor(Distribution, levels = 
-                             c("Prior_some", "Posterior_Generalization_some", "Posterior_Generalization_generic"),
-                                labels = c("Prior/Silence", "Some", "Generalization")),
-         PriorShape = fct_relevel(PriorShape, "uniform", "barks","laysEggs","carriesMalaria","isFemale"
+                             c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
+                                labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")),
+         PriorShape = factor(PriorShape, levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
+                             labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                   #"eatsFood","areSick", "uniformRare", 
@@
     #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   scale_fill_manual(values = c("#636363", "#2b83ba","#d7191c"))+
-    scale_color_manual(values = c("#636363","#2b83ba", "#d7191c"))+
+   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
     #scale_linetype_manual(values = c(3, 4, 2, 1))+
@@
     scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    xlab("Degree of propensity (probability)") +
-    ylab("Probability density") +
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Degree of probability h") +
+    ylab("Scaled probability density") +
   facet_grid(PriorShape~Distribution, scales = 'free')+
+  guides(fill = F, color = F)+
   theme(strip.text.y = element_text(angle = 0))
@@
 
-All of the RSA models defined in the previous section predict that the interpretation and endorsement of a generalization depends listener's *a priori* beliefs about the probabilty in question $P(h)$.
-Qualitatively, the predictions of the different formulations of the RSA models for understanding generalizations are not appreciably different (though their quantitative predictive flexibility is).
-For purposes of illustration, we present present predictions of the simplest model with an underspecified threshold and a model where the threshold is fixed to 0 (corresponding intuitively to *some* statements).
-
-Before, we described how an underspecified threshold interacts with a uniformly uncertain belief about the probability.
+The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon a listener's *a priori* beliefs about the probabilty in question $P(h)$.
+For purposes of illustration, we present present the listener $L$ interpretations of the generalization for the underspecified threshol model as well as a fixed threshold model where the threhsold is set to the lowest possible value, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+
+Above, we described the intuition for how an underspecified threshold interacts with a uniformly uncertain belief about the probability $h$.
 Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
-Our model of endorsements is a model of speaker who decides whether or not to say the generic or stay silent. 
-Thus, qualitatively model predictions for endorsement can be gleaned by comparing the prior distribution over the probability $h$ (which is the same as posterior upon hearing "silence") with the posterior distribution over $h$ upon hearing the generalization.
+Note that our model of endorsements is a model of a speaker who decides whether or not to say the generic or stay silent. 
+Qualitatively speaking, model predictions for endorsement can be gleaned by comparing the posterior distribution over the probability $h$ upon hearing the generalization with the prior distribution over $h$ (which is the same as the listener's posterior upon hearing "silence").
+For different degrees of target probability $h$ that the speaker wants to communicate, the generalization will be more or less good at communicating it.
 
 In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
-Here, we show the prior is bimodal with peaks at 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have 0\% prevalence) and for those that do have members that bark, many of them bark (i.e., have some high prevalence value).
-The fact that "those that do not bark" is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who does not usually bark (say, a cat) could somehow have the feature (e.g., due to some transient or accidental state).
-We see that the quantifier "Some" (middle row) struggles to differentiate those that accidentally do have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.
+Here, we posit the prior is bimodal with peaks near 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have $h \sim 0$) and for those that do have members that bark, many of them bark (i.e., have some high $h$).
+<!--  -->
+We see that the fixed threshold (middle row) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
+We model "those that do not generally have the feature" a Beta distribution with an expected value (mean) close to zero. 
+The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
+]
 Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.
 
-The strength of a listener's inference (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over the prevalence of the feature.
+The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
 Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
@@
 Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
-The intuitive differences in the endorsements of these statements comes from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
+Differences in the endorsements of these two statements would come from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
 In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content.
@@
 
-In the rest of this paper, we examine the validity and generality of this theory of communicating generalizations through three case studies: generalizations about categories, events, and causes.
+In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$ as well as the inferences derived from a fixed-threshold semantics.
+In the rest of this paper, we examine the behavior of the speaker model as a model of endorsements through three case studies: generalizations about categories, events, and causes.
 

### 2017-06-08 paper/generics-paper.Rmd
fix citations

@@
 ---
-title             : "Communicating generalizations about categories, events, and causes"
+title             : "Communicating generalizations"
 shorttitle        : "Communicating generalizations"
@@
 
-Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
+Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
 The basic currency of inference in these models is probability.
@@
 
-```{r simulations, fig.width = 8, fig.height=5}
+```{r simulations, fig.width = 9, fig.height=5}
 all.simulations %>%
@@
 Generic language (e.g., *Birds fly.*) exhibits substantial flexibility in meaning and truth conditions as described above.
+As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs.
+"Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties.
+We do this by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
+\ref{eq:L0} as well as the target probabilitiy that the speaker model seeks to convey $h$ in Eq.
+\ref{eq:S1}.
+We show how these measurements systematically predict, via our model, endorsements of generic statements about familiar categories (Expt. 1b).
+
 <!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
@@
 <!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->
-
-As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties and show how it systematically predicts endorsements of familiar generic statements (Expt.
-1).
-In Experiment 3, we replicate and extend a paradigm used by @Cimpian2010 to demonstrate the asymmetry between endorsements and interpretations and find that a similar pattern is predicted by our model.
 
@@
 We hypothesize that this prior distribution encodes probabilities associated with deeper conceptual knowledge [e.g., of the kind discussed by @Prasada2013].
-This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada; @Gelman; @Leslie].
+This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
 If, indeed, there are such things as different types of kind--property relations (e.g., *principled* v.
 *accidental relations*), we would expect the prevalence prior data to follow a multi-modal, mixture distribution where different modes or components of the prior are the results of the different types of relations.
-As a simple of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
+As a simple test of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
 
@@
                       labels = c(
-                                 "Speaker model - uncertain semantics",
-                                 "Speaker model - fixed semantics",
-                                 "Prevalence alone", "Prevalence & Cue validity"
+                                 "Uncertain semantics model",
+                                 "Fixed semantics model",
+                                 "Prevalence alone", "Prevalence + Cue validity"
                                  ))) %>%
@@
 
-```{r generics-endorsement-figure, fig.width=7, fig.height=5}
+```{r generics-endorsement-figure, fig.width=11, fig.height=8}
 grid.arrange(generics.endorsement.spectrum, 
@@
 
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality (CITE noah's and kemp's causality and causal models papers?).
+Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
 Communicating generalizations about causally related events is potentially highly useful because no one individual can run all the experiments that she wants to run in a life time. 
@@
 In this domain, an instance of the category is a single causal event (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough at a particular time of the day). 
-@Gerstenberg
-The study of *elemental causal induction* is itself very subtle, depending on an observer's background theory of causality. [@Griffiths2005; @Schulz].
+[Gerstenberg]
+The study of *elemental causal induction* is itself very subtle, depending on an observer's background theory of causality. [@Griffiths2005; @Schulz2008a].
 
@@
 This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Pelletier; @Cohen1999; @Nickel].
-As @Nickel2013 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
+We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
+As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
 We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
@@
 This may be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance: (1) that the meaning is a threshold-function (i.e., $\denote{u}(p, \theta) = \{p :p > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance: (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
 If there is no fixed value of the threshold, then a uniform prior over the threshold in the truth-functional threshold semantics is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is *the degree itself*, normalized by the prior distribution over the degree (i.e., the comparison class).
@@
 $$
-\int_{0}^{1} \delta_{p > \theta} \diff \theta =  p
+\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
 $$
@@
 Finally, (4) is used to argue that even if the property is widespread (perhaps in a soft sense, as in our model, relative to other kinds or groups), we might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive, we might still not want to say *Women are submissive* [@Haslanger]. 
+That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive, we might still not want to say *Women are submissive* [@Haslanger2011]. 
 In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 

### 2017-06-08 paper/generics-paper.Rmd
clean up habituals methods

@@
   var marginalPrevalence = sample(flip(phi) ? stableComponent : transientComponent)
-  return {g, d,phi, marginalPrevalence}
+  return {g, d, phi, marginalPrevalence}
 }
@@
 ```
+
 ```{r, eval = F}
-
 ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
@@
   ylab("MAP estimate and 95% HDI of Mixture parameter")
-
 ```
@@
 
-Habituals about people are of particularly importance because they are likely central to intuitive theories of personality and behavior. 
+Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
+Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
 @McGuire1986 explored 5th to 12th graders' responses to open ended probes such as ``Tell us about your school / family''. 
@@
 ``My brother works part-time at the restaurant.'').
-Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
 Habitual language may be a more conservative form of trait language (e.g. \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
 
-Habituals are a particularly amenable domain to manipulating the target propensity that a speaker aims to communicate.
+From a methodological standpoint, habituals are a particularly amenable domain to manipulating the target propensity that a speaker aims to communicate.
 People are often in the situation of being introduced to new people and learning new information about them.
@@
 Some items show substantial differences between the genders (e.g. \emph{wears a bra}) and some show subtle differences (e.g. \emph{watches professional football}).
-%It is \emph{a priori} unclear whether or not $P(x)$ in Eqs.~\ref{eq:L1}, \ref{eq:L0} is the distribution over frequency of action with respect to \emph{all people}, or if it is restricted to be gender specific.
-%For example, are the frequency conditions by which a man would qualify to ``wear a bra'' (habitually) different than those by which a woman would qualify to ``wear a bra''?
-We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender.
-%In order to explore this possibility, we will select items with priors that differ by gender to explore more closely in Experiment 2.
+Our prior distributions $P(h)$ are with respect to an alternative class of entities (e.g., other individuals). 
+It's possible that when evaluating habitual statements, $P(h)$ is with respect to either *all people* or *people of the same gender*. 
+For example, are the frequency conditions by which a man would qualify to "watch professional football" (habitually) different than those by which a woman would qualify to "watch professional football"?
+We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender.
 
@@
 Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed 37 trials, which were composed of the 27 items from the prior elicitation task and 4 additional filler items not in the prior elicitation task randomly paired with either a male or female character name.
+Participants completed 37 trials, which were composed of the 31 items from the prior elicitation task randomly paired with either a male or female character name.
 6 of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who watched professional football).
 These were used for an exploratory analysis on gender differences.
-The 4 filler items were not used in the prior elicitation because they described illegal activities (e.g., "doing cocaine", "stealing cars").
 The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-2.html}.

### 2017-06-09 paper/generics-paper.Rmd
clean intro to causals; causals prior analysis and figures; endorsements for causals

@@
 Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
-We acquire such *generalizations* early in life, simply by observing instances and drawing inductive inferences [@Xu2008; @Dewar2010].
+We acquire such *generalizations* early in life, simply by observing instances and drawing inductive inferences [@Baldwin1993; @Xu2008; @Dewar2010].
 Once learners have the capacity to infer the intention of others, social learning can dramatically faciliate inductive reasoning [@Csibra2009; @Tomasello1999; @Butler2012].
@@
 Our framework for communicating generalizations makes predictions about statements conveying genericty about a category of causal events. 
-In this domain, an instance of the category is a single causal event (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough at a particular time of the day). 
-[Gerstenberg]
-The study of *elemental causal induction* is itself very subtle, depending on an observer's background theory of causality. [@Griffiths2005; @Schulz2008a].
-
-We design this last experiment with the goal of testing whether background knowledge that gives rise to the prevalence priors is causally related to the endorsement of causal statements.
+In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
+<!-- [Gerstenberg] -->
+Determining whether or not a singular event itself is causal is challenging, plausibly having to do with counterfactual reasoning [e.g., @Gerstenberg2015how]. 
+Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
+
+Language provides a way to bypass the observational data needed to make a causal induction.
+Indeed, causal language has been shown to faciliate causal learning for nonobvious causal relations [@Bonawitz2010].
+We design this last experiment with the goal of testing the causal relationship between the prevalence priors that we posit as a mediating representation between abstract conecptual structure and endorsements of generalizations about causes.
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
@@
 
-People have theories about how different casusal systems work. 
-Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force. 
-If the experiment is repeated exactly, we would expect the same results.
-In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't. 
-Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
-
-In this experiment, we examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present.
-We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains.
+In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
+This prediction task serves as a manipulation check for our prevalence prior manipulation.
+
+<!-- examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present. -->
+<!-- We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains. -->
+
+<!-- People have theories about how different casusal systems work.  -->
+<!-- Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force.  -->
+<!-- If the experiment is repeated exactly, we would expect the same results. -->
+<!-- In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't.  -->
+<!-- Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
+-->
 
@@
 
+```{r causal-priors-data}
+
+d.cas.priors <- read.csv(paste(project.path,
+                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
+                           sep= ""))
+
+n.subj.cas <- length(unique(d.cas.priors$workerid))
+
+ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
+
+```
+
 #### Participants
 
-We recruited N participants from Amazon's Mechanical Turk.
+We recruited `r n.subj.cas` participants from Amazon's Mechanical Turk.
 Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average N minutes and participants were compensated \$N.NN for their work.
+The experiment took on average `r ave.minutes.cas` minutes and participants were compensated \$0.50 for their work.
 
@@
 
+#### Procedure
+
 The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain in question.
+In the first phase, participants are given a story about a causal domain.
 In the second phase, participants are asked to make a judgment corresponding to the between-subjects condition they are assigned (prior, endorsement, interpretation).
 
-#### Procedure
-
-Participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (e.g., how to make a certain kind of animal more alert). They are told:
+In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
+The story for the "sleepy animals" condition read:
 
@@
 You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called  (e.g., daiths) and your team of scientists wants to figure out what makes daiths's hair turn brown. 
-Your team runs experiments trying to make daiths's hair turn brown with different chemical compounds. 
+On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. 
+Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
 The results are shown below:
@@
 Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., The team tested Food A on 100 daiths.
-30 of them were made more alert.) as well as put into a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 6).
+Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
+Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
+Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
 After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
 
-Upon proceeding to phase 2, the results of the "experiments" are removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 4 experiments.
-Participants were given 4 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., foods M, N, P, and Q).
+Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
+Participants were asked to predict the results of the next 5 experiments.
+Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
 
@@
 
-The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model.
-Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
-So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.
-
-A second dimension of manipulation corresponds to the extent to which *determinism* is expected in the domain. 
-For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.
+Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
+The cover story for the "tall plants" condition read:
+
+\begin{quotation}
+You are an astronaut-scientist exploring a distant planet. 
+On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
+Your team runs experiments trying to make feps grow tall with different fertilizers. 
+The results are shown below:
+\end{quotation}
+
+Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
+In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
+In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
+In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
+
+The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
+These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
+
+```{r causals-conditions, fig.caption = "Four background distributions participants were exposed to in Expt. 4"}
+sample.dists <- bind_rows(
+  data.frame(
+    dist = "rare weak",
+    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
+          rbeta(n = 7000, shape1 = 2, shape2 = 50)
+          )
+  ),
+  data.frame(
+    dist = "common weak",
+    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
+  ),
+  data.frame(
+    dist = "rare deterministic",
+    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
+          rbeta(n = 7000, shape1 = 2, shape2 = 50)
+          )
+  ),
+  data.frame(
+    dist = "common deterministic",
+    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
+  )
+) %>%
+    mutate(Distribution = factor(dist, 
+                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
+         labels = c("Common Deterministic", "Rare Deterministic",
+                    "Common Weak", "Rare Weak")))
+
+ggplot(sample.dists, aes(x = x, fill = Distribution, color = Distribution))+ 
+  geom_density( adjust = 1.3, alpha =0.8, 
+               size = 1.2,
+               aes( y = ..scaled..))+ #
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
+  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
+  ylab("Scaled Prior Probability")+
+  xlab("Target probability")+
+  facet_wrap(~Distribution, scales = 'free')+
+  guides(fill = F, color = F)
+```
+
+<!-- #### Materials  -->
+
+<!-- The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model. -->
+<!-- Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
+-->
+<!-- So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.  -->
+
+<!-- A second dimension of man ipulation corresponds to the extent to which *determinism* is expected in the domain.  -->
+<!-- For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.  -->
 
@@
 
-...
+The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:empirical-causal-prior-densities}.
+These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
+We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
+
+```{r empirical-causal-prior-densities, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
+
+d.cas.priors %>%
+  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
+      mutate(Distribution = factor(distribution, 
+                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
+         labels = c("Rare Deterministic",
+                    "Common Weak", "Rare Weak"))) %>% 
+ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
+  geom_density( adjust = 0.8, alpha =0.8, 
+               size = 1.2,
+               aes( y = ..scaled..))+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
+  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
+  ylab("Scaled Prior Probability")+
+  xlab("Target probability")+
+  facet_wrap(~Distribution, scales = 'free')+
+  guides(fill = F, color = F)
+```
+
+### Model predictions
+
+... run RSA model using fixed parameters and MAP estimates of these priors ...
 
@@
 
-#### Participants
-
-We recruited N participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 4a. 
-The experiment took on average N minutes and participants were compensated \$N.NN for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 4a.
-Phase 1 of the experiment was identical to that of Experiment 4a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants were then asked to judge the causal sentence: "Treatment X makes the effect happen". 
-Partipants responded by either clicking "Yes" or "No".
-
-Participants saw 1 of 3 frequencies: 20\%, 50\%, or 80\%.
-
-### Results
-
-```{r causals-endorsement}
+```{r}
 d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
@@
 d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
+
+n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
+ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
+
+n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
 
@@
 
+```
+
+#### Participants
+
+We recruited `r n.subj.cas.endorse` participants from Amazon's Mechanical Turk.
+Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
+None of the participants had participated in Experiment 4a. 
+The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
+
+#### Procedure and materials
+
+The materials were the same as in Experiment 4a.
+Phase 1 of the experiment was identical to that of Experiment 4a.
+In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
+The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
+Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
+Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
+Partipants responded by either clicking "Yes" or "No".
+
+After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
+This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
+
+### Results
+
+```{r causals-endorsement, fig.width = 4, fig.height = 3}
+
 ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
@@
   scale_fill_solarized()+
-  xlab("Frequency")+
+  xlab("Target frequency")+
   ylab("Proportion Causal Endorsement")
 ```
+
+`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
+Figure \ref{fig:causals-endorsement} shows the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement for the different experimentally-manipulated priors and target frequencies.
 

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
update bib and appendix

@@
 
+```{r generic-endorsement}
+d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
+                    "truth-judgments_catch-trials.csv", sep = ""))
+
+d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
+                    "truth-judgments.csv", sep = ""))
+
+d.gen.endorse.summary <- left_join(
+  d.gen.endorse, 
+  d.gen.endorse.catch %>% select(workerid, pass)
+  ) %>%
+  filter(pass == 1) %>%
+  rowwise() %>%
+  mutate(response = ifelse(response == "agree-key", 1, 0),
+         sentence = gsub('&quotechar', '', sentence),
+         sentence = gsub('lyme', 'Lyme', sentence)) %>%
+  group_by(sentence) %>%
+  multi_boot_standard(column = "response") %>%
+  ungroup() %>%
+  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
+
+d.gen.endorse.bayes <- left_join(
+  d.gen.endorse, 
+  d.gen.endorse.catch %>% select(workerid, pass)
+  ) %>%
+  filter(pass == 1) %>%
+  rowwise() %>%
+  mutate(response = ifelse(response == "agree-key", 1, 0),
+         sentence = gsub('&quotechar', '', sentence),
+         sentence = gsub('lyme', 'Lyme', sentence)) %>%
+  group_by(sentence) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b)) %>% 
+  ungroup() %>%
+  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))
+```
+
 ### Uncertain threshold RSA
@@
 full_sentences <- mutate(md, sentence = paste(category, property, sep = "_"))$sentence
+
+d.gen.endorse.bayes
 

### 2017-06-09 paper/generics-paper.Rmd
grid arrange support

@@
 library(jsonlite)
+library(gridExtra)
 theme_set(theme_few())
@@
 }
-project.path <- "~/Documents/research/comgen-paper/"
+project.path <- "../"
 options("scipen"=10) 
@@
 `r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-Figure \ref{fig:causals-endorsement} shows the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement for the different experimentally-manipulated priors and target frequencies.
+Figure \ref{fig:causals-endorsement} shows the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement for the different experimentally-manipulated priors and frequencies.
 

### 2017-06-09 paper/generics-paper.Rmd
comment out latex style figures

@@
 
-\begin{figure*}[t]
-\centering
-  \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3}
-  \caption{
-  Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency). 
-  Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions. 
-  Actual frequency noted on x-axis for examples (left).
-  Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions. 
-  Error bars suppressed and points jittered on left facet for visual clarity.
-  }
-  \label{fig:tjScatters}
-\end{figure*}
+<!-- \begin{figure*}[t] -->
+<!-- \centering -->
+<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
+<!--   \caption{ -->
+<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
+<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
+<!--   Actual frequency noted on x-axis for examples (left). -->
+<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
+<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
+<!--   } -->
+<!--   \label{fig:tjScatters} -->
+<!-- \end{figure*} -->
 
@@
 
-\begin{figure*}[t]
-\centering
-  \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf}
-  \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity).
-  Middle: Human endorsements of habitual sentences (Expt.
+<!-- \begin{figure*}[t] -->
+<!-- \centering -->
+<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
+<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
+<!--   Middle: Human endorsements of habitual sentences (Expt.
 3b) vs.
@@
 2 (assumed to have the same predictive log frequency as baseline).
-  Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).}
-  \label{fig:tj3}
-  \vspace{-7pt}
-\end{figure*}
+-->
+<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
+<!--   \label{fig:tj3} -->
+<!--   \vspace{-7pt} -->
+<!-- \end{figure*} -->
 

### 2017-06-09 paper/appendix-cueValidity.Rmd
create alt models appendix; begin full posterior appendix
fix path in appendices

@@
 theme_set(theme_few())
-project.path <- "~/Documents/research/communicating-generalizations/"
+project.path <- "../"
 data.path <- "data/generics/endorsement/"
@@
 In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
-Here, the prevalence of the feature, or $P(f \mid k)$, is the important quantity.
+Here, the prevalence of the feature, or $P(f \mid k)$, is the central quantity.
 Quantifiers can be described as conditions on prevalence: $\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}$.

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
fix path in appendices

@@
 }
-project.path <- "~/Documents/research/comgen-paper/"
+project.path <- "../"
 data.path <- "data/generics/endorsement/"

### 2017-06-09 paper/generics-paper.Rmd
discuss causals, edits to gd

@@
 ```{r include = FALSE}
-library("papaja")
+
 ```
@@
 ```{r libraries}
+library(papaja)
+library(formatR)
 library(rwebppl)
@@
 `r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-Figure \ref{fig:causals-endorsement} shows the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement for the different experimentally-manipulated priors and frequencies.
+As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior (i.e., a Beta-Binomial model).
+These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
 
 ## Discussion
+
+In our third case study, we applied our same model to generalizations about causal events.
+In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 4a).
+We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
+In Expt. 4b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
+In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ construct that we posit is causally related to endorsement.
+
+In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
+In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
+These two features of the domains make them particularly amenable to manipulation.
+That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
+
+It's likely that there exist domains for which abstract, intuitive theories might interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
+If this were happening in our domains, we would expect this to show up in the results of Expt.
+4a.
+Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
+]
+For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "strong" priors conditions. 
+Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
+Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
 
@@
 The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language (CITE).
+Generic language is one of the earliest emerging forms of complex, compositional language.
 Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-More on development.
+...More on development...
 
@@
 The extreme flexibility of generic meaning stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward, emerge much *later* in development.
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (namely, a truth-functional threshold) will not work for generic language [@Leslie2008].
-
-This may be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance: (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-If there is no fixed value of the threshold, then a uniform prior over the threshold in the truth-functional threshold semantics is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is *the degree itself*, normalized by the prior distribution over the degree (i.e., the comparison class).
-
+In fact, quantified statements, whose formal meaning is much more straight-forward, emerge much *later* in development [@Brandone2014; @Gelman2015].
+This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) will not work for generic language [@Leslie2008].
+
+This would be throwing out the baby with the bathwater.
+When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
+This prior could then be updated with more data to acquire its fixed meaning.
+For the generic statement, the language learner is done once she acquires (1). 
+The rest of the meaning is inferred in context.
+
+There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
+A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
 $$
@@
 
-Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early.
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* sematnics.
+This *soft semantics* (corresponding intuitively to something like "more is better") is perhaps the simplest semantics one could imagine.
+<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
+The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
 This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
@@
 Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
+
+This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
+This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual prevalence is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
+In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
+4a) and the structured elictation used in habituals (Expt.
+2a), we have observed that the prior distribution over the prevalence of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
+That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors. 
+Thus, our model would also predict these effects, but by way of the prevalence prior rather than something special about dangerous features per se.
+However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
+
 Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
@@
 
-With reasonable assumptions about the prior (e.g., assuming international elephants are unlikely), upon the hearing "Elephants live in Africa", the moddel infers that most elephants live in Africa.
+With reasonable assumptions about the prior (e.g., assuming international elephants are unlikely), upon the hearing "Elephants live in Africa", the model infers that most elephants live in Africa.
 When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
+A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
 This is a nice feature of the uncertain threshold semantics: flexibility in accomodating new evidence that might otherwise contradict previous statements.
@@
 Finally, (4) is used to argue that even if the property is widespread (perhaps in a soft sense, as in our model, relative to other kinds or groups), we might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive, we might still not want to say *Women are submissive* [@Haslanger2011]. 
+That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to say *Women are submissive* [@Haslanger2011].
 In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth [cf., @Cimpian2010].
-The current formulation of the model is relatively ambivalent the deviations of the listener's beliefs from the speaker's beliefa.
-Other models in the RSA framework have identified states of the world with different subjective values (e.g., how good of a job a listener did on a task), and speakers with utilities that extend beyond conveying information can produce qualitatively different patterns of utterances [e.g., polite speech; @Yoon2016; @Yoon2017].
-If our model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
+If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
+Note that this can naturally capture the central phenoman described in @Cimpian2010.
+].
+The current formulation of the model is relatively ambivalent the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence can be exaggerated from the generic statement).
+If states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
+This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
+If our model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
+We find this possibility intruiging for future work.
 

### 2017-06-09 paper/generics-paper.Rmd
predictive habituals data and some analysis

@@
 library(gridExtra)
+library(lme4)
 theme_set(theme_few())
@@
 
+```{r habituals-predictive-elicitation}
+d.hab.predictive <- read.csv(paste(
+  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
+
+n.subj.hab.pred < - length(unique(d.hab.predictive$workerid))
+ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
+      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
+      summarize(total = mean(totalSec))
+
+# participant reported this in the comments section (it was recorded as a symbol)
+d.hab.predictive[
+  (d.hab.predictive$workerid==44 & 
+     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
+d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
+
+d.hab.predictive<- d.hab.predictive %>%
+  rowwise() %>%
+  mutate(
+    annualPredictiveRate =
+           annualRates[[as.character(past_interval)]]*response,
+    annualPastRate =
+           annualRates[[as.character(past_interval)]]*past_freq,
+    annualPredictiveRate = ifelse(
+      annualPredictiveRate == 0, 0.05, 
+      annualPredictiveRate),
+    logAnnualPredictiveRate = log(annualPredictiveRate),
+    logAnnualPastRate = log(annualPastRate)
+    )
+
+d.hab.predictive.summary <- d.hab.predictive %>%
+  group_by(condition, item, logAnnualPastRate) %>%
+  multi_boot_standard(column = "logAnnualPredictiveRate")
+
+fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary, 
+       aes(x=logAnnualPastRate, 
+                              y = mean, 
+                              ymin = ci_lower, ymax = ci_upper, 
+                              fill = condition, shape=condition))+
+  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
+  scale_shape_manual(values=c(21,22,23))+
+  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
+  # #geom_errorbar(width=0.1)+
+  scale_x_continuous(limits = c(-3,6), 
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(-3,6), 
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+  guides(fill=F, shape=F)+
+  scale_fill_solarized()+
+  xlab("Past frequency (log scale)")+
+  ylab("Predicted frequency (log scale)")+
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
 #### Methods
 
-We recruited 120 participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took 4 minutes on average and participants were compensated \$0.40.
+We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
+The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
 
@@
 
-Figure \ref{fig:tj3} (left) shows the predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g.
-participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
+Figure \ref{fig:habituals-predictive-figure} (left) shows the predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
+We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
 This means that our model makes identical predictions for Expt.
 2 whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:tj3} left; blue and green dots).
-
-+ MHT: Add some regression analysis here
+Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
+
+```{r habituals-predictive-elicitation-predictions}
+lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
+     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
+       (1 + condition | workerid) + 
+       (1 + condition | item)
+)
+lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
+```
+
+We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
+To account for participants and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
+Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
+).
+There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
+).
+Finally, past frequency was a significant predictor of predicted future frequency (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
+).
 
@@
 
+```{r habituals-predictive-endorsement}
+d.hab.predictive.endorsment <- read.csv(paste(
+  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
+d.hab.predictive.endorsment.catch <- read.csv(paste(
+  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
+
+n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
+ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
+      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
+      summarize(total = mean(totalSec))
+
+d.hab.predictive.endorsment.condition.summary <- left_join(
+  d.hab.predictive.endorsment, 
+  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
+  by = "workerid"
+  ) %>% filter(pass==1) %>%
+  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
+  rename(item = habitual) %>%
+  group_by(condition) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'baseline')
+
+d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'preventative')
+
+d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'enabling')
+
+d.hab.predictive.endorsment.summary <- left_join(
+  d.hab.predictive.endorsment, 
+  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
+  by = "workerid"
+  ) %>% filter(pass==1) %>%
+  mutate(response = ifelse(response=="agree-key", 1, 0),
+         time_period = factor(time_period,
+                              levels=c("month",
+                                       "2 months",
+                                       "year",
+                                       "2 years",
+                                       "5 years")),
+         condition = factor(condition,
+                            levels=c("enabling", "baseline", "preventative")),
+         hab_time = paste(habitual, time_period, sep='-')) %>%
+  rename(item = habitual) %>%
+  group_by(item, condition, hab_time, time_period) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.predictive.endorsment.summary <- left_join(
+  d.hab.predictive.endorsment.summary,
+  d.hab.predictive.summary %>% select(condition, item, logAnnualPastRate, mean, ci_lower, ci_upper) %>%
+    rename(logAnnualFutureRate = mean,
+         future_lower = ci_lower, future_upper = ci_upper)
+)
+
+fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
+  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
+                 fill=condition, shape=condition,
+                 xmin = future_lower, xmax=future_upper,
+                 ymin=low, ymax = high))+
+  geom_errorbar(alpha=0.3)+
+  geom_errorbarh(alpha=0.3)+
+  scale_shape_manual(values=c(21,22,23,24))+
+  geom_point(alpha = 0.7)+
+  xlab("Predicted frequency (log scale)")+
+  ylab("Endorsement probability")+
+  scale_x_continuous(limits = c(-3,6), 
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  coord_fixed(ratio=9)+
+  scale_fill_solarized()+
+  theme(
+    axis.text.x = element_text(angle = 90),
+    legend.position="bottom",
+    legend.direction="horizontal"
+    )
+
+```
+
+```{r habituals-predictive-figure, fig.cap="Left: Results of Expt 3a. Right: Results of Expt. 3b as they relate to the predicted frequencies from Expt. 3a"}
+grid.arrange(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, nrow = 1)
+```
+
 #### Methods
 
-We recruited 150 participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took 4 minutes on average on participants were compensated \$0.40 for their work.
+We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
+The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
 None of the participants had completed Expt. 3a.
-%\subsubsection{Procedure and materials}
 The only difference from Expt. 3a is the dependent measure. 
@@
 The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
+
 #### Results
 
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:tj3}, middle; blue points).
-When collapsing across items and subjecting the data to a generalized mixed-effects model with random by-participant effects of intercept and random by-item effects of intercept and conditions, we find evidence for a small effect of \emph{enabling} conditions on endorsements (M =  0.89; 95\% Bootstrapped CI [0.88, 0.91]) as compared to baseline (M = 0.85 [0.83, 0.87]) [$\beta = 0.42; SE = 0.15; z = 2.8$]
-, and a large effect of \emph{preventative} conditions on endorsements (M = 0.29 [0.26, 0.31]) [$\beta = -3.22; SE = 0.21; z = -15.2$]. 
-<!-- %\mht{should I add points from Expt. 2 to left-most scatter, or maybe there is a better plot?} -->
-
-We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b.
-We infer the two model parameters using the same analysis approach in Expt. 2. 
-The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right).
-The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$).
-These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past.
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points). 
-This may be due, in part, to an effect of the experimental context on participants: 
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
+There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}, middle; blue points).
+When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
+`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [
+`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
+`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
+], enabling = 
+`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [
+`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
+`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
+], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [
+`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
+`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
+]
+
+... ADD REGRESSION MODEL RESULTS ...
+
+... ADD RSA RESULTS ...
+<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
+<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
+<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
+<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
+<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
+
+<!-- Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).  -->
+<!-- This may be due, in part, to an effect of the experimental context on participants:  -->
+<!-- in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
 2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
+-->
+<!-- Future investigation into this issue is warranted. -->
 

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
generics prevalence distribution posterior plots

@@
 
-full_sentences <- mutate(md, sentence = paste(category, property, sep = "_"))$sentence
+full_sentences <- d.gen.endorse.bayes$sentence
 
@@
 d.prior.summary <- d.prior %>% 
-  mutate(sentence = paste(Category, Property, sep = "_")) %>%
+  mutate(sentence = paste(Category," " ,Property, ".", sep = "")) %>%
   filter(sentence %in% full_sentences) %>%
@@
   multi_boot_standard(column = "prevalence")
+```
+
+```{r fig.width = 6, fig.height = 6}
+bind_rows(
+  d.prior %>% 
+  mutate(sentence = paste(Category," " ,Property, ".", sep = "")) %>%
+  filter(sentence %in% full_sentences) %>%
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+    select(-workerid, -trial_type),
+  m.samp %>% 
+    filter(type == "withinKind") %>%
+    select(property, category, val) %>%
+    rename(Category = category, Property = property, prevalence = val) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = prevalence, color = src))+
+  geom_density(size = 1.1, aes( y = ..scaled.. ))+
+  facet_wrap(~Property + Category)+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(0,1)) +
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r}
+# joint model inferred prevalence 
+m.samp.targetPrev <- m.samp %>% 
+  filter(type == "withinKind") %>% 
+  group_by(category, property) %>%
+  summarize(MAP = estimate_mode(val),
+          cred_upper = hdi_upper(val),
+          cred_lower = hdi_lower(val)) %>%
+  ungroup() %>% rename(Category = category, Property = property)
+
+left_join(d.prior.summary, 
+          m.samp.targetPrev) %>%
+  ggplot(., aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+                y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0, 1))+
+  scale_y_continuous(limits = c(0, 1))+
+  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
+  coord_fixed()
 ```
@@
 Marginal distributions on prevalence
-```{r}
-
+```{r fig.width = 8, fig.height = 5}
+bind_rows(
+  d.prior %>% 
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+  select(-workerid, -trial_type, -Category),
+  m.samp.prevalence.prior %>% 
+    rename(Property = property) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = prevalence, color = src))+
+  geom_density(size = 1.1, aes( y = ..scaled.. ))+
+  facet_wrap( ~ Property, nrow = 3)+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(0,1)) +
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
 ```
@@
 
-```{r}
+```{r fig.width = 8, fig.height = 5}
 
@@
   d.prior %>% 
-    mutate(prevalence = prevalence / 100) %>%
-    rename(property = Property) %>% 
-    select(property, prevalence) %>%
-    mutate(src = 'data'),
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+  select(-workerid, -trial_type, -Category),
   m.samp.prevalence.prior %>% 
+    rename(Property = property) %>%
     mutate(src = 'model') 
@@
     stat_ecdf()+
-    facet_wrap(~property)+
+    facet_wrap(~Property, nrow = 3)+
     scale_color_solarized()+

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
more figures of full posterior on generics

@@
   paste(project.path,"models/generics/results/", 
-        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain1.csv",
+        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain2.csv",
         sep = "")
@@
 
+Forward sample Target Prevalence from posterior on parameters
+```{r}
+m.samp.prev.params <- m.samp %>%
+    filter(type == "targetPrevalence") %>%
+    mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type) %>%
+    #mutate(item = paste(parameter, property, sep = "_")) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category"), sep= "_")
+
+m.samp.prevalence <- m.samp.prev.params %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+```
+
 ```{r fig.width = 6, fig.height = 6}
@@
     select(-workerid, -trial_type),
-  m.samp %>% 
-    filter(type == "withinKind") %>%
-    select(property, category, val) %>%
-    rename(Category = category, Property = property, prevalence = val) %>%
+  m.samp.prevalence %>% 
+    select(property, category, prevalence) %>%
+    rename(Category = category, Property = property) %>%
     mutate(src = 'model') 
@@
 # joint model inferred prevalence 
-m.samp.targetPrev <- m.samp %>% 
-  filter(type == "withinKind") %>% 
+m.samp.targetPrev <- m.samp.prevalence %>% 
   group_by(category, property) %>%
-  summarize(MAP = estimate_mode(val),
-          cred_upper = hdi_upper(val),
-          cred_lower = hdi_lower(val)) %>%
+  summarize(MAP = estimate_mode(prevalence),
+          cred_upper = hdi_upper(prevalence),
+          cred_lower = hdi_lower(prevalence),
+          prevMean = mean(prevalence)) %>%
   ungroup() %>% rename(Category = category, Property = property)
@@
           m.samp.targetPrev) %>%
-  ggplot(., aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+  ggplot(., aes(x = prevMean, xmin = cred_lower, xmax = cred_upper,
                 y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0, 1))+
+  scale_y_continuous(limits = c(0, 1))+
+  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
+  coord_fixed()
+```
+
+```{r}
+left_join(
+  d.gen.endorse.bayes,
+  m.samp.prevalence %>% 
+  group_by(category, property) %>%
+  summarize(MAP = estimate_mode(prevalence),
+          cred_upper = hdi_upper(prevalence),
+          cred_lower = hdi_lower(prevalence),
+          prevMean = mean(prevalence)) %>%
+  ungroup() %>% rename(Category = category, Property = property) %>%
+  mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
+) %>%
+  ggplot(., aes(x = prevMean, xmin = cred_lower, xmax = cred_upper,
+                y = MAP_h, ymin = low, ymax = high))+
   geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+

### 2017-06-09 paper/generics-paper.Rmd
more figures of full posterior on generics

@@
 
-```{r fig.height = 8, eval = F}
-
-m.samp %>% filter(type == "param") %>%
-  ggplot(., aes( x = val))+geom_histogram()+
-  facet_wrap(~habitual)
-
-m.samp %>% filter(type == "prior") %>%
-  ggplot(., aes( x = val, fill = time_period))+geom_histogram() + facet_grid(habitual~cat, scales = 'free')+
-  theme(strip.text.y = element_text(angle = 0))
-
-#tail(m.samp)
-```
-
 #### Behavioral results

### 2017-06-10 paper/comgen-paper.Rmd
rename paper file

--- 2017-06-09 paper/generics-paper.Rmd
@@
 
-n.subj.hab.pred < - length(unique(d.hab.predictive$workerid))
+n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
 ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%

### 2017-06-10 paper/appendix-fullModelPosteriors.Rmd
add appendix c to doc

@@
 
-```{r libraries}
+```{r}
 library(rwebppl)
@@
 
-```{r generic-endorsement}
+```{r}
 d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
@@
 
-d.gen.endorse.bayes
+#d.gen.endorse.bayes
 
@@
 
-```{r}
+```{r eval = F}
 left_join(

### 2017-06-10 paper/comgen-paper.Rmd
add appendix c to doc

@@
 <!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning.
---> -->
+-->
 <!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning).
@@
 ```
+
+```{r child = 'appendix-fullModelPosteriors.Rmd'}
+```

### 2017-06-10 paper/comgen-paper.Rmd
fix generics insets fig

@@
 
+m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
+    filter(type == "targetPrevalence") %>%
+    mutate(Sentence = paste(category, property)) %>%
+    filter(Sentence %in% example.generics) %>%
+    mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      val = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+
 gen.inset.distributions <- bind_rows(
@@
   m.gen.speakerBeliefs %>%
-    select(-type, -param, -chain, -Sentence) %>%
+    select(property, val) %>%
     rename(value = val) %>%

### 2017-06-10 paper/comgen-paper.Rmd
habituals structured prior model, data, analysis and figure

@@
 
-```{r habituals-prior}
+```{r habituals-prior-data}
 annualRates = list("5 years" = 1/5, "2 years" = 1/2,
@@
                            sep= ""))
-
-d.hab.priors.tidy <- d.hab.priors %>%
+d.hab.priors <- read.csv("/Users/mht/Documents/research/habituals/data/priors/priors-2.csv")
+
+d.hab.priors <- d.hab.priors %>%
+  mutate(comparisonTime_men = as.character(comparisonTime_men),
+         comparisonTime_women = as.character(comparisonTime_women)) %>%
   rowwise() %>%
-  mutate(annualRate = annualRates[[as.character(interval)]]*n_times,
-         never = ifelse(annualRate == 0, 1, 0),
-         action = as.character(action),
-         action = ifelse(action == "sell things on eBay", "sells things on eBay", action))
-
-d.hab.priors.distinctiveness <- d.hab.priors.tidy %>%
-  group_by(action) %>%
-  multi_boot_standard(column = 'never') %>%
-  ungroup() %>%
-  rename(distinctiveness = mean, 
-         distinct_low = ci_lower, distinct_high = ci_upper)
-#d.hab.priors
-#d.hab.priors.distinctiveness
-# 
-# 
-# df.out <- df.tidy %>%
-#   mutate(annualRate = ifelse(annualRate == 0, 0.15, annualRate),
-#          lograte = log(annualRate),
-#          binned_lograte = round(lograte*2)/2) %>%
-#   group_by(action, binned_lograte) %>%
-#   summarize(counts = n())
-# 
-# 
-# # make sure 0s are represented
-# df.out2 <- left_join(
-#   expand.grid(action = levels(df.out$action), binned_lograte = levels(factor(df.out$binned_lograte))),
-#   df.out %>% mutate(binned_lograte = factor(binned_lograte))) 
-# 
-# df.out2[is.na(df.out2)] <- 0
-# df.out2 <- df.out2 %>%
-#   mutate(binned_lograte = as.numeric(binned_lograte))
-#   
-# ggplot(df.out2, aes( x = binned_lograte, y = counts))+
-#   #geom_histogram()+
-#   geom_bar(stat = 'identity', position = position_dodge())+
-#   #geom_density()+
-#   facet_wrap(~action, scales = 'free')+
-#   xlim(-3.5, 8.5)
-# d.hab.priors.tidy
+  mutate(
+    mixture_male = nPersons_men / comparisonNum_men,
+    mixture_female = nPersons_women / comparisonNum_women,
+    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
+                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
+                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
+                   ifelse(comparisonTime_men == "5 years", 
+                          nInstances_men / (5*365), -99)))),
+    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
+                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
+                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
+                   ifelse(comparisonTime_women == "5 years", 
+                          nInstances_women / (5*365), -99)))),
+    annualRate_male = dayRate_male * 365,
+    annualRate_female = dayRate_female * 365
+  )
+
+d.hab.priors.filtered <- filter(d.hab.priors, 
+       !(
+         (mixture_male == 0) ||   (mixture_female == 0) ||   
+           (dayRate_male == 0) ||   (dayRate_female == 0)  )
+       )
+
+```
+
+```{r habituals-prior-forwardsample}
+# this is basically bootstrapping and combining using the structured model
+
+d.hab.priors.samples <- data.frame()
+for (i in 1:10){
+
+  d.hab.priors.samples <- bind_rows(
+    d.hab.priors.samples,
+    d.hab.priors.filtered %>% 
+    select(workerid, item, starts_with("annualRate"), 
+           starts_with("mixture")) %>%
+    rowwise() %>%
+    mutate(
+      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
+       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
+       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
+       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
+       ) %>%
+    select(item, freq_male, freq_female) %>%
+    gather(gender, val, freq_male, freq_female) %>%
+  mutate(gender = gsub("freq_", "", gender))
+  )
+  print(i)
+}
+
+```
+
+```{r habituals-prior-model}
+hab.prior.bda.model <- '
+var betaShape = function(p){
+  return {a: p.g * p.d, b: (1-p.g) * p.d}
+};
+
+var model = function(){
+	var mixtureParams = {
+		male: {
+      g: uniformDrift({a: 0, b: 1, width: 0.2}),
+      d: uniformDrift({a: 0, b: 100, width: 5})
+    },
+		female: {
+      g: uniformDrift({a: 0, b: 1, width: 0.2}),
+      d: uniformDrift({a: 0, b: 100, width: 5})
+    }
+	};
+
+	var mixtureShapes = {
+		male: betaShape(mixtureParams.male),
+		female: betaShape(mixtureParams.female)
+	};
+
+	mapData({data: data.mixture}, function(d){
+    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
+     // display(Beta(mixtureShapes[d.gender]).score(d.val))
+		observe(Beta(mixtureShapes[d.gender]), d.val)
+	})
+
+	var stableFrequency = {
+		male: {
+			mu: uniformDrift({a: -5, b:10, width: 2}),
+			sigma: uniformDrift({a:0, b:5, width: 1})
+		},
+		female: {
+			mu: uniformDrift({a:-5, b:10, width: 2}),
+			sigma: uniformDrift({a:0, b:5, width: 1})
+		}
+	}
+
+	mapData({data: data.frequency}, function(d){
+    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
+        display(JSON.stringify(d)) : null
+    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
+		observe(Gaussian(stableFrequency[d.gender]), d.logval)
+	})
+
+	var existenceProb = {
+		male: beta(mixtureShapes.male),
+		female: beta(mixtureShapes.female)
+	};
+
+	var freqWhenPresent = {
+		male: gaussian(stableFrequency.male),
+		female: gaussian(stableFrequency.female)
+	}
+
+  var marginalFreq = {
+    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
+    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
+  }
+
+  return {
+    mix_mean_male : mixtureParams.male.g,
+    mix_mean_female : mixtureParams.female.g,
+    mix_samplesize_male : mixtureParams.male.d,
+    mix_samplesize_female : mixtureParams.female.d,
+    stableFreq_mean_male : stableFrequency.male.mu,
+    stableFreq_mean_female :stableFrequency.female.mu,
+    stableFreq_sd_male : stableFrequency.male.sigma,
+    stableFreq_sd_female :stableFrequency.female.sigma,
+    marginalFreq_NA_male: marginalFreq.male,
+    marginalFreq_NA_female: marginalFreq.female
+  }
+}
+'
+```
+
+```{r habituals-prior-model-run}
+items <- levels(d.hab.priors.filtered$item)
+n_samples <- 500
+rs.habituals.bda.prior <- data.frame()
+
+for (it in items){
+
+ df.prior.toPass <- list(
+   frequency = d.hab.priors.filtered %>%
+      filter(item == it) %>%
+      select(item, starts_with("annualRate")) %>%
+      gather(gender, val, -item) %>%
+      mutate(gender = gsub("annualRate_", "", gender),
+             logval = log(val)),
+   mixture = d.hab.priors.filtered %>% 
+      filter(item == it) %>%
+      select(item, starts_with("mixture")) %>%
+      gather(gender, val, -item) %>%
+      mutate(gender = gsub("mixture_", "", gender)) %>%
+      rowwise() %>%
+      mutate(val = ifelse(val == 1, 0.9999, 
+                          ifelse(val == 0, 0.000001, val)))
+  )
+
+  rs <- webppl(program_code = hab.prior.bda.model,
+       model_var = "model",
+       inference_opts = list(method = "MCMC", samples = n_samples,
+                             burn = n_samples / 2),
+       data = df.prior.toPass,
+       data_var = "data")
+
+  rs.habituals.bda.prior <- bind_rows(
+    rs.habituals.bda.prior, 
+    rs %>% 
+      mutate(item = it) %>% 
+      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
+  )
+}
+
+rs.habituals.bda.prior %>% 
+  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
+  select(-Variable, -Parameter, -Chain) %>%
+  spread(param, value) 
+```
+
+```{r habituals-prior-model-forwardSample}
+rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
+  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
+  select(-Variable, -Parameter, -Chain) %>%
+  spread(param, value)
+
+rs.habituals.bda.prior.samples <- data.frame()
+for (i in 1:1){
+  rs.habituals.bda.prior.samples <- bind_rows(
+    rs.habituals.bda.prior.samples,
+    rs.habituals.bda.prior.spread %>%
+    rowwise() %>%
+    mutate(
+      a = mix_mean * mix_samplesize,
+      b = (1 - mix_mean) * mix_samplesize,
+      theta = rbeta(n = 1, shape1 = a, shape2 = b),
+      stable = rbinom(n = 1, size = 1, prob = theta),
+      logannualRate = ifelse(stable == 1, 
+                             rnorm(n = 1, 
+                                   mean = stableFreq_mean, 
+                                   sd = stableFreq_sd), -5),
+       annualRate =  exp(logannualRate)
+    )
+  )
+}
+```
+
+```{r habituals-prior-fig, fig.width = 8.5, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
+2a).
+Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
+
+bind_rows(
+  d.hab.priors.samples %>% 
+    mutate(src = 'data', 
+           val = log(val)),
+  rs.habituals.bda.prior.samples %>%
+    rename(gender = Gender, val = logannualRate) %>%
+    select(gender, item, val) %>%
+    mutate(src = 'model')
+  ) %>%
+ggplot(. , aes( x = val, color = src))+
+  geom_density(size = 0.8, aes( y = ..scaled.. ))+
+  facet_wrap(~item, nrow = 4)+
+  scale_color_solarized()+
+  xlab("Frequency")+
+  ylab("Scaled prior density")+
+  scale_x_continuous(limits = c(-5,10)) +
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0),
+        legend.position = c(0.95, 0.075),
+        axis.text.x = element_text(angle = 90))+
+    scale_x_continuous(limits = c(-5, 8), 
+                     breaks = c(-5, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
+
 ```

### 2017-06-10 paper/comgen-paper.Rmd
remove print statements, etc.

@@
   )
-  print(i)
 }
@@
 }
-
-rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value) 
 ```

### 2017-06-10 paper/comgen-paper.Rmd
clean up habituals freq fig; data analysis for distinctiveness habituals

@@
 
-d.hab.priors <- read.csv(paste(project.path,
-                           "data/habituals/priors/friends-and-family-2-trials.csv",
-                           sep= ""))
 d.hab.priors <- read.csv("/Users/mht/Documents/research/habituals/data/priors/priors-2.csv")
@@
   mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women)) %>%
+         comparisonTime_women = as.character(comparisonTime_women),
+         item = as.character(item),
+         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
   rowwise() %>%
@@
        )
-
 ```
@@
 In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-(1) It smooths effects that are clearly results of the response format.
+First, it smooths effects that are clearly results of the response format.
 For example, a very common rating for certain events is \emph{1 time per year}.
 Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-(2) It better captures the tails of the prior distribution (e.g., the probability of a rate of going to the movies two times every five years) which have relatively little data and need to be regularized by the analysis.
+Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
 
@@
 
+```{r habituals-prior-mixture-summarize}
+d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
+  select(item, starts_with("mixture_")) %>%
+  gather(key, value, -item) %>%
+  group_by(item) %>%
+  multi_boot_standard( column = 'value' )
+```
+
 ```{r habituals-endorsement}
@@
   filter(pass == 1),
-  d.hab.priors.distinctiveness %>% rename(habitual = action)) %>%
-  mutate(response = as.character(response),
-         response = ifelse(response == "agree-key", 1, 0),
-         roundedFreq = round(log_times * 2) / 2)
+  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
+  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
+  rowwise() %>%
+  mutate(
+    annualRate = annualRates[[as.character(time_period)]]*n_instances,
+    logAnnualRate = log(annualRate)
+  )
 
 d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, time_period, log_times, roundedFreq) %>%
+  group_by(habitual, logAnnualRate) %>%
   summarize(k = sum(response), n = n()) %>%
@@
 
-ggplot(d.hab.endorsement.bayes, aes( x = roundedFreq, y = MAP_h, ymin = low, ymax = high, fill = roundedFreq))+
-  geom_jitter(width = 0.1, shape = 21)
-
-#d.hab.endorsement.bayes
+fig.habituals.endorsement.vs.freq <- 
+  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
+  geom_jitter(width = 0.1, shape = 21)+
+  ylab("Human endorsement probability")+
+  xlab("Frequency of target")+
+  scale_x_continuous(limits = c(-1,6), 
+                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
+                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(-0.01, 1.01), 
+                     breaks = c(0, 0.5, 1))+
+  theme(axis.text.x = element_text(angle = 90))
 ```
@@
 
-glm.hab.endorse.freq <- glm(response ~ log_times, 
+glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
               data = d.hab.endorsement, family = 'binomial')
 
-glm.hab.endorse.freq.distinct <- glm(response ~ log_times + distinctiveness, 
+glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
               data = d.hab.endorsement, family = 'binomial')
@@
   unique(select(
-    d.hab.endorsement, habitual, log_times, roundedFreq, distinctiveness
+    d.hab.endorsement, habitual, logAnnualRate, mixture
   )) %>%
@@
 ggplot(d.hab.endorse.regression,
-       aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = distinctiveness))+
+       aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
   geom_errorbar(alpha = 0.1)+

### 2017-06-11 paper/comgen-paper.Rmd
add info about atttention check in habituals priors

@@
 
-We anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
+The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
+After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
+They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
+They did this to test their understanding and attention for each of the two questions.
+
+For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
 Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
@@
 
+All participants responded correctly to both questions in the attention check trial, so all data was used in the analysis.
 We built a Bayesian data analysis model for this prior elicitation task.

### 2017-06-12 paper/comgen-paper.Rmd
habituals prior data and local path in paper
habituals model figures

@@
 
-d.hab.priors <- read.csv("/Users/mht/Documents/research/habituals/data/priors/priors-2.csv")
+d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
 
@@
 d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate) %>%
+  group_by(habitual, logAnnualRate, time_period) %>%
   summarize(k = sum(response), n = n()) %>%
@@
 
+example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
+                       "goes to the movies_month", "smokes cigarettes_month")
 fig.habituals.endorsement.vs.freq <- 
@@
   xlab("Frequency of target")+
+  geom_label_repel(data = d.hab.endorsement.bayes %>% 
+                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
+                    filter(sentence %in% example.habituals), aes( label = habitual ),
+                       fontface = 'bold', color = 'white',
+    box.padding = unit(0.35, "lines"),
+    point.padding = unit(0.5, "lines"),
+    segment.color = 'grey50')+
   scale_x_continuous(limits = c(-1,6), 
@@
   theme(axis.text.x = element_text(angle = 90))
+
 ```
@@
   unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, mixture
+    d.hab.endorsement, habitual, logAnnualRate, time_period, mixture
   )) %>%
@@
 
-ggplot(d.hab.endorse.regression,
-       aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-  geom_errorbar(alpha = 0.1)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-  #                   filter(sqErr > 0.1),
-  #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-  geom_point()+
-  xlim(0,1)+
-  ylim(0,1)+
-  coord_fixed()+
-  xlab("Logistic model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src)
+# ggplot(d.hab.endorse.regression,
+#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
+#   geom_errorbar(alpha = 0.1)+
+#   geom_abline(intercept = 0, slope = 1, lty = 3)+
+#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
+#   #                   filter(sqErr > 0.1),
+#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
+#   geom_point()+
+#   xlim(0,1)+
+#   ylim(0,1)+
+#   coord_fixed()+
+#   xlab("Logistic model prediction")+
+#   ylab("Human habitual endorsement")+
+#   facet_wrap(~src)
 
@@
 n_samples <- 10000
-burn <- n_samples / 2
-lag <- 5
-i <- 2
-model_prefix <- "results-habituals-S1-ffPrior2-3components-normalPrior-silenceAlt-"
-
-m.samp <- data.frame()
+burn <- n_samples
+lg <- 5
+i <- 1
+model_prefix <- "results-habituals-jointModel-S1-"
+
+m.hab.samp <- data.frame()
 for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/habituals/results/", model_prefix, 
-                    n_samples, "_burn", burn, "_lag", lag, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i) %>% rename(habitual = item, time_period = param)
-  m.samp <- bind_rows(m.samp, m.samp.i)
-  #print(i)
+  mi <- fread(paste(project.path,  "models/habituals/results/", 
+                    model_prefix, "smtncs_habitual-",
+                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.samp.i <- mi %>% mutate(chain = i)
+  m.hab.samp <- bind_rows(m.hab.samp, m.samp.i)
 }
 
-m.hab.somemodel.endorsement <- fread(
-  paste(project.path,"models/habituals/results/", 
-        "results-habituals-fixedThreshold-S1-ffPrior2HyperStructured-silenceAlt-10000_burn5000_lag5_chain1.csv",
-        sep = "")
-  ) %>% mutate(chain = 1) %>% rename(habitual = item, time_period = param) %>%
+n_chains <- 1
+n_samples <- 1000
+burn <- n_samples
+lg <- 5
+i <- 1
+m.hab.fixed.samp <- data.frame()
+for (i in seq(1, n_chains)){
+  mi <- fread(paste(project.path,  "models/habituals/results/", 
+                    model_prefix, "smtncs_some-",
+                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.samp.i <- mi %>% mutate(chain = i)
+  m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
+}
+
+m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
   filter(type == 'predictive') %>%
-  group_by(type, habitual, time_period, cat, gender) %>%
+  rename(habitual = B, time_period = D, binned_freq = E) %>%
+  group_by(habitual, time_period, binned_freq) %>%
   summarize(MAP = estimate_mode(val),
@@
 
-m.hab.fullmodel.endorsement <- m.samp %>%
+m.hab.fullmodel.endorsement <- m.hab.samp %>%
   filter(type == 'predictive') %>%
-  group_by(type, habitual, time_period, cat, gender) %>%
+  rename(habitual = B, time_period = D, binned_freq = E) %>%
+  group_by(habitual, time_period, binned_freq) %>%
   summarize(MAP = estimate_mode(val),
@@
   ) %>%
-    mutate(src = "generics_model"),
+    mutate(src = "habituals_model"),
   left_join(
@@
     d.hab.endorse.regression %>% 
-    select(habitual, time_period, log_times, distinctiveness)
+    select(habitual, time_period, logAnnualRate, mixture)
   )
@@
   mutate(src = factor(src, levels = c( 
-                                      "generics_model",
+                                      "habituals_model",
                                       "some_model",
@@
                                  ))) %>%
-  filter(src == "Speaker model - uncertain semantics") %>%
   ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = log_times ))+
+                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
   geom_abline(intercept = 0, slope = 1, lty = 3)+
@@
 
-# with(m.hab.endorse.rsa %>% 
-#   filter(src == "generics_model"), cor(MAP_h, MAP, use='pairwise.complete.obs'))^2
-
-habituals.endorsement.models
+```
+```{r habituals-endorsement-figure, fig.width=11, fig.height=8}
+grid.arrange(fig.habituals.endorsement.vs.freq, 
+             habituals.endorsement.models,
+             generics.endorsement.insets, ncol = 2,
+             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
 ```

### 2017-06-13 paper/comgen-paper.Rmd
fix minor bug in habituals data processing
begin constructing habituals inset figs

@@
 
-```{r include = FALSE}
-
-```
-
 ```{r libraries}
@@
 library(langcog)
-# library(tidyr)
 # library(dplyr)
@@
 
-```{r habituals-prior-model-run}
-items <- levels(d.hab.priors.filtered$item)
+```{r habituals-prior-model-run, cache = T}
+items <- levels(factor(d.hab.priors.filtered$item))
 n_samples <- 500
@@
 ```
+
+```{r habituals-simulation-model, eval = F}
+l0.hab.model <- '
+var probability = function(Dist, x) {
+    return Math.exp(Dist.score(x));
+}
+var targetUtterance = "habitual";
+
+var lowerBound = -5, upperBound = 10, binWidth = 0.5;
+
+var stateBins =  _.range(
+  lowerBound, upperBound, binWidth
+)
+
+var thetaBins = map2(function(b1, b2){
+  var diff = Math.abs(b2 - b1) / 2;
+  return roundTo3(diff+ b1);
+}, stateBins(0, stateBins.length-1), stateBins.slice(1))
+
+var utterancePrior = Infer({model: function(){
+  return uniformDraw([targetUtterance,"silence"])
+}});
+
+var thetaPrior = Infer({model: function(){
+ return uniformDraw(thetaBins)
+}});
+
+var meaning = function(utt,state, theta) {
+  return utt=="generic"? state > theta :
+         utt=="generic is false"? state<=theta :
+         utt=="silence"? true :
+         utt=="some"? state> _.min(thetaBins):
+         true
+}
+
+var mixture = data.prior.mix[0];
+var priorParams = data.prior.params[0];
+
+  {
+    "action": "climbs mountains",
+    "mixture_female_mean": 0.0949,
+    "mixture_female_samplesize": 3.7153,
+    "mixture_male_mean": 0.0566,
+    "mixture_male_samplesize": 0.9652,
+    "stableFreq_female_mean": 0.3953,
+    "stableFreq_female_samplesize": 1.6992,
+    "stableFreq_male_mean": 0.8339,
+    "stableFreq_male_samplesize": 1.5171
+  }
+]
+
+var stable_female = beta({
+  a: mixture_female_mean * mixture_female_samplesize,
+  b: (1 - mixture_female_mean) * mixture_female_samplesize
+})
+
+var stable_male = beta({
+  a: mixture_male_mean * mixture_male_samplesize,
+  b: (1 - mixture_male_mean) * mixture_male_samplesize
+})
+
+var statePrior = Infer({model: function(){
+  var gender = flip(0.5) ? "female" : "male";
+  return gender == "female" ?
+    flip(stable_female) ? 
+      categorical({
+        vs: stateBins,
+        ps: map(function(b) {
+          return probability(Gaussian({
+                mu: stableFreq_female_mean, 
+                sigma: stableFreq_female_samplesize
+          }), b) + Number.EPSILON
+        }, stateBins )
+      }) :
+    _.min(stateBins) : 
+    flip(stable_male) ? 
+      categorical({
+        vs: stateBins,
+        ps: map(function(b) {
+          return probability(Gaussian({
+                mu: stableFreq_male_mean, 
+                sigma: stableFreq_male_samplesize
+          }), b) + Number.EPSILON
+        }, stateBins )
+      }) :
+    _.min(stateBins)
+}});
+
+var listener0 = cache(function(utterance) {
+  Infer({model: function(){
+    var state = sample(statePrior)
+    var state_prior = sample(statePrior)
+    var theta = utterance == "generic" ? sample(thetaPrior) : -99
+    condition(meaning(utterance, state, theta))
+    return {
+      state_Posterior: state, 
+      state_Prior: state_prior
+  }
+ }})}, 10000)
+
+var continuousListener0 = function(utterance) {
+  Infer({model: function(){
+   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
+//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
+//    var theta = uniform(0,1)
+    factor(
+    (utterance == "generic") ? 
+      Math.log(state) : 
+    (state > 0.017) ? 0 : -Infinity
+    )
+    return {
+      state_Posterior: state, 
+      state_Prior: state_prior
+  }
+ }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+
+//var out = {generic: listener0("generic"), some: listener0("some")}
+//out
+continuousListener0(data.utt[0])
+'
+```
+
+```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, eval = F}
+example.habituals.actions <- separate(data.frame(example.habituals), 
+                                      example.habituals, 
+                                      into=c("action", "time_period"), sep = "_")$action
+
+m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
+  filter(type == "prior", B %in% example.habituals.actions) %>%
+  rename(action = B, variable = C, gender = D, parameter = E) %>%
+  group_by(action, variable, gender, parameter) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
+
+m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
+  ungroup() %>%
+  select(action, variable, gender, parameter, MAP) %>%
+  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
+  select(-variable, -gender, -parameter) %>%
+  spread(param, MAP)
+
+hab.listener.predictions <- data.frame()
+
+for (p in example.habituals.actions){
+ priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
+
+ inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
+                                                   b = priorParams[["b"]]),
+                               mix = priorParams[["mix"]]), 
+                  utt = "habitual")
+
+ l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
+
+ hab.listener.predictions <- bind_rows(
+   hab.listener.predictions, 
+   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
+   )
+
+}
+
+m.gen.fullmodel.target.prevalence <- m.samp %>%
+  filter(type == "withinKind") %>%
+  group_by(param, property, category) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+m.gen.speakerBeliefs <- m.samp %>%
+  filter(type == "withinKind") %>%
+  mutate(Sentence = paste(category, property)) %>%
+  filter(Sentence %in% example.generics)
+
+m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
+    filter(type == "targetPrevalence") %>%
+    mutate(Sentence = paste(category, property)) %>%
+    filter(Sentence %in% example.generics) %>%
+    mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      val = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+
+gen.inset.distributions <- bind_rows(
+  gen.listener.predictions %>%
+    mutate(category = NA),
+  m.gen.speakerBeliefs %>%
+    select(property, val) %>%
+    rename(value = val) %>%
+    mutate(Parameter = "speakerBeliefs")
+)
+
+category.text.labels <- data.frame(property = c("dont eat people", 
+                      "carry malaria", "lay eggs",  "are female", "have spots"),
+             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
+             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
+            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
+
+generics.endorsement.insets <- gen.inset.distributions %>%
+  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
+                                                  "state_Posterior",
+                                                  "speakerBeliefs"),
+                            labels = c("Listener Prior (Posterior given Silence)", 
+                                       "Listener Posterior given Generic", 
+                                       "Speaker Beliefs")),
+         property = fct_relevel(property,
+                                "have spots", "lay eggs","carry malaria", 
+                                "are female", "dont eat people") ) %>%
+  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
+  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
+  facet_wrap(~property, nrow = 1)+
+  geom_text_repel(data = category.text.labels,
+                  aes(label = category, x = x , y = y),
+                  inherit.aes = F, color = "#2b83ba")+
+    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    #scale_linetype_manual(values = c(3, 4, 2, 1))+
+    scale_linetype_manual(values = c(3, 4, 1))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Prevalence") +
+    ylab("Scaled probability density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+
+```
+
 ```{r habituals-endorsement-figure, fig.width=11, fig.height=8}

### 2017-06-14 paper/comgen-paper.Rmd
finished draft of habituals results figure

@@
 knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
+                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
 
@@
 
-```{r habituals-prior-fig, fig.width = 8.5, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
+```{r habituals-prior-fig, fig.width = 9, fig.height = 6, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
 2a).
@@
                      breaks = c(0, 0.5, 1))+
-  theme(axis.text.x = element_text(angle = 90))
-
+  theme(axis.text.x = element_text(angle = 90))+
+  coord_fixed(ratio = 7)+
+  guides(fill = F)
 ```
@@
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
   coord_fixed()+
@@
 
-```{r habituals-simulation-model, eval = F}
+```{r habituals-simulation-model}
 l0.hab.model <- '
@@
 }
+var betaShape = function(p){
+  return {a: p.g * p.d, b: (1-p.g) * p.d}
+};
+
+var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
+
 var targetUtterance = "habitual";
+
+var roundTo3 = function(x){
+  return Math.round(x * 10000) / 10000
+}
 
@@
   return roundTo3(diff+ b1);
-}, stateBins(0, stateBins.length-1), stateBins.slice(1))
+}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
 
@@
 
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-  {
-    "action": "climbs mountains",
-    "mixture_female_mean": 0.0949,
-    "mixture_female_samplesize": 3.7153,
-    "mixture_male_mean": 0.0566,
-    "mixture_male_samplesize": 0.9652,
-    "stableFreq_female_mean": 0.3953,
-    "stableFreq_female_samplesize": 1.6992,
-    "stableFreq_male_mean": 0.8339,
-    "stableFreq_male_samplesize": 1.5171
-  }
-]
-
-var stable_female = beta({
-  a: mixture_female_mean * mixture_female_samplesize,
-  b: (1 - mixture_female_mean) * mixture_female_samplesize
+var priorParams = data.priorParams[0];
+
+var stable_female_params = betaShape({
+  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
 })
 
-var stable_male = beta({
-  a: mixture_male_mean * mixture_male_samplesize,
-  b: (1 - mixture_male_mean) * mixture_male_samplesize
+var stable_male_params = betaShape({
+  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
 })
 
+// this marginalizes out the mixture parameter
 var statePrior = Infer({model: function(){
   var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ?
-    flip(stable_female) ? 
+  return gender == "female" ? // 
+    flip(
+        categorical({
+          vs: probBins,
+          ps: map(function(b) {
+            return probability(Beta(stable_female_params), b) + Number.EPSILON
+          }, probBins )
+        })
+    ) ? // stable female distribution
       categorical({
@@
           return probability(Gaussian({
-                mu: stableFreq_female_mean, 
-                sigma: stableFreq_female_samplesize
+                mu: priorParams.stableFreq_female_mean, 
+                sigma: priorParams.stableFreq_female_samplesize
           }), b) + Number.EPSILON
         }, stateBins )
-      }) :
+      }) : // unstable female distribution
     _.min(stateBins) : 
-    flip(stable_male) ? 
+    flip(        
+      categorical({
+          vs: probBins,
+          ps: map(function(b) {
+            return probability(Beta(stable_male_params), b) + Number.EPSILON
+          }, probBins )
+      })
+    ) ? 
       categorical({
@@
           return probability(Gaussian({
-                mu: stableFreq_male_mean, 
-                sigma: stableFreq_male_samplesize
+                mu: priorParams.stableFreq_male_mean, 
+                sigma: priorParams.stableFreq_male_samplesize
           }), b) + Number.EPSILON
@@
     var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
+    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
     condition(meaning(utterance, state, theta))
@@
   Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
+   var state = flip(0.5) ? 
+        flip(beta(stable_female_params)) ? 
+          gaussian({
+                mu: priorParams.stableFreq_female_mean, 
+                sigma: priorParams.stableFreq_female_samplesize
+          }) : delta({v:-5}) :
+        flip(beta(stable_male_params)) ? 
+          gaussian({
+                mu: priorParams.stableFreq_male_mean, 
+                sigma: priorParams.stableFreq_male_samplesize
+          }) : delta({v:-5})
+   var state_prior = flip(0.5) ? 
+        flip(beta(stable_female_params)) ? 
+          gaussian({
+                mu: priorParams.stableFreq_female_mean, 
+                sigma: priorParams.stableFreq_female_samplesize
+          }) : delta({v:lowerBound}) :
+        flip(beta(stable_male_params)) ? 
+          gaussian({
+                mu: priorParams.stableFreq_male_mean, 
+                sigma: priorParams.stableFreq_male_samplesize
+          }) : delta({v:lowerBound})
+    var theta = uniform(lowerBound, upperBound)
+    condition(
+      (utterance == "habitual") ? 
+      state > theta : 
+      (state > _.min(lowerBound))
     )
@@
   }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
+ }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
+
 continuousListener0(data.utt[0])
@@
 
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, eval = F}
+```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
 example.habituals.actions <- separate(data.frame(example.habituals), 
@@
 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
+ inputData = list(priorParams = priorParams,
                   utt = "habitual")
@@
 
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "withinKind") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "withinKind") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
-    filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
+# m.gen.fullmodel.target.prevalence <- m.samp %>%
+#   filter(type == "withinKind") %>%
+#   group_by(param, property, category) %>%
+#   summarize(MAP = estimate_mode(val),
+#             cred_upper = hdi_upper(val),
+#             cred_lower = hdi_lower(val))
+
+# m.gen.speakerBeliefs <- m.samp %>%
+#   filter(type == "withinKind") %>%
+#   mutate(Sentence = paste(category, property)) %>%
+#   filter(Sentence %in% example.generics)
+
+# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
+#     filter(type == "targetPrevalence") %>%
+#     mutate(Sentence = paste(category, property)) %>%
+#     filter(Sentence %in% example.generics) %>%
+#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
+#     select(-param, -property, -category, -chain, -type) %>%
+#     group_by(parameter) %>%
+#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+#     ungroup() %>%
+#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
+#     group_by(category, property, iteration) %>%
+#     spread(parameter, val) %>%
+#     rowwise() %>%
+#     mutate(
+#       a = mean*sampleSize,
+#       b = (1-mean)*sampleSize,
+#       val = rbeta(n = 1, shape1 = a, shape2 = b)
+#       ) %>%
+#     ungroup()
+
+# gen.inset.distributions <- bind_rows(
+#   gen.listener.predictions %>%
+#     mutate(category = NA),
+#   m.gen.speakerBeliefs %>%
+#     select(property, val) %>%
+#     rename(value = val) %>%
+#     mutate(Parameter = "speakerBeliefs")
+# )
+# 
+# 
+# category.text.labels <- data.frame(property = c("dont eat people", 
+#                       "carry malaria", "lay eggs",  "are female", "have spots"),
+#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
+#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
+#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
+
+habituals.endorsement.insets <- hab.listener.predictions %>% 
     mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
+                                                  "state_Posterior"
+                                                  ),
                             labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
+                                       "Listener Posterior given Habitual")),
+         action = fct_relevel(action,
+                                "climbs mountains", "hikes", "runs",
+                              "goes to the movies", "smokes cigarettes"
+                              ) ) %>%
   ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
   geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_text_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
+  facet_wrap(~action, nrow = 1)+
+  # geom_text_repel(data = category.text.labels,
+  #                 aes(label = category, x = x , y = y),
+  #                 inherit.aes = F, color = "#2b83ba")+
   #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
   #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  #scale_linetype_manual(values = c(3, 4, 1))+
+  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
   scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
@@
   ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
+  theme(legend.position = "bottom", legend.title = element_blank(),
+        axis.text.x = element_text(angle = 90))+
+      scale_x_continuous(limits = c(-5, 8), 
+                     breaks = c(-5, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
 
@@
              habituals.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
+             habituals.endorsement.insets, ncol = 2,
              layout_matrix = cbind(c(1,1,3), c(2,2,3)))

### 2017-06-14 paper/comgen-paper.Rmd
causals prior and model figure schematics

@@
 ```{r simluationsModel, eval = T, cache = T}
-
 l0.model <- '
@@
 
-```{r generic-endorsement-priors, eval = F}
+```{r generic-endorsement-priors}
 d.gen.endorse.priors <- read.csv(paste(project.path, 
@@
 '
+```
+
+```{r generic-endorsement-priors-model-run, eval = F}
 marginal.prevalence <- data.frame()
@@
 }
-
 ```
 
-```{r, eval = F}
+```{r generic-endorsement-priors-figure, eval = F}
 ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
@@
 ```{r causal-priors-data}
-
 d.cas.priors <- read.csv(paste(project.path,
@@
 ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
+```
+
+```{r causal-priors-model, cache = T}
+causal.distributions <- levels(factor(d.cas.priors$distribution))
+p <- causal.distributions[1]
+m.cas.marginal.prevalence <- data.frame()
+m.cas.endorse.priors.summary <- data.frame()
+
+for (p in causal.distributions){
+  priorData <- 100*filter(d.cas.priors, distribution == p)$response
+
+  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
+         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
+
+  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
+    spread(Parameter, value) %>%
+    rowwise() %>%
+    mutate(
+      a = g * d,
+      b = (1 - g) * d,
+      stable = rbinom(n = 1, size = 1, prob = phi),
+      prevalence = ifelse(stable == 1, 
+                             rbeta(n = 1, shape1 = a, shape2 = b),
+                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
+      distribution = p
+    )
+  )
+
+  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
+                                            m.cas.endorse.priors %>% 
+                                              mutate(distribution = p) %>%
+                                              group_by(distribution, Parameter) %>%
+                                              summarize(MAP = estimate_mode(value),
+                                                        cred_upper = hdi_upper(value),
+                                                        cred_lower = hdi_lower(value))
+                                              )
+}
 
@@
 
-```{r causals-conditions, fig.caption = "Four background distributions participants were exposed to in Expt. 4"}
+```{r causals-conditions, fig.caption = "Four background distributions participants were exposed to in Expt. 4 (stimuli) and priors reconstructed from participants' responses (model). "}
 sample.dists <- bind_rows(
@@
 
-ggplot(sample.dists, aes(x = x, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 1.3, alpha =0.8, 
+bind_rows(
+  sample.dists %>%
+    mutate(src = "stimuli") %>%
+    select(-dist),
+  m.cas.marginal.prevalence %>%
+    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
+    mutate(Distribution = factor(distribution, 
+                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
+           labels = c("Common Deterministic", "Rare Deterministic",
+                      "Common Weak", "Rare Weak"))) %>%
+    select(Distribution, prevalence) %>%
+    mutate(src = 'model') %>%
+    rename(x = prevalence)
+) %>%
+  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
+  ggplot(., aes(x = x, fill = src, color = src, alpha = src, lty = src))+ 
+  geom_density( adjust = 1.3, 
                size = 1.2,
@@
   scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
+  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_color_manual(values = c("#636363", "#d7191c"))+
+  scale_alpha_manual(values = c(0, 0.4))+
+  scale_linetype_manual(values = c(3, 1))+
   ylab("Scaled Prior Probability")+
   xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
+  facet_wrap(~Distribution, scales = 'free')
+```
+
+```{r s1-model}
+s1.model <- '
+var probability = function(Dist, x) {
+    return Math.exp(Dist.score(x));
+}
+var targetUtterance = "generic";
+
+var utterancePrior = Infer({model: function(){
+  return uniformDraw([targetUtterance,"silence"])
+}});
+
+var betaShape = function(params){
+  return {
+      a: params.g * params.d,
+      b : (1-params.g) * params.d
+  }
+}
+
+var thetaPrior = Infer({model: function(){
+ return uniformDraw([
+   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
+ ])}
+});
+
+var bins = [
+  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
+];
+
+var meaning = function(utt,state, theta) {
+  return utt=="generic"? state > theta :
+         utt=="generic is false"? state<=theta :
+         utt=="silence"? true :
+         utt=="some"? state>0.01:
+         utt=="most"? state> 0.5:
+         utt=="all"? state >= 0.99:
+         true
+}
+var alpha = 2;
+var mixture = data.prior[0].phi;
+var priorParams = betaShape(data.prior[0]);
+
+var statePrior = Infer({model: function(){
+  var component = flip(mixture);
+  return component ?
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta(priorParams), b) + Number.EPSILON
+      }, bins )
+    }) :
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
+      }, bins )
+    })
+}});
+
+var listener0 = cache(function(utterance) {
+  Infer({model: function(){
+    var state = sample(statePrior)
+    var theta = utterance == "generic" ? sample(thetaPrior) : -99
+    condition(meaning(utterance, state, theta))
+    return state
+ }})}, 10000)
+
+var speaker1 = function(state) {
+  Infer({model: function(){
+    var utterance = sample(utterancePrior);
+    var listener_posterior = listener0(utterance);
+    factor(alpha * listener_posterior.score(state))
+    return utterance
+  }})
+}
+
+probability(speaker1(data.state[0]), "generic")
+'
+```
+
+```{r causal-endorsement-predictions, cache = T, eval = F}
+causal.priorParams <- m.cas.endorse.priors.summary %>%
+    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
+           Parameter != 'marginalPrevalence') %>%
+  select(distribution, Parameter, MAP) %>%
+  spread(Parameter, MAP)
+experimental.frequencies <- c(0.2, 0.7)
+causal.endorsement.predictions <- data.frame()
+for (p in causal.priorParams$distribution){
+  for (s in experimental.frequencies){
+
+    inputData = list(prior = filter(causal.priorParams, distribution == p), 
+                     state = s)
+
+    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
+
+    causal.endorsement.predictions <- bind_rows(
+      causal.endorsement.predictions,
+      data.frame(state = s, distribution = p, prob = s1.rs)
+    )
+  }
+  print(p)
+}
+
+causal.endorsement.predictions
 ```
@@
 
-```{r empirical-causal-prior-densities, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
+```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
 
@@
 
-```{r}
+```{r causal-endorsement-data}
 d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
@@
          mean = a / (a + b))
-
 ```
@@
 
-```{r causals-endorsement, fig.width = 4, fig.height = 3}
+```{r causals-endorsement, fig.width = 4, fig.height = 3, eval = F}
 
@@
 
+```{r causals-fullmodel}
+n_chains <- 1
+n_samples <- 5000
+burn <- n_samples / 2
+lg <- 5
+i <- 1
+
+model_prefix <- "pilot-results-causals-jointModel-S1-"
+
+m.cas.samp <- data.frame()
+for (i in seq(1, n_chains)){
+  mi <- fread(paste(project.path,  "models/causals/results/", 
+                    model_prefix, "smntcs_causal-",
+                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
+}
+
+# n_chains <- 1
+# n_samples <- 1000
+# burn <- n_samples
+# lg <- 5
+# i <- 1
+# m.hab.fixed.samp <- data.frame()
+# for (i in seq(1, n_chains)){
+#   mi <- fread(paste(project.path,  "models/habituals/results/", 
+#                     model_prefix, "smtncs_some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.samp.i <- mi %>% mutate(chain = i)
+#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
+# }
+
+# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
+#   filter(type == 'predictive') %>%
+#   rename(habitual = B, time_period = D, binned_freq = E) %>%
+#   group_by(habitual, time_period, binned_freq) %>%
+#   summarize(MAP = estimate_mode(val),
+#             cred_upper = hdi_upper(val),
+#             cred_lower = hdi_lower(val))
+
+m.cas.fullmodel.endorsement <- m.cas.samp %>%
+  filter(type == 'predictive') %>%
+  group_by(dist, frequency) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+bind_rows(
+  m.cas.fullmodel.endorsement %>%
+    mutate(src = "model"),
+  d.caus.endorse.summary %>%
+    select(distribution, frequency, MAP_h, low, high) %>%
+    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
+    mutate(src = 'data')
+) %>%
+  mutate(src = factor(src, levels = c("model", "data"))) %>%
+  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
+                        group = dist))+
+  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
+  geom_linerange(width = 0.2, position = position_dodge(0.3))+
+  #geom_line(position = position_dodge(0.3))+
+  theme(axis.text.x = element_blank())+
+  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
+  scale_fill_solarized()+
+  xlab("Background Distribution")+
+  ylab("Proportion Causal Endorsement")+
+  facet_grid(frequency~src)
+```
+
 ## Discussion

### 2017-06-15 paper/comgen-paper.Rmd
causal insets to represent listener prior and posterior

@@
 
-m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
+m.samp.prev.params <- m.samp %>%
     filter(type == "targetPrevalence") %>%
@@
 
-```{r causal-priors-model, cache = T}
+```{r causal-priors-runModel, cache = T}
 causal.distributions <- levels(factor(d.cas.priors$distribution))
@@
 
-```{r causals-conditions, fig.caption = "Four background distributions participants were exposed to in Expt. 4 (stimuli) and priors reconstructed from participants' responses (model). "}
+```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
+4 (stimuli) and priors reconstructed from participants' responses (model).
+", fig.width = 8, fig.height = 3}
 sample.dists <- bind_rows(
@@
 
-bind_rows(
+figure.causals.priors <- bind_rows(
   sample.dists %>%
@@
   mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = src, color = src, alpha = src, lty = src))+ 
+  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
+                ))+ 
   geom_density( adjust = 1.3, 
@@
   scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0, 0.4))+
-  scale_linetype_manual(values = c(3, 1))+
+  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_fill_solarized()+scale_color_solarized()+
+  #scale_color_manual(values = c("#636363", "#d7191c"))+
+  scale_alpha_manual(values = c(0.1, 0.4))+
+  scale_linetype_manual(values = c(2, 1))+
   ylab("Scaled Prior Probability")+
   xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')
+  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
+  guides(fill = F, color = F)+
+  theme(legend.position = 'bottom', legend.direction = 'horizontal')
 ```
@@
 }
-
-causal.endorsement.predictions
 ```
@@
 
-```{r causals-endorsement, fig.width = 4, fig.height = 3, eval = F}
+```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
 
@@
             cred_lower = hdi_lower(val))
-
-bind_rows(
+```
+
+```{r causal-model-insets, fig.width = 8, fig.height = 3.5}
+
+m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
+  filter(type == "prior") %>%
+  rename(variable = item, parameter = roundedFreq) %>%
+  group_by(dist, variable, parameter) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
+
+m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
+  ungroup() %>%
+  select(dist, variable, parameter, MAP) %>%
+  mutate(param = paste(variable, parameter, sep = "_")) %>%
+  select(-variable, -parameter) %>%
+  spread(param, MAP) %>%
+  rename(mix = mixture_NA, 
+         stable_mean = stableFreq_mean, 
+         stable_concentration = stableFreq_sampleSize) %>%
+  mutate( a = stable_mean * stable_concentration, 
+          b = (1 - stable_mean) * stable_concentration)
+
+cas.listener.predictions <- data.frame()
+
+for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
+ priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
+ inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
+                                                   b = priorParams[["b"]]),
+                               mix = priorParams[["mix"]]), 
+                  utt = "generic")
+ l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
+ cas.listener.predictions <- bind_rows(
+   cas.listener.predictions, 
+   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
+   )
+}
+
+causals.endorsement.insets <- cas.listener.predictions %>% 
+    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
+                                                  "state_Posterior"
+                                                  ),
+                            labels = c("Listener Prior (Posterior given Silence)",
+                                       "Listener Posterior given Causal")),
+    Distribution = factor(distribution, 
+                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
+         labels = c("Common Deterministic", "Rare Deterministic",
+                    "Common Weak", "Rare Weak"))) %>%
+  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
+  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
+  facet_wrap(~Distribution, nrow = 1)+
+  # geom_text_repel(data = category.text.labels,
+  #                 aes(label = category, x = x , y = y),
+  #                 inherit.aes = F, color = "#2b83ba")+
+  scale_fill_solarized()+ scale_color_solarized()+
+  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  #scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_alpha_manual(values = c(0.1, 0.8))+#, 0))+
+  #scale_linetype_manual(values = c(3, 4, 2, 1))+
+  scale_linetype_manual(values = c(2, 1))+
+  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  xlab("Prevalence") +
+  ylab("Scaled probability density")+
+  theme(legend.position = "bottom", legend.title = element_blank())+
+  guides(fill = F, color = F)#,
+  #       axis.text.x = element_text(angle = 90))+
+      # scale_x_continuous(limits = c(-5, 8),
+      #                breaks = c(-5, 0, 2.5, 4, 5.9),
+      #                labels = c("almost never", "annually", "monthly", "weekly", "daily"))
+```
+
+```{r figure-causals-endorsement, fig.width=7, fig.height=3.5}
+figure.causals.endorsement <- bind_rows(
   m.cas.fullmodel.endorsement %>%
@@
 ) %>%
-  mutate(src = factor(src, levels = c("model", "data"))) %>%
+  ungroup() %>%
+  mutate(
+    src = factor(src, levels = c( "data", "model")),
+    dist = factor(dist, 
+           levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
+           labels = c("Common Deterministic", "Rare Deterministic",
+                      "Common Weak", "Rare Weak"))
+    ) %>%
   ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = dist))+
+                        group = src, alpha = src))+
   geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(width = 0.2, position = position_dodge(0.3))+
+  geom_linerange(position = position_dodge(0.3), alpha = 1)+
   #geom_line(position = position_dodge(0.3))+
-  theme(axis.text.x = element_blank())+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
+  #theme(axis.text.x = element_text(angle = 90))+
+  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_alpha_manual(values = c(1, 0.3))+
   scale_fill_solarized()+
-  xlab("Background Distribution")+
+  xlab("")+
   ylab("Proportion Causal Endorsement")+
-  facet_grid(frequency~src)
+  facet_grid(.~frequency)+
+  coord_flip()+
+  guides(fill = F)+
+  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+```
+
+```{r figure-causals, fig.width=11, fig.height=8}
+grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
+             layout_matrix = cbind(c(1,1,2)))
+
+# ,
+#              habituals.endorsement.insets, ncol = 2,
+#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
 ```

### 2017-06-15 paper/comgen-paper.Rmd
elaborate discussion of books are paperbacks

@@
 We posit that the weirdness of these examples is the result of a failure of the comparison class.
-If the comparison class can be derived with respect to the property [c.f., @Keil1979], one would expect the entities in the class to
+<!-- Specifically, the target category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
+
+Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
+His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
+Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
+For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
+Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
+Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
+From the taxonomic relation of the subordinate categories (e.g., types of books) to the target category (i.e., books), the true prevalence of the feature among the target category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
+Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue.
 

### 2017-06-15 paper/comgen-paper.Rmd
clean up mary handles mail

@@
 
-(2) is often used to argue that no actual instances need have occurred to make a generalization true. 
-In this thought experiment, part (or perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary has handled the mail from Antarctica in the past.
-Our framework takes the fundamental currency of a generalizatoin in language to be a subjective predictive probability. 
-In Expt. 3, we manipulate predictive probability and saw the endorsements for habitual language were affected. 
-This example bears similarity to the *enabling* condition of that experiment, wherein causal events increased the propensity of the event in the future, and also resulted in an increase in endorsements of habitual language.
+(2) is often used to argue that no actual instances need have the property to make a generalization true. 
+Part (or perhaps all) of Mary's job is to handle the mail from Antarctica; in this thought experiment, to date, there has not been any mail from Antarctica [@Cohen1999]. 
+Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
+This example is an extreme case of the phenomenon highlighted by Expt. 3.
+In Expt.
+3, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
+Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
+Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
 

### 2017-06-15 paper/comgen-paper.Rmd
tweaking to other phil probs

@@
 
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. 
-(3) sounds true but if one takes the conjunction to apply to the properties, it is not true.
-That is, we don't think there to be international elephants (i.e., individual elephants who live in Africa part time and Asia part time).
-Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
-This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia."
-Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.
-
-With reasonable assumptions about the prior (e.g., assuming international elephants are unlikely), upon the hearing "Elephants live in Africa", the model infers that most elephants live in Africa.
+(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
+This example was first introduced, to our knowledge, by @Nickel2008.
+]
+@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
+This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
+That is, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+
+<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
+-->
+<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
+<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
+
+With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
+1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
 When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
+This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
+Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
 A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-This is a nice feature of the uncertain threshold semantics: flexibility in accomodating new evidence that might otherwise contradict previous statements.
-
-Finally, (4) is used to argue that even if the property is widespread (perhaps in a soft sense, as in our model, relative to other kinds or groups), we might find it avervise to actually assert the generic.
+
+Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
 That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to say *Women are submissive* [@Haslanger2011].
@@
 ].
-The current formulation of the model is relatively ambivalent the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence can be exaggerated from the generic statement).
-If states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
+The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated from the generic statement).
+However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
 This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].

### 2017-06-15 paper/comgen-paper.Rmd
incorporate raw generics data file

@@
 ```{r generic-endorsement-priors}
+# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
+
 d.gen.endorse.priors <- read.csv(paste(project.path, 
@@
 #### Method
+```{r}
+d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
+                    "truth-judgments.csv", sep = ""))
+d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
+                    "naturalGenerics-trials-formatted.csv", sep = ""))
+
+head(d1)
+head(d2)
+
+write.csv(
+  left_join(
+  d1 %>%
+    mutate(sentence = as.character(sentence),
+           sentence = gsub('&quotechar', '', sentence),
+         sentence = gsub('lyme', 'Lyme', sentence)),
+  unique(d2 %>%
+    mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
+    select(Category, Property, sentence))
+), file = paste(project.path, "data/generics/endorsement/",
+                    "truth-judgments-n100.csv", sep = ""), row.names = F)
+```
 
@@
 d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments.csv", sep = ""))
+                    "truth-judgments-n100.csv", sep = ""))
 
@@
   rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
+  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
   group_by(sentence) %>%
@@
 Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as ``Tell us about your school / family''. 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g.
-``My brother works part-time at the restaurant.'').
-Habitual language may be a more conservative form of trait language (e.g. \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
+@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
+A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
+Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
 
@@
 4 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3}
+", fig.width = 8, fig.height = 3, eval = F}
 sample.dists <- bind_rows(
@@
 
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5}
-
+```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = F}
 m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
@@
 
+inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
+
 causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
+    mutate(Parameter = factor(Parameter, 
+                              levels = c("state_Prior","state_Posterior"),
                             labels = c("Listener Prior (Posterior given Silence)",
@@
   facet_wrap(~Distribution, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  scale_fill_solarized()+ scale_color_solarized()+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.1, 0.8))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
+  scale_fill_manual(values =inset.color.order )+
+  scale_color_manual(values = inset.color.order)+
+  scale_alpha_manual(values = c(0.1, 0.8))+
   scale_linetype_manual(values = c(2, 1))+
@@
   theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)#,
-  #       axis.text.x = element_text(angle = 90))+
-      # scale_x_continuous(limits = c(-5, 8),
-      #                breaks = c(-5, 0, 2.5, 4, 5.9),
-      #                labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5}
+  guides(fill = F, color = F)
+```
+
+```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
 figure.causals.endorsement <- bind_rows(
@@
     dist = factor(dist, 
-           levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))
+           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
+           labels = c(
+                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
     ) %>%
@@
   scale_alpha_manual(values = c(1, 0.3))+
-  scale_fill_solarized()+
+  #scale_fill_solarized()+
+  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
   xlab("")+
@@
 
-```{r figure-causals, fig.width=11, fig.height=8}
+```{r figure-causals, fig.width=11, fig.height=8, cache = F}
 grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,

### 2017-06-22 paper/appendix-fullModelPosteriors.Rmd
adjust data paths

@@
 # Appendix C: Full model posteriors
+```{r}
+knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
+                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
+```
 

### 2017-06-22 paper/comgen-paper.Rmd
adjust data paths

@@
 #### Method
-```{r}
+```{r eval = F}
 d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments.csv", sep = ""))
+                    "truth-judgments-n100.csv", sep = ""))
 d2 <- read.csv(paste(project.path, "data/generics/endorsement/",

### 2017-06-24 paper/comgen-paper.Rmd
many attempts at bf computation; working bf for prior model comparison; cached temp results

@@
 }
+logmeanexp <- function(x){
+  x.num <- as.numeric(x)
+  xstar = max(x.num)
+  return(xstar + log(mean(exp(x.num - xstar))))
+}
+
 project.path <- "../"
@@
 
-We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge
+We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
 We formalize this hypothesis using a simple, Bayesian mixture model. 
-We test the simplest "structural" hypothesis, where there are two distinct components, for example, if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not [@Griffiths2005].
-In this task, participants give responses in the form of numbers between 0 and 100 (or, rescaled to be between 0 - 1).
-The canonical prior for generating numbers between 0 - 1 is the Beta distribution.
-
-We then assume the data, for each item independently, was generated from one of two distributions: a distribution corresponds to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
+We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
+The "unstructured", alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.
+
+For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
 The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
@@
 Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$.
-This problem does not appear for 0 being adjusted to $\epsilon$ as we explicitly posit a left-skewed "transient" distribution.
+This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
 Similar results can be obtained by rounding 0 to 0.01. 
@@
 ]
-Finally, we assume that these two components combine with some weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \alpha, \beta) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.
-
-We put priors over the latent parameters of this model and infer their credible values by way of Bayesian infernence.
+Finally, we assume that these two components combine with some mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.^[
+We use the mean / concentration parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
+The shape parameterization can be recovered using: $\alpha = \gamma \cdot \delta; \beta = (1 - \gamma) \cdot \delta$.
+]
+The unstructured hypothesis only represents a single component in the prior distribution $P(d) = \text{Beta} (d \mid \gamma, \xi)$.
+
+We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account the flexibility of each model [@LW2014].
+We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\theta$):
 
@@
 \theta & \sim & \text{Uniform}(0, 1) \\
-\alpha & \sim & \text{Uniform}(0, 100) \\
-\beta & \sim & \text{Uniform}(0, 100) \\
+\gamma & \sim & \text{Uniform}(0, 1) \\
+\xi & \sim & \text{Uniform}(0, 100) \\
 \end{eqnarray}
 
-To see how well this data-analytic model fits the prevalence prior data, we can use the inferred parameters to generate new data.
-This is called the *posterior predictive distribution* and is an important step in model validation. 
-If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
-We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
-If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
-If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
-]
-
-We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
-To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
+Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property has its own parameters).
+
+### Results
 
@@
 
-genericEndorsementPriorModel <- '
+genericEndorsementPriorModelHelpers <- '
 var eps = 0.01;//Number.EPSILON;
@@
 }, data)
-
+'
+
+structuredPriorModel <- '
 var model = function(){
   var phi = uniformDrift({a:0, b: 1, width:0.2});
-  //var a = uniformDrift({a:0, b: 100, width:5});
-  //var b = uniformDrift({a:0, b: 100, width:5});
   var g = uniformDrift({a:0, b: 1, width:0.2});
@@
   })
-
-  var marginalPrevalence = sample(flip(phi) ? stableComponent : transientComponent)
-  return {g, d, phi, marginalPrevalence}
+  return {g, d, phi}
 }
 '
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-marginal.prevalence <- data.frame()
-m.gen.endorse.priors.summary <- data.frame()
-
+
+unstructuredPriorModel <- '
+var model = function(){
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  mapData({data: preprocessedResponses}, function(d){
+    factor(stableComponent.score(d))
+  })
+  return {g, d}
+}
+'
+```
+
+```{r generic-endorsement-priors-bayesFactors, eval = F}
+genericEndorsementPriorModelPriorLikelihoodHelpers <- '
+var properties = _.uniqBy(_.map(data, "Property"));
+
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var betaShape = function(params){
+  return {
+      a: params.g * params.d,
+      b : (1-params.g) * params.d
+  }
+}
+'
+
+genericEndorsementPriorModelsPriorLikelihood <- '
+var transientComponent = Beta({a:1, b:100})
+
+var model = function(){
+
+  var propertyLogLikes = map(function(property){
+
+    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
+    var preprocessedResponses = map(function(d){
+        return avoidEndPoints(d / 100)
+    }, propertyData);
+
+    var phi = uniformDrift({a:0, b: 1, width:0.2});
+    var g = uniformDrift({a:0, b: 1, width:0.2});
+    var d = uniformDrift({a:0, b: 100, width:5});
+    var stableParams = betaShape({g, d})
+    var stableComponent = Beta(stableParams)
+
+    var logLikes = map(function(d){
+      var structuredLL = log(
+        phi * exp(stableComponent.score(d)) +
+        (1 - phi) * exp(transientComponent.score(d))
+      )
+
+      var unstructuredLL = stableComponent.score(d);
+
+      return {structuredLL, unstructuredLL}
+    }, preprocessedResponses)
+
+    return {
+      structuredLL: sum(_.map(logLikes, "structuredLL")), 
+      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
+    }
+
+  }, properties)
+
+  return {
+    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
+    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
+  }
+}
+'
+
+```
+
+```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
+marginal.prior.likelihoods <- data.frame()
+
+# 100 samples takes 30s
+m.gen.endorse.priors.logLike <- webppl(
+    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
+          genericEndorsementPriorModelsPriorLikelihood,
+          sep = '\n'), 
+    data = d.gen.endorse.priors, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "forward", samples = 1000),
+    chains = 3, cores = 3
+) %>% 
+  mutate(value = as.numeric(value))
+
+min.ll.1 <- min(
+  m.gen.endorse.priors.logLike$value[
+    is.finite(
+      m.gen.endorse.priors.logLike$value
+      )
+    ]
+  )
+
+m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
+  rowwise() %>%
+  mutate(value = ifelse(value == -Inf, min.ll.1, value))
+
+save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
+```
+
+```{r generic-endorsement-priors-bayesFactorsLoad}
+load(file = '../analysis/generics-priors-loglike.Rdata')
+marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
+  group_by(Chain, Parameter) %>%
+  summarize(mll  = logmeanexp(value))
+
+marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
+  spread(Parameter, mll) %>%
+  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
+
+roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
+```
+The Bayes Factor indicates the extent to which the data support one model over another.
+The overall Bayes Factor in terms of Structured Model (S) over the Unstructured Model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
+Indeed, the data strongly suggests the prevalence prior is structured.
+
+It is possible that the data is, in fact, more structured than our simple two-component model. 
+To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
+This is called the *posterior predictive distribution* and is an important step in model validation. 
+If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
+We construct a posterior predictive distribution by "forward sampling" the model.^[
+This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
+If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
+If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
+We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
+]
+
+We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
+To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
+Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
+There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
+One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
+The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
+Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
+]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
+We could fit a more complex model to this data (i.e., one with three mixture components); however, we retain the imperfect simpler model for data-analytic ease going forward.
+
+```{r generic-endorsement-priors-savageDickeyModel, eval = F}
+savageDickeyModel <-'
+var model = function(){
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data: preprocessedResponses}, function(d){
+    factor( log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    ))
+  })
+  return {phi}
+}
+
+//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
+// var samples = 2000, burn = burn / 2, lag = 0;
+var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
+verbose: true}, model)
+var modelPrior = Infer({method: "forward", samples:10000}, model)
+
+var pointNull = 1;
+
+var logBFs = map(function(diff){
+  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
+  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
+  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
+  return [diff, Math.log(savageDickeyRatio)]
+}, [0.01, 0.02, 0.03, 0.04, 0.05])
+
+var returnVals = {
+  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
+}
+returnVals
+'
+```
+
+```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
+genericEndorsementPriorSupermodel <- '
+var model = function(){
+  var alpha = uniformDrift({a:0, b: 1, width:0.2});
+  //var structured = flip();
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g1 = uniformDrift({a:0, b: 1, width:0.2});
+  var d1 = uniformDrift({a:0, b: 100, width:5});
+  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
+  // var d0 = uniformDrift({a:0, b: 100, width:5});
+  var stableParams1 = betaShape({g: g1, d: d1})//, 
+      //stableParams0 = betaShape({g: g0, d: d0});
+  var stableComponent1 = Beta(stableParams1)//,
+      //stableComponent0 = Beta(stableParams0);
+
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data:preprocessedResponses},
+    function(d){
+    var scr1 = log(phi * exp(stableComponent1.score(d)) +
+                    (1 - phi) * exp(transientComponent.score(d)))
+    var scr0 = stableComponent1.score(d);
+    // display(exp(scr1) + " " + exp(scr0));
+    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
+    // factor(structured ? scr1 : scr0)
+    factor(combined_ll)
+  })
+  return alpha
+}
+'
+```
+
+```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
 for (p in gen.endorse.properties){
   priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-  m.gen.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 1000, burn = 500, verbose = T))
-
-  marginal.prevalence <- bind_rows(marginal.prevalence, 
-                                   m.gen.endorse.priors %>% 
-                                     filter(Parameter == "marginalPrevalence") %>%
-                                     mutate(Property = p))
-
-  m.gen.endorse.priors.summary <- bind_rows(m.gen.endorse.priors.summary,
-                                            m.gen.endorse.priors %>% 
-                                              mutate(Property = p) %>%
-                                              group_by(Property, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
+
+  m.gen.endorse.priors.supermodel.posterior <- webppl(
+    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model",  chains = 2,
+                                 cores = 2,
+                                 inference_opts = 
+                                   list(method = "MCMC",
+                                        samples = 2000, 
+                                        burn = 2000, 
+                                        lag = 2, 
+                                        verbose = T)
     )
+
+  qplot(m.gen.endorse.priors.supermodel.posterior$value)
+}
+```
+
+```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
+genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
+var eps = 0.00000001;
+
+var model = function(){
+  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
+  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
+  var d = uniformDraw(_.range(eps, 100, 2))
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  var logLike = sum(map(function(d){
+    var scr = log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    )
+    return scr
+  }, preprocessedResponses))
+  return logLike
+}
+'
+genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
+var eps = 0.00000001;
+
+var model = function(){
+  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
+  var d = uniformDraw(_.range(eps, 100, 2))
+  var stableParams = betaShape({g, d});
+  var stableComponent = Beta(stableParams);
+  var logLike = sum(map(function(d){
+    return stableComponent.score(d)
+  }, preprocessedResponses))
+  return logLike
+}
+'
+```
+
+```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
+marginal.prior.likelihoods <- data.frame()
+
+for (p in gen.endorse.properties){
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+  m.gen.endorse.priors.logLike.enum1 <- webppl(
+    paste(genericEndorsementPriorModelHelpers,
+          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "enumerate")
+    )
+
+  m.gen.endorse.priors.logLike.enum0 <- webppl(
+    paste(genericEndorsementPriorModelHelpers,
+          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "enumerate")
+    )
+
+  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
+  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
+
+  marginal.prior.likelihoods <- bind_rows(
+    marginal.prior.likelihoods, 
+    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
+  )
+}
+
+marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
+
+```
+
+```{r generic-endorsement-priors-model-run, eval = F}
+m.gen.endorse.priors.posteriorPredictive <- data.frame()
+n_samples <- 1000
+lg = 0
+example.generics.prior.properties <- c(
+  "dont eat people", "have beautiful feathers",
+  "have wings", "are red",
+  "carry malaria", "lay eggs", 
+  "are female", "have spots"
+  )
+
+for (p in example.generics.prior.properties ) {
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+    m.gen.endorse.priors.structured <- webppl(
+      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
+      group_by(Iteration, Chain) %>%
+      spread(Parameter, value) %>%
+      rowwise() %>%
+      mutate(
+        a = g*d,
+        b = (1-g)*d,
+        isPresent = rbinom(1, 1, prob = phi),
+        prevalence = ifelse(isPresent == 1, 
+                           rbeta(n = 1, 
+                                 shape1 = a,
+                                 shape2 = b),
+                           rbeta(n = 1,
+                                 shape1 = 1,
+                                 shape2 = 100)),
+        Property = p, src = "Structured"
+      ) %>% ungroup()
+
+    m.gen.endorse.priors.unstructured <- webppl(
+      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
+      group_by(Iteration, Chain) %>%
+      spread(Parameter, value) %>%
+      rowwise() %>%
+      mutate(
+        a = g*d,
+        b = (1-g)*d,
+        prevalence = rbeta(n = 1, 
+                                 shape1 = a,
+                                 shape2 = b),
+        Property = p, src = "Unstructured"
+      ) %>% ungroup()
+
+    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
+      m.gen.endorse.priors.posteriorPredictive,
+      bind_rows(
+       m.gen.endorse.priors.structured.predictive %>%
+          select( src, Property, prevalence),
+      m.gen.endorse.priors.unstructured.predictive %>%
+          select( src, Property, prevalence),
+      data.frame(Property = p,
+                 src = "Data",
+                 prevalence = priorData/100)
+      )
+    )
+
+  # for (c in 1:2){
+  #     m.gen.endorse.priors.savage <- webppl(
+  #   paste(genericEndorsementPriorModelHelpers, 
+  #         savageDickeyModel, sep = '\n'), 
+  #   data = priorData, 
+  #   data_var = "data"
+  #   )
+
+  # m.inferred.prior <- get_samples(
+  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
+  #     rename(prob = probs), n_samples)
+  # 
+  # m.inferred.posterior <- get_samples(
+  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
+  #     rename(prob = probs), n_samples)
+  # 
+  # posterior.density <- density(m.inferred.posterior$phi,
+  #         from = 0, to = 1)
+  # 
+  # prior.density <- density(m.inferred.prior$phi,
+  #         from = 0, to = 1)
+  # 
+  # logBF01 = log(approxfun(posterior.density)(1)) - 
+  #   log(approxfun(prior.density)(1))
+
+  # m.gen.endorse.priors.savage.summary <- bind_rows(
+  #   m.gen.endorse.priors.savage.summary,
+  #     bind_rows(
+  #     data.frame(Property = p, 
+  #                Chain = c, 
+  #                diff = NA,
+  #                logBF01 = logBF01,
+  #                BF01= exp(logBF01)),
+  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
+  #       rename(diff = X1, logBF01 = X2) %>%
+  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
+  #     )
+  # )
+  # 
+  # }
+
+    #for (c in 1:3){
+
+      # posterior.logspline <-  polspline::logspline(filter(
+      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
+      #   lbound = 0, ubound = 1)
+      # 
+      #   posterior <- dlogspline(1, posterior.logspline)
+      # prior <- dunif(1, min = 0, max = 1)
+      # BF01 <- posterior/prior
+      # 
+      # print(log(BF01))
+
+  #}
+
   #print(p)
-}
-```
-
-```{r generic-endorsement-priors-figure, eval = F}
+  #print(priorData)
+}
+save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
+
+```
+
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density functions for prior distributions representing the prevalence of eight different features.
+Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
+A completely uniform distribution would be represented as the y = x line."}
+load('../analysis/generics-priors-posteriorPredictives.Rdata')
+    ggplot(m.gen.endorse.priors.posteriorPredictive, 
+           aes( x = prevalence, color = src, lty = src))+
+      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    stat_ecdf(size = 1)+
+    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    facet_wrap(~Property, nrow = 2)+
+    scale_linetype_manual(values = c(1, 4, 3))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  coord_fixed()+
+    xlab("Prevalence") +
+    ylab("Cumulative probability density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+
+```
+
+```{r generic-endorsement-priors-figure2, eval = F}
 ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
@@
 
-### Results
-
-The prevalence prior data is indeed structure.
-
-We also see tremendous variability in the shapes of these prevalence distributions.
-
 <!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
@@
 
-Having measured the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) in addition to target-category prevalence (e.g., how many robins lay eggs; Expt.
-1a), our speaker model (Eq.
-\ref{eq:S1}) can predict endorsements for the corresponding generic statements (e.g., Robins lay eggs).
+In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
+This data also includes informaiton about the target-category prevalence (e.g., how many robins lay eggs).
+Using the target-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
 To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
@@
                     "naturalGenerics-trials-formatted.csv", sep = ""))
-
-head(d1)
-head(d2)
 
@@
 In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
-This argues against any simple theory that only predicts whether or not a generic statement is true or false. 
+Such a continuum of judgments is evidence against any theory that only predicts whether a generic statement is true or false.
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
 
-To try to understand this endorsement data, we articulate alternative models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
+To try to understand this endorsement data, we articulate a set of simple models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
 As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
 As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
+We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (e.g., prevalence, cue validity) by bootstrapping those data.
 
@@
 The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
-There are thus three unique components of this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
-As a control model, we use the same infrastructure but assign the semantics of "Some" to the utterance (i.e., a fixed-threshold which only rules out the lowest possible degree). 
+There are thus three unique components to this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
+As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
 This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
 This provides a strict test of our *simple but underspecified* hypothesis.
-
-##### Prevalence baseline
-
-From the prevalence prior data (Expt.
-1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
-We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
-This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
-However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $ 20\% < prevalence < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).
-
-##### Prevalence and cue validity
-
-<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
-If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though a strong version of cue validity has been argued against on *a priori* grounds [@Leslie2007; @Leslie2008].
-
-For a prevalence distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the prevalence prior distribution (i.e., it is a summary statistic of this distribution).
-In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
-To measure cue validity, we employed a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix.
-
-A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(30) = 0.79$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of cue validity, which is in fact a point-summary statistic based on the prevalence distribution (see Appendix more details).
-"Lays eggs" is a somewhat diagnostic features for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A single metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the learned regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high.
-
-##### Fixed threshold RSA model
-
-The RSA model we propose for generic endorsement is a speaker model who decides whether or not to say the generic to a naive listener, who has access to the full prior distribution on prevalence $P(h)$.
-As a strong alternative model, we retain the specification of the speaker reasoning about a listener with this prior distribution, but remove the uncertainty about the generic threshold. 
-For this model, we set $\theta = 0$, and thus the generic statement corresponds to the quantified statement "Some".
-
-<!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
--->
-We use the empirically estimated within-kind target prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
-1a as the listener's prevalence prior $P(h)$.^[
-Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener.
-This corresponds to the more general form of the model described in **Alternative Formulations** section.
-With these data, the predictions of these two models are nearly identical.
-]
-The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-We infer this parameter, as well as the values of target prevalence $h$, and parameters of the prevalence priors $P(h)$ (assuming the structured model validated in Expt.
-1a) using Bayesian data analysis [@LW2014].
-For the prevalence parameters, we use the same priors described in Expt.
-1a; for the speaker optimality parameter, we use an informative prior, with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of our model parameters by collecting samples from MCMC chains of 10,000 iterations removing the first 5,000 iterations, using the Metropolis-Hastings algorithm.
-
-We compare the "Some" model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(The posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
-In accord with intuition, assigning a fixed semantics corresponding to "Some" is too lenient a specification. 
-Even for patently false generics (e.g., "Mosquitos don't carry malaria"), the speaker model is unable to prefer staying silent than producing the generic (with a "some" semantics).
-It also doesn't strongly prefer producing the generic, possibly because the information content is so small.
-
-##### Uncertain threshold RSA model with diverse priors
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0.5$, it has *a priori* uncertainty over the threshold.
-We perform the same Bayesian data analysis as the "Some" model.
-As we see in Figure \ref{fig:commongenerics}b, the pragmatic speaker model $S_2$, using empirically measured priors, explains nearly all of the variance in human truth judgments ($r^2=0.98$; MSE=0.003; Figure \ref{fig:commongenerics}b).
 
@@
 ```
+
+##### Prevalence baseline
+
+From the prevalence prior data (Expt.
+1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
+We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
+This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
+However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $20\% < \text{prevalence} < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).
+
+##### Prevalence and cue validity
+
+<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
+If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
+For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
+Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008].
+
+For a prevalence distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the prevalence prior distribution.
+In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
+For this analysis, we measured cue validity using a free production paradigm, following @Cree2006.
+Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
+For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B.
+
+A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(30) = 0.79$).
+This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
+Deviations, however, still remain.
+For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
+
+These highlight a shortcoming of a simple model based on cue validity.
+"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
+A single metric like cue validity is too blunt to capture this subtlety.
+Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high.
+
+##### Fixed threshold RSA model
+
+\begin{figure}
+\centering
+    \includegraphics[width=\columnwidth]{figs/generics_bayesnetmodel.pdf}
+    \caption{Caption
+    }
+  \label{fig:genericsModelDiagram}
+\end{figure}
+
+The RSA model we propose for generic endorsement is a speaker model who decides whether or not to say the generic to a naive listener, who has access to the full prior distribution on prevalence $P(h)$.
+As a strong alternative model, we retain the specification of the speaker reasoning about a listener with this prior distribution, but remove the uncertainty about the generic threshold. 
+For this model, we set $\theta = 0$, and thus the generic statement corresponds to the quantified statement "Some".
+
+<!-- Our pragmatic speaker model, $S_1$ in Eq.
+\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
+-->
+We use the empirically estimated within-kind target prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
+1a as the listener's prevalence prior $P(h)$.^[
+Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
+This corresponds to the more general form of the model described in **Alternative Formulations** section. 
+With these data, the predictions of these two models are nearly identical.
+]
+The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+We combine the RSA model with the Bayesian data analysis model of the prevalence prior data (Expt.
+1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$, the target prevalence $h$, and parameters of the prevalence priors $P(h)$ are inferred simultaneously via both data sources (Expt.
+1a \& b; see Figure).
+For the prevalence parameters, we use the same priors described in Expt.
+1a; for the speaker optimality parameter, we use an informative prior, with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
+We learn about the \emph{a posteriori} credible values of our model parameters by collecting samples from MCMC chains of 10,000 iterations removing the first 5,000 iterations, using the Metropolis-Hastings algorithm.
+
+We compare the "Some" model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
+(The posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
+In accord with intuition, assigning a fixed semantics corresponding to "Some" is too lenient a specification. 
+Even for patently false generics (e.g., "Mosquitos don't carry malaria"), the speaker model is unable to prefer staying silent than producing the generic (with a "some" semantics).
+It also doesn't strongly prefer producing the generic, possibly because the information content is so small.
+
+##### Uncertain threshold RSA model
+
+Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0.5$, it has *a priori* uncertainty over the threshold.
+We perform the same Bayesian data analysis as the "Some" model.
+As we see in Figure \ref{fig:commongenerics}b, the pragmatic speaker model $S_2$, using empirically measured priors, explains nearly all of the variance in human truth judgments ($r^2=0.98$; MSE=0.003; Figure \ref{fig:commongenerics}b).
 

### 2017-06-24 paper/comgen-paper.Rmd
replace manipulation check regression with bayesian CIs, calculate in line

@@
 
+```{r generic-endorsement-manipulationcheck}
+# MHT's truth judgments of sentences
+# t --> true; f --> false; i --> indeterminate/uncertain
+all.sentences <- list("Cardinals are red." = "t",
+ "Ducks have wings." = "t",
+ "Kangaroos have pouches." = "t",
+ "Kangaroos have spots." = "f",
+ "Leopards are juvenile." = "i",
+ "Leopards have spots." = "t",
+ "Leopards have wings." = "f",
+ "Lions are male." = "i",
+ "Lions have manes." = "t",
+ "Lions lay eggs." = "f",
+ "Mosquitos attack swimmers." = "i",
+ "Mosquitos carry malaria." = "t",
+ "Mosquitos dont carry malaria." = "f",
+ "Peacocks dont have beautiful feathers." = "f",
+ "Peacocks have beautiful feathers." = "t",
+ "Robins are female." = "i",
+ "Robins carry malaria." = "f",
+ "Robins lay eggs." = "t",
+ "Sharks are white." = "i",
+ "Sharks attack swimmers." = "t",
+ "Sharks dont attack swimmers." = "f",
+ "Sharks have manes." = "f",
+ "Sharks lay eggs." = "i",
+ "Swans are full-grown." = "i",
+ "Swans are white." = "t",
+ "Ticks carry Lyme disease." = "t",
+ "Ticks dont carry Lyme disease."= "f",
+ "Tigers dont eat people."= "f",
+ "Tigers eat people." = "t",
+ "Tigers have pouches."= "f")
+
+mht.truth.judgments <- data.frame(sentence = names(all.sentences),
+           truth_judgment = as.vector(unlist(all.sentences)))
+
+d.gen.endorse.manipulation.check.bayes <- left_join(
+  left_join(
+    d.gen.endorse, 
+    d.gen.endorse.catch %>% select(workerid, pass)
+    ),
+  mht.truth.judgments ) %>%
+  filter(pass == 1) %>%
+  rowwise() %>%
+  mutate(response = ifelse(response == "agree-key", 1, 0),
+         sentence = gsub('&quotechar', '', sentence),
+         sentence = gsub('lyme', 'Lyme', sentence)) %>%
+  group_by(truth_judgment) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b)) %>% 
+  ungroup() %>%
+  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
+
+true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
+true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
+true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]
+
+false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
+false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
+false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]
+
+uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
+uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
+uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
+
+```
+
 As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-This was a significant predictor of the empirical truth judgments: true generics were significantly more likely to be agreed with than the indeterminate generics ($\beta = 3.14; SE = 0.15; z = 21.5$), as revealed by a mixed-effect logistic regression with random by-participant effects of intercept.
-Indeterminate generics were agreed with \emph{less} likely than chance ($\beta = -0.49; SE = 0.09; z = -5.3$) but significantly more than false generics ($\beta = 2.09; SE = 0.14; z = 14.5$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
-Such a continuum of judgments is evidence against any theory that only predicts whether a generic statement is true or false.
+As one would expect, there were substantial differencesin empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP` [`r true_low`, `r true_high`])$;
+indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP` [`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP` [`r false_low`, `r false_high`])$).
+
+In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure}).
+Such a continuum of judgments is already evidence against any theory that only predicts whether a generic statement is true or false.
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.

### 2017-06-25 paper/comgen-paper.Rmd
bootstrap errorbars for prevalence and cuevalidity; make generics numbers generated by code

@@
 As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differencesin empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP` [`r true_low`, `r true_high`])$;
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP` [`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP` [`r false_low`, `r false_high`])$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure}).
+As one would expect, there were substantial differencesin empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`])$;
+indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
+
+In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
 Such a continuum of judgments is already evidence against any theory that only predicts whether a generic statement is true or false.
@@
 
-```{r generic-regression-models}
+```{r generic-regression-models, cache = T}
 d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
@@
 
-# need to filter by items specified with endorsement
-d.gen.cv.summary <- left_join(
-  d.target.items %>% select(-sentence),
-  d.cv %>%
-    rename(category = response) %>%
+d.cv.bootstrapped <- data.frame()
+resample_n <- length(levels(factor(d.cv$workerid)))
+for (i in 1:1000){
+
+  d.cv.bsample <- d.cv %>% 
+    select(workerid, property, response) %>% 
+    spread(property, response) %>% 
+    sample_n(resample_n, replace = TRUE) %>%
+    gather(property, category, -workerid) %>% 
         group_by(property) %>%
@@
               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials)
+              prop = mentions / trials,
+              prop = ifelse(is.na(prop), 0.01, prop),
+              iteration = i)
+
+  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
+}
+
+empiricalLower = function(dist){
+  xi <- quantile(dist, 0.025)
+  return (xi[["2.5%"]])
+}
+empiricalUpper = function(dist){
+  xi <- quantile(dist, 0.975)
+  return (xi[["97.5%"]])
+}
+empiricalMean = function(dist){
+  xi <- quantile(dist, 0.5)
+  return (xi[["50%"]])
+}
+
+d.gen.cv.summary <- left_join(
+    d.target.items %>% select(-sentence),
+    d.cv.bootstrapped %>%
+      group_by(property) %>%
+      summarize(cv_mean = empiricalMean(prop),
+                cv_ci_lower = empiricalLower(prop),
+                cv_ci_upper = empiricalUpper(prop))
 ) %>%
-  mutate(prop = ifelse(is.na(prop), 0.01, prop))
+  mutate(
+    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
+    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
+    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
+  )
+
+# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
+# 
+# d.cv.bootstrapped %>%
+#   group_b
+
+# need to filter by items specified with endorsement
+# d.gen.cv.summary <- left_join(
+#   d.target.items %>% select(-sentence),
+#   d.cv %>%
+#     rename(category = response) %>%
+#     group_by(property) %>%
+#     mutate(n = n(),
+#            item = paste(category, property)) %>%
+#     filter(item %in% d.target.items$item) %>%
+#     group_by(category, property) %>%
+#     summarize(mentions = n(),
+#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
+#               prop = mentions / trials)
+#   ) %>%
+#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
 
@@
     d.prev.summary %>% 
-      rename(prevalence = mean,
-             sentence = item) %>% 
-      select(-ci_lower, -ci_upper)
+      rename(prev_mean = mean,
+             sentence = item,
+             prev_ci_lower = ci_lower,
+             prev_ci_upper = ci_upper)
     ),
@@
 
-glm.gen.endorse.prev <- glm(response ~ prevalence, 
+glm.gen.endorse.prev <- glm(response ~ prev_mean, 
               data = d.gen.endorse.prev.cue, family = 'binomial')
 
-glm.gen.endorse.prev.cv <- glm(response ~ prevalence + prop, 
+glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
               data = d.gen.endorse.prev.cue, family = 'binomial')
+
+d.gen.endorse.prev.cue.uniq <- unique(select(
+    d.gen.endorse.prev.cue, Property, Category, sentence, 
+    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
+  ))
+
+d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
+  select(-prev_mean, -cv_mean) %>% 
+  rename(prev_mean = prev_ci_lower,
+         cv_mean = cv_ci_lower)
+d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
+  select(-prev_mean, -cv_mean) %>% 
+  rename(prev_mean = prev_ci_upper,
+         cv_mean = cv_ci_upper)
 
@@
   d.gen.endorse.bayes,
-  unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
-  )) %>%
-    mutate(prediction = predict(glm.gen.endorse.prev, ., type = "response")) %>%
+  d.gen.endorse.prev.cue.uniq %>%
+    mutate(
+      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
+      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
+      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
+    ) %>%
     mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(sqErr = (mean - prediction) ^ 2,
-             cuevalidity = prop)
+) %>% mutate(
+  sqErr = (MAP_h - prediction_mean) ^ 2
+)
 
@@
   d.gen.endorse.bayes,
-   unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, prevalence, prop
-    )) %>% 
-    mutate(prediction = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-           sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(sqErr = (mean - prediction) ^ 2,
-             cuevalidity = prop)
+  d.gen.endorse.prev.cue.uniq %>%
+    mutate(
+      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
+      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
+      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
+      sentence = paste(Category, " ", Property, ".", sep = "")
+      )
+) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
 
@@
 #   facet_wrap(~src)
+
+r2.gen.n <- length(d.gen.endorse.bayes$sentence)
+r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
+mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)
+
+r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
+mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)
+
+intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))
+
+d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
+  filter(
+    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
+    (prev_mean < intermediate.prev.quantiles[["76%"]])
+)
+r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)
+
+r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
+mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
 ```
@@
 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
-We find a little over half of the variance in the endorsement data is explained this way ($r^2 = 0.599$; MSE=0.065; Figure \ref{fig:commongenerics}b, right). 
+We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:commongenerics}b, right).
 This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
-However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $20\% < \text{prevalence} < 64\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2 = 0.029$; MSE = 0.110).
+However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
 
@@
 
-A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(30) = 0.79$).
+A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
 This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
@@
 generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression %>% 
-  mutate(prediction_lower = prediction,
-         prediction_upper = prediction),
+  d.gen.endorse.regression,
   left_join(
     m.gen.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
+      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
     d.gen.endorse.regression %>% 
-    select(sentence, Property, Category, prevalence, cuevalidity)
+      select(sentence, Property, Category, prev_mean, cv_mean)
   )
@@
                                  ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prevalence ))+
+  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
+                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
   geom_abline(intercept = 0, slope = 1, lty = 3)+
@@
 
+generics.endorsement.models
 ```

### 2017-06-26 paper/comgen-paper.Rmd
code for rsa model stats (generics); beef up results section of RSA model and alternative

@@
   return(xstar + log(mean(exp(x.num - xstar))))
+}
+
+compute_r2 <- function(df,v1, v2, sigfigs = 3){
+  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
+}
+
+compute_mse <- function(df, v1, v2, sigfigs = 3){
+  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
 }
@@
 '
+genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
+
 ```
@@
 
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics_bayesnetmodel.pdf}
-    \caption{Caption
-    }
-  \label{fig:genericsModelDiagram}
-\end{figure}
-
-The RSA model we propose for generic endorsement is a speaker model who decides whether or not to say the generic to a naive listener, who has access to the full prior distribution on prevalence $P(h)$.
-As a strong alternative model, we retain the specification of the speaker reasoning about a listener with this prior distribution, but remove the uncertainty about the generic threshold. 
-For this model, we set $\theta = 0$, and thus the generic statement corresponds to the quantified statement "Some".
-
-<!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
--->
-We use the empirically estimated within-kind target prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
-1a as the listener's prevalence prior $P(h)$.^[
-Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-This corresponds to the more general form of the model described in **Alternative Formulations** section. 
-With these data, the predictions of these two models are nearly identical.
-]
-The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-We combine the RSA model with the Bayesian data analysis model of the prevalence prior data (Expt.
-1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$, the target prevalence $h$, and parameters of the prevalence priors $P(h)$ are inferred simultaneously via both data sources (Expt.
-1a \& b; see Figure).
-For the prevalence parameters, we use the same priors described in Expt.
-1a; for the speaker optimality parameter, we use an informative prior, with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of our model parameters by collecting samples from MCMC chains of 10,000 iterations removing the first 5,000 iterations, using the Metropolis-Hastings algorithm.
-
-We compare the "Some" model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(The posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
-In accord with intuition, assigning a fixed semantics corresponding to "Some" is too lenient a specification. 
-Even for patently false generics (e.g., "Mosquitos don't carry malaria"), the speaker model is unable to prefer staying silent than producing the generic (with a "some" semantics).
-It also doesn't strongly prefer producing the generic, possibly because the information content is so small.
-
-##### Uncertain threshold RSA model
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0.5$, it has *a priori* uncertainty over the threshold.
-We perform the same Bayesian data analysis as the "Some" model.
-As we see in Figure \ref{fig:commongenerics}b, the pragmatic speaker model $S_2$, using empirically measured priors, explains nearly all of the variance in human truth judgments ($r^2=0.98$; MSE=0.003; Figure \ref{fig:commongenerics}b).
-
-```{r generic-fullmodel, fig.width = 8}
+```{r generic-RSAmodels, fig.width = 8}
 # n_chains <- 1
@@
     mutate(src = "some_model")
+)
+
+r2.gen.rsa.generics <- compute_r2(
+  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
+  "MAP", "MAP_h", sigfigs = 3
+)
+
+r2.gen.rsa.fixed <- compute_r2(
+  m.gen.endorse.rsa %>% filter(src == "some_model"),  
+  "MAP", "MAP_h", sigfigs = 3
+)
+
+mse.gen.rsa.generics <- compute_mse(
+  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
+  "MAP", "MAP_h", sigfigs = 3
+)
+
+mse.gen.rsa.fixed <- compute_mse(
+  m.gen.endorse.rsa %>% filter(src == "some_model"),  
+  "MAP", "MAP_h", sigfigs = 3
 )
@@
   theme(legend.position = "bottom")
-
-generics.endorsement.models
 ```
@@
 m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "withinKind") %>%
+  filter(type == "targetPrevalence") %>%
   group_by(param, property, category) %>%
@@
 m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "withinKind") %>%
+  filter(type == "targetPrevalence") %>%
   mutate(Sentence = paste(category, property)) %>%
@@
     theme(legend.position = "bottom", legend.title = element_blank())
-
 ```
@@
 ```
+
+The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
+Unlike the simple regression models based on point-estimates of target-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
+This model has two other main architectural differences: an information-theoretic decision between producing the generic vs.
+an information-less alternative and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.
+
+We first test a model that has two of the the above three main architectural features.
+This model has access to the full prior distribution on prevalence as well as models an information-theoretic decision of producing the generic vs. an alternative.
+The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
+For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
+Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria").
+]
+This is a strong alterantive model to our uncertain-threshold model; the only difference concerns the threshold.
+
+<!-- Our pragmatic speaker model, $S_1$ in Eq.
+\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
+-->
+We use the empirically estimated target-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
+1a as the listener's prevalence prior $P(h)$.^[
+Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
+This corresponds to the more general form of the model described in **Alternative Formulations** section. 
+With these data, the predictions of these two models are nearly identical.
+]
+The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+
+\begin{figure}
+\centering
+    \includegraphics[width=\columnwidth]{figs/generics_bayesnetmodel.pdf}
+    \caption{Caption
+    }
+  \label{fig:genericsModelDiagram}
+\end{figure}
+
+To fit this model, we incorporate the RSA model into the Bayesian data analysis model of the prevalence prior data (Expt.
+1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$ is inferred jointly with the target prevalence $h_{k, f}$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_f(h)$ for each property $f$ using data from Expt.
+1a \& b (see Figure \ref{fig:genericsModelDiagram}).
+For the parameters of the prevalence distributions, we use the same priors described in Expt.
+1a; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
+We learn about the \emph{a posteriori} credible values of this joint inference model using an incrementalized-version of the  by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
+
+The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (prevalences, prevalence priors, and the speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
+Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the target-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+1a).
+This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the prevalence distributions).
+
+We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
+(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
+Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
+For almost all items, it assigns an intermediate endorsement.
+This is because almost all items get endorsed by some participants; the model then infers that the prevalence must be at least a little greater than 0\%; but, if the prevalence is greater than 0\%, the statement is literally true.
+The speaker model then must decide is it better to say the 0\%-threshold meaning or stay silent.
+For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5).
+For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing some statements (most model predictions around 0.5\%).
+Consistent with intuition, assigning a fixed-semantics is too lenient a specification.
+
+MHT: Outfit fixed-threshold model with noise parameter?
+
+##### Uncertain threshold RSA model
+
+Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold.
+We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
+As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the speaker model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+
+To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
+The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the target category (also in blue).
+The grey distribution shows the listener's prior distribution over prevalence of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
+It is also the listener $L_0$'s posterior upon hearing the silent utterance.
+The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
+The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
+Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
+"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
+"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.
+
+<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g.
+\emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
+-->
+<!-- We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false.
+-->
+<!-- \emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model. -->
+<!-- This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context.
+-->
 
@@
 <!-- This is akin to fitting the parameters and is the critical step in model validation: It shows what data is actually predicted by the model.)  -->
-
-Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g.
-\emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
-We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false.
-\emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model.
-This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context.
 

### 2017-06-27 paper/comgen-paper.Rmd
discuss relationship of mixture parameter to cue validity in discussion of prior expt

@@
 
-Generalizations about categories (i.e., *generic language*) have received substantial interest in psychology for their role in concept formation [@Gelman2004] and stereotype propogation [@Rhodes2012].
-Generic language (e.g., *Birds fly.*) exhibits substantial flexibility in meaning and truth conditions as described above.
+Generalizations about categories (i.e., *generic language*; e.g., *Birds fly.*) have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
+It is the premier case study of generalizations in language and has received the most attention from philosophers, linguists, and psychologists.
+
+Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
+That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
 As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs.
@@
 We do this by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
-\ref{eq:L0} as well as the target probabilitiy that the speaker model seeks to convey $h$ in Eq.
-\ref{eq:S1}.
-We show how these measurements systematically predict, via our model, endorsements of generic statements about familiar categories (Expt. 1b).
-
-<!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
-<!-- Unlike universals, however, generics are resilient to counter-examples (e.g., *Birds fly* seems true even in the face of flightless birds like kiwis or penguins). -->
-<!-- *Most* birds fly seems more reasonable, and yet most mosquitos *do not* carry malaria while *Mosquitos carry malaria* seems like a true statement. -->
-<!-- Finally, the probability of a bird being female is much higher than the probability of a mosquito carrying malaria, but *Birds are female* seems weird to say. -->
-<!-- *Birds lay eggs*, however, is fine, even though the rate is the same as *are female* (only females lay eggs). -->
-
-<!-- Empirical work done on category generalizations has elucidated another puzzling phenomenon. -->
-<!-- Generic statements often imply the property is widespread in the category [e.g., *Swans have hollow bones* implies something much stronger than *Some swans have hollow bones*; @Gelman2002; @Cimpian2010; @Brandone2014].
--->
-<!-- This characteristically strong interpretation interacts with the indeterminacy in truth conditions, resulting in an *asymmetry* between endorsement and interpretation. -->
-<!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->
-
-We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data.
-Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
-After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.
-
-<!-- Interpreting the generic as meaning "most" (i.e.
-\emph{Most swans are white}) captures many cases, but cannot explain why \emph{Robins lay eggs} and \emph{Mosquitos carry malaria} are so intuitively compelling: Only adult female robins lay eggs and a very tiny fraction of mosquitos actually carry malaria.
--->
-<!-- Indeed, it appears that any \emph{truth condition} stated in terms of how common the property is within the kind violates intuitions. -->
-<!-- Consider the birds: for a bird, being female practically implies you will lay eggs (the properties are present in the same proportion), yet we say things like \emph{Birds lay eggs} and we do not say things like \emph{Birds are female}.
--->
-
-<!-- One case study in the language of generalizations is about category generalizations. -->
-<!-- Category generalizations, called *generic statement*, has been studied extensively in cognitive and developmental psychology: *generic* statements, or generalizations about categories. -->
-
-<!-- These *strong implications* might underly stereotype formation in social categories [@Rhodes2012]. -->
-<!-- In addition to the flexibility in truth conditions, two phenomena have been noted.  -->
-<!-- The case of *Mosquitos carry malaria* suggests the utterance must in some way be analogous to the quantifier "some" (e.g., *Some mosquitos carry malaria*).  -->
-<!-- Generic language, however, is often interpreted as implying the property is widespread: *Swans have hollow bones* means something different than *Some swans have hollow bones* [@Gelman2002]. -->
-
-<!-- These three phenomena---flexible truth, strong interpretations, and evidence exaggeration---have confounded all formal models aimed to capture the meaning of generalizations in language. -->
-<!-- Informal theories have argued that the nature of concepts and their relations are inextricably tied to their linguistic expression [@Leslie2007; @Prasada2013]. -->
-<!-- Formal theories have limited themselves to a measurable quantitative degree (e.g., how prevalent a property is in a category), which, in isolation, is difficult to reconcile with the extreme flexibility of generic language.
--->
-<!-- Here, we present a theory formalizing the inuition that the core meaning of a linguistic generalization is simple, but underspecified, and that general principles of communication may be used to resolve the precise meaning in context.
--->
-<!-- This theory inherently relies upon measurable quantities (i.e., prevalence) but situates it within a Bayesian agent with potentially structured prior knowledge, providing a bridge to conceptual theories.
--->
-<!-- We find that this formalism (and not simpler ones) explains all three empirical puzzles. -->
-
-<!-- When interpretations are compared directly against truth conditions (i.e., how prevalent a property would need to be for the generic to be true),  -->
-
-<!-- Three empirical phenomena make generalizations in language difficult to formalize. -->
-<!-- The conditions under which a generalizations becomes "true" are variable: -->
-
-<!-- Existing work in both adults and children suggests that choosing to communicate a generalization can be used to exagerate evidence [@Cimpian2010; @Brandone2014]. -->
-
-<!-- In addition to having manifold interpretations, what makes linguistic generalizations true or false (i.e., their truth conditions) is also a mystery. -->
-<!-- The statement *Birds lay eggs* is true even though only about half of them do (namely, the females). -->
-<!-- Half of birds are also female, and yet *Birds are female* sounds like a strange thing to say. -->
-<!--  while *Canadians are right-handed* is also weird, even though the vast majority of them are.  -->
-
-## Experiment 1: Endorsing generalizations about categories
-
-Any theory of generic language must explain their puzzling flexibility of usage with respect to prevalence.
-That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
+\ref{eq:L0} as well as the target-category prevalence $h$ that the speaker model seeks to convey in Eq.
+\ref{eq:S1} (Expt.
+1a).
+
 <!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
@@
 
-To compare the model to empirical truth judgments, we first measure the prior distribution over prevalence of these properties (Expt. 1a).
-We hypothesize that this prior distribution encodes probabilities associated with deeper conceptual knowledge [e.g., of the kind discussed by @Prasada2013].
-This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
-If, indeed, there are such things as different types of kind--property relations (e.g., *principled* v.
-*accidental relations*), we would expect the prevalence prior data to follow a multi-modal, mixture distribution where different modes or components of the prior are the results of the different types of relations.
-As a simple test of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
-
-After exploring the prevalence prior, we move on to the issue of primary theoretical interest: How well our *simple but underspecified* hypothesis accounts for endorsements of generic sentences (Expt.
+To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
+We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
+In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
+*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasda2013] can be observed in the prevalence prior.
+If, in fact, the prevalence prior is one manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively modes or components of the prior, the results of the different types of kinds with respect to the property.
+This is important because it is one way in which our formal theory connects to other, informal psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
+As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
+
+After having validated a measure of the prevalence prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
 1b).
-
-### Experiment 1a: Measuring the Prevalence Prior for Categories
+In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model.
+To preview our results, we find that only our formulation of an uncertain threshold RSA model is able to account for the flexibility in generic endorsement.
+
+<!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
+<!-- Unlike universals, however, generics are resilient to counter-examples (e.g., *Birds fly* seems true even in the face of flightless birds like kiwis or penguins). -->
+<!-- *Most* birds fly seems more reasonable, and yet most mosquitos *do not* carry malaria while *Mosquitos carry malaria* seems like a true statement. -->
+<!-- Finally, the probability of a bird being female is much higher than the probability of a mosquito carrying malaria, but *Birds are female* seems weird to say. -->
+<!-- *Birds lay eggs*, however, is fine, even though the rate is the same as *are female* (only females lay eggs). -->
+
+<!-- Empirical work done on category generalizations has elucidated another puzzling phenomenon. -->
+<!-- Generic statements often imply the property is widespread in the category [e.g., *Swans have hollow bones* implies something much stronger than *Some swans have hollow bones*; @Gelman2002; @Cimpian2010; @Brandone2014].
+-->
+<!-- This characteristically strong interpretation interacts with the indeterminacy in truth conditions, resulting in an *asymmetry* between endorsement and interpretation. -->
+<!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->
+
+<!-- Interpreting the generic as meaning "most" (i.e.
+\emph{Most swans are white}) captures many cases, but cannot explain why \emph{Robins lay eggs} and \emph{Mosquitos carry malaria} are so intuitively compelling: Only adult female robins lay eggs and a very tiny fraction of mosquitos actually carry malaria.
+-->
+<!-- Indeed, it appears that any \emph{truth condition} stated in terms of how common the property is within the kind violates intuitions. -->
+<!-- Consider the birds: for a bird, being female practically implies you will lay eggs (the properties are present in the same proportion), yet we say things like \emph{Birds lay eggs} and we do not say things like \emph{Birds are female}.
+-->
+
+<!-- One case study in the language of generalizations is about category generalizations. -->
+<!-- Category generalizations, called *generic statement*, has been studied extensively in cognitive and developmental psychology: *generic* statements, or generalizations about categories. -->
+
+<!-- These *strong implications* might underly stereotype formation in social categories [@Rhodes2012]. -->
+<!-- In addition to the flexibility in truth conditions, two phenomena have been noted.  -->
+<!-- The case of *Mosquitos carry malaria* suggests the utterance must in some way be analogous to the quantifier "some" (e.g., *Some mosquitos carry malaria*).  -->
+<!-- Generic language, however, is often interpreted as implying the property is widespread: *Swans have hollow bones* means something different than *Some swans have hollow bones* [@Gelman2002]. -->
+
+<!-- These three phenomena---flexible truth, strong interpretations, and evidence exaggeration---have confounded all formal models aimed to capture the meaning of generalizations in language. -->
+<!-- Informal theories have argued that the nature of concepts and their relations are inextricably tied to their linguistic expression [@Leslie2007; @Prasada2013]. -->
+<!-- Formal theories have limited themselves to a measurable quantitative degree (e.g., how prevalent a property is in a category), which, in isolation, is difficult to reconcile with the extreme flexibility of generic language.
+-->
+<!-- Here, we present a theory formalizing the inuition that the core meaning of a linguistic generalization is simple, but underspecified, and that general principles of communication may be used to resolve the precise meaning in context.
+-->
+<!-- This theory inherently relies upon measurable quantities (i.e., prevalence) but situates it within a Bayesian agent with potentially structured prior knowledge, providing a bridge to conceptual theories.
+-->
+<!-- We find that this formalism (and not simpler ones) explains all three empirical puzzles. -->
+
+<!-- When interpretations are compared directly against truth conditions (i.e., how prevalent a property would need to be for the generic to be true),  -->
+
+<!-- Three empirical phenomena make generalizations in language difficult to formalize. -->
+<!-- The conditions under which a generalizations becomes "true" are variable: -->
+
+<!-- Existing work in both adults and children suggests that choosing to communicate a generalization can be used to exagerate evidence [@Cimpian2010; @Brandone2014]. -->
+
+<!-- In addition to having manifold interpretations, what makes linguistic generalizations true or false (i.e., their truth conditions) is also a mystery. -->
+<!-- The statement *Birds lay eggs* is true even though only about half of them do (namely, the females). -->
+<!-- Half of birds are also female, and yet *Birds are female* sounds like a strange thing to say. -->
+<!--  while *Canadians are right-handed* is also weird, even though the vast majority of them are.  -->
+
+## Experiment 1a: Measuring the Prevalence Prior for Categories
 
 The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, imagine your favorite kind of animal.
-Then answer, "what percentage of that kind of animal is female?".
+To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are on an alien planet and you come across your favorite kind of animal from Earth.
+Now try to predict whether or not that animal is female.
+To get an intuition for your subjective probability, ask yourself "What percentage of that kind of animal is female?".
 The answer is probably 50\%. 
-Then ask yourself, "what percentage of that kind of animal lays eggs?".
-Depending on what animal you thought of, the answer is probably either 50\% or 0\% (e.g., lions, tigers, and bears each have 0\% egg-laying members).
-
-This decomposition of the prevalence prior $P(h)$ into a kind prior $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
+Now try to predict whether or not that animal lays eggs (or, "What percentage of that kind of animal lays eggs?").
+Depending on what your favorite animal is, the answer is probably either 50\% or 0\% (e.g., if your favorite animal is a dog, there is a 0\% chance that it lays eggs)^[
+The subjective probability may, in fact, be non-zero but very small.
+This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with the alien environment.
+].
+
+This decomposition of the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
 We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
@@
 
-#### Method
-
-##### Participants
+### Method
+
+#### Participants
 
@@
 
-##### Procedure and materials
+#### Procedure and materials
 
 On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories (randomly sampled from a set corresponding to the generic sentences used in Expt.
+Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt.
 1b (e.g.
@@
 In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
-For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix).
+<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
 The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.
@@
 
-We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
-We formalize this hypothesis using a simple, Bayesian mixture model. 
+To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
+In analyzing the prevalence prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
+We formalize this hypothesis using a simple Bayesian mixture model. 
 We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
-The "unstructured", alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.
-
-For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
+The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.
+
+For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
 The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
-We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
-The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
+We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
+Note that we use the alterantive mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
+The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
+]
+The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
 Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
@@
 ]
-Finally, we assume that these two components combine with some mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.^[
-We use the mean / concentration parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
-The shape parameterization can be recovered using: $\alpha = \gamma \cdot \delta; \beta = (1 - \gamma) \cdot \delta$.
-]
-The unstructured hypothesis only represents a single component in the prior distribution $P(d) = \text{Beta} (d \mid \gamma, \xi)$.
-
-We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account the flexibility of each model [@LW2014].
-We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\theta$):
+Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
+The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$.
+
+We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account model flexibility [@LW2014].
+We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\phi$):
 
 \begin{eqnarray}
-\theta & \sim & \text{Uniform}(0, 1) \\
+\phi & \sim & \text{Uniform}(0, 1) \\
 \gamma & \sim & \text{Uniform}(0, 1) \\
@@
 
-Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property has its own parameters).
+Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property's prevalence prior has its own parameters).
 
@@
 ```
+
 The Bayes Factor indicates the extent to which the data support one model over another.
-The overall Bayes Factor in terms of Structured Model (S) over the Unstructured Model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
+The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
 Indeed, the data strongly suggests the prevalence prior is structured.
 
-It is possible that the data is, in fact, more structured than our simple two-component model. 
+It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
 To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
 This is called the *posterior predictive distribution* and is an important step in model validation. 
-If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
+If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
 We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
-If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
-If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
+This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
+If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
+If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
 We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
@@
 ]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-We could fit a more complex model to this data (i.e., one with three mixture components); however, we retain the imperfect simpler model for data-analytic ease going forward.
+A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.
 
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density functions for prior distributions representing the prevalence of eight different features.
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the prevalence of eight different features.
 Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
@@
 
+### Discussion
+
+The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
+These distributions are structured and must be represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
+
+<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->
+
+If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
+For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
+
+A natural proposal is that endorsements for generic language have to do with cue validity.
+This possibility has been investigated empirically, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
+However, cue validity has some empirical and theoretical issues.
+Empirically, cue validity is not a necessary criteria for generic endorsement (e.g., *Dogs have four legs*).
+Theoretically, it's not obvious why cue validity would be part of the semantic content of generics.
+If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
+<!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
+<!-- ^[ -->
+<!-- As a simple demonstration, imagine we've just discovered a new kind of animal called a fep. -->
+<!-- It should be easy to estimate the prevalence of being female among feps (probably 50\%) even without any knowledge of feps.  -->
+<!-- However, if you learn in another context that a particular entity is green, it's impossible to estimate the cue validity of being green for feps -->
+<!-- that it's easy to estimate the prevalence of being female among  -->
+<!-- ] -->
+
+However, we shouldn't throw away the possibility that distributional information about the property is relevant. 
+The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of cue validity. 
+Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D_{stable}}$ and the transient cause distribution $\mathcal{D_{transient}}$).
+If there is a finite number of kinds in the prevalence prior for a feature, and one knows the prevalence of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the prevalence prior, in that it can be derived via Bayes' Rule:
+$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
+
+Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is not longer defined (or, it is zero for all kinds). 
+This is for the same reason that for a continuous probability distribution, the probability of any particular number is zero. 
+For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
+The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds}, but there are many kinds of birds and the feature is not particularly diagnostic for anyone of them. 
+At the same time, the mixture parameter for the distribution over the prevalence of "having wings" is still relatively small, since it represents information about the distribution and not one particular kind.
+This is an important point of departure in our work from previous work.
+
+<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
+<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
+<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
+<!-- However, cue validity requires knowledge of the target category $k$ -->
+
+<!-- For example, suppose there are 10 possible kinds and 3 of them belong the stable cause distribution and 7 belong to the transient cause distribution.  -->
+<!-- Say we observe the feature and want to know what the probability that the entity is of a particular kind that we know to be of the stable distribution.  -->
+<!-- If we know the prevalence given each distribution (i.e, $P(f \mid k_{stable})$ and $P(f \mid k_{transient})$). -->
+
+<!-- For simplicity, assume that each component corresponds to a single probability (i.e., a single prevalence value) as opposed to a distribution. -->
+<!-- Thus, $\mathcal{D_{stable}} = P(f \mid \mathcal{D_{stable}}) = p_{stable}$ -->
+
+<!-- $n_{stable} n_{transient}$ -->
+
+<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
+<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
+<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
+<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
+<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
 <!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
@@
 
-### Experiment 1b: Endorsing generic statements
+## Experiment 1b: Endorsing generic statements
 

### 2017-06-27 paper/comgen-paper.Rmd
integrate some of sophies feedback for intro

@@
 We acquire such *generalizations* early in life, simply by observing instances and drawing inductive inferences [@Baldwin1993; @Xu2008; @Dewar2010].
-Once learners have the capacity to infer the intention of others, social learning can dramatically faciliate inductive reasoning [@Csibra2009; @Tomasello1999; @Butler2012].
+Once learners have the capacity to infer the intention of other cooperative agents, social learning can dramatically faciliate inductive reasoning [@Csibra2009; @Tomasello1999; @Butler2012].
 At around the first birthday, a child's mind gains access to a new, human-unique source of data: language.
@@
 But language also has the ability to refer to *generalization itself*.
-At around the age of two and a half, children begin to understand that *generic language* (e.g., "Dogs bark") refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
-<!-- *Causal language*, expressing generalization beyond an individual causal event (e.g., "The block *makes* it [the machine] go."), faciliates more abstract forms of causal reasoning [@Bonawitz2010].
--->
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].
+Generic meaning, or *genericity*, can be observed in seemingly disparate kinds of linguistic devices [@Carlson1977; @Carlson1995].
+Speakers can talk about categories generically (*generic language*; e.g., *Dogs bark*), individual people in generalizations (*habitual language*; e.g., "Mary swims after work."), causal events in generalizations (*causal language*; e.g., "Drinking moonshine makes you go blind."), and people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+
+It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that such languge is central to the growth of conceptual knowledge [@Gelman2004].
+At around the age of two and a half, children begin to understand that *generic language* refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
+<!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
+<!-- Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. -->
 Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
-
-Generic meaning, or *genericity*, can be observed in seemingly disparate kinds of linguistic devices [@Carlson1977; @Carlson1995].
-Speakers can talk about individual people in generalizations (*habitual language*; e.g., "Mary swims after work."), individual causal events in generalizations (*causal language*; e.g., "Drinking moonshine makes you go blind."), and people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that such languge is central to the growth of conceptual knowledge [@Gelman2004] 
 It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].
@@
 
-Computational models of learning formalize the inferences derived from observations, explaining how children and adults generalize from sparse data [@Tenenbaum2011]. 
+The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011].
 Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
@@
 When we hear "Dogs bark", we may feel it's a universal statment as in *All* dogs bark.
-Yet, exquisitely well-trained dogs, among others, do not bark; the statement should signal something weaker like *Most* dogs bark.
+Yet, Basenji dogs are barkless^[
+http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
+]; the statement should signal something weaker like *Most* dogs bark.
 Indeed, many generalizations seem to have the quantificational force of *most*. 

### 2017-06-27 paper/comgen-paper.Rmd
tweaks to intro

@@
 -->
-Learning from language is helpful because many properties are costly to directly observe (e.g., being poisonous) or events statistically unlikely (e.g., observing lightning).
+Learning from language is important because many properties are costly to directly observe (e.g., being poisonous) or events statistically unlikely (e.g., observing lightning).
 Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
@@
 Generic meaning, or *genericity*, can be observed in seemingly disparate kinds of linguistic devices [@Carlson1977; @Carlson1995].
-Speakers can talk about categories generically (*generic language*; e.g., *Dogs bark*), individual people in generalizations (*habitual language*; e.g., "Mary swims after work."), causal events in generalizations (*causal language*; e.g., "Drinking moonshine makes you go blind."), and people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
-
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that such languge is central to the growth of conceptual knowledge [@Gelman2004].
-At around the age of two and a half, children begin to understand that *generic language* refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
+Speakers communicate generalizations about categories (*generic language*; e.g., *Dogs bark*), about individual people (*habitual language*; e.g., "Mary swims after work."), about causal events (*causal language*; e.g., "Drinking moonshine makes you go blind."), and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+
+It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995].
+Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and around the age of two and a half, children begin to understand that *generic language* refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
+Because of its powerful implications, generalizations in language are thought to be central to the growth of conceptual knowledge [@Gelman2004].
 <!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
-<!-- Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. -->
 Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
@@
 
-The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011].
-Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
-Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000].
-Probabilistic models have recently made progress in describing pragmatic language understanding in precise terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
-These models of rational communication describe inferences one can draw from language about *particular* situations: utterances that convey information about a specific entity or event.
-The language of generalizations --- statements that extend beyond the here-and-now --- has heretofore eluded precise formalization.
-
-The major issue in formalizing genericity is determining what makes statements that convey generalizations true or false. 
-When we hear "Dogs bark", we may feel it's a universal statment as in *All* dogs bark.
+Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
+Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
+Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
+<!-- The language of generalization is exceedingly difficult to formalize, however. -->
+<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
+<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
+-->
+<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->
+
+The major issue in formalizing genericity is determining what makes such statements true or false. 
+When we hear "Dogs bark", we may feel it's a universal statment, like *All* dogs bark.
 Yet, Basenji dogs are barkless^[
 http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-]; the statement should signal something weaker like *Most* dogs bark.
+]; the generalization instead should signal something weaker like *Most* dogs bark.
 Indeed, many generalizations seem to have the quantificational force of *most*. 
 But most mosquitos do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
-The only quantifier that would permit such a generalization would be "Some" (e.g., *some mosquitos carry malaria*).
+The only quantifier that would permit such a statement would be "Some" (e.g., *some mosquitos carry malaria*).
 But equating the generalization with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
-Perhaps we should make exceptions for properties that only apply to one gender, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
-
-In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to define the truth conditions of generalizations in language. 
-By formalizing such a hypothesis in a probabilistic language understanding model, we can derive predictions for endorsements of such statements by specifying relevant prior knowledge in the model.
+One might feel exceptions should be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
+
+In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to articulate a formal theory of the truth conditions of generalizations in language. 
+By formalizing this semantic hypothesis in a pragmatic language understanding model, we derive predictions for the endorsements of such statements which we show to depend in systematic ways on relevant prior knowledge.
 Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
@@
 We do this in three domains: generalizations about categories, events, and causes. 
-In each domain, we define a scale that corresponds to the relevant metric by which a learner should generalize. 
 We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fall short.
@@
 Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments the measure both (i) and (ii) and relate them to the endorsements of generalizations about categories, or *generic language*. 
-In Section 4, we describe experiments that measure (i) and manipulate (ii) to predict endorsements of generalizations about events, or *habitual language*.
-In Section 5, we describe experiments that manipulate both (i) and (ii) to predict endorsements of generalizations about causes, or *causal language*. 
+In Section 3, we describe experiments the measure both quantities and relate them to the endorsements of generalizations about categories, or *generic language*. 
+In Section 4, we describe experiments that manipulate the speaker's intended message in communicating generalizations about events, or *habitual language*.
+In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's intended message in communicating generalizations about causes, or *causal language*.
 Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
 In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
-Our theory also opens up a number of new directions for understanding generic language and building models that learn from language like people.
+Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language like people.
 

### 2017-06-27 paper/comgen-paper.Rmd
edits to model section; up to predictions

@@
 
-Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
+Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
 Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
@@
 
-# The Bayesian Framework for Generalizations
+# A Formal View of Generalization
 
@@
 To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
-The linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
+This is faciliated through the use of labeling; the linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
 To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
 That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
-We call this kind of statement a *particular*.
+We call this latter kind of statement a *particular*.
 
@@
   f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
-) #%>% xtable(., 
- #        caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
-  #       label = c("tab:genpart"))
-
-apa_table(df.tab, 
-          caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
-          escape = TRUE, small = TRUE
-)
-
-#print(df.tab,  type = "latex", tabular.environment = "tabularx", width = "\\textwidth",  include.rownames = FALSE, comment = F)
-```
-
-Particular statements can be made about objects, events, and causes.
-We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
+) %>% xtable(.,
+         caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
+        label = c("tab:genpart"))
+
+# apa_table(df.tab, 
+#           caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
+#           escape = TRUE, small = TRUE
+# )
+
+print(df.tab, type = "latex", 
+      tabular.environment = "tabularx", width = "\\textwidth",
+      scalebox='0.75',
+      include.rownames = FALSE, comment = F)
+```
+
+Particular statements can be made about objects, events, and causes (e.g., "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind.").
 To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
 We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
-Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).
+Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
 
 Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
-For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
+For properties among instances of a category (e.g., being friendly among dogs), we can describe this inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
 With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
@@
 <!-- In the study of categories and properties, $x$ is an object. -->
-For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
+For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
 <!-- In this case, $x$ is a instance of an agent. -->
-Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$, known as causal power: $h = P(x \in e \mid x \in c)$.
-Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
+Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
+Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency of some instance in a category.
 <!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->
@@
 As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the friendliness of dogs.
+If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).
 
@@
 This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
-Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent, which is predicted assuming the data-generating process (i.e., the likelihood function) is another agent [@Goodman2009].
+Observations that are generated by an intentional agent can similar lead to subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].
 
@@
 
-# Communicating Generalizations with a Formal Model
+# Formalizing Generalizations in Language
 
 We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
-Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly").
+Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly").
 Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .
@@
 These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+**Conceptual accounts** of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as a special way of expressing mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
 From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
@@
 
-The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
+The *generics as default* view argues that general cognitive principles explain why certain generics are true or not.
 *Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
@@
 Yet, generics are not limited to conveying rich relations. 
-Arbitrary relations can also be expressed such as *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
+Arbitrary relationships can also be expressed (e.g., *Barns are red*; *Ravens are bigger than toasters*) which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
 The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
-How do we make sense of this panoply of conditions?
-Is there some more general, unified principle that explains what makes generic statements true or false?
-
-Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
-The basic currency of inference in these models is probability.
-In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
-If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
+It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
+This diversity is interested, but what is common across generics?
+Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false?
+
+We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction.
+We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities. 
+Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
+Thee basic currency of inference in these models is probability.
+In generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
+<!-- In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability. -->
+<!-- If that's true, a simple, semantic theory  -->
 
@@
 What threshold $\theta$ should be used for the generic generalization?
-We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
-In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
-We assume this prior is uninformed: $P(\theta) = \text{Uniform}(0, 1)$.
+
+To answer this, we draw a metaphor to Bayesian statistics and data analysis.
+When there is a latent parameter the Bayesian scientist doesn't know much about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
+In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$ (in the form of a prior distribution $P(\theta)$) and infers $\theta$ in context (i.e., after having heard the utterance).
+Though it's possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across context and is completely uninformed: $P(\theta) = \text{Uniform}(0, 1)$.
 
@@
 We term this prior distribution the *prevalence prior*.
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
+$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances described above.
 
@@
 This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
-Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq.
+Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
 \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
@@
 
-The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
+The intuition behind the model's behavior can be gleaned by imagining what the listener $L$ would believe with different thresholds and averaging over those possibilities.
 If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
@@
 When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
-When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.
-
-In this paper, we are interested in explaining the variable endorsements of generalizations based on some known or believed probability $h$.
+When the listener averages over these possibilities, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.
+
+In this paper, we are interested in explaining the variable endorsements of generalizations (e.g., *Birds lay eggs* is good; *Birds are female* is not) based on some known or believed probability $h$ (e.g., only female birds lay eggs).^[
+A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that she is trying to communicate.
+Rather, the speaker may have a belief distribution over $h$ for the category. $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
+In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution: 
+$S_{belief}(u \mid k) \propto \exp{(\lambda = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
+]
 Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
@@
 Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
+Since the speaker $S$ doesn't know the threshold $\theta$, she must integrate over the likely values that the listener will infer.
+
 The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
 To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
-with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
+with just two alternatives (say the utterance vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
 Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
@@
 \delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
-1 &\text{for all h}\ 
+1 &\text{for all h}
 \end{cases}
@@
 
-Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[
-A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate.
-Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind. 
-In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution: 
-$U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
-]
-
 The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
-This *simple but underspecified* hypothesis defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix A.
+This *simple but underspecified* hypothesis defines a *class* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
+We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix.
 

### 2017-06-27 paper/comgen-paper.Rmd
edits to model prediction section

@@
 The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
-This *simple but underspecified* hypothesis defines a *class* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix.
+The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
+These are not of primary theoretical interest to this paper, as *any* formal model that explains the very flexible endorsement patterns of generalizations in language will be a substantial contribution.
+However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
+We discuss these alternative formulations and provide formal model comparison between these RSA models in Appendix.
 
@@
 
-All models were implemented in the probabilisitic programming language WebPPL [@dippl], and a complete, runable versions of the models in the following section can be found at \url{http://forestdb.org/models/generics.html}
+All models were implemented in the probabilisitic programming language WebPPL [@dippl].
+The following simulations were implemented in the Rmarkdown document that generated this paper text and figures, using the R package RWebPPL.
 
 The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon a listener's *a priori* beliefs about the probabilty in question $P(h)$.
-For purposes of illustration, we present present the listener $L$ interpretations of the generalization for the underspecified threshol model as well as a fixed threshold model where the threhsold is set to the lowest possible value, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+For purposes of illustration, we present present the listener $L$ interpretations of the generalization for the underspecified threshold model as well as a fixed threshold model where the threhsold is set to the lowest possible value, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
 
 Above, we described the intuition for how an underspecified threshold interacts with a uniformly uncertain belief about the probability $h$.
-Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
-Note that our model of endorsements is a model of a speaker who decides whether or not to say the generic or stay silent. 
-Qualitatively speaking, model predictions for endorsement can be gleaned by comparing the posterior distribution over the probability $h$ upon hearing the generalization with the prior distribution over $h$ (which is the same as the listener's posterior upon hearing "silence").
-For different degrees of target probability $h$ that the speaker wants to communicate, the generalization will be more or less good at communicating it.
+Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
+Note that our model of endorsements is a model of a speaker who decides whether or not to say the generic to the listener or to stay silent. 
+Qualitatively speaking, model predictions for endorsement can be read off Figure \ref{fig:simulations} by comparing the posterior distribution over the probability $h$ upon hearing the generalization with the prior distribution over $h$ (which is the same as the listener's posterior upon hearing "silence").
+The speaker decides, for the degree of target probability $h$ that she seeks to communicate, will the generalization be better than nothing?
 
 In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
-Here, we posit the prior is bimodal with peaks near 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have $h \sim 0$) and for those that do have members that bark, many of them bark (i.e., have some high $h$).
+Here, we posit the prior is bimodal with peaks near 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and for those that do have members that bark, many of them bark (i.e., have some high $h$).
 <!--  -->
@@
 Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
-The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than with "barks" prior: The listener thinks that about 50% of robins lay eggs.
+The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than the "barks" prior: The listener thinks that about 50% of robins lay eggs.
 Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
@@
 In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content. 
+In the case of "lays eggs", the utterance carries a lot of information (relative to the prior).
 
 Finally, we look at how a listener would interpret the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-Indeed, we see that for the prior over "carries malaria", which *a priori* assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread, the listener's posterior upon hearing the generalization is similar to what she learns about hearing "Some mosquitos carry malaria".
+Indeed, we see that for the prior over "carries malaria"---which *a priori* assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread---the listener's posterior upon hearing the generalization is similar to what she learns about hearing "Some mosquitos carry malaria".
 Thus, a speaker who believes "some but very few" mosquitos carry malaria will still endorse the generalization.

### 2017-06-27 paper/comgen-paper.Rmd
edit intro to generics section

@@
 The following simulations were implemented in the Rmarkdown document that generated this paper text and figures, using the R package RWebPPL.
+That document, as well as the other models, analysis, data and experiments used in this paper can be found at \url{https://github.com/mhtess/comgen-paper}.
 
@@
 Generalizations about categories (i.e., *generic language*; e.g., *Birds fly.*) have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
-It is the premier case study of generalizations in language and has received the most attention from philosophers, linguists, and psychologists.
+It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., *Most birds fly*) and has received the most attention from philosophers, linguists, and psychologists.
 
@@
 As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs.
-"Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties.
-We do this by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
+"Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties, as explored through simulation in the **Model predictions** section.
+We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
 \ref{eq:L0} as well as the target-category prevalence $h$ that the speaker model seeks to convey in Eq.
@@
 In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
-*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasda2013] can be observed in the prevalence prior.
-If, in fact, the prevalence prior is one manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively modes or components of the prior, the results of the different types of kinds with respect to the property.
-This is important because it is one way in which our formal theory connects to other, informal psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
+*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the prevalence prior.
+If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
+This is important because it is one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
 As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
@@
 
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = F}
+```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
 m.cas.fullmodel.prior.parameters <- m.cas.samp %>%

### 2017-06-28 paper/comgen-paper.Rmd
habituals priors analysis and figure

@@
 
-In this paper, we are interested in explaining the variable endorsements of generalizations (e.g., *Birds lay eggs* is good; *Birds are female* is not) based on some known or believed probability $h$ (e.g., only female birds lay eggs).^[
-A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that she is trying to communicate.
+In this paper, we are interested in explaining the variable endorsements of generalizations (e.g., *Birds lay eggs* is good; *Birds are female* is not) based on some known or believed probability $h$ (e.g., only female birds lay eggs).^[A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that she is trying to communicate.
 Rather, the speaker may have a belief distribution over $h$ for the category. $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
 In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
-$S_{belief}(u \mid k) \propto \exp{(\lambda = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
+$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
 ]
@@
 Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-This corresponds to the more general form of the model described in **Alternative Formulations** section. 
+This corresponds to the more general form of the model described in a footnote in the model section. 
 With these data, the predictions of these two models are nearly identical.
@@
 By measuring listeners' prior beliefs about the prevalence of the property across kinds and the prevalence of the target kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical claim is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
+The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
 The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
@@
 Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013].
+<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
 @McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
@@
 
-From a methodological standpoint, habituals are a particularly amenable domain to manipulating the target propensity that a speaker aims to communicate.
-People are often in the situation of being introduced to new people and learning new information about them.
-In addition, the propensity information can be expressed in an easily-interpretable frequency with which a person does an action (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-While target probability can be manipulated for generalizations about categories (generic language) (e.g., by stating the prevalence of feature in a kind), this may interact with domain knowledge in complex ways (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
+From a methodological standpoint, habituals are a domain particularly amenable to manipulating the target propensity that a speaker aims to communicate.^[
+While target probability can be manipulated for generalizations about categories (generic language) (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what prevalence values are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
 ]
-In our first experiment concerning habitual language, we manipulate the target frequency as well as the kind of event (Expt.
-2b), creating a data set of endorsements that is three times as large as the data from Expt.
-1b (generic endorsement).
-To measure participants' latent prior belief distribution over the frequencies of people doing various actions (e.g., how often people *run*; Expt.
-2a), we take advantage of the structured representation discovered in Expt.
-1a, and learn about the prior by asking questions about the parameters of this model.
-In addition to directly manipulating the target propensity, these experiments provide the first test of the generality of our theory, that it can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect expectations, not merely observations. 
+First of all, because of the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
+In addition, propensity information of people doing actions can be expressed in an easily-interpretable frequency (e.g., "Last month, Mary smoked cigarettes 3 times.").
+
+We follow the same general experimental structure as in Experiment 1. 
+First, we measure the prior distribution over the frequency of events, for different kinds of events (Expt. 2a).
+We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
+Then, we test endorsements of habitual sentences, manipulating the actual frequency with which a person does an action (Expt. 2b).
+In addition to directly manipulating the target propensity, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
+
+Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
 Up to this point, we have been relatively agnostic as to the interpretation of $h$, the target propensity that the speaker aims to convey.
-In our first investigation of the degree scale, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive probability that this event will occur in the near future (e.g., how likely it is that Mary will smoke next week)?
-In Expts.
-3a \& 3b, we show that $h$, the target of communication, is a speaker’s prediction about the future frequency of action, and not past frequency, tying the phenomenon of *genericity* even more to subjective beliefs.
+In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive probability that this event will occur in the near future (e.g., how likely it is that Mary will smoke next week)?
+We do this by measuring particpants predictions about future frequency in situations where there are causal forces enabling or preventing the action (Expt. 2c). 
+We separately measure endorsements under the same contexts (Expt.
+2d) and use the prediction measurements (Expt.
+2c) as the target propensity $h$ that the speaker model is trying to communicate in order to predict habitual endorsements.
+To anticipate our results, we find that only a model that uses *predictive frequency* as the object of communication is able to predict the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
 
@@
 
-## Experiment 2: Endorsing generalizations about events
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the frequency of events, for different kinds of events.
-Then, we test endorsements of habitual sentences, manipulating the actual frequency with which a person does an action.
-
-### Experiment 2a: Measuring the propensity prior for event knowledge
-
-In this experiment we elicit the prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements.
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with a different frequency.
+## Experiment 2a: Measuring the propensity prior for event knowledge
+
+In this experiment we elicit the prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
+For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with some frequency.
 To better understand what frequencies should be expected for different actions, we took advantage of the 
@@
 
-For the case of background knowledge over the frequency with which people do actions, we consider again two components.
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action (expected frequency: once every hundred years). 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.^[
+For the case of background knowledge over the frequency with which people do actions, we consider again two components.^[
 In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
@@
 ]
-
-#### Method
-
-##### Participants
+To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
+The second component represents the frequencies of the event among the people who have not done the action before. 
+We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
+In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
+
+### Method
+
+#### Participants
 
@@
 
-##### Materials
+#### Materials
 
@@
 
-##### Procedure
+#### Procedure
 
@@
 
+```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
+
+example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
+                       "climbs mountains", "hikes", "runs", 
+                       "wears a suit", "wears a watch", "wears socks", 
+                       "writes poems", "goes to the movies", "plays the banjo"
+                       )
+
+rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
+  filter(Parameter == "mean") %>%
+  group_by(Variable, Gender, item) %>%
+  summarize(MAP = estimate_mode(value),
+            cred_upper = hdi_upper(value),
+            cred_lower = hdi_lower(value)) %>%
+  ungroup()
+rs.habituals.bda.prior.summary.wide <- left_join(
+  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
+    select(-Variable) %>%
+    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
+  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
+    select(-Variable) %>%
+    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
+)
+
+figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
+          d.hab.priors %>% select(item, category)) %>%
+ggplot(.,
+       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
+            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
+             fill = category))+
+    scale_shape_manual(values=c(21,22))+
+  #scale_color_solarized()+scale_fill_solarized()+
+  scale_fill_brewer(palette='Set1')+
+
+  geom_point(size=4, inherit.aes = F, 
+             aes(x = mix_mean,y = sfreq_mean,  fill = category,
+            shape = Gender),  alpha = 0.9)+
+  geom_errorbar(alpha = 0.5)+
+  geom_errorbarh( alpha = 0.5)+
+  xlab("% of Americans who have DONE ACTION")+
+  ylab("Log Frequency of DOING ACTION")+
+  #scale_
+  coord_fixed(ratio = 1/8)+
+  theme(legend.title = element_text(hjust=0),
+        legend.position="bottom",
+        legend.direction="horizontal") +
+        scale_y_continuous(limits = c(-1.5, 6.5), 
+                     breaks = c(0, 2.5, 4, 5.9),
+                     labels = c("annually", "monthly", "weekly", "daily"))+
+  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
+                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
+                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
+```
+
 ```{r habituals-prior-model-forwardSample}
@@
 
-```{r habituals-prior-fig, fig.width = 9, fig.height = 6, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
+```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
 2a).
@@
 
-bind_rows(
+figure.habituals.priors.marginals <- bind_rows(
   d.hab.priors.samples %>% 
@@
   ) %>%
-ggplot(. , aes( x = val, color = src))+
+  filter(item %in% example.habituals,
+         src == 'model') %>%
+  mutate(item = factor(item, levels = example.habituals)) %>%
+ggplot(. , aes( x = val, color = gender))+
   geom_density(size = 0.8, aes( y = ..scaled.. ))+
@@
   ylab("Scaled prior density")+
-  scale_x_continuous(limits = c(-5,10)) +
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
   theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.95, 0.075),
+        legend.position = c(0.9, 0.12),
         axis.text.x = element_text(angle = 90))+
@@
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
+```
+
+```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Propensity priors for events (Expt.
+2a).
+Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
+Right: Reconstructed priors on frequency from the structured, prior elicitation task.
+Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
+grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
 ```
@@
 
-#### Data analysis and results
+### Data analysis and results
 
@@
 
-#### Behavioral results
-
 On each trial of the experiment, the participant was told a person did a particular action 3 times during some time window. 
-A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one. 
+A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
 Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements.
@@
 Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:tjScatters} (left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency.
+First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
 It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (log frequency $\sim$ -1; 3 times in a 5-year interval; e.g.
@@
 
-We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.~1) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
+We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.
+2a) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
 Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
@@
 
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
+```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
 figure.causals.endorsement <- bind_rows(

### 2017-06-29 paper/appendix-fullModelPosteriors.Rmd
incorporate final? generics bda results into paper and appendix

@@
 
-```{r}
-m.samp <- fread(
-  paste(project.path,"models/generics/results/", 
-        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain2.csv",
-        sep = "")
-  ) %>% mutate(chain = 1)
+```{r gen-loadModels, eval = F}
+n_chains <- 3
+n_samples <- 100000
+burn <- n_samples / 2
+lg <- 20
+
+model_prefix <- "results-generics-jointModel-S1-smntcs_"
+
+m.samp <- data.frame()
+m.samp.fixed <- data.frame()
+for (i in seq(1, n_chains)){
+  mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+
+  mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
+                    n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
+  m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
+
+  #print(i)
+}
 ```
-
-### Parameter posteriors
 
@@
 
-```{r}
+```{r gen-speakeropt}
 m.samp %>% 
@@
 
-```{r}
+```{r gen-prev-loadData}
 d.prior <- read.csv(paste(project.path, data.path, 
@@
 
-Forward sample Target Prevalence from posterior on parameters
-```{r}
+```{r gen-prev-forward}
+#Forward sample Target Prevalence from posterior on parameters
 m.samp.prev.params <- m.samp %>%
@@
 
-```{r fig.width = 6, fig.height = 6}
+#### Target prevalence
+
+##### Full distributions
+
+```{r gen-prev-dists, fig.width = 8, fig.height = 6}
 bind_rows(
@@
 ggplot(. , aes( x = prevalence, color = src))+
-  geom_density(size = 1.1, aes( y = ..scaled.. ))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
+  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+   #              position = position_dodge())+
   facet_wrap(~Property + Category)+
   scale_color_solarized()+
-  scale_x_continuous(limits = c(0,1)) +
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
   theme(strip.text.y = element_text(angle = 0))
@@
 
-```{r}
+##### Means and CIs
+
+```{r gen-prev-means}
 # joint model inferred prevalence 
@@
 
-```{r eval = F}
+##### Does posterior on target prevalence predict generic endorsement?
+
+```{r gen-prevalence-vs-endorsement}
 left_join(
@@
 
-Forward sample from posterior on parameters
-```{r}
-
+```{r gen-prevprior-forward}
+#Forward sample from posterior on parameters
 m.samp.prior.params <- m.samp %>%
@@
     rowwise() %>%
-    mutate(isPresent = rbinom(1, 1, prob = isPresent_na),
+    mutate(isPresent = rbinom(1, 1, prob = mixture_NA),
        prevalence = ifelse(isPresent == 1, 
                            rbeta(n = 1, 
-                                 shape1 = prevalenceGivenPresent_mean* prevalenceGivenPresent_sampleSize,
-                                 shape2 = (1-prevalenceGivenPresent_mean)*prevalenceGivenPresent_sampleSize),
+                                 shape1 = stableFreq_mean* stableFreq_sampleSize,
+                                 shape2 = (1-stableFreq_mean)*stableFreq_sampleSize),
                            rbeta(n = 1,
@@
 
-Marginal distributions on prevalence
-```{r fig.width = 8, fig.height = 5}
+##### Marginal distributions on prevalence
+
+```{r gen-prevprior-marginals, fig.width = 8, fig.height = 5}
 bind_rows(
@@
 ggplot(. , aes( x = prevalence, color = src))+
-  geom_density(size = 1.1, aes( y = ..scaled.. ))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
   facet_wrap( ~ Property, nrow = 3)+
   scale_color_solarized()+
-  scale_x_continuous(limits = c(0,1)) +
+  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
   scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
@@
 
-CDFs
+##### Cumulative Density Functions
 
-```{r fig.width = 8, fig.height = 5}
-
+```{r gen-prevprior-cdf, fig.width = 8, fig.height = 5}
 bind_rows(
@@
 
-```{r}
-m.gen.somemodel.endorsement <- fread(
-  paste(project.path,"models/generics/results/", 
-        #"results-fullModel-s1-smtncssome-20000_burn10000_chain1.csv", 
-        "results-fullModel-s1-lowestTheta-smtncssome-1000_burn500_lag10_chain1.csv",
-        sep = "")
-  ) %>% mutate(chain = 1) %>%
-  filter(type == 'predictive') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
+### Fixed threshold model

### 2017-06-29 paper/comgen-paper.Rmd
incorporate final? generics bda results into paper and appendix

@@
 
-write.csv(
-  left_join(
-  d1 %>%
-    mutate(sentence = as.character(sentence),
-           sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)),
-  unique(d2 %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-    select(Category, Property, sentence))
-), file = paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""), row.names = F)
+# write.csv(
+#   left_join(
+#   d1 %>%
+#     mutate(sentence = as.character(sentence),
+#            sentence = gsub('&quotechar', '', sentence),
+#          sentence = gsub('lyme', 'Lyme', sentence)),
+#   unique(d2 %>%
+#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
+#     select(Category, Property, sentence))
+# ), file = paste(project.path, "data/generics/endorsement/",
+#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
 ```
@@
 ```{r generic-RSAmodels, fig.width = 8}
-# n_chains <- 1
-# n_samples <- 50000
-# burn <- n_samples
-# 
-# model_prefix <- "results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-"
-# 
-# m.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/generics/results/", model_prefix, 
-#                     n_samples, "_burn", burn, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.samp <- bind_rows(m.samp, m.samp.i)
-#   #print(i)
-# }
-
-m.samp <- fread(
-  paste(project.path,"models/generics/results/", 
-        "results-generics-jointModel-S1-smtncs_generic-25000_burn12500_lag20_chain2.csv",
-        sep = "")
-  ) %>% mutate(chain = 1)
-
-m.gen.somemodel.endorsement <- fread(
-  paste(project.path,"models/generics/results/", 
-        #"results-fullModel-s1-smtncssome-20000_burn10000_chain1.csv", 
-        "results-fullModel-s1-lowestTheta-smtncssome-1000_burn500_lag10_chain1.csv",
-        sep = "")
-  ) %>% mutate(chain = 1) %>%
-  filter(type == 'predictive') %>%
+n_chains <- 3
+n_samples <- 100000
+burn <- n_samples / 2
+lg <- 20
+
+model_prefix <- "results-generics-jointModel-S1-smntcs_"
+
+m.samp <- data.frame()
+m.samp.fixed <- data.frame()
+for (i in seq(1, n_chains)){
+  mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+
+  mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
+                    n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
+  m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
+
+  #print(i)
+}
+
+m.gen.somemodel.endorsement <- m.samp.fixed %>%
+  filter(type == 'endorsement') %>%
   group_by(type, param, property, category) %>%
@@
 m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'predictive') %>%
+  filter(type == 'endorsement') %>%
   group_by(type, param, property, category) %>%
@@
   m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 3
+  "MAP", "MAP_h", sigfigs = 4
 )
@@
   m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 3
+  "MAP", "MAP_h", sigfigs = 4
 )

### 2017-07-01 paper/comgen-paper.Rmd
add table for habituals by gender

@@
 library(lme4)
+library(knitr)
 theme_set(theme_few())
@@
   spread(param, MAP) %>%
-  rename(mix = isPresent_na, 
-         stable_mean = prevalenceGivenPresent_mean, 
-         stable_concentration = prevalenceGivenPresent_sampleSize) %>%
+  rename(mix = mixture_NA, 
+         stable_mean = stableFreq_mean, 
+         stable_concentration = stableFreq_sampleSize) %>%
   mutate( a = stable_mean * stable_concentration, 
@@
 
-From the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
+Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
 That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
@@
 
-Some items show substantial differences between the genders (e.g. \emph{wears a bra}) and some show subtle differences (e.g. \emph{watches professional football}).
-Our prior distributions $P(h)$ are with respect to an alternative class of entities (e.g., other individuals). 
-It's possible that when evaluating habitual statements, $P(h)$ is with respect to either *all people* or *people of the same gender*. 
-For example, are the frequency conditions by which a man would qualify to "watch professional football" (habitually) different than those by which a woman would qualify to "watch professional football"?
-We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender.
+Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}).
+Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals). 
+It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*. 
+For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"?
+We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender.
 
@@
 6 of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who watched professional football).
-These were used for an exploratory analysis on gender differences.
+These were used for an exploratory analysis on differences in endorsements by gender of the target character.
 The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-2.html}.
@@
 
-On each trial of the experiment, the participant was told a person did a particular action 3 times during some time window. 
+#### Descriptive behavioral results
+
+On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
 A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements.
+Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action 3 times during some time window. 
 A more sophisticated alternative hypothesis is that the degree to which the habitual statement is good is the frequency itself. 
@@
 
-Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:tjScatters} (left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
+Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
 First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (log frequency $\sim$ -1; 3 times in a 5-year interval; e.g.
+It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g.
 \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
 We see in addition that even when actions are done relatively frequently (e.g.
-3 times in a one month interval; log frequency $\sim$ 5), some habitual sentences receive less than full endorsement (e.g.
+3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g.
 \emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval; log frequency $\sim$ 6.5) receive at a minimum 75\% endorsement, though there is still variability among them (e.g.
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g.
 between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the raw (log) frequency of action predicts only a fraction of the variability in responses ($r^2(93) = 0.33$).
+Overall, the raw log-frequency of action predicts only a fraction of the variability in responses ($r^2(93) = 0.33$).
 For actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(50) = 0.07$)
@@
 This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
+
+```{r habituals-endorsement-gender-exploration, results="asis"}
+gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
+                    "wears a bra", "wears a watch", "wears a suit")
+
+d.hab.bayes.gendered <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+left_join(
+    d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high,  -characterGender),
+  d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    #rename(male_MAP, male_low = low, male_high = high) %>%
+    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high, -characterGender)
+    #rename(female_MAP, female_low = low, female_high = high)
+) %>% xtable(.,
+         caption = c("Exploratory ananlysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
+        label = c("tab:habituals-endorsement-gender")) %>%
+print(., type = "latex", 
+      tabular.environment = "tabularx", width = "\\textwidth",
+      scalebox='0.75',
+      include.rownames = FALSE, comment = F)
+```
+
+For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
+Differences in endorsements would suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
+Endorsement probabilities and 95\% credible intervals for these six items for each gender are showed in Table \ref{tab:habituals-endorsement-gender}.
+Descriptively, we do not observe appreciate
 

### 2017-07-03 paper/comgen-paper.Rmd
change table to scatterplot, add text by gender habitual analysis

@@
 
-```{r habituals-endorsement-gender-exploration, results="asis"}
+```{r habituals-endorsement-gender-exploration-scatter, fig.cap="Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
+"John...") for six events that displayed appreciable differences in the prior elicitation.
+Labeled points all correspond to the time period of 3 times / month.}
+gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
+                    "wears a bra", "wears a watch", "wears a suit")
+
+d.hab.bayes.gendered <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender, time_period) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.bayes.gendered.wide <- left_join(
+    d.hab.bayes.gendered %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
+    select(-characterGender),
+  d.hab.bayes.gendered %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
+    select(-characterGender)
+)
+
+r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
+
+ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
+                 xmin = low_female, ymin = low_male,
+                 xmax = high_female, ymax = high_male, fill = habitual))+
+  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
+                    filter(time_period== "month"), aes(label = habitual,
+                                                       color = habitual),
+                  force = 3, nudge_x = -1, segment.size = 0.3)+
+  guides(fill = F, color = F)+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_point(shape = 21)+
+  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+  coord_fixed()+
+  xlab("Habitual endorsement (female character)")+
+  ylab("Habitual endorsement (male character)")+
+  scale_fill_solarized()+
+  scale_color_solarized()
+
+```
+
+```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
@@
 ) %>% xtable(.,
-         caption = c("Exploratory ananlysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
+         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
         label = c("tab:habituals-endorsement-gender")) %>%
@@
 For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
-Differences in endorsements would suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
-Endorsement probabilities and 95\% credible intervals for these six items for each gender are showed in Table \ref{tab:habituals-endorsement-gender}.
-Descriptively, we do not observe appreciate
-
-We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$. 
-This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women). 
-Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
+Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
+Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
+We see no appreciable differences in endorsements for the two genders. 
+This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters.
+
+<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
+<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
+<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
 

### 2017-07-03 paper/comgen-paper.Rmd
add errorsbars to habituals regression model plots

@@
 
+```{r}
+d.gen.endorse.regression.prevalence <- left_join(
+  d.gen.endorse.bayes,
+  d.gen.endorse.prev.cue.uniq %>%
+    mutate(
+      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
+      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
+      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
+    ) %>%
+    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
+) %>% mutate(
+  sqErr = (MAP_h - prediction_mean) ^ 2
+)
+
+d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
+  d.gen.endorse.bayes,
+  d.gen.endorse.prev.cue.uniq %>%
+    mutate(
+      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
+      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
+      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
+      sentence = paste(Category, " ", Property, ".", sep = "")
+      )
+) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
+
+d.gen.endorse.regression <- bind_rows(
+  d.gen.endorse.regression.prevalence.cuevalidity %>%
+    mutate(src = "regression_Prev_Cuevalidity"),
+  d.gen.endorse.regression.prevalence %>% 
+    mutate(src = "regression_Prev")
+  )
+```
+
 ```{r habituals-regression-models}
@@
 
-d.hab.endorse.regression <- left_join(
+d.hab.endorse.freq.mix.uniq <- unique(select(
+    d.hab.endorsement, habitual, logAnnualRate, time_period, 
+    mixture, mix_low, mix_high
+  ))
+
+d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
+  select(-mixture) %>% 
+  rename(mixture = mix_low)
+
+d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
+  select(-mixture) %>% 
+  rename(mixture = mix_high)
+
+d.hab.endorse.regression.freq <- left_join(
   d.hab.endorsement.bayes,
-  unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, mixture
-  )) %>%
-    mutate(regression_freq = predict(glm.hab.endorse.freq, ., type = "response"), 
-           regression_freq_distinct = predict(glm.hab.endorse.freq.distinct, ., type = "response"))
-) %>%
-  gather(src, prediction, regression_freq, regression_freq_distinct) %>%
+  d.hab.endorse.freq.mix.uniq %>%
+    mutate(
+      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
+      prediction_lower = prediction,
+      prediction_upper = prediction,
+      src = "regression_freq"
+      )
+)
+
+# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
+d.hab.endorse.regression.freq.mix <- left_join(
+  d.hab.endorsement.bayes,
+  d.hab.endorse.freq.mix.uniq %>%
+    mutate(
+      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
+      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
+      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
+      src = "regression_freq_distinct"
+      )
+)
+
+d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
   mutate(sqErr = (MAP_h-prediction)^2)
@@
 habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression %>% 
-  mutate(prediction_lower = prediction,
-         prediction_upper = prediction),
+  d.hab.endorse.regression,
   left_join(
@@
   theme(legend.position = "bottom")
-
 ```

### 2017-07-03 paper/comgen-paper.Rmd
reorganize habituals analysis section to provide parallel to generics; codify some numbers

@@
 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:commongenerics}b, right).
+We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
 This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
@@
 Figure \ref{fig:priorScatter} (right) shows example inferred priors.
-
 Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}).
@@
 
-```{r}
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-```
+```{r habituals-endorsement-gender-exploration-scatter, fig.cap="Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
+"John...") for six events that displayed appreciable differences in the prior elicitation.
+Labeled points all correspond to the time period of 3 times / month.}
+gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
+                    "wears a bra", "wears a watch", "wears a suit")
+
+d.hab.bayes.gendered <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender, time_period) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.bayes.gendered.wide <- left_join(
+    d.hab.bayes.gendered %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
+    select(-characterGender),
+  d.hab.bayes.gendered %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
+    select(-characterGender)
+)
+
+r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
+
+ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
+                 xmin = low_female, ymin = low_male,
+                 xmax = high_female, ymax = high_male, fill = habitual))+
+  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
+                    filter(time_period== "month"), aes(label = habitual,
+                                                       color = habitual),
+                  force = 3, nudge_x = -1, segment.size = 0.3)+
+  guides(fill = F, color = F)+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_point(shape = 21)+
+  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+  coord_fixed()+
+  xlab("Habitual endorsement (female character)")+
+  ylab("Habitual endorsement (male character)")+
+  scale_fill_solarized()+
+  scale_color_solarized()
+
+```
+
+```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
+gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
+                    "wears a bra", "wears a watch", "wears a suit")
+
+d.hab.bayes.gendered <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+left_join(
+    d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high,  -characterGender),
+  d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    #rename(male_MAP, male_low = low, male_high = high) %>%
+    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high, -characterGender)
+    #rename(female_MAP, female_low = low, female_high = high)
+) %>% xtable(.,
+         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
+        label = c("tab:habituals-endorsement-gender")) %>%
+print(., type = "latex", 
+      tabular.environment = "tabularx", width = "\\textwidth",
+      scalebox='0.75',
+      include.rownames = FALSE, comment = F)
+```
+
+<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
+<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
+<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
 
@@
 )
+
+r2.hab.n <- length(r2.habituls.regression.freq$MAP_h)
+
+r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
+                                          "MAP_h", "prediction")
+
+mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
+                                          "MAP_h", "prediction")
+
+r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
+  filter(logAnnualRate < 1.1)
+
+r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
+
+r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
+                                          "MAP_h", "prediction")
+
+mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
+                                          "MAP_h", "prediction")
 
@@
 )
+
+r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
+                                          "MAP_h", "prediction")
+
+mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
+                                          "MAP_h", "prediction")
 
@@
 
-#### Descriptive behavioral results
-
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action 3 times during some time window. 
-A more sophisticated alternative hypothesis is that the degree to which the habitual statement is good is the frequency itself. 
-<!-- Our computational model predicts that the the degree to which the habitual statement is good is the frequency of event, normalized by the alternative possible frequencies under the prior. -->
-<!-- [MHT: SENTENCE ABOVE IS THE SOFT-SEMANTICS INTERPRETATION] -->
-
-Both of the simple alternative hypotheses can immediately be ruled by out by visual inspection of Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
+Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
+Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ.
+
+For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
+Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
+Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
+We see no appreciable differences in endorsements for the two genders. 
+This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters.
+For all remaining analyses, we collapse across character gender when analyzing endorsements.
+
+#### Frequency baseline
+
+The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is good is the frequency itself. 
+This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
 First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
@@
 between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the raw log-frequency of action predicts only a fraction of the variability in responses ($r^2(93) = 0.33$).
-For actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(50) = 0.07$)
+Overall, the raw log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
+In addition, for actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
 
@@
 
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap="Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
-r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
-Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
-Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
-We see no appreciable differences in endorsements for the two genders. 
-This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters.
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
+#### Frequency and distinctiveness
+
+FILL IN
+
+#### Fixed-threshold RSA model
+
+On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
+A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
+Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action 3 times during some time window.
+
+#### Uncertain-threshold RSA model
+
+We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.
+2a) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
+Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
+The model has two free parameters---the speaker optimality parameters, $\alpha_i$, in Eqs.~\ref{eq:S2} \& \ref{eq:S1}. 
+We use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.~2.
+To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
+The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6].
+%The MAP and HPD interval for the data-analytic guessing parameter is 0.004 [0.0003, 0.03], suggesting that there is not a substantial amount of the data that is better explained by a model of random guessing than by our pragmatic speaker model.
+
+As shown in Figure \ref{fig:tjScatters}, right, the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(93) = 0.94$), including actions done on the time scale of years or more  ($r^2(50) = 0.92$).
+The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.
+
+As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
+
+Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data.
 
@@
 <!-- \end{figure*} -->
-
-#### Model criticism and comparison
-
-We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
-The model has two free parameters---the speaker optimality parameters, $\alpha_i$, in Eqs.~\ref{eq:S2} \& \ref{eq:S1}. 
-We use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.~2.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6].
-%The MAP and HPD interval for the data-analytic guessing parameter is 0.004 [0.0003, 0.03], suggesting that there is not a substantial amount of the data that is better explained by a model of random guessing than by our pragmatic speaker model.
-
-As shown in Figure \ref{fig:tjScatters}, right, the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(93) = 0.94$), including actions done on the time scale of years or more  ($r^2(50) = 0.92$).
-The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.
-
-As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
-
-Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data.
 

### 2017-07-03 paper/comgen-paper.Rmd
analyze distinctivesness regression model on habituals and describe counterexamples

@@
 
-m.samp <- data.frame()
-m.samp.fixed <- data.frame()
-for (i in seq(1, n_chains)){
-  mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-
-  mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-                    n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-  m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-
-  #print(i)
-}
+# m.samp <- data.frame()
+# m.samp.fixed <- data.frame()
+# for (i in seq(1, n_chains)){
+#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+#   
+#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
+#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
+#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
+#   }
+# 
+# save(m.samp,
+#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# 
+# save(m.samp.fixed,
+#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
 
@@
 ) %>%
-  mutate(src = factor(src, levels = c( 
+  mutate(src = factor(src, levels = c( "some_model",
                                       "generics_model",
-                                      "some_model",
+
                                       "regression_Prev", 
@@
                                      ),
-                      labels = c(
+                      labels = c("Fixed semantics model",
                                  "Uncertain semantics model",
-                                 "Fixed semantics model",
-                                 "Prevalence alone", "Prevalence + Cue validity"
+
+                                 "Prevalence alone",
+                                 "Prevalence + Cue validity"
                                  ))) %>%
@@
 
+<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
+Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
+-->
+
 For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
@@
 
-FILL IN
+In the prior elicitation task (Expt.
+2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
+With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement.
+Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
+This is analagous to the regression model based on cue validity and prevalence in the domain of generics.
+
+```{r habituals-distinctiveness-counterexamples}
+
+format_endorsment_ci <- function(
+  df, estimate = "MAP_h", low = "low",
+  high = "high", sigfigs = 2){
+  return(paste(
+    round(df[[1,estimate]], sigfigs),
+    " [",
+    round(df[[1,low]], sigfigs),
+    ", ",
+    round(df[[1,high]], sigfigs),
+    "]", sep = ""))
+}
+
+movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
+
+movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
+                                                        time_period == "year"),
+                                                        estimate = "prediction",
+                                                        low = "prediction_lower",
+                                                        high = "prediction_upper")
+
+banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
+
+banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
+                                                        time_period == "2 years"),
+                                                        estimate = "prediction",
+                                                        low = "prediction_lower",
+                                                        high = "prediction_upper")
+```
+
+We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
+Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
+Still, this model is not able to capture some of the subtle sensitivities in endorsments.
+For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
+Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
+On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
+Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
 

### 2017-07-03 paper/comgen-paper.Rmd
analyze and discuss fixed and uncertain threshold models for habituals; fix knit

@@
 
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap="Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
+```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
 "John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.}
+Labeled points all correspond to the time period of 3 times / month.'}
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
@@
 
-r2.hab.n <- length(r2.habituls.regression.freq$MAP_h)
+r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
 
@@
 
+r2.habituals.rsa.fixed <- compute_r2(
+  m.hab.endorse.rsa %>% filter(src == "some_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.fixed <- compute_mse(
+  m.hab.endorse.rsa %>% filter(src == "some_model"),
+                                          "MAP_h", "MAP")
+
+r2.habituals.rsa.uncertain <- compute_r2(
+  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.uncertain <- compute_mse(
+  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
+                                          "MAP_h", "MAP")
+
+habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)
+
+r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)
+
+r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
+                                          "MAP_h", "MAP")
+
 habituals.endorsement.models <- bind_rows(
@@
   mutate(src = factor(src, levels = c( 
+                                      "some_model",
                                       "habituals_model",
-                                      "some_model",
                                       "regression_freq", 
@@
                       labels = c(
+                                 "Speaker model - fixed semantics",
                                  "Speaker model - uncertain semantics",
-                                 "Speaker model - fixed semantics",
                                  "Frequency alone", "Frequency + Distinctiveness"
@@
 
+The above regression models are too rigid to explain the flexibility in habitual endorsements. 
+Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
+Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
+To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
+
+We used the pragmatic speaker model $S_1$ (Eq.
+\ref{eq:S1}) with the priors elicited above (Expt.
+2a) to predict felicity judgments in Expt.
+2b, assuming the target propensity ($h$, to be conveyed by $S_1$) is the provided frequency (e.g., 3 times in the past year).
+Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
+The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
+As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
+2b.
+To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
+<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
+
 On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A simple null hypothesis is that habitual statements convey that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action 3 times during some time window.
+A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
+Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
+Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
+\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
+The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
+The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
+Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
 
@@
 
-We used the pragmatic speaker model $S_2$ (Eq.~\ref{eq:S2}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.~2, assuming the target propensity (to be conveyed by $S_2$) is the provided frequency.
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(\lambda)$ across individuals.
-The model has two free parameters---the speaker optimality parameters, $\alpha_i$, in Eqs.~\ref{eq:S2} \& \ref{eq:S1}. 
-We use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.~2.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6].
-%The MAP and HPD interval for the data-analytic guessing parameter is 0.004 [0.0003, 0.03], suggesting that there is not a substantial amount of the data that is better explained by a model of random guessing than by our pragmatic speaker model.
-
-As shown in Figure \ref{fig:tjScatters}, right, the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(93) = 0.94$), including actions done on the time scale of years or more  ($r^2(50) = 0.92$).
-The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.
-
-As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
-
-Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data.
+We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
+As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
+
+### Discussion
+
+<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
+
+<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
+-->
+
+<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
 

### 2017-07-03 paper/comgen-paper.Rmd
some discussion of habituals endorsement expts and model results

@@
 
+In Expt.
+2b, we manipulated the event type (e.g., drinks coffee vs.
+beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
+year) and measured the corresponding endorsements for habitual statements.
+We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
+
+Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
+The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
+This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
+
+Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
+People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
+By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
+The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
+
+This is particularly
+
 <!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->

### 2017-07-03 paper/comgen-paper.Rmd
small edits to predictive habituals expts

@@
 
-## Experiment 2b: Endorsing generalizations about events
+## Experiment 2b: Endorsing habitual statements
 
@@
 
-This is particularly
+In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
+This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
+Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
 
@@
 
-## Experiment 3: Communicating predictive propensities
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
+## Experiment 2c: Measuring predictive frequency
 
@@
 
-In this pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 3a, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 3b, we examine felicity judgments of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
+In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
+In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
+In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
 This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-### Experiment 3a: Prediction elicitation
 
@@
 
-#### Methods
+### Methods
 
@@
 Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to most intermediate endorsement of the habitual in Expt. 2b. 
+To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
 In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
@@
 
-#### Results
+### Results
 
@@
 
-### Experiment 3b: Felicity judgments
+## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
 
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiment 3, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-3a) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-3b).
+In Experiments 2c \& 2d, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
+2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
+2c).
 To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.

### 2017-07-04 paper/comgen-paper.Rmd
add support for saved habituals model results

@@
 			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:5, width: 1})
+			sigma: uniformDrift({a:0, b:10, width: 1})
 		},
@@
 			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:5, width: 1})
+			sigma: uniformDrift({a:0, b:10, width: 1})
 		}
@@
 ```{r habituals-fullmodel}
-n_chains <- 1
-n_samples <- 10000
-burn <- n_samples
-lg <- 5
-i <- 1
+n_chains <- 3
+n_samples <- 100000
+burn <- n_samples / 2
+lg <- 20
 model_prefix <- "results-habituals-jointModel-S1-"
 
-m.hab.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/habituals/results/", 
-                    model_prefix, "smtncs_habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i)
-  m.hab.samp <- bind_rows(m.hab.samp, m.samp.i)
-}
-
-n_chains <- 1
-n_samples <- 1000
-burn <- n_samples
-lg <- 5
-i <- 1
-m.hab.fixed.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/habituals/results/", 
-                    model_prefix, "smtncs_some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.samp.i <- mi %>% mutate(chain = i)
-  m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-}
+# m.hab.samp <- data.frame()
+# m.hab.fixed.samp <- data.frame()
+
+# for (i in seq(1, n_chains)){
+#   mi <- fread(paste(project.path,  "models/habituals/results/",
+#                     model_prefix, "smtncs_habitual-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
+# 
+#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
+#                     model_prefix, "smtncs_some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
+# 
+# }
+# 
+# save(m.hab.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# 
+# save(m.hab.fixed.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
 
@@
 
+Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
+With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
+Thus, this model makes the same predictions for different target frequencies in the same event.
+For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.
+
 #### Uncertain-threshold RSA model
@@
 
+```{r habituals-predictive-rsa}
+
+```
+
 ```{r habituals-predictive-figure, fig.cap="Left: Results of Expt 3a. Right: Results of Expt. 3b as they relate to the predicted frequencies from Expt. 3a"}
@@
 The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 3a.
-The only difference from Expt. 3a is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2).
+None of the participants had completed Expt. 2c.
+The only difference from Expt. 2c is the dependent measure. 
+On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
 The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
 
-#### Results
+### Results
 

### 2017-07-04 paper/appendix-fullModelPosteriors.Rmd
bayesian analysis of predictive elictation; intermediate model results for predictive hab; new figure for predictive hab

@@
 
-```{r gen-loadModels, eval = F}
+```{r gen-loadModels}
 n_chains <- 3
@@
 
-m.samp <- data.frame()
-m.samp.fixed <- data.frame()
-for (i in seq(1, n_chains)){
-  mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+# m.samp <- data.frame()
+# m.samp.fixed <- data.frame()
+# for (i in seq(1, n_chains)){
+#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+#   
+#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
+#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
+#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
+#   
+#   #print(i)
+# }
 
-  mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-                    n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-  m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
+load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
 
-  #print(i)
-}
+load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
 ```
@@
 ### Fixed threshold model
+
+#### Speaker optimality parameter
+
+```{r gen-fixed-speakeropt}
+m.samp.fixed %>% 
+  filter(type == "param") %>%
+  ggplot(., aes(x = val, fill = factor(chain)))+
+  geom_histogram(position = position_dodge())+
+  facet_wrap(~param + property, scales = 'free')
+```
+
+#### Posterior predictive distribution on target prevalence
+
+```{r gen-fixed-prev-forward}
+#Forward sample Target Prevalence from posterior on parameters
+m.samp.fixed.prev.params <- m.samp.fixed %>%
+    filter(type == "targetPrevalence") %>%
+    mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type) %>%
+    #mutate(item = paste(parameter, property, sep = "_")) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category"), sep= "_")
+
+m.samp.fixed.prevalence <- m.samp.fixed.prev.params %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+```
+
+#### Target prevalence
+
+##### Full distributions
+
+```{r gen-fixed-prev-dists, fig.width = 8, fig.height = 6}
+bind_rows(
+  d.prior %>% 
+  mutate(sentence = paste(Category," " ,Property, ".", sep = "")) %>%
+  filter(sentence %in% full_sentences) %>%
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+    select(-workerid, -trial_type),
+  m.samp.fixed.prevalence %>% 
+    select(property, category, prevalence) %>%
+    rename(Category = category, Property = property) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = prevalence, color = src))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
+  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+   #              position = position_dodge())+
+  facet_wrap(~Property + Category)+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+##### Means and CIs
+
+```{r gen-fixed-prev-means}
+# joint model inferred prevalence 
+m.samp.fixed.targetPrev <- m.samp.fixed.prevalence %>% 
+  group_by(category, property) %>%
+  summarize(MAP = estimate_mode(prevalence),
+          cred_upper = hdi_upper(prevalence),
+          cred_lower = hdi_lower(prevalence),
+          prevMean = mean(prevalence)) %>%
+  ungroup() %>% rename(Category = category, Property = property)
+
+left_join(d.prior.summary, 
+          m.samp.fixed.targetPrev) %>%
+  ggplot(., aes(x = prevMean, xmin = cred_lower, xmax = cred_upper,
+                y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0, 1))+
+  scale_y_continuous(limits = c(0, 1))+
+  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
+  coord_fixed()
+```
+
+##### Does posterior on target prevalence predict generic endorsement?
+
+```{r gen-fixed-prevalence-vs-endorsement}
+left_join(
+  d.gen.endorse.bayes,
+  m.samp.fixed.prevalence %>% 
+  group_by(category, property) %>%
+  summarize(MAP = estimate_mode(prevalence),
+          cred_upper = hdi_upper(prevalence),
+          cred_lower = hdi_lower(prevalence),
+          prevMean = mean(prevalence)) %>%
+  ungroup() %>% rename(Category = category, Property = property) %>%
+  mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
+) %>%
+  ggplot(., aes(x = prevMean, xmin = cred_lower, xmax = cred_upper,
+                y = MAP_h, ymin = low, ymax = high))+
+  geom_point()+geom_errorbar(alpha = 0.3)+ geom_errorbarh(alpha = 0.3)+
+  scale_x_continuous(limits = c(0, 1))+
+  scale_y_continuous(limits = c(0, 1))+
+  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
+  coord_fixed()
+```
+
+#### Posterior predictive distribution on prevalance priors
+
+```{r gen-fixed-prevprior-forward}
+#Forward sample from posterior on parameters
+m.samp.fixed.prior.params <- m.samp.fixed %>%
+    filter(type == "prior") %>%
+    mutate(parameter = paste(param, category, sep = "_")) %>%
+    select(-param, -category, -chain, -type) %>%
+    mutate(item = paste(parameter, property, sep = "_")) %>%
+    group_by(item) %>%
+    mutate(iteration = ave(item==item, item, FUN=cumsum)) %>%
+    ungroup() %>%
+    select(-item)
+
+  m.samp.fixed.prevalence.prior <- m.samp.fixed.prior.params %>%
+    group_by(parameter, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(isPresent = rbinom(1, 1, prob = mixture_NA),
+       prevalence = ifelse(isPresent == 1, 
+                           rbeta(n = 1, 
+                                 shape1 = stableFreq_mean* stableFreq_sampleSize,
+                                 shape2 = (1-stableFreq_mean)*stableFreq_sampleSize),
+                           rbeta(n = 1,
+                                 shape1 = 1,
+                                 shape2 = 100))) %>%
+    ungroup() %>%
+    select(property, prevalence)
+```
+
+##### Marginal distributions on prevalence
+
+```{r gen-fixed-prevprior-marginals, fig.width = 8, fig.height = 5}
+bind_rows(
+  d.prior %>% 
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+  select(-workerid, -trial_type, -Category),
+  m.samp.fixed.prevalence.prior %>% 
+    rename(Property = property) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = prevalence, color = src))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
+  facet_wrap( ~ Property, nrow = 3)+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+##### Cumulative Density Functions
+
+```{r gen-fixed-prevprior-cdf, fig.width = 8, fig.height = 5}
+bind_rows(
+  d.prior %>% 
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+  select(-workerid, -trial_type, -Category),
+  m.samp.fixed.prevalence.prior %>% 
+    rename(Property = property) %>%
+    mutate(src = 'model') 
+  ) %>% ggplot(., aes( x = prevalence, color = src))+
+    stat_ecdf()+
+    facet_wrap(~Property, nrow = 3)+
+    scale_color_solarized()+
+    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+    theme(strip.text.y = element_text(angle = 0))
+```

### 2017-07-04 paper/comgen-paper.Rmd
bayesian analysis of predictive elictation; intermediate model results for predictive hab; new figure for predictive hab

@@
 library(knitr)
+library(cowplot)
 theme_set(theme_few())
@@
 
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary, 
-       aes(x=logAnnualPastRate, 
-                              y = mean, 
-                              ymin = ci_lower, ymax = ci_upper, 
+# fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary, 
+#        aes(x=logAnnualPastRate, 
+#                               y = mean, 
+#                               ymin = ci_lower, ymax = ci_upper, 
+#                               fill = condition, shape=condition))+
+#   geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
+#   scale_shape_manual(values=c(21,22,23))+
+#   geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
+#   # #geom_errorbar(width=0.1)+
+#   scale_x_continuous(limits = c(-3,6), 
+#                      breaks = c(-3, 0, 2.5, 4, 5.9),
+#                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+#   scale_y_continuous(limits = c(-3,6), 
+#                      breaks = c(-3, 0, 2.5, 4, 5.9),
+#                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+#   guides(fill=F, shape=F)+
+#   scale_fill_solarized()+
+#   xlab("Past frequency (log scale)")+
+#   ylab("Predicted frequency (log scale)")+
+#   theme(axis.text.x = element_text(angle = 90))
+
+```
+
+### Methods
+
+We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
+The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
+
+The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
+On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
+Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
+On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
+The final third of trials had no additional evidence and were identical to Expt. 2b.
+
+Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
+To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
+In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
+
+Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
+The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/predictive-1.html}.
+
+```{r habituals-predictive-model}
+hab.predictive.bda.model <- '
+var model = function(){
+
+	var predictiveFrequency = {
+			mu: uniformDrift({a: -5, b:10, width: 2}),
+			sigma: uniformDrift({a:0, b:10, width: 1})
+	}
+
+	mapData({data: data}, function(d){
+		observe(Gaussian(predictiveFrequency),
+        d.logAnnualPredictiveRate)
+	})
+
+  return predictiveFrequency
+}
+'
+```
+
+```{r habituals-predictive-model-run, cache = T}
+items <- levels(factor(d.hab.predictive$item))
+conditions <- levels(factor(d.hab.predictive$condition))
+n_samples <- 500
+rs.habituals.bda.predictive <- data.frame()
+
+for (it in items){
+  for (cn in conditions){
+     df.predictive.toPass <- d.hab.predictive %>%
+       filter(condition == cn, item == it)
+
+    rs <- webppl(program_code = hab.predictive.bda.model,
+       model_var = "model",
+       inference_opts = list(method = "MCMC", samples = n_samples,
+                             burn = n_samples / 2),
+       data = df.predictive.toPass,
+       data_var = "data")
+    rs.habituals.bda.predictive <- bind_rows(
+        rs.habituals.bda.predictive, 
+        rs %>% 
+            mutate(item = it, condition = cn) 
+        )
+  }
+}
+```
+
+```{r habituals-predictive-forwardSample}
+rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
+  spread(Parameter, value) %>%
+  rowwise() %>%
+  mutate(
+    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
+  ) %>%
+  gather(key, val, mu, sigma, logannualRate) %>%
+  group_by(item, condition, key) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+```
+
+```{r habituals-predictive-bda-figure}
+fig.hab.freq.predictive.vs.past <- left_join(
+  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
+  unique(d.hab.predictive %>% 
+    select(item, condition, logAnnualPastRate)
+  )) %>% ggplot(., 
+       aes(x=logAnnualPastRate, y = MAP, 
+                              ymin = cred_lower, ymax = cred_upper, 
                               fill = condition, shape=condition))+
@@
   # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
+  scale_x_continuous(limits = c(-4,7), 
+                     breaks = c(-4, 0, 2.5, 4, 5.9),
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
+  scale_y_continuous(limits = c(-4,7), 
+                     breaks = c(-4, 0, 2.5, 4, 5.9),
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
@@
   xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
+  ylab("Predicted frequency MAP (log scale)")+
   theme(axis.text.x = element_text(angle = 90))
-
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/predictive-1.html}.
-
-### Results
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
+```
+
+### Modeling and results
+
+We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
+As we assumed for the prior elicitation task (Expt.
+2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
+$$
+\ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic})
+$$
+
+Figure \ref{fig:habituals-predictive-figure} (left) shows the Maximum A-Posteriori predicted future frequency as a function of the past frequency given to the participant and the type of causal information given.
 We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
@@
   d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>% select(condition, item, logAnnualPastRate, mean, ci_lower, ci_upper) %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
+  rs.habituals.bda.predictive.summary %>% 
+    filter(key == "logannualRate") %>%
+    rename(logAnnualFutureRate = MAP,
+         future_lower = cred_lower, future_upper = cred_upper)
+  # %>%
+  #   rowwise() %>%
+  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
+  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
 )
@@
   ylab("Endorsement probability")+
-  scale_x_continuous(limits = c(-3,6), 
+  scale_x_continuous(limits = c(-4.2,7.2), 
                      breaks = c(-3, 0, 2.5, 4, 5.9),
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
   coord_fixed(ratio=9)+
   scale_fill_solarized()+
+  guides(fill = F, shape = F)+
   theme(
@@
 ```{r habituals-predictive-rsa}
-
-```
-
-```{r habituals-predictive-figure, fig.cap="Left: Results of Expt 3a. Right: Results of Expt. 3b as they relate to the predicted frequencies from Expt. 3a"}
-grid.arrange(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, nrow = 1)
+n_chains <- 3
+n_samples <- 100000
+burn <- n_samples / 2
+lg <- 20
+model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
+
+m.hab.pred.samp <- data.frame()
+m.hab.past.samp <- data.frame()
+
+# for (i in seq(1, n_chains)){
+#   mi <- fread(paste(project.path,  "models/habituals/results/",
+#                     model_prefix, "targetH_predictive-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
+# 
+#   mi.past <- fread(paste(project.path,  "models/habituals/results/",
+#                     model_prefix, "targetH_past-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
+# 
+# }
+# 
+# save(m.hab.pred.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# 
+# save(m.hab.past.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(paste(project.path,  "models/habituals/results/", model_prefix, "past-",
+                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
+  filter(type == 'predictive', C == "endorsement") %>%
+  rename(item = B, condition = D, binned_freq = E) %>%
+  group_by(item, condition) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+m.hab.predictive.endorsement <- m.hab.pred.samp %>%
+  filter(type == 'predictive', C == "endorsement") %>%
+  rename(item = B, condition = D, binned_freq = E) %>%
+  group_by(item, condition) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+m.hab.predictive.endorse.rsa <- bind_rows(
+  left_join(
+    d.hab.predictive.endorsment.summary,
+    m.hab.predictive.endorsement
+  ) %>%
+    mutate(src = "predictive_model"),
+  left_join(
+    d.hab.predictive.endorsment.summary,
+    m.hab.pastmodel.endorsement
+  ) %>%
+    mutate(src = "past_model")
+)
+
+r2.habituals.rsa.past <- compute_r2(
+  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.past <- compute_mse(
+  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
+                                          "MAP_h", "MAP")
+
+r2.habituals.rsa.predictive <- compute_r2(
+  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.predictive <- compute_mse(
+  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
+                                          "MAP_h", "MAP")
+
+r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
+
+habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Speaker model - past frequency",
+                                 "Speaker model - predictive frequency"
+
+                                 ))) %>%
+  filter(src == "Speaker model - past frequency") %>%
+  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_linerange(alpha = 0.7)+
+  geom_errorbarh(alpha = 0.7)+
+  geom_point(shape = 21)+
+  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  xlab("Model prediction")+
+  ylab("Human habitual endorsement")+
+  facet_wrap(~src, nrow = 1)+
+  guides(fill = F)+
+  #theme(legend.position = "bottom")+
+    scale_fill_solarized()
+
+habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Speaker model - past frequency",
+                                 "Speaker model - predictive frequency"
+
+                                 ))) %>%
+  filter(src == "Speaker model - predictive frequency") %>%
+  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_linerange(alpha = 0.7)+
+  geom_errorbarh(alpha = 0.7)+
+  geom_point(shape = 21)+
+  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  xlab("Model prediction")+
+  ylab("Human habitual endorsement")+
+  facet_wrap(~src, nrow = 1)+
+  #guides(fill = F)+
+  #theme(legend.position = "bottom")+
+  scale_fill_solarized()
+```
+
+```{r fig.height = 14, fig.width=10, echo = F, eval=F}
+m.hab.pred.samp %>%
+  #filter(type == "predictive", C == "predictiveFreq") %>%
+  filter(type == "predictive", C == "endorsement") %>%
+  mutate(E = as.numeric(as.character(E))) %>%
+  ggplot(., aes(x = E, fill = D))+
+  geom_histogram(position = position_dodge())+
+  #facet_grid(B~E)+
+  facet_wrap(~B)
+```
+
+```{r habituals-predictive-figure, fig.cap="A: Results of Expt 3a.
+B: Results of Expt.
+3b as they relate to the predicted frequencies from Expt.
+3a, C & D: Endorsement models based on past frequency (C) and predictive frequency (D).", fig.width = 9, fig.height = 9}
+legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+
+prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model + theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
+
+plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
 ```
@@
 
-In Experiment 4a, we manipulate participants' beliefs about a causal system and measure their updated beliefs about system, serving a manipulation check.
-In Experiment 4b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 4a: Manipulating the Prevalence Prior for Causes
+In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs about system, serving a manipulation check.
+In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
+
+## Experiment 3a: Manipulating the Prevalence Prior for Causes
 
@@
 
-... run RSA model using fixed parameters and MAP estimates of these priors ...
-
-## Experiment 4b: Endorsing Causal Language
+... run RSA model using fixed parameters and MAP estimates of these priors ?
+
+## Experiment 3b: Endorsing Causal Language
 
@@
 Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 4a. 
+None of the participants had participated in Experiment 3a. 
 The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
@@
 
-The materials were the same as in Experiment 4a.
-Phase 1 of the experiment was identical to that of Experiment 4a.
+The materials were the same as in Experiment 3a.
+Phase 1 of the experiment was identical to that of Experiment 3a.
 In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 

### 2017-07-05 paper/comgen-paper.Rmd
describe results of predictive habituals models

@@
 
+r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+
 fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
@@
 n_chains <- 3
+# n_samples <- 500000
+# burn <- n_samples / 2
+# lg <- 150
+model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
 n_samples <- 100000
@@
 lg <- 20
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
 
@@
 #   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
+#                     model_prefix, "targetH_predictiveMean-",
 #                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
 #   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-# 
+
   # mi.past <- fread(paste(project.path,  "models/habituals/results/",
@@
   # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-# 
-# }
+
+#}
 # 
@@
 
-load(paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
+load(file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
 
-load(paste(project.path,  "models/habituals/results/", model_prefix, "past-",
+load(file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
@@
 
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}, middle; blue points).
+There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
+Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
+
 When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
+`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
 `r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
 ], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
+`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
 `r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
+], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
 `r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
@@
 
-... ADD REGRESSION MODEL RESULTS ...
-
-... ADD RSA RESULTS ...
+We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
+To formalize the predictive frequency speaker model, we use the predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
+The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
+
+We analyze this model in the same Bayesian data analysis regime as for our previous models, integrating the simple Bayesian analysis of the predictive frequency data (Expt.
+2c; for the predictive model only) with the joint model of the priors (Expt.
+2a) and the new endorsement data (Expt.
+2d).
+We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of N iterations (removing the first M for burn-in). 
+Figure \ref{fig:habituals-predictive-figure} C \& D shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
+Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
+The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
+
 <!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
@@
 
-<!-- Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).  -->
-<!-- This may be due, in part, to an effect of the experimental context on participants:  -->
-<!-- in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
+Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
+This may be due, in part, to an effect of the experimental context on participants:
+in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
 2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
--->
-<!-- Future investigation into this issue is warranted. -->
+Future investigation into this issue is warranted.
 

### 2017-07-06 paper/comgen-paper.Rmd
light edits to discussion

@@
 All models were implemented in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented in the Rmarkdown document that generated this paper text and figures, using the R package RWebPPL.
-That document, as well as the other models, analysis, data and experiments used in this paper can be found at \url{https://github.com/mhtess/comgen-paper}.
+The following simulations were implemented in the RMarkdown document that generated this paper text and figures, using the R package RWebPPL.
+That document, as well as the other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
 
@@
 <!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.
 
@@
 Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/priors-2.html}.
 
@@
 These were used for an exploratory analysis on differences in endorsements by gender of the target character.
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-2.html}.
 
@@
 
-# fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary, 
-#        aes(x=logAnnualPastRate, 
-#                               y = mean, 
-#                               ymin = ci_lower, ymax = ci_upper, 
-#                               fill = condition, shape=condition))+
-#   geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-#   scale_shape_manual(values=c(21,22,23))+
-#   geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-#   # #geom_errorbar(width=0.1)+
-#   scale_x_continuous(limits = c(-3,6), 
-#                      breaks = c(-3, 0, 2.5, 4, 5.9),
-#                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-#   scale_y_continuous(limits = c(-3,6), 
-#                      breaks = c(-3, 0, 2.5, 4, 5.9),
-#                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-#   guides(fill=F, shape=F)+
-#   scale_fill_solarized()+
-#   xlab("Past frequency (log scale)")+
-#   ylab("Predicted frequency (log scale)")+
-#   theme(axis.text.x = element_text(angle = 90))
+fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
+       aes(x=logAnnualPastRate,
+                              y = mean,
+                              ymin = ci_lower, ymax = ci_upper,
+                              fill = condition, shape=condition))+
+  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
+  scale_shape_manual(values=c(21,22,23))+
+  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
+  # #geom_errorbar(width=0.1)+
+  scale_x_continuous(limits = c(-3,6),
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(-3,6),
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+  guides(fill=F, shape=F)+
+  scale_fill_solarized()+
+  xlab("Past frequency (log scale)")+
+  ylab("Predicted frequency (log scale)")+
+  theme(axis.text.x = element_text(angle = 90))
 
@@
 Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/priors/predictive-1.html}.
 
@@
 
-```{r habituals-predictive-model-run, cache = T}
+```{r habituals-predictive-model-run, cache = T, eval=F}
 items <- levels(factor(d.hab.predictive$item))
 conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 500
+n_samples <- 5000
 rs.habituals.bda.predictive <- data.frame()
@@
 
-```{r habituals-predictive-forwardSample}
+```{r eval = F}
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
+#  geom_density(size = 1, aes( y = ..scaled.. ))+
+  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+               position = position_dodge())+
+  facet_wrap(~item, scales = 'free')+
+  scale_color_solarized()+
+  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_x_continuous(limits = c(-5,10)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
+rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
+  spread(Parameter, value) %>%
+  rowwise() %>%
+  mutate(
+    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
+  )
+
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
+#  geom_density(size = 1, aes( y = ..scaled.. ))+
+  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+               position = position_dodge())+
+  facet_wrap(~item, scales = 'free')+
+  scale_color_solarized()+
+  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_x_continuous(limits = c(-5,10)) +
+  theme(strip.text.y = element_text(angle = 0))
+
+bind_rows(
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate),
+  rs.habituals.bda.predictive.samples %>% 
+    select(item, condition, logannualRate) %>%
+    rename(logAnnualPredictiveRate = logannualRate) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
+#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+#               position = position_dodge())+
+  facet_grid(condition ~ item )+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(-5,10)) +
+  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r habituals-predictive-bda-summary, eval =F}
 rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
@@
 
-```{r habituals-predictive-bda-figure}
+```{r habituals-predictive-bda-figure, eval = F}
 fig.hab.freq.predictive.vs.past <- left_join(
@@
 
-### Modeling and results
-
-We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
-As we assumed for the prior elicitation task (Expt.
+### Results
+
+<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
+-->
+<!-- As we assumed for the prior elicitation task (Expt.
 2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
-$$
-\ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic})
-$$
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the Maximum A-Posteriori predicted future frequency as a function of the past frequency given to the participant and the type of causal information given.
+-->
+<!-- $$ -->
+<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
+<!-- $$ -->
+
+Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
 We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
 This means that our model makes identical predictions for Expt.
-2 whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
+2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
 Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
@@
 We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participants and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
+To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
 Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
@@
 model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
+#model_prefix <- "results-habituals-predictive-jointModel-predMin-3-S1-smtncs_habitual-"
 n_samples <- 100000
@@
 m.hab.past.samp <- data.frame()
+# m.hab.pred.samp <- fread(paste(project.path,
+#                                 "models/habituals/results/",
+#                                 "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-targetH_predictive-10000_burn5000_lag20_chain1.csv",
+#                                 sep = ""))
 
@@
 #   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictiveMean-",
+#                     model_prefix, "targetH_predictive-",
 #                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
@@
 #}
+
 # 
@@
   scale_fill_solarized()
-```
-
-```{r fig.height = 14, fig.width=10, echo = F, eval=F}
+#habituals.predictive.predictive.model
+```
+
+```{r fig.height = 6, fig.width=14, echo = F, eval=F}
 m.hab.pred.samp %>%
-  #filter(type == "predictive", C == "predictiveFreq") %>%
-  filter(type == "predictive", C == "endorsement") %>%
-  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = E, fill = D))+
+  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
+  #filter(type == "predictive", C == "endorsement") %>%
+#  mutate(E = as.numeric(as.character(E))) %>%
+  ggplot(., aes(x = val, fill = D))+
   geom_histogram(position = position_dodge())+
   #facet_grid(B~E)+
-  facet_wrap(~B)
+  facet_grid(D~B)
+```
+
+```{r, eval = F}
+m.hab.predfreq.summary <- m.hab.pred.samp %>%
+  filter(type == "predictive", C == "predictiveFreq") %>%
+  group_by(B, D, E) %>%
+  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
+
+left_join(m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Speaker model - past frequency",
+                                 "Speaker model - predictive frequency"
+
+                                 ))) %>%
+  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
 ```
@@
 3b as they relate to the predicted frequencies from Expt.
-3a, C & D: Endorsement models based on past frequency (C) and predictive frequency (D).", fig.width = 9, fig.height = 9}
+3a, C & D: Endorsement models based on past frequency (C) and predictive frequency (D).", fig.width = 10.5, fig.height = 11}
 legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
@@
 
-prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model + theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
+grid.arrange(
+  arrangeGrob(
+    fig.hab.freq.predictive.vs.past, 
+    fig.hab.endorse.vs.predfreq, 
+    habituals.predictive.past.model, 
+    habituals.predictive.predictive.model + theme(legend.position="none"),
+    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
+legend_b, nrow=2,heights=c(8, 1))
+
+#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
+
+#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
 ```
@@
 On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
 
@@
 We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
+To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
 The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
 
-We analyze this model in the same Bayesian data analysis regime as for our previous models, integrating the simple Bayesian analysis of the predictive frequency data (Expt.
-2c; for the predictive model only) with the joint model of the priors (Expt.
-2a) and the new endorsement data (Expt.
-2d).
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of N iterations (removing the first M for burn-in). 
-Figure \ref{fig:habituals-predictive-figure} C \& D shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
+We analyze this model in the same Bayesian data analysis regime as for our previous models.
+We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
+Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
 Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
@@
 2a).
-We have seen that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context that people exhibit (Expt. 2b).
+We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
 In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
+By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
+In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
+Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
+
 <!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
@@
 2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2c).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while measuring the propensity priors.
-Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlational associated with generic endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and test experimentally whether the propensity prior is indeed causally related to generic endorsement.
+2d).
+To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
+
+In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the propensity of the event.
+Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic endorsement but not directly causally related.
+In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the propensity prior is indeed causally related to generic endorsement.
 
@@
 Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly useful because no one individual can run all the experiments that she wants to run in a life time. 
+Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
 The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
 
-Our framework for communicating generalizations makes predictions about statements conveying genericty about a category of causal events. 
+Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
 In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
 <!-- [Gerstenberg] -->
-Determining whether or not a singular event itself is causal is challenging, plausibly having to do with counterfactual reasoning [e.g., @Gerstenberg2015how]. 
+Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
 Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
@@
 Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language has been shown to faciliate causal learning for nonobvious causal relations [@Bonawitz2010].
-We design this last experiment with the goal of testing the causal relationship between the prevalence priors that we posit as a mediating representation between abstract conecptual structure and endorsements of generalizations about causes.
+Indeed, causal language has been shown to faciliate causal learning for nonobvious causal relations in 2-year-olds [@Bonawitz2010].
+
+In this paper, we posit that prevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
+In this last set of experiments, we test the causal relationship between the prevalence priors and endorsements of generalizations about causes.
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
 
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs about system, serving a manipulation check.
+In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
 In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
@@
 
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:empirical-causal-prior-densities}.
+The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
 These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
@@
 
-In this experiment, we tested whether the manipulated priors of Expt. 4a are causally related to the endorsement of causal statements.
+In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
 
@@
 
-Most of the experiment was identical to that of Experiment 4a.
+Most of the experiment was identical to that of Experiment 3a.
 
@@
 
-### Results
-
 ```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
@@
 ```
-
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior (i.e., a Beta-Binomial model).
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
 
@@
   guides(fill = F, color = F)
+```
+
+```{r}
+md.caus.endorse <- left_join(
+  m.cas.fullmodel.endorsement,
+    d.caus.endorse.summary %>%
+    select(distribution, frequency, MAP_h, low, high) %>%
+    rename(dist = distribution)
+)
+
+n.caus.endorse <- length(md.caus.endorse$MAP_h)
+r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
+mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")
+
 ```
@@
 
+### Results
+
+`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
+As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
+These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
+
+As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
+When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
+By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
+The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
+Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
+
 ## Discussion
@@
 In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 4a).
+In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
 We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
-In Expt. 4b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ construct that we posit is causally related to endorsement.
+In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
+In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ is causally related to endorsements of generalizations in language.
 
@@
 
-It's likely that there exist domains for which abstract, intuitive theories might interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
+It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
 If this were happening in our domains, we would expect this to show up in the results of Expt.
-4a.
+3a.
 Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
 ]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "strong" priors conditions. 
+For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
 Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
@@
 We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data.
-
-It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
+To our knowledge, this is the first formal theory of genericity in language that makes precise quantitative predictions about human endorsement data.
+
+As a formal theory of genericity in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
 What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *propensity*, or probability (Expts. 1, 3, \& 4).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expt. 2).
+Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *propensity*, or probability (Expt. 1, 2a \& 2b, 3).
+This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
 We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
@@
 
-Our separation of world knowledge from the semantics of generics allows a way for conceptual structure to influence generic production and comprehension, without having to posit conceptual structure and semantics are one in the same.
+Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
+We do this without having to posit that conceptual structure and semantics are one in the same.
 This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
@@
 Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008]. 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g.~\emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g.~\emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g.~\emph{Tigers eat people.}) is useful and thus permitted to be a generic.
+Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
+Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
 Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
@@
 We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different prevalence priors. 
-In Expt. 4 we showed that these prevalence distributions are causally related to endorsement.
+In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
 
@@
 It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expt.~3 that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
+Indeed, we elucidated in Expts.
+2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
 
 The focus on subjective, predictive probability casts new light on puzzles surrounding accidentally-true situations.
-To take a thought-experiment from the linguistics litearature, imagine that currently every Supreme Court justice's social security number is an even number. 
+Consider a classic thought experiment in the linguistics and philosophy literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
 Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation is this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
+Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
 That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
@@
 
+<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the target category belong?".
+This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
+-->
+
 <!-- ### The Problems with Communicating Generalizations -->
@@
 Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-...More on development...
+Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
 
@@
 If generics convey something about the prevalence of feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-Rehash linguistic puzzles.
-The extreme flexibility of generic meaning stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward, emerge much *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) will not work for generic language [@Leslie2008].
-
-This would be throwing out the baby with the bathwater.
+The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
+In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge much *later* in development [@Brandone2014; @Gelman2015].
+This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
+
+We think this would be throwing out the baby with the bathwater.
 When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
@@
 The rest of the meaning is inferred in context.
+With that lens, generic meaning would be primary, while quantified utterances would be refinements.
 
@@
 
-This *soft semantics* (corresponding intuitively to something like "more is better") is perhaps the simplest semantics one could imagine.
+This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
 <!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
@@
 From the taxonomic relation of the subordinate categories (e.g., types of books) to the target category (i.e., books), the true prevalence of the feature among the target category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue.
+Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Birds are female".
 
 (2) is often used to argue that no actual instances need have the property to make a generalization true. 
-Part (or perhaps all) of Mary's job is to handle the mail from Antarctica; in this thought experiment, to date, there has not been any mail from Antarctica [@Cohen1999]. 
+In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
 Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expt. 3.
-In Expt.
-3, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
+This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
+In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
 Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
@@
 This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-That is, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
 
@@
 Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to say *Women are submissive* [@Haslanger2011].
+That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
 In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
@@
 This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
+If our speaker model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
 We find this possibility intruiging for future work.

### 2017-07-06 paper/comgen-paper.Rmd
final results for habituals predictive models

@@
 model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-#model_prefix <- "results-habituals-predictive-jointModel-predMin-3-S1-smtncs_habitual-"
+model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
 n_samples <- 100000
 burn <- n_samples / 2
-lg <- 20
+lg <- 50
 
@@
 m.hab.past.samp <- data.frame()
-# m.hab.pred.samp <- fread(paste(project.path,
-#                                 "models/habituals/results/",
-#                                 "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-targetH_predictive-10000_burn5000_lag20_chain1.csv",
-#                                 sep = ""))
 
@@
 #}
-
 # 
+# 
+# # 
 # save(m.hab.pred.samp,
@@
 #                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
+# # # 
 # save(m.hab.past.samp,
@@
 
-load(file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
+
+load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
 
@@
   scale_fill_solarized()
-#habituals.predictive.predictive.model
+habituals.predictive.predictive.model
 ```

### 2017-07-07 paper/appendix-cueValidity.Rmd
make better figure for cue validity appendix

@@
 
-# Appendix B: Measuring cue validity
+# Appendix B: Measuring Cue Validity
 
 In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
-Here, the prevalence of the feature, or $P(f \mid k)$, is the central quantity.
-Quantifiers can be described as conditions on prevalence: $\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}$.
+Here, the prevalence of the feature, or $P(f \mid k)$, is the critical quantity.
+Quantifiers can be described as conditions on prevalence: 
+$$
+\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}
+$$
 The question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
-Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice.
+Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice (i.e., *Some mosquitos carry malaria*).
 
-Some (who?) have noted, however, that the inverse probability, the probability of the kind $k$ given the feature $f$ --- $P(k \mid f)$ --- might be able to save statistical-based approaches [@Leslie2007].
+@Leslie2007 notes that mosquitos are the only species to carry malaria, and perhaps this explains why the generic is true.
+More formally, the inverse probability --- the probability of the kind $k$ given the feature $f$: $P(k \mid f)$ --- might be able to save statistical-based approaches [@Leslie2007; @Khemlani2012].
 This inverse probability, referred to as *cue validity*, encodes the diagnosticity of the feature for the kind.
 For example, after learning that an entity *carries malaria*, the probability that the entity is a *mosquito* is very high.
-
-An approach based only on cue-validity would be insufficient because of cases like *Dogs have four legs*. 
-Tons of animals have four legs, and so the diagnositicity of having four legs for a dog is very low. 
-However, one could argue for some integration of the two probabilities --- prevalence and cue validity.
-This is often tested by measuring prevalence and cue validity and using both measurements as predictors of generic endorsement in a logistic-regression [@Khemlani2012; @Prasada2013].
 
@@
 
-where $x$ is an arbitrary entity, $k$ is a kind represented as a collection of entities in the kind, and $f$ is a feature represented as a collection of entities with the feature.
+where $x$ is an arbitrary entity, $k$ is a kind (represented as a collection of entities in the kind), and $f$ is a feature (represented as a collection of entities with the feature).
 However, in a generative model composed of a potentially infinite number of kinds, the cue validity of a feature for a particular kind is 0. 
-In our mixture model formulation of the prevalence prior, we explicitly represent the prevalence prior as a generative model with a potentially infinite number of kinds (see Appendix A for more details).
-In this formulation, there is a mixture parameter $\phi$ that we consider the *potential of the property to be present in a kind*. 
-This is generalization of cue validity to the case of an infinite number of kinds.
+In our mixture model formulation of the prevalence prior, we explicitly represent the prevalence prior as a generative model with a potentially infinite number of kinds.
+In this formulation, the mixture parameter $\phi$ can be seen as a generalization of cue validity, to the case of potentially infinite numbers of kinds.
 
-## Cue validity is a special case of the prevalence prior structure
+Cue validity is not itself sufficient to explain endorsements because of cases like *Dogs have four legs*, where many kinds have the feature. 
+However, one could argue for some integration of the two probabilities --- prevalence and cue validity.
+This is often used as the "statistical-based approach" and operationalized by measuring prevalence and cue validity, and using both measurements as predictors of generic endorsement in a logistic-regression of generic endorsement [@Khemlani2012; @Prasada2013].
+
+In Expt. 1, we articulated this alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a regression model.
+In a small review of the literature, we discovered different methods for measuring cue validity, which lead to different results. 
+Therefore, here we propose three *a priori* desiderata that a measurement of cue validity should satisfy.
+We describe two experiments that represent the primary methods for measuring cue validity and compare them with these desiderata in mind.
+Finally, we compare the cue validity measured using these different methods to cue validity derived from our prevalence prior elicitation task (Expt. 1a, main text).
 
@@
 
-Measuring cue validity involves collecting participants' judgments that rely upon the probability of the kind given the feature.
-There are at least two conceivable ways of trying to measure cue validity.
-One way is ask participants directly about the probability (or likelihood, odds, etc...) of the kind given the feature, using a likert scale or slider.
-This is the paradigm used by @Khemlani2012 and @Prasada2013.
+Measuring cue validity involves collecting participants' judgments that relate to the probability of the kind given the feature.
+There are at least two distinct, prominent ways of measuring cue validity.
+One way is ask participants directly about the probability (or likelihood, odds, etc...) of the kind given the feature, using a likert scale or slider [@Khemlani2012; @Prasada2013].
 We'll call this approach the "direct question" approach.
-Another way is to supply participants with the feature alone and have them generate the kind.
+Another way is to supply participants with the feature alone and have them generate the kind or kinds [@Cree2006].
 We'll call this approach the "free production" approach.
@@
 Of primary interest is the measurement for the boundary conditions described above.
+The experiments can be seen on \url{https://mhtess.github.io}.
 
@@
 Materials were the same for both experiments.
-They were a collection of familiar properties and animal categories used in Expt. X (endorsement of generalizations about categories) described in the main text.
+They were a collection of familiar properties and animal categories used in Expt. 1b (endorsement of generic statements) described in the main text.
 There were twenty-one properties in total.
@@
 ### Method
+
 #### Participants
@@
 The slider appeared with no handle present; participants had to click on the slider for the slider handle to appear.
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/generics/speaker_familiar-kinds/cue-validity-1.html}
 
@@
 Trials were presented in a randomized order.
-The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/generics/speaker_familiar-kinds/cue-validity-2-freeProduction.html}
 
@@
 
-ggplot(d.cv.summary, aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  facet_wrap(~type, scales = 'free')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  theme(axis.text.x = element_text(angle = 90))+
-  xlab("")+
-  ylab("Probability rating of cue validity")+
-  ggtitle("Direct question paradigm")
+# ggplot(d.cv.summary, aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
+#   geom_bar(stat = 'identity', position = position_dodge())+
+#   geom_errorbar(position = position_dodge())+
+#   facet_wrap(~type, scales = 'free')+
+#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+#   theme(axis.text.x = element_text(angle = 90))+
+#   xlab("")+
+#   ylab("Probability rating of cue validity")+
+#   ggtitle("Direct question paradigm")
 
@@
 
-ggplot(d.cv.fp.summary, aes ( x = item, y = prop))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  facet_wrap(~type, scales = 'free')+
+d.cv.bootstrapped <- data.frame()
+resample_n <- length(levels(factor(d.cv.fp$workerid)))
+for (i in 1:100){
+
+  d.cv.bsample <-left_join(
+    target.items,
+    d.cv.fp %>% 
+    select(workerid, property, response) %>% 
+    spread(property, response) %>% 
+    sample_n(resample_n, replace = TRUE) %>%
+    gather(property, category, -workerid) %>% 
+    group_by(property) %>%
+    mutate(n = n(),
+           item = paste(category, property))
+    ) %>%
+    group_by(category, property, item, type) %>%
+    summarize(mentions = n(),
+              trials = mean(n), # mean(n) == n, because it's just the number of subjects
+              prop = mentions / trials,
+              prop = ifelse(is.na(prop), 0.01, prop),
+              iteration = i)
+
+  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
+}
+
+empiricalLower = function(dist){
+  xi <- quantile(dist, 0.025)
+  return (xi[["2.5%"]])
+}
+empiricalUpper = function(dist){
+  xi <- quantile(dist, 0.975)
+  return (xi[["97.5%"]])
+}
+empiricalMean = function(dist){
+  xi <- quantile(dist, 0.5)
+  return (xi[["50%"]])
+}
+
+d.cv.fp.summary <- d.cv.bootstrapped %>%
+      group_by(item, type) %>%
+      summarize(mean = empiricalMean(prop),
+                ci_lower = empiricalLower(prop),
+                ci_upper = empiricalUpper(prop)) %>%
+  mutate(
+    ci_lower = ifelse(is.na(mean), 0.01, ci_lower),
+    ci_upper = ifelse(is.na(mean), 0.01, ci_upper),
+    mean = ifelse(is.na(mean), 0.01, mean)
+  )
+
+d.cv.bothtasks <- bind_rows(
+  d.cv.summary %>% mutate(task = 'direct question'),
+  d.cv.fp.summary %>% mutate(task = 'free production')
+)
+
+theoretical.cv <- data.frame(
+  type = c( "false", "undiagnostic","diagnostic"),
+  cv = c(0.05, 0.05, 0.95)
+)
+
+```
+```{r cv-bothquestions-barplots, fig.cap="Empirically measured cue validity for two different tasks.
+Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
+Dotted lines denote theoretical cue validity representing the desiderata (see text).
+Error bars denote bootstrapped 95\% confidence intervals."}
+d.cv.bothtasks %>%
+  mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
+  ggplot(., aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_bar(stat = 'identity', position = position_dodge(0.5),
+           width = 0.5, color = 'black', fill = 'white')+
+  geom_errorbar(position = position_dodge(0.5), width = 0.3)+
+  facet_grid(task~type, scales = 'free')+
   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  theme(axis.text.x = element_text(angle = 90))+
+  geom_hline(data = theoretical.cv, aes(yintercept = cv), lty = 2)+
+  theme(axis.text.x = element_text(angle = 90),
+        strip.text.y = element_text(angle = 0))+
   xlab("")+
-  ylab("Proportion produced target category")+
-  ggtitle("Free production paradigm")
+  ylab("Cue validity")+
+  guides(color = F)
 

### 2017-07-07 paper/comgen-paper.Rmd
remove discussion of gender differed habituals

@@
 
-All participants responded correctly to both questions in the attention check trial, so all data was used in the analysis.
+All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
 We built a Bayesian data analysis model for this prior elicitation task.
@@
 Each item was modeled independently for each gender.
-
-We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
+We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
 
@@
 Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.~\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
+This diversity is relevant because the speaker model (Eq.
+\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
 the ballet.}) contingent on the shape of the prior distribution.
@@
 We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-
-Figure \ref{fig:priorScatter} (right) shows example inferred priors.
-Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}).
-Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals). 
-It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*. 
-For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"?
-We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender.
+Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
+
+<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
+<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
+<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
+<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
+<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
 
@@
 Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed 37 trials, which were composed of the 31 items from the prior elicitation task randomly paired with either a male or female character name.
-6 of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who watched professional football).
-These were used for an exploratory analysis on differences in endorsements by gender of the target character.
+Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
+Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
+<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
 
@@
 "John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.'}
+Labeled points all correspond to the time period of 3 times / month.', eval=F}
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
@@
 
+<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
 Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ.
+For all analyses, we collapse across gender of the target character.
+<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
 
@@
 
-For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements. 
-Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
-Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
-We see no appreciable differences in endorsements for the two genders. 
-This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters.
-For all remaining analyses, we collapse across character gender when analyzing endorsements.
+<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
+<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
+-->
+<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
+-->
+<!-- We see no appreciable differences in endorsements for the two genders.  -->
+<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
+<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
 
@@
   scale_fill_solarized()
-habituals.predictive.predictive.model
+#habituals.predictive.predictive.model
 ```

### 2017-07-07 paper/appendix-cueValidity.Rmd
add analyses comparing prevpriorderived cv and empirical cv for diff measures

@@
 ```
+
+## Comparison with prevalence prior derived cue validity
+
+Here, we treat each entry (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
+This will have the prevalence prior favor kinds that are easy to produce (like dogs and cats) as well as the experimentally supplied kinds (like mosquitos and robins).
+
+```{r cv-fp-data-analyzeAll}
+d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
+  mutate(
+    property = gsub("'", "", property),
+    Property = gsub("'", "", Property),
+    sentence = paste(Category, Property),
+    item = paste(category, property))
+
+# d.prev.summary <- d.prev %>%
+#   mutate(item = paste(Category, Property)) %>%
+#   filter(item %in% d.target.items$sentence) %>%
+#   mutate(prevalence = prevalence / 100) %>%
+#   group_by(Category, Property, item) %>%
+#   multi_boot_standard(column = "prevalence")
+
+d.cv.bootstrapped.all <- data.frame()
+resample_n <- length(levels(factor(d.cv.fp$workerid)))
+for (i in 1:1000){
+
+  d.cv.bsample <- d.cv.fp %>% 
+    select(workerid, property, response) %>% 
+    spread(property, response) %>% 
+    sample_n(resample_n, replace = TRUE) %>%
+    gather(property, category, -workerid) %>% 
+        group_by(property) %>%
+    mutate(n = n(),
+           item = paste(category, property)) %>%
+    filter(item %in% d.target.items$item) %>%
+    group_by(category, property) %>%
+    summarize(mentions = n(),
+              trials = mean(n), # mean(n) == n, because it's just the number of subjects
+              prop = mentions / trials,
+              prop = ifelse(is.na(prop), 0.01, prop),
+              iteration = i)
+
+  d.cv.bootstrapped.all <- bind_rows(d.cv.bootstrapped.all, d.cv.bsample)
+}
+
+d.gen.cv.all.summary <- left_join(
+    d.target.items %>% select(-sentence),
+    d.cv.bootstrapped.all %>%
+      group_by(category, property) %>%
+      summarize(cv_mean = empiricalMean(prop),
+                cv_ci_lower = empiricalLower(prop),
+                cv_ci_upper = empiricalUpper(prop))
+) %>%
+  mutate(
+    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
+    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
+    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
+  )
+
+```
+
+```{r, echo = F, eval = F}
+wp.pkg.path <- paste(project.path, "models/generics/node_modules/utils/", sep = "")
+
+cueValidityModel1 <- '
+var cueValidity = function(){
+  var kind = uniformDraw(data.prior);
+  observe(Bernoulli({p: kind.prevalence/100}), true)
+  return kind.Category == data.kind[0]
+}
+
+expectation(Infer({model: cueValidity}))
+'
+
+d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
+                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+
+d.gen.endorse.priors <- read.csv(paste(project.path, 
+                                       "data/generics/endorsement/",
+                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
+
+wp.cueValidity <- data.frame()
+for (p in gen.endorse.properties){
+  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
+  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)
+
+  for (catg in categories){
+
+    dataToPass <- list(
+      prior = prevPriorData,
+      kind = catg
+    )
+
+    wp.rs <- webppl(cueValidityModel2, 
+       #packages = c(wp.pkg.path),
+       data_var = "data",
+       data = dataToPass)
+
+    wp.cueValidity <- bind_rows(wp.cueValidity, 
+                                data.frame(Category = catg,
+                                           Property = p,
+                                           cv = wp.rs))
+
+  }
+  print(p)
+}
+# save(wp.cueValidity, file =
+#        paste(project.path, model.path,
+#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
+# load(file = 
+#        paste(project.path, model.path, 
+#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
+```
+
+```{r}
+md.fp <- left_join(left_join(
+  d.gen.cv.all.summary,
+  wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
+), target.items2)
+
+ggplot(md.fp, aes (x = prev_prior_derived_cv, y = cv_mean, ymin = cv_ci_lower, ymax = cv_ci_upper,
+                   color = type, alpha = type))+
+  geom_point()+
+  scale_alpha_manual(values = c(1,1,1,0.5))+
+  geom_errorbar()+
+  ylim(0, 1) + xlim(0, 1)+
+  coord_fixed()
+
+compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
+compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
+
+diagnostic.props <- data.frame(
+  item = c("kangaroo has a pouch", "lion has a mane", 
+           "mosquito carries malaria", "tick carries Lyme disease"),
+  type = "diagnostic"
+)
+
+undiagnostic.props <- data.frame(
+  item = c("leopard is juvenile", "lion is male", "robin is female", "swan is full-grown"),
+  type = "undiagnostic"
+)
+
+false.props <- data.frame(
+  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
+  type = "false"
+)
+
+target.items2 <- bind_rows(diagnostic.props, undiagnostic.props, false.props)
+md.fp.desid <- md.fp %>%
+  filter(item %in% target.items2$item)
+
+compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+```
+
+```{r}
+target.items
+md.fp
+```
+
+```{r}
+d.cv.dq.all <- d.cv.dq %>%
+  mutate(property = gsub("&quotechar", "", property), 
+         item = paste(category, property)) %>%
+  group_by(category, property) %>%
+  multi_boot_standard(column = 'response')
+
+md.dq <-  left_join( left_join(
+    left_join(
+    d.gen.cv.all.summary %>% select(Category, Property, category, property, item),
+    d.cv.dq.all),
+    wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
+  ), target.items2)
+
+ggplot(md.dq, aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
+                     color = type))+
+  geom_point()+
+  geom_errorbar()+
+  ylim(0, 1) + xlim(0, 1)+
+  coord_fixed()
+
+compute_r2(md.dq, "mean", "prev_prior_derived_cv")
+compute_mse(md.dq, "mean", "prev_prior_derived_cv")
+
+md.dq.desid <- md.dq %>%
+  filter(item %in% target.items2$item)
+
+compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
+compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
+
+```
+
+```{r cvModel-uniformPrior, echo = F, eval = F}
+cueValidityModel2 <- '
+var cueValidity = function(){
+  var kind = uniformDraw(data.allKinds);
+  var responses = _.filter(data.prior, {Category: kind});
+  var response = _.isEmpty(responses) ? {prevalence: 0} : uniformDraw(responses);
+  observe(Bernoulli({p: response.prevalence/100}), true)
+  return kind == data.kind[0]
+}
+
+expectation(Infer({model: cueValidity}))
+'
+
+allKinds = levels(factor(d.gen.endorse.priors$Category))
+
+wp.cueValidity.uniform <- data.frame()
+for (p in gen.endorse.properties){
+  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
+  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)
+
+  for (catg in categories){
+
+    dataToPass <- list(
+      prior = prevPriorData,
+      kind = filter(prevPriorData, Category == catg)[1, "Category"],
+      allKinds = allKinds
+    )
+
+    wp.rs <- webppl(cueValidityModel2, data_var = "data", data = dataToPass)
+
+    wp.cueValidity.uniform <- bind_rows(wp.cueValidity.uniform, 
+                                data.frame(Category = catg,
+                                           Property = p,
+                                           cv = wp.rs))
+
+  }
+  print(p)
+}
+# save(wp.cueValidity, file = 
+#        paste(project.path, model.path, 
+#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
+# dataToPass %>% toJSON(.)
+# 
+# wp.rs
+wp.cueValidity.uniform
+```

### 2017-07-08 paper/appendix-cueValidity.Rmd
clean up cv figure

@@
 We propose three boundary cases *a priori* that the measurement should be able to satisfy.
+For each case, we provide four examples which will be used to evaluate each measure.
+
 \begin{enumerate}
@@
 \item{Completely absent features: For features that are completely absent in a kind, the cue validity should be extremely low or 0.
-There are many examples of these kinds of pairings; for example, \emph{having wings} (leopards), \emph{laying eggs} (lions).}
+There are many examples of these kinds of pairings; for example, \emph{has wings} (leopard), \emph{has a mane} (shark), "has spots" (kangaroo), "has a pouch" (tiger).
+}
 \item{Completely undiagnostic features: We contend there are a number of features that almost every category contains.
-Examples include: \emph{being female / male}, \emph{being juvenile}.
+Examples include: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard).
 The cue validity of these features for particular categories should be extremely low or 0.
@@
 
-## Results
+## Results and Evaluation
 
@@
 As well, "mosquito" was a commonly mispelled label; we counted anything that started with "mosqu", "mesqu", "misqu", "mosiq" as "mosquito".
+
+To calculate confidence intervals for the free production data, we resampled participants (with replacement) and computed the proportion of responses that were of the target category (e.g., the proportion of "mosquito" responses for the cue "carries malaria").
+We did this one-thousand times to took the empirical 95\% quantile of those proportions.
+
+We are interested in the results of each measure (direct question and free production) for the three conditions corresponding to the desiderata outlined above. 
+To evaluate each measure, we selected four examples property--category pairs that we believe are unambiguously instances of the boundary conditions described above (these items are described above with the desiderata).
+
+Figure \ref{fig:cv-bothquestions-barplots} shows the results for the twelve items of interest for both measurements.
+We see that for the "false" features, both measures behave as desired (shown by the dotted line). 
+The cue validity of a feature that is false is zero or near-zero.
+For "diagnostic" features, both measures behave reasonably well.
+Learning that an entity has malaria strongly implies that it is a mosquito. 
+However, there are some subtle differences among our examples that only the free production measure picks up on.
+"Having a mane" is strongly diagnostic for a "lion" but also for a "horse" (and so the overall cue validity for lion is around 0.5).
+"Carrying Lyme disease" is mostly diagnostic for a "tick" but also "deer" (and thus, the cue validity for tick is not maximal).
+
+The measures deviate the most in their treatment of the undiagnostic features. 
+Learning that an entity is female does not strongly imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
+A similar phenomena can be observed in direct question measure for the other undiagnostic features.
 
@@
 ```
-```{r cv-bothquestions-barplots, fig.cap="Empirically measured cue validity for two different tasks.
-Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
-Dotted lines denote theoretical cue validity representing the desiderata (see text).
-Error bars denote bootstrapped 95\% confidence intervals."}
-d.cv.bothtasks %>%
+
+```{r, cache = F}
+cv.bothquestions.bars <- d.cv.bothtasks %>%
   mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
@@
   geom_hline(data = theoretical.cv, aes(yintercept = cv), lty = 2)+
-  theme(axis.text.x = element_text(angle = 90),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
         strip.text.y = element_text(angle = 0))+
@@
   guides(color = F)
-
 ```
 
-```{r dq.histogram, fig.height = 4, eval = F}
-ggplot(d.cv.targets, aes( x = response ))+
+```{r dq.histogram, fig.width = 3}
+dq.histograms <- ggplot(d.cv.targets %>%
+         filter(item %in% undiagnostic.props$item), aes( x = response ))+
   geom_histogram() + 
-  facet_wrap(~type) + 
-  scale_x_continuous(breaks = c(0, 0.5, 1))
+  facet_wrap(~item, nrow = 1) + 
+  scale_x_continuous(breaks = c(0, 1))+
+  scale_y_continuous(breaks = c(0, 10))
+```
+
+```{r cv-bothquestions-barplots, fig.height = 6, fig.width = 8, fig.cap="Empirically measured cue validity for two different tasks.
+Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
+Dotted lines denote theoretical cue validity representing the desiderata (see text).
+Error bars denote bootstrapped 95% confidence intervals."}
+grid.arrange(cv.bothquestions.bars, dq.histograms, heights = c(2.5, 1))
 ```
@@
 
-```{r cv-fp-data-analyzeAll}
+```{r}
+diagnostic.props <- data.frame(
+  item = c("kangaroo has a pouch", "lion has a mane", 
+           "mosquito carries malaria", "tick carries Lyme disease"),
+  type = "diagnostic"
+)
+
+undiagnostic.props <- data.frame(
+  item = c("leopard is juvenile", "lion is male", "robin is female", "swan is full-grown"),
+  type = "undiagnostic"
+)
+
+false.props <- data.frame(
+  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
+  type = "false"
+)
+
+target.items2 <- bind_rows(diagnostic.props, undiagnostic.props, false.props)
+```
+
+```{r cv-fp-data-analyzeAll, cache = T}
 d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
@@
     item = paste(category, property))
-
-# d.prev.summary <- d.prev %>%
-#   mutate(item = paste(Category, Property)) %>%
-#   filter(item %in% d.target.items$sentence) %>%
-#   mutate(prevalence = prevalence / 100) %>%
-#   group_by(Category, Property, item) %>%
-#   multi_boot_standard(column = "prevalence")
 
@@
 
-```{r, echo = F, eval = F}
+```{r cuevalidity-model-pk}
 wp.pkg.path <- paste(project.path, "models/generics/node_modules/utils/", sep = "")
@@
 
-    wp.rs <- webppl(cueValidityModel2, 
-       #packages = c(wp.pkg.path),
+    wp.rs <- webppl(cueValidityModel1, 
        data_var = "data",
@@
   wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
+  #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
 ), target.items2)
@@
 
-diagnostic.props <- data.frame(
-  item = c("kangaroo has a pouch", "lion has a mane", 
-           "mosquito carries malaria", "tick carries Lyme disease"),
-  type = "diagnostic"
-)
-
-undiagnostic.props <- data.frame(
-  item = c("leopard is juvenile", "lion is male", "robin is female", "swan is full-grown"),
-  type = "undiagnostic"
-)
-
-false.props <- data.frame(
-  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
-  type = "false"
-)
-
-target.items2 <- bind_rows(diagnostic.props, undiagnostic.props, false.props)
 md.fp.desid <- md.fp %>%
@@
 compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
-```
-
-```{r}
-target.items
-md.fp
 ```
@@
     d.cv.dq.all),
+    #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
     wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
@@
 
-```{r cvModel-uniformPrior, echo = F, eval = F}
+```{r cvModel-uniformPrior}
 cueValidityModel2 <- '
@@
 # wp.rs
-wp.cueValidity.uniform
+
 ```

### 2017-07-10 paper/appendix-cueValidity.Rmd
fix knitting issues

@@
 
-```{r, cache = F}
+```{r}
 cv.bothquestions.bars <- d.cv.bothtasks %>%
@@
   scale_x_continuous(breaks = c(0, 1))+
-  scale_y_continuous(breaks = c(0, 10))
+  scale_y_continuous(breaks = c(0, 10))+
+  xlab("Direct question response")+
+  ylab("Number of responses")
 ```

### 2017-07-10 paper/comgen-paper.Rmd
fix knitting issues

@@
 
-```{r habituals-predictive-bda-figure, eval = F}
+```{r habituals-predictive-bda-figure, eval =F}
 fig.hab.freq.predictive.vs.past <- left_join(
@@
   d.hab.predictive.endorsment.summary,
-  rs.habituals.bda.predictive.summary %>% 
-    filter(key == "logannualRate") %>%
-    rename(logAnnualFutureRate = MAP,
-         future_lower = cred_lower, future_upper = cred_upper)
+  d.hab.predictive.summary %>%
+    rename(logAnnualFutureRate = mean,
+         future_lower = ci_lower, future_upper = ci_upper)
+  # rs.habituals.bda.predictive.summary %>% 
+  #   filter(key == "logannualRate") %>%
+  #   rename(logAnnualFutureRate = MAP,
+  #        future_lower = cred_lower, future_upper = cred_upper)
   # %>%

### 2017-07-22 paper/appendix-cueValidity.Rmd
clean up most of cue validity appendix

@@
 $$
-The question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
-Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice (i.e., *Some mosquitos carry malaria*).
+The driving question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
+Fixed constraints on $\theta$ (e.g., $\theta = 0.5$) are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice (i.e., *Some mosquitos carry malaria*).
 
-@Leslie2007 notes that mosquitos are the only species to carry malaria, and perhaps this explains why the generic is true.
+With respect to malaria-carrying mosquitos, @Leslie2007 notes that the mosquito is the only species to carry malaria. 
+The distinctiveness of *carrying malaria* then perhaps why *Mosquitos carry malaria* is true.
 More formally, the inverse probability --- the probability of the kind $k$ given the feature $f$: $P(k \mid f)$ --- might be able to save statistical-based approaches [@Leslie2007; @Khemlani2012].
@@
 \item{Completely absent features: For features that are completely absent in a kind, the cue validity should be extremely low or 0.
-There are many examples of these kinds of pairings; for example, \emph{has wings} (leopard), \emph{has a mane} (shark), "has spots" (kangaroo), "has a pouch" (tiger).
+There are many examples of these kinds of pairings; for example, \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger).
 }
@@
 Of primary interest is the measurement for the boundary conditions described above.
-The experiments can be seen on \url{https://mhtess.github.io}.
+Links to the experiments can be found on \url{https://mhtess.github.io}.
 
@@
 
-Participants completed the thirty target trials (corresponding to the thirty generic statements used in Expt. X) in addition to ten filler trials (total number of trials = 40).
+Participants completed the thirty target trials (corresponding to the thirty generic statements used in Expt. 1b) in addition to ten filler trials (total number of trials = 40).
 The filler trials were made up of random category -- property pairings.
@@
 
-## Results and Evaluation
+### Free production data processing
 
@@
 To calculate confidence intervals for the free production data, we resampled participants (with replacement) and computed the proportion of responses that were of the target category (e.g., the proportion of "mosquito" responses for the cue "carries malaria").
-We did this one-thousand times to took the empirical 95\% quantile of those proportions.
+We did this 1000 times to generate an empirical distribution from which 95\% intervals could be calculated.
+
+## Results and Evaluation
 
@@
 
-The measures deviate the most in their treatment of the undiagnostic features. 
+The measures deviate in their characterization of the undiagnostic features. 
 Learning that an entity is female does not strongly imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
-A similar phenomena can be observed in direct question measure for the other undiagnostic features.
+A similar phenomenon can be observed in direct question measure for the other undiagnostic features.
+Figure \ref{fig:cv-bothquestions-barplots} (bottom) shows the raw empirical distributions of responses for the direct question measure. 
+We observe suggestive evidence that participants respond to this question for unidagnostic features in one of two ways: (i) reporting near-0 likelihood (accurate response) or (ii) reported near-0.5 likelihood.
+This latter response option may be a pragmatic effect of asking the direct question and/or participants "opting out" of a response. 
+For example, in response to the question "There is a thing that is female.
+What are the odds that it is a robin?", a reasonable human response may be "I don't know".
+Participants may cope with the awkwardness of the question by placing the slider bar in the middle of the scale.
 
@@
 
-Here, we treat each entry (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
-This will have the prevalence prior favor kinds that are easy to produce (like dogs and cats) as well as the experimentally supplied kinds (like mosquitos and robins).
+We can further understand our measures of cue validity by comparing them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
+Expt.
+1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated.
+(Participants freely generated the other half).
+Thus, we do not have the best measurement of the prior probability of categories $P(k)$.
+
+In this analysis, we treat each category entry from Expt. 1a (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
+This will result in the prevalence prior favoring kinds that are easy to produce (like dogs and cats, which is plausibly a good approximation for $P(k)$) as well as favoring the experimentally supplied kinds (like mosquitos and robins).
+
+We compute cue validity from the prevalence prior using Bayes' rule. 
+Figure \ref{fig:cv-scatters} show the ...
 
@@
   }
-  print(p)
+  #print(p)
 }
@@
 
-```{r cvModel-uniformPrior}
+```{r cvModel-uniformPrior, eval = F}
 cueValidityModel2 <- '

### 2017-07-22 paper/appendix-cueValidity.Rmd
summary and mega figure for cv app

@@
 
-Figure \ref{fig:cv-bothquestions-barplots} shows the results for the twelve items of interest for both measurements.
+Figure \ref{fig:cv-bothquestions-barplots} (top) shows the results for the twelve items of interest for both measurements.
 We see that for the "false" features, both measures behave as desired (shown by the dotted line). 
@@
 A similar phenomenon can be observed in direct question measure for the other undiagnostic features.
-Figure \ref{fig:cv-bothquestions-barplots} (bottom) shows the raw empirical distributions of responses for the direct question measure. 
+Figure \ref{fig:cv-bothquestions-barplots} (bottom left) shows the raw empirical distributions of responses for the direct question measure. 
 We observe suggestive evidence that participants respond to this question for unidagnostic features in one of two ways: (i) reporting near-0 likelihood (accurate response) or (ii) reported near-0.5 likelihood.
@@
 
-```{r dq.histogram, fig.width = 3}
+```{r dq.histogram}
 dq.histograms <- ggplot(d.cv.targets %>%
@@
   geom_histogram() + 
-  facet_wrap(~item, nrow = 1) + 
+  facet_wrap(~item, nrow = 2) + 
   scale_x_continuous(breaks = c(0, 1))+
@@
 ```
-
-```{r cv-bothquestions-barplots, fig.height = 6, fig.width = 8, fig.cap="Empirically measured cue validity for two different tasks.
-Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
-Dotted lines denote theoretical cue validity representing the desiderata (see text).
-Error bars denote bootstrapped 95% confidence intervals."}
-grid.arrange(cv.bothquestions.bars, dq.histograms, heights = c(2.5, 1))
-```
-
-## Comparison with prevalence prior derived cue validity
-
-We can further understand our measures of cue validity by comparing them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
-Expt.
-1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated.
-(Participants freely generated the other half).
-Thus, we do not have the best measurement of the prior probability of categories $P(k)$.
-
-In this analysis, we treat each category entry from Expt. 1a (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
-This will result in the prevalence prior favoring kinds that are easy to produce (like dogs and cats, which is plausibly a good approximation for $P(k)$) as well as favoring the experimentally supplied kinds (like mosquitos and robins).
-
-We compute cue validity from the prevalence prior using Bayes' rule. 
-Figure \ref{fig:cv-scatters} show the ...
 
@@
   #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
-), target.items2)
+), target.items2) %>%
+  mutate(type = ifelse(is.na(type), "other", type),
+           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
+                       labels = c("diagnostic", "undiagnostic", "false", "other")))
 
-ggplot(md.fp, aes (x = prev_prior_derived_cv, y = cv_mean, ymin = cv_ci_lower, ymax = cv_ci_upper,
-                   color = type, alpha = type))+
-  geom_point()+
-  scale_alpha_manual(values = c(1,1,1,0.5))+
-  geom_errorbar()+
-  ylim(0, 1) + xlim(0, 1)+
-  coord_fixed()
+fill.colors <- RColorBrewer::brewer.pal(3, "Set1")
 
-compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
-compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
+# ggplot(md.fp, aes (x = prev_prior_derived_cv, y = cv_mean, ymin = cv_ci_lower, ymax = cv_ci_upper,
+#                    color = type))+
+#   #scale_alpha_manual(values = c(1,1,1,0.5))+
+#   geom_errorbar(alpha = 0.4)+
+#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+#   geom_point(data = md.fp %>% filter(type == "other"), size = 2)+
+#   geom_point(data = md.fp %>% filter(!(type == "other")), size = 2)+
+#   coord_fixed()+
+#   #scale_color_solarized()+
+#   scale_color_manual(values = c(fill.colors, "grey8"))+
+#   xlab("Prevalence Prior Derived Cue Validity")+
+#   ylab("Free Production Measured Cue Validity")+
+#   theme(legend.title = element_blank())
+
+r2.fp <- compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
+mse.fp <- compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
+n.fp <- length(md.fp$item)
 
@@
 
-compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
-compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+r2.fp.desid <- compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+mse.fp.desid <- compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+n.fp.desid <- length(md.fp.desid$item)
 ```
@@
     wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
-  ), target.items2)
+  ), target.items2) %>%
+  mutate(type = ifelse(is.na(type), "other", type),
+           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
+                       labels = c("diagnostic", "undiagnostic", "false", "other")))
 
-ggplot(md.dq, aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
-                     color = type))+
-  geom_point()+
-  geom_errorbar()+
-  ylim(0, 1) + xlim(0, 1)+
-  coord_fixed()
-
-compute_r2(md.dq, "mean", "prev_prior_derived_cv")
-compute_mse(md.dq, "mean", "prev_prior_derived_cv")
+# ggplot(md.dq, aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
+#                      color = type))+
+#   geom_errorbar(alpha = 0.4)+
+#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+#   geom_point(data = md.dq %>% filter(type == "other"), size = 2)+
+#   geom_point(data = md.dq %>% filter(!(type == "other")), size = 2)+
+#   coord_fixed()+
+#   #scale_color_solarized()+
+#   scale_color_manual(values = c(fill.colors, "grey8"))+
+#   xlab("Prevalence Prior Derived Cue Validity")+
+#   ylab("Direct Question Measured Cue Validity")+
+#   theme(legend.title = element_blank())
+# 
+#   
+r2.dq <- compute_r2(md.dq, "mean", "prev_prior_derived_cv")
+mse.dq <- compute_mse(md.dq, "mean", "prev_prior_derived_cv")
+n.dq <- length(md.dq$item)
 
@@
 
-compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
-compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
+r2.dq.desid <- compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
+mse.dq.desid <- compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
+n.dq.desid <- length(md.dq.desid$item)
 
+prevprior.cv.scatters <- bind_rows(
+  md.fp %>%
+    rename(mean = cv_mean, ci_lower = cv_ci_lower, ci_upper = cv_ci_upper) %>%
+    mutate(src = "Free production"),
+  md.dq %>%
+    mutate(src = "Direct question")
+) %>%
+  ggplot(., aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
+                     color = type))+
+  geom_errorbar(alpha = 0.4)+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  geom_point(data = . %>% filter(type == "other"), size = 2)+
+  geom_point(data = . %>% filter(!(type == "other")), size = 2)+
+  coord_fixed()+
+  #scale_color_solarized()+
+  scale_color_manual(values = c(fill.colors, "grey8"))+
+  xlab("Prevalence Prior Derived Cue Validity")+
+  ylab("Measured Cue Validity")+
+  theme(legend.title = element_blank(),
+        legend.position = 'bottom',
+        legend.direction = 'horizontal')+
+  facet_wrap(~src)
 ```
+
+```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, fig.cap="Top: Empirically measured cue validity for two different tasks.
+Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
+Dotted lines denote theoretical cue validity representing the desiderata (see text).
+Error bars denote bootstrapped 95% confidence intervals.
+Bottom left: Raw empirical distributions for direct question task.
+Bottom right: Correspondence between measured cue validity and prevalence prior derived cue validity."}
+grid.arrange(cv.bothquestions.bars, 
+             dq.histograms, 
+             prevprior.cv.scatters,
+             ncol = 4,
+             layout_matrix = cbind(c(1,1,2,2),
+                                   c(1,1,2,2),
+                                   c(1,1,3,3),
+                                   c(1,1,3,3)
+                                   ))
+```
+
+## Comparison with prevalence prior derived cue validity
+
+We can further understand our measures of cue validity by comparing them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
+Expt.
+1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated.
+(Participants freely generated the other half).
+Thus, we do not have the best measurement of the prior probability of categories $P(k)$.
+
+In this analysis, we treat each category entry from Expt. 1a (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
+This will result in the prevalence prior favoring kinds that are easy to produce (like dogs and cats, which is plausibly a good approximation for $P(k)$) as well as favoring the experimentally supplied kinds (like mosquitos and robins).
+
+We compute cue validity from the prevalence prior using Bayes' rule. 
+Figure \ref{fig:cv-bothquestions-barplots} (bottom right) shows the two measurements of cue validity as they relate to the prevalence prior derived cue validity. 
+The prevalence prior derived cue validity is high associated with both measurements: $r_{direct}^2(`r n.dq`) = `r r2.dq`; MSE_{direct} = `r mse.dq`$ and $r_{free}^2(`r n.fp`) = `r r2.fp`; MSE_{free} = `r mse.fp`$.
+Of primary interest is how the measurements behave for for desiderata items. 
+We see that the prevalence prior derived cue validity converges with the free production measurement for the desiderata items ($r_{free}^2(`r n.fp.desid`) = `r r2.fp.desid`; MSE_{free} = `r mse.fp.desid`$), whereas the direct question measurement overestimates the cue validity of undiagnositic features ($r_{direct}^2(`r n.dq.desid`) = `r r2.dq.desid`; MSE_{direct} = `r mse.dq.desid`$).
+Interestingly, the direct question measurement consistently overestimates cue validity in comparison to the prevalence prior derived cue validity.
+
+## Summary
+
+*Cue validity* is often used as a measurement for understanding generic truth conditions. 
+We articulated three *a priori* boundary conditions for a measurement of cue validity, because we observe different measurements being used in the literature. 
+We found that the "free production" measurement (i.e., having participants generate categories given a feature), and not the direct question measurement (i.e., asking participants a likelihood judgment of the category given the feature), satisfied all three boundary conditions.
+In addition, cue validity derived from our prevalence prior measurement (Expt. 1a) also satisfied these boundary conditions. 
+We conclude that researchers interested in generic truth conditions should use a free production paradigm for measuring cue validity.
 

### 2017-08-08 paper/comgen-paper.Rmd
edits to first two grafs

@@
 Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
-We acquire such *generalizations* early in life, simply by observing instances and drawing inductive inferences [@Baldwin1993; @Xu2008; @Dewar2010].
-Once learners have the capacity to infer the intention of other cooperative agents, social learning can dramatically faciliate inductive reasoning [@Csibra2009; @Tomasello1999; @Butler2012].
-At around the first birthday, a child's mind gains access to a new, human-unique source of data: language.
+Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
+Other cooperative agents can facilitate this, and learners can draw stronger inductive inferences in social learning contexts [@Csibra2009; @Tomasello1999; @Butler2012].
+At around a child's first birthday, however, the mind gains access to a new, human-unique source of data: language.
 
@@
 -->
-Learning from language is important because many properties are costly to directly observe (e.g., being poisonous) or events statistically unlikely (e.g., observing lightning).
-Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
-But language also has the ability to refer to *generalization itself*.
-Generic meaning, or *genericity*, can be observed in seemingly disparate kinds of linguistic devices [@Carlson1977; @Carlson1995].
-Speakers communicate generalizations about categories (*generic language*; e.g., *Dogs bark*), about individual people (*habitual language*; e.g., "Mary swims after work."), about causal events (*causal language*; e.g., "Drinking moonshine makes you go blind."), and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+Learning from language is important because observations can be costly (e.g., a plant being poisonous) or statistically unlikely (e.g., lightning).
+Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a bird."; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
+Objects have many properties though; when speakers attach kind-labels to properties (e.g., *Birds fly*), listeners hear a *generalization*.
+The above example is a generalization about a category (*generic language*); individual entities can also be talked about in generalization (*habitual language*; e.g., "Mary swims after work.") in addition to causal events (*causal language*; e.g., "Drinking moonshine makes you go blind."), to name just a few.
+What these statements have in common is that they convey generalizations [also referred to as generic meaning, or *genericity*; @Carlson1977; @Carlson1995].
+
+<!-- and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017]. -->
 
@@
 
+```{r child = 'appendix-cueValidity.Rmd'}
+```
+
 ```{r child = 'appendix-alternativeRSAmodels.Rmd'}
 ```
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-```{r child = 'appendix-fullModelPosteriors.Rmd'}
-```

### 2017-08-08 paper/comgen-paper.Rmd
more edits to intro

@@
 Learning from language is important because observations can be costly (e.g., a plant being poisonous) or statistically unlikely (e.g., lightning).
-Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a bird."; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
-Objects have many properties though; when speakers attach kind-labels to properties (e.g., *Birds fly*), listeners hear a *generalization*.
+Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
+Objects have many properties though; when speakers attach kind-labels to properties (e.g., *Dogs bark*), listeners hear a *generalization*.
 The above example is a generalization about a category (*generic language*); individual entities can also be talked about in generalization (*habitual language*; e.g., "Mary swims after work.") in addition to causal events (*causal language*; e.g., "Drinking moonshine makes you go blind."), to name just a few.
@@
 Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
-It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].
+
+<!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
 
@@
 The major issue in formalizing genericity is determining what makes such statements true or false. 
-When we hear "Dogs bark", we may feel it's a universal statment, like *All* dogs bark.
+When we hear "Dogs bark", it feels like a universal statement, like *All* dogs bark.
 Yet, Basenji dogs are barkless^[
@@
 Indeed, many generalizations seem to have the quantificational force of *most*. 
-But most mosquitos do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
+But *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
 The only quantifier that would permit such a statement would be "Some" (e.g., *some mosquitos carry malaria*).
 But equating the generalization with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
-One might feel exceptions should be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.
+Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females.
 
@@
 By formalizing this semantic hypothesis in a pragmatic language understanding model, we derive predictions for the endorsements of such statements which we show to depend in systematic ways on relevant prior knowledge.
-Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
+Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
 <!-- We relate known measurements on factors regarding generic language to each other via our model. -->

### 2017-08-10 paper/comgen-paper.Rmd
new attempt at intro

@@
 
-Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
-Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
-Other cooperative agents can facilitate this, and learners can draw stronger inductive inferences in social learning contexts [@Csibra2009; @Tomasello1999; @Butler2012].
+Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an open-ended world.
+Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
+It thus is crucial that language allow us to communicate abstract ideas to each other.
+The most basic kind of abstract idea is a *generalization*
+
+*Generalizations* are acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
+Cooperative agents can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
 At around a child's first birthday, however, the mind gains access to a new, human-unique source of data: language.
+Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
+Objects have many properties though; when speakers attach properties to kind-labels (e.g., *Dogs bark*), listeners hear a *generalization*.
+
+Generalizations in language are often studied in *generic language* or generics.
+Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
+Around the age of two and a half, children begin to understand that *generic language* refers to abstract categories and conveys information that extend beyond the present context [@Cimpian2008].
+It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and such generalizations in language are thought to be central to the growth of conceptual knowledge [@Gelman2004].
+<!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
+Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
+
+Generic statements ascribing properties to categories are just one kind of generalization found in language. 
+Individual entities can also be talked about in generalization using so-called *habitual language* (e.g., "Mary swims after work.").
+<!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+-->
+Communicating about causality can also take the form of communicating a generalization about a causal event (*causal language*; e.g., "Drinking moonshine makes you go blind.").
+What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995].
 
@@
 -->
-Learning from language is important because observations can be costly (e.g., a plant being poisonous) or statistically unlikely (e.g., lightning).
-Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
-Objects have many properties though; when speakers attach kind-labels to properties (e.g., *Dogs bark*), listeners hear a *generalization*.
-The above example is a generalization about a category (*generic language*); individual entities can also be talked about in generalization (*habitual language*; e.g., "Mary swims after work.") in addition to causal events (*causal language*; e.g., "Drinking moonshine makes you go blind."), to name just a few.
-What these statements have in common is that they convey generalizations [also referred to as generic meaning, or *genericity*; @Carlson1977; @Carlson1995].
-
 <!-- and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017]. -->
-
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995].
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and around the age of two and a half, children begin to understand that *generic language* refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
-Because of its powerful implications, generalizations in language are thought to be central to the growth of conceptual knowledge [@Gelman2004].
-<!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
-Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 
@@
 
-Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
-Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
-Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
+Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had received a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
+Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
+Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
+They refers to concepts in the head and have proved tricky to formalize.
 <!-- The language of generalization is exceedingly difficult to formalize, however. -->
@@
 
-The major issue in formalizing genericity is determining what makes such statements true or false. 
+The major issue in formalizing generalizations in language is determining what makes such statements true or false.
 When we hear "Dogs bark", it feels like a universal statement, like *All* dogs bark.
-Yet, Basenji dogs are barkless^[
+But the property doesn't apply to all dogs: Basenji dogs are barkless^[
 http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-]; the generalization instead should signal something weaker like *Most* dogs bark.
-Indeed, many generalizations seem to have the quantificational force of *most*. 
-But *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
+].
+So, the generalization should signal something weaker like *Most* dogs bark.
+<!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
+However, *Mosquitos carry malaria* is intuitively a true statement, despite less than 1\% of moquitos actually carrying malaria.
+<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
 The only quantifier that would permit such a statement would be "Some" (e.g., *some mosquitos carry malaria*).
-But equating the generalization with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
-Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females.
-
-In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to articulate a formal theory of the truth conditions of generalizations in language. 
-By formalizing this semantic hypothesis in a pragmatic language understanding model, we derive predictions for the endorsements of such statements which we show to depend in systematic ways on relevant prior knowledge.
+But weakening the generalization to *some* goes too far: Half of robins are female, but saying *Robins are female* seems odd.
+That same half of robins, however, also lay eggs, and *Robins lay eggs* is again intuively reasonable.
+
+<!-- Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females. -->
+<!-- Generics roughly convey that the properties is widespread in the category (e.g., *Most dogs are friendly*), however they don't always imply the same degree of prevalence. -->
+<!-- *Birds are female* sounds strange even though half of birds of female.  -->
+
+In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
+We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
+We show that this decision depends in systematic ways on the prior knowledge of the listener.
 Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
@@
 <!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-We do this in three domains: generalizations about categories, events, and causes.
-We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fall short.
-
-The rest of this paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in our three domains. 
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a general framework for pragmatic language understanding -- the Rational Speech Act framework.
+Our three case studies correspond to generalizations about categories, events, and causes.
+We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
+
+The paper is organized as follows. 
+In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in our three case studies. 
+In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a framework for pragmatic language understanding -- the Rational Speech Act framework.
 
@@
 In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's intended message in communicating generalizations about causes, or *causal language*.
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
+Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
 In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.

### 2017-08-10 paper/comgen-paper.Rmd
tightening intro rewrite

@@
 Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
-It thus is crucial that language allow us to communicate abstract ideas to each other.
-The most basic kind of abstract idea is a *generalization*
-
-*Generalizations* are acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
+It thus is crucial that language allow us to communicate such *generalizations* to each other.
+<!-- The most basic kind of abstract idea is a *generalization* -->
+
+Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
 Cooperative agents can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
-At around a child's first birthday, however, the mind gains access to a new, human-unique source of data: language.
+At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
 Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
-Objects have many properties though; when speakers attach properties to kind-labels (e.g., *Dogs bark*), listeners hear a *generalization*.
+Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.
 
@@
 Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-Around the age of two and a half, children begin to understand that *generic language* refers to abstract categories and conveys information that extend beyond the present context [@Cimpian2008].
+Around the age of two and a half, children begin to understand that generic language refers to categories and conveys information that extends beyond the present context [@Cimpian2008].
 It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and such generalizations in language are thought to be central to the growth of conceptual knowledge [@Gelman2004].
@@
 Generic statements ascribing properties to categories are just one kind of generalization found in language. 
-Individual entities can also be talked about in generalization using so-called *habitual language* (e.g., "Mary swims after work.").
+Individual entities can also be talked about in generalization, using so-called *habitual language* (e.g., "Mary swims after work.").
 <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
@@
 
-Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had received a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
 Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 

### 2017-08-10 paper/comgen-paper.Rmd
edit intro

--- 2017-08-08 paper/comgen-paper.Rmd
@@
     Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible in communicating generalizations.
-    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (i.e., *generic language*, e.g., *Birds fly*), events (i.e., *habitual language*, e.g., *John runs*), and causes (i.e., *causal language*, e.g., *The block makes the machine play music.*).
-Across these divesre domains, we find that our model, and not simpler models, explains the full spectra of endorsements of generalizations in language.
-    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
+    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible. 
+    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language*, such as *Birds fly*), events (*habitual language*, such as *John runs*), and causes (*causal language*, such as *The block makes the machine play music.*).
+Across these diverse domains, we find that our model explains the full spectra of endorsements of generalizations in language, while simpler models do not.
+    These results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
 
@@
 
-```{r figure-causals, fig.width=11, fig.height=8, cache = F}
+```{r figure-causals, fig.width=11, fig.height=8, cache = T}
 grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,

### 2017-08-10 paper/comgen-paper.Rmd
working on intro

@@
 
-Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
-Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
+The knowledge that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an uncertain world.
+Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. /ndg{older cites for this? hume?}
 Other cooperative agents can facilitate this, and learners can draw stronger inductive inferences in social learning contexts [@Csibra2009; @Tomasello1999; @Butler2012].
@@
 
+[XXX first three pars are floppy. tighten.
+There haven't been (many)? Formal models of generic language. Say why this is important.
+To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
+Then we need to say how these probabilities are communicated. Use RSA...]
+
 <!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
@@
 
-Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
-Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
-Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
 <!-- The language of generalization is exceedingly difficult to formalize, however. -->
@@
 Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females.
+
+Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
+Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
 

### 2017-08-10 paper/comgen-paper.Rmd

--- 2017-08-10 paper/comgen-paper.Rmd
@@
 
-Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an open-ended world.
+Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an open-ended world.
 Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-<!-- The most basic kind of abstract idea is a *generalization* -->
-
-Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
-Cooperative agents can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
+
+Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. [XXX cite older stuff. eg hume]
+Cooperative teachers can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
 At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
@@
 
-Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
-Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
-Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
-Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
-They refers to concepts in the head and have proved tricky to formalize.
 <!-- The language of generalization is exceedingly difficult to formalize, however. -->
@@
 
+Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
+Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
+Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
+They refers to concepts in the head and have proved tricky to formalize.
+
 In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
@@
 We show that this decision depends in systematic ways on the prior knowledge of the listener.
+
 Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.

### 2017-08-10 paper/comgen-paper.Rmd
fix /ndg /mht inline commenting commands

@@
     Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible. 
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language*, such as *Birds fly*), events (*habitual language*, such as *John runs*), and causes (*causal language*, such as *The block makes the machine play music.*).
-Across these diverse domains, we find that our model explains the full spectra of endorsements of generalizations in language, while simpler models do not.
-    These results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
+    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible in communicating generalizations.
+    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (i.e., *generic language*, e.g., *Birds fly*), events (i.e., *habitual language*, e.g., *John runs*), and causes (i.e., *causal language*, e.g., *The block makes the machine play music.*).
+Across these divesre domains, we find that our model, and not simpler models, explains the full spectra of endorsements of generalizations in language.
+    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
 
@@
 \definecolor{Blue}{RGB}{10,100,200}
-<!-- \newcommand{\ndg}[1]{\textcolor{Green}{$[ndg: #1 ]$}} -->
-<!-- \newcommand{\mht}[1]{\textcolor{Blue}{$[mht: #1 ]$}} -->
-<!-- \newcommand{\red}[1]{\textcolor{Red}{$#1$}} -->
+
+\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
+\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
+\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
 
@@
 
-Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an open-ended world.
+Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an open-ended world.
 Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-
-Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. [XXX cite older stuff. eg hume]
-Cooperative teachers can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
+<!-- The most basic kind of abstract idea is a *generalization* -->
+
+Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
+Cooperative agents can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
 At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
@@
 
-[XXX first three pars are floppy. tighten.
-There haven't been (many)? Formal models of generic language. Say why this is important.
-To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
-Then we need to say how these probabilities are communicated. Use RSA...]
-
 <!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
@@
 
+Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
+Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
+Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
+They refers to concepts in the head and have proved tricky to formalize.
 <!-- The language of generalization is exceedingly difficult to formalize, however. -->
@@
 
-Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
-Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
-Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
-Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
-They refers to concepts in the head and have proved tricky to formalize.
-
 In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
@@
 We show that this decision depends in systematic ways on the prior knowledge of the listener.
-
 Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
@@
 
-```{r figure-causals, fig.width=11, fig.height=8, cache = T}
+```{r figure-causals, fig.width=11, fig.height=8, cache = F}
 grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,

### 2017-08-10 paper/comgen-paper.Rmd
minor changes

--- 2017-08-10 paper/comgen-paper.Rmd
@@
 
-Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
+Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in an open-ended world.
+Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just rare (e.g., understanding the properties of lightning).
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
+By sharing painfully-won generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
 

### 2017-08-11 paper/comgen-paper.Rmd
edits to formal view section

--- 2017-08-10 paper/comgen-paper.Rmd
@@
 
-Particular statements can be made about objects, events, and causes (e.g., "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind.").
-To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
-We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
-Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
+Particular statements can be made about objects, events, and causes. For example:
+
+1. My dog is friendly. (object)
+2. John ran this afternoon. (event)
+3. My grandfather drank moonshine and it made him go blind. (cause)
+
+Particular statements refer to individuals of a category of which generalizatons can be made. For example,
+
+4. Dogs are friendly
+5. John runs
+6. Drinking moonshines makes you go blind
+
+That is, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
 

### 2017-08-11 paper/comgen-paper.Rmd
wip

--- 2017-08-10 paper/comgen-paper.Rmd
@@
 
-Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in an open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just rare (e.g., understanding the properties of lightning).
+Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in our open-ended world.
+Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding the properties of lightning).
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-By sharing painfully-won generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
-
-Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. [XXX cite older stuff. eg hume]
-Cooperative teachers can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
+By sharing generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
+Furthermore, sharing generalizations from one generation to the next may be a crucial mechanism behind the cultural ratchet \ndg{cite. or remove if you don't like it here}.
+
+Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume}
+Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
 At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
@@
 Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.
+\ndg{this par doesn't really do much}
 
@@
 
-[XXX first three pars are floppy. tighten.
-There haven't been (many)? Formal models of generic language. Say why this is important.
+\ndg{prev three pars are floppy. tighten.
+There haven't been (many?) formal models of generic language. Say why this is important.
 To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
-Then we need to say how these probabilities are communicated. Use RSA...]
+Then we need to say how these probabilities are communicated. Use RSA...}
 

### 2017-08-19 paper/comgen-paper.Rmd
minor edits to generics section

@@
 We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
-\ref{eq:L0} as well as the target-category prevalence $h$ that the speaker model seeks to convey in Eq.
+\ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq.
 \ref{eq:S1} (Expt.
@@
 The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are on an alien planet and you come across your favorite kind of animal from Earth.
-Now try to predict whether or not that animal is female.
-To get an intuition for your subjective probability, ask yourself "What percentage of that kind of animal is female?".
-The answer is probably 50\%. 
-Now try to predict whether or not that animal lays eggs (or, "What percentage of that kind of animal lays eggs?").
-Depending on what your favorite animal is, the answer is probably either 50\% or 0\% (e.g., if your favorite animal is a dog, there is a 0\% chance that it lays eggs)^[
-The subjective probability may, in fact, be non-zero but very small.
-This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with the alien environment.
+To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
+Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
+Now, do you think it lays eggs?
+Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; If you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
+That is, the answer is either 50\% or 0\% depending on the kind of creature we are thinking of.
+^[
+The subjective probability may, in fact, be non-zero in what we're calling as 0\%, non-zero but very small.
+This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a foreign environment.
 ].
 
-This decomposition of the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
-We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
-We then ask whether a structured, prior model accounts better for this data than an unstructured model.
+This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$.
+We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
+We measured prior distributions empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
+After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.
 
@@
 The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
+Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
 ]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
@@
 <!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
-<!-- However, cue validity requires knowledge of the target category $k$ -->
+<!-- However, cue validity requires knowledge of the referent-category $k$ -->
 
@@
 <!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
-<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.
+<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the referent-category.
 -->
@@
 In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
-This data also includes informaiton about the target-category prevalence (e.g., how many robins lay eggs).
-Using the target-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
+This data also includes information about the referent-category prevalence (e.g., how many robins lay eggs).
+Using the referent-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
 To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
@@
 This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
-However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
+However, large deviations from an account based purely on referent-category prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
 
@@
 The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
-Unlike the simple regression models based on point-estimates of target-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
+Unlike the simple regression models based on point-estimates of referent-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
 This model has two other main architectural differences: an information-theoretic decision between producing the generic vs.
@@
 <!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$).
--->
-We use the empirically estimated target-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
+\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the referent-category $h'$).
+-->
+We use the empirically estimated referent-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
 1a as the listener's prevalence prior $P(h)$.^[
@@
 The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (prevalences, prevalence priors, and the speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the target-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the referent-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1a).
@@
 
-MHT: Outfit fixed-threshold model with noise parameter?
+\mht{Outfit fixed-threshold model with noise parameter?}
 
@@
 To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the target category (also in blue).
+The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the referent-category (also in blue).
 The grey distribution shows the listener's prior distribution over prevalence of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
@@
 
-<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g.
+<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which referent-category prevalence is not a good indicator of the acceptability (e.g.
 \emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
@@
 <!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
-<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a target category. -->
+<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a referent-category. -->
 <!--     (b) -->
-<!--     Human acceptability judgments compared with model predictions (left) and the target-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
-<!--     Color denotes target-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
+<!--     Human acceptability judgments compared with model predictions (left) and the referent-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
+<!--     Color denotes referent-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
 <!--      Error bars denote 95\% Bayesian credible intervals. -->
@@
 
-In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the target category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
+In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
 Thus, we have shown how these measurements are related to generic endorsement via our model. 
@@
 <!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the target category belong?".
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
 This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
@@
 -->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the target category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
+<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
 -->
@@
 We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the target category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
+<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
 
@@
 Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the target category (i.e., books), the true prevalence of the feature among the target category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
+From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true prevalence of the feature among the referent-category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
 Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Birds are female".

### 2017-08-25 paper/comgen-paper.Rmd
minor
revise stuff about generalization

@@
 \ndg{prev three pars are floppy. tighten.
-There haven't been (many?) formal models of generic language. Say why this is important.
+There haven't been many formal models of generic language, none have made quantitative predictions. Say why this is important.
 To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
@@
 
-# A Formal View of Generalization
-
-Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
+# Generalization from observations
+
+Generalizations are used to make predictions about properties instances that an agent has yet to experience [@HumeTHN]. 
 From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
-To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
-This is faciliated through the use of labeling; the linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
-To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
-That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
-We call this latter kind of statement a *particular*.
-
-```{r table-generalization, results="asis"}
-df.tab <- data.frame(
-  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
-  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
-  "Generalization over" = c("Category", "Event", "Cause"),
-  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
-  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
-  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
-  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
-) %>% xtable(.,
-         caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
-        label = c("tab:genpart"))
-
-# apa_table(df.tab, 
-#           caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
-#           escape = TRUE, small = TRUE
-# )
-
-print(df.tab, type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-Particular statements can be made about objects, events, and causes. For example:
-
-1. My dog is friendly. (object)
-2. John ran this afternoon. (event)
-3. My grandfather drank moonshine and it made him go blind. (cause)
-
-Particular statements refer to individuals of a category of which generalizatons can be made. For example,
-
-4. Dogs are friendly
-5. John runs
-6. Drinking moonshines makes you go blind
-
-That is, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
-
-Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
-For properties among instances of a category (e.g., being friendly among dogs), we can describe this inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
-With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
-].
-<!-- In the study of categories and properties, $x$ is an object. -->
-For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
-<!-- In this case, $x$ is a instance of an agent. -->
-Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
-Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency of some instance in a category.
+As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
+In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
+The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
+The properties can vary greatly (e.g. having fur, causing jitters, typing). 
+Yet the prediction for a new entity can be described as a *predictive probability*: 
+$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.
+\ndg{say what we call $h$ throughout. prevalence?}
+
+<!-- To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category. -->
+<!-- This is faciliated through the use of labeling; the linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..." -->
+<!-- To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature. -->
+<!-- That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$". -->
+<!-- We call this latter kind of statement a *particular*. -->
+
+<!-- ```{r table-generalization, results="asis"} -->
+<!-- df.tab <- data.frame( -->
+<!--   Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"), -->
+<!--   #x = c("an instance of K in space", "an instance of K in time", "an instance of a "), -->
+<!--   "Generalization over" = c("Category", "Event", "Cause"), -->
+<!--   "Linguistic construct" = c("Generic", "Habitual", "Causal"), -->
+<!--   x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"), -->
+<!--   k = c("DOGS", "JOHN", "DRINKING MOONSHINE"), -->
+<!--   f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind") -->
+<!-- ) %>% xtable(., -->
+<!--          caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."), -->
+<!--         label = c("tab:genpart")) -->
+
+<!-- # apa_table(df.tab,  -->
+<!-- #           caption = "Decomposition of generalizations into concrete particulars and corresponding properties.",  -->
+<!-- #           escape = TRUE, small = TRUE -->
+<!-- # ) -->
+
+<!-- print(df.tab, type = "latex",  -->
+<!--       tabular.environment = "tabularx", width = "\\textwidth", -->
+<!--       scalebox='0.75', -->
+<!--       include.rownames = FALSE, comment = F) -->
+<!-- ``` -->
+
+<!-- Particular statements can be made about objects, events, and causes. For example: -->
+
+<!-- 1. My dog is friendly. (object) -->
+<!-- 2. John ran this afternoon. (event) -->
+<!-- 3. My grandfather drank moonshine and it made him go blind. (cause) -->
+
+<!-- Particular statements refer to individuals of a category of which generalizatons can be made. For example, -->
+
+<!-- 4. Dogs are friendly -->
+<!-- 5. John runs -->
+<!-- 6. Drinking moonshines makes you go blind -->
+
+<!-- That is, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
+-->
+
+<!-- Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
+-->
+<!-- For properties among instances of a category (e.g., being friendly among dogs), we can describe this inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[ -->
+<!-- With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$. -->
+<!-- ]. -->
+<!-- <!-- In the study of categories and properties, $x$ is an object. --> -->
+<!-- For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$ -->
+<!-- <!-- In this case, $x$ is a instance of an agent. --> -->
+<!-- Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
+-->
+<!-- Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency of some instance in a category. -->
 <!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->
@@
 <!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
-Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
+
+The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
+Observing some number of instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
 As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
@@
 
-The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
-Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
+Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
 For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
@@
 
-# Formalizing Generalizations in Language
+# Generalization from Language
 

### 2017-08-29 paper/comgen-paper.Rmd
add a note
rewrite introduction to incorporate generics literature and tighten

@@
 
-Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding the properties of lightning).
+Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be necessary to thrive in our open-ended world.
+Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
-Furthermore, sharing generalizations from one generation to the next may be a crucial mechanism behind the cultural ratchet \ndg{cite. or remove if you don't like it here}.
-
-Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume}
-Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
-At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
-Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
-Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.
-\ndg{this par doesn't really do much}
-
-Generalizations in language are often studied in *generic language* or generics.
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-Around the age of two and a half, children begin to understand that generic language refers to categories and conveys information that extends beyond the present context [@Cimpian2008].
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and such generalizations in language are thought to be central to the growth of conceptual knowledge [@Gelman2004].
+By sharing generalizations we flourish collectively without individually needing to taste each potentially-poisonous plant or witness enough lightning strikes.
+Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
+
+<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
+<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
+<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
+<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
+-->
+<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
+<!-- \ndg{this par doesn't really do much} -->
+
+Generalizations in language are often studied in *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+In contrast to *particular statements* which describe individual entities or situations (e.g., "Rufus is friendly") and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which two-and-a-half-year-olds recognize [@Cimpian2008].
+<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
+-->
+Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
+Generalizations are not limited to generics, however; they can be found in statements about individuals (*habitual language*; e.g., "Mary swims after work.") as well as causal events (*causal language*; e.g., "Staring at the sun makes you go blind.").
+It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
+
+<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
+<!-- Individual entities can also be talked about in generalization, using so-called  -->
+<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
+-->
+<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
+<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
+
+Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about observable behavior.
+A formal model in this domain is advantageous to make explicit the relevant assumptions of a psychological or linguistic hypothesis for predicting human behavior; this, in turn, makes the theory more falsifiable.
+The major challenge in formalizing generalizations in language is determining what makes such statements true or false.
+When we hear "Dogs bark", it feels like a universal statement, like *All* dogs bark.
+But the property doesn't apply to all dogs: Basenji dogs are barkless^[
+http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
+].
+The generalization could signal something weaker like *Most* dogs bark.
+<!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
+However, less than 1\% of moquitos actually carry malaria and still "Mosquitos carry malaria" is intuitively true.
+<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
+The only quantifier that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
+But weakening the generalization to *some* goes too far: Half of robins are female, but saying "Robins are female" seems odd.
+That same half of robins (i.e., the females), however, also lay eggs, and "Robins lay eggs" is intuively reasonable.
+
+These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of category having a property) is only incidentally related to generic meaning.
+**Conceptual accounts** of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
+
+With this perspective, @Leslie2007 proposes generics express a cognitively primitive, default generalization. 
+The *generics as default* view argues that certain principles explain how generics become true or false.
+"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know about if you are trying to survive in a hostile world.
+This theory correctly predicted that generics that convey striking properties would be true even if the property were relatively rare [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
+"Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].
+
+Yet, generics are not limited to conveying rich, conceptual relations. 
+Arbitrary relationships can also be expressed with generics (e.g., "Barns are red"; "Ravens are bigger than toasters") which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
+The *generics as default* view must then be supplemented with the principle that, in certain situations, statistics influence generic endorsement.
+The diversity of generic statements highlighted by this view is interesting, but insofar as generics are a single, unified phenomenon, there should be a general, unified principle that explains what makes the statements true or false.
+<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
+-->
+<!-- This diversity is interesting, but what is common across generics? -->
+<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
+
+We propose a formal, unified account of generalizations in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
+We do so by first describing the much more well-studied form of generalization: generalization from observations. 
+The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is a good model of human generalizations [@Shepard1987; @Tenenbaum2001].
+We then formalize how these probabilities are communicated, using a rational model of communication --- the Rational Speech Act theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016].
+Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals. 
+Heretofore, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
+The language of generalizations, however, does not make reference to entities in the world or concrete situations, but instead refers to concepts in the head.
+
+Specifically, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations concerns subjective probability in a *simple but underspecified* way.
+We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
+We show that this decision depends in systematic ways on the prior knowledge of the listener.
+
+Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
+<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
+Our three case studies correspond to generalizations about categories, events, and causes.
+We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
+
+The paper is organized as follows. 
+In Section 1, we describe the Bayesian framework for generalization from observations, serving as the foundation for our semantic theory.
+In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a framework for pragmatic language understanding -- the Rational Speech Act framework.
+
+To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
+Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
+In Section 3, we describe experiments the measure both quantities and relate them via our model to the endorsements of generalizations about categories, or *generic language*. 
+In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events, or *habitual language*.
+In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes, or *causal language*.
+Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
+In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
+Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language in the way that people learn from language.
+
+<!-- (2) It also allows us to consider sources of gradience in behavior, determining whether or not we should allocate it to *noise* in the observed data or to *uncertainty* in the head of the language user.
+-->
 <!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
-Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
-
-Generic statements ascribing properties to categories are just one kind of generalization found in language. 
-Individual entities can also be talked about in generalization, using so-called *habitual language* (e.g., "Mary swims after work.").
-<!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-Communicating about causality can also take the form of communicating a generalization about a causal event (*causal language*; e.g., "Drinking moonshine makes you go blind.").
-What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995].
+
+<!-- \ndg{There haven't been many formal models of generic language, none have made quantitative predictions. Say why this is important. -->
+<!-- To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities. -->
+<!-- Then we need to say how these probabilities are communicated. Use RSA...} -->
+
+<!-- Rational models of communication have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
+-->
 
@@
 
-\ndg{prev three pars are floppy. tighten.
-There haven't been many formal models of generic language, none have made quantitative predictions. Say why this is important.
-To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
-Then we need to say how these probabilities are communicated. Use RSA...}
-
 <!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
@@
 
-The major issue in formalizing generalizations in language is determining what makes such statements true or false.
-When we hear "Dogs bark", it feels like a universal statement, like *All* dogs bark.
-But the property doesn't apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-].
-So, the generalization should signal something weaker like *Most* dogs bark.
-<!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
-However, *Mosquitos carry malaria* is intuitively a true statement, despite less than 1\% of moquitos actually carrying malaria.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "Some" (e.g., *some mosquitos carry malaria*).
-But weakening the generalization to *some* goes too far: Half of robins are female, but saying *Robins are female* seems odd.
-That same half of robins, however, also lay eggs, and *Robins lay eggs* is again intuively reasonable.
-
 <!-- Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females. -->
@@
 <!-- *Birds are female* sounds strange even though half of birds of female.  -->
-
-Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
-Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
-Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
-Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
-They refers to concepts in the head and have proved tricky to formalize.
-
-In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
-We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
-We show that this decision depends in systematic ways on the prior knowledge of the listener.
-
-Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-Our three case studies correspond to generalizations about categories, events, and causes.
-We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
-
-The paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in our three case studies. 
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a framework for pragmatic language understanding -- the Rational Speech Act framework.
-
-To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
-Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments the measure both quantities and relate them to the endorsements of generalizations about categories, or *generic language*. 
-In Section 4, we describe experiments that manipulate the speaker's intended message in communicating generalizations about events, or *habitual language*.
-In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's intended message in communicating generalizations about causes, or *causal language*.
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
-In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
-Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language like people.
 
@@
 
-# Generalization from observations
+# Generalization from Observations
 
@@
 
-We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
 Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly").
-Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .
-
+Bare plural statements (e.g., "Dogs are friendly") tend to yield a generic meaning, though other forms can express such a meaning [e.g., "A mongoose eats snakes."; @Carlson1977] .
 Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
-At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
-*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs, which is debatable whether or not that counts as *most robins*. 
+At first glance, generics convey that *most* have the property, such as "Most dogs are friendly".
+"Robins lay eggs" is true, though, despite the fact that only female robins lay eggs.
 If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
-Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
+Finally, "Mosquitos carry malaria" is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
 It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.
-
-These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
-**Conceptual accounts** of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as a special way of expressing mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
-The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.
-
-The *generics as default* view argues that general cognitive principles explain why certain generics are true or not.
-*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
-This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which was empirically corroborated [@Cimpian2010; @Prasada2013].
-Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].
-
-Yet, generics are not limited to conveying rich relations. 
-Arbitrary relationships can also be expressed (e.g., *Barns are red*; *Ravens are bigger than toasters*) which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
-The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
-It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
-This diversity is interested, but what is common across generics?
-Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false?
 
@@
 Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
-Thee basic currency of inference in these models is probability.
-In generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
+The basic currency of inductive reasoning in these models is probability.
+If generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
+
+\ndg{move all this background about generics earlier, so that this section can go straight to our model.}
+
+We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
+
 <!-- In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability. -->

### 2017-08-29 paper/comgen-paper.Rmd
small edits to gen from obs; begin editing gen from lang

@@
 Generalizations are used to make predictions about properties instances that an agent has yet to experience [@HumeTHN]. 
-From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
+From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
 As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
@@
 The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
-The properties can vary greatly (e.g. having fur, causing jitters, typing). 
-Yet the prediction for a new entity can be described as a *predictive probability*: 
-$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.
-\ndg{say what we call $h$ throughout. prevalence?}
+The properties can vary greatly (e.g., having fur, causing jitters, typing). 
+Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **prevalence**: 
+$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
+We denote prevalence as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency.
+]
 
@@
 Observing some number of instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
-As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).
+As a concrete example, consider the feature \textsc{is friendly} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
+If an agent were to encounter some number of individual dogs and note how many of them were friendly ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).
 
@@
 For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
-This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
-Observations that are generated by an intentional agent can similar lead to subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].
+This subtlety can be modeled using heirarchical models to provide structure to the prior distribution in a Bayesian model [@Kemp2008].
+Observations that are generated by an intentional agent can lead to similarly subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].
 
 Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
-Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
+Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to costly to observe (e.g., *starting at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
 For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
@@
 # Generalization from Language
+
+If generalization from observations can be described using probability, then it seems very natural to consider the semantic content of generalizations in language as relating to probability. 
+One very simple semantic theory that has been used for describing quantified statements is a *threshold semantics*:
 
@@
 <!-- If that's true, a simple, semantic theory  -->
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
-&\propto  &
-\begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}
-\end{eqnarray}
 

### 2017-08-29 paper/comgen-paper.Rmd
more edits to gen from lang

@@
 
-If generalization from observations can be described using probability, then it seems very natural to consider the semantic content of generalizations in language as relating to probability. 
-One very simple semantic theory that has been used for describing quantified statements is a *threshold semantics*:
-
-Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly").
-Bare plural statements (e.g., "Dogs are friendly") tend to yield a generic meaning, though other forms can express such a meaning [e.g., "A mongoose eats snakes."; @Carlson1977] .
-Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
-At first glance, generics convey that *most* have the property, such as "Most dogs are friendly".
-"Robins lay eggs" is true, though, despite the fact that only female robins lay eggs.
-If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
-Finally, "Mosquitos carry malaria" is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
-It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.
-
-We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction.
-We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities. 
-Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
-The basic currency of inductive reasoning in these models is probability.
-If generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:
-
-\ndg{move all this background about generics earlier, so that this section can go straight to our model.}
-
-We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
+If generalization from observations can be described using probability, then it seems very natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
+One very simple semantic theory that has been used for describing quantified statements (e.g., "some", "all") is a *threshold semantics*.
+For generalizations, the threshold would apply to the subjective probability or *prevalence* $h$:
+
+\begin{eqnarray}
+\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
+&\propto  &
+\begin{cases}
+1 & \text{if } h > \theta \\
+0 & \text{otherwise}
+\end{cases}
+\end{eqnarray}
+
+<!-- Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly").
+-->
+<!-- Bare plural statements (e.g., "Dogs are friendly") tend to yield a generic meaning, though other forms can express such a meaning [e.g., "A mongoose eats snakes."; @Carlson1977] . -->
+<!-- Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
+-->
+<!-- At first glance, generics convey that *most* have the property, such as "Most dogs are friendly". -->
+<!-- "Robins lay eggs" is true, though, despite the fact that only female robins lay eggs. -->
+<!-- If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make? -->
+<!-- Finally, "Mosquitos carry malaria" is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos. -->
+<!-- It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.  -->
+
+<!-- We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction. -->
+<!-- We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities.  -->
+<!-- Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
+-->
+<!-- The basic currency of inductive reasoning in these models is probability. -->
+<!-- If generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$: -->
+
+<!-- We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
+-->
 
@@
 
-$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
+$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for probabilities $h$ greater than threshold $\theta$ and $0$ otherwise. 
 Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
@@
 To answer this, we draw a metaphor to Bayesian statistics and data analysis.
-When there is a latent parameter the Bayesian scientist doesn't know much about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
+When there is a latent parameter the Bayesian scientist does not know much about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
 In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$ (in the form of a prior distribution $P(\theta)$) and infers $\theta$ in context (i.e., after having heard the utterance).
-Though it's possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across context and is completely uninformed: $P(\theta) = \text{Uniform}(0, 1)$.
+Though it is possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.
 
@@
 
-Equation \ref{eq:L0} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
-$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
-The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
-We term this prior distribution the *prevalence prior*.
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances described above.
+Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
+$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
+The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008; cf., $Prasada2006; Prasada2013].
+We term this prior distribution the **prevalence prior**.
+$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
 
@@
 
-This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
-Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
+This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold) but underspecified.
+Figure \ref{fig:simulations} shows model $L$'s posterior distribution on prevalence $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
 \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
-The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
-The fixed threshold model rules out only the lowest possible state and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.
-
-The intuition behind the model's behavior can be gleaned by imagining what the listener $L$ would believe with different thresholds and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
-If the threshold $\theta$  is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$  takes on lower and lower values, more and more $h$ probabilities would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
-When the listener averages over these possibilities, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.
-
-In this paper, we are interested in explaining the variable endorsements of generalizations (e.g., *Birds lay eggs* is good; *Birds are female* is not) based on some known or believed probability $h$ (e.g., only female birds lay eggs).^[A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that she is trying to communicate.
-Rather, the speaker may have a belief distribution over $h$ for the category. $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
+The differences in the semantics are easily seen when considering a uniform prior distribution over $h$ (top left facet).
+The fixed threshold model rules out only the lowest possible prevalence ($h=0$) and returns a posterior very similar to the prior.
+The behavior of the generalization is distinct: The higher the $h$, the more likely it is after hearing the generalization.
+
+The intuition behind the model's behavior can be gleaned by imagining what the listener $L$ would believe given different thresholds and averaging over those possibilities.
+If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold.
+If the threshold $\theta$ is slightly lower but still high, the highest $h$ would still pass the threshold, as would some that are slightly lower.
+As the threshold $\theta$  takes on lower and lower values, more and more $h$'s would surpass it.
+When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
+When the listener averages over these possibilities, $h$'s with higher values pass more thresholds; thus, higher $h$'s are more likely *a posteriori*.
+
+In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
+Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
+\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that she is trying to communicate.
+Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
 In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
@@
 ]
-Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).
+
 \begin{equation} 
@@
 In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
-Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
+Following RSA, the speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
 Since the speaker $S$ doesn't know the threshold $\theta$, she must integrate over the likely values that the listener will infer.
 
-The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
+The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
 To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
@@
 The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-These are not of primary theoretical interest to this paper, as *any* formal model that explains the very flexible endorsement patterns of generalizations in language will be a substantial contribution.
+These are not of primary theoretical interest to this paper, as *any* formal model that explains the very flexible endorsement patterns of generalizations in language will be a substantial advancement.
 However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
@@
 <!-- Though intuitively appealing and simple, this threshold-based truth function for a generalization is problematic. -->
-<!-- <!-- fixed value of $\theta$ seems unlikely. --> -->
+<!-- <!-- fixed value of $\theta$ seems unlikely. -->
 <!-- The generalization *Mary smokes cigarettes* suggests a daily-habit (e.g., $h > \text{once a day}$), while *Bill writes poems* implies something much weaker, perhaps a poem every few weeks (e.g., $h > \text{once a month}$.

### 2017-08-29 paper/comgen-paper.Rmd
edits up to model simulation section

@@
 
-<!-- We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction. -->
-<!-- We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities.  -->
-<!-- Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts].
--->
-<!-- The basic currency of inductive reasoning in these models is probability. -->
-<!-- If generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$: -->
-
-<!-- We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.
--->
-
 <!-- In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability. -->
@@
 Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
+$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
 $P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
-The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008; cf., $Prasada2006; Prasada2013].
+The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
+This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; Prasada2006; Prasada2013].
+Critically in our model, this structure is in listener's knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$. 
+<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
+influence the meaning of a generic statement via their influence on subjective probability.
+-->
+<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts].
+-->
 We term this prior distribution the **prevalence prior**.
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
 

### 2017-08-29 paper/comgen-paper.Rmd
fix citation display and other superficial edits

@@
 abstract: > 
-    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
-    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
+    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Birds fly").
+    The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
     Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing *genericity* is in determining the conditions under which such statements are true or false; these conditions are extremely flexible. 
+    The major issue in formalizing *genericity* is in determining what which such statements are true or false.
     Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language*, such as *Birds fly*), events (*habitual language*, such as *John runs*), and causes (*causal language*, such as *The block makes the machine play music.*).
-Across these diverse domains, we find that our model explains the full spectra of endorsements of generalizations in language, while simpler models do not.
-    These results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
+    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
+    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
+    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
 
@@
 Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-Generalizations are not limited to generics, however; they can be found in statements about individuals (*habitual language*; e.g., "Mary swims after work.") as well as causal events (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generalizations are much than just generics, however; they can be found in statements about individuals (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about observable behavior.
-A formal model in this domain is advantageous to make explicit the relevant assumptions of a psychological or linguistic hypothesis for predicting human behavior; this, in turn, makes the theory more falsifiable.
+A formal model in this domain is useful to make explicit the relevant assumptions of a psychological or linguistic hypothesis for predicting human behavior; this, in turn, makes the theory more falsifiable.
 The major challenge in formalizing generalizations in language is determining what makes such statements true or false.
-When we hear "Dogs bark", it feels like a universal statement, like *All* dogs bark.
+When we hear "Dogs bark", it sounds like a universal statement, like *All* dogs bark.
 But the property doesn't apply to all dogs: Basenji dogs are barkless^[
@@
 <!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
-However, less than 1\% of moquitos actually carry malaria and still "Mosquitos carry malaria" is intuitively true.
+However, only a tiny fraction of moquitos carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
@@
 But weakening the generalization to *some* goes too far: Half of robins are female, but saying "Robins are female" seems odd.
-That same half of robins (i.e., the females), however, also lay eggs, and "Robins lay eggs" is intuively reasonable.
+That same half of robins (i.e., the females), however, also lay eggs, and "Robins lay eggs" is again intuively true.
 
@@
 From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
-
-With this perspective, @Leslie2007 proposes generics express a cognitively primitive, default generalization. 
+With this perspective, @Leslie2007 proposes that generics express a cognitively primitive, default generalization. 
 The *generics as default* view argues that certain principles explain how generics become true or false.
-"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know about if you are trying to survive in a hostile world.
-This theory correctly predicted that generics that convey striking properties would be true even if the property were relatively rare [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
+"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know if you are to survive in a hostile world.
+This theory correctly predicted that generics that convey striking properties would be true even if the property was relatively uncommon [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
 "Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].
@@
 Yet, generics are not limited to conveying rich, conceptual relations. 
-Arbitrary relationships can also be expressed with generics (e.g., "Barns are red"; "Ravens are bigger than toasters") which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
+Arbitrary relationships can also be expressed with generics (e.g., "Barns are red"; "Ravens are bigger than toasters") which seem only to be true only because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
 The *generics as default* view must then be supplemented with the principle that, in certain situations, statistics influence generic endorsement.
-The diversity of generic statements highlighted by this view is interesting, but insofar as generics are a single, unified phenomenon, there should be a general, unified principle that explains what makes the statements true or false.
+The diversity of generic statements highlighted by the conceptual accounts is interesting, but insofar as generics are a single, unified phenomenon, there should be a general, unified principle that explains what makes the statements true or false.
 <!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
@@
 <!-- ]. -->
-<!-- <!-- In the study of categories and properties, $x$ is an object. --> -->
+<!-- <!-- In the study of categories and properties, $x$ is an object. --> 
 <!-- For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$ -->
-<!-- <!-- In this case, $x$ is a instance of an agent. --> -->
+<!-- <!-- In this case, $x$ is a instance of an agent. --> 
 <!-- Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
@@
 The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
-This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; Prasada2006; Prasada2013].
+This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
 Critically in our model, this structure is in listener's knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$. 
@@
 
-For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
+For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
 The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
@@
 Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$.
+Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $\mathcal{D}_{stable}$.
 This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
@@
 The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of cue validity. 
-Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D_{stable}}$ and the transient cause distribution $\mathcal{D_{transient}}$).
+Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
 If there is a finite number of kinds in the prevalence prior for a feature, and one knows the prevalence of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the prevalence prior, in that it can be derived via Bayes' Rule:

### 2017-08-29 paper/comgen-paper.Rmd
edits to discussion of expt 1a

@@
 We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
-Note that we use the alterantive mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
+Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
 The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
@@
 A natural proposal is that endorsements for generic language have to do with cue validity.
-This possibility has been investigated empirically, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
+This possibility has been investigated empirically in one of few examples of statistical modeling of generics, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
 However, cue validity has some empirical and theoretical issues.
-Empirically, cue validity is not a necessary criteria for generic endorsement (e.g., *Dogs have four legs*).
-Theoretically, it's not obvious why cue validity would be part of the semantic content of generics.
-If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
+Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
+Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
+<!-- If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
+-->
 <!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
@@
 
-However, we shouldn't throw away the possibility that distributional information about the property is relevant. 
-The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of cue validity. 
+However, we should not throw away the possibility that distributional information about the property is relevant. 
+The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of the construct of cue validity. 
 Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
@@
 
-Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is not longer defined (or, it is zero for all kinds). 
-This is for the same reason that for a continuous probability distribution, the probability of any particular number is zero. 
+Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is no longer well-defined (or, it is zero for all kinds). 
+This is for the same reason that for a probability distribution over the real numbers (a *continuous* probability distribution), the probability of any particular number is zero. 
 For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
-The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds}, but there are many kinds of birds and the feature is not particularly diagnostic for anyone of them. 
-At the same time, the mixture parameter for the distribution over the prevalence of "having wings" is still relatively small, since it represents information about the distribution and not one particular kind.
+The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds} (and hence, $\phi$ is relatively low), but there are many kinds of birds and the feature is not particularly diagnostic for any given one of the subkinds (e.g., robins).
+$phi$ is still relatively small in this case because it encodes information about the distribution across kinds and not just one particular kind.
 This is an important point of departure in our work from previous work.
@@
 ]
-This is a strong alterantive model to our uncertain-threshold model; the only difference concerns the threshold.
+This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
 

### 2017-08-29 paper/comgen-paper.Rmd
small edits in discussion

@@
 It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., *John runs.*, *Dogs are friendly.*, *The block makes the machine play music*) are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
+Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
 We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of genericity in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of genericity in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
+To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
+
+As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
 What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *propensity*, or probability (Expt. 1, 2a \& 2b, 3).
+Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *prevalence*, or probability (Expt. 1, 2a \& 2b, 3).
 This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
 We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from linguistics of generalizations about categories, or *generic language* (Expt. 1).
+Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
 In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
@@
 This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for influence on generic language [c.f., @Leslie2008].
+At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
 
@@
 In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the propensity of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the target is evaluated. 
-$P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
+We constructed the prior belief distribution for the prevalence of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
+These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
+Thus, the prevalence prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
 
@@
 Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language to the study of *vague language*.
-
-In this work, we made the design decision to construct the comparison class with respect to other kinds, people, or causes.
+We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
+
+In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
 In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
 In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class, with respect to other features. 
+There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
 This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
 
-Statements of genericity can be used to address either QUD, and this difference can even be observed the same sentence.
-"Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; say, in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., said sardonically).
+Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
+The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
 We chose to focus in this work on the category-wise comparison class for methodological convenience. 
@@
 *Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the property-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
+Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
 
@@
 
-Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
+Our approach makes the strong claim that beliefs about predicted prevalence is the connective tissue between conceptual knowledge and the semantics of generic language.
 That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
@@
 
-The focus on subjective, predictive probability casts new light on puzzles surrounding accidentally-true situations.
-Consider a classic thought experiment in the linguistics and philosophy literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
+The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
+Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
 Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
@@
 The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge much *later* in development [@Brandone2014; @Gelman2015].
+In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
 This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
@@
 We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$ and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
 Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
@@
 Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how category generalizations are conveyed and how beliefs play a central role in understanding language.
+The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
 

### 2017-08-31 paper/coverletter.tex
copy over coverletter from last submission

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
%\usepackage[urw-garamond]{mathdesign}
\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
%\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage{url}
% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter
\def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

%----------------------------------------------------------------------------------------
%	DOCUMENT MARGINS
%----------------------------------------------------------------------------------------

\textwidth 6.75in
\textheight 9.25in
\oddsidemargin -.25in
\evensidemargin -.25in
\topmargin -1in
\longindentation 0.50\textwidth
\parindent 0.4in

%----------------------------------------------------------------------------------------
%	SENDER INFORMATION
%----------------------------------------------------------------------------------------

\def\Who{} % Your name
\def\What{} % Your title
\def\Autha{Michael Henry Tessler} % Your name
\def\Authb{Noah D. Goodman} % Your name
\def\Where{Department of Psychology} % Your department/institution
\def\Address{450 Serra Mall, Bldg 420} % Your address
\def\CityZip{Stanford, CA 94305} % Your city, zip code, country, etc
\def\Email{E-mail: mtessler@stanford.edu} % Your email address
\def\TEL{Phone: (757) 561-7971} % Your phone number

%----------------------------------------------------------------------------------------
%	HEADER AND FROM ADDRESS STRUCTURE
%----------------------------------------------------------------------------------------

\address{
\includegraphics[width=0.8in]{logo-simple.pdf} % Include the logo of your institution
\hspace{5.1in} % Position of the institution logo, increase to move left, decrease to move right
\vskip -0.85in~\\ % Position of the text in relation to the institution logo, increase to move down, decrease to move up
\Large\hspace{1.5in}STANFORD UNIVERSITY \hfill %~\\[0.05in] % First line of institution name, adjust hspace if your logo is wide
%\hspace{1.5in}University 
\hfill 
\normalsize % Second line of institution name, adjust hspace if your logo is wide
\makebox[0ex][r]{\bf \Who \What }\hspace{0.08in} % Print your name and title with a little whitespace to the right
~\\[-0.11in] % Reduce the whitespace above the horizontal rule
\hspace{1.5in}\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
\hspace{\fill}\parbox[t]{2.85in}{ % Create a box for your details underneath the horizontal rule on the right
%\flushright 
\footnotesize % Use a smaller font size for the details
\flushright
%\Who \\  % Your name, all text after this will be italicized
\Autha\\
\Authb\\
\Where\\ % Your department
\Address\\ % Your address
\CityZip\\ % Your city and zip code
%\TEL\\ % Your phone number
%\Email\\ % Your email address
%\URL % Your URL
}
\hspace{0in} % Horizontal position of this block, increase to move left, decrease to move right
\vspace{-1in} % Move the letter content up for a more compact look
}

%----------------------------------------------------------------------------------------
%	TO ADDRESS STRUCTURE
%----------------------------------------------------------------------------------------

\def\opening#1{\thispagestyle{empty}
{\centering\fromaddress \vspace{0.6in} \\ % Print the header and from address here, add whitespace to move date down
\hspace*{\longindentation}\hspace*{\fill}\par} % Print today's date, remove \today to not display it
%{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{0.4in} % White space after the to address
\noindent #1 % Print the opening line
% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}
}

%----------------------------------------------------------------------------------------
%	SIGNATURE STRUCTURE
%----------------------------------------------------------------------------------------

\signature{\Autha \\ \Authb \What} % The signature is a combination of your name and title

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
\hspace*{\longindentation} % Move the signature right
\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.1in % Whitespace between the signature text and your name
\fromsig}} % Print your name and title

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

\begin{letter}
%{Prof. Jones\\
%Mathematics Search Committee\\
%Department of Mathematics\\
%University of California\\
%Berkeley, California 12345\\
%}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Editor,}

We enclose the manuscript \emph{A pragmatic theory of generic language} to be considered for publication in \emph{Psychological Review}. 
This paper explores the linguistic means by which generalizations about categories are communicated.  
We present a Bayesian model of understanding generic language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
We probe the theory in more detail, and find that the semantics of generic language depend in a fundamental way on subjective beliefs. 
%generalizations (e.g. ``Dogs bark.'') are conveyed.
% Generalizing properties to categories is central to human understanding of the world.

Categories are inherently unobservable; thus, it is critical that language allow us to transmit hard-won information about categories. Generic language (e.g.~\emph{Swans are white.}) is a simple and ubiquitous way to do this. 
Generic utterances are common in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.

Though this type of language is found everywhere, the meaning of generic language is philosophically puzzling and has resisted precise formalization. 
The major issue in formalizing generic language is determining what makes a generic sentence true or false.
Generic utterances are often about characteristic properties contained by a majority (e.g. \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g. \emph{Robins lay eggs}, even though only adult, female, fertile robins do). 
Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier would suffice. 
%The acceptability of generics seems not to have to do with the statistics of the property because while \emph{Robins lay eggs} is true, \emph{Robins are female} is not, despite the prevalence of the properties being equivalent.

%properties with the same statistics generate infelicitous generics (e.g. ``Robins are female'').
% and it's not useful to say ``Sharks don't attack swimmers'' even though the overwhelming majority don't. 
Parallel to these extremely flexible truth conditions are the surprisingly strong interpretations of novel generic utterances.
Generic language seems to exaggerate the statistics of the property; listeners typically interpret ``Bears like to eat ants.'' as ``\emph{Almost all} bears like to eat ants.''
This strength of interpretation has been identified as a mechanism in the propagation of social stereotypes.

% This article provides a formal account (instantiated in a computational model) of ``generics'', the primary linguistic construct by which interlocutors talk about categories and concepts (e.g. ``\emph{Dogs} bark.'', ``\emph{Tall folks} are good at basketball.'', ``\emph{The French} eat snails.'').  
% 
% At the same time, the conditions by which generic utterances are true seem at once to be associated with the the number of instances with the property (e.g. ``Barns are red.'' is true because most barns are red) and not associated with it (e.g. ``Lions have manes.'' is a good generic utterance but ``Lions are male.'' is not, even though the set of lions that are male is a superset of those that have manes.)

We explore a meaning of the generic that is based on the prevalence of the property (``what \% of the category has the property?'') but 
whose criterion is left underspecified in the language, and must be resolved in context.
We instantiate this idea in a probabilistic model of pragmatic reasoning, encompassing the basic communicative qualities to be truthful and informative. 
We show how these basic communicative principles coupled with the interlocutors' beliefs about the property in the question (which we measure empirically) are sufficient to explain the paradoxical phenomena of flexible truth conditions with simultaneously strong implications.
The model explains almost all of the variance in human judgments for the evaluation and comprehension of generic utterances.
We go on to further interrogate the semantic scale against which the generic is evaluated, and find that it is intelocutors' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, that matters for generic language. This research opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces.

This work will be of strong interest to psychologists, as well as linguists, philosophers, and computer scientists interested in language and interaction.
The puzzles of generic language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
Our solution represents the first formal model of generic language to be validated by quantitative agreement with human behavioral data.
It is not, however, uncontroversial: we champion a statistical view that has been often dismissed in the literature.
Indeed, in presentations around the world we have found this work to excite broad interest and engagement.

%We resolve the philosophical paradoxes in the meaning of generic utterances by positing a stable meaning that is as simple as possible: a threshold on the number of instances with the property (i.e. the property's \emph{prevalence}), where the threshold is uncertain \emph{a priori} and only resolved by pragmatic reasoning.
%This simple semantics is consistent with the phenomenon from cognitive development that generics are learned at a very young age and are important for conceptual development.
%Interlocutors' beliefs about the prevalence of properties are represented as probability distribution; a framework that is useful for representing rich, structured knowledge of the world. 
%This work thus furthers the mathematical connection between language and the mind, by providing a bridge between the quantifiable properties of the world and the stuff of thought.

%Using this vague semantics, we explain two major puzzles surrounding generic language.

%This look provides insight into the stable properties

%The first is that generic utterances can be true for a wide range of prevalences: from tigers with stripes ($\sim 100\%$) all the way down to mosquitos with malaria (very few). 
%How can the prevalence of the property alone explain what makes some generics good things to say and others not as good? 
%The insight is that with an uncertain semantics, the likely meaning of the generic (i.e. the likely threshold for acceptance) is inferred using listeners' \emph{a priori} beliefs and the communicative force of a speech act, in a probabilistic pragmatics framework. Speakers who takes this into account will have different criteria to satisfy (different thresholds) for different different types of properties (Expts.~1a and 1b). At the same time, listeners' inferences about the likely prevalence will often be stronger than what a speaker would to justify such a claim. This captures human inferences with a high degree of quantitative accuracy (Expts.~2a and 2b). 
%

The following reviewers have expertise in the phenomenology of generic language, experimental studies of pragmatics, and/or the Bayesian modeling tools we use:

\begin{itemize}
\item Greg N. Carlson, Department of Linguistics, University of Rochester carlson@ling.rochester.edu
\item Ted Gibson, Department of Brain and Cognitive Sciences, MIT egibson@mit.edu
\item Gerhard J{\"a}ger, Department of General Linguistics, University of T{\"u}bingen gerhard.jaeger@uni-tuebingen.de
%\item Mark Steedman, School of Informatics, University of Edinburgh  steedman@inf.ed.ac.uk
\item Susan A. Gelman, Department of Psychology, University of Michigan gelman@umich.edu
\item Naomi Feldman, Department of Linguistics, University of Maryland nhf@umd.edu
\item Amy Perfors, Department of Psychology, University of Adelaide amy.perfors@adelaide.edu.au
\item Klinton Bicknell, Department of Linguistics, Northwestern University kbicknell@northwestern.edu
\item Michael Franke, University of T{\"u}bingen, mchfranke@gmail.com
\item Tamar Kushnir, Department of Psychology, Cornell University, tk397@cornell.edu
%\item Michael Lee, Department of Cognitive Sciences, University of California, Irvine mdlee@uci.edu
\end{itemize}

We look forward to receiving your opinion.

\closing{Sincerely yours,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

%
%
%
%
%%----------------------------------------------------------------------------------------
%%	ADDRESSEE AND GREETING/CLOSING
%%----------------------------------------------------------------------------------------
%
%\greetto{Dear Editor,} % Greeting text
%\closeline{Sincerely yours,} % Closing text
%
%%\nameto{Mrs. Jane Smith} % Addressee of the letter above the to address
%
%%\addrto{
%%Recruitment Officer \\ % To address
%%The Corporation \\
%%123 Pleasant Lane \\
%%City, State 12345
%%}
%
%%----------------------------------------------------------------------------------------
%
%\begin{document}
%\begin{newlfm}
%
%%----------------------------------------------------------------------------------------
%%	LETTER CONTENT
%%----------------------------------------------------------------------------------------
%
%%
%%Generalizations about categories are central to human understanding, and generic language (e.g.~\emph{Dogs bark.}) provides a simple and ubiquitous way to communicate these generalizations. 
%%Yet the meaning of generic language is philosophically puzzling and has resisted precise formalization.
%%We explore the idea that the core meaning of a generic sentence is simple but underspecified, 
%%and that general principles of pragmatic reasoning are responsible for establishing the precise meaning in context.
%%Building on recent probabilistic models of language understanding, we provide a formal model for the evaluation and comprehension of generic sentences. 
%%
%%This model explains the puzzling flexibility in usage of generics in terms of diverse prior beliefs about properties.
%%We elicit these priors experimentally and show that the resulting model predictions explain almost all of the variance in human judgements for both common and novel generics.
%%
%
%We enclose the manuscript \emph{A pragmatic theory of generic language} to be considered for publication in \emph{Science Magazine}. 
%This paper explores the linguistic means by which generalizations about categories, some of the most central aspects of human understanding, are communicated.  
%We present a Bayesian model of understanding generic language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
%
%%generalizations (e.g. ``Dogs bark.'') are conveyed.
%% Generalizing properties to categories is central to human understanding of the world. 
%
%Categories are inherently unobservable; thus, it is critical that language allow us to transmit hard-won information about categories. Generic language (e.g.~\emph{Swans are white.}) is a simple and ubiquitous way to do this. 
%Generic utterances are common in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups.}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Taxes are high.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
%
%Though this type of language is found everywhere, the meaning of generic language is philosophically puzzling and has resisted precise formalization. 
%One major roadblock has been specifying the conditions in which a generic utterance is true, or a felicitous thing to say.
%Generic utterances are often about majority characteristic properties (e.g. \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g. \emph{Robins lay eggs}, even though only adult, female, fertile robins do). 
%Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier would suffice. 
%%The acceptability of generics seems not to have to do with the statistics of the property because while \emph{Robins lay eggs} is true, \emph{Robins are female} is not, despite the prevalence of the properties being equivalent. 
%
%%properties with the same statistics generate infelicitous generics (e.g. ``Robins are female'').
%% and it's not useful to say ``Sharks don't attack swimmers'' even though the overwhelming majority don't. 
%Parallel to these extremely flexible truth conditions are the surprisingly strong interpretations of novel generic utterances.
%Generic language seems to exaggerate the statistics of the property; listeners typically interpret ``Bears like to eat ants.'' as ``\emph{Almost all} bears like to eat ants.''
%This strength of interpretation has been identified as a mechanism in the propagation of social stereotypes. 
%
%
%% This article provides a formal account (instantiated in a computational model) of ``generics'', the primary linguistic construct by which interlocutors talk about categories and concepts (e.g. ``\emph{Dogs} bark.'', ``\emph{Tall folks} are good at basketball.'', ``\emph{The French} eat snails.'').  
%% 
%% At the same time, the conditions by which generic utterances are true seem at once to be associated with the the number of instances with the property (e.g. ``Barns are red.'' is true because most barns are red) and not associated with it (e.g. ``Lions have manes.'' is a good generic utterance but ``Lions are male.'' is not, even though the set of lions that are male is a superset of those that have manes.)
%
%We explore a meaning of the generic that is based on statistics (``what \% of the category has the property?'') but 
%whose criterion is left underspecified in the language, and must be resolved in context.
%We instantiate this idea in a probabilistic model of pragmatic reasoning, encompassing the basic communicative qualities to be truthful and informative. 
%We show how these basic communicative principles coupled with the listener's beliefs about the property in the question (which we measure empirically) are sufficient to explain the paradoxical phenomena of flexible truth conditions with simultaneously strong implications.
%The model explains almost all of the variance in human judgments for the evaluation and comprehension of generic utterances.
%
%This work will be of strong interest to psychologists, linguists and philosophers, as well as to computer scientists interested in language and interaction.
%The puzzles of generic language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
%Our solution represents the first formal model of generic language to be validated by quantitative agreement with human behavioral data.
%It is not, however, uncontroversial: we champion a statistical view that has been largely dismissed in the literature.
%Indeed, in presentations around the world we have found this work to excite broad interest and engagement.
%
%%We resolve the philosophical paradoxes in the meaning of generic utterances by positing a stable meaning that is as simple as possible: a threshold on the number of instances with the property (i.e. the property's \emph{prevalence}), where the threshold is uncertain \emph{a priori} and only resolved by pragmatic reasoning.
%%This simple semantics is consistent with the phenomenon from cognitive development that generics are learned at a very young age and are important for conceptual development.
%%Interlocutors' beliefs about the prevalence of properties are represented as probability distribution; a framework that is useful for representing rich, structured knowledge of the world. 
%%This work thus furthers the mathematical connection between language and the mind, by providing a bridge between the quantifiable properties of the world and the stuff of thought. 
%
%
%
%
%
%
%%Using this vague semantics, we explain two major puzzles surrounding generic language. 
%
%%This look provides insight into the stable properties 
%
%%The first is that generic utterances can be true for a wide range of prevalences: from tigers with stripes ($\sim 100\%$) all the way down to mosquitos with malaria (very few). 
%%How can the prevalence of the property alone explain what makes some generics good things to say and others not as good? 
%%The insight is that with an uncertain semantics, the likely meaning of the generic (i.e. the likely threshold for acceptance) is inferred using listeners' \emph{a priori} beliefs and the communicative force of a speech act, in a probabilistic pragmatics framework. Speakers who takes this into account will have different criteria to satisfy (different thresholds) for different different types of properties (Expts.~1a and 1b). At the same time, listeners' inferences about the likely prevalence will often be stronger than what a speaker would to justify such a claim. This captures human inferences with a high degree of quantitative accuracy (Expts.~2a and 2b). 
%%
%
%
%
%The following reviewers have expertise in the phenomenology of generic language and/or the Bayesian modeling tools we use:
%
%\begin{itemize}
%\item Greg N. Carlson, Department of Linguistics, University of Rochester \url{carlson@ling.rochester.edu}
%\item Susan A. Gelman, Department of Psychology, University of Michigan \url{gelman@umich.edu}
%\item Mark Steedman, School of Informatics, University of Edinburgh,  \url{steedman@inf.ed.ac.uk}
%\item Michael Lee, Department of Cognitive Sciences, University of California, Irvine, \url{mdlee@uci.edu}
%\item Ted Gibson, Department of Brain and Cognitive Sciences, MIT, \url{egibson@mit.edu}
%\end{itemize}
%
%
%%\item Andrei Cimpian, Department of Psychology, University of Illinois at Urbana-Champaign \url{acimpian@illinois.edu}
%%\item Sandeep Prasada, Department of Psychology, Hunter College \url{sprasada@hunter.cuny.edu}
%%\end{itemize}
%%The following reviewers have expertise in the Bayesian modeling techniques we use:
%%\begin{itemize}
%%\item Amy Perfors
%%\item Gerhardt Jaeger
%%
%%\ndg{MH, fill in emails etc?}
%
%
%
%%----------------------------------------------------------------------------------------
%
%\end{newlfm}
%\end{document}

### 2017-08-31 paper/coverletter.tex
update half of letter for new paper

@@
 
-%----------------------------------------------------------------------------------------
-%	TO ADDRESS
-%----------------------------------------------------------------------------------------
-
 \begin{letter}
-%{Prof. Jones\\
-%Mathematics Search Committee\\
-%Department of Mathematics\\
-%University of California\\
-%Berkeley, California 12345\\
-%}
-
-%----------------------------------------------------------------------------------------
-%	TO ADDRESS
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-%	LETTER CONTENT
-%----------------------------------------------------------------------------------------
 
@@
 
-We enclose the manuscript \emph{A pragmatic theory of generic language} to be considered for publication in \emph{Psychological Review}. 
-This paper explores the linguistic means by which generalizations about categories are communicated.  
-We present a Bayesian model of understanding generic language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
+We enclose the manuscript \emph{Communicating Generalizations} to be considered for publication in \emph{Psychological Review}. 
+This paper explores the linguistic means by which generalizations about categories, events, and causality are communicated.  
+We present a Bayesian model of understanding generalizations in language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
 We probe the theory in more detail, and find that the semantics of generic language depend in a fundamental way on subjective beliefs.
-%generalizations (e.g. ``Dogs bark.'') are conveyed.
-% Generalizing properties to categories is central to human understanding of the world.
 
-Categories are inherently unobservable; thus, it is critical that language allow us to transmit hard-won information about categories.
-Generic language (e.g.~\emph{Swans are white.}) is a simple and ubiquitous way to do this.
+Understanding how the world works requires learning generalizations. 
+The kinds of observations that would facilitate such learning, however, can be rare (e.g., \emph{figuring out that lightning strikes tall objects}) or costly (e.g., \emph{learning that certain plants are poisonous}).
+We don't need to need taste every plant to figure out which ones are poisonous; we don't need to stand under objects of various heights to learn that lightning strikes tall objects.
+Language allow us to communicate generalizations to each other.
+
+The language of generalizations is often studied in what's called \emph{generic language} (e.g., ~\emph{Birds fly}).
 Generic utterances are common in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
+Generalizations can be transmitted about more than just categories.
+\emph{Habitual language} conveys generalizations about events (e.g., ~\emph{Mary swims after work}).
+\emph{Causal language} conveys generalizations about causal events (e.g., ~\emph{Staring at the sun makes you go blind}).
 
-Though this type of language is found everywhere, the meaning of generic language is philosophically puzzling and has resisted precise formalization. 
-The major issue in formalizing generic language is determining what makes a generic sentence true or false.
-Generic utterances are often about characteristic properties contained by a majority (e.g.
-\emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g.
-\emph{Robins lay eggs}, even though only adult, female, fertile robins do).
-Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier would suffice.
-%The acceptability of generics seems not to have to do with the statistics of the property because while \emph{Robins lay eggs} is true, \emph{Robins are female} is not, despite the prevalence of the properties being equivalent.
+Though this type of language is found everywhere, the meaning of generalizations in language is philosophically puzzling and has resisted precise formalization. 
+The major issue in formalizing generalizations in language is determining what makes such statements true or false.
+Consider generic utterances:
+Generics are often about characteristic properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
+Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier (i.e., \emph{some}) would suffice.
+Some have taken this evidence to suggest that generics must express special mental relationships between kinds and properties, but arbitrary generalizations --- which seem only to depend on the actual statistics of the world --- can also be conveyed with generics (e.g., \emph{Ravens are bigger than toasters}).
+There have been a few formal models proposed for generic language, but none that have made precise, quantitative predictions about human endorsement patterns.
 
-%properties with the same statistics generate infelicitous generics (e.g. ``Robins are female'').
-% and it's not useful to say ``Sharks don't attack swimmers'' even though the overwhelming majority don't. 
-Parallel to these extremely flexible truth conditions are the surprisingly strong interpretations of novel generic utterances.
-Generic language seems to exaggerate the statistics of the property; listeners typically interpret ``Bears like to eat ants.'' as ``\emph{Almost all} bears like to eat ants.''
-This strength of interpretation has been identified as a mechanism in the propagation of social stereotypes.
+Analogous phenomena can be observed in habitual and causal language.
+If John smokes once a year, one might hesitate to endorse the statement \emph{John smokes}.
+Yet, climbing a mountain once a year makes John really seem like he \emph{climbs mountains}.
+\emph{Drinking moonshine makes you go blind} and so does \emph{staring at the sun}, but neither statement conveys precise information about the relative risk.
 
-% This article provides a formal account (instantiated in a computational model) of ``generics'', the primary linguistic construct by which interlocutors talk about categories and concepts (e.g.
-``\emph{Dogs} bark.'', ``\emph{Tall folks} are good at basketball.'', ``\emph{The French} eat snails.'').
-% 
-% At the same time, the conditions by which generic utterances are true seem at once to be associated with the the number of instances with the property (e.g.
-``Barns are red.'' is true because most barns are red) and not associated with it (e.g.
-``Lions have manes.'' is a good generic utterance but ``Lions are male.'' is not, even though the set of lions that are male is a superset of those that have manes.)
+In this paper, we propose that the core meaning of generalizations in language is \emph{simple but underspecified}.
+We adopt a familiar formalism for the truth conditions of this language: a threshold function (e.g., the statement is true if the frequency is greater than some criterion $\theta$), but whose criterion $\theta$ is left underspecified in the language, and must be resolved in context.
+We instantiate this idea in a state-of-the-art probabilistic model of communication, and operationalize \emph{endorsement} (i.e., felicity or agreement with a statement) as a speaker's decision about whether or not to say the generalization to a naive listener (as opposed to staying silent).
+We show how this simple model coupled with the interlocutors' beliefs about the property or event in the question (which we both \emph{measure and manipulate} empirically) are sufficient to explain the puzzling phenomenon of flexible truth conditions.
+The model explains almost all of the variance in human judgments for the evaluation of generic, habitual, and causal utterances.
 
-We explore a meaning of the generic that is based on the prevalence of the property (``what \% of the category has the property?'') but 
-whose criterion is left underspecified in the language, and must be resolved in context.
-We instantiate this idea in a probabilistic model of pragmatic reasoning, encompassing the basic communicative qualities to be truthful and informative. 
-We show how these basic communicative principles coupled with the interlocutors' beliefs about the property in the question (which we measure empirically) are sufficient to explain the paradoxical phenomena of flexible truth conditions with simultaneously strong implications.
-The model explains almost all of the variance in human judgments for the evaluation and comprehension of generic utterances.
 We go on to further interrogate the semantic scale against which the generic is evaluated, and find that it is intelocutors' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, that matters for generic language.

### 2017-08-31 paper/coverletter.tex
finish redrafting cover letter

@@
 In this paper, we propose that the core meaning of generalizations in language is \emph{simple but underspecified}.
-We adopt a familiar formalism for the truth conditions of this language: a threshold function (e.g., the statement is true if the frequency is greater than some criterion $\theta$), but whose criterion $\theta$ is left underspecified in the language, and must be resolved in context.
-We instantiate this idea in a state-of-the-art probabilistic model of communication, and operationalize \emph{endorsement} (i.e., felicity or agreement with a statement) as a speaker's decision about whether or not to say the generalization to a naive listener (as opposed to staying silent).
-We show how this simple model coupled with the interlocutors' beliefs about the property or event in the question (which we both \emph{measure and manipulate} empirically) are sufficient to explain the puzzling phenomenon of flexible truth conditions.
-The model explains almost all of the variance in human judgments for the evaluation of generic, habitual, and causal utterances.
-
-We go on to further interrogate the semantic scale against which the generic is evaluated, and find that it is intelocutors' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, that matters for generic language.
-This research opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces.
+We adopt a formalism for the truth conditions of this language which has antecedents in formal semantics: a threshold function (e.g., the statement is true if the frequency is greater than some criterion $\theta$).
+The critical novelty of our approach is that the criterion $\theta$ is left underspecified in the language, and must be resolved in context.
+We instantiate this idea in a state-of-the-art probabilistic model of communication, and operationalize \emph{endorsement} (i.e., felicity or agreement with a statement) as a speaker's decision about whether or not to say the generalization to a naive listener.
+We show how this simple model naturally explains \emph{flexible truth conditions} via interlocutors' beliefs about the property or event in the question.
+Across our three case studies, we both \emph{measure and manipulate} prior knowledge, showing that it is strongly and causally related (via our model) to endorsement. 
+Using the case study of habitual language, we go on to further interrogate the semantic scale from which generalizations are evaluated.
+We find that speakers' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past is what drives endorsements. 
+Across our case studies, we show very strong agreement between the predictions of our model with empirical human data; additionally, we do so in situations where simpler models would not suffice. 
+This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
 
 This work will be of strong interest to psychologists, as well as linguists, philosophers, and computer scientists interested in language and interaction.
-The puzzles of generic language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
+The puzzles of generalizations in language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
 Our solution represents the first formal model of generic language to be validated by quantitative agreement with human behavioral data.
@@
 
-%We resolve the philosophical paradoxes in the meaning of generic utterances by positing a stable meaning that is as simple as possible: a threshold on the number of instances with the property (i.e.
-the property's \emph{prevalence}), where the threshold is uncertain \emph{a priori} and only resolved by pragmatic reasoning.
-%This simple semantics is consistent with the phenomenon from cognitive development that generics are learned at a very young age and are important for conceptual development.
-%Interlocutors' beliefs about the prevalence of properties are represented as probability distribution; a framework that is useful for representing rich, structured knowledge of the world. 
-%This work thus furthers the mathematical connection between language and the mind, by providing a bridge between the quantifiable properties of the world and the stuff of thought.
-
-%Using this vague semantics, we explain two major puzzles surrounding generic language.
-
-%This look provides insight into the stable properties
-
-%The first is that generic utterances can be true for a wide range of prevalences: from tigers with stripes ($\sim 100\%$) all the way down to mosquitos with malaria (very few). 
-%How can the prevalence of the property alone explain what makes some generics good things to say and others not as good? 
-%The insight is that with an uncertain semantics, the likely meaning of the generic (i.e.
-the likely threshold for acceptance) is inferred using listeners' \emph{a priori} beliefs and the communicative force of a speech act, in a probabilistic pragmatics framework.
-Speakers who takes this into account will have different criteria to satisfy (different thresholds) for different different types of properties (Expts.~1a and 1b).
-At the same time, listeners' inferences about the likely prevalence will often be stronger than what a speaker would to justify such a claim.
-This captures human inferences with a high degree of quantitative accuracy (Expts.~2a and 2b).
-%
-
 The following reviewers have expertise in the phenomenology of generic language, experimental studies of pragmatics, and/or the Bayesian modeling tools we use:
@@
 \begin{itemize}
+\item Susan A. Gelman, Department of Psychology, University of Michigan gelman@umich.edu
 \item Greg N. Carlson, Department of Linguistics, University of Rochester carlson@ling.rochester.edu
@@
 %\item Mark Steedman, School of Informatics, University of Edinburgh  steedman@inf.ed.ac.uk
-\item Susan A. Gelman, Department of Psychology, University of Michigan gelman@umich.edu
 \item Naomi Feldman, Department of Linguistics, University of Maryland nhf@umd.edu
@@
 
-%----------------------------------------------------------------------------------------
-
 \end{letter}
@@
 \end{document}
-
-%
-%
-%
-%
-%%----------------------------------------------------------------------------------------
-%%	ADDRESSEE AND GREETING/CLOSING
-%%----------------------------------------------------------------------------------------
-%
-%\greetto{Dear Editor,} % Greeting text
-%\closeline{Sincerely yours,} % Closing text
-%
-%%\nameto{Mrs. Jane Smith} % Addressee of the letter above the to address
-%
-%%\addrto{
-%%Recruitment Officer \\ % To address
-%%The Corporation \\
-%%123 Pleasant Lane \\
-%%City, State 12345
-%%}
-%
-%%----------------------------------------------------------------------------------------
-%
-%\begin{document}
-%\begin{newlfm}
-%
-%%----------------------------------------------------------------------------------------
-%%	LETTER CONTENT
-%%----------------------------------------------------------------------------------------
-%
-%%
-%%Generalizations about categories are central to human understanding, and generic language (e.g.~\emph{Dogs bark.}) provides a simple and ubiquitous way to communicate these generalizations. 
-%%Yet the meaning of generic language is philosophically puzzling and has resisted precise formalization.
-%%We explore the idea that the core meaning of a generic sentence is simple but underspecified, 
-%%and that general principles of pragmatic reasoning are responsible for establishing the precise meaning in context.
-%%Building on recent probabilistic models of language understanding, we provide a formal model for the evaluation and comprehension of generic sentences. 
-%%
-%%This model explains the puzzling flexibility in usage of generics in terms of diverse prior beliefs about properties.
-%%We elicit these priors experimentally and show that the resulting model predictions explain almost all of the variance in human judgements for both common and novel generics.
-%%
-%
-%We enclose the manuscript \emph{A pragmatic theory of generic language} to be considered for publication in \emph{Science Magazine}. 
-%This paper explores the linguistic means by which generalizations about categories, some of the most central aspects of human understanding, are communicated.  
-%We present a Bayesian model of understanding generic language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
-%
-%%generalizations (e.g. ``Dogs bark.'') are conveyed.
-%% Generalizing properties to categories is central to human understanding of the world. 
-%
-%Categories are inherently unobservable; thus, it is critical that language allow us to transmit hard-won information about categories.
-Generic language (e.g.~\emph{Swans are white.}) is a simple and ubiquitous way to do this.
-%Generic utterances are common in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups.}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Taxes are high.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
-%
-%Though this type of language is found everywhere, the meaning of generic language is philosophically puzzling and has resisted precise formalization. 
-%One major roadblock has been specifying the conditions in which a generic utterance is true, or a felicitous thing to say.
-%Generic utterances are often about majority characteristic properties (e.g.
-\emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g.
-\emph{Robins lay eggs}, even though only adult, female, fertile robins do).
-%Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier would suffice.
-%%The acceptability of generics seems not to have to do with the statistics of the property because while \emph{Robins lay eggs} is true, \emph{Robins are female} is not, despite the prevalence of the properties being equivalent.
-%
-%%properties with the same statistics generate infelicitous generics (e.g. ``Robins are female'').
-%% and it's not useful to say ``Sharks don't attack swimmers'' even though the overwhelming majority don't. 
-%Parallel to these extremely flexible truth conditions are the surprisingly strong interpretations of novel generic utterances.
-%Generic language seems to exaggerate the statistics of the property; listeners typically interpret ``Bears like to eat ants.'' as ``\emph{Almost all} bears like to eat ants.''
-%This strength of interpretation has been identified as a mechanism in the propagation of social stereotypes. 
-%
-%
-%% This article provides a formal account (instantiated in a computational model) of ``generics'', the primary linguistic construct by which interlocutors talk about categories and concepts (e.g.
-``\emph{Dogs} bark.'', ``\emph{Tall folks} are good at basketball.'', ``\emph{The French} eat snails.'').
-%% 
-%% At the same time, the conditions by which generic utterances are true seem at once to be associated with the the number of instances with the property (e.g.
-``Barns are red.'' is true because most barns are red) and not associated with it (e.g.
-``Lions have manes.'' is a good generic utterance but ``Lions are male.'' is not, even though the set of lions that are male is a superset of those that have manes.)
-%
-%We explore a meaning of the generic that is based on statistics (``what \% of the category has the property?'') but 
-%whose criterion is left underspecified in the language, and must be resolved in context.
-%We instantiate this idea in a probabilistic model of pragmatic reasoning, encompassing the basic communicative qualities to be truthful and informative. 
-%We show how these basic communicative principles coupled with the listener's beliefs about the property in the question (which we measure empirically) are sufficient to explain the paradoxical phenomena of flexible truth conditions with simultaneously strong implications.
-%The model explains almost all of the variance in human judgments for the evaluation and comprehension of generic utterances.
-%
-%This work will be of strong interest to psychologists, linguists and philosophers, as well as to computer scientists interested in language and interaction.
-%The puzzles of generic language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
-%Our solution represents the first formal model of generic language to be validated by quantitative agreement with human behavioral data.
-%It is not, however, uncontroversial: we champion a statistical view that has been largely dismissed in the literature.
-%Indeed, in presentations around the world we have found this work to excite broad interest and engagement.
-%
-%%We resolve the philosophical paradoxes in the meaning of generic utterances by positing a stable meaning that is as simple as possible: a threshold on the number of instances with the property (i.e.
-the property's \emph{prevalence}), where the threshold is uncertain \emph{a priori} and only resolved by pragmatic reasoning.
-%%This simple semantics is consistent with the phenomenon from cognitive development that generics are learned at a very young age and are important for conceptual development.
-%%Interlocutors' beliefs about the prevalence of properties are represented as probability distribution; a framework that is useful for representing rich, structured knowledge of the world. 
-%%This work thus furthers the mathematical connection between language and the mind, by providing a bridge between the quantifiable properties of the world and the stuff of thought. 
-%
-%
-%
-%
-%
-%
-%%Using this vague semantics, we explain two major puzzles surrounding generic language. 
-%
-%%This look provides insight into the stable properties 
-%
-%%The first is that generic utterances can be true for a wide range of prevalences: from tigers with stripes ($\sim 100\%$) all the way down to mosquitos with malaria (very few). 
-%%How can the prevalence of the property alone explain what makes some generics good things to say and others not as good? 
-%%The insight is that with an uncertain semantics, the likely meaning of the generic (i.e.
-the likely threshold for acceptance) is inferred using listeners' \emph{a priori} beliefs and the communicative force of a speech act, in a probabilistic pragmatics framework.
-Speakers who takes this into account will have different criteria to satisfy (different thresholds) for different different types of properties (Expts.~1a and 1b).
-At the same time, listeners' inferences about the likely prevalence will often be stronger than what a speaker would to justify such a claim.
-This captures human inferences with a high degree of quantitative accuracy (Expts.~2a and 2b).
-%%
-%
-%
-%
-%The following reviewers have expertise in the phenomenology of generic language and/or the Bayesian modeling tools we use:
-%
-%\begin{itemize}
-%\item Greg N. Carlson, Department of Linguistics, University of Rochester \url{carlson@ling.rochester.edu}
-%\item Susan A. Gelman, Department of Psychology, University of Michigan \url{gelman@umich.edu}
-%\item Mark Steedman, School of Informatics, University of Edinburgh,  \url{steedman@inf.ed.ac.uk}
-%\item Michael Lee, Department of Cognitive Sciences, University of California, Irvine, \url{mdlee@uci.edu}
-%\item Ted Gibson, Department of Brain and Cognitive Sciences, MIT, \url{egibson@mit.edu}
-%\end{itemize}
-%
-%
-%%\item Andrei Cimpian, Department of Psychology, University of Illinois at Urbana-Champaign \url{acimpian@illinois.edu}
-%%\item Sandeep Prasada, Department of Psychology, Hunter College \url{sprasada@hunter.cuny.edu}
-%%\end{itemize}
-%%The following reviewers have expertise in the Bayesian modeling techniques we use:
-%%\begin{itemize}
-%%\item Amy Perfors
-%%\item Gerhardt Jaeger
-%%
-%%\ndg{MH, fill in emails etc?}
-%
-%
-%
-%%----------------------------------------------------------------------------------------
-%
-%\end{newlfm}
-%\end{document}

### 2017-09-01 paper/comgen-paper.Rmd
edits to model section; caption on simulations figure

@@
 
-If generalization from observations can be described using probability, then it seems very natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
+If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
 One very simple semantic theory that has been used for describing quantified statements (e.g., "some", "all") is a *threshold semantics*.
@@
 \begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
+\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \label{eq:delta} \\ 
 &\propto  &
@@
 
-<!-- Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable to an individual (i.e., "My dog is friendly").
--->
-<!-- Bare plural statements (e.g., "Dogs are friendly") tend to yield a generic meaning, though other forms can express such a meaning [e.g., "A mongoose eats snakes."; @Carlson1977] . -->
-<!-- Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
--->
-<!-- At first glance, generics convey that *most* have the property, such as "Most dogs are friendly". -->
-<!-- "Robins lay eggs" is true, though, despite the fact that only female robins lay eggs. -->
-<!-- If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make? -->
-<!-- Finally, "Mosquitos carry malaria" is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos. -->
-<!-- It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.  -->
-
-<!-- In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability. -->
-<!-- If that's true, a simple, semantic theory  -->
-
-$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for probabilities $h$ greater than threshold $\theta$ and $0$ otherwise. 
+$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function that returns probabilities proportional to $1$ for prevalence values $h$ greater than threshold $\theta$, and $0$ otherwise. 
 Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
@@
 To answer this, we draw a metaphor to Bayesian statistics and data analysis.
-When there is a latent parameter the Bayesian scientist does not know much about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
-In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$ (in the form of a prior distribution $P(\theta)$) and infers $\theta$ in context (i.e., after having heard the utterance).
+When there is a latent parameter the Bayesian scientist knows little about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
+In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
 Though it is possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.
+
+Given the likelihood "meaning" function defined in Eq.
+\ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over the prevalence $P(h)$:
 
@@
 $P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
-The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
+The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
 This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
 Critically in our model, this structure is in listener's knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$.
+
 <!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
@@
 -->
-We term this prior distribution the **prevalence prior**.
 
@@
 
-This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold) but underspecified.
-Figure \ref{fig:simulations} shows model $L$'s posterior distribution on prevalence $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
+Figure\ \@ref(fig:simulations) shows the listener model $L$'s posterior distribution on prevalence $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
 \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
-The differences in the semantics are easily seen when considering a uniform prior distribution over $h$ (top left facet).
-The fixed threshold model rules out only the lowest possible prevalence ($h=0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct: The higher the $h$, the more likely it is after hearing the generalization.
-
-The intuition behind the model's behavior can be gleaned by imagining what the listener $L$ would believe given different thresholds and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest $h$ would still pass the threshold, as would some that are slightly lower.
+The differences in the semantics are easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
+The fixed-threshold model rules out only the lowest possible prevalence ($h=0$) and returns a posterior very similar to the prior.
+The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.
+
+The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
+If the threshold $\theta$ is very high, only the highest prevalences $h$ would pass the threshold.
+If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower.
 As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
 When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-When the listener averages over these possibilities, $h$'s with higher values pass more thresholds; thus, higher $h$'s are more likely *a posteriori*.
+The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
 
 In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
-Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that she is trying to communicate.
+Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an **endorsement model** as a Bayesian speaker's decision of whether or not to say the generalization to the listener $L$ (Eq.
+\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that he is trying to communicate.
 Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
@@
 \begin{equation} 
-S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
+S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta )}
 \label{eq:S1}
@@
 
-In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
-Following RSA, the speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
-Since the speaker $S$ doesn't know the threshold $\theta$, she must integrate over the likely values that the listener will infer.
+Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. 
+<!-- In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener. -->
+Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$, which acts as a soft-max function.
 
@@
 <!-- This is a simple Bayesian model of interpreting a statement conveying a generalization. -->
+
+<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
+\ref{eq:L0}).
+-->
+
+<!-- <!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } --> 
+<!-- \begin{equation}  -->
+<!-- S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h)  } -->
+<!-- \label{eq:S1} -->
+<!-- \end{equation} -->
+
+<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda$. -->
+<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
+<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
+-->
+<!-- \begin{equation} -->
+<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
+<!-- \label{eq:utilS1marginalization} -->
+<!-- \end{equation} -->
+<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
+<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
+<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
+<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
+<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
+<!-- ] -->
+<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
 
@@
 
-```{r simulations, fig.width = 9, fig.height=5}
+```{r simulations, fig.cap = "Prior distributions over the prevalence of a feature (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
+The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
+Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 9, fig.height=5}
 all.simulations %>%
@@
 ```
-
-<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
-\ref{eq:L0}).
--->
-
-<!-- <!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } --> 
-<!-- \begin{equation}  -->
-<!-- S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h)  } -->
-<!-- \label{eq:S1} -->
-<!-- \end{equation} -->
-
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda$. -->
-<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
-<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
--->
-<!-- \begin{equation} -->
-<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
-<!-- \label{eq:utilS1marginalization} -->
-<!-- \end{equation} -->
-<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
-<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
-<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
-<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
-<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
-<!-- ] -->
-<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
 

### 2017-09-01 paper/comgen-paper.Rmd
reorganize model prediction section

@@
 
-Figure\ \@ref(fig:simulations) shows the listener model $L$'s posterior distribution on prevalence $h$ upon hearing utterances corresponding to the uncertain threshold (Eq.
-\ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
-The differences in the semantics are easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible prevalence ($h=0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.
-
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest prevalences $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-
 In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
@@
 
-Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. 
-<!-- In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener. -->
+The speaker $S$ doesn't know the threshold $\theta$; rather, he integrates over the likely values that the listener will believe. 
 Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$, which acts as a soft-max function.
@@
 We discuss these alternative formulations and provide formal model comparison between these RSA models in Appendix.
-
-<!-- This decision is based on whether or not the generalization would accurately convey the $h$ -->
-<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
-\ref{eq:L0}).
--->
-
-<!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } -->
-
-<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
-<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
--->
-<!-- \begin{equation} -->
-<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
-<!-- \label{eq:utilS1marginalization} -->
-<!-- \end{equation} -->
-<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
-<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
-<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
-<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
-<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
-<!-- ] -->
-<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
-
-<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g., *Mosquitos carry malaria*; *Robins lay eggs* v. *Robins are female*). -->
-
-<!-- Abstract mental representations, then, may thus be influencing generic endorsement via its influence on subjective probability. -->
-
-<!-- To understand how generalizations are conveyed in language, we start by considering general purpose language understanding principles. -->
-<!-- Foremost, understanding language depends upon assumptions interlocutors make about each other and can exhibit a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000]. -->
-<!-- Though once viewed as a wastebasket in which to dump unexplained loose ends in service of more rigorous formal analysis, *pragmatics* --- or language understanding in context --- has seen an emergence of formal frameworks that connect closely with behavioral data [@Franke2015].
--->
-
-<!-- One dominant framework --- the Rational Speech Act theory --- has had considerable success in providing a formal account of pragmatic language phenomena [i.e., interactions between language and context; @Goodman2016].
--->
-<!-- This framework has been used to explain, in precise mathematical terms, how it is that utterances like "some of the kids failed the test" are interpreted to mean "some (but not all) of the kids failed the test" [@Goodman2013], how "I waited a million years to get a table" is interpreted as "I waited an obnoxiously long time to get a table" [@Kao2014], how "John is tall" can mean John is 5'4" is John if a 12-year-old but means John is 6'2" if he is 24-years-old [@Lassiter2015], and how "Your talk was fine" can be a polite way of saying your talk was less than fine [@Yoon2016].
--->
-<!-- Computational modeling has pushed our understanding of these complex linguistic phenomena, but so far, rational models of language use have focused on *specific* statements: utterances that convey information about a particular entity or situation.
--->
-<!-- A formal theory of statements that convey generalizations about entities or situations ---  statements that extend beyond the here-and-now --- has remained elusive. -->
-
-<!-- Formalizing the meaning of linguistic expressions requires specifying *truth conditions*, or the states of the world in which the expression is true vs. false. -->
-<!-- Using the tools of formal semantics, we specify a *truth function*: A function from states of the world to truth-values.  -->
-<!-- A simple truth function for a generalization could be a threshold on an agent's posterior probability: $\denote{u_{generalization}}(h, \theta): \{ h: h > \theta\}$, where $\denote{u_{generalization}}$ represents a function from a state of the world $h$ and a threshold variable $\theta$ to the set of the states of the world where $h > \theta$.
--->
-<!-- Applying this function to a set of worlds returns a set of worlds that are consistent with $h > \theta$. -->
-
-<!-- Though intuitively appealing and simple, this threshold-based truth function for a generalization is problematic. -->
-<!-- <!-- fixed value of $\theta$ seems unlikely. -->
-<!-- The generalization *Mary smokes cigarettes* suggests a daily-habit (e.g., $h > \text{once a day}$), while *Bill writes poems* implies something much weaker, perhaps a poem every few weeks (e.g., $h > \text{once a month}$.
--->
-<!-- *Drinking moonshine makes you go blind* and so does *staring at the sun*, but neither causal statement tells you to precisely the increased relative risk. -->
-<!-- *Mosquitos carry malaria* is a true statement despite the prevalence of carrying malaria among mosquitos being a just a fraction of 1\%, while *Ducks are female* might seem like a weird thing to say, even though the rate is much higher than the malaria-carrying mosquitos.
--->
-<!-- Finally, *Ducks lay eggs* is a good generalization, though the rate is the same as *Ducks are female*. -->
-<!-- The meaning of generalizations, it seems, cannot reduce to a single, precise quantitative statement; this is the major stumbling block to providing a formal account of genericity [@Carlson1977; @Leslie2008; @NickelBlackwell].
--->
-
-<!-- We hypothesize the simple threshold-based truth function for lingusitic generalizations can be rescued by positing an *underspecified* meaning.  -->
-<!-- That is, we adopt a threshold semantics as described above, but imagine that $\theta$ is not a fixed property of language but rather is drawn from a prior probability distribution. -->
-<!-- In this formulation, listeners infer thresholds along with speakers' intended meanings in context. -->
-<!-- We formalize this hypothesis with a "literal listener" model from the Rational Speech Act framework [@Frank2012; @Goodman2013; @Goodman2016]. -->
-
-<!-- *Bills writes poems* might true if Bill does it a few times a year, while we might be hesitant to say *Mary smokes cigarettes* if she only does it once every few months. -->
-<!-- *Ducks lay eggs* is true despite only the female ducks laying eggs, while *Ducks are female* is strange to say (even though only the females are female). -->
-
-<!-- The language of generalizations is so simple that it appears everywhere in human conversation (*Movie theaters are cold.*), pedagogy (*The blicket makes the machine play music.*), political and scientific discourse (*The President peddles falsehoods.*, *Psychology experiments don’t replicate.*), stereotypes (*Boys are good at math*), motivation (*Big girls eat their broccoli!*), emotion-regulation  (*Accidents happen.*), child-directed (*Mommy works late*) and child-produced speech (*Slides aren't for grown-ups!*), and many other facets of experience [@GelmanEtAl2004; @Gelman2008; @Cimpian2010motivation; @Rhodes2012].
--->
-
-<!-- Though the language of generalizations is found everywhere and in every language [@Behrens2005; @Carlson1995], the meaning of such linguistic expressions is philosophically puzzling and has resisted precise formalization.
--->
-<!-- Intuitively, generalizations should convey something about the probability of an instance of the category to have a property, but exactly what is conveyed is unclear. -->
-
-<!-- What if we leave the $\theta$ underspecified in the semantics? -->
-<!-- That is, what would a listener believe if she drew $\theta$ from an uninformed prior belief distribution: $P(\theta)$?^[ -->
-<!-- Previous attempts have been made to salvage this threshold semantics, using a semantic a technique called "domain restriction", wherein the scope of generalization is restricted to a smaller subset of entities or instances [e.g., "only female ducks"; @Cohen1999].
--->
-<!-- Though effective at dealing with at least some of these semantic puzzles, this approach leaves unresolved why the domain should be restricted in some cases and not others. -->
-<!-- We return to this more fully in the General Discussion. -->
-<!-- ] -->
-
-<!-- [MHT: talk about soft semantics here?] -->
-
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-
-<!-- The threshold $\theta$ is assumed to be drawn by an uninformative prior distribution, defined on the same scale as the probability $h$: $\theta \sim \text{Uniform}(0, 1)$.^[ -->
-<!-- Though it's plausible that different thresholds could be learned for different domains, we assume an uninformed prior distribution in our model to show how background knowledge about how the world works drives inferences.
--->
-<!-- ] -->
-<!-- Finally, the prior distribution $P(h)$ is a distribution over the degrees of probability. -->
-<!-- The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenabum2006; @Kemp2008].
--->
-<!-- This is a simple Bayesian model of interpreting a statement conveying a generalization. -->
-
-<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq.
-\ref{eq:L0}).
--->
-
-<!-- <!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } --> 
-<!-- \begin{equation}  -->
-<!-- S_{1}(u \mid h) \propto \exp{(\lambda \cdot U(u; h)  } -->
-<!-- \label{eq:S1} -->
-<!-- \end{equation} -->
-
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda$. -->
-<!-- Inspired by Bayesian decision theory, the speaker takes actions (i.e., produces utterances) soft-max optimally in accord with his utility function \cite{Baker2009}. -->
-<!-- The utility function of a speaker is based on the informativeness of the utterance, which is computed with respect to what a naive listener $L_0$ would believe after hearing the utterance, taking into account the cost of the utterance $C(u)$.
--->
-<!-- \begin{equation} -->
-<!-- U(u; h) = \ln{ \int_{\theta} L_0(h \mid u)}  \diff \theta - C(u) -->
-<!-- \label{eq:utilS1marginalization} -->
-<!-- \end{equation} -->
-<!-- Since the speaker doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[ -->
-<!-- A more general version of this model could relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate. -->
-<!-- Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind.  -->
-<!-- In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution:  -->
-<!-- $U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$ -->
-<!-- ] -->
-<!-- $S_1$ thus seeks to minimize the surprisal of $s$ given $u$ for the naive listener, while bearing in the mind the utterance cost $C(u)$. -->
 
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Degree of probability h") +
+    xlab("Prevalence h") +
     ylab("Scaled probability density") +
@@
 All models were implemented in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented in the RMarkdown document that generated this paper text and figures, using the R package RWebPPL.
+The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
 That document, as well as the other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
 
-The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon a listener's *a priori* beliefs about the probabilty in question $P(h)$.
-For purposes of illustration, we present present the listener $L$ interpretations of the generalization for the underspecified threshold model as well as a fixed threshold model where the threhsold is set to the lowest possible value, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
-
-Above, we described the intuition for how an underspecified threshold interacts with a uniformly uncertain belief about the probability $h$.
-Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-Note that our model of endorsements is a model of a speaker who decides whether or not to say the generic to the listener or to stay silent. 
-Qualitatively speaking, model predictions for endorsement can be read off Figure \ref{fig:simulations} by comparing the posterior distribution over the probability $h$ upon hearing the generalization with the prior distribution over $h$ (which is the same as the listener's posterior upon hearing "silence").
-The speaker decides, for the degree of target probability $h$ that she seeks to communicate, will the generalization be better than nothing?
-
-In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
-Here, we posit the prior is bimodal with peaks near 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and for those that do have members that bark, many of them bark (i.e., have some high $h$).
-<!--  -->
-We see that the fixed threshold (middle row) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" a Beta distribution with an expected value (mean) close to zero. 
+The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability of that utterance vs.
+silence accurately conveying to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
+This probability is given by $L(h \mid u, \theta)$ (Eq.
+\ref{eq:S1}) and depends upon  the listener's *a priori* beliefs about the prevalence $h$ in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
+\ref{eq:S1}).
+Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
+For purposes of illustration, we present different hypothetical priors on prevalence $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+
+These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
+The fixed-threshold model rules out only the lowest possible prevalence ($h \sim 0$) and returns a posterior very similar to the prior.
+The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[
+The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
+If the threshold $\theta$ is very high, only the highest prevalences $h$ would pass the threshold.
+If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower.
+As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
+When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
+The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
+]
+
+Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
+The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
+In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this sort of prior could be over the prevalence of the feature "barks" because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
+We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
 The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
 ]
-Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.
-
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
-The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than the "barks" prior: The listener thinks that about 50% of robins lay eggs.
-Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
-Differences in the endorsements of these two statements would come from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
-In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content. 
-In the case of "lays eggs", the utterance carries a lot of information (relative to the prior).
-
-Finally, we look at how a listener would interpret the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-Indeed, we see that for the prior over "carries malaria"---which *a priori* assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread---the listener's posterior upon hearing the generalization is similar to what she learns about hearing "Some mosquitos carry malaria".
-Thus, a speaker who believes "some but very few" mosquitos carry malaria will still endorse the generalization.
+The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
+
+How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
+In each case, we must consider the prevalence prior for the feature:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
+For being female, no matter want animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., \%50 of X are female; Figure \ref{fig:simulations} bottom row).
+For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
+This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure \ref{fig:simulations} row 3).
+For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure \ref{fig:simulations} rows and 5, middle red panel).
+The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
+In other words, "Robins are female" has little very informational content as the listener's the posterior is nearly identical with her prior.
+"Robins lay eggs", however, has a lot of informational content.
+
+Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
+The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
+Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns about hearing "Some mosquitos carry malaria" (the fixed threshold; Figure \ref{fig:simluations} row 4).
+Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
 
 In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$ as well as the inferences derived from a fixed-threshold semantics.
-In the rest of this paper, we examine the behavior of the speaker model as a model of endorsements through three case studies: generalizations about categories, events, and causes.
+For these simulations, we had specify the prevalence prior $P(h)$.
+In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
 

### 2017-09-01 paper/comgen-paper.Rmd
small edits from beginning to case study 1

@@
 Generalizations in language are often studied in *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-In contrast to *particular statements* which describe individual entities or situations (e.g., "Rufus is friendly") and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which two-and-a-half-year-olds recognize [@Cimpian2008].
+Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
+In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which 2-and-a-half-year-olds appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 -->
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-Generalizations are much than just generics, however; they can be found in statements about individuals (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generics are just one case of generalizations in language, however;  individuals can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 We propose a formal, unified account of generalizations in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
-We do so by first describing the much more well-studied form of generalization: generalization from observations. 
-The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is a good model of human generalizations [@Shepard1987; @Tenenbaum2001].
+We do so by first reviewing the much more well-studied form of generalization: generalization from observations. 
+The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is a good model of human generalization [@Shepard1987; @Tenenbaum2001].
 We then formalize how these probabilities are communicated, using a rational model of communication --- the Rational Speech Act theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016].
@@
 Heretofore, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
-The language of generalizations, however, does not make reference to entities in the world or concrete situations, but instead refers to concepts in the head.
+The language of generalizations, however, does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
 
@@
 
-Generalizations are used to make predictions about properties instances that an agent has yet to experience [@HumeTHN]. 
+As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
+Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN]. 
 From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
-As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
@@
 Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
-Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to costly to observe (e.g., *starting at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
+Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *starting at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
 For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
@@
 
-$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function that returns probabilities proportional to $1$ for prevalence values $h$ greater than threshold $\theta$, and $0$ otherwise. 
-Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
+Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for prevalence values $h$ greater than threshold $\theta$, and $0$ otherwise.
+Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
 What threshold $\theta$ should be used for the generic generalization?
@@
 
-Given the likelihood "meaning" function defined in Eq.
+Given the semantic likelihood function defined in Eq.
 \ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over the prevalence $P(h)$:
@@
 The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
-This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
-Critically in our model, this structure is in listener's knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$.
+This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
+Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$.
 
@@
 We discuss these alternative formulations and provide formal model comparison between these RSA models in Appendix.
+
+## Model simulations
+
+All models were implemented in the probabilisitic programming language WebPPL [@dippl].
+The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
+That document, as well as the other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+
+The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability of that utterance vs.
+silence accurately conveying to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
+This probability is given by $L(h \mid u, \theta)$ (Eq.
+\ref{eq:S1}) and depends upon  the listener's *a priori* beliefs about the prevalence $h$ in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
+\ref{eq:S1}).
+Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
+For purposes of illustration, we present different hypothetical priors on prevalence $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
 
@@
 
-## Model simulations
-
-All models were implemented in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as the other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability of that utterance vs.
-silence accurately conveying to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
-This probability is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon  the listener's *a priori* beliefs about the prevalence $h$ in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
-\ref{eq:S1}).
-Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
-For purposes of illustration, we present different hypothetical priors on prevalence $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
-
 These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
@@
 The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this sort of prior could be over the prevalence of the feature "barks" because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this sort of prior could be over the prevalence of the feature "barks" because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
 The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
@@
 In each case, we must consider the prevalence prior for the feature:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter want animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., \%50 of X are female; Figure \ref{fig:simulations} bottom row).
+For being female, no matter want animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
 For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure \ref{fig:simulations} row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure \ref{fig:simulations} rows and 5, middle red panel).
+This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
+For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
 The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's the posterior is nearly identical with her prior.
+In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
 "Robins lay eggs", however, has a lot of informational content.
@@
 The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns about hearing "Some mosquitos carry malaria" (the fixed threshold; Figure \ref{fig:simluations} row 4).
+Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns about hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
 Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".

### 2017-09-01 paper/comgen-paper.Rmd
sophies feedback for model section

@@
 
-As adults we readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
 Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
+People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
@@
 The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
-Observing some number of instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
-As a concrete example, consider the feature \textsc{is friendly} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs and note how many of them were friendly ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will be friendly (in other words, a belief about the friendliness of dogs).
+From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
+The Bayesian probability calculus provides a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011]: Observing some number of instances of $k$ with $f$ will update what an observer believes *a priori* (formally: a prior belief distribution) in order to make predictions about unobserved instances, via a posterior belief distribution.
+As a concrete example, consider the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{barks}\} \mid x \in \{\text{is a dog}\})$.
+If an agent were to encounter some number of individual dogs and note how many of them bark ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will bark (in other words, a belief about the barkiness of dogs).
 
@@
 
-Our ability to use this updated belief $P(h \mid d)$ in order to make predictions about unobserved instances is a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011].
-
 Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
-For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
-This subtlety can be modeled using heirarchical models to provide structure to the prior distribution in a Bayesian model [@Kemp2008].
+For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
+This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
 Observations that are generated by an intentional agent can lead to similarly subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].
@@
 Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
-Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *starting at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
-For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
+Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
+For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
 
@@
 If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
-One very simple semantic theory that has been used for describing quantified statements (e.g., "some", "all") is a *threshold semantics*.
+One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
 For generalizations, the threshold would apply to the subjective probability or *prevalence* $h$:
@@
 This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
-Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$.
+Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.
 
@@
 In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
-Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an **endorsement model** as a Bayesian speaker's decision of whether or not to say the generalization to the listener $L$ (Eq.
+Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
 \ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that he is trying to communicate.
@@
 The speaker $S$ doesn't know the threshold $\theta$; rather, he integrates over the likely values that the listener will believe. 
-Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$, which acts as a soft-max function.
+Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with rationality governed by parameter $\lambda$, which acts as a soft-max function.
 
 The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
-To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
-with just two alternatives (say the utterance vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
+We specify a single alternative utterance corresponding to *not saying the generalization*:
+With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. 
 Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
@@
 The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-These are not of primary theoretical interest to this paper, as *any* formal model that explains the very flexible endorsement patterns of generalizations in language will be a substantial advancement.
+These are not of primary theoretical interest to this paper, as *any* formal model that explains the flexible endorsement patterns of generalizations in language will be a substantial advancement.
 However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
@@
 
-The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability of that utterance vs.
-silence accurately conveying to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
+The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability that utterance vs.
+silence accurate conveys to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
 This probability is given by $L(h \mid u, \theta)$ (Eq.
@@
 In each case, we must consider the prevalence prior for the feature:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter want animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
+For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
 For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.

### 2017-09-01 paper/comgen-paper.Rmd
more of sophies feedback from into to expt 1b

@@
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations we flourish collectively without individually needing to taste each potentially-poisonous plant or witness enough lightning strikes.
+By sharing generalizations, we flourish collectively without individually needing to taste  potentially-poisonous plants or personally witness enough lightning strikes.
 Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
@@
 To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
-Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments the measure both quantities and relate them via our model to the endorsements of generalizations about categories, or *generic language*. 
-In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events, or *habitual language*.
-In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes, or *causal language*.
+Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
+In Section 3, we describe experiments that measure both quantities and relate them via our model to the endorsements of generalizations about categories (*generic language*). 
+In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events (*habitual language*).
+In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes (*causal language*).
+
 Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
-In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
+In the final section of the paper, we discuss how our model paves a path to unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
 Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language in the way that people learn from language.
@@
 This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
-Observations that are generated by an intentional agent can lead to similarly subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].
+Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009].
 
@@
 In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
-Though it is possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.
+Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.
 
@@
 
-Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
+Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according to the meaning of an utterance $u$.
 $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
@@
 The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-These are not of primary theoretical interest to this paper, as *any* formal model that explains the flexible endorsement patterns of generalizations in language will be a substantial advancement.
+To our knowledge there is no unifying computational account of linguistic genericity and as such, the primary theoretical interest of this paper is to outline such an account, rather than discuss possible variations within it.
 However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in Appendix.
+We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
 
@@
 The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this sort of prior could be over the prevalence of the feature "barks" because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of the feature *barks* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
 The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
@@
 The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns about hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
+Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
 Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
 
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$ as well as the inferences derived from a fixed-threshold semantics.
+In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
 For these simulations, we had specify the prevalence prior $P(h)$.
@@
 
-Generalizations about categories (i.e., *generic language*; e.g., *Birds fly.*) have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
-It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., *Most birds fly*) and has received the most attention from philosophers, linguists, and psychologists.
+Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
+It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., "Most dogs bark") and has received the most attention from philosophers, linguists, and psychologists.
 
 Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
-That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
-As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs.
-"Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties, as explored through simulation in the **Model predictions** section.
+That is, "Mosquitos carry malaria" and "Birds lay eggs" are reasonable things to say, but "Birds are female" is not.
+As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
 We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
@@
 <!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
-We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g.
-\emph{Ducks have wings.}), minority (e.g.
-\emph{Robins lay eggs.}), striking (e.g.
-\emph{Mosquitos carry malaria.}), false generalization (e.g.
-\emph{Robins are female.}), and false (e.g.
-\emph{Lions lay eggs.}).
-In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.
+We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
+"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
+"Lions lay eggs.").
+In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.
 
@@
 If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
-This is important because it is one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
+A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
 As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
@@
 Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; If you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature we are thinking of.
-^[
-The subjective probability may, in fact, be non-zero in what we're calling as 0\%, non-zero but very small.
-This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a foreign environment.
+Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
+That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
+The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
+Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
 ].
@@
 We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
+We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
 After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.
@@
 Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-3 participants were accidentally allowed to complete the experiment for a second time; we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
+Three participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
+Two participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
 The experiment took about 10 minutes and participants were compensated \$1.00.
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt.
-1b (e.g.
-\textsc{robins, mosquitos}) and asked to generate five of their own.
-
-A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
+1b (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own.
+
+A column then appeared to the right of the animal names with a property in the header (e.g., *lays eggs*).
 Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
-Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
-In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
+Eight property--columns appeared in the table, and this whole procedure was repeated two times.
+In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
 <!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
@@
 We formalize this hypothesis using a simple Bayesian mixture model. 
-We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
+We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while other kinds do not; cf., @Griffiths2005].
 The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.
 
-For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
+For the structured hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
 The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
@@
 Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $\mathcal{D}_{stable}$.
+Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
 This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
@@
 
-Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property's prevalence prior has its own parameters).
+Each property (e.g., *lays eggs*, *carries malaria*) is modeled independently (i.e., each property's prevalence prior has its own parameters).
 
@@
 It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
-To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
-This is called the *posterior predictive distribution* and is an important step in model validation. 
+To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the *a posteriori* likely values of the parameters and then use the inferred parameters to generate new data.
+The generated data from the model's posterior is called the *posterior predictive distribution* and is an important step in model validation. 
 If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
@@
 
-We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
 To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
@@
 The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
+Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
 ]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
@@
 The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
-These distributions are structured and must be represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
+These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
 

### 2017-09-01 paper/comgen-paper.Rmd
fig caption for generics

@@
 
-```{r generics-endorsement-figure, fig.width=11, fig.height=8}
+```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generaliztions about categories.
+Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
+Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on prevalence alone (lower left) and prevalence and cue validity (lower right).
+Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the prevalence of the feature within a referent category.
+These distributions are inferred using all three data sources from Expt.
+1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach)."}
 grid.arrange(generics.endorsement.spectrum, 

### 2017-09-02 paper/comgen-paper.Rmd
add captions for all figures

@@
   - \usepackage{booktabs}
+  - \usepackage{amsmath}
 
@@
 
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generaliztions about categories.
+```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
 Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
@@
 
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics_bayesnetmodel.pdf}
-    \caption{Caption
-    }
-  \label{fig:genericsModelDiagram}
-\end{figure}
+```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
+The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
+1a.
+The prevalence within the referent category $d^{pr}_{k,f}$ is generated from a latent prevalence $h_{k,f}$.
+The fixed-threshold (control model) or uncertain-threshold RSA model takes the prevalence prior $P_f(h)$, the referent-category prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
+This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
+Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion.
+"}
+knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
+```
 
@@
 
-```{r habituals-endorsement-figure, fig.width=11, fig.height=8}
+```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the (log) frequency of the referent action.
+Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on (log) frequency alone (lower left) and log frequency and distinctiveness (lower right).
+Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
+These distributions are inferred using both data sources from Expts.
+2a & 2b.
+(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})"}
 grid.arrange(fig.habituals.endorsement.vs.freq, 
@@
 
-```{r habituals-predictive-figure, fig.cap="A: Results of Expt 3a.
-B: Results of Expt.
-3b as they relate to the predicted frequencies from Expt.
-3a, C & D: Endorsement models based on past frequency (C) and predictive frequency (D).", fig.width = 10.5, fig.height = 11}
+```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
+Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
+Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10.5, fig.height = 11}
 legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
@@
 
-```{r figure-causals, fig.width=11, fig.height=8, cache = T}
+```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
+Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
+Bottom: Prevalence priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
+These distributions are inferred using both data sources from Expt.
+3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
 grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,

### 2017-09-02 paper/comgen-paper.Rmd
begin replacing prevalence w feature-probability

@@
 abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Birds fly").
+    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Dogs bark").
     The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
@@
     Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
     Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
@@
 These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of category having a property) is only incidentally related to generic meaning.
-**Conceptual accounts** of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+*Conceptual accounts* of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
 From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
@@
 The properties can vary greatly (e.g., having fur, causing jitters, typing). 
-Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **prevalence**: 
+Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **feature-probability**: 
 $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
-We denote prevalence as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency.
+We denote feature-probability as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency or prevalence.
 ]
@@
 One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
-For generalizations, the threshold would apply to the subjective probability or *prevalence* $h$:
+For generalizations, the threshold would apply to the *feature-probability* $h$:
 
@@
 
-Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for prevalence values $h$ greater than threshold $\theta$, and $0$ otherwise.
+Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for feature-probabilities $h$ greater than threshold $\theta$, and $0$ otherwise.
 Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
@@
 Given the semantic likelihood function defined in Eq.
-\ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over the prevalence $P(h)$:
+\ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over feature-probabilities $P(h)$:
 
@@
 
-Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according to the meaning of an utterance $u$.
+Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$.
 $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
-$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
-The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
+$P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$.
+The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
 This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
@@
 
-In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
+In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Robins lay eggs" is good; "Robins are female" is not) based on some known or believed feature-probability $h$ in a referent category (e.g., only female robins lay eggs).
 Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that he is trying to communicate.
-Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
+\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
+Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the feature-probability of the property in the category. 
 In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
@@
 
-The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
+The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **referent feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.
 We specify a single alternative utterance corresponding to *not saying the generalization*:
@@
 The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability that utterance vs.
-silence accurate conveys to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
-This probability is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon  the listener's *a priori* beliefs about the prevalence $h$ in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
+silence accurate conveys to a naive listener a feature-probability $h$ in a referent-category (e.g., the \% of robins that lay eggs).
+This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
+\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
 \ref{eq:S1}).
 Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
-For purposes of illustration, we present different hypothetical priors on prevalence $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
 
@@
 
-```{r simulations, fig.cap = "Prior distributions over the prevalence of a feature (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
+```{r simulations, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
 The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence h") +
+    xlab("Feature-probability h") +
     ylab("Scaled probability density") +
@@
 These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible prevalence ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[
+The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
+The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
 The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest prevalences $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower.
+If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
+If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
 As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
@@
 The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of the feature *barks* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
 The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
@@
 How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the prevalence prior for the feature:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
+In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
 For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
@@
 In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the prevalence prior $P(h)$.
+For these simulations, we had specify the feature-probability priors $P(h)$.
 In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
@@
 
-Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
-That is, "Mosquitos carry malaria" and "Birds lay eggs" are reasonable things to say, but "Birds are female" is not.
+Any theory of generic language must explain its puzzling flexibility of usage with respect to feature-probability.
+That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not.
 As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
-We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq.
-\ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq.
+We validate these simulations empirically by measuring the prior belief distribution over the feature-probabilities $P(h)$ used in Eq.
+\ref{eq:L0} and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq.
 \ref{eq:S1} (Expt.
@@
 "Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.
-
-To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
+In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low, medium, and high feature-probability properties.
+
+To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a).
 We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
 In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
-*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the prevalence prior.
-If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
+*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the feature-probability prior.
+If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
 A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
-As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
-
-After having validated a measure of the prevalence prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
+As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
+
+After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
 1b).
@@
 
-## Experiment 1a: Measuring the Prevalence Prior for Categories
-
-The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
+## Experiment 1a: Measuring the feature-probability prior for categories
+
+The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
 To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
@@
 
-This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
+This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
+We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
 We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
@@
 Eight property--columns appeared in the table, and this whole procedure was repeated two times.
-In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
+In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
 <!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
@@
 To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-In analyzing the prevalence prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
+In analyzing the feature-probability prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
 We formalize this hypothesis using a simple Bayesian mixture model. 
 We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while other kinds do not; cf., @Griffiths2005].
-The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.
+The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the feature-probability prior data.
 
@@
 
-Each property (e.g., *lays eggs*, *carries malaria*) is modeled independently (i.e., each property's prevalence prior has its own parameters).
+Each property (e.g., *lays eggs*, *carries malaria*) is modeled independently (i.e., each property's feature-probability prior has its own parameters).
 
@@
 The Bayes Factor indicates the extent to which the data support one model over another.
-The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
-Indeed, the data strongly suggests the prevalence prior is structured.
+The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
+Indeed, the data strongly suggests the feature-probability prior is structured.
 
 It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
-To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the *a posteriori* likely values of the parameters and then use the inferred parameters to generate new data.
+To see how well the structured model fits the feature-probability prior data, we use Bayesian inference to infer the *a posteriori* likely values of the parameters and then use the inferred parameters to generate new data.
 The generated data from the model's posterior is called the *posterior predictive distribution* and is an important step in model validation. 
@@
 If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
+We do this many times using the posterior distibution to generate a distribution over predicted feature-probability ratings.
 ]
@@
 The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
+Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
 ]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the prevalence of eight different features.
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
 Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
@@
   coord_fixed()+
-    xlab("Prevalence") +
+    xlab("Feature-probability") +
     ylab("Cumulative probability density")+
@@
 
-The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
+The feature-probability prior distribution $P_f(h)$ encodes beliefs about the feature-probability (or, probabilities) of a feature $f$ across different kinds.
 These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
@@
 
-If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
+If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
 For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
@@
 However, we should not throw away the possibility that distributional information about the property is relevant. 
-The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of the construct of cue validity. 
-Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
-If there is a finite number of kinds in the prevalence prior for a feature, and one knows the prevalence of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the prevalence prior, in that it can be derived via Bayes' Rule:
+The mixture parameter $\phi$ in the feature-probability prior distribution can be seen as a generalization of the construct of cue validity. 
+Recall that $\phi$ is the weighting between the two generative components of the feature-probability prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
+If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the feature-probability prior, in that it can be derived via Bayes' Rule:
 $$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
@@
 
-In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
-This data also includes information about the referent-category prevalence (e.g., how many robins lay eggs).
-Using the referent-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
+In Expt. 1a, we measured and modeled the feature-probability prior distribution (e.g., the probability of laying eggs for different kinds of animals) for different features.
+This data also includes information about the referent-category feature-probability (e.g., how many robins lay eggs).
+Using the referent-category feature-probability as $h$ in our speaker model (Eq.
+\ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
 To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
@@
 To try to understand this endorsement data, we articulate a set of simple models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
-As the simplest baseline hypothesis, we first explore whether prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (e.g., prevalence, cue validity) by bootstrapping those data.
-
-Our underspecified threshold model has access to the full prior distribution on prevalence $P(h)$, from which it infers likely thresholds for the generic. 
+As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
+As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
+We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
+
+Our underspecified threshold model has access to the full prior distribution on feature-probabilities $P(h)$, from which it infers likely thresholds for the generic. 
 The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
@@
 
-##### Prevalence baseline
-
-From the prevalence prior data (Expt.
-1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
+##### Referent feature-probability baseline
+
+From the feature-probability prior data (Expt.
+1a), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
-However, large deviations from an account based purely on referent-category prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-
-##### Prevalence and cue validity
+This is because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
+However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
+
+##### Cue validity and referent feature-probability
 
 <!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
-If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
 *Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
@@
 
-For a prevalence distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the prevalence prior distribution.
+For a feature-probability distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the feature-probability prior distribution.
 In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
@@
 
-A linear model that uses predictors for both prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
+A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
 This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
@@
 "Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A single metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high.
+A simple metric like cue validity is too blunt to capture this subtlety.
+Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
 
@@
 
-                                 "Prevalence alone",
-                                 "Prevalence + Cue validity"
+                                 "Feature-probability alone",
+                                 "Cue validity + Feature-probability"
                                  ))) %>%
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence") +
+    xlab("Feature-probability") +
     ylab("Scaled probability density")+
@@
 Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on prevalence alone (lower left) and prevalence and cue validity (lower right).
-Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the prevalence of the feature within a referent category.
+Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
+Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
 These distributions are inferred using all three data sources from Expt.
@@
 The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
-Unlike the simple regression models based on point-estimates of referent-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
+Unlike the simple regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
 This model has two other main architectural differences: an information-theoretic decision between producing the generic vs.
-an information-less alternative and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.
+an information-less alternative (formalized using RSA) and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.
 
 We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on prevalence as well as models an information-theoretic decision of producing the generic vs. an alternative.
+This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
 The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
 For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria").
+Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under this semantics).
 ]
@@
 <!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the referent-category $h'$).
--->
-We use the empirically estimated referent-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
-1a as the listener's prevalence prior $P(h)$.^[
+\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the feature-probability of the property within the referent-category $h'$).
+-->
+We use the empirically estimated referent-category feature-probability as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
+1a as the listener's feature-probability prior $P(h)$.^[
 Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
@@
 ```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
-The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
+The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
 1a.
-The prevalence within the referent category $d^{pr}_{k,f}$ is generated from a latent prevalence $h_{k,f}$.
-The fixed-threshold (control model) or uncertain-threshold RSA model takes the prevalence prior $P_f(h)$, the referent-category prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
+The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$.
+The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
@@
 
-To fit this model, we incorporate the RSA model into the Bayesian data analysis model of the prevalence prior data (Expt.
-1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$ is inferred jointly with the target prevalence $h_{k, f}$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_f(h)$ for each property $f$ using data from Expt.
+To fit this model, we incorporate the RSA model into the Bayesian data analysis model of the feature-probability prior data (Expt.
+1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$ is inferred jointly with the referent feature-probability $h_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$ using data from Expt.
 1a \& b (see Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the prevalence distributions, we use the same priors described in Expt.
+For the parameters of the feature-probability distributions, we use the same priors described in Expt.
 1a; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
@@
 
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (prevalences, prevalence priors, and the speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the referent-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
+Importantly, the model recapitulates the feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1a).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the prevalence distributions).
+This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the feature-probability distributions).
 
@@
 For almost all items, it assigns an intermediate endorsement.
-This is because almost all items get endorsed by some participants; the model then infers that the prevalence must be at least a little greater than 0\%; but, if the prevalence is greater than 0\%, the statement is literally true.
+This is because almost all items get endorsed by some participants; the model then infers that the referent feature-probability must be at least a little greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true.
 The speaker model then must decide is it better to say the 0\%-threshold meaning or stay silent.
@@
 To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the referent-category (also in blue).
-The grey distribution shows the listener's prior distribution over prevalence of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
-It is also the listener $L_0$'s posterior upon hearing the silent utterance.
+The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
+The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
+It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
 The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
@@
 "Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.
+"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
 
@@
 
-By measuring listeners' prior beliefs about the prevalence of the property across kinds and the prevalence of the target kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
+By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
 The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
@@
 
-In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
+In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
 Thus, we have shown how these measurements are related to generic endorsement via our model. 
-Yet, this evidence is still correlational in nature.
+This evidence is correlational in nature, however.
 We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the target propensity that the speaker aims to communicate.
+In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
 
@@
 
-From a methodological standpoint, habituals are a domain particularly amenable to manipulating the target propensity that a speaker aims to communicate.^[
-While target probability can be manipulated for generalizations about categories (generic language) (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what prevalence values are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
+From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
+While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
 ]
-First of all, because of the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, propensity information of people doing actions can be expressed in an easily-interpretable frequency (e.g., "Last month, Mary smoked cigarettes 3 times.").
+Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
+In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
+In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability.
+Rates are, of course, not constrained to be between 0 and 1 as probabilities are.
+However, a rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
+]
 
 We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the frequency of events, for different kinds of events (Expt. 2a).
+First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
 We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the actual frequency with which a person does an action (Expt. 2b).
-In addition to directly manipulating the target propensity, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
+Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
+In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
 
 Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have been relatively agnostic as to the interpretation of $h$, the target propensity that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive probability that this event will occur in the near future (e.g., how likely it is that Mary will smoke next week)?
-We do this by measuring particpants predictions about future frequency in situations where there are causal forces enabling or preventing the action (Expt. 2c). 
+Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
+In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week)?
+We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
 We separately measure endorsements under the same contexts (Expt.
 2d) and use the prediction measurements (Expt.
-2c) as the target propensity $h$ that the speaker model is trying to communicate in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses *predictive frequency* as the object of communication is able to predict the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
+2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
+To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
 
@@
 
-## Experiment 2a: Measuring the propensity prior for event knowledge
-
-In this experiment we elicit the prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
+## Experiment 2a: Measuring the feature-probability prior for events
+
+In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
 For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with some frequency.
-To better understand what frequencies should be expected for different actions, we took advantage of the 
-structured representation of the prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that prior distribution over the prevalence of a feature across different categories can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable frequencies of the property, among those that normally have the property.
-The second component (the "unstable" or "transient cause" component) represents the frequencies of the property among those categories who do not typically have the property.
-This second component will usually result in frequencies of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero frequencies (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the frequency with which people do actions, we consider again two components.^[
+To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
+
+In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
+The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
+The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
+This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
+
+For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
 In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
@@
 
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Propensity priors for events (Expt.
+```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
 2a).
 Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on frequency from the structured, prior elicitation task.
+Right: Reconstructed priors on rates from the structured, prior elicitation task.
 Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
@@
 This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate, or relative frequency, with which a person does the action.
+Question 2 elicits the rate or frequency with which a person does the action.
 This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 

### 2017-09-03 paper/comgen-paper.Rmd
more on feature-probability, light edits to abstract

@@
 abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Dogs bark").
-    The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
+    Generalizations are central to human understanding and language provides simple ways to convey generalization (e.g., "Dogs bark").
+    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
     Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing *genericity* is in determining what which such statements are true or false.
+    The major issue in formalizing generalizations in language is in determining what which such statements are true or false.
     Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
@@
 
-keywords          : "genericity, generalizations, generics, pragmatics, semantics, bayesian modeling"
+keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
 wordcount         : "X"
@@
 One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
-For generalizations, the threshold would apply to the *feature-probability* $h$:
+For generalizations, the threshold would apply to the *feature-probability* $h$:^[
+We emphasize that our account is based on an agent's subjective probability $h$.
+The literature on generic language has often examined *prevalence*, or the proportion of members of a category with the property, as the primary quantitative metric that could relate to generic meaning (in addition to *cue validity*, described below).
+A Bayesian agent, however, would only use prevalence as a way to update her existing state of knowldege to form a subjective probability for future use.
+Thus, we consider the semantic content of a generalization to be related to probability, not necessarily prevalence.
+]
 
@@
 In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-Rates are, of course, not constrained to be between 0 and 1 as probabilities are.
-However, a rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
+A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
 ]
@@
 Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week)?
+In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
 We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
@@
 In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with some frequency.
+For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
 To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
@@
 
-We next explore the endorsements of habituals from the items whose priors were measured the prior elicitation task.
+We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
 
@@
                                  "Speaker model - uncertain semantics",
-                                 "Frequency alone", "Frequency + Distinctiveness"
+                                 "Referent frequency alone", "Distinctiveness + referent frequency"
                                  ))) %>%
@@
 
-```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the (log) frequency of the referent action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on (log) frequency alone (lower left) and log frequency and distinctiveness (lower right).
+```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
+Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
 Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
@@
 Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the target character.
+For all analyses, we collapse across gender of the referent character.
 <!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
@@
 
-#### Frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is good is the frequency itself. 
+#### Referent frequency baseline
+
+The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
 This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
 First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g.
-\emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g.
-3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g.
-\emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g.
-between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the raw log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-We observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
+It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
+We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
+Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
+In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
+
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
 This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
 
-#### Frequency and distinctiveness
+#### Distinctiveness and referent frequency
 
@@
 Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and prevalence in the domain of generics.
+This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
 
@@
 
-We used the pragmatic speaker model $S_1$ (Eq.
+We used the speaker model $S_1$ (Eq.
 \ref{eq:S1}) with the priors elicited above (Expt.
 2a) to predict felicity judgments in Expt.
-2b, assuming the target propensity ($h$, to be conveyed by $S_1$) is the provided frequency (e.g., 3 times in the past year).
+2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
 Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
@@
 In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
+This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
 Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
@@
 While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate propensity in terms of past frequency or future expectations?
+Does habitual language communicate probabilities in terms of past frequency or future expectations?
 On one hand, speakers can only *know* about what has happened in the past.
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
+In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
 2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
@@
 
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the propensity of the event.
-Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the propensity prior is indeed causally related to generic endorsement.
+In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
+Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
+In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
 
@@
 Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language has been shown to faciliate causal learning for nonobvious causal relations in 2-year-olds [@Bonawitz2010].
-
-In this paper, we posit that prevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the prevalence priors and endorsements of generalizations about causes.
+Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
+
+In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
+In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
@@
 
-## Experiment 3a: Manipulating the Prevalence Prior for Causes
+## Experiment 3a: Manipulating the feature-probability priors for causes
 
 In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our prevalence prior manipulation.
+This prediction task serves as a manipulation check for our feature-probability prior manipulation.
 
@@
 In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to the between-subjects condition they are assigned (prior, endorsement, interpretation).
+In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
 
@@
   scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Prevalence") +
+  xlab("Feature-probability") +
   ylab("Scaled probability density")+
@@
 Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Prevalence priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
+Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
 These distributions are inferred using both data sources from Expt.
@@
 In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ is causally related to endorsements of generalizations in language.
+In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
+To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
 
@@
 What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *prevalence*, or probability (Expt. 1, 2a \& 2b, 3).
+Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
 This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
@@
 In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the prevalence of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
+We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
 These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the prevalence prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
+Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
 
@@
 
-## Structured prior knowledge and Implications for Conceptual Structure
+## Structured prior knowledge and implications for conceptual accounts
 
@@
 
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008]. 
+Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
+In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
+As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
+] 
 Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
@@
 Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the prevalence-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted prevalence is the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different prevalence priors. 
-In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
+Where in the probability-based semantics could such conceptual distinctions come into play?
+
+Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
+That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
+We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
+In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
 
 It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical prevalence distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
+We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
 It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
 Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective prevalence.
+Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
 
@@
 Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive prevalence would not be any different for Supreme Court Justices than any other profession.
+Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
 This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
@@
 
-## Acquiring the Language of Generalizations
+## Acquiring the language of generalizations
 
@@
 What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the prevalence of feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
+If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
 The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
@@
 
-Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
+Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
 Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to *prevalence* as a metric against which generics get evaluated.
+Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
 For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on prevalence and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
+"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
 Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
@@
 
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the prevalence of *laying eggs* among *robins*?).
+It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
 These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
@@
 3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Prevalence or propensity in our theory is a posterior predictive probability, which incorporates background knowledge in order to make predictions about the future. 
+Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
 The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
@@
 This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual prevalence is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
+This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
 In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
 4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the prevalence of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors. 
-Thus, our model would also predict these effects, but by way of the prevalence prior rather than something special about dangerous features per se.
+2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
+That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
+Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
 However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
@@
 @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on prevalence $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence of properties across different categories.
+In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
+In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
 This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
@@
 
-(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
+(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
 The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
@@
 Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true prevalence of the feature among the referent-category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Birds are female".
+From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
+Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
 
@@
 ].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated from the generic statement).
+The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
 However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
 This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the prevalence of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
+If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
 We find this possibility intruiging for future work.
@@
 Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the target prevalence, the prior distributions on prevalence, or the comparison class.
+Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
 <!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->

### 2017-09-14 paper/comgen-paper.Rmd
light edits in intro through model pred; make habituals figure prettier

@@
 abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey generalization (e.g., "Dogs bark").
+    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Dogs bark").
     The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalizations in language is in determining what which such statements are true or false.
+    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
+    The major issue in formalizing generalization in language is in determining what which such statements are true or false.
     Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
     To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
+    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of generalizations in language, while simpler models fall short.
     This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
-    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
+    The results suggest that central phenomena emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
 
 keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "X"
+wordcount         : "20000"
 
@@
 
-```{r libraries}
+```{r libraries, cache = F}
 library(papaja)
@@
 -->
-Generics are just one case of generalizations in language, however;  individuals can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generics are just one case of generalization in language, however;  events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 
-Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about observable behavior.
+Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about human understanding.
 A formal model in this domain is useful to make explicit the relevant assumptions of a psychological or linguistic hypothesis for predicting human behavior; this, in turn, makes the theory more falsifiable.
@@
 
-These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of category having a property) is only incidentally related to generic meaning.
+These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of a category having a property) is only incidentally related to generic meaning.
 *Conceptual accounts* of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
@@
 "Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know if you are to survive in a hostile world.
-This theory correctly predicted that generics that convey striking properties would be true even if the property was relatively uncommon [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
+This theory predicts that generics which convey striking properties would be true even if the property was relatively uncommon (e.g., "Sharks attack swimmers"), which has been borne out emprically [@Cimpian2010; @Prasada2013].
 "Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].
@@
 
-We propose a formal, unified account of generalizations in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
+We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
 We do so by first reviewing the much more well-studied form of generalization: generalization from observations. 
@@
 Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals. 
-Heretofore, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
-The language of generalizations, however, does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
-
-Specifically, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations concerns subjective probability in a *simple but underspecified* way.
+Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
+The language of generalization, however, does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
+
+Specifically, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalization concerns subjective probability in a *simple but underspecified* way.
 We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
@@
 As a concrete example, consider the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{barks}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs and note how many of them bark ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will bark (in other words, a belief about the barkiness of dogs).
+If an agent were to encounter some number of individual dogs and note how many of them bark ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will bark (in other words, a belief about the barking capacity of dogs).
 
@@
 If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
-One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
+Perhaps the simplest, quantitative semantic theory is a *threshold semantics*: an utterance is true if some quantity or *degree* is above a threshold.
 For generalizations, the threshold would apply to the *feature-probability* $h$:^[
@@
 Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
+\ref{eq:L0}).
+
+\begin{equation} 
+S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta )}
+\label{eq:S1}
+\end{equation}
+
+The speaker $S$ doesn't know the threshold $\theta$; rather, he integrates over the likely values that the listener will believe. 
+Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with rationality governed by parameter $\lambda$, which acts as a soft-max function.
+
+The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **referent feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
 Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the feature-probability of the property in the category. 
@@
 ]
-
-\begin{equation} 
-S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta )}
-\label{eq:S1}
-\end{equation}
-
-The speaker $S$ doesn't know the threshold $\theta$; rather, he integrates over the likely values that the listener will believe. 
-Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-
-The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **referent feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.
 We specify a single alternative utterance corresponding to *not saying the generalization*:
@@
   facet_wrap(~property, nrow = 1)+
-  geom_text_repel(data = category.text.labels,
+  geom_label_repel(data = category.text.labels,
                   aes(label = category, x = x , y = y),
@@
   ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21)+
+  geom_jitter(width = 0.1, shape = 21, size = 5)+
   ylab("Human endorsement probability")+
   xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
+  geom_text_repel(data = d.hab.endorsement.bayes %>% 
                     mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
                     filter(sentence %in% example.habituals), aes( label = habitual ),
-                       fontface = 'bold', color = 'white',
+                       color = 'black', fill = 'white',
     box.padding = unit(0.35, "lines"),
-    point.padding = unit(0.5, "lines"),
-    segment.color = 'grey50')+
+    point.padding = unit(1e-06, "lines"),
+    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
   scale_x_continuous(limits = c(-1,6), 
@@
                      breaks = c(0, 0.5, 1))+
-  theme(axis.text.x = element_text(angle = 90))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+        legend.position = "bottom")+
   coord_fixed(ratio = 7)+
-  guides(fill = F)
+  guides(fill = guide_colorbar(title = 'log annual rate'))
 ```
@@
   geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21)+
+  geom_linerange(alpha = 0.15)+
+  geom_errorbarh(alpha = 0.15)+
+  geom_point(shape = 21, size = 3)+
   scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
@@
   facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom")+
+  guides(fill = F)
 ```
@@
   scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Prevalence") +
+  xlab("Frequency (log scale)") +
   ylab("Scaled probability density")+
   theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90))+
+        axis.text.x = element_text(angle = 90, vjust = 1))+
       scale_x_continuous(limits = c(-5, 8), 
@@
 
-```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
+```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
 Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
@@
 2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})"}
+(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
 grid.arrange(fig.habituals.endorsement.vs.freq, 
@@
                               fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
+  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
   scale_shape_manual(values=c(21,22,23))+
@@
   ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 90))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
 
@@
   geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23))+
+  scale_shape_manual(values=c(21,22,23, size = 4))+
   geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
@@
   ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 90))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
 ```
@@
                  ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.3)+
-  geom_errorbarh(alpha=0.3)+
+  geom_errorbar(alpha=0.8)+
+  geom_errorbarh(alpha=0.8)+
   scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 0.7)+
+  geom_point(alpha = 1, size = 4)+
   xlab("Predicted frequency (log scale)")+
-  ylab("Endorsement probability")+
+  ylab("Human habitual endorsement")+
   scale_x_continuous(limits = c(-4.2,7.2), 
@@
   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=9)+
+  coord_fixed(ratio=11.4)+
   scale_fill_solarized()+
@@
   theme(
-    axis.text.x = element_text(angle = 90),
+    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
     legend.position="bottom",
@@
   geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21)+
+  geom_point(shape = 21, size = 4)+
   scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
@@
 Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10.5, fig.height = 11}
+Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
 legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))

### 2017-09-14 paper/comgen-paper.Rmd
improve generics figure; tweak habituals fig

@@
          mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))
+  ungroup()
+
+d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
+                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+
+d.prev.summary <- d.prev %>%
+  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
+  filter(item %in% d.gen.endorse.bayes$sentence) %>%
+  mutate(prevalence = prevalence / 100) %>%
+  group_by(Category, Property, item) %>%
+  multi_boot_standard(column = "prevalence")
 
@@
 #   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- d.gen.endorse.bayes %>%
+generics.endorsement.spectrum <- left_join(
+  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
+) %>%
+  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
   #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5))+
-  geom_bar(stat = 'identity', position = position_dodge(),fill = 'grey')+
+  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
+  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
   geom_linerange(position = position_dodge())+
@@
   coord_flip()+
-  ylab("Proportion Endorsement")+
+  ylab("Human generic endorsement")+
   xlab("")+
   #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))#+
+  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
+  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
+  guides(fill = guide_colorbar(title = 'feature probability',
+                               ticks = F))+
+  theme(legend.position = 'bottom')
   #geom_hline(yintercept = -0.25, lty = 3)+
@@
 
-```{r generic-regression-models, cache = T}
+```{r generic-regression-models}
 d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
@@
     item = paste(category, property))
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, Property)) %>%
-  filter(item %in% d.target.items$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(column = "prevalence")
 
@@
              prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper)
+             prev_ci_upper = ci_upper) %>%
+      mutate(sentence = gsub('[.]', '', sentence))
     ),
@@
   geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21)+
+  geom_linerange(alpha = 0.4)+
+  geom_errorbarh(alpha = 0.4)+
+  geom_point(shape = 21, size = 3)+
   scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
   coord_fixed()+
@@
   facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")
+  #theme(legend.position = "bottom")+
+  guides(fill = F)
 ```
@@
 These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach)."}
+1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
 grid.arrange(generics.endorsement.spectrum, 
@@
   xlab("Frequency of target")+
-  geom_text_repel(data = d.hab.endorsement.bayes %>% 
+  geom_label_repel(data = d.hab.endorsement.bayes %>% 
                     mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
@@
                      breaks = c(0, 0.5, 1))+
+  scale_fill_continuous(breaks = c(0, 5))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
@@
   coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate'))
+  guides(fill = guide_colorbar(title = 'log annual rate',
+                               ticks = F))
 ```

### 2017-09-22 paper/comgen-paper.Rmd
intro edits

@@
   - \usepackage{amsmath}
+  - \usepackage{graphicx}
+  - \usepackage{subcaption}
 
 author_note: >
-  Enter author note here.
+  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
 
@@
 It thus is crucial that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste  potentially-poisonous plants or personally witness enough lightning strikes.
+By sharing generalizations, we flourish collectively without individually needing to taste  potentially-poisonous plants or personally witness many lightning strikes.
 Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
@@
 Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which 2-and-a-half-year-olds appreciate [@Cimpian2008].
+In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which 2-and-a-half-year-olds already appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 -->
-Generics are just one case of generalization in language, however;  events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generics are just one case of generalization in language, however;  events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as can causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about human understanding.
-A formal model in this domain is useful to make explicit the relevant assumptions of a psychological or linguistic hypothesis for predicting human behavior; this, in turn, makes the theory more falsifiable.
+A formal model is useful to make explicit the relevant assumptions of a psychological or linguistic hypothesis that is meant to predict human behavior; this, in turn, makes the theory more testable. 
+\ndg{we go on to talk about informal models next... maybe this defense of formal models needs to be later? adjust flow somehow.}
 The major challenge in formalizing generalizations in language is determining what makes such statements true or false.
@@
 http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-].
+], for example.
 The generalization could signal something weaker like *Most* dogs bark.
@@
 The *generics as default* view argues that certain principles explain how generics become true or false.
-"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know if you are to survive in a hostile world.
+"Mosquitos carry malaria" conveys a dangerous or striking property, which is useful to know if you are to survive in a hostile world.
 This theory predicts that generics which convey striking properties would be true even if the property was relatively uncommon (e.g., "Sharks attack swimmers"), which has been borne out emprically [@Cimpian2010; @Prasada2013].
@@
 We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
-We do so by first reviewing the much more well-studied form of generalization: generalization from observations. 
-The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is a good model of human generalization [@Shepard1987; @Tenenbaum2001].
-We then formalize how these probabilities are communicated, using a rational model of communication --- the Rational Speech Act theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016].
+We do so by first considering a much more well-studied form of generalization: generalization from observations. 
+The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization [@Shepard1987; @Tenenbaum2001].
+Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the *object* of communication for generalizations. 
+We thus explore how these probabilities can be communicated in natural language. 
+We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016].
 Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals. 
 Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
-The language of generalization, however, does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
-
+The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
 Specifically, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalization concerns subjective probability in a *simple but underspecified* way.
-We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
+We combine this notion of generic semantics with RSA, and derive predictions for the endorsements of such statements by considering whether or not a speaker would bother to say the generalization to a listener.
 We show that this decision depends in systematic ways on the prior knowledge of the listener.
@@
 
+\ndg{the next two paragraphs feel partly redundant with what just came...}
 The paper is organized as follows. 
 In Section 1, we describe the Bayesian framework for generalization from observations, serving as the foundation for our semantic theory.
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a framework for pragmatic language understanding -- the Rational Speech Act framework.
+In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into the RSA framework for pragmatic language understanding.
 
@@
 
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
+Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
 In the final section of the paper, we discuss how our model paves a path to unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt.
-1b (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own.
+1b (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
 
 A column then appeared to the right of the animal names with a property in the header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
+Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
 Eight property--columns appeared in the table, and this whole procedure was repeated two times.
@@
 <!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
+
+\begin{figure}
+\centering
+    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
+    \caption{Design of Experiment 1a for eliciting prior knowledge about feature-probabilities.
+Left: Participants first generated animal names after seeing six example categories.
+Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
+    \label{fig:generics-prior-task}
+\end{figure}
+
+<!-- ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. -->
 

### 2017-09-23 paper/comgen-paper.Rmd
move defense of formalizing to right before proposal, for flow; update gitignore

--- 2017-09-22 paper/comgen-paper.Rmd
@@
 Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about human understanding.
-A formal model is useful to make explicit the relevant assumptions of a psychological or linguistic hypothesis that is meant to predict human behavior; this, in turn, makes the theory more testable. 
-\ndg{we go on to talk about informal models next... maybe this defense of formal models needs to be later? adjust flow somehow.}
 The major challenge in formalizing generalizations in language is determining what makes such statements true or false.
@@
 The diversity of generic statements highlighted by the conceptual accounts is interesting, but insofar as generics are a single, unified phenomenon, there should be a general, unified principle that explains what makes the statements true or false.
+In addition, a unified theory should be formalized to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to predict human behavior; this, in turn, makes the theory more testable.
+\ndg{we go on to talk about informal models next... maybe this defense of formal models needs to be later? adjust flow somehow.}
+\mht{moved it here}
 <!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.

### 2017-09-27 paper/comgen-paper.Rmd
more comments wip

@@
 
-The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
+\ndg{smooth out this par.}
+The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
 From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
@@
 
+\ndg{what is this par doing for us? delete?}
 Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
@@
 
+\ndg{i'm not sure that generalization from examples should have it's own section, as opposed to be a subsection or couple pars of the next...}
+
 # Generalization from Language
 
-If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability.
-Perhaps the simplest, quantitative semantic theory is a *threshold semantics*: an utterance is true if some quantity or *degree* is above a threshold.
+If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys a generalization to be related to probability.
+If we wish to connect to the semantic tools of *truth values* \ndg{cite montague?}, then we will need to connect the scalar quantity of probability to a boolean truth value.
+Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: an utterance is true if the underlying quantity is above a threshold.
 For generalizations, the threshold would apply to the *feature-probability* $h$:^[
@@
 ]
+
+\ndg{why are there any deltas yet? so far we only want a truth functional semantics, so something like $\denote{u_{gen}} = h>\theta$. then we use the delta in eq:L0.}
 
@@
 Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
+
 What threshold $\theta$ should be used for the generic generalization?
-
-To answer this, we draw a metaphor to Bayesian statistics and data analysis.
-When there is a latent parameter the Bayesian scientist knows little about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
+In Bayesian statistics, when there is a latent parameter that little is known about, one puts a prior distribution over the parameter and infers the parameter's likely value given any data.
 In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
@@
 
-Given the semantic likelihood function defined in Eq.
+Given the semantic function defined in Eq.
 \ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over feature-probabilities $P(h)$:
@@
 Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$.
+\ndg{i don't like describing L0 as a bayesian agent, because this is not an instance of Bayes' rule (because the semantics doesn't provide a likelihood, but only a weight)}
 $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
@@
 The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
-This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
-Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.
+In our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.
+This is a different approach than in conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013], but provides a potential bridge, as explored later.
 

### 2017-10-02 paper/comgen-paper.Rmd
more comments and edits in model section

@@
 \ref{eq:L0}).
+\ndg{prabably should say something more about modeling endorsements as a speaker model...}
 
@@
 
-The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **referent feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
+\ndg{i wonder if we shoud start with the speaker / endorsement idea? introducing the listener and semantics might be more natural then.}
+
+The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
 Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the feature-probability of the property in the category. 
@@
 ]
-We specify a single alternative utterance corresponding to *not saying the generalization*:
-With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. 
-Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
+We specify a single alternative utterance corresponding to *staying silent*^[
 This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
@@
 ]:
-
+With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. \ndg{why?}
+Because staying silent carries no information content to the listener, it can be modeled as a uniform utterance:
 \begin{equation*}
-\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
-1 &\text{for all h}
-\end{cases}
+\denote{u_{silence}(h, \theta)} \propto \text{True}
 \end{equation*}
-
-The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
-The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
-To our knowledge there is no unifying computational account of linguistic genericity and as such, the primary theoretical interest of this paper is to outline such an account, rather than discuss possible variations within it.
+\ndg{i simplified the eq... ok?}
+
+The pair of speaker-listener models presented above correspond to the simplest communicative models with an underspecified threshold-meaning for a generalization. 
+Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
+The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
 However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).

### 2017-10-14 paper/appendix-cueValidity.Rmd
update packrat and relevant code chunks; refactor intro

@@
   group_by(item, type) %>%
-  multi_boot_standard(column = "response")
+  multi_boot_standard(col = "response")
 
@@
 cv.bothquestions.bars <- d.cv.bothtasks %>%
+  ungroup() %>%
   mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
@@
   group_by(category, property) %>%
-  multi_boot_standard(column = 'response')
+  multi_boot_standard(col = 'response')
 

### 2017-10-14 paper/comgen-paper.Rmd
update packrat and relevant code chunks; refactor intro

@@
 
-Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be necessary to thrive in our open-ended world.
+Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
 Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is crucial that language allow us to communicate such *generalizations* to each other.
+It thus is important that language allow us to communicate such *generalizations* to each other.
 By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
@@
 
-Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions about human understanding.
-The major challenge in formalizing generalizations in language is determining what makes such statements true or false.
+Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions to match human intuitions. 
+The major challenge in formalizing the language of generalizations is in determining what makes such statements true or false.
 When we hear "Dogs bark", it sounds like a universal statement, like *All* dogs bark.
@@
 
-These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of a category having a property) is only incidentally related to generic meaning.
-*Conceptual accounts* of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
-With this perspective, @Leslie2007 proposes that generics express a cognitively primitive, default generalization. 
-The *generics as default* view argues that certain principles explain how generics become true or false.
-"Mosquitos carry malaria" conveys a dangerous or striking property, which is useful to know if you are to survive in a hostile world.
-This theory predicts that generics which convey striking properties would be true even if the property was relatively uncommon (e.g., "Sharks attack swimmers"), which has been borne out emprically [@Cimpian2010; @Prasada2013].
-"Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].
-
-Yet, generics are not limited to conveying rich, conceptual relations. 
-Arbitrary relationships can also be expressed with generics (e.g., "Barns are red"; "Ravens are bigger than toasters") which seem only to be true only because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
-The *generics as default* view must then be supplemented with the principle that, in certain situations, statistics influence generic endorsement.
-The diversity of generic statements highlighted by the conceptual accounts is interesting, but insofar as generics are a single, unified phenomenon, there should be a general, unified principle that explains what makes the statements true or false.
-In addition, a unified theory should be formalized to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to predict human behavior; this, in turn, makes the theory more testable.
-\ndg{we go on to talk about informal models next... maybe this defense of formal models needs to be later? adjust flow somehow.}
-\mht{moved it here}
+These observations have led to proposals that the prevalence or probability of a member of a category having the property (e.g., $P(x \text{ barks} \mid x \text{ is a dog})$) is only tangentially related to generic meaning.
+*Conceptual accounts* of generics emphasize the structure of "generic knowledge" [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+From this perspective, the statement "Bishops move diagonally" is true not because bishops tend to move diagonally, but rather because those are the rules of chess.
+With this in mind, @Leslie2007 proposes *cognitively primitive* principles that dictate how generics become true or false.
+*Characteristic* features are one such principle; "Robins lay eggs" is thus true because it is the mode of reproduction, and reproduction is a characteristic dimension for animal kinds.
+*Horrifying* or *striking* information also leads to true generics, which is why "Mosquitos carry malaria" is true despite its low prevalence.
+
+Yet others have observed that generics are not limited to conveying rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
+<!-- Arbitrary relationships are also expressed with generics:  -->
+"Barns are red" is true because that is how barn-owners tend to paint their barns; if barn-owners decided to switch to blue, the things they would be painting would still be considered barns.
+"Ravens are bigger than toasters" because of the size of ravens and the size of toasters, not because of a special relationship between ravens and toasters.
+*Conceptual accounts* must then be supplemented with the proviso that, in certain situations, the statistics of the world do influence human intuitions about generics.
+
+Needless to say, generic statements are a diverse class, and the conceptual view highlights this diversity [e.g., @Prasada2013].
+But insofar as generics are a single class in language---indeed, insofar as they are a subclass of generalization in language---there should be a general, unified principle that explains what makes the statements true or false.
+The same logic should apply to all generalizations in language, including habitual and causal language.
+This is the goal of this paper.
+
 <!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
@@
 <!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-
-We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances.
-We do so by first considering a much more well-studied form of generalization: generalization from observations. 
-The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization [@Shepard1987; @Tenenbaum2001].
+<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
+-->
+
+In this paper, we take a critical look at the notion that prevalence---or its more general formulation, probability---cannot serve as the core of a semantic theory of generalization in language (including generics).
+We strive for a probability-based semantics for its generality: Probability is the universal currency of belief and serves as a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
 Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the *object* of communication for generalizations. 
-We thus explore how these probabilities can be communicated in natural language. 
-We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016].
-Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals. 
-Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
-The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head.
-Specifically, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalization concerns subjective probability in a *simple but underspecified* way.
-We combine this notion of generic semantics with RSA, and derive predictions for the endorsements of such statements by considering whether or not a speaker would bother to say the generalization to a listener.
-We show that this decision depends in systematic ways on the prior knowledge of the listener.
-
-Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+We formalize such a semantics in a general probabilistic framework for modeling cognition, and thus incorporate generalizations in language into models designed to formalize concepts and intuitive theories [@Goodmanconcepts].
+Formalizing such a theory is scientifically useful as well to make explicit the assumptions of the psycho--linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
+
+We take the primary desideratum for a theory of the language of generalization to be adult human intuitions into the truth or felicity of statements conveying generalization, which we measure empirically.
+To test the theory that probability can serve as the core semantic theory, we build a computational model of endorsement around this core semantic theory and compare our model to human judgments.
+Though concepts such as *striking properties* are not explicitly formalized in our model, there is a natural avenue for future integration as our theory is couched in a general cognitive modeling framework.
+
+Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecified* function of probability.
+We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement.
+We show that the decision to endorse depends in systematic ways on the prior knowledge of the agent who hears the generalizations, the listener.
+We test this theory in three distinct case studies, by both measuring and manipulating listener prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+Our three case studies correspond to generalizations about categories, events, and causes.
+We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
+
+<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
+-->
+
+<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
+<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
+<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
+
+<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
+<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
+<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
+-->
+<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
+
 <!-- We relate known measurements on factors regarding generic language to each other via our model. -->
 <!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-Our three case studies correspond to generalizations about categories, events, and causes.
-We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
-
-\ndg{the next two paragraphs feel partly redundant with what just came...}
+
 The paper is organized as follows. 
 In Section 1, we describe the Bayesian framework for generalization from observations, serving as the foundation for our semantic theory.
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into the RSA framework for pragmatic language understanding.
-
-To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
-Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
-In Section 3, we describe experiments that measure both quantities and relate them via our model to the endorsements of generalizations about categories (*generic language*). 
-In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events (*habitual language*).
-In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes (*causal language*).
+In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a computational model of endorsement.
+<!-- To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes. -->
+<!-- Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
+-->
+In Section 3, we describe experiments that measure both listener prior knowledge and the prevalence of the properties in question, and relate them via our model to the endorsements of generalizations about categories (*generic language*).
+In Section 4, we describe experiments that measure listener prior knowledge and manipulate the frequency of various events to explain endorsements of generalizations about events (*habitual language*).
+Finally, in Section 5, we describe experiments that manipulate both the listener's prior knowledge and the prevalence of the properties in question in endorsing generalizations about causes (*causal language*).
 
 Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-In the final section of the paper, we discuss how our model paves a path to unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
-Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language in the way that people learn from language.
+In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
+We also show how our endorsement model is a special case of a speaker model in a rational framework of communication. 
+This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
 
@@
   group_by(sentence) %>%
-  multi_boot_standard(column = "response") %>%
+  multi_boot_standard(col = "response") %>%
   ungroup() %>%
@@
   group_by(Category, Property, item) %>%
-  multi_boot_standard(column = "prevalence")
+  multi_boot_standard(col = "prevalence")
 
@@
 resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:1000){
+for (i in 1:10){
 
@@
              prev_ci_upper = ci_upper) %>%
+      ungroup() %>%
       mutate(sentence = gsub('[.]', '', sentence))
@@
   group_by(item) %>%
-  multi_boot_standard( column = 'value' )
+  multi_boot_standard( col = 'value' )
 ```
@@
   group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(column = "logAnnualPredictiveRate")
+  multi_boot_standard(col = "logAnnualPredictiveRate")
 

### 2017-10-14 paper/comgen-paper.Rmd
refactor of model section up to simulations; need to figure out what to do with gen from obs section

@@
 
-Generalizations in language are often studied in *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+Generalizations in language are often studied via *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
 Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which 2-and-a-half-year-olds already appreciate [@Cimpian2008].
+In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which even 2-and-a-half-year-olds appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 -->
-Generics are just one case of generalization in language, however;  events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as can causality (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generics are just one case of generalization in language, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 
-These observations have led to proposals that the prevalence or probability of a member of a category having the property (e.g., $P(x \text{ barks} \mid x \text{ is a dog})$) is only tangentially related to generic meaning.
+These observations have led to proposals that the prevalence or probability of a member of the category having the property (e.g., $P(x \text{ barks} \mid x \text{ is a dog})$) is only tangentially related to generic meaning.
 *Conceptual accounts* of generics emphasize the structure of "generic knowledge" [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
@@
 
-Needless to say, generic statements are a diverse class, and the conceptual view highlights this diversity [e.g., @Prasada2013].
+Hence, generic statements are a diverse class, and the conceptual view highlights this diversity [e.g., @Prasada2013].
 But insofar as generics are a single class in language---indeed, insofar as they are a subclass of generalization in language---there should be a general, unified principle that explains what makes the statements true or false.
@@
 We formalize such a semantics in a general probabilistic framework for modeling cognition, and thus incorporate generalizations in language into models designed to formalize concepts and intuitive theories [@Goodmanconcepts].
-Formalizing such a theory is scientifically useful as well to make explicit the assumptions of the psycho--linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
+Formalizing such a theory is scientifically useful as well to make explicit the assumptions of the psycho--linguistic hypothesis meant to match human intuitions, which in turn, elucidates the conditions under which the theory may be meaningfully tested.
 
@@
 
-Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecified* function of probability.
+Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
+In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000].
 We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement.
-We show that the decision to endorse depends in systematic ways on the prior knowledge of the agent who hears the generalizations, the listener.
-We test this theory in three distinct case studies, by both measuring and manipulating listener prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
-Our three case studies correspond to generalizations about categories, events, and causes.
-We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
+We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...}
+We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
 
@@
 
-# Generalization from Observations
+# Computational Framework
 
 Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
+People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
-The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
+The specific exemplars can be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
 The properties can vary greatly (e.g., having fur, causing jitters, typing). 
-Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **feature-probability**: 
+Yet the prediction for the new exemplar can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **feature-probability**: 
 $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
@@
 \ndg{smooth out this par.}
+
+## Generalization from observation
+
 The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
 From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
-The Bayesian probability calculus provides a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011]: Observing some number of instances of $k$ with $f$ will update what an observer believes *a priori* (formally: a prior belief distribution) in order to make predictions about unobserved instances, via a posterior belief distribution.
-As a concrete example, consider the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$): $h = P(x \in \{\text{barks}\} \mid x \in \{\text{is a dog}\})$.
-If an agent were to encounter some number of individual dogs and note how many of them bark ($d$), using Bayes' rule, she could form a posterior belief distribution about the probability that the next dog she encounters will bark (in other words, a belief about the barking capacity of dogs).
-
+Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
+This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances.
+
+As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$).
+$h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
+Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
+That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$.
+The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
+
+The observer goes around the world, encountering dogs and taking note of how many bark.
+This could be represented as a number of positive examples $d$ out of a number of total examples $n$. 
+With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
+That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
+This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$. 
+Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule:
 $$
-P(h \mid d) = \frac{P(d \mid h) \cdot P(h)}{\int_{h'}P(d \mid h') \cdot P(h')}
+P(h \mid d) \propto P(d \mid h) \cdot P(h)
 $$
-
-\ndg{what is this par doing for us? delete?}
-Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
-For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
-This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
-Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009].
-
-Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
+$P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking.
+This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
+<!-- \ndg{what is this par doing for us? delete?} -->
+<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
+<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
+-->
+<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
+-->
+<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
+Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
 Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
+How do we acquire these generalizations?
 For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
 
-\ndg{i'm not sure that generalization from examples should have it's own section, as opposed to be a subsection or couple pars of the next...}
-
-# Generalization from Language
-
-If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys a generalization to be related to probability.
-If we wish to connect to the semantic tools of *truth values* \ndg{cite montague?}, then we will need to connect the scalar quantity of probability to a boolean truth value.
-Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: an utterance is true if the underlying quantity is above a threshold.
-For generalizations, the threshold would apply to the *feature-probability* $h$:^[
+## Generalization from language
+
+If generalization from observations can be described using probability, then it seems natural to consider probability to be central to the semantic content of an utterance that conveys a generalization.
+To connect to the semantic tools of *truth values* [@Montague1973], we will need to relate the scalar quantity of probability to a Boolean truth value.
+Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: An utterance is true if the underlying quantity is above a threshold.
+For generalizations, then, the threshold would apply to the *feature-probability* $h$:^[
 We emphasize that our account is based on an agent's subjective probability $h$.
@@
 ]
-
-\ndg{why are there any deltas yet? so far we only want a truth functional semantics, so something like $\denote{u_{gen}} = h>\theta$. then we use the delta in eq:L0.}
+$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
+
+### Resolving underspecification
+
+What threshold $\theta$ should be used for the generalization?
+We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
+That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
 
 \begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \label{eq:delta} \\ 
-&\propto  &
-\begin{cases}
+Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
+\end{eqnarray}
+
+Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
+We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
+The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
+
+\begin{eqnarray}
+\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
 1 & \text{if } h > \theta \\
 0 & \text{otherwise}
-\end{cases}
+\end{cases}\label{eq:delta}
 \end{eqnarray}
 
-Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for feature-probabilities $h$ greater than threshold $\theta$, and $0$ otherwise.
-Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
-
-What threshold $\theta$ should be used for the generic generalization?
-In Bayesian statistics, when there is a latent parameter that little is known about, one puts a prior distribution over the parameter and infers the parameter's likely value given any data.
-In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
-Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.
-
-Given the semantic function defined in Eq.
-\ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over feature-probabilities $P(h)$:
-
-\begin{eqnarray}
-L(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$.
-\ndg{i don't like describing L0 as a bayesian agent, because this is not an instance of Bayes' rule (because the semantics doesn't provide a likelihood, but only a weight)}
-$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
-$P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$.
-The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
-In our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.
-This is a different approach than in conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013], but provides a potential bridge, as explored later.
-
-<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
-influence the meaning of a generic statement via their influence on subjective probability.
--->
-<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts].
--->
-
-<!-- \begin{eqnarray} -->
-<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
-<!-- \end{eqnarray} -->
-
-In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Robins lay eggs" is good; "Robins are female" is not) based on some known or believed feature-probability $h$ in a referent category (e.g., only female robins lay eggs).
-Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq.
-\ref{eq:L0}).
-\ndg{prabably should say something more about modeling endorsements as a speaker model...}
+Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
+
+### Endorsement model
+
+The above model determines how $\theta$ should be resolved in context.
+Now, how do we decide when a statement conveying a generalization is true or not?
+To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
+The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
 
 \begin{equation} 
-S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta )}
+E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
 \label{eq:S1}
@@
 
-The speaker $S$ doesn't know the threshold $\theta$; rather, he integrates over the likely values that the listener will believe. 
-Additionaly, following RSA, the speaker model is assumed to be an approximately rational Bayesian agent with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-
-\ndg{i wonder if we shoud start with the speaker / endorsement idea? introducing the listener and semantics might be more natural then.}
-
-The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
-Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
+Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
+Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
+
+The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
+Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
+In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
 $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
 ]
-We specify a single alternative utterance corresponding to *staying silent*^[
-This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
+The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
+This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
 All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]:
-With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. \ndg{why?}
-Because staying silent carries no information content to the listener, it can be modeled as a uniform utterance:
-\begin{equation*}
-\denote{u_{silence}(h, \theta)} \propto \text{True}
-\end{equation*}
-\ndg{i simplified the eq... ok?}
-
-The pair of speaker-listener models presented above correspond to the simplest communicative models with an underspecified threshold-meaning for a generalization. 
+]
+
+\begin{equation} 
+U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
+\end{equation}
+
+Thus, Eq.
+\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
+It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
+Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
+
+The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
+
 Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
@@
 
-## Model simulations
+<!-- In Bayesian statistics, when there is uncertainty about latent parameter, one specifies a prior distribution over the parameter and reasons backward about the parameter's likely value given any data.
+-->
+<!-- In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
+-->
+<!-- Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context *a priori*: $P(\theta) = \text{Uniform}(0, 1)$.
+-->
+
+<!-- \ndg{i wonder if we shoud start with the speaker / endorsement idea? introducing the listener and semantics might be more natural then.} -->
+
+<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
+influence the meaning of a generic statement via their influence on subjective probability.
+-->
+<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts].
+-->
+
+<!-- \begin{eqnarray} -->
+<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
+<!-- \end{eqnarray} -->
+
+### The feature-probability prior and model simulations
+
+<!-- $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance. -->
+<!-- $P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$. -->
+<!-- The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
+-->
+<!-- In our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$. -->
+<!-- This is a different approach than in conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013], but provides a potential bridge, as explored later. -->
 

### 2017-10-18 paper/comgen-paper.Rmd
stab at streamlining gen from obs

@@
 ---
-title             : "Communicating generalizations"
-shorttitle        : "Communicating generalizations"
+title             : "The language of generalization"
+shorttitle        : "The language of generalization"
 
@@
 
+<!-- 
+possible titles:
+- Communicating generalizations
+- The language of generalization
+- The language of generalization: Probability, vagueness, and interaction
+-->
+
 # Introduction
@@
 
-Hence, generic statements are a diverse class, and the conceptual view highlights this diversity [e.g., @Prasada2013].
+Generic statements have diverse theoretical underpinnings, and the conceptual view highlights this diversity [e.g., @Prasada2013].
 But insofar as generics are a single class in language---indeed, insofar as they are a subclass of generalization in language---there should be a general, unified principle that explains what makes the statements true or false.
@@
 We strive for a probability-based semantics for its generality: Probability is the universal currency of belief and serves as a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the *object* of communication for generalizations. 
-We formalize such a semantics in a general probabilistic framework for modeling cognition, and thus incorporate generalizations in language into models designed to formalize concepts and intuitive theories [@Goodmanconcepts].
-Formalizing such a theory is scientifically useful as well to make explicit the assumptions of the psycho--linguistic hypothesis meant to match human intuitions, which in turn, elucidates the conditions under which the theory may be meaningfully tested.
+Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the object of communication for generalizations. 
+We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
+Formalizing such a theory is scientifically useful as well to make explicit the assumptions the theory, which in turn, elucidates the conditions under which the theory may be meaningfully tested.
 
 We take the primary desideratum for a theory of the language of generalization to be adult human intuitions into the truth or felicity of statements conveying generalization, which we measure empirically.
-To test the theory that probability can serve as the core semantic theory, we build a computational model of endorsement around this core semantic theory and compare our model to human judgments.
+To test the hypothesis that probability can serve as the core semantic theory, we build a computational model of endorsement around this semantic theory and compare our model to human judgments.
 Though concepts such as *striking properties* are not explicitly formalized in our model, there is a natural avenue for future integration as our theory is couched in a general cognitive modeling framework.
@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-The specific exemplars can be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties can vary greatly (e.g., having fur, causing jitters, typing). 
-Yet the prediction for the new exemplar can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **feature-probability**: 
-$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
-We denote feature-probability as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency or prevalence.
-]
-
-<!-- To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category. -->
-<!-- This is faciliated through the use of labeling; the linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..." -->
-<!-- To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature. -->
-<!-- That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$". -->
-<!-- We call this latter kind of statement a *particular*. -->
-
-<!-- ```{r table-generalization, results="asis"} -->
-<!-- df.tab <- data.frame( -->
-<!--   Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"), -->
-<!--   #x = c("an instance of K in space", "an instance of K in time", "an instance of a "), -->
-<!--   "Generalization over" = c("Category", "Event", "Cause"), -->
-<!--   "Linguistic construct" = c("Generic", "Habitual", "Causal"), -->
-<!--   x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"), -->
-<!--   k = c("DOGS", "JOHN", "DRINKING MOONSHINE"), -->
-<!--   f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind") -->
-<!-- ) %>% xtable(., -->
-<!--          caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."), -->
-<!--         label = c("tab:genpart")) -->
-
-<!-- # apa_table(df.tab,  -->
-<!-- #           caption = "Decomposition of generalizations into concrete particulars and corresponding properties.",  -->
-<!-- #           escape = TRUE, small = TRUE -->
-<!-- # ) -->
-
-<!-- print(df.tab, type = "latex",  -->
-<!--       tabular.environment = "tabularx", width = "\\textwidth", -->
-<!--       scalebox='0.75', -->
-<!--       include.rownames = FALSE, comment = F) -->
-<!-- ``` -->
-
-<!-- Particular statements can be made about objects, events, and causes. For example: -->
-
-<!-- 1. My dog is friendly. (object) -->
-<!-- 2. John ran this afternoon. (event) -->
-<!-- 3. My grandfather drank moonshine and it made him go blind. (cause) -->
-
-<!-- Particular statements refer to individuals of a category of which generalizatons can be made. For example, -->
-
-<!-- 4. Dogs are friendly -->
-<!-- 5. John runs -->
-<!-- 6. Drinking moonshines makes you go blind -->
-
-<!-- That is, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tab:genpart}).
--->
-
-<!-- Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
--->
-<!-- For properties among instances of a category (e.g., being friendly among dogs), we can describe this inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[ -->
-<!-- With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$. -->
-<!-- ]. -->
-<!-- <!-- In the study of categories and properties, $x$ is an object. --> 
-<!-- For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability mass: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$ -->
-<!-- <!-- In this case, $x$ is a instance of an agent. --> 
-<!-- Causal learning can be described with the same formalism as for categories, a probability referring to the likelihood of an effect $e$ given a cause $c$, also known as causal power: $h = P(x \in e \mid x \in c)$.
--->
-<!-- Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency of some instance in a category. -->
-<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->
-
-<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
-
-\ndg{smooth out this par.}
-
-## Generalization from observation
-
-The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
-From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007].
-Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
-This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances.
-
-As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$).
-$h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
-That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$.
-The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
-
-The observer goes around the world, encountering dogs and taking note of how many bark.
-This could be represented as a number of positive examples $d$ out of a number of total examples $n$. 
-With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
-That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
-This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$. 
-Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule:
+This prediction can be described by a conditional probability: $h = P(x \in F \mid x \in K)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
+The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
+The properties can also vary widely (e.g., having fur, causing jitters, typing). 
+Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
+
+How does one come to learn $h$, the uncertainty that underlies an inductive inference about a category having a property?
+One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
+But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
+For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
+If an addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
+This kind of knowledge can be represented formally in a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule:
+
 $$
@@
 $$
-$P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking.
-This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
+
+Yet, generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
+Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
+How do we acquire these generalizations?
+For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
+
+<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
+-->
+<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
+<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
+-->
+<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
+
+<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
+<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
+Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
+-->
+<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
+<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
+-->
+
+<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
+<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
+<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
+-->
+<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
+-->
+<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
+<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
+
+<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
+<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
+-->
 <!-- \ndg{what is this par doing for us? delete?} -->
@@
 <!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
-Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
-How do we acquire these generalizations?
-For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
+<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
+<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
+-->
+<!-- How do we acquire these generalizations? -->
+<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
+-->
 
@@
 
-All models were implemented in the probabilisitic programming language WebPPL [@dippl].
+The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
+We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
+We implemented the models in the probabilisitic programming language WebPPL [@dippl].
 The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as the other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability that utterance vs.
-silence accurate conveys to a naive listener a feature-probability $h$ in a referent-category (e.g., the \% of robins that lay eggs).
-This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
+That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+
+<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
+<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
 \ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
@@
 \ref{eq:S1}).
-Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
-For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+-->
+<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
+-->
+<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+-->
 
@@
 priorNames <- c(
-  "uniform", #"uniformRare", 
+  "doesntEatPeople", #"uniformRare", 
   "isFemale", 
@@
   "barks",
-  "carriesMalaria"#,
+  "carriesMalaria",
+  "hasSpots"
  # "areSick"
@@
 priorShapes <- list(
-  uniform =  list(params = data.frame(a = 1, b = 1), mix = 1), 
-  #uniformRare =  list(params = data.frame(a = 1, b = 1), mix = 0.4), 
   isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
   laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  #eatsFood =  list(params = data.frame(a = 50, b = 1), mix = 1), 
+  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
   barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  #areSick =  list(params = data.frame(a = 1, b = 5), mix = 1), 
+  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
   carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
@@
 for (p in priorNames){
-  for (u in c("generic", "some")){
+  for (u in c("generic")){
 
@@
 
-```{r simulations, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
+```{r simluationEndorsementModel, eval = T, cache = T}
+s1.model <- '
+var probability = function(Dist, x) {
+    return Math.exp(Dist.score(x));
+}
+var targetUtterance = "generic";
+
+var utterancePrior = Infer({model: function(){
+  return uniformDraw([targetUtterance,"silence"])
+}});
+
+var thetaPrior = Infer({model: function(){
+ return uniformDraw([
+   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
+ ])}
+});
+
+var bins = [
+  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
+];
+
+var meaning = function(utt,state, theta) {
+  return utt=="generic"? state > theta :
+         utt=="generic is false"? state<=theta :
+         utt=="silence"? true :
+         utt=="some"? state>0.01:
+         utt=="most"? state> 0.5:
+         utt=="all"? state >= 0.99:
+         true
+}
+
+var mixture = data.mix[0];
+var priorParams = data.params[0];
+
+var statePrior = Infer({model: function(){
+  var component = flip(mixture);
+  return component ?
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta(priorParams), b) + Number.EPSILON
+      }, bins )
+    }) :
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
+      }, bins )
+    })
+}});
+
+var continuousListener0 = function(utterance) {
+  Infer({model: function(){
+   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+    factor(
+    (utterance == "generic") ? 
+      Math.log(state) : 
+    (state > 0.017) ? 0 : -Infinity
+    )
+    return {
+      state_Posterior: state, 
+      state_Prior: state_prior
+  }
+ }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+
+var listener0 = cache(function(utterance) {
+  Infer({model: function(){
+    var state = sample(statePrior)
+    var state_prior = sample(statePrior)
+    var theta = utterance == "generic" ? sample(thetaPrior) : -99
+    condition(meaning(utterance, state, theta))
+    return {
+      state_Posterior: state, 
+      state_Prior: state_prior
+  }
+ }})}, 10000)
+var alpha = 2
+
+var endorser = function(featureProb){
+  Infer({model: function(){
+    var endorsement = sample(utterancePrior)
+    var L0 = marginalize(listener0(endorsement), "state_Posterior")
+    factor(alpha * L0.score(featureProb))
+    return endorsement
+  }})
+}
+
+probability(endorser(data.featureProb[0]), "generic")
+'
+
+exampleGenerics <- c(
+  "sharksDontEatPeople",
+  "robinsAreFemale", 
+  "robinsLayEggs", 
+  "kangaroosHaveSpots",
+  "dogsBark",
+  "mosquitosCarryMalaria"
+  )
+exampleParameters <- list(
+  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
+  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
+  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
+  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
+  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
+  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
+)
+
+s1.simulations <- data.frame()
+for (p in exampleGenerics){
+
+    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
+    s1.simulations <- bind_rows(s1.simulations,
+                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
+
+}
+
+```
+
+```{r}
+s1.simulations.relabeled <- s1.simulations %>%
+  mutate(example = factor(example, 
+                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
+                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
+
+s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
+  #geom_jitter(width = 0.1, shape = 21, size = 5)+
+  #ylab("Human endorsement probability")+
+  #xlab("Frequency of target")+
+  geom_label_repel(data = s1.simulations.relabeled, 
+                   aes( label = example, fill = example),
+                       color = 'white',
+    box.padding = unit(0.0, "lines"),
+    #point.padding = unit(1e-06, "lines"),
+    segment.color = 'grey37')+
+  scale_fill_solarized()+
+  scale_x_continuous(limits = c(0, 1), 
+                     breaks = c(0, 0.5, 1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), 
+                     breaks = c(0, 1),
+                     labels = c("False", "True"))+
+  coord_fixed(ratio = 1)+
+  guides(fill = F)+
+  ylab("Endorsement model prediction")+
+  xlab("Hypothesized feature-probability")
+
+```
+
+```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
 The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 9, fig.height=5}
-all.simulations %>%
+Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
+all.simulations.refactored <- all.simulations %>%
   mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
+  filter(Distribution != "Some", Distribution != "Most") %>%
   mutate(Distribution = factor(Distribution, levels = 
-                             c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                                labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")),
-         PriorShape = factor(PriorShape, levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             labels = c("uniform", "bark","lay eggs","carry malaria","are female")
+                                c( "Prior_generic", "Posterior_Generalization_generic"),
+                                labels = c( "Prior/Silence", "Generalization")
+                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
+                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
+                             ),
+         PriorShape = factor(PriorShape, 
+                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
+                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
+                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
+                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                   #"eatsFood","areSick", "uniformRare", 
@@
                                   )
-         ) %>%
-  ggplot(., aes(x = value, #y = prob, 
+         )
+
+l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                 #lty = Distribution, 
-                color = Distribution, fill = Distribution))+
-    geom_density(#stat= 'identity', 
-                aes(y = ..scaled..),
-                 size = 0.6, alpha = 0.7, adjust = 1.5)+
+                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
+    geom_density(aes(y = ..scaled..),
+                 size = 0.6,  adjust = 1.5)+
     #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
     theme_few() +
-    #scale_color_solarized()+
-    #scale_fill_solarized()+
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    scale_alpha_manual(values = c(0.7, 0.3))+
+    scale_linetype_manual(values = c(1, 3))+
     #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
     #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
     #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
     scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
@@
     xlab("Feature-probability h") +
-    ylab("Scaled probability density") +
-  facet_grid(PriorShape~Distribution, scales = 'free')+
+    ylab("Scaled prior probability density") +
+  facet_wrap(~PriorShape, scales = 'free')+
   guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0))
+  theme(strip.text.y = element_text(angle = 0),
+          legend.position = c(0.92, 0.35))
+```
+
+```{r simulations, fig.cap = "Model behavior.
+Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
+The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
+Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
+grid.arrange(l0.simulations.distributions, 
+             s1.simulations.scatter, ncol = 3,
+             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
+
 ```
@@
 
+```
+
+```{r generic-endorsement-priors-unbounded, eval = F}
+# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
+
+d.gen.endorse.priors <- read.csv(paste(project.path, 
+                                       "data/generics/endorsement/",
+                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
+
+unboundedModel <- '
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var preprocessedResponses = map(function(d){
+  return avoidEndPoints(d / 100)
+}, data)
+
+var shapeParams = function(params){
+  return {
+    a: params.g * params.d,
+    b: (1 - params.g) * params.d
+  }
+}
+
+var model = function(){
+
+  // var numComponents = (1 + poisson(1));
+  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
+  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
+    return uniformDrift({a: 0, b:1, width: 0.2})
+  }))).reverse()
+
+  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
+  var componentParams = map(function(i){
+    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
+    var betaParams = shapeParams({g, d})
+    return betaParams
+  }, _.range(numComponents))
+
+  mapData({data: preprocessedResponses}, function(d){
+
+    var scr = log(sum(map(function(cParams){
+      cParams[1] * exp(Beta(cParams[0]).score(d))
+    }, _.zip(componentParams, mixtureWeights))))
+//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
+    factor(scr)
+  })
+
+  var componentPredictives = map(function(cParams){
+      return beta(cParams)
+  }, componentParams)
+
+  return _.fromPairs(
+    _.zip(
+        map(function(i){ i + "_weight" }, _.range(5)), 
+        mixtureWeights
+      ).concat(
+      _.zip(
+        map(function(i){ i + "_predictive" }, _.range(5)), 
+        componentPredictives
+      )
+    )
+  )//sort(T.toScalars(mixtureWeights))
+};
+'
+
+example.generics.prior.properties <- c(
+  "dont eat people", "have beautiful feathers",
+  "have wings", "are red",
+  "carry malaria", "lay eggs", 
+  "are female", "have spots"
+  )
+priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
+  n_samples <- 10000
+lg = 0
+  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 1,
+                                 cores = 1,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+```
+```{r eval = F}
+m.gen.endorse.priors.unbounded %>%
+      separate(Parameter, into = c("c", "var")) %>% 
+      ggplot(., aes( x=  value, fill = c))+
+ geom_histogram(position = position_dodge(), binwidth = 0.05)+
+ facet_wrap(~var)+
+  scale_fill_solarized()
 ```

### 2017-10-19 paper/comgen-paper.Rmd
tweaks to gen from obs

@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in F \mid x \in K)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
+This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties can also vary widely (e.g., having fur, causing jitters, typing). 
+The properties correspondingly also vary widely (e.g., having fur, causing jitters, typing). 
 Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
 
-How does one come to learn $h$, the uncertainty that underlies an inductive inference about a category having a property?
+How does one come to learn $h$, the uncertainty that underlies an inductive inference about a member of a category having a property?
 One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
@@
 For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If an addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally in a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule:
-
-$$
-P(h \mid d) \propto P(d \mid h) \cdot P(h)
-$$
-
-Yet, generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
+If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
+This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
+Here, $P(d \mid h)$ is the observer's generative model of the observed data. 
+It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.
+
+Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
 Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
@@
 
-If generalization from observations can be described using probability, then it seems natural to consider probability to be central to the semantic content of an utterance that conveys a generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we will need to relate the scalar quantity of probability to a Boolean truth value.
+If generalization from observations can be described as a predictive probability, then it seems natural to consider that same metric to be central to the semantic content of an utterance that conveys a generalization.
+To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
 Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: An utterance is true if the underlying quantity is above a threshold.
@@
 The literature on generic language has often examined *prevalence*, or the proportion of members of a category with the property, as the primary quantitative metric that could relate to generic meaning (in addition to *cue validity*, described below).
-A Bayesian agent, however, would only use prevalence as a way to update her existing state of knowldege to form a subjective probability for future use.
+A Bayesian agent, however, would only use prevalence as a way to update her prior knowldege $P(h)$ to form a posterior probability for future use.
 Thus, we consider the semantic content of a generalization to be related to probability, not necessarily prevalence.

### 2017-10-24 paper/comgen-paper.Rmd
restructure and streamline generics case study

@@
 Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
-It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., "Most dogs bark") and has received the most attention from philosophers, linguists, and psychologists.
-
-Any theory of generic language must explain its puzzling flexibility of usage with respect to feature-probability.
-That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not.
-As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
-We validate these simulations empirically by measuring the prior belief distribution over the feature-probabilities $P(h)$ used in Eq.
-\ref{eq:L0} and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq.
+It has been the premier case study of generalization in language because of its similarity to quantified statements (e.g., "Most dogs bark").
+Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
+
+We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
+"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
+"Lions lay eggs.").
+In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
+1a).
+
+We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
+Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
+\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
+To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
+
+<!-- That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not. -->
+<!-- As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
+-->
+<!-- We validate these simulations empirically by measuring t and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq.
 \ref{eq:S1} (Expt.
 1a).
-
-<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
-We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
-"Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low, medium, and high feature-probability properties.
-
-To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a).
-We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
-In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
+-->
+
+<!-- <!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  --> -->
+<!-- We test our model on -->
+
+<!-- To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a). -->
+<!-- We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013]. -->
+<!-- In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
 *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the feature-probability prior.
-If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
-A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
-As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.
-
-After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
+-->
+<!-- If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
+-->
+<!-- A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007]. -->
+<!-- As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one. -->
+
+<!-- After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
 1b).
-In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model.
-To preview our results, we find that only our formulation of an uncertain threshold RSA model is able to account for the flexibility in generic endorsement.
-
-<!-- At first glance, generics feel like universally-quantified statements as in *All* birds fly.  -->
-<!-- Unlike universals, however, generics are resilient to counter-examples (e.g., *Birds fly* seems true even in the face of flightless birds like kiwis or penguins). -->
-<!-- *Most* birds fly seems more reasonable, and yet most mosquitos *do not* carry malaria while *Mosquitos carry malaria* seems like a true statement. -->
-<!-- Finally, the probability of a bird being female is much higher than the probability of a mosquito carrying malaria, but *Birds are female* seems weird to say. -->
-<!-- *Birds lay eggs*, however, is fine, even though the rate is the same as *are female* (only females lay eggs). -->
-
-<!-- Empirical work done on category generalizations has elucidated another puzzling phenomenon. -->
-<!-- Generic statements often imply the property is widespread in the category [e.g., *Swans have hollow bones* implies something much stronger than *Some swans have hollow bones*; @Gelman2002; @Cimpian2010; @Brandone2014].
--->
-<!-- This characteristically strong interpretation interacts with the indeterminacy in truth conditions, resulting in an *asymmetry* between endorsement and interpretation. -->
-<!-- For a variety of features, both children and adults infer that a property is *more* prevalent when told the generalizations than when judging it true or not [@Cimpian2010; @Brandone2014]. -->
-
-<!-- Interpreting the generic as meaning "most" (i.e.
-\emph{Most swans are white}) captures many cases, but cannot explain why \emph{Robins lay eggs} and \emph{Mosquitos carry malaria} are so intuitively compelling: Only adult female robins lay eggs and a very tiny fraction of mosquitos actually carry malaria.
--->
-<!-- Indeed, it appears that any \emph{truth condition} stated in terms of how common the property is within the kind violates intuitions. -->
-<!-- Consider the birds: for a bird, being female practically implies you will lay eggs (the properties are present in the same proportion), yet we say things like \emph{Birds lay eggs} and we do not say things like \emph{Birds are female}.
--->
-
-<!-- One case study in the language of generalizations is about category generalizations. -->
-<!-- Category generalizations, called *generic statement*, has been studied extensively in cognitive and developmental psychology: *generic* statements, or generalizations about categories. -->
-
-<!-- These *strong implications* might underly stereotype formation in social categories [@Rhodes2012]. -->
-<!-- In addition to the flexibility in truth conditions, two phenomena have been noted.  -->
-<!-- The case of *Mosquitos carry malaria* suggests the utterance must in some way be analogous to the quantifier "some" (e.g., *Some mosquitos carry malaria*).  -->
-<!-- Generic language, however, is often interpreted as implying the property is widespread: *Swans have hollow bones* means something different than *Some swans have hollow bones* [@Gelman2002]. -->
-
-<!-- These three phenomena---flexible truth, strong interpretations, and evidence exaggeration---have confounded all formal models aimed to capture the meaning of generalizations in language. -->
-<!-- Informal theories have argued that the nature of concepts and their relations are inextricably tied to their linguistic expression [@Leslie2007; @Prasada2013]. -->
-<!-- Formal theories have limited themselves to a measurable quantitative degree (e.g., how prevalent a property is in a category), which, in isolation, is difficult to reconcile with the extreme flexibility of generic language.
--->
-<!-- Here, we present a theory formalizing the inuition that the core meaning of a linguistic generalization is simple, but underspecified, and that general principles of communication may be used to resolve the precise meaning in context.
--->
-<!-- This theory inherently relies upon measurable quantities (i.e., prevalence) but situates it within a Bayesian agent with potentially structured prior knowledge, providing a bridge to conceptual theories.
--->
-<!-- We find that this formalism (and not simpler ones) explains all three empirical puzzles. -->
-
-<!-- When interpretations are compared directly against truth conditions (i.e., how prevalent a property would need to be for the generic to be true),  -->
-
-<!-- Three empirical phenomena make generalizations in language difficult to formalize. -->
-<!-- The conditions under which a generalizations becomes "true" are variable: -->
-
-<!-- Existing work in both adults and children suggests that choosing to communicate a generalization can be used to exagerate evidence [@Cimpian2010; @Brandone2014]. -->
-
-<!-- In addition to having manifold interpretations, what makes linguistic generalizations true or false (i.e., their truth conditions) is also a mystery. -->
-<!-- The statement *Birds lay eggs* is true even though only about half of them do (namely, the females). -->
-<!-- Half of birds are also female, and yet *Birds are female* sounds like a strange thing to say. -->
-<!--  while *Canadians are right-handed* is also weird, even though the vast majority of them are.  -->
-
-## Experiment 1a: Measuring the feature-probability prior for categories
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
-Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
-Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
-].
-
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
-After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.
-
-### Method
-
-#### Participants
-
-We recruited 60 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-Three participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-Two participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-#### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt.
-1b (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
-
-A column then appeared to the right of the animal names with a property in the header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
-Eight property--columns appeared in the table, and this whole procedure was repeated two times.
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1a for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
-
-<!-- ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. -->
-
-### Bayesian analysis
-
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-In analyzing the feature-probability prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
-We formalize this hypothesis using a simple Bayesian mixture model. 
-We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while other kinds do not; cf., @Griffiths2005].
-The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the feature-probability prior data.
-
-For the structured hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
-The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
-We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
-Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
-The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
-]
-The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
-Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
-This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
-Similar results can be obtained by rounding 0 to 0.01. 
-Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
-]
-Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
-The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$.
-
-We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account model flexibility [@LW2014].
-We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\phi$):
-
-\begin{eqnarray}
-\phi & \sim & \text{Uniform}(0, 1) \\
-\gamma & \sim & \text{Uniform}(0, 1) \\
-\xi & \sim & \text{Uniform}(0, 100) \\
-\end{eqnarray}
-
-Each property (e.g., *lays eggs*, *carries malaria*) is modeled independently (i.e., each property's feature-probability prior has its own parameters).
-
-### Results
-
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
-The Bayes Factor indicates the extent to which the data support one model over another.
-The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
-Indeed, the data strongly suggests the feature-probability prior is structured.
-
-It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
-To see how well the structured model fits the feature-probability prior data, we use Bayesian inference to infer the *a posteriori* likely values of the parameters and then use the inferred parameters to generate new data.
-The generated data from the model's posterior is called the *posterior predictive distribution* and is an important step in model validation. 
-If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
-We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
-If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
-If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted feature-probability ratings.
-]
-
-To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
-Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
-There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
-One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
-load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
-           aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
-    xlab("Feature-probability") +
-    ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
-### Discussion
-
-The feature-probability prior distribution $P_f(h)$ encodes beliefs about the feature-probability (or, probabilities) of a feature $f$ across different kinds.
-These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
-
-<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->
-
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
-
-A natural proposal is that endorsements for generic language have to do with cue validity.
-This possibility has been investigated empirically in one of few examples of statistical modeling of generics, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
-However, cue validity has some empirical and theoretical issues.
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-<!-- If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
--->
-<!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
-<!-- ^[ -->
-<!-- As a simple demonstration, imagine we've just discovered a new kind of animal called a fep. -->
-<!-- It should be easy to estimate the prevalence of being female among feps (probably 50\%) even without any knowledge of feps.  -->
-<!-- However, if you learn in another context that a particular entity is green, it's impossible to estimate the cue validity of being green for feps -->
-<!-- that it's easy to estimate the prevalence of being female among  -->
-<!-- ] -->
-
-However, we should not throw away the possibility that distributional information about the property is relevant. 
-The mixture parameter $\phi$ in the feature-probability prior distribution can be seen as a generalization of the construct of cue validity. 
-Recall that $\phi$ is the weighting between the two generative components of the feature-probability prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the feature-probability prior, in that it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-
-Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is no longer well-defined (or, it is zero for all kinds). 
-This is for the same reason that for a probability distribution over the real numbers (a *continuous* probability distribution), the probability of any particular number is zero. 
-For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
-The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds} (and hence, $\phi$ is relatively low), but there are many kinds of birds and the feature is not particularly diagnostic for any given one of the subkinds (e.g., robins).
-$phi$ is still relatively small in this case because it encodes information about the distribution across kinds and not just one particular kind.
-This is an important point of departure in our work from previous work.
-
-<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
-<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
-<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
-<!-- However, cue validity requires knowledge of the referent-category $k$ -->
-
-<!-- For example, suppose there are 10 possible kinds and 3 of them belong the stable cause distribution and 7 belong to the transient cause distribution.  -->
-<!-- Say we observe the feature and want to know what the probability that the entity is of a particular kind that we know to be of the stable distribution.  -->
-<!-- If we know the prevalence given each distribution (i.e, $P(f \mid k_{stable})$ and $P(f \mid k_{transient})$). -->
-
-<!-- For simplicity, assume that each component corresponds to a single probability (i.e., a single prevalence value) as opposed to a distribution. -->
-<!-- Thus, $\mathcal{D_{stable}} = P(f \mid \mathcal{D_{stable}}) = p_{stable}$ -->
-
-<!-- $n_{stable} n_{transient}$ -->
-
-<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
-<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
-<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
-<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
-<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
-<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
--->
-<!-- Do a BDA to describe the data in a more compact form. -->
-<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq.
-\ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).
--->
-<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content.
--->
-<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
-<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
-<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the referent-category.
--->
-<!-- Some properties have priors that are unimodal with low variance (e.g.
-\textsc{is female}); these properties are present in every kind in almost exactly the same proportion.
-The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.
--->
-<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->
-
-## Experiment 1b: Endorsing generic statements
-
-In Expt. 1a, we measured and modeled the feature-probability prior distribution (e.g., the probability of laying eggs for different kinds of animals) for different features.
-This data also includes information about the referent-category feature-probability (e.g., how many robins lay eggs).
-Using the referent-category feature-probability as $h$ in our speaker model (Eq.
-\ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
-To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
+-->
+<!-- In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model.
+-->
+## Experiment 1a: Generic endorsements
+
+In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
+The goal of this study is to observe a range of endorsements for generic statements about animal categories.
 
@@
 
-We recruited 100 participants over MTurk. 
-4 participants were excluded for failing to pass a catch trial.
+We recruited 100 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
+Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
+4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
 5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
@@
 
-#### Data and model analysis
+#### Results
 
@@
 As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differencesin empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`])$;
+As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
 indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
@@
 In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
-Such a continuum of judgments is already evidence against any theory that only predicts whether a generic statement is true or false.
+Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
 
-To try to understand this endorsement data, we articulate a set of simple models that have been proposed in the literature and a reduced-form of our proposed RSA model. 
+In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
+
+## Experiment 1b: Feature-probability prior elicitation
+
+The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
+To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
+Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
+Now, do you think it lays eggs?
+Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
+That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
+The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
+Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
+].
+
+This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
+We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
+We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
+To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
+
+### Method
+
+#### Participants
+
+We recruited 60 participants over Amazon MTurk.  
+3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
+2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
+The experiment took about 10 minutes and participants were compensated \$1.00.
+
+#### Procedure and materials
+
+On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
+Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
+1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
+A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
+Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
+Eight property--columns appeared in the table.
+
+This whole procedure was repeated two times (two trials).
+In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
+<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
+
+\begin{figure}
+\centering
+    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
+    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
+Left: Participants first generated animal names after seeing six example categories.
+Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
+    \label{fig:generics-prior-task}
+\end{figure}
+
+### Bayesian data analysis
+
+In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
+We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
+One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
+The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
+\text{has wings}).
+
+Formally, we assume the prior data (analzyed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
+The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
+We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
+Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
+The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
+]
+The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
+Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
+Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
+This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
+Similar results can be obtained by rounding 0 to 0.01. 
+Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
+]
+Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
+
+<!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->
+
+We put the following priors over the latent parameters of the model:
+
+\begin{eqnarray}
+\phi_i & \sim & \text{Uniform}(0, 1) \\
+\gamma_i & \sim & \text{Uniform}(0, 1) \\
+\xi_i & \sim & \text{Uniform}(0, 100) \\
+\end{eqnarray}
+
+where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).
+
+'s data; however, we retain the imperfect simpler model for data-analytic ease going forward.
+
+### Results
+
+```{r generic-endorsement-priors}
+# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
+
+d.gen.endorse.priors <- read.csv(paste(project.path, 
+                                       "data/generics/endorsement/",
+                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
+
+genericEndorsementPriorModelHelpers <- '
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var betaShape = function(params){
+  return {
+      a: params.g * params.d,
+      b : (1-params.g) * params.d
+  }
+}
+
+var preprocessedResponses = map(function(d){
+  return avoidEndPoints(d / 100)
+}, data)
+'
+
+structuredPriorModel <- '
+var model = function(){
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data: preprocessedResponses}, function(d){
+    factor( log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    ))
+  })
+  return {g, d, phi}
+}
+'
+
+unstructuredPriorModel <- '
+var model = function(){
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  mapData({data: preprocessedResponses}, function(d){
+    factor(stableComponent.score(d))
+  })
+  return {g, d}
+}
+'
+genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
+
+```
+
+```{r generic-endorsement-priors-unbounded, eval = F}
+# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
+
+d.gen.endorse.priors <- read.csv(paste(project.path, 
+                                       "data/generics/endorsement/",
+                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
+gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
+
+unboundedModel <- '
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var preprocessedResponses = map(function(d){
+  return avoidEndPoints(d / 100)
+}, data)
+
+var shapeParams = function(params){
+  return {
+    a: params.g * params.d,
+    b: (1 - params.g) * params.d
+  }
+}
+
+var model = function(){
+
+  // var numComponents = (1 + poisson(1));
+  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
+  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
+    return uniformDrift({a: 0, b:1, width: 0.2})
+  }))).reverse()
+
+  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
+  var componentParams = map(function(i){
+    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
+    var betaParams = shapeParams({g, d})
+    return betaParams
+  }, _.range(numComponents))
+
+  mapData({data: preprocessedResponses}, function(d){
+
+    var scr = log(sum(map(function(cParams){
+      cParams[1] * exp(Beta(cParams[0]).score(d))
+    }, _.zip(componentParams, mixtureWeights))))
+//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
+    factor(scr)
+  })
+
+  var componentPredictives = map(function(cParams){
+      return beta(cParams)
+  }, componentParams)
+
+  return _.fromPairs(
+    _.zip(
+        map(function(i){ i + "_weight" }, _.range(5)), 
+        mixtureWeights
+      ).concat(
+      _.zip(
+        map(function(i){ i + "_predictive" }, _.range(5)), 
+        componentPredictives
+      )
+    )
+  )//sort(T.toScalars(mixtureWeights))
+};
+'
+
+example.generics.prior.properties <- c(
+  "dont eat people", "have beautiful feathers",
+  "have wings", "are red",
+  "carry malaria", "lay eggs", 
+  "are female", "have spots"
+  )
+priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
+  n_samples <- 10000
+lg = 0
+  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 1,
+                                 cores = 1,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+```
+```{r eval = F}
+m.gen.endorse.priors.unbounded %>%
+      separate(Parameter, into = c("c", "var")) %>% 
+      ggplot(., aes( x=  value, fill = c))+
+ geom_histogram(position = position_dodge(), binwidth = 0.05)+
+ facet_wrap(~var)+
+  scale_fill_solarized()
+```
+
+```{r generic-endorsement-priors-bayesFactors, eval = F}
+genericEndorsementPriorModelPriorLikelihoodHelpers <- '
+var properties = _.uniqBy(_.map(data, "Property"));
+
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var betaShape = function(params){
+  return {
+      a: params.g * params.d,
+      b : (1-params.g) * params.d
+  }
+}
+'
+
+genericEndorsementPriorModelsPriorLikelihood <- '
+var transientComponent = Beta({a:1, b:100})
+
+var model = function(){
+
+  var propertyLogLikes = map(function(property){
+
+    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
+    var preprocessedResponses = map(function(d){
+        return avoidEndPoints(d / 100)
+    }, propertyData);
+
+    var phi = uniformDrift({a:0, b: 1, width:0.2});
+    var g = uniformDrift({a:0, b: 1, width:0.2});
+    var d = uniformDrift({a:0, b: 100, width:5});
+    var stableParams = betaShape({g, d})
+    var stableComponent = Beta(stableParams)
+
+    var logLikes = map(function(d){
+      var structuredLL = log(
+        phi * exp(stableComponent.score(d)) +
+        (1 - phi) * exp(transientComponent.score(d))
+      )
+
+      var unstructuredLL = stableComponent.score(d);
+
+      return {structuredLL, unstructuredLL}
+    }, preprocessedResponses)
+
+    return {
+      structuredLL: sum(_.map(logLikes, "structuredLL")), 
+      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
+    }
+
+  }, properties)
+
+  return {
+    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
+    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
+  }
+}
+'
+
+```
+
+```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
+marginal.prior.likelihoods <- data.frame()
+
+# 100 samples takes 30s
+m.gen.endorse.priors.logLike <- webppl(
+    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
+          genericEndorsementPriorModelsPriorLikelihood,
+          sep = '\n'), 
+    data = d.gen.endorse.priors, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "forward", samples = 1000),
+    chains = 3, cores = 3
+) %>% 
+  mutate(value = as.numeric(value))
+
+min.ll.1 <- min(
+  m.gen.endorse.priors.logLike$value[
+    is.finite(
+      m.gen.endorse.priors.logLike$value
+      )
+    ]
+  )
+
+m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
+  rowwise() %>%
+  mutate(value = ifelse(value == -Inf, min.ll.1, value))
+
+save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
+```
+
+```{r generic-endorsement-priors-bayesFactorsLoad}
+load(file = '../analysis/generics-priors-loglike.Rdata')
+marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
+  group_by(Chain, Parameter) %>%
+  summarize(mll  = logmeanexp(value))
+
+marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
+  spread(Parameter, mll) %>%
+  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
+
+roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
+```
+
+To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
+To see how well the mixture model fits the feature-probability prior data, we use the inferred parameters to generate new data.
+The data generated from the model's posterior is called the *posterior predictive distribution* and is an important step in model criticism. 
+If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
+We construct a posterior predictive distribution by "forward sampling" the model.^[
+This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
+If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
+If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
+We do this many times using the posterior distibution to generate a distribution over predicted feature-probability ratings.
+]
+
+Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
+There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
+One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
+The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
+Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
+]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
+A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
+
+<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
+<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
+-->
+<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
+
+```{r generic-endorsement-priors-savageDickeyModel, eval = F}
+savageDickeyModel <-'
+var model = function(){
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data: preprocessedResponses}, function(d){
+    factor( log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    ))
+  })
+  return {phi}
+}
+
+//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
+// var samples = 2000, burn = burn / 2, lag = 0;
+var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
+verbose: true}, model)
+var modelPrior = Infer({method: "forward", samples:10000}, model)
+
+var pointNull = 1;
+
+var logBFs = map(function(diff){
+  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
+  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
+  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
+  return [diff, Math.log(savageDickeyRatio)]
+}, [0.01, 0.02, 0.03, 0.04, 0.05])
+
+var returnVals = {
+  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
+}
+returnVals
+'
+```
+
+```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
+genericEndorsementPriorSupermodel <- '
+var model = function(){
+  var alpha = uniformDrift({a:0, b: 1, width:0.2});
+  //var structured = flip();
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g1 = uniformDrift({a:0, b: 1, width:0.2});
+  var d1 = uniformDrift({a:0, b: 100, width:5});
+  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
+  // var d0 = uniformDrift({a:0, b: 100, width:5});
+  var stableParams1 = betaShape({g: g1, d: d1})//, 
+      //stableParams0 = betaShape({g: g0, d: d0});
+  var stableComponent1 = Beta(stableParams1)//,
+      //stableComponent0 = Beta(stableParams0);
+
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data:preprocessedResponses},
+    function(d){
+    var scr1 = log(phi * exp(stableComponent1.score(d)) +
+                    (1 - phi) * exp(transientComponent.score(d)))
+    var scr0 = stableComponent1.score(d);
+    // display(exp(scr1) + " " + exp(scr0));
+    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
+    // factor(structured ? scr1 : scr0)
+    factor(combined_ll)
+  })
+  return alpha
+}
+'
+```
+
+```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
+for (p in gen.endorse.properties){
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+  m.gen.endorse.priors.supermodel.posterior <- webppl(
+    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model",  chains = 2,
+                                 cores = 2,
+                                 inference_opts = 
+                                   list(method = "MCMC",
+                                        samples = 2000, 
+                                        burn = 2000, 
+                                        lag = 2, 
+                                        verbose = T)
+    )
+
+  qplot(m.gen.endorse.priors.supermodel.posterior$value)
+}
+```
+
+```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
+genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
+var eps = 0.00000001;
+
+var model = function(){
+  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
+  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
+  var d = uniformDraw(_.range(eps, 100, 2))
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  var logLike = sum(map(function(d){
+    var scr = log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    )
+    return scr
+  }, preprocessedResponses))
+  return logLike
+}
+'
+genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
+var eps = 0.00000001;
+
+var model = function(){
+  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
+  var d = uniformDraw(_.range(eps, 100, 2))
+  var stableParams = betaShape({g, d});
+  var stableComponent = Beta(stableParams);
+  var logLike = sum(map(function(d){
+    return stableComponent.score(d)
+  }, preprocessedResponses))
+  return logLike
+}
+'
+```
+
+```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
+marginal.prior.likelihoods <- data.frame()
+
+for (p in gen.endorse.properties){
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+  m.gen.endorse.priors.logLike.enum1 <- webppl(
+    paste(genericEndorsementPriorModelHelpers,
+          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "enumerate")
+    )
+
+  m.gen.endorse.priors.logLike.enum0 <- webppl(
+    paste(genericEndorsementPriorModelHelpers,
+          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
+    data = priorData, data_var = "data",
+    model_var = "model", 
+    inference_opts = list(method = "enumerate")
+    )
+
+  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
+  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
+
+  marginal.prior.likelihoods <- bind_rows(
+    marginal.prior.likelihoods, 
+    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
+  )
+}
+
+marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
+
+```
+
+```{r generic-endorsement-priors-model-run, eval = F}
+m.gen.endorse.priors.posteriorPredictive <- data.frame()
+n_samples <- 1000
+lg = 0
+example.generics.prior.properties <- c(
+  "dont eat people", "have beautiful feathers",
+  "have wings", "are red",
+  "carry malaria", "lay eggs", 
+  "are female", "have spots"
+  )
+
+for (p in example.generics.prior.properties ) {
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+    m.gen.endorse.priors.structured <- webppl(
+      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
+      group_by(Iteration, Chain) %>%
+      spread(Parameter, value) %>%
+      rowwise() %>%
+      mutate(
+        a = g*d,
+        b = (1-g)*d,
+        isPresent = rbinom(1, 1, prob = phi),
+        prevalence = ifelse(isPresent == 1, 
+                           rbeta(n = 1, 
+                                 shape1 = a,
+                                 shape2 = b),
+                           rbeta(n = 1,
+                                 shape1 = 1,
+                                 shape2 = 100)),
+        Property = p, src = "Structured"
+      ) %>% ungroup()
+
+    m.gen.endorse.priors.unstructured <- webppl(
+      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
+      group_by(Iteration, Chain) %>%
+      spread(Parameter, value) %>%
+      rowwise() %>%
+      mutate(
+        a = g*d,
+        b = (1-g)*d,
+        prevalence = rbeta(n = 1, 
+                                 shape1 = a,
+                                 shape2 = b),
+        Property = p, src = "Unstructured"
+      ) %>% ungroup()
+
+    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
+      m.gen.endorse.priors.posteriorPredictive,
+      bind_rows(
+       m.gen.endorse.priors.structured.predictive %>%
+          select( src, Property, prevalence),
+      m.gen.endorse.priors.unstructured.predictive %>%
+          select( src, Property, prevalence),
+      data.frame(Property = p,
+                 src = "Data",
+                 prevalence = priorData/100)
+      )
+    )
+
+  # for (c in 1:2){
+  #     m.gen.endorse.priors.savage <- webppl(
+  #   paste(genericEndorsementPriorModelHelpers, 
+  #         savageDickeyModel, sep = '\n'), 
+  #   data = priorData, 
+  #   data_var = "data"
+  #   )
+
+  # m.inferred.prior <- get_samples(
+  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
+  #     rename(prob = probs), n_samples)
+  # 
+  # m.inferred.posterior <- get_samples(
+  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
+  #     rename(prob = probs), n_samples)
+  # 
+  # posterior.density <- density(m.inferred.posterior$phi,
+  #         from = 0, to = 1)
+  # 
+  # prior.density <- density(m.inferred.prior$phi,
+  #         from = 0, to = 1)
+  # 
+  # logBF01 = log(approxfun(posterior.density)(1)) - 
+  #   log(approxfun(prior.density)(1))
+
+  # m.gen.endorse.priors.savage.summary <- bind_rows(
+  #   m.gen.endorse.priors.savage.summary,
+  #     bind_rows(
+  #     data.frame(Property = p, 
+  #                Chain = c, 
+  #                diff = NA,
+  #                logBF01 = logBF01,
+  #                BF01= exp(logBF01)),
+  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
+  #       rename(diff = X1, logBF01 = X2) %>%
+  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
+  #     )
+  # )
+  # 
+  # }
+
+    #for (c in 1:3){
+
+      # posterior.logspline <-  polspline::logspline(filter(
+      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
+      #   lbound = 0, ubound = 1)
+      # 
+      #   posterior <- dlogspline(1, posterior.logspline)
+      # prior <- dunif(1, min = 0, max = 1)
+      # BF01 <- posterior/prior
+      # 
+      # print(log(BF01))
+
+  #}
+
+  #print(p)
+  #print(priorData)
+}
+save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
+
+```
+
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
+Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
+A completely uniform distribution would be represented as the y = x line."}
+load('../analysis/generics-priors-posteriorPredictives.Rdata')
+ggplot(m.gen.endorse.priors.posteriorPredictive, 
+           aes( x = prevalence, color = src, lty = src))+
+      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    stat_ecdf(size = 1)+
+    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    facet_wrap(~Property, nrow = 2)+
+    scale_linetype_manual(values = c(1, 4, 3))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  coord_fixed()+
+    xlab("Feature-probability") +
+    ylab("Cumulative probability density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+
+```
+
+```{r generic-endorsement-priors-figure2, eval = F}
+ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
+         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
+       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
+  geom_bar(stat = 'identity', position = position_dodge())+
+  geom_errorbar(position = position_dodge())+
+  coord_flip()+
+  ylab("MAP estimate and 95% HDI of Mixture parameter")
+```
+
+## Endorsement model comparison
+
+To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
 As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity* (the probability of a kind given the feature; described in more detail below) predicts generic endorsement of these items.
+As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
 We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
 
-Our underspecified threshold model has access to the full prior distribution on feature-probabilities $P(h)$, from which it infers likely thresholds for the generic. 
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic.
-There are thus three unique components to this model: (i) the prior distribution $P(h)$, (ii) the speaker model deciding whether or not to produce the generic, and (iii) the uncertain threshold.
+Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
+1b), from which the interpreter model infers likely thresholds for the generic.
+The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
+We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement deciding whether or not to produce the generic, and (c) the uncertain threshold.
 As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (i) and (ii) but lacks the uncertainty over the threshold.
+This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
 This provides a strict test of our *simple but underspecified* hypothesis.
@@
 
-##### Referent feature-probability baseline
+### Referent feature-probability baseline
 
 From the feature-probability prior data (Expt.
-1a), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
+1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-This is because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
+The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
+
 However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-
-##### Cue validity and referent feature-probability
+This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
+
+### Cue validity and referent feature-probability
 
@@
 
-##### Fixed threshold RSA model
+### Fixed threshold endorsement model
 
@@
 
-##### Uncertain threshold RSA model
+### Uncertain threshold RSA model
 
@@
 
-<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which referent-category prevalence is not a good indicator of the acceptability (e.g.
-\emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades).
--->
-<!-- We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false.
--->
-<!-- \emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model. -->
-<!-- This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context.
--->
-
-<!-- The above analysis provides a single estimate for model predictions, but it is based on noisy empirical measurements of $P(x)$.
-In order to estimate the impact of this empirical noise on our model predictions, we resampled the prior data (with replacement) for 57 participants worth of data, discretizing and binning as we did above and then inferring parameters.
--->
-<!-- This procedure (re-sample prior, discretize and bin, infer parameters) was repeated 500 times to bootstrap the model predictions. -->
-<!-- The Maximum A-Posteriori (MAP) estimate and 95\% Highest Probability Density (HPD) interval for $\lambda_1$ is 0.5 [0.004, 12.7] and $\lambda_2$ is 1.7 [1.3, 2.1]. -->
-<!-- ^[ -->
-<!-- The fact that $\lambda_1$ is credibly less than 1 suggests that the generic utterance may be more costly than "staying silent" (our model assumes equal cost). -->
-<!-- We maintain using only the two $\lambda$ parameters in the model for simplicity. -->
-<!-- ] -->
-
-<!-- This is akin to fitting the parameters and is the critical step in model validation: It shows what data is actually predicted by the model.)  -->
-
-<!-- basic communicative principles (\emph{be truthful}, \emph{be informative}) operating over diverse prior beliefs about the properties, all of which are at play in understanding language.  -->
-
-<!-- \begin{figure} -->
-<!-- \centering -->
-<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-prevalence-tj.pdf} -->
-<!--     \caption{Endorsing familiar generics. (a)  -->
-<!--     Prevalence prior distributions empirically elicited for twenty-one animal properties. -->
-<!--     Prior distributions summarized by two parameters of a structured Bayesian model: $\phi$----a property's potential to be present in a category----and $\gamma$----the mean prevalence when it is possible for the property to be present in a category.
--->
-<!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
-<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a referent-category. -->
-<!--     (b) -->
-<!--     Human acceptability judgments compared with model predictions (left) and the referent-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
-<!--     Color denotes referent-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
-<!--      Error bars denote 95\% Bayesian credible intervals. -->
-<!--     } -->
-<!--   \label{fig:commongenerics} -->
-
-<!-- \end{figure} -->
-
 ## Discussion
@@
 In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
+
+### Discussion (from priors)
+
+The feature-probability prior distribution $P_f(h)$ encodes beliefs about the feature-probability (or, probabilities) of a feature $f$ across different kinds.
+These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
+
+<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->
+
+If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
+For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
+
+A natural proposal is that endorsements for generic language have to do with cue validity.
+This possibility has been investigated empirically in one of few examples of statistical modeling of generics, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
+However, cue validity has some empirical and theoretical issues.
+Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
+Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
+<!-- If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
+-->
+<!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
+<!-- ^[ -->
+<!-- As a simple demonstration, imagine we've just discovered a new kind of animal called a fep. -->
+<!-- It should be easy to estimate the prevalence of being female among feps (probably 50\%) even without any knowledge of feps.  -->
+<!-- However, if you learn in another context that a particular entity is green, it's impossible to estimate the cue validity of being green for feps -->
+<!-- that it's easy to estimate the prevalence of being female among  -->
+<!-- ] -->
+
+However, we should not throw away the possibility that distributional information about the property is relevant. 
+The mixture parameter $\phi$ in the feature-probability prior distribution can be seen as a generalization of the construct of cue validity. 
+Recall that $\phi$ is the weighting between the two generative components of the feature-probability prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
+If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the feature-probability prior, in that it can be derived via Bayes' Rule:
+$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
+
+Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is no longer well-defined (or, it is zero for all kinds). 
+This is for the same reason that for a probability distribution over the real numbers (a *continuous* probability distribution), the probability of any particular number is zero. 
+For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
+The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds} (and hence, $\phi$ is relatively low), but there are many kinds of birds and the feature is not particularly diagnostic for any given one of the subkinds (e.g., robins).
+$phi$ is still relatively small in this case because it encodes information about the distribution across kinds and not just one particular kind.
+This is an important point of departure in our work from previous work.
+
+<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
+<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
+<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
+<!-- However, cue validity requires knowledge of the referent-category $k$ -->
+
+<!-- For example, suppose there are 10 possible kinds and 3 of them belong the stable cause distribution and 7 belong to the transient cause distribution.  -->
+<!-- Say we observe the feature and want to know what the probability that the entity is of a particular kind that we know to be of the stable distribution.  -->
+<!-- If we know the prevalence given each distribution (i.e, $P(f \mid k_{stable})$ and $P(f \mid k_{transient})$). -->
+
+<!-- For simplicity, assume that each component corresponds to a single probability (i.e., a single prevalence value) as opposed to a distribution. -->
+<!-- Thus, $\mathcal{D_{stable}} = P(f \mid \mathcal{D_{stable}}) = p_{stable}$ -->
+
+<!-- $n_{stable} n_{transient}$ -->
+
+<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
+<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
+<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
+<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
+<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
+<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
+-->
+<!-- Do a BDA to describe the data in a more compact form. -->
+<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq.
+\ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).
+-->
+<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content.
+-->
+<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
+<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
+<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the referent-category.
+-->
+<!-- Some properties have priors that are unimodal with low variance (e.g.
+\textsc{is female}); these properties are present in every kind in almost exactly the same proportion.
+The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.
+-->
+<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->
 

### 2017-10-25 paper/comgen-paper.Rmd
finish restructuring generics case study

@@
 
-<!-- Consider how an uniformly underspecified threshold would interact with a uniformly uncertain belief about a probability (recall the thresholds defines what probabilities or states of the world should be ruled out).
--->
-<!-- If the threshold is very high, only the highest probabilities would be left (i.e., pass the threshold). -->
-<!-- If the threshold is slightly lower but still high, the highest probabilities would still pass the threshold, as would some that are slightly lower. -->
-<!-- As the threshold takes on lower and lower values, more and more probabilities would surpass it. -->
-<!-- When the threshold is very low, almost all probabilities are consistent with it. -->
-<!-- But since we don't know *a priori* what the threshold is likely to be, each of theses situations is plausible. -->
-<!-- The posterior distribution on probabilities or states of the world will favor higher probabilities (because they pass more thresholds), but will still include probabilities that are quite low [though they are *a posteriori* unlikely; see Figure \ref{fig:simluations} ].
--->
-<!-- Speakers, thus, will produce generalizations with some probability in each state of the world, though the speaker will say the generalization more often when the propensities associated with the states of the world are higher [see Figure \ref{fig:simluations}].
--->
-
-<!-- - Figure -->
-  <!-- - Subfigure 1 [width = 0.2] (Uniform priors) [two rows, left subfigure] -->
-  <!--   -- Basic L0 posteriors on degrees for uncertain, fixed at 0 and fixed at 0.5 -->
-  <!--   -- Basic S1 posteriors on utterances, for prevalence 0 - 1 (and for fixed thresholds) -->
-  <!-- - Subfigure 2 [width = 0.8] (L0 vs. L1 lifted vs. L1 unlifted x 4 priors x {speaker, listener} ) [model as color, lty; priors as columns x {speaker, listeners} as rows]  -->
-  <!--   -- priors = [uniform, n-shaped, u-shaped, mixture model / maybe put more in appendix: rare, accidental, female, eggs] -->
-
-<!--
-mht: is it possible to construct priors in causals that would reflect the qualitative prediction shown here?
--->
-
-<!-- $P(x)$ is a distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across animal categories.  -->
-<!-- In Figure \ref{fig:schematic-unif}, are $L_1$ (Eq.~\ref{eq:L1}) posterior prevalence distributions on $x$ (red solid line) for several example prior prevalence distributions $P(x)$ (blue dashed line), as well as the $S_2$ generic endorsement probability for different levels of prevalence.
--->
-<!-- We name these example prior distributions to suggest properties that might be associated with such priors.  -->
-<!-- (Later, we will empirically measure these priors for properties of interest.) -->
-<!-- First, we explore generic interpretation and endorsement for priors of three different shapes (left column).  -->
-<!-- For each of these, the $L_1$ posterior distribution (red solid) over prevalence is heavily driven by the prior (blue dashed). -->
-<!-- $S_2$ endorsement probabilities for the generic (black solid) increase as a function of prevalence, and what counts as "true" (in terms of the prevalence) depends on the prior.  -->
-
-<!-- \begin{figure} -->
-<!-- \centering -->
-<!--     \includegraphics[width=\columnwidth]{figs/schematics_s2.pdf} -->
-<!--     \caption{Schematic prior distributions for prevalence $x$ (blue dashed), the pragmatic listener $L_1$ model's posterior distribution over prevalence upon hearing a generic utterance (red), and speaker $S_2$ model's endorsement of a generic utterance for different levels of prevalence (black).
--->
-<!--     The names given to these priors are meant to be suggestive of what kinds of properties these distributions might correspond to. -->
-<!--     The left column uses prevalence priors modeled as Beta(15,15), Beta(4,1), and Beta(4,16) distributions. -->
-<!--       The right column uses a prior distribution that is a mixture of the distribution to the left of it with a second component, modeled as Beta(0.5, 4.5), reflecting categories with 0\% property prevalence.
--->
-<!--     Horizontal dashed line at 0.5 is for convenience of comparing the point at which an utterance becomes judged as more true than false for $S_2$. -->
-<!-- 	Note that the prior distribution over prevalence will be the same as $L_1$'s posterior distribution upon hearing the "null" utterance. -->
-<!--     } -->
-<!--   \label{fig:schematic-unif} -->
-<!-- \end{figure} -->
-
-<!-- To take one example, consider the distribution over what might be the property "are female" (top-left facet). -->
-<!-- The \emph{a priori} prevalence is centered around 0.5. -->
-<!-- Because of pragmatics, the pressure to be \emph{truthful} will drive likely threshold values below 0.5 (lower values are more likely to be true).  -->
-<!-- At the same time, the pressure to be \emph{informative} will drive the threshold values up: Higher values are more likely to be informative.  -->
-<!-- The result is a posterior over prevalence that is only marginally greater than the prior, making higher prevalence values more likely after hearing the generic.  -->
-<!-- But the relative information gain is very little (the posterior is not very different from the prior), and thus the $S_2$ model is reluctant to endorse the generic unless the property is exceedingly prevalent.
--->
-<!-- The same basic phenomenon can be observed for the other two example priors (left column): The posterior over prevalence heavily depends upon the prior, but is also not very different from the prior.
--->
-
-<!-- We now imagine what would happen if there were some kinds where the property was completely absent, while being present at some rate in other kinds. -->
-<!-- Figure \ref{fig:schematic-unif} (right column) shows this possibility: mixing the distribution to the left of it with a second component at 0\% prevalence. -->
-<!-- Consider the schematic prior over "lay eggs". -->
-<!-- We see the pragmatic listener $L_1$'s posterior prevalence distribution is not very different from the interpretation that doesn't include the second component in the prior (here, "are female"), but it is dramatically different from the prior with two components (compare red with blue dashed line for the right column).
--->
-<!-- This suggests that when many categories have 0\% prevalence, lower thresholds are informative.  -->
-<!-- Indeed, the $S_2$ model predicts that the generic becomes felicitous at lower prevalence levels (compare black line of left v. right column). -->
-<!-- For "lay eggs", when the property is prevalent in 50\% of the kind (e.g., 50\% of birds lay eggs), endorsement of the generic (e.g., \emph{Birds lay eggs}) by the $S_2$ is roughly 0.85; for "are female", with the same prevalence (50\% of birds are female), endorsement for \emph{Birds are female} is only 0.50: It is judged to be neither true nor false.
--->
-<!-- The important result is the asymmetry: the first generic can be endorsed more strongly than the second, at the same prevalence level; the exact endorsement rates depend on quantitative aspects of the priors, which must be determined empirically.
--->
-
-<!-- The model thus predicts differences in truth judgments depending on the prevalence prior.  -->
-<!-- The first test of our theory, then, will be to see if these predictions correspond to human truth judgments of familiar generic sentences.  -->
-
-<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
-<!-- \begin{eqnarray} -->
-<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
-<!-- \end{eqnarray} -->
-<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->
-
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-<!-- In this model, a threshold $\theta$ is established in context by a Bayesian listener reasoning about what threshold would make this utterance true? -->
-
-<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-
-<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise.
--->
-<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->
-
-<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
-<!-- \begin{eqnarray} -->
-<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
-<!-- \end{eqnarray} -->
-<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
-<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->
-
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the propensity: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-<!-- The prior distribution $P(h)$ is a distribution over likely degrees of propensity.  -->
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-
-<!-- Life is only so long, however, and a person can only be in one place at a time. -->
-<!-- The amount of data we can gather about any particular category, event, or causal force is extremely limited by these physical constraints. -->
-<!-- Thus, it would be useful if language provided a simple way to communicate these generalizations to one another. -->
-
-<!-- # A Formal Theory of Generalizations in Language -->
-
-<!-- We find both the statistical and conceptual accounts compelling, but an important perspective is missing. -->
-<!-- Linguistic generalizations are not unique in their flexibility. -->
-<!-- Understanding language in general depends upon assumptions interlocutors make about each other and what content is under discussion.  -->
-<!-- Viewing language understanding as a social reasoning process reveals that utterances carry a mosaic of interpretations with a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000].
--->
-<!-- Can the puzzles of generic language be understood as effects of pragmatic reasoning? -->
-<!-- If so, we may be able to get away with a relatively simple, statistical,  semantic theory. -->
-<!-- Abstract mental representations, then, may be the conceptual backdrop against which generic language is interpreted.  -->
-
-<!-- We pursue such a line of inquiry, assuming the simplest truth-conditional meaning: a threshold on prevalence $P(F\mid K)>\theta$ [c.f., @Cohen1999]. -->
-<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g. \emph{Mosquitos carry malaria}; \emph{Robins lay eggs} v. \emph{Robins are female}),  -->
-<!-- so instead we allow this threshold to be established in context through pragmatic reasoning. -->
-<!-- Such an inference would depend on background knowledge about properties and categories---potentially structured, conceptual knowledge. -->
-<!-- This inference, nonetheless, is a general mechanism of understanding language, not specific to interpreting generic statements. -->
-<!-- We formalize this hypothesis in the Rational Speech Act (RSA) theory---a formal, probabilistic theory of language understanding. -->
-<!-- RSA is derived from social reasoning, formalized as recursive Bayesian inference between speaker and listener [@Frank2012; @Goodman2013; @Goodman2016; see also, @Franke2009; @Franke2015]. -->
-<!-- @Goodman2016 provides a good introduction to the RSA framework and Appendix A presents a brief tutorial on RSA for the reader unfamiliar. -->
-
-<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
-<!-- \begin{eqnarray} -->
-<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
-<!-- \end{eqnarray} -->
-<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
-<!-- The prior distribution $P(x)$ is a distribution over likely states of the world.  -->
-<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly).
--->
-<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise.
--->
-<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->
-
-<!-- To understand how language is interpreted pragmatically, we model a pragmatic listener $L_1$ who updates her prior beliefs $P(x)$ by reasoning about the generative process of the utterance, the speaker model $S_1$.
--->
-<!-- \begin{eqnarray} -->
-<!-- L_{1}(x , \theta \mid u) &\propto& S_{1}(u \mid x, \theta) \cdot P(x) \cdot P(\theta) \label{eq:L1} -->
-<!-- \end{eqnarray} -->
-<!-- Following @Lassiter2013, we model the pragmatic listener as having uncertainty about the threshold: $P(\theta)$. -->
-<!-- Though the listener doesn't know the threshold *a priori*, she resolves the threshold (i.e., the meaning) in context by integrating her prior beliefs $P(x)$ with the basic principles of communication to be truthful and informative, instantiated in her model of the speaker $S_1$ [@Lassiter2015; @GoodmanLassiter].
--->
-<!-- In principle, thresholds could be learned over time for different contexts, but here we assume the listener has no informative knowledge about the semantic variable $P(\theta) = \text{Uniform([0, 1])}$.
--->
-<!-- The pragmatic listener $L_1$ (Eq. \ref{eq:L1}) is thus a model of *generic interpretation*: Upon hearing a generic, how should a listener update her beliefs? -->
-
 # Case Study 1: Generic Language
@@
 
-<!-- That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not. -->
-<!-- As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
--->
-<!-- We validate these simulations empirically by measuring t and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq.
-\ref{eq:S1} (Expt.
-1a).
--->
-
-<!-- <!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  --> -->
-<!-- We test our model on -->
-
-<!-- To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a). -->
-<!-- We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013]. -->
-<!-- In particular, we hypothesize that different kind--property relations [e.g., *principled* v.
-*accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the feature-probability prior.
--->
-<!-- If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
--->
-<!-- A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007]. -->
-<!-- As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one. -->
-
-<!-- After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt.
-1b).
--->
-<!-- In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model.
--->
 ## Experiment 1a: Generic endorsements
@@
 Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
-
 <!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->
-
 We put the following priors over the latent parameters of the model:
-
 \begin{eqnarray}
@@
 \gamma_i & \sim & \text{Uniform}(0, 1) \\
-\xi_i & \sim & \text{Uniform}(0, 100) \\
+\xi_i & \sim & \text{Uniform}(0, 100)
 \end{eqnarray}
-
 where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).
-
-'s data; however, we retain the imperfect simpler model for data-analytic ease going forward.
 
@@
 The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement deciding whether or not to produce the generic, and (c) the uncertain threshold.
+We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
 As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
 This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of our *simple but underspecified* hypothesis.
+This provides a strict test of the uncertain-threshold hypothesis.
 
@@
 
-### Referent feature-probability baseline
+### Baseline models
+
+#### Referent feature-probability
 
@@
 
-### Cue validity and referent feature-probability
-
-<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
+#### Cue validity and referent feature-probability
+
+##### Model specification
+
+As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
+If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+*Cue validity* thus captures the distinctiveness of the feature for the category. 
 For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-
-For a feature-probability distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the feature-probability prior distribution.
-In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
-For this analysis, we measured cue validity using a free production paradigm, following @Cree2006.
+Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
+Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
+Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
+
+We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
+If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
+$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
+Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
+In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
 Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B.
+For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
+
+##### Results
 
@@
 
-### Fixed threshold endorsement model
+### Information-theoretic endorsement models
+
+The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
+Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
+This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
+an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
+We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
+We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
+
+##### Model specification
+
+For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
+\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
+Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
+This corresponds to the more general form of the model described in a footnote in the model section. 
+For these data, the predictions of these two models are nearly identical.
+]
+(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
+We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
+The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
+The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+
+```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
+The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
+1a.
+The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$.
+The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input.
+This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
+Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion.
+"}
+knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
+```
+
+To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
+1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
+1a \& b (see Figure \ref{fig:genericsModelDiagram}).
+For the parameters of the feature-probability prior distributions, we use the same priors described in Expt.
+1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
+We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
+
+#### Fixed-threshold  model
+
+We first test a model that has two of the the above three main architectural features.
+This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
+The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
+For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
+Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
+]
+This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
 
@@
 
-The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
-Unlike the simple regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural differences: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized using RSA) and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.
-
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under this semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
-
-<!-- Our pragmatic speaker model, $S_1$ in Eq.
-\ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the feature-probability of the property within the referent-category $h'$).
--->
-We use the empirically estimated referent-category feature-probability as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt.
-1a as the listener's feature-probability prior $P(h)$.^[
-Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-This corresponds to the more general form of the model described in a footnote in the model section. 
-With these data, the predictions of these two models are nearly identical.
-]
-The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-
-```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
-The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
-1a.
-The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$.
-The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input.
-This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
-Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion.
-"}
-knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
-```
-
-To fit this model, we incorporate the RSA model into the Bayesian data analysis model of the feature-probability prior data (Expt.
-1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$ is inferred jointly with the referent feature-probability $h_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$ using data from Expt.
-1a \& b (see Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the feature-probability distributions, we use the same priors described in Expt.
-1a; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of this joint inference model using an incrementalized-version of the  by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
-
 The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1a).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the feature-probability distributions).
+Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+1b).
+This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
 
 We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the pragmatics model and the observed data.)
+(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
 Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-For almost all items, it assigns an intermediate endorsement.
-This is because almost all items get endorsed by some participants; the model then infers that the referent feature-probability must be at least a little greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true.
-The speaker model then must decide is it better to say the 0\%-threshold meaning or stay silent.
+The model fails to distinguish any of the generic sentences because they are all somewhat true. 
+All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
+
+The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
 For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing some statements (most model predictions around 0.5\%).
-Consistent with intuition, assigning a fixed-semantics is too lenient a specification.
+For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
+Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
+This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
+The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
 
@@
 
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold.
+Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
 We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the speaker model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
 
@@
 In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
-### Discussion (from priors)
-
-The feature-probability prior distribution $P_f(h)$ encodes beliefs about the feature-probability (or, probabilities) of a feature $f$ across different kinds.
-These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
-
-<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->
-
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
-
-A natural proposal is that endorsements for generic language have to do with cue validity.
-This possibility has been investigated empirically in one of few examples of statistical modeling of generics, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
-However, cue validity has some empirical and theoretical issues.
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-<!-- If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
--->
-<!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
-<!-- ^[ -->
-<!-- As a simple demonstration, imagine we've just discovered a new kind of animal called a fep. -->
-<!-- It should be easy to estimate the prevalence of being female among feps (probably 50\%) even without any knowledge of feps.  -->
-<!-- However, if you learn in another context that a particular entity is green, it's impossible to estimate the cue validity of being green for feps -->
-<!-- that it's easy to estimate the prevalence of being female among  -->
-<!-- ] -->
-
-However, we should not throw away the possibility that distributional information about the property is relevant. 
-The mixture parameter $\phi$ in the feature-probability prior distribution can be seen as a generalization of the construct of cue validity. 
-Recall that $\phi$ is the weighting between the two generative components of the feature-probability prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the feature-probability prior, in that it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-
-Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is no longer well-defined (or, it is zero for all kinds). 
-This is for the same reason that for a probability distribution over the real numbers (a *continuous* probability distribution), the probability of any particular number is zero. 
-For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
-The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds} (and hence, $\phi$ is relatively low), but there are many kinds of birds and the feature is not particularly diagnostic for any given one of the subkinds (e.g., robins).
-$phi$ is still relatively small in this case because it encodes information about the distribution across kinds and not just one particular kind.
-This is an important point of departure in our work from previous work.
-
-<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
-<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
-<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
-<!-- However, cue validity requires knowledge of the referent-category $k$ -->
-
-<!-- For example, suppose there are 10 possible kinds and 3 of them belong the stable cause distribution and 7 belong to the transient cause distribution.  -->
-<!-- Say we observe the feature and want to know what the probability that the entity is of a particular kind that we know to be of the stable distribution.  -->
-<!-- If we know the prevalence given each distribution (i.e, $P(f \mid k_{stable})$ and $P(f \mid k_{transient})$). -->
-
-<!-- For simplicity, assume that each component corresponds to a single probability (i.e., a single prevalence value) as opposed to a distribution. -->
-<!-- Thus, $\mathcal{D_{stable}} = P(f \mid \mathcal{D_{stable}}) = p_{stable}$ -->
-
-<!-- $n_{stable} n_{transient}$ -->
-
-<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
-<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
-<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
-<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
-<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
-<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.
--->
-<!-- Do a BDA to describe the data in a more compact form. -->
-<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq.
-\ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).
--->
-<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content.
--->
-<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
-<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
-<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the referent-category.
--->
-<!-- Some properties have priors that are unimodal with low variance (e.g.
-\textsc{is female}); these properties are present in every kind in almost exactly the same proportion.
-The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.
--->
-<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->
-
-<!-- In addition, why generics often imply the property is widespread has also been puzzling [@Gelman2004]. -->
-<!-- We show that this is the result of the shape of listener's prior knowledge and that when that shape differs, the implied prevalence is much weaker (e.g., with accidental properties). -->
-<!-- Even more puzzling has been the basic asymmetry between endorsements and interpretations [@Cimpian2010]. -->
-<!-- We show that this asymmetry arises from the underspecified-threshold interacting with diverse prior beliefs.  -->
-<!-- While implied prevalences vary wildly for different kinds of properties under discussion, the endorsements are relatively less sensitive to these distinctions. -->
-<!-- Thus, the basic asymmetry is largely being driven by the listener's interpretation of a generic. -->
 

### 2017-10-31 paper/appendix-bda.Rmd
move bda details to appendix

--- 2017-10-25 paper/comgen-paper.Rmd
@@
----
-title             : "The language of generalization"
-shorttitle        : "The language of generalization"
-
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-  - \usepackage{amsmath}
-  - \usepackage{graphicx}
-  - \usepackage{subcaption}
-
-author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
-
-abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Dogs bark").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is in determining what which such statements are true or false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of generalizations in language, while simpler models fall short.
-    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
-    The results suggest that central phenomena emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "20000"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-
-\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
-\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
-\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
-```
-
-```{r libraries, cache = F}
-library(papaja)
-library(formatR)
-library(rwebppl)
-library(xtable)
+```{r echo = F}
+library(langcog)
 library(tidyverse)
-library(forcats)
-library(langcog)
-# library(dplyr)
-library(data.table)
-library(coda)
 library(ggthemes)
-library(ggrepel)
 library(jsonlite)
-library(gridExtra)
-library(lme4)
-library(knitr)
-library(cowplot)
 theme_set(theme_few())
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-logmeanexp <- function(x){
-  x.num <- as.numeric(x)
-  xstar = max(x.num)
-  return(xstar + log(mean(exp(x.num - xstar))))
-}
-
-compute_r2 <- function(df,v1, v2, sigfigs = 3){
-  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
-}
-
-compute_mse <- function(df, v1, v2, sigfigs = 3){
-  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
-}
-
 project.path <- "../"
-options("scipen"=10) 
-```
-
-<!-- 
-possible titles:
-- Communicating generalizations
-- The language of generalization
-- The language of generalization: Probability, vagueness, and interaction
--->
-
-# Introduction
-
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
-
-<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
-<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
-<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
-<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
--->
-<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
-<!-- \ndg{this par doesn't really do much} -->
-
-Generalizations in language are often studied via *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which even 2-and-a-half-year-olds appreciate [@Cimpian2008].
-<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
--->
-Generics are just one case of generalization in language, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
-
-<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
-<!-- Individual entities can also be talked about in generalization, using so-called  -->
-<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
-<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
-
-Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining what makes such statements true or false.
-When we hear "Dogs bark", it sounds like a universal statement, like *All* dogs bark.
-But the property doesn't apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
-The generalization could signal something weaker like *Most* dogs bark.
-<!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
-However, only a tiny fraction of moquitos carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to *some* goes too far: Half of robins are female, but saying "Robins are female" seems odd.
-That same half of robins (i.e., the females), however, also lay eggs, and "Robins lay eggs" is again intuively true.
-
-These observations have led to proposals that the prevalence or probability of a member of the category having the property (e.g., $P(x \text{ barks} \mid x \text{ is a dog})$) is only tangentially related to generic meaning.
-*Conceptual accounts* of generics emphasize the structure of "generic knowledge" [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-From this perspective, the statement "Bishops move diagonally" is true not because bishops tend to move diagonally, but rather because those are the rules of chess.
-With this in mind, @Leslie2007 proposes *cognitively primitive* principles that dictate how generics become true or false.
-*Characteristic* features are one such principle; "Robins lay eggs" is thus true because it is the mode of reproduction, and reproduction is a characteristic dimension for animal kinds.
-*Horrifying* or *striking* information also leads to true generics, which is why "Mosquitos carry malaria" is true despite its low prevalence.
-
-Yet others have observed that generics are not limited to conveying rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-<!-- Arbitrary relationships are also expressed with generics:  -->
-"Barns are red" is true because that is how barn-owners tend to paint their barns; if barn-owners decided to switch to blue, the things they would be painting would still be considered barns.
-"Ravens are bigger than toasters" because of the size of ravens and the size of toasters, not because of a special relationship between ravens and toasters.
-*Conceptual accounts* must then be supplemented with the proviso that, in certain situations, the statistics of the world do influence human intuitions about generics.
-
-Generic statements have diverse theoretical underpinnings, and the conceptual view highlights this diversity [e.g., @Prasada2013].
-But insofar as generics are a single class in language---indeed, insofar as they are a subclass of generalization in language---there should be a general, unified principle that explains what makes the statements true or false.
-The same logic should apply to all generalizations in language, including habitual and causal language.
-This is the goal of this paper.
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-
-In this paper, we take a critical look at the notion that prevalence---or its more general formulation, probability---cannot serve as the core of a semantic theory of generalization in language (including generics).
-We strive for a probability-based semantics for its generality: Probability is the universal currency of belief and serves as a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the object of communication for generalizations. 
-We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
-Formalizing such a theory is scientifically useful as well to make explicit the assumptions the theory, which in turn, elucidates the conditions under which the theory may be meaningfully tested.
-
-We take the primary desideratum for a theory of the language of generalization to be adult human intuitions into the truth or felicity of statements conveying generalization, which we measure empirically.
-To test the hypothesis that probability can serve as the core semantic theory, we build a computational model of endorsement around this semantic theory and compare our model to human judgments.
-Though concepts such as *striking properties* are not explicitly formalized in our model, there is a natural avenue for future integration as our theory is couched in a general cognitive modeling framework.
-
-Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
-In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000].
-We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement.
-We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...}
-We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
-The paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization from observations, serving as the foundation for our semantic theory.
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a computational model of endorsement.
-<!-- To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes. -->
-<!-- Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
--->
-In Section 3, we describe experiments that measure both listener prior knowledge and the prevalence of the properties in question, and relate them via our model to the endorsements of generalizations about categories (*generic language*).
-In Section 4, we describe experiments that measure listener prior knowledge and manipulate the frequency of various events to explain endorsements of generalizations about events (*habitual language*).
-Finally, in Section 5, we describe experiments that manipulate both the listener's prior knowledge and the prevalence of the properties in question in endorsing generalizations about causes (*causal language*).
-
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
-We also show how our endorsement model is a special case of a speaker model in a rational framework of communication. 
-This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
-
-<!-- (2) It also allows us to consider sources of gradience in behavior, determining whether or not we should allocate it to *noise* in the observed data or to *uncertainty* in the head of the language user.
--->
-<!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
-
-<!-- \ndg{There haven't been many formal models of generic language, none have made quantitative predictions. Say why this is important. -->
-<!-- To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities. -->
-<!-- Then we need to say how these probabilities are communicated. Use RSA...} -->
-
-<!-- Rational models of communication have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
--->
-
-<!-- give rise to the productivity of human thought and form of foundations of cultural knowledge. -->
-<!-- They allow us to understand the complex world around us and dream up how possible future situations might unfold. -->
-<!-- It's been suggested that were psychology to have *general laws* akin to Newtonian laws in physics, the first general law in psychology would be of generalizations [Shepard1987]. -->
-<!-- Generalizations are central to human understanding.  -->
-<!-- Even before birth, human and non-human animals alike gather statistical information and form generalizations to predict what will come next. -->
-<!-- The human learner, perhaps uniquely in the animal kingdom, displays striking sensitivity to the intentional and pedagogical actions of others, leading to distinct and often stronger inferences from data than would otherwise be warranted from random observations.
--->
-<!-- and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017]. -->
-
-<!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
-
-<!-- Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization. -->
-<!-- *Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general , specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
--->
-<!-- Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious.  -->
-<!-- Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.  -->
-
-<!-- The language of generalization is exceedingly difficult to formalize, however. -->
-<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
-<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
--->
-<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->
-
-<!-- Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females. -->
-<!-- Generics roughly convey that the properties is widespread in the category (e.g., *Most dogs are friendly*), however they don't always imply the same degree of prevalence. -->
-<!-- *Birds are female* sounds strange even though half of birds of female.  -->
-
-<!-- ALTERNATIVE INTRO -->
-
-<!-- Yet, generalizations can be hard to acquire. -->
-<!-- Consider what it would take to learn that under certain conditions (e.g., when eaten raw) a plant is poisonous, while under other conditions (e.g., when processed appropriately) the plant is nutritious.
--->
-<!-- This is a common ecological problem and historical examples suggest that humans are not particularly good at learning such generalizations [e.g., the Australian explorers case; @Henrich2015]. -->
-<!-- In this domain, the relationship to be learned (i.e., between different ways of food processing and the poisonousness of the plant) is non-obvious and trial-and-error learning is costly (negative examples entail death).
--->
-
-<!-- Crucially, once acquired, such hard-won generalizations can be communicated among humans, something which other animals struggle to accomplish [cite tomasello apes something]. -->
-<!-- Generalizable knowledge can be inferred through demonstration, or in pedagogical contexts when ostensive cues are present [@Csibra].  -->
-<!-- By and large, however, language provides the most flexible and generative way to communicate generalizations.  -->
-
-<!-- A generalization provides a relation between a category and a property: It tells us to predict that property of future instances of the category [@HumeTHN]. -->
-<!-- Generalization can be described as a probability and inductive inference as a probabilistic model [@Tenenbaum2011]. -->
-<!-- From a very young age, children make strong inductive inferences from their experience in a way consistent with the Bayesian probability calculus [@Dewar2010; @Gelman1986; @Markman1989]. -->
-
-<!-- If generalizations can be described by predictive probabilities, it would stand to reason that the most direct way to communicate a generalization would be to convey probability.  -->
-<!-- Ironically, humans are very bad at describing and interpreting probabilities explicitly [@Tversky1974]. -->
-<!-- Rather than be a deficiency, however, the difficulty we have in understanding numerical descriptions of probability might reflect the flexible adaptivity of natural language to make vague or ambiguous that which shared context can be relied upon to guide interpretation [@Piantadosi2012].
--->
-<!-- If language has evolved in a way to make efficient the kinds of inductive inferences that are central to human cognition, we would expect the language of generalizations to be simple [c.f., @Leslie2008].
--->
-
-<!-- Indeed, generalizations in language (e.g., *Dogs are friendly*, *Mary smokes cigarettes*, *Yeast makes bread rise*) are among the simplest forms of compositional expressions.  -->
-<!-- Generalizations do not come in just one syntactic form: "*Dogs* are friendly", "*A library book* should be treated with respect", "*The contemporary foodie* seeks culinary experinces in menu-less restaurants and grandmothers' kitchens" [@Carlson1995; @NickelBlackwell; @sepGenerics].
--->
-<!-- Each of these statements has in common the fact that they predicate a property of a category and the properties themselves apply to instances of the category (unlike, e.g., *Dinosaurs are extinct* because being extinct is not a property that can be true of a particular dinosaur).
--->
-<!-- In this way, these statements exhibit *genericity*, or put another way, they convey generalizations. -->
-
-<!-- In this paper, we formalize the language of generalizations with the interest is deciding what makes a generalization in language *true or false*. -->
-<!-- How speakers convey generalizations and how listeners interpret them. -->
-
-<!-- We examine three case studies of generalizations in language: Generalizations about agents, objects, and events.  -->
-<!-- In Section 1, we introduce an information-theoric communicative theory of how generalizations are conveyed in language and flesh out the model's predictions alongside alternative models. -->
-<!-- In order to do so, we provide a unified mathematical framework for dealing with agents, objects, and events, casting each as a category over which generalization can occur. -->
-<!-- Our model predicts the endorsements of generalizations should vary with the (A) the probability of an instances having the property and (B) the prior distribution over the property probability (e.g., how likely instances of other categories are to have the property).
--->
-<!-- In Section 2, we introduce our empirical paradigm which we use to measure endorsement and interpretation of linguisitic generalizations, examining generalizations about *agents* in what is known as *habitual language* (e.g., "Mary smokes cigarettes.").
--->
-<!-- In Section 3, we extend our paradigm to generalizations about *events* (i.e., *causal language* e.g., "Yeast makes bread rise.") and experimentally manipulate participants' background knowledge, showing that prior beliefs about probabilities are causally related to endorsement and interpretation of generalizations.
--->
-<!-- In Section 4, we use our paradigm to address long-standing theoretical and empirical puzzles regarding generalizations about *objects*, so-called *generic language*.  -->
-<!-- We show our how model explains three known psychological puzzles surrounding generic language.  -->
-<!-- In all case studies, we provide formal comparison to simpler models and in all cases, find that only our communicative theory explains the patterns of empirical data. -->
-<!-- We conclude with a general discussion about the relationship of our theory to extant theories in the psychology, linguistics, and philosophy of genericity, and highlight the implications for modeling language acquisition, conceptual development, and other avenues of research that this framework opens.
--->
-
-<!-- the truth conditions of generalizations of events (so called *habitual language*) by manipulating the target propensity (A) while surveying a wide variety of events (which should induce variability in B).
--->
-<!-- In Section 3, we manipulate both (A) and (B) while testing the model on generalizations about causes (*causal language*). -->
-<!-- If our theory is truly a theory about communicating generalizations, it should be able to explain the known psychological puzzles surrounding *generic language* (generalizations about categories).
--->
-
-<!-- In stark constrast, a computational understanding of communicating generalizations is not well understood at all.  -->
-
-<!-- Gathering data and observing evidence, however, is costly.  -->
-<!-- The human problem of induction even displays a complex sensitivity to not only the type of data, but how the data was generated [@Gweon2010; @Shafto2012]. -->
-<!-- A learner cannot form all of her abstract knowledge through direct experience, however. -->
-<!-- Life is only so long, and you can only be in one place at a time. -->
-
-<!-- In this paper, we introduce a formal model for understanding the language of generalizations. -->
-<!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning.
--->
-<!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning).
--->
-<!-- We extend a rational model of communication --- the Rational Speech Act theory --- to be able to understand general statements that extend beyond the here-and-now. -->
-<!-- We provide a number of stringest tests of this theory to explain generalizations about categories, events, and causal forces.  -->
-
-<!-- How can generalizations in language have such flexible truth conditions while simultaneously carrying intuitive and, at times, very strong implications? -->
-<!-- This question has been investigated by psychologists, linguists, and philosophers since @Carlson1977. -->
-<!-- Here, we provide a unified formal theory of generalizations conveyed in language. -->
-<!-- We test theory on the preeminent case study of linguistic generalizations: generic language, or generalizations about categories. -->
-<!--  -->
-<!-- To be precise, we develop a computational model that describes pragmatic reasoning about the propensity required to assert the generaization.   -->
-<!-- We find that this formalism resolves known philosophical and empirical puzzles. -->
-<!--We also provide the first set of experimental results about linguistic generalizations about events and causal forces, so called *habitual* and *causal statements*.-->
-
-<!-- and find extreme flexibility in usage, which our model predicts.  -->
-
-<!-- In Section 2, we conduct a set of experiments to test the *truth conditions* of familiar generalizations about categories (generic statements), and find our model predicts key patterns in human judgments -->
-<!-- In Section 3, we conduct a set of experiments to test *interpretations* of novel generic sentences, again finding our model predicts human judgments with high quantitative accuracy. -->
-<!-- In Section 4, we begin to test the generality of the theory, examining the *truth conditions* of generalizations about events. -->
-<!-- In Section 5, we further probe our theory's generality, investing the *truth conditions* and *interpretations* of novel generalizations about causal forces.  -->
-<!-- In all cases, we provide formal comparison to simpler models and in all cases, find that only our communicative theory with an underspecified meaning function explains the pattern of human data.
--->
-<!-- We also find that the prior beliefs used in our model reflect conceptual structure, and this provides an understanding of the conceptual implications of generics. -->
-<!-- Finally, we investigate the underlying semantic scale in more detail, and find that the core meaning of generalizations in language depends in a crucial way on subjective beliefs, not mere frequency.
--->
-
-<!--
-Most would agree that \emph{Swans are white}, but certainly not every swan is.
-This type of utterance conveys a generalization about a category (i.e. \textsc{swans}) and is known as a generic utterance [@Carlson1977; @Leslie2008].
-Communicating generically about categories is useful because categories themselves are unobservable [@Markman1989].
-Knowledge about categories, while central to human reasoning, is tricky to acquire because categories themselves are unobservable [Markman1989}.
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are essential to the growth of conceptual knowledge [@Gelman2004] and how kinds are represented in the mind [@Leslie2008].
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and children as young as two or three understand that generics refer to categories and support generalization [@Cimpian2008].
-and though English and many other languages do not possess an unambiguous form devoted to generic meaning [@Behrens2000, @AlMalki2014].
-Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@GelmanEtAl2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010motivation].
-Despite their psychological centrality, apparent simplicity, and ubiquity, a formal account of generic meaning remains elusive.
-
-How can generics have such flexible truth conditions while simultaneously carrying strong implications?
-In this paper, we explore the idea that the core meaning of a generic statement is simple, but underspecified, and that general principles of communication may be used to resolve precise meaning in context.
-In particular, we develop a mathematical model that describes pragmatic reasoning about the degree of prevalence required to assert the generic.  
-We find that this formalism resolves the philosophical and empirical puzzles.
--->
-
-# Computational Framework
-
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties correspondingly also vary widely (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
-
-How does one come to learn $h$, the uncertainty that underlies an inductive inference about a member of a category having a property?
-One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
-But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
-For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Here, $P(d \mid h)$ is the observer's generative model of the observed data. 
-It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.
-
-Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
-Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
-How do we acquire these generalizations?
-For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
-
-<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
--->
-<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
-<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
--->
-<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
-
-<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
-<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
--->
-<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
-<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
--->
-
-<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
-<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
-<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
--->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
--->
-<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
-<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
-
-<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
-<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
--->
-<!-- \ndg{what is this par doing for us? delete?} -->
-<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
-<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
--->
-<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
--->
-<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
--->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-
-## Generalization from language
-
-If generalization from observations can be described as a predictive probability, then it seems natural to consider that same metric to be central to the semantic content of an utterance that conveys a generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
-Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: An utterance is true if the underlying quantity is above a threshold.
-For generalizations, then, the threshold would apply to the *feature-probability* $h$:^[
-We emphasize that our account is based on an agent's subjective probability $h$.
-The literature on generic language has often examined *prevalence*, or the proportion of members of a category with the property, as the primary quantitative metric that could relate to generic meaning (in addition to *cue validity*, described below).
-A Bayesian agent, however, would only use prevalence as a way to update her prior knowldege $P(h)$ to form a posterior probability for future use.
-Thus, we consider the semantic content of a generalization to be related to probability, not necessarily prevalence.
-]
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-
-### Resolving underspecification
-
-What threshold $\theta$ should be used for the generalization?
-We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
-
-\begin{eqnarray}
-Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
-We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
-The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}\label{eq:delta}
-\end{eqnarray}
-
-Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
-
-### Endorsement model
-
-The above model determines how $\theta$ should be resolved in context.
-Now, how do we decide when a statement conveying a generalization is true or not?
-To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
-The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
-
-\begin{equation} 
-E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
-\label{eq:S1}
-\end{equation}
-
-Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
-
-The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
-Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
-$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
-]
-The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
-This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]
-
-\begin{equation} 
-U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
-\end{equation}
-
-Thus, Eq.
-\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
-Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
-
-The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
-
-Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
-The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
-However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
-
-<!-- In Bayesian statistics, when there is uncertainty about latent parameter, one specifies a prior distribution over the parameter and reasons backward about the parameter's likely value given any data.
--->
-<!-- In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
--->
-<!-- Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context *a priori*: $P(\theta) = \text{Uniform}(0, 1)$.
--->
-
-<!-- \ndg{i wonder if we shoud start with the speaker / endorsement idea? introducing the listener and semantics might be more natural then.} -->
-
-<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
-influence the meaning of a generic statement via their influence on subjective probability.
--->
-<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts].
--->
-
-<!-- \begin{eqnarray} -->
-<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
-<!-- \end{eqnarray} -->
-
-### The feature-probability prior and model simulations
-
-<!-- $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance. -->
-<!-- $P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$. -->
-<!-- The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
--->
-<!-- In our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$. -->
-<!-- This is a different approach than in conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013], but provides a potential bridge, as explored later. -->
-
-The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
-We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
-We implemented the models in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
-
-```{r simluationsModel, eval = T, cache = T}
-l0.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
-'
-
-priorNames <- c(
-  "doesntEatPeople", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria",
-  "hasSpots"
- # "areSick"
-  )
-priorShapes <- list(
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-all.simulations <- data.frame()
-for (p in priorNames){
-  for (u in c("generic")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
-    )
-  }
-  #print(p)
+data.path <- "data/generics/endorsement/"
+substrRight <- function(x, n){
+  substr(x, nchar(x)-n+1, nchar(x))
 }
@@
 
-```{r simluationEndorsementModel, eval = T, cache = T}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
+# Appendix: Bayesian Data Analysis
 
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
+## Case Study 1: Generic language
 
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
+### Modeling feature-probability priors
 
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.mix[0];
-var priorParams = data.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-var alpha = 2
-
-var endorser = function(featureProb){
-  Infer({model: function(){
-    var endorsement = sample(utterancePrior)
-    var L0 = marginalize(listener0(endorsement), "state_Posterior")
-    factor(alpha * L0.score(featureProb))
-    return endorsement
-  }})
-}
-
-probability(endorser(data.featureProb[0]), "generic")
-'
-
-exampleGenerics <- c(
-  "sharksDontEatPeople",
-  "robinsAreFemale", 
-  "robinsLayEggs", 
-  "kangaroosHaveSpots",
-  "dogsBark",
-  "mosquitosCarryMalaria"
-  )
-exampleParameters <- list(
-  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
-  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
-  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
-  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
-  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
-)
-
-s1.simulations <- data.frame()
-for (p in exampleGenerics){
-
-    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
-    s1.simulations <- bind_rows(s1.simulations,
-                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
-
-}
-
-```
-
-```{r}
-s1.simulations.relabeled <- s1.simulations %>%
-  mutate(example = factor(example, 
-                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-  #geom_jitter(width = 0.1, shape = 21, size = 5)+
-  #ylab("Human endorsement probability")+
-  #xlab("Frequency of target")+
-  geom_label_repel(data = s1.simulations.relabeled, 
-                   aes( label = example, fill = example),
-                       color = 'white',
-    box.padding = unit(0.0, "lines"),
-    #point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37')+
-  scale_fill_solarized()+
-  scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
-  coord_fixed(ratio = 1)+
-  guides(fill = F)+
-  ylab("Endorsement model prediction")+
-  xlab("Hypothesized feature-probability")
-
-```
-
-```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
-all.simulations.refactored <- all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                                c( "Prior_generic", "Posterior_Generalization_generic"),
-                                labels = c( "Prior/Silence", "Generalization")
-                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
-                             ),
-         PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
-                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         )
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability h") +
-    ylab("Scaled prior probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-```
-
-```{r simulations, fig.cap = "Model behavior.
-Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
-grid.arrange(l0.simulations.distributions, 
-             s1.simulations.scatter, ncol = 3,
-             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
-
-```
-
-These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-]
-
-Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
-The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
-The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
-]
-The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
-
-How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
-For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
-The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
-"Robins lay eggs", however, has a lot of informational content.
-
-Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
-Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
-
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the feature-probability priors $P(h)$.
-In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
-
-# Case Study 1: Generic Language
-
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
-It has been the premier case study of generalization in language because of its similarity to quantified statements (e.g., "Most dogs bark").
-Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
-
-We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
-"Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
-1a).
-
-We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
-Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
-\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
-To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
-
-## Experiment 1a: Generic endorsements
-
-In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
-The goal of this study is to observe a range of endorsements for generic statements about animal categories.
-
-#### Method
-```{r eval = F}
-d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "naturalGenerics-trials-formatted.csv", sep = ""))
-
-# write.csv(
-#   left_join(
-#   d1 %>%
-#     mutate(sentence = as.character(sentence),
-#            sentence = gsub('&quotechar', '', sentence),
-#          sentence = gsub('lyme', 'Lyme', sentence)),
-#   unique(d2 %>%
-#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-#     select(Category, Property, sentence))
-# ), file = paste(project.path, "data/generics/endorsement/",
-#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
-```
-
-```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(col = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup()
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
-  filter(item %in% d.gen.endorse.bayes$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(col = "prevalence")
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- left_join(
-  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
-) %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
-  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("Human generic endorsement")+
-  xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'feature probability',
-                               ticks = F))+
-  theme(legend.position = 'bottom')
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
-```
-
-##### Participants
-
-We recruited 100 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
-The experiment took about 3 minutes and participants were compensated \$0.35.
-
-##### Procedure and materials
-
-Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
-As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
-
-#### Results
-
-```{r generic-endorsement-manipulationcheck}
-# MHT's truth judgments of sentences
-# t --> true; f --> false; i --> indeterminate/uncertain
-all.sentences <- list("Cardinals are red." = "t",
- "Ducks have wings." = "t",
- "Kangaroos have pouches." = "t",
- "Kangaroos have spots." = "f",
- "Leopards are juvenile." = "i",
- "Leopards have spots." = "t",
- "Leopards have wings." = "f",
- "Lions are male." = "i",
- "Lions have manes." = "t",
- "Lions lay eggs." = "f",
- "Mosquitos attack swimmers." = "i",
- "Mosquitos carry malaria." = "t",
- "Mosquitos dont carry malaria." = "f",
- "Peacocks dont have beautiful feathers." = "f",
- "Peacocks have beautiful feathers." = "t",
- "Robins are female." = "i",
- "Robins carry malaria." = "f",
- "Robins lay eggs." = "t",
- "Sharks are white." = "i",
- "Sharks attack swimmers." = "t",
- "Sharks dont attack swimmers." = "f",
- "Sharks have manes." = "f",
- "Sharks lay eggs." = "i",
- "Swans are full-grown." = "i",
- "Swans are white." = "t",
- "Ticks carry Lyme disease." = "t",
- "Ticks dont carry Lyme disease."= "f",
- "Tigers dont eat people."= "f",
- "Tigers eat people." = "t",
- "Tigers have pouches."= "f")
-
-mht.truth.judgments <- data.frame(sentence = names(all.sentences),
-           truth_judgment = as.vector(unlist(all.sentences)))
-
-d.gen.endorse.manipulation.check.bayes <- left_join(
-  left_join(
-    d.gen.endorse, 
-    d.gen.endorse.catch %>% select(workerid, pass)
-    ),
-  mht.truth.judgments ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(truth_judgment) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
-
-true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
-true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
-true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]
-
-false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
-false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
-false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]
-
-uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
-uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
-uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
-
-```
-
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
-Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
-
-## Experiment 1b: Feature-probability prior elicitation
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
-Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
-Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
-].
-
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-
-### Method
-
-#### Participants
-
-We recruited 60 participants over Amazon MTurk.  
-3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-#### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
-A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
-Eight property--columns appeared in the table.
-
-This whole procedure was repeated two times (two trials).
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
-
-### Bayesian data analysis
-
-In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
-We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
-\text{has wings}).
-
-Formally, we assume the prior data (analzyed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
+In Case Study 1 (Generic Language), we elicited the prevalence of features for many different categories. 
+These can be thought of as *samples* from the feature-probability prior distribution. 
+Formally, we assume the prior data (analyzed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
 The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
@@
 
-### Results
-
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
 To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
@@
 
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
-There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
-One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
+## Jointly modeling referent feature-probability, feature-probability priors, and generic endorsements
 
-<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
--->
-<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
-load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
-           aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
-    xlab("Feature-probability") +
-    ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
-## Endorsement model comparison
-
-To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
-1b), from which the interpreter model infers likely thresholds for the generic.
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
-As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of the uncertain-threshold hypothesis.
-
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:10){
-
-  d.cv.bsample <- d.cv %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.gen.cv.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped %>%
-      group_by(property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
-# 
-# d.cv.bootstrapped %>%
-#   group_b
-
-# need to filter by items specified with endorsement
-# d.gen.cv.summary <- left_join(
-#   d.target.items %>% select(-sentence),
-#   d.cv %>%
-#     rename(category = response) %>%
-#     group_by(property) %>%
-#     mutate(n = n(),
-#            item = paste(category, property)) %>%
-#     filter(item %in% d.target.items$item) %>%
-#     group_by(category, property) %>%
-#     summarize(mentions = n(),
-#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-#               prop = mentions / trials)
-#   ) %>%
-#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prev_mean = mean,
-             sentence = item,
-             prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper) %>%
-      ungroup() %>%
-      mutate(sentence = gsub('[.]', '', sentence))
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prev_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.prev.cue.uniq <- unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, 
-    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
-  ))
-
-d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_lower,
-         cv_mean = cv_ci_lower)
-d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_upper,
-         cv_mean = cv_ci_upper)
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
-
-r2.gen.n <- length(d.gen.endorse.bayes$sentence)
-r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)
-
-r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
-mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)
-
-intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))
-
-d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
-  filter(
-    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
-    (prev_mean < intermediate.prev.quantiles[["76%"]])
-)
-r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)
-
-r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
-```
-
-### Baseline models
-
-#### Referent feature-probability
-
-From the feature-probability prior data (Expt.
-1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
-
-However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
-
-#### Cue validity and referent feature-probability
-
-##### Model specification
-
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* thus captures the distinctiveness of the feature for the category. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
-In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
-
-##### Results
-
-A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of a simple model based on cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A simple metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
-
-### Information-theoretic endorsement models
-
-The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
-Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
-We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
-We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
-
-##### Model specification
-
-For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
-Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-This corresponds to the more general form of the model described in a footnote in the model section. 
-For these data, the predictions of these two models are nearly identical.
-]
-(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
+1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
+1a \& b (Figure \ref{fig:genericsModelDiagram}).
+For the parameters of the feature-probability prior distributions, we use the same priors described in Expt.
+1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
+We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
 
@@
 ```
-
-To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the feature-probability prior distributions, we use the same priors described in Expt.
-1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
-
-#### Fixed-threshold  model
-
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
-
-```{r generic-RSAmodels, fig.width = 8}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
-
-# m.samp <- data.frame()
-# m.samp.fixed <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-#   
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-#   }
-# 
-# save(m.samp,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.samp.fixed,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.gen.rsa.generics <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-r2.gen.rsa.fixed <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-mse.gen.rsa.generics <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-mse.gen.rsa.fixed <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression,
-  left_join(
-    m.gen.endorse.rsa %>% 
-      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-      select(sentence, Property, Category, prev_mean, cv_mean)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( "some_model",
-                                      "generics_model",
-
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c("Fixed semantics model",
-                                 "Uncertain semantics model",
-
-                                 "Feature-probability alone",
-                                 "Cue validity + Feature-probability"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.4)+
-  geom_errorbarh(alpha = 0.4)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human generic endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  #theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
-    filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_label_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
-    ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-```
-
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
-Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
-Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
-These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
-
-We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
-Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-The model fails to distinguish any of the generic sentences because they are all somewhat true. 
-All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
-
-The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
-For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
-Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
-This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
-The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
-
-\mht{Outfit fixed-threshold model with noise parameter?}
-
-### Uncertain threshold RSA model
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-
-To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
-It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
-"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
-
-## Discussion
-
-Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-This evidence is correlational in nature, however.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
-# Case Study 2: Habitual Language
-
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
-Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
-While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
-]
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
-In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
-We separately measure endorsements under the same contexts (Expt.
-2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
-## Experiment 2a: Measuring the feature-probability prior for events
-
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
-To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
-The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
-This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
-
-### Method
-
-#### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-#### Materials
-
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
-
-#### Procedure
-
-For each event, participants were asked two questions, with associated dependent measures:
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
-\end{enumerate}
-
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
-After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
-They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-They did this to test their understanding and attention for each of the two questions.
-
-For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
-<!--   \caption{ -->
-<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
-<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
-<!--   Actual frequency noted on x-axis for examples (left). -->
-<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
-<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
-<!--   } -->
-<!--   \label{fig:tjScatters} -->
-<!-- \end{figure*} -->
-
-<!-- #### Data preprocessing -->
-
-```{r habituals-prior-data}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
-
-d.hab.priors <- d.hab.priors %>%
-  mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women),
-         item = as.character(item),
-         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
-  rowwise() %>%
-  mutate(
-    mixture_male = nPersons_men / comparisonNum_men,
-    mixture_female = nPersons_women / comparisonNum_women,
-    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
-                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
-                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
-                   ifelse(comparisonTime_men == "5 years", 
-                          nInstances_men / (5*365), -99)))),
-    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
-                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
-                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
-                   ifelse(comparisonTime_women == "5 years", 
-                          nInstances_women / (5*365), -99)))),
-    annualRate_male = dayRate_male * 365,
-    annualRate_female = dayRate_female * 365
-  )
-
-d.hab.priors.filtered <- filter(d.hab.priors, 
-       !(
-         (mixture_male == 0) ||   (mixture_female == 0) ||   
-           (dayRate_male == 0) ||   (dayRate_female == 0)  )
-       )
-```
-
-```{r habituals-prior-forwardsample}
-# this is basically bootstrapping and combining using the structured model
-
-d.hab.priors.samples <- data.frame()
-for (i in 1:10){
-
-  d.hab.priors.samples <- bind_rows(
-    d.hab.priors.samples,
-    d.hab.priors.filtered %>% 
-    select(workerid, item, starts_with("annualRate"), 
-           starts_with("mixture")) %>%
-    rowwise() %>%
-    mutate(
-      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
-       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
-       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
-       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
-       ) %>%
-    select(item, freq_male, freq_female) %>%
-    gather(gender, val, freq_male, freq_female) %>%
-  mutate(gender = gsub("freq_", "", gender))
-  )
-}
-
-```
-
-```{r habituals-prior-model}
-hab.prior.bda.model <- '
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var model = function(){
-	var mixtureParams = {
-		male: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    },
-		female: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    }
-	};
-
-	var mixtureShapes = {
-		male: betaShape(mixtureParams.male),
-		female: betaShape(mixtureParams.female)
-	};
-
-	mapData({data: data.mixture}, function(d){
-    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
-     // display(Beta(mixtureShapes[d.gender]).score(d.val))
-		observe(Beta(mixtureShapes[d.gender]), d.val)
-	})
-
-	var stableFrequency = {
-		male: {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		},
-		female: {
-			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		}
-	}
-
-	mapData({data: data.frequency}, function(d){
-    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
-        display(JSON.stringify(d)) : null
-    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
-		observe(Gaussian(stableFrequency[d.gender]), d.logval)
-	})
-
-	var existenceProb = {
-		male: beta(mixtureShapes.male),
-		female: beta(mixtureShapes.female)
-	};
-
-	var freqWhenPresent = {
-		male: gaussian(stableFrequency.male),
-		female: gaussian(stableFrequency.female)
-	}
-
-  var marginalFreq = {
-    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
-    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
-  }
-
-  return {
-    mix_mean_male : mixtureParams.male.g,
-    mix_mean_female : mixtureParams.female.g,
-    mix_samplesize_male : mixtureParams.male.d,
-    mix_samplesize_female : mixtureParams.female.d,
-    stableFreq_mean_male : stableFrequency.male.mu,
-    stableFreq_mean_female :stableFrequency.female.mu,
-    stableFreq_sd_male : stableFrequency.male.sigma,
-    stableFreq_sd_female :stableFrequency.female.sigma,
-    marginalFreq_NA_male: marginalFreq.male,
-    marginalFreq_NA_female: marginalFreq.female
-  }
-}
-'
-```
-
-```{r habituals-prior-model-run, cache = T}
-items <- levels(factor(d.hab.priors.filtered$item))
-n_samples <- 500
-rs.habituals.bda.prior <- data.frame()
-
-for (it in items){
-
- df.prior.toPass <- list(
-   frequency = d.hab.priors.filtered %>%
-      filter(item == it) %>%
-      select(item, starts_with("annualRate")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("annualRate_", "", gender),
-             logval = log(val)),
-   mixture = d.hab.priors.filtered %>% 
-      filter(item == it) %>%
-      select(item, starts_with("mixture")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("mixture_", "", gender)) %>%
-      rowwise() %>%
-      mutate(val = ifelse(val == 1, 0.9999, 
-                          ifelse(val == 0, 0.000001, val)))
-  )
-
-  rs <- webppl(program_code = hab.prior.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.prior.toPass,
-       data_var = "data")
-
-  rs.habituals.bda.prior <- bind_rows(
-    rs.habituals.bda.prior, 
-    rs %>% 
-      mutate(item = it) %>% 
-      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
-  )
-}
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
-
-example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
-                       "climbs mountains", "hikes", "runs", 
-                       "wears a suit", "wears a watch", "wears socks", 
-                       "writes poems", "goes to the movies", "plays the banjo"
-                       )
-
-rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
-  filter(Parameter == "mean") %>%
-  group_by(Variable, Gender, item) %>%
-  summarize(MAP = estimate_mode(value),
-            cred_upper = hdi_upper(value),
-            cred_lower = hdi_lower(value)) %>%
-  ungroup()
-rs.habituals.bda.prior.summary.wide <- left_join(
-  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
-    select(-Variable) %>%
-    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
-  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
-    select(-Variable) %>%
-    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
-)
-
-figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) %>%
-ggplot(.,
-       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
-            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = category))+
-    scale_shape_manual(values=c(21,22))+
-  #scale_color_solarized()+scale_fill_solarized()+
-  scale_fill_brewer(palette='Set1')+
-
-  geom_point(size=4, inherit.aes = F, 
-             aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            shape = Gender),  alpha = 0.9)+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  xlab("% of Americans who have DONE ACTION")+
-  ylab("Log Frequency of DOING ACTION")+
-  #scale_
-  coord_fixed(ratio = 1/8)+
-  theme(legend.title = element_text(hjust=0),
-        legend.position="bottom",
-        legend.direction="horizontal") +
-        scale_y_continuous(limits = c(-1.5, 6.5), 
-                     breaks = c(0, 2.5, 4, 5.9),
-                     labels = c("annually", "monthly", "weekly", "daily"))+
-  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
-                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-```
-
-```{r habituals-prior-model-forwardSample}
-rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value)
-
-rs.habituals.bda.prior.samples <- data.frame()
-for (i in 1:1){
-  rs.habituals.bda.prior.samples <- bind_rows(
-    rs.habituals.bda.prior.samples,
-    rs.habituals.bda.prior.spread %>%
-    rowwise() %>%
-    mutate(
-      a = mix_mean * mix_samplesize,
-      b = (1 - mix_mean) * mix_samplesize,
-      theta = rbeta(n = 1, shape1 = a, shape2 = b),
-      stable = rbinom(n = 1, size = 1, prob = theta),
-      logannualRate = ifelse(stable == 1, 
-                             rnorm(n = 1, 
-                                   mean = stableFreq_mean, 
-                                   sd = stableFreq_sd), -5),
-       annualRate =  exp(logannualRate)
-    )
-  )
-}
-```
-
-```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
-2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
-
-figure.habituals.priors.marginals <- bind_rows(
-  d.hab.priors.samples %>% 
-    mutate(src = 'data', 
-           val = log(val)),
-  rs.habituals.bda.prior.samples %>%
-    rename(gender = Gender, val = logannualRate) %>%
-    select(gender, item, val) %>%
-    mutate(src = 'model')
-  ) %>%
-  filter(item %in% example.habituals,
-         src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals)) %>%
-ggplot(. , aes( x = val, color = gender))+
-  geom_density(size = 0.8, aes( y = ..scaled.. ))+
-  facet_wrap(~item, nrow = 4)+
-  scale_color_solarized()+
-  xlab("Frequency")+
-  ylab("Scaled prior density")+
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.12),
-        axis.text.x = element_text(angle = 90))+
-    scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
-2a).
-Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on rates from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-### Data analysis and results
-
-All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-We built a Bayesian data analysis model for this prior elicitation task.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-First, it smooths effects that are clearly results of the response format.
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
-
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate or frequency with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
-
-<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
-<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
-<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
-<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
-<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-## Experiment 2b: Endorsing habitual statements
-
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Procedure and materials
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
-<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
-
-### Results
-
-```{r habituals-prior-mixture-summarize}
-d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
-  select(item, starts_with("mixture_")) %>%
-  gather(key, value, -item) %>%
-  group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
-  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
-  rowwise() %>%
-  mutate(
-    annualRate = annualRates[[as.character(time_period)]]*n_instances,
-    logAnnualRate = log(annualRate)
-  )
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
-                       "goes to the movies_month", "smokes cigarettes_month")
-fig.habituals.endorsement.vs.freq <- 
-  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21, size = 5)+
-  ylab("Human endorsement probability")+
-  xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
-                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
-                    filter(sentence %in% example.habituals), aes( label = habitual ),
-                       color = 'black', fill = 'white',
-    box.padding = unit(0.35, "lines"),
-    point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
-  scale_x_continuous(limits = c(-1,6), 
-                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
-                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        legend.position = "bottom")+
-  coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F))
-```
-
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.', eval=F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
-r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
-
-```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.freq.mix.uniq <- unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, 
-    mixture, mix_low, mix_high
-  ))
-
-d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_low)
-
-d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_high)
-
-d.hab.endorse.regression.freq <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
-      prediction_lower = prediction,
-      prediction_upper = prediction,
-      src = "regression_freq"
-      )
-)
-
-r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
-
-r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
-  filter(logAnnualRate < 1.1)
-
-r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
-
-r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
-d.hab.endorse.regression.freq.mix <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
-      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
-      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
-      src = "regression_freq_distinct"
-      )
-)
-
-r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-model_prefix <- "results-habituals-jointModel-S1-"
-
-# m.hab.samp <- data.frame()
-# m.hab.fixed.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
-#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-# 
-# }
-# 
-# save(m.hab.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.hab.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "habituals_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.habituals.rsa.fixed <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.fixed <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.uncertain <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)
-
-r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)
-
-r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression,
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, logAnnualRate, mixture)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "some_model",
-                                      "habituals_model",
-                                      "regression_freq", 
-                                      "regression_freq_distinct"
-                                     ),
-                      labels = c(
-                                 "Speaker model - fixed semantics",
-                                 "Speaker model - uncertain semantics",
-                                 "Referent frequency alone", "Distinctiveness + referent frequency"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.15)+
-  geom_errorbarh(alpha = 0.15)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r habituals-simulation-model}
-l0.hab.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
-
-var targetUtterance = "habitual";
-
-var roundTo3 = function(x){
-  return Math.round(x * 10000) / 10000
-}
-
-var lowerBound = -5, upperBound = 10, binWidth = 0.5;
-
-var stateBins =  _.range(
-  lowerBound, upperBound, binWidth
-)
-
-var thetaBins = map2(function(b1, b2){
-  var diff = Math.abs(b2 - b1) / 2;
-  return roundTo3(diff+ b1);
-}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state> _.min(thetaBins):
-         true
-}
-
-var priorParams = data.priorParams[0];
-
-var stable_female_params = betaShape({
-  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
-})
-
-var stable_male_params = betaShape({
-  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
-})
-
-// this marginalizes out the mixture parameter
-var statePrior = Infer({model: function(){
-  var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ? // 
-    flip(
-        categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_female_params), b) + Number.EPSILON
-          }, probBins )
-        })
-    ) ? // stable female distribution
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) : // unstable female distribution
-    _.min(stateBins) : 
-    flip(        
-      categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_male_params), b) + Number.EPSILON
-          }, probBins )
-      })
-    ) ? 
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) :
-    _.min(stateBins)
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:-5}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:-5})
-   var state_prior = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:lowerBound}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:lowerBound})
-    var theta = uniform(lowerBound, upperBound)
-    condition(
-      (utterance == "habitual") ? 
-      state > theta : 
-      (state > _.min(lowerBound))
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
-
-continuousListener0(data.utt[0])
-'
-```
-
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
-
-m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
-  filter(type == "prior", B %in% example.habituals.actions) %>%
-  rename(action = B, variable = C, gender = D, parameter = E) %>%
-  group_by(action, variable, gender, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(action, variable, gender, parameter, MAP) %>%
-  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
-  select(-variable, -gender, -parameter) %>%
-  spread(param, MAP)
-
-hab.listener.predictions <- data.frame()
-
-for (p in example.habituals.actions){
- priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
-
- inputData = list(priorParams = priorParams,
-                  utt = "habitual")
-
- l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
-
- hab.listener.predictions <- bind_rows(
-   hab.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
-   )
-
-}
-
-# m.gen.fullmodel.target.prevalence <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   group_by(param, property, category) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-# m.gen.speakerBeliefs <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   mutate(Sentence = paste(category, property)) %>%
-#   filter(Sentence %in% example.generics)
-
-# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-# gen.inset.distributions <- bind_rows(
-#   gen.listener.predictions %>%
-#     mutate(category = NA),
-#   m.gen.speakerBeliefs %>%
-#     select(property, val) %>%
-#     rename(value = val) %>%
-#     mutate(Parameter = "speakerBeliefs")
-# )
-# 
-# 
-# category.text.labels <- data.frame(property = c("dont eat people", 
-#                       "carry malaria", "lay eggs",  "are female", "have spots"),
-#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Habitual")),
-         action = fct_relevel(action,
-                                "climbs mountains", "hikes", "runs",
-                              "goes to the movies", "smokes cigarettes"
-                              ) ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~action, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
-  #scale_linetype_manual(values = c(3, 4, 1))+
-  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
-      scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-```
-
-```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
-Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
-These distributions are inferred using both data sources from Expts.
-2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
-grid.arrange(fig.habituals.endorsement.vs.freq, 
-             habituals.endorsement.models,
-             habituals.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the referent character.
-<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
-
-<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
-Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
--->
-
-<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
-<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
--->
-<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
--->
-<!-- We see no appreciable differences in endorsements for the two genders.  -->
-<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
-<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
-
-#### Referent frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
-This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-#### Distinctiveness and referent frequency
-
-In the prior elicitation task (Expt.
-2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
-With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
-
-```{r habituals-distinctiveness-counterexamples}
-
-format_endorsment_ci <- function(
-  df, estimate = "MAP_h", low = "low",
-  high = "high", sigfigs = 2){
-  return(paste(
-    round(df[[1,estimate]], sigfigs),
-    " [",
-    round(df[[1,low]], sigfigs),
-    ", ",
-    round(df[[1,high]], sigfigs),
-    "]", sep = ""))
-}
-
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
-
-movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
-                                                        time_period == "year"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
-
-banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
-                                                        time_period == "2 years"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-```
-
-We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture some of the subtle sensitivities in endorsments.
-For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold RSA model
-
-The above regression models are too rigid to explain the flexibility in habitual endorsements. 
-Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
-Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
-To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
-
-We used the speaker model $S_1$ (Eq.
-\ref{eq:S1}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.
-2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
-The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
-As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
-2b.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
-
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
-Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
-\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
-The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
-The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
-Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
-
-Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
-With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
-Thus, this model makes the same predictions for different target frequencies in the same event.
-For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.
-
-#### Uncertain-threshold RSA model
-
-We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-
-### Discussion
-
-In Expt.
-2b, we manipulated the event type (e.g., drinks coffee vs.
-beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
-year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
-
-Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
-The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
-
-Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
-
-<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
-
-<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
--->
-
-<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
-<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
-<!--   Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
--->
-<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
-<!--   \label{fig:tj3} -->
-<!--   \vspace{-7pt} -->
-<!-- \end{figure*} -->
-
-## Experiment 2c: Measuring predictive frequency
-
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
-       aes(x=logAnnualPastRate,
-                              y = mean,
-                              ymin = ci_lower, ymax = ci_upper,
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
-  scale_shape_manual(values=c(21,22,23))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-
-fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
-  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
-                 fill=condition, shape=condition,
-                 xmin = future_lower, xmax=future_upper,
-                 ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.8)+
-  geom_errorbarh(alpha=0.8)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 1, size = 4)+
-  xlab("Predicted frequency (log scale)")+
-  ylab("Human habitual endorsement")+
-  scale_x_continuous(limits = c(-4.2,7.2), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=11.4)+
-  scale_fill_solarized()+
-  guides(fill = F, shape = F)+
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-    legend.position="bottom",
-    legend.direction="horizontal"
-    )
-
-```
-
-```{r habituals-predictive-rsa}
-n_chains <- 3
-# n_samples <- 500000
-# burn <- n_samples / 2
-# lg <- 150
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 50
-
-m.hab.pred.samp <- data.frame()
-m.hab.past.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-
-  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "targetH_past-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-
-#}
-# 
-# 
-# # 
-# save(m.hab.pred.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# # # 
-# save(m.hab.past.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
-
-m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorsement <- m.hab.pred.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.predictive.endorsement
-  ) %>%
-    mutate(src = "predictive_model"),
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.pastmodel.endorsement
-  ) %>%
-    mutate(src = "past_model")
-)
-
-r2.habituals.rsa.past <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.past <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.predictive <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.predictive <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
-
-habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - past frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-
-habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  #guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-#habituals.predictive.predictive.model
-```
-
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
-grid.arrange(
-  arrangeGrob(
-    fig.hab.freq.predictive.vs.past, 
-    fig.hab.endorse.vs.predfreq, 
-    habituals.predictive.past.model, 
-    habituals.predictive.predictive.model + theme(legend.position="none"),
-    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
-legend_b, nrow=2,heights=c(8, 1))
-
-#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 2c.
-The only difference from Expt. 2c is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-
-When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
-], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
-
-We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
-The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
-
-We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
-Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
-The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
-
-<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
-<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
-<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
-<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
-<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
-This may be due, in part, to an effect of the experimental context on participants:
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
-## Discussion
-
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
-2a).
-We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
-By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
-In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
-Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
-
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2d).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
-
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
-Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
-
-# Case Study 3: Causal Language
-
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
-
-Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
-In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
-<!-- [Gerstenberg] -->
-Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
-Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
-
-Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
-
-In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
-
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
-In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 3a: Manipulating the feature-probability priors for causes
-
-In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our feature-probability prior manipulation.
-
-<!-- examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present. -->
-<!-- We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains. -->
-
-<!-- People have theories about how different casusal systems work.  -->
-<!-- Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force.  -->
-<!-- If the experiment is repeated exactly, we would expect the same results. -->
-<!-- In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't.  -->
-<!-- Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
--->
-
-### Method
-
-```{r causal-priors-data}
-d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
-                           sep= ""))
-
-n.subj.cas <- length(unique(d.cas.priors$workerid))
-
-ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-```
-
-```{r causal-priors-runModel, cache = T}
-causal.distributions <- levels(factor(d.cas.priors$distribution))
-p <- causal.distributions[1]
-m.cas.marginal.prevalence <- data.frame()
-m.cas.endorse.priors.summary <- data.frame()
-
-for (p in causal.distributions){
-  priorData <- 100*filter(d.cas.priors, distribution == p)$response
-
-  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
-
-  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
-    spread(Parameter, value) %>%
-    rowwise() %>%
-    mutate(
-      a = g * d,
-      b = (1 - g) * d,
-      stable = rbinom(n = 1, size = 1, prob = phi),
-      prevalence = ifelse(stable == 1, 
-                             rbeta(n = 1, shape1 = a, shape2 = b),
-                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
-      distribution = p
-    )
-  )
-
-  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
-                                            m.cas.endorse.priors %>% 
-                                              mutate(distribution = p) %>%
-                                              group_by(distribution, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-}
-
-```
-
-#### Participants
-
-We recruited `r n.subj.cas` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average `r ave.minutes.cas` minutes and participants were compensated \$0.50 for their work.
-
-<!-- The different kinds of system are described in more detail below. -->
-<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->
-
-#### Procedure
-
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
-
-In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
-The story for the "sleepy animals" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. 
-Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-The results are shown below:
-\end{quotation}
-
-Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
-
-Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
-
-#### Materials
-
-Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
-The cover story for the "tall plants" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
-Your team runs experiments trying to make feps grow tall with different fertilizers. 
-The results are shown below:
-\end{quotation}
-
-Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
-In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
-
-```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-4 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3, eval = F}
-sample.dists <- bind_rows(
-  data.frame(
-    dist = "rare weak",
-    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common weak",
-    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
-  ),
-  data.frame(
-    dist = "rare deterministic",
-    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common deterministic",
-    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
-  )
-) %>%
-    mutate(Distribution = factor(dist, 
-                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak")))
-
-figure.causals.priors <- bind_rows(
-  sample.dists %>%
-    mutate(src = "stimuli") %>%
-    select(-dist),
-  m.cas.marginal.prevalence %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
-    mutate(Distribution = factor(distribution, 
-                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))) %>%
-    select(Distribution, prevalence) %>%
-    mutate(src = 'model') %>%
-    rename(x = prevalence)
-) %>%
-  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
-                ))+ 
-  geom_density( adjust = 1.3, 
-               size = 1.2,
-               aes( y = ..scaled..))+ #
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_fill_solarized()+scale_color_solarized()+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0.1, 0.4))+
-  scale_linetype_manual(values = c(2, 1))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
-  guides(fill = F, color = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal')
-```
-
-```{r s1-model}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-var alpha = 2;
-var mixture = data.prior[0].phi;
-var priorParams = betaShape(data.prior[0]);
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var speaker1 = function(state) {
-  Infer({model: function(){
-    var utterance = sample(utterancePrior);
-    var listener_posterior = listener0(utterance);
-    factor(alpha * listener_posterior.score(state))
-    return utterance
-  }})
-}
-
-probability(speaker1(data.state[0]), "generic")
-'
-```
-
-```{r causal-endorsement-predictions, cache = T, eval = F}
-causal.priorParams <- m.cas.endorse.priors.summary %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           Parameter != 'marginalPrevalence') %>%
-  select(distribution, Parameter, MAP) %>%
-  spread(Parameter, MAP)
-experimental.frequencies <- c(0.2, 0.7)
-causal.endorsement.predictions <- data.frame()
-for (p in causal.priorParams$distribution){
-  for (s in experimental.frequencies){
-
-    inputData = list(prior = filter(causal.priorParams, distribution == p), 
-                     state = s)
-
-    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
-
-    causal.endorsement.predictions <- bind_rows(
-      causal.endorsement.predictions,
-      data.frame(state = s, distribution = p, prob = s1.rs)
-    )
-  }
-  print(p)
-}
-```
-
-<!-- #### Materials  -->
-
-<!-- The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model. -->
-<!-- Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
--->
-<!-- So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.  -->
-
-<!-- A second dimension of man ipulation corresponds to the extent to which *determinism* is expected in the domain.  -->
-<!-- For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.  -->
-
-### Results
-
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
-These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
-We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
-
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
-
-d.cas.priors %>%
-  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
-      mutate(Distribution = factor(distribution, 
-                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>% 
-ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 0.8, alpha =0.8, 
-               size = 1.2,
-               aes( y = ..scaled..))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
-```
-
-### Model predictions
-
-... run RSA model using fixed parameters and MAP estimates of these priors ?
-
-## Experiment 3b: Endorsing Causal Language
-
-In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-
-### Method
-
-Most of the experiment was identical to that of Experiment 3a.
-
-```{r causal-endorsement-data}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
-ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-
-n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-```
-
-#### Participants
-
-We recruited `r n.subj.cas.endorse` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 3a. 
-The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 3a.
-Phase 1 of the experiment was identical to that of Experiment 3a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
-Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Partipants responded by either clicking "Yes" or "No".
-
-After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
-
-```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Target frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-```{r causals-fullmodel}
-n_chains <- 1
-n_samples <- 5000
-burn <- n_samples / 2
-lg <- 5
-i <- 1
-
-model_prefix <- "pilot-results-causals-jointModel-S1-"
-
-m.cas.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/causals/results/", 
-                    model_prefix, "smntcs_causal-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
-}
-
-# n_chains <- 1
-# n_samples <- 1000
-# burn <- n_samples
-# lg <- 5
-# i <- 1
-# m.hab.fixed.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/", 
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-# }
-
-# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-#   filter(type == 'predictive') %>%
-#   rename(habitual = B, time_period = D, binned_freq = E) %>%
-#   group_by(habitual, time_period, binned_freq) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.cas.fullmodel.endorsement <- m.cas.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(dist, frequency) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
-m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
-  filter(type == "prior") %>%
-  rename(variable = item, parameter = roundedFreq) %>%
-  group_by(dist, variable, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
-
-m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(dist, variable, parameter, MAP) %>%
-  mutate(param = paste(variable, parameter, sep = "_")) %>%
-  select(-variable, -parameter) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-cas.listener.predictions <- data.frame()
-
-for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
- priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- cas.listener.predictions <- bind_rows(
-   cas.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
-   )
-}
-
-inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
-
-causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, 
-                              levels = c("state_Prior","state_Posterior"),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Causal")),
-    Distribution = factor(distribution, 
-                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>%
-  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~Distribution, nrow = 1)+
-  scale_fill_manual(values =inset.color.order )+
-  scale_color_manual(values = inset.color.order)+
-  scale_alpha_manual(values = c(0.1, 0.8))+
-  scale_linetype_manual(values = c(2, 1))+
-  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Feature-probability") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)
-```
-
-```{r}
-md.caus.endorse <- left_join(
-  m.cas.fullmodel.endorsement,
-    d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution)
-)
-
-n.caus.endorse <- length(md.caus.endorse$MAP_h)
-r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
-mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")
-
-```
-
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
-figure.causals.endorsement <- bind_rows(
-  m.cas.fullmodel.endorsement %>%
-    mutate(src = "model"),
-  d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
-    mutate(src = 'data')
-) %>%
-  ungroup() %>%
-  mutate(
-    src = factor(src, levels = c( "data", "model")),
-    dist = factor(dist, 
-           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
-           labels = c(
-                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
-    ) %>%
-  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = src, alpha = src))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(0.3), alpha = 1)+
-  #geom_line(position = position_dodge(0.3))+
-  #theme(axis.text.x = element_text(angle = 90))+
-  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_alpha_manual(values = c(1, 0.3))+
-  #scale_fill_solarized()+
-  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("")+
-  ylab("Proportion Causal Endorsement")+
-  facet_grid(.~frequency)+
-  coord_flip()+
-  guides(fill = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
-```
-
-```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
-Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
-These distributions are inferred using both data sources from Expt.
-3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
-grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
-             layout_matrix = cbind(c(1,1,2)))
-
-# ,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-### Results
-
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
-
-As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
-When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
-By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
-The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
-
-## Discussion
-
-In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
-We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
-In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
-
-In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
-These two features of the domains make them particularly amenable to manipulation.
-That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
-
-It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
-If this were happening in our domains, we would expect this to show up in the results of Expt.
-3a.
-Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
-]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
-
-# General Discussion
-
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
-As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
-
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
-
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
-
-In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge and implications for conceptual accounts
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
-In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
-As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
-] 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
-In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
-
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expts.
-2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
-
-The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
-Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
-This prior could then be updated with more data to acquire its fixed meaning.
-For the generic statement, the language learner is done once she acquires (1). 
-The rest of the meaning is inferred in context.
-With that lens, generic meaning would be primary, while quantified utterances would be refinements.
-
-There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
-A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-
-This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
-
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical Accounts
-
-Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
-
-### Conceptual Accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-
-This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
-In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
-4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
-However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
-
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
-]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-```

### 2017-10-31 paper/comgen-paper.Rmd
move bda details to appendix

@@
 
-### Bayesian data analysis
+### Results
 
@@
 \text{has wings}).
-
-Formally, we assume the prior data (analzyed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
-The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
-We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
-Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference.
-The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
-]
-The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
-Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
-This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
-Similar results can be obtained by rounding 0 to 0.01. 
-Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
-]
-Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
-<!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->
-We put the following priors over the latent parameters of the model:
-\begin{eqnarray}
-\phi_i & \sim & \text{Uniform}(0, 1) \\
-\gamma_i & \sim & \text{Uniform}(0, 1) \\
-\xi_i & \sim & \text{Uniform}(0, 100)
-\end{eqnarray}
-where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).
-
-### Results
+For model implementation and inference details, see Appendix.
 
@@
 ```
-
-To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
-To see how well the mixture model fits the feature-probability prior data, we use the inferred parameters to generate new data.
-The data generated from the model's posterior is called the *posterior predictive distribution* and is an important step in model criticism. 
-If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
-We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
-If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
-If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted feature-probability ratings.
-]
 
@@
 
-##### Model specification
-
 For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
@@
 The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-
-```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
-The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
-1a.
-The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$.
-The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input.
-This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
-Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion.
-"}
-knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
-```
-
 To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
 1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the feature-probability prior distributions, we use the same priors described in Expt.
-1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
+1a \& b (see Appendix and Figure \ref{fig:genericsModelDiagram}).
 
@@
 
+```{r child = 'appendix-bda.Rmd'}
+```
+
 ```{r child = 'appendix-alternativeRSAmodels.Rmd'}

### 2017-11-03 paper/comgen-paper.Rmd
edits to intro and start of model section

@@
 abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Dogs bark").
+    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
     The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
     Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is in determining what which such statements are true or false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of generalizations in language, while simpler models fall short.
-    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
-    The results suggest that central phenomena emerge from the interaction of diverse prior beliefs about properties with general communicative principles.
+    The major issue in formalizing generalization in language is determining which such statements are true or which are false.
+    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
+    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
+    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of language conveying generalization, while simpler models fall short.
+    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
+    The results suggest the central phenomena emerge from the interaction of underspecified meaning with diverse beliefs about properties.
 
@@
 
-Generalizations in language are often studied via *generic language* (or, generics): simple statements that convey generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+The language of generalization is often studied via *generic language* (or, generics): simple statements  about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
 Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which even 2-and-a-half-year-olds appreciate [@Cimpian2008].
+In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 -->
-Generics are just one case of generalization in language, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Generics are just one case of the language of generalizations, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
 It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
@@
 
-Despite their ubiquity and relative simplicity, there have been few formal models of generic language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining what makes such statements true or false.
-When we hear "Dogs bark", it sounds like a universal statement, like *All* dogs bark.
-But the property doesn't apply to all dogs: Basenji dogs are barkless^[
+Despite their ubiquity and relative simplicity, there have been few formal models of this language and none that have made precise, quantitative predictions to match human intuitions. 
+The major challenge in formalizing the language of generalizations is in determining *what makes the statements true or false*.
+When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
+But the property does not apply to all dogs: Basenji dogs are barkless^[
 http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
 ], for example.
-The generalization could signal something weaker like *Most* dogs bark.
-<!-- Indeed, many generalizations seem to have the quantificational force of *most*. -->
-However, only a tiny fraction of moquitos carry malaria, while the statement "Mosquitos carry malaria" is intuitively true.
+The generalization could signal something weaker like "Most dogs bark".
+However, "Most mosquitos do not carry malaria" (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to *some* goes too far: Half of robins are female, but saying "Robins are female" seems odd.
-That same half of robins (i.e., the females), however, also lay eggs, and "Robins lay eggs" is again intuively true.
-
-These observations have led to proposals that the prevalence or probability of a member of the category having the property (e.g., $P(x \text{ barks} \mid x \text{ is a dog})$) is only tangentially related to generic meaning.
-*Conceptual accounts* of generics emphasize the structure of "generic knowledge" [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-From this perspective, the statement "Bishops move diagonally" is true not because bishops tend to move diagonally, but rather because those are the rules of chess.
-With this in mind, @Leslie2007 proposes *cognitively primitive* principles that dictate how generics become true or false.
-*Characteristic* features are one such principle; "Robins lay eggs" is thus true because it is the mode of reproduction, and reproduction is a characteristic dimension for animal kinds.
-*Horrifying* or *striking* information also leads to true generics, which is why "Mosquitos carry malaria" is true despite its low prevalence.
-
-Yet others have observed that generics are not limited to conveying rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
+The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
+But weakening the generalization to "some" is too permissive: "Some Robins are female" (in fact, half of them are), but asserting "Robins are female" seems odd.
+Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
+
+These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not central to the meaning of generalizations in language.
+Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+A paradigm case is the statement "Bishops move diagonally", which is true but not because bishops tend to move diagonally but rather because those are the rules of the game.
+It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
+One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.
+Whatever their mode of reproduction, regardless of the actual prevalence of the feature, will make a true generic statement (e.g., "Robins lay eggs").
+*Horrifying* or *striking* is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is felicitous.
+
+Examining a wider range of examples makes one realize that generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
+Purely arbitrary relationships sound like true generics true.
 <!-- Arbitrary relationships are also expressed with generics:  -->
-"Barns are red" is true because that is how barn-owners tend to paint their barns; if barn-owners decided to switch to blue, the things they would be painting would still be considered barns.
-"Ravens are bigger than toasters" because of the size of ravens and the size of toasters, not because of a special relationship between ravens and toasters.
-*Conceptual accounts* must then be supplemented with the proviso that, in certain situations, the statistics of the world do influence human intuitions about generics.
-
-Generic statements have diverse theoretical underpinnings, and the conceptual view highlights this diversity [e.g., @Prasada2013].
-But insofar as generics are a single class in language---indeed, insofar as they are a subclass of generalization in language---there should be a general, unified principle that explains what makes the statements true or false.
-The same logic should apply to all generalizations in language, including habitual and causal language.
-This is the goal of this paper.
+For example, "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are blue" would be true.
+Ravens and toasters have no priviledge relationship to each other, but the statement "Ravens are bigger than toasters" is still a true genaralization.
+Conceptual accounts must then be supplemented with the proviso that, in some situations, the actual prevalence of the feature does influence human intuitions about generics.
+
+What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
+But insofar as there is a single class of linguistic expressions that we can describe as communicating generalizations, there should be something common to them all: a general, unified semantic core.
+The test of a unified semantic core is its ability to explain what makes the statements true or false.
 
@@
 
-In this paper, we take a critical look at the notion that prevalence---or its more general formulation, probability---cannot serve as the core of a semantic theory of generalization in language (including generics).
-We strive for a probability-based semantics for its generality: Probability is the universal currency of belief and serves as a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the *result* of inductive generalization, it would make sense that these are the object of communication for generalizations. 
-We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
-Formalizing such a theory is scientifically useful as well to make explicit the assumptions the theory, which in turn, elucidates the conditions under which the theory may be meaningfully tested.
-
-We take the primary desideratum for a theory of the language of generalization to be adult human intuitions into the truth or felicity of statements conveying generalization, which we measure empirically.
-To test the hypothesis that probability can serve as the core semantic theory, we build a computational model of endorsement around this semantic theory and compare our model to human judgments.
-Though concepts such as *striking properties* are not explicitly formalized in our model, there is a natural avenue for future integration as our theory is couched in a general cognitive modeling framework.
-
-Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
-In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000].
-We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement.
-We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...}
-We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+In this paper, we propose a semantic core for the language of generalization.
+To do so, we look to probability, a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
+Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
+We then consider the background knowledge that listeners bring to bear when interpreting generalizations, and formalize an endorsement model based on this interpretation hypothesis.
+Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
+Our endorsement model is the first formal theory that makes quantitative predictions about what makes generalizations in language true or false; the assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
+
+<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
+-->
+
+<!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
+-->
+<!-- In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000]. -->
+<!-- We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement. -->
+<!-- We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...} -->
+<!-- We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
+-->
+
 <!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
@@
 The paper is organized as follows. 
-In Section 1, we describe the Bayesian framework for generalization from observations, serving as the foundation for our semantic theory.
-In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this *uncertain semantics* into a computational model of endorsement.
-<!-- To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes. -->
-<!-- Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate.
--->
-In Section 3, we describe experiments that measure both listener prior knowledge and the prevalence of the properties in question, and relate them via our model to the endorsements of generalizations about categories (*generic language*).
-In Section 4, we describe experiments that measure listener prior knowledge and manipulate the frequency of various events to explain endorsements of generalizations about events (*habitual language*).
-Finally, in Section 5, we describe experiments that manipulate both the listener's prior knowledge and the prevalence of the properties in question in endorsing generalizations about causes (*causal language*).
-
-Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
-We also show how our endorsement model is a special case of a speaker model in a rational framework of communication. 
-This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
-
-<!-- (2) It also allows us to consider sources of gradience in behavior, determining whether or not we should allocate it to *noise* in the observed data or to *uncertainty* in the head of the language user.
--->
-<!-- *Causal language* (e.g., "The block *makes* it [the machine] go.") faciliates more abstract forms of causal reasoning [@Bonawitz2010]. -->
-
-<!-- \ndg{There haven't been many formal models of generic language, none have made quantitative predictions. Say why this is important. -->
-<!-- To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities. -->
-<!-- Then we need to say how these probabilities are communicated. Use RSA...} -->
-
-<!-- Rational models of communication have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
--->
-
-<!-- give rise to the productivity of human thought and form of foundations of cultural knowledge. -->
-<!-- They allow us to understand the complex world around us and dream up how possible future situations might unfold. -->
-<!-- It's been suggested that were psychology to have *general laws* akin to Newtonian laws in physics, the first general law in psychology would be of generalizations [Shepard1987]. -->
-<!-- Generalizations are central to human understanding.  -->
-<!-- Even before birth, human and non-human animals alike gather statistical information and form generalizations to predict what will come next. -->
-<!-- The human learner, perhaps uniquely in the animal kingdom, displays striking sensitivity to the intentional and pedagogical actions of others, leading to distinct and often stronger inferences from data than would otherwise be warranted from random observations.
--->
-<!-- and about people in general [e.g., "You never know what will happen on a blind date."; @Orvell2017]. -->
-
-<!-- It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015]. -->
-
-<!-- Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization. -->
-<!-- *Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general , specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
--->
-<!-- Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious.  -->
-<!-- Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.  -->
-
-<!-- The language of generalization is exceedingly difficult to formalize, however. -->
-<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
-<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
--->
-<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->
-
-<!-- Exceptions could be made for properties that only apply to one gender (like being female), but *Robins lay eggs* is intuitively true despite the property also being only present in females. -->
-<!-- Generics roughly convey that the properties is widespread in the category (e.g., *Most dogs are friendly*), however they don't always imply the same degree of prevalence. -->
-<!-- *Birds are female* sounds strange even though half of birds of female.  -->
-
-<!-- ALTERNATIVE INTRO -->
-
-<!-- Yet, generalizations can be hard to acquire. -->
-<!-- Consider what it would take to learn that under certain conditions (e.g., when eaten raw) a plant is poisonous, while under other conditions (e.g., when processed appropriately) the plant is nutritious.
--->
-<!-- This is a common ecological problem and historical examples suggest that humans are not particularly good at learning such generalizations [e.g., the Australian explorers case; @Henrich2015]. -->
-<!-- In this domain, the relationship to be learned (i.e., between different ways of food processing and the poisonousness of the plant) is non-obvious and trial-and-error learning is costly (negative examples entail death).
--->
-
-<!-- Crucially, once acquired, such hard-won generalizations can be communicated among humans, something which other animals struggle to accomplish [cite tomasello apes something]. -->
-<!-- Generalizable knowledge can be inferred through demonstration, or in pedagogical contexts when ostensive cues are present [@Csibra].  -->
-<!-- By and large, however, language provides the most flexible and generative way to communicate generalizations.  -->
-
-<!-- A generalization provides a relation between a category and a property: It tells us to predict that property of future instances of the category [@HumeTHN]. -->
-<!-- Generalization can be described as a probability and inductive inference as a probabilistic model [@Tenenbaum2011]. -->
-<!-- From a very young age, children make strong inductive inferences from their experience in a way consistent with the Bayesian probability calculus [@Dewar2010; @Gelman1986; @Markman1989]. -->
-
-<!-- If generalizations can be described by predictive probabilities, it would stand to reason that the most direct way to communicate a generalization would be to convey probability.  -->
-<!-- Ironically, humans are very bad at describing and interpreting probabilities explicitly [@Tversky1974]. -->
-<!-- Rather than be a deficiency, however, the difficulty we have in understanding numerical descriptions of probability might reflect the flexible adaptivity of natural language to make vague or ambiguous that which shared context can be relied upon to guide interpretation [@Piantadosi2012].
--->
-<!-- If language has evolved in a way to make efficient the kinds of inductive inferences that are central to human cognition, we would expect the language of generalizations to be simple [c.f., @Leslie2008].
--->
-
-<!-- Indeed, generalizations in language (e.g., *Dogs are friendly*, *Mary smokes cigarettes*, *Yeast makes bread rise*) are among the simplest forms of compositional expressions.  -->
-<!-- Generalizations do not come in just one syntactic form: "*Dogs* are friendly", "*A library book* should be treated with respect", "*The contemporary foodie* seeks culinary experinces in menu-less restaurants and grandmothers' kitchens" [@Carlson1995; @NickelBlackwell; @sepGenerics].
--->
-<!-- Each of these statements has in common the fact that they predicate a property of a category and the properties themselves apply to instances of the category (unlike, e.g., *Dinosaurs are extinct* because being extinct is not a property that can be true of a particular dinosaur).
--->
-<!-- In this way, these statements exhibit *genericity*, or put another way, they convey generalizations. -->
-
-<!-- In this paper, we formalize the language of generalizations with the interest is deciding what makes a generalization in language *true or false*. -->
-<!-- How speakers convey generalizations and how listeners interpret them. -->
-
-<!-- We examine three case studies of generalizations in language: Generalizations about agents, objects, and events.  -->
-<!-- In Section 1, we introduce an information-theoric communicative theory of how generalizations are conveyed in language and flesh out the model's predictions alongside alternative models. -->
-<!-- In order to do so, we provide a unified mathematical framework for dealing with agents, objects, and events, casting each as a category over which generalization can occur. -->
-<!-- Our model predicts the endorsements of generalizations should vary with the (A) the probability of an instances having the property and (B) the prior distribution over the property probability (e.g., how likely instances of other categories are to have the property).
--->
-<!-- In Section 2, we introduce our empirical paradigm which we use to measure endorsement and interpretation of linguisitic generalizations, examining generalizations about *agents* in what is known as *habitual language* (e.g., "Mary smokes cigarettes.").
--->
-<!-- In Section 3, we extend our paradigm to generalizations about *events* (i.e., *causal language* e.g., "Yeast makes bread rise.") and experimentally manipulate participants' background knowledge, showing that prior beliefs about probabilities are causally related to endorsement and interpretation of generalizations.
--->
-<!-- In Section 4, we use our paradigm to address long-standing theoretical and empirical puzzles regarding generalizations about *objects*, so-called *generic language*.  -->
-<!-- We show our how model explains three known psychological puzzles surrounding generic language.  -->
-<!-- In all case studies, we provide formal comparison to simpler models and in all cases, find that only our communicative theory explains the patterns of empirical data. -->
-<!-- We conclude with a general discussion about the relationship of our theory to extant theories in the psychology, linguistics, and philosophy of genericity, and highlight the implications for modeling language acquisition, conceptual development, and other avenues of research that this framework opens.
--->
-
-<!-- the truth conditions of generalizations of events (so called *habitual language*) by manipulating the target propensity (A) while surveying a wide variety of events (which should induce variability in B).
--->
-<!-- In Section 3, we manipulate both (A) and (B) while testing the model on generalizations about causes (*causal language*). -->
-<!-- If our theory is truly a theory about communicating generalizations, it should be able to explain the known psychological puzzles surrounding *generic language* (generalizations about categories).
--->
-
-<!-- In stark constrast, a computational understanding of communicating generalizations is not well understood at all.  -->
-
-<!-- Gathering data and observing evidence, however, is costly.  -->
-<!-- The human problem of induction even displays a complex sensitivity to not only the type of data, but how the data was generated [@Gweon2010; @Shafto2012]. -->
-<!-- A learner cannot form all of her abstract knowledge through direct experience, however. -->
-<!-- Life is only so long, and you can only be in one place at a time. -->
-
-<!-- In this paper, we introduce a formal model for understanding the language of generalizations. -->
-<!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning.
--->
-<!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning).
--->
-<!-- We extend a rational model of communication --- the Rational Speech Act theory --- to be able to understand general statements that extend beyond the here-and-now. -->
-<!-- We provide a number of stringest tests of this theory to explain generalizations about categories, events, and causal forces.  -->
-
-<!-- How can generalizations in language have such flexible truth conditions while simultaneously carrying intuitive and, at times, very strong implications? -->
-<!-- This question has been investigated by psychologists, linguists, and philosophers since @Carlson1977. -->
-<!-- Here, we provide a unified formal theory of generalizations conveyed in language. -->
-<!-- We test theory on the preeminent case study of linguistic generalizations: generic language, or generalizations about categories. -->
-<!--  -->
-<!-- To be precise, we develop a computational model that describes pragmatic reasoning about the propensity required to assert the generaization.   -->
-<!-- We find that this formalism resolves known philosophical and empirical puzzles. -->
-<!--We also provide the first set of experimental results about linguistic generalizations about events and causal forces, so called *habitual* and *causal statements*.-->
-
-<!-- and find extreme flexibility in usage, which our model predicts.  -->
-
-<!-- In Section 2, we conduct a set of experiments to test the *truth conditions* of familiar generalizations about categories (generic statements), and find our model predicts key patterns in human judgments -->
-<!-- In Section 3, we conduct a set of experiments to test *interpretations* of novel generic sentences, again finding our model predicts human judgments with high quantitative accuracy. -->
-<!-- In Section 4, we begin to test the generality of the theory, examining the *truth conditions* of generalizations about events. -->
-<!-- In Section 5, we further probe our theory's generality, investing the *truth conditions* and *interpretations* of novel generalizations about causal forces.  -->
-<!-- In all cases, we provide formal comparison to simpler models and in all cases, find that only our communicative theory with an underspecified meaning function explains the pattern of human data.
--->
-<!-- We also find that the prior beliefs used in our model reflect conceptual structure, and this provides an understanding of the conceptual implications of generics. -->
-<!-- Finally, we investigate the underlying semantic scale in more detail, and find that the core meaning of generalizations in language depends in a crucial way on subjective beliefs, not mere frequency.
--->
-
-<!--
-Most would agree that \emph{Swans are white}, but certainly not every swan is.
-This type of utterance conveys a generalization about a category (i.e. \textsc{swans}) and is known as a generic utterance [@Carlson1977; @Leslie2008].
-Communicating generically about categories is useful because categories themselves are unobservable [@Markman1989].
-Knowledge about categories, while central to human reasoning, is tricky to acquire because categories themselves are unobservable [Markman1989}.
-It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are essential to the growth of conceptual knowledge [@Gelman2004] and how kinds are represented in the mind [@Leslie2008].
-Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and children as young as two or three understand that generics refer to categories and support generalization [@Cimpian2008].
-and though English and many other languages do not possess an unambiguous form devoted to generic meaning [@Behrens2000, @AlMalki2014].
-Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@GelmanEtAl2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010motivation].
-Despite their psychological centrality, apparent simplicity, and ubiquity, a formal account of generic meaning remains elusive.
-
-How can generics have such flexible truth conditions while simultaneously carrying strong implications?
-In this paper, we explore the idea that the core meaning of a generic statement is simple, but underspecified, and that general principles of communication may be used to resolve precise meaning in context.
-In particular, we develop a mathematical model that describes pragmatic reasoning about the degree of prevalence required to assert the generic.  
-We find that this formalism resolves the philosophical and empirical puzzles.
--->
+In Section 1, formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
+The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
+Sections 2 - 4 presents our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
+We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
+<!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
+-->
+<!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
+<!-- This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.  -->
 
@@
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties correspondingly also vary widely (e.g., having fur, causing jitters, typing). 
+The properties also vary (e.g., having fur, causing jitters, typing). 
 Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
 
-How does one come to learn $h$, the uncertainty that underlies an inductive inference about a member of a category having a property?
+How does one come to have an $h$ in their head?
 One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
@@
 This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Here, $P(d \mid h)$ is the observer's generative model of the observed data. 
-It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.
-
-Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations.
-Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
-How do we acquire these generalizations?
-For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
-
+Relying upon observational evidence can only take you so far, though. 
+To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), it is better to learn from others.
+Fortunately, language has simple ways of encoding generalizations.
+
+<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
+<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
+<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
+<!-- How do we acquire these generalizations? -->
+<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
+-->
 <!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
@@
 
-If generalization from observations can be described as a predictive probability, then it seems natural to consider that same metric to be central to the semantic content of an utterance that conveys a generalization.
+Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity to be at the core of a semantic theory of the language of generalization.
 To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
-Perhaps the simplest way to connect a scalar quantity to a truth value is with a *threshold semantics*: An utterance is true if the underlying quantity is above a threshold.
-For generalizations, then, the threshold would apply to the *feature-probability* $h$:^[
-We emphasize that our account is based on an agent's subjective probability $h$.
-The literature on generic language has often examined *prevalence*, or the proportion of members of a category with the property, as the primary quantitative metric that could relate to generic meaning (in addition to *cue validity*, described below).
-A Bayesian agent, however, would only use prevalence as a way to update her prior knowldege $P(h)$ to form a posterior probability for future use.
-Thus, we consider the semantic content of a generalization to be related to probability, not necessarily prevalence.
+One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
+A threshold semantics for the language of generlaizaion would then apply to the *feature-probability* $h$:
+$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
+We emphasize that this account is based on a probability $h$.
+The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[
+  There has also been substantial discussion of *cue validity* , which we come back to below.
 ]
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-
-### Resolving underspecification
+Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself. 
+Probability is a measure of belief.
+
+### Semantics and background knowledge
 
@@
 
-<!-- In Bayesian statistics, when there is uncertainty about latent parameter, one specifies a prior distribution over the parameter and reasons backward about the parameter's likely value given any data.
--->
-<!-- In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
--->
-<!-- Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context *a priori*: $P(\theta) = \text{Uniform}(0, 1)$.
--->
-
-<!-- \ndg{i wonder if we shoud start with the speaker / endorsement idea? introducing the listener and semantics might be more natural then.} -->
-
-<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al.
-influence the meaning of a generic statement via their influence on subjective probability.
--->
-<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts].
--->
-
-<!-- \begin{eqnarray} -->
-<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
-<!-- \end{eqnarray} -->
-
 ### The feature-probability prior and model simulations
-
-<!-- $\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance. -->
-<!-- $P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$. -->
-<!-- The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
--->
-<!-- In our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$. -->
-<!-- This is a different approach than in conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013], but provides a potential bridge, as explored later. -->
 
@@
 
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
-It has been the premier case study of generalization in language because of its similarity to quantified statements (e.g., "Most dogs bark").
+Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
+Generics have been the case study of choice for generalizations in language because of theiry vexing similarity to quantified statements (e.g., "*Most* dogs bark").
+Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
+Here, we take our first look at the
+
+Here, we take 
 Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).

### 2017-11-04 paper/comgen-paper.Rmd
edits to intro, model, and simulations

@@
 What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that we can describe as communicating generalizations, there should be something common to them all: a general, unified semantic core.
+But insofar as there is a single class of linguistic expressions that convey generalizations, there should be something common to them all: a general, unified semantic core.
 The test of a unified semantic core is its ability to explain what makes the statements true or false.
@@
 In this paper, we propose a semantic core for the language of generalization.
-To do so, we look to probability, a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
+To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
 Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
@@
 The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
-Sections 2 - 4 presents our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
 Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
@@
 <!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-<!-- This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.  -->
+This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
 
@@
 
-How does one come to have an $h$ in their head?
-One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
-But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
-For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Relying upon observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), it is better to learn from others.
+How does one acquire such an inductive belief?
+One can observe instances of the category $k$ and note how many of them have $f$.
+These observations can support prediction to new instances by integrating them with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
+For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
+Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
+This kind of background knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
+
+Learning from observational evidence can only take you so far, though. 
+To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), one would much rather learn from others.
 Fortunately, language has simple ways of encoding generalizations.
@@
 
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity to be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
+Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
+To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
 One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlaizaion would then apply to the *feature-probability* $h$:
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-We emphasize that this account is based on a probability $h$.
-The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[
-  There has also been substantial discussion of *cue validity* , which we come back to below.
-]
-Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself. 
-Probability is a measure of belief.
-
-### Semantics and background knowledge
-
-What threshold $\theta$ should be used for the generalization?
-We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
+A threshold semantics for the language of generlizations would then apply to the *feature-probability* $h$:
+\begin{equation}
+\denote{generalization}(h, \theta) = \{h>\theta\}
+\label{eq:semantics}
+\end{equation}
+Various attempts of this kind have been made before [e.g., @Cohen1999].
+We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $h$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+$h$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief (due to background knowledge, see above).
+
+<!-- We emphasize that this account is based on a probability $h$. -->
+<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[ -->
+<!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
+<!-- ] -->
+<!-- Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself.  -->
+<!-- Probability is a measure of belief.  -->
+
+### Literal interpretation model
+
+Quantifier statements can be described using a similar threshold semantics: $\denote{some}(x) = \{h > 0\}; \denote{all} = \{h = 1\}$.
+So what threshold should be used for the generalizations? 
+What is $\theta$?
+Unlike quantified language, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
+That is, we hypothesize that $\theta$ is contextually-determined, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+
+We formalize this underspecified semantics in a probabilistic model, where the underspecifed threshold $\theta$ is sampled from a uninformed prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013].
+After making explicit the relevant background knowledge $P(h)$, the model becomes:
 
 \begin{eqnarray}
-Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
+Interpret(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
 \end{eqnarray}
 
-Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
-We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
-The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
+Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the feature-probability $h$ according to the truth-functional meaning of the utterance $u$. 
+Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
 
@@
 
-Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
+<!-- Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.  -->
 
@@
 
-The above model determines how $\theta$ should be resolved in context.
-Now, how do we decide when a statement conveying a generalization is true or not?
-To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
-The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
+Given the above minimal model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
+We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of producition? 
+We formalize this by considering how well the generalization would convey the feature-probability $h$ to the $Interpret$ model (Eq.
+\ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific feature-probability $h'$ that it wants to communicate.
+Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the feature-probability. 
+In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorser's belief distribution:
+$Endorse(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} Interpret(h, \theta \mid u)} \diff \theta )}$
+].
 
 \begin{equation} 
-E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
+Endorse(u \mid h = h') \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Interpret(h = h', \theta \mid u)  \diff \theta } )}
 \label{eq:S1}
@@
 
-Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
-
-The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
-Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
-$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
+The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$): $Interpret(h = h', \theta \mid u)$.
+$Endorse$ is not interested in communicating $\theta$ (in fact, it does not know $\theta$), and so integrates over the values of $\theta$.
+We assume the decision to endorse is an approximately rational one, with degree of rationality given by $\lambda$.
+The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
+We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
+"disagree") as supplying two alternatives: *Endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [cf., @Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$^[
+  This "null" alternative  to the generalization ("Ks F") can be realized in at least two other ways: the negation of the generalization (i.e., "It is   not the case that Ks F") or the negative generalization (i.e., "Ks do not F").
+  All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity.
 ]
-The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
-This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]
-
-\begin{equation} 
-U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
-\end{equation}
-
-Thus, Eq.
-\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
-Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
-
-The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
-
-Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
-The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
-However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
-
-### The feature-probability prior and model simulations
-
-The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
-We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
-We implemented the models in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
+
+Our endorsement model (Eq.
+\ref{eq:S1}) provides a straight-forward mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
+It does this assuming a threshold semantics based on probability but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
+This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.
+
+<!-- Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$. -->
+
+<!-- The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization. -->
+
+<!-- Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener). -->
+<!-- The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it.  -->
+<!-- However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
+-->
+<!-- We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix. -->
+
+<!-- The null alternative returns a posterior interpretation distribution that is identical with the prior $P(h)$. -->
+
+<!-- Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
+-->
+<!-- Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
+-->
+
+<!-- The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$. -->
+
+<!-- The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:   -->
+
+<!-- \begin{equation}  -->
+<!-- U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility} -->
+<!-- \end{equation} -->
+
+We implemented the model in the probabilisitic programming language WebPPL [@dippl].
+The following simulations were implemented using the R package RWebPPL [@rwebppl] in the RMarkdown document that generated this paper text and figures.
 That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+
+### Model simulations
+
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the feature-probability communicated in the category under discussion $h'$ in Eq.
+\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about feature-probabilities $P(h)$ (Eq.
+\ref{eq:L0}).
+We simulate how these two factors change both literal interpretation and endorsement using hypothetical values based on intuition about classic examples from the literature on generic language.
 
@@
 
-These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-]
-
-Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
-The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
-The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
-]
-The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
-
-How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
-For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
-The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
-"Robins lay eggs", however, has a lot of informational content.
-
-Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
-Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
-
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the feature-probability priors $P(h)$.
-In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
+Figure\ \@ref(fig:simulations) (left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property.
+These distributions can be thought of as distributions over categories, displaying only the feature-probability for the property in question.
+For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the feature-probability of \textsc{barks} (top left; solid pink distribution).
+In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the feature-probability distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).
+
+The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}. 
+This gives the literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") given the background knowledge about the property.
+For instance, the interpretation of a generalization about the property \textsc{barks} is that the feature-probability is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
+This would correspond to a rather strong interpretation (i.e., "Almost all feps bark").
+This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green). 
+Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
+The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple).
+Again, the literal interpretation depends upon the background knowledge in a deep way.
+
+The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right).
+Given a feature-probability of a referent category $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
+\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
+We see the model correctly predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent feature-probabilities varying substantially between these three examples.
+Intruigingly, the model predicts "Robins are female" (which has the same feature-probability as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
+To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) left; blue distributions).
+The endorsement model decides if it is better to produce the generalization or stay silent (which results in the interpretation distribution being the prior). 
+In this case, there is no difference in interpretation, and thus, the model is completely ambivalent about whether or not to endorse the statement.
+This can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
+\mht{For further discussion about the behavior of the model, and these six examples, see Appendix?}
+
+These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(h)$ as well as the feature-probability $h'$ communicated. 
+We chose reasonable, hypothetical values for each of these, and saw that the endorsement model recapitulated standard intuitions about the truth or falsity of classic examples from the generics literature.
+In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
+We do this by both measurning and manipulating background knowledge and feature-probability communicated and relate it to human elicited endorsements of generalizations.
+
+<!-- that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics. -->
+<!-- For these simulations, we had specify both the feature-probability priors $P(h)$ and the referent feature-probability $h'$.. -->
+<!-- In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes. -->
+
+<!-- These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row). -->
+<!-- The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior. -->
+<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[ -->
+<!-- The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities. -->
+<!-- If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold. -->
+<!-- If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower. -->
+<!-- As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it. -->
+<!-- When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model). -->
+<!-- The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*. -->
+<!-- ] -->
+
+<!-- Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements. -->
+<!-- The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$. -->
+<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+-->
+<!-- The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[ -->
+<!-- We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero.  -->
+<!-- The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
+-->
+<!-- ] -->
+<!-- The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category. -->
+
+<!-- How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"? -->
+<!-- In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
+<!-- For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
+-->
+<!-- For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs. -->
+<!-- This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3). -->
+<!-- For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
+-->
+<!-- The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case.
+-->
+<!-- In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
+-->
+<!-- "Robins lay eggs", however, has a lot of informational content. -->
+
+<!-- Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria". -->
+<!-- The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread. -->
+<!-- Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
+-->
+<!-- Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria". -->
 

### 2017-11-11 paper/case1-generics.Rmd
edits to end of generics; half of habituals; modularize paper into separate files for each case study

--- 2017-11-03 paper/comgen-paper.Rmd
@@
----
-title             : "The language of generalization"
-shorttitle        : "The language of generalization"
-
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-  - \usepackage{amsmath}
-  - \usepackage{graphicx}
-  - \usepackage{subcaption}
-
-author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
-
-abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which such statements are true or which are false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of language conveying generalization, while simpler models fall short.
-    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results suggest the central phenomena emerge from the interaction of underspecified meaning with diverse beliefs about properties.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "20000"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-
-\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
-\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
-\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
-```
-
-```{r libraries, cache = F}
-library(papaja)
-library(formatR)
-library(rwebppl)
-library(xtable)
-library(tidyverse)
-library(forcats)
-library(langcog)
-# library(dplyr)
-library(data.table)
-library(coda)
-library(ggthemes)
-library(ggrepel)
-library(jsonlite)
-library(gridExtra)
-library(lme4)
-library(knitr)
-library(cowplot)
-theme_set(theme_few())
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-logmeanexp <- function(x){
-  x.num <- as.numeric(x)
-  xstar = max(x.num)
-  return(xstar + log(mean(exp(x.num - xstar))))
-}
-
-compute_r2 <- function(df,v1, v2, sigfigs = 3){
-  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
-}
-
-compute_mse <- function(df, v1, v2, sigfigs = 3){
-  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
-}
-
-project.path <- "../"
-options("scipen"=10) 
-```
-
-<!-- 
-possible titles:
-- Communicating generalizations
-- The language of generalization
-- The language of generalization: Probability, vagueness, and interaction
--->
-
-# Introduction
-
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
-
-<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
-<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
-<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
-<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
--->
-<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
-<!-- \ndg{this par doesn't really do much} -->
-
-The language of generalization is often studied via *generic language* (or, generics): simple statements  about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
--->
-Generics are just one case of the language of generalizations, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
-
-<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
-<!-- Individual entities can also be talked about in generalization, using so-called  -->
-<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
-<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
-
-Despite their ubiquity and relative simplicity, there have been few formal models of this language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining *what makes the statements true or false*.
-When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
-The generalization could signal something weaker like "Most dogs bark".
-However, "Most mosquitos do not carry malaria" (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to "some" is too permissive: "Some Robins are female" (in fact, half of them are), but asserting "Robins are female" seems odd.
-Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
-
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not central to the meaning of generalizations in language.
-Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-A paradigm case is the statement "Bishops move diagonally", which is true but not because bishops tend to move diagonally but rather because those are the rules of the game.
-It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
-One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.
-Whatever their mode of reproduction, regardless of the actual prevalence of the feature, will make a true generic statement (e.g., "Robins lay eggs").
-*Horrifying* or *striking* is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is felicitous.
-
-Examining a wider range of examples makes one realize that generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships sound like true generics true.
-<!-- Arbitrary relationships are also expressed with generics:  -->
-For example, "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are blue" would be true.
-Ravens and toasters have no priviledge relationship to each other, but the statement "Ravens are bigger than toasters" is still a true genaralization.
-Conceptual accounts must then be supplemented with the proviso that, in some situations, the actual prevalence of the feature does influence human intuitions about generics.
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that we can describe as communicating generalizations, there should be something common to them all: a general, unified semantic core.
-The test of a unified semantic core is its ability to explain what makes the statements true or false.
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-
-In this paper, we propose a semantic core for the language of generalization.
-To do so, we look to probability, a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-We then consider the background knowledge that listeners bring to bear when interpreting generalizations, and formalize an endorsement model based on this interpretation hypothesis.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-Our endorsement model is the first formal theory that makes quantitative predictions about what makes generalizations in language true or false; the assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-
-<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
--->
-
-<!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
--->
-<!-- In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000]. -->
-<!-- We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement. -->
-<!-- We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...} -->
-<!-- We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
--->
-
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
-The paper is organized as follows. 
-In Section 1, formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
-Sections 2 - 4 presents our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-<!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
--->
-<!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-<!-- This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.  -->
-
-# Computational Framework
-
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
-
-How does one come to have an $h$ in their head?
-One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
-But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
-For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Relying upon observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), it is better to learn from others.
-Fortunately, language has simple ways of encoding generalizations.
-
-<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
-<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
-<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
--->
-<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
-<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
--->
-<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
-
-<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
-<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
--->
-<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
-<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
--->
-
-<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
-<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
-<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
--->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
--->
-<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
-<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
-
-<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
-<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
--->
-<!-- \ndg{what is this par doing for us? delete?} -->
-<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
-<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
--->
-<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
--->
-<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
--->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-
-## Generalization from language
-
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity to be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
-One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlaizaion would then apply to the *feature-probability* $h$:
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-We emphasize that this account is based on a probability $h$.
-The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[
-  There has also been substantial discussion of *cue validity* , which we come back to below.
-]
-Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself. 
-Probability is a measure of belief.
-
-### Semantics and background knowledge
-
-What threshold $\theta$ should be used for the generalization?
-We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
-
-\begin{eqnarray}
-Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
-We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
-The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}\label{eq:delta}
-\end{eqnarray}
-
-Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
-
-### Endorsement model
-
-The above model determines how $\theta$ should be resolved in context.
-Now, how do we decide when a statement conveying a generalization is true or not?
-To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
-The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
-
-\begin{equation} 
-E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
-\label{eq:S1}
-\end{equation}
-
-Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
-
-The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
-Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
-$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
-]
-The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
-This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]
-
-\begin{equation} 
-U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
-\end{equation}
-
-Thus, Eq.
-\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
-Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
-
-The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
-
-Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
-The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
-However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
-
-### The feature-probability prior and model simulations
-
-The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
-We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
-We implemented the models in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
-
-```{r simluationsModel, eval = T, cache = T}
-l0.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
-'
-
-priorNames <- c(
-  "doesntEatPeople", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria",
-  "hasSpots"
- # "areSick"
-  )
-priorShapes <- list(
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-all.simulations <- data.frame()
-for (p in priorNames){
-  for (u in c("generic")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
-    )
-  }
-  #print(p)
-}
-```
-
-```{r simluationEndorsementModel, eval = T, cache = T}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.mix[0];
-var priorParams = data.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-var alpha = 2
-
-var endorser = function(featureProb){
-  Infer({model: function(){
-    var endorsement = sample(utterancePrior)
-    var L0 = marginalize(listener0(endorsement), "state_Posterior")
-    factor(alpha * L0.score(featureProb))
-    return endorsement
-  }})
-}
-
-probability(endorser(data.featureProb[0]), "generic")
-'
-
-exampleGenerics <- c(
-  "sharksDontEatPeople",
-  "robinsAreFemale", 
-  "robinsLayEggs", 
-  "kangaroosHaveSpots",
-  "dogsBark",
-  "mosquitosCarryMalaria"
-  )
-exampleParameters <- list(
-  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
-  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
-  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
-  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
-  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
-)
-
-s1.simulations <- data.frame()
-for (p in exampleGenerics){
-
-    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
-    s1.simulations <- bind_rows(s1.simulations,
-                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
-
-}
-
-```
-
-```{r}
-s1.simulations.relabeled <- s1.simulations %>%
-  mutate(example = factor(example, 
-                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-  #geom_jitter(width = 0.1, shape = 21, size = 5)+
-  #ylab("Human endorsement probability")+
-  #xlab("Frequency of target")+
-  geom_label_repel(data = s1.simulations.relabeled, 
-                   aes( label = example, fill = example),
-                       color = 'white',
-    box.padding = unit(0.0, "lines"),
-    #point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37')+
-  scale_fill_solarized()+
-  scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
-  coord_fixed(ratio = 1)+
-  guides(fill = F)+
-  ylab("Endorsement model prediction")+
-  xlab("Hypothesized feature-probability")
-
-```
-
-```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
-all.simulations.refactored <- all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                                c( "Prior_generic", "Posterior_Generalization_generic"),
-                                labels = c( "Prior/Silence", "Generalization")
-                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
-                             ),
-         PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
-                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         )
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability h") +
-    ylab("Scaled prior probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-```
-
-```{r simulations, fig.cap = "Model behavior.
-Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
-grid.arrange(l0.simulations.distributions, 
-             s1.simulations.scatter, ncol = 3,
-             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
-
-```
-
-These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-]
-
-Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
-The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
-The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
-]
-The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
-
-How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
-For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
-The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
-"Robins lay eggs", however, has a lot of informational content.
-
-Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
-Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
-
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the feature-probability priors $P(h)$.
-In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
-
 # Case Study 1: Generic Language
@@
 Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-Generics have been the case study of choice for generalizations in language because of theiry vexing similarity to quantified statements (e.g., "*Most* dogs bark").
+In addition, generics have been the case study of choice for the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
 Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
-Here, we take our first look at the
-
-Here, we take 
-Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
-
-We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
+
+Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
+We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions [@Prasada2013]: *majority characteristic* (e.g., "Ducks have wings."),  *minority characteristic* (e.g., "Robins lay eggs."), *striking* (e.g.
 "Mosquitos carry malaria."),  *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
 "Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
+We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high feature-probabilities (Expt.
 1a).
-
-We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
-Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
-\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
-To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
+We examine generics about animal categories in order to reliably measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
+This elicitation procedure includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
+\ref{eq:S1}) as well as for simpler, alternative models.
 
@@
 Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
@@
 
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
+In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) top left).
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
+We next measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
 
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
+1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ \@ref(fig:generics-prior-task) left).
 A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
+Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ \@ref(fig:generics-prior-task) right).
 Eight property--columns appeared in the table.
@@
 We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
+One of these distributions is fixed to represent kinds of animals who *do not have* an stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
+The second distribution is flexible and represents kinds of animals who *do have* such a mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
 \text{has wings}).
@@
 
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
+Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \  \@ref(fig:generic-endorsement-priors-figure).
 There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
@@
 1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
+We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \  \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
 The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
@@
 
-### Information-theoretic endorsement models
-
-The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
-Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
-We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
-We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
-
-For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
-  Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-  This corresponds to the more general form of the model described in a footnote in the model section. 
-  For these data, the predictions of these two models are nearly identical.
-]
-(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
+### Communicative endorsement models
+
+The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpretor.
+The endorsement model $Endorse$ (Eq.
+\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpretor $Interpret$ (Eq.
+\ref{eq:L0}) conditioned on a particular referent-category feature-probability $h'$ (e.g.,  the percentage of robins that lay eggs).
+We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorsement model.
 The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Appendix and Figure \ref{fig:genericsModelDiagram}).
+
+To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category feature-probabilities $h'$, feature-probability priors $P(h)$ (both from Expt.
+1b data), and the endorsement data (Expt.
+1a).
+Modeling the data from both Expt.
+1a and 1b by a single, joint-inference model simultaneously makes explicit all of our assumptions about how these data were generated, and is the proper Bayesian way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix and Figure \  \@ref(fig:genericsModelDiagram) for further model specification details).
+The $Endorse$ model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie] for 3 chains of 100,000 iterations, discarding the first 50,000 for burnin.
+
+The number of parameters of this full data-analytic model is relatively large, and thus there is a concern that the parameters themselves (as opposed to the exact structure of our model) are doing the work.
+To address this concern, we construct a strong, alternative model that uses the same data analytic strategy with the same number of the parameters.
+This control model is a lesioned version of the uncertain threshold model, which we construct by removing the uncertainty about the semantic threshold $\theta$. 
+All other architectural features (the prior distribution, the information-theoretic decision of whether or not to produce the generalizations) as well as their respective parameters are the same as for the uncertain threshold model.
+We examine the predictions of the control model first.
 
@@
 
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
+The fixed-threshold model is a lesioned version of the unceratin-threshold model: It has access to the full prior distribution on feature-probabilities $P(h)$ and models endorsement as an information-theoretic decision of producing the generic vs.
+an alternative.
+The only difference is that this model uses a fixed-threshold as the core meaning of a generic statement, rather than an uncertain threshold.
 For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
@@
 
+#model_prefix <- "results-generics-jointModel-10bins-S1-smntcs_"
+
+#m.samp <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+                     #20000, "_burn", 10000, "_lag", 20, "_chain", 2, ".csv", sep = ""))
+#m.samp <- fread("~/Documents/research/communicating-generalizations/models/generics/results/results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-100000_burn100000_chain1.csv")
+
 m.gen.fullmodel.endorsement <- m.samp %>%
+ # filter(type == 'endorsement', param == 'generic') %>%
+  #filter(type == 'predictive', param == 'generic') %>%
   filter(type == 'endorsement') %>%
@@
   m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
+  "MAP", "MAP_h", sigfigs = 5
 )
@@
   m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
+  "MAP", "MAP_h", sigfigs = 5
 )
@@
 
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
+To evaluate this model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions of the model given these parameter values.
 Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1b).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
+This means the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
 
 We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
-Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
+Figure \@ref(fig:generics-endorsement-figure) (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
 The model fails to distinguish any of the generic sentences because they are all somewhat true. 
@@
 We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
 
@@
 The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
+The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure).
 It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
@@
 Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
+Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have deep implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
+Heretofore, no formal model has made precise, quantitative predictions about the flexible endorsement patterns of generics (*Birds lay eggs* v. *are female*; *Mosquitos carry malaria*).
+
+By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable in spite of alleged counterexamples.
+The key theoretical insight is that the threshold must be *underspecified* in the semantics and determined in context.
+The decision of whether or not to endorse the generic comes down to whether or not the generic would make the interpretation belief distribution more in line with the feature-probability that the endorser had in mind.
 
@@
 Thus, we have shown how these measurements are related to generic endorsement via our model. 
-This evidence is correlational in nature, however.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
-# Case Study 2: Habitual Language
-
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
-Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
-While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
-]
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
-In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
-We separately measure endorsements under the same contexts (Expt.
-2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
-## Experiment 2a: Measuring the feature-probability prior for events
-
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
-To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
-The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
-This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
-
-### Method
-
-#### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-#### Materials
-
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
-
-#### Procedure
-
-For each event, participants were asked two questions, with associated dependent measures:
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
-\end{enumerate}
-
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
-After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
-They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-They did this to test their understanding and attention for each of the two questions.
-
-For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
-<!--   \caption{ -->
-<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
-<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
-<!--   Actual frequency noted on x-axis for examples (left). -->
-<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
-<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
-<!--   } -->
-<!--   \label{fig:tjScatters} -->
-<!-- \end{figure*} -->
-
-<!-- #### Data preprocessing -->
-
-```{r habituals-prior-data}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
-
-d.hab.priors <- d.hab.priors %>%
-  mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women),
-         item = as.character(item),
-         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
-  rowwise() %>%
-  mutate(
-    mixture_male = nPersons_men / comparisonNum_men,
-    mixture_female = nPersons_women / comparisonNum_women,
-    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
-                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
-                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
-                   ifelse(comparisonTime_men == "5 years", 
-                          nInstances_men / (5*365), -99)))),
-    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
-                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
-                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
-                   ifelse(comparisonTime_women == "5 years", 
-                          nInstances_women / (5*365), -99)))),
-    annualRate_male = dayRate_male * 365,
-    annualRate_female = dayRate_female * 365
-  )
-
-d.hab.priors.filtered <- filter(d.hab.priors, 
-       !(
-         (mixture_male == 0) ||   (mixture_female == 0) ||   
-           (dayRate_male == 0) ||   (dayRate_female == 0)  )
-       )
-```
-
-```{r habituals-prior-forwardsample}
-# this is basically bootstrapping and combining using the structured model
-
-d.hab.priors.samples <- data.frame()
-for (i in 1:10){
-
-  d.hab.priors.samples <- bind_rows(
-    d.hab.priors.samples,
-    d.hab.priors.filtered %>% 
-    select(workerid, item, starts_with("annualRate"), 
-           starts_with("mixture")) %>%
-    rowwise() %>%
-    mutate(
-      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
-       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
-       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
-       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
-       ) %>%
-    select(item, freq_male, freq_female) %>%
-    gather(gender, val, freq_male, freq_female) %>%
-  mutate(gender = gsub("freq_", "", gender))
-  )
-}
-
-```
-
-```{r habituals-prior-model}
-hab.prior.bda.model <- '
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var model = function(){
-	var mixtureParams = {
-		male: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    },
-		female: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    }
-	};
-
-	var mixtureShapes = {
-		male: betaShape(mixtureParams.male),
-		female: betaShape(mixtureParams.female)
-	};
-
-	mapData({data: data.mixture}, function(d){
-    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
-     // display(Beta(mixtureShapes[d.gender]).score(d.val))
-		observe(Beta(mixtureShapes[d.gender]), d.val)
-	})
-
-	var stableFrequency = {
-		male: {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		},
-		female: {
-			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		}
-	}
-
-	mapData({data: data.frequency}, function(d){
-    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
-        display(JSON.stringify(d)) : null
-    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
-		observe(Gaussian(stableFrequency[d.gender]), d.logval)
-	})
-
-	var existenceProb = {
-		male: beta(mixtureShapes.male),
-		female: beta(mixtureShapes.female)
-	};
-
-	var freqWhenPresent = {
-		male: gaussian(stableFrequency.male),
-		female: gaussian(stableFrequency.female)
-	}
-
-  var marginalFreq = {
-    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
-    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
-  }
-
-  return {
-    mix_mean_male : mixtureParams.male.g,
-    mix_mean_female : mixtureParams.female.g,
-    mix_samplesize_male : mixtureParams.male.d,
-    mix_samplesize_female : mixtureParams.female.d,
-    stableFreq_mean_male : stableFrequency.male.mu,
-    stableFreq_mean_female :stableFrequency.female.mu,
-    stableFreq_sd_male : stableFrequency.male.sigma,
-    stableFreq_sd_female :stableFrequency.female.sigma,
-    marginalFreq_NA_male: marginalFreq.male,
-    marginalFreq_NA_female: marginalFreq.female
-  }
-}
-'
-```
-
-```{r habituals-prior-model-run, cache = T}
-items <- levels(factor(d.hab.priors.filtered$item))
-n_samples <- 500
-rs.habituals.bda.prior <- data.frame()
-
-for (it in items){
-
- df.prior.toPass <- list(
-   frequency = d.hab.priors.filtered %>%
-      filter(item == it) %>%
-      select(item, starts_with("annualRate")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("annualRate_", "", gender),
-             logval = log(val)),
-   mixture = d.hab.priors.filtered %>% 
-      filter(item == it) %>%
-      select(item, starts_with("mixture")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("mixture_", "", gender)) %>%
-      rowwise() %>%
-      mutate(val = ifelse(val == 1, 0.9999, 
-                          ifelse(val == 0, 0.000001, val)))
-  )
-
-  rs <- webppl(program_code = hab.prior.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.prior.toPass,
-       data_var = "data")
-
-  rs.habituals.bda.prior <- bind_rows(
-    rs.habituals.bda.prior, 
-    rs %>% 
-      mutate(item = it) %>% 
-      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
-  )
-}
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
-
-example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
-                       "climbs mountains", "hikes", "runs", 
-                       "wears a suit", "wears a watch", "wears socks", 
-                       "writes poems", "goes to the movies", "plays the banjo"
-                       )
-
-rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
-  filter(Parameter == "mean") %>%
-  group_by(Variable, Gender, item) %>%
-  summarize(MAP = estimate_mode(value),
-            cred_upper = hdi_upper(value),
-            cred_lower = hdi_lower(value)) %>%
-  ungroup()
-rs.habituals.bda.prior.summary.wide <- left_join(
-  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
-    select(-Variable) %>%
-    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
-  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
-    select(-Variable) %>%
-    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
-)
-
-figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) %>%
-ggplot(.,
-       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
-            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = category))+
-    scale_shape_manual(values=c(21,22))+
-  #scale_color_solarized()+scale_fill_solarized()+
-  scale_fill_brewer(palette='Set1')+
-
-  geom_point(size=4, inherit.aes = F, 
-             aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            shape = Gender),  alpha = 0.9)+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  xlab("% of Americans who have DONE ACTION")+
-  ylab("Log Frequency of DOING ACTION")+
-  #scale_
-  coord_fixed(ratio = 1/8)+
-  theme(legend.title = element_text(hjust=0),
-        legend.position="bottom",
-        legend.direction="horizontal") +
-        scale_y_continuous(limits = c(-1.5, 6.5), 
-                     breaks = c(0, 2.5, 4, 5.9),
-                     labels = c("annually", "monthly", "weekly", "daily"))+
-  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
-                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-```
-
-```{r habituals-prior-model-forwardSample}
-rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value)
-
-rs.habituals.bda.prior.samples <- data.frame()
-for (i in 1:1){
-  rs.habituals.bda.prior.samples <- bind_rows(
-    rs.habituals.bda.prior.samples,
-    rs.habituals.bda.prior.spread %>%
-    rowwise() %>%
-    mutate(
-      a = mix_mean * mix_samplesize,
-      b = (1 - mix_mean) * mix_samplesize,
-      theta = rbeta(n = 1, shape1 = a, shape2 = b),
-      stable = rbinom(n = 1, size = 1, prob = theta),
-      logannualRate = ifelse(stable == 1, 
-                             rnorm(n = 1, 
-                                   mean = stableFreq_mean, 
-                                   sd = stableFreq_sd), -5),
-       annualRate =  exp(logannualRate)
-    )
-  )
-}
-```
-
-```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
-2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
-
-figure.habituals.priors.marginals <- bind_rows(
-  d.hab.priors.samples %>% 
-    mutate(src = 'data', 
-           val = log(val)),
-  rs.habituals.bda.prior.samples %>%
-    rename(gender = Gender, val = logannualRate) %>%
-    select(gender, item, val) %>%
-    mutate(src = 'model')
-  ) %>%
-  filter(item %in% example.habituals,
-         src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals)) %>%
-ggplot(. , aes( x = val, color = gender))+
-  geom_density(size = 0.8, aes( y = ..scaled.. ))+
-  facet_wrap(~item, nrow = 4)+
-  scale_color_solarized()+
-  xlab("Frequency")+
-  ylab("Scaled prior density")+
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.12),
-        axis.text.x = element_text(angle = 90))+
-    scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
-2a).
-Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on rates from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-### Data analysis and results
-
-All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-We built a Bayesian data analysis model for this prior elicitation task.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-First, it smooths effects that are clearly results of the response format.
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
-
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate or frequency with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
-
-<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
-<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
-<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
-<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
-<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-## Experiment 2b: Endorsing habitual statements
-
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Procedure and materials
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
-<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
-
-### Results
-
-```{r habituals-prior-mixture-summarize}
-d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
-  select(item, starts_with("mixture_")) %>%
-  gather(key, value, -item) %>%
-  group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
-  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
-  rowwise() %>%
-  mutate(
-    annualRate = annualRates[[as.character(time_period)]]*n_instances,
-    logAnnualRate = log(annualRate)
-  )
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
-                       "goes to the movies_month", "smokes cigarettes_month")
-fig.habituals.endorsement.vs.freq <- 
-  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21, size = 5)+
-  ylab("Human endorsement probability")+
-  xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
-                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
-                    filter(sentence %in% example.habituals), aes( label = habitual ),
-                       color = 'black', fill = 'white',
-    box.padding = unit(0.35, "lines"),
-    point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
-  scale_x_continuous(limits = c(-1,6), 
-                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
-                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        legend.position = "bottom")+
-  coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F))
-```
-
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.', eval=F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
-r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
-
-```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.freq.mix.uniq <- unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, 
-    mixture, mix_low, mix_high
-  ))
-
-d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_low)
-
-d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_high)
-
-d.hab.endorse.regression.freq <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
-      prediction_lower = prediction,
-      prediction_upper = prediction,
-      src = "regression_freq"
-      )
-)
-
-r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
-
-r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
-  filter(logAnnualRate < 1.1)
-
-r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
-
-r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
-d.hab.endorse.regression.freq.mix <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
-      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
-      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
-      src = "regression_freq_distinct"
-      )
-)
-
-r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-model_prefix <- "results-habituals-jointModel-S1-"
-
-# m.hab.samp <- data.frame()
-# m.hab.fixed.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
-#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-# 
-# }
-# 
-# save(m.hab.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.hab.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "habituals_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.habituals.rsa.fixed <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.fixed <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.uncertain <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)
-
-r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)
-
-r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression,
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, logAnnualRate, mixture)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "some_model",
-                                      "habituals_model",
-                                      "regression_freq", 
-                                      "regression_freq_distinct"
-                                     ),
-                      labels = c(
-                                 "Speaker model - fixed semantics",
-                                 "Speaker model - uncertain semantics",
-                                 "Referent frequency alone", "Distinctiveness + referent frequency"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.15)+
-  geom_errorbarh(alpha = 0.15)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r habituals-simulation-model}
-l0.hab.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
-
-var targetUtterance = "habitual";
-
-var roundTo3 = function(x){
-  return Math.round(x * 10000) / 10000
-}
-
-var lowerBound = -5, upperBound = 10, binWidth = 0.5;
-
-var stateBins =  _.range(
-  lowerBound, upperBound, binWidth
-)
-
-var thetaBins = map2(function(b1, b2){
-  var diff = Math.abs(b2 - b1) / 2;
-  return roundTo3(diff+ b1);
-}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state> _.min(thetaBins):
-         true
-}
-
-var priorParams = data.priorParams[0];
-
-var stable_female_params = betaShape({
-  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
-})
-
-var stable_male_params = betaShape({
-  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
-})
-
-// this marginalizes out the mixture parameter
-var statePrior = Infer({model: function(){
-  var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ? // 
-    flip(
-        categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_female_params), b) + Number.EPSILON
-          }, probBins )
-        })
-    ) ? // stable female distribution
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) : // unstable female distribution
-    _.min(stateBins) : 
-    flip(        
-      categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_male_params), b) + Number.EPSILON
-          }, probBins )
-      })
-    ) ? 
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) :
-    _.min(stateBins)
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:-5}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:-5})
-   var state_prior = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:lowerBound}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:lowerBound})
-    var theta = uniform(lowerBound, upperBound)
-    condition(
-      (utterance == "habitual") ? 
-      state > theta : 
-      (state > _.min(lowerBound))
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
-
-continuousListener0(data.utt[0])
-'
-```
-
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
-
-m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
-  filter(type == "prior", B %in% example.habituals.actions) %>%
-  rename(action = B, variable = C, gender = D, parameter = E) %>%
-  group_by(action, variable, gender, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(action, variable, gender, parameter, MAP) %>%
-  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
-  select(-variable, -gender, -parameter) %>%
-  spread(param, MAP)
-
-hab.listener.predictions <- data.frame()
-
-for (p in example.habituals.actions){
- priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
-
- inputData = list(priorParams = priorParams,
-                  utt = "habitual")
-
- l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
-
- hab.listener.predictions <- bind_rows(
-   hab.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
-   )
-
-}
-
-# m.gen.fullmodel.target.prevalence <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   group_by(param, property, category) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-# m.gen.speakerBeliefs <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   mutate(Sentence = paste(category, property)) %>%
-#   filter(Sentence %in% example.generics)
-
-# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-# gen.inset.distributions <- bind_rows(
-#   gen.listener.predictions %>%
-#     mutate(category = NA),
-#   m.gen.speakerBeliefs %>%
-#     select(property, val) %>%
-#     rename(value = val) %>%
-#     mutate(Parameter = "speakerBeliefs")
-# )
-# 
-# 
-# category.text.labels <- data.frame(property = c("dont eat people", 
-#                       "carry malaria", "lay eggs",  "are female", "have spots"),
-#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Habitual")),
-         action = fct_relevel(action,
-                                "climbs mountains", "hikes", "runs",
-                              "goes to the movies", "smokes cigarettes"
-                              ) ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~action, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
-  #scale_linetype_manual(values = c(3, 4, 1))+
-  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
-      scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-```
-
-```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
-Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
-These distributions are inferred using both data sources from Expts.
-2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
-grid.arrange(fig.habituals.endorsement.vs.freq, 
-             habituals.endorsement.models,
-             habituals.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the referent character.
-<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
-
-<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
-Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
--->
-
-<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
-<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
--->
-<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
--->
-<!-- We see no appreciable differences in endorsements for the two genders.  -->
-<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
-<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
-
-#### Referent frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
-This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-#### Distinctiveness and referent frequency
-
-In the prior elicitation task (Expt.
-2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
-With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
-
-```{r habituals-distinctiveness-counterexamples}
-
-format_endorsment_ci <- function(
-  df, estimate = "MAP_h", low = "low",
-  high = "high", sigfigs = 2){
-  return(paste(
-    round(df[[1,estimate]], sigfigs),
-    " [",
-    round(df[[1,low]], sigfigs),
-    ", ",
-    round(df[[1,high]], sigfigs),
-    "]", sep = ""))
-}
-
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
-
-movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
-                                                        time_period == "year"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
-
-banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
-                                                        time_period == "2 years"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-```
-
-We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture some of the subtle sensitivities in endorsments.
-For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold RSA model
-
-The above regression models are too rigid to explain the flexibility in habitual endorsements. 
-Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
-Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
-To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
-
-We used the speaker model $S_1$ (Eq.
-\ref{eq:S1}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.
-2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
-The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
-As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
-2b.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
-
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
-Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
-\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
-The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
-The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
-Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
-
-Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
-With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
-Thus, this model makes the same predictions for different target frequencies in the same event.
-For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.
-
-#### Uncertain-threshold RSA model
-
-We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-
-### Discussion
-
-In Expt.
-2b, we manipulated the event type (e.g., drinks coffee vs.
-beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
-year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
-
-Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
-The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
-
-Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
-
-<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
-
-<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
--->
-
-<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
-<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
-<!--   Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
--->
-<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
-<!--   \label{fig:tj3} -->
-<!--   \vspace{-7pt} -->
-<!-- \end{figure*} -->
-
-## Experiment 2c: Measuring predictive frequency
-
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
-       aes(x=logAnnualPastRate,
-                              y = mean,
-                              ymin = ci_lower, ymax = ci_upper,
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
-  scale_shape_manual(values=c(21,22,23))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-
-fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
-  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
-                 fill=condition, shape=condition,
-                 xmin = future_lower, xmax=future_upper,
-                 ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.8)+
-  geom_errorbarh(alpha=0.8)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 1, size = 4)+
-  xlab("Predicted frequency (log scale)")+
-  ylab("Human habitual endorsement")+
-  scale_x_continuous(limits = c(-4.2,7.2), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=11.4)+
-  scale_fill_solarized()+
-  guides(fill = F, shape = F)+
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-    legend.position="bottom",
-    legend.direction="horizontal"
-    )
-
-```
-
-```{r habituals-predictive-rsa}
-n_chains <- 3
-# n_samples <- 500000
-# burn <- n_samples / 2
-# lg <- 150
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 50
-
-m.hab.pred.samp <- data.frame()
-m.hab.past.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-
-  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "targetH_past-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-
-#}
-# 
-# 
-# # 
-# save(m.hab.pred.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# # # 
-# save(m.hab.past.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
-
-m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorsement <- m.hab.pred.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.predictive.endorsement
-  ) %>%
-    mutate(src = "predictive_model"),
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.pastmodel.endorsement
-  ) %>%
-    mutate(src = "past_model")
-)
-
-r2.habituals.rsa.past <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.past <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.predictive <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.predictive <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
-
-habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - past frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-
-habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  #guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-#habituals.predictive.predictive.model
-```
-
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
-grid.arrange(
-  arrangeGrob(
-    fig.hab.freq.predictive.vs.past, 
-    fig.hab.endorse.vs.predfreq, 
-    habituals.predictive.past.model, 
-    habituals.predictive.predictive.model + theme(legend.position="none"),
-    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
-legend_b, nrow=2,heights=c(8, 1))
-
-#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 2c.
-The only difference from Expt. 2c is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-
-When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
-], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
-
-We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
-The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
-
-We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
-Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
-The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
-
-<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
-<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
-<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
-<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
-<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
-This may be due, in part, to an effect of the experimental context on participants:
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
-## Discussion
-
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
-2a).
-We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
-By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
-In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
-Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
-
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2d).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
-
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
-Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
-
-# Case Study 3: Causal Language
-
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
-
-Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
-In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
-<!-- [Gerstenberg] -->
-Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
-Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
-
-Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
-
-In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
-
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
-In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 3a: Manipulating the feature-probability priors for causes
-
-In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our feature-probability prior manipulation.
-
-<!-- examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present. -->
-<!-- We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains. -->
-
-<!-- People have theories about how different casusal systems work.  -->
-<!-- Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force.  -->
-<!-- If the experiment is repeated exactly, we would expect the same results. -->
-<!-- In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't.  -->
-<!-- Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
--->
-
-### Method
-
-```{r causal-priors-data}
-d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
-                           sep= ""))
-
-n.subj.cas <- length(unique(d.cas.priors$workerid))
-
-ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-```
-
-```{r causal-priors-runModel, cache = T}
-causal.distributions <- levels(factor(d.cas.priors$distribution))
-p <- causal.distributions[1]
-m.cas.marginal.prevalence <- data.frame()
-m.cas.endorse.priors.summary <- data.frame()
-
-for (p in causal.distributions){
-  priorData <- 100*filter(d.cas.priors, distribution == p)$response
-
-  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
-
-  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
-    spread(Parameter, value) %>%
-    rowwise() %>%
-    mutate(
-      a = g * d,
-      b = (1 - g) * d,
-      stable = rbinom(n = 1, size = 1, prob = phi),
-      prevalence = ifelse(stable == 1, 
-                             rbeta(n = 1, shape1 = a, shape2 = b),
-                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
-      distribution = p
-    )
-  )
-
-  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
-                                            m.cas.endorse.priors %>% 
-                                              mutate(distribution = p) %>%
-                                              group_by(distribution, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-}
-
-```
-
-#### Participants
-
-We recruited `r n.subj.cas` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average `r ave.minutes.cas` minutes and participants were compensated \$0.50 for their work.
-
-<!-- The different kinds of system are described in more detail below. -->
-<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->
-
-#### Procedure
-
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
-
-In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
-The story for the "sleepy animals" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. 
-Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-The results are shown below:
-\end{quotation}
-
-Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
-
-Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
-
-#### Materials
-
-Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
-The cover story for the "tall plants" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
-Your team runs experiments trying to make feps grow tall with different fertilizers. 
-The results are shown below:
-\end{quotation}
-
-Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
-In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
-
-```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-4 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3, eval = F}
-sample.dists <- bind_rows(
-  data.frame(
-    dist = "rare weak",
-    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common weak",
-    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
-  ),
-  data.frame(
-    dist = "rare deterministic",
-    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common deterministic",
-    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
-  )
-) %>%
-    mutate(Distribution = factor(dist, 
-                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak")))
-
-figure.causals.priors <- bind_rows(
-  sample.dists %>%
-    mutate(src = "stimuli") %>%
-    select(-dist),
-  m.cas.marginal.prevalence %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
-    mutate(Distribution = factor(distribution, 
-                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))) %>%
-    select(Distribution, prevalence) %>%
-    mutate(src = 'model') %>%
-    rename(x = prevalence)
-) %>%
-  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
-                ))+ 
-  geom_density( adjust = 1.3, 
-               size = 1.2,
-               aes( y = ..scaled..))+ #
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_fill_solarized()+scale_color_solarized()+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0.1, 0.4))+
-  scale_linetype_manual(values = c(2, 1))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
-  guides(fill = F, color = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal')
-```
-
-```{r s1-model}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-var alpha = 2;
-var mixture = data.prior[0].phi;
-var priorParams = betaShape(data.prior[0]);
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var speaker1 = function(state) {
-  Infer({model: function(){
-    var utterance = sample(utterancePrior);
-    var listener_posterior = listener0(utterance);
-    factor(alpha * listener_posterior.score(state))
-    return utterance
-  }})
-}
-
-probability(speaker1(data.state[0]), "generic")
-'
-```
-
-```{r causal-endorsement-predictions, cache = T, eval = F}
-causal.priorParams <- m.cas.endorse.priors.summary %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           Parameter != 'marginalPrevalence') %>%
-  select(distribution, Parameter, MAP) %>%
-  spread(Parameter, MAP)
-experimental.frequencies <- c(0.2, 0.7)
-causal.endorsement.predictions <- data.frame()
-for (p in causal.priorParams$distribution){
-  for (s in experimental.frequencies){
-
-    inputData = list(prior = filter(causal.priorParams, distribution == p), 
-                     state = s)
-
-    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
-
-    causal.endorsement.predictions <- bind_rows(
-      causal.endorsement.predictions,
-      data.frame(state = s, distribution = p, prob = s1.rs)
-    )
-  }
-  print(p)
-}
-```
-
-<!-- #### Materials  -->
-
-<!-- The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model. -->
-<!-- Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
--->
-<!-- So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.  -->
-
-<!-- A second dimension of man ipulation corresponds to the extent to which *determinism* is expected in the domain.  -->
-<!-- For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.  -->
-
-### Results
-
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
-These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
-We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
-
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
-
-d.cas.priors %>%
-  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
-      mutate(Distribution = factor(distribution, 
-                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>% 
-ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 0.8, alpha =0.8, 
-               size = 1.2,
-               aes( y = ..scaled..))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
-```
-
-### Model predictions
-
-... run RSA model using fixed parameters and MAP estimates of these priors ?
-
-## Experiment 3b: Endorsing Causal Language
-
-In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-
-### Method
-
-Most of the experiment was identical to that of Experiment 3a.
-
-```{r causal-endorsement-data}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
-ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-
-n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-```
-
-#### Participants
-
-We recruited `r n.subj.cas.endorse` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 3a. 
-The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 3a.
-Phase 1 of the experiment was identical to that of Experiment 3a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
-Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Partipants responded by either clicking "Yes" or "No".
-
-After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
-
-```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Target frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-```{r causals-fullmodel}
-n_chains <- 1
-n_samples <- 5000
-burn <- n_samples / 2
-lg <- 5
-i <- 1
-
-model_prefix <- "pilot-results-causals-jointModel-S1-"
-
-m.cas.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/causals/results/", 
-                    model_prefix, "smntcs_causal-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
-}
-
-# n_chains <- 1
-# n_samples <- 1000
-# burn <- n_samples
-# lg <- 5
-# i <- 1
-# m.hab.fixed.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/", 
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-# }
-
-# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-#   filter(type == 'predictive') %>%
-#   rename(habitual = B, time_period = D, binned_freq = E) %>%
-#   group_by(habitual, time_period, binned_freq) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.cas.fullmodel.endorsement <- m.cas.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(dist, frequency) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
-m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
-  filter(type == "prior") %>%
-  rename(variable = item, parameter = roundedFreq) %>%
-  group_by(dist, variable, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
-
-m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(dist, variable, parameter, MAP) %>%
-  mutate(param = paste(variable, parameter, sep = "_")) %>%
-  select(-variable, -parameter) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-cas.listener.predictions <- data.frame()
-
-for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
- priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- cas.listener.predictions <- bind_rows(
-   cas.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
-   )
-}
-
-inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
-
-causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, 
-                              levels = c("state_Prior","state_Posterior"),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Causal")),
-    Distribution = factor(distribution, 
-                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>%
-  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~Distribution, nrow = 1)+
-  scale_fill_manual(values =inset.color.order )+
-  scale_color_manual(values = inset.color.order)+
-  scale_alpha_manual(values = c(0.1, 0.8))+
-  scale_linetype_manual(values = c(2, 1))+
-  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Feature-probability") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)
-```
-
-```{r}
-md.caus.endorse <- left_join(
-  m.cas.fullmodel.endorsement,
-    d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution)
-)
-
-n.caus.endorse <- length(md.caus.endorse$MAP_h)
-r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
-mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")
-
-```
-
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
-figure.causals.endorsement <- bind_rows(
-  m.cas.fullmodel.endorsement %>%
-    mutate(src = "model"),
-  d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
-    mutate(src = 'data')
-) %>%
-  ungroup() %>%
-  mutate(
-    src = factor(src, levels = c( "data", "model")),
-    dist = factor(dist, 
-           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
-           labels = c(
-                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
-    ) %>%
-  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = src, alpha = src))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(0.3), alpha = 1)+
-  #geom_line(position = position_dodge(0.3))+
-  #theme(axis.text.x = element_text(angle = 90))+
-  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_alpha_manual(values = c(1, 0.3))+
-  #scale_fill_solarized()+
-  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("")+
-  ylab("Proportion Causal Endorsement")+
-  facet_grid(.~frequency)+
-  coord_flip()+
-  guides(fill = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
-```
-
-```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
-Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
-These distributions are inferred using both data sources from Expt.
-3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
-grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
-             layout_matrix = cbind(c(1,1,2)))
-
-# ,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-### Results
-
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
-
-As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
-When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
-By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
-The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
-
-## Discussion
-
-In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
-We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
-In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
-
-In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
-These two features of the domains make them particularly amenable to manipulation.
-That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
-
-It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
-If this were happening in our domains, we would expect this to show up in the results of Expt.
-3a.
-Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
-]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
-
-# General Discussion
-
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
-As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
-
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
-
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
-
-In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge and implications for conceptual accounts
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
-In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
-As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
-] 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
-In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
-
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expts.
-2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
-
-The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
-Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
-This prior could then be updated with more data to acquire its fixed meaning.
-For the generic statement, the language learner is done once she acquires (1). 
-The rest of the meaning is inferred in context.
-With that lens, generic meaning would be primary, while quantified utterances would be refinements.
-
-There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
-A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-
-This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
-
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical Accounts
-
-Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
-
-### Conceptual Accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-
-This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
-In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
-4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
-However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
-
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
-]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-```{r child = 'appendix-bda.Rmd'}
-```
-
-```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-```
+In our second case study, we extend the theory to the domain of events and provide the first evidence that the factors identified by our theory are causally related to endorsement. 
+<!-- This evidence is correlational in nature, however. -->
+<!-- We do not yet know if the variables that we are measuring are causally related to endorsement. -->

### 2017-11-11 paper/case2-habituals.Rmd
edits to end of generics; half of habituals; modularize paper into separate files for each case study

--- 2017-11-03 paper/comgen-paper.Rmd
@@
----
-title             : "The language of generalization"
-shorttitle        : "The language of generalization"
-
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-  - \usepackage{amsmath}
-  - \usepackage{graphicx}
-  - \usepackage{subcaption}
-
-author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
-
-abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which such statements are true or which are false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of language conveying generalization, while simpler models fall short.
-    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results suggest the central phenomena emerge from the interaction of underspecified meaning with diverse beliefs about properties.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "20000"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-
-\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
-\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
-\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
-```
-
-```{r libraries, cache = F}
-library(papaja)
-library(formatR)
-library(rwebppl)
-library(xtable)
-library(tidyverse)
-library(forcats)
-library(langcog)
-# library(dplyr)
-library(data.table)
-library(coda)
-library(ggthemes)
-library(ggrepel)
-library(jsonlite)
-library(gridExtra)
-library(lme4)
-library(knitr)
-library(cowplot)
-theme_set(theme_few())
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-logmeanexp <- function(x){
-  x.num <- as.numeric(x)
-  xstar = max(x.num)
-  return(xstar + log(mean(exp(x.num - xstar))))
-}
-
-compute_r2 <- function(df,v1, v2, sigfigs = 3){
-  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
-}
-
-compute_mse <- function(df, v1, v2, sigfigs = 3){
-  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
-}
-
-project.path <- "../"
-options("scipen"=10) 
-```
-
-<!-- 
-possible titles:
-- Communicating generalizations
-- The language of generalization
-- The language of generalization: Probability, vagueness, and interaction
--->
-
-# Introduction
-
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
-
-<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
-<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
-<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
-<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
--->
-<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
-<!-- \ndg{this par doesn't really do much} -->
-
-The language of generalization is often studied via *generic language* (or, generics): simple statements  about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
--->
-Generics are just one case of the language of generalizations, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
-
-<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
-<!-- Individual entities can also be talked about in generalization, using so-called  -->
-<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
-<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
-
-Despite their ubiquity and relative simplicity, there have been few formal models of this language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining *what makes the statements true or false*.
-When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
-The generalization could signal something weaker like "Most dogs bark".
-However, "Most mosquitos do not carry malaria" (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to "some" is too permissive: "Some Robins are female" (in fact, half of them are), but asserting "Robins are female" seems odd.
-Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
-
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not central to the meaning of generalizations in language.
-Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-A paradigm case is the statement "Bishops move diagonally", which is true but not because bishops tend to move diagonally but rather because those are the rules of the game.
-It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
-One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.
-Whatever their mode of reproduction, regardless of the actual prevalence of the feature, will make a true generic statement (e.g., "Robins lay eggs").
-*Horrifying* or *striking* is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is felicitous.
-
-Examining a wider range of examples makes one realize that generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships sound like true generics true.
-<!-- Arbitrary relationships are also expressed with generics:  -->
-For example, "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are blue" would be true.
-Ravens and toasters have no priviledge relationship to each other, but the statement "Ravens are bigger than toasters" is still a true genaralization.
-Conceptual accounts must then be supplemented with the proviso that, in some situations, the actual prevalence of the feature does influence human intuitions about generics.
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that we can describe as communicating generalizations, there should be something common to them all: a general, unified semantic core.
-The test of a unified semantic core is its ability to explain what makes the statements true or false.
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-
-In this paper, we propose a semantic core for the language of generalization.
-To do so, we look to probability, a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-We then consider the background knowledge that listeners bring to bear when interpreting generalizations, and formalize an endorsement model based on this interpretation hypothesis.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-Our endorsement model is the first formal theory that makes quantitative predictions about what makes generalizations in language true or false; the assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-
-<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
--->
-
-<!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
--->
-<!-- In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000]. -->
-<!-- We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement. -->
-<!-- We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...} -->
-<!-- We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
--->
-
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
-The paper is organized as follows. 
-In Section 1, formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
-Sections 2 - 4 presents our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-<!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
--->
-<!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-<!-- This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.  -->
-
-# Computational Framework
-
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
-
-How does one come to have an $h$ in their head?
-One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
-But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
-For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Relying upon observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), it is better to learn from others.
-Fortunately, language has simple ways of encoding generalizations.
-
-<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
-<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
-<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
--->
-<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
-<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
--->
-<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
-
-<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
-<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
--->
-<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
-<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
--->
-
-<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
-<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
-<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
--->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
--->
-<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
-<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
-
-<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
-<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
--->
-<!-- \ndg{what is this par doing for us? delete?} -->
-<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
-<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
--->
-<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
--->
-<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
--->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-
-## Generalization from language
-
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity to be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
-One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlaizaion would then apply to the *feature-probability* $h$:
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-We emphasize that this account is based on a probability $h$.
-The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[
-  There has also been substantial discussion of *cue validity* , which we come back to below.
-]
-Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself. 
-Probability is a measure of belief.
-
-### Semantics and background knowledge
-
-What threshold $\theta$ should be used for the generalization?
-We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
-
-\begin{eqnarray}
-Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
-We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
-The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}\label{eq:delta}
-\end{eqnarray}
-
-Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
-
-### Endorsement model
-
-The above model determines how $\theta$ should be resolved in context.
-Now, how do we decide when a statement conveying a generalization is true or not?
-To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
-The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
-
-\begin{equation} 
-E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
-\label{eq:S1}
-\end{equation}
-
-Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
-
-The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
-Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
-$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
-]
-The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
-This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]
-
-\begin{equation} 
-U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
-\end{equation}
-
-Thus, Eq.
-\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
-Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
-
-The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
-
-Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
-The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
-However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
-
-### The feature-probability prior and model simulations
-
-The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
-We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
-We implemented the models in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
-
-```{r simluationsModel, eval = T, cache = T}
-l0.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
-'
-
-priorNames <- c(
-  "doesntEatPeople", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria",
-  "hasSpots"
- # "areSick"
-  )
-priorShapes <- list(
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-all.simulations <- data.frame()
-for (p in priorNames){
-  for (u in c("generic")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
-    )
-  }
-  #print(p)
-}
-```
-
-```{r simluationEndorsementModel, eval = T, cache = T}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.mix[0];
-var priorParams = data.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-var alpha = 2
-
-var endorser = function(featureProb){
-  Infer({model: function(){
-    var endorsement = sample(utterancePrior)
-    var L0 = marginalize(listener0(endorsement), "state_Posterior")
-    factor(alpha * L0.score(featureProb))
-    return endorsement
-  }})
-}
-
-probability(endorser(data.featureProb[0]), "generic")
-'
-
-exampleGenerics <- c(
-  "sharksDontEatPeople",
-  "robinsAreFemale", 
-  "robinsLayEggs", 
-  "kangaroosHaveSpots",
-  "dogsBark",
-  "mosquitosCarryMalaria"
-  )
-exampleParameters <- list(
-  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
-  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
-  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
-  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
-  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
-)
-
-s1.simulations <- data.frame()
-for (p in exampleGenerics){
-
-    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
-    s1.simulations <- bind_rows(s1.simulations,
-                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
-
-}
-
-```
-
-```{r}
-s1.simulations.relabeled <- s1.simulations %>%
-  mutate(example = factor(example, 
-                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-  #geom_jitter(width = 0.1, shape = 21, size = 5)+
-  #ylab("Human endorsement probability")+
-  #xlab("Frequency of target")+
-  geom_label_repel(data = s1.simulations.relabeled, 
-                   aes( label = example, fill = example),
-                       color = 'white',
-    box.padding = unit(0.0, "lines"),
-    #point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37')+
-  scale_fill_solarized()+
-  scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
-  coord_fixed(ratio = 1)+
-  guides(fill = F)+
-  ylab("Endorsement model prediction")+
-  xlab("Hypothesized feature-probability")
-
-```
-
-```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
-all.simulations.refactored <- all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                                c( "Prior_generic", "Posterior_Generalization_generic"),
-                                labels = c( "Prior/Silence", "Generalization")
-                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
-                             ),
-         PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
-                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         )
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability h") +
-    ylab("Scaled prior probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-```
-
-```{r simulations, fig.cap = "Model behavior.
-Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
-grid.arrange(l0.simulations.distributions, 
-             s1.simulations.scatter, ncol = 3,
-             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
-
-```
-
-These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-]
-
-Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
-The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
-The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
-]
-The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
-
-How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
-For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
-The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
-"Robins lay eggs", however, has a lot of informational content.
-
-Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
-Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
-
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the feature-probability priors $P(h)$.
-In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
-
-# Case Study 1: Generic Language
-
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-Generics have been the case study of choice for generalizations in language because of theiry vexing similarity to quantified statements (e.g., "*Most* dogs bark").
-Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
-Here, we take our first look at the
-
-Here, we take 
-Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
-
-We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
-"Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
-1a).
-
-We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
-Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
-\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
-To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
-
-## Experiment 1a: Generic endorsements
-
-In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
-The goal of this study is to observe a range of endorsements for generic statements about animal categories.
-
-#### Method
-```{r eval = F}
-d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "naturalGenerics-trials-formatted.csv", sep = ""))
-
-# write.csv(
-#   left_join(
-#   d1 %>%
-#     mutate(sentence = as.character(sentence),
-#            sentence = gsub('&quotechar', '', sentence),
-#          sentence = gsub('lyme', 'Lyme', sentence)),
-#   unique(d2 %>%
-#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-#     select(Category, Property, sentence))
-# ), file = paste(project.path, "data/generics/endorsement/",
-#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
-```
-
-```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(col = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup()
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
-  filter(item %in% d.gen.endorse.bayes$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(col = "prevalence")
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- left_join(
-  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
-) %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
-  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("Human generic endorsement")+
-  xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'feature probability',
-                               ticks = F))+
-  theme(legend.position = 'bottom')
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
-```
-
-##### Participants
-
-We recruited 100 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
-The experiment took about 3 minutes and participants were compensated \$0.35.
-
-##### Procedure and materials
-
-Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
-As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
-
-#### Results
-
-```{r generic-endorsement-manipulationcheck}
-# MHT's truth judgments of sentences
-# t --> true; f --> false; i --> indeterminate/uncertain
-all.sentences <- list("Cardinals are red." = "t",
- "Ducks have wings." = "t",
- "Kangaroos have pouches." = "t",
- "Kangaroos have spots." = "f",
- "Leopards are juvenile." = "i",
- "Leopards have spots." = "t",
- "Leopards have wings." = "f",
- "Lions are male." = "i",
- "Lions have manes." = "t",
- "Lions lay eggs." = "f",
- "Mosquitos attack swimmers." = "i",
- "Mosquitos carry malaria." = "t",
- "Mosquitos dont carry malaria." = "f",
- "Peacocks dont have beautiful feathers." = "f",
- "Peacocks have beautiful feathers." = "t",
- "Robins are female." = "i",
- "Robins carry malaria." = "f",
- "Robins lay eggs." = "t",
- "Sharks are white." = "i",
- "Sharks attack swimmers." = "t",
- "Sharks dont attack swimmers." = "f",
- "Sharks have manes." = "f",
- "Sharks lay eggs." = "i",
- "Swans are full-grown." = "i",
- "Swans are white." = "t",
- "Ticks carry Lyme disease." = "t",
- "Ticks dont carry Lyme disease."= "f",
- "Tigers dont eat people."= "f",
- "Tigers eat people." = "t",
- "Tigers have pouches."= "f")
-
-mht.truth.judgments <- data.frame(sentence = names(all.sentences),
-           truth_judgment = as.vector(unlist(all.sentences)))
-
-d.gen.endorse.manipulation.check.bayes <- left_join(
-  left_join(
-    d.gen.endorse, 
-    d.gen.endorse.catch %>% select(workerid, pass)
-    ),
-  mht.truth.judgments ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(truth_judgment) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
-
-true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
-true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
-true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]
-
-false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
-false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
-false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]
-
-uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
-uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
-uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
-
-```
-
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
-Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
-
-## Experiment 1b: Feature-probability prior elicitation
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
-Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
-Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
-].
-
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-
-### Method
-
-#### Participants
-
-We recruited 60 participants over Amazon MTurk.  
-3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-#### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
-A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
-Eight property--columns appeared in the table.
-
-This whole procedure was repeated two times (two trials).
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
-
-### Results
-
-In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
-We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
-\text{has wings}).
-For model implementation and inference details, see Appendix.
-
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
-There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
-One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
-
-<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
--->
-<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
-load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
-           aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
-    xlab("Feature-probability") +
-    ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
-## Endorsement model comparison
-
-To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
-1b), from which the interpreter model infers likely thresholds for the generic.
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
-As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of the uncertain-threshold hypothesis.
-
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:10){
-
-  d.cv.bsample <- d.cv %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.gen.cv.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped %>%
-      group_by(property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
-# 
-# d.cv.bootstrapped %>%
-#   group_b
-
-# need to filter by items specified with endorsement
-# d.gen.cv.summary <- left_join(
-#   d.target.items %>% select(-sentence),
-#   d.cv %>%
-#     rename(category = response) %>%
-#     group_by(property) %>%
-#     mutate(n = n(),
-#            item = paste(category, property)) %>%
-#     filter(item %in% d.target.items$item) %>%
-#     group_by(category, property) %>%
-#     summarize(mentions = n(),
-#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-#               prop = mentions / trials)
-#   ) %>%
-#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prev_mean = mean,
-             sentence = item,
-             prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper) %>%
-      ungroup() %>%
-      mutate(sentence = gsub('[.]', '', sentence))
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prev_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.prev.cue.uniq <- unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, 
-    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
-  ))
-
-d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_lower,
-         cv_mean = cv_ci_lower)
-d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_upper,
-         cv_mean = cv_ci_upper)
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
-
-r2.gen.n <- length(d.gen.endorse.bayes$sentence)
-r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)
-
-r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
-mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)
-
-intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))
-
-d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
-  filter(
-    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
-    (prev_mean < intermediate.prev.quantiles[["76%"]])
-)
-r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)
-
-r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
-```
-
-### Baseline models
-
-#### Referent feature-probability
-
-From the feature-probability prior data (Expt.
-1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
-
-However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
-
-#### Cue validity and referent feature-probability
-
-##### Model specification
-
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* thus captures the distinctiveness of the feature for the category. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
-In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
-
-##### Results
-
-A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of a simple model based on cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A simple metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
-
-### Information-theoretic endorsement models
-
-The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
-Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
-We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
-We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
-
-For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
-  Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-  This corresponds to the more general form of the model described in a footnote in the model section. 
-  For these data, the predictions of these two models are nearly identical.
-]
-(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Appendix and Figure \ref{fig:genericsModelDiagram}).
-
-#### Fixed-threshold model
-
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
-
-```{r generic-RSAmodels, fig.width = 8}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
-
-# m.samp <- data.frame()
-# m.samp.fixed <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-#   
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-#   }
-# 
-# save(m.samp,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.samp.fixed,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.gen.rsa.generics <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-r2.gen.rsa.fixed <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-mse.gen.rsa.generics <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-mse.gen.rsa.fixed <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression,
-  left_join(
-    m.gen.endorse.rsa %>% 
-      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-      select(sentence, Property, Category, prev_mean, cv_mean)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( "some_model",
-                                      "generics_model",
-
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c("Fixed semantics model",
-                                 "Uncertain semantics model",
-
-                                 "Feature-probability alone",
-                                 "Cue validity + Feature-probability"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.4)+
-  geom_errorbarh(alpha = 0.4)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human generic endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  #theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
-    filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_label_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
-    ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-```
-
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
-Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
-Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
-These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
-
-We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
-Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-The model fails to distinguish any of the generic sentences because they are all somewhat true. 
-All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
-
-The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
-For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
-Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
-This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
-The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
-
-\mht{Outfit fixed-threshold model with noise parameter?}
-
-### Uncertain threshold RSA model
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-
-To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
-It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
-"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
-
-## Discussion
-
-Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-This evidence is correlational in nature, however.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
 # Case Study 2: Habitual Language
 
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
-Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
-While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
-]
-
-We follow the same general experimental structure as in Experiment 1. 
+<!-- THINK ABOUT: -->
+<!-- Kelley, H. H. (1973). The processes of causal attribution. American psychologist, 28(2), 107-128. -->
+<!-- Orvis, B.
+R., Cunningham, J.
+D., & Kelley, H.
+H.
+(1975).
+A closer examination of causal inference: The roles of consensus, distinctiveness, and consistency information.
+Journal of Personality and Social Psychology, 32(4), 605-616.
+-->
+
+We meet new people all the time, and hear about them at least as often.
+*Habitual language* (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events, including people doing actions. 
+<!-- In this case study, we focus on a particular class of events: people doing actions. -->
+Habituals about people taking actions are of particular importance to social psychology because of their role in causal attribution [@Kelley1973] and intuitive theories of personality and behavior [@McGuire1986].
+Habitual language may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
+
+We use the same computational model and follow the same general experimental structure as in the first case study. 
+We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes."). 
 First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
+We do this using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b.
+Then, we test our model on endorsements of habitual sentences, manipulating the frequency of a referent person doing an action (Expt. 2b).
 In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
+We have said that $h$ represents a probability that a speaker aims to convey.
 In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
+We do this by measuring participants' predictions about future rates when causal forces enable or prevent the action (Expt. 2c). 
 We separately measure endorsements under the same contexts (Expt.
 2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
+2c) as the referent feature-probabilities $h$ that the endorsement model is trying to communicate.
+
+<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
+<!--  explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family".  -->
+<!-- A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
+-->
 
@@
 
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
-To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
-The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
-This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
+In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2d).
+For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the likely frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
+We designed our elicitation task to take advantage of the mixture-model representation of the feature-probability prior used in Expt.
+1 (namely: that the distribution over a feature-probability can be represented as a mixture of probabilities from those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
+For background knowledge of people doing actions, we consider again two components^[
+  In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
   We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
+], which we operationalize by *people who have done the action before* and *people who have not the action before*.
+We measure how often people do the action, among those who have done it before, as well as the people's beliefs about the how many people have done the action before; we assume for simplicity that people who have never done the action before will rarely do the action.
+
+<!-- In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components. -->
+<!-- The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature. -->
+<!-- The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property.  -->
+<!-- This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
+-->
 
@@
 
-For each event, participants were asked two questions, with associated dependent measures:
+For each event, participants were asked two questions, with different dependent measures:
 
@@
 
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
-After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
+For example, one set of prompts read: *How many women have smoked cigarettes before?*; *For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?*
+The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials, and tested for recall on a subsequent trial.
+<!-- After reading the instructions, participants were asked to recall the two types of questions. -->
 They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-They did this to test their understanding and attention for each of the two questions.
-
-For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
+<!-- They did this to test their understanding and attention for each of the two questions. -->
+For the experimental trials, we anticipated there to be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
 Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
@@
 
-### Data analysis and results
+### Results
 
 All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-We built a Bayesian data analysis model for this prior elicitation task.
+Question 1 elicits the proportion of people who have done an action before. 
+We rescale this to be a number between 0 and 1, and assume it was generated from a Beta distribution: $d_{Q1} \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1})$. 
+Question 2 elicits the rate or frequency with which a person (who has done the action before) does the action.
+We model this as generated by a log-normal distribution: $\ln d_{Q2} \sim \text{Gaussian}(\mu_{Q2}, \sigma_{Q2})$.
+Each item was modeled independently for each gender.
+We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
+
+The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter):
+We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
+Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
+This diversity is relevant because the speaker model (Eq.
+\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
+the ballet.}) contingent on the shape of the prior distribution.
+
+To generate feature-probability prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
+The only difference is that we estimate the mixture component directly from responses to Question 1. 
+We assume that those who have not done the action before will probably not do the action in the future. 
+With these assumptions, the feature-probability distribution is given by:
+
+\begin{align}
+\phi & \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1}) \nonumber \\ 
+\ln h & \sim \begin{cases}
+		\text{Gaussian}(\mu_{Q2}, \sigma_{Q2}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
+				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
+		\end{cases}
+\end{align}
+
+Figure \@ref(fig:habituals-prior-figure) (right) shows example reconstructed priors.
 In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
@@
 
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate or frequency with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
+<!-- Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
+-->
+<!-- That is, $P(h)$ was constructed by sampling $\lambda$ as follows: -->
+
+<!-- We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
+-->
+<!-- We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$. -->
+<!-- If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
 This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
+-->
+<!-- If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before. -->
+<!-- We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years). -->
 
@@
 
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
+We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task (Expt. 2a).
 
@@
 On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
+For example, "In the past month, Bill smoked cigarettes 3 times".
+The particular intervals used (\{weeks, months, years\}) were selected by simulating predictions of the endorsement model (Eq.
+\ref{eq:S1}) with the goal of yielding a range of predicted endorsement rates.
+The items were the same as in the prior elicitation task (Expt. 2a).
+
+Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
 Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
-<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
+Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
+These were used for an exploratory analysis on differences in endorsements by gender of the target character.
 
@@
 ```
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
 
@@
 <!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the referent character.
+Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model to better understand the data and the contribution of our model.
+For all analyses, we collapse across gender of the referent character.^[
+  In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
+  This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
+  Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
+]
 <!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
@@
 
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
-This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
+The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
+Several features in our data argue against this hypothesis.
+<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
+-->
+When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
+When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
 In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
 Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-#### Distinctiveness and referent frequency
-
-In the prior elicitation task (Expt.
-2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
-With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
+In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
+
+<!-- This is unlikely to be the case based on , which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
+-->
+
+#### Distinctiveness and referent frequency baseline
+
+In our empirically elicited priors, items differ in their mixture parameter reflecting the proportion of people who have done the action before (Figure \@ref(fig:habituals-prior-figure)).
+This could be seen as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
+A plausible alternative hypothesis is thus that some simple combination of frequency and distinctiveness information predicts habitual endorsements. 
+Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency to predict habitual endorsement.
 
@@
 Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture some of the subtle sensitivities in endorsments.
-For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold RSA model
-
-The above regression models are too rigid to explain the flexibility in habitual endorsements. 
-Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
-Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
-To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
-
-We used the speaker model $S_1$ (Eq.
-\ref{eq:S1}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.
-2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
-The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
-As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
+Still, this model is not able to capture fine-grained details in endorsments.
+For example, going to the movies is relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
+On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual, according to participants $`r banjo.2years.data`$.
+Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
+
+#### Fixed-threshold endorsement model
+
+We next examine an endorsement model based on a fixed-threshold semantics.
+A fixed-threshold model only conveys that a person *has done this action before*, analagous to how the quantifier "some" conveys that there exists at least one entity with the feature.
+As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to simultaneously predict both the priors data and the endorsement data.
+We assume the referent feature-probability $h'$ being conveyed by $Endorse$ (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
+Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$.
+To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 3 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
+
+<!-- The above regression models are too rigid to explain the flexibility in habitual endorsements.  -->
+<!-- Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge.  -->
+<!-- Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold. -->
+<!-- To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
+-->
+
+<!-- The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}.  -->
+<!-- As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
 2b.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
+-->
 <!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
 
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
-Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
-\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
-The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
-The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
-Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
-
+An endorsement model with fixed-threshold semantics has trouble differentiating between different habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet), as all of the items used in our experiment are literally true under a fixed-threshold semantics.
+In addition, the model exhibits a small dynamic range of endorsment, because the two options for the endorsement model (silence or a very low, fixed thresold) are only subtly different with respect to information conveyed.
 Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
@@
 For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month. 
-
-#### Uncertain-threshold RSA model
-
-We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
+Overall, this model is poor at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
+
+#### Uncertain-threshold endorsement model
+
+We used the same data analytic approach for the uncertain threshold endorsement model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
+As shown in Figure \@ref(fig:habituals-endorsement-figure) (top right: top right facet), the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
+Figure \@ref(fig:habituals-endorsement-figure) (bottom, insets) provides insight into how the model is able to do this. 
+An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is good statement to assert. 
+Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas the someone who went to the movies 3 times last month is fully a person who "goes to the movies".
+Only the uncertain-threshold model is able to draw this fine distinction.
 
@@
 year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
-
+We saw tremendous flexibility in the frequencies that leads participants to endorse habituals. 
 Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
 The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
-
-Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
+This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* endorsement model is doing.
+
+In this case study, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
+By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model. 
 The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
+
+<!-- People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation.  -->
 
@@
 
-# Case Study 3: Causal Language
-
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
-
-Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
-In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
-<!-- [Gerstenberg] -->
-Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
-Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
-
-Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
-
-In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
-
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
-In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 3a: Manipulating the feature-probability priors for causes
-
-In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our feature-probability prior manipulation.
-
-<!-- examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present. -->
-<!-- We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains. -->
-
-<!-- People have theories about how different casusal systems work.  -->
-<!-- Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force.  -->
-<!-- If the experiment is repeated exactly, we would expect the same results. -->
-<!-- In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't.  -->
-<!-- Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
--->
-
-### Method
-
-```{r causal-priors-data}
-d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
-                           sep= ""))
-
-n.subj.cas <- length(unique(d.cas.priors$workerid))
-
-ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-```
-
-```{r causal-priors-runModel, cache = T}
-causal.distributions <- levels(factor(d.cas.priors$distribution))
-p <- causal.distributions[1]
-m.cas.marginal.prevalence <- data.frame()
-m.cas.endorse.priors.summary <- data.frame()
-
-for (p in causal.distributions){
-  priorData <- 100*filter(d.cas.priors, distribution == p)$response
-
-  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
-
-  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
-    spread(Parameter, value) %>%
-    rowwise() %>%
-    mutate(
-      a = g * d,
-      b = (1 - g) * d,
-      stable = rbinom(n = 1, size = 1, prob = phi),
-      prevalence = ifelse(stable == 1, 
-                             rbeta(n = 1, shape1 = a, shape2 = b),
-                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
-      distribution = p
-    )
-  )
-
-  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
-                                            m.cas.endorse.priors %>% 
-                                              mutate(distribution = p) %>%
-                                              group_by(distribution, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-}
-
-```
-
-#### Participants
-
-We recruited `r n.subj.cas` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average `r ave.minutes.cas` minutes and participants were compensated \$0.50 for their work.
-
-<!-- The different kinds of system are described in more detail below. -->
-<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->
-
-#### Procedure
-
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
-
-In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
-The story for the "sleepy animals" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. 
-Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-The results are shown below:
-\end{quotation}
-
-Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
-
-Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
-
-#### Materials
-
-Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
-The cover story for the "tall plants" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
-Your team runs experiments trying to make feps grow tall with different fertilizers. 
-The results are shown below:
-\end{quotation}
-
-Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
-In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
-
-```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-4 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3, eval = F}
-sample.dists <- bind_rows(
-  data.frame(
-    dist = "rare weak",
-    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common weak",
-    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
-  ),
-  data.frame(
-    dist = "rare deterministic",
-    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common deterministic",
-    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
-  )
-) %>%
-    mutate(Distribution = factor(dist, 
-                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak")))
-
-figure.causals.priors <- bind_rows(
-  sample.dists %>%
-    mutate(src = "stimuli") %>%
-    select(-dist),
-  m.cas.marginal.prevalence %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
-    mutate(Distribution = factor(distribution, 
-                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))) %>%
-    select(Distribution, prevalence) %>%
-    mutate(src = 'model') %>%
-    rename(x = prevalence)
-) %>%
-  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
-                ))+ 
-  geom_density( adjust = 1.3, 
-               size = 1.2,
-               aes( y = ..scaled..))+ #
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_fill_solarized()+scale_color_solarized()+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0.1, 0.4))+
-  scale_linetype_manual(values = c(2, 1))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
-  guides(fill = F, color = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal')
-```
-
-```{r s1-model}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-var alpha = 2;
-var mixture = data.prior[0].phi;
-var priorParams = betaShape(data.prior[0]);
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var speaker1 = function(state) {
-  Infer({model: function(){
-    var utterance = sample(utterancePrior);
-    var listener_posterior = listener0(utterance);
-    factor(alpha * listener_posterior.score(state))
-    return utterance
-  }})
-}
-
-probability(speaker1(data.state[0]), "generic")
-'
-```
-
-```{r causal-endorsement-predictions, cache = T, eval = F}
-causal.priorParams <- m.cas.endorse.priors.summary %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           Parameter != 'marginalPrevalence') %>%
-  select(distribution, Parameter, MAP) %>%
-  spread(Parameter, MAP)
-experimental.frequencies <- c(0.2, 0.7)
-causal.endorsement.predictions <- data.frame()
-for (p in causal.priorParams$distribution){
-  for (s in experimental.frequencies){
-
-    inputData = list(prior = filter(causal.priorParams, distribution == p), 
-                     state = s)
-
-    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
-
-    causal.endorsement.predictions <- bind_rows(
-      causal.endorsement.predictions,
-      data.frame(state = s, distribution = p, prob = s1.rs)
-    )
-  }
-  print(p)
-}
-```
-
-<!-- #### Materials  -->
-
-<!-- The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model. -->
-<!-- Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
--->
-<!-- So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.  -->
-
-<!-- A second dimension of man ipulation corresponds to the extent to which *determinism* is expected in the domain.  -->
-<!-- For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.  -->
-
-### Results
-
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
-These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
-We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
-
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
-
-d.cas.priors %>%
-  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
-      mutate(Distribution = factor(distribution, 
-                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>% 
-ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 0.8, alpha =0.8, 
-               size = 1.2,
-               aes( y = ..scaled..))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
-```
-
-### Model predictions
-
-... run RSA model using fixed parameters and MAP estimates of these priors ?
-
-## Experiment 3b: Endorsing Causal Language
-
-In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-
-### Method
-
-Most of the experiment was identical to that of Experiment 3a.
-
-```{r causal-endorsement-data}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
-ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-
-n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-```
-
-#### Participants
-
-We recruited `r n.subj.cas.endorse` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 3a. 
-The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 3a.
-Phase 1 of the experiment was identical to that of Experiment 3a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
-Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Partipants responded by either clicking "Yes" or "No".
-
-After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
-
-```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Target frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-```{r causals-fullmodel}
-n_chains <- 1
-n_samples <- 5000
-burn <- n_samples / 2
-lg <- 5
-i <- 1
-
-model_prefix <- "pilot-results-causals-jointModel-S1-"
-
-m.cas.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/causals/results/", 
-                    model_prefix, "smntcs_causal-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
-}
-
-# n_chains <- 1
-# n_samples <- 1000
-# burn <- n_samples
-# lg <- 5
-# i <- 1
-# m.hab.fixed.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/", 
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-# }
-
-# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-#   filter(type == 'predictive') %>%
-#   rename(habitual = B, time_period = D, binned_freq = E) %>%
-#   group_by(habitual, time_period, binned_freq) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.cas.fullmodel.endorsement <- m.cas.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(dist, frequency) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
-m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
-  filter(type == "prior") %>%
-  rename(variable = item, parameter = roundedFreq) %>%
-  group_by(dist, variable, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
-
-m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(dist, variable, parameter, MAP) %>%
-  mutate(param = paste(variable, parameter, sep = "_")) %>%
-  select(-variable, -parameter) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-cas.listener.predictions <- data.frame()
-
-for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
- priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- cas.listener.predictions <- bind_rows(
-   cas.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
-   )
-}
-
-inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
-
-causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, 
-                              levels = c("state_Prior","state_Posterior"),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Causal")),
-    Distribution = factor(distribution, 
-                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>%
-  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~Distribution, nrow = 1)+
-  scale_fill_manual(values =inset.color.order )+
-  scale_color_manual(values = inset.color.order)+
-  scale_alpha_manual(values = c(0.1, 0.8))+
-  scale_linetype_manual(values = c(2, 1))+
-  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Feature-probability") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)
-```
-
-```{r}
-md.caus.endorse <- left_join(
-  m.cas.fullmodel.endorsement,
-    d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution)
-)
-
-n.caus.endorse <- length(md.caus.endorse$MAP_h)
-r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
-mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")
-
-```
-
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
-figure.causals.endorsement <- bind_rows(
-  m.cas.fullmodel.endorsement %>%
-    mutate(src = "model"),
-  d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
-    mutate(src = 'data')
-) %>%
-  ungroup() %>%
-  mutate(
-    src = factor(src, levels = c( "data", "model")),
-    dist = factor(dist, 
-           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
-           labels = c(
-                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
-    ) %>%
-  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = src, alpha = src))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(0.3), alpha = 1)+
-  #geom_line(position = position_dodge(0.3))+
-  #theme(axis.text.x = element_text(angle = 90))+
-  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_alpha_manual(values = c(1, 0.3))+
-  #scale_fill_solarized()+
-  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("")+
-  ylab("Proportion Causal Endorsement")+
-  facet_grid(.~frequency)+
-  coord_flip()+
-  guides(fill = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
-```
-
-```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
-Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
-These distributions are inferred using both data sources from Expt.
-3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
-grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
-             layout_matrix = cbind(c(1,1,2)))
-
-# ,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-### Results
-
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
-
-As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
-When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
-By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
-The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
-
-## Discussion
-
-In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
-We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
-In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
-
-In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
-These two features of the domains make them particularly amenable to manipulation.
-That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
-
-It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
-If this were happening in our domains, we would expect this to show up in the results of Expt.
-3a.
-Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
-]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
-
-# General Discussion
-
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
-As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
-
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
-
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
-
-In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge and implications for conceptual accounts
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
-In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
-As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
-] 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
-In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
-
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expts.
-2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
-
-The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
-Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
-This prior could then be updated with more data to acquire its fixed meaning.
-For the generic statement, the language learner is done once she acquires (1). 
-The rest of the meaning is inferred in context.
-With that lens, generic meaning would be primary, while quantified utterances would be refinements.
-
-There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
-A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-
-This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
-
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical Accounts
-
-Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
-
-### Conceptual Accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-
-This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
-In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
-4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
-However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
-
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
-]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-```{r child = 'appendix-bda.Rmd'}
-```
-
-```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-```
+<!-- To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
+-->
+
+<!-- Habituals are a particularly convenient case study for manipulating referent feature-probability. -->
+<!-- In the domain -->
+
+<!-- From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[ -->
+<!--   While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
+-->
+<!-- ] -->
+<!-- Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them. -->
+<!-- In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[ -->
+<!-- In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability.  -->
+<!-- A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate. -->
+<!-- ] -->

### 2017-11-11 paper/case3-causals.Rmd
edits to end of generics; half of habituals; modularize paper into separate files for each case study

--- 2017-11-03 paper/comgen-paper.Rmd
@@
----
-title             : "The language of generalization"
-shorttitle        : "The language of generalization"
-
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-  - \usepackage{amsmath}
-  - \usepackage{graphicx}
-  - \usepackage{subcaption}
-
-author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
-
-abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which such statements are true or which are false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of language conveying generalization, while simpler models fall short.
-    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results suggest the central phenomena emerge from the interaction of underspecified meaning with diverse beliefs about properties.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "20000"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-
-\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
-\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
-\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
-```
-
-```{r libraries, cache = F}
-library(papaja)
-library(formatR)
-library(rwebppl)
-library(xtable)
-library(tidyverse)
-library(forcats)
-library(langcog)
-# library(dplyr)
-library(data.table)
-library(coda)
-library(ggthemes)
-library(ggrepel)
-library(jsonlite)
-library(gridExtra)
-library(lme4)
-library(knitr)
-library(cowplot)
-theme_set(theme_few())
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-logmeanexp <- function(x){
-  x.num <- as.numeric(x)
-  xstar = max(x.num)
-  return(xstar + log(mean(exp(x.num - xstar))))
-}
-
-compute_r2 <- function(df,v1, v2, sigfigs = 3){
-  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
-}
-
-compute_mse <- function(df, v1, v2, sigfigs = 3){
-  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
-}
-
-project.path <- "../"
-options("scipen"=10) 
-```
-
-<!-- 
-possible titles:
-- Communicating generalizations
-- The language of generalization
-- The language of generalization: Probability, vagueness, and interaction
--->
-
-# Introduction
-
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
-
-<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
-<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
-<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
-<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
--->
-<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
-<!-- \ndg{this par doesn't really do much} -->
-
-The language of generalization is often studied via *generic language* (or, generics): simple statements  about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
--->
-Generics are just one case of the language of generalizations, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
-
-<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
-<!-- Individual entities can also be talked about in generalization, using so-called  -->
-<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
-<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
-
-Despite their ubiquity and relative simplicity, there have been few formal models of this language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining *what makes the statements true or false*.
-When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
-The generalization could signal something weaker like "Most dogs bark".
-However, "Most mosquitos do not carry malaria" (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to "some" is too permissive: "Some Robins are female" (in fact, half of them are), but asserting "Robins are female" seems odd.
-Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
-
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not central to the meaning of generalizations in language.
-Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-A paradigm case is the statement "Bishops move diagonally", which is true but not because bishops tend to move diagonally but rather because those are the rules of the game.
-It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
-One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.
-Whatever their mode of reproduction, regardless of the actual prevalence of the feature, will make a true generic statement (e.g., "Robins lay eggs").
-*Horrifying* or *striking* is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is felicitous.
-
-Examining a wider range of examples makes one realize that generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships sound like true generics true.
-<!-- Arbitrary relationships are also expressed with generics:  -->
-For example, "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are blue" would be true.
-Ravens and toasters have no priviledge relationship to each other, but the statement "Ravens are bigger than toasters" is still a true genaralization.
-Conceptual accounts must then be supplemented with the proviso that, in some situations, the actual prevalence of the feature does influence human intuitions about generics.
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that we can describe as communicating generalizations, there should be something common to them all: a general, unified semantic core.
-The test of a unified semantic core is its ability to explain what makes the statements true or false.
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-
-In this paper, we propose a semantic core for the language of generalization.
-To do so, we look to probability, a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-We then consider the background knowledge that listeners bring to bear when interpreting generalizations, and formalize an endorsement model based on this interpretation hypothesis.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-Our endorsement model is the first formal theory that makes quantitative predictions about what makes generalizations in language true or false; the assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-
-<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
--->
-
-<!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
--->
-<!-- In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000]. -->
-<!-- We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement. -->
-<!-- We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...} -->
-<!-- We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
--->
-
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
-The paper is organized as follows. 
-In Section 1, formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
-Sections 2 - 4 presents our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
-<!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
--->
-<!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-<!-- This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.  -->
-
-# Computational Framework
-
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
-
-How does one come to have an $h$ in their head?
-One way is through observation: One can observe instances of the category $k$ and note how many of them have $f$.
-But the inferences derived from observation will depend upon on one's background knowledge about the property [@Gelman2003; @Keil1992].
-For example, if you observe an instance of a novel creature category that \emph{has two legs}, you may infer that all of that category has two legs.
-If in addition you observe that it has broken wings, the corresponding prediction of another instance having broken wings is not nearly as strong [@Nisbett1983].
-This kind of knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
-Relying upon observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), it is better to learn from others.
-Fortunately, language has simple ways of encoding generalizations.
-
-<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
-<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
-<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
--->
-<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
-<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
--->
-<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
-
-<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
-<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
--->
-<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
-<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
--->
-
-<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
-<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
-<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
--->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
--->
-<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
-<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
-
-<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
-<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
--->
-<!-- \ndg{what is this par doing for us? delete?} -->
-<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
-<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
--->
-<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
--->
-<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
--->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-
-## Generalization from language
-
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity to be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean truth value.
-One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlaizaion would then apply to the *feature-probability* $h$:
-$$\denote{u_{gen}}(h, \theta) = \{h>\theta\}$$
-We emphasize that this account is based on a probability $h$.
-The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[
-  There has also been substantial discussion of *cue validity* , which we come back to below.
-]
-Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself. 
-Probability is a measure of belief.
-
-### Semantics and background knowledge
-
-What threshold $\theta$ should be used for the generalization?
-We posit that the language of generalization is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we posit that $\theta$ is contextually-determined, and specifically that it is determined by Bayesian reasoning using relevant prior knowledge.
-
-\begin{eqnarray}
-Lit(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} is a model of a "literal" listener $Lit$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$. 
-We formalize the underspecification of $\theta$ by a uninformed prior distribution over $\theta$ [i.e., *a priori* all thresholds are equally likely; cf., @Lassiter2013].
-The semantic content of an utterance is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
-
-\begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
-1 & \text{if } h > \theta \\
-0 & \text{otherwise}
-\end{cases}\label{eq:delta}
-\end{eqnarray}
-
-Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.
-
-### Endorsement model
-
-The above model determines how $\theta$ should be resolved in context.
-Now, how do we decide when a statement conveying a generalization is true or not?
-To answer this question, we draw upon recently developed tools in the field of probabilistic pragmatics [@Franke2009; @Frank2012; @Franke2015; @Goodman2016].
-The felicity or endorsement of a statement can be modeled by a speaker model who has in his repetoire only two possible utterances: convey the statement to a naive listener or stay silent [@Franke2014cogsci; @Degen2014].
-
-\begin{equation} 
-E(u \mid h = h') \propto \exp{(\lambda \cdot U(u; h') )}
-\label{eq:S1}
-\end{equation}
-
-Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
-Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
-
-The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$.^[A more general version of this model can relax the assumption that the endorser has access to a specific feature-probability $h'$ that he is trying to communicate.
-Rather, the endorser may have a belief distribution over $h'$ for the category $k$, corresponding to the endorser's beliefs about the feature-probability of the property in the category. 
-In this situation, we would define the endorsement utility to be the expected value of the informativity, which integrates over the endorser's belief distribution:
-$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
-]
-The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:  $\denote{u_{silence}(h, \theta)} \propto \text{True}$.^[
-This "silent" alternative can be realized in at least two other ways: the endorser could say the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not have F").
-All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
-]
-
-\begin{equation} 
-U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility}
-\end{equation}
-
-Thus, Eq.
-\ref{eq:S1} provides a mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics that deals only with *feature-probabilities* but without us having to specify the threshold (note that there is not $\theta$ is Eq. \ref{eq:S1}).
-Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$.
-
-The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization.
-
-Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener).
-The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it. 
-However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
-We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.
-
-### The feature-probability prior and model simulations
-
-The endorsement model defined in the previous section predicts that the endorsement of a generalization depends upon two factors: (i) the feature-probability $h$ in the referent-category (e.g., the \% of robins that lay eggs) and (ii) shared background knowledge about what feature-probabilities are likely *a priori*.
-We use classic examples from the literature on generics to elucidate the meaning of these two components and demonstrate why the endorsement model makes the predictions that it does. 
-We implemented the models in the probabilisitic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
-
-```{r simluationsModel, eval = T, cache = T}
-l0.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
-'
-
-priorNames <- c(
-  "doesntEatPeople", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria",
-  "hasSpots"
- # "areSick"
-  )
-priorShapes <- list(
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-all.simulations <- data.frame()
-for (p in priorNames){
-  for (u in c("generic")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
-    )
-  }
-  #print(p)
-}
-```
-
-```{r simluationEndorsementModel, eval = T, cache = T}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.mix[0];
-var priorParams = data.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-var alpha = 2
-
-var endorser = function(featureProb){
-  Infer({model: function(){
-    var endorsement = sample(utterancePrior)
-    var L0 = marginalize(listener0(endorsement), "state_Posterior")
-    factor(alpha * L0.score(featureProb))
-    return endorsement
-  }})
-}
-
-probability(endorser(data.featureProb[0]), "generic")
-'
-
-exampleGenerics <- c(
-  "sharksDontEatPeople",
-  "robinsAreFemale", 
-  "robinsLayEggs", 
-  "kangaroosHaveSpots",
-  "dogsBark",
-  "mosquitosCarryMalaria"
-  )
-exampleParameters <- list(
-  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
-  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
-  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
-  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
-  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
-)
-
-s1.simulations <- data.frame()
-for (p in exampleGenerics){
-
-    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
-    s1.simulations <- bind_rows(s1.simulations,
-                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
-
-}
-
-```
-
-```{r}
-s1.simulations.relabeled <- s1.simulations %>%
-  mutate(example = factor(example, 
-                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-  #geom_jitter(width = 0.1, shape = 21, size = 5)+
-  #ylab("Human endorsement probability")+
-  #xlab("Frequency of target")+
-  geom_label_repel(data = s1.simulations.relabeled, 
-                   aes( label = example, fill = example),
-                       color = 'white',
-    box.padding = unit(0.0, "lines"),
-    #point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37')+
-  scale_fill_solarized()+
-  scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
-  coord_fixed(ratio = 1)+
-  guides(fill = F)+
-  ylab("Endorsement model prediction")+
-  xlab("Hypothesized feature-probability")
-
-```
-
-```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
-all.simulations.refactored <- all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                                c( "Prior_generic", "Posterior_Generalization_generic"),
-                                labels = c( "Prior/Silence", "Generalization")
-                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
-                             ),
-         PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
-                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         )
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability h") +
-    ylab("Scaled prior probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-```
-
-```{r simulations, fig.cap = "Model behavior.
-Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
-grid.arrange(l0.simulations.distributions, 
-             s1.simulations.scatter, ncol = 3,
-             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
-
-```
-
-These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
-The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
-The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
-The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
-If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
-If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
-As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
-When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
-The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
-]
-
-Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
-The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
-In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
-The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
-We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
-The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
-]
-The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.
-
-How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
-In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
-For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
-For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
-This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
-For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
-The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
-In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
-"Robins lay eggs", however, has a lot of informational content.
-
-Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
-The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
-Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
-Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".
-
-In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
-For these simulations, we had specify the feature-probability priors $P(h)$.
-In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.
-
-# Case Study 1: Generic Language
-
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-Generics have been the case study of choice for generalizations in language because of theiry vexing similarity to quantified statements (e.g., "*Most* dogs bark").
-Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
-Here, we take our first look at the
-
-Here, we take 
-Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
-
-We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
-"Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
-1a).
-
-We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
-Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
-\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
-To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
-
-## Experiment 1a: Generic endorsements
-
-In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
-The goal of this study is to observe a range of endorsements for generic statements about animal categories.
-
-#### Method
-```{r eval = F}
-d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "naturalGenerics-trials-formatted.csv", sep = ""))
-
-# write.csv(
-#   left_join(
-#   d1 %>%
-#     mutate(sentence = as.character(sentence),
-#            sentence = gsub('&quotechar', '', sentence),
-#          sentence = gsub('lyme', 'Lyme', sentence)),
-#   unique(d2 %>%
-#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-#     select(Category, Property, sentence))
-# ), file = paste(project.path, "data/generics/endorsement/",
-#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
-```
-
-```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(col = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup()
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
-  filter(item %in% d.gen.endorse.bayes$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(col = "prevalence")
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- left_join(
-  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
-) %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
-  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("Human generic endorsement")+
-  xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'feature probability',
-                               ticks = F))+
-  theme(legend.position = 'bottom')
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
-```
-
-##### Participants
-
-We recruited 100 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
-The experiment took about 3 minutes and participants were compensated \$0.35.
-
-##### Procedure and materials
-
-Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
-As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
-
-#### Results
-
-```{r generic-endorsement-manipulationcheck}
-# MHT's truth judgments of sentences
-# t --> true; f --> false; i --> indeterminate/uncertain
-all.sentences <- list("Cardinals are red." = "t",
- "Ducks have wings." = "t",
- "Kangaroos have pouches." = "t",
- "Kangaroos have spots." = "f",
- "Leopards are juvenile." = "i",
- "Leopards have spots." = "t",
- "Leopards have wings." = "f",
- "Lions are male." = "i",
- "Lions have manes." = "t",
- "Lions lay eggs." = "f",
- "Mosquitos attack swimmers." = "i",
- "Mosquitos carry malaria." = "t",
- "Mosquitos dont carry malaria." = "f",
- "Peacocks dont have beautiful feathers." = "f",
- "Peacocks have beautiful feathers." = "t",
- "Robins are female." = "i",
- "Robins carry malaria." = "f",
- "Robins lay eggs." = "t",
- "Sharks are white." = "i",
- "Sharks attack swimmers." = "t",
- "Sharks dont attack swimmers." = "f",
- "Sharks have manes." = "f",
- "Sharks lay eggs." = "i",
- "Swans are full-grown." = "i",
- "Swans are white." = "t",
- "Ticks carry Lyme disease." = "t",
- "Ticks dont carry Lyme disease."= "f",
- "Tigers dont eat people."= "f",
- "Tigers eat people." = "t",
- "Tigers have pouches."= "f")
-
-mht.truth.judgments <- data.frame(sentence = names(all.sentences),
-           truth_judgment = as.vector(unlist(all.sentences)))
-
-d.gen.endorse.manipulation.check.bayes <- left_join(
-  left_join(
-    d.gen.endorse, 
-    d.gen.endorse.catch %>% select(workerid, pass)
-    ),
-  mht.truth.judgments ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(truth_judgment) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
-
-true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
-true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
-true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]
-
-false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
-false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
-false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]
-
-uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
-uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
-uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
-
-```
-
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
-Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
-
-## Experiment 1b: Feature-probability prior elicitation
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
-Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
-Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
-].
-
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-
-### Method
-
-#### Participants
-
-We recruited 60 participants over Amazon MTurk.  
-3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-#### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
-A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
-Eight property--columns appeared in the table.
-
-This whole procedure was repeated two times (two trials).
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
-
-### Results
-
-In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
-We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
-\text{has wings}).
-For model implementation and inference details, see Appendix.
-
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
-There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
-One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
-
-<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
--->
-<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
-load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
-           aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
-    xlab("Feature-probability") +
-    ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
-## Endorsement model comparison
-
-To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
-1b), from which the interpreter model infers likely thresholds for the generic.
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
-As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of the uncertain-threshold hypothesis.
-
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:10){
-
-  d.cv.bsample <- d.cv %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.gen.cv.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped %>%
-      group_by(property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
-# 
-# d.cv.bootstrapped %>%
-#   group_b
-
-# need to filter by items specified with endorsement
-# d.gen.cv.summary <- left_join(
-#   d.target.items %>% select(-sentence),
-#   d.cv %>%
-#     rename(category = response) %>%
-#     group_by(property) %>%
-#     mutate(n = n(),
-#            item = paste(category, property)) %>%
-#     filter(item %in% d.target.items$item) %>%
-#     group_by(category, property) %>%
-#     summarize(mentions = n(),
-#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-#               prop = mentions / trials)
-#   ) %>%
-#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prev_mean = mean,
-             sentence = item,
-             prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper) %>%
-      ungroup() %>%
-      mutate(sentence = gsub('[.]', '', sentence))
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prev_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.prev.cue.uniq <- unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, 
-    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
-  ))
-
-d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_lower,
-         cv_mean = cv_ci_lower)
-d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_upper,
-         cv_mean = cv_ci_upper)
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
-
-r2.gen.n <- length(d.gen.endorse.bayes$sentence)
-r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)
-
-r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
-mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)
-
-intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))
-
-d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
-  filter(
-    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
-    (prev_mean < intermediate.prev.quantiles[["76%"]])
-)
-r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)
-
-r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
-```
-
-### Baseline models
-
-#### Referent feature-probability
-
-From the feature-probability prior data (Expt.
-1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
-
-However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
-
-#### Cue validity and referent feature-probability
-
-##### Model specification
-
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* thus captures the distinctiveness of the feature for the category. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
-In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
-
-##### Results
-
-A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of a simple model based on cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A simple metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
-
-### Information-theoretic endorsement models
-
-The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
-Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
-We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
-We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
-
-For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
-  Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-  This corresponds to the more general form of the model described in a footnote in the model section. 
-  For these data, the predictions of these two models are nearly identical.
-]
-(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Appendix and Figure \ref{fig:genericsModelDiagram}).
-
-#### Fixed-threshold model
-
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
-
-```{r generic-RSAmodels, fig.width = 8}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
-
-# m.samp <- data.frame()
-# m.samp.fixed <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-#   
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-#   }
-# 
-# save(m.samp,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.samp.fixed,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.gen.rsa.generics <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-r2.gen.rsa.fixed <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-mse.gen.rsa.generics <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-mse.gen.rsa.fixed <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression,
-  left_join(
-    m.gen.endorse.rsa %>% 
-      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-      select(sentence, Property, Category, prev_mean, cv_mean)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( "some_model",
-                                      "generics_model",
-
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c("Fixed semantics model",
-                                 "Uncertain semantics model",
-
-                                 "Feature-probability alone",
-                                 "Cue validity + Feature-probability"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.4)+
-  geom_errorbarh(alpha = 0.4)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human generic endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  #theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
-    filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_label_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
-    ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-```
-
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
-Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
-Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
-These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
-
-We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
-Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-The model fails to distinguish any of the generic sentences because they are all somewhat true. 
-All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
-
-The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
-For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
-Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
-This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
-The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
-
-\mht{Outfit fixed-threshold model with noise parameter?}
-
-### Uncertain threshold RSA model
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-
-To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
-It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
-"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
-
-## Discussion
-
-Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-This evidence is correlational in nature, however.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
-# Case Study 2: Habitual Language
-
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
-Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
-While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
-]
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
-In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
-We separately measure endorsements under the same contexts (Expt.
-2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
-## Experiment 2a: Measuring the feature-probability prior for events
-
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
-To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
-The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
-This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
-
-### Method
-
-#### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-#### Materials
-
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
-
-#### Procedure
-
-For each event, participants were asked two questions, with associated dependent measures:
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
-\end{enumerate}
-
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
-After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
-They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-They did this to test their understanding and attention for each of the two questions.
-
-For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
-<!--   \caption{ -->
-<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
-<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
-<!--   Actual frequency noted on x-axis for examples (left). -->
-<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
-<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
-<!--   } -->
-<!--   \label{fig:tjScatters} -->
-<!-- \end{figure*} -->
-
-<!-- #### Data preprocessing -->
-
-```{r habituals-prior-data}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
-
-d.hab.priors <- d.hab.priors %>%
-  mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women),
-         item = as.character(item),
-         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
-  rowwise() %>%
-  mutate(
-    mixture_male = nPersons_men / comparisonNum_men,
-    mixture_female = nPersons_women / comparisonNum_women,
-    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
-                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
-                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
-                   ifelse(comparisonTime_men == "5 years", 
-                          nInstances_men / (5*365), -99)))),
-    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
-                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
-                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
-                   ifelse(comparisonTime_women == "5 years", 
-                          nInstances_women / (5*365), -99)))),
-    annualRate_male = dayRate_male * 365,
-    annualRate_female = dayRate_female * 365
-  )
-
-d.hab.priors.filtered <- filter(d.hab.priors, 
-       !(
-         (mixture_male == 0) ||   (mixture_female == 0) ||   
-           (dayRate_male == 0) ||   (dayRate_female == 0)  )
-       )
-```
-
-```{r habituals-prior-forwardsample}
-# this is basically bootstrapping and combining using the structured model
-
-d.hab.priors.samples <- data.frame()
-for (i in 1:10){
-
-  d.hab.priors.samples <- bind_rows(
-    d.hab.priors.samples,
-    d.hab.priors.filtered %>% 
-    select(workerid, item, starts_with("annualRate"), 
-           starts_with("mixture")) %>%
-    rowwise() %>%
-    mutate(
-      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
-       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
-       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
-       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
-       ) %>%
-    select(item, freq_male, freq_female) %>%
-    gather(gender, val, freq_male, freq_female) %>%
-  mutate(gender = gsub("freq_", "", gender))
-  )
-}
-
-```
-
-```{r habituals-prior-model}
-hab.prior.bda.model <- '
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var model = function(){
-	var mixtureParams = {
-		male: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    },
-		female: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    }
-	};
-
-	var mixtureShapes = {
-		male: betaShape(mixtureParams.male),
-		female: betaShape(mixtureParams.female)
-	};
-
-	mapData({data: data.mixture}, function(d){
-    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
-     // display(Beta(mixtureShapes[d.gender]).score(d.val))
-		observe(Beta(mixtureShapes[d.gender]), d.val)
-	})
-
-	var stableFrequency = {
-		male: {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		},
-		female: {
-			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		}
-	}
-
-	mapData({data: data.frequency}, function(d){
-    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
-        display(JSON.stringify(d)) : null
-    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
-		observe(Gaussian(stableFrequency[d.gender]), d.logval)
-	})
-
-	var existenceProb = {
-		male: beta(mixtureShapes.male),
-		female: beta(mixtureShapes.female)
-	};
-
-	var freqWhenPresent = {
-		male: gaussian(stableFrequency.male),
-		female: gaussian(stableFrequency.female)
-	}
-
-  var marginalFreq = {
-    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
-    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
-  }
-
-  return {
-    mix_mean_male : mixtureParams.male.g,
-    mix_mean_female : mixtureParams.female.g,
-    mix_samplesize_male : mixtureParams.male.d,
-    mix_samplesize_female : mixtureParams.female.d,
-    stableFreq_mean_male : stableFrequency.male.mu,
-    stableFreq_mean_female :stableFrequency.female.mu,
-    stableFreq_sd_male : stableFrequency.male.sigma,
-    stableFreq_sd_female :stableFrequency.female.sigma,
-    marginalFreq_NA_male: marginalFreq.male,
-    marginalFreq_NA_female: marginalFreq.female
-  }
-}
-'
-```
-
-```{r habituals-prior-model-run, cache = T}
-items <- levels(factor(d.hab.priors.filtered$item))
-n_samples <- 500
-rs.habituals.bda.prior <- data.frame()
-
-for (it in items){
-
- df.prior.toPass <- list(
-   frequency = d.hab.priors.filtered %>%
-      filter(item == it) %>%
-      select(item, starts_with("annualRate")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("annualRate_", "", gender),
-             logval = log(val)),
-   mixture = d.hab.priors.filtered %>% 
-      filter(item == it) %>%
-      select(item, starts_with("mixture")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("mixture_", "", gender)) %>%
-      rowwise() %>%
-      mutate(val = ifelse(val == 1, 0.9999, 
-                          ifelse(val == 0, 0.000001, val)))
-  )
-
-  rs <- webppl(program_code = hab.prior.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.prior.toPass,
-       data_var = "data")
-
-  rs.habituals.bda.prior <- bind_rows(
-    rs.habituals.bda.prior, 
-    rs %>% 
-      mutate(item = it) %>% 
-      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
-  )
-}
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
-
-example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
-                       "climbs mountains", "hikes", "runs", 
-                       "wears a suit", "wears a watch", "wears socks", 
-                       "writes poems", "goes to the movies", "plays the banjo"
-                       )
-
-rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
-  filter(Parameter == "mean") %>%
-  group_by(Variable, Gender, item) %>%
-  summarize(MAP = estimate_mode(value),
-            cred_upper = hdi_upper(value),
-            cred_lower = hdi_lower(value)) %>%
-  ungroup()
-rs.habituals.bda.prior.summary.wide <- left_join(
-  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
-    select(-Variable) %>%
-    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
-  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
-    select(-Variable) %>%
-    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
-)
-
-figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) %>%
-ggplot(.,
-       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
-            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = category))+
-    scale_shape_manual(values=c(21,22))+
-  #scale_color_solarized()+scale_fill_solarized()+
-  scale_fill_brewer(palette='Set1')+
-
-  geom_point(size=4, inherit.aes = F, 
-             aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            shape = Gender),  alpha = 0.9)+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  xlab("% of Americans who have DONE ACTION")+
-  ylab("Log Frequency of DOING ACTION")+
-  #scale_
-  coord_fixed(ratio = 1/8)+
-  theme(legend.title = element_text(hjust=0),
-        legend.position="bottom",
-        legend.direction="horizontal") +
-        scale_y_continuous(limits = c(-1.5, 6.5), 
-                     breaks = c(0, 2.5, 4, 5.9),
-                     labels = c("annually", "monthly", "weekly", "daily"))+
-  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
-                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-```
-
-```{r habituals-prior-model-forwardSample}
-rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value)
-
-rs.habituals.bda.prior.samples <- data.frame()
-for (i in 1:1){
-  rs.habituals.bda.prior.samples <- bind_rows(
-    rs.habituals.bda.prior.samples,
-    rs.habituals.bda.prior.spread %>%
-    rowwise() %>%
-    mutate(
-      a = mix_mean * mix_samplesize,
-      b = (1 - mix_mean) * mix_samplesize,
-      theta = rbeta(n = 1, shape1 = a, shape2 = b),
-      stable = rbinom(n = 1, size = 1, prob = theta),
-      logannualRate = ifelse(stable == 1, 
-                             rnorm(n = 1, 
-                                   mean = stableFreq_mean, 
-                                   sd = stableFreq_sd), -5),
-       annualRate =  exp(logannualRate)
-    )
-  )
-}
-```
-
-```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
-2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
-
-figure.habituals.priors.marginals <- bind_rows(
-  d.hab.priors.samples %>% 
-    mutate(src = 'data', 
-           val = log(val)),
-  rs.habituals.bda.prior.samples %>%
-    rename(gender = Gender, val = logannualRate) %>%
-    select(gender, item, val) %>%
-    mutate(src = 'model')
-  ) %>%
-  filter(item %in% example.habituals,
-         src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals)) %>%
-ggplot(. , aes( x = val, color = gender))+
-  geom_density(size = 0.8, aes( y = ..scaled.. ))+
-  facet_wrap(~item, nrow = 4)+
-  scale_color_solarized()+
-  xlab("Frequency")+
-  ylab("Scaled prior density")+
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.12),
-        axis.text.x = element_text(angle = 90))+
-    scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
-2a).
-Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on rates from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-### Data analysis and results
-
-All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-We built a Bayesian data analysis model for this prior elicitation task.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-First, it smooths effects that are clearly results of the response format.
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
-
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate or frequency with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
-
-<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
-<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
-<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
-<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
-<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-## Experiment 2b: Endorsing habitual statements
-
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Procedure and materials
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
-<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
-
-### Results
-
-```{r habituals-prior-mixture-summarize}
-d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
-  select(item, starts_with("mixture_")) %>%
-  gather(key, value, -item) %>%
-  group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
-  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
-  rowwise() %>%
-  mutate(
-    annualRate = annualRates[[as.character(time_period)]]*n_instances,
-    logAnnualRate = log(annualRate)
-  )
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
-                       "goes to the movies_month", "smokes cigarettes_month")
-fig.habituals.endorsement.vs.freq <- 
-  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21, size = 5)+
-  ylab("Human endorsement probability")+
-  xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
-                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
-                    filter(sentence %in% example.habituals), aes( label = habitual ),
-                       color = 'black', fill = 'white',
-    box.padding = unit(0.35, "lines"),
-    point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
-  scale_x_continuous(limits = c(-1,6), 
-                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
-                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        legend.position = "bottom")+
-  coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F))
-```
-
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.', eval=F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
-r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
-
-```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.freq.mix.uniq <- unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, 
-    mixture, mix_low, mix_high
-  ))
-
-d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_low)
-
-d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_high)
-
-d.hab.endorse.regression.freq <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
-      prediction_lower = prediction,
-      prediction_upper = prediction,
-      src = "regression_freq"
-      )
-)
-
-r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
-
-r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
-  filter(logAnnualRate < 1.1)
-
-r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
-
-r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
-d.hab.endorse.regression.freq.mix <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
-      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
-      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
-      src = "regression_freq_distinct"
-      )
-)
-
-r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-model_prefix <- "results-habituals-jointModel-S1-"
-
-# m.hab.samp <- data.frame()
-# m.hab.fixed.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
-#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-# 
-# }
-# 
-# save(m.hab.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.hab.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "habituals_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.habituals.rsa.fixed <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.fixed <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.uncertain <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)
-
-r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)
-
-r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression,
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, logAnnualRate, mixture)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "some_model",
-                                      "habituals_model",
-                                      "regression_freq", 
-                                      "regression_freq_distinct"
-                                     ),
-                      labels = c(
-                                 "Speaker model - fixed semantics",
-                                 "Speaker model - uncertain semantics",
-                                 "Referent frequency alone", "Distinctiveness + referent frequency"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.15)+
-  geom_errorbarh(alpha = 0.15)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r habituals-simulation-model}
-l0.hab.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
-
-var targetUtterance = "habitual";
-
-var roundTo3 = function(x){
-  return Math.round(x * 10000) / 10000
-}
-
-var lowerBound = -5, upperBound = 10, binWidth = 0.5;
-
-var stateBins =  _.range(
-  lowerBound, upperBound, binWidth
-)
-
-var thetaBins = map2(function(b1, b2){
-  var diff = Math.abs(b2 - b1) / 2;
-  return roundTo3(diff+ b1);
-}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state> _.min(thetaBins):
-         true
-}
-
-var priorParams = data.priorParams[0];
-
-var stable_female_params = betaShape({
-  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
-})
-
-var stable_male_params = betaShape({
-  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
-})
-
-// this marginalizes out the mixture parameter
-var statePrior = Infer({model: function(){
-  var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ? // 
-    flip(
-        categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_female_params), b) + Number.EPSILON
-          }, probBins )
-        })
-    ) ? // stable female distribution
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) : // unstable female distribution
-    _.min(stateBins) : 
-    flip(        
-      categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_male_params), b) + Number.EPSILON
-          }, probBins )
-      })
-    ) ? 
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) :
-    _.min(stateBins)
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:-5}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:-5})
-   var state_prior = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:lowerBound}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:lowerBound})
-    var theta = uniform(lowerBound, upperBound)
-    condition(
-      (utterance == "habitual") ? 
-      state > theta : 
-      (state > _.min(lowerBound))
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
-
-continuousListener0(data.utt[0])
-'
-```
-
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
-
-m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
-  filter(type == "prior", B %in% example.habituals.actions) %>%
-  rename(action = B, variable = C, gender = D, parameter = E) %>%
-  group_by(action, variable, gender, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(action, variable, gender, parameter, MAP) %>%
-  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
-  select(-variable, -gender, -parameter) %>%
-  spread(param, MAP)
-
-hab.listener.predictions <- data.frame()
-
-for (p in example.habituals.actions){
- priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
-
- inputData = list(priorParams = priorParams,
-                  utt = "habitual")
-
- l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
-
- hab.listener.predictions <- bind_rows(
-   hab.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
-   )
-
-}
-
-# m.gen.fullmodel.target.prevalence <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   group_by(param, property, category) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-# m.gen.speakerBeliefs <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   mutate(Sentence = paste(category, property)) %>%
-#   filter(Sentence %in% example.generics)
-
-# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-# gen.inset.distributions <- bind_rows(
-#   gen.listener.predictions %>%
-#     mutate(category = NA),
-#   m.gen.speakerBeliefs %>%
-#     select(property, val) %>%
-#     rename(value = val) %>%
-#     mutate(Parameter = "speakerBeliefs")
-# )
-# 
-# 
-# category.text.labels <- data.frame(property = c("dont eat people", 
-#                       "carry malaria", "lay eggs",  "are female", "have spots"),
-#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Habitual")),
-         action = fct_relevel(action,
-                                "climbs mountains", "hikes", "runs",
-                              "goes to the movies", "smokes cigarettes"
-                              ) ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~action, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
-  #scale_linetype_manual(values = c(3, 4, 1))+
-  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
-      scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-```
-
-```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
-Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
-These distributions are inferred using both data sources from Expts.
-2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
-grid.arrange(fig.habituals.endorsement.vs.freq, 
-             habituals.endorsement.models,
-             habituals.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the referent character.
-<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
-
-<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
-Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
--->
-
-<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
-<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
--->
-<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
--->
-<!-- We see no appreciable differences in endorsements for the two genders.  -->
-<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
-<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
-
-#### Referent frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
-This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-#### Distinctiveness and referent frequency
-
-In the prior elicitation task (Expt.
-2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
-With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
-
-```{r habituals-distinctiveness-counterexamples}
-
-format_endorsment_ci <- function(
-  df, estimate = "MAP_h", low = "low",
-  high = "high", sigfigs = 2){
-  return(paste(
-    round(df[[1,estimate]], sigfigs),
-    " [",
-    round(df[[1,low]], sigfigs),
-    ", ",
-    round(df[[1,high]], sigfigs),
-    "]", sep = ""))
-}
-
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
-
-movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
-                                                        time_period == "year"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
-
-banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
-                                                        time_period == "2 years"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-```
-
-We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture some of the subtle sensitivities in endorsments.
-For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold RSA model
-
-The above regression models are too rigid to explain the flexibility in habitual endorsements. 
-Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
-Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
-To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
-
-We used the speaker model $S_1$ (Eq.
-\ref{eq:S1}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.
-2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
-The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
-As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
-2b.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
-
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
-Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
-\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
-The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
-The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
-Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
-
-Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
-With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
-Thus, this model makes the same predictions for different target frequencies in the same event.
-For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.
-
-#### Uncertain-threshold RSA model
-
-We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-
-### Discussion
-
-In Expt.
-2b, we manipulated the event type (e.g., drinks coffee vs.
-beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
-year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
-
-Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
-The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
-
-Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
-
-<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
-
-<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
--->
-
-<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
-<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
-<!--   Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
--->
-<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
-<!--   \label{fig:tj3} -->
-<!--   \vspace{-7pt} -->
-<!-- \end{figure*} -->
-
-## Experiment 2c: Measuring predictive frequency
-
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
-       aes(x=logAnnualPastRate,
-                              y = mean,
-                              ymin = ci_lower, ymax = ci_upper,
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
-  scale_shape_manual(values=c(21,22,23))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-
-fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
-  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
-                 fill=condition, shape=condition,
-                 xmin = future_lower, xmax=future_upper,
-                 ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.8)+
-  geom_errorbarh(alpha=0.8)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 1, size = 4)+
-  xlab("Predicted frequency (log scale)")+
-  ylab("Human habitual endorsement")+
-  scale_x_continuous(limits = c(-4.2,7.2), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=11.4)+
-  scale_fill_solarized()+
-  guides(fill = F, shape = F)+
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-    legend.position="bottom",
-    legend.direction="horizontal"
-    )
-
-```
-
-```{r habituals-predictive-rsa}
-n_chains <- 3
-# n_samples <- 500000
-# burn <- n_samples / 2
-# lg <- 150
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 50
-
-m.hab.pred.samp <- data.frame()
-m.hab.past.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-
-  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "targetH_past-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-
-#}
-# 
-# 
-# # 
-# save(m.hab.pred.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# # # 
-# save(m.hab.past.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
-
-m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorsement <- m.hab.pred.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.predictive.endorsement
-  ) %>%
-    mutate(src = "predictive_model"),
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.pastmodel.endorsement
-  ) %>%
-    mutate(src = "past_model")
-)
-
-r2.habituals.rsa.past <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.past <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.predictive <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.predictive <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
-
-habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - past frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-
-habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  #guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-#habituals.predictive.predictive.model
-```
-
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
-grid.arrange(
-  arrangeGrob(
-    fig.hab.freq.predictive.vs.past, 
-    fig.hab.endorse.vs.predfreq, 
-    habituals.predictive.past.model, 
-    habituals.predictive.predictive.model + theme(legend.position="none"),
-    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
-legend_b, nrow=2,heights=c(8, 1))
-
-#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 2c.
-The only difference from Expt. 2c is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-
-When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
-], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
-
-We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
-The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
-
-We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
-Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
-The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
-
-<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
-<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
-<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
-<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
-<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
-This may be due, in part, to an effect of the experimental context on participants:
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
-## Discussion
-
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
-2a).
-We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
-By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
-In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
-Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
-
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2d).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
-
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
-Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
-
 # Case Study 3: Causal Language
@@
 Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
-
-# General Discussion
-
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
-As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
-
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
-
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
-
-In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge and implications for conceptual accounts
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
-In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
-As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
-] 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
-In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
-
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expts.
-2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
-
-The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
-Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
-This prior could then be updated with more data to acquire its fixed meaning.
-For the generic statement, the language learner is done once she acquires (1). 
-The rest of the meaning is inferred in context.
-With that lens, generic meaning would be primary, while quantified utterances would be refinements.
-
-There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
-A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-
-This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
-
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures. 
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical Accounts
-
-Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
-
-### Conceptual Accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-
-This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
-In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
-4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
-However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
-
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*. 
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
-]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-```{r child = 'appendix-bda.Rmd'}
-```
-
-```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-```

### 2017-11-11 paper/comgen-paper.Rmd
edits to end of generics; half of habituals; modularize paper into separate files for each case study

@@
 compute_r2 <- function(df,v1, v2, sigfigs = 3){
-  return(round(cor(df[[v1]], df[[v2]])^2, sigfigs))
+  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
 }
@@
 compute_mse <- function(df, v1, v2, sigfigs = 3){
-  return(round(mean( (df[[v1]]-df[[v2]])^2), sigfigs))
+  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
 }
@@
 $Endorse(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} Interpret(h, \theta \mid u)} \diff \theta )}$
+For the empirical case studies described below, these two versions of the model make almost identical predictions.
 ].
@@
 
-# Case Study 1: Generic Language
-
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-Generics have been the case study of choice for generalizations in language because of theiry vexing similarity to quantified statements (e.g., "*Most* dogs bark").
-Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
-Here, we take our first look at the
-
-Here, we take 
-Any theory of generic language must explain its puzzling flexibility of endorsements with respect to feature-probability (e.g., the number of dogs that bark; the number of mosquitos that carry malaria).
-
-We first measure endorsement for thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
-"Lions lay eggs.").
-In additional to the canonical cases from the linguistics literature, we craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminte") for generics with properties of low, medium, and high feature-probabilities (Expt.
-1a).
-
-We restrict our items to generics about animal categories so we may more easily measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
-Our measurement of the feature-probability priors includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
-\ref{eq:S1}) as well as for simpler, alternative models (e.g., endorsement as a linear function of referent feature-probability).
-To preview our results, we find that only an endorsement model based on an uncertain-threshold semantics is able to account for the flexibility observed in generic endorsement.
-
-## Experiment 1a: Generic endorsements
-
-In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
-The goal of this study is to observe a range of endorsements for generic statements about animal categories.
-
-#### Method
-```{r eval = F}
-d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "naturalGenerics-trials-formatted.csv", sep = ""))
-
-# write.csv(
-#   left_join(
-#   d1 %>%
-#     mutate(sentence = as.character(sentence),
-#            sentence = gsub('&quotechar', '', sentence),
-#          sentence = gsub('lyme', 'Lyme', sentence)),
-#   unique(d2 %>%
-#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-#     select(Category, Property, sentence))
-# ), file = paste(project.path, "data/generics/endorsement/",
-#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
+```{r child = 'case1-generics.Rmd'}
 ```
 
-```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(col = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup()
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
-  filter(item %in% d.gen.endorse.bayes$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(col = "prevalence")
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- left_join(
-  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
-) %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
-  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("Human generic endorsement")+
-  xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'feature probability',
-                               ticks = F))+
-  theme(legend.position = 'bottom')
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
+```{r child = 'case2-habituals.Rmd'}
 ```
 
-##### Participants
-
-We recruited 100 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
-Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
-The experiment took about 3 minutes and participants were compensated \$0.35.
-
-##### Procedure and materials
-
-Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-
-As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
-
-#### Results
-
-```{r generic-endorsement-manipulationcheck}
-# MHT's truth judgments of sentences
-# t --> true; f --> false; i --> indeterminate/uncertain
-all.sentences <- list("Cardinals are red." = "t",
- "Ducks have wings." = "t",
- "Kangaroos have pouches." = "t",
- "Kangaroos have spots." = "f",
- "Leopards are juvenile." = "i",
- "Leopards have spots." = "t",
- "Leopards have wings." = "f",
- "Lions are male." = "i",
- "Lions have manes." = "t",
- "Lions lay eggs." = "f",
- "Mosquitos attack swimmers." = "i",
- "Mosquitos carry malaria." = "t",
- "Mosquitos dont carry malaria." = "f",
- "Peacocks dont have beautiful feathers." = "f",
- "Peacocks have beautiful feathers." = "t",
- "Robins are female." = "i",
- "Robins carry malaria." = "f",
- "Robins lay eggs." = "t",
- "Sharks are white." = "i",
- "Sharks attack swimmers." = "t",
- "Sharks dont attack swimmers." = "f",
- "Sharks have manes." = "f",
- "Sharks lay eggs." = "i",
- "Swans are full-grown." = "i",
- "Swans are white." = "t",
- "Ticks carry Lyme disease." = "t",
- "Ticks dont carry Lyme disease."= "f",
- "Tigers dont eat people."= "f",
- "Tigers eat people." = "t",
- "Tigers have pouches."= "f")
-
-mht.truth.judgments <- data.frame(sentence = names(all.sentences),
-           truth_judgment = as.vector(unlist(all.sentences)))
-
-d.gen.endorse.manipulation.check.bayes <- left_join(
-  left_join(
-    d.gen.endorse, 
-    d.gen.endorse.catch %>% select(workerid, pass)
-    ),
-  mht.truth.judgments ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(truth_judgment) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
-
-true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
-true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
-true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]
-
-false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
-false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
-false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]
-
-uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
-uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
-uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
-
+```{r child = 'case3-causals.Rmd'}
 ```
-
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
-As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
-
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure} top left).
-Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-
-In order to better understand the process that generates this endorsement data, we measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
-
-## Experiment 1b: Feature-probability prior elicitation
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
-Now, do you think it lays eggs?
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
-Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
-].
-
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
-
-### Method
-
-#### Participants
-
-We recruited 60 participants over Amazon MTurk.  
-3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
-The experiment took about 10 minutes and participants were compensated \$1.00.
-
-#### Procedure and materials
-
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
-Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ref{fig:generics-prior-task} left).
-A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ref{fig:generics-prior-task} right).
-Eight property--columns appeared in the table.
-
-This whole procedure was repeated two times (two trials).
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
-
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
-
-### Results
-
-In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
-We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an internal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such an internal mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
-\text{has wings}).
-For model implementation and inference details, see Appendix.
-
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \ref{fig:generic-endorsement-priors-figure}.
-There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
-One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
-
-<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
--->
-<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
-load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
-           aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
-    xlab("Feature-probability") +
-    ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
-## Endorsement model comparison
-
-To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
-1b), from which the interpreter model infers likely thresholds for the generic.
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
-As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of the uncertain-threshold hypothesis.
-
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:10){
-
-  d.cv.bsample <- d.cv %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.gen.cv.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped %>%
-      group_by(property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
-# 
-# d.cv.bootstrapped %>%
-#   group_b
-
-# need to filter by items specified with endorsement
-# d.gen.cv.summary <- left_join(
-#   d.target.items %>% select(-sentence),
-#   d.cv %>%
-#     rename(category = response) %>%
-#     group_by(property) %>%
-#     mutate(n = n(),
-#            item = paste(category, property)) %>%
-#     filter(item %in% d.target.items$item) %>%
-#     group_by(category, property) %>%
-#     summarize(mentions = n(),
-#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-#               prop = mentions / trials)
-#   ) %>%
-#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prev_mean = mean,
-             sentence = item,
-             prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper) %>%
-      ungroup() %>%
-      mutate(sentence = gsub('[.]', '', sentence))
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prev_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.prev.cue.uniq <- unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, 
-    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
-  ))
-
-d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_lower,
-         cv_mean = cv_ci_lower)
-d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_upper,
-         cv_mean = cv_ci_upper)
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
-
-r2.gen.n <- length(d.gen.endorse.bayes$sentence)
-r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)
-
-r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
-mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)
-
-intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))
-
-d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
-  filter(
-    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
-    (prev_mean < intermediate.prev.quantiles[["76%"]])
-)
-r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)
-
-r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
-mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
-```
-
-### Baseline models
-
-#### Referent feature-probability
-
-From the feature-probability prior data (Expt.
-1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet).
-The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
-
-However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
-
-#### Cue validity and referent feature-probability
-
-##### Model specification
-
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* thus captures the distinctiveness of the feature for the category. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
-In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
-
-##### Results
-
-A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
-Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of a simple model based on cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A simple metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
-
-### Information-theoretic endorsement models
-
-The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
-Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
-This model has two other main architectural features: an information-theoretic decision between producing the generic vs.
-an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
-We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
-We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.
-
-For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
-  Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
-  This corresponds to the more general form of the model described in a footnote in the model section. 
-  For these data, the predictions of these two models are nearly identical.
-]
-(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
-1a \& b (see Appendix and Figure \ref{fig:genericsModelDiagram}).
-
-#### Fixed-threshold model
-
-We first test a model that has two of the the above three main architectural features.
-This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
-The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
-Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
-
-```{r generic-RSAmodels, fig.width = 8}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
-
-# m.samp <- data.frame()
-# m.samp.fixed <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-#   
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
-#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-#   }
-# 
-# save(m.samp,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.samp.fixed,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
-  filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.gen.rsa.generics <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-r2.gen.rsa.fixed <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 3
-)
-
-mse.gen.rsa.generics <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-mse.gen.rsa.fixed <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression,
-  left_join(
-    m.gen.endorse.rsa %>% 
-      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-      select(sentence, Property, Category, prev_mean, cv_mean)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( "some_model",
-                                      "generics_model",
-
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c("Fixed semantics model",
-                                 "Uncertain semantics model",
-
-                                 "Feature-probability alone",
-                                 "Cue validity + Feature-probability"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.4)+
-  geom_errorbarh(alpha = 0.4)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human generic endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  #theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
-    filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
-
-category.text.labels <- data.frame(property = c("dont eat people", 
-                      "carry malaria", "lay eggs",  "are female", "have spots"),
-             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-generics.endorsement.insets <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~property, nrow = 1)+
-  geom_label_repel(data = category.text.labels,
-                  aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
-    ylab("Scaled probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-```
-
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
-Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
-Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
-These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
-Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
-
-We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
-Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-The model fails to distinguish any of the generic sentences because they are all somewhat true. 
-All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
-
-The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
-For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
-Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
-This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
-The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
-
-\mht{Outfit fixed-threshold model with noise parameter?}
-
-### Uncertain threshold RSA model
-
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ref{fig:generics-endorsement-figure} (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-
-To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
-It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
-"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
-
-## Discussion
-
-Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-However, no formal model has been able to make precise quantitative predictions about the basic phonemena of generics, and classic counterexamples to theories based on probability (*Birds lay eggs* v.
-*are female*; *Mosquitos carry malaria*) have stifled the development of formal models.
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable inspite of these seeming counterexamples.
-The key theoretical contribution is that the threshold must be *underspecified* in the semantics and inferred in context by the listener.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the listener's belief distribution more in line with the speaker's.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-This evidence is correlational in nature, however.
-We do not yet know if the variables that we are measuring are causally related to endorsement.
-In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the referent feature-probability that the speaker aims to communicate.
-
-# Case Study 2: Habitual Language
-
-*Habitual* language (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events. 
-In this case study, we focus on a particular class of events: people doing actions.
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., \emph{Mary smokes cigarettes.}).
-
-Habituals about people are of particular importance because they are likely central to intuitive theories of personality and behavior. 
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-@McGuire1986 explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family". 
-A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
-Habitual language may be a more conservative form of trait language (e.g., \emph{Bill is a smoker.}) and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
-While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
-]
-Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
-In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
-In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
-A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
-]
-
-We follow the same general experimental structure as in Experiment 1. 
-First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the structured representation discovered in Expt. 1a.
-Then, we test endorsements of habitual sentences, manipulating the feature-probability of a particular person doing an action using rate information (Expt. 2b).
-In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
-We separately measure endorsements under the same contexts (Expt.
-2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
-To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
-## Experiment 2a: Measuring the feature-probability prior for events
-
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
-For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
-To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.
-
-In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components.
-The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature.
-The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property. 
-This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
-
-For the case of background knowledge over the feature-probabilities for people doing actions, we consider again two components.^[
-In the case of event knowledge about people, we might expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-To a first approximation, the first component represents the frequencies of the event among the people who have done the action before (e.g., how often a person hikes, given that they have hiked before).
-The second component represents the frequencies of the event among the people who have not done the action before. 
-We will assume for these experiments, that those people who have never done the action before will almost never do the action. 
-In this experiment, we measure the relative contribution of these two components to the prior, as well as the expected frequency among those people who have done the action before.
-
-### Method
-
-#### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-#### Materials
-
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
-
-#### Procedure
-
-For each event, participants were asked two questions, with associated dependent measures:
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
-\end{enumerate}
-
-For example, one set of prompts read: ``How many men have smoked cigarettes before?''; ``For a typical man who has smoked cigarettes before, how frequently does he smoke cigarettes?''
-
-The meaning of these questions were explained to participants on an instructions page before the experimental trials. 
-After reading the instructions, participants were asked to recall the two types of questions asked in the experiment.
-They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-They did this to test their understanding and attention for each of the two questions.
-
-For the experimental trials, we anticipated there might be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
-<!--   \caption{ -->
-<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
-<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
-<!--   Actual frequency noted on x-axis for examples (left). -->
-<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
-<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
-<!--   } -->
-<!--   \label{fig:tjScatters} -->
-<!-- \end{figure*} -->
-
-<!-- #### Data preprocessing -->
-
-```{r habituals-prior-data}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
-
-d.hab.priors <- d.hab.priors %>%
-  mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women),
-         item = as.character(item),
-         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
-  rowwise() %>%
-  mutate(
-    mixture_male = nPersons_men / comparisonNum_men,
-    mixture_female = nPersons_women / comparisonNum_women,
-    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
-                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
-                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
-                   ifelse(comparisonTime_men == "5 years", 
-                          nInstances_men / (5*365), -99)))),
-    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
-                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
-                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
-                   ifelse(comparisonTime_women == "5 years", 
-                          nInstances_women / (5*365), -99)))),
-    annualRate_male = dayRate_male * 365,
-    annualRate_female = dayRate_female * 365
-  )
-
-d.hab.priors.filtered <- filter(d.hab.priors, 
-       !(
-         (mixture_male == 0) ||   (mixture_female == 0) ||   
-           (dayRate_male == 0) ||   (dayRate_female == 0)  )
-       )
-```
-
-```{r habituals-prior-forwardsample}
-# this is basically bootstrapping and combining using the structured model
-
-d.hab.priors.samples <- data.frame()
-for (i in 1:10){
-
-  d.hab.priors.samples <- bind_rows(
-    d.hab.priors.samples,
-    d.hab.priors.filtered %>% 
-    select(workerid, item, starts_with("annualRate"), 
-           starts_with("mixture")) %>%
-    rowwise() %>%
-    mutate(
-      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
-       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
-       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
-       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
-       ) %>%
-    select(item, freq_male, freq_female) %>%
-    gather(gender, val, freq_male, freq_female) %>%
-  mutate(gender = gsub("freq_", "", gender))
-  )
-}
-
-```
-
-```{r habituals-prior-model}
-hab.prior.bda.model <- '
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var model = function(){
-	var mixtureParams = {
-		male: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    },
-		female: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    }
-	};
-
-	var mixtureShapes = {
-		male: betaShape(mixtureParams.male),
-		female: betaShape(mixtureParams.female)
-	};
-
-	mapData({data: data.mixture}, function(d){
-    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
-     // display(Beta(mixtureShapes[d.gender]).score(d.val))
-		observe(Beta(mixtureShapes[d.gender]), d.val)
-	})
-
-	var stableFrequency = {
-		male: {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		},
-		female: {
-			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		}
-	}
-
-	mapData({data: data.frequency}, function(d){
-    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
-        display(JSON.stringify(d)) : null
-    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
-		observe(Gaussian(stableFrequency[d.gender]), d.logval)
-	})
-
-	var existenceProb = {
-		male: beta(mixtureShapes.male),
-		female: beta(mixtureShapes.female)
-	};
-
-	var freqWhenPresent = {
-		male: gaussian(stableFrequency.male),
-		female: gaussian(stableFrequency.female)
-	}
-
-  var marginalFreq = {
-    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
-    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
-  }
-
-  return {
-    mix_mean_male : mixtureParams.male.g,
-    mix_mean_female : mixtureParams.female.g,
-    mix_samplesize_male : mixtureParams.male.d,
-    mix_samplesize_female : mixtureParams.female.d,
-    stableFreq_mean_male : stableFrequency.male.mu,
-    stableFreq_mean_female :stableFrequency.female.mu,
-    stableFreq_sd_male : stableFrequency.male.sigma,
-    stableFreq_sd_female :stableFrequency.female.sigma,
-    marginalFreq_NA_male: marginalFreq.male,
-    marginalFreq_NA_female: marginalFreq.female
-  }
-}
-'
-```
-
-```{r habituals-prior-model-run, cache = T}
-items <- levels(factor(d.hab.priors.filtered$item))
-n_samples <- 500
-rs.habituals.bda.prior <- data.frame()
-
-for (it in items){
-
- df.prior.toPass <- list(
-   frequency = d.hab.priors.filtered %>%
-      filter(item == it) %>%
-      select(item, starts_with("annualRate")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("annualRate_", "", gender),
-             logval = log(val)),
-   mixture = d.hab.priors.filtered %>% 
-      filter(item == it) %>%
-      select(item, starts_with("mixture")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("mixture_", "", gender)) %>%
-      rowwise() %>%
-      mutate(val = ifelse(val == 1, 0.9999, 
-                          ifelse(val == 0, 0.000001, val)))
-  )
-
-  rs <- webppl(program_code = hab.prior.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.prior.toPass,
-       data_var = "data")
-
-  rs.habituals.bda.prior <- bind_rows(
-    rs.habituals.bda.prior, 
-    rs %>% 
-      mutate(item = it) %>% 
-      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
-  )
-}
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
-
-example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
-                       "climbs mountains", "hikes", "runs", 
-                       "wears a suit", "wears a watch", "wears socks", 
-                       "writes poems", "goes to the movies", "plays the banjo"
-                       )
-
-rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
-  filter(Parameter == "mean") %>%
-  group_by(Variable, Gender, item) %>%
-  summarize(MAP = estimate_mode(value),
-            cred_upper = hdi_upper(value),
-            cred_lower = hdi_lower(value)) %>%
-  ungroup()
-rs.habituals.bda.prior.summary.wide <- left_join(
-  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
-    select(-Variable) %>%
-    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
-  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
-    select(-Variable) %>%
-    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
-)
-
-figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) %>%
-ggplot(.,
-       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
-            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = category))+
-    scale_shape_manual(values=c(21,22))+
-  #scale_color_solarized()+scale_fill_solarized()+
-  scale_fill_brewer(palette='Set1')+
-
-  geom_point(size=4, inherit.aes = F, 
-             aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            shape = Gender),  alpha = 0.9)+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  xlab("% of Americans who have DONE ACTION")+
-  ylab("Log Frequency of DOING ACTION")+
-  #scale_
-  coord_fixed(ratio = 1/8)+
-  theme(legend.title = element_text(hjust=0),
-        legend.position="bottom",
-        legend.direction="horizontal") +
-        scale_y_continuous(limits = c(-1.5, 6.5), 
-                     breaks = c(0, 2.5, 4, 5.9),
-                     labels = c("annually", "monthly", "weekly", "daily"))+
-  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
-                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-```
-
-```{r habituals-prior-model-forwardSample}
-rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value)
-
-rs.habituals.bda.prior.samples <- data.frame()
-for (i in 1:1){
-  rs.habituals.bda.prior.samples <- bind_rows(
-    rs.habituals.bda.prior.samples,
-    rs.habituals.bda.prior.spread %>%
-    rowwise() %>%
-    mutate(
-      a = mix_mean * mix_samplesize,
-      b = (1 - mix_mean) * mix_samplesize,
-      theta = rbeta(n = 1, shape1 = a, shape2 = b),
-      stable = rbinom(n = 1, size = 1, prob = theta),
-      logannualRate = ifelse(stable == 1, 
-                             rnorm(n = 1, 
-                                   mean = stableFreq_mean, 
-                                   sd = stableFreq_sd), -5),
-       annualRate =  exp(logannualRate)
-    )
-  )
-}
-```
-
-```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
-2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
-
-figure.habituals.priors.marginals <- bind_rows(
-  d.hab.priors.samples %>% 
-    mutate(src = 'data', 
-           val = log(val)),
-  rs.habituals.bda.prior.samples %>%
-    rename(gender = Gender, val = logannualRate) %>%
-    select(gender, item, val) %>%
-    mutate(src = 'model')
-  ) %>%
-  filter(item %in% example.habituals,
-         src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals)) %>%
-ggplot(. , aes( x = val, color = gender))+
-  geom_density(size = 0.8, aes( y = ..scaled.. ))+
-  facet_wrap(~item, nrow = 4)+
-  scale_color_solarized()+
-  xlab("Frequency")+
-  ylab("Scaled prior density")+
-  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.12),
-        axis.text.x = element_text(angle = 90))+
-    scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
-2a).
-Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on rates from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-### Data analysis and results
-
-All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-We built a Bayesian data analysis model for this prior elicitation task.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-First, it smooths effects that are clearly results of the response format.
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
-
-Question 1 elicits the proportion of people who have done an action before. 
-This number can be interpreted as a probability coming from a Beta distribution: $d_{mixture} \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture})$. 
-Question 2 elicits the rate or frequency with which a person does the action.
-This was modeled by a log-normal distribution: $\ln d_{stable} \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$. 
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
-That is, $P(h)$ was constructed by sampling $\lambda$ as follows:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{mixture}, \xi_{mixture}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{stable}, \sigma_{stable}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{true} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{false} \\
-		\end{cases}
-\end{align}
-
-We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
-We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$.
-If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
-If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before.
-We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years).
-Figure \ref{fig:habituals-prior-figure} (right) shows example inferred priors.
-
-<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
-<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
-<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
-<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
-<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-## Experiment 2b: Endorsing habitual statements
-
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Procedure and materials
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, \emph{In the past month, Bill smoked cigarettes 3 times}.
-The particular intervals used (\{weeks, months, years\}) were selected after examining the predictions of the speaker model (Eq.
-\ref{eq:S1}), for each item independently, to yield a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task.
-
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g., \emph{Bill smokes cigarettes}).
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants saw both a female character and a male character who drank beer).
-<!-- These were used for an exploratory analysis on differences in endorsements by gender of the target character. -->
-
-### Results
-
-```{r habituals-prior-mixture-summarize}
-d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
-  select(item, starts_with("mixture_")) %>%
-  gather(key, value, -item) %>%
-  group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
-  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
-  rowwise() %>%
-  mutate(
-    annualRate = annualRates[[as.character(time_period)]]*n_instances,
-    logAnnualRate = log(annualRate)
-  )
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
-                       "goes to the movies_month", "smokes cigarettes_month")
-fig.habituals.endorsement.vs.freq <- 
-  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21, size = 5)+
-  ylab("Human endorsement probability")+
-  xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
-                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
-                    filter(sentence %in% example.habituals), aes( label = habitual ),
-                       color = 'black', fill = 'white',
-    box.padding = unit(0.35, "lines"),
-    point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
-  scale_x_continuous(limits = c(-1,6), 
-                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
-                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        legend.position = "bottom")+
-  coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F))
-```
-
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.', eval=F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
-r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
-
-<!-- We find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.  -->
-<!-- This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{contrast class} is other people; not just other men or women).  -->
-<!-- Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered. -->
-
-```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.freq.mix.uniq <- unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, 
-    mixture, mix_low, mix_high
-  ))
-
-d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_low)
-
-d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_high)
-
-d.hab.endorse.regression.freq <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
-      prediction_lower = prediction,
-      prediction_upper = prediction,
-      src = "regression_freq"
-      )
-)
-
-r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
-
-r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
-  filter(logAnnualRate < 1.1)
-
-r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
-
-r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
-d.hab.endorse.regression.freq.mix <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
-      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
-      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
-      src = "regression_freq_distinct"
-      )
-)
-
-r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
-                                          "MAP_h", "prediction")
-
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-model_prefix <- "results-habituals-jointModel-S1-"
-
-# m.hab.samp <- data.frame()
-# m.hab.fixed.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
-#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-# 
-# }
-# 
-# save(m.hab.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.hab.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "habituals_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
-r2.habituals.rsa.fixed <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.fixed <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "some_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.uncertain <- compute_r2(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain <- compute_mse(
-  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
-                                          "MAP_h", "MAP")
-
-habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)
-
-r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)
-
-r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
-                                          "MAP_h", "MAP")
-
-habituals.endorsement.models <- bind_rows(
-  d.hab.endorse.regression,
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, logAnnualRate, mixture)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( 
-                                      "some_model",
-                                      "habituals_model",
-                                      "regression_freq", 
-                                      "regression_freq_distinct"
-                                     ),
-                      labels = c(
-                                 "Speaker model - fixed semantics",
-                                 "Speaker model - uncertain semantics",
-                                 "Referent frequency alone", "Distinctiveness + referent frequency"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.15)+
-  geom_errorbarh(alpha = 0.15)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")+
-  guides(fill = F)
-```
-
-```{r habituals-simulation-model}
-l0.hab.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
-
-var targetUtterance = "habitual";
-
-var roundTo3 = function(x){
-  return Math.round(x * 10000) / 10000
-}
-
-var lowerBound = -5, upperBound = 10, binWidth = 0.5;
-
-var stateBins =  _.range(
-  lowerBound, upperBound, binWidth
-)
-
-var thetaBins = map2(function(b1, b2){
-  var diff = Math.abs(b2 - b1) / 2;
-  return roundTo3(diff+ b1);
-}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state> _.min(thetaBins):
-         true
-}
-
-var priorParams = data.priorParams[0];
-
-var stable_female_params = betaShape({
-  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
-})
-
-var stable_male_params = betaShape({
-  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
-})
-
-// this marginalizes out the mixture parameter
-var statePrior = Infer({model: function(){
-  var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ? // 
-    flip(
-        categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_female_params), b) + Number.EPSILON
-          }, probBins )
-        })
-    ) ? // stable female distribution
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) : // unstable female distribution
-    _.min(stateBins) : 
-    flip(        
-      categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_male_params), b) + Number.EPSILON
-          }, probBins )
-      })
-    ) ? 
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) :
-    _.min(stateBins)
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:-5}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:-5})
-   var state_prior = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:lowerBound}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:lowerBound})
-    var theta = uniform(lowerBound, upperBound)
-    condition(
-      (utterance == "habitual") ? 
-      state > theta : 
-      (state > _.min(lowerBound))
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
-
-continuousListener0(data.utt[0])
-'
-```
-
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
-
-m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
-  filter(type == "prior", B %in% example.habituals.actions) %>%
-  rename(action = B, variable = C, gender = D, parameter = E) %>%
-  group_by(action, variable, gender, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(action, variable, gender, parameter, MAP) %>%
-  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
-  select(-variable, -gender, -parameter) %>%
-  spread(param, MAP)
-
-hab.listener.predictions <- data.frame()
-
-for (p in example.habituals.actions){
- priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
-
- inputData = list(priorParams = priorParams,
-                  utt = "habitual")
-
- l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
-
- hab.listener.predictions <- bind_rows(
-   hab.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
-   )
-
-}
-
-# m.gen.fullmodel.target.prevalence <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   group_by(param, property, category) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-# m.gen.speakerBeliefs <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   mutate(Sentence = paste(category, property)) %>%
-#   filter(Sentence %in% example.generics)
-
-# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-# gen.inset.distributions <- bind_rows(
-#   gen.listener.predictions %>%
-#     mutate(category = NA),
-#   m.gen.speakerBeliefs %>%
-#     select(property, val) %>%
-#     rename(value = val) %>%
-#     mutate(Parameter = "speakerBeliefs")
-# )
-# 
-# 
-# category.text.labels <- data.frame(property = c("dont eat people", 
-#                       "carry malaria", "lay eggs",  "are female", "have spots"),
-#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Habitual")),
-         action = fct_relevel(action,
-                                "climbs mountains", "hikes", "runs",
-                              "goes to the movies", "smokes cigarettes"
-                              ) ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~action, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
-  #scale_linetype_manual(values = c(3, 4, 1))+
-  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
-      scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-```
-
-```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
-Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
-These distributions are inferred using both data sources from Expts.
-2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
-grid.arrange(fig.habituals.endorsement.vs.freq, 
-             habituals.endorsement.models,
-             habituals.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
-For all analyses, we collapse across gender of the referent character.
-<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
-
-<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
-Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
--->
-
-<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
-<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
--->
-<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
--->
-<!-- We see no appreciable differences in endorsements for the two genders.  -->
-<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
-<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
-
-#### Referent frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
-This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
-First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
-It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
-We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}).
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
-This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-#### Distinctiveness and referent frequency
-
-In the prior elicitation task (Expt.
-2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
-With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement.
-This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.
-
-```{r habituals-distinctiveness-counterexamples}
-
-format_endorsment_ci <- function(
-  df, estimate = "MAP_h", low = "low",
-  high = "high", sigfigs = 2){
-  return(paste(
-    round(df[[1,estimate]], sigfigs),
-    " [",
-    round(df[[1,low]], sigfigs),
-    ", ",
-    round(df[[1,high]], sigfigs),
-    "]", sep = ""))
-}
-
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
-
-movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
-                                                        time_period == "year"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
-
-banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
-                                                        time_period == "2 years"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-```
-
-We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture some of the subtle sensitivities in endorsments.
-For example, endorsements for *goes to the movies* for a person who has *gone to the movies* three times in the past year are about $`r movies.year.data`$, while this model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-Going to the movies is relatively common and going three times in a year is not very frequent, and yet people still strongly endorse the habitual. 
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, this simple regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold RSA model
-
-The above regression models are too rigid to explain the flexibility in habitual endorsements. 
-Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge. 
-Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold.
-To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
-
-We used the speaker model $S_1$ (Eq.
-\ref{eq:S1}) with the priors elicited above (Expt.
-2a) to predict felicity judgments in Expt.
-2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
-The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
-As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
-2b.
-To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
-
-On each trial of the experiment, the participant was told a person did a particular past frequency and was asked to evaluate the corresponding habitual statements.
-A fixed threshold model only conveys that the a person *has done this action before*, analagous to how the quantifier *Some* conveys that there exists at least one entity with the feature.
-Under this hypothesis, all of the items used in our experiment would qualify as good habitual statements as the target character always did the action three times during some time window.
-Incorporating this semantics into the RSA framework makes it difficult for the speaker model (Eq.
-\ref{eq:S1}) to differentiate between the various habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet).
-The model has to decide between producing silence (which is always true) and a very uninformative statement (which is almost always true).
-The relatively small difference in information-gain on behalf of the listener is reflected in the small dynamic range of endorsments for the speaker.
-Overall, this model does poorly at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
-
-Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
-With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
-Thus, this model makes the same predictions for different target frequencies in the same event.
-For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.
-
-#### Uncertain-threshold RSA model
-
-We constructed the same joint model for the uncertain threshold RSA speaker model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-As shown in Figure \ref{fig:habituals-endorsement-figure}(top right: top right facet), the pragmatic speaker model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-
-### Discussion
-
-In Expt.
-2b, we manipulated the event type (e.g., drinks coffee vs.
-beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
-year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.
-
-Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
-The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.
-
-Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
-
-<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
-
-<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
--->
-
-<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
-<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
-<!--   Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
--->
-<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
-<!--   \label{fig:tj3} -->
-<!--   \vspace{-7pt} -->
-<!-- \end{figure*} -->
-
-## Experiment 2c: Measuring predictive frequency
-
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
-Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
-
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
-       aes(x=logAnnualPastRate,
-                              y = mean,
-                              ymin = ci_lower, ymax = ci_upper,
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
-  scale_shape_manual(values=c(21,22,23))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-
-fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
-  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
-                 fill=condition, shape=condition,
-                 xmin = future_lower, xmax=future_upper,
-                 ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.8)+
-  geom_errorbarh(alpha=0.8)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 1, size = 4)+
-  xlab("Predicted frequency (log scale)")+
-  ylab("Human habitual endorsement")+
-  scale_x_continuous(limits = c(-4.2,7.2), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=11.4)+
-  scale_fill_solarized()+
-  guides(fill = F, shape = F)+
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-    legend.position="bottom",
-    legend.direction="horizontal"
-    )
-
-```
-
-```{r habituals-predictive-rsa}
-n_chains <- 3
-# n_samples <- 500000
-# burn <- n_samples / 2
-# lg <- 150
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 50
-
-m.hab.pred.samp <- data.frame()
-m.hab.past.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-
-  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "targetH_past-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-
-#}
-# 
-# 
-# # 
-# save(m.hab.pred.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# # # 
-# save(m.hab.past.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
-
-m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorsement <- m.hab.pred.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.predictive.endorsement
-  ) %>%
-    mutate(src = "predictive_model"),
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.pastmodel.endorsement
-  ) %>%
-    mutate(src = "past_model")
-)
-
-r2.habituals.rsa.past <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.past <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.predictive <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.predictive <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
-
-habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - past frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-
-habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  #guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-#habituals.predictive.predictive.model
-```
-
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
-
-                                 ))) %>%
-  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
-grid.arrange(
-  arrangeGrob(
-    fig.hab.freq.predictive.vs.past, 
-    fig.hab.endorse.vs.predfreq, 
-    habituals.predictive.past.model, 
-    habituals.predictive.predictive.model + theme(legend.position="none"),
-    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
-legend_b, nrow=2,heights=c(8, 1))
-
-#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
-```
-
-### Methods
-
-We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 2c.
-The only difference from Expt. 2c is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-
-When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
-], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
-
-We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
-The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
-
-We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
-Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
-The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
-
-<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
-<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
-<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
-<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
-<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
-
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
-This may be due, in part, to an effect of the experimental context on participants:
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
-## Discussion
-
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
-2a).
-We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
-By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
-In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
-Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
-
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2d).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
-
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
-Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
-
-# Case Study 3: Causal Language
-
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
-
-Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
-In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
-<!-- [Gerstenberg] -->
-Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
-Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
-
-Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
-
-In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
-
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
-In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
-
-## Experiment 3a: Manipulating the feature-probability priors for causes
-
-In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our feature-probability prior manipulation.
-
-<!-- examine causal domains that vary as to whether or not probabilistic causes are plausible and whether or not a background cause of the event is intuitively present. -->
-<!-- We introduce participants to the results of several experiments about each domain and see how different experimental results update participants' beliefs about causal power in these domains. -->
-
-<!-- People have theories about how different casusal systems work.  -->
-<!-- Physical causation tends to have a deterministic bend to it: If one billiard ball hits a second with a certain force, the second will respond by moving with a certain force.  -->
-<!-- If the experiment is repeated exactly, we would expect the same results. -->
-<!-- In other domains, probabilistic causes are plausible: Giving a sick animal a certain medication may sometimes make it better and other times it won't.  -->
-<!-- Finally, some events could have multiple possible causes: Testing whether or not a drug makes an animal *blink* might be difficult because animals will tend to *blink* even without intervention.
--->
-
-### Method
-
-```{r causal-priors-data}
-d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
-                           sep= ""))
-
-n.subj.cas <- length(unique(d.cas.priors$workerid))
-
-ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-```
-
-```{r causal-priors-runModel, cache = T}
-causal.distributions <- levels(factor(d.cas.priors$distribution))
-p <- causal.distributions[1]
-m.cas.marginal.prevalence <- data.frame()
-m.cas.endorse.priors.summary <- data.frame()
-
-for (p in causal.distributions){
-  priorData <- 100*filter(d.cas.priors, distribution == p)$response
-
-  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
-
-  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
-    spread(Parameter, value) %>%
-    rowwise() %>%
-    mutate(
-      a = g * d,
-      b = (1 - g) * d,
-      stable = rbinom(n = 1, size = 1, prob = phi),
-      prevalence = ifelse(stable == 1, 
-                             rbeta(n = 1, shape1 = a, shape2 = b),
-                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
-      distribution = p
-    )
-  )
-
-  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
-                                            m.cas.endorse.priors %>% 
-                                              mutate(distribution = p) %>%
-                                              group_by(distribution, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-}
-
-```
-
-#### Participants
-
-We recruited `r n.subj.cas` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average `r ave.minutes.cas` minutes and participants were compensated \$0.50 for their work.
-
-<!-- The different kinds of system are described in more detail below. -->
-<!-- Participants are then told that the team of scientists is conducting experiments with different possible causes (e.g., different kinds of foods). -->
-
-#### Procedure
-
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
-
-In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
-The story for the "sleepy animals" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. 
-Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-The results are shown below:
-\end{quotation}
-
-Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
-
-Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
-
-#### Materials
-
-Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
-The cover story for the "tall plants" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
-Your team runs experiments trying to make feps grow tall with different fertilizers. 
-The results are shown below:
-\end{quotation}
-
-Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
-In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
-
-```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-4 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3, eval = F}
-sample.dists <- bind_rows(
-  data.frame(
-    dist = "rare weak",
-    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common weak",
-    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
-  ),
-  data.frame(
-    dist = "rare deterministic",
-    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common deterministic",
-    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
-  )
-) %>%
-    mutate(Distribution = factor(dist, 
-                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak")))
-
-figure.causals.priors <- bind_rows(
-  sample.dists %>%
-    mutate(src = "stimuli") %>%
-    select(-dist),
-  m.cas.marginal.prevalence %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
-    mutate(Distribution = factor(distribution, 
-                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))) %>%
-    select(Distribution, prevalence) %>%
-    mutate(src = 'model') %>%
-    rename(x = prevalence)
-) %>%
-  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
-                ))+ 
-  geom_density( adjust = 1.3, 
-               size = 1.2,
-               aes( y = ..scaled..))+ #
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_fill_solarized()+scale_color_solarized()+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0.1, 0.4))+
-  scale_linetype_manual(values = c(2, 1))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
-  guides(fill = F, color = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal')
-```
-
-```{r s1-model}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-var alpha = 2;
-var mixture = data.prior[0].phi;
-var priorParams = betaShape(data.prior[0]);
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var speaker1 = function(state) {
-  Infer({model: function(){
-    var utterance = sample(utterancePrior);
-    var listener_posterior = listener0(utterance);
-    factor(alpha * listener_posterior.score(state))
-    return utterance
-  }})
-}
-
-probability(speaker1(data.state[0]), "generic")
-'
-```
-
-```{r causal-endorsement-predictions, cache = T, eval = F}
-causal.priorParams <- m.cas.endorse.priors.summary %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           Parameter != 'marginalPrevalence') %>%
-  select(distribution, Parameter, MAP) %>%
-  spread(Parameter, MAP)
-experimental.frequencies <- c(0.2, 0.7)
-causal.endorsement.predictions <- data.frame()
-for (p in causal.priorParams$distribution){
-  for (s in experimental.frequencies){
-
-    inputData = list(prior = filter(causal.priorParams, distribution == p), 
-                     state = s)
-
-    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
-
-    causal.endorsement.predictions <- bind_rows(
-      causal.endorsement.predictions,
-      data.frame(state = s, distribution = p, prob = s1.rs)
-    )
-  }
-  print(p)
-}
-```
-
-<!-- #### Materials  -->
-
-<!-- The kind of causal events in question were selected to correspond roughly to different positions in a theoretically meaningful space defined by the model. -->
-<!-- Research in elemental causal induction suggests people use causal models that correspond to a mixture probability distributions, where one component of the distribution is a consequence to the intrinsic causal force while the other component is a result of some extrinsic background cause.
--->
-<!-- So we designed materials that corresponded to domains where various parameters of that mixture model could be manipulated.  -->
-
-<!-- A second dimension of man ipulation corresponds to the extent to which *determinism* is expected in the domain.  -->
-<!-- For example, people's theories of physical causation tends to be more deterministic (i.e., favoring probabilities 1 and 0) then causation in the social or psychological domain.  -->
-
-### Results
-
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
-These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
-We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
-
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
-
-d.cas.priors %>%
-  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
-      mutate(Distribution = factor(distribution, 
-                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>% 
-ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 0.8, alpha =0.8, 
-               size = 1.2,
-               aes( y = ..scaled..))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
-```
-
-### Model predictions
-
-... run RSA model using fixed parameters and MAP estimates of these priors ?
-
-## Experiment 3b: Endorsing Causal Language
-
-In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-
-### Method
-
-Most of the experiment was identical to that of Experiment 3a.
-
-```{r causal-endorsement-data}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
-ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-
-n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-```
-
-#### Participants
-
-We recruited `r n.subj.cas.endorse` participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-None of the participants had participated in Experiment 3a. 
-The experiment consisted of one trial and took on average `r ave.minutes.cas.endorse` minutes; participants were compensated \$0.25 for their work.
-
-#### Procedure and materials
-
-The materials were the same as in Experiment 3a.
-Phase 1 of the experiment was identical to that of Experiment 3a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
-The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
-Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Partipants responded by either clicking "Yes" or "No".
-
-After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
-
-```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Target frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-```{r causals-fullmodel}
-n_chains <- 1
-n_samples <- 5000
-burn <- n_samples / 2
-lg <- 5
-i <- 1
-
-model_prefix <- "pilot-results-causals-jointModel-S1-"
-
-m.cas.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/causals/results/", 
-                    model_prefix, "smntcs_causal-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
-}
-
-# n_chains <- 1
-# n_samples <- 1000
-# burn <- n_samples
-# lg <- 5
-# i <- 1
-# m.hab.fixed.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/", 
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-# }
-
-# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-#   filter(type == 'predictive') %>%
-#   rename(habitual = B, time_period = D, binned_freq = E) %>%
-#   group_by(habitual, time_period, binned_freq) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.cas.fullmodel.endorsement <- m.cas.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(dist, frequency) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
-m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
-  filter(type == "prior") %>%
-  rename(variable = item, parameter = roundedFreq) %>%
-  group_by(dist, variable, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
-
-m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(dist, variable, parameter, MAP) %>%
-  mutate(param = paste(variable, parameter, sep = "_")) %>%
-  select(-variable, -parameter) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-cas.listener.predictions <- data.frame()
-
-for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
- priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
- cas.listener.predictions <- bind_rows(
-   cas.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
-   )
-}
-
-inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
-
-causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, 
-                              levels = c("state_Prior","state_Posterior"),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Causal")),
-    Distribution = factor(distribution, 
-                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>%
-  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~Distribution, nrow = 1)+
-  scale_fill_manual(values =inset.color.order )+
-  scale_color_manual(values = inset.color.order)+
-  scale_alpha_manual(values = c(0.1, 0.8))+
-  scale_linetype_manual(values = c(2, 1))+
-  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Feature-probability") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)
-```
-
-```{r}
-md.caus.endorse <- left_join(
-  m.cas.fullmodel.endorsement,
-    d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution)
-)
-
-n.caus.endorse <- length(md.caus.endorse$MAP_h)
-r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
-mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")
-
-```
-
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
-figure.causals.endorsement <- bind_rows(
-  m.cas.fullmodel.endorsement %>%
-    mutate(src = "model"),
-  d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
-    mutate(src = 'data')
-) %>%
-  ungroup() %>%
-  mutate(
-    src = factor(src, levels = c( "data", "model")),
-    dist = factor(dist, 
-           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
-           labels = c(
-                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
-    ) %>%
-  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = src, alpha = src))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(0.3), alpha = 1)+
-  #geom_line(position = position_dodge(0.3))+
-  #theme(axis.text.x = element_text(angle = 90))+
-  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_alpha_manual(values = c(1, 0.3))+
-  #scale_fill_solarized()+
-  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("")+
-  ylab("Proportion Causal Endorsement")+
-  facet_grid(.~frequency)+
-  coord_flip()+
-  guides(fill = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
-```
-
-```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
-Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
-These distributions are inferred using both data sources from Expt.
-3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
-grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
-             layout_matrix = cbind(c(1,1,2)))
-
-# ,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-### Results
-
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
-As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
-
-As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
-When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
-By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
-The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
-
-## Discussion
-
-In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
-We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
-In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
-
-In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
-These two features of the domains make them particularly amenable to manipulation.
-That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
-
-It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
-If this were happening in our domains, we would expect this to show up in the results of Expt.
-3a.
-Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
-]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
 

### 2017-11-18 paper/case1-generics.Rmd
fix sectioning

@@
 
-In this experiment, we elicit human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].
+In this experiment, we elicit human endorsements for generalizations about categories (*generics*) taken from the linguistic and psychological literature on generics [@Prasada2013].
 The goal of this study is to observe a range of endorsements for generic statements about animal categories.
 
-#### Method
+### Method
 ```{r eval = F}
@@
 
-##### Participants
+#### Participants
 
@@
 
-##### Procedure and materials
+#### Procedure and materials
 
@@
 
-### Uncertain threshold RSA model
+#### Uncertain threshold model
 

### 2017-11-18 paper/case2-habituals.Rmd
streamline habituals procedure; make predictive expts a sigle expt

@@
 
+We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes."). 
 We use the same computational model and follow the same general experimental structure as in the first case study. 
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes."). 
-First, we measure the prior distribution over the feature-probabilities for different kinds of events (Expt. 2a).
-We do this using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b.
-Then, we test our model on endorsements of habitual sentences, manipulating the frequency of a referent person doing an action (Expt. 2b).
+First, we measure the prior distribution over the frequencies for different events/actions (e.g., how often different people smoke cigarttes; Expt. 2a).
+We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt.
+2b), and use our computational model to predict the habitual endorsements.
+<!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
 In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring participants' predictions about future rates when causal forces enable or prevent the action (Expt. 2c). 
-We separately measure endorsements under the same contexts (Expt.
-2d) and use the prediction measurements (Expt.
-2c) as the referent feature-probabilities $h$ that the endorsement model is trying to communicate.
+We do this by measuring participants' predictions about future frequencies when causal forces enable or prevent the action and separately measure endorsements of habituals under the same contexts (Expt.
+2c).
+We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
 
@@
 
-<!-- In our main test of the hypothesis, we collect felicity or truth judgments for habitual statements about people's actions. -->
-<!-- The computational model described in Eq.
-\ref{eq:S1} is fully specified except for the prior distribution over the frequency of an event $P(h)$, which plausibly varies across different kinds of events.
--->
-<!-- First, we measure the prior distribution, and use it and the computational model to predict human endorsement of habitual statements. -->
-
 ## Experiment 2a: Measuring the feature-probability prior for events
 
-In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2d).
+In this experiment we elicit the prior distributions over frequencies $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (measured in Expt.
+2b \& 2c).
 For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the likely frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
@@
 
-We created thirty-one events organized into pairs or triplets from 5 different conceptual categories:
-<!-- We created twenty-seven events organized into pairs or triplets from 5 different conceptual categories:  -->
-food and drug (e.g. \emph{eats caviar}, \emph{eats peanut butter}), 
-work (e.g. \emph{sells things on eBay}, \emph{sells companies}), 
-clothing (e.g. \emph{wears a suit}, \emph{wears a bra}), 
-entertainment (e.g. \emph{watches professional football}, \emph{watches space launches}), and 
-hobbies (e.g. \emph{runs}, \emph{hikes}). 
-Items were chosen to intuitively cover a range of likely frequencies of action, as well as to provide a minimal comparison to another item by having a common superordinate action (e.g.
-\emph{eating} caviar vs.
-peanut butter).
+To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
+For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. \emph{eating} caviar vs. peanut butter).
+The events were chosen to intuitively cover a range of likely frequencies.
+In total, thirty-one events were used.
+For a full list the stimulus set, see Table \mht{make table of stimuli}.
 
@@
 
-## Experiment 2b: Endorsing habitual statements
-
-We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task (Expt. 2a).
+## Experiment 2b: Habitual endorsements
+
+In this experiment, we elicit human endorsements for generalizations about events (*habituals*) while manipulating the frequency with which the target event occurs.
 
@@
 
-#### Procedure and materials
+#### Materials
+
+Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
+The frequencies were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
+For example, relatively high frequencies were chosen \mht{(e.g., 3 times every week vs.
+2 weeks vs.
+month)} for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen \mht{(e.g., )}.
+In total, \mht{93} unique items were created by pairing frequencies with events.
+
+#### Procedure
 
@@
 For example, "In the past month, Bill smoked cigarettes 3 times".
-The particular intervals used (\{weeks, months, years\}) were selected by simulating predictions of the endorsement model (Eq.
-\ref{eq:S1}) with the goal of yielding a range of predicted endorsement rates.
-The items were the same as in the prior elicitation task (Expt. 2a).
-
 Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
@@
 
+<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
+
 ### Results
+
+<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
+-->
+<!-- Several features in our data argue against this hypothesis. -->
+<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
+-->
+
+Habitual sentences were endorsed for a wide range of frequencies.
+When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
+When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
+
+In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
+This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
+Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
+We now turn to our model-based analyses.
+For all analyses, we collapse across gender of the referent character,
+
+### Endorsement model comparison
 
@@
 Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model to better understand the data and the contribution of our model.
-For all analyses, we collapse across gender of the referent character.^[
-  In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
-  This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
-  Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
-]
+
+#### Frequency baseline
+
+Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
+In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$).
+An account purely based on the referent frequency does not explain endorsements in this data set.
+Instead, we pursue an explanation where prior beliefs interact with an underspecified literal semantics to produce the pattern of habitual endorsement observed.
+
 <!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
@@
 
-#### Referent frequency baseline
-
-The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
-Several features in our data argue against this hypothesis.
-<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
--->
-When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
-When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)
-
 <!-- This is unlikely to be the case based on , which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
@@
 
-#### Distinctiveness and referent frequency baseline
+#### Distinctiveness and frequency baseline
 
@@
 
-In Expt.
-2b, we manipulated the event type (e.g., drinks coffee vs.
-beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs.
-year) and measured the corresponding endorsements for habitual statements.
-We saw tremendous flexibility in the frequencies that leads participants to endorse habituals. 
-Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
-The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
-This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* endorsement model is doing.
+Habitual sentence endorsement exhibits context-sensitivity directly parallel to that of generic sentences (Case Study 1).
+Habituals are endorsed for a wide range of frequencies, but show systematic patterns relative to the prior distribution of frequencies, as formalized by the uncertain-threshold model.
+Again, we articulated a number of alternative models and found that only the underspecified threshold model was able to explain the variability in endorsements.
 
@@
 By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model. 
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.
+The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question.
+
+In Expt. 2b, participants were given a statement about how often a person has done the action in the past and asked to judge the correspoding habitual statement.
+This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
+In Expt. 2c, we investigate this question by manipulating and measuring *predictive frequency* and habitual endorsement, while keeping fixed past frequency.
+
+<!-- In Expt.
+2b, we manipulated the frequency with which a person did an action in the past (e.g., three times in the past week vs.
+in the past year) for a wide range of events (e.g., drinks coffee vs.
+beer) and measured endorsements for the corresponding habitual statements.
+-->
+
+<!-- The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements.  -->
+<!-- This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* endorsement model is doing.  -->
 
 <!-- People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation.  -->
-
-In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).
 
@@
 
-## Experiment 2c: Measuring predictive frequency
+## Experiment 2c: Observations vs. Predictions
 
@@
 Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *know* about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.
-
-In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
-In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
-In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
-This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.
+On one hand, speakers can only *truly be certain* about what has happened in the past.
+On the other hand, language has a communicative function, and it would seem useful for speakers to convey their predictions of what will be the case in the future.
+
+We address this by introducing causal events that either enable or prevent future actions.
+In one condition, participants make a prediction about what will be the case in the future (*predictive frequency*).
+In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
+<!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
+We then compare two uncertain-thresholds models to each other: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt.
+2b).
 
@@
 ```
-
-### Methods
-
-We recruited `r n.subj.hab.pred` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred/60,1)` minutes on average and participants were compensated \$0.40.
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials and the use of a different dependent measure. 
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, on one third of the trials, participants were presented with a \textbf{preventative sentence} (e.g. \emph{Yesterday, Bill quit smoking.}).
-On one third of the trials, participants were presented with an \textbf{enabling sentence} (\emph{Yesterday, Bill bought a pack of cigarettes.}) 
-The final third of trials had no additional evidence and were identical to Expt. 2b.
-
-Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
-To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
-In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-
-Participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
 
@@
 ```
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-## Experiment 2d: Endorsing habituals under predictive-manipulated conditions
 
@@
 
-### Methods
-
-We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
-None of the participants had completed Expt. 2c.
-The only difference from Expt. 2c is the dependent measure. 
-On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
+### Method
+
+#### Participants
+
+We recruited `r n.subj.hab.pred + n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
+`r n.subj.hab.pred` were assigned to the *predictive frequency* condition and `r n.subj.hab.pred.endorse` were assigned to the *sentence endorsement* condition.
+The experiment took on average `r round(ave.seconds.hab.pred/60,1)` minutes (*predictive frequency*) and `r round(ave.seconds.hab.pred.endorse / 60)` minutes (*sentence endorsement*). 
+Participants were compensated \$0.40.
+
+#### Materials
+
+The events used were a subset of those used in Expts. 2a \& b (21 of the original 31).
+In addition, in order to increase the variability of responses across the experimental conditions, participants only saw the frequencies that led to the most intermediate endorsement of the habitual in Expt.
+2b.
+We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
+In addition, we crafted statements that were intended to either increase the frequency (*enabling*; e.g., "Yesterday, Bill bought a pack of cigarettes.") or decrease the frequency (*preventative*; "Yesterday, Bill quit smoking.") of the event in the future.
+See Table \mht{one table for Expt 2 stimuli} for a full list of the enabling and preventative information.
+
+#### Procedure
+
+The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials.
+On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
+Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2b), in equal proportions.
+
+In the *predictive frequency* condition, participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
+In the *sentence endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
 
 ### Results
+
+<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
+-->
+<!-- As we assumed for the prior elicitation task (Expt.
+2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
+-->
+<!-- $$ -->
+<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
+<!-- $$ -->
+
+#### Predictive frequency
+
+Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
+We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
+This means that our model makes identical predictions for Expt.
+2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
+Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
+
+```{r habituals-predictive-elicitation-predictions}
+lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
+     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
+       (1 + condition | workerid) + 
+       (1 + condition | item)
+)
+lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
+```
+
+We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
+To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
+Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
+).
+There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
+).
+Finally, past frequency was a significant predictor of predicted future frequency (
+$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
+$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
+).
+
+#### Sentence endorsement
 
@@
 
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt.
+Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the action (measured in Expt.
 2a).
-We saw that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b).
-In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
+Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b \& c).
+In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
 By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
-In particular, a fixed threshold model that has access to the same prior knowledge as our model and goes through the same information-theoretic decision making procedure as our speaker model is unable to make different predictions for different frequencies.
+In particular, a fixed threshold model that has access to the same prior knowledge and uses the same information-theoretic decision rule as our uncertain-threshold model is unable to make different predictions for different frequencies.
 Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt.
-2c) and using that, with the model, to predict the felicity of habitual sentences (Expt.
-2d).
-To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.
+In Expt. 2c, we further investigated the nature of the underlying feature-probability scale by introducing enabling and preventative causal evidence.
+We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
+We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is able to predict the influence of top-down moderators on habitual endorsement.
+<!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.
+-->
 
 In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
-Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
-In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.
+<!-- Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
+-->
+In our final case study, we extend our theory to communicating generlizations about causal relationships, and experimentally manipulate the feature-probability priors to examine whether or not they are causally related to endorsing generalizations in language.
 

### 2017-11-22 paper/case3-causals.Rmd
streamline intro to causals, make table with stimuli, edit procedure

@@
 
-Learning that an event consistently tends to result in another event serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a].
-Communicating generalizations about causally related events is potentially highly valuable because relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.
-The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
+Learning to that an event consistently tends to result in another event is a critical kind of generalization for understanding how the world works. 
+Adults and children can infer causal relationships from just a few examples [@Gopnik2000; @Schulz2004] and computational models have been used to formalize the problem of *elemental causal induction*, or learning a causal relationship from observational data [@Griffiths2005; @Kemp2010a].
+Having induced a causal relationship from observational data, people can communicate their causal knowledge using language. 
+Indeed, when causal relations are nonobvious, causal language helps children as young as 2-years learn those relations [@Bonawitz2010].
 
-Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events. 
-In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough). 
-<!-- [Gerstenberg] -->
-Ascribing causality to a singular pair of conjoined events is itself a challenging problem [e.g., @Gerstenberg2015how]. 
-Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a].
-
-Language provides a way to bypass the observational data needed to make a causal induction.
-Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].
+<!-- Such *token causation*  -->
+<!-- serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a]. -->
+<!-- Recognizing an event as *causal* is a challenging problem [e.g., @Gerstenberg2015how]. -->
+<!-- Inducing a generalization  -->
+<!-- Communicating generalizations about causally related events is highly valuable because  -->
+<!-- relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.  -->
+<!-- The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
+-->
+<!-- Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events.  -->
+<!-- In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough).  -->
+<!-- <!-- [Gerstenberg] -->
+<!-- Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a]. -->
+<!-- Language provides a way to bypass the observational data needed to make a causal induction. -->
 
 In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
+In this last set of experiments, we explicitly test the relationship between the feature-probability priors and endorsements of generalizations about causes.
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
 
-In Experiment 3a, we manipulate participants' beliefs about a causal system and measure their updated beliefs, serving a manipulation check.
-In Experiment 3b, we test whether these manipulated priors give rise to different endorsements of causal statements.
+## Experiment 3a: Manipulating priors for causes
 
-## Experiment 3a: Manipulating the feature-probability priors for causes
-
-In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
-This prediction task serves as a manipulation check for our feature-probability prior manipulation.
+In this experiment, we manipulate and measure participants' background knowledge in order to check whether or not manipulation of participants' background knowledge was successful. 
+Experiment 3b (*causal endorsement*) will then follow a mostly-identical experimental procedure.
 
@@
 
+#### Materials
+
+Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or plants grow tall). 
+Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the proprety (e.g., a naturally occurring herb causing animals to be sleepy).
+The two cover stories can be seen in Table \@ref(tab:causalItems).
+
+Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure \@ref(fig:causals-conditions). 
+In two of the conditions, participants saw results that were approximately all the same across the various experiments. 
+In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
+In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
+These distributions had the feeling that either there was some background cause which gave rise to the effect (e.g., a simple base rate) or that all substances were equally as efficacious at producing the effect.
+
+The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
+These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
+These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect.
+
+\begin{table}[]
+\centering
+\label{tab:causalMaterials}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{lll}
+                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\
+Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
+Your team runs experiments trying to make feps grow tall with different fertilizers.
+& On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy.
+Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
+\\
+Evidence statement & Your team gave fertilizer B to 100 different feps.
+Of those 100 treated, 2 feps grew tall.
+& Your team gave herb C to 100 different cheebas.
+Of those 100 treated, 98 cheebas were made sleepy.
+\end{tabular}
+}
+\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
+\end{table}
+
+```{r causalExpt, fig.cap="Overview of Experiment 3.
+A: Results of previous experiments are shown one at a time.
+One of the results were lost.
+B: Particiapnts are asked to review results before continuing.
+C: Prior elicitation task.
+D: Causal endorsement task."}
+knitr::include_graphics("figs/causal-expt.pdf", dpi = 108)
+```
+
 #### Procedure
 
-The experiment is a single-trial experiment with 2 phases to the trial.
-In the first phase, participants are given a story about a causal domain.
-In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).
+Each participant saw only one cover story with one distribution of previous experiments (i.e., the experiment was a single trial).
+<!-- In the first part of the trial, participants learned about different substances' ability to produce an effect ("previous experimental results"). -->
+<!-- Participants read a cover story and clicked a button to show the results of successive previous experiments. -->
+<!-- For each previous experiment, participants were presented with an *evidence statement* as well as a numerical representation of the results shown in a table above the text. -->
+<!-- The table was filled in gradually with each successive experiment.  -->
+<!-- The results of one experiment was said to be lost, and a "?" was placed in the table (Figure \@ref(fig:causalExpt)).  -->
+<!-- (These lost results would be found in the *causal endorsement* task, Expt. 4b). -->
+<!-- Participants were instructed to take a final look at the results of all of the previous experiments before continuing.  -->
+<!-- Once participants clicked the "continue" button, they were brought to a new screen where they would make predictions about new substances that have yet to be tested (Figure \@ref(fig:causalExpt)).
+-->
+<!-- Participants saw a list of new substances and slider bars that ranged from 0 to 100.  -->
+<!-- The second phase serves as a measurement of participants' feature-probability priors. -->
 
-In the first phase, participants are told that they are an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
+Participants were told that they were an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
 The story for the "sleepy animals" condition read:
@@
 Participants then must click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described verbally (e.g., *Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.*) as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though one of the experiments had their results misplaced so they cannot report on the results at that point (the significance of this "missing experiment" will be described in Experiment 4b).
+Experiment results appear one at a time (upon a click), and are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas.
+Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
+Eleven "experiments" are shown, though the results of one experiment were said to be lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)). 
+(These lost results would be found in the *causal endorsement* task, Expt. 3b).
 After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
 
-Upon proceeding to phase 2, the table of "experiment results" is removed and participants are told more experiments were conducted.
+Upon clicking the continue button, the table of "experiment results" is removed and participants are told more experiments were conducted.
 Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next four treatments (e.g., herbs M, N, P, Q, and R).
+Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).
 
-#### Materials
-
-Participants were either told a story of trying to make animals sleepy (described above) or trying to make plants grow tall. 
-The cover story for the "tall plants" condition read:
-
-\begin{quotation}
-You are an astronaut-scientist exploring a distant planet. 
-On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. 
-Your team runs experiments trying to make feps grow tall with different fertilizers. 
-The results are shown below:
-\end{quotation}
-
-Participants with either cover story were then exposed to one of four distributions of "experiment results", corresponding to our four experimental conditions, shown in Figure \ref{fig:causals-conditions}.
-In two of the conditions, participants saw results that were all approximately the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
+After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigated (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
+This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
 
 ```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-4 (stimuli) and priors reconstructed from participants' responses (model).
+3 (stimuli) and priors reconstructed from participants' responses (model).
 ", fig.width = 8, fig.height = 3, eval = F}
@@
 
-The distributions that resulted from participants predicting the causal efficacy of the new herbs / fertilizers are shown in Figure \ref{fig:figure-causals}.
+The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure \ref{fig:figure-causals}.
 These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
@@
 
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 4a)."}
+```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 3a)."}
 
@@
 
-### Model predictions
-
-... run RSA model using fixed parameters and MAP estimates of these priors ?
-
-## Experiment 3b: Endorsing Causal Language
+## Experiment 3b: Causal Endorsements
 
@@
 
-The materials were the same as in Experiment 3a.
-Phase 1 of the experiment was identical to that of Experiment 3a.
-In phase 2 of the endorsement task, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
+The materials were the same as in Experiment 3a,
+The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)).
+Upon continuing past the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found.
 The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
@@
 
-After responding, participants were then asked to recall what the herbs / fertilizers aimed to achieve (e.g., "make animals sleepy") and one of the ten results they saw on the previous page. 
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
+After responding, participants completed the same attention check as Expt. 3a.
 
@@
 In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
-We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
+This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
 In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
@@
 In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-In addition to their plausibility, these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
+We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
 These two features of the domains make them particularly amenable to manipulation.

### 2017-12-05 paper/comgen-paper.Rmd
edits to intro to gd

@@
 library(knitr)
+library(kableExtra)
 library(cowplot)
@@
 It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements --- statements understood by even the youngest language users --- can display complex sensitivity to context.
+Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
 We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human endorsement data.
-
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
-What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
-Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
-This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
-Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.
-
-The theory we present here has a number of desirable features that go beyond alternative accounts.
-The first is that our theory is accompanied by a formal model, which makes precise quantitative predictions about endorsments of statements that convey generalizations.
-The formal Bayesian model provides a clean separation of the semantics of a generalization from background, world knowledge.
-This is critical to understanding the contribution of a generalization in language above and beyond background knowledge.
-We believe this has been a stumbling block for formal semantic models that try to argue in one or another way for a statistical or probabilty based approach [@Cohen1999; @Nickel2008].
-As @Nickel2016 notes, genericity is particularly difficult to study because it intersects with many other phenomena in language (e.g., gradable adjectives in *Giraffes are tall*).
-We argue that it also intersects with world knowledge in subtle ways, and it is critical to accurately measure and describe world knowledge before making claims about the implications of a generalization *per se*.
-
-Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
+To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
+
+As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite different from one another: generalizations about categories, events, and causes.
+<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
+We have been able to formalize a unified, core meaning using the underlying scale of *feature-probability*.
+We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
+Our framework naturally accounts for a number of classic examples from the semantics of *generic language* (Expt. 1).
+We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
+Finally, we have shown that listeners' prior knowledge about the feature-probability scale is causally related to their endorsement of statements of genericity (Expt. 3).
+In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below
+
+<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
+The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments.
+The formal Bayesian model provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (operationalized in terms of the prior).
+This formal separation is key improvement beyond previous accounts. 
+Previous accounts have either tried to account for context-sensitivity by baking it into the semantics [e.g., @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
+Our model formalizes both the semantics of generalizations and the structure of world knowledge; this separation allows us to articulate a route for precise quantitative inlfuence of conceptual structure on generic language [c.f., @Leslie2008].
+<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
+-->
 We do this without having to posit that conceptual structure and semantics are one in the same.
-This is important for applied Natural Language Processing research that seeks to draw inferences about particular entities from information conveyed in generalizations in text [e.g., @Herbelot2011].
-At the same time, this paves the way for articulating formal theories about conceptual structure and provides a route for precise, quantitative influence on generic language [c.f., @Leslie2008].
-
+This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
+<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->
+
+<!-- @Nickel2016 notes that genericity is particularly challenging to study because it intersects with many other phenomena in natural language (e.g., gradable adjectives in "Giraffes are tall"). -->
+<!-- We agree, and add to this that genericity intersects with *world knowledge* in subtle ways, and it is critical to accurately describe and measure world knowledge before making claims about the semantics of a generalization.
+-->
 <!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
@@
 
-In the rest of this discussion, we discuss some key features of the theory that warrant future investigation and the relationship of our theories to extant theories of genericity.
-We conclude by sketching out arguments for other known philosophical puzzles in genericity.
+In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
+<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->
 

### 2017-12-05 paper/comgen-paper.Rmd
edits to four sections of discussion

@@
 
-## The Comparison Class and the Question Under Discussion
-
-In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
-We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
-Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague language* [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012].
-We have shown similar sensitivity to the statistics of comparison class in the language of generalizations, thus incorporating generic, habitual, and causal language into the study of *vague language*.
-
-In this work, we made the *a priori* decision to construct the comparison class with respect to other kinds, people, or causes.
-In this way, the statement of genericity is addressing the implicit Question Under Discussions (QUDs): *who \textsc{does action}?*, *what causes \textsc{effect}?*, or *what \textsc{has feature}?*, respectively.
-In the minimal contexts employed in our experiments, this is a reasonable assumption.
-There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features. 
-This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?*
-
-Statements of genericity can be used to address either QUD, and this difference can even be observed in the same sentence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., *Lawyers (as opposed to doctors, firefighters, ...) care about the law.*; one can imagine this interpretation in a pedagogical context) or a feature-wise comparison class (i.e., *Lawyers care about the law (as opposed to justice, ethics, ...)* e.g., when said sardonically).
-We chose to focus in this work on the category-wise comparison class for methodological convenience. 
-In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features.
-*Feature-wise* comparison classes are likely to be modulated by the feature itself.
-Future work should address the feature-wise reading of generalizations, and explore what cues lead listeners to one or the other interpretation.
+## Implicit aspects of language use: The comparison class and question under discussion
+
+In this paper, we proposed a model for understanding generalizations in language that formalizes a simple semantic theory that interfaces with interlocutors' shared beliefs over the statistics of the event or property in question, represented by the prior belief distribution over the feature-probability.
+The feature-probability priors for a property, event, or cause are constructed by considering other possible categories having the property, people doing the action, or causes producing the effect.
+Collectively, these other kinds, people, or causes form classes against which the referent-category is evaluated.
+That is, the feature-probability prior $P(h)$ is constructed with respect a class of other entities or events, *the comparison class* $C$: $P_C(h)$.
+
+The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
+Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
+Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.
+
+The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. 
+Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object). 
+We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017].
+Even if interlocutors coordinate on a particular comparison class, they may disagree about the feature-probabilities of other *other categories* in the class.
+That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how *other forces* (e.g., plate tectonics) influence the climate or how often other social categories (e.g., neo-nazis) commit acts of terrorism.
+Indeed, we saw in Expt. 3 how the statistics of other causes can influence the endorsement of a single generalization (e.g., "Herb C makes animals sleepy").
+Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.
+
+Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud].
+We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the feature-probability.
+However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD.
+For example, the comparison classes used in our case studies were with respect to the target category (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUDs of "*what* has feature?", "*who* does action?", or "*what* causes effect?".
+Were the QUDs to be reversed (e.g., "what features does category have?", "what does person do?", "what effects does cause bring about?"), the comparison classes would need to be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
+
+The QUD is thus another layer of flexibility that makes understanding generalizations so challenging.
+The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus].
+The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
+In this work, we focused on category-wise comparison classes for methodological convenience. 
+<!-- In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features. -->
+<!-- *Feature-wise* comparison classes are likely to be modulated by the feature itself. -->
+Future work should investigate the feature-wise reading of generalizations, and explore what cues listeners adopt for one or the other interpretation.
+
+<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
+<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
+<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->
 
@@
 
-## Structured prior knowledge and implications for conceptual accounts
+## Structured conceptual prior knowledge
 
@@
 
-Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
-In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
-As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
-] 
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
-Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
+Previous psychological and philosophical work on generics has looked beyond feature-probabilities and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
+Prasada has argued for a distinction between \emph{characteristic} properties (e.g., "Diapers are absorbent") and \emph{statistical} properties (e.g., "Diapers are white").
+Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generic.
 Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
@@
 
-Our approach makes the strong claim that beliefs about predicted feature-probability is the connective tissue between conceptual knowledge and the semantics of generic language.
+Our approach makes the strong claim that beliefs about predicted feature-probability are the connective tissue between conceptual knowledge and the semantics of generic language.
 That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to different feature-probability priors. 
+Modulations of feature-probability distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
+We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different feature-probability priors, even while keeping the comparison class fixed. 
 In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
 
-It is natural to ask how subjective probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a way that reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
+It is natural to ask how feature-probabilities might reflect conceptual knowledge.
+We found that empirical feature-probability distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
 It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, it has been argued that conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately captured via their impact on subjective feature-probability.
-
-## Communicating Predictive Probabilities
-
-It is important to note that our approach is based on \emph{subjective} probability, and not mere frequency.
-Indeed, we elucidated in Expts.
-2c \& 2d that using participants' \emph{predictions} of probability in our formal model perfectly track generic endorsement, when the present frequency would make the wrong prediction.
+Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on feature-probability priors.
+
+## Communicating predictive probabilities
+
+This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
+In previous accounts, feature-probability is treated as synonymous with the prevalence or frequency of the feature in the category. 
+We make the important distinction that probability can be more general than frequency, and in our account, underlies speakers' subjective, predictions about the future and is subject to top-down moderator.
+Expts.
+2c \& 2d that showed using participants' \emph{predictions} about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
+
+Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probabilities [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the *language used* to convey *explicit probabilties* [cf., @Levinson1995].
+Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
+Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
+
+<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
+This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
+-->
+
+<!-- ### The Problems with Communicating Generalizations -->
+
+<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
+<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
+<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
+-->
+<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
+
+<!-- Generalizations can be made about almost anything. -->
+<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
+-->
+<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
+
+<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
+-->
+<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
+-->
+
+<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
+-->
+<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
+
+<!-- ### Statistical Accounts of Generics -->
+
+<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
+<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
+<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
+<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
+<!-- Let's first introduce some notation: -->
+
+<!-- ### Conceptual Accounts of Generics -->
+
+## Acquiring the language of generalizations
+
+The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
+Generic language is one of the earliest emerging forms of complex, compositional language.
+Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
+Generics are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
+
+What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
+If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
+The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development.
+In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
+This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
+
+We think rejecting the normal tools of truth-functional semantics for generics would be throwing out the baby with the bathwater.
+When we consider the acquisition problem, there are three aspects of meaning that a child must acquire for a truth-functional quantifier semantics $\denote{u}(h, \theta) = \{h :h > \theta\}$: 
+(1) the dimension being described (i.e., the probability $h$),
+(2) the polarity of the relation (i.e., $>$ vs. $<$), and 
+(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+Upon learning the meaning has to do with probability and that it stands in a positive relation to some standard $\theta$, a rational learner would adopt a prior distribution over possible thresholds $\theta$, as a form of *lexical uncertainty* [@Bergen2016].
+This prior could then be updated with more data to acquire a fixed meaning.
+However, for the generic statement, the language learner is done once she acquires aspects (1) and (2).
+In our model, $\theta$ is left underspecified in the semantics and is inferred in context.
+Thus, in this sketch of an acquisition model, a child would first acquire generic language, and from that, carve out more precise meanings for quantified language.
+
+The uniform prior over the threshold $\theta$ in the truth-functional threshold semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
+Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the feature-probability $h$ *itself*:
+$$
+\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
+$$
+
+This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better the utterance", or simply "more is better") is perhaps the simplest semantics one could imagine.
+<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
+The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
+We leave for future work the precise implementation of the acquisition model we sketch out here.
+<!-- This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1). -->
+## Other philosophical puzzles
+
+In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
+In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
+
+1. Books are paperbacks.
+2. Mary handles the mail from Antarctica.
+3. Supreme Court Justices have even social security numbers.
+4. Elephants live in Africa and Asia.
+5. Women are submissive.
+
+(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
+The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
+This is not an isolated example.
+The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
+These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
+We posit that the weirdness of these examples is the result of a failure of the comparison class.
+<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
+
+Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
+His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
+Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
+For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
+Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
+Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
+From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
+Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
+
+(2) is often used to argue that no actual instances need have the property to make a generalization true. 
+In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
+Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
+This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
+In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
+Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
+Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
 
@@
 
-This paper puts forth the theory that the simplest language of abstractions (i.e., the language of generalizations) communicates predictive probabilities from speaker to hearer. 
-This might seem contrary to a basic tenet in cognitive psychology, that human cognition falters when reasoning about probabilities [@Tversky1974].
-In a multitude of demonstrations, Kahneman and Tversky observed that human reasoners perform poorly when reasoning about explicit probabilities.
-This has been taken to imply that people are bad with probabilties.
-
-We suggest that problems with communicating probabilities are a problem of the language used to convey *explicit* probabilties [cf., @Levinson1995]. 
-A host of developmental evidence suggests that even the youngest learners are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-In this work, we have argued that probabilities are central to even the most basic linguistic expressions.
-We convey probabilities to each other using language, but the most basic ways we have of conveying them are *vague*.
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between 2 and 3 years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are ubiqiutous in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., *Birds lay eggs* vs. *Birds are female*) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think this would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are two aspects of meaning that a language learner must acquire for the semantics of a quantified utterance (e.g., "some", "most"): (1) that the meaning is a threshold-function (i.e., $\denote{u}(h, \theta) = \{h :h > \theta\}$) and (2) the fixed value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning function is a threshold-function (1), a Bayesian language learner would be well-suited to adopt a prior distribution over possible thresholds $\theta$.
-This prior could then be updated with more data to acquire its fixed meaning.
-For the generic statement, the language learner is done once she acquires (1). 
-The rest of the meaning is inferred in context.
-With that lens, generic meaning would be primary, while quantified utterances would be refinements.
-
-There is an alternative reason why our uncertain threshold model makes the acquisition problem easier than quantifiers.
-A uniform prior over the threshold in the truth-functional threshold semantics (as we have assumed in this work) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the probability degree $h$ *itself*: ^[It is equivalent to the probability degree $h$ normalized by the prior distribution over the degree (i.e., the comparison class)]
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-
-This *soft semantics* (corresponding intuitively to something like "the higher the probability, the better the utterance", or just "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1).
-
-## Relationship to Other Theories
+(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
+This example was first introduced, to our knowledge, by @Nickel2008.
+]
+@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
+This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
+In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+
+<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
+-->
+<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
+<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
+
+With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
+1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
+When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
+This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
+Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
+A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
+
+Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
+That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
+In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
+If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
+Note that this can naturally capture the central phenoman described in @Cimpian2010.
+].
+The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
+However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
+This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
+If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
+We find this possibility intruiging for future work.
+
+In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
+The precise implementation of these hypotheses we leave for future work.
+
+<!-- -- Books are paperbacks. (failure of the constrast class) -->
+<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
+<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
+<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
+<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
+<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
+<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
+
+## Relationship to other theories
 
@@
 
-### Statistical Accounts
+### Statistical accounts
 
@@
 
-### Conceptual Accounts
+### Conceptual accounts
 
@@
 
-## Other philosophical puzzles
-
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Elephants live in Africa and Asia.
-4. Women are submissive.
-
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
-]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
 # Conclusion

### 2017-12-07 paper/case3-causals.Rmd
new stab at talking about causals

@@
 
-Learning to that an event consistently tends to result in another event is a critical kind of generalization for understanding how the world works. 
-Adults and children can infer causal relationships from just a few examples [@Gopnik2000; @Schulz2004] and computational models have been used to formalize the problem of *elemental causal induction*, or learning a causal relationship from observational data [@Griffiths2005; @Kemp2010a].
-Having induced a causal relationship from observational data, people can communicate their causal knowledge using language. 
-Indeed, when causal relations are nonobvious, causal language helps children as young as 2-years learn those relations [@Bonawitz2010].
+What is the meaning of the utterance: "Drinking moonshine makes you go blind"?
+A first pass could be *there exists a causal relationship between blindness and moonshine such that blindness causes moonshine*.
+Interestingly, this definition doesn't mention the increased risk in becoming blind from moonshine, but presumably it's more probable than the alternative (not drinking moonshine).
+We hypothesize that the semantics of the above statement (a *causal* statement) is underspecified and subject to the same context-sensitivity as generic and habitual language.
 
-<!-- Such *token causation*  -->
-<!-- serves as a foundation for an intuitive theory of causality [@Goodman2011; @Kemp2010a]. -->
-<!-- Recognizing an event as *causal* is a challenging problem [e.g., @Gerstenberg2015how]. -->
-<!-- Inducing a generalization  -->
-<!-- Communicating generalizations about causally related events is highly valuable because  -->
-<!-- relevant data can be prohibitively expensive and no one individual can run all the experiments that she wants to run in a life time.  -->
-<!-- The history of civilizations has shown that it is incredibly useful to divide labor: Some members can investigate modifications to the food preparation procedures while others can examine different ways of cutting stone.
--->
-<!-- Our framework for communicating generalizations makes predictions about statements conveying genericity about a category of causal events.  -->
-<!-- In this domain, an instance of the category is a single causal event, or *token causality* (e.g., adding a particular amount of a particular kind of yeast to an actual piece of dough).  -->
-<!-- <!-- [Gerstenberg] -->
-<!-- Inducing the existence of an abstract cause from observational evidence also depends in complex ways on an observer's background theory of causality [e.g., @Griffiths2005; @Schulz2008a]. -->
-<!-- Language provides a way to bypass the observational data needed to make a causal induction. -->
+We take language that conveys a causal relationship between two classes of things as our third case study: causal language, or *causals*.
+For simplicity, we identify the relevant dimension of the scale to be the conditional probability of the effect given the cause, though this representation will have problems for classic cases in causal reasoning.
+Our goal is not to explain the phenomena of causal reasoning *per se*, but rather to adopt a semantics that could apply to the causal domain and test our theory on the language of causal relations.
+In particular, we aim to demonstrate empirically that our theory of the language of generalization posits constructs that are causally related to sentence endorsement.
 
@@
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
+
+The problem of *causal induction*---knowing that one thing causes another----has been studied extensively in human psychology  [@Cheng1992; @Cheng1997; @Griffiths2005; @Griffiths2009].
+Classically, this is cast as a problem of inducing an unobservable relation from observable data. 
+For example, assuming a controlled experiment: observing E whenever C is present, and the absence of E whenever C is absent, is strong evidence for concluding that C causes E.
+At the same time, individual events (e.g., observing $c_i$ and $e_i$) can be construed as *causal*, depending on whether $c_i$ is seen as a difference-maker for $e_i$ and how exactly $c_i$ made that difference [@Gerstenberg2015how].
+Going from covariation to causation, then, implies that during the events observed (the covariation), causal attribution was withheld: The events were not seen as causal at the time, only in retrospect.
+Alternatively, we may conclude there is no cause after first seeing events in-the-moment as causal.
+
+<!-- If we see individual events as causal (*token level* causation), then we may reach a point when we organize those events as instances of a category-level causal relation (*type level* causation).
+-->
+<!-- How do we tell others about what we learned? -->
+<!-- We use language of the form "C causes E". -->
+
+<!-- Recently, causal attribution of a single event (*token causation*) -->
+<!-- Adults and children can infer causal relationships from just a few examples [@Gopnik2000; @Schulz2004] and computational models have been used to formalize the problem of *elemental causal induction*, or learning a causal relationship from observational data [@Griffiths2005; @Kemp2010a].
+-->
+<!-- Having induced a causal relationship from observational data, people communicate their causal knowledge using language.  -->
+<!-- Indeed, when causal relations are nonobvious, causal language helps children as young as 2-years learn those relations [@Bonawitz2010]. -->
 

### 2017-12-07 paper/comgen-paper.Rmd
new stab at talking about causals

@@
 Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in understanding language.
+The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
 

### 2017-12-07 paper/case2-habituals.Rmd
old changes intro to habituals

@@
 -->
+
+Segmenting the continuous stream of reality into events is a crucial task for cognition.
+We consider events as individuated entities as instances of a category. 
+For example, the event *Mary smoked a cigarette yesterday at 2:30pm*...
+
+Learning that an agent tends to exhibit a behavior is a special case of learning a generalization about an event. 
+The event, *the agent doing the action*,
 
@@
                                ticks = F))
+```
+```{r habituals-items-table}
+d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()
+
+d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
+  kable(.) %>% #, format = "latex", longtable = T, booktabs = T, caption = "a caption") %>% 
+  #column_spec(3, width = "10cm")%>%
+  collapse_rows(columns = 1:2)
 ```

### 2017-12-07 paper/comgen-paper.Rmd
edits to other philosophical puzzles section

@@
 Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the feature-probability $h$ *itself*:
+
 $$
@@
 $$
-
 This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better the utterance", or simply "more is better") is perhaps the simplest semantics one could imagine.
-<!-- Given this mathematical equivalence, we can imagine the *more is better* soft semantics is what is acquired early. -->
 The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
 We leave for future work the precise implementation of the acquisition model we sketch out here.
-<!-- This special case involves learning the value of the threshold (aspect 2) and not in recognizing that the utterance conveys something about the quantity (e.g., aspect 1). -->
 ## Other philosophical puzzles
 
-In our experiments, we have tried to include major known philosophically puzzling examples of generalizations in language. 
-In this section, we consider other previously-discussed troubling examples of generic statements and sketch out arguments rooted in the theoretical framework presented in this paper.
+In our experiments, we have tried to include classic, philosophically puzzling examples of generalizations in language in addition to crafting novel stimuli that provide stricter tests of the main hypothesis.
+In this section, we consider some other previously-discussed troubling examples of generalizations and sketch out arguments rooted in our theoretical framework to demonstrate how our theory could account for these cases.
+We consider the five following examples:
 
@@
 
-(1) is often used to demonstrate that the feature-probability is not sufficient for a generic to be true.
-The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
-This is not an isolated example.
-The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
-These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
-We posit that the weirdness of these examples is the result of a failure of the comparison class.
-<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->
-
-Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
-His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
-Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
-Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
-Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
-From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true probability of the feature among the referent-category must be the mean of the probabilities of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
-Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Robins are female".
-
-(2) is often used to argue that no actual instances need have the property to make a generalization true. 
-In this thought experiment, part (perhaps all) of Mary's job is to handle the mail from Antarctica; to date, however, there has not been any mail from Antarctica [@Cohen1999]. 
-Thus, it is not the case that Mary *has handled* any mail from Antarctica before.
-This example is an extreme case of the phenomenon highlighted by Expts. 2c \& 2d.
-In this pair of experiments, we manipulated predictive probability, while keeping fixed past frequency, and saw the endorsements of habitual statements indeed tracked predictive probability (with the linking function being the RSA speaker model).
-Our general cognitive modeling framework takes the fundamental currency of a generalization in language to be a subjective predictive probability. 
-Past frequency and actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different.
-
-The focus on subjective, predictive probability casts new light on classic puzzles surrounding accidentally-true situations.
-Consider a thought experiment from the linguistics and philosophical literature: Imagine that currently every Supreme Court Justice's social security number is an even number. 
-Linguists predict the statement "Supreme Court Justices have even social security numbers" would still be considered false [@Cohen1999].
-Our explanation of this phenomenon is that abstract intuitive theories lead us to reject observed frequencies in forming our subjective probabilities.
-That is, because we may believe selection for the Supreme Court is not influenced by one's social security number, we would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Thus, given that the all professions would have roughly the same probability of having employees with even social security numbers, the statement \emph{Supreme Court Justices have even social security numbers} would be similar to *Birds are female*.
-Thus, our model would not endorse the statement \emph{Supreme Court Justices have even social security numbers}, because the predictive feature-probability would not be any different for Supreme Court Justices than any other profession.
-This perspective makes the intriguing prediction that if we learned much more surprising information, we might be compelled to revise our theory of the domain, update our subjective probability of future instances, and then accept the generic.
-For instance, if every justice in history had \emph{prime numbered} social security numbers (a more suspicious coincidence), one might appeal to a conspiracy, which \emph{would} have predictive consequences.
-
-(3) shows a subtle interaction of generic language with another linguistic device: conjunction. ^[
-This example was first introduced, to our knowledge, by @Nickel2008.
+Sentence (1), strikes hearers as *odd* or perhaps *false*, despite the vast majority of books being paperback. 
+Why?
+A first observation is that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset ("paperbacks" is short-hand for "paperback books"). 
+We expect intuitions about this statement to generalize to other examples expressing an analogous relation (e.g., "Pastas are spaghetti", "Animals are humans").
+We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent feature-probabilty.
+Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers].^[
+  Note that this assumption is consistent with the comparison classes we have assumed in our three case studies.
 ]
-@Nickel2008 suggests this statement is semantically equivalent to: *Elephants live in Africa and elephants live in Asia*.
-This example is challenging for many statistical based approaches, since it cannot be the case that most elephants live in Africa and most elephants live in Asia.
-In addition, we should not take the statement to imply that there are international elephants (i.e., individual elephants who live in Africa part time and Asia part time); but that is the only possible interpretation if the generic statement is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+Then, "is a paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
+  Note that this idea is similar to @Cohen1999's notion of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his   Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
+]
+The relevant aggregations of entities, then, are collection of books, potentially including books of different genres or publication eras among other such sub-categories.
+Then, given that "books" is the superordinate category of "kinds of books", the referent-category feature-probability cannot be different from the mean of the feature-probability prior.
+Finally, given this feature-probability prior and the referent-category feature-probability, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in the a way analogous to "Robins are female".
+
+```{r booksArePaperbacks, fig.cap="Sketch of an argument for why 'Books are paperbacks' sounds odd.
+The feature 'is paperback' can only be predicated (in the sense of @Keil1979) of individual books, which are organized into collections (here, by genre).
+The feature-probability prior is constructed by aggregating these collections of books.
+Then the feature-probability of 'is paperbook' for the category of 'books' can never be higher than the mean of the prior distribution.
+The endorsement model would give this sentence a rating of 0.5, corresponding to neither true nor false."}
+knitr::include_graphics("figs/books-paperbacks.pdf", dpi = 108)
+```
+
+Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
+That is, the statement "Mary has handled mail from Antarctica" is false.
+Sentence (2) is still thought to be true despite zero actual instances of the event.
+We think (2) is a boundary case of generalizations expressing predictive probabilities, which we elucidated in Expt. 2c.
+In in that study, we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
+We expect the same to be true here, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
+Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
+
+Our focus on predictive probability makes even new prediction about some classic puzzles.
+Sentence (3) is the conceptual opposite of sentence (2).
+Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
+Sentence (3) is still considered false, every though the property holds in 100\% of the category [@Cohen1999].
+We predict this phenomenon is the result of abstract, intuitive theories guiding us to reject observed frequencies in forming our subjective probabilities.
+That is, because observers strongly believe selection for the Supreme Court is not influenced by one's social security number, speakers would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
+Then, given that the all professions would have roughly the same probability of having employees with even social security numbers, Sentence (3) is again similar to "Birds are female". 
+However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
+history had a social security number which was a *prime number*---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
+That is, we predict there are situations where statements like (3) could be considered felicitious generalizations.
+
+Understanding how a semantic representation *composes* is another critical test for a theory of generalizations in language.
+@Nickel2008 suggests Sentence (4) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
+Stastistical account of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
+However, this is the only interpretation if the generalization is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+Our theory does not provide a fixed semantics for the generalizations, but an uncertain one, which can be updated as more information comes in.
+In fact, with a strong constraint against the existence of *international elephants* but with any further semantic assumptions, our model infers that some elephants live in Africa and other lives in Asia.^[
+  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
+]
+Importantly, the model believes that most lives in Africa, when it only hears that "Elephants live in Africa", and only later revises it's beliefs to a weaker "some"-like interpretation after hearing they live in Asia as well.
+Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise interpretation of single utterances.
 
@@
 
-With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
+<!-- With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
 1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
-When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement, inferring that some live in Africa and other lives in Asia. 
-This is possible because our model has uncertainty over the semantic thresholds in the generic claim.
-Our model can flexibly accomodate new evidence (e.g., learning that elephants live in Asia) that might otherwise contradict previous statements (e.g., knowing that elephants live in Africa).
-A runnable version of the model for this example can be found at [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-
-Finally, (4) is used to argue that even if the property is widespread (or perhaps in a softer sense, as in our model, widespread relative to other kinds or groups), speakers might find it avervise to actually assert the generic.
-That is, even if it were the case that, because of a variety of socio-cultural reasons, women tend to be submissive (more so than men, and many other social categories), we might still not want to assert *Women are submissive* [@Haslanger2011].
-In our Model Simulations section, we showed that the generic often can imply the property is widespread, even with uninformed prior beliefs about the property. 
+-->
+<!-- When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement,  -->
+<!-- This is possible because our model has uncertainty over the semantic thresholds in the generic claim. -->
+
+Finally, sometimes a property is widespread relative to other kinds or groups, and it might be so systemic that we would believe it to be the case in the future, but speakers still might find it avertise to actually endorse the generalization.
+Such is the situation with Sentence (5) [@Haslanger2011]. 
+Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
+In our **Model Simulations** section, we showed that the genearlization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
 If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-Note that this can naturally capture the central phenoman described in @Cimpian2010.
+  Note that this can straight-forwardly capture the central phenomena of @Cimpian2010.
 ].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated from the generic statement).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective utilities, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to the RSA framework has already accounted for a variety of behaviors corresponding to polite speech understanding and production [@Yoon2016; @Yoon2017].
-If our speaker model believed that states of the world where the probability of the feature is high (e.g., a world where many women were submissive) were undesirable (either in absolute terms or as a belief), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such generic claims.
-We find this possibility intruiging for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to formalize a number of interesting and heretofore puzzling avenues in genericity.
+The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated in the mind of the listener).
+However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective values, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
+This kind of extension to rational models of communication has already been used to account for a variety of phenomena in *polite language* use [@Yoon2016; @Yoon2017].
+We propose adopting such a value-based utility structure for states of the world for language about social categories: If the speaker found states of the world where the probability of the feature is high (e.g., a world where many women were submissive) as undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
+We find this possibilitity intruiging and leave it for future work.
+
+In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
 The precise implementation of these hypotheses we leave for future work.

### 2017-12-08 paper/comgen-paper.Rmd
edit relation to statistical theories

@@
 
-To our knowledge, this is the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
+To our knowledge, the present papaer presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
 A number of other theories of genericity have been proposed in the linguistics and psychological literatures.
-By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
-
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., there is something about being K which causes it to F).
+We now turn to situating our account with respect to these previous theories.
+<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
+-->
+Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., *there is something about being K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
@@
 
-Statistical accounts take the feature-probability to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}. 
-Our probabilistic account has antecedents in @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Similar to our formulation, Cohen looks to feature-probability as a metric against which generics get evaluated.
-For Cohen, there are two kinds of generic statements: "Absolute" and "Relative".
-"Absolute generics" have a meaning with a fixed threshold on feature-probability and that threshold is taken to be 0.5: $P(F\mid K)>0.5$. 
+#### Relative and absolute generics
+
+Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
+For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means.
+He partitions generics into two types: *absolute* and *relative* generics.
+*Absolute generics* use a fixed, 50\% threshold on feature-probability: $P(F\mid K)>0.5$. 
 Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-"Relative generics" on the other hand depend upon an alternative set of kinds (his notation: $Alt(K)$), similar to our comparison class.
-These statements (e.g., *Mosquitos carry malaria*) are true if an arbitrary member of the target kind is more likely than an arbitrary member of an alternative kind to have the feature.
-
-There are two main points of deviation of our theory from Cohen's.
-First, though his theory is framed in terms of probabilities, it still relies upon a fixed threshold and only makes predictions about what is "true" or "false".
-Our theory posits that the meaning (i.e., threshold) is underspecified in the semantics and is inferred in context. 
-It is a probabilistic model and makes predictions about what is strongly endorsed, what is strongly rejected, and all of the shades in between.
-Second, Cohen draws the distinction between "Absolute" and "Relative" generics, providing different mechanisms to explain each; our underspecified threshold is able to handle both kinds of examples with the same basic machinery.
-
-It should be noted that another mechanism used in Cohen's theory is to contextually restrict the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-These entities are restricted to those that *could have some feature* in a (contextually-specified) alternative set of features (so called, $Alt(F)$). 
-For example, the property \emph{lays eggs} could induce a set of alternatives that all have to do with procreation (e.g., \emph{gives birth to live young}, \emph{undergoes mitosis}, ...).
-That is, *Robins lay eggs* can be evaluated as an "absolute generic" because the only individuals under consideration are the female members of kinds as only the female members can plausibly satisfy one or another of the alternatives having to do with procreation (i.e., the features in $Alt(F)$).
+*Relative generics* depend upon an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
+"Mosquitos carry malaria" is a relative generic: it is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
+
+Our uncertain-threshold model deviates from Cohen's account in two primary ways.
+First, though his theory is framed in terms of probabilities, it still utilities a fixed threshold semantics and thus is only able to make predictions about what is "true" and what is "false".
+In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement.
+Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each.
+We used examples of both in our stimuli (Expt.
+1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".^[
+  For a related theory that aims to do away with the distinction between "absolute" and "relative"   adjectives, see @Lassiter2015.
+]
+
+We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
+His theory posits that feature-probability is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$). 
+For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
+Therefore, "Robins lay eggs" is evaluated as an *absolute generic* because only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+The inferential machinery behind Cohen's domain restriction (i.e., what comrpises $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.
+]
+However, we note that this mechanism may be implicit in our own theory: the prior distribution over the feature-probability of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
+
 <!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-The inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].
-^[However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.]
-Because the mechanisms behind domain restriction plausibly require yet another pragmatic inference relying heavily on world knowledge, the theory we present here doesn't explicitly rely upon domain restriction.
-However, it's an open question whether there exists a reformulation of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-In the computational linguistics literature, a similar proposal about underspecification of generics has been made [@Herbelot2011].
-In their model, generics express a quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic. 
-Though similar in spirit, our theory does not posit that quantified relations corresponding to the words "Some", "Most", or "All" are in any way primitive; rather, we use a continuous distribution over possible thresholds to represent the inherenent vagueness in quantificational meaning in generics.
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to habitual language, where quantified relations like "Most" or "All" are not directly applicable.
-
-Our theory bears some conceptual similarity to a recent proposal in philosophy by @Sterken2015. 
-Sterken treats the generic as a kind of *indexical* (e.g., "this" or "I").
-She argues that kind of truth-conditional variability exhibited by generics is best accounted for by generics as indexicals where both domain restriction (described above) and "quantificational force" vary with context.
-We think our uncertain threshold model is a way of formalizing Sterken's "quantificational force", though we remain agnostic as to relationship between generics and indexicals. 
-As noted above, we have not yet formalized uncertainty about domain restriction but think this is a promising avenue for future research.
-
-Other theorists under the quantificational or statistical banner draw on the intuition that generics seem to express something about what is *normal* in the world [@Asher1995; @Pelletier1997; @Nickel2008].
-For example, it is a regrettable but true fact that due to unfortunate circumstances, not all dogs have four legs.
-However, we might want to hold onto the idea that were the world to work *normally*, then *all* dogs would have four legs. 
-This idea has intuitive appeal for rejecting accidentally true generalizations (e.g., *Supreme Court justices have even social security numbers*; described above).
-It also may underly what is problematic about stereotyped language (e.g., *Boys are good at math*).
-Though we do not directly address "what is normal" with our theory, we argue that a speaker's beliefs about what is *probable* (which may relate to what is *normal*) plays a role in endorsing and interpreting generalizations.
-<!-- is central to the formulation of our theory of generics in a Bayesian cognitive model. -->
-Indeed, we have shown in Expt.
-3 that speaker's beliefs about what is likely to be the case in the near future matters for endorsing generalizations above and beyond what is currently true in the world.
-Feature-probability in our theory is a predictive probability, which incorporates background knowledge in order to make predictions about the future. 
-The intersection of what is "normal" and an agent's predictive probability is another target for future research [though see @Icard2017 for some recent progress].
+
+#### "Normal" accounts
+
+The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008].
+For example, "Dogs have four legs" is a good generalization event though, regrettably, not all dogs have four legs.
+However, were the world to function *normally*, then *all* dogs would have four legs (i.e., dogs would not be involved in freak-tractor accidents).
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and tereotyped language (e.g., "Boys are good at math").
+Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
+We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations.
+Our notion of feature-probability is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
+
+#### Underquantification
+
+A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
+In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
+The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analagous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
+This distinction is relevant for the acquisition of the language of generalizations; we do not think that quantified relations (e.g., "Some", "All") are in any way primary or special. 
+<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
+-->
+Additionally, by using a vague, underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
+
+#### Generic as indexical
+
+@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
+The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
+Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" [and a generalization of *underquantification*, see above], and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
+We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
 
@@
 Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich relationships between kinds and properties.
-Examples like *Lions roar.*  and *Bishops move diagonally.* seem to express something beyond a statistical relationship.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion; 
-if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-\emph{Bishops move diagonally} because those are the rules of the game, not because they \emph{tend to} move diagonally.
-
-Perhaps the most influential conceptual account of generics is credited to @Leslie2007.
+This perspective draws intuition from the fact that generics can express rich, conceptual relationships between kinds and properties.
+That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
+If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar".
+
+The most influential conceptual account of generics is from @Leslie2007.
 For Leslie, generics are tied to the cognitive system's "default mode of generalization".

### 2017-12-13 paper/case3-causals.Rmd
fix causal stims table formatting

@@
 # Case Study 3: Causal Language
+
+<!-- delta_p = presence-absence -->
+<!-- cp = delta_p / normalization ... subset of relevant cases -->
+<!-- caus_supp ~ structure induction problem. -->
+<!--   - get to delta_p & cp assuming a different integration fn's -->
+
+<!-- caus_support = "" -->
+<!-- caus_strength = "This virus causes the disease." -->
 
@@
 \resizebox{\textwidth}{!}{
-\begin{tabular}{lll}
-                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\
+\begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|}
+\hline
+                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline
 Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
@@
 Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-\\
+\\ \hline
 Evidence statement & Your team gave fertilizer B to 100 different feps.
@@
 Of those 100 treated, 98 cheebas were made sleepy.
+\\   \hline
 \end{tabular}

### 2017-12-14 paper/comgen-paper.Rmd
finish going through discussion

@@
 ---
-title             : "The language of generalization"
+title             : "The language of generalization: Probability, vagueness, and interaction"
 shorttitle        : "The language of generalization"
@@
     To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains almost all of the variance in human endorsements of language conveying generalization, while simpler models fall short.
+    Across these diverse domains, we find that our model explains the wide variance in human endorsements of language conveying generalization, while simpler models fall short.
     Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
@@
 ```
-
 ```{r simluationEndorsementModel, eval = T, cache = T}
@@
 
-## Implicit aspects of language use: The comparison class and question under discussion
-
-In this paper, we proposed a model for understanding generalizations in language that formalizes a simple semantic theory that interfaces with interlocutors' shared beliefs over the statistics of the event or property in question, represented by the prior belief distribution over the feature-probability.
-The feature-probability priors for a property, event, or cause are constructed by considering other possible categories having the property, people doing the action, or causes producing the effect.
-Collectively, these other kinds, people, or causes form classes against which the referent-category is evaluated.
-That is, the feature-probability prior $P(h)$ is constructed with respect a class of other entities or events, *the comparison class* $C$: $P_C(h)$.
+## A step towards communicating generalizations
+<!-- Implicit aspects of language use: The comparison class and question under discussion -->
+
+In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
+Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
+Our endorsement model, which we use to generate predictions for our three case studies, can be seen as a special case of a speaker model who can only produce one of two utterances: the generalization or silence.
+Our interpreter model can be seen as a kind of "literal listener", who does not do any sort of pragmatic or communicative reasoning. 
+Our modeling framework could thus naturally be extended to more faithful models of pragamtic communication of generalizations, to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task.
+The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.
+
+### The comparison class
+
+Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the feature-probabilities $P(h)$.
+The feature-probability priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
+Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
+Thus, the feature-probability prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.
 
@@
 
+### Question under discussion
+
 Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud].
@@
 
-## Structured conceptual prior knowledge
+## Structured prior knowledge
 
@@
 We leave for future work the precise implementation of the acquisition model we sketch out here.
+
 ## Other philosophical puzzles
@@
 The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
-Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" [and a generalization of *underquantification*, see above], and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
+Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
 We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
@@
 Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-This perspective draws intuition from the fact that generics can express rich, conceptual relationships between kinds and properties.
+These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties.
 That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
@@
 The most influential conceptual account of generics is from @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization".
-The intuition comes from the fact that infants seem ready to make strong generalizations from small amounts of data [e.g., @Baldwin1993].
-This "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, \emph{Mosquitos carry malaria} is true because carrying malaria will kill you, which is a striking and a useful bit of information to convey.
-
-This theory thus predicted that generics that convey striking properties would be endorsed even when they are relatively rare (e.g., *Sharks attack swimmers*).
-This prediction was borne out experimentally when participants are supplied information about the dangerousness of a feature, even when the actual feature-probability is quite low [e.g., "30\% of lorches have purple feathers that are as sharp as needles and can easily get lodged in you, causing massive bleeding."; @Cimpian2010].
-In pilot work, using paradigms similar to the manipulation check paradigm employed in the causal language experiments (Expt.
-4a) and the structured elictation used in habituals (Expt.
-2a), we have observed that the prior distribution over the probability of the feature $P(h)$ also changes when supplied information about the dangerousness of the feature.
+For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
+Leslie's "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
+Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about.
+
+This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-category feature-probability; e.g., "Sharks attack swimmers").
+Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the feature-probability is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
+1 for naturalistic cases).
+In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
+3a), we have observed that the prior distribution over the feature-probabilities $P(h)$ change when supplied information about the dangerousness of the feature.
 That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability prior rather than something special about dangerous features per se.
-However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
-
-Of course, not all generics convey striking or appalling information (e.g., *Birds lay eggs*).
-Leslie's default mode can also distinguish "negative counter-instances" of a property  (e.g., a bird that doesn't lay eggs, like male birds) from "positive counter-instances" (e.g., a hypothetical bird that bears live young).
-Generics are much less reasonable when positive counter-instances exist.
-Hence, \emph{Birds are female} seems weird because "being male" is a positive counter-instance of "being female", but since there are no birds that bear live young,  \emph{Birds lay eggs} is fine.
-
-@Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts.
-Striking generics (e.g. \emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
-Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}).
-The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations.
-Statistical information takes a backseat to the conceptual structure.
-
-Generics can arbitrary relationships too: *Barns are red* because most barns are red.
-If farmers around the world decided to paint their barns green, they would be no less barns, but barns would be green.
-*Ravens are bigger than toasters* is a true statement, but doesn't tell us anything principled or causal about ravens.
-These sorts of conceptual accounts must always accomodate completely arbirtary, statistical relations.
-
-In the last fifteen years, there has been tremendous progress in formalizing rich, structural knowledge and the inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduce a probabilistic model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
+Thus, our model would also predict these effects, but by way of the feature-probability priors rather than some direct connection between generics and striking features.
+<!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
+-->
+
+Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs").
+Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young)
+The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist. 
+For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
+In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
+Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely feature-probabilities within- and across- categories or features.
+
+Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world. 
+"Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters.
+"Barns are red" because most barns are red.
+If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green".
+Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.
+
+Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations.
+In the last fifteen years, there has been tremendous progress in formalizing 
+Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011]. 
+For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
 @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.
-In this paper, we take a minimalist approach in modeling conceptual structure in our prior on feature-probabilities $P(h)$, and incorporate only what is necessary in our model of world knowledge. 
-In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories.
-This minimally structured model reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites). 
+
+In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on feature-probabilities $P(h)$.
+In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).  
 It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-
-The key point divergence between their and our view concerns the core meaning of a generic statement.
-For us, the semantics concerns a probability, which could be the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-This provides a more unifying view of generics, since the basic currency of generic meaning is a single metric: probability.
+<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories. -->
+<!-- This minimally structured model  -->
+
+The key point of divergence then between the conceptual accounts and our view concerns the core, semantic meaning of a generic statement.
+Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
+For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
+We believe this provides a more unifying view of generics, giving a single metric as the basic currency of generic meaning: probability.
+
+<!-- @Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts. -->
+<!-- Striking generics (e.g.
+\emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
+-->
+<!-- Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}). -->
+<!-- The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations. -->
+<!-- Statistical information takes a backseat to the conceptual structure. -->
 
@@
 Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve the uncertainty [@Piantadosi2012].
-In our work, context takes the form of a listener and speaker's shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations,
-which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generic utterance that he himself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category---we showed that biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which in framework could be differences in the referent feature-probability, the prior distributions on feature-probabilities, or the comparison class.
-<!-- It's an open question whether or not politically charged statements (e.g., "Black lives matter") can be understood by divergent beliefs about the these constituent factors.  -->
-For example, there is considerable disagreement as to whether or not "Humans cause global warming".
-Our theory predicts this disagreement may be the result of differences in the estimated \emph{causal power} of humans influencing global warming as well as the causal power of \emph{other forces} (e.g., plate tectonics) on climate change.
+To the contrary, underspecification can be efficient, given that context can be used to resolve  uncertainty in meaning [@Piantadosi2012].
+In our work, context takes the form of shared beliefs about the property in question. 
+By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
+
+The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
+Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
+Disagreements are also predicted when interlocutors fail to share background assumptions, which could be differences in the prior distributions on feature-probabilities or the comparison class.
+Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).
 This is a promising area for future research.
@@
 Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
+<!-- The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
+-->
+The theory presented here provides the first computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
 

### 2017-12-16 paper/case1-generics.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

@@
 
-\begin{figure}
-\centering
-    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
-    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
+```{r generics-prior-task, fig.cap:"Test"}
+fig.priors.expt <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-bothStages.pdf", sep=""), scale = 1)
+fig.priors.expt
+```
+
+<!-- \begin{figure} -->
+<!-- \centering -->
+<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf} -->
+<!--     \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
 Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
-    \label{fig:generics-prior-task}
-\end{figure}
+Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.} -->
+<!--     \label{fig:generics-prior-task} -->
+<!-- \end{figure} -->
 
@@
 
-The fixed-threshold model is a lesioned version of the unceratin-threshold model: It has access to the full prior distribution on feature-probabilities $P(h)$ and models endorsement as an information-theoretic decision of producing the generic vs.
-an alternative.
+The fixed-threshold model is a lesioned version of the unceratin-threshold model: It models endorsement as an information-theoretic decision of producing the generic vs.
+an alternative, and has access to the full prior distribution on feature-probabilities $P(h)$.
 The only difference is that this model uses a fixed-threshold as the core meaning of a generic statement, rather than an uncertain threshold.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
+For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).
+
+^[
   Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further   specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
@@
 model_prefix <- "results-generics-jointModel-S1-smntcs_"
-
+#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-"
 # m.samp <- data.frame()
 # m.samp.fixed <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+#for (i in seq(1, n_chains)){
+  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
   #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-#   
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
+  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+
+#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
 #                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
@@
 
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThreshold-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
+
+# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
+# 
+# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
+# 
+# tail(m.samp.fixed)
+
+fixed.params.posterior <-  m.samp.fixed %>% 
+  filter(param %in% c("noise", "fixedThreshold")) %>%
+  group_by(param) %>% 
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
 
 m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement') %>%
+  filter(type == 'endorsement', param == "some") %>%
   group_by(type, param, property, category) %>%
@@
 
-#model_prefix <- "results-generics-jointModel-10bins-S1-smntcs_"
-
-#m.samp <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                     #20000, "_burn", 10000, "_lag", 20, "_chain", 2, ".csv", sep = ""))
-#m.samp <- fread("~/Documents/research/communicating-generalizations/models/generics/results/results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-100000_burn100000_chain1.csv")
+# m.gen.fullmodel.endorsement <- m.samp.samp %>%
+#   rename(type = Parameter, property = Property, category = Category, val = Value, param = Extra) %>%
+#   group_by(type, property, category, param) %>%
+#   summarize(MAP = estimate_mode(val),
+#             cred_upper = hdi_upper(val),
+#             cred_lower = hdi_lower(val))
 
 m.gen.fullmodel.endorsement <- m.samp %>%
- # filter(type == 'endorsement', param == 'generic') %>%
-  #filter(type == 'predictive', param == 'generic') %>%
-  filter(type == 'endorsement') %>%
+ filter(type == 'endorsement', param == 'generic') %>%
+  # filter(type == 'predictive', param == 'generic') %>%
+ # filter(type == 'endorsement') %>%
   group_by(type, param, property, category) %>%
@@
             cred_lower = hdi_lower(val))
-
+```
+
+```{r generic-model-scatters}
 m.gen.endorse.rsa <- bind_rows(

### 2017-12-16 paper/case2-habituals.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

@@
 
-# for (i in seq(1, n_chains)){
+for (i in seq(1, n_chains)){
   # mi <- fread(paste(project.path,  "models/habituals/results/",
@@
   # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
+
   # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
@@
   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
+  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
+  #                         "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
   # 
-# }
-# 
+  #m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
+}
+
 # save(m.hab.samp,
@@
 
+# save(m.hab.fixed.samp,
+#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+
 load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
@@
 
-load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+load(paste(project.path,  
+           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+
+# m.hab.fixed.samp <- fread(paste(project.path,  "models/habituals/results/",
+#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
+
+fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
+  filter(B %in% c("noise", "fixedThreshold")) %>%
+  group_by(B) %>% 
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
 
@@
                       labels = c(
-                                 "Speaker model - fixed semantics",
-                                 "Speaker model - uncertain semantics",
+                                 "Fixed semantics model",
+                                 "Uncertain semantics model",
                                  "Referent frequency alone", "Distinctiveness + referent frequency"

### 2017-12-16 paper/case3-causals.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

@@
 
-What is the meaning of the utterance: "Drinking moonshine makes you go blind"?
-A first pass could be *there exists a causal relationship between blindness and moonshine such that blindness causes moonshine*.
-Interestingly, this definition doesn't mention the increased risk in becoming blind from moonshine, but presumably it's more probable than the alternative (not drinking moonshine).
-We hypothesize that the semantics of the above statement (a *causal* statement) is underspecified and subject to the same context-sensitivity as generic and habitual language.
+Language about causal relationships manifests as a generalization.
+The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analagous to how "John smokes" relates to  "John smoked yesterday". 
+We explore this hypothesis in our third case study: causal language or *causals* (e.g., "A causes B").
 
-We take language that conveys a causal relationship between two classes of things as our third case study: causal language, or *causals*.
-For simplicity, we identify the relevant dimension of the scale to be the conditional probability of the effect given the cause, though this representation will have problems for classic cases in causal reasoning.
-Our goal is not to explain the phenomena of causal reasoning *per se*, but rather to adopt a semantics that could apply to the causal domain and test our theory on the language of causal relations.
-In particular, we aim to demonstrate empirically that our theory of the language of generalization posits constructs that are causally related to sentence endorsement.
+The problem of *causal induction*---knowing that one thing causes another----has been studied extensively in human psychology  [@Cheng1992; @Cheng1997; @Griffiths2005; @Griffiths2009].
+Classically, this is cast as a problem of inducing an unobservable relation (*type causation*) from observable events or contingency data. 
+We take a different approaching, examining *type causation* by the language used to describe it (e.g., "A causes B").
+We assume that such language conveys a generalization about *token* or *actual causation* (e.g., "A caused B, in this instance") and that our theory of the language of generalizations extends in a natural way to describe *causal language*.
+Ascribing causation to an individual event (*token or actual causation*) is itself a complex, inferential process [e.g., depending on counterfactual reasoning; @Gerstenberg2015how], which we do not try to model here.
 
@@
 
-The problem of *causal induction*---knowing that one thing causes another----has been studied extensively in human psychology  [@Cheng1992; @Cheng1997; @Griffiths2005; @Griffiths2009].
-Classically, this is cast as a problem of inducing an unobservable relation from observable data. 
-For example, assuming a controlled experiment: observing E whenever C is present, and the absence of E whenever C is absent, is strong evidence for concluding that C causes E.
-At the same time, individual events (e.g., observing $c_i$ and $e_i$) can be construed as *causal*, depending on whether $c_i$ is seen as a difference-maker for $e_i$ and how exactly $c_i$ made that difference [@Gerstenberg2015how].
-Going from covariation to causation, then, implies that during the events observed (the covariation), causal attribution was withheld: The events were not seen as causal at the time, only in retrospect.
-Alternatively, we may conclude there is no cause after first seeing events in-the-moment as causal.
+<!-- Going from covariation to causation, as in the classic causal reasoning paradigms, then, actual involves two inferences  -->
+
+<!-- implies that during the events observed (the covariation), causal attribution was withheld: The events were not seen as causal at the time, only in retrospect. -->
+
+<!-- A first pass could be *there exists a causal relationship between blindness and moonshine such that blindness causes moonshine*. -->
+<!-- Interestingly, this definition doesn't mention the increased risk in becoming blind from moonshine, but presumably it's more probable than the alternative (not drinking moonshine). -->
+<!-- We hypothesize that the semantics of the above statement (a *causal* statement) is underspecified and subject to the same context-sensitivity as generic and habitual language. -->
+
+<!-- We take language that conveys a causal relationship between two classes of things as our third case study: causal language, or *causals*. -->
+<!-- For simplicity, we identify the relevant dimension of the scale to be the conditional probability of the effect given the cause, though this representation will have problems for classic cases in causal reasoning.
+-->
+<!-- Our goal is not to explain the phenomena of causal reasoning *per se*, but rather to adopt a semantics that could apply to the causal domain and test our theory on the language of causal relations.
+-->
+<!-- In particular, we aim to demonstrate empirically that our theory of the language of generalization posits constructs that are causally related to sentence endorsement. -->
 
@@
 d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/pilot-causals-7-prior-trials.csv",
+                           "data/causals/priors/causals-8-prior-trials.csv",
                            sep= ""))
 
+d.cas.priors.catch <- read.csv(paste(project.path,
+                           "data/causals/priors/causals-8-prior-catch_trials.csv",
+                           sep= ""))
+
+# some participants were mischaracterized as failing the catch trial because they put something of the form "0/100" or "herb F: 19" 
+mischaracterized <- c( 24, 48, 62, 94, 106, 110, 111, 112, 113, 116, 125, 132, 145, 155, 158)
+
+d.cas.priors <- left_join(d.cas.priors, d.cas.priors.catch) %>%
+  mutate(pass_numeric = ifelse(workerid %in% mischaracterized, 1, pass_numeric),
+         passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
+
 n.subj.cas <- length(unique(d.cas.priors$workerid))
+
+n.subj.cas.failed <- length(unique(filter(d.cas.priors, passBoth == 0)$workerid))
+
+d.cas.priors <- d.cas.priors %>% filter(passBoth == 1)
 
@@
 
+`r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
 The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure \ref{fig:figure-causals}.
@@
 ```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 3a)."}
-
 d.cas.priors %>%
@@
 ```{r causals-fullmodel}
-n_chains <- 1
-n_samples <- 5000
+n_chains <- 2
+n_samples <- 100000
 burn <- n_samples / 2
@@
 
-```{r causal-model-insets, fig.width = 8, fig.height = 3.5, cache = T}
+```{r causal-model-insets, fig.width = 4, fig.height = 3.5, cache = T}
 m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
@@
 
-inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
+#inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
+inset.color.order <- c("#859900","#d33682","#dc322f", "#268bd2")
 
@@
                               levels = c("state_Prior","state_Posterior"),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Causal")),
+                            labels = c("Feature-probability Prior (Expt. 3a)",
+                                       "Interpreter model posterior")),
     Distribution = factor(distribution, 
-                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>%
+                               levels = c("rare_weak",  "common_weak", "rare_deterministic", "common_deterministic"),
+         labels = c("Weak, Rare", "Weak, Common", "Strong, Rare", "Strong, Common"))) %>%
   ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
-  facet_wrap(~Distribution, nrow = 1)+
+  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+  facet_wrap(~Distribution, nrow = 2)+
   scale_fill_manual(values =inset.color.order )+
   scale_color_manual(values = inset.color.order)+
-  scale_alpha_manual(values = c(0.1, 0.8))+
-  scale_linetype_manual(values = c(2, 1))+
+  scale_alpha_manual(values = c(0.8, 0.1))+
+  scale_linetype_manual(values = c(1, 2))+
   scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
@@
   ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank())+
-  guides(fill = F, color = F)
+  theme(legend.position = "bottom", 
+        legend.direction = 'vertical',
+        legend.title = element_blank(),
+        plot.margin = unit(c(16,6,6,6), "pt"))+
+  guides(fill = F, color = F, alpha = F)
+
+#causals.endorsement.insets
 ```
@@
   mutate(
-    src = factor(src, levels = c( "data", "model")),
+    src = factor(src, levels = c( "model", "data")),
     dist = factor(dist, 
@@
            labels = c(
-                       "Rare Weak", "Common Weak","Rare Deterministic","Common Deterministic"))
+                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))
     ) %>%
-  ggplot(., aes( x = dist, y = MAP, ymin = cred_lower, ymax = cred_upper, fill = dist,
-                        group = src, alpha = src))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(0.3), alpha = 1)+
-  #geom_line(position = position_dodge(0.3))+
+  ggplot(., aes( x = frequency, y = MAP, ymin = cred_lower, ymax = cred_upper, 
+                 color = dist, #linetype = dist, 
+                 shape = dist,
+                        group = dist#, 
+                 #alpha = src
+                 ))+
+  #geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
+  geom_linerange(position = position_dodge(8), alpha = 1, alpha=0.8)+
+  geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
+  geom_point(position = position_dodge(8), size = 2.25)+
   #theme(axis.text.x = element_text(angle = 90))+
-  geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  #geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
   scale_alpha_manual(values = c(1, 0.3))+
+  scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
   #scale_fill_solarized()+
-  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("")+
-  ylab("Proportion Causal Endorsement")+
-  facet_grid(.~frequency)+
-  coord_flip()+
-  guides(fill = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+  scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
+  xlab("Referent feature-probability")+
+  ylab("Causal Endorsement")+
+  facet_grid(.~src)+
+  #coord_flip()+
+  coord_fixed(ratio = 90)+
+  #guides(fill = F)+
+  guides(
+    shape=guide_legend(title="Background distribution"),
+    color=guide_legend(title="Background distribution")
+    )+
+  theme(
+    plot.margin = unit(c(0,6,0,6), "pt")
+    #legend.position = 'bottom', 
+    # legend.direction = 'horizontal', 
+    # legend.title = element_blank()
+  )
 ```
 
-```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes.
-Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies.
-Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors.
-These distributions are inferred using both data sources from Expt.
-3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
-grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
-             layout_matrix = cbind(c(1,1,2)))
+```{r figure-causals, fig.width=9, fig.height=4, cache = T, fig.cap="Endorsing generalizations about causes.
+A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies.
+B: Background, feature-probability prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors.
+Endorsement mode predictions, interpreter model posteriors, and feature-probability priors are inferred using both Expt.
+3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix."}
+
+prow <- plot_grid( 
+  figure.causals.endorsement + theme(legend.position="none"),
+  causals.endorsement.insets,# + theme(legend.position="none"),
+   align = 'h',
+   labels = c("A", "B"),
+   #hjust = -1,
+   nrow = 1,
+  rel_widths = c(1, 0.7),
+  rel_heights = c(1, 0.7)
+  )
+#legend <- get_legend(causals.endorsement.insets)
+
+#plot_grid( prow, legend, rel_widths = c(3, .3))
+prow
+#grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
+             #layout_matrix = cbind(c(1,1,2)))
 
@@
 
-`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse.failed-n.subj.cas.endorse.failed` responses for analysis.
+`r n.subj.cas.endorse.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas.endorse-n.subj.cas.endorse.failed` responses for analysis.
 As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.

### 2017-12-16 paper/comgen-paper.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

@@
 library(cowplot)
+library(magick)
 theme_set(theme_few())
@@
 
-```{r simluationsModel, eval = T, cache = T}
-l0.model <- '
+```{r rsaHelpers}
+rsaHelpers <- '
 var probability = function(Dist, x) {
@@
 
+var round = function(x){
+  return Math.round(x*1000)/1000
+}
 var utterancePrior = Infer({model: function(){
@@
 
+var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
+// var thetaBins = [
+//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
+ // ]
 var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
+ return uniformDraw(thetaBins)
+}});
+
+var bins = map(round, _.range(0.01, 0.99, 0.01))
+
+// var bins = [
+  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
+// ];
 
@@
 }});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
+'
+```
+
+```{r rsaInterpretationModels, eval = T, cache = T}
+no.utterance.model <- '
+var noUtteranceInterpreter = function() {
   Infer({model: function(){
    var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-//     var state = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//     var state_prior = sample(flip(mixture) ? Beta( priorParams) : Delta({v:0}))
-//    var theta = uniform(0,1)
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
+    return { state }
+ }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+'
+
+fixed.threshold.model <- '
+var fixedThresholdInterpreter = function(threshold) {
+  Infer({model: function(){
+  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+  var state = sample(statePrior)
+  condition( state > threshold)
     return {
-      state_Posterior: state, 
-      state_Prior: state_prior
+      state: state
+  }
+ // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+ }, method: "enumerate"})}
+'
+
+uncertain.threshold.model <- '
+var uncertainThresholdInterpreter = function() {
+  Infer({model: function(){
+   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+    factor( Math.log(state) )
+    return {
+      state: state, 
   }
   }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-//var out = {generic: listener0("generic"), some: listener0("some")}
-//out
-continuousListener0(data.utt[0])
 '
 
+```
+
+```{r simulationCalls}
+fixed.threshold.calls <- '
+_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
+'
+no.utterance.call <- ' 
+  noUtteranceInterpreter()
+'
+uncertain.threshold.call <- '
+  uncertainThresholdInterpreter()
+'
+```
+
+```{r}
 priorNames <- c(
@@
 
-all.simulations <- data.frame()
+sims.fixed.thresholds <- data.frame()
+sims.priors <- data.frame()
+sims.uncertain.thresholds <- data.frame()
+
 for (p in priorNames){
-  for (u in c("generic")){
-
-    inputData = list(prior = priorShapes[[p]], utt = u)
-    l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
-
-    # all.simulations <- bind_rows(all.simulations,
-    #                         bind_rows(
-    #                           data.frame(l0.rs$generic) %>%
-    #                             gather(key, val, -probs) %>%
-    #                              group_by(key, val) %>%
-    #                              summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                               mutate(key = gsub("support.", "", key)) %>%
-    #                              separate(key, into = c("Parameter","Distribution")) %>%
-    #                               mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution)),
-    #                           data.frame(l0.rs$some) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_0", Distribution)) %>%
-    #                             filter(Distribution != "Prior"),
-    #                           data.frame(l0.rs$most) %>%
-    #                             gather(key, val, -probs) %>%
-    #                             group_by(key, val) %>%
-    #                             summarize(prob = sum(probs)) %>%
-    #                             ungroup() %>%
-    #                             mutate(key = gsub("support.", "", key)) %>%
-    #                             separate(key, into = c("Parameter","Distribution")) %>%
-    #                             mutate(Distribution = gsub("Posterior", "Posterior_05", Distribution)) %>%
-    #                             filter(Distribution != "Prior")
-    #                         ) %>%
-    #                           mutate(PriorShape = p)
-    # )
-      all.simulations <- bind_rows(all.simulations,
-                                   l0.rs %>%
-                                  separate(Parameter, into = c("Parameter","Distribution")) %>%
-                                  mutate(Distribution = gsub("Posterior", "Posterior_Generalization", Distribution))
-                                  %>%
-                              mutate(PriorShape = p, utterance = u)
+
+  inputData = list(prior = priorShapes[[p]])
+  rs.fixed.threshold.model <- webppl(paste(rsaHelpers, fixed.threshold.model, fixed.threshold.calls, sep = '\n'), data = inputData, data_var = "data")
+  rs.uncertain.threshold.model <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+  rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
+
+  sims.fixed.thresholds <- bind_rows(sims.fixed.thresholds,
+    bind_rows(
+      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.1`) %>% rename(prob = probs), 20000), threshold = 0.1) ,
+      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.3`) %>% rename(prob = probs), 20000), threshold = 0.3),
+      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.5`) %>% rename(prob = probs), 20000), threshold = 0.5),
+      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.7`) %>% rename(prob = probs), 20000), threshold = 0.7),
+      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.9`) %>% rename(prob = probs), 20000), threshold = 0.9)
+    ) %>% 
+      mutate(PriorShape = p)
     )
+
+  sims.uncertain.thresholds <- bind_rows(sims.uncertain.thresholds, rs.uncertain.threshold.model %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
+  sims.priors <- bind_rows(sims.priors, rs.prior %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
 }
-  #print(p)
-}
-```
+```
+
+```{r cache = F}
+fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
+    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
+    theme_few() +
+    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    ylab("Normalized probability density") +
+    xlab("")+
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    facet_grid(PriorShape~., scales = 'free')+
+    theme(strip.text.y = element_blank())
+```
+
+```{r cache = F}
+fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
+    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
+    theme_few() +
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Feature-probability") +
+    ylab("") +
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    facet_grid(PriorShape~threshold, scales = 'free')+
+    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
+```
+
+```{r cache = F}
+fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
+                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
+                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
+                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
+    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
+    theme_few() +
+    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("") +
+    ylab("") +
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    facet_grid(PriorShape~., scales = 'free')+
+    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
+```
+
+```{r fig.width = 9, eval = F}
+p1 <- fig.sims.priors +
+  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
+p2 <- fig.sims.fixed.thresholds +
+  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
+p3 <- fig.sims.uncertain.threshold+
+  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
+    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
+
+prow <- plot_grid( p1 + theme(legend.position="none"),
+           p2 + theme(legend.position="none"),
+           p3 + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("A", "B", "C"),
+           hjust = -1,
+           nrow = 1,
+           #rel_widths = c(1.2, 3, 2)
+           rel_widths = c(1.2, 3, 1.2)
+           )
+#prow
+#legend <- get_legend(p1)
+
+#plot_grid( prow, legend, rel_widths = c(3, .3))
+```
+
 ```{r simluationEndorsementModel, eval = T, cache = T}
 s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.mix[0];
-var priorParams = data.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-   var state_prior = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor(
-    (utterance == "generic") ? 
-      Math.log(state) : 
-    (state > 0.017) ? 0 : -Infinity
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-
-var listener0 = cache(function(utterance) {
+var interpreter = cache(function(utterance) {
   Infer({model: function(){
     var state = sample(statePrior)
-    var state_prior = sample(statePrior)
     var theta = utterance == "generic" ? sample(thetaPrior) : -99
     condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
+    return state
  }})}, 10000)
+
 var alpha = 2
@@
     var endorsement = sample(utterancePrior)
-    var L0 = marginalize(listener0(endorsement), "state_Posterior")
+    var L0 = interpreter(endorsement)
     factor(alpha * L0.score(featureProb))
@@
 }
-
+// console.log(data.featureProb[0])
 probability(endorser(data.featureProb[0]), "generic")
@@
   )
+
 exampleParameters <- list(
-  robinsAreFemale =  list(params = data.frame(a = 10, b = 10), mix = 1, featureProb = 0.5), 
-  robinsLayEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.2, featureProb = 0.5), 
-  sharksDontEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1, featureProb = 0.8), 
-  dogsBark =  list(params = data.frame(a = 5, b = 1), mix = 0.4, featureProb = 0.9), 
-  kangaroosHaveSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7, featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(params = data.frame(a = 1, b = 30), mix = 0.1, featureProb = 0.1)
+  robinsAreFemale =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 1), featureProb = 0.5), 
+  robinsLayEggs =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 0.2), featureProb = 0.5), 
+  sharksDontEatPeople =  list(prior = list(params = data.frame(a = 50, b = 1), mix = 1), featureProb = 0.8), 
+  dogsBark =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.4), featureProb = 0.9), 
+  kangaroosHaveSpots =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.7), featureProb = 0.1), 
+  mosquitosCarryMalaria =  list(prior = list(params = data.frame(a = 1, b = 30), mix = 0.1), featureProb = 0.1)
 )
@@
 
-    s1.rs <- webppl(s1.model, data = exampleParameters[[p]], data_var = "data")
+    s1.rs <- webppl(paste(rsaHelpers, s1.model, sep = "\n"), data = exampleParameters[[p]], data_var = "data")
     s1.simulations <- bind_rows(s1.simulations,
@@
                           levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")))
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-  #geom_jitter(width = 0.1, shape = 21, size = 5)+
-  #ylab("Human endorsement probability")+
-  #xlab("Frequency of target")+
-  geom_label_repel(data = s1.simulations.relabeled, 
-                   aes( label = example, fill = example),
-                       color = 'white',
-    box.padding = unit(0.0, "lines"),
-    #point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37')+
+                            labels = 
+                            c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")
+                            #c("Dogs", "Kangaroos", "Sharks", "Robins ", "Robins", "Mosquitos")
+                          ))
+
+# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
+#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
+#   #ylab("Human endorsement probability")+
+#   #xlab("Frequency of target")+
+#   geom_label_repel(data = s1.simulations.relabeled, 
+#                    aes( label = example, fill = example),
+#                        color = 'white',
+#     box.padding = unit(0.0, "lines"),
+#     #point.padding = unit(1e-06, "lines"),
+#     segment.color = 'grey37')+
+#   scale_fill_solarized()+
+#   scale_x_continuous(limits = c(0, 1), 
+#                      breaks = c(0, 0.5, 1))+
+#   scale_y_continuous(limits = c(-0.01, 1.01), 
+#                      breaks = c(0, 1),
+#                      labels = c("False", "True"))+
+#   coord_fixed(ratio = 1)+
+#   guides(fill = F)+
+#   ylab("Endorsement model prediction")+
+#   xlab("Hypothesized feature-probability")
+
+s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
+  geom_col(color = 'black')+
+  # geom_label_repel(data = s1.simulations.relabeled, 
+  #                  aes( label = example, fill = example),
+  #                      color = 'white',
+  #   box.padding = unit(0.0, "lines"),
+  #   #point.padding = unit(1e-06, "lines"),
+  #   segment.color = 'grey37')+
   scale_fill_solarized()+
@@
   scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
+                     breaks = c(0, 1))+
+                     #labels = c("False", "True"))+
   coord_fixed(ratio = 1)+
+  facet_grid(example~.)+
   guides(fill = F)+
-  ylab("Endorsement model prediction")+
-  xlab("Hypothesized feature-probability")
-
-```
-
-```{r simulations_l0, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions."}
+  ylab("Endorsement")+xlab("Referent feature-probability")+
+  theme(strip.text.y = element_text(angle = 0, hjust = 0), 
+        axis.title.x = element_text(hjust = 0)
+        #axis.title.y = element_text(vjust = 0)
+        )
+  #ylab("Endorsement model prediction")+
+  #xlab("Hypothesized feature-probability")
+#s1.simulations.scatter
+```
+
+```{r simulations, fig.cap = "Computational model behavior.
+A: Prior distributions over feature-probabilities for 6 example generalizations.
+B: Different fixed thresholds (columns) give rise to different posterior interpretations.
+C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
+D: Endorsement model predictions, assuming a particular referent feature-probability.
+Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
+p1 <- fig.sims.priors +
+  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
+p2 <- fig.sims.fixed.thresholds +
+  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
+p3 <- fig.sims.uncertain.threshold+
+  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
+    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
+p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,0), "pt"))
+
+prow <- plot_grid( p1 + theme(legend.position="none"),
+           p2 + theme(legend.position="none"),
+           p3 + theme(legend.position="none"),
+           p4,
+           align = 'vh',
+           labels = c("A", "B", "C", "D"),
+           hjust = -1,
+           nrow = 1,
+           #rel_widths = c(1.2, 3, 2)
+           rel_widths = c(1.2, 3, 1.1, 3)
+           )
+prow
+```
+
+```{r eval = F}
 all.simulations.refactored <- all.simulations %>%
@@
           legend.position = c(0.92, 0.35))
-```
-
-```{r simulations, fig.cap = "Model behavior.
+
+l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
+                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
+    geom_density(aes(y = ..scaled..),
+                 size = 0.6,  adjust = 1.5)+
+    theme_few() +
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    scale_alpha_manual(values = c(0.7, 0.3))+
+    scale_linetype_manual(values = c(1, 3))+
+    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Feature-probability h") +
+    ylab("Scaled prior probability density") +
+  facet_wrap(~PriorShape, scales = 'free')+
+  guides(fill = F, color = F)+
+  theme(strip.text.y = element_text(angle = 0),
+          legend.position = c(0.92, 0.35))
+
+```
+
+```{r simulationsOld, eval = F, fig.cap = "Model behavior.
 Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
@@
 
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong generalization to a na\"{i}ve listener.
+The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong generalization to a naive listener.
 Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].

### 2017-12-16 paper/case1-generics.Rmd
refresh to figures 2-4

@@
 
-```{r generics-prior-task, fig.cap:"Test"}
-fig.priors.expt <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-bothStages.pdf", sep=""), scale = 1)
-fig.priors.expt
+```{r generics-prior-task, fig.cap="Prior elicitation task.
+A: Participants first generated animal names after seeing six example categories.
+B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3}
+fig.priors.expt.stage1 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage1.jpeg", sep=""), scale = 1)
+fig.priors.expt.stage2 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage2.jpeg", sep=""), scale = 1)
+
+plot_grid(fig.priors.expt.stage1, fig.priors.expt.stage2, labels = "AUTO")
 ```
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
 Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
@@
 load('../analysis/generics-priors-posteriorPredictives.Rdata')
-ggplot(m.gen.endorse.priors.posteriorPredictive, 
+
+gen.priors.densities <- ggplot(m.gen.endorse.priors.posteriorPredictive %>%
+         filter(src == 'Data'), 
+           aes( x = prevalence))+
+           #aes( x = prevalence, color = src, lty = src))+
+    geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
+    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    #stat_ecdf(size = 1)+
+    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    facet_wrap(~Property, nrow = 2)+
+    #scale_linetype_manual(values = c(1, 4, 3))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #coord_fixed()+
+    xlab("") +
+    ylab("Normalized probability density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+
+gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
+  mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
+                      labels = c("Empirical distribution", 
+                                 "Mixture of Betas",
+                                 "Single Beta"))) %>%
+ggplot(.,
            aes( x = prevalence, color = src, lty = src))+
-      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
     #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  coord_fixed()+
+    #coord_fixed()+
     xlab("Feature-probability") +
     ylab("Cumulative probability density")+
-    theme(legend.position = "bottom", legend.title = element_blank())
-
+    theme(legend.title = element_blank(), legend.position = 'bottom')
+
+gen.prior.fig1 <- gen.priors.densities +
+  theme(plot.margin = unit(c(10,0,0,0), "pt")) 
+gen.prior.fig2 <- gen.priors.cdfs  +
+  theme(plot.margin = unit(c(10,0,6,0), "pt"))
+
+plot_grid( 
+ gen.prior.fig1, gen.prior.fig2,
+           align = 'vh',
+           labels = c("A", "B"),
+           hjust = -1,
+           nrow = 2,
+           rel_heights = c(1, 1.2)
+           #rel_widths = c(1.2, 3, 2)
+           #rel_widths = c(1, 1.3)
+           )
 ```
@@
 
+# run interpreter model to generate "hypothetical intepretation" plots
 for (p in example.generics.properties){
@@
                   utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
+ l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+ l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
  gen.listener.predictions <- bind_rows(
    gen.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(property = p)
+   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
+    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
    )
@@
   mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics)
-
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    mutate(Sentence = paste(category, property)) %>%
   filter(Sentence %in% example.generics) %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      val = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
+  mutate(property = factor(property))
+
+# m.samp.prev.params <- m.samp %>%
+#     filter(type == "targetPrevalence") %>%
+#     mutate(Sentence = paste(category, property)) %>%
+#     filter(Sentence %in% example.generics) %>%
+#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
+#     select(-param, -property, -category, -chain, -type) %>%
+#     group_by(parameter) %>%
+#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+#     ungroup() %>%
+#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
+#     group_by(category, property, iteration) %>%
+#     spread(parameter, val) %>%
+#     rowwise() %>%
+#     mutate(
+#       a = mean*sampleSize,
+#       b = (1-mean)*sampleSize,
+#       val = rbeta(n = 1, shape1 = a, shape2 = b)
+#       ) %>%
+#     ungroup()
 
@@
 
-generics.endorsement.insets <- gen.inset.distributions %>%
+gen.inset.distributions.refactored <- gen.inset.distributions %>%
   mutate(Parameter = factor(Parameter, levels = c("state_Prior",
@@
                                                   "speakerBeliefs"),
-                            labels = c("Listener Prior (Posterior given Silence)", 
-                                       "Listener Posterior given Generic", 
-                                       "Speaker Beliefs")),
+                            labels = c("Feature-probability Prior", 
+                                       "Interpretation given generalization", 
+                                       "Referent feature-probability")),
          property = fct_relevel(property,
                                 "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
+                                "are female", "dont eat people") )
+
+generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
+                                      aes( x = value, fill = Parameter, 
+                 color = Parameter, lty = Parameter, alpha = Parameter ))+
   geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
@@
 
-```{r generics-endorsement-figure, fig.width=12, fig.height=9.5, fig.cap="Endorsing generalizations about categories.
+```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories.
 Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
@@
 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-grid.arrange(generics.endorsement.spectrum, 
-             generics.endorsement.models,
-             generics.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
+
+fig.gen.endorse.data <- generics.endorsement.spectrum +
+  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ggtitle("Feature-probability priors")
+fig.gen.endorse.models <- generics.endorsement.models +
+  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ylab("")
+fig.gen.endorse.priors <- generics.endorsement.insets +
+  theme(plot.margin = unit(c(26,10,0,10), "pt"))
+
+#+ 
+    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
+#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
+
+fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
+                                     fig.gen.endorse.models, 
+                                    # align = 'v',
+                                    #  axis = 'l',
+                                    labels = c("A", "B"),
+                                    rel_widths = c(0.9, 1))
+
+plot_grid(fig.gen.endorse.toprow,
+          fig.gen.endorse.priors,
+          labels = c("", "C"), nrow = 2, rel_heights = c(1.1, 0.6)
+          )
+# prow <- plot_grid( p1 + theme(legend.position="none"),
+#            p2 + theme(legend.position="none"),
+#            p3 + theme(legend.position="none"),
+#            p4,
+#            align = 'vh',
+#            labels = c("A", "B", "C"),
+#            hjust = -1,
+#            #nrow = 1,
+#            #rel_widths = c(1.2, 3, 2)
+#            rel_widths = c(1.2, 3, 1.05, 1.7)
+#            )
+
+# grid.arrange(generics.endorsement.spectrum, 
+#              generics.endorsement.models,
+#              generics.endorsement.insets, ncol = 2,
+#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
+
 ```

### 2017-12-16 paper/comgen-paper.Rmd
refresh to figures 2-4

@@
 
-```{r}
+```{r simulationRuns}
 priorNames <- c(
@@
     theme_few() +
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
@@
   scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 0.5, 1))+
+                     breaks = c(0, 1))+
   scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1))+
-                     #labels = c("False", "True"))+
-  coord_fixed(ratio = 1)+
+                     breaks = c(0, 1),
+                     labels = c("False", "True"))+
+  #coord_fixed(ratio = 1)+
+  coord_flip()+
   facet_grid(example~.)+
@@
   ylab("Endorsement")+xlab("Referent feature-probability")+
-  theme(strip.text.y = element_text(angle = 0, hjust = 0), 
-        axis.title.x = element_text(hjust = 0)
+  theme(strip.text.y = element_text(angle = 0, hjust = 0)
+        #axis.title.x = element_text(hjust = 0)
         #axis.title.y = element_text(vjust = 0)
@@
   #xlab("Hypothesized feature-probability")
-#s1.simulations.scatter
 ```
@@
 p3 <- fig.sims.uncertain.threshold+
-  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
+  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
     theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,0), "pt"))
+p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
 
@@
            #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 3, 1.1, 3)
+           rel_widths = c(1.2, 3, 1.05, 1.7)
            )

### 2017-12-16 paper/case2-habituals.Rmd
clean intro to habituals

@@
 Segmenting the continuous stream of reality into events is a crucial task for cognition.
-We consider events as individuated entities as instances of a category. 
-For example, the event *Mary smoked a cigarette yesterday at 2:30pm*...
-
-Learning that an agent tends to exhibit a behavior is a special case of learning a generalization about an event. 
-The event, *the agent doing the action*,
-
-We meet new people all the time, and hear about them at least as often.
-*Habitual language* (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events, including people doing actions. 
+Once individuated, an event can be categorized as a kind of a event.
+For example, the event of Mary smoking at 2:30pm on January the 24th is an instance of *Mary smoking*. 
+Generalizations can be said of this event, in the form of *habitual language*: "Mary smokes".
+
+Events are a broad class of entities. 
+In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes.").
+Habituals about people doing actions are interesting because a 
+Learning about the behaviors of others is useful because it tells us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
+When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-ti8me at the restaurant"; @McGuire1986].
+Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
+
+<!-- of particular importance to social psychology because of their role in causal attribution [@Kelley1973] and intuitive theories of personality and behavior [@]. -->
+
+<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
+<!--  explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family".  -->
+<!-- A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
+-->
+
+<!-- We meet new people all the time, and hear about them at least as often. -->
+<!-- *Habitual language* (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events, including people doing actions.  -->
 <!-- In this case study, we focus on a particular class of events: people doing actions. -->
-Habituals about people taking actions are of particular importance to social psychology because of their role in causal attribution [@Kelley1973] and intuitive theories of personality and behavior [@McGuire1986].
-Habitual language may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-We focus on present-tense habitual sentences of the form \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes."). 
-We use the same computational model and follow the same general experimental structure as in the first case study. 
-First, we measure the prior distribution over the frequencies for different events/actions (e.g., how often different people smoke cigarttes; Expt. 2a).
+
+<!-- We focus on present-tense habitual sentences of the form  -->
+To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
+First, we measure the prior distribution over the frequencies for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
 We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt.
-2b), and use our computational model to predict the habitual endorsements.
+2b), and use our computational model to predict habitual endorsements.
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
-We have said that $h$ represents a probability that a speaker aims to convey.
-In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
-We do this by measuring participants' predictions about future frequencies when causal forces enable or prevent the action and separately measure endorsements of habituals under the same contexts (Expt.
-2c).
+By describing novel characters to participants, we are able to directly the manipulate the frequency (feature-probability) with which the referent does the action.
+<!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
+-->
+
+Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
+Our computational model predicts endorsement rates given a referent-category feature-probability $h$. 
+Does $h$ represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
+We extend our theory by measuring participants' predictions about future frequencies and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
 We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.

### 2017-12-16 paper/case1-generics.Rmd
clean up generics case study; add new fixed threshold alternative model prose; add data examples to prose

@@
 Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-In addition, generics have been the case study of choice for the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
+In addition, generics have been the case study of choice for the semantics of the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
 Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
@@
 Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
+All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure) A.
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
@@
 
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) top left).
+In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ \@ref(fig:generics-prior-task) left).
+1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ \@ref(fig:generics-prior-task) A).
 A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ \@ref(fig:generics-prior-task) right).
-Eight property--columns appeared in the table.
+Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ \@ref(fig:generics-prior-task) B).
+Eight property--columns in total appeared in the table.
 
@@
 In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).
-<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
 
@@
 
-<!-- \begin{figure} -->
-<!-- \centering -->
-<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf} -->
-<!--     \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities.
-Left: Participants first generated animal names after seeing six example categories.
-Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.} -->
-<!--     \label{fig:generics-prior-task} -->
-<!-- \end{figure} -->
-
-### Results
-
-In order to integrate the results of our prior measurement into richer models of endorsement, we first try to accurately model the prior data by itself.
-We do this using a Bayesian mixture model, which assumes that the data generated by participants for each property (e.g., \textsc{lay eggs}) comes from one of two underlying distributions. 
-One of these distributions is fixed to represent kinds of animals who *do not have* an stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}).
-The second distribution is flexible and represents kinds of animals who *do have* such a mechanism; this distribution is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs.
-\text{has wings}).
-For model implementation and inference details, see Appendix.
+### Qualitative results
+
+There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
+The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
+*Being red* exists mostly at extremely low prevalence levels (i.e., 0 feature-probability) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
+This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.
+
+### Quantitative modeling
+
+<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
+In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
+We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
+  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
+] 
+We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in feature-probability or prevalence values close to or equal to 0.
+This "null distribution" is potentially present for all features in exactly the same way.
+The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
+The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
+To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
+<!-- is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs. \text{has wings}). -->
+For more details about model implementation and inference, see Appendix.
 
@@
 ```
+
 ```{r eval = F}
@@
 
-Eight example prior distributions reconstructed from the mixture model's posterior parameter distribution, together with a comparison model that lacks one of the components of the mixture model (the "transient" distribution $D_{transient}$), are shown with the raw empirical distributions of feature-probability judgments in Figure \  \@ref(fig:generic-endorsement-priors-figure).
-There is a lot of diversity in the shapes of the distributions, which the mixture model accounts for quite well, while a model that only models a single distribution fails to.
-One feature-probability prior that the mixture model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
+The prior distributions over feature-probabilities are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs.
+blue lines).
+The *Single Beta* model does okay for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
+One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
 The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
 Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
+]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
 A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="Cumulative density plots for prior distributions representing the feature-probability of eight different features.
-Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution.
+```{r generic-endorsement-priors-figure2, eval = F}
+ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
+         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
+       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
+  geom_bar(stat = 'identity', position = position_dodge())+
+  geom_errorbar(position = position_dodge())+
+  coord_flip()+
+  ylab("MAP estimate and 95% HDI of Mixture parameter")
+```
+
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over feature-probabilities for eight properties.
+B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution.
+Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution.
 A completely uniform distribution would be represented as the y = x line."}
@@
 
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
-
 ## Endorsement model comparison
 
-To try to understand the generic endorsement data, we articulate a set of formal models that have been previously-proposed in the literature, a reduced-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore whether referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
+To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
+As the simplest baseline hypothesis, we first explore how well referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
 As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
@@
 
-Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt.
-1b), from which the interpreter model infers likely thresholds for the generic.
-The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
-We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
-As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
-This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
-This provides a strict test of the uncertain-threshold hypothesis.
+Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on feature-probabilities $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category feature-probability (e.g, the prevalence of laying eggs among robins).
+There are several substantive components to this hypothesis: (a) the prior distribution $P(h)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
+As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
+This provides a strict test of the uncertain-threshold hypothesis (c).
 
@@
   )
-# ggplot(d.gen.endorse.regression, 
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = cuevalidity))+
-#   geom_errorbar(alpha = 0.3)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.gen.endorse.regression.prevalence.cuevalidity %>% 
-#   #                   rename(cuevalidity = prop) %>% 
-#   #                   filter(sqErr > 0.05), 
-#   #                 aes(label = sentence, color = cuevalidity), force = 1, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human generic endorsement")+
-#   facet_wrap(~src)
 
@@
 
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
+As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* predict generic endorsementse.
 If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
@@
 Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
+In addition, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
 
 We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
+If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and can be derived via Bayes' Rule:
 $$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
+Previous empirical studies of generic language, however, have not measured feature-probability priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
 In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
@@
 
+```{r cue.validity.examples}
+generics.cuevalidity.examples <- c(
+  "Mosquitos carry malaria.", "Lions have manes.",
+  "Robins lay eggs.", 
+  "Mosquitos dont carry malaria."
+  )
+
+reg.mosquitos.carry <- d.gen.endorse.regression %>% filter(src == "regression_Prev_Cuevalidity", sentence == "Mosquitos carry malaria.")
+reg.robins.lay.eggs <- d.gen.endorse.regression %>% filter(src == "regression_Prev_Cuevalidity", sentence =="Robins lay eggs.")
+reg.lions.manes <- d.gen.endorse.regression %>% filter(src == "regression_Prev_Cuevalidity", sentence == "Lions have manes.")
+reg.mosquitos.dont.carry <- d.gen.endorse.regression %>% filter(src == "regression_Prev_Cuevalidity", sentence == "Mosquitos dont carry malaria.")
+```
+
 A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
-This model is able to account for the endorsements of examples like "Mosquitos carry malaria" and "Lions have manes", as these features are very diagnostic of the kind.
+This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
+`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
+`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
 Deviations, however, still remain.
-For example, "Robins lay eggs" still receives only intermediate endorsement by this model, and "Mosquitos don't carry malaria" is judged to be a good statement.
-
-These highlight a shortcoming of a simple model based on cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for "Robins".
-A simple metric like cue validity is too blunt to capture this subtlety.
-Additionally, negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category, and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high.
+For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
+`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
+`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is judged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
+`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
+`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).
+
+"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of a simple model based on cue validity.
+"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
+Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high (most mosquitos don't carry malaria).
+A simple metric like cue validity is too blunt to capture these subtleties.
 
@@
 The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpretor.
-The endorsement model $Endorse$ (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpretor $Interpret$ (Eq.
+The endorsement model (Eq.
+\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpretor (Eq.
 \ref{eq:L0}) conditioned on a particular referent-category feature-probability $h'$ (e.g.,  the percentage of robins that lay eggs).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorsement model.
+We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the referent-category feature-probability $h'$ in the endorsement model.
 The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
@@
 Modeling the data from both Expt.
-1a and 1b by a single, joint-inference model simultaneously makes explicit all of our assumptions about how these data were generated, and is the proper Bayesian way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix and Figure \  \@ref(fig:genericsModelDiagram) for further model specification details).
-The $Endorse$ model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie] for 3 chains of 100,000 iterations, discarding the first 50,000 for burnin.
+1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
+The endorsement model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burnin.
 
 The number of parameters of this full data-analytic model is relatively large, and thus there is a concern that the parameters themselves (as opposed to the exact structure of our model) are doing the work.
-To address this concern, we construct a strong, alternative model that uses the same data analytic strategy with the same number of the parameters.
-This control model is a lesioned version of the uncertain threshold model, which we construct by removing the uncertainty about the semantic threshold $\theta$. 
-All other architectural features (the prior distribution, the information-theoretic decision of whether or not to produce the generalizations) as well as their respective parameters are the same as for the uncertain threshold model.
-We examine the predictions of the control model first.
-
-#### Fixed-threshold model
-
-The fixed-threshold model is a lesioned version of the unceratin-threshold model: It models endorsement as an information-theoretic decision of producing the generic vs.
-an alternative, and has access to the full prior distribution on feature-probabilities $P(h)$.
-The only difference is that this model uses a fixed-threshold as the core meaning of a generic statement, rather than an uncertain threshold.
-For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).
-
-^[
-  Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further   specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
-]
-This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.
+To address this concern, we construct a strong, alternative model that uses the same data analytic strategy and only differs in the uncertain semantic threshold $\theta$ is replaced with a fixed-threshold.
+To provide the strongest possible test, we make the fixed-threshold a parameter of the data-analytic model, to search for the best possible fixed-threshold. 
+Finally, a fixed-threshold model will have to accomodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent feature-probability is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
+Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(h)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
+This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
+We examine the predictions of this alternative model first.
+
+#### Fixed-threshold with noise model
 
@@
 
-# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
+#m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-10000_burn5000_lag20_chain1.csv", sep = ""))
 # 
@@
             cred_lower = hdi_lower(val))
+
+fixed.threshold.posterior <- filter(fixed.params.posterior, param == "fixedThreshold")
+generics.fixed.noise.posterior <- filter(fixed.params.posterior, param == "noise")
 ```
@@
 
-To evaluate this model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions of the model given these parameter values.
-Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
+The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
+`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
+`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
+Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1b).
-This means the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
+This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
+
+```{r fixed-threshold-examples}
+fixed.threshold.generics.examples <- c("Tigers eat people.", "Peacocks have beautiful feathers.", "Lions lay eggs.", "Mosquitos attack swimmers.")
+fixed.threshold.model.examples <- m.gen.endorse.rsa %>% 
+  filter(src == "some_model", sentence %in% fixed.threshold.generics.examples)
+
+tigers.eat.people <- filter(fixed.threshold.model.examples, sentence == "Tigers eat people.")
+peacocks.feathers <- filter(fixed.threshold.model.examples, sentence == "Peacocks have beautiful feathers.")
+lions.lay.eggs <- filter(fixed.threshold.model.examples, sentence == "Lions lay eggs.")
+mosquitos.attack.swimmers <- filter(fixed.threshold.model.examples, sentence == "Mosquitos attack swimmers.")
+```
 
@@
 Figure \@ref(fig:generics-endorsement-figure) (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-The model fails to distinguish any of the generic sentences because they are all somewhat true. 
-All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
-
-The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
-For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
-For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
-Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
-This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
-The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
-
-\mht{Outfit fixed-threshold model with noise parameter?}
+Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither. 
+It treats "Tigers eat people" (`r round(tigers.eat.people[[1,"MAP"]],2)` [`r round(tigers.eat.people[[1,"cred_lower"]], 2)`,
+`r round(tigers.eat.people[[1,"cred_upper"]], 2)`]) as good a statement as "Peacocks have beautiful feathers" (`r round(peacocks.feathers[[1,"MAP"]],2)` [`r round(peacocks.feathers[[1,"cred_lower"]], 2)`,
+`r round(peacocks.feathers[[1,"cred_upper"]], 2)`]), though participants seem to give a substantially weaker endorsement of the former ("Tigers eat people" = `r round(tigers.eat.people[[1,"MAP_h"]],2)` [`r round(tigers.eat.people[[1,"low"]], 2)`,
+`r round(tigers.eat.people[[1,"high"]], 2)`]; "Peacocks have beautiful feathers" = `r round(peacocks.feathers[[1,"MAP_h"]],2)` [`r round(peacocks.feathers[[1,"low"]], 2)`,
+`r round(peacocks.feathers[[1,"high"]], 2)`]).
+Similarly, "Lions lay eggs" is judged to be just as bad as "Mosquitos attack swimmers"(`r round(lions.lay.eggs[[1,"MAP"]],2)` [`r round(lions.lay.eggs[[1,"cred_lower"]], 2)`,
+`r round(lions.lay.eggs[[1,"cred_upper"]], 2)`, `r round(mosquitos.attack.swimmers[[1,"MAP"]],2)` [`r round(mosquitos.attack.swimmers[[1,"cred_lower"]], 2)`,
+`r round(mosquitos.attack.swimmers[[1,"cred_upper"]], 2)`], respectively), though participants rate the former as completely false (`r round(lions.lay.eggs[[1,"MAP_h"]],2)` [`r round(lions.lay.eggs[[1,"low"]], 2)`,
+`r round(lions.lay.eggs[[1,"high"]], 2)`]) while the latter is kind of true (`r round(mosquitos.attack.swimmers[[1,"MAP_h"]],2)` [`r round(mosquitos.attack.swimmers[[1,"low"]], 2)`,
+`r round(mosquitos.attack.swimmers[[1,"high"]], 2)`]).
+This alternative model is unable to make these fine-grained distinctions because it must use the same semantic threshold in all contexts.
+
+<!-- The model fails to distinguish any of the generic sentences because they are all somewhat true.  -->
+<!-- All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
+-->
+
+<!-- The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent.  -->
+<!-- For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5).  -->
+<!-- For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%). -->
+<!-- Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences.  -->
+<!-- This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
+-->
+<!-- The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data. -->
 
@@
 
-Our underspecified threshold model is the same as the fixed-threshold RSA model described above, except that rather than having a fixed threshold at $\theta = 0$, it has uncertainty over the threshold specified with a uniform prior distribution over $\theta$.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis.
-As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that relies upon an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-
+Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers context-specific $\theta$'s.
+We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
+Thus, this model has two *fewer* parameters than the fixed-threshold model above.
+
+As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
 To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.

### 2017-12-16 paper/comgen-paper.Rmd
clean up generics case study; add new fixed threshold alternative model prose; add data examples to prose

@@
   - \usepackage{subcaption}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
 

### 2017-12-16 paper/case2-habituals.Rmd
tweak habituals figs

@@
 )
-
-figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) %>%
-ggplot(.,
+rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
+          d.hab.priors %>% select(item, category)) 
+figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide,
        aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
@@
 ```
-```{r habituals-items-table}
+
+```{r habituals-items-table, eval = F}
 d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()
@@
 d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
-  kable(.) %>% #, format = "latex", longtable = T, booktabs = T, caption = "a caption") %>% 
+  kable(., 
+        format = "latex", longtable = T, booktabs = T,
+        caption = "Demo table") %>% 
+  kable_styling(latex_options = c("repeat_header"),
+                font_size = 7)#%>%#, "hold_position")) %>%
   #column_spec(3, width = "10cm")%>%
-  collapse_rows(columns = 1:2)
+  #collapse_rows(columns = 1:2)
 ```
@@
                       labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
+                                 "Past-frequency endorsement model",
+                                 "Predictive-frequency endorsement model"
 
                                  ))) %>%
-  filter(src == "Speaker model - past frequency") %>%
+  filter(src == "Past-frequency endorsement model") %>%
   ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
@@
                       labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
+                                 "Past-frequency endorsement model",
+                                 "Predictive-frequency endorsement model"
 
                                  ))) %>%
-  filter(src == "Speaker model - predictive frequency") %>%
+  #filter(src == "Predictive-frequency endorsement model") %>%
   ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
@@
   coord_fixed()+
-  xlab("Model prediction")+
+  xlab("\n Model prediction")+
   ylab("Human habitual endorsement")+
@@
                       labels = c(
-                                 "Speaker model - past frequency",
-                                 "Speaker model - predictive frequency"
+                                 "Endorsement model (past frequency)",
+                                 "Endorsement model (predictive frequency)"
 
                                  ))) %>%
-  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
+  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
 ```
@@
 Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
+Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 13, fig.height = 3.5, cache=F}
 legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
@@
 
-grid.arrange(
-  arrangeGrob(
-    fig.hab.freq.predictive.vs.past, 
-    fig.hab.endorse.vs.predfreq, 
-    habituals.predictive.past.model, 
-    habituals.predictive.predictive.model + theme(legend.position="none"),
-    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
-legend_b, nrow=2,heights=c(8, 1))
-
-#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')
-
-#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
+plot_grid(
+  fig.hab.freq.predictive.vs.past + 
+    theme(plot.margin = unit(c(6,3,6,6), "pt")),
+fig.hab.endorse.vs.predfreq + 
+  theme(plot.margin = unit(c(6,0,6,6), "pt")),
+# habituals.predictive.past.model + 
+#   theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab(""),
+habituals.predictive.predictive.model + 
+  theme(plot.margin = unit(c(0,0,6,0), "pt")) + 
+  theme(legend.position="none") + ylab(""),
+align = 'h', 
+labels = c("A","B","C"),
+hjust = -1, nrow =1 , rel_widths = c(1.2, 0.95, 1.6))
 ```

### 2017-12-16 paper/case3-causals.Rmd
tweak causal figs

@@
                   utt = "generic")
- l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
+ l0.rs <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+  l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+ l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
  cas.listener.predictions <- bind_rows(
    cas.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
+      l0.rs.prior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Prior"),
+    l0.rs.posterior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Posterior")
    )

### 2017-12-17 paper/case1-generics.Rmd
edit generic discussion

@@
 Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and have been shown to have deep implications for wide ranging phenomena from stereotype propogataion [@Rhodes2012] to motivation [@Cimpian2007].
-Heretofore, no formal model has made precise, quantitative predictions about the flexible endorsement patterns of generics (*Birds lay eggs* v. *are female*; *Mosquitos carry malaria*).
-
-By measuring listeners' prior beliefs about the probability of the property across kinds and the feature-probability of the referent kind (e.g., the percentage of birds that lay eggs), we were able to show how a semantics based on probability is tenable in spite of alleged counterexamples.
-The key theoretical insight is that the threshold must be *underspecified* in the semantics and determined in context.
-The decision of whether or not to endorse the generic comes down to whether or not the generic would make the interpretation belief distribution more in line with the feature-probability that the endorser had in mind.
-
-In explaining the variable endorsements of generics, we measured the prior distribution over the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
-Thus, we have shown how these measurements are related to generic endorsement via our model. 
-In our second case study, we extend the theory to the domain of events and provide the first evidence that the factors identified by our theory are causally related to endorsement. 
+Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propogation [@Rhodes2012] to motivation [@Cimpian2007].
+Heretofore, however, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations, knowing when they are true and false.
+Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs.
+
+We have demonstrated that a semantics based on the probability of the feature is tenable in spite of alleged counterexamples.
+The key theoretical insight is that the truth-functional semantics is *underspecified* yet still is able to formalize, using recent developments in probabilistic modeling.
+Our model provides a clean delineation of world knowledge (formalized as a prior distribution) from the semantics of generalizations. 
+We return to this point, and its implications for theory-building, in the general discussion.
+
+<!-- The decision of whether or not to endorse the generic comes down to whether or not the generic would make the interpretation belief distribution more in line with the feature-probability that the endorser had in mind.
+-->
+
+In explaining the variable endorsements of generics, we related the referent-category feature-probability (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via the feature-probability priors (e.g., the percentage of different kinds of animals that lay eggs).
+In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs.
+"...
+are female".
+To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent feature-probability and the feature-probability priors), which people have access to via their mental representations of the category.
+We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent feature-probabilities (Case 2) and feature-probabilitiy priors (Case 3).
+In addition, we take this opportunty to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.
+
+<!-- With a tenable quantitative theory in hand,  -->
+
+<!-- In our second case study, we provide a stricter test of the quantitative precision of our theory and  -->
+
+<!-- the probabilities of features across categories in addition to the probability of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
+-->
+<!-- Thus, we have shown how these measurements are related to generic endorsement via our model.  -->
+<!-- In our second case study, we extend the theory to the domain of events and provide the first evidence that the factors identified by our theory are causally related to endorsement.  -->
 <!-- This evidence is correlational in nature, however. -->

### 2017-12-18 paper/case2-habituals.Rmd
edits throughout habituals, refactor main habituals figure

@@
 
-Segmenting the continuous stream of reality into events is a crucial task for cognition.
-Once individuated, an event can be categorized as a kind of a event.
-For example, the event of Mary smoking at 2:30pm on January the 24th is an instance of *Mary smoking*. 
-Generalizations can be said of this event, in the form of *habitual language*: "Mary smokes".
+The event of Mary smoking at 2:30pm on January the 24th is an instance of a kind of event: *Mary smoking*. 
+Just as with categories, generalization can occur over events of a particular type.
+When expressed in language, these generalizations take the form of *habitual language*: "Mary smokes".
 
@@
 In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes.").
-Habituals about people doing actions are interesting because a 
-Learning about the behaviors of others is useful because it tells us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
-When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-ti8me at the restaurant"; @McGuire1986].
+Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
+When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
 Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
@@
 To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
-First, we measure the prior distribution over the frequencies for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
+First, we measure the prevalence prior distribution for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
 We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt.
@@
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-By describing novel characters to participants, we are able to directly the manipulate the frequency (feature-probability) with which the referent does the action.
+By describing novel characters to participants, we are able to directly the manipulate the frequency (prevalence) with which the referent does the action.
 <!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
-Our computational model predicts endorsement rates given a referent-category feature-probability $h$. 
-Does $h$ represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
+Our computational model predicts endorsement rates given a referent-prevalence $h$. 
+Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
 We extend our theory by measuring participants' predictions about future frequencies and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
@@
 
-## Experiment 2a: Measuring the feature-probability prior for events
-
-In this experiment we elicit the prior distributions over frequencies $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (measured in Expt.
-2b \& 2c).
-For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the likely frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
-We designed our elicitation task to take advantage of the mixture-model representation of the feature-probability prior used in Expt.
-1 (namely: that the distribution over a feature-probability can be represented as a mixture of probabilities from those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
+## Experiment 2a: Measuring the prevalence prior for events
+
+In this experiment we elicit the prior distributions over frequencies for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2c).
+For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the  frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
+We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt.
+1 (namely: that the distribution over prevalence can be represented as a mixture of those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
 For background knowledge of people doing actions, we consider again two components^[
@@
 In total, thirty-one events were used.
-For a full list the stimulus set, see Table \mht{make table of stimuli}.
+For a full list the stimulus set, see \mht{Appendix}.
 
@@
 
-For example, one set of prompts read: *How many women have smoked cigarettes before?*; *For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?*
-The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials, and tested for recall on a subsequent trial.
-<!-- After reading the instructions, participants were asked to recall the two types of questions. -->
+For example, one set of prompts read: "How many women have smoked cigarettes before?"; "For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?"
+The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials and tested for recall on a subsequent trial.
 They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-<!-- They did this to test their understanding and attention for each of the two questions. -->
 For the experimental trials, we anticipated there to be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
 Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-
-<!-- The experiment began by having participants input the names of eight friends, family members, or people they knew well that they could answer some questions about. -->
-<!-- Participants were told that these names would only be used to assist them in reasoning through the second part of the experiment.  -->
-
-<!-- In the second phase of the experiment, participants were asked: "For each of the following people, how often does he or she \textsc{do action}?" -->
-<!-- Participants had to fill in the blanks in sentences of the form: "\text{friend does action} ___ times per ___". -->
-<!-- The first blank was a text box where participants could enter a number. -->
-<!-- The second blank was a drop-down menu where participants could select a time interval from the following options: \{week, 2 weeks, month, 2 months, 6 months, year, 2 years, 5 years\} -->
-<!-- They completed this task for each of their eight listed friends or family members. -->
-<!-- To make the task slightly less tedious, there was an option where participants could set the time window for all eight of their responses. -->
-
-<!-- In order to get sufficient data for actions that are relatively uncommon (e.g., *climbs mountains*, *writes novels*), if participants responded that all of their friends do the action with a frequency of "0 times" (in some interval), a follow-up question appeared that read: "Do you know anybody who has \textsc{done action} before?".
--->
-<!-- If they responded "Yes", another follow-up question appeared that read: "How often do you think that person \textsc{does action}?", with the same dependent measure format as before. -->
-
-<!-- Participants completed these elicitation trials for a random subset of 15 items, presented in a randomized order. -->
-<!-- The experiment can be viewed at \url{http://stanford.edu/~mtessler/generics-paper/experiments/habituals/priors/friends-and-family-1.html} -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
-<!--   \caption{ -->
-<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
-<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
-<!--   Actual frequency noted on x-axis for examples (left). -->
-<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
-<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
-<!--   } -->
-<!--   \label{fig:tjScatters} -->
-<!-- \end{figure*} -->
-
-<!-- #### Data preprocessing -->
 
@@
 
-### Results
+### Data analysis and results
 
@@
 
-To generate feature-probability prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
+To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
 The only difference is that we estimate the mixture component directly from responses to Question 1. 
 We assume that those who have not done the action before will probably not do the action in the future. 
-With these assumptions, the feature-probability distribution is given by:
+With these assumptions, the prevalence distribution is given by:
 
@@
 
-## Experiment 2b: Habitual endorsements
-
-In this experiment, we elicit human endorsements for generalizations about events (*habituals*) while manipulating the frequency with which the target event occurs.
-
-### Method
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Materials
-
-Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
-The frequencies were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
-For example, relatively high frequencies were chosen \mht{(e.g., 3 times every week vs.
-2 weeks vs.
-month)} for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen \mht{(e.g., )}.
-In total, \mht{93} unique items were created by pairing frequencies with events.
-
-#### Procedure
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, "In the past month, Bill smoked cigarettes 3 times".
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
-These were used for an exploratory analysis on differences in endorsements by gender of the target character.
-
-<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
-
-### Results
-
-<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
--->
-<!-- Several features in our data argue against this hypothesis. -->
-<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
--->
-
-Habitual sentences were endorsed for a wide range of frequencies.
-When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
-When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
-This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
-Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
-We now turn to our model-based analyses.
-For all analyses, we collapse across gender of the referent character,
-
-### Endorsement model comparison
-
 ```{r habituals-prior-mixture-summarize}
@@
 
+## Experiment 2b: Habitual endorsements
+
+In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigaerettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).
+
+### Method
 ```{r habituals-endorsement}
@@
 
+#### Participants
+
+We recruited 150 participants from MTurk.
+To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
+This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
+The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
+
+#### Materials
+
+Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
+Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
+\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
+For example, relatively high frequencies were chosen (e.g., three times every week vs.
+2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs.
+2 years).
+In total, `r nrow(d.hab.endorsement %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.
+
+#### Procedure
+
+On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
+For example, "In the past month, Bill smoked cigarettes 3 times".
+Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
+Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
+Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
+These were used for an exploratory analysis on differences in endorsements by gender of the target character.
+
+<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
+
+### Results
+
+<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
+-->
+<!-- Several features in our data argue against this hypothesis. -->
+<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
+-->
+
+Habitual sentences were endorsed for a wide range of frequencies.
+When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
+When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
+
+In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
+This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
+Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
+We now turn to our model-based analyses.
+For all analyses, we collapse across gender of the referent character,
+
+### Endorsement model comparison
+
 ```{r habituals-items-table, eval = F}
@@
 
-```{r habituals-fullmodel}
+```{r habituals-fullmodel, fig.width = 8}
 n_chains <- 3
@@
 #  m.hab.fixed.samp <- data.frame()
-
-for (i in seq(1, n_chains)){
-  # mi <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "smtncs_habitual-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-
+# 
+# for (i in seq(1, n_chains)){
+#   # mi <- fread(paste(project.path,  "models/habituals/results/",
+#   #                   model_prefix, "smtncs_habitual-",
+#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
+# 
+#   # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
+#   #                   model_prefix, "smtncs_some-",
+#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
 #   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "smtncs_some-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-  #                         "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
-  # 
-  #m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-}
+#                           "results-habituals-jointModel-inferFixedThresholdCts-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
+#   #
+#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
+# }
 
@@
 # save(m.hab.fixed.samp,
-#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
 
@@
 #                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-load(paste(project.path,  
-           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+# load(paste(project.path,  
+#            "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
 
@@
             cred_lower = hdi_lower(val))
-
+fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
+fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
 m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
@@
 
-habituals.endorsement.models <- bind_rows(
+md.hab <- bind_rows(
   d.hab.endorse.regression,
@@
   )
+)
+
+# %>%
+#   mutate(src = factor(src, levels = c( 
+#                                       "some_model",
+#                                       "habituals_model",
+#                                       "regression_freq", 
+#                                       "regression_freq_distinct"
+#                                      ),
+#                       labels = c(
+#                                  "Fixed semantics model",
+#                                  "Uncertain semantics model",
+#                                  "Referent frequency alone", 
+#                                  "Distinctiveness + referent frequency"
+#                                  )))
+
+example.habituals.actions <- separate(data.frame(example.habituals), 
+                                      example.habituals, 
+                                      into=c("action", "time_period"), sep = "_")$action
+
+example.habituals <- c( 
+                       #"wears a watch", "wears socks", 
+                       "writes poems", "writes novels",
+                      "goes to the movies", "watches space launches",
+                      "smokes cigarettes","drinks coffee",
+                       "climbs mountains","hikes", "runs"
+                       )
+
+md.hab.long <- bind_rows(
+  md.hab %>% 
+    #filter(habitual %in% example.habituals.actions) %>% 
+    filter(habitual %in% example.habituals) %>% 
+    select(-low, -high, -MAP_h, -mean, -k, -n, -a, -b),
+  md.hab %>%
+      filter(habitual %in% example.habituals) %>% 
+      select(-mean, -k, -n, -a, -b, -prediction, -prediction_lower, -prediction_upper) %>%
+      rename(prediction = MAP_h, prediction_lower = low, prediction_upper = high) %>%
+      mutate(src = 'data')  
 ) %>%
-  mutate(src = factor(src, levels = c( 
+  mutate(time_period = factor(time_period, levels = c("5 years", "2 years", "year",
+                                                      "6 months", 
+                                                      "2 months", "month", 
+                                                      "2 weeks", 
+                                                      "week")),
+         habitual = factor(habitual, levels = example.habituals
+                           #c("runs", "hikes", "climbs mountains", "goes to the movies",
+                           #                     "smokes cigarettes")
+                           ),
+         src = factor(src, levels = c("data",
+                                      "regression_freq", 
+                                      "regression_freq_distinct",
                                       "some_model",
-                                      "habituals_model",
+                                      "habituals_model"
+                                     ),
+                      labels = c("Human data",
+                                 "Referent frequency", 
+                                 "Distinctiveness +\n referent frequency",
+                                 "Fixed semantics",
+                                 "Uncertain semantics"
+                                 )))
+
+habituals.endorsement.bars <- ggplot(md.hab.long, aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
+                  x = time_period, fill = logAnnualRate))+
+  #geom_abline(intercept = 0, slope = 1, lty = 3)+
+  #geom_linerange(alpha = 0.15)+
+  geom_col(position = position_dodge(), color = 'black', width = 0.7)+
+  geom_errorbar(alpha = 0.7, width = 0.3)+
+  #geom_point(shape = 21, size = 3)+
+  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  ylab("Habitual endorsement")+
+  xlab("Frequency")+
+  facet_grid(src~habitual, scales = 'free')+
+  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
+        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45),
+        legend.position = "bottom") +
+   guides(fill = F)
+##habituals.endorsement.bar
+#fixed.hab.params.posterior
+```
+
+```{r habitual-endorsment-scatters}
+#View(md.hab)
+
+habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
                                       "regression_freq", 
-                                      "regression_freq_distinct"
+                                      "regression_freq_distinct",
+                                      "some_model",
+                                      "habituals_model"
                                      ),
                       labels = c(
-                                 "Fixed semantics model",
-                                 "Uncertain semantics model",
-                                 "Referent frequency alone", "Distinctiveness + referent frequency"
-                                 ))) %>%
+                                 "Referent frequency", 
+                                 "Distinctiveness + \n referent frequency",
+                                 "Fixed semantics",
+                                 "Uncertain semantics"
+                                 ) )) %>%
 ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
@@
   xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 2)+
-  theme(legend.position = "bottom")+
-  guides(fill = F)
+  ylab("Human endorsement")+
+  facet_wrap(~src, nrow = 1, strip.position = "top")+
+  guides(fill = guide_colorbar(title = 'log annual rate',
+                               ticks = F,
+                               title.position="top"))+ 
+  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
+        legend.direction = 'horizontal',
+        #legend.position = c(0.025,0.975),
+        #legend.position =c(1,1),
+        legend.justification = c(1,1)
+        )
+#habituals.endorsement.models
 ```
@@
                                                   ),
-                            labels = c("Listener Prior (Posterior given Silence)",
-                                       "Listener Posterior given Habitual")),
-         action = fct_relevel(action,
-                                "climbs mountains", "hikes", "runs",
-                              "goes to the movies", "smokes cigarettes"
-                              ) ) %>%
+                            labels = c("Prevalence Prior",
+                                       "Posterior given Habitual")),
+         action = factor(action, levels = example.habituals)
+                                #"climbs mountains", "hikes", "runs",
+                              #"goes to the movies", "smokes cigarettes"
+                              ) %>%
   ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
+  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
   facet_wrap(~action, nrow = 1)+
@@
   ylab("Scaled probability density")+
-  theme(legend.position = "bottom", legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
+  theme(#legend.position = "bottom", 
+        legend.title = element_blank(),
+        axis.text.x = element_text(angle = 90, vjust = 1),
+        axis.title.y = element_text(hjust = 1))+
       scale_x_continuous(limits = c(-5, 8), 
@@
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-```
-
-```{r habituals-endorsement-figure, fig.width=11, fig.height=9, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right).
-Bottom: Five example frequency priors and listener posteriors upon hearing the generalization.
+```
+
+```{r habituals-endorsement-figure, fig.width = 16, fig.height = 12.5, fig.cap="Endorsing generalizations about events.
+A: Endorsements for nine events given different frequencies of action by human participants and four models.
+B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
+Top right: Model fits for all ninety-three habitual sentences by each model.
+C: Nine example frequency priors and posteriors upon hearing the generalization.
 These distributions are inferred using both data sources from Expts.
-2a & 2b.
-(analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})", cache = F}
-grid.arrange(fig.habituals.endorsement.vs.freq, 
-             habituals.endorsement.models,
-             habituals.endorsement.insets, ncol = 2,
-             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
+2a & 2b.", cache = F}
+
+hab.legend <- get_legend(habituals.endorsement.models)
+fig.hab.endorse.bars <- habituals.endorsement.bars +
+  theme(plot.margin = unit(c(6,0,6,0), "pt")) #+ ggtitle("prevalence priors")
+fig.hab.endorse.scatters <- habituals.endorsement.models +
+  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
+fig.hab.endorse.priors <- habituals.endorsement.insets +
+  theme(plot.margin = unit(c(18,2,6,6), "pt"))
+
+#+ 
+    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
+#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
+
+# fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
+#                                      fig.gen.endorse.models, 
+#                                     # align = 'v',
+#                                     #  axis = 'l',
+#                                     labels = c("A", "B"),
+#                                     rel_widths = c(0.9, 1))
+
+#fig.hab.toprow <- 
+  plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters,
+                            # plot_grid(fig.hab.endorse.scatters,hab.legend, nrow = 1, rel_widths = c(0.6,4),
+                            #                                 axis = 't', align = 'h'),
+                            fig.hab.endorse.priors,
+                            labels = c("A", "B", "C"), nrow = 3,
+                            axis = 'lr', 
+                        align = 'v', 
+                            rel_heights = c(3.1, 1.4, 1.2))
+
+# plot_grid(fig.hab.toprow,
+#           fig.hab.endorse.priors,
+#           labels = c("", "C"), nrow = 2, rel_heights = c(3, 1.3)
+#           )
+
+#plot_grid( prow, legend, rel_widths = c(3, .3))
+
+# grid.arrange(fig.habituals.endorsement.vs.freq, 
+#              habituals.endorsement.models,
+#              habituals.endorsement.insets, ncol = 2,
+#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
 ```
@@
 <!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model to better understand the data and the contribution of our model.
+Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model to better understand the data and the contribution of our model.
 
@@
 
-Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
+To understand the role of frequency in habitual endorsement, we use the frequency supplied to the participants in our experiment as a predictor in a linear model. 
+This model predicts the same endorsement level for two actions done with the same frequency. 
+Obvious counterexamples exist in our data set:
+While participants are willing to endorse that a person "...
+climbs mountains" having done it 3 times in the past *year*, they are less willing to say that a person "...
+hikes" and not willing to say that a person "...
+runs"  (Figure \@ref(fig:habituals-endorsement-figure) A).
+Overall, the referent-frequency (log-frequency of action) predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$).
 In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$).
-An account purely based on the referent frequency does not explain endorsements in this data set.
-Instead, we pursue an explanation where prior beliefs interact with an underspecified literal semantics to produce the pattern of habitual endorsement observed.
+The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because of the larger stimulus set and presence of multiple referent-frequencies per item.
+<!-- An account purely based on the referent frequency does not explain endorsements in this data set. -->
+<!-- Instead, we pursue an explanation where prior beliefs interact with an underspecified literal semantics to produce the pattern of habitual endorsement observed. -->
 
@@
 
-In our empirically elicited priors, items differ in their mixture parameter reflecting the proportion of people who have done the action before (Figure \@ref(fig:habituals-prior-figure)).
-This could be seen as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
-A plausible alternative hypothesis is thus that some simple combination of frequency and distinctiveness information predicts habitual endorsements. 
-Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency to predict habitual endorsement.
+In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)).
+This parameter can be viewed as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
+We again construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
+We use participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency given to participants to predict habitual endorsement.
 
@@
 
-We find that this model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-Actions that are more rare across people (e.g., writing novels) are endorsed more overall. 
-Still, this model is not able to capture fine-grained details in endorsments.
-For example, going to the movies is relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-On the other hand, playing the banjo three times in the past two years is not very strong evidence for the habitual, according to participants $`r banjo.2years.data`$.
+This model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
+It can differentiate events done with the same frequency (e.g., *writing poems* vs. *novels*, 3 times in the past 5 years), and increase endorsement of the more rare action (*novels*). 
+Still, this model fails to capture fine-grained details in endorsment.
+For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
+On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants $`r banjo.2years.data`$.
 Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
@@
 We next examine an endorsement model based on a fixed-threshold semantics.
-A fixed-threshold model only conveys that a person *has done this action before*, analagous to how the quantifier "some" conveys that there exists at least one entity with the feature.
-As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to simultaneously predict both the priors data and the endorsement data.
-We assume the referent feature-probability $h'$ being conveyed by $Endorse$ (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
+A fixed-threshold model commits the habitual to conveying that a person *does the action with some frequency*, and that frequency is common to all actions.
+As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data.
 Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$.
+We assume the referent-prevalence $h'$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
+Additionally, to account for statements that would be literally false under this model (frequencies that fall below the fixed threshold), we include an additional noise parameter, as we did in Case Study 1.
 To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 3 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
 
-<!-- The above regression models are too rigid to explain the flexibility in habitual endorsements.  -->
-<!-- Our probabilistic RSA model has more flexibility than these models because of the introduction of prior knowledge.  -->
-<!-- Additionally, our theory posits that the flexibility in endorsements comes from an interaction of the prior knowledge with an uncertain threshold. -->
-<!-- To isolate the contribution of this interaction (prior knowledge with an uncertain threshold), we first show the predictions of a model that lacks the uncertainty over the threshold (i.e., it has a fixed threshold).
--->
-
-<!-- The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}.  -->
-<!-- As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt.
-2b.
--->
-<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->
-
-An endorsement model with fixed-threshold semantics has trouble differentiating between different habitual statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet), as all of the items used in our experiment are literally true under a fixed-threshold semantics.
-In addition, the model exhibits a small dynamic range of endorsment, because the two options for the endorsement model (silence or a very low, fixed thresold) are only subtly different with respect to information conveyed.
-Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
-With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
-Thus, this model makes the same predictions for different target frequencies in the same event.
-For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month. 
-Overall, this model is poor at predicting the range of endorsement data ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
+```{r hab-fixed-parameters}
+
+```
+
+```{r hab-fixed-threshold-examples, eval =F}
+```
+
+The fixed-threshold model is ill-defined for this data set.
+The data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
+`r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise.
+The inferred (fixed) threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
+`r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`]. 
+That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise. 
+Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[
+  An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some"). 
+  This model would explain even less data than the current model (if it was better, this situation would have been inferred).
+  That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
+]
+
+<!-- The lowest frequency used in our data set was $0.2$ times per year.  -->
+<!-- Thus, all of the utterances evaluated under a fixed-threshold model were literally true.  -->
+
+<!-- statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet). -->
+<!-- The model exhibits a small dynamic range of endorsement, because the two options for the endorsement model (silence or a very low, fixed thresold) are only slightly different with respect to information conveyed to the interpreter.
+-->
+<!-- Another shortcoming of this fixed threshold is illuminated by our manipulation of referent-frequency. -->
+<!-- With a fixed threshold, the difference between the interpreter's prior and posterior distribution is  (whatever is below the threshold).  -->
+
+<!-- Thus, this model makes the same predictions for different target frequencies in the same event. -->
+<!-- For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.  -->
 
@@
 We used the same data analytic approach for the uncertain threshold endorsement model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
+Again, this model has two fewer parameters than the fixed-threshold model (no threshold parameter and no extrinsic noise process).
 As shown in Figure \@ref(fig:habituals-endorsement-figure) (top right: top right facet), the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-Figure \@ref(fig:habituals-endorsement-figure) (bottom, insets) provides insight into how the model is able to do this. 
+Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model is able to do this. 
 An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is good statement to assert. 
@@
 
-Habitual sentence endorsement exhibits context-sensitivity directly parallel to that of generic sentences (Case Study 1).
+Habitual language exhibits context-sensitivity directly parallel to that of generic language (Case Study 1).
 Habituals are endorsed for a wide range of frequencies, but show systematic patterns relative to the prior distribution of frequencies, as formalized by the uncertain-threshold model.
@@
 In this case study, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model. 
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question.
-
-In Expt. 2b, participants were given a statement about how often a person has done the action in the past and asked to judge the correspoding habitual statement.
-This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-In Expt. 2c, we investigate this question by manipulating and measuring *predictive frequency* and habitual endorsement, while keeping fixed past frequency.
+By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model (and in a way that a fixed-threshold model cannot account for).
+The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in the question.
+
+In Expt. 2b, participants were given a statement about how often a person has done the action in the past and asked to judge the corresponding habitual statement.
+This design potentially confounds an important distinction for the language of generalization: Does the prevalence communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
+In Expt. 2c, we investigate this question by manipulating and measuring *predictive frequency* and habitual endorsement, while keeping past frequency fixed.
 
@@
 
-## Experiment 2c: Observations vs. Predictions
+## Experiment 2c: What is prevalence?
 
@@
 Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only *truly be certain* about what has happened in the past.
+On one hand, speakers can only be certain about what has happened in the past.
 On the other hand, language has a communicative function, and it would seem useful for speakers to convey their predictions of what will be the case in the future.
@@
   xlab("Predicted frequency (log scale)")+
-  ylab("Human habitual endorsement")+
+  ylab("Human endorsement")+
   scale_x_continuous(limits = c(-4.2,7.2), 
@@
   ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
+                  y = MAP_h, ymin = low, ymax = high, fill = condition,
+                  shape = condition))+
   geom_abline(intercept = 0, slope = 1, lty = 3)+
@@
   geom_errorbarh(alpha = 0.7)+
-  geom_point(shape = 21, size = 4)+
+  geom_point(size = 4)+
+  scale_shape_manual(values=c(21,22,23,24))+
   scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
@@
   ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
+                  y = MAP_h, ymin = low, ymax = high, fill = condition, shape = condition))+
   geom_abline(intercept = 0, slope = 1, lty = 3)+
@@
 plot_grid(
+  plot_grid(
     fig.hab.freq.predictive.vs.past + 
@@
     theme(legend.position="none") + ylab(""),
-align = 'h', 
+  align = 'h', axis = 'l',
   labels = c("A","B","C"),
-hjust = -1, nrow =1 , rel_widths = c(1.2, 0.95, 1.6))
+  #hjust = -1,
+  nrow =1 , rel_widths = c(1.2, 0.95, 1.6)),
+  legend_b, nrow = 2, rel_heights = c(1, 0.2))
+
+  #legend_b
 ```
@@
 The events used were a subset of those used in Expts. 2a \& b (21 of the original 31).
-In addition, in order to increase the variability of responses across the experimental conditions, participants only saw the frequencies that led to the most intermediate endorsement of the habitual in Expt.
+In addition, we crafted statements that were intended to either increase the frequency (*enabling*; e.g., "Yesterday, Bill bought a pack of cigarettes.") or decrease the frequency (*preventative*; "Yesterday, Bill quit smoking.") of the event in the future.
+In order to increase the potential variability of responses across the experimental conditions, participants only saw the frequencies that led to the most intermediate endorsement of the habitual in Expt.
 2b.
 We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-In addition, we crafted statements that were intended to either increase the frequency (*enabling*; e.g., "Yesterday, Bill bought a pack of cigarettes.") or decrease the frequency (*preventative*; "Yesterday, Bill quit smoking.") of the event in the future.
 See Table \mht{one table for Expt 2 stimuli} for a full list of the enabling and preventative information.
@@
 
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials.
+The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials (*preventative* and *enabling* trials).
 On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
@@
 
-In the *predictive frequency* condition, participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{event}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
+In the *predictive frequency* condition, participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{action}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
 In the *sentence endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
@@
 Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency (e.g., participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month).
-This means that our model makes identical predictions for Expt.
+We observe in the baseline condition that future frequency perfectly tracks past frequency. 
+That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
+This result implies that our model makes identical predictions for Expt.
 2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information appreciably decreasing and the enabling information slightly increasing predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
+Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
 
@@
 
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure} B; green points).
+There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}B; green points).
 Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-
 When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
@@
 
-We use our formal model to test whether past or predictive frequency is what is being communicated by these statements.
-To formalize the predictive frequency speaker model, we use the mran predictive frequency data (Expt. 2c) as the $h$ that the speaker model $S$ (Eq. \ref{eq:S1}) is aiming to communicate. 
-The past frequency model is constructed using the past frequency supplied to participants as the $h$ that the speaker $S$ model is trying to communicate.
-
+<!-- Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points). -->
+<!-- This may be due, in part, to an effect of the experimental context on participants: -->
+<!-- in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
+2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
+-->
+<!-- Future investigation into this issue is warranted. -->
+
+We use our formal model to test whether past or predictive frequency matters for endorsement.
+To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $h'$ that the endorsement model (Eq. \ref{eq:S1}) conditions on. 
+The past frequency model is constructed using the past frequency supplied to participants as the referent-prevalence.
 We analyze this model in the same Bayesian data analysis regime as for our previous models.
 We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure} (bottom, left and right) shows the resulting model predictions for the past frequency and the predictive frequency speaker models. 
-Participants judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the speaker model using the predictive frequency as input ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
+Figure \ref{fig:habituals-predictive-figure}C shows the resulting model predictions for the past frequency and the predictive frequency endorsement models. 
+Participants' judgments of the habitual statements was indeed influenced by the causal manipulations *in the way predicted* by the endorsement model that uses the predictive frequency as the object of communication ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
 The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
@@
 
-Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points).
-This may be due, in part, to an effect of the experimental context on participants:
-in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
-Future investigation into this issue is warranted.
-
 ## Discussion
 
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the action (measured in Expt.
+Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt.
 2a).
@@
 In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
-By manipulating (rather than measuring) the target frequency with which a person does an action, we showed how alternative models were insufficient to account for this gradience.
+By manipulating (rather than measuring) the referent frequency with which a person does an action, we showed how alternative models were insufficient to account for the gradience in endorsement.
 In particular, a fixed threshold model that has access to the same prior knowledge and uses the same information-theoretic decision rule as our uncertain-threshold model is unable to make different predictions for different frequencies.
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying feature-probability scale by introducing enabling and preventative causal evidence.
+In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing enabling and preventative causal evidence.
 We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
-We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is able to predict the influence of top-down moderators on habitual endorsement.
+We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is able to account for the influence of top-down moderators on habitual endorsement.
 <!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.
@@
 
-In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
+In these experiments, we introduced participants to novel actors and by doing so, were able to directly manipulated the frequency of a person doing the action.
+The kinds of events we used were familiar to participants (e.g., *running*) and so we measured the prevalence priors for those events.
 <!-- Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
 -->
-In our final case study, we extend our theory to communicating generlizations about causal relationships, and experimentally manipulate the feature-probability priors to examine whether or not they are causally related to endorsing generalizations in language.
+In our final case study, we experimentally manipulate the prevalence priors, testing their causal influence over endorsements.
+In addition, we further we extend our theory to the language of causal relationships.
 

### 2017-12-18 paper/comgen-paper.Rmd
revert to using prevalence as the term

@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
+This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **prevalence**.
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
 The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.
+Yet the mathematical description of the inductive inference is always given by the prevalence $h$.
 
@@
 Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
-This kind of background knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
+This kind of background knowledge can be represented formally as a probability distribution over the prevalence $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
 
@@
 <!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
-<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
+<!-- It is conditional on $h$ because the probability of various direct observations depends upon the prevalence that the observer assumes.  -->
 <!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
@@
 -->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs.
+<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the prevalence of barking among dogs.
 -->
@@
 One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlizations would then apply to the *feature-probability* $h$:
+A threshold semantics for the language of generlizations would then apply to the *prevalence* $h$:
 \begin{equation}
@@
 <!-- We emphasize that this account is based on a probability $h$. -->
-<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[ -->
+<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the prevalence $h$.^[ -->
 <!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
@@
 
-Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the feature-probability $h$ according to the truth-functional meaning of the utterance $u$. 
+Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the prevalence $h$ according to the truth-functional meaning of the utterance $u$. 
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
@@
 We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of producition? 
-We formalize this by considering how well the generalization would convey the feature-probability $h$ to the $Interpret$ model (Eq.
-\ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific feature-probability $h'$ that it wants to communicate.
-Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the feature-probability. 
+We formalize this by considering how well the generalization would convey the prevalence $h$ to the $Interpret$ model (Eq.
+\ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $h'$ that it wants to communicate.
+Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
 In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorser's belief distribution:
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a straight-forward mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics based on probability but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
+\ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
+It does this assuming a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
 This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.
@@
 -->
-<!-- Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
+<!-- Because we are interested in determining whether or not *prevalence* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category prevalence* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
 -->
@@
 
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the feature-probability communicated in the category under discussion $h'$ in Eq.
-\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about feature-probabilities $P(h)$ (Eq.
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $h'$ in Eq.
+\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(h)$ (Eq.
 \ref{eq:L0}).
@@
 <!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq.
+\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
 \ref{eq:S1}).
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
+    xlab("Prevalence of the feature in a category") +
     ylab("") +
@@
 p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
+  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
 p2 <- fig.sims.fixed.thresholds +
@@
 #   ylab("Endorsement model prediction")+
-#   xlab("Hypothesized feature-probability")
+#   xlab("Hypothesized prevalence")
 
@@
   guides(fill = F)+
-  ylab("Endorsement")+xlab("Referent feature-probability")+
+  ylab("Endorsement")+xlab("Referent prevalence")+
   theme(strip.text.y = element_text(angle = 0, hjust = 0)
@@
   #ylab("Endorsement model prediction")+
-  #xlab("Hypothesized feature-probability")
+  #xlab("Hypothesized prevalence")
 ```
@@
 ```{r simulations, fig.cap = "Computational model behavior.
-A: Prior distributions over feature-probabilities for 6 example generalizations.
-B: Different fixed thresholds (columns) give rise to different posterior interpretations.
+A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different posterior interpretations.
 C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
-D: Endorsement model predictions, assuming a particular referent feature-probability.
+D: Endorsement model predictions, assuming a particular referent-prevalence.
 Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
 p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
+  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
 p2 <- fig.sims.fixed.thresholds +
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability h") +
-    ylab("Scaled prior probability density") +
+    xlab("Prevalence of feature in a category") +
+    ylab("Scaled probability density") +
   facet_wrap(~PriorShape, scales = 'free')+
@@
 Figure\ \@ref(fig:simulations) (left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property.
-These distributions can be thought of as distributions over categories, displaying only the feature-probability for the property in question.
-For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the feature-probability of \textsc{barks} (top left; solid pink distribution).
-In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the feature-probability distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).
+These distributions can be thought of as distributions over categories, displaying only the prevalence for the property in question.
+For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the prevalence of \textsc{barks} (top left; solid pink distribution).
+In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the prevalence distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).
 
@@
 This gives the literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") given the background knowledge about the property.
-For instance, the interpretation of a generalization about the property \textsc{barks} is that the feature-probability is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
+For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
 This would correspond to a rather strong interpretation (i.e., "Almost all feps bark").
@@
 The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right).
-Given a feature-probability of a referent category $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
+Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
 \ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
-We see the model correctly predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent feature-probabilities varying substantially between these three examples.
-Intruigingly, the model predicts "Robins are female" (which has the same feature-probability as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
+We see the model correctly predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
+Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
 To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) left; blue distributions).
@@
 This can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
-\mht{For further discussion about the behavior of the model, and these six examples, see Appendix?}
-
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(h)$ as well as the feature-probability $h'$ communicated. 
+<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
+
+These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(h)$ as well as the prevalence $h'$ communicated. 
 We chose reasonable, hypothetical values for each of these, and saw that the endorsement model recapitulated standard intuitions about the truth or falsity of classic examples from the generics literature.
 In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measurning and manipulating background knowledge and feature-probability communicated and relate it to human elicited endorsements of generalizations.
+We do this by both measurning and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
 
 <!-- that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics. -->
-<!-- For these simulations, we had specify both the feature-probability priors $P(h)$ and the referent feature-probability $h'$.. -->
+<!-- For these simulations, we had specify both the prevalence priors $P(h)$ and the referent prevalence $h'$.. -->
 <!-- In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes. -->
@@
 <!-- The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior. -->
-<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[ -->
+<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[ -->
 <!-- The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities. -->
-<!-- If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold. -->
-<!-- If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower. -->
+<!-- If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold. -->
+<!-- If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower. -->
 <!-- As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it. -->
@@
 <!-- The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$. -->
-<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
 -->
@@
 <!-- How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"? -->
-<!-- In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
+<!-- In each case, we must consider the prevalence prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
 <!-- For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
@@
 <!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
-We have been able to formalize a unified, core meaning using the underlying scale of *feature-probability*.
+We have been able to formalize a unified, core meaning using the underlying scale of *prevalence*.
 We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
@@
 We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-Finally, we have shown that listeners' prior knowledge about the feature-probability scale is causally related to their endorsement of statements of genericity (Expt. 3).
+Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is causally related to their endorsement of statements of genericity (Expt. 3).
 In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below
@@
 
-Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the feature-probabilities $P(h)$.
-The feature-probability priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
+Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
+The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the feature-probability prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.
+Thus, the prevalence prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.
 
@@
 We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017].
-Even if interlocutors coordinate on a particular comparison class, they may disagree about the feature-probabilities of other *other categories* in the class.
+Even if interlocutors coordinate on a particular comparison class, they may disagree about the prevalences for other *other categories* in the class.
 That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how *other forces* (e.g., plate tectonics) influence the climate or how often other social categories (e.g., neo-nazis) commit acts of terrorism.
@@
 Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud].
-We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the feature-probability.
+We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the prevalence.
 However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD.
@@
 
-Previous psychological and philosophical work on generics has looked beyond feature-probabilities and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
+Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
 Prasada has argued for a distinction between \emph{characteristic} properties (e.g., "Diapers are absorbent") and \emph{statistical} properties (e.g., "Diapers are white").
@@
 
-Our approach makes the strong claim that beliefs about predicted feature-probability are the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding feature-probability distributions.
-Modulations of feature-probability distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different feature-probability priors, even while keeping the comparison class fixed. 
-In Expt. 3 we showed that these feature-probability distributions are causally related to endorsement.
-
-It is natural to ask how feature-probabilities might reflect conceptual knowledge.
-We found that empirical feature-probability distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
+Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
+That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
+Modulations of prevalence distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
+We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
+In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
+
+It is natural to ask how prevalence might reflect conceptual knowledge.
+We found that empirical prevalence distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
 It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
 Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on feature-probability priors.
+Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.
 
@@
 This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-In previous accounts, feature-probability is treated as synonymous with the prevalence or frequency of the feature in the category. 
+In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
 We make the important distinction that probability can be more general than frequency, and in our account, underlies speakers' subjective, predictions about the future and is subject to top-down moderator.
@@
 The uniform prior over the threshold $\theta$ in the truth-functional threshold semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the feature-probability $h$ *itself*:
+Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the prevalence $h$ *itself*:
 
@@
 We expect intuitions about this statement to generalize to other examples expressing an analogous relation (e.g., "Pastas are spaghetti", "Animals are humans").
-We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent feature-probabilty.
+We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent-prevalence.
 Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers].^[
@@
 The relevant aggregations of entities, then, are collection of books, potentially including books of different genres or publication eras among other such sub-categories.
-Then, given that "books" is the superordinate category of "kinds of books", the referent-category feature-probability cannot be different from the mean of the feature-probability prior.
-Finally, given this feature-probability prior and the referent-category feature-probability, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in the a way analogous to "Robins are female".
+Then, given that "books" is the superordinate category of "kinds of books", the referent-category prevalence cannot be different from the mean of the prevalence prior.
+Finally, given this prevalence prior and the referent-prevalence, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in the a way analogous to "Robins are female".
 
@@
 The feature 'is paperback' can only be predicated (in the sense of @Keil1979) of individual books, which are organized into collections (here, by genre).
-The feature-probability prior is constructed by aggregating these collections of books.
-Then the feature-probability of 'is paperbook' for the category of 'books' can never be higher than the mean of the prior distribution.
+The prevalence prior is constructed by aggregating these collections of books.
+Then the prevalence of 'is paperbook' for the category of 'books' can never be higher than the mean of the prior distribution.
 The endorsement model would give this sentence a rating of 0.5, corresponding to neither true nor false."}
@@
 ].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the feature-probability that she believes to be true will be exaggerated in the mind of the listener).
+The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated in the mind of the listener).
 However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective values, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
@@
 He partitions generics into two types: *absolute* and *relative* generics.
-*Absolute generics* use a fixed, 50\% threshold on feature-probability: $P(F\mid K)>0.5$. 
+*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
 Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
@@
 
-We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of feature-probability (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that feature-probability is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$). 
+We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
+His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$). 
 For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
@@
 ]
-However, we note that this mechanism may be implicit in our own theory: the prior distribution over the feature-probability of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
 Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
@@
 We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations.
-Our notion of feature-probability is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
+Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
 
@@
 
-This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-category feature-probability; e.g., "Sharks attack swimmers").
-Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the feature-probability is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
+This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
+Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
 1 for naturalistic cases).
 In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
-3a), we have observed that the prior distribution over the feature-probabilities $P(h)$ change when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the feature-probability priors. 
-Thus, our model would also predict these effects, but by way of the feature-probability priors rather than some direct connection between generics and striking features.
+3a), we have observed that the prior distribution over the prevalence $P(h)$ change when supplied information about the dangerousness of the feature.
+That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors. 
+Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features.
 <!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
@@
 In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
-Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely feature-probabilities within- and across- categories or features.
+Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
 
@@
 
-In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on feature-probabilities $P(h)$.
+In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
 In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).  
 It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the feature-probability across different categories. -->
+<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence across different categories. -->
 <!-- This minimally structured model  -->
@@
 Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which could be differences in the prior distributions on feature-probabilities or the comparison class.
+Disagreements are also predicted when interlocutors fail to share background assumptions, which could be differences in the prior distributions on prevalence or the comparison class.
 Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).

### 2017-12-18 paper/case1-generics.Rmd
switch out for prevalence label in case 1

@@
 "Lions lay eggs.").
-We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high feature-probabilities (Expt.
+We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt.
 1a).
-We examine generics about animal categories in order to reliably measure the prior belief distribution over the feature-probabilities $P(h)$ (Expt. 1b).
+We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(h)$ (Expt. 1b).
 This elicitation procedure includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
@@
   scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'feature probability',
+  guides(fill = guide_colorbar(title = 'Prevalence',
                                ticks = F))+
@@
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
-We next measure the prior distribution over feature-probabilities and articulate a set of formal models that try to predict these endorsement data.
-
-## Experiment 1b: Feature-probability prior elicitation
-
-The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
+We next measure the prevalence prior distribution and articulate a set of formal models that try to predict these endorsement data.
+
+## Experiment 1b: Prevalence prior elicitation
+
+The prevalence prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
 To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
@@
 
-This thought experiment decomposes the feature-probability prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the feature-probability given the kind $P(h \mid k)$.
-We will use this decomposition to measure the feature-probability prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
+This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(h \mid k)$.
+We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
 We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
@@
 This whole procedure was repeated two times (two trials).
-In total, each participant generated ten animal names and reported on the feature-probability of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).
+In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).
 
@@
 The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
-*Being red* exists mostly at extremely low prevalence levels (i.e., 0 feature-probability) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
+*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
 This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.
@@
 ] 
-We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in feature-probability or prevalence values close to or equal to 0.
+We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
 This "null distribution" is potentially present for all features in exactly the same way.
@@
 To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
-<!-- is flexible and can represent different shapes for different properties (e.g., the differences in feature-probability judgments for \textsc{lay eggs} vs. \text{has wings}). -->
+<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
 For more details about model implementation and inference, see Appendix.
@@
 
-The prior distributions over feature-probabilities are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs.
+The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs.
 blue lines).
@@
 The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other feature-probability elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
+Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
 ]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
@@
 <!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full feature-probability prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the feature-probability prior data.
+<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
 -->
-<!-- Indeed, the data strongly suggests the feature-probability prior is structured. -->
+<!-- Indeed, the data strongly suggests the prevalence prior is structured. -->
 
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over feature-probabilities for eight properties.
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties.
 B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution.
@@
     #coord_fixed()+
-    xlab("Feature-probability") +
+    xlab("prevalence") +
     ylab("Cumulative probability density")+
@@
 To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
-As the simplest baseline hypothesis, we first explore how well referent-category feature-probability itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent feature-probability and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent feature-probability, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on feature-probabilities $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category feature-probability (e.g, the prevalence of laying eggs among robins).
+As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
+As a secondary alternative hypothesis, we explore whether referent prevalence and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
+We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.
+
+Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category prevalence (e.g, the prevalence of laying eggs among robins).
 There are several substantive components to this hypothesis: (a) the prior distribution $P(h)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
@@
 
-#### Referent feature-probability
-
-From the feature-probability prior data (Expt.
+#### Referent prevalence
+
+From the prevalence prior data (Expt.
 1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \  \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
-The referent feature-probability baseline is a decent model of these data because our stimulus set includes generics that are true with high feature-probability properties (e.g., *Leopards have spots.*) and generics that are false with low feature-probability properties (e.g., *Leopards have wings.*).
-
-However, large deviations from an account based purely on referent feature-probabilities remain: Generics in which the referent-category has intermediate feature-probabilities (feature-probability quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{feature-probability} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent feature-probability ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
-This includes generics that are judged true with relatively low referent feature-probabilities (e.g., "Mosquitos carry malaria") and false with relatively high referent feature-probabilities (e.g., "Sharks don't eat people").
-
-#### Cue validity and referent feature-probability
+The referent prevalence baseline is a decent model of these data because our stimulus set includes generics that are true with high prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
+
+However, large deviations from an account based purely on referent prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent prevalence ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
+This includes generics that are judged true with relatively low referent prevalence (e.g., "Mosquitos carry malaria") and false with relatively high referent prevalence (e.g., "Sharks don't eat people").
+
+#### Cue validity and referent prevalence
 
@@
 As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* predict generic endorsementse.
-If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
 *Cue validity* thus captures the distinctiveness of the feature for the category. 
@@
 
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and can be derived via Bayes' Rule:
+We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$.
+If there is a finite number of kinds in the prevalence prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the prevalence prior and can be derived via Bayes' Rule:
 $$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured feature-probability priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
+Previous empirical studies of generic language, however, have not measured prevalence priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
 In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
 Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.
+For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *prevalence prior derived cue validity*, see Appendix.
 
@@
 
-A linear model that uses predictors for both referent feature-probability and cue validity does a better job at explaning the endorsement data than just feature-probability alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
+A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
 This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
@@
 "Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
-Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the feature-probability is high (most mosquitos don't carry malaria).
+Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high (most mosquitos don't carry malaria).
 A simple metric like cue validity is too blunt to capture these subtleties.
@@
 \ref{eq:S1}) decides whether or not to assert the generalization to a naive interpretor (Eq.
-\ref{eq:L0}) conditioned on a particular referent-category feature-probability $h'$ (e.g.,  the percentage of robins that lay eggs).
-We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the referent-category feature-probability $h'$ in the endorsement model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
-
-To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category feature-probabilities $h'$, feature-probability priors $P(h)$ (both from Expt.
+\ref{eq:L0}) conditioned on a particular referent-category prevalence $h'$ (e.g.,  the percentage of robins that lay eggs).
+We use the empirically estimated referent-category prevalence (the same as used in the baseline regression model) as the referent-category prevalence $h'$ in the endorsement model.
+The empirically measured priors from Expt. 1b are used as the literal interpreter's prevalence prior $P(h)$.
+
+To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category prevalence $h'$, prevalence priors $P(h)$ (both from Expt.
 1b data), and the endorsement data (Expt.
@@
 To provide the strongest possible test, we make the fixed-threshold a parameter of the data-analytic model, to search for the best possible fixed-threshold. 
-Finally, a fixed-threshold model will have to accomodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent feature-probability is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
+Finally, a fixed-threshold model will have to accomodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent prevalence is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
 Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(h)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
@@
 
-                                 "Feature-probability alone",
-                                 "Cue validity + Feature-probability"
+                                 "Prevalence",
+                                 "Cue validity + Prevalence"
                                  ))) %>%
@@
                                                   "speakerBeliefs"),
-                            labels = c("Feature-probability Prior", 
-                                       "Interpretation given generalization", 
-                                       "Referent feature-probability")),
+                            labels = c("Prevalence Prior", 
+                                       "Prevalence Posterior given generalization", 
+                                       "Referent Prevalence")),
          property = fct_relevel(property,
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Feature-probability") +
+    xlab("Prevalence") +
     ylab("Scaled probability density")+
@@
 Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent feature-probability alone (lower left) and feature-probability + cue validity (lower right).
-Bottom: Five example feature-probability priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent feature-probability.
+Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right).
+Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence.
 These distributions are inferred using all three data sources from Expt.
@@
 fig.gen.endorse.data <- generics.endorsement.spectrum +
-  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ggtitle("Feature-probability priors")
+  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ggtitle("prevalence priors")
 fig.gen.endorse.models <- generics.endorsement.models +
@@
 
-To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
+To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
 The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
@@
 `r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
-Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1b).
-This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).
+This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
 
@@
 <!-- The model fails to distinguish any of the generic sentences because they are all somewhat true.  -->
-<!-- All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
+<!-- All items get endorsed by at least some participants; the model then infers that the referent prevalence $h'$ must be greater than 0\%; but, if the referent prevalence is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.
 -->
@@
 To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent feature-probability*).
+The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent prevalence*).
 The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure).
-It is also the listener $L_0$'s posterior on referent feature-probability upon hearing the silent utterance.
+It is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
 The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
@@
 "Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the feature-probability is more than half.
+"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.
 
@@
 
-<!-- The decision of whether or not to endorse the generic comes down to whether or not the generic would make the interpretation belief distribution more in line with the feature-probability that the endorser had in mind.
+<!-- The decision of whether or not to endorse the generic comes down to whether or not the generic would make the interpretation belief distribution more in line with the prevalence that the endorser had in mind.
 -->
 
-In explaining the variable endorsements of generics, we related the referent-category feature-probability (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via the feature-probability priors (e.g., the percentage of different kinds of animals that lay eggs).
+In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via the prevalence priors (e.g., the percentage of different kinds of animals that lay eggs).
 In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs.
@@
 are female".
-To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent feature-probability and the feature-probability priors), which people have access to via their mental representations of the category.
-We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent feature-probabilities (Case 2) and feature-probabilitiy priors (Case 3).
+To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent prevalence and the prevalence priors), which people have access to via their mental representations of the category.
+We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and feature-probabilitiy priors (Case 3).
 In addition, we take this opportunty to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

### 2017-12-19 paper/comgen-paper.Rmd
edits to model section; draw relationship to cue validity earlier

@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **prevalence**.
+This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **prevalence**.
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
 The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the prevalence $h$.
+Yet the mathematical description of the inductive inference is always given by the probability $p_{fk}$.
 
 How does one acquire such an inductive belief?
-One can observe instances of the category $k$ and note how many of them have $f$.
-These observations can support prediction to new instances by integrating them with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
+Observing instances of the category $k$ and noting how many of them have $f$ can support prediction to new instances when integrated with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
 For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
 Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
-This kind of background knowledge can be represented formally as a probability distribution over the prevalence $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$
+This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$
 
@@
 
+The language of generalization manifests when a property is predicated of a category: "Ks F" (e.g., "Dogs bark", "Staring at the sun makes you go blind"). 
 Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
@@
 One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for the language of generlizations would then apply to the *prevalence* $h$:
-\begin{equation}
-\denote{generalization}(h, \theta) = \{h>\theta\}
-\label{eq:semantics}
-\end{equation}
+A threshold semantics for a generalization about category K with property F would then apply to the *prevalence* $p_{fk}$:
+$\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$
+
 Various attempts of this kind have been made before [e.g., @Cohen1999].
-We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $h$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
-$h$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief (due to background knowledge, see above).
+We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief due to background knowledge.
 
@@
 
-Quantifier statements can be described using a similar threshold semantics: $\denote{some}(x) = \{h > 0\}; \denote{all} = \{h = 1\}$.
-So what threshold should be used for the generalizations? 
-What is $\theta$?
-Unlike quantified language, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we hypothesize that $\theta$ is contextually-determined, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
-
-We formalize this underspecified semantics in a probabilistic model, where the underspecifed threshold $\theta$ is sampled from a uninformed prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013].
-After making explicit the relevant background knowledge $P(h)$, the model becomes:
+Quantifier statements can be described using a similar threshold semantics: $\denote{some \text{ } K \text{ } F}(p_{fk}) = \{p_{fk} > 0\}; \denote{all \text{ } K \text{ } F} = \{p_{fk} = 1\}$.
+So what threshold $\theta$? should be used for the generalizations? 
+Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
+That is, we hypothesize that $\theta$ is in part determined by contextual, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+
+We formalize this underspecified semantics in a probabilistic model, where the underspecifed threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013].
+After making explicit the relevant background knowledge about the property $P(p_f)$, the model becomes:
 
 \begin{eqnarray}
-Interpret(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
+Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{f}, \theta)} \cdot P(p_{f}) \cdot P(\theta)} \label{eq:L0}
 \end{eqnarray}
 
-Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the prevalence $h$ according to the truth-functional meaning of the utterance $u$. 
-Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.
+Equation \ref{eq:L0} ($Lit$) is a literal interpretation model, that updates its beliefs about the prevalence of a feature in the category described $p_{fk}$ according to the truth-functional meaning of the utterance $u_{KF}$.
+Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
 
 \begin{eqnarray}
-\delta_{\denote{u_{gen}}(h, \theta)} &\propto  & \begin{cases}
-1 & \text{if } h > \theta \\
+\delta_{\denote{u_{KF}}(p_{fk}, \theta)} &\propto  & \begin{cases}
+1 & \text{if } p_{fk} > \theta \\
 0 & \text{otherwise}
@@
 
-<!-- Finally, $h$ is sampled from a prior belief distribution $P(h)$, potentially informed by the property in question and discussed further below.  -->
-
 ### Endorsement model
 
-Given the above minimal model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
-We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of producition? 
-We formalize this by considering how well the generalization would convey the prevalence $h$ to the $Interpret$ model (Eq.
-\ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $h'$ that it wants to communicate.
-Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
-In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorser's belief distribution:
-$Endorse(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} Interpret(h, \theta \mid u)} \diff \theta )}$
+Given the minimal model of literal interpretation described above, how do we decide when a statement conveying a generalization is true or not?
+We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of production? 
+We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0})^[
+  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
+  Rather, the endorser may have a distribution over $p_{f}$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
+  In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
+  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}$
   For the empirical case studies described below, these two versions of the model make almost identical predictions.
@@
 \begin{equation} 
-Endorse(u \mid h = h') \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Interpret(h = h', \theta \mid u)  \diff \theta } )}
+S(u \mid p_{fk}) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)  \diff \theta } )}
 \label{eq:S1}
@@
 
-The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$): $Interpret(h = h', \theta \mid u)$.
-$Endorse$ is not interested in communicating $\theta$ (in fact, it does not know $\theta$), and so integrates over the values of $\theta$.
+The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$): $Lit(p_{fk}, \theta \mid u)$.
+$S$ is not interested in communicating $\theta$ (in fact, it does not know $\theta$), and so integrates over the values of $\theta$.
 We assume the decision to endorse is an approximately rational one, with degree of rationality given by $\lambda$.
@@
 We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives: *Endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [cf., @Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$^[
+"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [cf., @Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$^[
   This "null" alternative  to the generalization ("Ks F") can be realized in at least two other ways: the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not F").
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs").
-It does this assuming a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
+\ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $p_{fk}$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{KF} \mid p_{fk})$.
+The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
+\ref{eq:S1}).
 This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.
 
-<!-- Rather, the uncertainty over $\theta$ is resolved *internal* to the cognitive model, by reasoning about the literal semantics and the prior distribution over feature-probabilities $P(h)$. -->
-
-<!-- The endorsement model presented above is a special case of a family of rational models of communication that use an underspecified threshold-meaning for a generalization. -->
-
-<!-- Yet the *simple but underspecified* hypothesis defines a *family* of models (e.g., more levels of recursion: a listener who thinks about a speaker who thinks about a listener). -->
-<!-- The primary theoretical interest of this paper is to outline *a* formal account, rather than discuss possible variations within it.  -->
-<!-- However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
--->
-<!-- We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix. -->
-
-<!-- The null alternative returns a posterior interpretation distribution that is identical with the prior $P(h)$. -->
-
-<!-- Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function.
--->
-<!-- Because we are interested in determining whether or not *prevalence* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category prevalence* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$).
--->
-
-<!-- The utility of an utterance is defined by how well it conveys the speaker's beliefs ($h'$) to a naive listener $Lit$, after integrating out her residual uncertainty about $\theta$. -->
-
-<!-- The literal semantics for the generalization is the threshold function described above; the literal semantics for the option of staying silent carries no informational content:   -->
-
-<!-- \begin{equation}  -->
-<!-- U(u; h') =  \ln{ \int_{\theta} Lit(h = h', \theta \mid u)  \diff \theta } \label{eq:utility} -->
-<!-- \end{equation} -->
-
-We implemented the model in the probabilisitic programming language WebPPL [@dippl].
+### Prevalence priors and referent-prevalence
+
+Our model makes predictions about endorsing generalizations based on two externally-determined model components: The prevalence priors $P(p_f)$ in Eq.
+\ref{eq:L0} and the referent-prevalence $p_{fk}$ in Eqs.
+\ref{eq:S1} and \ref{eq:delta}.
+Referent-prevalence is the probability that an individual $x$ of the referent-category (e.g., "Dogs") will have the feature being predicated of the category (e.g., "...barks").
+We will return and refine this definition in Case Study 2, when considering generalizations about events.
+For now, the referent-prevalence is simply what determines the truth-conditional semantics. 
+Our hypothesis does not provide a mapping from the truth-conditional semantics directly to endorsement judgments, because $\theta$ is underspecified.
+
+The truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
+\ref{eq:L0}) by integrating prior belief about the feature in question---the *prevalence prior* $P(p_f)$---and the uncertain threshold $P(\theta)$ with the truth-functional semantics.
+Again, $P(\theta)$ is set to be a uniform distribution across all contexts, and thus, the generalization could in principle be felicitious with potentially any prevalence. 
+However, what the interpretation model believes *a priori* $P(p_f)$ must be considered before the endorsement model can say whether or not it would endorse the generalization.
+
+Beliefs about properties result from internal conceptual models of the world. 
+These internal models have domain-specific features but should all give to the domain-general currency of probability.
+One way of constructing prior distributions over prevalence, without appealing directly to domain-specific conceptual knowledge, is by considering the prevalence of the feature among different categories.^[
+  An alternative way is to consider the prevalence of different features among the same category. 
+  We return to this point in the general discussion.
+]
+For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0 .
+Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
+Conceptual differences can manifest in these prevalence priors; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+Indeed, previous studies have found cue validity to be highly correlated with endorsing generalizations about categories, or *generic language* [@Khemlani2012].
+Cue validity is defined for a particular category--feature pair, and relates to referent-prevalence by Bayes' Rule:
+$$ P(x \in k \mid x \in f) = \frac{P(x \in f \mid x \in k) \cdot P(x \in k)}{\sum_{k' \in K} P(x \in f \mid x \in k') \cdot P(x\in k')} $$
+In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
+Thus, $P(x \in k) = P(k) = P(p_{fk})$).
+The denominator of the cue validity expression above (the normalizing constant), then, is the expectation (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$.
+This relationship reveals a potential shortcoming of a point estimate like *cue validity*; the prevalence prior potentially encodes structured, conceptual knowledge of the world, which would be lost by reducing it to a single value.
+
+<!-- These distributions can be thought of as distributions over categories, displaying only the prevalence for the property in question. -->
+
+<!-- F(left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property. -->
+<!-- For example,   -->
+
+We implemented the model in the probabilistic programming language WebPPL [@dippl].
 The following simulations were implemented using the R package RWebPPL [@rwebppl] in the RMarkdown document that generated this paper text and figures.
@@
 
-Figure\ \@ref(fig:simulations) (left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property.
-These distributions can be thought of as distributions over categories, displaying only the prevalence for the property in question.
-For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the prevalence of \textsc{barks} (top left; solid pink distribution).
-In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the prevalence distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).
-
 The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}. 
@@
 The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
-For example, "Dogs have four legs" is a good generalization event though, regrettably, not all dogs have four legs.
-However, were the world to function *normally*, then *all* dogs would have four legs (i.e., dogs would not be involved in freak-tractor accidents).
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and tereotyped language (e.g., "Boys are good at math").
+For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
+However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
@@
 
+```{r child = 'appendix-bda.Rmd'}
+```
+
 ```{r child = 'appendix-cueValidity.Rmd'}
@@
 
-```{r child = 'appendix-bda.Rmd'}
-```
-
-```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-```
+# ```{r child = 'appendix-alternativeRSAmodels.Rmd'}
+# ```

### 2017-12-20 paper/appendix-cvDerivation.Rmd
appendix of relationship between cue validity and prevalence prior

# Appendix A: The Relationship between the Prevalence Prior and Cue Validity

Cue validity is defined for a particular category--property pair (e.g., *mosquitos* and *carry malaria*), and relates to referent-prevalence (e.g., how many mosquitos carry malaria) via the prevalence of *carrying malaria* in other categories $k'$ by Bayes' Rule:
$$ p(k \mid f) = \frac{p(f \mid k) \cdot p(k)}{Z} $$
where $Z =  \sum_{k' \in K} p( f \mid k') \cdot p( k')$

The prevalence prior $P(p_f)$ (Eq. \ref{eq:L0}) is a probability distribution over prevalence for different categories $k'$.
For ease of exposition, let $x = p_f = p(f \mid k)$; that is, $P(x) = P(p_f)$.

\underline{Claim:} The normalizing constant for computing cue validity is equal to the expected value of the prevalence prior distribution: $\mathbb{E}[P(x)] = Z$

\underline{Proof:}

By the definition of the expectation of a distribution:

\begin{eqnarray} \label{eq:expectation}
\mathbb{E}[P(x)] & = & \sum\limits_{x} x \cdot p(x) 
\end{eqnarray}

The probability of a prevalence $x$ can be decomposed into the prior probability of a category $k$ and the likelihood of the prevalence $x$ given that category $k$: $p(x) = p(x \mid k) \cdot p(k)$. 
We assume here, without loss of generality, that each category corresponds to one and only one prevalence $x$.
Thus, $p(x \mid k) = 1$ if $k \in K_x$, a set of categories that have a given prevalence: $K_x = \{k' : p_{fk'} = x\}$. 
Further,  e partition of the set of all categories $K$ into non-overlapping $K_x$s.
Thus:

\begin{eqnarray} \label{eq:prevToKinds}
p(x) & = & \sum\limits_{k' \in K_x} p(x \mid k') \cdot p( k') \nonumber \\
     & = & \sum\limits_{k' \in K_x} p(k')
\end{eqnarray}

since $\forall k' \in K_{x}:  p(x \mid k') = 1$.
Returning to Eq. \ref{eq:expectation}, we have:

\begin{eqnarray} \label{eq:eq3}
\mathbb{E}[P(x)] & = & \sum\limits_{x} x \sum\limits_{k' \in K_x} p(k') \nonumber \\
                  & = & \sum\limits_{x} \sum\limits_{k' \in K_x} x \cdot p(k')
\end{eqnarray}

The set of all partitioned subsets $K_x$ is in a one-to-one correspondence with the set of all prevalences $x$. Thus, we have:

\begin{eqnarray} \label{eq:bijection}
  & = & \sum\limits_{K_x} \sum\limits_{k' \in K_x} x \cdot p( k')
\end{eqnarray}

Then, since $\cup_{x}{K_x} = K$, we have

\begin{eqnarray} \label{eq:partition}
  & = & \sum\limits_{k' \in K} x \cdot p( k') \nonumber \\ 
  & = & \sum\limits_{k' \in K} p(f \mid k') \cdot p( k') \nonumber \\ 
  & = & Z
\end{eqnarray}

$\square.$

### 2017-12-20 paper/appendix-bda.Rmd
lots of edits to appendices

@@
 
-# Appendix: Bayesian Data Analysis
+# Appendix C: Bayesian Data Analysis
 
-## Case Study 1: Generic language
+<!-- - add issues with doing BDA on prevalence and cue validity models -->
+<!--   - look at scatter plots of MAP estimates of referent prevalence parameters (2 per item) for all 4 models -->
+<!--   - look at scatterplots of bootstrapped cue validity with inferred cv from cue validity + prev regression model  -->
 
-### Modeling feature-probability priors
+<!-- Add scatterplots of inferred parameters from prior or prevalence alone vs. joint inference model -->
 
-In Case Study 1 (Generic Language), we elicited the prevalence of features for many different categories. 
-These can be thought of as *samples* from the feature-probability prior distribution. 
+In our three case studies, we compare an information-theoretic, computational model of endorsement to human endorsements of generalizations in language. 
+The model has a single free parameter: the optimality parameter in Eq. \ref{eq:S1}.
+Other model parameters (governing the prevalence prior $P(h)$ and the referent-prevalence $h'$) are estimated using additional behavioral data (e.g., prior elicitation tasks). 
+Througout the paper, we model all sources of data (prevalence prior data, endorsement data) using a single joint-inference Bayesian data analytic model.
+In this appendix, we describe this procedure in more detail for each case study.
+
+## Modeling prevalence priors
+
+In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence prior by asking about individual about the prevalence of features for individual categories.
+We performed an analagous elicitation in Case Study 3: Causal Language (Expt. 3a).
+We describe the analysis using generics as our running example, but a parallel analysis was done for causals.
+
+Participants' responses can be thought of as *samples* from the prevalence prior distribution. 
 Formally, we assume the prior data (analyzed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
@@
 Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
+Similar results can be obtained by rounding 0 to 0.01. 
+Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
 Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
 This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
-Similar results can be obtained by rounding 0 to 0.01. 
-Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
 ]
 Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
-<!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->
 We put the following priors over the latent parameters of the model:
-\begin{eqnarray}
+\begin{eqnarray*}
 \phi_i & \sim & \text{Uniform}(0, 1) \\
@@
 \xi_i & \sim & \text{Uniform}(0, 100)
-\end{eqnarray}
+\end{eqnarray*}
 where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).
@@
 To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
-To see how well the mixture model fits the feature-probability prior data, we use the inferred parameters to generate new data.
+To see how well the mixture model fits the prevalence prior data, we use the inferred parameters to generate new data.
 The data generated from the model's posterior is called the *posterior predictive distribution* and is an important step in model criticism. 
@@
 If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
-We do this many times using the posterior distibution to generate a distribution over predicted feature-probability ratings.
+We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
 ]
 
-## Jointly modeling referent feature-probability, feature-probability priors, and generic endorsements
+In Case Study 2 (Expt.
+2a), we asked participants about parameters of this mixture model (by having participants answer questions abouut *different kinds of people*) rather than having participants give samples (e.g., by listing their friends and rating how often their friends did certain actions).
+In pilot testing, we found these different methodologies to give similar results.
+We made the decision to ask more abstract information about the events to get at participants' abstract beliefs about the property rather than their knowledge of true frequencies. 
+As well, by querying about abstract characters, we were able to include items that participants might not otherwise feel comfortable reporting off (e.g., how often their friends smoke marijuana).
+The questions used to elicit information about the parameters are described in the main text.
 
-To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt.
-1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt.
+## Modeling referent-prevalence
+
+In Case Study 1, we used participants prevalence ratings for the category-of-interest in our generic sentences as the referent-prevalence that is used in the endorsement model (Eq. \ref{eq:S1}).
+For a given generic sentence (e.g., "Robins lay eggs"), we took the prevalence ratings for the referent-category (e.g., the percentage of robins that lay eggs) from the prior elicitation task (Expt.
+1b) and assumed those were generated from a single Beta distribution.
+We used the same priors as we did for the *stable cause* component of the prevalence prior:
+\begin{eqnarray*}
+\gamma_i & \sim & \text{Uniform}(0, 1) \\
+\xi_i & \sim & \text{Uniform}(0, 100)
+\end{eqnarray*}
+We took samples from the posterior predictive of this Beta distribution (i.e., reconstructed prevalence ratings) as the *referent-prevalence* used in the model.
+
+In Expt. 2b (Habitual endorsement), we used the frequency given to participants in the experimental prompt (e.g., 3 times in the past week) as the referent-prevalence.
+In Expt.
+2c ("What is prevalence?"), we compared two endorsement models that differed in their representation of referent-prevalence.
+For one model (past frequency model), it was the frequency given to participants in the experimental prompt (same as in Expt.
+2b); for the other model (predictive frequency model), we used the mean elicited frequency from the *predictive frequency* condition (see main text).
+In Case Study 3 (Causal endorsement), we used the proportion of successful causal events  given to participants in the experimental prompt (e.g., 70 out of 100 uses of Herb C made animals sleepy).
+
+## Jointly modeling referent-prevalence, prevalence priors, and generic endorsements
+
+To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the prevalence prior data (described above) to create a single, joint-inference model where the optimality parameter $\lambda_1$ (Eq.
+\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_f(h)$ for each property $f$) using data from Expt.
 1a \& b (Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the feature-probability prior distributions, we use the same priors described in Expt.
+For the parameters of the prevalence prior distributions, we use the same priors described in Expt.
 1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
@@
 ```
+
+In addition to examining the posterior predictive distribution on endorsement judgments (presented in main text), we examined the marginal posteriors on parameters of the prevalence priors and referent-prevalence.
+These marginal distributions are important to examine to confirm that they have not changed significantly from the parameters inferred from their private data sources in isolation.
+For example, when modeling the referent-prevalence data in isolation, the model infers that roughly 50\% of robins lay eggs, as that is what participants tend to say in the prevalence elicitation task.^[
+  Some participants do report that 100\% of robins lay eggs so the average prevalence rating is closer to 65\%..
+].
+The question for this joint inference model is whether or not it still believes that roughly 50\% of robins lay eggs.
+We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only their data, suggesting that the modeling all three data sources together does not come at the cost of modeling any one of them accurately.

### 2017-12-20 paper/appendix-cueValidity.Rmd
lots of edits to appendices

@@
 
-In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
-Here, the prevalence of the feature, or $P(f \mid k)$, is the critical quantity.
-Quantifiers can be described as conditions on prevalence: 
-$$
-\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}
-$$
-The driving question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
-Fixed constraints on $\theta$ (e.g., $\theta = 0.5$) are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice (i.e., *Some mosquitos carry malaria*).
+<!-- ### Discussion (from main text priors expt) -->
 
-With respect to malaria-carrying mosquitos, @Leslie2007 notes that the mosquito is the only species to carry malaria. 
-The distinctiveness of *carrying malaria* then perhaps why *Mosquitos carry malaria* is true.
-More formally, the inverse probability --- the probability of the kind $k$ given the feature $f$: $P(k \mid f)$ --- might be able to save statistical-based approaches [@Leslie2007; @Khemlani2012].
-This inverse probability, referred to as *cue validity*, encodes the diagnosticity of the feature for the kind.
-For example, after learning that an entity *carries malaria*, the probability that the entity is a *mosquito* is very high.
+<!-- The feature-probability prior distribution $P_f(h)$ encodes beliefs about the feature-probability (or, probabilities) of a feature $f$ across different kinds. -->
+<!-- These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
+-->
 
-As noted in the main text, cue validity can be derived from a prevalence prior composed of a finite number of kinds.
-This relationship follows from Bayes' Rule:
+<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->
 
-$$
-P(x \in k | x \in f) = \frac{P(x \in f \mid x \in k) \cdot P(x \in k)}{\sum_{k'}P(x \in f \mid x \in k') \cdot P(x \in k')}
-$$
+<!-- If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
+-->
+<!-- For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.
+-->
 
-where $x$ is an arbitrary entity, $k$ is a kind (represented as a collection of entities in the kind), and $f$ is a feature (represented as a collection of entities with the feature).
-However, in a generative model composed of a potentially infinite number of kinds, the cue validity of a feature for a particular kind is 0. 
-In our mixture model formulation of the prevalence prior, we explicitly represent the prevalence prior as a generative model with a potentially infinite number of kinds.
-In this formulation, the mixture parameter $\phi$ can be seen as a generalization of cue validity, to the case of potentially infinite numbers of kinds.
+<!-- However, we should not throw away the possibility that distributional information about the property is relevant.  -->
+<!-- The mixture parameter $\phi$ in the feature-probability prior distribution can be seen as a generalization of the construct of cue validity.  -->
+<!-- Recall that $\phi$ is the weighting between the two generative components of the feature-probability prior (i.e., the stable cause distribution $\mathcal{D}_{stable}$ and the transient cause distribution $\mathcal{D}_{transient}$).
+-->
 
-Cue validity is not itself sufficient to explain endorsements because of cases like *Dogs have four legs*, where many kinds have the feature. 
-However, one could argue for some integration of the two probabilities --- prevalence and cue validity.
-This is often used as the "statistical-based approach" and operationalized by measuring prevalence and cue validity, and using both measurements as predictors of generic endorsement in a logistic-regression of generic endorsement [@Khemlani2012; @Prasada2013].
+<!-- Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is no longer well-defined (or, it is zero for all kinds).
+-->
+<!-- This is for the same reason that for a probability distribution over the real numbers (a *continuous* probability distribution), the probability of any particular number is zero.  -->
+<!-- For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$. -->
+<!-- The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds} (and hence, $\phi$ is relatively low), but there are many kinds of birds and the feature is not particularly diagnostic for any given one of the subkinds (e.g., robins).
+-->
+<!-- $phi$ is still relatively small in this case because it encodes information about the distribution across kinds and not just one particular kind. -->
+<!-- This is an important methodological point of departure in our work from previous work. -->
 
-In Expt. 1, we articulated this alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a regression model.
-In a small review of the literature, we discovered different methods for measuring cue validity, which lead to different results. 
-Therefore, here we propose three *a priori* desiderata that a measurement of cue validity should satisfy.
+<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
+<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
+<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
+<!-- However, cue validity requires knowledge of the referent-category $k$ -->
+
+<!-- In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...). -->
+<!-- Here, the prevalence of the feature, or $P(f \mid k)$, is the critical quantity. -->
+<!-- Quantifiers can be described as conditions on prevalence:  -->
+<!-- $$ -->
+<!-- \denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\} -->
+<!-- $$ -->
+<!-- The driving question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true? -->
+<!-- Fixed constraints on $\theta$ (e.g., $\theta = 0.5$) are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice (i.e., *Some mosquitos carry malaria*).
+-->
+
+<!-- Cue validity is not itself sufficient to explain endorsements because of cases like *Dogs have four legs*, where many kinds have the feature.  -->
+<!-- However, one could argue for some integration of the two probabilities --- prevalence and cue validity. -->
+<!-- This is often used as the "statistical-based approach" and operationalized by measuring prevalence and cue validity, and using both measurements as predictors of generic endorsement in a logistic-regression of generic endorsement [@Khemlani2012; @Prasada2013].
+-->
+
+In Experiment 1, we articulated an alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a regression model.
+In a small review of the literature, we discovered different methods for measuring cue validity; in piloting, these different methods lead to different results. 
+Therefore, we propose three *a priori* desiderata that a measurement of cue validity should satisfy.
 We describe two experiments that represent the primary methods for measuring cue validity and compare them with these desiderata in mind.
@@
 
-## Measuring cue validity
+## Desiderata
 
-Measuring cue validity involves collecting participants' judgments that relate to the probability of the kind given the feature.
-There are at least two distinct, prominent ways of measuring cue validity.
-One way is ask participants directly about the probability (or likelihood, odds, etc...) of the kind given the feature, using a likert scale or slider [@Khemlani2012; @Prasada2013].
-We'll call this approach the "direct question" approach.
-Another way is to supply participants with the feature alone and have them generate the kind or kinds [@Cree2006].
-We'll call this approach the "free production" approach.
+Measuring cue validity involves collecting participants' judgments that relate to the probability that an exemplar is a member of a kind given that is has a feature : $P(x \in k \mid x \in f)$.
+There are several ways one could measure cue validity. 
+Here we consider two measures: One that has participants estimate the probability $P(x \in k \mid x \in f)$ directly, a common technique in the literature on generic language [e.g., @Khemlani2012; @Prasada2013], and another that has participants freely produce categories given a feature [i.e., draw a sample from the conditional distribution on kinds given a feature; @Cree2006].
+We will the former the *direct question* method and the latter the *free production* method.
 
-What criteria can we use to validate one measurement over the other?
-We propose three boundary cases *a priori* that the measurement should be able to satisfy.
-For each case, we provide four examples which will be used to evaluate each measure.
+Are the *direct question* and the *free productions* equally valid for measuring cue validity?
+We propose *a priori* three boundary conditions that the measurement should be able to satisfy.
+For each case, we provide four examples from our larger stimulus set on generics (Case Study 1) which will be used to evaluate each measure.
 
 \begin{enumerate}
-\item{Completely diagnostic features: We contend there are a number of features that only one (or very small) of categories contain.
-Examples include: \emph{carrying malaria} (mosquitos), \emph{carrying Lyme disease} (ticks), \emph{having manes} (lions), \emph{having pouches} (kangaroos).
-The cue validity of these features for the corresponding categories should be very high (close to 1).}
-\item{Completely absent features: For features that are completely absent in a kind, the cue validity should be extremely low or 0.
-There are many examples of these kinds of pairings; for example, \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger).
+\item{Completely diagnostic features: Some features are only present in one (or a very small number) of categories.
+Examples include: \emph{carrying malaria} (mosquitos), \emph{carrying Lyme disease} (ticks, deer), \emph{having manes} (lions), \emph{having pouches} (marsupials, including most famously: kangaroos).
+The cue validity of these features for the corresponding categories should be very high (at least 0.5 and possibly close to 1).}
+\item{Completely absent features: Many features are completely absent in many kinds.
+For these, the cue validity should be extremely low or 0.
+There are infinite examples.
+The ones will use are \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger).
 }
-\item{Completely undiagnostic features: We contend there are a number of features that almost every category contains.
-Examples include: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard).
+\item{Completely undiagnostic features: A number of features are shared by almost every category.
+The ones we will use are: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard).
 The cue validity of these features for particular categories should be extremely low or 0.
@@
 For the free production experiment, the cue validity is the proportion of responses of the target category (e.g., "mosquitos") for the property (e.g., "carries malaria").
-Of primary interest is the measurement for the boundary conditions described above.
+Of primary interest is the measurement for the desiderata items described above.
 Links to the experiments can be found on \url{https://mhtess.github.io}.
@@
 The filler trials were made up of random category -- property pairings.
-All trials were presented in a randomized order.
+Trials were presented in a randomized order.
 
@@
 
-We recruited 50 participants from Amazon's Mechanical Turk.
+We recruited 100 participants from Amazon's Mechanical Turk.
 Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
@@
 There were twenty-one trials in total, one for each property.
+No filler trials were used.
 Trials were presented in a randomized order.
@@
 
-To process the free production, we forced all characters to lower case, removed spaces, and made all terms into singular terms (e.g., "lions" --> "lion").
+To process the free production, we forced all characters in a repsonse to lower case, removed spaces, and made all terms into singular terms (e.g., "lions" --> "lion").
 As well, "mosquito" was a commonly mispelled label; we counted anything that started with "mosqu", "mesqu", "misqu", "mosiq" as "mosquito".
@@
 We are interested in the results of each measure (direct question and free production) for the three conditions corresponding to the desiderata outlined above. 
-To evaluate each measure, we selected four examples property--category pairs that we believe are unambiguously instances of the boundary conditions described above (these items are described above with the desiderata).
+To evaluate each measure, we selected four example property--category pairs that we believe are unambiguously instances of the boundary conditions described above (these items are described above with the desiderata).
 
 Figure \ref{fig:cv-bothquestions-barplots} (top) shows the results for the twelve items of interest for both measurements.
-We see that for the "false" features, both measures behave as desired (shown by the dotted line). 
-The cue validity of a feature that is false is zero or near-zero.
-For "diagnostic" features, both measures behave reasonably well.
-Learning that an entity has malaria strongly implies that it is a mosquito. 
-However, there are some subtle differences among our examples that only the free production measure picks up on.
+We see that for the "false" features, both measures behave as desired (hypothsized results shown by the dotted line): The cue validity of a feature that is false is zero or near-zero.
+For "diagnostic" features, both measures also behave reasonably: Learning that an entity has malaria strongly implies that it is a mosquito. 
+However, there is some evidence that the free production measurement is more sensitive than the direct-question measure.
 "Having a mane" is strongly diagnostic for a "lion" but also for a "horse" (and so the overall cue validity for lion is around 0.5).
 "Carrying Lyme disease" is mostly diagnostic for a "tick" but also "deer" (and thus, the cue validity for tick is not maximal).
+These subtle differences among "diagnostic" features is picked up by the free-production measure but not by the direct-question measure.
 
-The measures deviate in their characterization of the undiagnostic features. 
-Learning that an entity is female does not strongly imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
+The measures deviate most strongly, however, in their characterization of the undiagnostic features. 
+Learning that an entity is female should not strongly imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
 A similar phenomenon can be observed in direct question measure for the other undiagnostic features.
@@
 This latter response option may be a pragmatic effect of asking the direct question and/or participants "opting out" of a response. 
-For example, in response to the question "There is a thing that is female.
-What are the odds that it is a robin?", a reasonable human response may be "I don't know".
+For example, in response to the question "There is a thing that is female. What are the odds that it is a robin?", a reasonable human response may be "I don't know". 
 Participants may cope with the awkwardness of the question by placing the slider bar in the middle of the scale.
@@
 d.cv.fp <- read.csv(paste(project.path, 
-                          data.path, "cue-validity-2-freeProduction-trials.csv", sep = ""))
+                          data.path, "cue-validity-2-freeProduction-trials-n100.csv", sep = ""))
 
@@
 
-We can further understand our measures of cue validity by comparing them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
+To further understand these measures of cue validity, we compare them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
 Expt.
-1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated.
-(Participants freely generated the other half).
-Thus, we do not have the best measurement of the prior probability of categories $P(k)$.
+1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated (the other half was freely generated by participants); including these supplied categories was important to measure referent-prevalence of interest (e.g., the percentage of mosquitos that carry malaria).
+Including them in this analysis, however, potentially distorts the prior probability of categories $P(k)$.
 
@@
 Figure \ref{fig:cv-bothquestions-barplots} (bottom right) shows the two measurements of cue validity as they relate to the prevalence prior derived cue validity. 
-The prevalence prior derived cue validity is high associated with both measurements: $r_{direct}^2(`r n.dq`) = `r r2.dq`; MSE_{direct} = `r mse.dq`$ and $r_{free}^2(`r n.fp`) = `r r2.fp`; MSE_{free} = `r mse.fp`$.
-Of primary interest is how the measurements behave for for desiderata items. 
-We see that the prevalence prior derived cue validity converges with the free production measurement for the desiderata items ($r_{free}^2(`r n.fp.desid`) = `r r2.fp.desid`; MSE_{free} = `r mse.fp.desid`$), whereas the direct question measurement overestimates the cue validity of undiagnositic features ($r_{direct}^2(`r n.dq.desid`) = `r r2.dq.desid`; MSE_{direct} = `r mse.dq.desid`$).
-Interestingly, the direct question measurement consistently overestimates cue validity in comparison to the prevalence prior derived cue validity.
+The prevalence prior derived cue validity is highly associated with both measurements: $r_{direct}^2(`r n.dq`) = `r r2.dq`$; $MSE_{direct} = `r mse.dq`$ and $r_{free}^2(`r n.fp`) = `r r2.fp`$; $MSE_{free} = `r mse.fp`$.
+Of primary interest is how the measurements behave for desiderata items. 
+We see that the prevalence prior derived cue validity converges with the free production measurement for the desiderata items ($r_{free}^2(`r n.fp.desid`) = `r r2.fp.desid`$; $MSE_{free} = `r mse.fp.desid`$), whereas the direct question measurement overestimates the cue validity of undiagnositic features ($r_{direct}^2(`r n.dq.desid`) = `r r2.dq.desid`$; $MSE_{direct} = `r mse.dq.desid`$).
+
+The points of largest deviation for the free-production measurement from the prevalence prior derived measurement occur where the prevalence prior derived measure rates the cue validity as relatively high when the free-production measure gives the item low cue validity (two black points in Fig.
+\ref{fig:cv-bothquestions-barplots} (right scatterplot) high X-value, low Y-value).
+These two items are: ("is red", "cardinal") and ("is white", "swan").
+These items should have low relatively cue validity and are overestimated by the prevalence prior because of the prior on categoryies $P(k)$ (i.e., because they were supplied to every participant and thus get a higher weighted in the prior for deriving cue validity).
+In comparison, the direct question measurement consistently overestimates cue validity relative to the prevalence prior.
 
@@
 
-*Cue validity* is often used as a measurement for understanding generic truth conditions. 
-We articulated three *a priori* boundary conditions for a measurement of cue validity, because we observe different measurements being used in the literature. 
+*Cue validity* is a commonly used measurement for understanding generic truth conditions. 
+Because we observe different measurements being used in the literature, we articulated three *a priori* desiderata to validate a measure of cue validity.
 We found that the "free production" measurement (i.e., having participants generate categories given a feature), and not the direct question measurement (i.e., asking participants a likelihood judgment of the category given the feature), satisfied all three boundary conditions.

### 2017-12-20 paper/comgen-paper.Rmd
add subsec to model about prevprior, summarize relation to cue validity

@@
 
-Our model makes predictions about endorsing generalizations based on two externally-determined model components: The prevalence priors $P(p_f)$ in Eq.
+Our model makes context-sensitive predictions about endorsing generalizations based on two model components: The prevalence priors $P(p_f)$ in Eq.
 \ref{eq:L0} and the referent-prevalence $p_{fk}$ in Eqs.
@@
 We will return and refine this definition in Case Study 2, when considering generalizations about events.
-For now, the referent-prevalence is simply what determines the truth-conditional semantics. 
-Our hypothesis does not provide a mapping from the truth-conditional semantics directly to endorsement judgments, because $\theta$ is underspecified.
-
-The truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating prior belief about the feature in question---the *prevalence prior* $P(p_f)$---and the uncertain threshold $P(\theta)$ with the truth-functional semantics.
-Again, $P(\theta)$ is set to be a uniform distribution across all contexts, and thus, the generalization could in principle be felicitious with potentially any prevalence. 
-However, what the interpretation model believes *a priori* $P(p_f)$ must be considered before the endorsement model can say whether or not it would endorse the generalization.
+For now, the referent-prevalence is simply a probability that determines the truth-conditional semantics. 
+Our hypothesis does not provide a mapping from the referent-prevalence directly to endorsement judgments, however, because $\theta$ is underspecified.
+
+The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
+\ref{eq:L0}) by integrating prior beliefs about the feature in question---the *prevalence prior* $P(p_f)$---with the truth-functional semantics.
+Again, $P(\theta)$ is set to be a uniform distribution across all contexts, and thus, the generalization could in principle be felicitious with potentially any referent-prevalence. 
+However, interpretation model's *a priori* beliefs $P(p_f)$ must be considered before the endorsement model can say whether or not it would endorse the generalization.
 
 Beliefs about properties result from internal conceptual models of the world. 
-These internal models have domain-specific features but should all give to the domain-general currency of probability.
-One way of constructing prior distributions over prevalence, without appealing directly to domain-specific conceptual knowledge, is by considering the prevalence of the feature among different categories.^[
-  An alternative way is to consider the prevalence of different features among the same category. 
-  We return to this point in the general discussion.
-]
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0 .
+These internal models have domain-specific features but should all give to the domain-general currency of inductive reasoning: probability.
+One way of constructing prior distributions over prevalence, without appealing directly to domain-specific conceptual knowledge, is by considering the prevalence of the feature among different categories.
+For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because what one would expect for a randomly-sampled category is that it has 0 or close to 0 exemplars that bark.
 Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
-Conceptual differences can manifest in these prevalence priors; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
+Conceptual differences can manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
 
 By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-Indeed, previous studies have found cue validity to be highly correlated with endorsing generalizations about categories, or *generic language* [@Khemlani2012].
-Cue validity is defined for a particular category--feature pair, and relates to referent-prevalence by Bayes' Rule:
-$$ P(x \in k \mid x \in f) = \frac{P(x \in f \mid x \in k) \cdot P(x \in k)}{\sum_{k' \in K} P(x \in f \mid x \in k') \cdot P(x\in k')} $$
+*Cue validity* implicitly encodes knowledge of other categories and has been shown to be  highly correlated with endorsing *generic sentences*, or generalizations about categories [@Khemlani2012].
+Cue validity is defined for a particular (category, property) pair (as is referent-prevalence), and relates to referent-prevalence by Bayes' Rule:
+\begin{equation}
+P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')} \label{eq:cuevalidity}
+\end{equation}
+Since *cue validity* implicitly encodes knowledge of other categories (by summing over $k'$) and the prevalence prior explicitly encodes knowledge of other categories, how are these two constructs related?
 In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
-Thus, $P(x \in k) = P(k) = P(p_{fk})$).
-The denominator of the cue validity expression above (the normalizing constant), then, is the expectation (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$.
-This relationship reveals a potential shortcoming of a point estimate like *cue validity*; the prevalence prior potentially encodes structured, conceptual knowledge of the world, which would be lost by reducing it to a single value.
+Thus, $P(p_{fk}) = P(k_{f})$.
+The denominator of Eq.
+\ref{eq:cuevalidity} (which encodes knowledge of other categories), then, is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$.
+For a more thorough derivation of this relationship, see Appendix A.
+The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potentialy shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
+This is particularly problematic for prevalence distributions that encode conceptual knowledge via multimodal distributions (e.g., Fig.
+\@ref(fig:simulations)A; bottom row); the mean of a multimodal distribution is not a good representation of that distribution.
+We return to this point empirically in Case Study 1.
 
@@
 
-We implemented the model in the probabilistic programming language WebPPL [@dippl].
+### Model simulations
+
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $p_{fk}$ in Eq.
+\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(p_f)$ (Eq.
+\ref{eq:L0}).
+We simulate how these two factors change both literal interpretation and endorsement using schematic parameter values based on intuition from classic examples in the literature on generic language.
+We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
 The following simulations were implemented using the R package RWebPPL [@rwebppl] in the RMarkdown document that generated this paper text and figures.
 That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-### Model simulations
-
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $h'$ in Eq.
-\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(h)$ (Eq.
-\ref{eq:L0}).
-We simulate how these two factors change both literal interpretation and endorsement using hypothetical values based on intuition about classic examples from the literature on generic language.
 
@@
 
-The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}. 
-This gives the literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") given the background knowledge about the property.
-For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
-This would correspond to a rather strong interpretation (i.e., "Almost all feps bark").
-This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green). 
-Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
-The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple).
-Again, the literal interpretation depends upon the background knowledge in a deep way.
-
-The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right).
-Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
-\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
-We see the model correctly predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
+The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$ (Figure\ \@ref(fig:simulations)B).
+Low thresholds (e.g., $\theta = 0.1$) rule out very few possibilities (only $p_{fk} \leq 0.1$), and thus are quite likely given that its consistent with much of the prevalence prior.
+The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be similar to staying silent (a posterior not very different from the prior).
+Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
+
+The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds.
+The prevalence-based interpretations of generalizations of novel categories are shown in Figure\ \@ref(fig:simulations)C.
+These interpretations depend heavily on the prevalence priors (different rows).
+Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (top row; pink).
+"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (4th row; green).
+The literal interpreter can also derive very weak interpretation, as shwon in the  \textsc{carries malaria} distribution (bottom row, purple).
+
+The endorsement model (Eq. \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs).
+Predictions for a few classic examples from the generics literature are shown in (Figure\ \@ref(fig:simulations)D).
+In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
 Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
-To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) left; blue distributions).
-The endorsement model decides if it is better to produce the generalization or stay silent (which results in the interpretation distribution being the prior). 
-In this case, there is no difference in interpretation, and thus, the model is completely ambivalent about whether or not to endorse the statement.
-This can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
-<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
-
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(h)$ as well as the prevalence $h'$ communicated. 
-We chose reasonable, hypothetical values for each of these, and saw that the endorsement model recapitulated standard intuitions about the truth or falsity of classic examples from the generics literature.
+To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) A vs.
+C; blue distributions).
+The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
+This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
+
+These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the prevalence $p_{fk}$ communicated. 
+We chose schematic values for each of these, and saw that the endorsement model recapitulates standard intuitions about the truth or falsity of classic examples from the generics literature.
 In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
 We do this by both measurning and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
+
+<!-- The literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") is given by Eq. \ref{eq:L0} and shown in  -->
+
+<!-- The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}.  -->
+<!-- For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
+-->
+<!-- This would correspond to a rather strong interpretation (i.e., "Almost all feps bark"). -->
+<!-- This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green).  -->
+<!-- Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
+-->
+<!-- The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple). -->
+<!-- Again, the literal interpretation depends upon the background knowledge in a deep way. -->
+
+<!-- The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right). -->
+<!-- Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
+\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
+-->
+<!-- We see the model correctly  -->
+
+<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
 
@@
 
+\newpage
+
 # References
@@
 
+\newpage
+
+```{r child = 'appendix-cvDerivation.Rmd'}
+```
+
+\newpage
+```{r child = 'appendix-cueValidity.Rmd'}
+```
+
+\newpage
+
 ```{r child = 'appendix-bda.Rmd'}
 ```
-
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-# ```{r child = 'appendix-alternativeRSAmodels.Rmd'}
-# ```

### 2017-12-20 paper/case1-generics.Rmd
streamline prev prior and cue validity model discussion

@@
 
-The prevalence prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
+The prevalence prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
 To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%).
+Ask yourself "is it female?" 
+Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). 
 Now, do you think it lays eggs? 
 Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
-The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
+That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of^[
+  The subjective probability may, in fact, be non-zero and small as opposed to 0. 
   Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange   generic mutation or the interaction of dog genetics with a strange environment. 
@@
 
-This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(h \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
+This thought experiment decomposes the prevalence prior $P(h)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(h \mid k)$.
+We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$ and perform  Bayesian data analysis to accurately reconstruct the prevalence prior.
 We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
@@
 
-As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* predict generic endorsementse.
-If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* thus captures the distinctiveness of the feature for the category. 
-For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
-Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
-Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
-In addition, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
-
-We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$.
-If there is a finite number of kinds in the prevalence prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the prevalence prior and can be derived via Bayes' Rule:
-$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
-Previous empirical studies of generic language, however, have not measured prevalence priors and instead tried to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
-In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
-Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *prevalence prior derived cue validity*, see Appendix.
+Cue validity is linearly related to a point-estimate of the prevalence prior distribution (see Model section and Appendix A).
+It thus implicitly captures information about other categories, though cannot capture the structure that is present in the prevalence priors.
+To show that this structure is important, we explore a secondary baseline model based on prevalence and cue validity.
+
+<!-- Whereas prevalence encodes a prediction about whether or not an entity $x$ of a certain kind $k$ will have the property $f$, $P(x \in f \mid x \in k)$, *cue validity* represents the inverse prediction: that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
+-->
+<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012]. -->
+<!-- For example, the truth of "Mosquitos carry malaria" can be explained by appealing to the fact that *only mosquitos* carry malaria, and htus if one learns that an entity carries malaria, that entity is probably a mosquito (high cue validity).
+-->
+<!-- Of course, cue validity is not a necessary feature of a true generic statament: "Dogs have four legs" is true despite the feature of having four legs being utterly undiagnostic for dogs. -->
+
+<!-- Cue validity is not unrelated to the prevalence prior.  -->
+<!-- The prevalence prior $P(h)$ is a probability distribution, which can decomposed into a distribution on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$. -->
+<!-- For simplicity, assume we have perfect knowledge of the prevalence for each kind: $P(h \mid k) = P(f \mid k)$. -->
+<!-- Then if the prevalence prior is composed of a finite number of kinds, the cue validity of that feature for a particular kind is given by Bayes' Rule: -->
+<!-- $$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')}  = \frac{P(f \mid k) \cdot P(k)}{\mathbb{E}_{k' \sim P(k')}P(h \mid k')} $$ -->
+<!-- The normalizing constant in this equation is the expected value of the prevalence prior distribution.  -->
+<!-- though its role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
+
+<!-- If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability:  -->
+<!-- *Cue validity* thus captures the distinctiveness of the feature for the category.  -->
+<!-- Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence:  -->
+<!-- In addition, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.
+-->
+
+Though the cue validity of a particular (category, property) pair can be derived from the prevalence prior distribution, previous empirical studies of generic language have not done this.
+Instead, these studies estimate cue validity by asking a separate group of participants about the distinctiveness of features for given animals [e.g., @Khemlani2012], though different studies use different measurements.
+Preliminary analysis of these different measurements revealed that a *free production* paradigm [@Cree2006] is preferred.
+Participants ($n = 100$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
+For a detailed analysis of different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.
 
@@
 
-"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of a simple model based on cue validity.
+"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
 "Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
-Negative properties (like, "not carrying malaria") are completely undiagnostic for almost every category (low cue validity), and the fitted regression model doesn't know how to penalize "Mosquitos don't carry malaria" because the prevalence is high (most mosquitos don't carry malaria).
+Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Fig.\ \@ref(fig:simulations)A bottom).
+Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
+Such a model makes the wrong prediction for non-distinctive properties that in, absolute terms, have high prevalence but in relative terms, low prevalence (e.g., "Mosquitos don't carry malaria").
 A simple metric like cue validity is too blunt to capture these subtleties.

### 2017-12-20 paper/case2-habituals.Rmd
minor edits to prose of habituals and causals

@@
 Events are a broad class of entities. 
-In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes.").
+In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes").
 Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
@@
 
-```{r habituals-prior-model-run, cache = T}
+```{r habituals-prior-model-run, cache = T, eval = F}
+
+n_samples <- 20000
 items <- levels(factor(d.hab.priors.filtered$item))
-n_samples <- 500
+
 rs.habituals.bda.prior <- data.frame()
@@
 }
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5, fig.height = 3}
+save(rs.habituals.bda.prior, 
+     file = paste(project.path,  "models/habituals/results/", 
+                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
+                  ".RData", sep = ""))
+
+```
+
+```{r habituals-prior-model-parameters, fig.width = 5}
+n_samples <- 20000
+items <- levels(factor(d.hab.priors.filtered$item))
+
+load(file = paste(project.path,  "models/habituals/results/", 
+                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
+                  ".RData", sep = ""))
 
@@
   ungroup()
+
 rs.habituals.bda.prior.summary.wide <- left_join(
@@
 )
+
 rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category)) 
-figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide,
+          d.hab.priors %>% select(item, category) %>% distinct())
+
+figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide %>%
+                                            mutate(Gender = factor(Gender, levels = c("male", "female"))),
        aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
             y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = category))+
+             fill = Gender, shape = Gender))+
+  geom_errorbar(alpha = 0.5)+
+  geom_errorbarh( alpha = 0.5)+
   scale_shape_manual(values=c(21,22))+
@@
   scale_fill_brewer(palette='Set1')+
-
-  geom_point(size=4, inherit.aes = F, 
-             aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            shape = Gender),  alpha = 0.9)+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  xlab("% of Americans who have DONE ACTION")+
-  ylab("Log Frequency of DOING ACTION")+
+  #scale_color_brewer(palette='Set1')+
+  geom_point(size=4, 
+            #  inherit.aes = F, 
+            #  aes(x = mix_mean,y = sfreq_mean,  fill = category,
+            # shape = Gender),  
+            alpha = 0.9)+
+
+  xlab("% have DONE ACTION")+
+  ylab("Frequency of DOING ACTION \n (log scale)")+
   #scale_
   coord_fixed(ratio = 1/8)+
-  theme(legend.title = element_text(hjust=0),
-        legend.position="bottom",
-        legend.direction="horizontal") +
+  guides(fill = F,  shape = F)+
+  theme(legend.title = element_blank(),#element_text(hjust=0),
+        legend.position=c(0.82,0.14),
+        legend.direction="vertical") +
         scale_y_continuous(limits = c(-1.5, 6.5), 
@@
   geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), inherit.aes =F,
+                    filter(item %in% example.habituals, Gender == "female"), 
+                  inherit.aes =F,
                   aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
+
+#figure.habituals.priors.scatter
 ```
@@
 
-```{r habituals-prior-marginals-fig, fig.width = 4, fig.height = 4, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
+```{r habituals-prior-marginals-fig, fig.width = 7, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
 2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red)."}
+Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red).", cache = F}
 
@@
          src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals)) %>%
+  mutate(item = factor(item, levels = example.habituals),
+         gender = factor(gender, levels = c("male", "female"))) %>%
 ggplot(. , aes( x = val, color = gender))+
@@
   xlab("Frequency")+
-  ylab("Scaled prior density")+
+  ylab("Scaled probability density")+
   scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
   theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.12),
+        legend.position = c(0.9, 0.11),
+        legend.title = element_blank(),
         axis.text.x = element_text(angle = 90))+
@@
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Feature-probability priors for events (Expt.
+
+#figure.habituals.priors.marginals
+```
+
+```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Prevalence priors for events (Expt.
 2a).
-Left: Inferred mixture mean parameter and stable frequency mean parameter for N events.
-Right: Reconstructed priors on rates from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the structured model."}
+Left: Mean mixture parameter and mean stable frequency parameter for 31 events.
+Right: Inferred priors on frequencies from the structured, prior elicitation task.
+Priors are reconstructed by forward sampling using the inferred parameters in the prior mixture model.", cache = F}
 grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
@@
 
-Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt.
+Habitual language conveys generalizations about events.
+Our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt.
 2a).
@@
 
+A regression model that takes into the frequency and the *distinctiveness* of the action does a reasonable job at explaining the variance in this data.
+We note that this kind of model is merely a re-decription of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization. 
+A theory of the semantics of a generalization must formalize the truth-conditions of the generalization as well as how those truth-conditions relate to endorsement. 
+This is precisely what our information-theoretic models do (both fixed- and uncertain-threshold).
+
 <!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing enabling and preventative causal evidence.
+In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventated future occurences of the action.
 We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
-We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is able to account for the influence of top-down moderators on habitual endorsement.
+We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
+Predicted prevalence thus captures the infleunce of top-down moderators (e.g., intervening causal forces) on endorsement.
 <!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.
@@
 
-In these experiments, we introduced participants to novel actors and by doing so, were able to directly manipulated the frequency of a person doing the action.
-The kinds of events we used were familiar to participants (e.g., *running*) and so we measured the prevalence priors for those events.
-<!-- Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
--->
+In these experiments, we introduced participants to novel actors and, by doing so, were able to directly manipulate the frequency of a person doing the action.
+The kinds of events we used were familiar to participants (e.g., *running*) and thus we measured the prevalence priors for those events.
 In our final case study, we experimentally manipulate the prevalence priors, testing their causal influence over endorsements.
 In addition, we further we extend our theory to the language of causal relationships.
+
+<!-- Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
+-->
 

### 2017-12-20 paper/case3-causals.Rmd
minor edits to prose of habituals and causals

@@
 
-Language about causal relationships manifests as a generalization.
+Language about causal relationships manifests in generalization.
 The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analagous to how "John smokes" relates to  "John smoked yesterday". 
@@
 
-In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we explicitly test the relationship between the feature-probability priors and endorsements of generalizations about causes.
+In this paper, we posit thatprevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
+In this last set of experiments, we explicitly test the relationship between the prevalence priors and endorsements of generalizations about causes.
 Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
@@
 
-## Experiment 3a: Manipulating priors for causes
+## Experiment 3a: Manipulating prevalence priors
 
@@
 Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure \@ref(fig:causals-conditions). 
-In two of the conditions, participants saw results that were approximately all the same across the various experiments. 
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common deterministic" condition).
+In two of the conditions, participants saw results that came from the same underlying distribution.
+In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common strong" condition).
 In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
-These distributions had the feeling that either there was some background cause which gave rise to the effect (e.g., a simple base rate) or that all substances were equally as efficacious at producing the effect.
-
+<!-- The results of the previous experiments were described verbally  -->
+<!-- These distributions had the feeling that either there was some background cause which gave rise to the effect (e.g., a simple base rate) or that all substances were equally as efficacious at producing the effect.
+-->
 The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare deterministic" and "rare weak" conditions, because the very existence of a greater than zero effect was "rare".
-These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect.
+These are the "rare strong" and "rare weak" conditions.
+<!-- These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect. -->
 
@@
 <!-- The second phase serves as a measurement of participants' feature-probability priors. -->
-
-Participants were told that they were an astronaut-scientist on a distant planet trying to figure out how some system works (how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
+Participants were told that they were an astronaut-scientist on a distant planet trying to figure out how some system works (i.e., how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
 The story for the "sleepy animals" condition read:
@@
 
-Participants then must click a button to show the results of the experiments.
+Participants then click a button to show the results of the experiments.
 Experiment results appear one at a time (upon a click), and are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes per number of attempts (always 100 per experiment).
-Eleven "experiments" are shown, though the results of one experiment were said to be lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)). 
+Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment).
+We described the results of these individual experiments using *token-level* causal language (e.g., "98 cheebas were made sleepy") to suggest that actual causation occurred in these cases.
+
+Participants see the results of eleven "experiments", though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)). 
 (These lost results would be found in the *causal endorsement* task, Expt. 3b).
-After participants view the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
+After participants viewed the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
 
-Upon clicking the continue button, the table of "experiment results" is removed and participants are told more experiments were conducted.
+Upon clicking the continue button, the table of experiment results is removed and participants are told more experiments were conducted.
 Participants were asked to predict the results of the next 5 experiments.
@@
 In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
+Most of the experimental deisgn was identical to that of Experiment 3a.
 
 ### Method
-
-Most of the experiment was identical to that of Experiment 3a.
 
@@
 
+```{r tests?}
+d.caus.endorse.passed <- left_join(
+  d.caus.endorse, 
+  d.caus.endorse.catch %>% select(workerid, passBoth)
+  ) %>%
+  filter(passBoth == 1)
+
+# str(d.caus.endorse.passed)
+# 
+# summary(glmer(response ~ frequency* across * within + (1 | story), family = 'binomial', data = d.caus.endorse.passed %>%
+#   separate(distribution, into =c("across", "within") ) %>%
+#     mutate(frequency = factor(frequency))))
+
+#str(d.caus.endorse.passed)  
+```
+
 #### Participants
@@
 The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)).
-Upon continuing past the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found.
+Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found.
 The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
@@
 Partipants responded by either clicking "Yes" or "No". 
-
 After responding, participants completed the same attention check as Expt. 3a.
@@
   scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Feature-probability") +
+  xlab("Prevalence") +
   ylab("Scaled probability density")+
@@
   scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("Referent feature-probability")+
+  xlab("Referent prevalence")+
   ylab("Causal Endorsement")+
@@
 As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \ref{fig:causals-endorsement}.
+These are shown for the different experimentally-manipulated priors and frequencies in Figure \@ref(fig:causals-endorsement).
 
@@
 In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
+In this domain, we succesfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
 This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
 In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
+In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ is causally related to endorsements of generalizations in language.
 To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
@@
 
-It's likely that there exist domains for which abstract, intuitive theories might interfere with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
+It's likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
 If this were happening in our domains, we would expect this to show up in the results of Expt.
@@
 Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the belief distribution over causal power.
+Our theory would predict in these cases that differences in endorsement would be attributable to differences in the prevalence prior distribution (here: the belief distribution over causal power).

### 2017-12-21 paper/case1-generics.Rmd
play around with plots, edits to habituals fixed model results

@@
 <!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
-For more details about model implementation and inference, see Appendix.
+For more details about model implementation and inference, see Appendix C.
 
@@
 
-  # for (c in 1:2){
-  #     m.gen.endorse.priors.savage <- webppl(
-  #   paste(genericEndorsementPriorModelHelpers, 
-  #         savageDickeyModel, sep = '\n'), 
-  #   data = priorData, 
-  #   data_var = "data"
-  #   )
-
-  # m.inferred.prior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$prior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # m.inferred.posterior <- get_samples(
-  #   data.frame(m.gen.endorse.priors.savage$posterior) %>%
-  #     rename(prob = probs), n_samples)
-  # 
-  # posterior.density <- density(m.inferred.posterior$phi,
-  #         from = 0, to = 1)
-  # 
-  # prior.density <- density(m.inferred.prior$phi,
-  #         from = 0, to = 1)
-  # 
-  # logBF01 = log(approxfun(posterior.density)(1)) - 
-  #   log(approxfun(prior.density)(1))
-
-  # m.gen.endorse.priors.savage.summary <- bind_rows(
-  #   m.gen.endorse.priors.savage.summary,
-  #     bind_rows(
-  #     data.frame(Property = p, 
-  #                Chain = c, 
-  #                diff = NA,
-  #                logBF01 = logBF01,
-  #                BF01= exp(logBF01)),
-  #     data.frame(m.gen.endorse.priors.savage$logBFs) %>%
-  #       rename(diff = X1, logBF01 = X2) %>%
-  #       mutate(Property = p, Chain = c, BF01 = exp(logBF01))
-  #     )
-  # )
-  # 
-  # }
-
-    #for (c in 1:3){
-
-      # posterior.logspline <-  polspline::logspline(filter(
-      #   m.gen.endorse.priors, Parameter == 'phi', Chain == c)$value,
-      #   lbound = 0, ubound = 1)
-      # 
-      #   posterior <- dlogspline(1, posterior.logspline)
-      # prior <- dunif(1, min = 0, max = 1)
-      # BF01 <- posterior/prior
-      # 
-      # print(log(BF01))
-
-  #}
-
-  #print(p)
-  #print(priorData)
 }
@@
 
-gen.priors.cdfs <-m.gen.endorse.priors.posteriorPredictive %>%
+gen.priors.cdfs <- m.gen.endorse.priors.posteriorPredictive %>%
   mutate(src = factor(src, levels = c("Data", "Structured", "Unstructured"),
@@
 ```{r generic-RSAmodels, fig.width = 8}
+example.generics <- c("Tigers dont eat people", 
+                      "Mosquitos carry malaria", 
+                      "Robins lay eggs", 
+                      "Robins are female",
+                      "Leopards have spots")
+
 n_chains <- 3
@@
 model_prefix <- "results-generics-jointModel-S1-smntcs_"
-#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-"
+#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
 # m.samp <- data.frame()
-# m.samp.fixed <- data.frame()
+#m.samp.fixed <- data.frame()
 #for (i in seq(1, n_chains)){
@@
 #
+
 # save(m.samp.fixed,
+#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
+
      # file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
@@
 #                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThreshold-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
+
+# load(m.samp.fixed, 
+#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdDisc-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
+
+load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
 
@@
 
+uncertain.threshold.s1opt <- m.samp %>% 
+  filter(type == "param") %>%
+  group_by(param) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+fixed.threshold.s1opt <- m.samp.fixed %>% 
+  filter(type == "param") %>%
+  group_by(param) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
 fixed.threshold.posterior <- filter(fixed.params.posterior, param == "fixedThreshold")
@@
 
-```{r generic-model-scatters}
+```{r generic-endorsement-referent-prevalence-model, eval = F}
+referentPrevalenceModel <- '
+var model = function(){
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var betaParams = betaShape({g, d})
+  var referentPrevDist = Beta(betaParams)
+  mapData({data: preprocessedResponses}, function(d){
+    observe(referentPrevDist, d)
+  })
+  return {g, d}
+}
+'
+genericEndorsementRefPrevModel <- paste(genericEndorsementPriorModelHelpers, referentPrevalenceModel, sep = "\n")
+```
+
+```{r generic-referent-prevalence-model-run, eval = F}
+m.gen.refprev.predictive <- data.frame()
+n_samples <- 10000
+lg = 0
+
+for (p in example.generics ) {
+
+  prevData <- d.prev %>% 
+  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
+  filter(sentence == p)
+
+  m.gen.refprev <- webppl(genericEndorsementRefPrevModel,
+                                 data = prevData$prevalence, data_var = "data",
+                                 model_var = "model",
+                                 chains = 1,
+                                 cores = 1,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+    m.gen.refprev.predictive.item <- m.gen.refprev %>%
+      group_by(Iteration, Chain) %>%
+      spread(Parameter, value) %>%
+      rowwise() %>%
+      mutate(
+        a = g*d,
+        b = (1-g)*d,
+        prevalence =rbeta(n = 1, shape1 = a,
+                                 shape2 = b),
+        Category = prevData[1,]$Category,
+        Property = prevData[1,]$Property,
+        src = "prevAloneModel"
+      ) %>% ungroup()
+
+    m.gen.refprev.predictive <- bind_rows(
+      m.gen.refprev.predictive,
+      m.gen.refprev.predictive.item %>%
+        select( src, Category, Property, prevalence)
+    )
+
+}
+#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
+#head(prevData)
+#n_samples
+```
+
+```{r gen-prev-forward, eval=F}
+#Forward sample Target Prevalence from posterior on parameters (joint inference model)
+m.samp.prev.params <- m.samp %>%
+    filter(type == "targetPrevalence") %>%
+    #filter(type == "withinKind") %>%
+    mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type) %>%
+    #mutate(item = paste(parameter, property, sep = "_")) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category"), sep= "_")
+
+m.samp.prevalence <- m.samp.prev.params %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+```
+
+```{r}
+example.generics.properties <- c("dont eat people", 
+                      "carry malaria", 
+                      "lay eggs", 
+                      "are female",
+                      "have spots")
+```
+
+```{r gen-prev-dists, eval=F}
+gen.prev.dists <- bind_rows(
+  d.prev %>% 
+  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
+  filter(sentence %in% example.generics) %>%
+  mutate(prevalence = prevalence / 100,
+         src = 'data') %>% 
+    select(-workerid, -trial_type),
+  m.samp.prevalence %>% 
+    mutate(sentence = paste(category," " ,property, sep = "")) %>%
+    filter(sentence %in% example.generics) %>%
+    select(property, category, prevalence) %>%
+    rename(Category = category, Property = property) %>%
+    mutate(src = 'model'),
+  m.gen.refprev.predictive
+)
+
+ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
+  geom_density(aes( y = ..scaled.. ))+
+    #  stat_ecdf(size = 1)+
+  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+   #              position = position_dodge())+
+  facet_wrap(~Property + Category, nrow = 1)+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r generic-model-scatters, cache = F}
 m.gen.endorse.rsa <- bind_rows(
@@
                                       "generics_model",
-
                                       "regression_Prev", 
@@
                                  "Uncertain semantics model",
-
                                  "Prevalence",
@@
 ```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
 
@@
 `r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
-Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
+The inferred optimality parameter in Eq.
+\ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
 
@@
 
+We first examine the posterior predictive distribution on the prevalence prior and referent-prevalence data to ensure that the joint-inference model fits these data as well as the Bayesian model that modeled these data in isolation.
+This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters.
+Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+1b).
+This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
+
+The inferred optimality parameter in Eq.
+\ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
+
 As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).

### 2017-12-21 paper/case2-habituals.Rmd
play around with plots, edits to habituals fixed model results

@@
 #  m.hab.fixed.samp <- data.frame()
-# 
-# for (i in seq(1, n_chains)){
-#   # mi <- fread(paste(project.path,  "models/habituals/results/",
-#   #                   model_prefix, "smtncs_habitual-",
-#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-# 
-#   # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#   #                   model_prefix, "smtncs_some-",
-#   #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+
+#for (i in seq(1, n_chains)){
+  # mi <- fread(paste(project.path,  "models/habituals/results/",
+  #                   model_prefix, "smtncs_habitual-",
+  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
+
   # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                           "results-habituals-jointModel-inferFixedThresholdCts-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
+  #                   model_prefix, "smtncs_some-",
+  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
+#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
 #   #
@@
 # save(m.hab.fixed.samp,
-#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+#      file = paste(project.path,  "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
 
@@
 #                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# load(paste(project.path,  
-#            "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
-load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+load(paste(project.path,
+           "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
+# load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
 
@@
             cred_lower = hdi_lower(val))
+
 fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
 fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
+
 m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
@@
    guides(fill = F)
-##habituals.endorsement.bar
+#habituals.endorsement.bars
+#fixed.hab.params.posterior
 #fixed.hab.params.posterior
@@
 As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data.
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$.
+Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(p_f)$, which we use for both fixed-threshold and uncertain-threshold models.
 We assume the referent-prevalence $h'$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
@@
 ```{r hab-fixed-parameters}
-
 ```
@@
 
-The fixed-threshold model is ill-defined for this data set.
+The fixed-threshold model exhibits a small dynamic range of endorsements. 
+The data analytic model infers that a low threshold is likely: the inferred threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
+`r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].
+The lowest frequency used in our data set was $0.6$ times per year (3 times every 5 years).
+Thus, all of the utterances evaluated under this fixed-threshold model were literally true.
+Therefore, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
+
+Differences in endorsement rate are due to the informativeness of the fixed-threshold model.
+This varies by items, but not by frequency within an item, analogous to how "some" is equally true of 20\% or 50\%.
+
 The data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
 `r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise.
-The inferred (fixed) threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
-`r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`]. 
-That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise. 
-Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[
-  An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some"). 
-  This model would explain even less data than the current model (if it was better, this situation would have been inferred).
-  That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
-]
-
-<!-- The lowest frequency used in our data set was $0.2$ times per year.  -->
-<!-- Thus, all of the utterances evaluated under a fixed-threshold model were literally true.  -->
+
+<!-- That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise.  -->
+<!-- Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[ -->
+<!--   An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some").  -->
+<!--   This model would explain even less data than the current model (if it was better, this situation would have been inferred). -->
+<!--   That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
+-->
+<!-- ] -->
+
+<!-- The fixed-threshold model is ill-defined for this data set. -->
+<!-- The data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`, -->
+<!-- `r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise. -->
+<!-- The inferred (fixed) threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`, -->
+<!-- `r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].  -->
+<!-- That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise.  -->
+<!-- Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[ -->
+<!--   An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some").  -->
+<!--   This model would explain even less data than the current model (if it was better, this situation would have been inferred). -->
+<!--   That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
+-->
+<!-- ] -->
 

### 2017-12-22 paper/case2-habituals.Rmd
clean up first half of habituals

@@
 
-<!-- of particular importance to social psychology because of their role in causal attribution [@Kelley1973] and intuitive theories of personality and behavior [@]. -->
-
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-<!--  explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family".  -->
-<!-- A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
--->
-
-<!-- We meet new people all the time, and hear about them at least as often. -->
-<!-- *Habitual language* (e.g,. "Mary smokes."; "My car won't start.") conveys generalizations about events, including people doing actions.  -->
-<!-- In this case study, we focus on a particular class of events: people doing actions. -->
-
-<!-- We focus on present-tense habitual sentences of the form  -->
 To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
-First, we measure the prevalence prior distribution for different actions (e.g., how often different people smoke cigarttes; Expt. 2a).
-We then measure endorsements of generalizations about events (*habituals*), while manipulating the frequency with which the event occurs (e.g., how often Mary smokes; Expt.
-2b), and use our computational model to predict habitual endorsements.
+We take event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).
+For the generalization "Mary smokes", instances of the category being generalized are *instances of Mary* and if for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
+We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarttes; Expt. 2a).
+We then measure endorsements of habitual statements while manipulating the *referent-prevalence*  (Expt. 2b), and use our computational model to predict habitual endorsements. 
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-By describing novel characters to participants, we are able to directly the manipulate the frequency (prevalence) with which the referent does the action.
+By describing novel characters to participants, we are able to directly the manipulate the *referent-prevalence* (rate), which we were unable to do for generalizations about familiar categories.
 <!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
-Our computational model predicts endorsement rates given a referent-prevalence $h$. 
-Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive rate of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
-We extend our theory by measuring participants' predictions about future frequencies and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
+Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
+Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
+We extend our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
 We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
@@
 
-In this experiment we elicit the prior distributions over frequencies for different events in order to generate model predictions for corresponding habitual statements (measured in Expt. 2b \& 2c).
-For language about the behaviors of people, $P(h)$ represents a language user's background knowledge about the  frequency of doing the behavior; this can be conceived as a distribution over *different people*, each of whom do the behavior with different rates.
-We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt.
-1 (namely: that the distribution over prevalence can be represented as a mixture of those with a stable causal mechanism that gives rise to the feature and those without such a mechanism).
-For background knowledge of people doing actions, we consider again two components^[
+In order to generate model predictions for corresponding habitual statement, we first elicit the prior distributions over rates for different events.
+For language about the behaviors of people, $P(p_f)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
+We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1 .
+In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not.^[
   In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
   We assume here a simple structure so as to not make the specification of the prior overly complex.
-], which we operationalize by *people who have done the action before* and *people who have not the action before*.
-We measure how often people do the action, among those who have done it before, as well as the people's beliefs about the how many people have done the action before; we assume for simplicity that people who have never done the action before will rarely do the action.
-
-<!-- In Expt. 1a, we discovered that feature-probability prior distribution can be modeled by a mixture model with two components. -->
-<!-- The first component (the "stable cause" component) represents the normal, stable probability of the feature, among those categories that normally have the feature. -->
-<!-- The second component (the "unstable" or "transient cause" component) represents the probability of the property among those categories who do not typically have the property.  -->
-<!-- This second component will usually result in feature-probabilities of 0\% (e.g., 0\% of lions have lay eggs), but could produce non-zero probabilities (e.g., in some hypothetical world, a lion who has undergone weird genetic mutations may lay eggs).
--->
+]
+With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
+We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people).
+We will aassume for simplicity that people who have never done the action before will rarely or never do the action.
 
@@
 To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
-For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. \emph{eating} caviar vs. peanut butter).
+For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. *writing* poems vs. novels).
 The events were chosen to intuitively cover a range of likely frequencies.
 In total, thirty-one events were used.
-For a full list the stimulus set, see \mht{Appendix}.
+For a full list the stimulus set, see Appendix D.
 
@@
 
-For each event, participants were asked two questions, with different dependent measures:
+For each event, participants were asked two questions, with different dependent measures. 
+These questions were designed to measure the two central components of the prevalence prior model.
+We anticipated there to be different beliefs about the rates and relative proportions of peopel depending on whether an actor is male or female, so we asked about both genders separately.
 
@@
 
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}; default: 1000).
+Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}, incremented by 10x; default setting: 1000).
 
@@
 
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default: year).
+Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default setting: year).
 \end{enumerate}
 
-For example, one set of prompts read: "How many women have smoked cigarettes before?"; "For a typical woman who has smoked cigarettes before, how frequently does he smoke cigarettes?"
+For example, one set of prompts read: "How many women have smoked cigarettes before?"; "For a typical woman who has smoked cigarettes before, how frequently does she smoke cigarettes?"
+Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
 The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials and tested for recall on a subsequent trial.
-They responded to this attention check by selecting an option from a drop-down menu consisting of four options. 
-For the experimental trials, we anticipated there to be different beliefs about the frequency of events depending on whether the actor is male or female, so we asked about both genders.
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
+Participants responded to this attention check by selecting an option from a drop-down menu consisting of four options (one correct description of the questions and three distractors).
 
@@
 
+# for displaying in text
+n.items.habituals.prior.modeling <- length(rs.habituals.bda.prior.summary.wide$item)
+
 rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
@@
                   aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-
-#figure.habituals.priors.scatter
 ```
@@
 Question 1 elicits the proportion of people who have done an action before. 
-We rescale this to be a number between 0 and 1, and assume it was generated from a Beta distribution: $d_{Q1} \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1})$. 
-Question 2 elicits the rate or frequency with which a person (who has done the action before) does the action.
-We model this as generated by a log-normal distribution: $\ln d_{Q2} \sim \text{Gaussian}(\mu_{Q2}, \sigma_{Q2})$.
+We rescale this to be a number between 0 and 1, and assume it was generated from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma, \xi)$. 
+Question 2 elicits the rate with which a person (who has done the action before) does the action.
+We model this as generated by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu, \sigma)$.
 Each item was modeled independently for each gender.
@@
 The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter):
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2} = 0.74$).
+We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2}(`r  n.items.habituals.prior.modeling`) = `r round(with(rs.habituals.bda.prior.summary.wide, cor(mix_mean, sfreq_mean)),2)`$).
 Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
@@
 To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
-The only difference is that we estimate the mixture component directly from responses to Question 1. 
+The only difference is that we estimate the mixture component $\phi$ directly from responses to Question 1. 
 We assume that those who have not done the action before will probably not do the action in the future. 
@@
 
-In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(93) = 0.91$.
-This may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, the \emph{comparison class} is other people; not just other men or women).
-Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
-We now turn to our model-based analyses.
-For all analyses, we collapse across gender of the referent character,
-
 ### Endorsement model comparison
@@
 d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
+  #filter(habitual %in% gendered.items) %>%
   group_by(habitual, characterGender, time_period) %>%
@@
 r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
-
-ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-                 xmin = low_female, ymin = low_male,
-                 xmax = high_female, ymax = high_male, fill = habitual))+
-  geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-                    filter(time_period== "month"), aes(label = habitual,
-                                                       color = habitual),
-                  force = 3, nudge_x = -1, segment.size = 0.3)+
-  guides(fill = F, color = F)+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_point(shape = 21)+
-  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-  scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-  coord_fixed()+
-  xlab("Habitual endorsement (female character)")+
-  ylab("Habitual endorsement (male character)")+
-  scale_fill_solarized()+
-  scale_color_solarized()
-
+n.habituals.gendered.analysis <- length(d.hab.bayes.gendered.wide$habitual)
+r.habituals.gendered.analysis <- round(with(d.hab.bayes.gendered.wide, cor(map_female, map_male)), 3)
+
+d.hab.bayes.gendered.subset <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender, time_period) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.bayes.gendered.subset.wide <- left_join(
+    d.hab.bayes.gendered.subset %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
+    select(-characterGender),
+  d.hab.bayes.gendered.subset %>%
+    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
+    select(-characterGender)
+)
+
+n.habituals.gendered.subset.analysis <- length(d.hab.bayes.gendered.subset.wide$habitual)
+r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, cor(map_female, map_male)), 3)
+
+# ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
+#                  xmin = low_female, ymin = low_male,
+#                  xmax = high_female, ymax = high_male, fill = habitual))+
+#   geom_text_repel(data = d.hab.bayes.gendered.wide %>%
+#                     filter(time_period== "month"), aes(label = habitual,
+#                                                        color = habitual),
+#                   force = 3, nudge_x = -1, segment.size = 0.3)+
+#   guides(fill = F, color = F)+
+#   geom_abline(intercept = 0, slope = 1, lty = 3)+
+#   geom_point(shape = 21)+
+#   geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
+#   scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+#   scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
+#   coord_fixed()+
+#   xlab("Habitual endorsement (female character)")+
+#   ylab("Habitual endorsement (male character)")+
+#   scale_fill_solarized()+
+#   scale_color_solarized()
+# r2.habituals.gendered
+#n.habituals.gendered.subset.analysis
+#r.habituals.gendered.subset.analysis
 ```
@@
 fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
-  filter(B %in% c("noise", "fixedThreshold")) %>%
+  filter(type == "param") %>%
+  #filter(B %in% c("noise", "fixedThreshold")) %>%
   group_by(B) %>% 
@@
 
+hab.uncertain.threshold.s1opt <- m.hab.samp %>% 
+  filter(type == "param") %>%
+  group_by(param) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
 fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
 fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
+hab.fixed.threshold.s1opt <- filter(fixed.hab.params.posterior, B == "speakerOptimality")
 
@@
         )
-#habituals.endorsement.models
+habituals.endorsement.models
 ```
@@
 
-<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model to better understand the data and the contribution of our model.
-
-#### Frequency baseline
+In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(`r n.habituals.gendered.analysis`) = `r r.habituals.gendered.analysis`$.
+Endorsements are even more highly correlated for the six events we anticipated differences by referent-gender:  $r(`r n.habituals.gendered.subset.analysis`) = `r r.habituals.gendered.subset.analysis`$
+This lack of a difference may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, in minimal contexts such as this, habituals are evaluated with respect to *other people*, not just other men or other women).
+Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
+
+We now turn to our model-based analyses to better understand the endorsement data and the contribution of our model.
+For all analyses, we collapse across gender of the referent character for endorsement judgments.
+Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model.
+Analyses which use the rate prior distribution $P(p_f)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prior distribution.
+To model the uncertainty in the input measurements, we bootstrap the data for the regression models and we construct joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-thresold).
+
+#### Referent frequency
 
 To understand the role of frequency in habitual endorsement, we use the frequency supplied to the participants in our experiment as a predictor in a linear model. 
-This model predicts the same endorsement level for two actions done with the same frequency. 
+This model predicts the same endorsement level for two actions done with the same rate. 
 Obvious counterexamples exist in our data set:
@@
 hikes" and not willing to say that a person "...
-runs"  (Figure \@ref(fig:habituals-endorsement-figure) A).
-Overall, the referent-frequency (log-frequency of action) predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$).
+runs".
+Some actions done with a relative high rate (e.g., 3 times in a month) do not receive full endorsement (e.g., *smokes cigarettes*; Figure \@ref(fig:habituals-endorsement-figure) A).
+Overall, the referent-frequency (in log-scale) predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$).
 In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$).
-The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because of the larger stimulus set and presence of multiple referent-frequencies per item.
+The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because we designed the stimulus set to be critical of a referent-frequency model.
 <!-- An account purely based on the referent frequency does not explain endorsements in this data set. -->
@@
 
-#### Distinctiveness and frequency baseline
+#### Distinctiveness and referent frequency
 
 In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)).
-This parameter can be viewed as a measure of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
-We again construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
+This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus is relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
+Thus, we take this parameter as an index of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
+We construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
 We use participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency given to participants to predict habitual endorsement.
@@
 
-We next examine an endorsement model based on a fixed-threshold semantics.
-A fixed-threshold model commits the habitual to conveying that a person *does the action with some frequency*, and that frequency is common to all actions.
-As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data.
-Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(p_f)$, which we use for both fixed-threshold and uncertain-threshold models.
-We assume the referent-prevalence $h'$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
-Additionally, to account for statements that would be literally false under this model (frequencies that fall below the fixed threshold), we include an additional noise parameter, as we did in Case Study 1.
-To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 3 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
+We next examine an information-theoretic endorsement model based on a fixed-threshold semantics.
+A fixed-threshold model commits the habitual to conveying that a person *does the action with some rate*, and the threshold on rates is common to all actions.
+As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data (for more details on model implementation, see Appendix C).
+We assume the referent-prevalence $p_{fk}$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
+Additionally, to account for statements that would be literally false under this model (frequencies that fall below the fixed threshold), we include an additional noise parameter, as we did for the fixed-threshold model in Case Study 1.
+To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
 
@@
 
-The fixed-threshold model exhibits a small dynamic range of endorsements. 
 The data analytic model infers that a low threshold is likely: the inferred threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
 `r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].
-The lowest frequency used in our data set was $0.6$ times per year (3 times every 5 years).
+Compare this with the lowest referent-frequency used in our data set: $0.6$ times per year (3 times every 5 years).
 Thus, all of the utterances evaluated under this fixed-threshold model were literally true.
-Therefore, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
-
-Differences in endorsement rate are due to the informativeness of the fixed-threshold model.
-This varies by items, but not by frequency within an item, analogous to how "some" is equally true of 20\% or 50\%.
-
-The data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
-`r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise.
+As a result, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
+The fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model.
+
+A fixed-threshold utterance updates the interpreter model's beliefs differentially depending on the item.
+For instance, it's highly unlikely that a random person *climbs mountains* with any non-zero rate; thus this model fully endorses "Mary climbs mountains" even with low-frequency (Figure \@ref(fig:habituals-endorsement-figure) A).
+However, the model doesn't differentiate doing the same action with different frequencies.
+It is equally true that a person does an action *with some frequency* for any frequency greater than zero, analogous to how "some Ks F" is equally true if 20\% or 50\% of Ks F.
+
+Finally, the data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
+`r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise and that the speaker optimality parameter is `r round(hab.fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(hab.fixed.threshold.s1opt[[1,"cred_lower"]], 2)`,
+`r round(hab.fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
 
@@
 We used the same data analytic approach for the uncertain threshold endorsement model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-Again, this model has two fewer parameters than the fixed-threshold model (no threshold parameter and no extrinsic noise process).
-As shown in Figure \@ref(fig:habituals-endorsement-figure) (top right: top right facet), the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model is able to do this. 
+Again, this model has two fewer parameters than the fixed-threshold model (no fixed-threshold parameter and no extrinsic noise process).
+As shown in Figure \@ref(fig:habituals-endorsement-figure)B, the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
+Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model achieves this. 
 An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is good statement to assert. 
-Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas the someone who went to the movies 3 times last month is fully a person who "goes to the movies".
+Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas someone who went to the movies 3 times last month more a person who "goes to the movies". 
 Only the uncertain-threshold model is able to draw this fine distinction.
@@
 
-In this case study, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
+In this case study, we manipulated rather than measured the referent frequency (e.g., the frequency with which a person drinks coffee).
 By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model (and in a way that a fixed-threshold model cannot account for).
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in the question.
+The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in question.
 
@@
 This design potentially confounds an important distinction for the language of generalization: Does the prevalence communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-In Expt. 2c, we investigate this question by manipulating and measuring *predictive frequency* and habitual endorsement, while keeping past frequency fixed.
+In Expt. 2c, we investigate this question by teasing apart *past* from *predictive frequency* and measuring its influence on habitual endorsement.
 

### 2017-12-22 paper/case1-generics.Rmd
minor edits; add footnote about hurdle models

@@
 ] 
-We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
-This "null distribution" is potentially present for all features in exactly the same way.
+We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
+  This assumption is similar in spirit that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
+]
+This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
 The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.

### 2017-12-22 paper/case2-habituals.Rmd
minor edits; add footnote about hurdle models

@@
 "John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.', eval=F}
+Labeled points all correspond to the time period of 3 times / month.'}
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
@@
   filter(type == "param") %>%
-  group_by(param) %>%
+  group_by(B) %>%
   summarize(MAP = estimate_mode(val),
@@
         )
-habituals.endorsement.models
 ```
@@
 
-While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
+While past frequency is often a good indicator of future tendency, the future is under no obligation to mimic the past.
 Does habitual language communicate probabilities in terms of past frequency or future expectations?
 On one hand, speakers can only be certain about what has happened in the past.
-On the other hand, language has a communicative function, and it would seem useful for speakers to convey their predictions of what will be the case in the future.
-
-We address this by introducing causal events that either enable or prevent future actions.
-In one condition, participants make a prediction about what will be the case in the future (*predictive frequency*).
+On the other hand, language has a communicative function, and it would be useful for speakers to convey their predictions of what will be the case in the future.
+
+People can change their behavior abruptly due to a variety of decisions and outside events.
+We introduce these causal events into our minimal endorsement paradigm and measure their influence on endorsement.
+<!-- that either enable or prevent future actions. -->
+To provide the appropriate model-based analysis, participants in one condition make a prediction about what will be the case in the future (*predictive frequency*).
 In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
@@
   multi_boot_standard(col = "logAnnualPredictiveRate")
+
+r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
+n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)
 
@@
 We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-See Table \mht{one table for Expt 2 stimuli} for a full list of the enabling and preventative information.
+See Appendix D for a full list of the enabling and preventative information.
 
@@
 
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency. 
+Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
+We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r r.hab.pred.past.baseline.freq`$). 
 That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
 This result implies that our model makes identical predictions for Expt.
-2b whether the target is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
+2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
 Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
@@
 We use our formal model to test whether past or predictive frequency matters for endorsement.
-To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $h'$ that the endorsement model (Eq. \ref{eq:S1}) conditions on. 
+To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p_{fk}$ that the endorsement model (Eq. \ref{eq:S1}) conditions on. 
 The past frequency model is constructed using the past frequency supplied to participants as the referent-prevalence.
 We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before, and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
+We use the same priors over the parameters as before and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
 Figure \ref{fig:habituals-predictive-figure}C shows the resulting model predictions for the past frequency and the predictive frequency endorsement models. 

### 2017-12-22 paper/comgen-paper.Rmd
play around with plots, edits to habituals fixed model results
minor edits; add footnote about hurdle models

@@
     Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which such statements are true or which are false.
-    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
+    The major issue in formalizing generalization in language is determining which statements are true or which are false.
+    Using an information-theoretic probabilistic model, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
+    To test this theory, we examine endorsements of generalizations about three different domains: categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
     Across these diverse domains, we find that our model explains the wide variance in human endorsements of language conveying generalization, while simpler models fall short.
     Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results suggest the central phenomena emerge from the interaction of underspecified meaning with diverse beliefs about properties.
+    The results demonstrate that the context-sensitivity of such language emerges from the interaction of an underspecified meaning with diverse beliefs about properties.
 
@@
 By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
+Flexibly communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
 
@@
 
-The language of generalization is often studied via *generic language* (or, generics): simple statements  about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+The language of generalization is often studied via *generic language* (or, *generics*): simple statements predicating properties of categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
 Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
@@
 -->
-Generics are just one case of the language of generalizations, however; events can be described in generalizations (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed that every language can express generalizations [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
+Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
+Every language, it is believed, can express generalization [@Behrens2005; @Carlson1995] and is central to the growth of conceptual knowledge [@Gelman2004].
+Considering generalization as a singular phenomenon in language, thus, promises to provide understanding of a wide variety of linguistic expressions with powerful implications.
 
@@
 
-Despite their ubiquity and relative simplicity, there have been few formal models of this language and none that have made precise, quantitative predictions to match human intuitions. 
-The major challenge in formalizing the language of generalizations is in determining *what makes the statements true or false*.
+Despite their ubiquity and relative simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions.
+The major challenge in formalization is determining *what makes the statements true or false*.
 When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
@@
 The generalization could signal something weaker like "Most dogs bark".
-However, "Most mosquitos do not carry malaria" (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
+However, most mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
 The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to "some" is too permissive: "Some Robins are female" (in fact, half of them are), but asserting "Robins are female" seems odd.
+But weakening the generalization to mean "some" is too permissive: some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
 Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
 
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not central to the meaning of generalizations in language.
+These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only parameter in the meaning of generalizations.
 Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-A paradigm case is the statement "Bishops move diagonally", which is true but not because bishops tend to move diagonally but rather because those are the rules of the game.
+"Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
 It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
 One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature. 
-Whatever their mode of reproduction, regardless of the actual prevalence of the feature, will make a true generic statement (e.g., "Robins lay eggs").
-*Horrifying* or *striking* is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is felicitous.
-
-Examining a wider range of examples makes one realize that generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships sound like true generics true.
+Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature.
+*Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true
+
+Yet, generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
+Purely arbitrary relationships can result in true generics.
 <!-- Arbitrary relationships are also expressed with generics:  -->
-For example, "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are blue" would be true.
-Ravens and toasters have no priviledge relationship to each other, but the statement "Ravens are bigger than toasters" is still a true genaralization.
-Conceptual accounts must then be supplemented with the proviso that, in some situations, the actual prevalence of the feature does influence human intuitions about generics.
+"Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false.
+Ravens and toasters have no priviledged relationship to each other, but the statement "Ravens are bigger than toasters" is still a true generalization.
+Conceptual accounts must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.
 
 What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that convey generalizations, there should be something common to them all: a general, unified semantic core.
-The test of a unified semantic core is its ability to explain what makes the statements true or false.
+But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
+In this paper, we propose such a semantic core for the language of generalization.
+To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
+Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
+To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would use when understanding such language.
+We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
+The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
+Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
+
+<!-- The test of a unified semantic core is its ability to explain what makes the statements true or false. -->
 
@@
 -->
-
-In this paper, we propose a semantic core for the language of generalization.
-To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-We then consider the background knowledge that listeners bring to bear when interpreting generalizations, and formalize an endorsement model based on this interpretation hypothesis.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-Our endorsement model is the first formal theory that makes quantitative predictions about what makes generalizations in language true or false; the assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-
 <!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
@@
 The paper is organized as follows. 
-In Section 1, formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions about depend upon the background knowledge and the probability communicated. 
+In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
+The endorsement model's predictions depend upon the background knowledge and the probability communicated, which we demonstrate via simulation.
 Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and probability communicated and measure its effect on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$).
+Across these three case studies, we both measure and manipulate background knowledge and the probability communicated, measuring their effects on endorsement. 
+We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alterantive models fall short.
+This work opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
+
+<!-- (cumulative $r^2(N) = 0.XX$). -->
 <!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
@@
 <!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-This opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
 
@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **prevalence**.
+This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ (formally, be in the set of things that have $f$) given that it is in $k$, which we will refer to as the **prevalence**.
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
@@
 We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
-$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief due to background knowledge.
+$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief.
 
@@
 For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because what one would expect for a randomly-sampled category is that it has 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
+Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
 Conceptual differences can manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
@@
 For a more thorough derivation of this relationship, see Appendix A.
-The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potentialy shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
+The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potential shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
 This is particularly problematic for prevalence distributions that encode conceptual knowledge via multimodal distributions (e.g., Fig.
@@
 We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL [@rwebppl] in the RMarkdown document that generated this paper text and figures.
+The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
 That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
@@
 We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent-prevalence.
-Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers].^[
+Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers1963].^[
   Note that this assumption is consistent with the comparison classes we have assumed in our three case studies.

### 2017-12-22 paper/case3-causals.Rmd
adjust notation

@@
                               levels = c("state_Prior","state_Posterior"),
-                            labels = c("Feature-probability Prior (Expt. 3a)",
+                            labels = c("Prevalence prior (Expt. 3a)",
                                        "Interpreter model posterior")),
@@
 A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies.
-B: Background, feature-probability prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors.
-Endorsement mode predictions, interpreter model posteriors, and feature-probability priors are inferred using both Expt.
-3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix."}
+B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors.
+Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt.
+3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}
 

### 2017-12-23 paper/appendix-bda.Rmd
improve causal expt figure; simulation figure

@@
 ```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
-The feature-probability prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
+The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
 1a.
-The referent-category feature-probability $d^{pr}_{k,f}$ is generated from a latent feature-probability $h_{k,f}$.
-The fixed-threshold (control model) or uncertain-threshold RSA model takes the feature-probability prior $P_f(h)$, the referent-category feature-probability $h$, and a single speaker optimality parameter $\\lambda$ as input.
+The referent-category prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
+The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P_f(h)$, the referent-prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
-Note that RSA corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; RSA cannot be represented by a graphical model because it has recursion.
+Note that S corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; S cannot be represented by a graphical model because it has recursion.
 "}

### 2017-12-23 paper/case3-causals.Rmd
improve causal expt figure; simulation figure

@@
 ```{r causalExpt, fig.cap="Overview of Experiment 3.
-A: Results of previous experiments are shown one at a time.
-One of the results were lost.
-B: Particiapnts are asked to review results before continuing.
-C: Prior elicitation task.
-D: Causal endorsement task."}
-knitr::include_graphics("figs/causal-expt.pdf", dpi = 108)
+A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table.
+One of the results was lost.
+Participants are asked to review previous results once all displayed.
+B: Prior elicitation task: Participants predict the results of the next 5 experiments.
+D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10}
+caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
+  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
+caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
+  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
+caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
+  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
+caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
+caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)
+
+caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh')
+
+title <- ggdraw() + draw_label("Prevalence prior manipulation")
+plot_grid(
+  plot_grid(title, caus.exp.toprow, ncol=1, rel_heights=c(0.1, 1)),
+  plot_grid(add_sub(caus.exp.4, "Prior elicitation"), add_sub(caus.exp.5,"Causal endorsement"), labels = c("D", "E"), nrow = 1),
+  nrow = 2)
 ```
@@
   scale_color_manual(values = inset.color.order)+
+  geom_vline(xintercept = 0.2, lty = 3)+
+  geom_vline(xintercept = 0.7, lty = 3)+
   scale_alpha_manual(values = c(0.8, 0.1))+
@@
 B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors.
+Vertical lines denote referent-prevalence levels for the causal endorsement task.
 Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt.

### 2017-12-23 paper/comgen-paper.Rmd
improve causal expt figure; simulation figure

@@
   guides(fill = F)+
-  ylab("Endorsement")+xlab("Referent prevalence")+
+  ylab("")+xlab("Referent prevalence")+
   theme(strip.text.y = element_text(angle = 0, hjust = 0)
@@
 ```{r simulations, fig.cap = "Computational model behavior.
-A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different posterior interpretations.
+A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations.
 C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
@@
 
-prow <- plot_grid( p1 + theme(legend.position="none"),
-           p2 + theme(legend.position="none"),
-           p3 + theme(legend.position="none"),
-           p4,
+prow <- plot_grid( 
+  add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
+  add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
+  add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
+  add_sub(p4, "Endorsement"),
            align = 'vh',
@@
            #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 3, 1.05, 1.7)
+           rel_widths = c(1.2, 2.9, 1.15, 1.7)
            )

### 2017-12-26 paper/comgen-paper.tex
add tex file and figures for simple compiling

\documentclass[english,floatsintext,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The language of generalization: Probability, vagueness, and interaction},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{The language of generalization: Probability, vagueness, and interaction}

  \shorttitle{The language of generalization}

  \author{Michael Henry Tessler\textsuperscript{1}~\& Noah D. Goodman\textsuperscript{1}}

  \def\affdep{{"", ""}}%
  \def\affcity{{"", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Department of Psychology, Stanford University  }

  \authornote{
    \newcounter{author}
    This manuscript is currently in prep. Comments or suggestions should be
    directed to MHT.

                      Correspondence concerning this article should be addressed to Michael Henry Tessler, 450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305. E-mail: \href{mailto:mtessler@stanford.edu}{\nolinkurl{mtessler@stanford.edu}}
                          }

  \abstract{Generalizations are central to human understanding and language provides
simple ways to convey them (e.g., ``Birds fly''). The language of
generalization is ubiquitous in everyday discourse and child-directed
speech. Yet the meaning of these expressions is logically puzzling
(e.g., not all birds fly) and has resisted precise formalization. The
major issue in formalizing generalization in language is determining
which statements are true or which are false. Using an
information-theoretic probabilistic model, we explore the hypothesis
that the meaning of these linguistic expressions is \emph{simple but
underspecified}, and that general communicative principles can be used
to establish a more precise meaning in context. To test this theory, we
examine endorsements of generalizations about three different domains:
categories (\emph{generic language} e.g., ``Birds fly''), events
(\emph{habitual language} e.g., ``John runs''), and causes (\emph{causal
language} e.g., ``Staring at the sun makes you go blind''). Across these
diverse domains, we find that our model explains the wide variance in
human endorsements of language conveying generalization, while simpler
models fall short. Ours is the first formal theory that makes precise,
quantitative predictions about human understanding of the language of
generalization. The results demonstrate that the context-sensitivity of
such language emerges from the interaction of an underspecified meaning
with diverse beliefs about properties.}
  \keywords{genericity, generalization, generics, pragmatics, semantics, bayesian
modeling \\

    \indent Word count: 20000
  }

  \usepackage{tabularx}
  \usepackage{multicol}
  \usepackage{wrapfig}
  \usepackage{caption}
  \usepackage{booktabs}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{subcaption}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{multirow}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}

\definecolor{Red}{RGB}{255,0,0} \definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}

\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}

\section{Introduction}\label{introduction}

Learning that an object tends to have a property, an entity tends to
exhibit a behavior, or a cause tends to produce an effect can be crucial
to thrive in our open-ended world. Yet such knowledge can be difficult
to acquire: Relevant observations may be costly (e.g., learning that a
plant is poisonous) or rare (e.g., understanding that lightning strikes
tall objects). It thus is important that language allow us to
communicate such \emph{generalizations} to each other. By sharing
generalizations, we flourish collectively without individually needing
to taste potentially-poisonous plants or personally witness many
lightning strikes. Flexibly communicating generalizations from one
generation to the next may be a foundational mechanism behind the
faithful transmission of knowledge necessary for cumulative cultural
evolution (Henrich, 2015; Tomasello, 1999).

The language of generalization is often studied via \emph{generic
language} (or, \emph{generics}): simple statements predicating
properties of categories (e.g., ``Dogs are friendly''; Carlson, 1977;
Cohen, 1999; Leslie, 2007; Nickel, 2008). Generics are ubiquitous in
everyday conversation as well as in child-directed speech (Gelman,
Goetz, Sarnecka, \& Flukes, 2008). In contrast to \emph{particular
statements} (e.g., \enquote{Rufus is friendly}) which describe
individual entities or situations and can be verified through
observation, generic statements refer to inherently unobservable
categories (e.g., the category of \textsc{dogs}) and convey information
that extends beyond the present context, a fact which children as young
as 2 appreciate (Cimpian \& Markman, 2008). Generics are just one case
in the language of generalization, however; events can be described in
generalization (\emph{habitual language}; e.g., \enquote{Mary swims
after work.}) as well as causal relationships (\emph{causal language};
e.g., \enquote{Staring at the sun makes you go blind.}). Every language,
it is believed, can express generalization (Behrens, 2005; Carlson \&
Pelletier, 1995) and is central to the growth of conceptual knowledge
(Gelman, 2004). Considering generalization as a singular phenomenon in
language, thus, promises to provide understanding of a wide variety of
linguistic expressions with powerful implications.

Despite their ubiquity and relative simplicity, there have been few
formal models of the language of generalization and none that have made
precise, quantitative predictions to match human intuitions. The major
challenge in formalization is determining \emph{what makes the
statements true or false}. When we hear \enquote{Dogs bark}, it sounds
like a universal statement, as in \enquote{All dogs bark}. But the
property does not apply to all dogs: Basenji dogs are barkless\footnote{\url{http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html}},
for example. The generalization could signal something weaker like
\enquote{Most dogs bark}. However, most mosquitos do not carry malaria
(in fact, only a tiny fraction do), but \enquote{Mosquitos carry
malaria} is intuitively true. The only quantifier that would permit such
a statement would be \enquote{some} (e.g., \enquote{Some mosquitos carry
malaria}). But weakening the generalization to mean \enquote{some} is
too permissive: some robins are female (in fact, half of them are), but
asserting \enquote{Robins are female} seems odd. Even more perplexing:
Those very same female robins lay eggs, and \enquote{Robins lay eggs} is
a perfectly fine thing to say.

These observations have led to the conclusion that the prevalence of the
feature (or the probability of a member of the category having the
property e.g., \(P(x \text{ barks} \mid x \text{ is a dog})\)) is not
the only parameter in the meaning of generalizations. Conceptual
accounts of generics emphasize the structure of \emph{generic knowledge}
(Prasada, 2000), and view generic utterances as the way of expressing
special, mental relationships between kinds and properties (Leslie,
2008; Prasada, Hennefield, \& Otap, 2012). \enquote{Bishops move
diagonally} not because bishops tend to move diagonally but rather
because those are the rules of the game. It's been suggested that the
mind has cognitive primitives that directly dictate what generalizations
are true or false. One such primitive is the ability to priviledge
\emph{characteristic features}: For an animal, their mode of
reproduction is a characteristic feature. Thus, whatever their mode of
reproduction may be will make a true generic statement (e.g.,
\enquote{Robins lay eggs}), regardless of the actual prevalence of the
feature. \emph{Horrifying} or \emph{striking} information is also
priviledged and creates true generics, which is why \enquote{Mosquitos
carry malaria} is true

Yet, generics convey more than just rich, conceptual relations (Nickel,
2008, 2016; Sterken, 2015). Purely arbitrary relationships can result in
true generics. \enquote{Barns are red} because barn-owners tend to paint
their barns red; were barn-owners to decide tomorrow to switch to blue,
then \enquote{Barns are red} would be false. Ravens and toasters have no
priviledged relationship to each other, but the statement
\enquote{Ravens are bigger than toasters} is still a true
generalization. Conceptual accounts must be supplemented with the
proviso that, in some situations, the actual prevalence of the feature
matters for making generalizations true.

What we are left with is hybrid theories, which try to classify
different kinds of generalizations and the various inferences they
support (e.g., Prasada, Khemlani, Leslie, \& Glucksberg, 2013). But
insofar as there is a single class of linguistic expressions that convey
generalization, there should be something common to them all: a general,
unified semantic core. In this paper, we propose such a semantic core
for the language of generalization. To do so, we look to probability,
the universal currency of belief and a useful representation for human
generalization from observations (Shepard, 1987; Tenenbaum \& Griffiths,
2001). Given that certain probabilities are the result of inductive
generalization, it would make sense that these are the object of
communication in the language of generalization. To formalize a model of
endorsement (i.e., what makes the statements true or false), we consider
the information-theoretic function of a generalization by explicitly
modeling the background knowledge a language interpreter would use when
understanding such language. We create an endorsement model based on
this interpretation hypothesis, providing the first formal theory that
makes quantitative predictions about what makes generalizations in
language true or false. The assumptions of the theory, and in turn, the
conditions under which the theory may be meaningfully tested are made
explicit by its instantiation in a formal model. Though concepts such as
\emph{striking properties} are not explicitly formalized in our model,
our general cognitive modeling framework provides natural avenues for
future integration.

The paper is organized as follows. In Section 1, we formalize the
hypothesis that the core of meaning of a generalization in language is
simple but \emph{underspecified}, articulate a thory of relevant
background knowledge used to understand a generalization in language,
and develop a computational model of endorsement around these
components. The endorsement model's predictions depend upon the
background knowledge and the probability communicated, which we
demonstrate via simulation. Sections 2 - 4 present our three empirical
case studies: generalizations about categories (\emph{generic
language}), events (\emph{habitual language}), and causes (\emph{causal
language}). Across these three case studies, we both measure and
manipulate background knowledge and the probability communicated,
measuring their effects on endorsement. We find a very strong agreement
of our model's predictions to the full spectrum of human elicited
endorsements, where alterantive models fall short. This work opens the
door to understanding generalizations in pragmatic language
understanding contexts and building models of learning from language.

\section{Computational Framework}\label{computational-framework}

Generalizations are used to make predictions about properties of
instances that an agent has yet to experience (Hume, 1888). People
readily predict that a new dog will have fur, drinking a new cup of
coffee will cause jitters, and a new day will find certain people
typing. In each case, we assign a specific exemplar \(x\) to a category
\(k\), and make a prediction that it will have property \(f\). This
prediction can be described by a conditional probability:
\(p_{fk} = P(x \in f \mid x \in k)\), the probability that \(x\) will
have \(f\) (formally, be in the set of things that have \(f\)) given
that it is in \(k\), which we will refer to as the \textbf{prevalence}.
The targets of our predictions can vary widely: They may be objects (a
dog), events (a coffee drink), or more fine grained types (a person on a
given day). The properties also vary (e.g., having fur, causing jitters,
typing). Yet the mathematical description of the inductive inference is
always given by the probability \(p_{fk}\).

How does one acquire such an inductive belief? Observing instances of
the category \(k\) and noting how many of them have \(f\) can support
prediction to new instances when integrated with one's prior
expectations about the property (cf., Gelman, 2003; Keil, 1992). For
example, if you observe creatures that \textsc{have two legs}, you might
infer that all creatures of that category have two legs. Observing new
creatures with \textsc{broken wings}, however, leads to a much weaker
prediction about other instances of the category having the property
(Nisbett, Krantz, Jepson, \& Kunda, 1983). This kind of domain-specific
knowledge about properties can be represented formally as a probability
distribution over the prevalence \(p_{f}\): \(P(p_{f})\) (Kemp \&
Tenenbaum, 2008), and observational data \(d\) can update one's beliefs
via Bayes' Rule:
\(P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})\)

Learning from observational evidence can only take you so far, though.
To learn about properties that are costly to observe (e.g.,
\emph{staring at the sun makes you go blind}) or events that are
statistically rare (e.g., \emph{lightning strikes tall objects}), one
would much rather learn from others. Fortunately, language has simple
ways of encoding generalizations.

\subsection{Generalization from
language}\label{generalization-from-language}

The language of generalization manifests when a property is predicated
of a category: \enquote{Ks F} (e.g., \enquote{Dogs bark},
\enquote{Staring at the sun makes you go blind}). Generalization from
observations can be described as a predictive probability; it is
intuitive then to posit that same quantity will be at the core of a
semantic theory of the language of generalization. To connect to the
semantic tools of \emph{truth values} (Montague, 1973), we must relate
the scalar quantity of probability to a Boolean value. One simple way is
with a \emph{threshold semantics}: An utterance is true if the relevant
quantity is above a threshold. A threshold semantics for a
generalization about category K with property F would then apply to the
\emph{prevalence} \(p_{fk}\):
\(\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}\)

Various attempts of this kind have been made before (e.g., Cohen, 1999).
We distinguish our proposal from previous ones by emphasizing the
cognitive underpinnings of \(p_{fk}\), as well as the formalization into
a model that makes precise, quantitative predictions about human
endorsements. \(p_{fk}\) describes a latent belief and should not be
confused with \emph{frequency}, which can inform a belief but is not
itself the belief.

\subsubsection{Literal interpretation
model}\label{literal-interpretation-model}

Quantifier statements can be described using a similar threshold
semantics:
\(\denote{some \text{ } K \text{ } F}(p_{fk}) = \{p_{fk} > 0\}; \denote{all \text{ } K \text{ } F} = \{p_{fk} = 1\}\).
So what threshold \(\theta\)? should be used for the generalizations?
Unlike quantified language which have fixed-thresholds, we posit that
the language of generalizations is \emph{underspecfied} with respect to
the actual truth-functional threshold \(\theta\). That is, we
hypothesize that \(\theta\) is in part determined by contextual, in a
way analagous to how gradable adjectives like \enquote{tall} have
contextually-determined thresholds (e.g., what counts as ``tall'' for a
four-year-old is different than what counts as ``tall'' for an adult;
Kennedy, 2007; Lassiter \& Goodman, 2013).

We formalize this underspecified semantics in a probabilistic model,
where the underspecifed threshold \(\theta\) is sampled from a uniform
prior distribution over possible thresholds \(P(\theta)\) (cf., Lassiter
\& Goodman, 2013). After making explicit the relevant background
knowledge about the property \(P(p_f)\), the model becomes:

\begin{eqnarray}
Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{f}, \theta)} \cdot P(p_{f}) \cdot P(\theta)} \label{eq:L0}
\end{eqnarray}

Equation \ref{eq:L0} (\(Lit\)) is a literal interpretation model, that
updates its beliefs about the prevalence of a feature in the category
described \(p_{fk}\) according to the truth-functional meaning of the
utterance \(u_{KF}\). Formally, the truth-functional meaning is
represented by the Kronecker delta function
\(\delta_{\denote{u}(p_{fk}, \theta)}\) that returns probabilities
proportional to \(1\) when the utterance is true (i.e., when
\(p_{fk} > \theta\)) and \(0\) otherwise.

\begin{eqnarray}
\delta_{\denote{u_{KF}}(p_{fk}, \theta)} &\propto  & \begin{cases}
1 & \text{if } p_{fk} > \theta \\
0 & \text{otherwise}
\end{cases}\label{eq:delta}
\end{eqnarray}

\subsubsection{Endorsement model}\label{endorsement-model}

Given the minimal model of literal interpretation described above, how
do we decide when a statement conveying a generalization is true or not?
We consider the notion of felicity or endorsement from the
information-theoretic perspective: Would a generalization convey
sufficient information to warrant the cost of production? We formalize
this by considering how well the generalization would convey the
prevalence \(p_{fk}\) to the \(Lit\) model (Eq. \ref{eq:L0})\footnote{A
  more general version of this model can relax the assumption that the
  endorsement model has access to a specific prevalence \(p_{fk}\) that
  it wants to communicate. Rather, the endorser may have a distribution
  over \(p_{f}\) for the category \(k\), corresponding to the endorser's
  uncertain beliefs about the prevalence. In this situation, we would
  define the endorsement model decision to be with respect to the
  expected value of the informativity, which integrates over the
  endorsement model's belief distribution:
  \(S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}\)
  For the empirical case studies described below, these two versions of
  the model make almost identical predictions.}.

\begin{equation} 
S(u \mid p_{fk}) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)  \diff \theta } )}
\label{eq:S1}
\end{equation}

The endorsement model simulates what the interpretation model would
believe upon hearing an utterance \(u\)):
\(Lit(p_{fk}, \theta \mid u)\). \(S\) is not interested in communicating
\(\theta\) (in fact, it does not know \(\theta\)), and so integrates
over the values of \(\theta\). We assume the decision to endorse is an
approximately rational one, with degree of rationality given by
\(\lambda\). The proportionality in Eq. \ref{eq:S1} implies
normalization over a set of alternative utterances. We interpret the
endorsement task (e.g., \enquote{true} vs \enquote{false};
\enquote{agree} vs. \enquote{disagree}) as supplying two alternatives:
\emph{endorse} or \emph{not}, where \emph{not} we take to be a silent
utterance that conveys no information content (Degen \& Goodman, 2014;
cf., Franke, 2014): \(\denote{null}(x, \theta) = \text{True}\)\footnote{This
  \enquote{null} alternative to the generalization (\enquote{Ks F}) can
  be realized in at least two other ways: the negation of the
  generalization (i.e., \enquote{It is not the case that Ks F}) or the
  negative generalization (i.e., \enquote{Ks do not F}). All results
  reported are similar for these two alternatives, and we use the
  alternative of the \enquote{silent} utterance for simplicity.}

Our endorsement model (Eq. \ref{eq:S1}) provides a straight-forward
mapping from a \emph{referent-category prevalence} \(p_{fk}\) (e.g.,
\(P(x \text{ lays eggs} \mid x \text{ is a robin})\)) to an endorsement
probability for the corresponding generalization (e.g., \enquote{Robins
lay eggs}): \(S(u = u_{KF} \mid p_{fk})\). The model assumes a threshold
semantics based on probability (prevalence) but does not require
specifying the threshold \emph{a priori} (note that there is no
\(\theta\) in the left-hand side of Eq. \ref{eq:S1}). This model can be
seen as a special case of a Rational Speech Act model (Frank \& Goodman,
2012; Goodman \& Frank, 2016), where there is only a single level of
recursion and the space of possible utterances is maximally constrained.

\subsubsection{Prevalence priors and
referent-prevalence}\label{prevalence-priors-and-referent-prevalence}

Our model makes context-sensitive predictions about endorsing
generalizations based on two model components: The prevalence priors
\(P(p_f)\) in Eq. \ref{eq:L0} and the referent-prevalence \(p_{fk}\) in
Eqs. \ref{eq:S1} and \ref{eq:delta}. Referent-prevalence is the
probability that an individual \(x\) of the referent-category (e.g.,
\enquote{Dogs}) will have the feature being predicated of the category
(e.g., \enquote{\ldots{}barks}). We will return and refine this
definition in Case Study 2, when considering generalizations about
events. For now, the referent-prevalence is simply a probability that
determines the truth-conditional semantics. Our hypothesis does not
provide a mapping from the referent-prevalence directly to endorsement
judgments, however, because \(\theta\) is underspecified.

The uncertain, truth-conditional threshold \(\theta\) is resolved by the
literal interpretation model \(Lit\) (Eq. \ref{eq:L0}) by integrating
prior beliefs about the feature in question---the \emph{prevalence
prior} \(P(p_f)\)---with the truth-functional semantics. Again,
\(P(\theta)\) is set to be a uniform distribution across all contexts,
and thus, the generalization could in principle be felicitious with
potentially any referent-prevalence. However, interpretation model's
\emph{a priori} beliefs \(P(p_f)\) must be considered before the
endorsement model can say whether or not it would endorse the
generalization.

Beliefs about properties result from internal conceptual models of the
world. These internal models have domain-specific features but should
all give to the domain-general currency of inductive reasoning:
probability. One way of constructing prior distributions over
prevalence, without appealing directly to domain-specific conceptual
knowledge, is by considering the prevalence of the feature among
different categories. For example, many different kinds of animals
\emph{do not bark} (more precisely: have close to 0 exemplars who bark);
thus, the prevalence prior for the feature \emph{barks} \(P(p_{barks})\)
should have substantial probability mass near 0, because what one would
expect for a randomly-sampled category is that it has 0 or close to 0
exemplars that bark. Furthermore, among the categories that do have
exemplars which bark (e.g., \emph{dogs}, \emph{seals}, \ldots{}), the
probability is quite high that an exemplar will bark; thus, the
prevalence prior should have substantial mass at relatively high values,
potentially with quite a bit of uncertainty;
Figure~\ref{fig:simulations}A; first row). Conceptual differences can
manifest in these prevalence priors in the form of multi-modal
distributions; for example, the prevalence prior for \emph{lays eggs}
should similiarly have substantial probability mass near 0 (since most
animal categories do not have egg-layers) but should have a secondary
component peaked around 0.5, because among the animals with egg-layers,
only the female members of the category have the property
(Figure~\ref{fig:simulations}A; bottom row).

By encoding knowledge about other categories, the prevalence prior
distributions are deeply connected to the construct of \emph{cue
validity}, or the probability that an entity with a certain property
\(f\) is a member of kind \(k\): \(P(x \in k \mid x \in f)\) (e.g.,
one's predictions about whether or not the entity is a robin, upon
learning that it lays eggs). \emph{Cue validity} implicitly encodes
knowledge of other categories and has been shown to be highly correlated
with endorsing \emph{generic sentences}, or generalizations about
categories (Khemlani, Leslie, \& Glucksberg, 2012). Cue validity is
defined for a particular (category, property) pair (as is
referent-prevalence), and relates to referent-prevalence by Bayes' Rule:

\begin{equation}
P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')} \label{eq:cuevalidity}
\end{equation}

Since \emph{cue validity} implicitly encodes knowledge of other
categories (by summing over \(k'\)) and the prevalence prior explicitly
encodes knowledge of other categories, how are these two constructs
related? In the prevalence prior \(P(p_f)\), a category is represented
only by its corresponding prevalence (i.e., a sample from the prevalence
prior can be thought of as a category \(k\), with the only information
available about the category being the prevalence of the feature in that
category \(p_{fk}\)). Thus, \(P(p_{fk}) = P(k_{f})\). The denominator of
Eq. \ref{eq:cuevalidity} (which encodes knowledge of other categories),
then, is the expected value (i.e., the mean) of the prevalence prior
distribution:
\(\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )\).
For a more thorough derivation of this relationship, see Appendix A. The
fact that the prevalence prior distribution relates only via its mean
value to \emph{cue validity} reveals a potential shortcoming of cue
validity: By reducing a distribution to a point estimate, the structure
of the distribution is lost. This is particularly problematic for
prevalence distributions that encode conceptual knowledge via multimodal
distributions (e.g., Fig. \ref{fig:simulations}A; bottom row); the mean
of a multimodal distribution is not a good representation of that
distribution. We return to this point empirically in Case Study 1.

\subsubsection{Model simulations}\label{model-simulations}

The endorsement model defined in the previous section explicitly
predicts that the variability in endorsements for generalizations in
language can be explained by two factors: (i) the prevalence
communicated in the category under discussion \(p_{fk}\) in Eq.
\ref{eq:S1} (e.g., \(P(x \text{ lays eggs} \mid x \text{ is a robin})\))
and (ii) the background knowledge about prevalences \(P(p_f)\) (Eq.
\ref{eq:L0}). We simulate how these two factors change both literal
interpretation and endorsement using schematic parameter values based on
intuition from classic examples in the literature on generic language.
We implemented these and all subsequent Bayesian models in the
probabilistic programming language WebPPL (Goodman \& Stuhlmüller,
2014). The following simulations were implemented using the R package
RWebPPL in the RMarkdown document that generated this paper text and
figures. That document, as well as all other models, analysis, data and
links to experiments used in this paper can be found at
\url{https://mhtess.github.io}.

\begin{figure}[htbp]
\centering
\includegraphics{figs/simulations-1.pdf}
\caption{\label{fig:simulations}Computational model behavior. A: Prior
distributions over the prevalence of a feature in a category for 6
example features B: Different fixed thresholds (columns) give rise to
different partial interpretations. C: The interpreter model averages
over all thresholds, producing posterior distributions that strongly
depend upon the priors. D: Endorsement model predictions, assuming a
particular referent-prevalence. Shapes of the priors were chosen to
intuitivly correspond to properties labeling the distributions.}
\end{figure}

The literal interpretation model computes a posterior distribution on
prevalence by considering different possible thresholds \(\theta\)
(Figure~\ref{fig:simulations}B). Low thresholds (e.g., \(\theta = 0.1\))
rule out very few possibilities (only \(p_{fk} \leq 0.1\)), and thus are
quite likely given that its consistent with much of the prevalence
prior. The flip-side of this is that the endorsement model is less
likely to produce an utterance with a low-threshold in mind, because the
end result would be similar to staying silent (a posterior not very
different from the prior). Higher thresholds (e.g., \(\theta = 0.9\))
rule out more possibilities and thus would be highly informative, but
the interpretation model must balance this with the prior probabilities
of the prevalences implied by the threshold
(Figure~\ref{fig:simulations}A).

The result of this reasoning process is a trade-off between highly
informative thresholds and the prior probabilities of the prevalences
implied by those thresholds. The prevalence-based interpretations of
generalizations of novel categories are shown in
Figure~\ref{fig:simulations}C. These interpretations depend heavily on
the prevalence priors (different rows). Hearing \enquote{Ks bark} tells
the literal interpretor that \emph{almost all} Ks bark, though there is
a good deal of uncertainty in the precise quantity (top row; pink).
\enquote{Ks lay eggs} has a strikingly different interpretation: It
means \enquote{Half of Ks lay eggs} (4th row; green). The literal
interpreter can also derive very weak interpretation, as shwon in the
\textsc{carries malaria} distribution (bottom row, purple).

The endorsement model (Eq. \ref{eq:S1}) predicts endorsement
probabilities based on the literal interpretation of the utterance and
the referent-category prevalence (e.g., how many robins lay eggs).
Predictions for a few classic examples from the generics literature are
shown in (Figure~\ref{fig:simulations}D). In accord with intuition, the
endorsement model predicts \enquote{Dogs bark}, \enquote{Robins lay
eggs}, and \enquote{Mosquitos carry malaria} are all true, despite the
referent-prevalences varying substantially between these three examples.
Intruigingly, the model predicts \enquote{Robins are female} (which has
the same prevalence as \enquote{Robins lay eggs}) should receive
intermediate endorsement: It is neither true nor false. To understand
this prediction, examine the interpretation distribution for the
\textsc{are female} distribution: It is identical with the prior
(Figure~\ref{fig:simulations} A vs.~C; blue distributions). The
endorsement model decides that is neither better nor worse to produce
the generalization than to stay silent, as they both carry the same
information content. This example can be contrasted with cases such as
\enquote{Sharks don't eat people} and \enquote{Kangaroos have spots},
which the model thinks would be misleading to say (i.e., better to say
nothing).

These simulations show how the model predicted endorsement depends upon
the background knowledge about the property \(P(p_f)\) as well as the
prevalence \(p_{fk}\) communicated. We chose schematic values for each
of these, and saw that the endorsement model recapitulates standard
intuitions about the truth or falsity of classic examples from the
generics literature. In what follows, we test this theory for a wide
range of generalizations, including generalizations of different types
(categories, events, and causes). We do this by both measurning and
manipulating background knowledge and referent-prevalence and relate it
to human elicited endorsements of generalizations.

\section{Case Study 1: Generic
Language}\label{case-study-1-generic-language}

Generalizations about categories (i.e., \emph{generic language}; e.g.,
\enquote{Dogs bark.}) have received substantial interest in psychology
for their role in concept and theory formation (e.g., Gelman, 2004),
stereotype propogation (Rhodes, Leslie, \& Tworek, 2012), and motivation
(Cimpian, Arce, Dweck, \& Markman, 2007), as well as many other facets
of everyday reasoning. In addition, generics have been the case study of
choice for the semantics of the language of generalization because of
their vexing similarity to quantified statements (e.g., \enquote{Most
dogs bark}). Time after time, psychologists have shown that generics
simply do not reduce to quantified statements (e.g., Khemlani et al.,
2012, Prasada et al. (2013), Cimpian, Brandone, and Gelman (2010)).

Here, we take our first empirical look at how the \emph{underspecified
threshold} endorsement model predicts actual human endorsements of
generic statements. We measure endorsement for thirty generic sentences
that cover a range of conceptual distinctions (Prasada et al., 2013):
\emph{majority characteristic} (e.g., \enquote{Ducks have wings.}),
\emph{minority characteristic} (e.g., \enquote{Robins lay eggs.}),
\emph{striking} (e.g. \enquote{Mosquitos carry malaria.}), \emph{false
generalization} (e.g., \enquote{Robins are female.}), and \emph{absent
features} (e.g. \enquote{Lions lay eggs.}). We further craft sentences
to elicit the full range of acceptability judgments (intuitively:
\enquote{true}, \enquote{false}, and \enquote{indeterminate}) for
generics with properties of low, medium, and high referent-prevalence
(Expt. 1a). We examine generics about animal categories in order to
reliably measure the prior belief distribution over the prevalence of
features \(P(h)\) (Expt. 1b). This elicitation procedure includes
measurements of the referent-category feature-probabilties \(h'\)
(e.g.,\(P(x \text{ lays eggs} \mid x \text{ is a robin})\)), allowing us
to both generate predictions for the endorsement model (Eq. \ref{eq:S1})
as well as for simpler, alternative models.

\subsection{Experiment 1a: Generic
endorsements}\label{experiment-1a-generic-endorsements}

In this experiment, we elicit human endorsements for generalizations
about categories (\emph{generics}) taken from the linguistic and
psychological literature on generics (Prasada et al., 2013). The goal of
this study is to observe a range of endorsements for generic statements
about animal categories.

\subsubsection{Method}\label{method}

\paragraph{Participants}\label{participants}

We recruited 100 participants over Amazon's crowd-sourcing platform
Mechanical Turk (MTurk). Participants were restricted to those with US
IP addresses and with at least a 95\% MTurk work approval rating (the
same criteria apply to all experiments reported). 4 participants were
excluded for failing to recall the button corresponding to
\emph{agreement} in the forced-choice task. 5 participants self-reported
a native language other than English; removing their data has no effect
on the results reported. The experiment took about 3 minutes and
participants were compensated \$0.35.

\paragraph{Procedure and materials}\label{procedure-and-materials}

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized
between-participants) to signify whether they agreed or disagreed with
the sentence (see Table 2 in Appendix for complete list). The thirty
sentences were presented in a random order between participants and
covered a range of conceptual categories described above. Approximately
10 true, 10 false, and 10 uncertain truth-value generics were selected.
All 30 generic sentences are shown in Figure
~\ref{fig:generics-endorsement-figure} A. As an attention check,
participants were asked at the end of the trials which button
corresponded to \enquote{Agree}. 4 participants were excluded for
failing this trial.

\subsubsection{Results}\label{results}

As a manipulation check, the first author assigned an \emph{a priori}
truth-judgment (true/false/indeterminate) to each stimulus item. As one
would expect, there were substantial differences in empirical
endorsements: true generics were almost universally endorsed (Maximum
A-Posteriori estimate and 95\% credible interval of endorsement
probability: \(0.93\) \([0.91, 0.94]\)); indeterminate generics were
agreed with \emph{less} likely than chance (\(0.38\) \([0.35, 0.42])\))
but substantially more than false generics (\(0.08\) \([0.06, 0.09])\)).

In addition to these categorical differences between our thirty generic
statements, we find a contiuum of endorsement values (Figure
~\ref{fig:generics-endorsement-figure} A). Such a continuum of judgments
is already evidence against any theory that only predicts categorically
whether a generic statement is true or false. Ideally, a complete theory
of genericity should be able to explain statements that are endorsed
completely, unendorsed completely, and all shades in between. We next
measure the prevalence prior distribution and articulate a set of formal
models that try to predict these endorsement data.

\subsection{Experiment 1b: Prevalence prior
elicitation}\label{experiment-1b-prevalence-prior-elicitation}

The prevalence prior \(P(h)\) in Eq. \ref{eq:L0} describes the belief
distribution on the probability of a given feature (e.g.,
\textsc{lays eggs}) across relevant categories. To get an intuition for
the kind of knowledge encoded in this belief distribution, consider the
following thought experiment: You are walking around and you come across
an instance of your favorite kind of animal from Earth (e.g., a
peregrine falcon). Ask yourself \enquote{is it female?} Your answer will
probably depend upon the percentage of the category that you believe to
be female (e.g., the percentage of female peregrine falcons, i.e.,
50\%). Now, do you think it lays eggs? Your answer to this question will
likely depend upon on what animal you're thinking of: If you're thinking
of a peregrine falcon, the probability is similar to that of being
female (50\%) because female peregrine falcons lay eggs; if you're
thinking of a mammal, it's likely that it won't lay eggs (0\%) because
most mammals give birth to live young. That is, the answer is roughly
either 50\% or 0\% depending on the kind of creature you are thinking
of\footnote{The subjective probability may, in fact, be non-zero and
  small as opposed to 0. Non-zero probabilities allow for the intuitive
  possibility of a dog that lays eggs potentially due to some strange
  generic mutation or the interaction of dog genetics with a strange
  environment.}.

This thought experiment decomposes the prevalence prior \(P(h)\) into a
prior distribution on kinds \(P(k)\) and then a conditional probability
of the prevalence given the kind \(P(h \mid k)\). We will use this
decomposition to measure the prevalence prior
\(P(h) = \int_{k} P(h \mid k) \diff k\) and perform Bayesian data
analysis to accurately reconstruct the prevalence prior. We measured
prior distributions empirically for the set of properties (e.g.,
\textsc{lays eggs, carries malaria}; 21 in total) used in our generic
sentences in Expt. 1a. To create a larger set of properties, we
reverse-code responses for five properties to create their corresponding
negative properties (e.g., we create a property \enquote{doesn't have
beautiful feathers} by subtracting from 100\% the responses for
\enquote{has beautiful feathers}).

\subsubsection{Method}\label{method-1}

\paragraph{Participants}\label{participants-1}

We recruited 60 participants over Amazon MTurk.\\
3 participants were accidentally allowed to complete the experiment for
a second time, so we excluded their second responses (resulting in
\(n=57\)). 2 participants self-reported a native language other than
English; removing their data (\(n=55\)) has no effect on the results
reported. The experiment took about 10 minutes and participants were
compensated \$1.00.

\paragraph{Procedure and materials}\label{procedure-and-materials-1}

On each trial of the experiment, participants filled out a table where
each row was an animal category and each column was a property.
Participants first were shown six animal categories randomly sampled
from a set corresponding to referent-categories of the generic sentences
used in Expt. 1a (e.g., \textsc{robins, mosquitos}) and were asked to
generate five of their own (Figure ~\ref{fig:generics-prior-task} A). A
column then appeared to the right of the animal names with a property
label in the column header (e.g., \emph{lays eggs}). Participants were
asked to fill in each row with the percentage of members of each of the
species that had the property by giving a number (e.g., \enquote{50\%};
Figure ~\ref{fig:generics-prior-task} B). Eight property--columns in
total appeared in the table.

This whole procedure was repeated two times (two trials). In total, each
participant generated ten animal names and reported on the prevalence of
sixteen properties for twenty-two animals (their own ten and the
experimentally-supplied twelve).

\begin{figure}[htbp]
\centering
\includegraphics{figs/generics-prior-task-1.pdf}
\caption{\label{fig:generics-prior-task}Prior elicitation task. A:
Participants first generated animal names after seeing six example
categories. B: One feature at a time, participants estimated the
percentage of the category with the feature, for each category.}
\end{figure}

\subsubsection{Qualitative results}\label{qualitative-results}

There is a lot of diversity in the shapes of the elicited prior
distributions (8 examples shown in Figure~
\ref{fig:generic-endorsement-priors-figure} A), which is roughly
consistent with the schematic prior distributions used in the
\emph{Model Simulations} section (Figure ~ \ref{fig:simulations} A). The
property \emph{being female} is present in almost all categories in
almost exactly the same proportion, where as properties such as
\emph{laying eggs} or \emph{having spots} exhibit more structure
represented by the multimodality of these distributions. \emph{Being
red} exists mostly at extremely low prevalence levels (i.e., 0
prevalence) but also at high prevalence levels (e.g., 50\% or 100\%),
whereas \emph{carrying malaria} is really only present at low prevalence
levels. This diversity is important because the endorsement model makes
different predictions depending on the shape of the prior.

\subsubsection{Quantitative modeling}\label{quantitative-modeling}

In order to integrate the results of this prior measurement task into
our model of endorsement, we must accurately model the prior elicitation
data. We do this using a Bayesian mixture model, which assumes that the
data generated for each property (e.g., \textsc{lay eggs}) comes from
one of two underlying Beta distributions (\emph{Mixture of
Betas}).\footnote{The Beta distribution is chosen because the support of
  this distribution is numerical values between 0 - 1, exactly the form
  of the response data in the prior elicitation task.} We specify one of
these distributions \emph{a priori} to represent kinds of animals who
\emph{do not have} a stable causal mechanism that could give rise to the
property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in
prevalence or prevalence values close to or equal to 0.\footnote{This
  assumption is similar in spirit that employed by \emph{Hurdle Models}
  of epidemiological data, where the observed count of zeros is often
  substantially greater than one would expect from standard models, such
  as the Poisson (e.g., when modeling adverse reactions to vaccines;
  Rose, Martin, Wannemuehler, \& Plikaytis, 2006)} This \enquote{null
distribution} is potentially present for all features in exactly the
same way (i.e., the lack of producing the feature). The second
distribution represents kinds of animals who \emph{do have} such a
mechanism, and the two parameters of this distribution are not specified
\emph{a priori} and are not the same for all properties, but are
inferred on a property-wise basis from participants' responses. The
\emph{Mixture of Betas} distribution has a third free parameter (for
each property), the relative contribution of the \enquote{null
distribution} (for example: we expect the \enquote{null distribution} to
not contribute at all to properties like \emph{being female}, for which
almost all categories have at least some members with the property). To
ensure the \emph{Mixture of Betas} model of the prior is not overly
complex, we fit an additional model that represents only a single
underlying distribution (\emph{Single Beta}) for a comparison. For more
details about model implementation and inference, see Appendix C.

The prior distributions over prevalence are well modeled as a mixture of
two Beta distributions and not as a single Beta distribution (Figure~
\ref{fig:generic-endorsement-priors-figure} B; red vs.~blue lines). The
\emph{Single Beta} model does okay for the \emph{being female}
distribution, but overly smooths the other distributions, washing out
the latent structure in participants' responses. One prior that the
\emph{mixture of Betas} model does not perfectly capture is the prior
distribution over the feature \textsc{lay eggs}. The empirical
distribution is tri-modal, with reliable modes at 0\%, 50\%, and
100\%\footnote{Similar phenomena have been observed in other prevalence
  elicitation tasks when the referent-category is fixed (e.g.,
  estimating only the percentage of \emph{robins} that \emph{lay eggs};
  Prasada et al., 2013)}; a simple two-component mixture model has no
way to account for such a tri-modal distribution. A more complex model
(i.e., one with three mixture components) is necessary to perfectly
account for this item.

\begin{figure}[htbp]
\centering
\includegraphics{figs/generic-endorsement-priors-figure-1.pdf}
\caption{\label{fig:generic-endorsement-priors-figure}A: Empirically
elicited prior distributions over prevalence for eight properties. B:
Cumulative density plots reveal that a model of a mixture of two Beta
distributions does substantially better at capturing the structure of
the priors than a single Beta distribution. Distributions are the
posterior predictive distributions for the models of the prio and the
raw empirical distribution. A completely uniform distribution would be
represented as the y = x line.}
\end{figure}

\subsection{Endorsement model
comparison}\label{endorsement-model-comparison}

To understand the generative process of generic endorsement, we
articulate a set of formal models that have been previously-proposed in
the literature, an alternative-form of our proposed endorsement model,
and our full endorsement model. As the simplest baseline hypothesis, we
first explore how well referent-category prevalence itself predicts
generic endorsement (e.g., does the fraction of \textsc{robins} that
\textsc{lay eggs} predict the felicity of \emph{Robins lay eggs}?). As a
secondary alternative hypothesis, we explore whether referent prevalence
and \emph{cue validity}---the probability of a kind given the feature
(described in more detail below)---predicts the endorsement data. We fit
these models using standard maximum-likelihood techniques; we model
uncertainty in the input measurements (i.e., referent prevalence, cue
validity) by bootstrapping those data.

Our underspecified-threshold hypothesis models endorsement by
considering how well the generalization would bring a naive
interpreter's prior distribution on prevalence \(P(h)\) (e.g., the
prevalence of laying eggs among other animals) in line with the
referent-category prevalence (e.g, the prevalence of laying eggs among
robins). There are several substantive components to this hypothesis:
(a) the prior distribution \(P(h)\) is relevant, (b) endorsement is a
decision-theoretic process of uttering the generalization vs.~not
uttering it, and (c) the core semantics of a generalization is an
uncertain threshold. As a control model, we assign a fixed semantics to
the generalization (i.e., analogous to the quantified statements) but
keep the prior and the decision-theoretic architecture in place. This
provides a strict test of the uncertain-threshold hypothesis (c).

\subsubsection{Baseline models}\label{baseline-models}

\paragraph{Referent prevalence}\label{referent-prevalence}

From the prevalence prior data (Expt. 1b), we estimate participants'
beliefs about the probability of a feature for the referent categories
(e.g., the percentage of \textsc{robins} that \textsc{lay eggs}). We
find a little over half of the variance in the endorsement data is
explained this way (\(r^2(30) = 0.51\); MSE=\(0.08\); Figure ~
\ref{fig:generic-endorsement-priors-figure}, upper-right: lower-left
facet). The referent prevalence baseline is a decent model of these data
because our stimulus set includes generics that are true with high
prevalence properties (e.g., \emph{Leopards have spots.}) and generics
that are false with low prevalence properties (e.g., \emph{Leopards have
wings.}).

However, large deviations from an account based purely on referent
prevalence remain: Generics in which the referent-category has
intermediate prevalence (prevalence quartiles 2 and 3:
\(16\% < \text{prevalence} < 64\%\)), are not at all explained by
referent prevalence (\(r_{Q2,3}^2(15) = 0.01\); MSE = \(0.14\)). This
includes generics that are judged true with relatively low referent
prevalence (e.g., \enquote{Mosquitos carry malaria}) and false with
relatively high referent prevalence (e.g., \enquote{Sharks don't eat
people}).

\paragraph{Cue validity and referent
prevalence}\label{cue-validity-and-referent-prevalence}

\subparagraph{Model specification}\label{model-specification}

Cue validity is linearly related to a point-estimate of the prevalence
prior distribution (see Model section and Appendix A). It thus
implicitly captures information about other categories, though cannot
capture the structure that is present in the prevalence priors. To show
that this structure is important, we explore a secondary baseline model
based on prevalence and cue validity.

Though the cue validity of a particular (category, property) pair can be
derived from the prevalence prior distribution, previous empirical
studies of generic language have not done this. Instead, these studies
estimate cue validity by asking a separate group of participants about
the distinctiveness of features for given animals (e.g., Khemlani et
al., 2012), though different studies use different measurements.
Preliminary analysis of these different measurements revealed that a
\emph{free production} paradigm (Cree, McNorgan, \& McRae, 2006) is
preferred. Participants (\(n = 100\)) were supplied with a feature
(e.g., \enquote{X lays eggs}) and asked to generate a kind (e.g.,
\enquote{what do you think X is ?}). For a detailed analysis of
different cue validity measurements and comparison to \emph{prevalence
prior derived cue validity}, see Appendix B.

\subparagraph{Results}\label{results-1}

A linear model that uses predictors for both referent-prevalence and cue
validity does a better job at explaning the endorsement data than just
prevalence alone (\(r^2(30) = 0.73\); MSE=\(0.04\)). This model is able
to account for the endorsements of examples like \enquote{Mosquitos
carry malaria} (model endorsement and bootstrapped-95\% confidence
interval = 0.84 {[}0.72, 0.92{]}) and \enquote{Lions have manes} (0.79
{[}0.63, 0.88{]})), as these features are very diagnostic of the kind
(human endorsement both \(> 0.9\)). Deviations, however, still remain.
For example, \enquote{Robins lay eggs} still receives only intermediate
endorsement by this model (0.68 {[}0.57, 0.79{]}; human endorsement =
0.94 {[}0.87, 0.97{]}), and \enquote{Mosquitos don't carry malaria} is
judged to be a pretty good statement (0.57 {[}0.42, 0.71{]}; human
endorsement = 0.07 {[}0.04, 0.14{]}).

\enquote{Robins lay eggs} and \enquote{Mosquitos don't carry malaria}
highlight a shortcoming of reducing structured prevalence prior
distributions to single point-estimates of cue validity. \enquote{Lays
eggs} is a somewhat diagnostic feature for \emph{birds}, but there are
many kinds of birds, and the feature is not itself diagnostic for a
particular kind of bird like \enquote{Robins}. Thus, the cue validity is
low even though robins are in the distinctive part of the \enquote{lays
eggs} prevalence prior distribution (e.g., Fig.~\ref{fig:simulations}A
bottom). Furthermore, cue validity glosses over the difference between
\enquote{undiagnostic} features (features present in almost every
category; e.g., \enquote{not carrying malaria}) and \enquote{false}
features (features that are absent a particular category; e.g.,
\enquote{lions} and \enquote{lay eggs}; see Appendix B for more
discussion of this distinction). Such a model makes the wrong prediction
for non-distinctive properties that in, absolute terms, have high
prevalence but in relative terms, low prevalence (e.g.,
\enquote{Mosquitos don't carry malaria}). A simple metric like cue
validity is too blunt to capture these subtleties.

\subsubsection{Communicative endorsement
models}\label{communicative-endorsement-models}

The model we propose for endorsing generalizations is a model of an
agent that decides whether or not to say the generalization to a naive
interpretor. The endorsement model (Eq. \ref{eq:S1}) decides whether or
not to assert the generalization to a naive interpretor (Eq.
\ref{eq:L0}) conditioned on a particular referent-category prevalence
\(h'\) (e.g., the percentage of robins that lay eggs). We use the
empirically estimated referent-category prevalence (the same as used in
the baseline regression model) as the referent-category prevalence
\(h'\) in the endorsement model. The empirically measured priors from
Expt. 1b are used as the literal interpreter's prevalence prior
\(P(h)\).

To incorporate the measurements of these model components into our
endorsement model, we build a single, Bayesian joint-inference model of
the referent-category prevalence \(h'\), prevalence priors \(P(h)\)
(both from Expt. 1b data), and the endorsement data (Expt. 1a). Modeling
the data from both Expt. 1a and 1b by a single, joint-inference model
simultaneously makes explicit our assumptions about how these data were
generated and is the proper way to represent the uncertainty in our
measurement of the prior elicitation data (see Appendix and Figure~
\ref{fig:genericsModelDiagram} for further model specification details).
The endorsement model is then fully specified after setting the single
optimality parameter \(\lambda_1\) (in Eq. \ref{eq:S1}). To learn about
the credible values of the parameters of the model and resulting model
predictions, we ran an incrementalized version of MCMC (Ritchie,
Stuhlmüller, \& Goodman, 2016) for 3 chains of 100,000 iterations,
discarding the first 50,000 for burnin.

The number of parameters of this full data-analytic model is relatively
large, and thus there is a concern that the parameters themselves (as
opposed to the exact structure of our model) are doing the work. To
address this concern, we construct a strong, alternative model that uses
the same data analytic strategy and only differs in the uncertain
semantic threshold \(\theta\) is replaced with a fixed-threshold. To
provide the strongest possible test, we make the fixed-threshold a
parameter of the data-analytic model, to search for the best possible
fixed-threshold. Finally, a fixed-threshold model will have to
accomodate responses that are inconsistent with the threshold (i.e., a
participant endorsing the generalization when the referent prevalence is
low); we thus outfit this model with an \emph{additional} noise
parameter, to allow for random guessing. Thus, our fixed-threshold
alternative model says that participants make an information-theoretic
decision, taking into account the interpreter's prior distribution
\(P(h)\), using a fixed-threshold semantics, where deviations from a
pure information-theoretic decision are accounted for by noise. This
alternative model has 2 additional parameters to our uncertain threshold
model (the fixed-threshold and the proportion of noise responses). We
examine the predictions of this alternative model first.

\paragraph{Fixed-threshold with noise
model}\label{fixed-threshold-with-noise-model}

\begin{figure}[htbp]
\centering
\includegraphics{figs/generics-endorsement-figure-1.pdf}
\caption{\label{fig:generics-endorsement-figure}Endorsing generalizations
about categories. Top left: Human elicited endorsements for thirty
generic sentences reveal a continuuum of endorsements. Top right: Model
fits for the uncertain semantics speaker model (upper right), a fixed
semantics speaker model (upper left), and regression models based on
referent prevalence alone (lower left) and prevalence + cue validity
(lower right). Bottom: Five example prevalence priors, listener
posteriors upon hearing the generalization, and speaker belief
distributions about the referent prevalence. These distributions are
inferred using all three data sources from Expt. 1 (see Figure
\ref{fig:genericsModelDiagram} for an overview of the Bayesian data
analytic approach).}
\end{figure}

To evaluate the fixed-threhsold model, we examine the posterior
distribution which represents what we should believe about the latent
parameters of the model (referent prevalence, prevalence priors, the
optimality, fixed-threshold, and noise parameters) given the observed
data, as well as what predictions of the model given these parameter
values. The Maximum A-Posteriori value and 95\% highest probability
density interval for the inferred (fixed) threshold and noise parameters
are 0.34 {[}0.25, 0.37{]} and 0.20 {[}0.18, 0.22{]}, respectively. The
inferred optimality parameter in Eq. \ref{eq:S1} is 0.34 {[}0.25,
0.37{]}.

We compare the fixed-threshold model's posterior predictive distribution
of generic endorsement to the empirical truth judgments. Figure
\ref{fig:generics-endorsement-figure} (top right; top left subplot)
shows the fixed-threshold model's ability to predict the generic
endorsement data (\(r^2(30) = 0.9329\); MSE = \(0.010964\)). Though the
model is able to capture a lot of the variance, it only makes three
kinds of judgments: true, false, or neither. It treats \enquote{Tigers
eat people} (0.90 {[}0.85, 0.91{]}) as good a statement as
\enquote{Peacocks have beautiful feathers} (0.88 {[}0.85, 0.91{]}),
though participants seem to give a substantially weaker endorsement of
the former (\enquote{Tigers eat people} = 0.69 {[}0.59, 0.77{]};
\enquote{Peacocks have beautiful feathers} = 0.99 {[}0.94, 1{]}).
Similarly, \enquote{Lions lay eggs} is judged to be just as bad as
\enquote{Mosquitos attack swimmers}(0.10 {[}0.09, 0.15, 0.10 {[}0.09,
0.15{]}, respectively), though participants rate the former as
completely false (0.01 {[}0, 0.06{]}) while the latter is kind of true
(0.38 {[}0.28, 0.48{]}). This alternative model is unable to make these
fine-grained distinctions because it must use the same semantic
threshold in all contexts.

\paragraph{Uncertain threshold model}\label{uncertain-threshold-model}

Our underspecified threshold model is the same as the fixed-threshold
model, except that rather than having a fixed \(\theta\) for all
contexts, the model infers context-specific \(\theta\)'s. We construct
the same joint-inference Bayesian data analytic model as we did for the
fixed-threshold analysis; however, we are able to drop the additional
parameters required for the fixed-threshold model (the fixed-threshold
and noise parameters). Thus, this model has two \emph{fewer} parameters
than the fixed-threshold model above.

We first examine the posterior predictive distribution on the prevalence
prior and referent-prevalence data to ensure that the joint-inference
model fits these data as well as the Bayesian model that modeled these
data in isolation. This is an important step in model validation because
it tells us that our model's predictions are derived from reasonable
values of the parameters. Importantly, the model recapitulates the prior
elicitation data (e.g., the probability of laying eggs among various
species) and the referent-category prevalence data (e.g., the
probability of laying eggs among robins) as it did when the Bayesian
data analysis model only included these data and their associated model
(results section of Expt. 1b). This result confirms that the
theoretically-interesting predictions of this model --- predictions of
generic endorsement --- are based on intuitively meaningful model
components (i.e., the shapes of the prevalence distributions).

The inferred optimality parameter in Eq. \ref{eq:S1} is 0.34 {[}0.25,
0.37{]}.

As we see in Figure ~\ref{fig:generics-endorsement-figure} (top right,
top right subplot), the endorsement model that uses an
uncertain-threshold semantics explains nearly all of the variance in
human endorsements (\(r^2(30) = 0.9978\); MSE = \(0.00035185\)). To gain
some intuition for why that is the case, examine the bottom row of
Figure \ref{fig:generics-endorsement-figure}. The blue, solid lined
distribution corresponds to the speaker's beliefs about the probability
of the feature for the referent-category (i.e., \emph{referent
prevalence}). The grey distribution shows the listener's prior
distribution over probabilities of the feature (these are the
corresponding Probability Density Functions of the Cumulative Density
Functions shown in Figure ~\ref{fig:generic-endorsement-priors-figure}.
It is also the listener \(L_0\)'s posterior on referent prevalence upon
hearing the silent utterance. The red distribution shows the \(L_0\)
posterior upon hearing the generic utterance that corresponding to an
uncertain threshold-semantics. The speaker model decides when the
generic utterance conveys information that would bring the listener's
distribution more in line with the speaker's own distrubtion. Thus, it
finds that \enquote{Leopards have spots}, \enquote{Robins lay eggs}, and
\enquote{Mosquitos carry malaria} are also useful things to say.
\enquote{Robins are female} is neither good nor bad, as the
information-content of the utterance is very small relative to silence.
\enquote{Tigers don't eat people} is rather misleading, however; it
doesn't bring the listener closer to the speaker's distribution, despite
the speaker believing that the prevalence is more than half.

\subsection{Discussion}\label{discussion}

Generic language is the premier case study for generalizations in
language. Generics have been studied extensively in the cognitive and
developmental psychological literatures and shown to have deep
implications for wide ranging phenomena from stereotype propogation
(Rhodes et al., 2012) to motivation (Cimpian et al., 2007). Heretofore,
however, no formal model has been able to pass the most basic
truth-functional tests of the semantics of generalizations, knowing when
they are true and false. Determining the truth conditions is the first
step towards articulating a formal theory of how the language updates
beliefs.

We have demonstrated that a semantics based on the probability of the
feature is tenable in spite of alleged counterexamples. The key
theoretical insight is that the truth-functional semantics is
\emph{underspecified} yet still is able to formalize, using recent
developments in probabilistic modeling. Our model provides a clean
delineation of world knowledge (formalized as a prior distribution) from
the semantics of generalizations. We return to this point, and its
implications for theory-building, in the general discussion.

In explaining the variable endorsements of generics, we related the
referent-category prevalence (e.g., the percentage of robins that lay
eggs) to the endorsement of the generalization (e.g., \enquote{Robins
lay eggs}) via the prevalence priors (e.g., the percentage of different
kinds of animals that lay eggs). In doing so, we used generic statements
about familiar animal categories, which has long been the cleanest
domain for testing semantic theories of generics by providing minimal
comparison like \enquote{Robins lay eggs} vs. \enquote{\ldots{} are
female}. To model statements about familiar categories, we were forced
to \emph{measure} the relevant quantities in the model (i.e., the
referent prevalence and the prevalence priors), which people have access
to via their mental representations of the category. We now seek to
demonstrate how these quantities are causally related to endorsement, by
manipulating referent prevalence (Case 2) and feature-probabilitiy
priors (Case 3). In addition, we take this opportunty to highlight the
generality of the theory, by performing these additional empirical tests
in different domains for generalization: events and causes.

\section{Case Study 2: Habitual
Language}\label{case-study-2-habitual-language}

The event of Mary smoking at 2:30pm on January the 24th is an instance
of a kind of event: \emph{Mary smoking}. Just as with categories,
generalization can occur over events of a particular type. When
expressed in language, these generalizations take the form of
\emph{habitual language}: \enquote{Mary smokes}.

Events are a broad class of entities. In our second case study, we focus
on habituals about people's behaviors that take the form:
\textsc{singular noun phrase} \(+\)
\textsc{present tense simple verb phrase} (e.g., \enquote{Mary smokes
cigarettes}). Learning about the behaviors of others is useful because
they tell us about what that person is like more generally (e.g.,
Repacholi \& Gopnik, 1997; Seiver, Gopnik, \& Goodman, 2013). When
children describe their lives to other, a surprisingly large amount of
the langauge produced concerns the actions of people close to them
(e.g., ``My brother works part-time at the restaurant''; W. J. McGuire
\& McGuire, 1986). Habitual language about people may be a more
conservative form of \emph{trait language} (e.g., \enquote{Mary is a
smoker.}) and convey that behaviors are relatively enduring (Gelman,
2004; Gelman \& Heyman, 1999).

To test the generality of our theory, we use the same computational
model and follow the same general experimental structure as in the first
case study. We take event analogue of prevalence to be the \emph{rate}
with which the event occurs (e.g., how often Mary smokes). For the
generalization \enquote{Mary smokes}, instances of the category being
generalized are \emph{instances of Mary} and if for the instance to have
the feature, it means the instance of Mary is one in which she is
smoking. We test this by first measuring the prevalence (rate) prior
distribution for various actions (e.g., how often different people smoke
cigarttes; Expt. 2a). We then measure endorsements of habitual
statements while manipulating the \emph{referent-prevalence} (Expt. 2b),
and use our computational model to predict habitual endorsements. By
describing novel characters to participants, we are able to directly the
manipulate the \emph{referent-prevalence} (rate), which we were unable
to do for generalizations about familiar categories.

Finally, if habituals (and generics) are truly language for conveying
generalizations, it would be useful for them to reflect a speaker's
expectations, not merely her observations. Our computational model
predicts endorsement rates given a referent-prevalence \(p_{fk}\). Does
prevalence represent the actual, past frequency of the event (e.g., how
often Mary has actually smoked in the past month) or the predictive
probability of the event in the near future (e.g., how often we should
expect Mary to smoke next week)? We extend our theory by measuring
participants' predictions about future rates and endorsements of
habituals when causal forces intervene on the world (Expt. 2c). We then
use our model to test whether habitual endorsements are based on past
frequencies or future expectations.

\subsection{Experiment 2a: Measuring the prevalence prior for
events}\label{experiment-2a-measuring-the-prevalence-prior-for-events}

In order to generate model predictions for corresponding habitual
statement, we first elicit the prior distributions over rates for
different events. For language about the behaviors of people, \(P(p_f)\)
represents a language user's background knowledge about the rates with
which people do a behavior; this prior can be constructed as a
distribution over \emph{different people}, each of whom do the behavior
with a different rate. We designed our elicitation task to take
advantage of the mixture-model representation of the prevalence prior
used in Expt. 1 . In particular, we assume, to a first approximation,
that the distribution over prevalence can be represented as a mixture of
those who tend to do the action with a stable rate and those who do
not.\footnote{In the case of event knowledge about people, we expect
  there to be several more than just these two possibilities represented
  in the prior, corresponding to individuals with different traits or
  demographics. We assume here a simple structure so as to not make the
  specification of the prior overly complex.} With the further
assumption that, all else being equal, past is predictive of future
behavior, we operationalize these two kinds of people as \emph{people
who have done the action before} and \emph{people who have not the
action before}. We design this experiment to measure participants'
beliefs about the relative proportion of these two kinds of people (as a
measure of the mixture parameter in the model) as well as the rate at
which people (who have done the action before) do the action (as a
measure of the mean of stable-rate people). We will aassume for
simplicity that people who have never done the action before will rarely
or never do the action.

\subsubsection{Method}\label{method-2}

\paragraph{Participants}\label{participants-2}

We recruited 40 participants from Amazon's Mechanical Turk. Participants
were restricted to those with U.S. IP addresses and who had at least a
95\% work approval rating. The experiment took on average 12 minutes and
participants were compensated \$1.25 for their work.

\paragraph{Materials}\label{materials}

To construct our stimulus set, we choose actions from five categories of
typical human behaviors: eating/consuming food and drug, work, wearing
clothing, entertaining activities, and hobbies. For each category, we
created pairs or triplets of events that shared a superordinate actions
(e.g. \emph{writing} poems vs.~novels). The events were chosen to
intuitively cover a range of likely frequencies. In total, thirty-one
events were used. For a full list the stimulus set, see Appendix D.

\paragraph{Procedure}\label{procedure}

For each event, participants were asked two questions, with different
dependent measures. These questions were designed to measure the two
central components of the prevalence prior model. We anticipated there
to be different beliefs about the rates and relative proportions of
peopel depending on whether an actor is male or female, so we asked
about both genders separately.

\begin{enumerate}
\item ``How many \{men, women\} have \textsc{done action} before?'' \\

Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}, incremented by 10x; default setting: 1000).

\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\

Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default setting: year).
\end{enumerate}

For example, one set of prompts read: \enquote{How many women have
smoked cigarettes before?}; \enquote{For a typical woman who has smoked
cigarettes before, how frequently does she smoke cigarettes?}
Participants answered both questions for both genders on each slide (4
questions total per slide, order of male / female randomized
between-subjects), and every participant completed all 31 items in a
randomized order. The difference in meaning of these questions was
explained to participants on an instructions page before the
experimental trials and tested for recall on a subsequent trial.
Participants responded to this attention check by selecting an option
from a drop-down menu consisting of four options (one correct
description of the questions and three distractors).

\begin{figure}[htbp]
\centering
\includegraphics{figs/habituals-prior-figure-1.pdf}
\caption{\label{fig:habituals-prior-figure}Prevalence priors for events
(Expt. 2a). Left: Mean mixture parameter and mean stable frequency
parameter for 31 events. Right: Inferred priors on frequencies from the
structured, prior elicitation task. Priors are reconstructed by forward
sampling using the inferred parameters in the prior mixture model.}
\end{figure}

\subsubsection{Data analysis and
results}\label{data-analysis-and-results}

All participants responded correctly to both questions in the attention
check trial, so all collected data was used in the analysis. Question 1
elicits the proportion of people who have done an action before. We
rescale this to be a number between 0 and 1, and assume it was generated
from a Beta distribution: \(d_{1} \sim \text{Beta}(\gamma, \xi)\).
Question 2 elicits the rate with which a person (who has done the action
before) does the action. We model this as generated by a log-normal
distribution: \(\ln d_{2} \sim \text{Gaussian}(\mu, \sigma)\). Each item
was modeled independently for each gender. We learned about the credible
values of the parameters by running MCMC for 100,000 iterations,
discarding the first 50,000 for burnin.

The priors elicited cover a range of possible parameter values as
intended (Figure \ref{fig:priorScatter}, scatter): We observe a
correlation in our items between the mean \% of Americans who have
\textsc{done action} before (Question 1) and the mean log-frequency of
action (Question 2) (\(r_{1,2}(62) = 0.73\)). Items in our data set that
tend to be more popular actions also tend to be more frequent actions
(e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}),
though there are notable exceptions (e.g., \emph{plays the banjo} is not
popular but done frequently when done at all, as is
\emph{smokes cigarettes}; \emph{goes to the movies} is a popular
activity though not done particularly often). This diversity is relevant
because the speaker model (Eq. \ref{eq:S1}) will endorse habitual
sentences (e.g., \emph{Sam goes to the movies vs. the ballet.})
contingent on the shape of the prior distribution.

To generate prevalence prior distributions, we built a Bayesian
mixture-model for this prior elicitation task, analagous to that used in
Case Study 1 (Expt. 1b). The only difference is that we estimate the
mixture component \(\phi\) directly from responses to Question 1. We
assume that those who have not done the action before will probably not
do the action in the future. With these assumptions, the prevalence
distribution is given by:

\begin{align}
\phi & \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1}) \nonumber \\ 
\ln h & \sim \begin{cases}
        \text{Gaussian}(\mu_{Q2}, \sigma_{Q2}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
                \text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
        \end{cases}
\end{align}

Figure \ref{fig:habituals-prior-figure} (right) shows example
reconstructed priors. In addition to specifying the correct way to
combine our two prior-elicitation questions, using this inferred prior
resolves two technical difficulties. First, it smooths effects that are
clearly results of the response format. For example, a very common
rating for certain events is \emph{1 time per year}. Presumably
participants would be just as happy reporting \emph{approximately} 1
time per year (e.g., on average, 1.2 times per year); the raw data does
not reflect this due to demands of the dependent measure. Second, this
methodology better captures the tails of the prior distribution (i.e.,
very frequent or very infrequent rates) which have relatively little
data and need to be regularized by the analysis.

\subsection{Experiment 2b: Habitual
endorsements}\label{experiment-2b-habitual-endorsements}

In this experiment, we elicit human endorsements for generalizations
about events (\emph{habituals}; e.g., \enquote{Mary smokes cigaerettes})
while manipulating the frequency with which the referent-event occurs
(e.g., how often Mary smokes cigarettes).

\subsubsection{Method}\label{method-3}

\paragraph{Participants}\label{participants-3}

We recruited 150 participants from MTurk. To arrive at this number, we
performed a Bayesian precision analysis to determine the minimum sample
size necessary to reliably ensure 95\% posterior credible intervals no
larger than 0.3 for a parameter whose true value is 0.5 and for which
the data is a 2-alternative forced choice. This analysis revealed a
minimum sample size of 50 per item; since participants only completed
about one third of the items, we recruited 150 participants. The
experiment took 4 minutes on average and participants were compensated
\$0.55 for their work.

\paragraph{Materials}\label{materials-1}

Each event from Expt. 2a was then paired with between 2 - 4 frequencies,
for which the habitual statement would be evaluated. Frequencies were
always \enquote{3 times every \textsc{time period}} so that the referent
character had always completed the event multiple times.
\textsc{time period}s were chosen specific to each event by simulating
predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of
maximizing the variability in endorsements across items. For example,
relatively high frequencies were chosen (e.g., three times every week
vs.~2 months) for an item that was expected to occur rather often (e.g.,
\enquote{runs}) because the model predicted that much of the variability
in endorsement would occur in this range; for an item was expected to
occur infrequently (e.g., \enquote{climbs mountains}), lower frequencies
were chosen (e.g., three times every 5 years vs.~2 years). In total, 93
unique items were created by pairing frequencies with events.

\paragraph{Procedure}\label{procedure-1}

On each trial, participants were presented with a
\emph{past frequency statement} for a given event of the form:
\enquote{In the past M \{weeks, months, years\}, \textsc{person}
\textsc{did x} 3 times}. For example, \enquote{In the past month, Bill
smoked cigarettes 3 times}. Participants were asked whether they agreed
or disagreed with the corresponding habitual sentence:
\enquote{\textsc{person does x}} (e.g.,\enquote{Bill smokes
cigarettes.}). Participants completed thirty-seven trials, which were
composed of the thirty-one items from the prior elicitation task
randomly paired with either a male or female character name. Six of
these items were then also paired with a name of the opposite gender
(e.g., participants rated both a female character and a male character
who drank beer). These were used for an exploratory analysis on
differences in endorsements by gender of the target character.

\subsubsection{Results}\label{results-2}

Habitual sentences were endorsed for a wide range of frequencies. When
actions are very infrequent (3 times in a 5-year interval), habituals
can receive strong agreement (e.g., \emph{writes novels},
\emph{climbs mountains}). When actions are relatively frequent (e.g., 3
times in a one month interval), habitual sentences can receive less than
full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). In
our data, actions completed with a high frequency (3 times in a one week
interval) receive at a minimum 75\% endorsement, though there is still
variability among them (e.g., between 10-25\% of people disagree with
\emph{wears a watch} and \emph{wears a bra}). In addition, we observe
that none of our items receive less than 25\% endorsement (i.e., a
maximum of about 75\% of participants disagree with the felicity of the
utterance), reflecting the fact that these statements are not altogether
\emph{false} even though the action is done very rarely.

\subsubsection{Endorsement model
comparison}\label{endorsement-model-comparison-1}

\begin{figure}[htbp]
\centering
\includegraphics{figs/habituals-endorsement-figure-1.pdf}
\caption{\label{fig:habituals-endorsement-figure}Endorsing generalizations
about events. A: Endorsements for nine events given different
frequencies of action by human participants and four models. B: Human
elicited endorsements for ninety-three habitual sentences as a function
of the referent (log) frequency of action. Top right: Model fits for all
ninety-three habitual sentences by each model. C: Nine example frequency
priors and posteriors upon hearing the generalization. These
distributions are inferred using both data sources from Expts. 2a \&
2b.}
\end{figure}

In an exploratory analysis, we find no differences between endorsements
of the habitual of characters with male and female names, and overall,
the mean endorsements by gender are strongly correlated
\(r(93) = 0.91\). Endorsements are even more highly correlated for the
six events we anticipated differences by referent-gender:
\(r(21) = 0.97\) This lack of a difference may be because the felicity
of habitual sentences depends on a comparison to individuals of both
genders (i.e, in minimal contexts such as this, habituals are evaluated
with respect to \emph{other people}, not just other men or other women).
Less interestingly, the lack of a difference may be the result of gender
being not very salient in our paradigm, perhaps because the names used
were not sufficiently gendered.

We now turn to our model-based analyses to better understand the
endorsement data and the contribution of our model. For all analyses, we
collapse across gender of the referent character for endorsement
judgments. Parallel to our analysis of generic language endorsements, we
articulate a set of simple regression models and an alternative to our
uncertain-threshold endorsement model. Analyses which use the rate prior
distribution \(P(p_f)\) (all models except \enquote{referent frequency}
regression) use a 50\% mixture of the inferred priors for each gender to
construct a single prior distribution. To model the uncertainty in the
input measurements, we bootstrap the data for the regression models and
we construct joint-inference, Bayesian data analytic models for the
information-theoretic endorsement models (fixed-threshold and
uncertain-thresold).

\paragraph{Referent frequency}\label{referent-frequency}

To understand the role of frequency in habitual endorsement, we use the
frequency supplied to the participants in our experiment as a predictor
in a linear model. This model predicts the same endorsement level for
two actions done with the same rate. Obvious counterexamples exist in
our data set: While participants are willing to endorse that a person
\enquote{\ldots{} climbs mountains} having done it 3 times in the past
\emph{year}, they are less willing to say that a person
\enquote{\ldots{} hikes} and not willing to say that a person
\enquote{\ldots{} runs}. Some actions done with a relative high rate
(e.g., 3 times in a month) do not receive full endorsement (e.g.,
\emph{smokes cigarettes}; Figure \ref{fig:habituals-endorsement-figure}
A). Overall, the referent-frequency (in log-scale) predicts only a
fraction of the variability in responses (\(r^2(93) = 0.325\);
MSE=\(0.0355\)). In addition, for actions that are done on the time
scale of years or longer (lower median of frequency), referent frequency
no longer explains endorsements (\(r^2(50) = 0.0662\); MSE =\(0.0477\)).
The prevalence baseline does appreciably worse in this data set in
comparison to the generics data set (Case Study 1) because we designed
the stimulus set to be critical of a referent-frequency model.

\paragraph{Distinctiveness and referent
frequency}\label{distinctiveness-and-referent-frequency}

In our empirically elicited priors, items differ the proportion of
people who have done the action before (the \emph{mixture parameter} of
the mixture model; Figure \ref{fig:habituals-prior-figure}). This
mixture parameter is a major contributor to the mean of the prevalence
prior distribution, and thus is relates to the \emph{cue validity} of a
particular feature for a particular individual (see Appendix A for a
derivation of the relationship between the prevalence prior and cue
validity). Thus, we take this parameter as an index of the
\emph{distinctiveness} of the action, analagous to \emph{cue validity}
in the case study of generic langauge. We construct a regression model
that treats endorsement as a linear combination of frequency and
distinctiveness information. We use participants' responses to the
question about the mixture parameter \(\phi\) (i.e., the proportion of
people who have done the action before) as well as frequency given to
participants to predict habitual endorsement.

This model is able to explain more of the variance in endorsements
(\(r^2(93) = 0.583\); MSE=\(0.0219\)). It can differentiate events done
with the same frequency (e.g., \emph{writing poems} vs. \emph{novels}, 3
times in the past 5 years), and increase endorsement of the more rare
action (\emph{novels}). Still, this model fails to capture fine-grained
details in endorsment. For example, going to the movies is a relatively
nondistinctive action (many people do it) and going three times in a
year is not very frequent, and yet people still strongly endorse the
habitual \(0.81 [0.69, 0.89]\), while this regression model predicts
quite lower judgments \(0.41 [0.38, 0.43]\). On the other hand, playing
the banjo three times in the past two years is not strong evidence for
the habitual, according to participants \(0.45 [0.33, 0.59]\).
Nevertheless, because playing the banjo is a distinct skill, the
regression model wants to endorse the habitual strongly in this case
\(0.75 [0.74, 0.76]\).

\paragraph{Fixed-threshold endorsement
model}\label{fixed-threshold-endorsement-model}

We next examine an information-theoretic endorsement model based on a
fixed-threshold semantics. A fixed-threshold model commits the habitual
to conveying that a person \emph{does the action with some rate}, and
the threshold on rates is common to all actions. As in Case Study 1, we
incorporate this model into a Bayesian joint-inference model to infer
the fixed-threshold and simultaneously predict both the priors data and
the endorsement data (for more details on model implementation, see
Appendix C). We assume the referent-prevalence \(p_{fk}\) being conveyed
by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to
participants (e.g., 3 times in the past year). Additionally, to account
for statements that would be literally false under this model
(frequencies that fall below the fixed threshold), we include an
additional noise parameter, as we did for the fixed-threshold model in
Case Study 1. To learn about the credible values of the model's
parameters and generate predictions given those inferred parameter
values, we collected 2 MCMC chains of 100,000 iterations, discarding the
first 50,000 iterations for burn in.

The data analytic model infers that a low threshold is likely: the
inferred threshold in units of number of times per year is 0.01 {[}0.01,
0.37{]}. Compare this with the lowest referent-frequency used in our
data set: \(0.6\) times per year (3 times every 5 years). Thus, all of
the utterances evaluated under this fixed-threshold model were literally
true. As a result, the lowest endorsement this model can apply to an
utterance is 0.5 (since both the habitual and silence are always true).
The fixed-threshold model exhibits a small dynamic range of
endorsements, similar to the referent-frequency model.

A fixed-threshold utterance updates the interpreter model's beliefs
differentially depending on the item. For instance, it's highly unlikely
that a random person \emph{climbs mountains} with any non-zero rate;
thus this model fully endorses \enquote{Mary climbs mountains} even with
low-frequency (Figure \ref{fig:habituals-endorsement-figure} A).
However, the model doesn't differentiate doing the same action with
different frequencies. It is equally true that a person does an action
\emph{with some frequency} for any frequency greater than zero,
analogous to how \enquote{some Ks F} is equally true if 20\% or 50\% of
Ks F.

Finally, the data-analytic model infers that 10\% {[}1, 19{]} of the
data is noise and that the speaker optimality parameter is 0.77 {[}0.70,
1.25{]}.

\paragraph{Uncertain-threshold endorsement
model}\label{uncertain-threshold-endorsement-model}

We used the same data analytic approach for the uncertain threshold
endorsement model and performed the same Bayesian statistical inference
over the model to learn about its parameters and predictions. Again,
this model has two fewer parameters than the fixed-threshold model (no
fixed-threshold parameter and no extrinsic noise process). As shown in
Figure \ref{fig:habituals-endorsement-figure}B, the uncertain-threshold
endorsement model does a good job of accounting for the variability in
responses (\(r^2(93) = 0.894\); MSE=\(0.00598\)), including actions done
on the time scale of years or more (\(r^2(50) = 0.903\);
MSE=\(0.00617\)). Figure \ref{fig:habituals-endorsement-figure}C
provides insight into how the model achieves this. An interpreter who
hears a generalization interprets it relative the prior distribution
over frequencies, which results in different points at which the
generalization is good statement to assert. Someone who smoked
cigarettes 3 times last month is not fully someone who \enquote{smokes
cigarettes}, whereas someone who went to the movies 3 times last month
more a person who \enquote{goes to the movies}. Only the
uncertain-threshold model is able to draw this fine distinction.

\subsubsection{Discussion}\label{discussion-1}

Habitual language exhibits context-sensitivity directly parallel to that
of generic language (Case Study 1). Habituals are endorsed for a wide
range of frequencies, but show systematic patterns relative to the prior
distribution of frequencies, as formalized by the uncertain-threshold
model. Again, we articulated a number of alternative models and found
that only the underspecified threshold model was able to explain the
variability in endorsements.

In this case study, we manipulated rather than measured the referent
frequency (e.g., the frequency with which a person drinks coffee). By
manipulating the target frequency, we have shown that it is causally
related to habitual endorsements in the way predicted by our model (and
in a way that a fixed-threshold model cannot account for). The
relationship is not linear (or log-linear), however; habitual
endorsements vary in complex ways that reflect interpreters' prior
knowledge about the event in question.

In Expt. 2b, participants were given a statement about how often a
person has done the action in the past and asked to judge the
corresponding habitual statement. This design potentially confounds an
important distinction for the language of generalization: Does the
prevalence communicated by a generalization indicate an objective, past
frequency or a subjective, future expectation? In Expt. 2c, we
investigate this question by teasing apart \emph{past} from
\emph{predictive frequency} and measuring its influence on habitual
endorsement.

\subsection{Experiment 2c: What is
prevalence?}\label{experiment-2c-what-is-prevalence}

While past frequency is often a good indicator of future tendency, the
future is under no obligation to mimic the past. Does habitual language
communicate probabilities in terms of past frequency or future
expectations? On one hand, speakers can only be certain about what has
happened in the past. On the other hand, language has a communicative
function, and it would be useful for speakers to convey their
predictions of what will be the case in the future.

People can change their behavior abruptly due to a variety of decisions
and outside events. We introduce these causal events into our minimal
endorsement paradigm and measure their influence on endorsement. To
provide the appropriate model-based analysis, participants in one
condition make a prediction about what will be the case in the future
(\emph{predictive frequency}). In another condition, participants decide
whether or not to endorse the habitual sentence (as in Expt. 2b). We
then compare two uncertain-thresholds models to each other: one which
uses participants' ratings of \emph{predictive frequency} as the object
of communication and one which uses the \emph{past frequency} (as was
done for Expt. 2b).

\begin{figure}[htbp]
\centering
\includegraphics{figs/habituals-predictive-figure-1.pdf}
\caption{\label{fig:habituals-predictive-figure}Top left: Predicted
frequency of event (log-scale) as a function of (log) past frequency and
condition manipulation (enabling, preventative, and baseline). Top
right: Human endorsement of habitual sentences as a function of log
predicted frequency and condition manipulation. Bottom row: Endorsement
models based on past frequency (left) and measured predictive frequency
(row).}
\end{figure}

\subsubsection{Method}\label{method-4}

\paragraph{Participants}\label{participants-4}

We recruited 270 participants from MTurk, using the same criterion as
Expt. 2b. 120 were assigned to the \emph{predictive frequency} condition
and 150 were assigned to the \emph{sentence endorsement} condition. The
experiment took on average minutes (\emph{predictive frequency}) and
minutes (\emph{sentence endorsement}). Participants were compensated
\$0.40.

\paragraph{Materials}\label{materials-2}

The events used were a subset of those used in Expts. 2a \& b (21 of the
original 31). In addition, we crafted statements that were intended to
either increase the frequency (\emph{enabling}; e.g.,
\enquote{Yesterday, Bill bought a pack of cigarettes.}) or decrease the
frequency (\emph{preventative}; \enquote{Yesterday, Bill quit smoking.})
of the event in the future. In order to increase the potential
variability of responses across the experimental conditions,
participants only saw the frequencies that led to the most intermediate
endorsement of the habitual in Expt. 2b. We did not include separate
trials for both male and female names for the select items we did in
Expt. 2b, since we saw no differences in their endorsements of the
habitual. See Appendix D for a full list of the enabling and
preventative information.

\paragraph{Procedure}\label{procedure-2}

The procedure was identical to Expt. 2b except for the inclusion of a
second sentence on a subset of trials (\emph{preventative} and
\emph{enabling} trials). On all trials, participants were presented with
a \emph{past frequency sentence} (same as Expt. 2b). Additionally,
trials either included \emph{preventative} information, \emph{enabling}
information, or no additional information (identical to Expt. 2b), in
equal proportions.

In the \emph{predictive frequency} condition, participants were asked
``In the next \textsc{time window}, how many times do you think
\textsc{person} does \textsc{action}?'', where the \textsc{time window}
was the same as given in the \emph{past frequency statement}. In the
\emph{sentence endorsement} condition, participants were asked if they
agreed or disagreed with the corresponding habitual sentence (as in
Expt. 2b).

\subsubsection{Results}\label{results-3}

\paragraph{Predictive frequency}\label{predictive-frequency}

Figure \ref{fig:habituals-predictive-figure} (left) shows the mean
predicted future rate as a function of the past rate given to the
participant and the type of causal information given. We observe in the
baseline condition that future frequency perfectly tracks past frequency
(\(r(21) = 0.99\)). That is, participants believe if a person smoked
cigarettes 3 times last month, they will smoke cigarettes 3 times next
month. This result implies that our model makes identical predictions
for Expt. 2b whether the referent is past frequency or expected future
frequency (indicating, as expected, that we must look to the new data to
distinguish these models). Critically, we observe the preventative
information strongly decreases and the enabling information slightly
increases predicted frequency (Figure
\ref{fig:habituals-predictive-elicitation} left; blue and green dots).

We confirm these observations using a linear mixed-effects model,
predicting the log-transformed responses from the log-transormed past
frequency and the experimental condition (baseline, preventative,
enabling). To account for participant and item variability in this
analysis, we also include random effects of intercept and condition for
both participants and items. Confirming our predictions, the
preventative information led to significantly lower predictions for
future frequency, relative to the baseline condition (
\(\beta = -3.18\); \(SE = 0.27;\) \(t = -11.96\) ). There was also
tendency for the enabling information to lead to higher predictions for
future frequency, relative to baseline ( \(\beta = 0.96\);
\(SE = 0.11;\) \(t = 8.54\) ). Finally, past frequency was a significant
predictor of predicted future frequency ( \(\beta = 1.01\);
\(SE = 0.02;\) \(t = 40.80\) ).

\paragraph{Sentence endorsement}\label{sentence-endorsement}

There is a clear and consistent negative effect of preventative
information on endorsements for the habitual sentence (Figure
\ref{fig:habituals-predictive-figure}B; green points). Still, frequency
--- even predictive frequency --- does not perfectly explain the
endorsements (\(r^2(63) = 0.518\); MSE = \(4.3\)). When collapsing
across items, the Bayesian Maximum A-Posteriori estimate and 95\%
highest probability density interval for the true endorsement
probabilities per condition are: baseline = 0.85 {[}0.83, 0.87{]},
enabling = 0.90 {[}0.88, 0.92{]}, preventative = 0.29 {[}0.26, 0.32{]}

We use our formal model to test whether past or predictive frequency
matters for endorsement. To formalize the predictive frequency speaker
model, we use the mean predictive frequency as the referent-prevalence
\(p_{fk}\) that the endorsement model (Eq. \ref{eq:S1}) conditions on.
The past frequency model is constructed using the past frequency
supplied to participants as the referent-prevalence. We analyze this
model in the same Bayesian data analysis regime as for our previous
models. We use the same priors over the parameters as before and learn
about the posterior distribution by collecting three independent MCMC
chains of 100,000 iterations (removing the first 50,000 for burn-in).
Figure \ref{fig:habituals-predictive-figure}C shows the resulting model
predictions for the past frequency and the predictive frequency
endorsement models. Participants' judgments of the habitual statements
was indeed influenced by the causal manipulations \emph{in the way
predicted} by the endorsement model that uses the predictive frequency
as the object of communication (\(r^2(63) = 0.931\); MSE = \(0.00594\)).
The model based on past frequency does not make different predictions
for the different causal manipulation conditions and does a poor job at
explaining the endorsements (\(r^2(63) = 0.0334\); MSE = \(0.0833\)).

\subsection{Discussion}\label{discussion-2}

Habitual language conveys generalizations about events. Our model
decides if a habitual sentence is a pragmatically useful way to describe
the rate at which a person does an action, taking into account a naive
interpreter's prior beliefs about the event (measured in Expt. 2a). Our
computational model endorses statements that communicate generalizations
about events with the same sensitivity to context and frequency that
people exhibit (Expt. 2b \& c). In Expt. 2b, we varied the type of event
and the past frequency with which the person did the action, and found
graded endorsements of the corresponding habitual sentences. By
manipulating (rather than measuring) the referent frequency with which a
person does an action, we showed how alternative models were
insufficient to account for the gradience in endorsement. In particular,
a fixed threshold model that has access to the same prior knowledge and
uses the same information-theoretic decision rule as our
uncertain-threshold model is unable to make different predictions for
different frequencies. Only our uncertain threshold model was able to
precisely account for the wide range of endorsements.

A regression model that takes into the frequency and the
\emph{distinctiveness} of the action does a reasonable job at explaining
the variance in this data. We note that this kind of model is merely a
re-decription of the data (and thus, the behavior of the uncertain
threshold model), and does not represent a theory of the semantics of a
generalization. A theory of the semantics of a generalization must
formalize the truth-conditions of the generalization as well as how
those truth-conditions relate to endorsement. This is precisely what our
information-theoretic models do (both fixed- and uncertain-threshold).

In Expt. 2c, we further investigated the nature of the underlying
prevalence scale by introducing causal information that enabled and
preventated future occurences of the action. We used the
empirically-measured predicted future frequency as the object of
communication for our endorsement model. We found that the endorsement
model that seeks to communicate its predictions (rather than its
observations) is a better model of habitual endorsements under these
situations. Predicted prevalence thus captures the infleunce of top-down
moderators (e.g., intervening causal forces) on endorsement.

In these experiments, we introduced participants to novel actors and, by
doing so, were able to directly manipulate the frequency of a person
doing the action. The kinds of events we used were familiar to
participants (e.g., \emph{running}) and thus we measured the prevalence
priors for those events. In our final case study, we experimentally
manipulate the prevalence priors, testing their causal influence over
endorsements. In addition, we further we extend our theory to the
language of causal relationships.

\section{Case Study 3: Causal
Language}\label{case-study-3-causal-language}

Language about causal relationships manifests in generalization. The
utterance \enquote{Drinking moonshine makes you go blind} relates to
\enquote{My grandpa's drinking moonshine made him go blind} in a way
analagous to how \enquote{John smokes} relates to \enquote{John smoked
yesterday}. We explore this hypothesis in our third case study: causal
language or \emph{causals} (e.g., \enquote{A causes B}).

The problem of \emph{causal induction}---knowing that one thing causes
another----has been studied extensively in human psychology (Cheng,
1997; Cheng \& Npvick, 1992; Griffiths \& Tenenbaum, 2005, 2009).
Classically, this is cast as a problem of inducing an unobservable
relation (\emph{type causation}) from observable events or contingency
data. We take a different approaching, examining \emph{type causation}
by the language used to describe it (e.g., \enquote{A causes B}). We
assume that such language conveys a generalization about \emph{token} or
\emph{actual causation} (e.g., \enquote{A caused B, in this instance})
and that our theory of the language of generalizations extends in a
natural way to describe \emph{causal language}. Ascribing causation to
an individual event (\emph{token or actual causation}) is itself a
complex, inferential process (e.g., depending on counterfactual
reasoning; T. Gerstenberg, Goodman, Lagnado, \& Tenenbaum, 2015), which
we do not try to model here.

In this paper, we posit thatprevalence priors are a mediating
representation between abstract conceptual structure and generalizations
in language. In this last set of experiments, we explicitly test the
relationship between the prevalence priors and endorsements of
generalizations about causes. Also, by designing the experiments in the
domain of causal language, we further demonstrate the generality of our
theory of communicating generalizations.

\subsection{Experiment 3a: Manipulating prevalence
priors}\label{experiment-3a-manipulating-prevalence-priors}

In this experiment, we manipulate and measure participants' background
knowledge in order to check whether or not manipulation of participants'
background knowledge was successful. Experiment 3b (\emph{causal
endorsement}) will then follow a mostly-identical experimental
procedure.

\subsubsection{Method}\label{method-5}

\paragraph{Participants}\label{participants-5}

We recruited 160 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had
at least a 95\% work approval rating. The experiment took on average
1.70 minutes and participants were compensated \$0.50 for their work.

\paragraph{Materials}\label{materials-3}

Participants were told a story of a scientific experiment testing
different substances to produce an effect (either to make animals sleepy
or plants grow tall). Our cover stories were constructed so that the
potential cause could have some plausible intuitive mechanism that could
give rise to the proprety (e.g., a naturally occurring herb causing
animals to be sleepy). The two cover stories can be seen in Table
\ref{tab:causalItems}.

Participants were then shown \enquote{previous experimental results},
which followed one of four distributions, shown in Figure
\ref{fig:causals-conditions}. In two of the conditions, participants saw
results that came from the same underlying distribution. In one of these
conditions, all causes produced a strong effect (average efficacy
approximately 98\%; the \enquote{common strong} condition). In the
second of these conditions, all causes produced a weak effect (average
efficacy approximately 20\%; the \enquote{common weak} condition). The
two other conditions used distributions in which some experiments
resulted in either no or very few succeses (i.e., produced 0s or 1s or
2s), and others that either had strong or weak effects as above. These
are the \enquote{rare strong} and \enquote{rare weak} conditions.

\begin{table}[]
\centering
\label{tab:causalMaterials}
\resizebox{\textwidth}{!}{
\begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|}
\hline
                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline
Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. Your team runs experiments trying to make feps grow tall with different fertilizers. & On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs. \\ \hline
Evidence statement & Your team gave fertilizer B to 100 different feps. Of those 100 treated, 2 feps grew tall.                                                                                                              & Your team gave herb C to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.    \\   \hline                                                                                                                            
\end{tabular}
}
\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics{figs/causalExpt-1.pdf}
\caption{\label{fig:causalExpt}Overview of Experiment 3. A-C: Results of
previous experiments are shown one at a time, described in text and
displayed in a table. One of the results was lost. Participants are
asked to review previous results once all displayed. B: Prior
elicitation task: Participants predict the results of the next 5
experiments. D: Causal endorsement task: Results of previously lost
experiment are found and participants are asked to evaluate the causal
generalization.}
\end{figure}

\paragraph{Procedure}\label{procedure-3}

Each participant saw only one cover story with one distribution of
previous experiments (i.e., the experiment was a single trial).
Participants were told that they were an astronaut-scientist on a
distant planet trying to figure out how some system works (i.e., how to
make a certain kind of animal sleepy with different herbs or how to make
a plant grow tall with different fertilizers). The story for the
\enquote{sleepy animals} condition read:

\begin{quotation}
You are an astronaut-scientist exploring a distant planet. 
On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy.
Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
The results are shown below:
\end{quotation}

Participants then click a button to show the results of the experiments.
Experiment results appear one at a time (upon a click), and are
described in an \emph{evidence statement} (e.g., \enquote{Your team gave
herb A to 100 different cheebas. Of those 100 treated, 98 cheebas were
made sleepy.}) as well as displayed in a table showing the number of
successes (e.g., \enquote{animals made sleepy}) per number of attempts
(always 100 per experiment). We described the results of these
individual experiments using \emph{token-level} causal language (e.g.,
\enquote{98 cheebas were made sleepy}) to suggest that actual causation
occurred in these cases.

Participants see the results of eleven \enquote{experiments}, though
they are told the results of one experiment were lost and a \enquote{?}
was placed in the table (Figure \ref{fig:causalExpt}). (These lost
results would be found in the \emph{causal endorsement} task, Expt. 3b).
After participants viewed the results of the 10 \enquote{experiments}
(and 1 missing experiment), they are told to review the results of the
experiments before continuing.

Upon clicking the continue button, the table of experiment results is
removed and participants are told more experiments were conducted.
Participants were asked to predict the results of the next 5
experiments. Participants were given 5 slider bars ranging from 0 - 100,
and asked to predict the next five substances (e.g., herbs M, N, P, Q,
and R).

After responding, participants then completed an attention check survey
where they were asked what the team of scientists were investigated
(choosing a response from a drop-down menu with 12 options) and to input
one of the numerical results they saw on the previous screen. This
attention check served to confirm that participants had encoded some
part of both relevant aspects of the experiment (the domain and the
frequencies).

\subsubsection{Results}\label{results-4}

20 participants were excluded from the analysis for failing to answer
both of the attention check questions correctly, leaving a total of 140
responses for analysis. The distributions that resulted from
participants predicting the causal efficacy of the new substances are
shown in Figure \ref{fig:figure-causals}. These distributions nicely
recapitulate the distributions supplied in the different experimental
conditions, suggesting that the manipulation does indeed change
participants' representations of what probabilities are likely to occur
in each experimental condition. We hypothesize that with the
distributions altered, endorsements of generalizations will similarly be
affected.

\subsection{Experiment 3b: Causal
Endorsements}\label{experiment-3b-causal-endorsements}

In this experiment, we tested whether the manipulated priors of Expt. 3a
are causally related to the endorsement of causal statements. Most of
the experimental deisgn was identical to that of Experiment 3a.

\subsubsection{Method}\label{method-6}

\paragraph{Participants}\label{participants-6}

We recruited 400 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had
at least a 95\% work approval rating. None of the participants had
participated in Experiment 3a. The experiment consisted of one trial and
took on average 1.40 minutes; participants were compensated \$0.25 for
their work.

\paragraph{Procedure and materials}\label{procedure-and-materials-2}

The materials were the same as in Experiment 3a, The first part of the
experimental trial was the same as in Expt. 3a (the table of
\enquote{previous experiments}; Figure \ref{fig:causalExpt}). Upon
continuing beyond the first part of the trial, the table of results and
background story were removed from the screen and the participant is
told that the results of the \enquote{lost experiment} were found. The
results are reported to the participant in terms of how many out of 100
of the attempts were successful. Participants saw 1 of 2 reported
frequencies: 20\% or 70\% (randomized between-subjects). Participants
were then asked to judge the causal sentence (e.g., \enquote{Herb X
makes the animals sleepy}). Partipants responded by either clicking
\enquote{Yes} or \enquote{No}. After responding, participants completed
the same attention check as Expt. 3a.

\begin{figure}[htbp]
\centering
\includegraphics{figs/figure-causals-1.pdf}
\caption{\label{fig:figure-causals}Endorsing generalizations about causes.
A: Endorsement model predictions (left) and human elicited endorsements
(right) for four background distributions and two observed frequencies.
B: Prevalence prior distributions and interpreter model posteriors upon
hearing a causal generalization, for the experimentally manipulated
priors. Vertical lines denote referent-prevalence levels for the causal
endorsement task. Endorsement mode predictions, interpreter model
posteriors, and prevalence priors are inferred using both Expt. 3a and
3b data, following the same Bayesian data analytic approach outlined in
Appendix C.}
\end{figure}

\subsubsection{Results}\label{results-5}

42 participants were excluded from the analysis for failing to answer
both of the attention check questions correctly, leaving a total of 358
responses for analysis. As in our other analyses of endorsement
responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate
and 95\% highest probability density interval of the true population
probability of endorsing the statement, assuming a uniform prior. These
are shown for the different experimentally-manipulated priors and
frequencies in Figure \ref{fig:causals-endorsement}.

As predicted by our model, endorsements for a causal statement were
sensitive to the background distribution of other causes and the causal
power of the target cause. When many other causes produced the effect
very reliably (\emph{common deterministic} condition), very few
participants endorsed the causal statement for a cause with causal power
of 0.2, and were at chance when the causal power was 0.7 (Figure
\textbackslash{}ref\{fig:figure-causals-endorsement; top, blue). By
contrast, when many other causes failed to produce the effect and those
that did were not very reliable (\emph{rare weak} condition; green in
figure), at least half of participants endorsed the causal statement for
a cause with causal power of 0.2, and were at ceiling when the causal
power was 0.7. The other two conditions (\emph{rare deterministic} and
\emph{common weak}) led to endorsements intermediate between these two
conditions. Our model predicted these effects again with strong
quantitative accuracy (\(r^2(8) = 0.835\); MSE = \(0.0123\)).

\subsection{Discussion}\label{discussion-3}

In our third case study, we applied our same model to generalizations
about causal events. In this domain, we succesfully manipulated
participants' beliefs about the expected prevalence of a causal
relationship in a domain (Expt. 3a). This was done using both unimodal
(\emph{common weak}, \emph{common strong}) and bimodal (\emph{rare
weak}, \emph{rare strong}) distributions. In Expt. 3b, we showed that
these manipulated priors influenced endorsements of the corresponding
causal statements. In addition to further demonstrating the generality
of this theory, these experiments show that the \emph{prevalence prior}
\(P(h)\) is causally related to endorsements of generalizations in
language. To our knowledge, these are the first experiments to
demonstrate how the probabilities of other categories having a feature
can influence endorsing a generalization about a different category.

In these experiments, we used two cover stories that described plausible
causal events: herbs making animals sleepy and fertilizers making plants
grow tall. We chose these items because there was a plausible causal
mechanism that could give rise to the property and these causal events
could have ambiguous causal power associated with them (e.g., it's
plausible that there are herbs that only weakly make animals sleepy and
it's also plausible that there are herbs that almost deterministically
make animals sleepy). These two features of the domains make them
particularly amenable to manipulation. That is, people's abstract
theories about these domains are flexible enough to permit such
manipulations.

It's likely that other domain knowledge would interact with the
experimentally-supplied \enquote{experimental data} to form a hybrid
belief distribution.\footnote{If this were happening in our domains, we
  would expect this to show up in the results of Expt. 3a. Participants'
  predictions about the likely causal power of new causes would be
  expected to show a mixture of their abstract, intuitive theories and
  the experimentally supplied data.} For example, physical causal
systems (e.g., billiard balls hitting each other) could strongly induce
near-deterministic notions of causal power, analagous to our
\enquote{deterministic} priors conditions. Causal systems that
demonstrate surprising or \emph{a priori} unlikely effects (e.g.,
liquids melting concrete) could induce rarity about the existence of a
non-zero causal power, analgous to our \enquote{rare} prior conditions.
Our theory would predict in these cases that differences in endorsement
would be attributable to differences in the prevalence prior
distribution (here: the belief distribution over causal power).

\section{General Discussion}\label{general-discussion}

It is a remarkable fact that so much is learned from ideas expressed
vaguely in words. Generalizations in language (e.g., \enquote{John
runs.}, \enquote{Dogs are friendly.}, \enquote{Staring at the sun makes
you go blind.}) are a premier example of how simple
statements---statements understood by even the youngest language
users---can display complex sensitivities to context. We have argued
that the core meaning of such linguistic expressions is, in fact,
simple, but underspecified. To our knowledge, this is the first formal
theory of generalizations in language that makes precise quantitative
predictions about human behavioral data.

As a formal theory of generalizations in language, we aim to unify
significant swaths of language that are, on their surface, quite
different from one another: generalizations about categories, events,
and causes. We have been able to formalize a unified, core meaning using
the underlying scale of \emph{prevalence}. We showed that all three
kinds of generalizations exhibit the same kind of sensitivity to context
(Expt. 1, 2a \& 2b, 3). Our framework naturally accounts for a number of
classic examples from the semantics of \emph{generic language} (Expt.
1). We provide an avenue for top-down moderators on language use, by
elucidating the scale as defined by a subjective, predictive
probability, not mere frequency (Expts. 2c \& 2d). Finally, we have
shown that listeners' prior knowledge about the prevalence of the
feature in a category is causally related to their endorsement of
statements of genericity (Expt. 3). In addition to unifying seemingly
disparate parts of language, this paper provides a theoretical framework
for asking further questions about genericity, which we outline below

The foremost contribution of our theory is that it is accompanied by a
formal model, which makes precise quantitative predictions about
endorsments. The formal Bayesian model provides a clean separation of
the semantics of a generalization (operationalized in terms of the
likelihood function) from background, world knowledge (operationalized
in terms of the prior). This formal separation is key improvement beyond
previous accounts. Previous accounts have either tried to account for
context-sensitivity by baking it into the semantics (e.g., Cohen, 1999)
or positing a semantics that cannot be separated from world knowledge
(e.g., Leslie, 2008). Our model formalizes both the semantics of
generalizations and the structure of world knowledge; this separation
allows us to articulate a route for precise quantitative inlfuence of
conceptual structure on generic language (c.f., Leslie, 2008). We do
this without having to posit that conceptual structure and semantics are
one in the same. This is makes it possible to connect with theories of
formal semantics as well as applied Natural Language technologies that
seeks to draw inferences from information conveyed in generalizations in
text (e.g., Herbelot \& Copestake, 2011).

In the rest of this discussion, we elaborate some key features of the
theory that warrant future investigation, sketch out arguments for other
known philosophical puzzles in genericity, and situate our theory with
respect to extant theories of genericity.

\subsection{A step towards communicating
generalizations}\label{a-step-towards-communicating-generalizations}

In this paper, we proposed a model for interpreting and endorsing
generalizations in language by formalizing a simple semantic theory in a
probabilistic model with structured, prior knowledge. Our pair of models
can be seen as a special case of a Rational Speech Act model, a rational
framework of pragmatic language understanding (Frank \& Goodman, 2012;
Goodman \& Frank, 2016). Our endorsement model, which we use to generate
predictions for our three case studies, can be seen as a special case of
a speaker model who can only produce one of two utterances: the
generalization or silence. Our interpreter model can be seen as a kind
of \enquote{literal listener}, who does not do any sort of pragmatic or
communicative reasoning. Our modeling framework could thus naturally be
extended to more faithful models of pragamtic communication of
generalizations, to explore when and how people choose to communicate
their abstract knowledge when they have more options than in a
two-alternative forced-choice task. The view of our endorsement model as
a minimal communicative model highlights aspects of our modeling
approach for further future development.

\subsubsection{The comparison class}\label{the-comparison-class}

Our model of an interpreter, or naive listener, has access to implicit
statistics of the event or property in question, represented by the
prior belief distribution over the prevalence \(P(h)\). The prevalence
priors for a property, event, or cause are constructed by considering
\emph{other possible} categories having the property, people doing the
action, or causes producing the effect. Collectively, these other kinds,
people, or causes form \emph{comparison classes} against which the
referent-category is evaluated. Thus, the prevalence prior \(P(h)\) is
constructed with respect \emph{the comparison class} \(C\): \(P_C(h)\).

The existence of comparison classes is uncontroversial in the study of
\emph{vague} or \emph{underspecified} language (e.g., gradable
adjectives like \emph{tall} and vague quantifiers like \emph{many};
Bale, 2011; Solt, 2009). Adult judgments of the felicity of gradable
adjectives like \emph{tall} or \emph{dark} depend upon fine-grained
details of the statistics of the comparison class (Qing \& Franke, 2014;
Schmidt, Goodman, Barner, \& Tenenbaum, 2009; Solt \& Gotzner, 2012) in
ways directly analagous to the context-sensitivity of the language of
generalizations explored in this paper. Thus, we conclude generic,
habitual, and causal language can be seen as a special case of
\emph{vague language}.

The construction of a comparison class adds another layer of flexibility
into the use of generalizations in language. Objects can be
conceptualized and categorized in multiple ways, giving rise to
multiple, logically-possible comparison classes (e.g., a robin is a
bird, is an animal, is an object). We have begun doing work
investigating how pragmatic reasoning can help constrain this open-ended
problem (Tessler, Lopez-Brau, \& Goodman, 2017). Even if interlocutors
coordinate on a particular comparison class, they may disagree about the
prevalences for other \emph{other categories} in the class. That is, our
model makes the prediction that the acceptance or rejection of the
statement \enquote{Humans cause global warming} or \enquote{Muslims are
terrorists} depends upon a speaker's beliefs about how \emph{other
forces} (e.g., plate tectonics) influence the climate or how often other
social categories (e.g., neo-nazis) commit acts of terrorism. Indeed, we
saw in Expt. 3 how the statistics of other causes can influence the
endorsement of a single generalization (e.g., \enquote{Herb C makes
animals sleepy}). Understanding how knowledge of the comparison class
influences language use is an exciting new area for future research in
the language of generalizations.

\subsubsection{Question under
discussion}\label{question-under-discussion}

Rational models of communication, of the kind we have developed in this
paper, are required to make explicit a speaker's assumptions about the
goal of communication, otherwise known as the Question Under Discussion
or QUD (Roberts, 1996). We have made a very minimalist assumption, that
the goal of communication (at least, for purposes of endorsement) is the
prevalence. However, the choice in constructing a comparison class can
be thought of as the result of addressing a particular QUD. For example,
the comparison classes used in our case studies were with respect to the
target category (\emph{other animals}, \emph{other people}, \emph{other
possible causes}); thus, our model addresses the implicit QUDs of
\enquote{\emph{what} has feature?}, \enquote{\emph{who} does action?},
or \enquote{\emph{what} causes effect?}. Were the QUDs to be reversed
(e.g., \enquote{what features does category have?}, \enquote{what does
person do?}, \enquote{what effects does cause bring about?}), the
comparison classes would need to be constructed with respect to the
feature (e.g., \emph{other features}, \emph{other actions}, \emph{other
effects}).

The QUD is thus another layer of flexibility that makes understanding
generalizations so challenging. The same sentence can be used to address
multiple QUDs (Krifka, 1995). The statement \enquote{Lawyers care about
the law.} can be interpreted with a category-wise comparison class
(i.e., \enquote{Lawyers \emph{(as opposed to doctors, firefighters,
\ldots{})} care about the law.}; imagine in a pedagogical context) or a
feature-wise comparison class (i.e., \enquote{Lawyers care about the law
\emph{(as opposed to justice, doing what's morally right, \ldots{})}}
e.g., when said sardonically). In this work, we focused on category-wise
comparison classes for methodological convenience. Future work should
investigate the feature-wise reading of generalizations, and explore
what cues listeners adopt for one or the other interpretation.

\subsection{Structured prior
knowledge}\label{structured-prior-knowledge}

Previous psychological and philosophical work on generics has looked
beyond prevalence and focused on conceptual distinctions and relations
(Gelman, 2003; Leslie, 2007, 2008; Prasada et al., 2013). Prasada has
argued for a distinction between \emph{characteristic} properties (e.g.,
\enquote{Diapers are absorbent}) and \emph{statistical} properties
(e.g., \enquote{Diapers are white}). Leslie suggests information that is
striking (e.g., \enquote{Tigers eat people}) is ecologically useful and
thus permitted to be a generic. Gelman outlines how generics tend to
express \emph{essential} qualities that are relatively timeless and
enduring. Where in the probability-based semantics could such conceptual
distinctions come into play?

Our approach makes the strong claim that beliefs about predicted
prevalence are the connective tissue between conceptual knowledge and
the semantics of generic language. That is, the effect of conceptually
meaningful differences on generic language is predicted to be mediated
by differences in corresponding prevalence distributions. Modulations of
prevalence distributions can occur for multiple reasons (e.g., by
changing the comparison class) as described in the previous section. We
found in Expts. 1 \& 2 that conceptually different kinds of properties
and events gave rise to quantitatively different prevalence priors, even
while keeping the comparison class fixed. In Expt. 3 we showed that
these prevalence distributions are causally related to endorsement.

It is natural to ask how prevalence might reflect conceptual knowledge.
We found that empirical prevalence distributions are structured in a
mixture-model that plausibly reflects intuitions about causal mechanisms
underlying different properties; the differences in shape of these
distributions in turn led to variable endorsements of generalizations.
It is plausible that richer conceptual knowledge also influences these
distributions, such as higher-order conceptual knowledge about the
nature of properties and categories (Gelman, 2003; Keil, 1992). Indeed,
conceptual structure in general, including higher-order abstractions,
can be captured by probabilisitic causal models (Gopnik, 2003; Pearl,
1988) and their generalization in probabilistic programs (Goodman,
Tenenbaum, \& Gerstenberg, 2015). Future work will be needed to explore
whether probabilistic representations of conceptual knowledge can
capture the relations identified in other accounts of generics (such as
principled, essential, and striking properties), and whether the effect
of these relations can then be adequately described via their impact on
prevalence priors.

\subsection{Communicating predictive
probabilities}\label{communicating-predictive-probabilities}

This paper puts forth the theory that the language of generalization
communicates predictive probabilities from speaker to hearer. In
previous accounts, prevalence is treated as synonymous with the
frequency of the feature in the category. We make the important
distinction that probability can be more general than frequency, and in
our account, underlies speakers' subjective, predictions about the
future and is subject to top-down moderator. Expts. 2c \& 2d that showed
using participants' \emph{predictions} about the future as the object of
communication in our formal model perfectly tracked habitual
endorsement, when the present frequency would make the wrong prediction.

Communicating probabilities might seem contrary to a basic tenet in
cognitive psychology, that human cognition falls short when reasoning
about probabilities (Tversky \& Kahneman, 1974). Our theory suggests
that the problems with understanding probabilities observed in classic,
cognitive psychology paradigms are a problem in understanding the
\emph{language used} to convey \emph{explicit probabilties} (cf.,
Levinson, 1995). Rather than conveying \emph{explicit probabilities},
generalizations we argue convey \emph{implicit probabilities}, which are
easier to understand and quite useful for statistical reasoning. Given
the relationship to \emph{vague language} (described above), we argue
that the utterance \enquote{70\% of birds fly} is analagous to saying
that \enquote{John is 6'3}\enquote{, while saying}Birds fly" is more
similar to saying \enquote{John is tall}. The latter statements are
easier to process, understood at an earlier age, and may be more useful
for human reasoning. Indeed, young children are actually quite good
about reasoning about probabilities, but in ways that are not explicit
or tied to language (Dewar \& Xu, 2010; Gweon, Tenenbaum, \& Schulz,
2010).

\subsection{Acquiring the language of
generalizations}\label{acquiring-the-language-of-generalizations}

The linguistic outlet for generalizations about categories---so called,
\emph{generic language}---has received tremendous attention from
psychologists, linguists, and philosophers. Generic language is one of
the earliest emerging forms of complex, compositional language.
Somewhere between two and three years of age, children recognize that
generics convey a generalization about a category, not directly tied to
concrete instances in a scene (Cimpian \& Markman, 2008). Generics are
common in child-directed and child-produced speech (Gelman, Coley,
Rosengren, Hartman, \& Pappas, 1998; Gelman, Taylor, Nguyen, Leaper, \&
Bigler, 2004) and are believed to be central to the growth of conceptual
knowledge (Gelman, 2004),

What is perhaps surprising from a formal perspective is that generic
language is far from trivial to characterize. If generics convey
something about the probabilty of a feature, we would expect them to be
in some way comparable to quantifier statments (e.g., \enquote{some},
\enquote{most}, \enquote{all}, \ldots{}). The extreme flexibility of
generic meaning (e.g., \enquote{Birds lay eggs} vs. \enquote{Birds are
female}) stands in stark contrast to its early emergence in development.
In fact, quantified statements, whose formal meaning is much more
straight-forward (e.g., \enquote{Some} means more than zero), emerge
\emph{later} in development (Brandone, Gelman, \& Hedglen, 2014; Gelman,
Leslie, Was, \& Koch, 2015), and are often confused for generic
statements (Leslie \& Gelman, 2012). This has led some to conclude that
the normal tools for describing the semantics of quantified utterances
(i.e., a truth-functional threshold) is not approrpriate for generic
language (Leslie, 2008).

We think rejecting the normal tools of truth-functional semantics for
generics would be throwing out the baby with the bathwater. When we
consider the acquisition problem, there are three aspects of meaning
that a child must acquire for a truth-functional quantifier semantics
\(\denote{u}(h, \theta) = \{h :h > \theta\}\): (1) the dimension being
described (i.e., the probability \(h\)), (2) the polarity of the
relation (i.e., \(>\) vs. \(<\)), and (3) the value of the threshold
(e.g., \(\theta = 0\) for \enquote{some}, \(\theta = 0.5\) for
\enquote{most}). Upon learning the meaning has to do with probability
and that it stands in a positive relation to some standard \(\theta\), a
rational learner would adopt a prior distribution over possible
thresholds \(\theta\), as a form of \emph{lexical uncertainty} (Bergen,
Levy, \& Goodman, To appear). This prior could then be updated with more
data to acquire a fixed meaning. However, for the generic statement, the
language learner is done once she acquires aspects (1) and (2). In our
model, \(\theta\) is left underspecified in the semantics and is
inferred in context. Thus, in this sketch of an acquisition model, a
child would first acquire generic language, and from that, carve out
more precise meanings for quantified language.

The uniform prior over the threshold \(\theta\) in the truth-functional
threshold semantics (as we have assumed in our model) provides a
secondary argument for why acquiring our semantics for generics should
be easy. Uniform uncertainty over values in the unit interval \([0, 1]\)
for threshold \(\theta\) in a threshold-function is mathematically
equivalent to a \emph{soft semantics} wherein the degree to which the
utterance is true is proportional to the prevalence \(h\) \emph{itself}:

\[
\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
\] This \emph{soft semantics} (corresponding intuitively to a meaning
like \enquote{the higher the probability, the better the utterance}, or
simply \enquote{more is better}) is perhaps the simplest semantics one
could imagine. The difficulty in acquiring the meaning of quantifiers is
then a difficulty in recognizing a fixed-threshold semantics as a
special case of this \emph{more is better} semantics. We leave for
future work the precise implementation of the acquisition model we
sketch out here.

\subsection{Other philosophical
puzzles}\label{other-philosophical-puzzles}

In our experiments, we have tried to include classic, philosophically
puzzling examples of generalizations in language in addition to crafting
novel stimuli that provide stricter tests of the main hypothesis. In
this section, we consider some other previously-discussed troubling
examples of generalizations and sketch out arguments rooted in our
theoretical framework to demonstrate how our theory could account for
these cases. We consider the five following examples:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Books are paperbacks.
\item
  Mary handles the mail from Antarctica.
\item
  Supreme Court Justices have even social security numbers.
\item
  Elephants live in Africa and Asia.
\item
  Women are submissive.
\end{enumerate}

Sentence (1), strikes hearers as \emph{odd} or perhaps \emph{false},
despite the vast majority of books being paperback. Why? A first
observation is that the sentence is constructed by pairing a category
(\enquote{Books}) with a property that describes a strict subset
(\enquote{paperbacks} is short-hand for \enquote{paperback books}). We
expect intuitions about this statement to generalize to other examples
expressing an analogous relation (e.g., \enquote{Pastas are spaghetti},
\enquote{Animals are humans}). We hypothesize that the strangeness of
these examples has to do an inflexible relationship between the
comparison class and the referent-prevalence. Assume that the comparison
class is constructed by considering the \emph{predicability} of the
property (in the sense of Keil, 1979, originally from Sommers
(1963)).\footnote{Note that this assumption is consistent with the
  comparison classes we have assumed in our three case studies.} Then,
\enquote{is a paperback} can only be informatively said of individual
books, because these are the only objects that can plausibly have the
property; that is, world knowledge gives us that an elephant cannot be
predicated (either true or falsely) by the property \enquote{is a
paperback.}\footnote{Note that this idea is similar to Cohen (1999)'s
  notion of \enquote{Relative generics}, which have truth conditions
  that are determined by a comparison to an alternative set of Ks (his
  Alt(K), our comparison class) which is composed of Ks that could
  satisfy some F in an an alternative set of Fs.} The relevant
aggregations of entities, then, are collection of books, potentially
including books of different genres or publication eras among other such
sub-categories. Then, given that \enquote{books} is the superordinate
category of \enquote{kinds of books}, the referent-category prevalence
cannot be different from the mean of the prevalence prior. Finally,
given this prevalence prior and the referent-prevalence, our endorsement
model would predict \enquote{Books are paperbacks} is neither true nor
untrue, in the a way analogous to \enquote{Robins are female}.

\begin{figure}[htbp]
\centering
\includegraphics{figs/books-paperbacks.pdf}
\caption{\label{fig:booksArePaperbacks}Sketch of an argument for why
\enquote{Books are paperbacks} sounds odd. The feature \enquote{is
paperback} can only be predicated (in the sense of Keil (1979)) of
individual books, which are organized into collections (here, by genre).
The prevalence prior is constructed by aggregating these collections of
books. Then the prevalence of \enquote{is paperbook} for the category of
\enquote{books} can never be higher than the mean of the prior
distribution. The endorsement model would give this sentence a rating of
0.5, corresponding to neither true nor false.}
\end{figure}

Imagine there is a job in the local beaurocrat's office to handle the
mail from Antarctica and this job is assigned to Mary; to date, however,
there has never been any mail from Antarctica (Cohen, 1999). That is,
the statement \enquote{Mary has handled mail from Antarctica} is false.
Sentence (2) is still thought to be true despite zero actual instances
of the event. We think (2) is a boundary case of generalizations
expressing predictive probabilities, which we elucidated in Expt. 2c. In
in that study, we experimentally dissociated predictive probability from
past frequency, and saw that only a model that took into account
predictive probability could explain participants' endorsements of
generalizations. We expect the same to be true here, elucidated by the
intuition that: were there to be any mail coming from Antarctica, Mary
would handle it. Past frequency or actual prevalence in the world often
tracks predictive probabilities, but language users' internal models of
how the world works can lead them in certain situations to expect
something different in the future.

Our focus on predictive probability makes even new prediction about some
classic puzzles. Sentence (3) is the conceptual opposite of sentence
(2). Imagine that currently every Supreme Court Justice has a social
security number which is an \emph{even number}. Sentence (3) is still
considered false, every though the property holds in 100\% of the
category (Cohen, 1999). We predict this phenomenon is the result of
abstract, intuitive theories guiding us to reject observed frequencies
in forming our subjective probabilities. That is, because observers
strongly believe selection for the Supreme Court is not influenced by
one's social security number, speakers would assign a roughly 50\%
subjective probability that the \emph{next} justice would have an even
social security number. Then, given that the all professions would have
roughly the same probability of having employees with even social
security numbers, Sentence (3) is again similar to \enquote{Birds are
female}. However, were we to learn much more surprising
information---for instance, if every Supreme Court Justice in U.S.
history had a social security number which was a \emph{prime
number}---the shear suspiciousness could compel an observer to revise
their theory of the domain (appealing perhaps to a conspiracy), update
their subjective probability of future instances, and then accept the
generic. That is, we predict there are situations where statements like
(3) could be considered felicitious generalizations.

Understanding how a semantic representation \emph{composes} is another
critical test for a theory of generalizations in language. Nickel (2008)
suggests Sentence (4) is semantically equivalent to: \enquote{Elephants
live in Africa and elephants live in Asia}. Stastistical account of
generalizations have trouble with this kind of conjunction: It cannot be
the case that \emph{most} (more than half) elephants live in Africa and
\emph{most} (more than half) elephants live in Asia, unless we are to
posit \emph{international elephants} (i.e., individual elephants who
live part-time in Africa and part-time in Asia), which we would rather
not have to posit. However, this is the only interpretation if the
generalization is given a fixed, majority based quantificational account
(e.g., if the generic means \emph{most}). Our theory does not provide a
fixed semantics for the generalizations, but an uncertain one, which can
be updated as more information comes in. In fact, with a strong
constraint against the existence of \emph{international elephants} but
with any further semantic assumptions, our model infers that some
elephants live in Africa and other lives in Asia.\footnote{An
  implementation of this example can be found:
  \url{http://forestdb.org/models/generics-conjunction.html}.}
Importantly, the model believes that most lives in Africa, when it only
hears that \enquote{Elephants live in Africa}, and only later revises
it's beliefs to a weaker \enquote{some}-like interpretation after
hearing they live in Asia as well. Our model flexibly accomodates new
evidence that might otherwise contradict previous utterances because it
maintains uncertainty about the precise interpretation of single
utterances.

Finally, sometimes a property is widespread relative to other kinds or
groups, and it might be so systemic that we would believe it to be the
case in the future, but speakers still might find it avertise to
actually endorse the generalization. Such is the situation with Sentence
(5) (Haslanger, 2011). Due of a variety of socio-cultural reasons,
Haslanger (2011) argues that women tend to be submissive (more so than
men, and many other social categories), yet still cautions against
asserting (5). In our \textbf{Model Simulations} section, we showed that
the genearlization often implies the property is widespread, even with
relatively uninformed prior beliefs about the property. If the generic
conveys the property is in fact more widespread than the speaker herself
might believe, this can lead to a distortion of the truth..\footnote{Note
  that this can straight-forwardly capture the central phenomena of
  Cimpian et al. (2010).} The current formulation of the model is
relatively ambivalent about the deviations of the listener's beliefs
from the speaker's belief (i.e., the speaker doesn't mind that the
prevalence that she believes to be true will be exaggerated in the mind
of the listener). However, if states of the world (or, listener's
beliefs about states of the world) correspond to different subjective
values, speakers who take into the account the subjective utilities of
the listener may produce language that deviates from what a pure
informational transmission speaker might say. This kind of extension to
rational models of communication has already been used to account for a
variety of phenomena in \emph{polite language} use (Yoon, Tessler,
Goodman, \& Frank, 2016, 2017). We propose adopting such a value-based
utility structure for states of the world for language about social
categories: If the speaker found states of the world where the
probability of the feature is high (e.g., a world where many women were
submissive) as undesirable, then a speaker who considered both the
informational content of the utterance and the utility in the states of
the world implied by that utterance would too find it reprehensible to
make such a generalization. We find this possibilitity intruiging and
leave it for future work.

In sum, we've tried to argue that our information-theoretic
communicative model couched in general cognitive framework can be used
to explain a number of interesting and heretofore puzzling phenomena in
genericity as well as make novel predictions about a wider range of
language. The precise implementation of these hypotheses we leave for
future work.

\subsection{Relationship to other
theories}\label{relationship-to-other-theories}

To our knowledge, the present papaer presents the first formal theory of
genericity in language that makes accurate and precise quantitative
predictions about human behavioral data. A number of other theories of
genericity have been proposed in the linguistics and psychological
literatures. We now turn to situating our account with respect to these
previous theories. Semantic theories fall into one of two broad camps:
Those that appeal to the statistics of the world (e.g., how many Ks have
F) and those that appeal to structured, conceptual representations
(e.g., \emph{there is something about being K which causes it to F}).
Statistical and conceptual theories express the major contrasting views
of the truth conditions of generic statements (Carlson, 1995).\footnote{We
  use the terms statistical and conceptual to refer to what Carlson
  (1995) referred to as \enquote{inductive} and \enquote{rules and
  regulations} views, respectively.}

\subsubsection{Statistical accounts}\label{statistical-accounts}

\paragraph{Relative and absolute
generics}\label{relative-and-absolute-generics}

Our underspecified threshold model has clear antecedents in other
statistical accounts, most notably Cohen (1999) 's theory of generics as
a frequency adverb (e.g., \enquote{generally}). For Cohen, the statement
\enquote{Birds lay eggs} means \enquote{Generally, birds lay eggs}, and
then he takes up the task of explaining what \enquote{generally} means.
He partitions generics into two types: \emph{absolute} and
\emph{relative} generics. \emph{Absolute generics} use a fixed, 50\%
threshold on prevalence: \(P(F\mid K)>0.5\). Roughly speaking,
\enquote{Dogs have four legs} is true because a given dog is more likely
than not to have four legs. \emph{Relative generics} depend upon an
alternative set of kinds (his notation: \(Alt(K)\)), analogous to our
comparison class. \enquote{Mosquitos carry malaria} is a relative
generic: it is true because an arbitrary mosquito is more likely than an
arbitrary member of an alternative kind to have the feature.

Our uncertain-threshold model deviates from Cohen's account in two
primary ways. First, though his theory is framed in terms of
probabilities, it still utilities a fixed threshold semantics and thus
is only able to make predictions about what is \enquote{true} and what
is \enquote{false}. In our theory, there is uncertainty about the core
semantic meaning, and this uncertainty (though reduced in context)
drives the model to make graded predictions about endorsement. Second,
Cohen draws an \emph{a priori} distinction between \emph{Absolute} and
\emph{Relative} generics, and provides different mechanisms for each
each. We used examples of both in our stimuli (Expt. 1) and found that
our single model handles both without any addition assumptions, casting
doubt on the \emph{a priori} distinction between \enquote{absolute} and
\enquote{relative.}\footnote{For a related theory that aims to do away
  with the distinction between \enquote{absolute} and \enquote{relative}
  adjectives, see Lassiter and Goodman (2015).}

We note additional machinery that Cohen's theory relies upon (and that
is not currently required in our account) to explain the
context-sensitivity of generics: contextually restricting the entities
that go into the computation of prevalence (i.e., which robins do we
look at to compute the probability of \emph{laying eggs} among
\emph{robins}?). His theory posits that prevalence is calculuated by
only considering entities that \emph{could have some feature} in a
contextually-specified alternative set of features (so called
\(Alt(F)\)). For example, the property \enquote{lays eggs} induces a set
of alternatives that are associated with mechanisms of reproduction
(e.g., \enquote{gives birth to live young}, \enquote{undergoes mitosis},
\ldots{}). Therefore, \enquote{Robins lay eggs} is evaluated as an
\emph{absolute generic} because only individuals that are female members
of kinds are under consideration, because only the female members can
plausibly satisfy one of the other aternatives having to do with
reproduction (i.e., the alternative features in \(Alt(F)\)). The
inferential machinery behind Cohen's domain restriction (i.e., what
comrpises \(Alt(F)\)?) relies upon conceptual information, but the
details remain obscure (Carlson, 1995).\footnote{However, see Cohen
  (2004) for a discussion of how his semantic constraints relate to
  different kinds of generics and different kinds of conceptual
  representational frameworks found in cognitive science.} However, we
note that this mechanism may be implicit in our own theory: the prior
distribution over the prevalence of \emph{lays eggs} presumably includes
aspects of people's theories about reproduction (i.e., that only females
lay eggs). Thus, there may exist a refactorization of the uncertain
threshold model to a fixed threshold where the listener has uncertainty
about the relevant domain restriction.

\paragraph{\texorpdfstring{\enquote{Normal}
accounts}{Normal accounts}}\label{normal-accounts}

The primary alternative view under the statistical banner draws on the
intuition that generics express something normative in the world (Asher
\& Morreau, 1995; Nickel, 2008; F. J. Pelletier \& Asher, 1997). For
example, \enquote{Dogs have four legs} is a good generalization even
though, regrettably, not all dogs have four legs. However, were the
world to function \emph{normally} (e.g., dogs would not be involved in
freak-tractor accidents or be born with strange genetic mutations), then
\emph{all} dogs would have four legs. The idea that our beliefs about
what is normal in the world influences our judgments about
generalizations has intuitive appeal for rejecting accidentally true
generalizations (e.g., \enquote{Supreme Court justices have even social
security numbers}; described above) and stereotyped language (e.g.,
\enquote{Boys are good at math}). Our theory does not directly formalize
\enquote{what is normal}, though we argue that a speaker's beliefs about
what is \emph{probable} (which may relate to what is \emph{normal}; see
Icard, Kominsky, \& Knobe, 2017) plays a role in endorsing and
interpreting generalizations. We showed in Expt. 2c that a speaker's
beliefs about what is likely to be the case in the near future matters
above and beyond what is currently true in the world for endorsing
generalizations. Our notion of prevalence is as a predictive
probability, which incorporates background knowledge in order to make
predictions about the future.

\paragraph{Underquantification}\label{underquantification}

A proposal similar to our account concerning underspecification of
generics has been made in the computational linguistics literature
(so-called \emph{underquantification}; Herbelot \& Copestake, 2011). In
their model, generics express an explicit quantified relation,
specifically either \enquote{Some}, \enquote{Most}, or \enquote{All}.
The task of the computational linguist, then, is to construct a set of
features that accurately predicts (relative to human judgments) the
quantified relationship expressed by the generic (Cimpian et al., 2010;
analagous to a quantifier version of the \emph{implied prevalence} task
used in Gelman \& Raman, 2003). Our semantic theory can be seen as a
generalization of the \emph{underquantification} to a continuous
interval of possible meanings. This distinction is relevant for the
acquisition of the language of generalizations; we do not think that
quantified relations (e.g., \enquote{Some}, \enquote{All}) are in any
way primary or special. Additionally, by using a vague, underspecified
threshold, our formulation naturally extends to other scales and other
kinds of generalizations (e.g., habitual language), where quantified
relations like \enquote{Most} or \enquote{All} are not directly
applicable.

\paragraph{Generic as indexical}\label{generic-as-indexical}

Sterken (2015) has recently proposed an intruiging account of the
context-sensitive of generic language by treating generics as a kind of
\emph{indexical} (e.g., \enquote{this} or \enquote{I}). The variability
of endorsements is then attributed to mechanisms of domain restriction
(described above with Cohen (1999)) and context-sensitive
\enquote{quantificational force}. Our uncertain-threshold semantics may
be a precise formalization of Sterken (2015)'s \enquote{quantificational
force} (and a generalization of \emph{underquantification}, see above),
and we have argued above that domain restriction is not a necessary
mechanisms for the cases considered in this paper. We leave for future
work exploring how the context-sensitivity of an indexical may differ
from the kind of context-sensitivity in our model.

\subsubsection{Conceptual accounts}\label{conceptual-accounts}

Conceptual accounts of generics emphasize the structure of generic
knowledge (Prasada, 2000), and view generic utterances as the way of
expressing special mental relationships between kinds and properties
(Leslie, 2008; Prasada et al., 2012). These accounts start with the
perspective that generics express rich, conceptual relationships between
kinds and properties. That is, \enquote{Bishops move diagonally} not
because of a statistical relationship, but rather, because those are the
rules of the game; if you start moving the bishop other ways besides
diagonally, you cease to be playing chess. If a lion lacked the capacity
to roar, we might consider a less good example of being a lion because
\enquote{lions roar}.

The most influential conceptual account of generics is from Leslie
(2007). For Leslie, generics are tied to the cognitive system's
\enquote{default mode of generalization}, which infants seem ready to
make use of by drawing strong generalizations from small amounts of data
(e.g., Baldwin, Markman, \& Melartin, 1993). Leslie's \enquote{default
mode} comes equipped with the ability to single-out
\emph{striking properties} (e.g., properties which are dangerous or
appalling) as particularly useful aspects of the world to know about.
Hence, \enquote{Mosquitos carry malaria} is true because malaria can
kill you and is useful to know about.

This accounts predicts that generics that convey striking properties
should be endorsed even when they are relatively rare in the category
(i.e., low referent-prevalence; e.g., \enquote{Sharks attack swimmers}).
Indeed, naturalistic examples (e.g., \enquote{Sharks attack swimmers})
and artificial examples (e.g., \enquote{Lorches have purple feathers})
supplemented with striking information (e.g.,\enquote{These feathers are
as sharp as needles and can easily get lodged in you, causing massive
bleeding}) are endorsed when the prevalence is quite low (e.g., 30\% of
lorches have purple feathers; Cimpian et al. (2010); see Expt. 1 for
naturalistic cases). In pilot work, using a paradigm similar to the
prior manipulation paradigm employed in the causal language experiments
(Expt. 3a), we have observed that the prior distribution over the
prevalence \(P(h)\) change when supplied information about the
dangerousness of the feature. That is, our pilot work suggests that
experiments that experimentally induce beliefs about the dangerousness
of a feature also manipulate the prevalence priors. Thus, our model
would also predict these effects, but by way of the prevalence priors
rather than some direct connection between generics and striking
features.

Of course, not all generics convey striking or appalling information
(e.g., \enquote{Birds lay eggs}). Leslie's default mode, thus, also
distinguishes \emph{negative counter-instances} of a property (e.g., a
bird that doesn't lay eggs, such as a male bird) from \emph{positive
counter-instances} (e.g., a hypothetical bird that bears live young) The
conceptual account argues that generics are much less reasonable when
\emph{positive} counter-instances exist. For example, \enquote{Birds are
female} seems weird because \emph{being male} is a \emph{positive}
counter-instance of \emph{being female}, but since there are no birds
that bear live young (i.e., no \emph{positive counter-instances}),
\enquote{Birds lay eggs} is fine. In the current version of our theory,
both kinds of counter-instances influence the referent-category
feature-probabilities, though only positive counter-instances could
impact the statistical details of the comparison class (in particular,
when constructed with respect to the feature; see discussion about the
Comparison Class). Thus, the notion of \emph{positive} and
\emph{negative} counter-instances may result from a particular way of
looking at the constructs posited in our model, namely prevalences
within- and across- categories or features.

Finally, generics are not limited to conveying rich, conceptual
information; they are also used to describe facts of the world.
\enquote{Ravens are bigger than toasters} is a true statement, but not
because of a rich relationship between ravens and toasters.
\enquote{Barns are red} because most barns are red. If farmers around
the world decided to paint their barns green, the things they would be
painting would still be barns; in that world, we might say
\enquote{Barns are green}. Thus, conceptual accounts must be
supplemented with the proviso that in ceratin situations, the statistics
of the world are relevant.

Our view is that subjective probabilities can be formed either from
worldly observations or because of the structure of people's mental
representations. In the last fifteen years, there has been tremendous
progress in formalizing Rich, structural mental representations can be
formalized in probabilistic models, which can be used to derive
quantitative predictions about inferences derived from that knowledge
(Tenenbaum, Kemp, Griffiths, \& Goodman, 2011). For example, Kemp and
Tenenbaum (2008) introduced a model for learning different kinds of
structural relationships between objects and properties (e.g.,
taxonomies, social cliques, dominance relations). Goodman et al. (2015)
argue that concepts and intuitive theories can be constructed from
elementary random primitives using insights from \emph{probabilistic
programmming}.

In this paper, we take a minimalist approach to modeling conceptual
structure, incorporating only what is necessary into the interpreter's
background knowledge, the prior on prevalence \(P(h)\). In our Bayesian
data analysis of background knowledge, we use a mixture model that
reflects basic knowledge about kinds and properties (e.g., that most
kinds don't have most properites).\\
It's plausible that more richly structured knowledge of the kind
described by Prasada et al. (2013) and Leslie (2007) can be
incorporating into the general probabilsitic framework that we use here.

The key point of divergence then between the conceptual accounts and our
view concerns the core, semantic meaning of a generic statement.
Conceptual accounts try to identify the core meaning of a generalization
directly with aspects of conceptual structure. For us, the semantics
concerns a probability, which is the byproduct of a conceptual
structure, but it is not the conceptual structure itself. We believe
this provides a more unifying view of generics, giving a single metric
as the basic currency of generic meaning: probability.

\section{Conclusion}\label{conclusion}

It might seem paradoxical that a part of language that is so common in
communication and central to learning should be vague. Shouldn't
speakers and teachers want to express their ideas as crisply as
possible? To the contrary, underspecification can be efficient, given
that context can be used to resolve uncertainty in meaning (Piantadosi,
Tily, \& Gibson, 2012). In our work, context takes the form of shared
beliefs about the property in question. By leveraging this common
ground, genericity provide a powerful way to communicate and learn
generalizations, which would otherwise be difficult or costly
information to learn through direct experience.

The dark side of this flexibility is the potential for miscommunication
or deceit: A speaker might assert a generalization that she herself
would not accept, conveying a too-strong generalization to a naive
listener. Our model predicts this potential particularly for properties
which, when present, are widespread in a category; biological properties
are believed to have this distribution, but many properties of social
categories may as well (Cimpian \& Markman, 2011; Cimpian, Mu, \&
Erickson, 2012; Rhodes et al., 2012). Disagreements are also predicted
when interlocutors fail to share background assumptions, which could be
differences in the prior distributions on prevalence or the comparison
class. Core aspects of political disagreement then (e.g., as to whether
\enquote{Humans cause global warming}) could be derived from differences
in the estimated causal responsibility of the category in question
(e.g., what impacts humans are having), of \emph{other forces} (e.g.,
plate tectonics), as well as the comparison class of other forces (e.g.,
what are the alternative causes?). This is a promising area for future
research.

Categories are inherently unobservable. You cannot see the category
\textsc{dog}, only some number of instances of it. Yet we easily talk
about these abstractions, conveying hard-won generalizations to each
other and down through generations. The theory presented here provides
the first computational perspective on how we communicate
generalizations and how beliefs play a central role in the meaning of
words.

\newpage

\section{References}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Asher1995}{}
Asher, N., \& Morreau, M. (1995). What some generic sentences mean.
\emph{The Generic Book}, 300--338.

\hypertarget{ref-Baldwin1993}{}
Baldwin, D. A., Markman, E. M., \& Melartin, R. L. (1993). Infants '
Ability to Draw Inferences about Nonobvious Object Properties: Evidence
from Exploratory Play. \emph{Child Development}, \emph{64}(3), 711--728.

\hypertarget{ref-Bale2011}{}
Bale, A. C. (2011). Scales and comparison classes. \emph{Natural
Language Semantics}, \emph{19}, 169--190.

\hypertarget{ref-Behrens2005}{}
Behrens, L. (2005). Genericity from a cross-linguistic perspective.
\emph{Linguistics}, \emph{43}(2), 275--344.

\hypertarget{ref-Bergen2016}{}
Bergen, L., Levy, R., \& Goodman, N. D. (To appear). Pragmatic reasoning
through semantic inference. \emph{Semantics and Pragmatics}.

\hypertarget{ref-Brandone2014}{}
Brandone, A. C., Gelman, S. A., \& Hedglen, J. (2014). Children's
Developing Intuitions About the Truth Conditions and Implications of
Novel Generics Versus Quantified Statements. \emph{Cognitive Science},
1--28.

\hypertarget{ref-Carlson1977}{}
Carlson, G. N. (1977). \emph{Reference to kinds in english}
(PhD thesis). University of Massachusetts, Amherst.

\hypertarget{ref-Carlson1995essay}{}
Carlson, G. N. (1995). Truth conditions of generic sentences: Two
contrasting views. In G. N. Carlson \& F. J. Pelletier (Eds.), \emph{The
generic book} (pp. 224--38). Chicago: University of Chicago Press.

\hypertarget{ref-Carlson1995}{}
Carlson, G. N., \& Pelletier, F. J. (1995). \emph{The generic book.}
Chicago, IL: Chicago University Press.

\hypertarget{ref-Cheng1997}{}
Cheng, P. W. (1997). From Covariation to Causation: A Causal Power
Theory. \emph{Psychological Review}, \emph{104}(2), 367--405. Retrieved
from \url{http://psycnet.apa.org/fulltext/1997-03612-007.pdf}

\hypertarget{ref-Cheng1992}{}
Cheng, P. W., \& Npvick, L. R. (1992). Covariation in Natural Causal
Induction. \emph{Psychological Review}, \emph{99}(2), 365--382.
Retrieved from \url{http://psycnet.apa.org/fulltext/1992-26096-001.pdf}

\hypertarget{ref-Cimpian2008}{}
Cimpian, A., \& Markman, E. M. (2008). Preschool children's use of cues
to generic meaning. \emph{Cognition}, \emph{107}, 19--53.
doi:\href{https://doi.org/10.1016/j.cognition.2007.07.008}{10.1016/j.cognition.2007.07.008}

\hypertarget{ref-Cimpian2011a}{}
Cimpian, A., \& Markman, E. M. (2011). The Generic/Nongeneric
Distinction Influences How Children Interpret New Information About
Social Others. \emph{Child Development}, \emph{82}(2), 471--492.
doi:\href{https://doi.org/10.1111/j.1467-8624.2010.01525.x}{10.1111/j.1467-8624.2010.01525.x}

\hypertarget{ref-Cimpian2007}{}
Cimpian, A., Arce, H.-M. C., Dweck, C. S., \& Markman, E. M. (2007).
Subtle Linguistic Cues Affect Children's Motivation. \emph{Psychological
Science}, \emph{18}(4), 314--316.

\hypertarget{ref-Cimpian2010}{}
Cimpian, A., Brandone, A. C., \& Gelman, S. A. (2010). Generic
statements require little evidence for acceptance but have powerful
implications. \emph{Cognitive Science}, \emph{34}(8), 1452--1482.

\hypertarget{ref-Cimpian2012b}{}
Cimpian, A., Mu, Y., \& Erickson, L. C. (2012). Who Is Good at This
Game? Linking an Activity to a Social Category Undermines Children's
Achievement. \emph{Psychological Science}, \emph{23}(5), 533--541.
doi:\href{https://doi.org/10.1177/0956797611429803}{10.1177/0956797611429803}

\hypertarget{ref-Cohen1999}{}
Cohen, A. (1999). Generics, Frequency Adverbs, and Probability.
\emph{Linguistics and Philosophy}, \emph{22}.

\hypertarget{ref-Cohen2004}{}
Cohen, A. (2004). Generics and Mental Representations. \emph{Linguistics
and Philosophy}, \emph{27}(5), 529--556.
doi:\href{https://doi.org/10.1023/B:LING.0000033851.25870.3e}{10.1023/B:LING.0000033851.25870.3e}

\hypertarget{ref-Cree2006}{}
Cree, G. S., McNorgan, C., \& McRae, K. (2006). Distinctive features
hold a privileged status in the computation of word meaning:
Implications for theories of semantic memory. \emph{Journal of
Experimental Psychology. Learning, Memory, and Cognition}, \emph{32}(4),
643--658.
doi:\href{https://doi.org/10.1037/0278-7393.32.4.643}{10.1037/0278-7393.32.4.643}

\hypertarget{ref-Degen2014}{}
Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
dependent measures in experimental pragmatics. In \emph{Proceedings of
the thirty-sixth annual conference of the Cognitive Science Society}.

\hypertarget{ref-Dewar2010}{}
Dewar, K. M., \& Xu, F. (2010). Induction, overhypothesis, and the
origin of abstract knowledge: Evidence from 9-month-old infants.
\emph{Psychological Science}, \emph{21}, 1871--1877.
doi:\href{https://doi.org/10.1177/0956797610388810}{10.1177/0956797610388810}

\hypertarget{ref-Frank2012}{}
Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
in language games. \emph{Science}, \emph{336}(6084).

\hypertarget{ref-Franke2014cogsci}{}
Franke, M. (2014). Typical use of quantifiers: A probabilistic speaker
model. In \emph{Proceedings of the 36th annual meeting of the cogntiive
science society} (pp. 1--6). Retrieved from
\href{http://staff.science.uva.nl/\%7B~\%7Dmfranke/Papers/Franke\%7B/_\%7D2014\%7B/_\%7DTypical\%20use\%20of\%20quantifiers\%20A\%20probabilistic\%20speaker\%20model.pdf}{http://staff.science.uva.nl/\{\textasciitilde{}\}mfranke/Papers/Franke\{\textbackslash{}\_\}2014\{\textbackslash{}\_\}Typical use of quantifiers A probabilistic speaker model.pdf}

\hypertarget{ref-Gelman2003}{}
Gelman, S. A. (2003). \emph{Essential child: Origins of
essentialntialism in everyday thought.} Oxford University Press.

\hypertarget{ref-Gelman2004}{}
Gelman, S. A. (2004). Learning words for kinds: Generic noun phrases in
acquisition. In \emph{Weaving a lexicon} (pp. 445--484). MIT Press.

\hypertarget{ref-Gelman1999}{}
Gelman, S. A., \& Heyman, G. D. (1999). Carrot-Eaters and
Creature-Believers: The Effects of Lexicalization on Children's
Inferences About Social Categories. \emph{Psychological Science},
\emph{10}(6), 489--493.
doi:\href{https://doi.org/10.1111/1467-9280.00194}{10.1111/1467-9280.00194}

\hypertarget{ref-Gelman2003b}{}
Gelman, S. A., \& Raman, L. (2003). Preschool children use linguistic
form class and pragmatic cues to interpret generics. \emph{Child
Development}, \emph{74}(1), 308--325.

\hypertarget{ref-Gelman1998}{}
Gelman, S. A., Coley, J. D., Rosengren, K. S., Hartman, E., \& Pappas,
A. (1998). Beyond labeling: the role of maternal input in the
acquisition of richly structured categories. \emph{Monographs of the
Society for Research in Child Development}, \emph{63}(1), I--V,
1--148;discussion 149--157.

\hypertarget{ref-Gelman2008}{}
Gelman, S. A., Goetz, P. J., Sarnecka, B. W., \& Flukes, J. (2008).
Generic Language in Parent-Child Conversations. \emph{Language Learning
and Development}, \emph{4}(1), 1--31.
doi:\href{https://doi.org/10.1080/15475440701542625.Generic}{10.1080/15475440701542625.Generic}

\hypertarget{ref-Gelman2015}{}
Gelman, S. A., Leslie, S.-J., Was, A. M., \& Koch, C. M. (2015).
Children's interpretations of general quantifiers, specific quantifiers
and generics. \emph{Language, Cognition and Neuroscience}, \emph{30}(4),
448--461.
doi:\href{https://doi.org/10.1080/23273798.2014.931591}{10.1080/23273798.2014.931591}

\hypertarget{ref-GelmanEtAl2004}{}
Gelman, S. A., Taylor, M. G., Nguyen, S. P., Leaper, C., \& Bigler, R.
S. (2004). Mother-child conversations about gender: Understanding the
acquisition of essentialist beliefs. \emph{Monographs of the Society for
Research in Child Development}, \emph{69}(1), vii, 116--127.
doi:\href{https://doi.org/10.1111/j.1540-5834.2004.06901001.x}{10.1111/j.1540-5834.2004.06901001.x}

\hypertarget{ref-Gerstenberg2015how}{}
Gerstenberg, T., Goodman, N. D., Lagnado, D. A., \& Tenenbaum, J. B.
(2015). How, whether, why: Causal judgments as counterfactual contrasts.
In D. C. Noelle, R. Dale, A. S. Warlaumont, J. Yoshimi, J. Matlock T.,
C. D., \& P. P. Maglio (Eds.), \emph{Proceedings of the 37th Annual
Conference of the Cognitive Science Society} (pp. 782--787). Austin, TX:
Cognitive Science Society.

\hypertarget{ref-Goodman2016}{}
Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language
interpretation as probabilistic inference. \emph{Trends in Cognitive
Sciences}.

\hypertarget{ref-dippl}{}
Goodman, N. D., \& Stuhlmüller, A. (2014). The Design and Implementation
of Probabilistic Programming Languages. \url{http://dippl.org}.

\hypertarget{ref-Goodmanconcepts}{}
Goodman, N. D., Tenenbaum, J. B., \& Gerstenberg, T. (2015). Concepts in
a probabilistic language of thought. In \emph{The conceptual mind: New
directions in the study of concepts}. MIT Press.

\hypertarget{ref-Gopnik2003theory}{}
Gopnik, A. (2003). The theory theory as an alternative to the innateness
hypothesis. \emph{Chomsky and His Critics}, 238--254.

\hypertarget{ref-Griffiths2005}{}
Griffiths, T. L., \& Tenenbaum, J. B. (2005). Structure and strength in
causal induction. \emph{Cognitive Psychology}, \emph{51}(4), 334--84.
doi:\href{https://doi.org/10.1016/j.cogpsych.2005.05.004}{10.1016/j.cogpsych.2005.05.004}

\hypertarget{ref-Griffiths2009}{}
Griffiths, T. L., \& Tenenbaum, J. B. (2009). Theory-Based Causal
Induction. \emph{Psychological Review}, \emph{116}(4), 661--716.
doi:\href{https://doi.org/10.1037/a0017201}{10.1037/a0017201}

\hypertarget{ref-Gweon2010}{}
Gweon, H., Tenenbaum, J. B., \& Schulz, L. E. (2010). Infants consider
both the sample and the sampling process in inductive generalization.
\emph{Proceedings of the National Academy of Sciences of the United
States of America}, \emph{107}(20), 9066--71.
doi:\href{https://doi.org/10.1073/pnas.1003095107}{10.1073/pnas.1003095107}

\hypertarget{ref-Haslanger2011}{}
Haslanger, S. (2011). Ideology, generics, and common ground. In
\emph{Feminist metaphysics} (pp. 179--207). Springer.

\hypertarget{ref-Henrich2015}{}
Henrich, J. (2015). \emph{The secret of our success: how culture is
driving human evolution, domesticating our species, and making us
smarter}. Princeton University Press.

\hypertarget{ref-Herbelot2011}{}
Herbelot, A., \& Copestake, A. (2011). Formalising and specifying
underquantification Quantification resolution. In \emph{IWCS} (pp.
165--174).

\hypertarget{ref-HumeTHN}{}
Hume, D. (1888). (L. A. Selby Bigge, Ed.). Oxford, Clarendon Press.

\hypertarget{ref-Icard2017}{}
Icard, T. F., Kominsky, J. F., \& Knobe, J. (2017). Normality and actual
causal strength. \emph{Cognition}, \emph{161}, 80--93.
doi:\href{https://doi.org/10.1016/j.cognition.2017.01.010}{10.1016/j.cognition.2017.01.010}

\hypertarget{ref-Keil1979}{}
Keil, F. C. (1979). \emph{Semantic and conceptual development.} Harvard
University Press.

\hypertarget{ref-Keil1992}{}
Keil, F. C. (1992). \emph{Concepts, kind, and cognitive development.}
MIT Press.

\hypertarget{ref-Kemp2008}{}
Kemp, C., \& Tenenbaum, J. B. (2008). The discovery of structural form.
\emph{Proceedings of the National Academy of Sciences of the United
States of America}, \emph{105}(31), 10687--10692.
doi:\href{https://doi.org/10.1073/pnas.0802631105}{10.1073/pnas.0802631105}

\hypertarget{ref-Kennedy2007}{}
Kennedy, C. (2007). Vagueness and grammar: the semantics of relative and
absolute gradable adjectives. \emph{Linguistics and Philosophy},
\emph{30}, 1--35.
doi:\href{https://doi.org/10.1007/s10988-006-9008-0}{10.1007/s10988-006-9008-0}

\hypertarget{ref-Khemlani2012}{}
Khemlani, S., Leslie, S.-J., \& Glucksberg, S. (2012). Inferences about
members of kinds: The generics hypothesis. \emph{Language and Cognitive
Processes}, \emph{27}(6), 887--900.
doi:\href{https://doi.org/10.1080/01690965.2011.601900}{10.1080/01690965.2011.601900}

\hypertarget{ref-KrifkaGenericBookFocus}{}
Krifka, M. (1995). Focus and the interpretation of generic sentences. In
G. N. Carlson \& F. J. Pelletier (Eds.), \emph{The generic book} (pp.
238--264). Chicago: University of Chicago Press.

\hypertarget{ref-Lassiter2013}{}
Lassiter, D., \& Goodman, N. D. (2013). Context, scale structure, and
statistics in the interpretation of positive-form adjectives. In
\emph{Semantics and Linguistic Theory (SALT) 23}.

\hypertarget{ref-Lassiter2015}{}
Lassiter, D., \& Goodman, N. D. (2015). Adjectival vagueness in a
bayesian model of interpretation. \emph{Synthese}.

\hypertarget{ref-Leslie2007}{}
Leslie, S.-J. (2007). Generics and the Structure of the Mind.
\emph{Philosophical Perspectives}, \emph{21}(1), 375--403.

\hypertarget{ref-Leslie2008}{}
Leslie, S.-J. (2008). Generics: Cognition and acquisition.
\emph{Philosophical Review}, \emph{117}(1).

\hypertarget{ref-Leslie2012a}{}
Leslie, S.-J., \& Gelman, S. A. (2012). Quantified statements are
recalled as generics: Evidence from preschool children and adults.
\emph{Cognitive Psychology}, \emph{64}(3), 186--214.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.12.001}{10.1016/j.cogpsych.2011.12.001}

\hypertarget{ref-Levinson1995}{}
Levinson, S. C. (1995). Interactional biases in human thinking. In E. N.
Goody (Ed.), \emph{Social intelligence and interaction} (pp. 221--260).
Cambridge University Press.

\hypertarget{ref-McGuire1986}{}
McGuire, W. J., \& McGuire, C. V. (1986). Differences in conceptualizing
self versus conceptualizing other people as manifested in contrasting
verb types used in natural speech. \emph{Journal of Personality and
Social Psychology}, \emph{51}(6), 1135--43.
doi:\href{https://doi.org/10.1037/0022-3514.51.6.1135}{10.1037/0022-3514.51.6.1135}

\hypertarget{ref-Montague1973}{}
Montague, R. (1973). The Proper Treatment of Quantification in Ordinary
English. In \emph{Philosophy, language, and artificial intelligence}
(pp. 141-----162). Springer. Retrieved from
\url{http://semantics.uchicago.edu/kennedy/classes/s08/semantics2/montague73.pdf}

\hypertarget{ref-Nickel2008}{}
Nickel, B. (2008). Generics and the ways of normality. \emph{Linguistics
and Philosophy}, \emph{31}(6), 629--648.
doi:\href{https://doi.org/10.1007/s10988-008-9049-7}{10.1007/s10988-008-9049-7}

\hypertarget{ref-Nickel2016}{}
Nickel, B. (2016). \emph{Between logic and the world}. Oxford: Oxford
UP; Oxford UP.

\hypertarget{ref-Nisbett1983}{}
Nisbett, R. E., Krantz, D. H., Jepson, C., \& Kunda, Z. (1983). The use
of statistical heuristics in everyday inductive reasoning.
\emph{Psychological Review}, \emph{90}(4), 339--363.
doi:\href{https://doi.org/10.1037/0033-295X.90.4.339}{10.1037/0033-295X.90.4.339}

\hypertarget{ref-pearl1988probabilistic}{}
Pearl, J. (1988). Probabilistic reasoning in intelligent systems:
Networks of plausible reasoning. Morgan Kaufmann Publishers, Los Altos.

\hypertarget{ref-Pelletier1997}{}
Pelletier, F. J., \& Asher, N. (1997). Generics and defaults. handbook
of logic and language, ed. by j. van benthem and alice gb ter meulen,
1125--1177. Cambridge: The MIT Press.

\hypertarget{ref-Piantadosi2012}{}
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.
doi:\href{https://doi.org/10.1016/j.cognition.2011.10.004}{10.1016/j.cognition.2011.10.004}

\hypertarget{ref-Prasada2000}{}
Prasada, S. (2000). Acquiring generic knowledge. \emph{Trends in
Cognitive Sciences}, \emph{4}(2), 66--72.
doi:\href{https://doi.org/10.1016/S1364-6613(99)01429-1}{10.1016/S1364-6613(99)01429-1}

\hypertarget{ref-Prasada2012}{}
Prasada, S., Hennefield, L., \& Otap, D. (2012). Conceptual and
Linguistic Representations of Kinds and Classes. \emph{Cognitive
Science}, \emph{36}(7), 1224--1250.
doi:\href{https://doi.org/10.1111/j.1551-6709.2012.01254.x}{10.1111/j.1551-6709.2012.01254.x}

\hypertarget{ref-Prasada2013}{}
Prasada, S., Khemlani, S., Leslie, S.-J., \& Glucksberg, S. (2013).
Conceptual distinctions amongst generics. \emph{Cognition},
\emph{126}(3), 405--22.
doi:\href{https://doi.org/10.1016/j.cognition.2012.11.010}{10.1016/j.cognition.2012.11.010}

\hypertarget{ref-Qing2014}{}
Qing, C., \& Franke, M. (2014). Gradable adjectives, vagueness, and
optimal language use: A speaker-oriented model. In \emph{Semantics and
Linguistic Theory (SALT) 24}.

\hypertarget{ref-Repacholi1997}{}
Repacholi, B. M., \& Gopnik, A. (1997). Early reasoning about desires:
evidence from 14- and 18-month-olds. \emph{Developmental Psychology},
\emph{33}(1), 12--21.
doi:\href{https://doi.org/10.1037/0012-1649.33.1.12}{10.1037/0012-1649.33.1.12}

\hypertarget{ref-Rhodes2012}{}
Rhodes, M., Leslie, S.-J., \& Tworek, C. M. (2012). Cultural
transmission of social essentialism. \emph{Proceedings of the National
Academy of Sciences}, \emph{109}(34), 13526--13531.
doi:\href{https://doi.org/10.1073/pnas.1208951109}{10.1073/pnas.1208951109}

\hypertarget{ref-Ritchie2016}{}
Ritchie, D., Stuhlmüller, A., \& Goodman, N. D. (2016). C3: Lightweight
incrementalized mcmc for probabilistic programs using continuations and
callsite caching. In \emph{AISTATS 2016}.

\hypertarget{ref-roberts1996qud}{}
Roberts, C. (1996). Information structure in discourse: Towards an
integrated formal theory of pragmatics. \emph{Working Papers in
Linguistics-Ohio State University Department of Linguistics}, 91--136.

\hypertarget{ref-hurdleModels}{}
Rose, C. E., Martin, S. W., Wannemuehler, K. A., \& Plikaytis, B. D.
(2006). On the use of zero-inflated and hurdle models for modeling
vaccine adverse event count data. \emph{Journal of Biopharmaceutical
Statistics}, \emph{16}(4), 463--481.

\hypertarget{ref-Schmidt2009}{}
Schmidt, L. A., Goodman, N. D., Barner, D., \& Tenenbaum, J. B. (2009).
How Tall Is Tall? Compositionality, Statistics, and Gradable Adjectives.
In \emph{Proceedings of the 31st annual conference of the cognitive
science society}.

\hypertarget{ref-Seiver2013}{}
Seiver, E., Gopnik, A., \& Goodman, N. D. (2013). Did She Jump Because
She Was the Big Sister or Because the Trampoline Was Safe? Causal
Inference and the Development of Social Attribution. \emph{Child
Development}, \emph{84}(2), 443--454.
doi:\href{https://doi.org/10.1111/j.1467-8624.2012.01865.x}{10.1111/j.1467-8624.2012.01865.x}

\hypertarget{ref-Shepard1987}{}
Shepard, R. N. (1987). Toward a universal law of generalization for
psychological science. \emph{Science (New York, N.Y.)},
\emph{237}(4820), 1317--1323.
doi:\href{https://doi.org/10.1126/science.3629243}{10.1126/science.3629243}

\hypertarget{ref-Solt2009}{}
Solt, S. (2009). Notes on the Comparison Class. In \emph{International
workshop on vagueness in communication} (pp. 189-----206). Springer.

\hypertarget{ref-Solt2012}{}
Solt, S., \& Gotzner, N. (2012). Experimenting with degree.
\emph{Proceedings of SALT}, \emph{22}, 166--187.

\hypertarget{ref-Sommers1963}{}
Sommers, F. (1963). Types and ontology. \emph{The Philosophical Review},
327--363.

\hypertarget{ref-Sterken2015}{}
Sterken, R. K. (2015). Generics in Context. \emph{Philosophers'
Imprint}, \emph{15}(i), 1--30.

\hypertarget{ref-Tenenbaum2001}{}
Tenenbaum, J. B., \& Griffiths, T. L. (2001). Generalization, similarity
and Bayesian inference. \emph{Behavioral and Brain Sciences}, \emph{24},
629--640.
doi:\href{https://doi.org/10.1017/S0140525X01000061}{10.1017/S0140525X01000061}

\hypertarget{ref-Tenenbaum2011}{}
Tenenbaum, J. B., Kemp, C., Griffiths, T. L., \& Goodman, N. D. (2011).
How to grow a mind: statistics, structure, and abstraction.
\emph{Science (New York, N.Y.)}, \emph{331}(6022), 1279--85.
doi:\href{https://doi.org/10.1126/science.1192788}{10.1126/science.1192788}

\hypertarget{ref-Tessler2017}{}
Tessler, M. H., Lopez-Brau, M., \& Goodman, N. D. (2017). Warm (for
winter): Comparison class understanding in vague language. In
\emph{Proceedings of the thirty-ninth annual conference of the cognitive
science society}.

\hypertarget{ref-Tomasello1999}{}
Tomasello, M. (1999). \emph{The cultural origins of human cognition}.
Cambridge, MA: Harvard University Press.

\hypertarget{ref-Tversky1974}{}
Tversky, A., \& Kahneman, D. (1974). Judgment under Uncertainty:
Heuristics and Biases. \emph{Science}, \emph{185}(4157), 1124--31.
doi:\href{https://doi.org/10.1126/science.185.4157.1124}{10.1126/science.185.4157.1124}

\hypertarget{ref-Yoon2016}{}
Yoon, E. J., Tessler, M. H., Goodman, N. D., \& Frank, M. C. (2016).
Talking with tact: Polite language as a balance between kindness and
informativity. In \emph{Proceedings of the thirty-eighth annual
conference of the cognitive science society}.

\hypertarget{ref-Yoon2017}{}
Yoon, E. J., Tessler, M. H., Goodman, N. D., \& Frank, M. C. (2017). ``I
won't lie, it wasn't amazing'': Modeling polite indirect speech.

\newpage

\section{Appendix A: The Relationship between the Prevalence Prior and
Cue
Validity}\label{appendix-a-the-relationship-between-the-prevalence-prior-and-cue-validity}

Cue validity is defined for a particular category--property pair (e.g.,
\emph{mosquitos} and \emph{carry malaria}), and relates to
referent-prevalence (e.g., how many mosquitos carry malaria) via the
prevalence of \emph{carrying malaria} in other categories \(k'\) by
Bayes' Rule: \[ p(k \mid f) = \frac{p(f \mid k) \cdot p(k)}{Z} \] where
\(Z = \sum_{k' \in K} p( f \mid k') \cdot p( k')\)

The prevalence prior \(P(p_f)\) (Eq. \ref{eq:L0}) is a probability
distribution over prevalence for different categories \(k'\). For ease
of exposition, let \(x = p_f = p(f \mid k)\); that is,
\(P(x) = P(p_f)\).

\underline{Claim:} The normalizing constant for computing cue validity
is equal to the expected value of the prevalence prior distribution:
\(\mathbb{E}[P(x)] = Z\)

\underline{Proof:}

By the definition of the expectation of a distribution:

\begin{eqnarray} \label{eq:expectation}
\mathbb{E}[P(x)] & = & \sum\limits_{x} x \cdot p(x) 
\end{eqnarray}

The probability of a prevalence \(x\) can be decomposed into the prior
probability of a category \(k\) and the likelihood of the prevalence
\(x\) given that category \(k\): \(p(x) = p(x \mid k) \cdot p(k)\). We
assume here, without loss of generality, that each category corresponds
to one and only one prevalence \(x\). Thus, \(p(x \mid k) = 1\) if
\(k \in K_x\), a set of categories that have a given prevalence:
\(K_x = \{k' : p_{fk'} = x\}\). Further, e partition of the set of all
categories \(K\) into non-overlapping \(K_x\)s. Thus:

\begin{eqnarray} \label{eq:prevToKinds}
p(x) & = & \sum\limits_{k' \in K_x} p(x \mid k') \cdot p( k') \nonumber \\
     & = & \sum\limits_{k' \in K_x} p(k')
\end{eqnarray}

since \(\forall k' \in K_{x}: p(x \mid k') = 1\). Returning to Eq.
\ref{eq:expectation}, we have:

\begin{eqnarray} \label{eq:eq3}
\mathbb{E}[P(x)] & = & \sum\limits_{x} x \sum\limits_{k' \in K_x} p(k') \nonumber \\
                  & = & \sum\limits_{x} \sum\limits_{k' \in K_x} x \cdot p(k')
\end{eqnarray}

The set of all partitioned subsets \(K_x\) is in a one-to-one
correspondence with the set of all prevalences \(x\). Thus, we have:

\begin{eqnarray} \label{eq:bijection}
  & = & \sum\limits_{K_x} \sum\limits_{k' \in K_x} x \cdot p( k')
\end{eqnarray}

Then, since \(\cup_{x}{K_x} = K\), we have

\begin{eqnarray} \label{eq:partition}
  & = & \sum\limits_{k' \in K} x \cdot p( k') \nonumber \\ 
  & = & \sum\limits_{k' \in K} p(f \mid k') \cdot p( k') \nonumber \\ 
  & = & Z
\end{eqnarray}

\(\square.\)

\newpage

\section{Appendix B: Measuring Cue
Validity}\label{appendix-b-measuring-cue-validity}

In Experiment 1, we articulated an alternative model by measuring cue
validity (and prevalence) and predicting generic endorsement from a
regression model. In a small review of the literature, we discovered
different methods for measuring cue validity; in piloting, these
different methods lead to different results. Therefore, we propose three
\emph{a priori} desiderata that a measurement of cue validity should
satisfy. We describe two experiments that represent the primary methods
for measuring cue validity and compare them with these desiderata in
mind. Finally, we compare the cue validity measured using these
different methods to cue validity derived from our prevalence prior
elicitation task (Expt. 1a, main text).

\subsection{Desiderata}\label{desiderata}

Measuring cue validity involves collecting participants' judgments that
relate to the probability that an exemplar is a member of a kind given
that is has a feature : \(P(x \in k \mid x \in f)\). There are several
ways one could measure cue validity. Here we consider two measures: One
that has participants estimate the probability
\(P(x \in k \mid x \in f)\) directly, a common technique in the
literature on generic language (e.g., Khemlani et al., 2012; Prasada et
al., 2013), and another that has participants freely produce categories
given a feature (i.e., draw a sample from the conditional distribution
on kinds given a feature; Cree et al., 2006). We will the former the
\emph{direct question} method and the latter the \emph{free production}
method.

Are the \emph{direct question} and the \emph{free productions} equally
valid for measuring cue validity? We propose \emph{a priori} three
boundary conditions that the measurement should be able to satisfy. For
each case, we provide four examples from our larger stimulus set on
generics (Case Study 1) which will be used to evaluate each measure.

\begin{enumerate}
\item{Completely diagnostic features: Some features are only present in one (or a very small number) of categories. Examples include: \emph{carrying malaria} (mosquitos), \emph{carrying Lyme disease} (ticks, deer), \emph{having manes} (lions), \emph{having pouches} (marsupials, including most famously: kangaroos). The cue validity of these features for the corresponding categories should be very high (at least 0.5 and possibly close to 1).}
\item{Completely absent features: Many features are completely absent in many kinds. For these, the cue validity should be extremely low or 0. There are infinite examples. The ones will use are \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger). }
\item{Completely undiagnostic features: A number of features are shared by almost every category. The ones we will use are: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard). The cue validity of these features for particular categories should be extremely low or 0. Learning that an entity is female tells you almost nothing about what kind of animal it is.}
\end{enumerate}

We collected cue validity ratings by running both a direct question and
a free production experiment. For the free production experiment, the
cue validity is the proportion of responses of the target category
(e.g., \enquote{mosquitos}) for the property (e.g., \enquote{carries
malaria}). Of primary interest is the measurement for the desiderata
items described above. Links to the experiments can be found on
\url{https://mhtess.github.io}.

\subsection{Experimental materials}\label{experimental-materials}

Materials were the same for both experiments. They were a collection of
familiar properties and animal categories used in Expt. 1b (endorsement
of generic statements) described in the main text. There were twenty-one
properties in total.

\subsection{Direct question
experiment}\label{direct-question-experiment}

\subsubsection{Method}\label{method-7}

\paragraph{Participants}\label{participants-7}

We recruited 40 participants from Amazon's Mechanical Turk. Participants
were restricted to those with U.S. IP addresses and who had at least a
95\% work approval rating. The experiment took on average 5 minutes and
participants were compensated \$0.75 for their work.

\paragraph{Procedure}\label{procedure-4}

Following the procedure in Khemlani et al. (2012) and Prasada et al.
(2013), participants were presented with prompts of the following form:

\begin{quotation}
Imagine you come across a thing that \textsc{f}.
What are the odds that it is a \textsc{k}?
\end{quotation}

Participants responded using a slider bar with endpoints labeled
\enquote{unlikely} and \enquote{likely}. The slider appeared with no
handle present; participants had to click on the slider for the slider
handle to appear.

Participants completed the thirty target trials (corresponding to the
thirty generic statements used in Expt. 1b) in addition to ten filler
trials (total number of trials = 40). The filler trials were made up of
random category -- property pairings. Trials were presented in a
randomized order.

\subsection{Free production
experiment}\label{free-production-experiment}

\subsubsection{Method}\label{method-8}

\paragraph{Participants}\label{participants-8}

We recruited 100 participants from Amazon's Mechanical Turk.
Participants were restricted to those with U.S. IP addresses and who had
at least a 95\% work approval rating. The experiment took on average 3
minutes and participants were compensated \$0.40 for their work.

\paragraph{Procedure}\label{procedure-5}

On each trial, participants were presented with prompts of the following
form:

\begin{quotation}
Imagine you come across a thing (animal or insect) that \textsc{f}.
What do you think it is?
\end{quotation}

Participants responded by filling in a text box with their response.
There were twenty-one trials in total, one for each property. No filler
trials were used. Trials were presented in a randomized order.

\subsubsection{Free production data
processing}\label{free-production-data-processing}

To process the free production, we forced all characters in a repsonse
to lower case, removed spaces, and made all terms into singular terms
(e.g., \enquote{lions} --\textgreater{} \enquote{lion}). As well,
\enquote{mosquito} was a commonly mispelled label; we counted anything
that started with \enquote{mosqu}, \enquote{mesqu}, \enquote{misqu},
\enquote{mosiq} as \enquote{mosquito}.

To calculate confidence intervals for the free production data, we
resampled participants (with replacement) and computed the proportion of
responses that were of the target category (e.g., the proportion of
\enquote{mosquito} responses for the cue \enquote{carries malaria}). We
did this 1000 times to generate an empirical distribution from which
95\% intervals could be calculated.

\subsection{Results and Evaluation}\label{results-and-evaluation}

We are interested in the results of each measure (direct question and
free production) for the three conditions corresponding to the
desiderata outlined above. To evaluate each measure, we selected four
example property--category pairs that we believe are unambiguously
instances of the boundary conditions described above (these items are
described above with the desiderata).

Figure \ref{fig:cv-bothquestions-barplots} (top) shows the results for
the twelve items of interest for both measurements. We see that for the
\enquote{false} features, both measures behave as desired (hypothsized
results shown by the dotted line): The cue validity of a feature that is
false is zero or near-zero. For \enquote{diagnostic} features, both
measures also behave reasonably: Learning that an entity has malaria
strongly implies that it is a mosquito. However, there is some evidence
that the free production measurement is more sensitive than the
direct-question measure. \enquote{Having a mane} is strongly diagnostic
for a \enquote{lion} but also for a \enquote{horse} (and so the overall
cue validity for lion is around 0.5). \enquote{Carrying Lyme disease} is
mostly diagnostic for a \enquote{tick} but also \enquote{deer} (and
thus, the cue validity for tick is not maximal). These subtle
differences among \enquote{diagnostic} features is picked up by the
free-production measure but not by the direct-question measure.

The measures deviate most strongly, however, in their characterization
of the undiagnostic features. Learning that an entity is female should
not strongly imply that it is a robin, which is accurately reflected in
the free production measure but not in the direct question measure. A
similar phenomenon can be observed in direct question measure for the
other undiagnostic features. Figure \ref{fig:cv-bothquestions-barplots}
(bottom left) shows the raw empirical distributions of responses for the
direct question measure. We observe suggestive evidence that
participants respond to this question for unidagnostic features in one
of two ways: (i) reporting near-0 likelihood (accurate response) or (ii)
reported near-0.5 likelihood. This latter response option may be a
pragmatic effect of asking the direct question and/or participants
\enquote{opting out} of a response. For example, in response to the
question \enquote{There is a thing that is female. What are the odds
that it is a robin?}, a reasonable human response may be \enquote{I
don't know}. Participants may cope with the awkwardness of the question
by placing the slider bar in the middle of the scale.

\begin{figure}[htbp]
\centering
\includegraphics{figs/cv-bothquestions-barplots-1.pdf}
\caption{\label{fig:cv-bothquestions-barplots}Top: Empirically measured cue
validity for two different tasks. Items are grouped by whether the
property is never present in the category (false), the property is
always present in the category and every other category (undiagnostic),
or present in the category and absent from most other categories
(diagnostic). Dotted lines denote theoretical cue validity representing
the desiderata (see text). Error bars denote bootstrapped 95\%
confidence intervals. Bottom left: Raw empirical distributions for
direct question task. Bottom right: Correspondence between measured cue
validity and prevalence prior derived cue validity.}
\end{figure}

\subsection{Comparison with prevalence prior derived cue
validity}\label{comparison-with-prevalence-prior-derived-cue-validity}

To further understand these measures of cue validity, we compare them to
cue validity derived from our prevalence prior elicitation task (Expt.
1a). Expt. 1a is not perfectly designed for this comparison, as we
supplied participants with half of the animal categories that they rated
(the other half was freely generated by participants); including these
supplied categories was important to measure referent-prevalence of
interest (e.g., the percentage of mosquitos that carry malaria).
Including them in this analysis, however, potentially distorts the prior
probability of categories \(P(k)\).

In this analysis, we treat each category entry from Expt. 1a
(participant free production or experimentally supplied category like
mosquitos) as contributing to the prevalence prior. This will result in
the prevalence prior favoring kinds that are easy to produce (like dogs
and cats, which is plausibly a good approximation for \(P(k)\)) as well
as favoring the experimentally supplied kinds (like mosquitos and
robins).

We compute cue validity from the prevalence prior using Bayes' rule.
Figure \ref{fig:cv-bothquestions-barplots} (bottom right) shows the two
measurements of cue validity as they relate to the prevalence prior
derived cue validity. The prevalence prior derived cue validity is
highly associated with both measurements: \(r_{direct}^2(30) = 0.781\);
\(MSE_{direct} = 0.0482\) and \(r_{free}^2(30) = 0.728\);
\(MSE_{free} = 0.0265\). Of primary interest is how the measurements
behave for desiderata items. We see that the prevalence prior derived
cue validity converges with the free production measurement for the
desiderata items (\(r_{free}^2(12) = 0.957\); \(MSE_{free} = 0.00778\)),
whereas the direct question measurement overestimates the cue validity
of undiagnositic features (\(r_{direct}^2(12) = 0.776\);
\(MSE_{direct} = 0.0567\)).

The points of largest deviation for the free-production measurement from
the prevalence prior derived measurement occur where the prevalence
prior derived measure rates the cue validity as relatively high when the
free-production measure gives the item low cue validity (two black
points in Fig. \ref{fig:cv-bothquestions-barplots} (right scatterplot)
high X-value, low Y-value). These two items are: (\enquote{is red},
\enquote{cardinal}) and (\enquote{is white}, \enquote{swan}). These
items should have low relatively cue validity and are overestimated by
the prevalence prior because of the prior on categoryies \(P(k)\) (i.e.,
because they were supplied to every participant and thus get a higher
weighted in the prior for deriving cue validity). In comparison, the
direct question measurement consistently overestimates cue validity
relative to the prevalence prior.

\subsection{Summary}\label{summary}

\emph{Cue validity} is a commonly used measurement for understanding
generic truth conditions. Because we observe different measurements
being used in the literature, we articulated three \emph{a priori}
desiderata to validate a measure of cue validity. We found that the
\enquote{free production} measurement (i.e., having participants
generate categories given a feature), and not the direct question
measurement (i.e., asking participants a likelihood judgment of the
category given the feature), satisfied all three boundary conditions. In
addition, cue validity derived from our prevalence prior measurement
(Expt. 1a) also satisfied these boundary conditions. We conclude that
researchers interested in generic truth conditions should use a free
production paradigm for measuring cue validity.

\newpage

\section{Appendix C: Bayesian Data
Analysis}\label{appendix-c-bayesian-data-analysis}

In our three case studies, we compare an information-theoretic,
computational model of endorsement to human endorsements of
generalizations in language. The model has a single free parameter: the
optimality parameter in Eq. \ref{eq:S1}. Other model parameters
(governing the prevalence prior \(P(h)\) and the referent-prevalence
\(h'\)) are estimated using additional behavioral data (e.g., prior
elicitation tasks). Througout the paper, we model all sources of data
(prevalence prior data, endorsement data) using a single joint-inference
Bayesian data analytic model. In this appendix, we describe this
procedure in more detail for each case study.

\subsection{Modeling prevalence
priors}\label{modeling-prevalence-priors}

In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence
prior by asking about individual about the prevalence of features for
individual categories. We performed an analagous elicitation in Case
Study 3: Causal Language (Expt. 3a). We describe the analysis using
generics as our running example, but a parallel analysis was done for
causals.

Participants' responses can be thought of as \emph{samples} from the
prevalence prior distribution. Formally, we assume the prior data
(analyzed independently for each property) was generated from one of two
distributions: a distribution corresponding to those kinds with a stable
causal mechanism that \emph{could} give rise to the property
(\(\mathcal{D}_{stable}\)) and a \enquote{transient cause} distribution
corresponding to those kinds without a stable mechanism
(\(\mathcal{D}_{transient}\)). The \enquote{transient} distribution
intuitively corresponds to accidental causes of the feature (e.g., a
lion, who through some genetic mutation, reproduces by laying eggs). We
model this distribution as a Beta distribuition that heavily favors
probabilities near 0:
\(\text{Beta}(\gamma = 0.01, \delta = 100)\).\footnote{Note that we use
  the noncanonical mean \(\gamma\) and concentration \(\xi\) (or,
  inverse-variance) parameterization of the Beta distribution rather
  than the canonical shape (or pseudocount) parameterization for ease of
  posterior inference. The shape parameterization can be recovered
  using: \(\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi\).}
The \enquote{stable} distribution is modeled as a Beta distribution with
unknown parameters \(\text{Beta}(\gamma, \xi)\).\footnote{Because the
  Beta distribution is not defined at the points 0 and 1, we add
  \(\epsilon\) to the 0 responses and round 1 to 0.99. Similar results
  can be obtained by rounding 0 to 0.01. Alternatively, the
  \enquote{transient} distribution could be defined as a Delta
  distribution at 0, and 0 responses could remain in their raw form.
  Adjusting 1 to \(1- \epsilon\) leads to improper inferences for this
  model, as \(1 - \epsilon\) is only likely under a highly right-skewed
  distribution; treating 1 as \(1- \epsilon\) disproportionately
  influences the shape of \(\mathcal{D}_{stable}\) relative to other
  responses. This problem does not appear for 0 being adjusted to
  \(\epsilon\) because the \enquote{transient} distribution already
  expects such low values.} Finally, we assume that these two components
combine with mixture weighting \(\phi\) such that the data we observe is
\[P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) \].
We put the following priors over the latent parameters of the model:

\begin{eqnarray*}
\phi_i & \sim & \text{Uniform}(0, 1) \\
\gamma_i & \sim & \text{Uniform}(0, 1) \\
\xi_i & \sim & \text{Uniform}(0, 100)
\end{eqnarray*}

where \(i\) ranges over the different properties (e.g., \emph{lays
eggs}, \emph{carries malaria}).

To learn about the credible values of the parameters, we ran separate
MCMC chains for each item, collecting 75,000 samples, removing the first
25,000 for burn-in. To see how well the mixture model fits the
prevalence prior data, we use the inferred parameters to generate new
data. The data generated from the model's posterior is called the
\emph{posterior predictive distribution} and is an important step in
model criticism. If the model is a good representation of the data, the
posterior predictive data will align with the observed experimental
data. We construct a posterior predictive distribution by
\enquote{forward sampling} the model.\footnote{This can be described by
  the following algorithm: First, flip a coin weighted by \(\phi\). If
  it comes up heads, we then sample from the \enquote{stable} component:
  \(\text{Beta}(\gamma, \xi)\). If it comes up tails, we sample from the
  \enquote{transient} component: \(\text{Beta}(0.01, 100)\). We do this
  many times using the posterior distibution to generate a distribution
  over predicted prevalence ratings.}

In Case Study 2 (Expt. 2a), we asked participants about parameters of
this mixture model (by having participants answer questions abouut
\emph{different kinds of people}) rather than having participants give
samples (e.g., by listing their friends and rating how often their
friends did certain actions). In pilot testing, we found these different
methodologies to give similar results. We made the decision to ask more
abstract information about the events to get at participants' abstract
beliefs about the property rather than their knowledge of true
frequencies. As well, by querying about abstract characters, we were
able to include items that participants might not otherwise feel
comfortable reporting off (e.g., how often their friends smoke
marijuana). The questions used to elicit information about the
parameters are described in the main text.

\subsection{Modeling
referent-prevalence}\label{modeling-referent-prevalence}

In Case Study 1, we used participants prevalence ratings for the
category-of-interest in our generic sentences as the referent-prevalence
that is used in the endorsement model (Eq. \ref{eq:S1}). For a given
generic sentence (e.g., \enquote{Robins lay eggs}), we took the
prevalence ratings for the referent-category (e.g., the percentage of
robins that lay eggs) from the prior elicitation task (Expt. 1b) and
assumed those were generated from a single Beta distribution. We used
the same priors as we did for the \emph{stable cause} component of the
prevalence prior:

\begin{eqnarray*}
\gamma_i & \sim & \text{Uniform}(0, 1) \\
\xi_i & \sim & \text{Uniform}(0, 100)
\end{eqnarray*}

We took samples from the posterior predictive of this Beta distribution
(i.e., reconstructed prevalence ratings) as the
\emph{referent-prevalence} used in the model.

In Expt. 2b (Habitual endorsement), we used the frequency given to
participants in the experimental prompt (e.g., 3 times in the past week)
as the referent-prevalence. In Expt. 2c (\enquote{What is prevalence?}),
we compared two endorsement models that differed in their representation
of referent-prevalence. For one model (past frequency model), it was the
frequency given to participants in the experimental prompt (same as in
Expt. 2b); for the other model (predictive frequency model), we used the
mean elicited frequency from the \emph{predictive frequency} condition
(see main text). In Case Study 3 (Causal endorsement), we used the
proportion of successful causal events given to participants in the
experimental prompt (e.g., 70 out of 100 uses of Herb C made animals
sleepy).

\subsection{Jointly modeling referent-prevalence, prevalence priors, and
generic
endorsements}\label{jointly-modeling-referent-prevalence-prevalence-priors-and-generic-endorsements}

To fit the generic endorsement models, we incorporate them into the
Bayesian data analytic model of the prevalence prior data (described
above) to create a single, joint-inference model where the optimality
parameter \(\lambda_1\) (Eq. \ref{eq:S1}) is inferred jointly with all
the other latent parameters of the full model (the referent-prevalence
\(h'_{k, f}\) for each category \(k\) and property \(f\) and the
parameters of the prevalence priors \(P_f(h)\) for each property \(f\))
using data from Expt. 1a \& b (Figure \ref{fig:genericsModelDiagram}).
For the parameters of the prevalence prior distributions, we use the
same priors described in Expt. 1b; for the speaker optimality parameter,
we use a prior with a range consistent with previous literature using
the same model class: \(\lambda_1 \sim \text{Uniform}(0,5)\). We learn
about the \emph{a posteriori} credible values of the joint inference
models by collecting samples from 3 MCMC chains of 100,000 iterations
removing the first 50,000 iterations for burn-in, using an
incrementalized version of the Metropolis-Hastings algorithm (Ritchie et
al., 2016).

\begin{figure}[htbp]
\centering
\includegraphics{figs/generics_bayesnetmodel.pdf}
\caption{\label{fig:genericsModelDiagram}Graphical model corresponding to
the fully Bayesian data analysis of the RSA model. The prevalence prior
data \(d^{pr}_{f}\) is assumed to be generated from the mixture model
validated in Expt. 1a. The referent-category prevalence \(d^{pr}_{k,f}\)
is generated from a latent prevalence \(p_{fk}\). The fixed-threshold
(control model) or uncertain-threshold model take the prevalence priors
\(P_f(h)\), the referent-prevalence \(h\), and a single speaker
optimality parameter \(\lambda\) as input. This overall structured is
repeated (except \(\lambda\)) for each of the unique properties \(f\)
and categories \(k\) that correspond to the generic sentences in our
stimulus set. Note that S corresponds to a probabilistic \emph{function}
and not a \emph{random variable} that is standard in graphical model
notation; S cannot be represented by a graphical model because it has
recursion.}
\end{figure}

In addition to examining the posterior predictive distribution on
endorsement judgments (presented in main text), we examined the marginal
posteriors on parameters of the prevalence priors and
referent-prevalence. These marginal distributions are important to
examine to confirm that they have not changed significantly from the
parameters inferred from their private data sources in isolation. For
example, when modeling the referent-prevalence data in isolation, the
model infers that roughly 50\% of robins lay eggs, as that is what
participants tend to say in the prevalence elicitation task.\footnote{Some
  participants do report that 100\% of robins lay eggs so the average
  prevalence rating is closer to 65\%..}. The question for this joint
inference model is whether or not it still believes that roughly 50\% of
robins lay eggs. We found that the referent-prevalences and prevalence
priors inferred under the joint model were almost indistinguishable from
those inferred using only their data, suggesting that the modeling all
three data sources together does not come at the cost of modeling any
one of them accurately.

\end{document}

### 2017-12-27 paper/case3-causals.Rmd
tweak wording

@@
 We take a different approaching, examining *type causation* by the language used to describe it (e.g., "A causes B").
-We assume that such language conveys a generalization about *token* or *actual causation* (e.g., "A caused B, in this instance") and that our theory of the language of generalizations extends in a natural way to describe *causal language*.
+We explore the idea that such language conveys a generalization about *token* or *actual causation* (e.g., "A caused B, in this instance") and that our theory of the language of generalizations extends in a natural way to describe *causal language*.
 Ascribing causation to an individual event (*token or actual causation*) is itself a complex, inferential process [e.g., depending on counterfactual reasoning; @Gerstenberg2015how], which we do not try to model here.
 
-In this paper, we posit thatprevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
+In this paper, we posit that prevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
 In this last set of experiments, we explicitly test the relationship between the prevalence priors and endorsements of generalizations about causes.

### 2018-01-17 paper/appendix-fullModelPosteriors.Rmd
remove data table from packrat and associated files

@@
 library(langcog)
-library(data.table)
 library(coda)
@@
 
+# m.samp <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
+#                      10000, "_burn", 5000, "_lag", 20, "_chain", 4, ".csv", sep = ""))
+# 
+# m.samp <- m.samp %>%
+#   filter(param != "score")
+# 
+# m.samp <- m.samp %>% mutate(chain = 0)
 ```
@@
   group_by(Category, Property) %>%
-  multi_boot_standard(column = "prevalence")
+  multi_boot_standard(col = "prevalence")
 ```
@@
     filter(type == "targetPrevalence") %>%
+    #filter(type == "withinKind") %>%
     mutate(parameter = paste(param, property, category, sep = "_")) %>%
@@
 ```{r gen-prevprior-forward}
+
+m.samp <- m.samp %>% filter(!(param == "prevalencePrior")) %>%
+  mutate(param = factor(param, levels = c("isPresent", "prevalenceGivenPresent"),
+                        labels = c("")))
 #Forward sample from posterior on parameters

### 2018-01-17 paper/case3-causals.Rmd
remove data table from packrat and associated files

@@
 for (i in seq(1, n_chains)){
-  mi <- fread(paste(project.path,  "models/causals/results/", 
+  mi <- read_csv(paste(project.path,  "models/causals/results/", 
                     model_prefix, "smntcs_causal-",

### 2018-01-17 paper/comgen-paper.Rmd
try packrat src files

@@
 library(papaja)
-library(formatR)
+#library(formatR)
 library(rwebppl)
@@
 library(langcog)
-# library(dplyr)
-library(data.table)
 library(coda)

### 2018-01-18 paper/comgen-paper.Rmd
update packrat lock

@@
 library(papaja)
-#library(formatR)
+library(formatR)
 library(rwebppl)

### 2018-02-05 analysis/model-simulations.Rmd
simply fig1, modularize code to analysis script for model simulation, cache model sims

--- 2018-01-18 paper/comgen-paper.Rmd
@@
 ---
-title             : "The language of generalization: Probability, vagueness, and interaction"
-shorttitle        : "The language of generalization"
-
-author: 
-  - name          : "Michael Henry Tessler"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
-  - name          : "Noah D. Goodman"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-
-header-includes:
-  - \usepackage{tabularx}
-  - \usepackage{multicol}
-  - \usepackage{wrapfig}
-  - \usepackage{caption}
-  - \usepackage{booktabs}
-  - \usepackage{amsmath}
-  - \usepackage{graphicx}
-  - \usepackage{subcaption}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-
-author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
-
-abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which statements are true or which are false.
-    Using an information-theoretic probabilistic model, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains the wide variance in human endorsements of language conveying generalization, while simpler models fall short.
-    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results demonstrate that the context-sensitivity of such language emerges from the interaction of an underspecified meaning with diverse beliefs about properties.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
-wordcount         : "20000"
-
-bibliography      : ["generics.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-
-lang              : "english"
-class             : "man"
-output            : papaja::apa6_pdf
+title: "Lang-gen model simulations"
+output: html_notebook
 ---
-
-\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\definecolor{Red}{RGB}{255,0,0}
-\definecolor{Green}{RGB}{10,200,100}
-\definecolor{Blue}{RGB}{10,100,200}
-
-\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
-\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
-\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
-
-```{r global_options, include=FALSE}
-rm(list=ls())
-knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
-```
 
@@
 
-<!-- 
-possible titles:
-- Communicating generalizations
-- The language of generalization
-- The language of generalization: Probability, vagueness, and interaction
--->
-
-# Introduction
-
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Flexibly communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
-
-<!-- Generalizations can be acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. \ndg{cite older stuff. eg hume} -->
-<!-- Cooperative teachers can facilitate inductive learning by supplying helpful observations to the learner [@Csibra2009; @Tomasello1999; @Butler2012]. -->
-<!-- At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language. -->
-<!-- Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
--->
-<!-- Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization. -->
-<!-- \ndg{this par doesn't really do much} -->
-
-The language of generalization is often studied via *generic language* (or, *generics*): simple statements predicating properties of categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-<!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
--->
-Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-Every language, it is believed, can express generalization [@Behrens2005; @Carlson1995] and is central to the growth of conceptual knowledge [@Gelman2004].
-Considering generalization as a singular phenomenon in language, thus, promises to provide understanding of a wide variety of linguistic expressions with powerful implications.
-
-<!-- Generic statements ascribing properties to categories are just one kind of generalization found in language.  -->
-<!-- Individual entities can also be talked about in generalization, using so-called  -->
-<!-- <!-- Recent evidence suggests talking about the other in generalization (using so-called *generic You*) can help make meaning from difficult situations   [e.g., "You never know what will happen on a blind date."; @Orvell2017].
--->
-<!-- Communicating about causality can also take the form of communicating a generalization about a causal event  -->
-<!-- What these statements have in common is that they convey generalizations, or exhibit *genericity* [@Carlson1977; @Carlson1995]. -->
-
-Despite their ubiquity and relative simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions.
-The major challenge in formalization is determining *what makes the statements true or false*.
-When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
-The generalization could signal something weaker like "Most dogs bark".
-However, most mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
-<!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to mean "some" is too permissive: some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
-Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
-
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only parameter in the meaning of generalizations.
-Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-"Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
-It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
-One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature. 
-Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature.
-*Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true
-
-Yet, generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships can result in true generics.
-<!-- Arbitrary relationships are also expressed with generics:  -->
-"Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false.
-Ravens and toasters have no priviledged relationship to each other, but the statement "Ravens are bigger than toasters" is still a true generalization.
-Conceptual accounts must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
-But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
-In this paper, we propose such a semantic core for the language of generalization.
-To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would use when understanding such language.
-We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
-The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-
-<!-- The test of a unified semantic core is its ability to explain what makes the statements true or false. -->
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
--->
-
-<!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
--->
-<!-- In its simplest form, context takes the shape of interlocutors' shared beliefs about the relevant properties or categories under discussion [cf., @Grice1975; @Clark1996; @Levinson2000]. -->
-<!-- We then ask what a rational speaker---who can only either endorse the generalization or stay silent---would say in different contexts; this is our formal model of endorsement. -->
-<!-- We show how the decision to endorse depends in systematic ways on the shared prior knowledge of the interlocutors. \mht{"interlocutors" may be confusing here...} -->
-<!-- We test this theory in three distinct case studies---generalizations about categories, events, and causes---by both measuring and manipulating prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
--->
-
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
-The paper is organized as follows. 
-In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions depend upon the background knowledge and the probability communicated, which we demonstrate via simulation.
-Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and the probability communicated, measuring their effects on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alterantive models fall short.
-This work opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
-
-<!-- (cumulative $r^2(N) = 0.XX$). -->
-<!-- In the final section of the paper, we discuss the generality of our approach and pave a path to unifying the extant psychological, linguistic, and philosophical literatures on generalization in language.
--->
-<!-- We also show how our endorsement model is a special case of a speaker model in a rational framework of communication.  -->
-
-# Computational Framework
-
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ (formally, be in the set of things that have $f$) given that it is in $k$, which we will refer to as the **prevalence**.
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the probability $p_{fk}$.
-
-How does one acquire such an inductive belief?
-Observing instances of the category $k$ and noting how many of them have $f$ can support prediction to new instances when integrated with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
-For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
-Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
-This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$
-
-Learning from observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), one would much rather learn from others.
-Fortunately, language has simple ways of encoding generalizations.
-
-<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
-<!-- It is conditional on $h$ because the probability of various direct observations depends upon the prevalence that the observer assumes.  -->
-<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
--->
-<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
-<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).
--->
-<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->
-
-<!-- As a concrete example, consider a learner investigating the feature \textsc{barks} ($f$) for the category \textsc{dog} ($k$). -->
-<!-- $h$ describes the learner's subjective probability that the next dog she encounters will bark^[At the moment, we assume the feature \textsc{barks} is an all-or-none Boolean property.
-Later, we will see how the presence of this feature itself can be thought of as a generalization over events of barking.], or more abstractly, her belief about the barking capacity of dogs.
--->
-<!-- That is, $h = P(x \text{ barks} \mid x \text{ is a dog})$. -->
-<!-- The learner does not know $h$, but has some idea about what $h$ could be; this is represented by $P(h)$, the learner's prior beliefs about how likely it is that $x$ will bark given that $x$ is a dog.
--->
-
-<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
-<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
-<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.
--->
-<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the prevalence of barking among dogs.
--->
-<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
-<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->
-
-<!-- $P(h \mid d)$ is then the strength of the learner's belief in the next dog she encounters barking. -->
-<!-- This simple idea of integrating observational evidence with prior knowledge is surprisingly powerful in explaining a multitude of diverse phenomena, from perception to word learning to inductive reasoning [e.g., @Tenenbaum2006; @Tenenbaum2011].
--->
-<!-- \ndg{what is this par doing for us? delete?} -->
-<!-- Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place. -->
-<!-- For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
--->
-<!-- This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
--->
-<!-- Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009]. -->
-<!-- Yet generalizations from observational evidence is limited in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
-<!-- Relying upon observations would be particularly problematic, for example, to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*).
--->
-<!-- How do we acquire these generalizations? -->
-<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.
--->
-
-## Generalization from language
-
-The language of generalization manifests when a property is predicated of a category: "Ks F" (e.g., "Dogs bark", "Staring at the sun makes you go blind"). 
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
-One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for a generalization about category K with property F would then apply to the *prevalence* $p_{fk}$:
-$\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$
-
-Various attempts of this kind have been made before [e.g., @Cohen1999].
-We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
-$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief.
-
-<!-- We emphasize that this account is based on a probability $h$. -->
-<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the prevalence $h$.^[ -->
-<!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
-<!-- ] -->
-<!-- Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself.  -->
-<!-- Probability is a measure of belief.  -->
-
-### Literal interpretation model
-
-Quantifier statements can be described using a similar threshold semantics: $\denote{some \text{ } K \text{ } F}(p_{fk}) = \{p_{fk} > 0\}; \denote{all \text{ } K \text{ } F} = \{p_{fk} = 1\}$.
-So what threshold $\theta$? should be used for the generalizations? 
-Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we hypothesize that $\theta$ is in part determined by contextual, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
-
-We formalize this underspecified semantics in a probabilistic model, where the underspecifed threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013].
-After making explicit the relevant background knowledge about the property $P(p_f)$, the model becomes:
-
-\begin{eqnarray}
-Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{f}, \theta)} \cdot P(p_{f}) \cdot P(\theta)} \label{eq:L0}
-\end{eqnarray}
-
-Equation \ref{eq:L0} ($Lit$) is a literal interpretation model, that updates its beliefs about the prevalence of a feature in the category described $p_{fk}$ according to the truth-functional meaning of the utterance $u_{KF}$.
-Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
-
-\begin{eqnarray}
-\delta_{\denote{u_{KF}}(p_{fk}, \theta)} &\propto  & \begin{cases}
-1 & \text{if } p_{fk} > \theta \\
-0 & \text{otherwise}
-\end{cases}\label{eq:delta}
-\end{eqnarray}
-
-### Endorsement model
-
-Given the minimal model of literal interpretation described above, how do we decide when a statement conveying a generalization is true or not?
-We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of production? 
-We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0})^[
-  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
-  Rather, the endorser may have a distribution over $p_{f}$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
-  In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
-  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}$
-  For the empirical case studies described below, these two versions of the model make almost identical predictions.
-].
-
-\begin{equation} 
-S(u \mid p_{fk}) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)  \diff \theta } )}
-\label{eq:S1}
-\end{equation}
-
-The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$): $Lit(p_{fk}, \theta \mid u)$.
-$S$ is not interested in communicating $\theta$ (in fact, it does not know $\theta$), and so integrates over the values of $\theta$.
-We assume the decision to endorse is an approximately rational one, with degree of rationality given by $\lambda$.
-The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
-We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [cf., @Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$^[
-  This "null" alternative  to the generalization ("Ks F") can be realized in at least two other ways: the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not F").
-  All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity.
-]
-
-Our endorsement model (Eq.
-\ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $p_{fk}$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{KF} \mid p_{fk})$.
-The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
-\ref{eq:S1}).
-This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.
-
-### Prevalence priors and referent-prevalence
-
-Our model makes context-sensitive predictions about endorsing generalizations based on two model components: The prevalence priors $P(p_f)$ in Eq.
-\ref{eq:L0} and the referent-prevalence $p_{fk}$ in Eqs.
-\ref{eq:S1} and \ref{eq:delta}.
-Referent-prevalence is the probability that an individual $x$ of the referent-category (e.g., "Dogs") will have the feature being predicated of the category (e.g., "...barks").
-We will return and refine this definition in Case Study 2, when considering generalizations about events.
-For now, the referent-prevalence is simply a probability that determines the truth-conditional semantics. 
-Our hypothesis does not provide a mapping from the referent-prevalence directly to endorsement judgments, however, because $\theta$ is underspecified.
-
-The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating prior beliefs about the feature in question---the *prevalence prior* $P(p_f)$---with the truth-functional semantics.
-Again, $P(\theta)$ is set to be a uniform distribution across all contexts, and thus, the generalization could in principle be felicitious with potentially any referent-prevalence. 
-However, interpretation model's *a priori* beliefs $P(p_f)$ must be considered before the endorsement model can say whether or not it would endorse the generalization.
-
-Beliefs about properties result from internal conceptual models of the world. 
-These internal models have domain-specific features but should all give to the domain-general currency of inductive reasoning: probability.
-One way of constructing prior distributions over prevalence, without appealing directly to domain-specific conceptual knowledge, is by considering the prevalence of the feature among different categories.
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because what one would expect for a randomly-sampled category is that it has 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
-Conceptual differences can manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* implicitly encodes knowledge of other categories and has been shown to be  highly correlated with endorsing *generic sentences*, or generalizations about categories [@Khemlani2012].
-Cue validity is defined for a particular (category, property) pair (as is referent-prevalence), and relates to referent-prevalence by Bayes' Rule:
-\begin{equation}
-P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')} \label{eq:cuevalidity}
-\end{equation}
-Since *cue validity* implicitly encodes knowledge of other categories (by summing over $k'$) and the prevalence prior explicitly encodes knowledge of other categories, how are these two constructs related?
-In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
-Thus, $P(p_{fk}) = P(k_{f})$.
-The denominator of Eq.
-\ref{eq:cuevalidity} (which encodes knowledge of other categories), then, is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$.
-For a more thorough derivation of this relationship, see Appendix A.
-The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potential shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
-This is particularly problematic for prevalence distributions that encode conceptual knowledge via multimodal distributions (e.g., Fig.
-\@ref(fig:simulations)A; bottom row); the mean of a multimodal distribution is not a good representation of that distribution.
-We return to this point empirically in Case Study 1.
-
-<!-- These distributions can be thought of as distributions over categories, displaying only the prevalence for the property in question. -->
-
-<!-- F(left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property. -->
-<!-- For example,   -->
-
-### Model simulations
-
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $p_{fk}$ in Eq.
-\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(p_f)$ (Eq.
-\ref{eq:L0}).
-We simulate how these two factors change both literal interpretation and endorsement using schematic parameter values based on intuition from classic examples in the literature on generic language.
-We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
+# RSA model
 
@@
 
-```{r rsaInterpretationModels, eval = T, cache = T}
+```{r rsaInterpretationModels}
 no.utterance.model <- '
@@
 
-```{r cache = F}
-fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
-    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
-    theme_few() +
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    ylab("Normalized probability density") +
-    xlab("")+
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    facet_grid(PriorShape~., scales = 'free')+
-    theme(strip.text.y = element_blank())
-```
-
-```{r cache = F}
-fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
-    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
-    theme_few() +
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence of the feature in a category") +
-    ylab("") +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    facet_grid(PriorShape~threshold, scales = 'free')+
-    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
-```
-
-```{r cache = F}
-fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
-                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
-    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
-    theme_few() +
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("") +
-    ylab("") +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    facet_grid(PriorShape~., scales = 'free')+
-    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
-```
-
-```{r fig.width = 9, eval = F}
-p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
-p2 <- fig.sims.fixed.thresholds +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
-p3 <- fig.sims.uncertain.threshold+
-  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
-    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-
-prow <- plot_grid( p1 + theme(legend.position="none"),
-           p2 + theme(legend.position="none"),
-           p3 + theme(legend.position="none"),
-           align = 'vh',
-           labels = c("A", "B", "C"),
-           hjust = -1,
-           nrow = 1,
-           #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 3, 1.2)
-           )
-#prow
-#legend <- get_legend(p1)
-
-#plot_grid( prow, legend, rel_widths = c(3, .3))
-```
-
-```{r simluationEndorsementModel, eval = T, cache = T}
+```{r simluationEndorsementModelRuns}
 s1.model <- '
@@
 
-```
-
-```{r}
 s1.simulations.relabeled <- s1.simulations %>%
@@
 
-# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
-#   #ylab("Human endorsement probability")+
-#   #xlab("Frequency of target")+
-#   geom_label_repel(data = s1.simulations.relabeled, 
+```
+
+```{r}
+save(sims.priors, sims.uncertain.thresholds, sims.fixed.thresholds,s1.simulations.relabeled, file = "../paper/cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData")
+```
+
+# Misc extra
+
+old scatter plot version of endorsements
+```{r}
+#s1.simulations.scatter <-
+
+  ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
+  #geom_jitter(width = 0.1, shape = 21, size = 5)+
+  #ylab("Human endorsement probability")+
+  #xlab("Frequency of target")+
+  geom_point()+
+  #geom_label_repel(data = s1.simulations.relabeled,
    #                aes( label = example, fill = example),
   #                     color = 'white',
-#     box.padding = unit(0.0, "lines"),
-#     #point.padding = unit(1e-06, "lines"),
-#     segment.color = 'grey37')+
-#   scale_fill_solarized()+
-#   scale_x_continuous(limits = c(0, 1), 
-#                      breaks = c(0, 0.5, 1))+
-#   scale_y_continuous(limits = c(-0.01, 1.01), 
-#                      breaks = c(0, 1),
-#                      labels = c("False", "True"))+
-#   coord_fixed(ratio = 1)+
-#   guides(fill = F)+
-#   ylab("Endorsement model prediction")+
-#   xlab("Hypothesized prevalence")
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
-  geom_col(color = 'black')+
-  # geom_label_repel(data = s1.simulations.relabeled, 
-  #                  aes( label = example, fill = example),
-  #                      color = 'white',
-  #   box.padding = unit(0.0, "lines"),
-  #   #point.padding = unit(1e-06, "lines"),
-  #   segment.color = 'grey37')+
+    #box.padding = unit(0.0, "lines"),
+    #point.padding = unit(1e-06, "lines"),
+    #segment.color = 'grey37')+
   scale_fill_solarized()+
   scale_x_continuous(limits = c(0, 1),
-                     breaks = c(0, 1))+
+                     breaks = c(0, 0.5, 1))+
   scale_y_continuous(limits = c(-0.01, 1.01),
@@
                      labels = c("False", "True"))+
-  #coord_fixed(ratio = 1)+
-  coord_flip()+
-  facet_grid(example~.)+
+  coord_fixed(ratio = 1)+
   guides(fill = F)+
-  ylab("")+xlab("Referent prevalence")+
-  theme(strip.text.y = element_text(angle = 0, hjust = 0)
-        #axis.title.x = element_text(hjust = 0)
-        #axis.title.y = element_text(vjust = 0)
-        )
-  #ylab("Endorsement model prediction")+
-  #xlab("Hypothesized prevalence")
-```
+  ylab("Endorsement model prediction")+
+  xlab("Hypothesized prevalence")
 
-```{r simulations, fig.cap = "Computational model behavior.
-A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations.
-C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
-D: Endorsement model predictions, assuming a particular referent-prevalence.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
-p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
-p2 <- fig.sims.fixed.thresholds +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
-p3 <- fig.sims.uncertain.threshold+
-  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
-    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
-
-prow <- plot_grid( 
-  add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
-  add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
-  add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
-  add_sub(p4, "Endorsement"),
-           align = 'vh',
-           labels = c("A", "B", "C", "D"),
-           hjust = -1,
-           nrow = 1,
-           #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 2.9, 1.15, 1.7)
-           )
-prow
 ```
@@
 
-The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$ (Figure\ \@ref(fig:simulations)B).
-Low thresholds (e.g., $\theta = 0.1$) rule out very few possibilities (only $p_{fk} \leq 0.1$), and thus are quite likely given that its consistent with much of the prevalence prior.
-The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be similar to staying silent (a posterior not very different from the prior).
-Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
-
-The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds.
-The prevalence-based interpretations of generalizations of novel categories are shown in Figure\ \@ref(fig:simulations)C.
-These interpretations depend heavily on the prevalence priors (different rows).
-Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (top row; pink).
-"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (4th row; green).
-The literal interpreter can also derive very weak interpretation, as shwon in the  \textsc{carries malaria} distribution (bottom row, purple).
-
-The endorsement model (Eq. \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs).
-Predictions for a few classic examples from the generics literature are shown in (Figure\ \@ref(fig:simulations)D).
-In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
-Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
-To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) A vs.
-C; blue distributions).
-The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
-This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
-
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the prevalence $p_{fk}$ communicated. 
-We chose schematic values for each of these, and saw that the endorsement model recapitulates standard intuitions about the truth or falsity of classic examples from the generics literature.
-In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measurning and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
-
-<!-- The literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") is given by Eq. \ref{eq:L0} and shown in  -->
-
-<!-- The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}.  -->
-<!-- For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
--->
-<!-- This would correspond to a rather strong interpretation (i.e., "Almost all feps bark"). -->
-<!-- This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green).  -->
-<!-- Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
--->
-<!-- The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple). -->
-<!-- Again, the literal interpretation depends upon the background knowledge in a deep way. -->
-
-<!-- The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right). -->
-<!-- Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
-\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
--->
-<!-- We see the model correctly  -->
-
-<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
-
-<!-- that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics. -->
-<!-- For these simulations, we had specify both the prevalence priors $P(h)$ and the referent prevalence $h'$.. -->
-<!-- In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes. -->
-
-<!-- These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row). -->
-<!-- The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior. -->
-<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[ -->
-<!-- The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities. -->
-<!-- If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold. -->
-<!-- If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower. -->
-<!-- As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it. -->
-<!-- When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model). -->
-<!-- The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*. -->
-<!-- ] -->
-
-<!-- Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements. -->
-<!-- The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$. -->
-<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
--->
-<!-- The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[ -->
-<!-- We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero.  -->
-<!-- The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
--->
-<!-- ] -->
-<!-- The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category. -->
-
-<!-- How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"? -->
-<!-- In each case, we must consider the prevalence prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
-<!-- For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
--->
-<!-- For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs. -->
-<!-- This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3). -->
-<!-- For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
--->
-<!-- The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case.
--->
-<!-- In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
--->
-<!-- "Robins lay eggs", however, has a lot of informational content. -->
-
-<!-- Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria". -->
-<!-- The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread. -->
-<!-- Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
--->
-<!-- Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria". -->
-
-```{r child = 'case1-generics.Rmd'}
+```{r fim.sims.fixd.thresholds, cache = F}
+fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
+    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
+    theme_few() +
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Prevalence") +
+    ylab("") +
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    facet_grid(PriorShape~threshold, scales = 'free')+
+    theme(strip.text.y = element_blank()) 
+          #axis.title.x = element_text(hjust = 1))
 ```
 
-```{r child = 'case2-habituals.Rmd'}
+```{r figs.sim.posterior, cache = F}
+fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
+                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
+                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
+                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
+    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
+    theme_few() +
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Prevalence") +
+    ylab("") +
+    scale_color_solarized()+
+    scale_fill_solarized()+
+    facet_grid(.~PriorShape, scales = 'free')+
+    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
 ```
 
-```{r child = 'case3-causals.Rmd'}
+```{r fig.sims.endorsement}
+s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example,
+                                                                label = example))+
+  geom_col(color = 'black')+
+   #geom_text(vjust="inward",hjust="inward")+
+  geom_label(data = s1.simulations.relabeled,
+                   aes( label = example),
+             vjust="inward",hjust="inward",
+             color = 'white')+
+  # geom_label_repel(data = s1.simulations.relabeled,
+  #                  aes( label = example),
+  #                      color = 'white',
+  #   box.padding = unit(0.0, "lines"),
+  #   #point.padding = unit(1e-06, "lines"),
+  #   segment.color = 'grey37')+
+  scale_fill_solarized()+
+  scale_x_continuous(limits = c(0, 1), 
+                     breaks = c(0, 1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), 
+                     breaks = c(0, 1),
+                     labels = c("False", "True"))+
+  #coord_fixed(ratio = 1)+
+  coord_flip()+
+  facet_grid(example~.)+
+  guides(fill = F)+
+  ylab("")+xlab("Referent prevalence")+
+  theme(#strip.text.y = element_text(angle = 0, hjust = 0)
+        strip.text.y = element_blank()
+        #axis.title.x = element_text(hjust = 0)
+        #axis.title.y = element_text(vjust = 0)
+        )
+  #ylab("Endorsement model prediction")+
+  #xlab("Hypothesized prevalence")
 ```
 
-# General Discussion
+```{r simulationsOld2, fig.cap = "Computational model behavior.
+A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations.
+C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
+D: Endorsement model predictions, assuming a particular referent-prevalence.
+Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, fig.asp = 0.6, out.width = "95%", cache=F, eval=F}
 
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
+# p1 <- fig.sims.priors +
+#   theme(plot.margin = unit(c(6,0,6,0), "pt")) #+ ggtitle("prevalence priors")
+# p2 <- fig.sims.fixed.thresholds +
+#   theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
+# p3 <- fig.sims.uncertain.threshold+
+#   theme(plot.margin = unit(c(6,6,6,0), "pt"))+ 
+#     theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
+# p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(6,0,6,6), "pt"))
+# 
+# sim.prevalence.prior.title <- ggdraw() + draw_label("Prevalence priors", fontface='bold')
+# sim.prevalence.partial.title <- ggdraw() + draw_label("Partial interpretations given fixed-thresholds", fontface='bold')
+# 
+# sim.prevalence.posterior.title <- ggdraw() + draw_label("Prevalence posterior (interpretation)", fontface='bold')
+# 
+# sim.endorsement.title <- ggdraw() + draw_label("Endorsement prediction", fontface='bold', hjust = 0.47)
 
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite different from one another: generalizations about categories, events, and causes.
-<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
-We have been able to formalize a unified, core meaning using the underlying scale of *prevalence*.
-We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
-Our framework naturally accounts for a number of classic examples from the semantics of *generic language* (Expt. 1).
-We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is causally related to their endorsement of statements of genericity (Expt. 3).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below
+# prow <- plot_grid( 
+#   plot_grid(sim.prevalence.prior.title, 
+#             p1 + theme(legend.position="none"), ncol=1, rel_heights=c(0.1, 1)),
+#   plot_grid(sim.prevalence.partial.title, 
+#             p2 + theme(legend.position="none"), ncol=1, rel_heights=c(0.1, 1)),
+#   plot_grid(sim.prevalence.posterior.title, 
+#             p3 + theme(legend.position="none"), ncol=1, rel_heights=c(0.1, 1)),
+#   plot_grid(sim.endorsement.title, 
+#             p4, ncol=1, rel_heights=c(0.1, 1)),
+#            align = 'vh',
+#            labels = c("A", "B", "C", "D"),
+#            hjust = -1,
+#            nrow = 1,
+#            #rel_widths = c(1.2, 3, 2)
+#            rel_widths = c(1.2, 2.9, 1.4, 1.4)
+#            )
 
-<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
-The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments.
-The formal Bayesian model provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (operationalized in terms of the prior).
-This formal separation is key improvement beyond previous accounts. 
-Previous accounts have either tried to account for context-sensitivity by baking it into the semantics [e.g., @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
-Our model formalizes both the semantics of generalizations and the structure of world knowledge; this separation allows us to articulate a route for precise quantitative inlfuence of conceptual structure on generic language [c.f., @Leslie2008].
-<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
--->
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
-<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->
+prow <- plot_grid( 
+  plot_grid(sim.prevalence.prior.title, 
+            p1 + theme(legend.position="none"), ncol=1, rel_heights=c(0.1, 1)),
+  plot_grid(sim.prevalence.posterior.title, 
+            p3 + theme(legend.position="none"), ncol=1, rel_heights=c(0.1, 1)),
+  # plot_grid(sim.endorsement.title, 
+  #           p4, ncol=1, rel_heights=c(0.1, 1)),
+           align = 'vh',
+           labels = c("A", "B"),
+           hjust = -1,
+           nrow = 2,
+           #rel_widths = c(1.2, 3, 2)
+           #rel_widths = c(1.2, 2.9, 1.4, 1.4),
+            rel_heights = c(1,1)
+           )
 
-<!-- @Nickel2016 notes that genericity is particularly challenging to study because it intersects with many other phenomena in natural language (e.g., gradable adjectives in "Giraffes are tall"). -->
-<!-- We agree, and add to this that genericity intersects with *world knowledge* in subtle ways, and it is critical to accurately describe and measure world knowledge before making claims about the semantics of a generalization.
--->
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
+# prow <- plot_grid(
+#   add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
+#   add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
+#   add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
+#   add_sub(p4, "Endorsement"),
+#            align = 'vh',
+#            labels = c("A", "B", "C", "D"),
+#            hjust = -1,
+#            nrow = 1,
+#            #rel_widths = c(1.2, 3, 2)
+#            rel_widths = c(1.2, 2.9, 1.15, 1.7)
+#            )
 
-In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
-<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->
+s1.simulations.relabeled
+ggdraw(add_sub(fig.sims.priors, 
+          expression(
+            paste(S("Sharks don't eat people | x = 0.8" ), " = ", 0.4)), size=12, hjust =0))
 
-## A step towards communicating generalizations
-<!-- Implicit aspects of language use: The comparison class and question under discussion -->
-
-In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
-Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
-Our endorsement model, which we use to generate predictions for our three case studies, can be seen as a special case of a speaker model who can only produce one of two utterances: the generalization or silence.
-Our interpreter model can be seen as a kind of "literal listener", who does not do any sort of pragmatic or communicative reasoning. 
-Our modeling framework could thus naturally be extended to more faithful models of pragamtic communication of generalizations, to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task.
-The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.
-
-### The comparison class
-
-Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
-The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
-Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
-Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.
-
-The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. 
-Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object). 
-We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017].
-Even if interlocutors coordinate on a particular comparison class, they may disagree about the prevalences for other *other categories* in the class.
-That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how *other forces* (e.g., plate tectonics) influence the climate or how often other social categories (e.g., neo-nazis) commit acts of terrorism.
-Indeed, we saw in Expt. 3 how the statistics of other causes can influence the endorsement of a single generalization (e.g., "Herb C makes animals sleepy").
-Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.
-
-### Question under discussion
-
-Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud].
-We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the prevalence.
-However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD.
-For example, the comparison classes used in our case studies were with respect to the target category (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUDs of "*what* has feature?", "*who* does action?", or "*what* causes effect?".
-Were the QUDs to be reversed (e.g., "what features does category have?", "what does person do?", "what effects does cause bring about?"), the comparison classes would need to be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
-
-The QUD is thus another layer of flexibility that makes understanding generalizations so challenging.
-The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus].
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
-In this work, we focused on category-wise comparison classes for methodological convenience. 
-<!-- In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features. -->
-<!-- *Feature-wise* comparison classes are likely to be modulated by the feature itself. -->
-Future work should investigate the feature-wise reading of generalizations, and explore what cues listeners adopt for one or the other interpretation.
-
-<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
-<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
-<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Structured prior knowledge
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., "Diapers are absorbent") and \emph{statistical} properties (e.g., "Diapers are white").
-Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
-Modulations of prevalence distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
-In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
-
-It is natural to ask how prevalence might reflect conceptual knowledge.
-We found that empirical prevalence distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
-Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.
-
-## Communicating predictive probabilities
-
-This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
-We make the important distinction that probability can be more general than frequency, and in our account, underlies speakers' subjective, predictions about the future and is subject to top-down moderator.
-Expts.
-2c \& 2d that showed using participants' \emph{predictions} about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
-
-Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probabilities [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the *language used* to convey *explicit probabilties* [cf., @Levinson1995].
-Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
-Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think rejecting the normal tools of truth-functional semantics for generics would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are three aspects of meaning that a child must acquire for a truth-functional quantifier semantics $\denote{u}(h, \theta) = \{h :h > \theta\}$: 
-(1) the dimension being described (i.e., the probability $h$),
-(2) the polarity of the relation (i.e., $>$ vs. $<$), and 
-(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning has to do with probability and that it stands in a positive relation to some standard $\theta$, a rational learner would adopt a prior distribution over possible thresholds $\theta$, as a form of *lexical uncertainty* [@Bergen2016].
-This prior could then be updated with more data to acquire a fixed meaning.
-However, for the generic statement, the language learner is done once she acquires aspects (1) and (2).
-In our model, $\theta$ is left underspecified in the semantics and is inferred in context.
-Thus, in this sketch of an acquisition model, a child would first acquire generic language, and from that, carve out more precise meanings for quantified language.
-
-The uniform prior over the threshold $\theta$ in the truth-functional threshold semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the prevalence $h$ *itself*:
-
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better the utterance", or simply "more is better") is perhaps the simplest semantics one could imagine.
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-We leave for future work the precise implementation of the acquisition model we sketch out here.
-
-## Other philosophical puzzles
-
-In our experiments, we have tried to include classic, philosophically puzzling examples of generalizations in language in addition to crafting novel stimuli that provide stricter tests of the main hypothesis.
-In this section, we consider some other previously-discussed troubling examples of generalizations and sketch out arguments rooted in our theoretical framework to demonstrate how our theory could account for these cases.
-We consider the five following examples:
-
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Supreme Court Justices have even social security numbers.
-4. Elephants live in Africa and Asia.
-5. Women are submissive.
-
-Sentence (1), strikes hearers as *odd* or perhaps *false*, despite the vast majority of books being paperback. 
-Why?
-A first observation is that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset ("paperbacks" is short-hand for "paperback books"). 
-We expect intuitions about this statement to generalize to other examples expressing an analogous relation (e.g., "Pastas are spaghetti", "Animals are humans").
-We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent-prevalence.
-Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers1963].^[
-  Note that this assumption is consistent with the comparison classes we have assumed in our three case studies.
-]
-Then, "is a paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
-  Note that this idea is similar to @Cohen1999's notion of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his   Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
-]
-The relevant aggregations of entities, then, are collection of books, potentially including books of different genres or publication eras among other such sub-categories.
-Then, given that "books" is the superordinate category of "kinds of books", the referent-category prevalence cannot be different from the mean of the prevalence prior.
-Finally, given this prevalence prior and the referent-prevalence, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in the a way analogous to "Robins are female".
-
-```{r booksArePaperbacks, fig.cap="Sketch of an argument for why 'Books are paperbacks' sounds odd.
-The feature 'is paperback' can only be predicated (in the sense of @Keil1979) of individual books, which are organized into collections (here, by genre).
-The prevalence prior is constructed by aggregating these collections of books.
-Then the prevalence of 'is paperbook' for the category of 'books' can never be higher than the mean of the prior distribution.
-The endorsement model would give this sentence a rating of 0.5, corresponding to neither true nor false."}
-knitr::include_graphics("figs/books-paperbacks.pdf", dpi = 108)
+#prow
 ```
-
-Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
-That is, the statement "Mary has handled mail from Antarctica" is false.
-Sentence (2) is still thought to be true despite zero actual instances of the event.
-We think (2) is a boundary case of generalizations expressing predictive probabilities, which we elucidated in Expt. 2c.
-In in that study, we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
-We expect the same to be true here, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
-Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
-
-Our focus on predictive probability makes even new prediction about some classic puzzles.
-Sentence (3) is the conceptual opposite of sentence (2).
-Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (3) is still considered false, every though the property holds in 100\% of the category [@Cohen1999].
-We predict this phenomenon is the result of abstract, intuitive theories guiding us to reject observed frequencies in forming our subjective probabilities.
-That is, because observers strongly believe selection for the Supreme Court is not influenced by one's social security number, speakers would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Then, given that the all professions would have roughly the same probability of having employees with even social security numbers, Sentence (3) is again similar to "Birds are female". 
-However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number*---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
-That is, we predict there are situations where statements like (3) could be considered felicitious generalizations.
-
-Understanding how a semantic representation *composes* is another critical test for a theory of generalizations in language.
-@Nickel2008 suggests Sentence (4) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Stastistical account of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
-However, this is the only interpretation if the generalization is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-Our theory does not provide a fixed semantics for the generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with a strong constraint against the existence of *international elephants* but with any further semantic assumptions, our model infers that some elephants live in Africa and other lives in Asia.^[
-  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-]
-Importantly, the model believes that most lives in Africa, when it only hears that "Elephants live in Africa", and only later revises it's beliefs to a weaker "some"-like interpretation after hearing they live in Asia as well.
-Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise interpretation of single utterances.
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-<!-- With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
--->
-<!-- When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement,  -->
-<!-- This is possible because our model has uncertainty over the semantic thresholds in the generic claim. -->
-
-Finally, sometimes a property is widespread relative to other kinds or groups, and it might be so systemic that we would believe it to be the case in the future, but speakers still might find it avertise to actually endorse the generalization.
-Such is the situation with Sentence (5) [@Haslanger2011]. 
-Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
-In our **Model Simulations** section, we showed that the genearlization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-  Note that this can straight-forwardly capture the central phenomena of @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated in the mind of the listener).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective values, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
-This kind of extension to rational models of communication has already been used to account for a variety of phenomena in *polite language* use [@Yoon2016; @Yoon2017].
-We propose adopting such a value-based utility structure for states of the world for language about social categories: If the speaker found states of the world where the probability of the feature is high (e.g., a world where many women were submissive) as undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
-We find this possibilitity intruiging and leave it for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
-The precise implementation of these hypotheses we leave for future work.
-
-<!-- -- Books are paperbacks. (failure of the constrast class) -->
-<!-- -- Birds lay eggs and are female vs. Elephants live in Asia and Africa -->
-<!-- can use pragmatics to resolve if the property is conjunctive or not.  -->
-<!-- -- Women are submissive. (Haslanger, 2011; generics + politeness mechanism, some states have lower value than others) -->
-<!-- -- Muslims are terrorists (vs. Mosquitos carry malaria) -->
-<!-- -- Mary handles the mail from antarctica (predictive propensity; also highlights domain restriction on events) -->
-<!-- - Glass breaks when struck. (so-called "disposition", but here: a generalization about the event of a glass being struck [already we are domain restricted]) -->
-
-## Relationship to other theories
-
-To our knowledge, the present papaer presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures.
-We now turn to situating our account with respect to these previous theories.
-<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
--->
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., *there is something about being K which causes it to F*).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical accounts
-
-#### Relative and absolute generics
-
-Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means.
-He partitions generics into two types: *absolute* and *relative* generics.
-*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-*Relative generics* depend upon an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
-"Mosquitos carry malaria" is a relative generic: it is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
-
-Our uncertain-threshold model deviates from Cohen's account in two primary ways.
-First, though his theory is framed in terms of probabilities, it still utilities a fixed threshold semantics and thus is only able to make predictions about what is "true" and what is "false".
-In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement.
-Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each.
-We used examples of both in our stimuli (Expt.
-1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".^[
-  For a related theory that aims to do away with the distinction between "absolute" and "relative"   adjectives, see @Lassiter2015.
-]
-
-We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$). 
-For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
-Therefore, "Robins lay eggs" is evaluated as an *absolute generic* because only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery behind Cohen's domain restriction (i.e., what comrpises $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
-  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.
-]
-However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
-Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-
-#### "Normal" accounts
-
-The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
-For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
-However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
-Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
-We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations. 
-Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
-
-#### Underquantification
-
-A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
-In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analagous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
-Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
-This distinction is relevant for the acquisition of the language of generalizations; we do not think that quantified relations (e.g., "Some", "All") are in any way primary or special. 
-<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
--->
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
-
-#### Generic as indexical
-
-@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
-The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
-Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
-We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
-
-### Conceptual accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties.
-That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar".
-
-The most influential conceptual account of generics is from @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
-Leslie's "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about.
-
-This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
-Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
-1 for naturalistic cases).
-In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
-3a), we have observed that the prior distribution over the prevalence $P(h)$ change when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors. 
-Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features.
-<!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
--->
-
-Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs").
-Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young)
-The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist. 
-For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
-In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
-Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
-
-Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world. 
-"Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters.
-"Barns are red" because most barns are red.
-If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green".
-Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.
-
-Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations.
-In the last fifteen years, there has been tremendous progress in formalizing 
-Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.
-
-In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
-In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).  
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
-<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence across different categories. -->
-<!-- This minimally structured model  -->
-
-The key point of divergence then between the conceptual accounts and our view concerns the core, semantic meaning of a generic statement.
-Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this provides a more unifying view of generics, giving a single metric as the basic currency of generic meaning: probability.
-
-<!-- @Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts. -->
-<!-- Striking generics (e.g.
-\emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
--->
-<!-- Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}). -->
-<!-- The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations. -->
-<!-- Statistical information takes a backseat to the conceptual structure. -->
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-# Conclusion
-
-It might seem paradoxical that a part of language that is so common in communication and central to learning should be vague. 
-Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve  uncertainty in meaning [@Piantadosi2012].
-In our work, context takes the form of shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong generalization to a naive listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which could be differences in the prior distributions on prevalence or the comparison class.
-Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).
-This is a promising area for future research.
-
-Categories are inherently unobservable. 
-You cannot see the category \textsc{dog}, only some number of instances of it.
-Yet we easily talk about these abstractions, conveying hard-won generalizations to each other and down through generations.
-<!-- The theory presented here gives one explanation of how we do so, providing a computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
--->
-The theory presented here provides the first computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
-
-\newpage
-
-# References
-
-<!-- \setlength{\parindent}{-0.1in}  -->
-<!-- \setlength{\leftskip}{0.125in} -->
-<!-- \noindent -->
-
-<div id = 'refs'></div>
-
-\newpage
-
-```{r child = 'appendix-cvDerivation.Rmd'}
-```
-
-\newpage
-```{r child = 'appendix-cueValidity.Rmd'}
-```
-
-\newpage
-
-```{r child = 'appendix-bda.Rmd'}
-```

### 2018-02-05 paper/comgen-paper.Rmd
simply fig1, modularize code to analysis script for model simulation, cache model sims

@@
 
-```{r rsaHelpers}
-rsaHelpers <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var round = function(x){
-  return Math.round(x*1000)/1000
-}
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
-// var thetaBins = [
-//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- // ]
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var bins = map(round, _.range(0.01, 0.99, 0.01))
-
-// var bins = [
-  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-// ];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-'
+```{r loadCachedSimulations, cache = F}
+load("cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData") # sims.priors, sims.fixed.thresholds, sims.uncertain.thresholds, s1.simulations.relabeled
+
+s1.simulations.relabeled.2 <- left_join(
+  s1.simulations.relabeled %>%  
+    mutate(PriorShape = factor(example, 
+                               levels = c("Dogs bark",
+                                          "Kangaroos have spots",
+                                          "Sharks don't eat people",
+                                                      "Robins lay eggs",
+                                                      "Robins are female",
+                                                      "Mosquitos carry malaria"),
+                               labels = c("bark", "have spots", "don't eat people", 
+                                          "lay eggs", "are female", "carry malaria")),
+              category = c("sharks", "robins", "robins", "kangaroos", "dogs", "mosquitos"),
+              xlabpos = c(0.8, 0.5, 0.5, 0.325, 0.85, 0.325),
+              ylabpos = c(0.12, 0.25, 0.25, 0.12, 0.12, 0.12)
+           ),
+                       data.frame(src =  c(rep("Prevalence priors", 6), rep("Interpretation posteriors",6 )),
+                                  example = with(s1.simulations.relabeled, c(as.character(example), as.character(example))))
+ ) %>%
+   mutate(featureProb = ifelse(as.character(src) == "Prevalence priors", featureProb, -99),
+          xlabpos = ifelse(as.character(src) == "Prevalence priors", xlabpos, -99))
 ```
 
-```{r rsaInterpretationModels, eval = T, cache = T}
-no.utterance.model <- '
-var noUtteranceInterpreter = function() {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    return { state }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-'
-
-fixed.threshold.model <- '
-var fixedThresholdInterpreter = function(threshold) {
-  Infer({model: function(){
-  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-  var state = sample(statePrior)
-  condition( state > threshold)
-    return {
-      state: state
-  }
- // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
- }, method: "enumerate"})}
-'
-
-uncertain.threshold.model <- '
-var uncertainThresholdInterpreter = function() {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor( Math.log(state) )
-    return {
-      state: state, 
-  }
-  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-'
-
-```
-
-```{r simulationCalls}
-fixed.threshold.calls <- '
-_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
-'
-no.utterance.call <- ' 
-  noUtteranceInterpreter()
-'
-uncertain.threshold.call <- '
-  uncertainThresholdInterpreter()
-'
-```
-
-```{r simulationRuns}
-priorNames <- c(
-  "doesntEatPeople", #"uniformRare", 
-  "isFemale", 
-  "laysEggs", 
-  #"eatsFood", 
-  "barks",
-  "carriesMalaria",
-  "hasSpots"
- # "areSick"
-  )
-priorShapes <- list(
-  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
-  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
-  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
-  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
-  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
-  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
-)
-
-sims.fixed.thresholds <- data.frame()
-sims.priors <- data.frame()
-sims.uncertain.thresholds <- data.frame()
-
-for (p in priorNames){
-
-  inputData = list(prior = priorShapes[[p]])
-  rs.fixed.threshold.model <- webppl(paste(rsaHelpers, fixed.threshold.model, fixed.threshold.calls, sep = '\n'), data = inputData, data_var = "data")
-  rs.uncertain.threshold.model <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
-  rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
-
-  sims.fixed.thresholds <- bind_rows(sims.fixed.thresholds,
-    bind_rows(
-      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.1`) %>% rename(prob = probs), 20000), threshold = 0.1) ,
-      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.3`) %>% rename(prob = probs), 20000), threshold = 0.3),
-      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.5`) %>% rename(prob = probs), 20000), threshold = 0.5),
-      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.7`) %>% rename(prob = probs), 20000), threshold = 0.7),
-      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.9`) %>% rename(prob = probs), 20000), threshold = 0.9)
-    ) %>% 
-      mutate(PriorShape = p)
-    )
-
-  sims.uncertain.thresholds <- bind_rows(sims.uncertain.thresholds, rs.uncertain.threshold.model %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
-  sims.priors <- bind_rows(sims.priors, rs.prior %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
-}
-```
-
-```{r cache = F}
-fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
+```{r simulations, fig.cap = "Computational model simulations.
+Top: Prior distributions over the prevalence of a feature for 6 example features.
+Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions.
+Arrows show intuitive referent-category prevalence for a target category.
+Bottom: The interpreter model posterior distributions over prevalence upon hearing a generalization about a novel category.
+Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for  the referent-category whose prevalence is shown in the top facets (e.g., \"Mosquitos carry malaria\").", fig.width = 9, fig.asp = 0.37, out.width = "100%", fig.align = "center", cache=F}
+
+fig.sims.priors <- ggplot(
+  bind_rows(sims.priors %>% 
+              mutate(src = 'priors'),
+            sims.uncertain.thresholds %>% 
+              mutate(src = 'posteriors')
+            ) %>% mutate(PriorShape = 
+                           factor(PriorShape,  
+                                  levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
+                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")),
+                         src = factor(src, levels = c("priors", "posteriors"),
+                                      labels = c("Prevalence priors", 
+                                                 "Interpretation posteriors"))), 
+  aes(x = state, fill = PriorShape, color = PriorShape))+
     geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
@@
     scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    # geom_rect(data = s1.simulations.relabeled.2,
+    #           aes(xmin = featureProb - 0.05, xmax = featureProb + 0.05, ymin = 0.0, ymax = 0.15),
+    #           fill = 'black', inherit.aes =F)+
+    geom_segment(data = s1.simulations.relabeled.2,
+              aes(x = featureProb, xend = featureProb, 
+                  yend = 0.02, y = 0.2), size = 1,
+              fill = 'black', inherit.aes =F, arrow = arrow(length = unit(0.2, "cm"),
+                                                            type = 'open'))+
+    geom_label(data = s1.simulations.relabeled.2,
+                aes(x = xlabpos, y=0.25, label = category),
+                label.padding = unit(0.075, "lines"),
+                  family = 'Palatino', fontface = 'bold', size = 3.2, inherit.aes =F, force = 15)+
     ylab("Normalized probability density") +
-    xlab("")+
+    xlab("Prevalence")+
     scale_color_solarized()+
     scale_fill_solarized()+
-    facet_grid(PriorShape~., scales = 'free')+
-    theme(strip.text.y = element_blank())
-```
-
-```{r cache = F}
-fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
-    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
-    theme_few() +
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence of the feature in a category") +
-    ylab("") +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    facet_grid(PriorShape~threshold, scales = 'free')+
-    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
-```
-
-```{r cache = F}
-fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
-                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
-    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
-    theme_few() +
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("") +
-    ylab("") +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    facet_grid(PriorShape~., scales = 'free')+
-    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
-```
-
-```{r fig.width = 9, eval = F}
-p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
-p2 <- fig.sims.fixed.thresholds +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
-p3 <- fig.sims.uncertain.threshold+
-  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
-    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-
-prow <- plot_grid( p1 + theme(legend.position="none"),
-           p2 + theme(legend.position="none"),
-           p3 + theme(legend.position="none"),
-           align = 'vh',
-           labels = c("A", "B", "C"),
-           hjust = -1,
-           nrow = 1,
-           #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 3, 1.2)
-           )
-#prow
-#legend <- get_legend(p1)
-
-#plot_grid( prow, legend, rel_widths = c(3, .3))
-```
-
-```{r simluationEndorsementModel, eval = T, cache = T}
-s1.model <- '
-var interpreter = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var alpha = 2
-
-var endorser = function(featureProb){
-  Infer({model: function(){
-    var endorsement = sample(utterancePrior)
-    var L0 = interpreter(endorsement)
-    factor(alpha * L0.score(featureProb))
-    return endorsement
-  }})
-}
-// console.log(data.featureProb[0])
-probability(endorser(data.featureProb[0]), "generic")
-'
-
-exampleGenerics <- c(
-  "sharksDontEatPeople",
-  "robinsAreFemale", 
-  "robinsLayEggs", 
-  "kangaroosHaveSpots",
-  "dogsBark",
-  "mosquitosCarryMalaria"
-  )
-
-exampleParameters <- list(
-  robinsAreFemale =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 1), featureProb = 0.5), 
-  robinsLayEggs =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 0.2), featureProb = 0.5), 
-  sharksDontEatPeople =  list(prior = list(params = data.frame(a = 50, b = 1), mix = 1), featureProb = 0.8), 
-  dogsBark =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.4), featureProb = 0.9), 
-  kangaroosHaveSpots =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.7), featureProb = 0.1), 
-  mosquitosCarryMalaria =  list(prior = list(params = data.frame(a = 1, b = 30), mix = 0.1), featureProb = 0.1)
-)
-
-s1.simulations <- data.frame()
-for (p in exampleGenerics){
-
-    s1.rs <- webppl(paste(rsaHelpers, s1.model, sep = "\n"), data = exampleParameters[[p]], data_var = "data")
-    s1.simulations <- bind_rows(s1.simulations,
-                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))
-
-}
-
-```
-
-```{r}
-s1.simulations.relabeled <- s1.simulations %>%
-  mutate(example = factor(example, 
-                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
-                            labels = 
-                            c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")
-                            #c("Dogs", "Kangaroos", "Sharks", "Robins ", "Robins", "Mosquitos")
-                          ))
-
-# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
-#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
-#   #ylab("Human endorsement probability")+
-#   #xlab("Frequency of target")+
-#   geom_label_repel(data = s1.simulations.relabeled, 
-#                    aes( label = example, fill = example),
-#                        color = 'white',
-#     box.padding = unit(0.0, "lines"),
-#     #point.padding = unit(1e-06, "lines"),
-#     segment.color = 'grey37')+
-#   scale_fill_solarized()+
-#   scale_x_continuous(limits = c(0, 1), 
-#                      breaks = c(0, 0.5, 1))+
-#   scale_y_continuous(limits = c(-0.01, 1.01), 
-#                      breaks = c(0, 1),
-#                      labels = c("False", "True"))+
-#   coord_fixed(ratio = 1)+
-#   guides(fill = F)+
-#   ylab("Endorsement model prediction")+
-#   xlab("Hypothesized prevalence")
-
-s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
-  geom_col(color = 'black')+
-  # geom_label_repel(data = s1.simulations.relabeled, 
-  #                  aes( label = example, fill = example),
-  #                      color = 'white',
-  #   box.padding = unit(0.0, "lines"),
-  #   #point.padding = unit(1e-06, "lines"),
-  #   segment.color = 'grey37')+
-  scale_fill_solarized()+
-  scale_x_continuous(limits = c(0, 1), 
-                     breaks = c(0, 1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 1),
-                     labels = c("False", "True"))+
-  #coord_fixed(ratio = 1)+
-  coord_flip()+
-  facet_grid(example~.)+
-  guides(fill = F)+
-  ylab("")+xlab("Referent prevalence")+
-  theme(strip.text.y = element_text(angle = 0, hjust = 0)
-        #axis.title.x = element_text(hjust = 0)
-        #axis.title.y = element_text(vjust = 0)
-        )
-  #ylab("Endorsement model prediction")+
-  #xlab("Hypothesized prevalence")
-```
-
-```{r simulations, fig.cap = "Computational model behavior.
-A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations.
-C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors.
-D: Endorsement model predictions, assuming a particular referent-prevalence.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
-p1 <- fig.sims.priors +
-  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
-p2 <- fig.sims.fixed.thresholds +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
-p3 <- fig.sims.uncertain.threshold+
-  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
-    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
-
-prow <- plot_grid( 
-  add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
-  add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
-  add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
-  add_sub(p4, "Endorsement"),
-           align = 'vh',
-           labels = c("A", "B", "C", "D"),
-           hjust = -1,
-           nrow = 1,
-           #rel_widths = c(1.2, 3, 2)
-           rel_widths = c(1.2, 2.9, 1.15, 1.7)
-           )
-prow
-```
-
-```{r eval = F}
-all.simulations.refactored <- all.simulations %>%
-  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
-  filter(Distribution != "Some", Distribution != "Most") %>%
-  mutate(Distribution = factor(Distribution, levels = 
-                                c( "Prior_generic", "Posterior_Generalization_generic"),
-                                labels = c( "Prior/Silence", "Generalization")
-                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
-                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
-                             ),
-         PriorShape = factor(PriorShape, 
-                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
-                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
-                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
-                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
-                                  #"eatsFood","areSick", "uniformRare", 
-                                  #"carriesMalaria"
-                                  )
-         )
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                #lty = Distribution, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    #scale_linetype_manual(values = c(3, 4, 2, 1))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence of feature in a category") +
-    ylab("Scaled probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-
-l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
-                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
-    geom_density(aes(y = ..scaled..),
-                 size = 0.6,  adjust = 1.5)+
-    theme_few() +
-    scale_color_solarized()+
-    scale_fill_solarized()+
-    scale_alpha_manual(values = c(0.7, 0.3))+
-    scale_linetype_manual(values = c(1, 3))+
-    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    xlab("Prevalence of feature in a category") +
-    ylab("Scaled probability density") +
-  facet_wrap(~PriorShape, scales = 'free')+
-  guides(fill = F, color = F)+
-  theme(strip.text.y = element_text(angle = 0),
-          legend.position = c(0.92, 0.35))
-
-```
-
-```{r simulationsOld, eval = F, fig.cap = "Model behavior.
-Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions.
-The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model.
-Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
-grid.arrange(l0.simulations.distributions, 
-             s1.simulations.scatter, ncol = 3,
-             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))
-
+    facet_grid(src~PriorShape, scales = 'free')+
+    theme(strip.text.y = element_text(angle = 0, hjust =0),
+          legend.position = "none", 
+          plot.margin=unit(c(0.5,0.5,1.5,0.5),"cm"))
+
+ggdraw(fig.sims.priors) + 
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Dogs bark"),endorsement))[[1]], 2), 
+             0.12, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Kangaroos have spots"),endorsement))[[1]], 2), 
+             0.25, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Sharks don't eat people"),endorsement))[[1]], 2),
+             0.36, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Robins lay eggs"),endorsement))[[1]], 2), 
+             0.48, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Robins are female"),endorsement))[[1]], 2), 
+             0.6, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Mosquitos carry malaria"),endorsement))[[1]], 2), 
+             0.72, 0.12, fontface = "italic", fontfamily = "Times") +
+  draw_label("Endorsement Prediction", 0.885, 0.12, size = 10)
 ```

### 2018-02-06 paper/case1-generics.Rmd
move code from case1 to analysis file, cache results

@@
 ### Method
-```{r eval = F}
-d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "naturalGenerics-trials-formatted.csv", sep = ""))
-
-# write.csv(
-#   left_join(
-#   d1 %>%
-#     mutate(sentence = as.character(sentence),
-#            sentence = gsub('&quotechar', '', sentence),
-#          sentence = gsub('lyme', 'Lyme', sentence)),
-#   unique(d2 %>%
-#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
-#     select(Category, Property, sentence))
-# ), file = paste(project.path, "data/generics/endorsement/",
-#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
-```
 
 ```{r generic-endorsement}
-d.gen.endorse.catch <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments_catch-trials.csv", sep = ""))
-
-d.gen.endorse <- read.csv(paste(project.path, "data/generics/endorsement/",
-                    "truth-judgments-n100.csv", sep = ""))
-
-d.gen.endorse.summary <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
-  group_by(sentence) %>%
-  multi_boot_standard(col = "response") %>%
-  ungroup() %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))
-
-d.gen.endorse.bayes <- left_join(
-  d.gen.endorse, 
-  d.gen.endorse.catch %>% select(workerid, pass)
-  ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup()
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.prev.summary <- d.prev %>%
-  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
-  filter(item %in% d.gen.endorse.bayes$sentence) %>%
-  mutate(prevalence = prevalence / 100) %>%
-  group_by(Category, Property, item) %>%
-  multi_boot_standard(col = "prevalence")
-
-# d.gen.endorse.summary %>%
-#   ggplot(., aes(x = sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
-generics.endorsement.spectrum <- left_join(
-  d.gen.endorse.bayes, d.prev.summary %>% rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper)
-) %>%
-  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))  %>%
-  #ggplot(., aes(x = sentence, y = MAP_h, ymin = low, ymax = high))+
-  ggplot(., aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev))+
-  geom_bar(stat = 'identity', position = position_dodge(), color= 'black', alpha = 0.9)+
-  geom_linerange(position = position_dodge())+
-  #geom_errorbar(position = position_dodge())+
+load("cached_results/case1_endorseSummary_byItem.RData") # d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes
+generics.endorsement.spectrum <- ggplot(
+    d.gen.endorse.bayes.prev, 
+    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
+  )+
+  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
+  geom_linerange(position = position_dodge(), size = 1)+
   coord_flip()+
@@
   xlab("")+
-  #scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1))+
+  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
   scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 1), limits = c(0, 1))+
-  guides(fill = guide_colorbar(title = 'Prevalence',
+  guides(color = guide_colorbar(title = 'Prevalence',
                                ticks = F))+
   theme(legend.position = 'bottom')
-  #geom_hline(yintercept = -0.25, lty = 3)+
-  #geom_hline(yintercept = 0.25, lty = 3)
 ```
@@
 
-mht.truth.judgments <- data.frame(sentence = names(all.sentences),
-           truth_judgment = as.vector(unlist(all.sentences)))
-
-d.gen.endorse.manipulation.check.bayes <- left_join(
-  left_join(
-    d.gen.endorse, 
-    d.gen.endorse.catch %>% select(workerid, pass)
-    ),
-  mht.truth.judgments ) %>%
-  filter(pass == 1) %>%
-  rowwise() %>%
-  mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(truth_judgment) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b)) %>% 
-  ungroup() %>%
-  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))
-
 true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
@@
 uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]
-
 ```
@@
 
-```{r generic-endorsement-priors}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-
-```
-
-```{r generic-endorsement-priors-unbounded, eval = F}
-# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-unboundedModel <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-
-var shapeParams = function(params){
-  return {
-    a: params.g * params.d,
-    b: (1 - params.g) * params.d
-  }
-}
-
-var model = function(){
-
-  // var numComponents = (1 + poisson(1));
-  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
-  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
-    return uniformDrift({a: 0, b:1, width: 0.2})
-  }))).reverse()
-
-  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
-  var componentParams = map(function(i){
-    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
-    var betaParams = shapeParams({g, d})
-    return betaParams
-  }, _.range(numComponents))
-
-  mapData({data: preprocessedResponses}, function(d){
-
-    var scr = log(sum(map(function(cParams){
-      cParams[1] * exp(Beta(cParams[0]).score(d))
-    }, _.zip(componentParams, mixtureWeights))))
-//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
-    factor(scr)
-  })
-
-  var componentPredictives = map(function(cParams){
-      return beta(cParams)
-  }, componentParams)
-
-  return _.fromPairs(
-    _.zip(
-        map(function(i){ i + "_weight" }, _.range(5)), 
-        mixtureWeights
-      ).concat(
-      _.zip(
-        map(function(i){ i + "_predictive" }, _.range(5)), 
-        componentPredictives
-      )
-    )
-  )//sort(T.toScalars(mixtureWeights))
-};
-'
-
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
-  n_samples <- 10000
-lg = 0
-  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-```
-
-```{r eval = F}
-m.gen.endorse.priors.unbounded %>%
-      separate(Parameter, into = c("c", "var")) %>% 
-      ggplot(., aes( x=  value, fill = c))+
- geom_histogram(position = position_dodge(), binwidth = 0.05)+
- facet_wrap(~var)+
-  scale_fill_solarized()
-```
-
-```{r generic-endorsement-priors-bayesFactors, eval = F}
-genericEndorsementPriorModelPriorLikelihoodHelpers <- '
-var properties = _.uniqBy(_.map(data, "Property"));
-
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-'
-
-genericEndorsementPriorModelsPriorLikelihood <- '
-var transientComponent = Beta({a:1, b:100})
-
-var model = function(){
-
-  var propertyLogLikes = map(function(property){
-
-    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
-    var preprocessedResponses = map(function(d){
-        return avoidEndPoints(d / 100)
-    }, propertyData);
-
-    var phi = uniformDrift({a:0, b: 1, width:0.2});
-    var g = uniformDrift({a:0, b: 1, width:0.2});
-    var d = uniformDrift({a:0, b: 100, width:5});
-    var stableParams = betaShape({g, d})
-    var stableComponent = Beta(stableParams)
-
-    var logLikes = map(function(d){
-      var structuredLL = log(
-        phi * exp(stableComponent.score(d)) +
-        (1 - phi) * exp(transientComponent.score(d))
-      )
-
-      var unstructuredLL = stableComponent.score(d);
-
-      return {structuredLL, unstructuredLL}
-    }, preprocessedResponses)
-
-    return {
-      structuredLL: sum(_.map(logLikes, "structuredLL")), 
-      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
-    }
-
-  }, properties)
-
-  return {
-    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
-    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
-  }
-}
-'
-
-```
-
-```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
-marginal.prior.likelihoods <- data.frame()
-
-# 100 samples takes 30s
-m.gen.endorse.priors.logLike <- webppl(
-    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
-          genericEndorsementPriorModelsPriorLikelihood,
-          sep = '\n'), 
-    data = d.gen.endorse.priors, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "forward", samples = 1000),
-    chains = 3, cores = 3
-) %>% 
-  mutate(value = as.numeric(value))
-
-min.ll.1 <- min(
-  m.gen.endorse.priors.logLike$value[
-    is.finite(
-      m.gen.endorse.priors.logLike$value
-      )
-    ]
-  )
-
-m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
-  rowwise() %>%
-  mutate(value = ifelse(value == -Inf, min.ll.1, value))
-
-save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
-```
-
-```{r generic-endorsement-priors-bayesFactorsLoad}
-load(file = '../analysis/generics-priors-loglike.Rdata')
-marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
-  group_by(Chain, Parameter) %>%
-  summarize(mll  = logmeanexp(value))
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
-  spread(Parameter, mll) %>%
-  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
-```
-
 The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs.
@@
 A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
-
-<!-- The Bayes Factor indicates the extent to which the data support one model over another. -->
-<!-- The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
--->
-<!-- Indeed, the data strongly suggests the prevalence prior is structured. -->
-
-```{r generic-endorsement-priors-savageDickeyModel, eval = F}
-savageDickeyModel <-'
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {phi}
-}
-
-//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
-// var samples = 2000, burn = burn / 2, lag = 0;
-var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
-verbose: true}, model)
-var modelPrior = Infer({method: "forward", samples:10000}, model)
-
-var pointNull = 1;
-
-var logBFs = map(function(diff){
-  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
-  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
-  return [diff, Math.log(savageDickeyRatio)]
-}, [0.01, 0.02, 0.03, 0.04, 0.05])
-
-var returnVals = {
-  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
-}
-returnVals
-'
-```
-
-```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
-genericEndorsementPriorSupermodel <- '
-var model = function(){
-  var alpha = uniformDrift({a:0, b: 1, width:0.2});
-  //var structured = flip();
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g1 = uniformDrift({a:0, b: 1, width:0.2});
-  var d1 = uniformDrift({a:0, b: 100, width:5});
-  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
-  // var d0 = uniformDrift({a:0, b: 100, width:5});
-  var stableParams1 = betaShape({g: g1, d: d1})//, 
-      //stableParams0 = betaShape({g: g0, d: d0});
-  var stableComponent1 = Beta(stableParams1)//,
-      //stableComponent0 = Beta(stableParams0);
-
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data:preprocessedResponses},
-    function(d){
-    var scr1 = log(phi * exp(stableComponent1.score(d)) +
-                    (1 - phi) * exp(transientComponent.score(d)))
-    var scr0 = stableComponent1.score(d);
-    // display(exp(scr1) + " " + exp(scr0));
-    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
-    // factor(structured ? scr1 : scr0)
-    factor(combined_ll)
-  })
-  return alpha
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.supermodel.posterior <- webppl(
-    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model",  chains = 2,
-                                 cores = 2,
-                                 inference_opts = 
-                                   list(method = "MCMC",
-                                        samples = 2000, 
-                                        burn = 2000, 
-                                        lag = 2, 
-                                        verbose = T)
-    )
-
-  qplot(m.gen.endorse.priors.supermodel.posterior$value)
-}
-```
-
-```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
-genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
-  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  var logLike = sum(map(function(d){
-    var scr = log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    )
-    return scr
-  }, preprocessedResponses))
-  return logLike
-}
-'
-genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
-var eps = 0.00000001;
-
-var model = function(){
-  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
-  var d = uniformDraw(_.range(eps, 100, 2))
-  var stableParams = betaShape({g, d});
-  var stableComponent = Beta(stableParams);
-  var logLike = sum(map(function(d){
-    return stableComponent.score(d)
-  }, preprocessedResponses))
-  return logLike
-}
-'
-```
-
-```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
-marginal.prior.likelihoods <- data.frame()
-
-for (p in gen.endorse.properties){
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-  m.gen.endorse.priors.logLike.enum1 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  m.gen.endorse.priors.logLike.enum0 <- webppl(
-    paste(genericEndorsementPriorModelHelpers,
-          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
-    data = priorData, data_var = "data",
-    model_var = "model", 
-    inference_opts = list(method = "enumerate")
-    )
-
-  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
-  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)
-
-  marginal.prior.likelihoods <- bind_rows(
-    marginal.prior.likelihoods, 
-    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
-  )
-}
-
-marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))
-
-```
-
-```{r generic-endorsement-priors-model-run, eval = F}
-m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
-lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
-  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
-
-    m.gen.endorse.priors.structured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.unstructured <- webppl(
-      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
-                                 data = priorData, data_var = "data",
-                                 model_var = "model",
-                                 chains = 2,
-                                 cores = 2,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence = rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-        Property = p, src = "Unstructured"
-      ) %>% ungroup()
-
-    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
-      m.gen.endorse.priors.posteriorPredictive,
-      bind_rows(
-       m.gen.endorse.priors.structured.predictive %>%
-          select( src, Property, prevalence),
-      m.gen.endorse.priors.unstructured.predictive %>%
-          select( src, Property, prevalence),
-      data.frame(Property = p,
-                 src = "Data",
-                 prevalence = priorData/100)
-      )
-    )
-
-}
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
 
@@
 
-```{r generic-regression-models}
-d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
-  mutate(sentence = paste(category, property))
-
-### Preprocessing
-# - Force all responses to lower case. 
-# - Remove spaces.
-# - Fix mosquito mispellings.
-# - Count "deertick" as "tick".
-# - Remove plural "s".
-# 
-# Mark if the produced animal matches the generic of interest.
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv$workerid)))
-for (i in 1:10){
-
-  d.cv.bsample <- d.cv %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.gen.cv.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped %>%
-      group_by(property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
-# 
-# d.cv.bootstrapped %>%
-#   group_b
-
-# need to filter by items specified with endorsement
-# d.gen.cv.summary <- left_join(
-#   d.target.items %>% select(-sentence),
-#   d.cv %>%
-#     rename(category = response) %>%
-#     group_by(property) %>%
-#     mutate(n = n(),
-#            item = paste(category, property)) %>%
-#     filter(item %in% d.target.items$item) %>%
-#     group_by(category, property) %>%
-#     summarize(mentions = n(),
-#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
-#               prop = mentions / trials)
-#   ) %>%
-#   mutate(prop = ifelse(is.na(prop), 0.01, prop))
-
-d.gen.endorse.prev.cue <- left_join(
-  left_join(
-    left_join(
-      d.gen.endorse, 
-      d.gen.endorse.catch %>% select(workerid, pass)
-      ) %>%
-      filter(pass == 1) %>%
-    rowwise() %>%
-    mutate(response = ifelse(response == "agree-key", 1, 0),
-         sentence = gsub('&quotechar', '', sentence),
-         sentence = gsub('lyme', 'Lyme', sentence),
-          sentence = gsub('[.]', '', sentence)
-    ),
-    d.prev.summary %>% 
-      rename(prev_mean = mean,
-             sentence = item,
-             prev_ci_lower = ci_lower,
-             prev_ci_upper = ci_upper) %>%
-      ungroup() %>%
-      mutate(sentence = gsub('[.]', '', sentence))
-    ),
-  d.gen.cv.summary %>% select(-item))
-
-glm.gen.endorse.prev <- glm(response ~ prev_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
-              data = d.gen.endorse.prev.cue, family = 'binomial')
-
-d.gen.endorse.prev.cue.uniq <- unique(select(
-    d.gen.endorse.prev.cue, Property, Category, sentence, 
-    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
-  ))
-
-d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_lower,
-         cv_mean = cv_ci_lower)
-d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
-  select(-prev_mean, -cv_mean) %>% 
-  rename(prev_mean = prev_ci_upper,
-         cv_mean = cv_ci_upper)
-
-d.gen.endorse.regression.prevalence <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
-    ) %>%
-    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
-) %>% mutate(
-  sqErr = (MAP_h - prediction_mean) ^ 2
-)
-
-d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
-  d.gen.endorse.bayes,
-  d.gen.endorse.prev.cue.uniq %>%
-    mutate(
-      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
-      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
-      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
-      sentence = paste(Category, " ", Property, ".", sep = "")
-      )
-) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)
-
-d.gen.endorse.regression <- bind_rows(
-  d.gen.endorse.regression.prevalence.cuevalidity %>%
-    mutate(src = "regression_Prev_Cuevalidity"),
-  d.gen.endorse.regression.prevalence %>% 
-    mutate(src = "regression_Prev")
-  )
-
-r2.gen.n <- length(d.gen.endorse.bayes$sentence)
+```{r}
+load("cached_results/case1_regressionResults.RData") # d.gen.endorse.regression.prevalence, d.gen.endorse.regression.prevalence.cuevalidity, d.gen.endorse.regression,
+r2.gen.n <- length(d.gen.endorse.bayes.prev$sentence)
 r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
@@
 
-```{r generic-RSAmodels, fig.width = 8}
-example.generics <- c("Tigers dont eat people", 
-                      "Mosquitos carry malaria", 
-                      "Robins lay eggs", 
-                      "Robins are female",
-                      "Leopards have spots")
-
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
-#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
-# m.samp <- data.frame()
-#m.samp.fixed <- data.frame()
-#for (i in seq(1, n_chains)){
-  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
-
-#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
-#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
-#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-# }
-# 
-# save(m.samp,
-#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-#
-
-# save(m.samp.fixed,
-#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
-
-     # file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-    #                 n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-# load(m.samp.fixed, 
-#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdDisc-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
-
-load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))
-
-#m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-10000_burn5000_lag20_chain1.csv", sep = ""))
-# 
-# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
-# 
-# tail(m.samp.fixed)
-
-fixed.params.posterior <-  m.samp.fixed %>% 
-  filter(param %in% c("noise", "fixedThreshold")) %>%
-  group_by(param) %>% 
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.somemodel.endorsement <- m.samp.fixed %>%
-  filter(type == 'endorsement', param == "some") %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# m.gen.fullmodel.endorsement <- m.samp.samp %>%
-#   rename(type = Parameter, property = Property, category = Category, val = Value, param = Extra) %>%
-#   group_by(type, property, category, param) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.gen.fullmodel.endorsement <- m.samp %>%
- filter(type == 'endorsement', param == 'generic') %>%
-  # filter(type == 'predictive', param == 'generic') %>%
- # filter(type == 'endorsement') %>%
-  group_by(type, param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-uncertain.threshold.s1opt <- m.samp %>% 
-  filter(type == "param") %>%
-  group_by(param) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-fixed.threshold.s1opt <- m.samp.fixed %>% 
-  filter(type == "param") %>%
-  group_by(param) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-fixed.threshold.posterior <- filter(fixed.params.posterior, param == "fixedThreshold")
-generics.fixed.noise.posterior <- filter(fixed.params.posterior, param == "noise")
-```
-
-```{r generic-endorsement-referent-prevalence-model, eval = F}
-referentPrevalenceModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var betaParams = betaShape({g, d})
-  var referentPrevDist = Beta(betaParams)
-  mapData({data: preprocessedResponses}, function(d){
-    observe(referentPrevDist, d)
-  })
-  return {g, d}
-}
-'
-genericEndorsementRefPrevModel <- paste(genericEndorsementPriorModelHelpers, referentPrevalenceModel, sep = "\n")
-```
-
-```{r generic-referent-prevalence-model-run, eval = F}
-m.gen.refprev.predictive <- data.frame()
-n_samples <- 10000
-lg = 0
-
-for (p in example.generics ) {
-
-  prevData <- d.prev %>% 
-  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
-  filter(sentence == p)
-
-  m.gen.refprev <- webppl(genericEndorsementRefPrevModel,
-                                 data = prevData$prevalence, data_var = "data",
-                                 model_var = "model",
-                                 chains = 1,
-                                 cores = 1,
-                                 inference_opts =
-                                   list(method = "MCMC",
-                                        samples = n_samples,
-                                        burn = n_samples / 2,
-                                        lag = lg,
-                                        verbose = T))
-
-    m.gen.refprev.predictive.item <- m.gen.refprev %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        prevalence =rbeta(n = 1, shape1 = a,
-                                 shape2 = b),
-        Category = prevData[1,]$Category,
-        Property = prevData[1,]$Property,
-        src = "prevAloneModel"
-      ) %>% ungroup()
-
-    m.gen.refprev.predictive <- bind_rows(
-      m.gen.refprev.predictive,
-      m.gen.refprev.predictive.item %>%
-        select( src, Category, Property, prevalence)
-    )
-
-}
-#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-#head(prevData)
-#n_samples
-```
-
-```{r gen-prev-forward, eval=F}
-#Forward sample Target Prevalence from posterior on parameters (joint inference model)
-m.samp.prev.params <- m.samp %>%
-    filter(type == "targetPrevalence") %>%
-    #filter(type == "withinKind") %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
-    #mutate(item = paste(parameter, property, sep = "_")) %>%
-    group_by(parameter) %>%
-    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-    ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_")
-
-m.samp.prevalence <- m.samp.prev.params %>%
-    group_by(category, property, iteration) %>%
-    spread(parameter, val) %>%
-    rowwise() %>%
-    mutate(
-      a = mean*sampleSize,
-      b = (1-mean)*sampleSize,
-      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
-      ) %>%
-    ungroup()
-```
-
-```{r}
-example.generics.properties <- c("dont eat people", 
-                      "carry malaria", 
-                      "lay eggs", 
-                      "are female",
-                      "have spots")
-```
-
-```{r gen-prev-dists, eval=F}
-gen.prev.dists <- bind_rows(
-  d.prev %>% 
-  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
-  filter(sentence %in% example.generics) %>%
-  mutate(prevalence = prevalence / 100,
-         src = 'data') %>% 
-    select(-workerid, -trial_type),
-  m.samp.prevalence %>% 
-    mutate(sentence = paste(category," " ,property, sep = "")) %>%
-    filter(sentence %in% example.generics) %>%
-    select(property, category, prevalence) %>%
-    rename(Category = category, Property = property) %>%
-    mutate(src = 'model'),
-  m.gen.refprev.predictive
-)
-
-ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
-  geom_density(aes( y = ..scaled.. ))+
-    #  stat_ecdf(size = 1)+
-  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-   #              position = position_dodge())+
-  facet_wrap(~Property + Category, nrow = 1)+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
 ```{r generic-model-scatters, cache = F}
-m.gen.endorse.rsa <- bind_rows(
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.fullmodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "generics_model"),
-  left_join(
-    d.gen.endorse.bayes,
-    m.gen.somemodel.endorsement %>%
-      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
-      ungroup() %>%
-      select(-type, -param)
-  ) %>%
-    mutate(src = "some_model")
-)
+load("cached_results/case1_modelPosteriors.RData")
+#d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt
 
 r2.gen.rsa.generics <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 4
+  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
+  "prediction_mean", "MAP_h", sigfigs = 4
 )
@@
 r2.gen.rsa.fixed <- compute_r2(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 4
+  d.gen.endorse.rsa.regression %>% filter(src == "Fixed semantics model"),  
+  "prediction_mean", "MAP_h", sigfigs = 4
 )
@@
 mse.gen.rsa.generics <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
-  "MAP", "MAP_h", sigfigs = 5
+  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
+  "prediction_mean", "MAP_h", sigfigs = 5
 )
@@
 mse.gen.rsa.fixed <- compute_mse(
-  m.gen.endorse.rsa %>% filter(src == "some_model"),  
-  "MAP", "MAP_h", sigfigs = 5
-)
-
-generics.endorsement.models <- bind_rows(
-  d.gen.endorse.regression,
-  left_join(
-    m.gen.endorse.rsa %>% 
-      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
-    d.gen.endorse.regression %>% 
-      select(sentence, Property, Category, prev_mean, cv_mean)
-  )
-) %>%
-  mutate(src = factor(src, levels = c( "some_model",
-                                      "generics_model",
-                                      "regression_Prev", 
-                                      "regression_Prev_Cuevalidity"
-                                     ),
-                      labels = c("Fixed semantics model",
-                                 "Uncertain semantics model",
-                                 "Prevalence",
-                                 "Cue validity + Prevalence"
-                                 ))) %>%
-  ggplot(., aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
+  d.gen.endorse.rsa.regression %>% filter(src == "Fixed semantics model"),  
+  "prediction_mean", "MAP_h", sigfigs = 5
+)
+
+generics.endorsement.models <- ggplot(d.gen.endorse.rsa.regression, 
+         aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                   y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
@@
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  scale_fill_viridis()+
   coord_fixed()+
@@
   facet_wrap(~src, nrow = 2)+
-  #theme(legend.position = "bottom")+
   guides(fill = F)
@@
 ```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-
-m.gen.fullmodel.prior.parameters <- m.samp %>%
-  filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(param, property, category, MAP) %>%
-  mutate(param = paste(param, category, sep = "_")) %>%
-  select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-gen.listener.predictions <- data.frame()
-
-# run interpreter model to generate "hypothetical intepretation" plots
-for (p in example.generics.properties){
- priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
- l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
- gen.listener.predictions <- bind_rows(
-   gen.listener.predictions, 
-   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
-    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
-   )
-}
-
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  mutate(Sentence = paste(category, property)) %>%
-  filter(Sentence %in% example.generics) %>%
-  mutate(property = factor(property))
-
-# m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-gen.inset.distributions <- bind_rows(
-  gen.listener.predictions %>%
-    mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
-    mutate(Parameter = "speakerBeliefs")
-)
 
@@
             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-gen.inset.distributions.refactored <- gen.inset.distributions %>%
-  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior",
-                                                  "speakerBeliefs"),
-                            labels = c("Prevalence Prior", 
-                                       "Prevalence Posterior given generalization", 
-                                       "Referent Prevalence")),
-         property = fct_relevel(property,
-                                "have spots", "lay eggs","carry malaria", 
-                                "are female", "dont eat people") )
 
@@
 
-#+ 
-    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
-
 fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
@@
           )
-# prow <- plot_grid( p1 + theme(legend.position="none"),
-#            p2 + theme(legend.position="none"),
-#            p3 + theme(legend.position="none"),
-#            p4,
-#            align = 'vh',
-#            labels = c("A", "B", "C"),
-#            hjust = -1,
-#            #nrow = 1,
-#            #rel_widths = c(1.2, 3, 2)
-#            rel_widths = c(1.2, 3, 1.05, 1.7)
-#            )
-
-# grid.arrange(generics.endorsement.spectrum, 
-#              generics.endorsement.models,
-#              generics.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-
 ```
@@
 fixed.threshold.generics.examples <- c("Tigers eat people.", "Peacocks have beautiful feathers.", "Lions lay eggs.", "Mosquitos attack swimmers.")
-fixed.threshold.model.examples <- m.gen.endorse.rsa %>% 
-  filter(src == "some_model", sentence %in% fixed.threshold.generics.examples)
+fixed.threshold.model.examples <- d.gen.endorse.rsa.regression %>% 
+  filter(src == "Fixed semantics model", sentence %in% fixed.threshold.generics.examples)
 
@@
 Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither. 
-It treats "Tigers eat people" (`r round(tigers.eat.people[[1,"MAP"]],2)` [`r round(tigers.eat.people[[1,"cred_lower"]], 2)`,
-`r round(tigers.eat.people[[1,"cred_upper"]], 2)`]) as good a statement as "Peacocks have beautiful feathers" (`r round(peacocks.feathers[[1,"MAP"]],2)` [`r round(peacocks.feathers[[1,"cred_lower"]], 2)`,
-`r round(peacocks.feathers[[1,"cred_upper"]], 2)`]), though participants seem to give a substantially weaker endorsement of the former ("Tigers eat people" = `r round(tigers.eat.people[[1,"MAP_h"]],2)` [`r round(tigers.eat.people[[1,"low"]], 2)`,
+It treats "Tigers eat people" (`r round(tigers.eat.people[[1,"prediction_mean"]],2)` [`r round(tigers.eat.people[[1,"prediction_ci_lower"]], 2)`,
+`r round(tigers.eat.people[[1,"prediction_ci_upper"]], 2)`]) as good a statement as "Peacocks have beautiful feathers" (`r round(peacocks.feathers[[1,"prediction_mean"]],2)` [`r round(peacocks.feathers[[1,"prediction_ci_lower"]], 2)`,
+`r round(peacocks.feathers[[1,"prediction_ci_upper"]], 2)`]), though participants seem to give a substantially weaker endorsement of the former ("Tigers eat people" = `r round(tigers.eat.people[[1,"MAP_h"]],2)` [`r round(tigers.eat.people[[1,"low"]], 2)`,
 `r round(tigers.eat.people[[1,"high"]], 2)`]; "Peacocks have beautiful feathers" = `r round(peacocks.feathers[[1,"MAP_h"]],2)` [`r round(peacocks.feathers[[1,"low"]], 2)`,
 `r round(peacocks.feathers[[1,"high"]], 2)`]).
-Similarly, "Lions lay eggs" is judged to be just as bad as "Mosquitos attack swimmers"(`r round(lions.lay.eggs[[1,"MAP"]],2)` [`r round(lions.lay.eggs[[1,"cred_lower"]], 2)`,
-`r round(lions.lay.eggs[[1,"cred_upper"]], 2)`, `r round(mosquitos.attack.swimmers[[1,"MAP"]],2)` [`r round(mosquitos.attack.swimmers[[1,"cred_lower"]], 2)`,
-`r round(mosquitos.attack.swimmers[[1,"cred_upper"]], 2)`], respectively), though participants rate the former as completely false (`r round(lions.lay.eggs[[1,"MAP_h"]],2)` [`r round(lions.lay.eggs[[1,"low"]], 2)`,
+Similarly, "Lions lay eggs" is judged to be just as bad as "Mosquitos attack swimmers"(`r round(lions.lay.eggs[[1,"prediction_mean"]],2)` [`r round(lions.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
+`r round(lions.lay.eggs[[1,"prediction_ci_upper"]], 2)`, `r round(mosquitos.attack.swimmers[[1,"prediction_mean"]],2)` [`r round(mosquitos.attack.swimmers[[1,"prediction_ci_lower"]], 2)`,
+`r round(mosquitos.attack.swimmers[[1,"prediction_ci_upper"]], 2)`], respectively), though participants rate the former as completely false (`r round(lions.lay.eggs[[1,"MAP_h"]],2)` [`r round(lions.lay.eggs[[1,"low"]], 2)`,
 `r round(lions.lay.eggs[[1,"high"]], 2)`]) while the latter is kind of true (`r round(mosquitos.attack.swimmers[[1,"MAP_h"]],2)` [`r round(mosquitos.attack.swimmers[[1,"low"]], 2)`,
@@
 The inferred optimality parameter in Eq.
-\ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
+\ref{eq:S1} is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`].
 

### 2018-02-06 paper/comgen-paper.Rmd
move code from case1 to analysis file, cache results

@@
 library(magick)
+library(viridis)
 theme_set(theme_few())

### 2018-02-08 paper/comgen-paper.Rmd
edits to discussion

@@
 Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
+People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ (formally, be in the set of things that have $f$) given that it is in $k$, which we will refer to as the **prevalence**.
+This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the **prevalence**.
+In particular, we define prevalence as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
-The properties also vary (e.g., having fur, causing jitters, typing). 
-Yet the mathematical description of the inductive inference is always given by the probability $p_{fk}$.
+The properties also vary (e.g., having fur, causing jitters, going to the gym).
+Yet the mathematical description of the inductive belief is always given by a probability $p_{fk}$.
 
 How does one acquire such an inductive belief?
-Observing instances of the category $k$ and noting how many of them have $f$ can support prediction to new instances when integrated with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
-For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
-Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
+If you observe creatures that *have two legs*, you might infer that all creatures of that kind have two legs.
+But not all properties have such strong projectibility or prevalence.
+Seeing a creature with *broken wings* tells you much less about other instances of the category having broken wings [@Nisbett1983].
 This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$
@@
 $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$
-
 Various attempts of this kind have been made before [e.g., @Cohen1999].
-We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
-$p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief.
+We distinguish our proposal from previous ones by emphasizing the predictive nature of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+<!-- $p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->
 
@@
 Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions is, in fact, simple, but underspecified. 
+We have argued that the core meaning of such linguistic expressions is simple, but underspecified. 
 To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
 
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite different from one another: generalizations about categories, events, and causes.
+As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
 <!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
-We have been able to formalize a unified, core meaning using the underlying scale of *prevalence*.
+We have formalized a unified, core meaning using the underlying scale of predictive probability or *prevalence*.
 We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
-Our framework naturally accounts for a number of classic examples from the semantics of *generic language* (Expt. 1).
-We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
-Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is causally related to their endorsement of statements of genericity (Expt. 3).
-In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below
+Our framework naturally accounts for a number of logically puzzling category generalizations, or *generics* (Expt. 1).
+We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
+Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
+<!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->
+
+In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
+Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
+The endorsement model, which we use to generate predictions for our three case studies, is a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
+The interpreter model is a "literal listener", who updates its beliefs by averaging over plausibly thresholds given prior knowledge and the simple truth-functional meaning.
 
 <!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
-The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments.
-The formal Bayesian model provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (operationalized in terms of the prior).
-This formal separation is key improvement beyond previous accounts. 
-Previous accounts have either tried to account for context-sensitivity by baking it into the semantics [e.g., @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
-Our model formalizes both the semantics of generalizations and the structure of world knowledge; this separation allows us to articulate a route for precise quantitative inlfuence of conceptual structure on generic language [c.f., @Leslie2008].
+<!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
+The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (the prior).
+This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
+Our model formalizes a simple semantics for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
+That is, we provide a route for precise quantitative influence of conceptual structure on generic language by way of shared background knowledge between speakers and listeners [c.f., @Leslie2008].
+In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
+
+Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations.
+That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding speaker beliefs or listener prevalence distributions, which can occur for multiple reasons (e.g., by changing the comparison class).
+We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
+In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
+
 <!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
 -->
-We do this without having to posit that conceptual structure and semantics are one in the same.
-This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
+<!-- We do this without having to posit that conceptual structure and semantics are one in the same. -->
+<!-- This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
+-->
 <!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->
@@
 
-In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
 <!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->
 
-## A step towards communicating generalizations
 <!-- Implicit aspects of language use: The comparison class and question under discussion -->
 
-In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
-Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
-Our endorsement model, which we use to generate predictions for our three case studies, can be seen as a special case of a speaker model who can only produce one of two utterances: the generalization or silence.
-Our interpreter model can be seen as a kind of "literal listener", who does not do any sort of pragmatic or communicative reasoning. 
-Our modeling framework could thus naturally be extended to more faithful models of pragamtic communication of generalizations, to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task.
-The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.
-
-### The comparison class
+<!-- to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task. -->
+<!-- The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.  -->
+
+## The comparison class
 
@@
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(h)$ is constructed with respect *the comparison class* $C$: $P_C(h)$.
+Thus, the prevalence prior $P(h)$ is constructed with respect some comparison class $C$: $P_C(h)$.
 
@@
 Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
-Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.
-
-The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. 
-Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object). 
-We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017].
-Even if interlocutors coordinate on a particular comparison class, they may disagree about the prevalences for other *other categories* in the class.
-That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how *other forces* (e.g., plate tectonics) influence the climate or how often other social categories (e.g., neo-nazis) commit acts of terrorism.
-Indeed, we saw in Expt. 3 how the statistics of other causes can influence the endorsement of a single generalization (e.g., "Herb C makes animals sleepy").
+However, like the semantics of generalizations, the other entities or categories that comprise the comparison class are underspecified.
+
+Uncertainty about the comparison class adds yet more flexibility to generalizations.
+Even if interlocutors coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other *other categories* in the class.
+That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how other forces (e.g., plate tectonics) influence the climate or how often other categories (e.g., neo-nazis) commit acts of terrorism.
+In Expt. 3, we demonstrated the influence of other categories on endorsement of a generalization.
 Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.
 
-### Question under discussion
-
-Rational models of communication, of the kind we have developed in this paper, are required to make explicit a speaker's assumptions about the goal of communication, otherwise known as the Question Under Discussion or QUD [@roberts1996qud].
-We have made a very minimalist assumption, that the goal of communication (at least, for purposes of endorsement) is the prevalence.
-However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD.
-For example, the comparison classes used in our case studies were with respect to the target category (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUDs of "*what* has feature?", "*who* does action?", or "*what* causes effect?".
-Were the QUDs to be reversed (e.g., "what features does category have?", "what does person do?", "what effects does cause bring about?"), the comparison classes would need to be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
-
-The QUD is thus another layer of flexibility that makes understanding generalizations so challenging.
-The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus].
+Interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but *how* the comparison class should be constructed.
+The comparison classes used in our case studies were with respect to the target *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit Question Under Discussion [QUD; @roberts1996qud] of "*what* has feature?".
+Were the QUD to be reversed (e.g., "what features does category have?"), the comparison classes would need to be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
+The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus], giving rise to multiple distinct comparison classes.
 The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
 In this work, we focused on category-wise comparison classes for methodological convenience.
-<!-- In our three case studies, the *category-wise* comparison classes are fixed to *other people*, *other causes*, or *other kinds*, even as we vary the features. -->
-<!-- *Feature-wise* comparison classes are likely to be modulated by the feature itself. -->
-Future work should investigate the feature-wise reading of generalizations, and explore what cues listeners adopt for one or the other interpretation.
-
+Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.
+
+<!-- Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.  -->
+<!-- The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. -->
+<!-- Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object).  -->
+<!-- We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017]. -->
+
+<!-- ### Question under discussion -->
+
+<!-- However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD. -->
+<!-- The QUD is thus another layer of flexibility that makes understanding generalizations so challenging. -->
 <!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
@@
 
+Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the goals of communication, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud].
+Our simple endorsement model assumes that the goal of communication is the prevalence.
+This idealization will surely be elaborated in richer communicative contexts. 
+It is noteworthy, however, when using a structured model of the prior (e.g., a mixture model), as we have used throughout this paper, that the endorsement model makes almost identical predictions if the QUD is assumed the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
+
 ## Structured prior knowledge
@@
 Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
-Prasada has argued for a distinction between \emph{characteristic} properties (e.g., "Diapers are absorbent") and \emph{statistical} properties (e.g., "Diapers are white").
-Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generic.
-Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
+Prasada has argued for a distinction between *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white").
+Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread.
+Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring. 
 Where in the probability-based semantics could such conceptual distinctions come into play?
 
-Our approach makes the strong claim that beliefs about predicted prevalence are the connective tissue between conceptual knowledge and the semantics of generic language.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding prevalence distributions.
-Modulations of prevalence distributions can occur for multiple reasons (e.g., by changing the comparison class) as described in the previous section.
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
-In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
-
-It is natural to ask how prevalence might reflect conceptual knowledge.
-We found that empirical prevalence distributions are structured in a mixture-model that plausibly reflects intuitions about causal mechanisms underlying different properties; the differences in shape of these distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992].
+We found that empirical prevalence distributions are best modeled as a mixture-model. 
+Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
+It is likely that conceptual knowledge is far-richer than our simple two-component mixture-model, though a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our data.
+<!-- influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992]. -->
 Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore whether probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.
+Future work will be needed to explore how probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.
 
@@
 In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
-We make the important distinction that probability can be more general than frequency, and in our account, underlies speakers' subjective, predictions about the future and is subject to top-down moderator.
-Expts.
-2c \& 2d that showed using participants' \emph{predictions} about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
-
-Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probabilities [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the *language used* to convey *explicit probabilties* [cf., @Levinson1995].
+We make the distinction that what is communicated is probability not frequency.
+Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+<!-- Expts.
+2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
+-->
+
+Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995].
 Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
@@
 The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to language [@Gweon2010; @Dewar2010].
+Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].
 
@@
 
-## Acquiring the language of generalizations
-
-The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers.
-Generic language is one of the earliest emerging forms of complex, compositional language.
-Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008].
-Generics are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004],
-
-What is perhaps surprising from a formal perspective is that generic language is far from trivial to characterize. 
-If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...).
-The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
-This has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is not approrpriate for generic language [@Leslie2008].
-
-We think rejecting the normal tools of truth-functional semantics for generics would be throwing out the baby with the bathwater.
-When we consider the acquisition problem, there are three aspects of meaning that a child must acquire for a truth-functional quantifier semantics $\denote{u}(h, \theta) = \{h :h > \theta\}$: 
-(1) the dimension being described (i.e., the probability $h$),
-(2) the polarity of the relation (i.e., $>$ vs. $<$), and 
+## Acquiring the language of generalization
+
+<!-- The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers. -->
+<!-- Generic language is one of the earliest emerging forms of complex, compositional language. -->
+<!-- Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008]. -->
+
+Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common they are in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
+<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
+<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
+Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is in fact *easier* to formalize, but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
+<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
+<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
+<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
+-->
+This asymmetry between the simplicity of the formal theory and the age acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generic language [@Leslie2008].
+
+Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
+The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three aspects of meaning: 
+(1) the *dimension* being described (i.e., the probability $h$),
+(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
 (3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon learning the meaning has to do with probability and that it stands in a positive relation to some standard $\theta$, a rational learner would adopt a prior distribution over possible thresholds $\theta$, as a form of *lexical uncertainty* [@Bergen2016].
-This prior could then be updated with more data to acquire a fixed meaning.
-However, for the generic statement, the language learner is done once she acquires aspects (1) and (2).
-In our model, $\theta$ is left underspecified in the semantics and is inferred in context.
-Thus, in this sketch of an acquisition model, a child would first acquire generic language, and from that, carve out more precise meanings for quantified language.
-
-The uniform prior over the threshold $\theta$ in the truth-functional threshold semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the prevalence $h$ *itself*:
-
-$$
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-$$
-This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better the utterance", or simply "more is better") is perhaps the simplest semantics one could imagine.
+Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
+Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
+However, for generalizations, no fixed threshold is required; the language of generalization is acquired once aspects (1) and (2) are learned.
+<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
+This informal analysis predicts that a child would first acquire generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
+
+There is a secondary argument for why the semantics we posit presents an easy learning problem.
+<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
+-->
+Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree, in this prevalence $h$ itself: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
+This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
 The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
@@
 
-In our experiments, we have tried to include classic, philosophically puzzling examples of generalizations in language in addition to crafting novel stimuli that provide stricter tests of the main hypothesis.
-In this section, we consider some other previously-discussed troubling examples of generalizations and sketch out arguments rooted in our theoretical framework to demonstrate how our theory could account for these cases.
+We aimed to balance two competing goals in designing our experimental stimuli: (1)  including familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model.
+In this section, we discuss how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
 We consider the five following examples:
 
-1. Books are paperbacks.
-2. Mary handles the mail from Antarctica.
-3. Supreme Court Justices have even social security numbers.
-4. Elephants live in Africa and Asia.
+1. Mary handles the mail from Antarctica.
+2. Supreme Court Justices have even social security numbers.
+3. Elephants live in Africa and Asia.
+4. Books are paperbacks.
 5. Women are submissive.
 
-Sentence (1), strikes hearers as *odd* or perhaps *false*, despite the vast majority of books being paperback. 
+Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
+That is, the statement "Mary has handled mail from Antarctica" is false.
+Sentence (1) is still thought to be true despite zero actual instances of the event.
+We think (1) is a boundary case of generalizations expressing predictive probabilities, which we elucidated in Expt. 2c.
+In in that study, we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
+We expect the same to be true here, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
+Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
+
+Our focus on predictive probability makes even new prediction about some classic puzzles.
+Sentence (2) is the conceptual opposite of sentence (1).
+Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
+Sentence (2) is still considered false, every though the property holds in 100\% of the category [@Cohen1999].
+We predict this phenomenon is the result of abstract, intuitive theories guiding us to reject observed frequencies in forming our subjective probabilities.
+That is, because observers strongly believe selection for the Supreme Court is not influenced by one's social security number, speakers would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
+Then, given that the all professions would have roughly the same probability of having employees with even social security numbers, Sentence (2) would be similar to "Birds are female". 
+However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
+history had a social security number which was a *prime number*---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
+That is, we predict there are situations where statements like (2) could be considered felicitious generalizations.
+
+Understanding how a semantic representation *composes* is another critical test for a theory of generalizations in language.
+@Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
+Stastistical account of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
+However, this is the only interpretation if the generalization is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
+Our theory does not provide a fixed semantics for the generalizations, but an uncertain one, which can be updated as more information comes in.
+In fact, with prior knowledge weighting against the existence of *international elephants* and without any further semantic assumptions, our model infers that some elephants live in Africa and others live in Asia (and they are different elephants).^[
+  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
+]
+Importantly, the model believes that most lives in Africa, when it only hears that "Elephants live in Africa", and only later revises it's beliefs to a weaker "some"-like interpretation after hearing they live in Asia as well.
+Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise interpretation of single utterances.
+
+<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
+-->
+<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
+<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
+
+<!-- With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
+1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
+-->
+<!-- When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement,  -->
+<!-- This is possible because our model has uncertainty over the semantic thresholds in the generic claim. -->
+
+Sentence (4), strikes hearers as *odd* or perhaps *false*, despite the vast majority of books being paperback. 
 Why?
@@
 
-Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
-That is, the statement "Mary has handled mail from Antarctica" is false.
-Sentence (2) is still thought to be true despite zero actual instances of the event.
-We think (2) is a boundary case of generalizations expressing predictive probabilities, which we elucidated in Expt. 2c.
-In in that study, we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
-We expect the same to be true here, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
-Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
-
-Our focus on predictive probability makes even new prediction about some classic puzzles.
-Sentence (3) is the conceptual opposite of sentence (2).
-Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (3) is still considered false, every though the property holds in 100\% of the category [@Cohen1999].
-We predict this phenomenon is the result of abstract, intuitive theories guiding us to reject observed frequencies in forming our subjective probabilities.
-That is, because observers strongly believe selection for the Supreme Court is not influenced by one's social security number, speakers would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Then, given that the all professions would have roughly the same probability of having employees with even social security numbers, Sentence (3) is again similar to "Birds are female". 
-However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number*---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
-That is, we predict there are situations where statements like (3) could be considered felicitious generalizations.
-
-Understanding how a semantic representation *composes* is another critical test for a theory of generalizations in language.
-@Nickel2008 suggests Sentence (4) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Stastistical account of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
-However, this is the only interpretation if the generalization is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-Our theory does not provide a fixed semantics for the generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with a strong constraint against the existence of *international elephants* but with any further semantic assumptions, our model infers that some elephants live in Africa and other lives in Asia.^[
-  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-]
-Importantly, the model believes that most lives in Africa, when it only hears that "Elephants live in Africa", and only later revises it's beliefs to a weaker "some"-like interpretation after hearing they live in Asia as well.
-Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise interpretation of single utterances.
-
-<!-- Instead, the statement should be glossed as *some elephants live in Africa* and *some elephants live in Asia*, and perhaps taken collectively, *most elephants live in either Africa or Asia* [@Nickel2008].
--->
-<!-- This reading of (3) gives it the same semantic content as two statements: "Elephants live in Africa. Elephants live in Asia." -->
-<!-- Our model is able to flexibly accomodate this statement by having uncertainty about the truth-conditional threshold.  -->
-
-<!-- With reasonable assumptions about the prior (e.g., that *lives in* is similar to other biological properties from Expt.
-1a and assuming international elephants are unlikely *a priori*), upon the hearing "Elephants live in Africa", our model will infer that most elephants live in Africa.
--->
-<!-- When the model then hears "Elephants live in Asia", the model updates its beliefs to accomodate this second statement,  -->
-<!-- This is possible because our model has uncertainty over the semantic thresholds in the generic claim. -->
-
 Finally, sometimes a property is widespread relative to other kinds or groups, and it might be so systemic that we would believe it to be the case in the future, but speakers still might find it avertise to actually endorse the generalization.
@@
 
-To our knowledge, the present papaer presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
+To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
 A number of other theories of genericity have been proposed in the linguistics and psychological literatures.
-We now turn to situating our account with respect to these previous theories.
+<!-- We now turn to situating our account with respect to these previous theories. -->
 <!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
 -->
-Semantic theories fall into one of two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., *there is something about being K which causes it to F*).
+These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., *there is something about being K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-### Statistical accounts
-
-#### Relative and absolute generics
-
-Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means.
-He partitions generics into two types: *absolute* and *relative* generics.
-*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
-Roughly speaking, "Dogs have four legs" is true because a given dog is more likely than not to have four legs. 
-*Relative generics* depend upon an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
-"Mosquitos carry malaria" is a relative generic: it is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
-
-Our uncertain-threshold model deviates from Cohen's account in two primary ways.
-First, though his theory is framed in terms of probabilities, it still utilities a fixed threshold semantics and thus is only able to make predictions about what is "true" and what is "false".
-In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement.
-Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each.
-We used examples of both in our stimuli (Expt.
-1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".^[
-  For a related theory that aims to do away with the distinction between "absolute" and "relative"   adjectives, see @Lassiter2015.
-]
-
-We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$). 
-For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
-Therefore, "Robins lay eggs" is evaluated as an *absolute generic* because only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery behind Cohen's domain restriction (i.e., what comrpises $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
-  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.
-]
-However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
-Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-
-#### "Normal" accounts
-
-The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
-For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
-However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
-Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
-We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations. 
-Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
-
-#### Underquantification
-
-A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
-In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analagous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
-Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
-This distinction is relevant for the acquisition of the language of generalizations; we do not think that quantified relations (e.g., "Some", "All") are in any way primary or special. 
-<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
--->
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
-
-#### Generic as indexical
-
-@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
-The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
-Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
-We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
 
@@
 That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
-If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar".
+<!-- If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar". -->
 
@@
 For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
-Leslie's "default mode" comes equipped with the ability to single-out \emph{striking properties} (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
+Leslie's "default mode" comes equipped with the ability to single-out *striking properties* (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
 Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about.
@@
 
+### Statistical accounts
+
+#### Relative and absolute generics
+
+Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
+Cohen treats generics as comprising two qualitatively different types: *relative* and *absolute* generics.
+<!-- For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means. -->
+*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
+That is, if a particular instance is more likely than not to have the feature, then the absolute generic is true. 
+By contrast, *relative generics* are true based on a comparison to an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
+"Mosquitos carry malaria" is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
+
+In our model, we do not draw a *relative* vs. *absolute* distinction, instead treating all generics as relative. 
+Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge.^[
+  For a related theory argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
+]
+Further, though Cohen's theory is framed in terms of probabilities, it is a fully semantic, fixed-threshold account which only makes deterministic predictions about what is true and what is false.
+In contrast, we posit an uncertain threshold which is resolved through a Bayesian interpretation model; our theory is a joint semantic--pragmatic theory.
+
+<!-- In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement. -->
+<!-- Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each. -->
+<!-- We used examples of both in our stimuli (Expt.
+1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".
+-->
+
+<!-- We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
+-->
+<!-- His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).  -->
+<!-- For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...). -->
+<!-- Therefore, "Robins lay eggs" is evaluated as an *absolute generic* because only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+-->
+<!-- The inferential machinery behind Cohen's domain restriction (i.e., what comrpises $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[ -->
+<!--   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.
+-->
+<!-- ] -->
+<!-- However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+-->
+<!-- Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.  -->
+
+<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
+
+#### "Normal" accounts
+
+The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
+For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
+However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
+Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
+We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations. 
+Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
+
+#### Underquantification
+
+A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
+In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
+The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analagous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
+This distinction is relevant for the acquisition of the language of generalizations; we do not think that quantified relations (e.g., "Some", "All") are in any way primary or special. 
+<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
+-->
+Additionally, by using a vague, underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
+
+#### Generic as indexical
+
+@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
+The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
+Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
+We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
+
 # Conclusion

### 2018-02-08 analysis/case2-habituals.Rmd
refactor code in first half of habituals

--- 2017-12-22 paper/case2-habituals.Rmd
@@
-# Case Study 2: Habitual Language
-
-<!-- THINK ABOUT: -->
-<!-- Kelley, H. H. (1973). The processes of causal attribution. American psychologist, 28(2), 107-128. -->
-<!-- Orvis, B.
-R., Cunningham, J.
-D., & Kelley, H.
-H.
-(1975).
-A closer examination of causal inference: The roles of consensus, distinctiveness, and consistency information.
-Journal of Personality and Social Psychology, 32(4), 605-616.
--->
-
-The event of Mary smoking at 2:30pm on January the 24th is an instance of a kind of event: *Mary smoking*. 
-Just as with categories, generalization can occur over events of a particular type.
-When expressed in language, these generalizations take the form of *habitual language*: "Mary smokes".
-
-Events are a broad class of entities. 
-In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes").
-Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
-When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
-Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-
-To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
-We take event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).
-For the generalization "Mary smokes", instances of the category being generalized are *instances of Mary* and if for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
-We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarttes; Expt. 2a).
-We then measure endorsements of habitual statements while manipulating the *referent-prevalence*  (Expt. 2b), and use our computational model to predict habitual endorsements. 
-<!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-By describing novel characters to participants, we are able to directly the manipulate the *referent-prevalence* (rate), which we were unable to do for generalizations about familiar categories.
-<!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
--->
-
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
-Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
-Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
-We extend our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
-We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
-
-<!-- Young children can use actors' behaviors to make inferences about what the actors are like more generally [e.g., @Repacholi1997; @Seiver2013]. -->
-<!--  explored 5th to 12th graders' responses to open ended probes such as "Tell us about your school / family".  -->
-<!-- A surprisingly large number of utterances (over 85\% in their study) were about people, and roughly two-thirds of those utterances used action verbs (e.g., "My brother works part-time at the restaurant.").
--->
-
-<!-- This set of experiments is organized as follows. -->
-<!-- In the **Event Prior Elicitation** study (Expt. 1), -->
-<!-- In the **Endorsing Habitual Language** experiment (Expt.
-2), we introduce a separate participants to different characters, each of whom have done some action with some frequeny (e.g., *In the last month, John ran 3 times*), and ask them to judge the corresponding generalization (e.g., *John runs*).
--->
-<!-- In the **Interpreting Habitual Language** experiment (Expt.
-3), we invert this paradigm, supplying participants with the generalization (e.g., *John runs*) and ask them to juge how often the person does some action (e.g., answer the question: *How often do you think John runs?*).
--->
-
-<!-- We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data. -->
-<!-- Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
--->
-<!-- After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.  -->
-<!-- Finally, having validated a communicative theory of genericity, we probe the theory in more detail in Experiment 4 by asking whether past frequency or predictive probability is what is being communicated.
--->
-
-<!-- The internal structure of particular events can differ in substantial ways. -->
-<!-- For example, events differ in their expected duration. -->
-<!-- For example, the event of *smoking a cigarette* plausibly takes between 5 - 10 minutes, while the event of *wearing socks* probably lasts for several hours. -->
-<!-- We take as a starting point the fact that events can be segmented and aggregated; the relevant dimension becomes the frequency with which the event occurs. -->
-
-## Experiment 2a: Measuring the prevalence prior for events
-
-In order to generate model predictions for corresponding habitual statement, we first elicit the prior distributions over rates for different events.
-For language about the behaviors of people, $P(p_f)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
-We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1 .
-In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not.^[
-  In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-  We assume here a simple structure so as to not make the specification of the prior overly complex.
-]
-With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
-We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people).
-We will aassume for simplicity that people who have never done the action before will rarely or never do the action.
-
-### Method
-
-#### Participants
-
-We recruited 40 participants from Amazon's Mechanical Turk.
-Participants were restricted to those with U.S. IP addresses and who had at least a 95\% work approval rating.
-The experiment took on average 12 minutes and participants were compensated \$1.25 for their work.
-
-#### Materials
-
-To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
-For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. *writing* poems vs. novels).
-The events were chosen to intuitively cover a range of likely frequencies.
-In total, thirty-one events were used.
-For a full list the stimulus set, see Appendix D.
-
-#### Procedure
-
-For each event, participants were asked two questions, with different dependent measures. 
-These questions were designed to measure the two central components of the prevalence prior model.
-We anticipated there to be different beliefs about the rates and relative proportions of peopel depending on whether an actor is male or female, so we asked about both genders separately.
-
-\begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
-
-Participants responded ``N out of every J.'' by entering a number for N and choosing J from a drop-down menu (options: \{1000 - 10 million\}, incremented by 10x; default setting: 1000).
-
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
-
-Participants responded ``M times in K.'' by entering a number for M and choosing K from a drop-down menu (options: \{week, month, year, 5 years\}; default setting: year).
-\end{enumerate}
-
-For example, one set of prompts read: "How many women have smoked cigarettes before?"; "For a typical woman who has smoked cigarettes before, how frequently does she smoke cigarettes?"
-Participants answered both questions for both genders on each slide (4 questions total per slide, order of male / female randomized between-subjects), and every participant completed all 31 items in a randomized order.
-The difference in meaning of these questions was explained to participants on an instructions page before the experimental trials and tested for recall on a subsequent trial.
-Participants responded to this attention check by selecting an option from a drop-down menu consisting of four options (one correct description of the questions and three distractors).
+---
+title: "Analysis for Case 2 (habituals)"
+output: html_notebook
+---
+
+```{r libraries, cache = F}
+library(papaja)
+library(formatR)
+library(rwebppl)
+library(xtable)
+library(tidyverse)
+library(forcats)
+library(langcog)
+library(coda)
+library(ggthemes)
+library(ggrepel)
+library(jsonlite)
+library(gridExtra)
+library(lme4)
+library(knitr)
+library(kableExtra)
+library(cowplot)
+library(magick)
+library(viridis)
+library(tidyboot)
+theme_set(theme_few())
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+logmeanexp <- function(x){
+  x.num <- as.numeric(x)
+  xstar = max(x.num)
+  return(xstar + log(mean(exp(x.num - xstar))))
+}
+
+compute_r2 <- function(df,v1, v2, sigfigs = 3){
+  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
+}
+
+compute_mse <- function(df, v1, v2, sigfigs = 3){
+  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
+}
+
+project.path <- "../"
+options("scipen"=10) 
+```
+
+# Experiment 2a: Prevalence priors
 
@@
        )
+
+df.hab.priors.filtered.tidy <- bind_rows(
+   d.hab.priors.filtered %>%
+      select(item, starts_with("annualRate")) %>%
+      gather(gender, val, -item) %>%
+      mutate(gender = gsub("annualRate_", "", gender),
+             logval = log(val),
+             measurement = "annualRate"), 
+   d.hab.priors.filtered %>% 
+      select(item, starts_with("mixture")) %>%
+      gather(gender, val, -item) %>%
+      mutate(gender = gsub("mixture_", "", gender)) %>%
+      rowwise() %>%
+      mutate(val = ifelse(val == 1, 0.9999, 
+                          ifelse(val == 0, 0.000001, val)),
+             measurement = "mixture_avoidedEnds",
+             logval = val)
+)
+
+df.hab.priors.filtered.summary <- df.hab.priors.filtered.tidy %>%
+  group_by(item, gender, measurement) %>%
+  tidyboot_mean(column = logval)
 ```
@@
 d.hab.priors.samples <- data.frame()
-for (i in 1:10){
+for (i in 1:100){
 
@@
 }
-save(rs.habituals.bda.prior, 
-     file = paste(project.path,  "models/habituals/results/", 
-                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
-                  ".RData", sep = ""))
+# save(rs.habituals.bda.prior, 
+#      file = paste(project.path,  "models/habituals/results/", 
+#                   "habituals-prior-", n_samples, "_burn", n_samples/2 , 
+#                   ".RData", sep = ""))
 
@@
 rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category) %>% distinct())
-
-figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide %>%
-                                            mutate(Gender = factor(Gender, levels = c("male", "female"))),
+          d.hab.priors %>% select(item, category) %>% distinct())  %>%
+                mutate(Gender = factor(Gender, levels = c("male", "female")))
+
+figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide,
        aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
@@
                   aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
+```
+
+```{r priors_posteriorPredictive_measurementSpace}
+rs.habituals.bda.posterior.predictive.measurementSpace <- left_join(
+  rs.habituals.bda.prior.summary %>%
+    rename(measurement = Variable,
+           gender = Gender) %>%
+    mutate(measurement = factor(measurement, 
+                        levels = c("mix","stableFreq"),
+                        labels = c("mixture_avoidedEnds", "annualRate"))),
+  df.hab.priors.filtered.summary
+  )
+
+ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
+       aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+           y = empirical_mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_point()+
+  facet_wrap(~measurement, scales = 'free')+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)
+
 ```
@@
 
-figure.habituals.priors.marginals <- bind_rows(
+habituals.priors.marginals <- bind_rows(
   d.hab.priors.samples %>% 
@@
     mutate(src = 'model')
-  ) %>%
+)
+
+save(habituals.priors.marginals, rs.habituals.bda.posterior.predictive.measurementSpace,rs.habituals.bda.prior.summary.wide, file = "../paper/cached_results/case2_priors_parametersPredictives.RData")
+
+figure.habituals.priors.marginals <- ggplot(habituals.priors.marginals %>%
   filter(item %in% example.habituals,
@@
   mutate(item = factor(item, levels = example.habituals),
-         gender = factor(gender, levels = c("male", "female"))) %>%
-ggplot(. , aes( x = val, color = gender))+
+         gender = factor(gender, levels = c("male", "female"))), 
+  aes( x = val, color = gender))+
   geom_density(size = 0.8, aes( y = ..scaled.. ))+
@@
 
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Prevalence priors for events (Expt.
+```{r}
+figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
+       aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+           y = empirical_mean, ymin = ci_lower, ymax = ci_upper, color = gender))+
+  facet_wrap(~measurement, scales = 'free', nrow = 2)+
+  scale_color_solarized()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+    geom_label_repel(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+                    filter(item %in% example.habituals, gender == "female"), 
+                  inherit.aes =F,
+                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 3)+
+  geom_point()+
+  coord_fixed()+
+  xlab("Model posterior predictive")+
+  ylab("Empirical means")+
+  theme(legend.position = c(0.86, 0.09))
+
+figure.habituals.priors.marginals <- ggplot(habituals.priors.marginals %>%
+  filter(val > -4.9) %>%
+  mutate(gender = factor(gender, levels = c("female", "male"))), 
+  aes( x = val, color = gender, lty = src))+
+  geom_density(size = 0.4, aes( y = ..scaled.. ))+
+  facet_wrap(~item, nrow = 4)+
+  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+               filter(gender == 'male', measurement == "% people who have done action before"), 
+            aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = MAP),
+              fill = "#268bd2", 
+            color = 'black',
+             inherit.aes = F)+
+  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+               filter(gender == 'female', measurement == "% people who have done action before"), 
+            aes(xmin = -4.25, xmax = -3.75,
+                                            ymin = 0, ymax = MAP),
+            fill = "#cb4b16",
+            color = 'black',
+             inherit.aes = F)+
+  scale_color_solarized()+
+  xlab("Frequency")+
+  ylab("Scaled probability density")+
+  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
+  theme(legend.position = c(0.93, -0.1),
+        legend.title = element_blank(),
+        legend.box = 'vertical',
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1),
+        legend.margin=margin(t=0, r=0, b=-0.25, l=0, unit="cm"),
+    strip.text = element_text(size = 7))+
+  scale_x_continuous(
+      limits = c(-5, 8),
+      breaks = c(-5, 0, 2.5, 4, 5.9),
+      labels = c("almost never", "annually", "monthly", "weekly", "daily")
+      )+
+  guides(color = F)
+```
+
+```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, fig.cap="Prevalence priors for events (Expt.
 2a).
-Left: Mean mixture parameter and mean stable frequency parameter for 31 events.
-Right: Inferred priors on frequencies from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the prior mixture model.", cache = F}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
-```
-
-<!-- Every response for a frequency of a person doing an action is a sample from $P_{event}(h)$. -->
-<!-- We first transformed all responses onto the same scale of "times per year" (assuming 52 weeks per year; 12 months per year). -->
-<!-- An empirical distribution can be found by making a histogram of these responses.  -->
-<!-- The empirical distributions follows a kind-of log-normal distribution, with the additional feature of having a substantial probability mass at the frequency of 0 (for those individuals who never do the action).
--->
-<!-- We thus log-transformed the empirical data.  -->
-<!-- To avoid values of -Infinity, we set the responses of 0 to mean roughly "once every twenty years". -->
-
-<!-- We took the log-transformed (and "-Infinity"-adjusted) raw data and binned each response to the closest bins on a grid with binwidth of 0.5 in the log-"times per year" scale. -->
-<!-- This yields a grid of 23 points with frequencies ranging from "once every twenty years" (log-frequency = -3) to "twenty times per day" (log-frequency = 9). -->
-
-### Data analysis and results
-
-All participants responded correctly to both questions in the attention check trial, so all collected data was used in the analysis.
-Question 1 elicits the proportion of people who have done an action before. 
-We rescale this to be a number between 0 and 1, and assume it was generated from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma, \xi)$. 
-Question 2 elicits the rate with which a person (who has done the action before) does the action.
-We model this as generated by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu, \sigma)$.
-Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
-
-The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter):
-We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2}(`r  n.items.habituals.prior.modeling`) = `r round(with(rs.habituals.bda.prior.summary.wide, cor(mix_mean, sfreq_mean)),2)`$).
-Items in our data set that tend to be more popular actions also tend to be more frequent actions (e.g., \emph{wears socks}) and visa-versa (e.g., \emph{steals cars}), though there are notable exceptions (e.g., \emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done particularly often).
-This diversity is relevant because the speaker model (Eq.
-\ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
-
-To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
-The only difference is that we estimate the mixture component $\phi$ directly from responses to Question 1. 
-We assume that those who have not done the action before will probably not do the action in the future. 
-With these assumptions, the prevalence distribution is given by:
-
-\begin{align}
-\phi & \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1}) \nonumber \\ 
-\ln h & \sim \begin{cases}
-		\text{Gaussian}(\mu_{Q2}, \sigma_{Q2}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
-		\end{cases}
-\end{align}
-
-Figure \@ref(fig:habituals-prior-figure) (right) shows example reconstructed priors.
-In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
-First, it smooths effects that are clearly results of the response format. 
-For example, a very common rating for certain events is \emph{1 time per year}.
-Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure.
-Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
-
-<!-- Analagous to what was done with the prior knowledge for generic language, from the inferred parameters and the assumed functional forms (i.e., the mixture distribution), we can generate $P(h)$ modeled as a mixture of individuals who have done the action before and those that haven't.
--->
-<!-- That is, $P(h)$ was constructed by sampling $\lambda$ as follows: -->
-
-<!-- We first sample a mixture weight $\phi$ from the posterior distribution over the mixture component hyperparameters $\text{Beta}(\gamma_{mixture}, \xi_{mixture})$, inferred from the first question of the experiment.
--->
-<!-- We then flip a coin weighted by $\phi$: $\text{Bernoulli}(\phi)$. -->
-<!-- If the coin comes up heads (i.e., $\text{Bernoulli}(\phi) = \textsc{true}$), a frequency $h$ is sampled from the distribution of people who have done the action before.
-This distribution is a log-normal distribution with parameters inferred from the second question of the experiment $\ln h \sim \text{Gaussian}(\mu_{stable}, \sigma_{stable})$.
--->
-<!-- If the coin comes up tails, a frequency $h$ is sampled from the distribution of people who have not done the action before. -->
-<!-- We make the simplifying assumption that people who have not done the action before will probably never do the action (expected frequency: once every hundred years). -->
-
-<!-- Some items show substantial differences between the genders (e.g., \emph{wears a bra}) and some show subtle differences (e.g., \emph{watches professional football}). -->
-<!-- Recall that the prior distributions $P(h)$ used in the RSA are with respect to an alternative class of entities (e.g., other individuals).  -->
-<!-- It's possible that when evaluating habitual statements under certain contexts, $P(h)$ is with respect to either *all people* or *people of the same gender*.  -->
-<!-- For example, are the frequency conditions by which a man would qualify to "watch  football" (habitually) different than those by which a woman would qualify to "watch  football"? -->
-<!-- We explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2b, for select items with priors that differ substantially by gender. -->
-
-<!-- We analyze the data using a Bayesian approach to allow for a consistent integration into the computational model. -->
-<!-- The data we would like to explain are: the bins $n_i \in \{-3, -2.5, ..., 8.5, 9\}$ that participants gave in response to items $i \in \{1, ..., 27\}$. -->
-<!-- The data is explained as a function of subjective beliefs $P_i$, with $P_{ij}$ being participants' (as a collective) belief about the relative likelihood for bin $j$ for item $i$.  -->
-<!-- Each $P_i$ defines a likelihood for our data, assuming an appropriate linking function. -->
-
-<!-- Following @Franke2016, the linking function for this data treats each bin $n_{i}$ as a draw from a categorical distribution where the probability of bin $j$ is proportional to $\exp{(a\cdot P_i)}$, i.e., a soft-max choice from $P_{i}$.
--->
-<!-- The higher parameter $a$, the more likely $n_{i}$ is the mode of $P_{i}$.  -->
-<!-- For $a \rightarrow 0$, all bins become equiprobable. -->
-
-<!-- \begin{eqnarray} -->
-<!-- P_{i} &\sim& \text{Dirichlet}(1, ..., 1) \\  -->
-<!-- a & \sim & \text{Gamma}(2,1) \\ -->
-<!-- n_{i} &\sim & \text{Categorical}(\exp(a \cdot P_i)) -->
-<!-- \end{eqnarray} -->
-
-<!-- VIZ (as before)? -->
-
-<!-- We assume each "binned" response is a sample from a multinomial distribution with unknown probability vector. -->
-<!-- We put a Dirichlet-prior over this probability vector. -->
-
-<!-- We built a Bayesian data analysis model for this prior elicitation task. -->
-<!-- Question 1 elicits the proportion of people who have done an action before.  -->
-<!-- We model this data as coming from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma_{1}, \xi_{1})$.  -->
-<!-- Question 2 elicits the rate, or relative frequency, with which a person does the action. -->
-<!-- This was modeled by a log-normal distribution: $\ln d_{2} \sim \text{Gaussian}(\mu_{2}, \sigma_{2})$.  -->
-<!-- Each item was modeled independently for each gender. -->
-<!-- We implemented this model using the probabilistic programming language WebPPL \cite{dippl}, and found the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
--->
-
-<!-- The priors elicited cover a range of possible parameter values as intended (Figure \ref{fig:priorScatter}, scatter), resulting in parametrized distributions of dramatically different shapes (insets).
--->
-<!-- We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency  of action (Question 2) ($r_{1,2} = 0.74$). -->
-<!-- Items that tend to be more popular actions also tend to be more frequent actions (e.g.
-\emph{wears socks}) and visa-versa (e.g.
-\emph{steals cars}), though there are notable exceptions (e.g.
-\emph{plays the banjo} is not popular but done frequently when done at all, as is \emph{smokes cigarettes}; \emph{goes to the movies} is a popular activity though not done very often).
--->
-<!-- This diversity is relevant because the speaker model (Eq.~\ref{eq:S2}) will produce habitual sentences (e.g.
-\emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
--->
-
-<!-- From the inferred parameters and assumed functional forms, we get an inferred $P(p)$ modeled as a mixture of individuals with the possibility of carrying out the action and those without the possibility of doing it.
--->
-<!-- That is, $P(p)$ was constructed by sampling $p$ as follows: -->
-
-<!-- \begin{align} -->
-<!-- \theta & \sim \text{Beta}(\gamma_{1}, \xi_{1}) \nonumber \\  -->
-<!-- \ln \lambda & \sim \begin{cases} -->
-<!-- 		\text{Gaussian}(\mu_{2}, \sigma_{2}) &\mbox{if } \text{Bernoulli}(\theta) = \textsc{t} \label{eq:priorModel}  \\ -->
-<!-- 				\delta_{\lambda=-\infty} &\mbox{if } \text{Bernoulli}(\theta) = \textsc{f} \\ -->
-<!-- 		\end{cases} -->
-<!-- \end{align} -->
-
-<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior in our language model resolves two technical difficulties: (1) It smooths effects that are clearly results of the response format^[ -->
-<!-- For example, a very common rating is *1 time per year*.
-Presumably participants would be just as happy reporting *approximately* 1 time per year; the raw data does not reflect this due to demands of the dependent measure.
--->
-<!-- ] -->
-<!-- and (2) it better captures the tails of the prior distribution which have relatively little data and need to be regularized by the analysis. -->
-<!-- Figure \ref{fig:priorScatter} (right) shows example inferred priors. -->
-
-<!-- Some items show substantial differences between the genders (e.g., *wears a bra*) and some show subtle differences (e.g., *watches professional football*).  -->
-<!-- We will explore the possibility of different truth conditions for habituals of different gendered characters in Experiment 2, for select items with priors that differ substantially by gender. -->
-
-```{r habituals-prior-mixture-summarize}
+A: Mixture-model posterior predictions in comparison to the empirical mean responses for the two prior elicitation questions.
+Items cover the full spectrum of possible parameter values.
+B: Reconstructed prevalence priors.
+In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (same as the \\emph{proportion of people who have done action before} scatter-plot), reflecting the (inverse) rarity of the event across people.", cache = F}
+cowplot::plot_grid(
+  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
+  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
+  labels = c("A", "B"), #nrow = 1,
+  align = 'h',
+  rel_widths = c(1, 3)
+  )
+```
+
+## Experiment 2b: Habitual endorsements
+
+#### Load and summarize data
+
+```{r habituals-endorsement}
+d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
+                    "habituals-endorsement-catch_trials.csv", sep = ""))
+
+d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
+                    "habituals-endorsement.csv", sep = ""))
+
 d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
@@
   group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
-## Experiment 2b: Habitual endorsements
-
-In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigaerettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).
-
-### Method
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
+  tidyboot_mean( column = value)
 
@@
                      breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
+  scale_fill_viridis(breaks = c(0, 5))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
@@
                                ticks = F))
-```
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Materials
-
-Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
-Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
-\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
-For example, relatively high frequencies were chosen (e.g., three times every week vs.
-2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs.
-2 years).
-In total, `r nrow(d.hab.endorsement %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.
-
-#### Procedure
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, "In the past month, Bill smoked cigarettes 3 times".
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
-These were used for an exploratory analysis on differences in endorsements by gender of the target character.
-
-<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
-
-### Results
-
-<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
--->
-<!-- Several features in our data argue against this hypothesis. -->
-<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
--->
-
-Habitual sentences were endorsed for a wide range of frequencies.
-When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
-When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-### Endorsement model comparison
-
-```{r habituals-items-table, eval = F}
-d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()
-
-d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
-  kable(., 
-        format = "latex", longtable = T, booktabs = T,
-        caption = "Demo table") %>% 
-  kable_styling(latex_options = c("repeat_header"),
-                font_size = 7)#%>%#, "hold_position")) %>%
-  #column_spec(3, width = "10cm")%>%
-  #collapse_rows(columns = 1:2)
-```
+
+rs.habituals.bda.posterior.predictive.measurementSpace
+```
+
+#### Gender item stuff
 
@@
 r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, cor(map_female, map_male)), 3)
-
-# ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-#                  xmin = low_female, ymin = low_male,
-#                  xmax = high_female, ymax = high_male, fill = habitual))+
-#   geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-#                     filter(time_period== "month"), aes(label = habitual,
-#                                                        color = habitual),
-#                   force = 3, nudge_x = -1, segment.size = 0.3)+
-#   guides(fill = F, color = F)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   geom_point(shape = 21)+
-#   geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-#   scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-#   scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-#   coord_fixed()+
-#   xlab("Habitual endorsement (female character)")+
-#   ylab("Habitual endorsement (male character)")+
-#   scale_fill_solarized()+
-#   scale_color_solarized()
-# r2.habituals.gendered
-#n.habituals.gendered.subset.analysis
-#r.habituals.gendered.subset.analysis
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
-```
+save(d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide,
+     file = "../paper/cached_results/case2_endorsement_genderItemAnalysis.RData")
+```
+
+#### Regression models
 
 ```{r habituals-regression-models}
-
 glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
@@
 )
-
-r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
-
-r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
-                                          "MAP_h", "prediction")
-
-r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
-  filter(logAnnualRate < 1.1)
-
-r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
-
-r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
-
-mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
-                                          "MAP_h", "prediction")
 
@@
 
+d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
+  mutate(sqErr = (MAP_h-prediction)^2)
+
+save(d.hab.endorse.regression.freq.mix,
+     d.hab.endorse.regression.freq,
+     d.hab.endorse.regression, file = "../paper/cached_results/case2_endorsement_regressionResults.RData")
+
+r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)
+
+r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
+                                          "MAP_h", "prediction")
+
+mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
+                                          "MAP_h", "prediction")
+
+r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
+  filter(logAnnualRate < 1.1)
+
+r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)
+
+r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
+                                          "MAP_h", "prediction")
+
+mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
+                                          "MAP_h", "prediction")
+
 r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
@@
                                           "MAP_h", "prediction")
-
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
+```
+
+#### RSA models
 
@@
             cred_lower = hdi_lower(val))
-
-fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
-fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
-hab.fixed.threshold.s1opt <- filter(fixed.hab.params.posterior, B == "speakerOptimality")
 
@@
 
-# %>%
-#   mutate(src = factor(src, levels = c( 
-#                                       "some_model",
-#                                       "habituals_model",
-#                                       "regression_freq", 
-#                                       "regression_freq_distinct"
-#                                      ),
-#                       labels = c(
-#                                  "Fixed semantics model",
-#                                  "Uncertain semantics model",
-#                                  "Referent frequency alone", 
-#                                  "Distinctiveness + referent frequency"
-#                                  )))
-
 example.habituals.actions <- separate(data.frame(example.habituals), 
@@
   md.hab %>% 
-    #filter(habitual %in% example.habituals.actions) %>% 
     filter(habitual %in% example.habituals) %>% 
@@
                                                       "week")),
-         habitual = factor(habitual, levels = example.habituals
-                           #c("runs", "hikes", "climbs mountains", "goes to the movies",
-                           #                     "smokes cigarettes")
-                           ),
+         habitual = factor(habitual, levels = example.habituals),
          src = factor(src, levels = c("data",
@@
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  scale_fill_viridis()+
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
@@
 
-```{r habitual-endorsment-scatters}
-#View(md.hab)
-
-habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
-                                      "regression_freq", 
-                                      "regression_freq_distinct",
-                                      "some_model",
-                                      "habituals_model"
-                                     ),
-                      labels = c(
-                                 "Referent frequency", 
-                                 "Distinctiveness + \n referent frequency",
-                                 "Fixed semantics",
-                                 "Uncertain semantics"
-                                 ) )) %>%
-ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.15)+
-  geom_errorbarh(alpha = 0.15)+
-  geom_point(shape = 21, size = 3)+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human endorsement")+
-  facet_wrap(~src, nrow = 1, strip.position = "top")+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F,
-                               title.position="top"))+ 
-  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
-        legend.direction = 'horizontal',
-        #legend.position = c(0.025,0.975),
-        #legend.position =c(1,1),
-        legend.justification = c(1,1)
-        )
-```
+#### Simulations for insets
 
@@
 #             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
-habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
-                                                  ),
-                            labels = c("Prevalence Prior",
-                                       "Posterior given Habitual")),
-         action = factor(action, levels = example.habituals)
-                                #"climbs mountains", "hikes", "runs",
-                              #"goes to the movies", "smokes cigarettes"
-                              ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-  facet_wrap(~action, nrow = 1)+
-  # geom_text_repel(data = category.text.labels,
-  #                 aes(label = category, x = x , y = y),
-  #                 inherit.aes = F, color = "#2b83ba")+
-  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
-  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
-  #scale_linetype_manual(values = c(3, 4, 2, 1))+
-  #scale_linetype_manual(values = c(3, 4, 1))+
-  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
-  theme(#legend.position = "bottom", 
-        legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1),
-        axis.title.y = element_text(hjust = 1))+
-      scale_x_continuous(limits = c(-5, 8), 
-                     breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-```
-
-```{r habituals-endorsement-figure, fig.width = 16, fig.height = 12.5, fig.cap="Endorsing generalizations about events.
-A: Endorsements for nine events given different frequencies of action by human participants and four models.
-B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
-Top right: Model fits for all ninety-three habitual sentences by each model.
-C: Nine example frequency priors and posteriors upon hearing the generalization.
-These distributions are inferred using both data sources from Expts.
-2a & 2b.", cache = F}
-
-hab.legend <- get_legend(habituals.endorsement.models)
-fig.hab.endorse.bars <- habituals.endorsement.bars +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) #+ ggtitle("prevalence priors")
-fig.hab.endorse.scatters <- habituals.endorsement.models +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
-fig.hab.endorse.priors <- habituals.endorsement.insets +
-  theme(plot.margin = unit(c(18,2,6,6), "pt"))
-
-#+ 
-    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
-
-# fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
-#                                      fig.gen.endorse.models, 
-#                                     # align = 'v',
-#                                     #  axis = 'l',
-#                                     labels = c("A", "B"),
-#                                     rel_widths = c(0.9, 1))
-
-#fig.hab.toprow <- 
-  plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters,
-                            # plot_grid(fig.hab.endorse.scatters,hab.legend, nrow = 1, rel_widths = c(0.6,4),
-                            #                                 axis = 't', align = 'h'),
-                            fig.hab.endorse.priors,
-                            labels = c("A", "B", "C"), nrow = 3,
-                            axis = 'lr', 
-                        align = 'v', 
-                            rel_heights = c(3.1, 1.4, 1.2))
-
-# plot_grid(fig.hab.toprow,
-#           fig.hab.endorse.priors,
-#           labels = c("", "C"), nrow = 2, rel_heights = c(3, 1.3)
-#           )
-
-#plot_grid( prow, legend, rel_widths = c(3, .3))
-
-# grid.arrange(fig.habituals.endorsement.vs.freq, 
-#              habituals.endorsement.models,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
-```
-
-In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(`r n.habituals.gendered.analysis`) = `r r.habituals.gendered.analysis`$.
-Endorsements are even more highly correlated for the six events we anticipated differences by referent-gender:  $r(`r n.habituals.gendered.subset.analysis`) = `r r.habituals.gendered.subset.analysis`$
-This lack of a difference may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, in minimal contexts such as this, habituals are evaluated with respect to *other people*, not just other men or other women).
-Less interestingly, the lack of a difference may be the result of gender being not very salient in our paradigm, perhaps because the names used were not sufficiently gendered.
-
-We now turn to our model-based analyses to better understand the endorsement data and the contribution of our model.
-For all analyses, we collapse across gender of the referent character for endorsement judgments.
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model.
-Analyses which use the rate prior distribution $P(p_f)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prior distribution.
-To model the uncertainty in the input measurements, we bootstrap the data for the regression models and we construct joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-thresold).
-
-#### Referent frequency
-
-To understand the role of frequency in habitual endorsement, we use the frequency supplied to the participants in our experiment as a predictor in a linear model. 
-This model predicts the same endorsement level for two actions done with the same rate. 
-Obvious counterexamples exist in our data set:
-While participants are willing to endorse that a person "...
-climbs mountains" having done it 3 times in the past *year*, they are less willing to say that a person "...
-hikes" and not willing to say that a person "...
-runs".
-Some actions done with a relative high rate (e.g., 3 times in a month) do not receive full endorsement (e.g., *smokes cigarettes*; Figure \@ref(fig:habituals-endorsement-figure) A).
-Overall, the referent-frequency (in log-scale) predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$).
-In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$).
-The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because we designed the stimulus set to be critical of a referent-frequency model.
-<!-- An account purely based on the referent frequency does not explain endorsements in this data set. -->
-<!-- Instead, we pursue an explanation where prior beliefs interact with an underspecified literal semantics to produce the pattern of habitual endorsement observed. -->
-
-<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->
-
-<!-- NOTE: Alternatively: We could not discuss this analysis (or, in a footnote).
-Since participants judged both genders for these items, we could only analyze their first gender and drop their second, for consistency with the other items.
--->
-
-<!-- For our six items that showed substantial variability in the elicited priors between genders, we explore differences in endorsements.  -->
-<!-- Differences in endorsements could suggest that the *comparison class* of entities in the prior distribution used in our model might be gender-specific (i.e., when evaluating "Mary drinks beer." participants implicitly consider the distribution of frequencies for other women and not other men).
--->
-<!-- Endorsement probabilities and 95\% credible intervals for these six items at each time interavl for each gender are showed in Figure \ref{fig:habituals-endorsement-gender-exploration-scatter}.
--->
-<!-- We see no appreciable differences in endorsements for the two genders.  -->
-<!-- This suggests that, at least the minimal experimental contexts we are exploring, the comparison class is not different for female vs. male target characters. -->
-<!-- For all remaining analyses, we collapse across character gender when analyzing endorsements. -->
-
-<!-- This is unlikely to be the case based on , which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence.
--->
-
-#### Distinctiveness and referent frequency
-
-In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)).
-This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus is relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
-Thus, we take this parameter as an index of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
-We construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
-We use participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency given to participants to predict habitual endorsement.
-
-```{r habituals-distinctiveness-counterexamples}
-
-format_endorsment_ci <- function(
-  df, estimate = "MAP_h", low = "low",
-  high = "high", sigfigs = 2){
-  return(paste(
-    round(df[[1,estimate]], sigfigs),
-    " [",
-    round(df[[1,low]], sigfigs),
-    ", ",
-    round(df[[1,high]], sigfigs),
-    "]", sep = ""))
-}
-
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
-
-movies.year.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies",
-                                                        time_period == "year"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
-
-banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
-                                                        time_period == "2 years"),
-                                                        estimate = "prediction",
-                                                        low = "prediction_lower",
-                                                        high = "prediction_upper")
-```
-
-This model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-It can differentiate events done with the same frequency (e.g., *writing poems* vs. *novels*, 3 times in the past 5 years), and increase endorsement of the more rare action (*novels*). 
-Still, this model fails to capture fine-grained details in endorsment.
-For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
-
-#### Fixed-threshold endorsement model
-
-We next examine an information-theoretic endorsement model based on a fixed-threshold semantics.
-A fixed-threshold model commits the habitual to conveying that a person *does the action with some rate*, and the threshold on rates is common to all actions.
-As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data (for more details on model implementation, see Appendix C).
-We assume the referent-prevalence $p_{fk}$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
-Additionally, to account for statements that would be literally false under this model (frequencies that fall below the fixed threshold), we include an additional noise parameter, as we did for the fixed-threshold model in Case Study 1.
-To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-
-```{r hab-fixed-parameters}
-```
-
-```{r hab-fixed-threshold-examples, eval =F}
-```
-
-The data analytic model infers that a low threshold is likely: the inferred threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
-`r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].
-Compare this with the lowest referent-frequency used in our data set: $0.6$ times per year (3 times every 5 years).
-Thus, all of the utterances evaluated under this fixed-threshold model were literally true.
-As a result, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
-The fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model.
-
-A fixed-threshold utterance updates the interpreter model's beliefs differentially depending on the item.
-For instance, it's highly unlikely that a random person *climbs mountains* with any non-zero rate; thus this model fully endorses "Mary climbs mountains" even with low-frequency (Figure \@ref(fig:habituals-endorsement-figure) A).
-However, the model doesn't differentiate doing the same action with different frequencies.
-It is equally true that a person does an action *with some frequency* for any frequency greater than zero, analogous to how "some Ks F" is equally true if 20\% or 50\% of Ks F.
-
-Finally, the data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
-`r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise and that the speaker optimality parameter is `r round(hab.fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(hab.fixed.threshold.s1opt[[1,"cred_lower"]], 2)`,
-`r round(hab.fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
-
-<!-- That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise.  -->
-<!-- Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[ -->
-<!--   An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some").  -->
-<!--   This model would explain even less data than the current model (if it was better, this situation would have been inferred). -->
-<!--   That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
--->
-<!-- ] -->
-
-<!-- The fixed-threshold model is ill-defined for this data set. -->
-<!-- The data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`, -->
-<!-- `r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise. -->
-<!-- The inferred (fixed) threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`, -->
-<!-- `r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].  -->
-<!-- That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise.  -->
-<!-- Thus, our identical data analytic strategy paired with a fixed-threshold model is unable to predict the range of endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).^[ -->
-<!--   An alternative formulation of this model could fix the threshold to be the lowest possible threshold (analagous to the quantifier "some").  -->
-<!--   This model would explain even less data than the current model (if it was better, this situation would have been inferred). -->
-<!--   That model would have trouble differentiating between different frequencies for the same habitual statement (as the current model does), analogous to how "some" is equally true of 20\% or 50\%.
--->
-<!-- ] -->
-
-<!-- statements (Figure \ref{fig:habituals-endorsement-figure}, top-right: upper-left facet). -->
-<!-- The model exhibits a small dynamic range of endorsement, because the two options for the endorsement model (silence or a very low, fixed thresold) are only slightly different with respect to information conveyed to the interpreter.
--->
-<!-- Another shortcoming of this fixed threshold is illuminated by our manipulation of referent-frequency. -->
-<!-- With a fixed threshold, the difference between the interpreter's prior and posterior distribution is  (whatever is below the threshold).  -->
-
-<!-- Thus, this model makes the same predictions for different target frequencies in the same event. -->
-<!-- For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.  -->
-
-#### Uncertain-threshold endorsement model
-
-We used the same data analytic approach for the uncertain threshold endorsement model and performed the same Bayesian statistical inference over the model to learn about its parameters and predictions.
-Again, this model has two fewer parameters than the fixed-threshold model (no fixed-threshold parameter and no extrinsic noise process).
-As shown in Figure \@ref(fig:habituals-endorsement-figure)B, the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model achieves this. 
-An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is good statement to assert. 
-Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas someone who went to the movies 3 times last month more a person who "goes to the movies". 
-Only the uncertain-threshold model is able to draw this fine distinction.
-
-### Discussion
-
-Habitual language exhibits context-sensitivity directly parallel to that of generic language (Case Study 1).
-Habituals are endorsed for a wide range of frequencies, but show systematic patterns relative to the prior distribution of frequencies, as formalized by the uncertain-threshold model.
-Again, we articulated a number of alternative models and found that only the underspecified threshold model was able to explain the variability in endorsements.
-
-In this case study, we manipulated rather than measured the referent frequency (e.g., the frequency with which a person drinks coffee).
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model (and in a way that a fixed-threshold model cannot account for).
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in question.
-
-In Expt. 2b, participants were given a statement about how often a person has done the action in the past and asked to judge the corresponding habitual statement.
-This design potentially confounds an important distinction for the language of generalization: Does the prevalence communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-In Expt. 2c, we investigate this question by teasing apart *past* from *predictive frequency* and measuring its influence on habitual endorsement.
-
-<!-- In Expt.
-2b, we manipulated the frequency with which a person did an action in the past (e.g., three times in the past week vs.
-in the past year) for a wide range of events (e.g., drinks coffee vs.
-beer) and measured endorsements for the corresponding habitual statements.
--->
-
-<!-- The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements.  -->
-<!-- This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* endorsement model is doing.  -->
-
-<!-- People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation.  -->
-
-<!-- The speaker model endorses the statement when the observed frequency is relatively high, compared to the prior distribution over people doing the action.  -->
-
-<!-- As another potential alternative hypothesis, we formulate a model of a speaker who judges the felicity of the habitual utterance based on simple summary statistics of the prior, such as the mean and variance.
--->
-
-<!-- Only our pragmatic speaker model who reasons about a listener is able to capture the quantitative variability in our data. -->
-
-<!-- \begin{figure*}[t] -->
-<!-- \centering -->
-<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
-<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
-<!--   Middle: Human endorsements of habitual sentences (Expt.
-3b) vs.
-Predicted log frequency (Expt.
-3a), with data for corresponding items from Expt.
-2 (assumed to have the same predictive log frequency as baseline).
--->
-<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
-<!--   \label{fig:tj3} -->
-<!--   \vspace{-7pt} -->
-<!-- \end{figure*} -->
-
-## Experiment 2c: What is prevalence?
-
-While past frequency is often a good indicator of future tendency, the future is under no obligation to mimic the past.
-Does habitual language communicate probabilities in terms of past frequency or future expectations?
-On one hand, speakers can only be certain about what has happened in the past.
-On the other hand, language has a communicative function, and it would be useful for speakers to convey their predictions of what will be the case in the future.
-
-People can change their behavior abruptly due to a variety of decisions and outside events.
-We introduce these causal events into our minimal endorsement paradigm and measure their influence on endorsement.
-<!-- that either enable or prevent future actions. -->
-To provide the appropriate model-based analysis, participants in one condition make a prediction about what will be the case in the future (*predictive frequency*).
-In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
-<!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
-We then compare two uncertain-thresholds models to each other: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt.
-2b).
-
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
-r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
-n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)
-
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
-       aes(x=logAnnualPastRate,
-                              y = mean,
-                              ymin = ci_lower, ymax = ci_upper,
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
-  scale_shape_manual(values=c(21,22,23))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-3,6),
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
+```
+
+```{r}
+save(m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions,
+     file = "../paper/cached_results/case2_endorsement_rsaModelResults.RData")
+
+```
+
+#### Gender exploratory stuff
+
+```{r habituals-items-table, eval = F}
+d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()
+
+d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
+  kable(., 
+        format = "latex", longtable = T, booktabs = T,
+        caption = "Demo table") %>% 
+  kable_styling(latex_options = c("repeat_header"),
+                font_size = 7)#%>%#, "hold_position")) %>%
+  #column_spec(3, width = "10cm")%>%
+  #collapse_rows(columns = 1:2)
+```
+
+```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
+gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
+                    "wears a bra", "wears a watch", "wears a suit")
+
+d.hab.bayes.gendered <- d.hab.endorsement %>%
+  filter(habitual %in% gendered.items) %>%
+  group_by(habitual, characterGender) %>%
   summarize(k = sum(response), n = n()) %>%
@@
 
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-
-fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
-  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
-                 fill=condition, shape=condition,
-                 xmin = future_lower, xmax=future_upper,
-                 ymin=low, ymax = high))+
-  geom_errorbar(alpha=0.8)+
-  geom_errorbarh(alpha=0.8)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  geom_point(alpha = 1, size = 4)+
-  xlab("Predicted frequency (log scale)")+
-  ylab("Human endorsement")+
-  scale_x_continuous(limits = c(-4.2,7.2), 
-                     breaks = c(-3, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  coord_fixed(ratio=11.4)+
-  scale_fill_solarized()+
-  guides(fill = F, shape = F)+
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-    legend.position="bottom",
-    legend.direction="horizontal"
-    )
-
-```
-
-```{r habituals-predictive-rsa}
-n_chains <- 3
-# n_samples <- 500000
-# burn <- n_samples / 2
-# lg <- 150
-model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
-model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 50
-
-m.hab.pred.samp <- data.frame()
-m.hab.past.samp <- data.frame()
-
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/",
-#                     model_prefix, "targetH_predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
-
-  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "targetH_past-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
-
-#}
-# 
-# 
-# # 
-# save(m.hab.pred.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# # # 
-# save(m.hab.past.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
-
-load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
-
-m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorsement <- m.hab.pred.samp %>%
-  filter(type == 'predictive', C == "endorsement") %>%
-  rename(item = B, condition = D, binned_freq = E) %>%
-  group_by(item, condition) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.predictive.endorse.rsa <- bind_rows(
 left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.predictive.endorsement
-  ) %>%
-    mutate(src = "predictive_model"),
-  left_join(
-    d.hab.predictive.endorsment.summary,
-    m.hab.pastmodel.endorsement
-  ) %>%
-    mutate(src = "past_model")
-)
-
-r2.habituals.rsa.past <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.past <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
-                                          "MAP_h", "MAP")
-
-r2.habituals.rsa.predictive <- compute_r2(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-mse.habituals.rsa.predictive <- compute_mse(
-  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
-                                          "MAP_h", "MAP")
-
-r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
-
-habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Past-frequency endorsement model",
-                                 "Predictive-frequency endorsement model"
-
-                                 ))) %>%
-  filter(src == "Past-frequency endorsement model") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition,
-                  shape = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(size = 4)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-
-habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Past-frequency endorsement model",
-                                 "Predictive-frequency endorsement model"
-
-                                 ))) %>%
-  #filter(src == "Predictive-frequency endorsement model") %>%
-  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
-                  y = MAP_h, ymin = low, ymax = high, fill = condition, shape = condition))+
-  geom_abline(intercept = 0, slope = 1, lty = 3)+
-  geom_linerange(alpha = 0.7)+
-  geom_errorbarh(alpha = 0.7)+
-  geom_point(size = 4)+
-  scale_shape_manual(values=c(21,22,23,24))+
-  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
-  xlab("\n Model prediction")+
-  ylab("Human habitual endorsement")+
-  facet_wrap(~src, nrow = 1)+
-  #guides(fill = F)+
-  #theme(legend.position = "bottom")+
-  scale_fill_solarized()
-#habituals.predictive.predictive.model
-```
-
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Endorsement model (past frequency)",
-                                 "Endorsement model (predictive frequency)"
-
-                                 ))) %>%
-  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 13, fig.height = 3.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
-plot_grid(
-  plot_grid(
-    fig.hab.freq.predictive.vs.past + 
-      theme(plot.margin = unit(c(6,3,6,6), "pt")),
-  fig.hab.endorse.vs.predfreq + 
-    theme(plot.margin = unit(c(6,0,6,6), "pt")),
-  # habituals.predictive.past.model + 
-  #   theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab(""),
-  habituals.predictive.predictive.model + 
-    theme(plot.margin = unit(c(0,0,6,0), "pt")) + 
-    theme(legend.position="none") + ylab(""),
-  align = 'h', axis = 'l',
-  labels = c("A","B","C"),
-  #hjust = -1,
-  nrow =1 , rel_widths = c(1.2, 0.95, 1.6)),
-  legend_b, nrow = 2, rel_heights = c(1, 0.2))
-
-  #legend_b
-```
-
-### Method
-
-#### Participants
-
-We recruited `r n.subj.hab.pred + n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-`r n.subj.hab.pred` were assigned to the *predictive frequency* condition and `r n.subj.hab.pred.endorse` were assigned to the *sentence endorsement* condition.
-The experiment took on average `r round(ave.seconds.hab.pred/60,1)` minutes (*predictive frequency*) and `r round(ave.seconds.hab.pred.endorse / 60)` minutes (*sentence endorsement*). 
-Participants were compensated \$0.40.
-
-#### Materials
-
-The events used were a subset of those used in Expts. 2a \& b (21 of the original 31).
-In addition, we crafted statements that were intended to either increase the frequency (*enabling*; e.g., "Yesterday, Bill bought a pack of cigarettes.") or decrease the frequency (*preventative*; "Yesterday, Bill quit smoking.") of the event in the future.
-In order to increase the potential variability of responses across the experimental conditions, participants only saw the frequencies that led to the most intermediate endorsement of the habitual in Expt.
-2b.
-We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-See Appendix D for a full list of the enabling and preventative information.
-
-#### Procedure
-
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials (*preventative* and *enabling* trials).
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2b), in equal proportions.
-
-In the *predictive frequency* condition, participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{action}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-In the *sentence endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
-
-<!-- We analyze this data by building a simple Bayesian model of the measurement so that it may be integrated seamlessly into a joint model with the endorsement data (as we have done for all previous case studies).
--->
-<!-- As we assumed for the prior elicitation task (Expt.
-2a), we assume participant's responses for each event $i$ and condition $c$ are generated from a log-normal distribution with unknown mean and variance.
--->
-<!-- $$ -->
-<!-- \ln d_{ic} \sim \text{Gaussian}(\mu_{ic}, \sigma_{ic}) -->
-<!-- $$ -->
-
-#### Predictive frequency
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r r.hab.pred.past.baseline.freq`$). 
-That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
-This result implies that our model makes identical predictions for Expt.
-2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
-
-```{r habituals-predictive-elicitation-predictions}
-lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
-     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
-       (1 + condition | workerid) + 
-       (1 + condition | item)
-)
-lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
-```
-
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
-To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
-$SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-#### Sentence endorsement
-
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
-When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.baseline.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.baseline.summary[[1,"high"]], 2)`
-], enabling = 
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.enabling.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.enabling.summary[[1,"high"]], 2)`
-], preventative = `r round(d.hab.predictive.endorsment.preventative.summary[[1,"MAP_h"]], 2)` [`r round(d.hab.predictive.endorsment.preventative.summary[[1,"low"]], 2)`,
-`r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
-
-<!-- Interestingly, we observe endorsements in this experiment that are appreciably higher than in Expt. 2 for the same items (Figure \ref{fig:tj3}, middle; red vs. purple points). -->
-<!-- This may be due, in part, to an effect of the experimental context on participants: -->
-<!-- in this experiment the overall population of frequencies is much lower (both because we selected moderate frequencies from Expt.
-2 and because of the preventative information) and participants may infer that the experimenter believes this to be a representative range and adjust judgments accordingly.
--->
-<!-- Future investigation into this issue is warranted. -->
-
-We use our formal model to test whether past or predictive frequency matters for endorsement.
-To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p_{fk}$ that the endorsement model (Eq. \ref{eq:S1}) conditions on. 
-The past frequency model is constructed using the past frequency supplied to participants as the referent-prevalence.
-We analyze this model in the same Bayesian data analysis regime as for our previous models.
-We use the same priors over the parameters as before and learn about the posterior distribution by collecting three independent MCMC chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure}C shows the resulting model predictions for the past frequency and the predictive frequency endorsement models. 
-Participants' judgments of the habitual statements was indeed influenced by the causal manipulations *in the way predicted* by the endorsement model that uses the predictive frequency as the object of communication ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
-The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
-
-<!-- We use the mean predicted log frequency from Expt. 3a as the input to the speaker $S_1$ model to predict the felicity judgments measured in Expt. 3b. -->
-<!-- We infer the two model parameters using the same analysis approach in Expt. 2.  -->
-<!-- The model matches the data well ($r^2(63) = 0.91$; Figure \ref{fig:tj3}, right). -->
-<!-- The same model using the past frequency as the object of communication does not match the data at all ($r^2(63) = 0.02$). -->
-<!-- These results suggest that the felicity of habituals is based on an underlying scale of predicted future propensity, not merely the observed frequency in the past. -->
-
-## Discussion
-
-Habitual language conveys generalizations about events.
-Our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt.
-2a).
-Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b \& c).
-In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
-By manipulating (rather than measuring) the referent frequency with which a person does an action, we showed how alternative models were insufficient to account for the gradience in endorsement.
-In particular, a fixed threshold model that has access to the same prior knowledge and uses the same information-theoretic decision rule as our uncertain-threshold model is unable to make different predictions for different frequencies.
-Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
-
-A regression model that takes into the frequency and the *distinctiveness* of the action does a reasonable job at explaining the variance in this data.
-We note that this kind of model is merely a re-decription of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization. 
-A theory of the semantics of a generalization must formalize the truth-conditions of the generalization as well as how those truth-conditions relate to endorsement. 
-This is precisely what our information-theoretic models do (both fixed- and uncertain-threshold).
-
-<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
-<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
-<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventated future occurences of the action.
-We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
-We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
-Predicted prevalence thus captures the infleunce of top-down moderators (e.g., intervening causal forces) on endorsement.
-<!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.
--->
-
-In these experiments, we introduced participants to novel actors and, by doing so, were able to directly manipulate the frequency of a person doing the action.
-The kinds of events we used were familiar to participants (e.g., *running*) and thus we measured the prevalence priors for those events.
-In our final case study, we experimentally manipulate the prevalence priors, testing their causal influence over endorsements.
-In addition, we further we extend our theory to the language of causal relationships.
-
-<!-- Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
--->
-
-<!-- To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.
--->
-
-<!-- Habituals are a particularly convenient case study for manipulating referent feature-probability. -->
-<!-- In the domain -->
-
-<!-- From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[ -->
-<!--   While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
--->
-<!-- ] -->
-<!-- Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them. -->
-<!-- In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[ -->
-<!-- In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability.  -->
-<!-- A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate. -->
-<!-- ] -->
+    d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "female") %>%
+    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high,  -characterGender),
+  d.hab.bayes.gendered %>%
+    select(habitual, characterGender, MAP_h, low, high) %>%
+    filter(characterGender == "male") %>%
+    #rename(male_MAP, male_low = low, male_high = high) %>%
+    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
+                        as.character(round(low, 2)), ", ",
+                        as.character(round(high, 2)), "]", sep = "")) %>%
+    select(-MAP_h, -low, -high, -characterGender)
+    #rename(female_MAP, female_low = low, female_high = high)
+) %>% xtable(.,
+         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
+        label = c("tab:habituals-endorsement-gender")) %>%
+print(., type = "latex", 
+      tabular.environment = "tabularx", width = "\\textwidth",
+      scalebox='0.75',
+      include.rownames = FALSE, comment = F)
+```

### 2018-02-08 paper/case2-habituals.Rmd
refactor code in first half of habituals

@@
 
-```{r habituals-prior-data}
-annualRates = list("5 years" = 1/5, "2 years" = 1/2,
-                   "year" = 1, "6 months" = 2, "2 months" = 6,
-                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
-
-d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))
-
-d.hab.priors <- d.hab.priors %>%
-  mutate(comparisonTime_men = as.character(comparisonTime_men),
-         comparisonTime_women = as.character(comparisonTime_women),
-         item = as.character(item),
-         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
-  rowwise() %>%
-  mutate(
-    mixture_male = nPersons_men / comparisonNum_men,
-    mixture_female = nPersons_women / comparisonNum_women,
-    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
-                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
-                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
-                   ifelse(comparisonTime_men == "5 years", 
-                          nInstances_men / (5*365), -99)))),
-    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
-                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
-                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
-                   ifelse(comparisonTime_women == "5 years", 
-                          nInstances_women / (5*365), -99)))),
-    annualRate_male = dayRate_male * 365,
-    annualRate_female = dayRate_female * 365
-  )
-
-d.hab.priors.filtered <- filter(d.hab.priors, 
-       !(
-         (mixture_male == 0) ||   (mixture_female == 0) ||   
-           (dayRate_male == 0) ||   (dayRate_female == 0)  )
-       )
-```
-
-```{r habituals-prior-forwardsample}
-# this is basically bootstrapping and combining using the structured model
-
-d.hab.priors.samples <- data.frame()
-for (i in 1:10){
-
-  d.hab.priors.samples <- bind_rows(
-    d.hab.priors.samples,
-    d.hab.priors.filtered %>% 
-    select(workerid, item, starts_with("annualRate"), 
-           starts_with("mixture")) %>%
-    rowwise() %>%
-    mutate(
-      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
-       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
-       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
-       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
-       ) %>%
-    select(item, freq_male, freq_female) %>%
-    gather(gender, val, freq_male, freq_female) %>%
-  mutate(gender = gsub("freq_", "", gender))
-  )
-}
-
-```
-
-```{r habituals-prior-model}
-hab.prior.bda.model <- '
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var model = function(){
-	var mixtureParams = {
-		male: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    },
-		female: {
-      g: uniformDrift({a: 0, b: 1, width: 0.2}),
-      d: uniformDrift({a: 0, b: 100, width: 5})
-    }
-	};
-
-	var mixtureShapes = {
-		male: betaShape(mixtureParams.male),
-		female: betaShape(mixtureParams.female)
-	};
-
-	mapData({data: data.mixture}, function(d){
-    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
-     // display(Beta(mixtureShapes[d.gender]).score(d.val))
-		observe(Beta(mixtureShapes[d.gender]), d.val)
-	})
-
-	var stableFrequency = {
-		male: {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		},
-		female: {
-			mu: uniformDrift({a:-5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-		}
-	}
-
-	mapData({data: data.frequency}, function(d){
-    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
-        display(JSON.stringify(d)) : null
-    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
-		observe(Gaussian(stableFrequency[d.gender]), d.logval)
-	})
-
-	var existenceProb = {
-		male: beta(mixtureShapes.male),
-		female: beta(mixtureShapes.female)
-	};
-
-	var freqWhenPresent = {
-		male: gaussian(stableFrequency.male),
-		female: gaussian(stableFrequency.female)
-	}
-
-  var marginalFreq = {
-    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
-    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
-  }
-
-  return {
-    mix_mean_male : mixtureParams.male.g,
-    mix_mean_female : mixtureParams.female.g,
-    mix_samplesize_male : mixtureParams.male.d,
-    mix_samplesize_female : mixtureParams.female.d,
-    stableFreq_mean_male : stableFrequency.male.mu,
-    stableFreq_mean_female :stableFrequency.female.mu,
-    stableFreq_sd_male : stableFrequency.male.sigma,
-    stableFreq_sd_female :stableFrequency.female.sigma,
-    marginalFreq_NA_male: marginalFreq.male,
-    marginalFreq_NA_female: marginalFreq.female
-  }
-}
-'
-```
-
-```{r habituals-prior-model-run, cache = T, eval = F}
-
-n_samples <- 20000
-items <- levels(factor(d.hab.priors.filtered$item))
-
-rs.habituals.bda.prior <- data.frame()
-
-for (it in items){
-
- df.prior.toPass <- list(
-   frequency = d.hab.priors.filtered %>%
-      filter(item == it) %>%
-      select(item, starts_with("annualRate")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("annualRate_", "", gender),
-             logval = log(val)),
-   mixture = d.hab.priors.filtered %>% 
-      filter(item == it) %>%
-      select(item, starts_with("mixture")) %>%
-      gather(gender, val, -item) %>%
-      mutate(gender = gsub("mixture_", "", gender)) %>%
-      rowwise() %>%
-      mutate(val = ifelse(val == 1, 0.9999, 
-                          ifelse(val == 0, 0.000001, val)))
-  )
-
-  rs <- webppl(program_code = hab.prior.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.prior.toPass,
-       data_var = "data")
-
-  rs.habituals.bda.prior <- bind_rows(
-    rs.habituals.bda.prior, 
-    rs %>% 
-      mutate(item = it) %>% 
-      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
-  )
-}
-save(rs.habituals.bda.prior, 
-     file = paste(project.path,  "models/habituals/results/", 
-                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
-                  ".RData", sep = ""))
-
-```
-
-```{r habituals-prior-model-parameters, fig.width = 5}
-n_samples <- 20000
-items <- levels(factor(d.hab.priors.filtered$item))
-
-load(file = paste(project.path,  "models/habituals/results/", 
-                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
-                  ".RData", sep = ""))
-
+```{r habituals-priors-subfigs, fig.width = 8}
 example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
@@
                        )
-
-rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
-  filter(Parameter == "mean") %>%
-  group_by(Variable, Gender, item) %>%
-  summarize(MAP = estimate_mode(value),
-            cred_upper = hdi_upper(value),
-            cred_lower = hdi_lower(value)) %>%
-  ungroup()
-
-rs.habituals.bda.prior.summary.wide <- left_join(
-  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
-    select(-Variable) %>%
-    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
-  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
-    select(-Variable) %>%
-    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
-)
-
-# for displaying in text
+annualRates = list("5 years" = 1/5, "2 years" = 1/2,
+                   "year" = 1, "6 months" = 2, "2 months" = 6,
+                   "month" = 12, "2 weeks" = 26 ,"week" = 52)
+
+load("cached_results/case2_priors_parametersPredictives.RData") #habituals.priors.marginals, rs.habituals.bda.posterior.predictive.measurementSpace, rs.habituals.bda.prior.summary.wide
+
 n.items.habituals.prior.modeling <- length(rs.habituals.bda.prior.summary.wide$item)
 
-rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
-          d.hab.priors %>% select(item, category) %>% distinct())
-
-figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide %>%
-                                            mutate(Gender = factor(Gender, levels = c("male", "female"))),
-       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
-            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
-             fill = Gender, shape = Gender))+
-  geom_errorbar(alpha = 0.5)+
-  geom_errorbarh( alpha = 0.5)+
-  scale_shape_manual(values=c(21,22))+
-  #scale_color_solarized()+scale_fill_solarized()+
-  scale_fill_brewer(palette='Set1')+
-  #scale_color_brewer(palette='Set1')+
-  geom_point(size=4, 
-            #  inherit.aes = F, 
-            #  aes(x = mix_mean,y = sfreq_mean,  fill = category,
-            # shape = Gender),  
-            alpha = 0.9)+
-
-  xlab("% have DONE ACTION")+
-  ylab("Frequency of DOING ACTION \n (log scale)")+
-  #scale_
-  coord_fixed(ratio = 1/8)+
-  guides(fill = F,  shape = F)+
-  theme(legend.title = element_blank(),#element_text(hjust=0),
-        legend.position=c(0.82,0.14),
-        legend.direction="vertical") +
-        scale_y_continuous(limits = c(-1.5, 6.5), 
-                     breaks = c(0, 2.5, 4, 5.9),
-                     labels = c("annually", "monthly", "weekly", "daily"))+
-  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
-                    filter(item %in% example.habituals, Gender == "female"), 
+figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
+       aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+           y = empirical_mean, ymin = ci_lower, ymax = ci_upper, color = gender))+
+  facet_wrap(~measurement, scales = 'free', nrow = 2)+
+  scale_color_solarized()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+    geom_label_repel(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+                    filter(item %in% example.habituals, gender == "female"), 
                   inherit.aes =F,
-                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
-```
-
-```{r habituals-prior-model-forwardSample}
-rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
-  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
-  select(-Variable, -Parameter, -Chain) %>%
-  spread(param, value)
-
-rs.habituals.bda.prior.samples <- data.frame()
-for (i in 1:1){
-  rs.habituals.bda.prior.samples <- bind_rows(
-    rs.habituals.bda.prior.samples,
-    rs.habituals.bda.prior.spread %>%
-    rowwise() %>%
-    mutate(
-      a = mix_mean * mix_samplesize,
-      b = (1 - mix_mean) * mix_samplesize,
-      theta = rbeta(n = 1, shape1 = a, shape2 = b),
-      stable = rbinom(n = 1, size = 1, prob = theta),
-      logannualRate = ifelse(stable == 1, 
-                             rnorm(n = 1, 
-                                   mean = stableFreq_mean, 
-                                   sd = stableFreq_sd), -5),
-       annualRate =  exp(logannualRate)
-    )
-  )
-}
-```
-
-```{r habituals-prior-marginals-fig, fig.width = 7, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt.
-2a).
-Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red).", cache = F}
-
-figure.habituals.priors.marginals <- bind_rows(
-  d.hab.priors.samples %>% 
-    mutate(src = 'data', 
-           val = log(val)),
-  rs.habituals.bda.prior.samples %>%
-    rename(gender = Gender, val = logannualRate) %>%
-    select(gender, item, val) %>%
-    mutate(src = 'model')
-  ) %>%
-  filter(item %in% example.habituals,
-         src == 'model') %>%
-  mutate(item = factor(item, levels = example.habituals),
-         gender = factor(gender, levels = c("male", "female"))) %>%
-ggplot(. , aes( x = val, color = gender))+
-  geom_density(size = 0.8, aes( y = ..scaled.. ))+
+                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 3)+
+  geom_point()+
+  coord_fixed()+
+  xlab("Model posterior predictive")+
+  ylab("Empirical means")+
+  theme(legend.position = c(0.86, 0.09))
+
+figure.habituals.priors.marginals <- ggplot(habituals.priors.marginals %>%
+  filter(val > -4.9) %>%
+  mutate(gender = factor(gender, levels = c("female", "male"))), 
+  aes( x = val, color = gender, lty = src))+
+  geom_density(size = 0.4, aes( y = ..scaled.. ))+
   facet_wrap(~item, nrow = 4)+
+  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+               filter(gender == 'male', measurement == "% people who have done action before"), 
+            aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = MAP),
+              fill = "#268bd2", 
+            color = 'black',
+             inherit.aes = F)+
+  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+               filter(gender == 'female', measurement == "% people who have done action before"), 
+            aes(xmin = -4.25, xmax = -3.75,
+                                            ymin = 0, ymax = MAP),
+            fill = "#cb4b16",
+            color = 'black',
+             inherit.aes = F)+
   scale_color_solarized()+
@@
   scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(strip.text.y = element_text(angle = 0),
-        legend.position = c(0.9, 0.11),
+  theme(legend.position = c(0.93, -0.1),
         legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90))+
-    scale_x_continuous(limits = c(-5, 8), 
+        legend.box = 'vertical',
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1),
+        legend.margin=margin(t=0, r=0, b=-0.25, l=0, unit="cm"),
+    strip.text = element_text(size = 7))+
+  scale_x_continuous(
+      limits = c(-5, 8),
       breaks = c(-5, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
-
-#figure.habituals.priors.marginals
-```
-
-```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Prevalence priors for events (Expt.
+      labels = c("almost never", "annually", "monthly", "weekly", "daily")
+      )+
+  guides(color = F)
+```
+
+```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, fig.cap="Prevalence priors for events (Expt.
 2a).
-Left: Mean mixture parameter and mean stable frequency parameter for 31 events.
-Right: Inferred priors on frequencies from the structured, prior elicitation task.
-Priors are reconstructed by forward sampling using the inferred parameters in the prior mixture model.", cache = F}
-grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
+A: Mixture-model posterior predictions in comparison to the empirical mean responses for the two prior elicitation questions.
+Items cover the full spectrum of possible parameter values.
+B: Reconstructed prevalence priors.
+In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (same as the \\emph{proportion of people who have done action before} scatter-plot), reflecting the (inverse) rarity of the event across people.", cache = F}
+cowplot::plot_grid(
+  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
+  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
+  labels = c("A", "B"), #nrow = 1,
+  align = 'h',
+  rel_widths = c(1, 3)
+  )
 ```
@@
 
-```{r habituals-prior-mixture-summarize}
-d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
-  select(item, starts_with("mixture_")) %>%
-  gather(key, value, -item) %>%
-  group_by(item) %>%
-  multi_boot_standard( col = 'value' )
-```
-
 ## Experiment 2b: Habitual endorsements
@@
 
-### Method
-```{r habituals-endorsement}
-d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement-catch_trials.csv", sep = ""))
-
-d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
-                    "habituals-endorsement.csv", sep = ""))
-
-d.hab.endorsement <- left_join(
-  left_join(d.hab.endorsement, 
-           d.hab.endorsement.catch %>% 
-             select(workerid, pass)
-           ) %>%
-  filter(pass == 1),
-  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
-  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
-  rowwise() %>%
-  mutate(
-    annualRate = annualRates[[as.character(time_period)]]*n_instances,
-    logAnnualRate = log(annualRate)
-  )
-
-d.hab.endorsement.bayes <- d.hab.endorsement %>% 
-  group_by(habitual, logAnnualRate, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
-                       "goes to the movies_month", "smokes cigarettes_month")
-fig.habituals.endorsement.vs.freq <- 
-  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
-  geom_jitter(width = 0.1, shape = 21, size = 5)+
-  ylab("Human endorsement probability")+
-  xlab("Frequency of target")+
-  geom_label_repel(data = d.hab.endorsement.bayes %>% 
-                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
-                    filter(sentence %in% example.habituals), aes( label = habitual ),
-                       color = 'black', fill = 'white',
-    box.padding = unit(0.35, "lines"),
-    point.padding = unit(1e-06, "lines"),
-    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
-  scale_x_continuous(limits = c(-1,6), 
-                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
-                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-0.01, 1.01), 
-                     breaks = c(0, 0.5, 1))+
-  scale_fill_continuous(breaks = c(0, 5))+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        legend.position = "bottom")+
-  coord_fixed(ratio = 7)+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F))
-```
-
-#### Participants
-
-We recruited 150 participants from MTurk.
-To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
-This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
-The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
-
-#### Materials
-
-Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
-Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
-\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
-For example, relatively high frequencies were chosen (e.g., three times every week vs.
-2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs.
-2 years).
-In total, `r nrow(d.hab.endorsement %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.
-
-#### Procedure
-
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
-For example, "In the past month, Bill smoked cigarettes 3 times".
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
-Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
-Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
-These were used for an exploratory analysis on differences in endorsements by gender of the target character.
-
-<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
-
-### Results
-
-<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
--->
-<!-- Several features in our data argue against this hypothesis. -->
-<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
--->
-
-Habitual sentences were endorsed for a wide range of frequencies.
-When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
-When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
-
-### Endorsement model comparison
-
-```{r habituals-items-table, eval = F}
-d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()
-
-d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
-  kable(., 
-        format = "latex", longtable = T, booktabs = T,
-        caption = "Demo table") %>% 
-  kable_styling(latex_options = c("repeat_header"),
-                font_size = 7)#%>%#, "hold_position")) %>%
-  #column_spec(3, width = "10cm")%>%
-  #collapse_rows(columns = 1:2)
-```
-
-```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs.
-"John...") for six events that displayed appreciable differences in the prior elicitation.
-Labeled points all correspond to the time period of 3 times / month.'}
+```{r habituals-endorsement-gender-exploration}
+load("cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                     "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  #filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.wide <- left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
 
@@
 
-d.hab.bayes.gendered.subset <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.bayes.gendered.subset.wide <- left_join(
-    d.hab.bayes.gendered.subset %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
-    select(-characterGender),
-  d.hab.bayes.gendered.subset %>%
-    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
-    select(-characterGender)
-)
-
 n.habituals.gendered.subset.analysis <- length(d.hab.bayes.gendered.subset.wide$habitual)
-r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, cor(map_female, map_male)), 3)
-
-# ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
-#                  xmin = low_female, ymin = low_male,
-#                  xmax = high_female, ymax = high_male, fill = habitual))+
-#   geom_text_repel(data = d.hab.bayes.gendered.wide %>%
-#                     filter(time_period== "month"), aes(label = habitual,
-#                                                        color = habitual),
-#                   force = 3, nudge_x = -1, segment.size = 0.3)+
-#   guides(fill = F, color = F)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   geom_point(shape = 21)+
-#   geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
-#   scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-#   scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
-#   coord_fixed()+
-#   xlab("Habitual endorsement (female character)")+
-#   ylab("Habitual endorsement (male character)")+
-#   scale_fill_solarized()+
-#   scale_color_solarized()
-# r2.habituals.gendered
-#n.habituals.gendered.subset.analysis
-#r.habituals.gendered.subset.analysis
-```
-
-```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
-gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
-                    "wears a bra", "wears a watch", "wears a suit")
-
-d.hab.bayes.gendered <- d.hab.endorsement %>%
-  filter(habitual %in% gendered.items) %>%
-  group_by(habitual, characterGender) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-left_join(
-    d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "female") %>%
-    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high,  -characterGender),
-  d.hab.bayes.gendered %>%
-    select(habitual, characterGender, MAP_h, low, high) %>%
-    filter(characterGender == "male") %>%
-    #rename(male_MAP, male_low = low, male_high = high) %>%
-    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
-                        as.character(round(low, 2)), ", ",
-                        as.character(round(high, 2)), "]", sep = "")) %>%
-    select(-MAP_h, -low, -high, -characterGender)
-    #rename(female_MAP, female_low = low, female_high = high)
-) %>% xtable(.,
-         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
-        label = c("tab:habituals-endorsement-gender")) %>%
-print(., type = "latex", 
-      tabular.environment = "tabularx", width = "\\textwidth",
-      scalebox='0.75',
-      include.rownames = FALSE, comment = F)
+r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, 
+                                                   cor(map_female, map_male)), 3)
 ```
@@
 ```{r habituals-regression-models}
-
-glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
-              data = d.hab.endorsement, family = 'binomial')
-
-glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
-              data = d.hab.endorsement, family = 'binomial')
-
-d.hab.endorse.freq.mix.uniq <- unique(select(
-    d.hab.endorsement, habitual, logAnnualRate, time_period, 
-    mixture, mix_low, mix_high
-  ))
-
-d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_low)
-
-d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
-  select(-mixture) %>% 
-  rename(mixture = mix_high)
-
-d.hab.endorse.regression.freq <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
-      prediction_lower = prediction,
-      prediction_upper = prediction,
-      src = "regression_freq"
-      )
-)
+load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression
 
@@
 
-# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
-d.hab.endorse.regression.freq.mix <- left_join(
-  d.hab.endorsement.bayes,
-  d.hab.endorse.freq.mix.uniq %>%
-    mutate(
-      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
-      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
-      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
-      src = "regression_freq_distinct"
-      )
-)
-
 r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
@@
 
-d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
-  mutate(sqErr = (MAP_h-prediction)^2)
-
-# ggplot(d.hab.endorse.regression,
-#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
-#   geom_errorbar(alpha = 0.1)+
-#   geom_abline(intercept = 0, slope = 1, lty = 3)+
-#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
-#   #                   filter(sqErr > 0.1),
-#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
-#   geom_point()+
-#   xlim(0,1)+
-#   ylim(0,1)+
-#   coord_fixed()+
-#   xlab("Logistic model prediction")+
-#   ylab("Human habitual endorsement")+
-#   facet_wrap(~src)
-
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-# 
-# with(d.hab.endorse.regression %>%
-#        filter(src == "regression_freq_distinct"), 
-#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
-```
-
-```{r habituals-fullmodel, fig.width = 8}
-n_chains <- 3
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 20
-model_prefix <- "results-habituals-jointModel-S1-"
-
-# m.hab.samp <- data.frame()
-#  m.hab.fixed.samp <- data.frame()
-
-#for (i in seq(1, n_chains)){
-  # mi <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "smtncs_habitual-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
-
-  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-  #                   model_prefix, "smtncs_some-",
-  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
-#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
-#   #
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
-# }
-
-# save(m.hab.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-# 
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-# save(m.hab.fixed.samp,
-#      file = paste(project.path,  "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
-
-load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-load(paste(project.path,
-           "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
-# load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
-
-# m.hab.fixed.samp <- fread(paste(project.path,  "models/habituals/results/",
-#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
-
-fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
-  filter(type == "param") %>%
-  #filter(B %in% c("noise", "fixedThreshold")) %>%
-  group_by(B) %>% 
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-hab.uncertain.threshold.s1opt <- m.hab.samp %>% 
-  filter(type == "param") %>%
-  group_by(B) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
+```
+
+```{r habituals-rsamodels}
+load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions
+
+## model parameters
 fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
@@
 
-m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.fullmodel.endorsement <- m.hab.samp %>%
-  filter(type == 'predictive') %>%
-  rename(habitual = B, time_period = D, binned_freq = E) %>%
-  group_by(habitual, time_period, binned_freq) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.hab.endorse.rsa <- bind_rows(
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.fullmodel.endorsement
-  ) %>%
-    mutate(src = "habituals_model"),
-  left_join(
-    d.hab.endorsement.bayes,
-    m.hab.somemodel.endorsement
-  ) %>%
-    mutate(src = "some_model")
-)
-
 r2.habituals.rsa.fixed <- compute_r2(
@@
                                           "MAP_h", "MAP")
-
-md.hab <- bind_rows(
-  d.hab.endorse.regression,
-  left_join(
-    m.hab.endorse.rsa %>% 
-    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
-    d.hab.endorse.regression %>% 
-    select(habitual, time_period, logAnnualRate, mixture)
-  )
-)
-
-# %>%
-#   mutate(src = factor(src, levels = c( 
-#                                       "some_model",
-#                                       "habituals_model",
-#                                       "regression_freq", 
-#                                       "regression_freq_distinct"
-#                                      ),
-#                       labels = c(
-#                                  "Fixed semantics model",
-#                                  "Uncertain semantics model",
-#                                  "Referent frequency alone", 
-#                                  "Distinctiveness + referent frequency"
-#                                  )))
-
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
 
@@
                        )
-
-md.hab.long <- bind_rows(
-  md.hab %>% 
-    #filter(habitual %in% example.habituals.actions) %>% 
-    filter(habitual %in% example.habituals) %>% 
-    select(-low, -high, -MAP_h, -mean, -k, -n, -a, -b),
-  md.hab %>%
-      filter(habitual %in% example.habituals) %>% 
-      select(-mean, -k, -n, -a, -b, -prediction, -prediction_lower, -prediction_upper) %>%
-      rename(prediction = MAP_h, prediction_lower = low, prediction_upper = high) %>%
-      mutate(src = 'data')  
-) %>%
-  mutate(time_period = factor(time_period, levels = c("5 years", "2 years", "year",
-                                                      "6 months", 
-                                                      "2 months", "month", 
-                                                      "2 weeks", 
-                                                      "week")),
-         habitual = factor(habitual, levels = example.habituals
-                           #c("runs", "hikes", "climbs mountains", "goes to the movies",
-                           #                     "smokes cigarettes")
-                           ),
-         src = factor(src, levels = c("data",
-                                      "regression_freq", 
-                                      "regression_freq_distinct",
-                                      "some_model",
-                                      "habituals_model"
-                                     ),
-                      labels = c("Human data",
-                                 "Referent frequency", 
-                                 "Distinctiveness +\n referent frequency",
-                                 "Fixed semantics",
-                                 "Uncertain semantics"
-                                 )))
-
+```
+
+### Method
+
+#### Participants
+
+We recruited 150 participants from MTurk.
+To arrive at this number, we performed a Bayesian precision analysis to determine the minimum sample size necessary to reliably ensure 95\% posterior credible intervals no larger than 0.3 for a parameter whose true value is 0.5 and for which the data is a 2-alternative forced choice.
+This analysis revealed a minimum sample size of 50 per item; since participants only completed about one third of the items, we recruited 150 participants.
+The experiment took 4 minutes on average and participants were compensated \$0.55 for their work.
+
+#### Materials
+
+Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
+Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
+\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
+For example, relatively high frequencies were chosen (e.g., three times every week vs.
+2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs.
+2 years).
+In total, `r nrow(md.hab.long %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.
+
+#### Procedure
+
+On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
+For example, "In the past month, Bill smoked cigarettes 3 times".
+Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
+Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
+Six of these items were then also paired with a name of the opposite gender (e.g., participants rated both a female character and a male character who drank beer).
+These were used for an exploratory analysis on differences in endorsements by gender of the target character.
+
+<!-- The items were the same as in the prior elicitation task (Expt. 2a). -->
+
+### Results
+
+<!-- The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency (Figure \@ref(fig:habituals-endorsement-figure) top-left).
+-->
+<!-- Several features in our data argue against this hypothesis. -->
+<!-- It is clear that not all habitual statements are strongly assented to, even though it is true that all the events occurred with a non-zero frequency (i.e., they occurred at least 3 times before).
+-->
+
+Habitual sentences were endorsed for a wide range of frequencies.
+When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
+When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
+
+### Endorsement model comparison
+
+```{r habituals-endorsement-bars, fig.width = 8}
 habituals.endorsement.bars <- ggplot(md.hab.long, aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
@@
    guides(fill = F)
-#habituals.endorsement.bars
-#fixed.hab.params.posterior
-#fixed.hab.params.posterior
 ```
@@
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  scale_fill_viridis()+
   coord_fixed()+
@@
 
-```{r habituals-simulation-model}
-l0.hab.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var betaShape = function(p){
-  return {a: p.g * p.d, b: (1-p.g) * p.d}
-};
-
-var probBins = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9];
-
-var targetUtterance = "habitual";
-
-var roundTo3 = function(x){
-  return Math.round(x * 10000) / 10000
-}
-
-var lowerBound = -5, upperBound = 10, binWidth = 0.5;
-
-var stateBins =  _.range(
-  lowerBound, upperBound, binWidth
-)
-
-var thetaBins = map2(function(b1, b2){
-  var diff = Math.abs(b2 - b1) / 2;
-  return roundTo3(diff+ b1);
-}, stateBins.slice(0, stateBins.length-1), stateBins.slice(1))
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state> _.min(thetaBins):
-         true
-}
-
-var priorParams = data.priorParams[0];
-
-var stable_female_params = betaShape({
-  g: priorParams.mixture_female_mean, d: priorParams.mixture_female_samplesize
-})
-
-var stable_male_params = betaShape({
-  g: priorParams.mixture_male_mean, d: priorParams.mixture_male_samplesize
-})
-
-// this marginalizes out the mixture parameter
-var statePrior = Infer({model: function(){
-  var gender = flip(0.5) ? "female" : "male";
-  return gender == "female" ? // 
-    flip(
-        categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_female_params), b) + Number.EPSILON
-          }, probBins )
-        })
-    ) ? // stable female distribution
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) : // unstable female distribution
-    _.min(stateBins) : 
-    flip(        
-      categorical({
-          vs: probBins,
-          ps: map(function(b) {
-            return probability(Beta(stable_male_params), b) + Number.EPSILON
-          }, probBins )
-      })
-    ) ? 
-      categorical({
-        vs: stateBins,
-        ps: map(function(b) {
-          return probability(Gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }), b) + Number.EPSILON
-        }, stateBins )
-      }) :
-    _.min(stateBins)
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var state_prior = sample(statePrior)
-    var theta = utterance == "habitual" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }})}, 10000)
-
-var continuousListener0 = function(utterance) {
-  Infer({model: function(){
-   var state = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:-5}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:-5})
-   var state_prior = flip(0.5) ? 
-        flip(beta(stable_female_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_female_mean, 
-                sigma: priorParams.stableFreq_female_samplesize
-          }) : delta({v:lowerBound}) :
-        flip(beta(stable_male_params)) ? 
-          gaussian({
-                mu: priorParams.stableFreq_male_mean, 
-                sigma: priorParams.stableFreq_male_samplesize
-          }) : delta({v:lowerBound})
-    var theta = uniform(lowerBound, upperBound)
-    condition(
-      (utterance == "habitual") ? 
-      state > theta : 
-      (state > _.min(lowerBound))
-    )
-    return {
-      state_Posterior: state, 
-      state_Prior: state_prior
-  }
- }, method: "rejection", samples: 10000, burn:5000, verbose: T})}
-
-continuousListener0(data.utt[0])
-'
-```
-
-```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, cache = T}
-example.habituals.actions <- separate(data.frame(example.habituals), 
-                                      example.habituals, 
-                                      into=c("action", "time_period"), sep = "_")$action
-
-m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
-  filter(type == "prior", B %in% example.habituals.actions) %>%
-  rename(action = B, variable = C, gender = D, parameter = E) %>%
-  group_by(action, variable, gender, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | generic) & L(h | silence) predictions
-
-m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(action, variable, gender, parameter, MAP) %>%
-  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
-  select(-variable, -gender, -parameter) %>%
-  spread(param, MAP)
-
-hab.listener.predictions <- data.frame()
-
-for (p in example.habituals.actions){
- priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)
-
- inputData = list(priorParams = priorParams,
-                  utt = "habitual")
-
- l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")
-
- hab.listener.predictions <- bind_rows(
-   hab.listener.predictions, 
-   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
-   )
-
-}
-
-# m.gen.fullmodel.target.prevalence <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   group_by(param, property, category) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-# m.gen.speakerBeliefs <- m.samp %>%
-#   filter(type == "withinKind") %>%
-#   mutate(Sentence = paste(category, property)) %>%
-#   filter(Sentence %in% example.generics)
-
-# m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
-
-# gen.inset.distributions <- bind_rows(
-#   gen.listener.predictions %>%
-#     mutate(category = NA),
-#   m.gen.speakerBeliefs %>%
-#     select(property, val) %>%
-#     rename(value = val) %>%
-#     mutate(Parameter = "speakerBeliefs")
-# )
-# 
-# 
-# category.text.labels <- data.frame(property = c("dont eat people", 
-#                       "carry malaria", "lay eggs",  "are female", "have spots"),
-#              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-#              x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-#             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-
+```{r habituals-model-insets, fig.width = 8, cache = T}
 habituals.endorsement.insets <- hab.listener.predictions %>% 

### 2018-02-08 analysis/case2-habituals.Rmd
port over more code into scripts

@@
 #             y = c(0.45, 0.5, 0.45, 0.5, 0.26))
-```
-
-```{r}
-save(m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions,
+hab.listener.predictions
+
+m.hab.endorse.rsa
+hab.uncertain.threshold.s1opt
+fixed.hab.params.posterior
+md.hab
+md.hab.long
+md.hab
+hab.listener.predictions
+```
+
+```{r saveModels}
+save(m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior,
+     md.hab.long, md.hab, hab.listener.predictions,
      file = "../paper/cached_results/case2_endorsement_rsaModelResults.RData")
-
 ```
@@
 ```
+
+## Experiment 2c: What is prevalence?
+
+```{r habituals-predictive-elicitation}
+d.hab.predictive <- read.csv(paste(
+  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
+
+n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
+ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
+      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
+      summarize(total = mean(totalSec))
+
+# participant reported this in the comments section (it was recorded as a symbol)
+d.hab.predictive[
+  (d.hab.predictive$workerid==44 & 
+     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
+d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
+
+d.hab.predictive<- d.hab.predictive %>%
+  rowwise() %>%
+  mutate(
+    annualPredictiveRate =
+           annualRates[[as.character(past_interval)]]*response,
+    annualPastRate =
+           annualRates[[as.character(past_interval)]]*past_freq,
+    annualPredictiveRate = ifelse(
+      annualPredictiveRate == 0, 0.05, 
+      annualPredictiveRate),
+    logAnnualPredictiveRate = log(annualPredictiveRate),
+    logAnnualPastRate = log(annualPastRate)
+    )
+
+d.hab.predictive.summary <- d.hab.predictive %>%
+  group_by(condition, item, logAnnualPastRate) %>%
+  tidyboot_mean(column = logAnnualPredictiveRate)
+
+r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
+n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)
+
+fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
+       aes(x=logAnnualPastRate,
+                              y = mean,
+                              ymin = ci_lower, ymax = ci_upper,
+                              fill = condition, shape=condition))+
+  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
+  scale_shape_manual(values=c(21,22,23))+
+  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
+  # #geom_errorbar(width=0.1)+
+  scale_x_continuous(limits = c(-3,6),
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(-3,6),
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+  guides(fill=F, shape=F)+
+  scale_fill_solarized()+
+  xlab("Past frequency (log scale)")+
+  ylab("Predicted frequency (log scale)")+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
+
+d.hab.predictive.summary
+```
+
+```{r habituals-predictive-model}
+hab.predictive.bda.model <- '
+var model = function(){
+
+	var predictiveFrequency = {
+			mu: uniformDrift({a: -5, b:10, width: 2}),
+			sigma: uniformDrift({a:0, b:10, width: 1})
+	}
+
+	mapData({data: data}, function(d){
+		observe(Gaussian(predictiveFrequency),
+        d.logAnnualPredictiveRate)
+	})
+
+  return predictiveFrequency
+}
+'
+```
+
+```{r habituals-predictive-model-run, cache = T, eval=F}
+items <- levels(factor(d.hab.predictive$item))
+conditions <- levels(factor(d.hab.predictive$condition))
+n_samples <- 5000
+rs.habituals.bda.predictive <- data.frame()
+
+for (it in items){
+  for (cn in conditions){
+     df.predictive.toPass <- d.hab.predictive %>%
+       filter(condition == cn, item == it)
+
+    rs <- webppl(program_code = hab.predictive.bda.model,
+       model_var = "model",
+       inference_opts = list(method = "MCMC", samples = n_samples,
+                             burn = n_samples / 2),
+       data = df.predictive.toPass,
+       data_var = "data")
+    rs.habituals.bda.predictive <- bind_rows(
+        rs.habituals.bda.predictive, 
+        rs %>% 
+            mutate(item = it, condition = cn) 
+        )
+  }
+}
+```
+
+```{r eval = F}
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
+#  geom_density(size = 1, aes( y = ..scaled.. ))+
+  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+               position = position_dodge())+
+  facet_wrap(~item, scales = 'free')+
+  scale_color_solarized()+
+  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_x_continuous(limits = c(-5,10)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
+# rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
+#   spread(Parameter, value) %>%
+#   rowwise() %>%
+#   mutate(
+#     logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
+#   )
+
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
+#  geom_density(size = 1, aes( y = ..scaled.. ))+
+  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+               position = position_dodge())+
+  facet_wrap(~item, scales = 'free')+
+  scale_color_solarized()+
+  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
+  scale_x_continuous(limits = c(-5,10)) +
+  theme(strip.text.y = element_text(angle = 0))
+
+bind_rows(
+  d.hab.predictive %>% 
+    mutate(src = 'data') %>% 
+    select(item, condition, src, logAnnualPredictiveRate),
+  rs.habituals.bda.predictive.samples %>% 
+    select(item, condition, logannualRate) %>%
+    rename(logAnnualPredictiveRate = logannualRate) %>%
+    mutate(src = 'model') 
+  ) %>%
+ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
+  geom_density(size = 1, aes( y = ..scaled.. ))+
+#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
+#               position = position_dodge())+
+  facet_grid(condition ~ item )+
+  scale_color_solarized()+
+  scale_x_continuous(limits = c(-5,10)) +
+  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
+  theme(strip.text.y = element_text(angle = 0))
+```
+
+```{r habituals-predictive-bda-summary, eval =F}
+rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
+  spread(Parameter, value) %>%
+  rowwise() %>%
+  mutate(
+    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
+  ) %>%
+  gather(key, val, mu, sigma, logannualRate) %>%
+  group_by(item, condition, key) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+```
+
+```{r habituals-predictive-bda-figure, eval =F}
+fig.hab.freq.predictive.vs.past <- left_join(
+  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
+  unique(d.hab.predictive %>% 
+    select(item, condition, logAnnualPastRate)
+  )) %>% ggplot(., 
+       aes(x=logAnnualPastRate, y = MAP, 
+                              ymin = cred_lower, ymax = cred_upper, 
+                              fill = condition, shape=condition))+
+  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
+  scale_shape_manual(values=c(21,22,23, size = 4))+
+  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
+  # #geom_errorbar(width=0.1)+
+  scale_x_continuous(limits = c(-4,7), 
+                     breaks = c(-4, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(-4,7), 
+                     breaks = c(-4, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+  guides(fill=F, shape=F)+
+  scale_fill_solarized()+
+  xlab("Past frequency (log scale)")+
+  ylab("Predicted frequency MAP (log scale)")+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
+```
+
+```{r habituals-predictive-endorsement}
+d.hab.predictive.endorsment <- read.csv(paste(
+  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
+d.hab.predictive.endorsment.catch <- read.csv(paste(
+  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
+
+n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
+ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
+      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
+      summarize(total = mean(totalSec))
+
+d.hab.predictive.endorsment.condition.summary <- left_join(
+  d.hab.predictive.endorsment, 
+  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
+  by = "workerid"
+  ) %>% filter(pass==1) %>%
+  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
+  rename(item = habitual) %>%
+  group_by(condition) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'baseline')
+
+d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'preventative')
+
+d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'enabling')
+
+d.hab.predictive.endorsment.summary <- left_join(
+  d.hab.predictive.endorsment, 
+  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
+  by = "workerid"
+  ) %>% filter(pass==1) %>%
+  mutate(response = ifelse(response=="agree-key", 1, 0),
+         time_period = factor(time_period,
+                              levels=c("month",
+                                       "2 months",
+                                       "year",
+                                       "2 years",
+                                       "5 years")),
+         condition = factor(condition,
+                            levels=c("enabling", "baseline", "preventative")),
+         hab_time = paste(habitual, time_period, sep='-')) %>%
+  rename(item = habitual) %>%
+  group_by(item, condition, hab_time, time_period) %>%
+  summarize(k = sum(response), n = n()) %>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         low  = qbeta(.025, a, b),
+         high = qbeta(.975, a, b),
+         MAP_h = (a-1)/(a+b-2),
+         mean = a / (a + b))
+
+d.hab.predictive.endorsment.summary <- left_join(
+  d.hab.predictive.endorsment.summary,
+  d.hab.predictive.summary %>%
+    rename(logAnnualFutureRate = mean,
+         future_lower = ci_lower, future_upper = ci_upper) %>%
+    select(-n)
+  # rs.habituals.bda.predictive.summary %>% 
+  #   filter(key == "logannualRate") %>%
+  #   rename(logAnnualFutureRate = MAP,
+  #        future_lower = cred_lower, future_upper = cred_upper)
+  # %>%
+  #   rowwise() %>%
+  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
+  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
+)
+
+r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+
+fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
+  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
+                 fill=condition, shape=condition,
+                 xmin = future_lower, xmax=future_upper,
+                 ymin=low, ymax = high))+
+  geom_errorbar(alpha=0.8)+
+  geom_errorbarh(alpha=0.8)+
+  scale_shape_manual(values=c(21,22,23,24))+
+  geom_point(alpha = 1, size = 4)+
+  xlab("Predicted frequency (log scale)")+
+  ylab("Human endorsement")+
+  scale_x_continuous(limits = c(-4.2,7.2), 
+                     breaks = c(-3, 0, 2.5, 4, 5.9),
+                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  coord_fixed(ratio=11.4)+
+  scale_fill_solarized()+
+  guides(fill = F, shape = F)+
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+    legend.position="bottom",
+    legend.direction="horizontal"
+    )
+
+```
+
+```{r habituals-predictive-rsa}
+n_chains <- 3
+# n_samples <- 500000
+# burn <- n_samples / 2
+# lg <- 150
+model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
+model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
+n_samples <- 100000
+burn <- n_samples / 2
+lg <- 50
+
+m.hab.pred.samp <- data.frame()
+m.hab.past.samp <- data.frame()
+
+# for (i in seq(1, n_chains)){
+#   mi <- fread(paste(project.path,  "models/habituals/results/",
+#                     model_prefix, "targetH_predictive-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+#   m.hab.pred.samp <- bind_rows(m.hab.pred.samp, mi %>% mutate(chain = i))
+
+  # mi.past <- fread(paste(project.path,  "models/habituals/results/",
+  #                   model_prefix, "targetH_past-",
+  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  # m.hab.past.samp <- bind_rows(m.hab.past.samp, mi.past %>% mutate(chain = i))
+
+#}
+# 
+# 
+# # 
+# save(m.hab.pred.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "predictive-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+# # # 
+# save(m.hab.past.samp,
+#      file = paste(project.path,  "models/habituals/results/", model_prefix, "past-",
+#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+
+load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))
+
+load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))
+
+m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
+  filter(type == 'predictive', C == "endorsement") %>%
+  rename(item = B, condition = D, binned_freq = E) %>%
+  group_by(item, condition) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+m.hab.predictive.endorsement <- m.hab.pred.samp %>%
+  filter(type == 'predictive', C == "endorsement") %>%
+  rename(item = B, condition = D, binned_freq = E) %>%
+  group_by(item, condition) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+
+m.hab.predictive.endorse.rsa <- bind_rows(
+  left_join(
+    d.hab.predictive.endorsment.summary,
+    m.hab.predictive.endorsement
+  ) %>%
+    mutate(src = "predictive_model"),
+  left_join(
+    d.hab.predictive.endorsment.summary,
+    m.hab.pastmodel.endorsement
+  ) %>%
+    mutate(src = "past_model")
+)
+
+r2.habituals.rsa.past <- compute_r2(
+  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.past <- compute_mse(
+  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
+                                          "MAP_h", "MAP")
+
+r2.habituals.rsa.predictive <- compute_r2(
+  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
+                                          "MAP_h", "MAP")
+
+mse.habituals.rsa.predictive <- compute_mse(
+  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
+                                          "MAP_h", "MAP")
+
+r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
+
+habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Past-frequency endorsement model",
+                                 "Predictive-frequency endorsement model"
+
+                                 ))) %>%
+  filter(src == "Past-frequency endorsement model") %>%
+  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                  y = MAP_h, ymin = low, ymax = high, fill = condition,
+                  shape = condition))+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_linerange(alpha = 0.7)+
+  geom_errorbarh(alpha = 0.7)+
+  geom_point(size = 4)+
+  scale_shape_manual(values=c(21,22,23,24))+
+  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  xlab("Model prediction")+
+  ylab("Human habitual endorsement")+
+  facet_wrap(~src, nrow = 1)+
+  guides(fill = F)+
+  #theme(legend.position = "bottom")+
+  scale_fill_solarized()
+
+habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Past-frequency endorsement model",
+                                 "Predictive-frequency endorsement model"
+
+                                 ))) %>%
+  #filter(src == "Predictive-frequency endorsement model") %>%
+  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                  y = MAP_h, ymin = low, ymax = high, fill = condition, shape = condition))+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  geom_linerange(alpha = 0.7)+
+  geom_errorbarh(alpha = 0.7)+
+  geom_point(size = 4)+
+  scale_shape_manual(values=c(21,22,23,24))+
+  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  xlab("\n Model prediction")+
+  ylab("Human habitual endorsement")+
+  facet_wrap(~src, nrow = 1)+
+  #guides(fill = F)+
+  #theme(legend.position = "bottom")+
+  scale_fill_solarized()
+#habituals.predictive.predictive.model
+```
+
+```{r fig.height = 6, fig.width=14, echo = F, eval=F}
+m.hab.pred.samp %>%
+  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
+  #filter(type == "predictive", C == "endorsement") %>%
+#  mutate(E = as.numeric(as.character(E))) %>%
+  ggplot(., aes(x = val, fill = D))+
+  geom_histogram(position = position_dodge())+
+  #facet_grid(B~E)+
+  facet_grid(D~B)
+```
+
+```{r, eval = F}
+m.hab.predfreq.summary <- m.hab.pred.samp %>%
+  filter(type == "predictive", C == "predictiveFreq") %>%
+  group_by(B, D, E) %>%
+  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
+
+left_join(m.hab.predictive.endorse.rsa %>%
+  mutate(src = factor(src, levels = c( 
+                                      "past_model",
+                                      "predictive_model"
+                                     ),
+                      labels = c(
+                                 "Endorsement model (past frequency)",
+                                 "Endorsement model (predictive frequency)"
+
+                                 ))) %>%
+  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
+```
+
+```{r habituals-predictive-elicitation-predictions}
+lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
+     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
+       (1 + condition | workerid) + 
+       (1 + condition | item)
+)
+lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
+```
+
+```{r}
+save(d.hab.predictive.endorsment.summary, d.hab.predictive.summary, 
+     n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse, 
+     n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, 
+     lmer.rs.hab.predictive.summary,
+     file = "../paper/cached_results/case2_predictive_data.RData")
+```

### 2018-02-08 paper/case2-habituals.Rmd
port over more code into scripts

@@
 load("cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
+load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression
+load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, md.hab, hab.listener.predictions
+
 gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
@@
 ```{r habituals-regression-models}
-load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression
 
@@
 ```{r habituals-rsamodels}
-load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions
 
@@
 
-movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))
+movies.year.data <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies", time_period == "year"))
 
@@
 
-banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))
+banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo", time_period == "2 years"))
 
@@
                                                         high = "prediction_upper")
+
 ```
@@
 To learn about the credible values of the model's parameters and generate predictions given those inferred parameter values, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
-
-```{r hab-fixed-parameters}
-```
-
-```{r hab-fixed-threshold-examples, eval =F}
-```
 
@@
 
-```{r habituals-predictive-elicitation}
-d.hab.predictive <- read.csv(paste(
-  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
-
-n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
-ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-# participant reported this in the comments section (it was recorded as a symbol)
-d.hab.predictive[
-  (d.hab.predictive$workerid==44 & 
-     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
-
-d.hab.predictive<- d.hab.predictive %>%
-  rowwise() %>%
-  mutate(
-    annualPredictiveRate =
-           annualRates[[as.character(past_interval)]]*response,
-    annualPastRate =
-           annualRates[[as.character(past_interval)]]*past_freq,
-    annualPredictiveRate = ifelse(
-      annualPredictiveRate == 0, 0.05, 
-      annualPredictiveRate),
-    logAnnualPredictiveRate = log(annualPredictiveRate),
-    logAnnualPastRate = log(annualPastRate)
-    )
-
-d.hab.predictive.summary <- d.hab.predictive %>%
-  group_by(condition, item, logAnnualPastRate) %>%
-  multi_boot_standard(col = "logAnnualPredictiveRate")
-
+```{r}
+load("cached_results/case2_predictive_data.RData")
+#d.hab.predictive.endorsment.summary, d.hab.predictive.summary, n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse,n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, lmer.rs.hab.predictive.summary
+```
+
+```{r, cache = F}
 r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
@@
 
+r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
+                                          "logAnnualFutureRate", "MAP_h")
+
+d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'baseline')
+
+d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'preventative')
+
+d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
+  filter(condition == 'enabling')
+```
+
+```{r fighabfreq_predictive_vs_past, cache = F}
 fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-```
-
-```{r habituals-predictive-model}
-hab.predictive.bda.model <- '
-var model = function(){
-
-	var predictiveFrequency = {
-			mu: uniformDrift({a: -5, b:10, width: 2}),
-			sigma: uniformDrift({a:0, b:10, width: 1})
-	}
-
-	mapData({data: data}, function(d){
-		observe(Gaussian(predictiveFrequency),
-        d.logAnnualPredictiveRate)
-	})
-
-  return predictiveFrequency
-}
-'
-```
-
-```{r habituals-predictive-model-run, cache = T, eval=F}
-items <- levels(factor(d.hab.predictive$item))
-conditions <- levels(factor(d.hab.predictive$condition))
-n_samples <- 5000
-rs.habituals.bda.predictive <- data.frame()
-
-for (it in items){
-  for (cn in conditions){
-     df.predictive.toPass <- d.hab.predictive %>%
-       filter(condition == cn, item == it)
-
-    rs <- webppl(program_code = hab.predictive.bda.model,
-       model_var = "model",
-       inference_opts = list(method = "MCMC", samples = n_samples,
-                             burn = n_samples / 2),
-       data = df.predictive.toPass,
-       data_var = "data")
-    rs.habituals.bda.predictive <- bind_rows(
-        rs.habituals.bda.predictive, 
-        rs %>% 
-            mutate(item = it, condition = cn) 
-        )
-  }
-}
-```
-
-```{r eval = F}
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
-rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  )
-
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
-#  geom_density(size = 1, aes( y = ..scaled.. ))+
-  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-               position = position_dodge())+
-  facet_wrap(~item, scales = 'free')+
-  scale_color_solarized()+
-  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
-  scale_x_continuous(limits = c(-5,10)) +
-  theme(strip.text.y = element_text(angle = 0))
-
-bind_rows(
-  d.hab.predictive %>% 
-    mutate(src = 'data') %>% 
-    select(item, condition, src, logAnnualPredictiveRate),
-  rs.habituals.bda.predictive.samples %>% 
-    select(item, condition, logannualRate) %>%
-    rename(logAnnualPredictiveRate = logannualRate) %>%
-    mutate(src = 'model') 
-  ) %>%
-ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
-  geom_density(size = 1, aes( y = ..scaled.. ))+
-#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
-#               position = position_dodge())+
-  facet_grid(condition ~ item )+
-  scale_color_solarized()+
-  scale_x_continuous(limits = c(-5,10)) +
-  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
-```{r habituals-predictive-bda-summary, eval =F}
-rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
-  spread(Parameter, value) %>%
-  rowwise() %>%
-  mutate(
-    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
-  ) %>%
-  gather(key, val, mu, sigma, logannualRate) %>%
-  group_by(item, condition, key) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r habituals-predictive-bda-figure, eval =F}
-fig.hab.freq.predictive.vs.past <- left_join(
-  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
-  unique(d.hab.predictive %>% 
-    select(item, condition, logAnnualPastRate)
-  )) %>% ggplot(., 
-       aes(x=logAnnualPastRate, y = MAP, 
-                              ymin = cred_lower, ymax = cred_upper, 
-                              fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
-  scale_shape_manual(values=c(21,22,23, size = 4))+
-  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
-  # #geom_errorbar(width=0.1)+
-  scale_x_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
-  scale_y_continuous(limits = c(-4,7), 
-                     breaks = c(-4, 0, 2.5, 4, 5.9),
-                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
-  guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency MAP (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-```{r habituals-predictive-endorsement}
-d.hab.predictive.endorsment <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
-d.hab.predictive.endorsment.catch <- read.csv(paste(
-  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
-  group_by(condition) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'baseline')
-
-d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'preventative')
-
-d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
-  filter(condition == 'enabling')
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment, 
-  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
-  by = "workerid"
-  ) %>% filter(pass==1) %>%
-  mutate(response = ifelse(response=="agree-key", 1, 0),
-         time_period = factor(time_period,
-                              levels=c("month",
-                                       "2 months",
-                                       "year",
-                                       "2 years",
-                                       "5 years")),
-         condition = factor(condition,
-                            levels=c("enabling", "baseline", "preventative")),
-         hab_time = paste(habitual, time_period, sep='-')) %>%
-  rename(item = habitual) %>%
-  group_by(item, condition, hab_time, time_period) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-
-d.hab.predictive.endorsment.summary <- left_join(
-  d.hab.predictive.endorsment.summary,
-  d.hab.predictive.summary %>%
-    rename(logAnnualFutureRate = mean,
-         future_lower = ci_lower, future_upper = ci_upper)
-  # rs.habituals.bda.predictive.summary %>% 
-  #   filter(key == "logannualRate") %>%
-  #   rename(logAnnualFutureRate = MAP,
-  #        future_lower = cred_lower, future_upper = cred_upper)
-  # %>%
-  #   rowwise() %>%
-  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
-  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
-)
-
-r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
-mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
-                                          "logAnnualFutureRate", "MAP_h")
+```
+
+```{r habituals-predictive-endorsement, cache = F}
 
@@
 
-```
-
-```{r habituals-predictive-rsa}
+fig.hab.endorse.vs.predfreq
+```
+
+```{r habituals-predictive-rsa, cache = F}
 n_chains <- 3
@@
 
-```{r fig.height = 6, fig.width=14, echo = F, eval=F}
-m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
-  #filter(type == "predictive", C == "endorsement") %>%
-#  mutate(E = as.numeric(as.character(E))) %>%
-  ggplot(., aes(x = val, fill = D))+
-  geom_histogram(position = position_dodge())+
-  #facet_grid(B~E)+
-  facet_grid(D~B)
-```
-
-```{r, eval = F}
-m.hab.predfreq.summary <- m.hab.pred.samp %>%
-  filter(type == "predictive", C == "predictiveFreq") %>%
-  group_by(B, D, E) %>%
-  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)
-
-left_join(m.hab.predictive.endorse.rsa %>%
-  mutate(src = factor(src, levels = c( 
-                                      "past_model",
-                                      "predictive_model"
-                                     ),
-                      labels = c(
-                                 "Endorsement model (past frequency)",
-                                 "Endorsement model (predictive frequency)"
-
-                                 ))) %>%
-  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
-```
-
 ```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
@@
 Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
-We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r r.hab.pred.past.baseline.freq`$). 
+We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r format(r.hab.pred.past.baseline.freq, digits = 3)`$). 
 That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
@@
 
-```{r habituals-predictive-elicitation-predictions}
+```{r habituals-predictive-elicitation-predictions, eval=F}
 lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 

### 2018-02-08 paper/case3-causals.Rmd
port over more code into scripts

@@
 -->
+
+```{r}
+genericEndorsementPriorModelHelpers <- '
+var eps = 0.01;//Number.EPSILON;
+var log = function(x){ return Math.log(x) }
+var exp = function(x){ return Math.exp(x) }
+
+var avoidEndPoints = function(x){
+  x == 0 ? eps : 
+  x == 1 ? 1 - eps : 
+  x
+}
+
+var betaShape = function(params){
+  return {
+      a: params.g * params.d,
+      b : (1-params.g) * params.d
+  }
+}
+
+var preprocessedResponses = map(function(d){
+  return avoidEndPoints(d / 100)
+}, data)
+'
+
+structuredPriorModel <- '
+var model = function(){
+  var phi = uniformDrift({a:0, b: 1, width:0.2});
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  var transientComponent = Beta({a:1, b:100})
+  mapData({data: preprocessedResponses}, function(d){
+    factor( log(
+      phi * exp(stableComponent.score(d)) +
+      (1 - phi) * exp(transientComponent.score(d))
+    ))
+  })
+  return {g, d, phi}
+}
+'
+
+unstructuredPriorModel <- '
+var model = function(){
+  var g = uniformDrift({a:0, b: 1, width:0.2});
+  var d = uniformDrift({a:0, b: 100, width:5});
+  var stableParams = betaShape({g, d})
+  var stableComponent = Beta(stableParams)
+  mapData({data: preprocessedResponses}, function(d){
+    factor(stableComponent.score(d))
+  })
+  return {g, d}
+}
+'
+genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
+```
+
+```{r rsaHelpers}
+rsaHelpers <- '
+var probability = function(Dist, x) {
+    return Math.exp(Dist.score(x));
+}
+var targetUtterance = "generic";
+
+var round = function(x){
+  return Math.round(x*1000)/1000
+}
+var utterancePrior = Infer({model: function(){
+  return uniformDraw([targetUtterance,"silence"])
+}});
+
+var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
+// var thetaBins = [
+//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
+ // ]
+var thetaPrior = Infer({model: function(){
+ return uniformDraw(thetaBins)
+}});
+
+var bins = map(round, _.range(0.01, 0.99, 0.01))
+
+// var bins = [
+  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
+// ];
+
+var meaning = function(utt,state, theta) {
+  return utt=="generic"? state > theta :
+         utt=="generic is false"? state<=theta :
+         utt=="silence"? true :
+         utt=="some"? state>0.01:
+         utt=="most"? state> 0.5:
+         utt=="all"? state >= 0.99:
+         true
+}
+
+var mixture = data.prior.mix[0];
+var priorParams = data.prior.params[0];
+
+var statePrior = Infer({model: function(){
+  var component = flip(mixture);
+  return component ?
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta(priorParams), b) + Number.EPSILON
+      }, bins )
+    }) :
+    categorical({
+      vs: bins,
+      ps: map(function(b) {
+        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
+      }, bins )
+    })
+}});
+'
+```
+
+```{r rsaInterpretationModels}
+no.utterance.model <- '
+var noUtteranceInterpreter = function() {
+  Infer({model: function(){
+   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+    return { state }
+ }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+'
+
+fixed.threshold.model <- '
+var fixedThresholdInterpreter = function(threshold) {
+  Infer({model: function(){
+  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+  var state = sample(statePrior)
+  condition( state > threshold)
+    return {
+      state: state
+  }
+ // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+ }, method: "enumerate"})}
+'
+
+uncertain.threshold.model <- '
+var uncertainThresholdInterpreter = function() {
+  Infer({model: function(){
+   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
+    factor( Math.log(state) )
+    return {
+      state: state, 
+  }
+  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+'
+
+```
+
+```{r simulationCalls}
+fixed.threshold.calls <- '
+_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
+'
+no.utterance.call <- ' 
+  noUtteranceInterpreter()
+'
+uncertain.threshold.call <- '
+  uncertainThresholdInterpreter()
+'
+```
 

### 2018-02-09 paper/case2-habituals.Rmd
refashion predictive habituals figure

@@
 ```{r habitual-endorsment-scatters}
-#View(md.hab)
-
 habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
@@
 
-```{r}
+```{r loadCase2PredictiveData, cache =F}
 load("cached_results/case2_predictive_data.RData")
@@
 ```{r fighabfreq_predictive_vs_past, cache = F}
-fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
+fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary %>%
+                                            ungroup() %>%
+                                            mutate(condition = factor(condition,
+                                                                      levels = c("preventative", "baseline", "enabling"))) %>%
+                                            mutate(src = 'Manipulation check'),
        aes(x=logAnnualPastRate,
@@
                               fill = condition, shape=condition))+
-  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
+  geom_jitter(position = position_jitter(width = .13), size = 4)+
   scale_shape_manual(values=c(21,22,23))+
@@
                      labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
+  facet_wrap(~src)+
   guides(fill=F, shape=F)+
-  scale_fill_solarized()+
-  xlab("Past frequency (log scale)")+
-  ylab("Predicted frequency (log scale)")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-```
-
-```{r habituals-predictive-endorsement, cache = F}
+  scale_fill_viridis(discrete = T)+
+  xlab("Past frequency")+
+  ylab("Predicted frequency")+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+        axis.title.x = element_text(vjust = 1),
+        axis.title.y = element_text(vjust = 1))
+```
+
+```{r habituals-predictive-endorsement, cache = F, eval = F}
 
@@
     )
-
-fig.hab.endorse.vs.predfreq
-```
-
-```{r habituals-predictive-rsa, cache = F}
+```
+
+```{r habituals-predictive-rsa, cache = T, eval=T}
 n_chains <- 3
@@
 
+```{r habituals-predictive-endorsement-bars}
+pred.items.of.interest <- c("climbs mountains","steals cars", "steals chewing gum",
+                            "writes novels", "hikes","plays the banjo",
+                            "smokes marijuana","runs","watches space launches",
+                            "smokes cigarettes","drinks coffee")
+
+habituals.endorsement.pred.bars <- m.hab.predictive.endorse.allModels %>%
+  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
+         src =factor(src , levels = c("human data","predictive_model", "regression_pastfreq",
+                                      "regression_futurefreq","past_model"),
+                     labels= c("Human data", "Uncertain semantics  \n(Predictive frequency)", "regression_pastfreq",
+                               "Regression              \n(Predictive frequency)", "Uncertain semantics\n(Past frequency)      ")),
+         hab_time = gsub("-","\n(", hab_time),
+         hab_time = paste(hab_time, ")", sep = ""),
+         hab_time = factor(hab_time, 
+                           levels = c("climbs mountains\n(5 years)","steals cars\n(5 years)", "steals chewing gum\n(5 years)",
+                            "writes novels\n(5 years)", "watches space launches\n(2 years)", "hikes\n(year)","plays the banjo\n(year)",
+                            "smokes marijuana\n(year)","runs\n(2 months)","drinks coffee\n(month)",
+                            "smokes cigarettes\n(month)"))) %>%
+  filter(src != "regression_pastfreq",
+         item %in% pred.items.of.interest) %>%
+ggplot(., 
+       aes (y = MAP, ymin = cred_lower, ymax = cred_upper, 
+            x = hab_time, fill = condition))+
+  #geom_abline(intercept = 0, slope = 1, lty = 3)+
+  #geom_linerange(alpha = 0.15)+
+  geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
+  geom_linerange(alpha = 0.7, size = 1, position = position_dodge(0.7))+
+  #geom_point(shape = 21, size = 3)+
+  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  scale_fill_viridis(discrete = T)+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  #coord_fixed()+
+  ylab("Habitual endorsement")+
+  xlab("Item (past frequency: 3 times per interval)")+
+  facet_grid(src~., scales = 'free')+
+  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
+        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45,
+                                   lineheight = 0.7),
+        legend.position = "bottom")
+```
+
+```{r habituals-predictive-endorsement-scatters, cache = F}
+habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
+  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
+         src =factor(src , levels = c("human data", "regression_pastfreq",
+                                     "past_model", "regression_futurefreq",
+                                      "predictive_model"),
+                     labels= c("Human data","regression_pastfreq", 
+                                "Uncertain semantics (Past)", "Linear model (Predictive frequency)","Uncertain semantics (Predictive)"))) %>%
+  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
+ggplot(., 
+       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
+            y = MAP_h, ymin= low, ymax = high, fill = condition,
+            shape = condition))+
+  geom_abline(intercept = 0, slope = 1, lty = 3)+
+  #geom_linerange(alpha = 0.15)+
+  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
+  geom_linerange(alpha = 0.7, size = 1)+
+  geom_errorbarh()+
+  geom_point(size = 3)+
+  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_shape_manual(values=c(21,22,23))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  scale_fill_viridis(discrete = T)+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  coord_fixed()+
+  ylab("Habitual endorsement")+
+  xlab("Model prediction")+
+  facet_grid(.~src, scales = 'free')+
+  theme(legend.position = "right")
+```
+
 ```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
 Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 13, fig.height = 3.5, cache=F}
-legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))
-
-# add the legend underneath the row we made earlier. Give it 10% of the height
-# of one plot (via rel_heights).
-
+Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 14,  fig.asp = 0.6, cache=F}
 plot_grid(
+  habituals.endorsement.pred.bars +
+    theme(plot.margin = unit(c(6,6,6,6), "pt"), legend.position="none",
+          axis.title.x = element_blank()),
   plot_grid(
     fig.hab.freq.predictive.vs.past + 
-      theme(plot.margin = unit(c(6,3,6,6), "pt")),
-  fig.hab.endorse.vs.predfreq + 
-    theme(plot.margin = unit(c(6,0,6,6), "pt")),
-  # habituals.predictive.past.model + 
-  #   theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab(""),
-  habituals.predictive.predictive.model + 
-    theme(plot.margin = unit(c(0,0,6,0), "pt")) + 
-    theme(legend.position="none") + ylab(""),
-  align = 'h', axis = 'l',
-  labels = c("A","B","C"),
-  #hjust = -1,
-  nrow =1 , rel_widths = c(1.2, 0.95, 1.6)),
-  legend_b, nrow = 2, rel_heights = c(1, 0.2))
-
-  #legend_b
+     theme(plot.margin = unit(c(0,6,0,0), "pt"), legend.position="none",
+           axis.text = element_text(size = 8),
+           axis.title = element_text(size = 9)),
+    habituals.endorsement.pred.scatters +
+      theme(plot.margin = unit(c(0,0,12,12), "pt"),
+            legend.position = c(1.1,1.1)),
+    labels = c("B", "C"),
+    nrow = 1,  axis = 'tblr', rel_widths = c(1, 1.8)), 
+  labels = c("A", ""), 
+  nrow = 2, align = 'v', axis = 'lr', rel_heights = c(3.1, 1.5))
 ```

### 2018-02-09 paper/comgen-paper.Rmd
streamline and restructure most of discussion

@@
 Our framework naturally accounts for a number of logically puzzling category generalizations, or *generics* (Expt. 1).
-We provide an avenue for top-down moderators on language use, by elucidating the scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
+We provide an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
 Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
@@
 <!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
-The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization (operationalized in terms of the likelihood function) from background, world knowledge (the prior).
+The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from background, world knowledge.
 This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
@@
 
-Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations.
-That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding speaker beliefs or listener prevalence distributions, which can occur for multiple reasons (e.g., by changing the comparison class).
-We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed. 
-In Expt. 3 we showed that these prevalence distributions are causally related to endorsement.
-
 <!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
@@
 <!-- The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.  -->
+
+## Prior knowledge and kind representations
+
+Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted and that the language interfaces directly with *prevalence*.
+Previous psychological and philosophical work on generics has looked beyond prevalence and focused kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
+Indeed, we agree that generics are about kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge.
+This background knowledge can very well presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties.
+In other situations, relevant background knowledge may be merely correlational in nature.
+The important commonality among such different possible domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language gets to interface with.
+Thus, our theory provides a clean separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
+
+<!-- Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations. -->
+<!-- That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding speaker beliefs or listener prevalence distributions, which can occur for multiple reasons (e.g., by changing the comparison class).
+-->
+<!-- We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed.  -->
+<!-- In Expt. 3 we showed that these prevalence distributions are causally related to endorsement. -->
+
+Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
+We do not assume a particular view of natural kinds in our theory, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory.
+Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement.
+
+In our modeling work, we found that empirical data that underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
+Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
+It is likely that the actual conceptual knowledge against which generalizations are interpreted is far-richer than simply a two-component mixture-model.
+We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in classic philosophical cases as well as in our empirical endorsement data.
+
+Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the *goals of communication*, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud].
+Our simple endorsement model assumes that the goal of communication is the prevalence.
+That is, the endorsement decision is about the *prevalence* information conveyed to the listener.
+This idealization will surely be elaborated in 
+Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context.
+We note, however, that the endorsement model makes almost identical predictions if the QUD is assumed to be about the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
+This finding is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
+
+<!-- Primarily investigated through generic language (category generalizations), this perspective holds that generics are the linguistic outlet of the mind's default mode of representing kinds [@Leslie2007] and "...an adequate account of the meanings of generic sentences requires an understanding of the ways in which we represent connections between kinds and properties [p.406; @Prasada2013]." -->
+<!-- @Prasada2006 and later @Prasada2013 distinguish properties that have *principled connections* to kinds, *statistical connections*, and *causal connections*.  -->
+
+<!-- Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread. -->
+<!-- Prasada has argued that *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white") are  -->
+<!-- Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring.  -->
+<!-- Where in the probability-based semantics could such conceptual distinctions come into play? -->
+
+<!-- Inferential role semantics -->
+<!-- We take the view the causal relations only does anything because it implies statistical regularities, and these statistical regularities are what our linguistic model depends on. -->
+
+<!-- - what are habituals like under Leslie? -->
+
+<!-- probabilistic treatment of kinds vs. of causality -->
+<!-- conceptual representation vs. causal structure -->
+
+<!-- rational rules: concepts are relatively definitional (with some probabilistic structure on those definitions) -->
+<!-- - leslie: my kinds are your probabilistic concept representations -->
+<!-- - the reason why particular generics are licensed. not that there are kinds and that generics communicate about them. -->
+  <!-- - fundamentally communicative element to what the prevalence is and why a generic would sound good in a praticular case (information relative to the prevalence prior) -->
+
+<!-- - Ellen: causality implies a mechanism, not just a statistical relation. -->
+<!-- - are there parts of the  -->
+<!-- - essentialism: different generative models that imply the same statistics with different causal relations (but orthogonal) -->
+
+## Communicating predictive probabilities
+
+This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
+We distinguish this construct from other uses of *prevalence* in the literature, namely the usage as synonymous with frequency.
+<!-- the distinction that what is communicated is probability not frequency. -->
+<!-- In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category.  -->
+Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+Predictions about the presence of a feature can be the result of internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
+What matters for their influence on generic endorsement, we posit, is their influence on subjective, predictive probability or *prevalence*.
+
+<!-- Expts.
+2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
+-->
+
+Communicating probabilities might seem contrary to the long attested phenomena of failures in reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995].
+Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
+Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].
+
+<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
+This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
+-->
+
+<!-- ### The Problems with Communicating Generalizations -->
+
+<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
+<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
+<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
+-->
+<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
+
+<!-- Generalizations can be made about almost anything. -->
+<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
+-->
+<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
+
+<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
+-->
+<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
+-->
+
+<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
+-->
+<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
+
+<!-- ### Statistical Accounts of Generics -->
+
+<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
+<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
+<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
+<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
+<!-- Let's first introduce some notation: -->
+
+<!-- ### Conceptual Accounts of Generics -->
 
@@
 -->
-
-Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the goals of communication, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud].
-Our simple endorsement model assumes that the goal of communication is the prevalence.
-This idealization will surely be elaborated in richer communicative contexts. 
-It is noteworthy, however, when using a structured model of the prior (e.g., a mixture model), as we have used throughout this paper, that the endorsement model makes almost identical predictions if the QUD is assumed the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
-
-## Structured prior knowledge
-
-<!-- -- add tomasello about learning about how to take turns, as a generalization about an event type which is the event of how the game is supposed to be played -->
-
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].
-Prasada has argued for a distinction between *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white").
-Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread.
-Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring. 
-Where in the probability-based semantics could such conceptual distinctions come into play?
-
-We found that empirical prevalence distributions are best modeled as a mixture-model. 
-Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
-It is likely that conceptual knowledge is far-richer than our simple two-component mixture-model, though a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our data.
-<!-- influences these distributions, such as higher-order conceptual knowledge about the nature of properties and categories [@Gelman2003; @Keil1992]. -->
-Indeed, conceptual structure in general, including higher-order abstractions, can be captured by probabilisitic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-Future work will be needed to explore how probabilistic representations of conceptual knowledge can capture the relations identified in other accounts of generics (such as principled, essential, and striking properties), and whether the effect of these relations can then be adequately described via their impact on prevalence priors.
-
-## Communicating predictive probabilities
-
-This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category. 
-We make the distinction that what is communicated is probability not frequency.
-Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-<!-- Expts.
-2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
--->
-
-Communicating probabilities might seem contrary to a basic tenet in cognitive psychology, that human cognition falls short when reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995].
-Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
-Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
 
@@
 
-## Relationship to other theories
+## Relationship to other semantic theories
 
 To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the linguistics and psychological literatures.
+A number of other theories of genericity have been proposed in the formal semantics  literatures.
 <!-- We now turn to situating our account with respect to these previous theories. -->
@@
 
-### Conceptual accounts
-
-Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
-These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties.
-That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
+The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 was described above.
+We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
+Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
+For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
+We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: probability.
+
+<!-- ### Conceptual accounts -->
+
+<!-- Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+-->
+<!-- These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties. -->
+<!-- That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
+-->
+
 <!-- If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar". -->
 
-The most influential conceptual account of generics is from @Leslie2007.
-For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
-Leslie's "default mode" comes equipped with the ability to single-out *striking properties* (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
-Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about.
-
-This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
-Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
+<!-- The most influential conceptual account of generics is from @Leslie2007. -->
+<!-- For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
+-->
+<!-- Leslie's "default mode" comes equipped with the ability to single-out *striking properties* (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
+-->
+<!-- Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about. -->
+
+<!-- This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
+-->
+<!-- Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
 1 for naturalistic cases).
-In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
+-->
+<!-- In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
 3a), we have observed that the prior distribution over the prevalence $P(h)$ change when supplied information about the dangerousness of the feature.
-That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors. 
-Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features.
+-->
+<!-- That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors.  -->
+<!-- Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features. -->
 <!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
@@
 
-Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs").
-Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young)
-The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist. 
-For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
-In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
-Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
-
-Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world. 
-"Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters.
-"Barns are red" because most barns are red.
-If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green".
-Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.
-
-Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations.
-In the last fifteen years, there has been tremendous progress in formalizing 
-Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011]. 
-For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations).
-@Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.
-
-In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
-In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).  
-It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here.
+<!-- Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs"). -->
+<!-- Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young) -->
+<!-- The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist.  -->
+<!-- For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
+-->
+<!-- In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
+-->
+<!-- Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
+-->
+
+<!-- Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world.  -->
+<!-- "Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters. -->
+<!-- "Barns are red" because most barns are red. -->
+<!-- If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green". -->
+<!-- Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.  -->
+
+<!-- Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations. -->
+<!-- In the last fifteen years, there has been tremendous progress in formalizing  -->
+<!-- Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011].
+-->
+<!-- For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations). -->
+<!-- @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.  -->
+
+<!-- In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
+-->
+<!-- In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).   -->
+<!-- It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here. -->
+
 <!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence across different categories. -->
 <!-- This minimally structured model  -->
-
-The key point of divergence then between the conceptual accounts and our view concerns the core, semantic meaning of a generic statement.
-Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this provides a more unifying view of generics, giving a single metric as the basic currency of generic meaning: probability.
 
@@
 
-### Statistical accounts
-
-#### Relative and absolute generics
+<!-- ### Statistical accounts -->
+
+### Relative and absolute generics
 
@@
 
-#### "Normal" accounts
+### "Normal" accounts
 
@@
 
-#### Underquantification
+### Underquantification
 
@@
 
-#### Generic as indexical
+### Generic as indexical
 

### 2018-02-09 paper/comgen-paper.Rmd
cleaning first 3rd of discussion

@@
 
-As a formal theory of generalizations in language, we aim to unify significant swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
-<!-- What these expressions have in common is *genericity*, the fact that these statements convey generalizations.  -->
-We have formalized a unified, core meaning using the underlying scale of predictive probability or *prevalence*.
-We showed that all three kinds of generalizations exhibit the same kind of sensitivity to context (Expt. 1, 2a \& 2b, 3).
-Our framework naturally accounts for a number of logically puzzling category generalizations, or *generics* (Expt. 1).
-We provide an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt. 2c).
+As a formal theory of the language of generalization, our framework aims to unify large swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
+<!-- What these expressions have in common is not surface features but generalization (also referred to as *genericity*). -->
+We have formalized a unified, core meaning of generalization in language using the underlying scale of predictive probability or *prevalence*.
+We showed that endorsements of all three types of generalizations exhibit the same sensitivity to a background distribution comprised of other categories (Expt. 1, 2a \& 2b, 3).
+As well, our framework naturally accounts for a number of logically puzzling category generalizations (Expt.
+1) and provides an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt.
+2c).
 Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
@@
 
-In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a probabilistic model with structured, prior knowledge.
+In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a communicative model with shared background knowledge.
 Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
@@
 This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
-Our model formalizes a simple semantics for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
-That is, we provide a route for precise quantitative influence of conceptual structure on generic language by way of shared background knowledge between speakers and listeners [c.f., @Leslie2008].
-In the rest of this discussion, we elaborate some key features of the theory that warrant future investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
+Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
+That is, we provide a route for precise quantitative influence of conceptual knowledge on generic language by way of shared background knowledge between speakers and listeners.
+In the rest of this discussion, we elaborate some key features of the theory that warrant further investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
 
@@
 
-Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted and that the language interfaces directly with *prevalence*.
+Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted.
+Given this representation of background knowledge (*prevalence prior*), language interfaces with conceptual knowledge via *prevalence*. 
 Previous psychological and philosophical work on generics has looked beyond prevalence and focused kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Indeed, we agree that generics are about kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge.
-This background knowledge can very well presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties.
+Indeed, we see generics as describing kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge, formalized with by prevalence prior.
+In the right situations, this shared background knowledge can presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties [a la @Prasada2013].
 In other situations, relevant background knowledge may be merely correlational in nature.
-The important commonality among such different possible domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language gets to interface with.
-Thus, our theory provides a clean separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
+
+Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
+We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory.
+The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
+Thus, our theory provides a separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*. 
+Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.
 
@@
 
-Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
-We do not assume a particular view of natural kinds in our theory, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory.
-Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement.
-
-In our modeling work, we found that empirical data that underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
-Such a prior distribution draws qualitative distinctions (with respect to the feature) between different kinds of categories by virtue of the model representing multiple distinct components. 
-It is likely that the actual conceptual knowledge against which generalizations are interpreted is far-richer than simply a two-component mixture-model.
-We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in classic philosophical cases as well as in our empirical endorsement data.
-
-Rational models of communication, of the kind we have developed in this paper, make explicit a speaker's assumptions about the *goals of communication*, sometimes referred to as the Question Under Discussion or QUD [@roberts1996qud].
-Our simple endorsement model assumes that the goal of communication is the prevalence.
-That is, the endorsement decision is about the *prevalence* information conveyed to the listener.
-This idealization will surely be elaborated in 
-Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context.
-We note, however, that the endorsement model makes almost identical predictions if the QUD is assumed to be about the more abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
-This finding is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
+In our modeling work, we found that the empirical data which underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
+Such a prior distribution draws qualitative distinctions between different kinds of categories by virtue of the prevalence prior model representing multiple distinct components. 
+Actual conceptual knowledge against which generalizations are interpreted is most likely far-richer than simply a two-component mixture-model.
+We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our empirical data.
+
+The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
+Our simple endorsement model assumes that the goal of communication is the prevalence (Eq.\ref{eq:S1}).
+In other words, the endorsement decision is computed with respect to the prevalence information conveyed to the listener.
+Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced.
+We note, however, that the endorsement model makes almost identical predictions if the QUD in the model is assumed to be about the abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
+This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
 
@@
 Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-Predictions about the presence of a feature can be the result of internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
-What matters for their influence on generic endorsement, we posit, is their influence on subjective, predictive probability or *prevalence*.
+Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
+What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
 
@@
 
-Communicating probabilities might seem contrary to the long attested phenomena of failures in reasoning about probability [@Tversky1974].
+Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
 Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995].
-Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*, which are easier to understand and quite useful for statistical reasoning.
-Given the relationship to *vague language* (described above), we argue that the utterance "70% of birds fly" is analagous to saying that "John is 6'3"", while saying "Birds fly" is more similar to saying "John is tall".
+Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*.
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
 The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good about reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Gweon2010; @Dewar2010].
+Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Xu2008; @xu2009statistical].
 
@@
 
-Our model of an interpreter, or naive listener, has access to implicit statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
-The prevalence priors for a property, event, or cause are constructed by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
+The probabilistic communicative model we introduce in this paper assumes shared background 
+<!-- Our model of an interpreter, or naive listener, has access to implicit  -->
+statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
+We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(h)$ is constructed with respect some comparison class $C$: $P_C(h)$.
+Thus, the prevalence prior $P(h)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(h \mid C)$.
 
@@
 Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
-However, like the semantics of generalizations, the other entities or categories that comprise the comparison class are underspecified.
-
-Uncertainty about the comparison class adds yet more flexibility to generalizations.
-Even if interlocutors coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other *other categories* in the class.
-That is, our model makes the prediction that the acceptance or rejection of the statement "Humans cause global warming" or "Muslims are terrorists" depends upon a speaker's beliefs about how other forces (e.g., plate tectonics) influence the climate or how often other categories (e.g., neo-nazis) commit acts of terrorism.
-In Expt. 3, we demonstrated the influence of other categories on endorsement of a generalization.
+An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
+
+Uncertainty about the comparison class adds yet more opportunity for miscommunication, deceit, or just faultless disagreement to the language of generalization.
+Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other categories in the comparison class.
+That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis commiting acts of terrorism).
+In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of a generalization.
 Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.
 
-Interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but *how* the comparison class should be constructed.
-The comparison classes used in our case studies were with respect to the target *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit Question Under Discussion [QUD; @roberts1996qud] of "*what* has feature?".
-Were the QUD to be reversed (e.g., "what features does category have?"), the comparison classes would need to be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
-The same sentence can be used to address multiple QUDs [@KrifkaGenericBookFocus], giving rise to multiple distinct comparison classes.
+Finally, interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but the very nature of *how* the comparison class should be constructed.
+The comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
+Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
+It's long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
 The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
-In this work, we focused on category-wise comparison classes for methodological convenience.
+In this work, we focused on category-wise comparison classes purely for methodological convenience.
 Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.
@@
 
-Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common they are in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
+Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
 <!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generic language [@Leslie2008].
+This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generalizations  [@Leslie2008].
 
 Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
-The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three aspects of meaning: 
-(1) the *dimension* being described (i.e., the probability $h$),
+The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three distinct aspects of meaning: 
+(1) the *dimension* being described (i.e., probability $h$),
 (2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
@@
 Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
-However, for generalizations, no fixed threshold is required; the language of generalization is acquired once aspects (1) and (2) are learned.
+However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
-This informal analysis predicts that a child would first acquire generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
-
-There is a secondary argument for why the semantics we posit presents an easy learning problem.
+This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
+
+There is a secondary argument for why our semantics presents an easy learning problem.
 <!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
 -->
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree, in this prevalence $h$ itself: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
+Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $h$: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
 This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
@@
 
+### Generic as indexical
+
+@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
+The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
+Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
+We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
+
 ### "Normal" accounts
@@
 
-### Generic as indexical
-
-@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
-The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
-Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
-We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
-
 # Conclusion

### 2018-02-09 paper/comgen-paper.Rmd
finish editing discussion

@@
 
-We aimed to balance two competing goals in designing our experimental stimuli: (1)  including familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model.
+In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model vis-a-vis alternative models.
 In this section, we discuss how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
@@
 Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
-That is, the statement "Mary has handled mail from Antarctica" is false.
-Sentence (1) is still thought to be true despite zero actual instances of the event.
-We think (1) is a boundary case of generalizations expressing predictive probabilities, which we elucidated in Expt. 2c.
-In in that study, we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
-We expect the same to be true here, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
+That is, the statement "Mary *has handled* mail from Antarctica" is false.
+Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
+In our framework, we treat Sentence (1) is a boundary case of generalizations expressing predictive probabilities.
+In Expt.
+2c., we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
+We expect the same to be true with Mary, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
 Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
 
-Our focus on predictive probability makes even new prediction about some classic puzzles.
+Our focus on predictive probability makes even novel predictions about some classic puzzles.
 Sentence (2) is the conceptual opposite of sentence (1).
 Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (2) is still considered false, every though the property holds in 100\% of the category [@Cohen1999].
-We predict this phenomenon is the result of abstract, intuitive theories guiding us to reject observed frequencies in forming our subjective probabilities.
-That is, because observers strongly believe selection for the Supreme Court is not influenced by one's social security number, speakers would assign a roughly 50\% subjective probability that the \emph{next} justice would have an even social security number.
-Then, given that the all professions would have roughly the same probability of having employees with even social security numbers, Sentence (2) would be similar to "Birds are female". 
+Sentence (2) is still considered false, every though the property holds in exactly 100\% of the category [@Cohen1999].
+We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective probabilities.
+That is, because observers strongly believe one's social security number does not infleunce selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
+Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated similarly by our model as "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
@@
 @Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Stastistical account of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
-However, this is the only interpretation if the generalization is given a fixed, majority based quantificational account (e.g., if the generic means *most*).
-Our theory does not provide a fixed semantics for the generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with prior knowledge weighting against the existence of *international elephants* and without any further semantic assumptions, our model infers that some elephants live in Africa and others live in Asia (and they are different elephants).^[
+Stastistical accounts of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
+This is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics (e.g., if the generic means *most*).
+Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
+In fact, with prior knowledge pushing against the existence of *international elephants* and without any further semantic assumptions, our model can interpret Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
   An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
 ]
-Importantly, the model believes that most lives in Africa, when it only hears that "Elephants live in Africa", and only later revises it's beliefs to a weaker "some"-like interpretation after hearing they live in Asia as well.
-Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise interpretation of single utterances.
+Importantly, an incremental parsing of Sentence (3) leads our model to first believe that *most* elephants live in Africa (when it only hears that "Elephants live in Africa"), and then later believe that *some* elephants live in Africa (while others live in Asia) after hearing the end of the utterance ("...and Asia").
+Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 
@@
 Why?
-A first observation is that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset ("paperbacks" is short-hand for "paperback books"). 
-We expect intuitions about this statement to generalize to other examples expressing an analogous relation (e.g., "Pastas are spaghetti", "Animals are humans").
-We hypothesize that the strangeness of these examples has to do an inflexible relationship between the comparison class and the referent-prevalence.
-Assume that the comparison class is constructed by considering the *predicability* of the property [in the sense of @Keil1979, originally from @Sommers1963].^[
+We first observe that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset (i.e., "paperbacks", or "paperback books"). 
+We hypothesize that the strangeness of this example has to do an inflexible relationship between the comparison class and the referent-prevalence.
+Assume that the comparison class is constructed by considering the *predicability of the property* [in the sense of @Keil1979, originally from @Sommers1963].^[
   Note that this assumption is consistent with the comparison classes we have assumed in our three case studies.
@@
 Then, "is a paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
-  Note that this idea is similar to @Cohen1999's notion of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his   Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
+  Note that this idea is related to @Cohen1999's notion of "Relative generics" (described more fully below), which have truth conditions that are determined by a comparison to an alternative set of Ks (his   Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an alternative set of Fs.
 ]
-The relevant aggregations of entities, then, are collection of books, potentially including books of different genres or publication eras among other such sub-categories.
-Then, given that "books" is the superordinate category of "kinds of books", the referent-category prevalence cannot be different from the mean of the prevalence prior.
-Finally, given this prevalence prior and the referent-prevalence, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in the a way analogous to "Robins are female".
+The relevant aggregations of entities (i.e., of individual books), then, are collections of books (e.g., books of different genres or publication eras among other such sub-categories).
+Then, given that "books" is the superordinate category of "kinds of books", the referent-category prevalence (the % of books that are paperbacks) is the mean of the prevalence prior (the average of the % of sub-classes of books that are paperbacks).
+Given this prevalence prior and the referent-prevalence, our endorsement model would predict "Books are paperbacks" is neither true nor untrue, in a way analogous to "Robins are female". 
+We expect these intuitions to generalize to other examples expressing an analogous relation (e.g., "Pastas are spaghetti", "Animals are humans").
 
@@
 
-Finally, sometimes a property is widespread relative to other kinds or groups, and it might be so systemic that we would believe it to be the case in the future, but speakers still might find it avertise to actually endorse the generalization.
+Finally, a property can be widespread relative to other kinds or groups as well as being so systemic that we would predict it to be the case in the future, and speakers still might find it aversive to actually endorse the generalization.
 Such is the situation with Sentence (5) [@Haslanger2011]. 
@@
 In our **Model Simulations** section, we showed that the genearlization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
-If the generic conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth. ^[
-  Note that this can straight-forwardly capture the central phenomena of @Cimpian2010.
-].
-The current formulation of the model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated in the mind of the listener).
-However, if states of the world (or, listener's beliefs about states of the world) correspond to different subjective values, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
+If the generalization conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth [@Cimpian2010].
+The current formulation of our model is relatively ambivalent about the deviations of the listener's beliefs from the speaker's belief (i.e., the speaker doesn't mind that the prevalence that she believes to be true will be exaggerated in the mind of the listener).
+However, if states of the world (or, listener's beliefs about states of the world) have different *subjective values*, speakers who take into the account the subjective utilities of the listener may produce language that deviates from what a pure informational transmission speaker might say.
 This kind of extension to rational models of communication has already been used to account for a variety of phenomena in *polite language* use [@Yoon2016; @Yoon2017].
-We propose adopting such a value-based utility structure for states of the world for language about social categories: If the speaker found states of the world where the probability of the feature is high (e.g., a world where many women were submissive) as undesirable, then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
-We find this possibilitity intruiging and leave it for future work.
-
-In sum, we've tried to argue that our information-theoretic communicative model couched in general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
+We propose adopting such a value-based utility structure for states of the world for language about social categories: If the speaker found states of the world where the probability of the feature is high as undesirable (e.g., a world where many women were submissive), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
+
+In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
 The precise implementation of these hypotheses we leave for future work.
@@
 -->
-These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to structured, conceptual representations (e.g., *there is something about being K which causes it to F*).
+These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
 
-The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 was described above.
+The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
 We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
@@
 For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: probability.
+We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
 
@@
 
-<!-- We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
--->
-<!-- His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).  -->
-<!-- For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...). -->
-<!-- Therefore, "Robins lay eggs" is evaluated as an *absolute generic* because only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
--->
-<!-- The inferential machinery behind Cohen's domain restriction (i.e., what comrpises $Alt(F)$?) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[ -->
-<!--   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks found in cognitive science.
--->
-<!-- ] -->
-<!-- However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
--->
-<!-- Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.  -->
+We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
+His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
+For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
+"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+The inferential machinery behind Cohen's domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
+]
+However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
 
@@
 
-@Sterken2015 has recently proposed an intruiging account of the context-sensitive of generic language by treating generics as a kind of *indexical* (e.g., "this" or "I").
-The variability of endorsements is then attributed to mechanisms of domain restriction (described above with @Cohen1999) and context-sensitive "quantificational force".
-Our uncertain-threshold semantics may be a precise formalization of @Sterken2015's "quantificational force" (and a generalization of *underquantification*, see above), and we have argued above that domain restriction is not a necessary mechanisms for the cases considered in this paper.
-We leave for future work exploring how the context-sensitivity of an indexical may differ from the kind of context-sensitivity in our model.
+@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analagous to *indexicals* (e.g., "this" or "I").
+Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restrictor [of the kind used by @Cohen1999, and many others].
+Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive "quantificational force". 
+We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
+<!-- Finally, how the context-sensitivity of an indexical differs from the kind of context-sensitivity with an uncertain-threshold is an important question for future research. -->
 
@@
 
-The primary alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
+A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
 For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
@@
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
-We showed in Expt. 2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations. 
-Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.
+<!-- We showed in Expt.
+2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations.
+-->
+<!-- Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.  -->
 
@@
 Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
-This distinction is relevant for the acquisition of the language of generalizations; we do not think that quantified relations (e.g., "Some", "All") are in any way primary or special. 
+This distinction is relevant for the acquisition of the language of generalizations; we do not take as primary the quantified relations (e.g., "Some", "All").
 <!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
 -->
-Additionally, by using a vague, underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
+Additionally, by using an underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
 
@@
 Shouldn't speakers and teachers want to express their ideas as crisply as possible?
-To the contrary, underspecification can be efficient, given that context can be used to resolve  uncertainty in meaning [@Piantadosi2012].
-In our work, context takes the form of shared beliefs about the property in question. 
-By leveraging this common ground, genericity provide a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong generalization to a naive listener.
+To the contrary, underspecification can be efficient, given that context can be relied upon to resolve uncertainty in the moment [@Piantadosi2012].
+In our work, context takes the form of shared beliefs between speakers and listeners. 
+By leveraging this common ground, the language of generalizations provide a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
+
+The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong impression to a naive listener.
 Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which could be differences in the prior distributions on prevalence or the comparison class.
+Disagreements are also predicted when interlocutors fail to share background assumptions, which could manifest as differences in the prior distributions on prevalence or what goes into the comparison class.
 Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).
-This is a promising area for future research.
+This is an important area for future research.
 

### 2018-02-10 paper/comgen-paper.Rmd
edits to full model section up until simulations

@@
 Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
-In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
-This prediction can be described by a conditional probability: $p_{fk} = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the **prevalence**.
-In particular, we define prevalence as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
+People readily predict that a new dog will have fur, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
+In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
+This prediction can be described by a conditional probability: $p(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence*.
+In particular, we define *prevalence* as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a particular day of the week).
 The properties also vary (e.g., having fur, causing jitters, going to the gym).
-Yet the mathematical description of the inductive belief is always given by a probability $p_{fk}$.
-
-How does one acquire such an inductive belief?
-If you observe creatures that *have two legs*, you might infer that all creatures of that kind have two legs.
-But not all properties have such strong projectibility or prevalence.
-Seeing a creature with *broken wings* tells you much less about other instances of the category having broken wings [@Nisbett1983].
-This kind of domain-specific knowledge about properties can be represented formally as a probability distribution over the prevalence $p_{f}$: $P(p_{f})$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})$
-
-Learning from observational evidence can only take you so far, though. 
-To learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically rare (e.g., *lightning strikes tall objects*), one would much rather learn from others.
-Fortunately, language has simple ways of encoding generalizations.
+Yet the mathematical description of the inductive belief is always given by a probability $p(f \mid k)$.
+
+How do we come to know things? How does one acquire inductive beliefs?
+If you *observe* wugs that have two legs, you might infer that all wugs have two legs.
+But not all properties have such strong projectibility (prevalence).
+Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
+Abstract, potentially domain-specific, beliefs about properties can be represented by a probability distribution over the prevalence $P(p_{fk})$ [@Kemp2008].^[
+  We adopt the following notational conventions: $p_{fk} = p(f \mid k)$ as prevalence of feature $f$ for a category $k$. 
+]
+Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and their beliefs about the generative process that resulted in the observed data given some prevelance (the likelihood: $P(d \mid p_{fk})$).
+
+We do not always have access to observational data $d$.
+Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
+Fortunately, language provides simple ways of communicating generalizations.
 
@@
 
-## Generalization from language
-
-The language of generalization manifests when a property is predicated of a category: "Ks F" (e.g., "Dogs bark", "Staring at the sun makes you go blind"). 
-Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
-To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
-One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
-A threshold semantics for a generalization about category K with property F would then apply to the *prevalence* $p_{fk}$:
-$\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$
-Various attempts of this kind have been made before [e.g., @Cohen1999].
-We distinguish our proposal from previous ones by emphasizing the predictive nature of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+## The language of generalization
+
+The language of generalization is easy to spot when a property is predicated of a category: "Ks F" (e.g., "Dogs bark").
+This is often called *generic language* or *generics* [@Carlson1977].
+But generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
+Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an intance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
+  We adopt this somewhat idiosyncratic categorization in order to emphasize the different semantic types predicated. 
+  Some authors refer to all of these types as *generics*.
+  Still, however, the primary "generic" investigated in the literature are generalizations about categories ("Ks F").
+]
+Psychologists, linguists, and philosphers have long studied the language of generalization, as it appears very simple (e.g., syntactically) and yet challenging to formalize.
+
+If generalization from observations can be described by a probability $p_{fk}$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
+The semantic tools of *truth values* provide a way to update a state of knowledge by relating the semantic quantity (probability) to  Boolean values [@Montague1973].
+The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
+Thus, the simplest semantics for a generalization about category K with property F is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.
+
+Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has been made to make precise, quantitative predictions about adult judgments.
+In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantic hypothesis in order to update its beliefs about the world. 
+We then ask: When would a rational speaker choose to produce a generalization (vs. staying silent) to update the Bayesian model's state of knowledge?
+
+<!-- We distinguish our proposal from previous ones by emphasizing the predictive nature of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+-->
 <!-- $p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->
@@
 
-Quantifier statements can be described using a similar threshold semantics: $\denote{some \text{ } K \text{ } F}(p_{fk}) = \{p_{fk} > 0\}; \denote{all \text{ } K \text{ } F} = \{p_{fk} = 1\}$.
-So what threshold $\theta$? should be used for the generalizations? 
-Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$.
-That is, we hypothesize that $\theta$ is in part determined by contextual, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
-
-We formalize this underspecified semantics in a probabilistic model, where the underspecifed threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013].
-After making explicit the relevant background knowledge about the property $P(p_f)$, the model becomes:
+The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what is the semantic variable $\theta$?
+Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}; \denote{all} = \{p_{fk} = 1\}$.
+The extreme flexiblity of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no threshold would suffice. 
+Indeed, no particular threshold would suffice: The semantics of the language of generalizations is *underspecified*.
+To resolve this underspecification, we hypothesize that $\theta$ is determined by context, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+
+<!-- So what threshold $\theta$? should be used for the generalizations?  -->
+<!-- Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$. -->
+
+We can formalize this underspecified semantics in a Bayesian cognitive model, where the underspecifed threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013; @Lassiter2015].
+This model also has prior knowledge about the property $P(p_f)$ and so literal interpretation is given by updating these prior beliefs according the (underspecified) truth-functional meaning of utterance $u$:
 
 \begin{eqnarray}
-Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{f}, \theta)} \cdot P(p_{f}) \cdot P(\theta)} \label{eq:L0}
+Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{fk}, \theta)} \cdot P(p_{fk}) \cdot P(\theta)} \label{eq:L0}
 \end{eqnarray}
 
-Equation \ref{eq:L0} ($Lit$) is a literal interpretation model, that updates its beliefs about the prevalence of a feature in the category described $p_{fk}$ according to the truth-functional meaning of the utterance $u_{KF}$.
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
+Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.
 
@@
 
-Given the minimal model of literal interpretation described above, how do we decide when a statement conveying a generalization is true or not?
-We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of production? 
+Given the above model of literal interpretation described above, how do we decide when a statement conveying a generalization is true or not?
+We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
 We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0})^[
@@
 
-The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$): $Lit(p_{fk}, \theta \mid u)$.
-$S$ is not interested in communicating $\theta$ (in fact, it does not know $\theta$), and so integrates over the values of $\theta$.
-We assume the decision to endorse is an approximately rational one, with degree of rationality given by $\lambda$.
+The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p_{fk}, \theta \mid u)$.
+$S$ does not know $\theta$ and integrates over the interpreter posterior beliefs about $\theta$.
+We assume the decision to endorse is approximately rational, with degree of rationality given by $\lambda$.
 The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
 We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [cf., @Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$^[
+"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [@Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$.^[
   This "null" alternative to the generalization ("Ks F") can be realized in at least two other ways: the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not F").
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $p_{fk}$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{KF} \mid p_{fk})$.
+\ref{eq:S1}) provides a mapping from a *referent-category prevalence* $p_{fk}$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{KF} \mid p_{fk})$.
 The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
@@
 
-### Prevalence priors and referent-prevalence
-
-Our model makes context-sensitive predictions about endorsing generalizations based on two model components: The prevalence priors $P(p_f)$ in Eq.
+### Prevalence priors
+
+The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
+\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_fk)$---with the truth-functional semantics.
+Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitious with any referent-prevalence. 
+However, the interpretation model's *a priori* beliefs $P(p_fk)$ must be considered before the endorsement model can say whether or not it would endorse the statement.
+
+<!-- Our model makes context-sensitive predictions about endorsing generalizations based on two model components: The prevalence priors $P(p_fk)$ in Eq.
 \ref{eq:L0} and the referent-prevalence $p_{fk}$ in Eqs.
 \ref{eq:S1} and \ref{eq:delta}.
-Referent-prevalence is the probability that an individual $x$ of the referent-category (e.g., "Dogs") will have the feature being predicated of the category (e.g., "...barks").
-We will return and refine this definition in Case Study 2, when considering generalizations about events.
-For now, the referent-prevalence is simply a probability that determines the truth-conditional semantics. 
-Our hypothesis does not provide a mapping from the referent-prevalence directly to endorsement judgments, however, because $\theta$ is underspecified.
-
-The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating prior beliefs about the feature in question---the *prevalence prior* $P(p_f)$---with the truth-functional semantics.
-Again, $P(\theta)$ is set to be a uniform distribution across all contexts, and thus, the generalization could in principle be felicitious with potentially any referent-prevalence. 
-However, interpretation model's *a priori* beliefs $P(p_f)$ must be considered before the endorsement model can say whether or not it would endorse the generalization.
+-->
+<!-- Referent-prevalence is the probability that an individual $x$ of the referent-category (e.g., *dogs*) will have the feature being predicated of the category (e.g., *barks*). -->
+<!-- We will return and refine this definition in Case Study 2. -->
+<!-- For now, the referent-prevalence is simply a probability that determines the truth-conditional semantics.  -->
+<!-- Our hypothesis does not provide a complete mapping from the referent-prevalence directly to endorsement judgments, however, because $\theta$ is underspecified. -->
+
+<!-- These internal models may have domain-specific features but can be described by the domain-general currency of inductive belief: probability. -->
 
 Beliefs about properties result from internal conceptual models of the world. 
-These internal models have domain-specific features but should all give to the domain-general currency of inductive reasoning: probability.
-One way of constructing prior distributions over prevalence, without appealing directly to domain-specific conceptual knowledge, is by considering the prevalence of the feature among different categories.
+With appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
 For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because what one would expect for a randomly-sampled category is that it has 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the prevalence prior should have substantial mass at relatively high values, potentially with quite a bit of uncertainty; Figure\ \@ref(fig:simulations)A; first row).
-Conceptual differences can manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since most animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
-*Cue validity* implicitly encodes knowledge of other categories and has been shown to be  highly correlated with endorsing *generic sentences*, or generalizations about categories [@Khemlani2012].
-Cue validity is defined for a particular (category, property) pair (as is referent-prevalence), and relates to referent-prevalence by Bayes' Rule:
-\begin{equation}
-P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')} \label{eq:cuevalidity}
-\end{equation}
-Since *cue validity* implicitly encodes knowledge of other categories (by summing over $k'$) and the prevalence prior explicitly encodes knowledge of other categories, how are these two constructs related?
-In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
-Thus, $P(p_{fk}) = P(k_{f})$.
-The denominator of Eq.
-\ref{eq:cuevalidity} (which encodes knowledge of other categories), then, is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$.
-For a more thorough derivation of this relationship, see Appendix A.
-The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potential shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
-This is particularly problematic for prevalence distributions that encode conceptual knowledge via multimodal distributions (e.g., Fig.
+Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have substantial mass at relatively high prevalences, potentially with some uncertainty; Figure\ \@ref(fig:simulations)A; first row).
+Abstract beliefs between different kinds of categories would manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a robin, upon learning that it lays eggs).
+*Cue validity* implicitly encodes knowledge of other categories, by averaging over other categories $k'$ via Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$ and has been shown to be highly correlated with endorsements of generalizations about categories, or *generics* [@Khemlani2012].
+Since cue validity is defined for a particular (category, property) pair, it can be seen as a point estimate of the prevalence prior distribution.
+In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})]$.
+For a slower derivation of this relationship, see Appendix A.
+
+<!-- Since *cue validity* implicitly encodes knowledge of other categories (by summing over $k'$) and the prevalence prior explicitly encodes knowledge of other categories, how are these two constructs related?
+-->
+<!-- In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
+-->
+<!-- Thus, $P(p_{fk}) = P(k_{f})$. -->
+
+<!-- cut on 2/9: -->
+<!-- The fact that the prevalence prior distribution relates only via its mean value to *cue validity* reveals a potential shortcoming of cue validity: By reducing a distribution to a point estimate, the structure of the distribution is lost.
+-->
+<!-- This is particularly problematic for prevalence distributions that encode conceptual knowledge via multimodal distributions (e.g., Fig.
 \@ref(fig:simulations)A; bottom row); the mean of a multimodal distribution is not a good representation of that distribution.
-We return to this point empirically in Case Study 1.
+-->
+<!-- We return to this point empirically in Case Study 1. -->
 

### 2018-02-12 analysis/model-simulations.Rmd
add figure showing uniform prior simulation in detail

@@
 
+```{r saveResults}
+#save(sims.priors, sims.uncertain.thresholds, sims.fixed.thresholds,s1.simulations.relabeled, file = "../paper/cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData")
+```
+
+# Schematic (uniform prior) figure
+
+```{r schematicModel}
+schematicModel <- '
+var round = function(x){
+  return Math.round(x*100)/100
+}
+
+var isNegation = function(utt){
+  return (utt.split("_")[0] == "not")
+};
+
+var avoidEnds = function(x){
+  return x >= 1 ? 0.99 : x == 0 ? 0.01 : x
+}
+
+var lb = 0, ub = 1, diff = 0.05;
+var bins = _.range(lb, ub + diff, diff)
+
+var DiscreteBeta = function(a, b){
+  Infer({model: function(){
+    categorical({
+      vs:bins,
+      ps:map(function(x){
+        Math.exp(Beta({a, b}).score(avoidEnds(x)))
+      }, bins)
+    })
+  }})
+}
+
+var utterances = [
+  "gen",
+  "null"
+];
+
+var utterancePrior = Infer({model: function(){
+  return uniformDraw(utterances)
+}});
+
+var meaning = function(words, state, threshold){
+  return words == "gen" ? state > threshold :
+  true
+};
+
+var speakerOptimality = 3;
+var speakerOptimality2 = 1;
+
+var fixedThetalistener0 = cache(function(utterance, threshold) {
+  Infer({model: function(){
+    var state = sample(DiscreteBeta(1, 1));
+    var m = meaning(utterance, state, threshold);
+    condition(m);
+    return state;
+  }})
+}, 10000);
+
+var greaterThanThresholdBins = _.range(lb, ub, diff)
+var lessThanThresholdBins = _.range(lb+diff, ub+diff, diff)
+
+var litInterpreter = cache(function(utterance) {
+  Infer({model: function(){
+    var threshold = uniformDraw(greaterThanThresholdBins)
+
+    var state = sample(DiscreteBeta(1, 1));
+    var m = meaning(utterance, state, threshold);
+    condition(m);
+    return state
+  }})
+}, 10000);
+
+var speaker1 = cache(function(state) {
+  Infer({model: function(){
+    var utterance = sample(utterancePrior);
+    var L0 = litInterpreter(utterance);
+    factor(speakerOptimality*L0.score(state));
+    return utterance;
+  }})
+}, 10000);
+'
+
+listenerCall <- '
+_.fromPairs(map(function(u){
+  var post = litInterpreter(u)
+  return [u, post]
+}, utterances))
+'
+
+speakerCall <- '
+_.flatten(
+    map(function(s){
+      var speakProbs = speaker1(s)
+       return {  
+          state: s,
+          "gen": Math.exp(speakProbs.score("gen")),
+          "null": Math.exp(speakProbs.score("null"))
+        }
+    }, bins)
+)
+'
+
+literalListenerCall <- '
+_.flatten(_.flatten(
+map(function(tH){
+    var l0posterior = fixedThetalistener0("gen", tH)
+    display(expectation(l0posterior))
+    map(function(s){
+       return {  
+          state: s,
+          theta:tH, 
+          literalPosterior: Math.exp(l0posterior.score(s))
+        }
+    }, bins)
+}, greaterThanThresholdBins)
+))
+'
+```
+
+### Fixed thresholds
+
+```{r schematicFixed}
+rs.wp.l0 <- webppl(paste(schematicModel, literalListenerCall,  sep = '\n'))
+
+fig.l0.thresholds <- ggplot(rs.wp.l0, aes( x = state, 
+                                           y = literalPosterior, 
+                                       group = theta))+
+  geom_line(size = 2)+
+  geom_vline(aes(xintercept = theta), 
+             color = 'darkred', size = 2)+
+  #scale_color_solarized()+
+  scale_x_continuous(breaks = c(0, 0.5, 1))+
+  scale_y_continuous(breaks = c(0, 0.5, 1))+
+  #scale_color_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  ggtitle("truth-functional threshold = ")+
+  ylab("Literal listener posterior probability")+
+  xlab("Degree of happiness")+
+  facet_wrap(~theta)+
+  theme(text = element_text(size = 16))
+```
+
+Integrate out threshold (full interpretation model)
+
+```{r schematicUncertain}
+rs.listener.wp <- webppl(paste(schematicModel, listenerCall,  sep = '\n'))
+
+rs.listener.wp.tidy <- bind_rows(
+  data.frame(rs.listener.wp$gen) %>% 
+    mutate(utterance = "gen"),
+  data.frame(rs.listener.wp$null) %>% 
+    mutate(utterance = "null")
+)
+
+rs.listener.wp.tidy.samples <- get_samples(
+  rs.listener.wp.tidy %>% rename(prob = probs), 10000)
+
+ggplot(rs.listener.wp.tidy.samples, 
+       aes( x = support,fill = utterance, color = utterance))+
+  geom_density(alpha = 0.4, size = 1.3)+
+  scale_fill_solarized()+
+  scale_color_solarized()+
+  xlab("prevalence")+
+  ylab("Posterior probability density")+
+  scale_x_continuous(breaks =c(0, 1))+
+  scale_y_continuous(breaks = c(0, 2))+
+  #guides(fill = F, color = F)+
+  ggtitle("prevalence posterior")
+
+#ggsave("figs/lassiterL1_posteriors_wCost1,5_alpha1.png", width = 6, height = 4)
+```
+
+```{r schematicEndorsement}
+rs.wp <- webppl(paste(schematicModel, speakerCall,  sep = '\n'))
+
+rs.tidy <- data.frame(rs.wp) %>%
+  gather(utt, prob, -state)
+
+fig.thresholds <- ggplot(rs.tidy %>%
+                           mutate(utt = factor(utt,
+                                               levels=c("null","gen"))), 
+                         aes( x = state, y = prob, fill = utt))+
+  geom_col( 
+           color = 'black')+
+  #facet_wrap(~happy_theta)+
+  scale_x_continuous(breaks = c(0, 0.5, 1))+
+  scale_y_continuous(breaks = c(0, 0.5, 1))+
+  ggtitle("truth-functional threshold = ")+
+  ylab("Speaker probability of saying 'happy'")+
+  xlab("Degree of happiness")+
+  theme(text = element_text(size = 16))+
+  scale_fill_solarized()
+
+fig.thresholds
+#ggsave(fig.thresholds, 
+ #      file = "figs/lassiterS1_uttXstateXtheta_wCost.pdf", width = 7, height = 7)
+```
+
 ```{r}
-save(sims.priors, sims.uncertain.thresholds, sims.fixed.thresholds,s1.simulations.relabeled, file = "../paper/cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData")
+save(rs.wp.l0, rs.listener.wp.tidy.samples, rs.tidy,
+     file = "../paper/cached_results/modelSims-uniform_fixedT_uncertainT_speaker.RData")
 ```

### 2018-02-12 paper/comgen-paper.Rmd
add figure showing uniform prior simulation in detail

@@
 ---
-title             : "The language of generalization: Probability, vagueness, and interaction"
+title             : "The language of generalization"
 shorttitle        : "The language of generalization"
@@
 
-Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that a new dog will have fur, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
+Generalizations are used to make predictions about properties of instances or events that an agent has yet to experience [@HumeTHN].
+People readily predict that the next dog will have fur, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
@@
 In particular, we define *prevalence* as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a particular day of the week).
+The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
 The properties also vary (e.g., having fur, causing jitters, going to the gym).
@@
 
-How do we come to know things? How does one acquire inductive beliefs?
+<!-- How do we come to know things?  -->
+How does one acquire inductive beliefs?
 If you *observe* wugs that have two legs, you might infer that all wugs have two legs.
@@
 ]
-Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and their beliefs about the generative process that resulted in the observed data given some prevelance (the likelihood: $P(d \mid p_{fk})$).
-
-We do not always have access to observational data $d$.
+Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data (the likelihood: $P(d \mid p_{fk})$).
+
+But we do not always have access to observational data $d$.
 Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
@@
   Some authors refer to all of these types as *generics*.
-  Still, however, the primary "generic" investigated in the literature are generalizations about categories ("Ks F").
+  Still, however, the primary "generics" investigated in the literature have been generalizations about categories ("Ks F").
 ]
-Psychologists, linguists, and philosphers have long studied the language of generalization, as it appears very simple (e.g., syntactically) and yet challenging to formalize.
+Psychologists, linguists, and philosphers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
+  We take up the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
+  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
+  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
+]
 
@@
 
-Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has been made to make precise, quantitative predictions about adult judgments.
-In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantic hypothesis in order to update its beliefs about the world. 
+Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has made precise, quantitative predictions about adult judgments.
+In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantics in order to update its beliefs from language.
 We then ask: When would a rational speaker choose to produce a generalization (vs. staying silent) to update the Bayesian model's state of knowledge?
@@
 
-The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what is the semantic variable $\theta$?
+The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what threshold is appropriate?
 Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}; \denote{all} = \{p_{fk} = 1\}$.
-The extreme flexiblity of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no threshold would suffice. 
-Indeed, no particular threshold would suffice: The semantics of the language of generalizations is *underspecified*.
+The extreme flexiblity of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
+Indeed, no particular threshold can suffice: The semantics of the language of generalizations is *underspecified*.
 To resolve this underspecification, we hypothesize that $\theta$ is determined by context, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
@@
 
-We can formalize this underspecified semantics in a Bayesian cognitive model, where the underspecifed threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [cf., @Lassiter2013; @Lassiter2015].
-This model also has prior knowledge about the property $P(p_f)$ and so literal interpretation is given by updating these prior beliefs according the (underspecified) truth-functional meaning of utterance $u$:
+We can formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
+The model also has prior knowledge about the property $P(p_f)$ and so literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
 
@@
 
-Given the above model of literal interpretation described above, how do we decide when a statement conveying a generalization is true or not?
+Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
 We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
@@
 The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p_{fk}, \theta \mid u)$.
-$S$ does not know $\theta$ and integrates over the interpreter posterior beliefs about $\theta$.
-We assume the decision to endorse is approximately rational, with degree of rationality given by $\lambda$.
+$S$ does not know $\theta$ and integrates over the interpreter's posterior beliefs about $\theta$.
+Following Bayesian decision theory, we assume the decision to endorse is approximately rational, with degree of rationality given by $\lambda$.
 The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
@@
 \ref{eq:S1}).
-This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.
+This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016] with only a single level of recursion and the space of possible utterances maximally constrained; the endorsement model is a "speaker", while the interpretation model is a "listener".
 
@@
 The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_fk)$---with the truth-functional semantics.
+\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_fk)$---with the underspecified semantics.
 Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitious with any referent-prevalence. 
-However, the interpretation model's *a priori* beliefs $P(p_fk)$ must be considered before the endorsement model can say whether or not it would endorse the statement.
+However, the interpretation model's *a priori* beliefs $P(p_fk)$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
 
@@
 <!-- Our hypothesis does not provide a complete mapping from the referent-prevalence directly to endorsement judgments, however, because $\theta$ is underspecified. -->
-
 <!-- These internal models may have domain-specific features but can be described by the domain-general currency of inductive belief: probability. -->
@@
 Beliefs about properties result from internal conceptual models of the world. 
-With appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because what one would expect for a randomly-sampled category is that it has 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have substantial mass at relatively high prevalences, potentially with some uncertainty; Figure\ \@ref(fig:simulations)A; first row).
-Abstract beliefs between different kinds of categories would manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; bottom row).
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a robin, upon learning that it lays eggs).
-*Cue validity* implicitly encodes knowledge of other categories, by averaging over other categories $k'$ via Bayes' Rule:
-$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$ and has been shown to be highly correlated with endorsements of generalizations about categories, or *generics* [@Khemlani2012].
-Since cue validity is defined for a particular (category, property) pair, it can be seen as a point estimate of the prevalence prior distribution.
+Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
+For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would a randomly-sampled category to have 0 or close to 0 exemplars that bark.
+Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have substantial mass at relatively high prevalences, potentially with some uncertainty; Figure\ \@ref(fig:simulations); row 1, column 1).
+Abstract beliefs between different kinds of categories would manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; row 1, column 4).
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
+This statistic has been shown to be highly correlated with endorsements of generalizations about categories, or *generics* [@Khemlani2012].
+*Cue validity* implicitly encodes knowledge of other categories, by averaging over those categories $k'$ via the normalizing constant in Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
+Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
 In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})]$.
@@
 We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-The following simulations were implemented using the R package RWebPPL in the RMarkdown document that generated this paper text and figures.
-That document, as well as all other models, analysis, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
 
@@
 load("cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData") # sims.priors, sims.fixed.thresholds, sims.uncertain.thresholds, s1.simulations.relabeled
+load("cached_results/modelSims-uniform_fixedT_uncertainT_speaker.RData") # rs.wp.l0, rs.listener.wp.tidy.samples, rs.tidy
 
@@
 
-```{r simulations, fig.cap = "Computational model simulations.
+```{r uniformPriorSimulation, fig.cap = "Computational model behavior.
+A: Interpretation model posteriors assuming different fixed thresholds.
+High thresholds rule out more world-states (prevalence levels), leaving fewer world-states among which to distribute the full probability mass.
+B: Full interpretation model marginalizes over possible thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
+C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
+
+fig.l0.thresholds <- ggplot(rs.wp.l0 %>% 
+                              mutate(theta = round(theta, 2)) %>%
+                              filter(theta %in% c(0, 0.25, 0.50, 0.75)), aes( x = state, 
+                                           y = literalPosterior, 
+                                       group = theta))+
+  geom_line(size = 1)+
+  geom_vline(aes(xintercept = theta), 
+             color = 'darkred', size = 1)+
+  scale_x_continuous(breaks = c(0, 1))+
+  scale_y_continuous(breaks = c(0, 0.2))+
+  ylab("Posterior probability mass")+
+  xlab("Prevalence")+
+  facet_wrap(~theta, nrow = 1)+
+  ggtitle("Fixed-threshold interpretations")
+
+fig.fullInterpretation = ggplot(rs.listener.wp.tidy.samples %>%
+                           mutate(utterance = factor(utterance,
+                                               levels=c("null","gen"),
+                                               labels =c("silence", "generalization"))), 
+       aes( x = support,fill = utterance, color = utterance))+
+  geom_density(alpha = 0.4, size = 1.3)+
+  scale_fill_solarized()+
+  scale_color_solarized()+
+  xlab("Prevalence")+
+  ylab("Posterior probability density")+
+  scale_x_continuous(breaks =c(0, 1))+
+  scale_y_continuous(breaks = c(0, 1.5))+
+  guides(fill = guide_legend(reverse = T), color = guide_legend(reverse = T))+
+  ggtitle("Uncertain-threshold interpretation")+
+  theme(legend.position = c(0.25, 0.8))
+
+fig.endorsement.thresholds <- ggplot(rs.tidy %>%
+                           mutate(utt = factor(utt,
+                                               levels=c("null","gen"))), 
+                         aes( x = state, y = prob, fill = utt, color = utt))+
+  geom_col(size = 1, alpha = 0.4, color= 'black')+
+  scale_x_continuous(breaks = c(0, 0.5, 1))+
+  scale_y_continuous(breaks = c(0, 0.5, 1))+
+  ylab("Endorsement probability")+
+  xlab("Prevalence (Speaker beliefs)")+
+  ggtitle("Endorsement predictions")+
+  scale_fill_solarized()+
+  scale_color_solarized()+
+  guides(fill = F, color = F)
+
+cowplot::plot_grid(
+  fig.l0.thresholds,
+  fig.fullInterpretation,
+  fig.endorsement.thresholds,
+  nrow = 1, labels = c("A", "B", "C"),
+  align = 'h',
+  rel_widths = c(1.5, 1, 1)
+)
+```
+
+```{r simulations, fig.cap = "Model simulations assuming different prevalence priors.
 Top: Prior distributions over the prevalence of a feature for 6 example features.
@@
 
-The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$ (Figure\ \@ref(fig:simulations)B).
-Low thresholds (e.g., $\theta = 0.1$) rule out very few possibilities (only $p_{fk} \leq 0.1$), and thus are quite likely given that its consistent with much of the prevalence prior.
-The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be similar to staying silent (a posterior not very different from the prior).
-Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
-
-The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds.
-The prevalence-based interpretations of generalizations of novel categories are shown in Figure\ \@ref(fig:simulations)C.
-These interpretations depend heavily on the prevalence priors (different rows).
-Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (top row; pink).
-"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (4th row; green).
-The literal interpreter can also derive very weak interpretation, as shwon in the  \textsc{carries malaria} distribution (bottom row, purple).
-
-The endorsement model (Eq. \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs).
-Predictions for a few classic examples from the generics literature are shown in (Figure\ \@ref(fig:simulations)D).
+The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
+Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior. 
+If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
+As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:simulations)A).
+The uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
+The endorsement model thus predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevealence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
+
+<!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
+<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p_{fk} \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
+-->
+<!-- Higher thresholds  (e.g., $\theta = 0.75$) rule out many possibilities; an interpretation with this threshold has correspondingly less uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, right).
+-->
+<!-- The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be, from an information-theoretic perspective, similar to staying silent (a posterior not very different from the prior).
+-->
+<!-- Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
+-->
+<!-- The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds. -->
+
+The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
+Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
+"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
+The interpretation model can also derive very weak interpretation, as shown in the  *carries malaria* distribution (column 6).
+
+The endorsement model (Eq.
+\ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
+Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations).
 In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
 Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
-To understand this prediction, examine the interpretation distribution for the \textsc{are female} distribution: It is identical with the prior (Figure\ \@ref(fig:simulations) A vs.
-C; blue distributions).
+To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs. bottom row).
 The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
@@
 
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the prevalence $p_{fk}$ communicated. 
-We chose schematic values for each of these, and saw that the endorsement model recapitulates standard intuitions about the truth or falsity of classic examples from the generics literature.
+These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the referent-prevalence $p_{fk}$ communicated. 
+We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
 In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).

### 2018-02-12 paper/case2-habituals.Rmd
tweaks habituals figs

@@
 ```{r habituals-priors-subfigs, fig.width = 8}
-example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
+example.habituals <- c(#"smokes marijuana", 
+                       "smokes cigarettes","drinks coffee",
                        "climbs mountains", "hikes", "runs", 
-                       "wears a suit", "wears a watch", "wears socks", 
-                       "writes poems", "goes to the movies", "plays the banjo"
+                       #"wears a suit", "wears a watch", "wears socks", 
+                       #"writes poems", 
+                       "goes to the movies"#, "plays the banjo"
                        )
@@
   scale_color_solarized()+
+  geom_point()+
   geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
@@
                     filter(item %in% example.habituals, gender == "female"), 
-                  inherit.aes =F,
-                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 3)+
-  geom_point()+
+                  inherit.aes =F, segment.alpha = 0.1,label.size = 0.15,
+                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 2)+
   coord_fixed()+
@@
 ```{r habituals-endorsement-bars, fig.width = 8}
-habituals.endorsement.bars <- ggplot(md.hab.long, aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
+habituals.endorsement.bars <- ggplot(md.hab.long %>%
+                                       mutate(src = factor(src, levels = c(
+                                         "Human data", "Uncertain semantics",
+                                         "Fixed semantics", "Referent frequency",
+                                         "Distinctiveness +\n referent frequency"
+                                       ))), aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
                   x = time_period, fill = logAnnualRate))+

### 2018-02-12 paper/comgen-paper.Rmd
edits to intro

@@
 
-Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world.
-Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-It thus is important that language allow us to communicate such *generalizations* to each other.
-By sharing generalizations, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Flexibly communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].
+<!-- Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world. -->
+Extracting generalizable knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
+Yet such knowledge can be difficult to acquire: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
+Fortunately, we are not bound to acquiring generalizations on our own; language allow us to communicate generalizations between each other.
+By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
+Furthermore, flexibly communicating generalizations from one generation to the next may be a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].
 
@@
 
-The language of generalization is often studied via *generic language* (or, *generics*): simple statements predicating properties of categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
-Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008]. 
-In contrast to *particular statements* (e.g., "Rufus is friendly") which describe individual entities or situations and can be verified through observation, generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dogs}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
+Certain linguistic expressions encode generalizations.
+The *language of generalization* is most commonly studied with *generic language* (or, *generics*), generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+<!-- Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].  -->
+In contrast to statements about concrete individuals or events (e.g., "Rufus is friendly"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the here and now, a fact which children as young as 2 appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
@@
 Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-Every language, it is believed, can express generalization [@Behrens2005; @Carlson1995] and is central to the growth of conceptual knowledge [@Gelman2004].
-Considering generalization as a singular phenomenon in language, thus, promises to provide understanding of a wide variety of linguistic expressions with powerful implications.
+It is believed every language can express generalization [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
+<!-- Thus, an understanding of the language of generalization that extends to a wide variety of types (e.g., categories, events, causes)  -->
+
+<!-- Thus, an understanding of generalization as a singular phenomenon in language  -->
+<!-- promises to provide an understanding of a wide variety of linguistic expressions with rich meanings. -->
 
@@
 
-Despite their ubiquity and relative simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions.
-The major challenge in formalization is determining *what makes the statements true or false*.
+Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions.
+The major challenge in formalizing generalization in language is determining *what makes the statements true or false*.
 When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless^[
-http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html
-], for example.
+But the property does not apply to all dogs: Basenji dogs are barkless,
+<!-- ^[ -->
+<!-- http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html -->
+<!-- ],  -->
+for example.
 The generalization could signal something weaker like "Most dogs bark".
@@
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only quantifier that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to mean "some" is too permissive: some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
+The only *quantifier* that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
+But weakening the generalization to mean "some" is too permissive: Some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
 Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
 
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only parameter in the meaning of generalizations.
-Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
+The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
+<!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+-->
 "Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
-It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false.
-One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature. 
-Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature.
-*Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true
-
-Yet, generics convey more than just rich, conceptual relations [@Nickel2008; @Nickel2016; @Sterken2015]. 
-Purely arbitrary relationships can result in true generics.
-<!-- Arbitrary relationships are also expressed with generics:  -->
-"Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false.
-Ravens and toasters have no priviledged relationship to each other, but the statement "Ravens are bigger than toasters" is still a true generalization.
-Conceptual accounts must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [e.g., @Prasada2013].
+The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013].
+<!-- It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false. -->
+<!-- One such primitive is the ability to priviledge *characteristic features*: For an animal, their mode of reproduction is a characteristic feature.  -->
+<!-- Thus, whatever their mode of reproduction may be will make a true generic statement (e.g., "Robins lay eggs"), regardless of the actual prevalence of the feature. -->
+<!-- *Horrifying* or *striking* information is also priviledged and creates true generics, which is why "Mosquitos carry malaria" is true -->
+
+Yet, purely arbitrary relationships can result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
+Ravens and toasters have no priviledged relationship to each other, but "Ravens are bigger than toasters" is still true.
+An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.
+
+<!-- Furthermore, how conceptual accounts of the language of generalizations should extend beyond category generalizations (i.e., generics) is less clear.  -->
+<!-- "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. -->
+
+What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
 But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
@@
 Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would use when understanding such language.
+To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
 We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
 The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-Though concepts such as *striking properties* are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
+Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
 
@@
 In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
-The endorsement model's predictions depend upon the background knowledge and the probability communicated, which we demonstrate via simulation.
+The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
 Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and the probability communicated, measuring their effects on endorsement. 
+Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
 We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alterantive models fall short.
-This work opens the door to understanding generalizations in pragmatic language understanding contexts and building models of learning from language.
+This work opens the door to understanding generalizations in richer, pragmatic language understanding contexts and building models that learn abstract knowledge from language.
 

### 2018-02-12 paper/case3-causals.Rmd
spell checking and some tweaks to causals

@@
 Language about causal relationships manifests in generalization.
-The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analagous to how "John smokes" relates to  "John smoked yesterday". 
+The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analogous to how "John smokes" relates to  "John smoked yesterday". 
 We explore this hypothesis in our third case study: causal language or *causals* (e.g., "A causes B").
 
-The problem of *causal induction*---knowing that one thing causes another----has been studied extensively in human psychology  [@Cheng1992; @Cheng1997; @Griffiths2005; @Griffiths2009].
+The problem of *causal induction*---knowing that one thing causes another---has been studied extensively in human psychology  [@Cheng1992; @Cheng1997; @Griffiths2005; @Griffiths2009].
 Classically, this is cast as a problem of inducing an unobservable relation (*type causation*) from observable events or contingency data. 
@@
 Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or plants grow tall). 
-Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the proprety (e.g., a naturally occurring herb causing animals to be sleepy).
-The two cover stories can be seen in Table \@ref(tab:causalItems).
+Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the property (e.g., a naturally occurring herb causing animals to be sleepy).
+The two cover stories can be seen in Table 1.
 
-Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure \@ref(fig:causals-conditions). 
+Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure \@ref(figure-causals)B. 
 In two of the conditions, participants saw results that came from the same underlying distribution.
@@
 -->
-The two other conditions used distributions in which some experiments resulted in either no or very few succeses (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
+The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
 These are the "rare strong" and "rare weak" conditions.
@@
 }
-\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
+\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3}
 \end{table}
@@
 
-Participants see the results of eleven "experiments", though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)). 
+Participants see the results of eleven "experiments", though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
 (These lost results would be found in the *causal endorsement* task, Expt. 3b).
@@
 `r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
-The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure \ref{fig:figure-causals}.
+The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure \ \@ref(fig:figure-causals).
 These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
@@
 In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-Most of the experimental deisgn was identical to that of Experiment 3a.
+Most of the experimental design was identical to that of Experiment 3a.
 
@@
 Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Partipants responded by either clicking "Yes" or "No". 
+Participants responded by either clicking "Yes" or "No". 
 After responding, participants completed the same attention check as Expt. 3a.
@@
 In our third case study, we applied our same model to generalizations about causal events.
-In this domain, we succesfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
+In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
 This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
 In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ is causally related to endorsements of generalizations in language.
+In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(p_{fk})$ is causally related to endorsements of generalizations in language.
 To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
@@
 ]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analagous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analgous to our "rare" prior conditions.
+For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analogous to our "deterministic" priors conditions. 
+Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our "rare" prior conditions.
 Our theory would predict in these cases that differences in endorsement would be attributable to differences in the prevalence prior distribution (here: the belief distribution over causal power).

### 2018-02-12 paper/comgen-paper.Rmd
clean intro; tweak model and discussion

@@
 <!-- Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world. -->
-Extracting generalizable knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
-Yet such knowledge can be difficult to acquire: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
+Acquiring understanding that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
+Yet such knowledge can be difficult to extract from the environment: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
 Fortunately, we are not bound to acquiring generalizations on our own; language allow us to communicate generalizations between each other.
@@
 
-Certain linguistic expressions encode generalizations.
-The *language of generalization* is most commonly studied with *generic language* (or, *generics*), generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+<!-- Certain linguistic expressions encode generalizations. -->
+<!-- Language provides multiple, distinct ways of encoding generalizations. -->
+The *language of generalization* is most commonly studied with *generic language* (*generics*) or generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
 <!-- Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].  -->
@@
 
-Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions to match human intuitions.
-The major challenge in formalizing generalization in language is determining *what makes the statements true or false*.
+Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions that match human intuitions.
+The major challenge in formalizing generalization in language is determining what makes the statements true or false.
 When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
@@
 The generalization could signal something weaker like "Most dogs bark".
-However, most mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
+However, *most* mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only *quantifier* that would permit such a statement would be "some" (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to mean "some" is too permissive: Some robins are female (in fact, half of them are), but asserting "Robins are female" seems odd.
+The only *quantifier* that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
+But weakening the generalization to mean *some* is too permissive: Some robins are female (in fact, half of them are), but endorsing "Robins are female" seems odd.
 Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
 
-These observations have led to the conclusion that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
+These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
 The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
@@
 
-Yet, purely arbitrary relationships can result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
-Ravens and toasters have no priviledged relationship to each other, but "Ravens are bigger than toasters" is still true.
-An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual prevalence of the feature matters for making generalizations true.
+Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
+Ravens and toasters have no privileged relationship to each other, but "Ravens are bigger than toasters" is still true.
+An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual statistics of the feature matters for making generalizations true.
 
@@
 Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the information-theoretic function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
+To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
 We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
@@
 The paper is organized as follows. 
-In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a thory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
+In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a theory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
 The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
-Sections 2 - 4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+Sections 2-4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
 Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alterantive models fall short.
+We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alternative models fall short.
 This work opens the door to understanding generalizations in richer, pragmatic language understanding contexts and building models that learn abstract knowledge from language.
@@
 Abstract, potentially domain-specific, beliefs about properties can be represented by a probability distribution over the prevalence $P(p_{fk})$ [@Kemp2008].^[
-  We adopt the following notational conventions: $p_{fk} = p(f \mid k)$ as prevalence of feature $f$ for a category $k$. 
+  We adopt the following notational simplification: $p_{fk} = p(f \mid k)$. 
 ]
-Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data (the likelihood: $P(d \mid p_{fk})$).
-
-But we do not always have access to observational data $d$.
-Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
+Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data---the likelihood $P(d \mid p_{fk})$.
+
+<!-- But we do not always have access to  -->
+Observational data $d$ is not always available, however.
+Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*), events that are statistically unlikely (e.g., *lightning strikes tall objects*), or just aspects of the world that we have yet to experience.
 Fortunately, language provides simple ways of communicating generalizations.
@@
 But generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
-Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an intance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
+Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
   We adopt this somewhat idiosyncratic categorization in order to emphasize the different semantic types predicated. 
@@
 ]
-Psychologists, linguists, and philosphers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
+Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
   We take up the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
@@
 The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-Thus, the simplest semantics for a generalization about category K with property F is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.
+Thus, the simplest semantics for a generalization about category $k$ with property $f$ is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.
 
@@
 The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what threshold is appropriate?
-Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}; \denote{all} = \{p_{fk} = 1\}$.
-The extreme flexiblity of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
-Indeed, no particular threshold can suffice: The semantics of the language of generalizations is *underspecified*.
-To resolve this underspecification, we hypothesize that $\theta$ is determined by context, in a way analagous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}$; $\denote{all} = \{p_{fk} = 1\}$.
+The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
+Rather than throw out the threshold-semantics, we posit this semantics is *underspecified*.
+We hypothesize that $\theta$ is determined by context in a way analogous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
 
@@
 
-We can formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
-The model also has prior knowledge about the property $P(p_f)$ and so literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
+We formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
+The model also has prior knowledge about the property $P(p_fk)$ and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
 
@@
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
-Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.
 
@@
 
+Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.
+
 ### Endorsement model
@@
 We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
-We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0})^[
+We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
@@
   For the empirical case studies described below, these two versions of the model make almost identical predictions.
-].
+]
 
@@
 The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_fk)$---with the underspecified semantics.
-Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitious with any referent-prevalence. 
-However, the interpretation model's *a priori* beliefs $P(p_fk)$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
+\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_{fk})$---with the underspecified semantics.
+Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence. 
+However, the interpretation model's prior beliefs $P(p_{fk})$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
 
@@
 Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would a randomly-sampled category to have 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have substantial mass at relatively high prevalences, potentially with some uncertainty; Figure\ \@ref(fig:simulations); row 1, column 1).
-Abstract beliefs between different kinds of categories would manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similiarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations)A; row 1, column 4).
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-This statistic has been shown to be highly correlated with endorsements of generalizations about categories, or *generics* [@Khemlani2012].
-*Cue validity* implicitly encodes knowledge of other categories, by averaging over those categories $k'$ via the normalizing constant in Bayes' Rule:
+For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
+Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have some probability mass at relatively high prevalences, potentially with some uncertainty (Figure\ \@ref(fig:simulations); column 1).
+Abstract beliefs between different kinds of categories could manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations); column 4).
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria), shown to be highly correlated with endorsements of generics [@Khemlani2012].
+*Cue validity* implicitly encodes knowledge of other categories $k'$ by averaging over those categories via the denominator in Bayes' Rule:
 $P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
 Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
-In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{f})]$.
-For a slower derivation of this relationship, see Appendix A.
+In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{fk})]$.
+For a more detailed derivation of this relationship, see Appendix A.
 
@@
 As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:simulations)A).
-The uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
-The endorsement model thus predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevealence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
+Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
+The endorsement model inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
 
@@
 The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
-Hearing "Ks bark" tells the literal interpretor that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
+Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
 "Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
@@
 In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
-Intruigingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
+Intriguingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
 To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs. bottom row).
@@
 In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measurning and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
+We do this by both measuring and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
 
@@
 2c).
-Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in a category is directly related to their endorsement of statements of genericity (Expt. 3).
+Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in other categories is directly influences their endorsement of generalizations for the same category (Expt.
+3).
 <!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->
@@
 The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from background, world knowledge.
-This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [e.g., @Leslie2008].
+This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
 Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
@@
 Given this representation of background knowledge (*prevalence prior*), language interfaces with conceptual knowledge via *prevalence*. 
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Indeed, we see generics as describing kinds, but argue that the reason why particular generics are licensed in a context is about the information conveyed to a listener relative to their background knowledge, formalized with by prevalence prior.
-In the right situations, this shared background knowledge can presuppose beliefs about natural kinds and assume richly structured relations between categories and the properties [a la @Prasada2013].
+Previous psychological and philosophical work on generics has looked beyond prevalence and focused on kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
+Indeed, we see generics as describing kinds, but argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge, formalized with by prevalence prior.
+In the right situations, this shared background knowledge can presuppose beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
 In other situations, relevant background knowledge may be merely correlational in nature.
@@
 Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-We believe such probabilistic concept representations can be adopted as a formal analog to an intuitive theory of natural kinds [@Gelman2003; @Keil1992].
+We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
 We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory.
@@
 Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced.
-We note, however, that the endorsement model makes almost identical predictions if the QUD in the model is assumed to be about the abstract parameters of the background knowledge (e.g., which mixture component the referent is part of).
+We note, however, that the endorsement model makes almost identical predictions for the data presented in this paper if the QUD is assumed to be about the abstract parameters of the background knowledge (e.g., which mixture component the referent is part of) as opposed to the prevalence itself.
 This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
@@
 Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilties [cf., @Levinson1995].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilities [cf., @Levinson1995].
 Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*.
@@
 The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analagous to the context-sensitivity of the language of generalizations explored in this paper.
+Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations explored in this paper.
 An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
@@
 Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other categories in the comparison class.
-That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis commiting acts of terrorism).
+That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis committing acts of terrorism).
 In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of a generalization.
@@
 
-Finally, interlocturs may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but the very nature of *how* the comparison class should be constructed.
+Finally, interlocutors may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but the very nature of *how* the comparison class should be constructed.
 The comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inapprorpriate for generalizations  [@Leslie2008].
+This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inappropriate for generalizations  [@Leslie2008].
 
@@
 
-Imagine there is a job in the local beaurocrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
+Imagine there is a job in the local bureaucrat's office to handle the mail from Antarctica and this job is assigned to Mary;  to date, however, there has never been any mail from Antarctica [@Cohen1999].
 That is, the statement "Mary *has handled* mail from Antarctica" is false.
@@
 We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective probabilities.
-That is, because observers strongly believe one's social security number does not infleunce selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
+That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
 Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated similarly by our model as "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number*---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
-That is, we predict there are situations where statements like (2) could be considered felicitious generalizations.
+history had a social security number which was a *prime number*---the shear auspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
+That is, we predict there are situations where statements like (2) could be considered felicitous generalizations.
 
@@
 @Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Stastistical accounts of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
+Statistical accounts of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
 This is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics (e.g., if the generic means *most*).
@@
 Importantly, an incremental parsing of Sentence (3) leads our model to first believe that *most* elephants live in Africa (when it only hears that "Elephants live in Africa"), and then later believe that *some* elephants live in Africa (while others live in Asia) after hearing the end of the utterance ("...and Asia").
-Our model flexibly accomodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
+Our model flexibly accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 
@@
 Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
-In our **Model Simulations** section, we showed that the genearlization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
+In our **Model Simulations** section, we showed that the generalization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
 If the generalization conveys the property is in fact more widespread than the speaker herself might believe, this can lead to a distortion of the truth [@Cimpian2010].
@@
 To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the formal semantics  literatures.
+A number of other theories of genericity have been proposed in the formal semantics  literature.
 <!-- We now turn to situating our account with respect to these previous theories. -->
@@
 We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that prevalence is calculuated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
+His theory posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
 For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
-"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other aternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
 The inferential machinery behind Cohen's domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
@@
 
-@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analagous to *indexicals* (e.g., "this" or "I").
-Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restrictor [of the kind used by @Cohen1999, and many others].
+@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analogous to *indexicals* (e.g., "this" or "I").
+Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999, and many others].
 Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive "quantificational force". 
@@
 In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analagous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
 Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.

### 2018-02-13 paper/comgen-paper.Rmd
change out bda figure; tweak formatting

@@
     address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mtessler@stanford.edu"
+    email         : "mhtessler@stanford.edu"
   - name          : "Noah D. Goodman"
@@
 lineno            : no
+toc               : yes
 
@@
 
-Despite its ubiquity and relative morphosyntactic simplicity, there have been few formal models of the language of generalization and none that have made precise, quantitative predictions that match human intuitions.
+Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models of and none that have made precise, quantitative predictions that match human intuitions.
 The major challenge in formalizing generalization in language is determining what makes the statements true or false.
@@
 
-The language of generalization is easy to spot when a property is predicated of a category: "Ks F" (e.g., "Dogs bark").
+The language of generalization is easy to spot when a property, that could project onto an individual, is predicated of a category (e.g., "Dogs are friendly"; *barks* could apply to an individual as in "This dog is friendly").
 This is often called *generic language* or *generics* [@Carlson1977].
-But generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
+Generic statements can be contrasted with kind-denoting statements which use properties that can only apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* is not a property that could apply to an individual).
+Generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
 Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[

### 2018-02-17 paper/coverletter.tex
refresh coverletter with graf about previous submisisons

@@
 
-We enclose the manuscript \emph{Communicating Generalizations} to be considered for publication in \emph{Psychological Review}. 
-This paper explores the linguistic means by which generalizations about categories, events, and causality are communicated.  
-We present a Bayesian model of understanding generalizations in language, and show that it predicts human judgments with high quantitative accuracy across several experiments.
-We probe the theory in more detail, and find that the semantics of generic language depend in a fundamental way on subjective beliefs.
+We enclose the manuscript \emph{The Language of Generalization} to be considered for publication in \emph{Psychological Review}. 
+This paper explores the linguistic means by which generalizations are communicated.  
+We present a Bayesian model of endorsing generalizations and show that it predicts human judgments with high quantitative accuracy across several experiments in diverse domains.
+The theory suggests that the language of generalizations can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
 
 Understanding how the world works requires learning generalizations. 
-The kinds of observations that would facilitate such learning, however, can be rare (e.g., \emph{figuring out that lightning strikes tall objects}) or costly (e.g., \emph{learning that certain plants are poisonous}).
-We don't need to need taste every plant to figure out which ones are poisonous; we don't need to stand under objects of various heights to learn that lightning strikes tall objects.
-Language allow us to communicate generalizations to each other.
+The kinds of observations that would facilitate such learning, however, may be rare (e.g., \emph{figuring out that lightning strikes tall objects}) or costly (e.g., \emph{learning that certain plants are poisonous}).
+We do not need to need taste every plant to figure out which ones are poisonous; we don't need to stand under objects of various heights to learn that lightning strikes tall objects.
+Language allow us to learn generalizations from each other.
 
-The language of generalizations is often studied in what's called \emph{generic language} (e.g., ~\emph{Birds fly}).
-Generic utterances are common in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
-Generalizations can be transmitted about more than just categories.
-\emph{Habitual language} conveys generalizations about events (e.g., ~\emph{Mary swims after work}).
-\emph{Causal language} conveys generalizations about causal events (e.g., ~\emph{Staring at the sun makes you go blind}).
+The language of generalization is most commonly studied in predications of categories (e.g., ~\emph{Birds fly}), otherwise known as \emph{generic language}.
+But different semantic types can described in generalization, including events (\emph{habitual language}; e.g., ~\emph{Mary swims after work}) and causal relationships (\emph{causal language}; e.g., ~\emph{Staring at the sun makes you go blind}).
+Generalizations are ubiquitous in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
 
-Though this type of language is found everywhere, the meaning of generalizations in language is philosophically puzzling and has resisted precise formalization. 
-The major issue in formalizing generalizations in language is determining what makes such statements true or false.
-Consider generic utterances:
-Generics are often about characteristic properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
-Indeed, \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier (i.e., \emph{some}) would suffice.
-Some have taken this evidence to suggest that generics must express special mental relationships between kinds and properties, but arbitrary generalizations --- which seem only to depend on the actual statistics of the world --- can also be conveyed with generics (e.g., \emph{Ravens are bigger than toasters}).
-There have been a few formal models proposed for generic language, but none that have made precise, quantitative predictions about human endorsement patterns.
-
-Analogous phenomena can be observed in habitual and causal language.
+%Given that inductive generalization can be described by probability (e.g., the probability that the next instance of the category will have a feature), it seems natural that the core meaning generalizations in language would relate to this predictive probability.
+Despite the ubiquity of the language, its meaning is philosophically puzzling and has resisted precise formalization. 
+%However, the language of generalizations displays extreme sensitivities to context, which has heretofore crippled previous attempts to formalize this major function of language. 
+%Though this type of language is found everywhere, the meaning of generalization is philosophically puzzling and has resisted precise formalization. 
+%The major issue in formalizing the language of generalizations is determining what makes such statements true or false.
+For example, generics can describe properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
+\emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier (i.e., \emph{some}) would suffice.
+Habitual and causal language display similar context-sensitivites:
 If John smokes once a year, one might hesitate to endorse the statement \emph{John smokes}.
@@
 
-In this paper, we propose that the core meaning of generalizations in language is \emph{simple but underspecified}.
-We adopt a formalism for the truth conditions of this language which has antecedents in formal semantics: a threshold function (e.g., the statement is true if the frequency is greater than some criterion $\theta$).
-The critical novelty of our approach is that the criterion $\theta$ is left underspecified in the language, and must be resolved in context.
-We instantiate this idea in a state-of-the-art probabilistic model of communication, and operationalize \emph{endorsement} (i.e., felicity or agreement with a statement) as a speaker's decision about whether or not to say the generalization to a naive listener.
-We show how this simple model naturally explains \emph{flexible truth conditions} via interlocutors' beliefs about the property or event in the question.
-Across our three case studies, we both \emph{measure and manipulate} prior knowledge, showing that it is strongly and causally related (via our model) to endorsement. 
-Using the case study of habitual language, we go on to further interrogate the semantic scale from which generalizations are evaluated.
-We find that speakers' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past is what drives endorsements. 
-Across our case studies, we show very strong agreement between the predictions of our model with empirical human data; additionally, we do so in situations where simpler models would not suffice. 
-This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
+%Some have taken this evidence to suggest that generics cannot be understood in terms of how prevalent the property is, instead appealing to special mental relationships between certain kinds and certain properties.
+%There have been a few formal models proposed for generic language, but none that have made precise, quantitative predictions about human endorsement patterns.
+
+%The dominant view in psychology has been to focus on special conceptual relations that supposedly determine what makes the language the generalization true or false.
+In this paper, we take the context-sensitivity of generalizations seriously and formalize the hypothesis that the core meaning of generalizations is \emph{simple but underspecified}. 
+We embed this idea in a simple, rational model of communication and use it to address the fundamental question: What makes the language of generalizations true or false?
+Our answer is that endorsement (true or false?) is a speaker's decision about whether or not to say the generalization to a naive listener.
+Our model is the first formal model to make precise quantitative predictions about the language of generalization.
+
+We have previously received peer-review of a similar manuscript submitted to other top-ranking journals including \emph{Psychological Review}.
+Those reviews questioned how much our work advances our understanding of the language of generalization and highlighted the need for comparison to other models. 
+This manuscript differs from previous submissions in two major ways.
+%We show how this model naturally explains the flexibility in endorsement patterns via interlocutors' prior beliefs about the property or event in the question.
+The empirical and much of the philosophical literatures has been focused on generalizations about categories, or generic language, which our previous manuscript also focused on.
+In this paper, we investigate three case studies: generalizations about categories, events, and causes. 
+Immediately we see the generality of our formal model: We are able to explain context-sensitive endorsements across these three domains without adopting domain-specific assumptions.
+Furthermore, each case study naturally lends methodological advantages to provide further tests of our model.
+With event generalizations, we are able to interrogate the underlying semantic scale, and find that speakers' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, is what drives endorsements.
+With causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge, and show it is in fact causally related to endorsement. 
+Finally, we develop three alternative models: two linear models based on empirically-elicited statistical knowledge and one rich, cognitive model which lacks the \emph{underspecification of meaning} at the core of our hypothesis.
+These alternative models fail to account for key aspects of the context-sensitivity that is observed in the data and that our full model predicts.
+These alternative models and the empirical paradigms used provide strong tests of the theoretical contribution of our paper. 
+%This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
+
+%, which we use to make precise, quantitative predictions about sentence endorsement. 
+% introduce the first formal model of generalizations in language and use it to make 
+% this hypothesis in a probabilistic model of language understanding.  that the core 
+%We adopt a formalism for the truth conditions of this language which has antecedents in formal semantics: a threshold function (e.g., the statement is true if the prevalence is greater than some criterion $\theta$).
+%Attempts of this kind have been proposed before but none have been formalized into a model that makes predictions about human judgments. 
+%The critical novelty of our approach is that the criterion $\theta$ is left underspecified in the language, and must be resolved in context.
+%We instantiate this idea in a state-of-the-art probabilistic model of communication, and operationalize \emph{endorsement} (i.e., felicity or agreement with a statement)
 
@@
 The puzzles of generalizations in language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
-Our solution represents the first formal model of generic language to be validated by quantitative agreement with human behavioral data.
+Our solution represents the first formal model of generalization in language to be validated by quantitative agreement with human behavioral data.
 It is not, however, uncontroversial: we champion a statistical view that has been often dismissed in the literature.

### 2018-02-18 analysis/case1-generics.Rmd

---
title: "Analysis for Case 1 (generics)"
output: html_notebook
---

```{r libraries, cache = F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
library(viridis)
library(tidyboot)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

compute_r2 <- function(df,v1, v2, sigfigs = 3){
  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
}

compute_mse <- function(df, v1, v2, sigfigs = 3){
  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
}

project.path <- "../"
options("scipen"=10) 
```

# Experiment 1:a: Generic endorsements

```{r eval = F}
#d1 <- read.csv(paste(project.path, "data/generics/endorsement/",
                    #"truth-judgments-n100.csv", sep = ""))
#d2 <- read.csv(paste(project.path, "data/generics/endorsement/",
              #      "naturalGenerics-trials-formatted.csv", sep = ""))

# write.csv(
#   left_join(
#   d1 %>%
#     mutate(sentence = as.character(sentence),
#            sentence = gsub('&quotechar', '', sentence),
#          sentence = gsub('lyme', 'Lyme', sentence)),
#   unique(d2 %>%
#     mutate(sentence = paste(Category, " ", Property, ".", sep = "")) %>%
#     select(Category, Property, sentence))
# ), file = paste(project.path, "data/generics/endorsement/",
#                     "truth-judgments-n100.csv", sep = ""), row.names = F)
```

```{r generic-endorsement}
d.gen.endorse.catch <- read_csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments_catch-trials.csv", sep = ""))

d.gen.endorse <- read_csv(paste(project.path, "data/generics/endorsement/",
                    "truth-judgments-n100.csv", sep = ""))

d.gen.endorse.summary <- left_join(
  d.gen.endorse,
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
  ungroup() %>%
  group_by(sentence) %>%
  tidyboot_mean(column = response) %>%
  ungroup() %>%
  mutate(sentence = factor(sentence, levels = sentence[order(mean)]))

d.gen.endorse.bayes <- left_join(
  d.gen.endorse, 
  d.gen.endorse.catch %>% select(workerid, pass)
  ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(sentence) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup()

d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
                       "naturalGenerics-prior-trials-n57.csv", sep = ""))

d.prev.summary <- d.prev %>%
  mutate(item = paste(Category, " ", Property, ".", sep = "")) %>%
  filter(item %in% d.gen.endorse.bayes$sentence) %>%
  mutate(prevalence = prevalence / 100) %>%
  group_by(Category, Property, item) %>%
  tidyboot_mean(column = prevalence)

d.gen.endorse.bayes.prev <- left_join(
  d.gen.endorse.bayes, 
  d.prev.summary %>% 
    rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper) %>%
    select(-n, -empirical_mean)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))

generics.endorsement.spectrum <- ggplot(
    d.gen.endorse.bayes.prev, 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1)+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(color = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
```

Summary of endorsements for true vs. false vs. uncertain generics

```{r generic-endorsement-manipulationcheck}
# MHT's truth judgments of sentences
# t --> true; f --> false; i --> indeterminate/uncertain
all.sentences <- list("Cardinals are red." = "t",
 "Ducks have wings." = "t",
 "Kangaroos have pouches." = "t",
 "Kangaroos have spots." = "f",
 "Leopards are juvenile." = "i",
 "Leopards have spots." = "t",
 "Leopards have wings." = "f",
 "Lions are male." = "i",
 "Lions have manes." = "t",
 "Lions lay eggs." = "f",
 "Mosquitos attack swimmers." = "i",
 "Mosquitos carry malaria." = "t",
 "Mosquitos dont carry malaria." = "f",
 "Peacocks dont have beautiful feathers." = "f",
 "Peacocks have beautiful feathers." = "t",
 "Robins are female." = "i",
 "Robins carry malaria." = "f",
 "Robins lay eggs." = "t",
 "Sharks are white." = "i",
 "Sharks attack swimmers." = "t",
 "Sharks dont attack swimmers." = "f",
 "Sharks have manes." = "f",
 "Sharks lay eggs." = "i",
 "Swans are full-grown." = "i",
 "Swans are white." = "t",
 "Ticks carry Lyme disease." = "t",
 "Ticks dont carry Lyme disease."= "f",
 "Tigers dont eat people."= "f",
 "Tigers eat people." = "t",
 "Tigers have pouches."= "f")

mht.truth.judgments <- data.frame(sentence = names(all.sentences),
           truth_judgment = as.vector(unlist(all.sentences)))

d.gen.endorse.manipulation.check.bayes <- left_join(
  left_join(
    d.gen.endorse, 
    d.gen.endorse.catch %>% select(workerid, pass)
    ),
  mht.truth.judgments ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(truth_judgment) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup() %>%
  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))

save(d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes,
     file = "../paper/cached_results/case1_endorseSummary_byItem.RData")

```

# Experiment 1b: Priors

```{r generic-endorsement-priors}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time

d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

genericEndorsementPriorModelHelpers <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)
'

structuredPriorModel <- '
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {g, d, phi}
}
'

unstructuredPriorModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  mapData({data: preprocessedResponses}, function(d){
    factor(stableComponent.score(d))
  })
  return {g, d}
}
'
genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")

```

```{r generic-endorsement-priors-unbounded, eval = F}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time

d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

unboundedModel <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)

var shapeParams = function(params){
  return {
    a: params.g * params.d,
    b: (1 - params.g) * params.d
  }
}

var model = function(){

  // var numComponents = (1 + poisson(1));
  var numComponents = 5//discrete([1, 1, 1, 1, 1]) + 1
  var mixtureWeights = sort(normalize(repeat(numComponents, function(){
    return uniformDrift({a: 0, b:1, width: 0.2})
  }))).reverse()

  // var mixtureWeights = dirichlet(ones([numComponents, 1]));
  var componentParams = map(function(i){
    var g = uniformDrift({a: 0, b:1, width: 0.2}), d = uniformDrift({a: 0, b:100, width: 20})
    var betaParams = shapeParams({g, d})
    return betaParams
  }, _.range(numComponents))

  mapData({data: preprocessedResponses}, function(d){

    var scr = log(sum(map(function(cParams){
      cParams[1] * exp(Beta(cParams[0]).score(d))
    }, _.zip(componentParams, mixtureWeights))))
//    }, _.zip(componentParams, T.toScalars(mixtureWeights)))))
    factor(scr)
  })

  var componentPredictives = map(function(cParams){
      return beta(cParams)
  }, componentParams)

  return _.fromPairs(
    _.zip(
        map(function(i){ i + "_weight" }, _.range(5)), 
        mixtureWeights
      ).concat(
      _.zip(
        map(function(i){ i + "_predictive" }, _.range(5)), 
        componentPredictives
      )
    )
  )//sort(T.toScalars(mixtureWeights))
};
'

example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )
priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
  n_samples <- 10000
lg = 0
  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))
```

```{r eval = F}
m.gen.endorse.priors.unbounded %>%
      separate(Parameter, into = c("c", "var")) %>% 
      ggplot(., aes( x=  value, fill = c))+
 geom_histogram(position = position_dodge(), binwidth = 0.05)+
 facet_wrap(~var)+
  scale_fill_solarized()
```

```{r generic-endorsement-priors-bayesFactors, eval = F}
genericEndorsementPriorModelPriorLikelihoodHelpers <- '
var properties = _.uniqBy(_.map(data, "Property"));

var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}
'

genericEndorsementPriorModelsPriorLikelihood <- '
var transientComponent = Beta({a:1, b:100})

var model = function(){

  var propertyLogLikes = map(function(property){

    var propertyData = _.map(_.filter(data, {Property: property}), "prevalence");
    var preprocessedResponses = map(function(d){
        return avoidEndPoints(d / 100)
    }, propertyData);

    var phi = uniformDrift({a:0, b: 1, width:0.2});
    var g = uniformDrift({a:0, b: 1, width:0.2});
    var d = uniformDrift({a:0, b: 100, width:5});
    var stableParams = betaShape({g, d})
    var stableComponent = Beta(stableParams)

    var logLikes = map(function(d){
      var structuredLL = log(
        phi * exp(stableComponent.score(d)) +
        (1 - phi) * exp(transientComponent.score(d))
      )

      var unstructuredLL = stableComponent.score(d);

      return {structuredLL, unstructuredLL}
    }, preprocessedResponses)

    return {
      structuredLL: sum(_.map(logLikes, "structuredLL")), 
      unstructuredLL: sum(_.map(logLikes, "unstructuredLL"))
    }

  }, properties)

  return {
    structuredLL: sum(_.map(propertyLogLikes, "structuredLL")), 
    unstructuredLL: sum(_.map(propertyLogLikes, "unstructuredLL"))
  }
}
'

```

```{r generic-endorsement-priors-bayesFactorsRun, eval = F}
marginal.prior.likelihoods <- data.frame()

# 100 samples takes 30s
m.gen.endorse.priors.logLike <- webppl(
    paste(genericEndorsementPriorModelPriorLikelihoodHelpers,
          genericEndorsementPriorModelsPriorLikelihood,
          sep = '\n'), 
    data = d.gen.endorse.priors, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "forward", samples = 1000),
    chains = 3, cores = 3
) %>% 
  mutate(value = as.numeric(value))

min.ll.1 <- min(
  m.gen.endorse.priors.logLike$value[
    is.finite(
      m.gen.endorse.priors.logLike$value
      )
    ]
  )

m.gen.endorse.priors.logLike <- m.gen.endorse.priors.logLike %>% 
  rowwise() %>%
  mutate(value = ifelse(value == -Inf, min.ll.1, value))

save(m.gen.endorse.priors.logLike, file = '../analysis/generics-priors-loglike.Rdata')
```

```{r generic-endorsement-priors-bayesFactorsLoad}
load(file = '../analysis/generics-priors-loglike.Rdata')
marginal.prior.likelihoods <- m.gen.endorse.priors.logLike %>%
  group_by(Chain, Parameter) %>%
  summarize(mll  = logmeanexp(value))

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% 
  spread(Parameter, mll) %>%
  mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
```

# Model comparisons

## Regression models

```{r generic-regression-models}
d.cv <- read.csv(paste(project.path, "data/generics/endorsement/", "cue-validity-2-freeProduction-trials.csv", sep = ""))

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims_wrongDeployment.json", sep = "")) %>%
  mutate(sentence = paste(category, property))

### Preprocessing
# - Force all responses to lower case. 
# - Remove spaces.
# - Fix mosquito mispellings.
# - Count "deertick" as "tick".
# - Remove plural "s".
# 
# Mark if the produced animal matches the generic of interest.

mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")

d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
  mutate(
    property = gsub("'", "", property),
    Property = gsub("'", "", Property),
    sentence = paste(Category, Property),
    item = paste(category, property))

d.cv.bootstrapped <- data.frame()
resample_n <- length(levels(factor(d.cv$workerid)))
for (i in 1:10){

  d.cv.bsample <- d.cv %>% 
    select(workerid, property, response) %>% 
    spread(property, response) %>% 
    sample_n(resample_n, replace = TRUE) %>%
    gather(property, category, -workerid) %>% 
        group_by(property) %>%
    mutate(n = n(),
           item = paste(category, property)) %>%
    filter(item %in% d.target.items$item) %>%
    group_by(category, property) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials,
              prop = ifelse(is.na(prop), 0.01, prop),
              iteration = i)

  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
}

empiricalLower = function(dist){
  xi <- quantile(dist, 0.025)
  return (xi[["2.5%"]])
}
empiricalUpper = function(dist){
  xi <- quantile(dist, 0.975)
  return (xi[["97.5%"]])
}
empiricalMean = function(dist){
  xi <- quantile(dist, 0.5)
  return (xi[["50%"]])
}

d.gen.cv.summary <- left_join(
    d.target.items %>% select(-sentence),
    d.cv.bootstrapped %>%
      group_by(property) %>%
      summarize(cv_mean = empiricalMean(prop),
                cv_ci_lower = empiricalLower(prop),
                cv_ci_upper = empiricalUpper(prop))
) %>%
  mutate(
    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
  )

# quantile(filter(d.cv.bootstrapped, property == "is red")$prop, c(0.025, 0.5, 0.975))
# 
# d.cv.bootstrapped %>%
#   group_b

# need to filter by items specified with endorsement
# d.gen.cv.summary <- left_join(
#   d.target.items %>% select(-sentence),
#   d.cv %>%
#     rename(category = response) %>%
#     group_by(property) %>%
#     mutate(n = n(),
#            item = paste(category, property)) %>%
#     filter(item %in% d.target.items$item) %>%
#     group_by(category, property) %>%
#     summarize(mentions = n(),
#               trials = mean(n), # mean(n) == n, because it's just the number of subjects
#               prop = mentions / trials)
#   ) %>%
#   mutate(prop = ifelse(is.na(prop), 0.01, prop))

d.gen.endorse.prev.cue <- left_join(
  left_join(
    left_join(
      d.gen.endorse, 
      d.gen.endorse.catch %>% select(workerid, pass)
      ) %>%
      filter(pass == 1) %>%
    rowwise() %>%
    mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence),
          sentence = gsub('[.]', '', sentence)
    ),
    d.prev.summary %>% 
      rename(prev_mean = mean,
             sentence = item,
             prev_ci_lower = ci_lower,
             prev_ci_upper = ci_upper) %>%
      ungroup() %>%
      mutate(sentence = gsub('[.]', '', sentence))
    ),
  d.gen.cv.summary %>% select(-item))

glm.gen.endorse.prev <- glm(response ~ prev_mean, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

glm.gen.endorse.prev.cv <- glm(response ~ prev_mean + cv_mean, 
              data = d.gen.endorse.prev.cue, family = 'binomial')

d.gen.endorse.prev.cue.uniq <- unique(select(
    d.gen.endorse.prev.cue, Property, Category, sentence, 
    prev_mean, prev_ci_lower, prev_ci_upper, cv_mean, cv_ci_lower, cv_ci_upper
  ))

d.gen.endorse.prev.cue.uniq.lower <- d.gen.endorse.prev.cue.uniq %>% 
  select(-prev_mean, -cv_mean) %>% 
  rename(prev_mean = prev_ci_lower,
         cv_mean = cv_ci_lower)
d.gen.endorse.prev.cue.uniq.upper <- d.gen.endorse.prev.cue.uniq %>% 
  select(-prev_mean, -cv_mean) %>% 
  rename(prev_mean = prev_ci_upper,
         cv_mean = cv_ci_upper)

d.gen.endorse.regression.prevalence <- left_join(
  d.gen.endorse.bayes,
  d.gen.endorse.prev.cue.uniq %>%
    mutate(
      prediction_mean = predict(glm.gen.endorse.prev, ., type = "response"),
      prediction_ci_lower = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
      prediction_ci_upper = predict(glm.gen.endorse.prev, d.gen.endorse.prev.cue.uniq.upper, type = "response")
    ) %>%
    mutate(sentence = paste(Category, " ", Property, ".", sep = ""))
) %>% mutate(
  sqErr = (MAP_h - prediction_mean) ^ 2
)

d.gen.endorse.regression.prevalence.cuevalidity <- left_join(
  d.gen.endorse.bayes,
  d.gen.endorse.prev.cue.uniq %>%
    mutate(
      prediction_mean = predict(glm.gen.endorse.prev.cv, ., type = "response"),
      prediction_ci_lower = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.lower, type = "response"),
      prediction_ci_upper = predict(glm.gen.endorse.prev.cv, d.gen.endorse.prev.cue.uniq.upper, type = "response"),
      sentence = paste(Category, " ", Property, ".", sep = "")
      )
) %>% mutate(sqErr = (MAP_h - prediction_mean) ^ 2)

d.gen.endorse.regression <- bind_rows(
  d.gen.endorse.regression.prevalence.cuevalidity %>%
    mutate(src = "regression_Prev_Cuevalidity"),
  d.gen.endorse.regression.prevalence %>% 
    mutate(src = "regression_Prev")
  )

save(d.gen.endorse.regression.prevalence, 
     d.gen.endorse.regression.prevalence.cuevalidity, 
     d.gen.endorse.regression, file = "../paper/cached_results/case1_regressionResults.RData")

r2.gen.n <- length(d.gen.endorse.bayes$sentence)
r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)

r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)

intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))

d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
  filter(
    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
    (prev_mean < intermediate.prev.quantiles[["76%"]])
)
r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)

r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
```

## RSA models

### model code
```{r rsaHelpers}
rsaHelpers <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var round = function(x){
  return Math.round(x*1000)/1000
}
var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
// var thetaBins = [
//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 // ]
var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var bins = map(round, _.range(0.01, 0.99, 0.01))

// var bins = [
  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
// ];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}

var mixture = data.prior.mix[0];
var priorParams = data.prior.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

fixed.threshold.model <- '
var fixedThresholdInterpreter = function(threshold) {
  Infer({model: function(){
  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
  var state = sample(statePrior)
  condition( state > threshold)
    return {
      state: state
  }
 // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
 }, method: "enumerate"})}
'

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

```

```{r simulationCalls}
fixed.threshold.calls <- '
_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
'
no.utterance.call <- ' 
  noUtteranceInterpreter()
'
uncertain.threshold.call <- '
  uncertainThresholdInterpreter()
'
```

### model analysis

```{r generic-RSAmodels, fig.width = 8}
example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
#m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
# }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

# save(m.samp.fixed,
#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

     # file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
    #                 n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# load(m.samp.fixed, 
#      file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdDisc-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThresholdCts-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

#m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-10000_burn5000_lag20_chain1.csv", sep = ""))
# 
# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
# 
# tail(m.samp.fixed)

fixed.params.posterior <-  m.samp.fixed %>% 
  filter(param %in% c("noise", "fixedThreshold")) %>%
  group_by(param) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.somemodel.endorsement <- m.samp.fixed %>%
  filter(type == 'endorsement', param == "some") %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

# m.gen.fullmodel.endorsement <- m.samp.samp %>%
#   rename(type = Parameter, property = Property, category = Category, val = Value, param = Extra) %>%
#   group_by(type, property, category, param) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

m.gen.fullmodel.endorsement <- m.samp %>%
 filter(type == 'endorsement', param == 'generic') %>%
  # filter(type == 'predictive', param == 'generic') %>%
 # filter(type == 'endorsement') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

uncertain.threshold.s1opt <- m.samp %>% 
  filter(type == "param") %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

fixed.threshold.s1opt <- m.samp.fixed %>% 
  filter(type == "param") %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

fixed.threshold.posterior <- filter(fixed.params.posterior, param == "fixedThreshold")
generics.fixed.noise.posterior <- filter(fixed.params.posterior, param == "noise")
```

```{r generic-endorsement-referent-prevalence-model, eval = F}
referentPrevalenceModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var betaParams = betaShape({g, d})
  var referentPrevDist = Beta(betaParams)
  mapData({data: preprocessedResponses}, function(d){
    observe(referentPrevDist, d)
  })
  return {g, d}
}
'
genericEndorsementRefPrevModel <- paste(genericEndorsementPriorModelHelpers, referentPrevalenceModel, sep = "\n")
```

```{r generic-referent-prevalence-model-run, eval = F}
m.gen.refprev.predictive <- data.frame()
n_samples <- 10000
lg = 0

for (p in example.generics ) {

  prevData <- d.prev %>% 
  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
  filter(sentence == p)

  m.gen.refprev <- webppl(genericEndorsementRefPrevModel,
                                 data = prevData$prevalence, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.refprev.predictive.item <- m.gen.refprev %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        prevalence =rbeta(n = 1, shape1 = a,
                                 shape2 = b),
        Category = prevData[1,]$Category,
        Property = prevData[1,]$Property,
        src = "prevAloneModel"
      ) %>% ungroup()

    m.gen.refprev.predictive <- bind_rows(
      m.gen.refprev.predictive,
      m.gen.refprev.predictive.item %>%
        select( src, Category, Property, prevalence)
    )

}
#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
#head(prevData)
#n_samples
```

```{r gen-prev-forward, eval=F}
#Forward sample Target Prevalence from posterior on parameters (joint inference model)
m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    #filter(type == "withinKind") %>%
    mutate(parameter = paste(param, property, category, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type) %>%
    #mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category"), sep= "_")

m.samp.prevalence <- m.samp.prev.params %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()
```

```{r}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")
```

```{r gen-prev-dists, eval=F}
gen.prev.dists <- bind_rows(
  d.prev %>% 
  mutate(sentence = paste(Category," " ,Property, sep = "")) %>%
  filter(sentence %in% example.generics) %>%
  mutate(prevalence = prevalence / 100,
         src = 'data') %>% 
    select(-workerid, -trial_type),
  m.samp.prevalence %>% 
    mutate(sentence = paste(category," " ,property, sep = "")) %>%
    filter(sentence %in% example.generics) %>%
    select(property, category, prevalence) %>%
    rename(Category = category, Property = property) %>%
    mutate(src = 'model'),
  m.gen.refprev.predictive
)

ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
  geom_density(aes( y = ..scaled.. ))+
    #  stat_ecdf(size = 1)+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
   #              position = position_dodge())+
  facet_wrap(~Property + Category, nrow = 1)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

```{r generic-model-scatters, cache = F}
m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

r2.gen.rsa.generics <- compute_r2(
  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
  "MAP", "MAP_h", sigfigs = 4
)

r2.gen.rsa.fixed <- compute_r2(
  m.gen.endorse.rsa %>% filter(src == "some_model"),  
  "MAP", "MAP_h", sigfigs = 4
)

mse.gen.rsa.generics <- compute_mse(
  m.gen.endorse.rsa %>% filter(src == "generics_model"), 
  "MAP", "MAP_h", sigfigs = 5
)

mse.gen.rsa.fixed <- compute_mse(
  m.gen.endorse.rsa %>% filter(src == "some_model"),  
  "MAP", "MAP_h", sigfigs = 5
)

d.gen.endorse.rsa.regression <- bind_rows(
  d.gen.endorse.regression,
  left_join(
    m.gen.endorse.rsa %>% 
      rename(prediction_mean = MAP, prediction_ci_lower = cred_lower, prediction_ci_upper = cred_upper),
    d.gen.endorse.regression %>% 
      select(sentence, Property, Category, prev_mean, cv_mean)
  )
) %>%
  mutate(src = factor(src, levels = c( "some_model",
                                      "generics_model",
                                      "regression_Prev", 
                                      "regression_Prev_Cuevalidity"
                                     ),
                      labels = c("Fixed semantics model",
                                 "Uncertain semantics model",
                                 "Prevalence",
                                 "Cue validity + Prevalence"
                                 )))

generics.endorsement.models <- ggplot(d.gen.endorse.rsa.regression, 
                                      aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  #theme(legend.position = "bottom")+
  guides(fill = F)
```

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}

m.gen.fullmodel.prior.parameters <- m.samp %>%
  filter(type == "prior", property %in% example.generics.properties) %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

# use MAP estimates to generate L(h | generic) & L(h | silence) predictions

m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
  ungroup() %>%
  select(param, property, category, MAP) %>%
  mutate(param = paste(param, category, sep = "_")) %>%
  select(-category) %>%
  spread(param, MAP) %>%
  rename(mix = mixture_NA, 
         stable_mean = stableFreq_mean, 
         stable_concentration = stableFreq_sampleSize) %>%
  mutate( a = stable_mean * stable_concentration, 
          b = (1 - stable_mean) * stable_concentration)

gen.listener.predictions <- data.frame()

# run interpreter model to generate "hypothetical intepretation" plots
for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
   )
}

m.gen.fullmodel.target.prevalence <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.speakerBeliefs <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  mutate(Sentence = paste(category, property)) %>%
  filter(Sentence %in% example.generics) %>%
  mutate(property = factor(property))

# m.samp.prev.params <- m.samp %>%
#     filter(type == "targetPrevalence") %>%
#     mutate(Sentence = paste(category, property)) %>%
#     filter(Sentence %in% example.generics) %>%
#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
#     select(-param, -property, -category, -chain, -type) %>%
#     group_by(parameter) %>%
#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
#     ungroup() %>%
#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
#     group_by(category, property, iteration) %>%
#     spread(parameter, val) %>%
#     rowwise() %>%
#     mutate(
#       a = mean*sampleSize,
#       b = (1-mean)*sampleSize,
#       val = rbeta(n = 1, shape1 = a, shape2 = b)
#       ) %>%
#     ungroup()

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.gen.speakerBeliefs %>%
    select(property, val) %>%
    rename(value = val) %>%
    mutate(Parameter = "speakerBeliefs")
)

category.text.labels <- data.frame(property = c("dont eat people", 
                      "carry malaria", "lay eggs",  "are female", "have spots"),
             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
            y = c(0.45, 0.5, 0.45, 0.5, 0.26))

gen.inset.distributions.refactored <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Prevalence Prior", 
                                       "Prevalence Posterior given generalization", 
                                       "Referent Prevalence")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") )

save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
     generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
     file = "../paper/cached_results/case1_modelPosteriors.RData")

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories. Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right). Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence. These distributions are inferred using all three data sources from Expt. 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}

fig.gen.endorse.data <- generics.endorsement.spectrum +
  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ggtitle("prevalence priors")
fig.gen.endorse.models <- generics.endorsement.models +
  theme(plot.margin = unit(c(6,2,0,0), "pt")) #+ ylab("")
fig.gen.endorse.priors <- generics.endorsement.insets +
  theme(plot.margin = unit(c(26,10,0,10), "pt"))

#+ 
    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
                                     fig.gen.endorse.models, 
                                    # align = 'v',
                                    #  axis = 'l',
                                    labels = c("A", "B"),
                                    rel_widths = c(0.9, 1))

plot_grid(fig.gen.endorse.toprow,
          fig.gen.endorse.priors,
          labels = c("", "C"), nrow = 2, rel_heights = c(1.1, 0.6)
          )
# prow <- plot_grid( p1 + theme(legend.position="none"),
#            p2 + theme(legend.position="none"),
#            p3 + theme(legend.position="none"),
#            p4,
#            align = 'vh',
#            labels = c("A", "B", "C"),
#            hjust = -1,
#            #nrow = 1,
#            #rel_widths = c(1.2, 3, 2)
#            rel_widths = c(1.2, 3, 1.05, 1.7)
#            )

# grid.arrange(generics.endorsement.spectrum, 
#              generics.endorsement.models,
#              generics.endorsement.insets, ncol = 2,
#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))

```

# Old models

```{r generic-endorsement-priors-savageDickeyModel, eval = F}
savageDickeyModel <-'
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {phi}
}

//var samples = data.samples[0], burn = data.burn[0], lag = data.lag[0];
// var samples = 2000, burn = burn / 2, lag = 0;
var modelPosterior = Infer({method: "MCMC", samples:10000, burn:5000, lag:0, 
verbose: true}, model)
var modelPrior = Infer({method: "forward", samples:10000}, model)

var pointNull = 1;

var logBFs = map(function(diff){
  var savageDickeyDenomenator = expectation(modelPrior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyNumerator = expectation(modelPosterior, function(x){return Math.abs(x.phi-pointNull)<diff})
  var savageDickeyRatio = savageDickeyNumerator / savageDickeyDenomenator
  return [diff, Math.log(savageDickeyRatio)]
}, [0.01, 0.02, 0.03, 0.04, 0.05])

var returnVals = {
  prior: modelPrior, posterior: modelPosterior, logBFs: logBFs
}
returnVals
'
```

```{r generic-endorsement-priors-bayesFactors-supermodel, eval= F}
genericEndorsementPriorSupermodel <- '
var model = function(){
  var alpha = uniformDrift({a:0, b: 1, width:0.2});
  //var structured = flip();
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g1 = uniformDrift({a:0, b: 1, width:0.2});
  var d1 = uniformDrift({a:0, b: 100, width:5});
  // var g0 = uniformDrift({a:0, b: 1, width:0.2});
  // var d0 = uniformDrift({a:0, b: 100, width:5});
  var stableParams1 = betaShape({g: g1, d: d1})//, 
      //stableParams0 = betaShape({g: g0, d: d0});
  var stableComponent1 = Beta(stableParams1)//,
      //stableComponent0 = Beta(stableParams0);

  var transientComponent = Beta({a:1, b:100})
  mapData({data:preprocessedResponses},
    function(d){
    var scr1 = log(phi * exp(stableComponent1.score(d)) +
                    (1 - phi) * exp(transientComponent.score(d)))
    var scr0 = stableComponent1.score(d);
    // display(exp(scr1) + " " + exp(scr0));
    var combined_ll = log(alpha * exp(scr1) + (1 - alpha) * exp(scr0));
    // factor(structured ? scr1 : scr0)
    factor(combined_ll)
  })
  return alpha
}
'
```

```{r generic-endorsement-priors-bayesFactor-supermodelRun, cache = T, eval = F}
for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.supermodel.posterior <- webppl(
    paste(genericEndorsementPriorModelHelpers, genericEndorsementPriorSupermodel, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model",  chains = 2,
                                 cores = 2,
                                 inference_opts = 
                                   list(method = "MCMC",
                                        samples = 2000, 
                                        burn = 2000, 
                                        lag = 2, 
                                        verbose = T)
    )

  qplot(m.gen.endorse.priors.supermodel.posterior$value)
}
```

```{r generic-endorsement-priors-bayesFactors-enumerate, eval = F}
genericEndorsementPriorModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var phi = uniformDraw(_.range(eps, 1-eps, 0.1))
  var g = uniformDraw(_.range(eps, 1-eps, 0.05))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  var logLike = sum(map(function(d){
    var scr = log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    )
    return scr
  }, preprocessedResponses))
  return logLike
}
'
genericEndorsementUnstructuredModelPriorLikelihoodEnumerate <- '
var eps = 0.00000001;

var model = function(){
  var g = uniformDraw(_.range(eps, 1-eps, 0.2))
  var d = uniformDraw(_.range(eps, 100, 2))
  var stableParams = betaShape({g, d});
  var stableComponent = Beta(stableParams);
  var logLike = sum(map(function(d){
    return stableComponent.score(d)
  }, preprocessedResponses))
  return logLike
}
'
```

```{r generic-endorsement-priors-bayesFactorsRunEnumerate, cache = T, eval =F}
marginal.prior.likelihoods <- data.frame()

for (p in gen.endorse.properties){
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

  m.gen.endorse.priors.logLike.enum1 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementPriorModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  m.gen.endorse.priors.logLike.enum0 <- webppl(
    paste(genericEndorsementPriorModelHelpers,
          genericEndorsementUnstructuredModelPriorLikelihoodEnumerate, sep = '\n'), 
    data = priorData, data_var = "data",
    model_var = "model", 
    inference_opts = list(method = "enumerate")
    )

  marginal.prior.likelihood1 <- logmeanexp(m.gen.endorse.priors.logLike.enum1$support)
  marginal.prior.likelihood0 <- logmeanexp(m.gen.endorse.priors.logLike.enum0$support)

  marginal.prior.likelihoods <- bind_rows(
    marginal.prior.likelihoods, 
    data.frame(Property = p, structuredLL = marginal.prior.likelihood1, unstructuredLL = marginal.prior.likelihood0)
  )
}

marginal.prior.likelihoods <- marginal.prior.likelihoods %>% mutate(logBF = structuredLL - unstructuredLL, BF = exp(logBF))

```

```{r generic-endorsement-priors-model-run, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 1000
lg = 0
example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )

for (p in example.generics.prior.properties ) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

    m.gen.endorse.priors.structured <- webppl(
      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        isPresent = rbinom(1, 1, prob = phi),
        prevalence = ifelse(isPresent == 1, 
                           rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
                           rbeta(n = 1,
                                 shape1 = 1,
                                 shape2 = 100)),
        Property = p, src = "Structured"
      ) %>% ungroup()

    m.gen.endorse.priors.unstructured <- webppl(
      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

    m.gen.endorse.priors.unstructured.predictive <- m.gen.endorse.priors.unstructured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        prevalence = rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
        Property = p, src = "Unstructured"
      ) %>% ungroup()

    m.gen.endorse.priors.posteriorPredictive <- bind_rows(
      m.gen.endorse.priors.posteriorPredictive,
      bind_rows(
       m.gen.endorse.priors.structured.predictive %>%
          select( src, Property, prevalence),
      m.gen.endorse.priors.unstructured.predictive %>%
          select( src, Property, prevalence),
      data.frame(Property = p,
                 src = "Data",
                 prevalence = priorData/100)
      )
    )

}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

```

```{r generic-endorsement-priors-figure2, eval = F}
ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")
```

### 2018-02-18 paper/appendix-bda.Rmd

@@
 The model has a single free parameter: the optimality parameter in Eq. \ref{eq:S1}.
-Other model parameters (governing the prevalence prior $P(h)$ and the referent-prevalence $h'$) are estimated using additional behavioral data (e.g., prior elicitation tasks). 
+Other model parameters (governing the prevalence prior $P(p_{fk})$ and the referent-prevalence $P_{fk'}$) are estimated using additional behavioral data (e.g., prior elicitation tasks). 
 Througout the paper, we model all sources of data (prevalence prior data, endorsement data) using a single joint-inference Bayesian data analytic model.
@@
 To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the prevalence prior data (described above) to create a single, joint-inference model where the optimality parameter $\lambda_1$ (Eq.
-\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_f(h)$ for each property $f$) using data from Expt.
+\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $p{fk'}$ for each category $k'$ and property $f$ and the parameters of the prevalence priors $P_(p_{fk})$ for each property $f$) using data from Expt.
 1a \& b (Figure \ref{fig:genericsModelDiagram}).
@@
 The referent-category prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
-The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P_f(h)$, the referent-prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
+The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P(p_{fk})$, the referent-prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.

### 2018-02-18 paper/case1-generics.Rmd

@@
 
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
+Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
 In addition, generics have been the case study of choice for the semantics of the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
@@
 1a).
-We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(h)$ (Expt. 1b).
-This elicitation procedure includes measurements of the referent-category feature-probabilties $h'$ (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
+We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$ (Expt. 1b).
+This elicitation procedure includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
 \ref{eq:S1}) as well as for simpler, alternative models.
@@
 
-In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
+In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
+Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
 We next measure the prevalence prior distribution and articulate a set of formal models that try to predict these endorsement data.
@@
 
-The prevalence prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
+The prevalence prior $P(p_{fk})$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
 To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
@@
 
-This thought experiment decomposes the prevalence prior $P(h)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(h \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$ and perform  Bayesian data analysis to accurately reconstruct the prevalence prior.
-We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences in Expt. 1a.
+This thought experiment decomposes the prevalence prior $P(p_{fk})$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p_{fk} \mid k)$.
+We will use this decomposition to measure the prevalence prior $P(p_{fk}) = \int_{k} P(p_{fk} \mid k) \diff k$ and perform Bayesian data analysis to accurately reconstruct the prevalence prior.
+We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
 To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
@@
 
-Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(h)$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category prevalence (e.g, the prevalence of laying eggs among robins).
-There are several substantive components to this hypothesis: (a) the prior distribution $P(h)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
+Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p_{fk})$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category prevalence (e.g, the prevalence of laying eggs among robins).
+There are several substantive components to this hypothesis: (a) the prior distribution $P(p_{fk})$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
 not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
@@
 <!-- Cue validity is not unrelated to the prevalence prior.  -->
-<!-- The prevalence prior $P(h)$ is a probability distribution, which can decomposed into a distribution on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$. -->
+<!-- The prevalence prior $P(p_{fk})$ is a probability distribution, which can decomposed into a distribution on kinds $P(k)$ and the likelihood of a prevalence given the kind $P(h \mid k)$. -->
 <!-- For simplicity, assume we have perfect knowledge of the prevalence for each kind: $P(h \mid k) = P(f \mid k)$. -->
@@
 
-A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaning the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
+A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaining the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
 This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
@@
 
-The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpretor.
+The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter.
 The endorsement model (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpretor (Eq.
-\ref{eq:L0}) conditioned on a particular referent-category prevalence $h'$ (e.g.,  the percentage of robins that lay eggs).
-We use the empirically estimated referent-category prevalence (the same as used in the baseline regression model) as the referent-category prevalence $h'$ in the endorsement model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's prevalence prior $P(h)$.
+\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpreter (Eq.
+\ref{eq:L0}) conditioned on a particular referent-category prevalence $p_{fk'}$  (e.g.,  the percentage of robins that lay eggs).
+We use the empirically estimated referent-category prevalence (the same as used in the baseline regression model) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
+The empirically measured priors from Expt. 1b are used as the literal interpreter's prevalence prior $P(p_{fk})$.
 
-To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category prevalence $h'$, prevalence priors $P(h)$ (both from Expt.
+To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt.
 1b data), and the endorsement data (Expt.
@@
 The endorsement model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burnin.
+To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burn-in.
 
@@
 To provide the strongest possible test, we make the fixed-threshold a parameter of the data-analytic model, to search for the best possible fixed-threshold. 
-Finally, a fixed-threshold model will have to accomodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent prevalence is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
-Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(h)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
+Finally, a fixed-threshold model will have to accommodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent prevalence is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
+Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p_{fk})$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
 This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
@@
 
-To evaluate the fixed-threhsold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
+To evaluate the fixed-threshold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
 The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
@@
 -->
-<!-- The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data. -->
+<!-- The fixed-threshold model, even with access to the full prior distribution $P(p_{fk})$, falls short in explaining the data. -->
 
@@
 The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
+The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distribution. 
 Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
@@
 Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propogation [@Rhodes2012] to motivation [@Cimpian2007].
+Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
 Heretofore, however, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations, knowing when they are true and false.
@@
 To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent prevalence and the prevalence priors), which people have access to via their mental representations of the category.
-We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and feature-probabilitiy priors (Case 3).
-In addition, we take this opportunty to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.
+We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and feature-probability priors (Case 3).
+In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.
 

### 2018-02-18 paper/case2-habituals.Rmd

@@
 Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
-When children describe their lives to other, a surprisingly large amount of the langauge produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
+When children describe their lives to other, a surprisingly large amount of the language produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
 Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
@@
 For the generalization "Mary smokes", instances of the category being generalized are *instances of Mary* and if for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
-We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarttes; Expt. 2a).
+We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2a).
 We then measure endorsements of habitual statements while manipulating the *referent-prevalence*  (Expt. 2b), and use our computational model to predict habitual endorsements. 
@@
 We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people).
-We will aassume for simplicity that people who have never done the action before will rarely or never do the action.
+We will assume for simplicity that people who have never done the action before will rarely or never do the action.
 
@@
 These questions were designed to measure the two central components of the prevalence prior model.
-We anticipated there to be different beliefs about the rates and relative proportions of peopel depending on whether an actor is male or female, so we asked about both genders separately.
+We anticipated there to be different beliefs about the rates and relative proportions of people depending on whether an actor is male or female, so we asked about both genders separately.
 
@@
 Each item was modeled independently for each gender.
-We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burnin.
+We learned about the credible values of the parameters by running MCMC for 100,000 iterations, discarding the first 50,000 for burn-in.
 
@@
 
-To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analagous to that used in Case Study 1 (Expt. 1b).
+To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analogous to that used in Case Study 1 (Expt. 1b).
 The only difference is that we estimate the mixture component $\phi$ directly from responses to Question 1. 
@@
 
-In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigaerettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).
+In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigarettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).
 
@@
 Analyses which use the rate prior distribution $P(p_f)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prior distribution.
-To model the uncertainty in the input measurements, we bootstrap the data for the regression models and we construct joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-thresold).
+To model the uncertainty in the input measurements, we bootstrap the data for the regression models and we construct joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-threshold).
 
@@
 This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus is relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
-Thus, we take this parameter as an index of the *distinctiveness* of the action, analagous to *cue validity* in the case study of generic langauge.
+Thus, we take this parameter as an index of the *distinctiveness* of the action, analogous to *cue validity* in the case study of generic language.
 We construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
@@
 It can differentiate events done with the same frequency (e.g., *writing poems* vs. *novels*, 3 times in the past 5 years), and increase endorsement of the more rare action (*novels*). 
-Still, this model fails to capture fine-grained details in endorsment.
+Still, this model fails to capture fine-grained details in endorsement.
 For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
@@
 
-We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transormed past frequency and the experimental condition (baseline, preventative, enabling).
+We confirm these observations using a linear mixed-effects model, predicting the log-transformed responses from the log-transformed past frequency and the experimental condition (baseline, preventative, enabling).
 To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
@@
 A regression model that takes into the frequency and the *distinctiveness* of the action does a reasonable job at explaining the variance in this data.
-We note that this kind of model is merely a re-decription of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization. 
+We note that this kind of model is merely a re-description of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization. 
 A theory of the semantics of a generalization must formalize the truth-conditions of the generalization as well as how those truth-conditions relate to endorsement. 
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventated future occurences of the action.
+In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventative future occurrences of the action.
 We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
 We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
-Predicted prevalence thus captures the infleunce of top-down moderators (e.g., intervening causal forces) on endorsement.
+Predicted prevalence thus captures the influence of top-down moderators (e.g., intervening causal forces) on endorsement.
 <!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.

### 2018-02-18 paper/coverletter.tex

@@
 This paper explores the linguistic means by which generalizations are communicated.  
-We present a Bayesian model of endorsing generalizations and show that it predicts human judgments with high quantitative accuracy across several experiments in diverse domains.
+We present a Bayesian model of endorsing generalizations and show that it predicts context-sensitive human judgments with high quantitative accuracy across several experiments in diverse domains.
 The theory suggests that the language of generalizations can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
@@
 Understanding how the world works requires learning generalizations. 
-The kinds of observations that would facilitate such learning, however, may be rare (e.g., \emph{figuring out that lightning strikes tall objects}) or costly (e.g., \emph{learning that certain plants are poisonous}).
-We do not need to need taste every plant to figure out which ones are poisonous; we don't need to stand under objects of various heights to learn that lightning strikes tall objects.
-Language allow us to learn generalizations from each other.
+The kinds of observations that would facilitate such learning, however, may be rare (e.g., figuring out that lightning strikes tall objects) or costly (e.g., learning that certain plants are poisonous).
+We do not need to need taste every plant to figure out which ones are poisonous, however.
+Language lets us learn generalizations from each other.
 
@@
 %Given that inductive generalization can be described by probability (e.g., the probability that the next instance of the category will have a feature), it seems natural that the core meaning generalizations in language would relate to this predictive probability.
-Despite the ubiquity of the language, its meaning is philosophically puzzling and has resisted precise formalization. 
+Despite their ubiquity and morphosyntactic simplicity, the language of generalization has a meaning, which is philosophically puzzling and has resisted precise formalization. 
 %However, the language of generalizations displays extreme sensitivities to context, which has heretofore crippled previous attempts to formalize this major function of language. 
@@
 %The major issue in formalizing the language of generalizations is determining what makes such statements true or false.
-For example, generics can describe properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority displaying the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
+For example, generics can describe properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority with the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
 \emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier (i.e., \emph{some}) would suffice.
-Habitual and causal language display similar context-sensitivites:
-If John smokes once a year, one might hesitate to endorse the statement \emph{John smokes}.
+Habitual and causal language display similar context-sensitivities:
+If John smokes once a year, one might hesitate to endorse that he \emph{smokes}.
 Yet, climbing a mountain once a year makes John really seem like he \emph{climbs mountains}.
@@
 In this paper, we take the context-sensitivity of generalizations seriously and formalize the hypothesis that the core meaning of generalizations is \emph{simple but underspecified}. 
-We embed this idea in a simple, rational model of communication and use it to address the fundamental question: What makes the language of generalizations true or false?
-Our answer is that endorsement (true or false?) is a speaker's decision about whether or not to say the generalization to a naive listener.
+We embed this idea in a simple, rational model of communication and use it to address the fundamental question: What makes generalizations in language true or false?
+Our answer is that endorsement (a true or false judgment) is a speaker's decision about whether or not to say the generalization to a naive listener.
 Our model is the first formal model to make precise quantitative predictions about the language of generalization.
@@
 We have previously received peer-review of a similar manuscript submitted to other top-ranking journals including \emph{Psychological Review}.
-Those reviews questioned how much our work advances our understanding of the language of generalization and highlighted the need for comparison to other models. 
-This manuscript differs from previous submissions in two major ways.
+Those reviews questioned how much our work advances understanding of the language of generalization and highlighted the need for comparison to other models. 
+The current manuscript differs from previous submissions in two major ways.
 %We show how this model naturally explains the flexibility in endorsement patterns via interlocutors' prior beliefs about the property or event in the question.
-The empirical and much of the philosophical literatures has been focused on generalizations about categories, or generic language, which our previous manuscript also focused on.
-In this paper, we investigate three case studies: generalizations about categories, events, and causes. 
+The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.
+Our previous manuscript also focused on categories; in this paper, however, we investigate three case studies: generalizations about categories, events, and causes. 
 Immediately we see the generality of our formal model: We are able to explain context-sensitive endorsements across these three domains without adopting domain-specific assumptions.

### 2018-02-18 paper/coverletter.tex

@@
 The language of generalization is most commonly studied in predications of categories (e.g., ~\emph{Birds fly}), otherwise known as \emph{generic language}.
-But different semantic types can described in generalization, including events (\emph{habitual language}; e.g., ~\emph{Mary swims after work}) and causal relationships (\emph{causal language}; e.g., ~\emph{Staring at the sun makes you go blind}).
+But different semantic types can be described in generalization, including events (\emph{habitual language}; e.g., ~\emph{Mary swims after work}) and causal relationships (\emph{causal language}; e.g., ~\emph{Staring at the sun makes you go blind}).
 Generalizations are ubiquitous in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
@@
 
-We have previously received peer-review of a similar manuscript submitted to other top-ranking journals including \emph{Psychological Review}.
-Those reviews questioned how much our work advances understanding of the language of generalization and highlighted the need for comparison to other models. 
-The current manuscript differs from previous submissions in two major ways.
-%We show how this model naturally explains the flexibility in endorsement patterns via interlocutors' prior beliefs about the property or event in the question.
-The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.
-Our previous manuscript also focused on categories; in this paper, however, we investigate three case studies: generalizations about categories, events, and causes. 
-Immediately we see the generality of our formal model: We are able to explain context-sensitive endorsements across these three domains without adopting domain-specific assumptions.
+We have previously received peer-review of a related manuscript submitted to top-ranking journals including \emph{Psychological Review}.
+Those reviews raised a umber of points regarding the presentation and generality of our work at the time, and highlighted the need for comparison to other models. 
+The current manuscript differs from previous submissions a number of important ways.
+First, we have completely re-written the paper for clarity and focus, especially simplifying and streamlining the modeling sections.
+Second, we have extended from generalizations about categories, or generic language, to investigate three case studies: generalizations about categories, events, and causes.
+We are able to explain endorsements across these three domains without adopting domain-specific assumptions. 
 Furthermore, each case study naturally lends methodological advantages to provide further tests of our model.
-With event generalizations, we are able to interrogate the underlying semantic scale, and find that speakers' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, is what drives endorsements.
-With causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge, and show it is in fact causally related to endorsement. 
+(E.g.
+with causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge.)
+%The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.
+%Our previous manuscript also focused on categories; in this paper, however, we investigate three case studies: generalizations about categories, events, and causes. 
+%Immediately we see the generality of our formal model: We are able to explain context-sensitive endorsements across these three domains without adopting domain-specific assumptions.
+%Furthermore, each case study naturally lends methodological advantages to provide further tests of our model.
+%With event generalizations, we are able to interrogate the underlying semantic scale, and find that speakers' subjective beliefs about what is likely to be the case in the future, and not the objective truth about what has been the case in the past, is what drives endorsements.
+%With causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge, and show it is in fact causally related to endorsement. 
 Finally, we develop three alternative models: two linear models based on empirically-elicited statistical knowledge and one rich, cognitive model which lacks the \emph{underspecification of meaning} at the core of our hypothesis.
 These alternative models fail to account for key aspects of the context-sensitivity that is observed in the data and that our full model predicts.
-These alternative models and the empirical paradigms used provide strong tests of the theoretical contribution of our paper. 
+%These alternative models and the empirical paradigms used provide strong tests of the theoretical contribution of our paper. 
 %This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
+Overall we feel that this paper represents a much improved, generalized and streamlined, study of generalization in language.
+(We would be happy to provide detailed responses to previous reviewers, however we feel this would be of limited use given the major changes in content and presentation.)
 
@@
 
-This work will be of strong interest to psychologists, as well as linguists, philosophers, and computer scientists interested in language and interaction.
+This work will be of interest to psychologists, as well as linguists, philosophers, and computer scientists interested in language and interaction.
 The puzzles of generalizations in language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
@@
 
-The following reviewers have expertise in the phenomenology of generic language, experimental studies of pragmatics, and/or the Bayesian modeling tools we use:
+We recommend the following reviewers have expertise in the phenomenology of generic language, experimental studies of language use, and/or the Bayesian modeling tools we use:
 

### 2018-02-18 paper/coverletter.tex
streamline presentation in first few pagraphs, lightly edit throughout

@@
 We present a Bayesian model of endorsing generalizations and show that it predicts context-sensitive human judgments with high quantitative accuracy across several experiments in diverse domains.
-The theory suggests that the language of generalizations can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
+The theory suggests that the language of generalization can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
 
 Understanding how the world works requires learning generalizations. 
-The kinds of observations that would facilitate such learning, however, may be rare (e.g., figuring out that lightning strikes tall objects) or costly (e.g., learning that certain plants are poisonous).
+The kinds of observations that would facilitate such learning may be rare, however (e.g., figuring out that lightning strikes tall objects) or costly (e.g., learning that certain plants are poisonous).
 We do not need to need taste every plant to figure out which ones are poisonous, however.
@@
 
-The language of generalization is most commonly studied in predications of categories (e.g., ~\emph{Birds fly}), otherwise known as \emph{generic language}.
-But different semantic types can be described in generalization, including events (\emph{habitual language}; e.g., ~\emph{Mary swims after work}) and causal relationships (\emph{causal language}; e.g., ~\emph{Staring at the sun makes you go blind}).
-Generalizations are ubiquitous in everyday conversation (\emph{Movie theaters are cold.}), the speech of young children (\emph{Slides aren't for grown ups!}), child-directed speech (\emph{Dogs are friendly.}), political and scientific discourse (\emph{Politicians make promises.}, \emph{Psychology experiments don't replicate.}), stereotypes (\emph{Boys are good at math.}), motivation (\emph{Big girls eat broccoli!}), and many other facets of experience.
+The language of generalization is most commonly studied in predications of categories (e.g.,~``Birds fly.''), otherwise known as \emph{generic language}.
+But generalization exists beyond classically defined categories (e.g., natural and artifact kinds): Events are described in generalization (e.g.,~``Mary swims after work.''; \emph{habitual language}) as well as causal relationships (e.g.,~``Staring at the sun makes you go blind''; \emph{causal language}).
+Generalization are ubiquitous in everyday conversation (``Movie theaters are cold.''), the speech of young children (``Slides aren't for grown ups!''), child-directed speech (``Dogs are friendly.''), political and scientific discourse (``Politicians make promises.'', ``Psychology experiments don't replicate.''), stereotypes (``Boys are good at math.''), motivation (``Big girls eat broccoli!''), and many other facets of experience.
 
 %Given that inductive generalization can be described by probability (e.g., the probability that the next instance of the category will have a feature), it seems natural that the core meaning generalizations in language would relate to this predictive probability.
-Despite their ubiquity and morphosyntactic simplicity, the language of generalization has a meaning, which is philosophically puzzling and has resisted precise formalization. 
+Despite their ubiquity and morphosyntactic simplicity, the language of generalization has a philosophically puzzling meaning, which has resisted precise formalization. 
 %However, the language of generalizations displays extreme sensitivities to context, which has heretofore crippled previous attempts to formalize this major function of language. 
@@
 %The major issue in formalizing the language of generalizations is determining what makes such statements true or false.
-For example, generics can describe properties contained by a majority (e.g., \emph{Dogs bark}) but still can be felicitous based on only a minority with the property (e.g., \emph{Robins lay eggs}, even though only adult, female, fertile robins do).
-\emph{Mosquitos carry malaria} sounds true, even though only 1\% of them do, highlighting that the acceptability of generics can be so flexible as to include cases where only the weakest quantifier (i.e., \emph{some}) would suffice.
+For example, true generic statements can describe properties contained by a majority of the category (e.g., ``Dogs bark.''), roughly half of the category (e.g., ``Robins lay eggs.'' is only true of adult, female, fertile robins), and even an outstanding minority (e.g., ``Mosquitos carry malaria.'' is true of less than 1\% of mosquitoes).
 Habitual and causal language display similar context-sensitivities:
-If John smokes once a year, one might hesitate to endorse that he \emph{smokes}.
-Yet, climbing a mountain once a year makes John really seem like he \emph{climbs mountains}.
-\emph{Drinking moonshine makes you go blind} and so does \emph{staring at the sun}, but neither statement conveys precise information about the relative risk.
+``John smokes'' may be infelicitous if he does so only once a year, but ``Mary climbs mountains'' seemingly is fine with the same frequency.
+Both \emph{drinking moonshine}  and \emph{staring at the sun} will ``...make you go blind'', though the latter seems more dangerous than the former despite neither statement conveying precise risk information.
 
@@
 %The dominant view in psychology has been to focus on special conceptual relations that supposedly determine what makes the language the generalization true or false.
-In this paper, we take the context-sensitivity of generalizations seriously and formalize the hypothesis that the core meaning of generalizations is \emph{simple but underspecified}. 
-We embed this idea in a simple, rational model of communication and use it to address the fundamental question: What makes generalizations in language true or false?
-Our answer is that endorsement (a true or false judgment) is a speaker's decision about whether or not to say the generalization to a naive listener.
-Our model is the first formal model to make precise quantitative predictions about the language of generalization.
+In this paper, we take seriously the context-sensitivity of such language and investigate the hypothesis that the meaning at the core of the language of generalization is \emph{simple but underspecified}.
+We formalize and embed this idea in a simple, rational model of communication and use it to address the fundamental outstanding question: What makes generalizations true or false?
+Our answer is that endorsement (a true or false judgment) is a speaker's decision about whether or not to say the \emph{simple but underspecified} generalization to a naive listener.
+Our model is the first formal model to make precise quantitative predictions about human understanding of generalizations in language.
 
@@
 Those reviews raised a umber of points regarding the presentation and generality of our work at the time, and highlighted the need for comparison to other models. 
-The current manuscript differs from previous submissions a number of important ways.
+The current manuscript differs from previous submissions in a number of important ways.
 First, we have completely re-written the paper for clarity and focus, especially simplifying and streamlining the modeling sections.
-Second, we have extended from generalizations about categories, or generic language, to investigate three case studies: generalizations about categories, events, and causes.
-We are able to explain endorsements across these three domains without adopting domain-specific assumptions. 
-Furthermore, each case study naturally lends methodological advantages to provide further tests of our model.
-(E.g.
-with causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge.)
+Second, we have extended from generalizations about categories (or \emph{generic language}) to investigate three case studies: generalizations about categories, events, and causes.
+We are able to explain endorsements across these three domains with minimal domain-specific assumptions. 
+Furthermore, each case study naturally lends methodological advantages to provide further tests of our hypothesis/model (e.g., with causal generalizations, we are able to manipulate---rather than merely measure---prior knowledge).
 %The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.
@@
 %This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
-Overall we feel that this paper represents a much improved, generalized and streamlined, study of generalization in language.
-(We would be happy to provide detailed responses to previous reviewers, however we feel this would be of limited use given the major changes in content and presentation.)
+Overall we feel that this paper represents a much improved, generalized and streamlined investigation of generalization in language.
+(We would be happy to provide detailed responses to previous reviewers; presently, we feel this would be of limited use given the major changes in content and presentation.)
 
@@
 This work will be of interest to psychologists, as well as linguists, philosophers, and computer scientists interested in language and interaction.
-The puzzles of generalizations in language are immediately compelling to a general audience, the more so because of their connections to cognitive development, cultural transmission of knowledge, and propagation of stereotypes.
+The puzzles of generalizations in language are immediately compelling to a general audience, the more so because of their connections to cognitive development, propagation of stereotypes, and cultural transmission of knowledge.
 Our solution represents the first formal model of generalization in language to be validated by quantitative agreement with human behavioral data.

### 2018-02-18 paper/coverletter.tex
minor tweaks to cl

@@
 
-\textwidth 6.75in
+\textwidth 6.55in
 \textheight 9.25in
@@
 This paper explores the linguistic means by which generalizations are communicated.  
-We present a Bayesian model of endorsing generalizations and show that it predicts context-sensitive human judgments with high quantitative accuracy across several experiments in diverse domains.
+We present a Bayesian model of endorsing generalizations and show that it predicts context-sensitive human judgments with high quantitative accuracy across diverse experimental contexts.
 The theory suggests that the language of generalization can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
@@
 We do not need to need taste every plant to figure out which ones are poisonous, however.
-Language lets us learn generalizations from each other.
+Language lets us learn complex and abstract generalizations from each other.
 
 The language of generalization is most commonly studied in predications of categories (e.g.,~``Birds fly.''), otherwise known as \emph{generic language}.
-But generalization exists beyond classically defined categories (e.g., natural and artifact kinds): Events are described in generalization (e.g.,~``Mary swims after work.''; \emph{habitual language}) as well as causal relationships (e.g.,~``Staring at the sun makes you go blind''; \emph{causal language}).
-Generalization are ubiquitous in everyday conversation (``Movie theaters are cold.''), the speech of young children (``Slides aren't for grown ups!''), child-directed speech (``Dogs are friendly.''), political and scientific discourse (``Politicians make promises.'', ``Psychology experiments don't replicate.''), stereotypes (``Boys are good at math.''), motivation (``Big girls eat broccoli!''), and many other facets of experience.
+But generalization exists beyond classically-defined natural and artifact kinds: Events are described in generalization (e.g.,~``Mary swims after work.''; \emph{habitual language}) as well as causal relationships (e.g.,~``Staring at the sun makes you go blind''; \emph{causal language}).
+Generalizations are ubiquitous in everyday conversation (``Movie theaters are cold.''), the speech of young children (``Slides aren't for grown ups!''), child-directed speech (``Dogs are friendly.''), political and scientific discourse (``Politicians make promises.'', ``Psychology experiments don't replicate.''), motivation (``Big girls eat broccoli!''), stereotypes (``Boys are good at math.''), and many other facets of experience.
 
@@
 We have previously received peer-review of a related manuscript submitted to top-ranking journals including \emph{Psychological Review}.
-Those reviews raised a umber of points regarding the presentation and generality of our work at the time, and highlighted the need for comparison to other models. 
+Those reviews raised a number of points regarding the presentation and generality of our work at the time, and highlighted the need for comparison to other models. 
 The current manuscript differs from previous submissions in a number of important ways.
@@
 %This novel approach for generalizations in language opens up a number of interesting questions about the nature of conceptual structure and its linguistic traces, which we discuss at the end of the paper.
-Overall we feel that this paper represents a much improved, generalized and streamlined investigation of generalization in language.
+Overall we feel that this paper represents a much improved, generalized and streamlined investigation of generalization in language, and a major breakthrough in computational modeling of language understanding.
 (We would be happy to provide detailed responses to previous reviewers; presently, we feel this would be of limited use given the major changes in content and presentation.)
@@
 Our solution represents the first formal model of generalization in language to be validated by quantitative agreement with human behavioral data.
-It is not, however, uncontroversial: we champion a statistical view that has been often dismissed in the literature.
+It is not, however, uncontroversial: We champion a statistical view that has been often dismissed in the literature.
 Indeed, in presentations around the world we have found this work to excite broad interest and engagement.

### 2018-02-20 paper/comgen-paper.Rmd
remove cacheing flags for some figures
previously, rmd-generated figures were cached for hastening compiling time. this caused major merge conflicts after a recent makover of figures.
so i deleted rmd-generated figures, but forgot to turn off the cacheing flags so that the figures could re-generated. this fixes that.
incorporate ellens feedback re intro

@@
 ---
-title             : "The language of generalization"
+title             : "The Language of Generalization"
 shorttitle        : "The language of generalization"
@@
 <!-- Learning that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to thrive in our open-ended world. -->
-Acquiring understanding that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
+Knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
 Yet such knowledge can be difficult to extract from the environment: The relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
-Fortunately, we are not bound to acquiring generalizations on our own; language allow us to communicate generalizations between each other.
-By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness many lightning strikes.
-Furthermore, flexibly communicating generalizations from one generation to the next may be a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].
+Fortunately, we are not limited to acquiring generalizations on our own; language allow us to communicate generalizations to each other.
+By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness lightning strikes.
+Furthermore, flexibly communicating generalizations from one generation to the next is a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].
 
@@
 
-Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models of and none that have made precise, quantitative predictions that match human intuitions.
+Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models and none that have made precise, quantitative predictions that match human intuitions.
 The major challenge in formalizing generalization in language is determining what makes the statements true or false.
@@
 
-These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not the only factor that goes into making a generalization true or false.
+These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not what makes generalization true or false.
 The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
@@
 -->
-"Bishops move diagonally" not because bishops tend to move diagonally but rather because those are the rules of the game.
+"Bishops move diagonally" or "The Speaker of the House succeeds the Vice President" are true statements not because of a tendency on behalf of the category to uphold the property.
+Rather, the utterances are believed to point out the existence of a conceptual structure (e.g., that bishops have a certain role in the game of chess).
 The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013].
@@
 Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
-To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
-We create an endorsement model based on this interpretation hypothesis, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
+However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
+Instead, we posit that the cut-off is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment.
+<!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
+-->
+With these ideas, we create an endorsement model, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
 The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
-
-<!-- The test of a unified semantic core is its ability to explain what makes the statements true or false. -->
-
-<!-- It is thus argued that there are qualitatively different kinds of generic statements (i.e., "striking", "characteristic", "statistical"), each with their own conditions on what makes them true.
--->
-<!-- This diversity is interesting, but what is common across generics? -->
-<!-- Is there some core meaning to *genericity*, a general unified principle that explains what makes generic statements true or false? -->
-<!-- Finally, formalizing such a theory is crucial to make explicit the relevant assumptions of the psychological or linguistic hypothesis meant to match human intuitions; this, in turn, makes the theory more testable.
--->
-<!-- We formalize such a semantics in a general cognitive modeling framework, and thus incorporate generalizations in language into a larger class of models designed to formalize concepts and common-sense reasoning [@Goodmanconcepts].
--->
 
@@
 
-<!-- We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.  -->
-
-<!-- We think prevalence may have been cast aside too quickly for two main reasons: (i) in previous empirical work, prevalence has been rather narrowly defined, as frequency, where in fact it can be more generally seen as probability (ii) the backround knowledge that adult speakers, whose intuitions are consulted to establish a theory of meaning, may bring to the table has not been explicitly considered or formalized in studies and theoretical work into the language of generalization.
--->
-
-<!-- We propose a formal, unified account of generalization in language that can make precise, quantitative predictions about these simple and ubiquituous utterances. -->
-<!-- We do so by first considering a much more well-studied form of generalization: generalization from observations.  -->
-<!-- The Bayesian probability calculus describes inductive generalizations in terms of probability, and this is has proven to be a good model of human generalization . -->
-
-<!-- We formalize this using a rational model of communication --- the Rational Speech Act (RSA) theory [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016]. -->
-<!-- Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their state of knowledge and communicative goals.  -->
-<!-- Heretofore, however, the fragments of language formalized in such models have been limited to *particular statements* that convey information about a specific entity or situation [e.g., in hyperbole: "My watch cost a million dollars"; @Kao2014, or vagueness: "John is tall"; @Lassiter2013].
--->
-<!-- The language of generalization does not make reference to entities in the world or concrete situations, but rather refer to unobservable concepts in the head. -->
-
-<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
-<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
-
 The paper is organized as follows. 
-In Section 1, we formalize the hypothesis that the core of meaning of a generalization in language is simple but *underspecified*, articulate a theory of relevant background knowledge used to understand a generalization in language, and develop a computational model of endorsement around these components.
+In Section 1, we formalize the hypothesis that the core meaning of a generalization in language is a simple but underspecified threshold, articulate a theory of relevant background knowledge used to understand a generalization in context, and develop a computational model of endorsement around these components.
 The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
-Sections 2-4 present our three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+Sections 2-4 present three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
 Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, where alternative models fall short.
-This work opens the door to understanding generalizations in richer, pragmatic language understanding contexts and building models that learn abstract knowledge from language.
+While alternative models fall short, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements.
+This work opens the door to understanding generalizations in richer, pragmatic language contexts and building models that learn abstract knowledge from language.
 
@@
 
+<!-- Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
+-->
+
 Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted.

### 2018-02-22 paper/case1-generics.Rmd
address ellens inline comments in intro and expts

@@
 
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
-In addition, generics have been the case study of choice for the semantics of the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
-Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
+Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
+In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
+However, intuitions and empirical data argue that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
 
 Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
-We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions [@Prasada2013]: *majority characteristic* (e.g., "Ducks have wings."),  *minority characteristic* (e.g., "Robins lay eggs."), *striking* (e.g.
-"Mosquitos carry malaria."),  *false generalization* (e.g., "Robins are female."), and *absent features* (e.g.
+We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g.
+"Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g.
 "Lions lay eggs.").
-We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt.
+We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt.
 1a).
@@
 A: Participants first generated animal names after seeing six example categories.
-B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3}
+B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3, cache = F}
 fig.priors.expt.stage1 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage1.jpeg", sep=""), scale = 1)
@@
 Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution.
-A completely uniform distribution would be represented as the y = x line."}
+A completely uniform distribution would be represented as the y = x line.", cache = F}
 load('../analysis/generics-priors-posteriorPredictives.Rdata')
@@
 
-Cue validity is linearly related to a point-estimate of the prevalence prior distribution (see Model section and Appendix A).
-It thus implicitly captures information about other categories, though cannot capture the structure that is present in the prevalence priors.
-To show that this structure is important, we explore a secondary baseline model based on prevalence and cue validity.
+Cue validity is a metric of how diagnostic the feature is of the kind, and is given formally by the probability of a kind given the feature $P(k \mid f)$.
+As discussed in the Computational Model section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
+Cue validity can thus be seen as a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution.
+
+To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity.
+Though the cue validity of a particular category by a particular property can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity in various ways from empirical data about distinctiveness [@Cree2006; @Khemlani2012].
+In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs.
+What is the probability that it is a robin?"; @Khemlani2012], though in the broader literature on semantic memory a *free production* paradigm is often employed [e.g., "X lays eggs.
+What do you think X is?"; @Cree2006].
+We found that these different ways of estimating cue validity diverge for a number of key cases, possibly due to an experimenter demand effect in the direct question paradigm.
+We thus used the data from the free production paradigm ($n = 100$) to estimate cue validity. 
+For a detailed analysis of the different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.
+
+<!-- It thus implicitly captures information about other categories, though cannot capture the structure that is present in the prevalence priors. -->
 
@@
 -->
-
-Though the cue validity of a particular (category, property) pair can be derived from the prevalence prior distribution, previous empirical studies of generic language have not done this.
-Instead, these studies estimate cue validity by asking a separate group of participants about the distinctiveness of features for given animals [e.g., @Khemlani2012], though different studies use different measurements.
-Preliminary analysis of these different measurements revealed that a *free production* paradigm [@Cree2006] is preferred.
-Participants ($n = 100$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
-For a detailed analysis of different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.
 
@@
 
-In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via the prevalence priors (e.g., the percentage of different kinds of animals that lay eggs).
+In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via our communicative model with prior knowledge about the distribution of prevalence (e.g., the prevalence of laying eggs for different kinds of animals).
 In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs.
@@
 are female".
-To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent prevalence and the prevalence priors), which people have access to via their mental representations of the category.
-We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and feature-probability priors (Case 3).
+However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.
+We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and prevalence priors (Case 3).
 In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

### 2018-02-22 paper/case2-habituals.Rmd
address ellens inline comments in intro and expts

@@
 
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
+Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely their observations. 
 Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
@@
 On one hand, speakers can only be certain about what has happened in the past.
-On the other hand, language has a communicative function, and it would be useful for speakers to convey their predictions of what will be the case in the future.
+On the other hand, it is important for speakers to be able to convey their predictions of what will be the case in the future.
 
 People can change their behavior abruptly due to a variety of decisions and outside events.
-We introduce these causal events into our minimal endorsement paradigm and measure their influence on endorsement.
+We introduce these causal events into our endorsement paradigm to measure their influence on endorsement.
 <!-- that either enable or prevent future actions. -->
-To provide the appropriate model-based analysis, participants in one condition make a prediction about what will be the case in the future (*predictive frequency*).
+To provide the appropriate model-based analysis, participants in one condition make a prediction about the future (*predictive frequency*).
 In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
 <!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
-We then compare two uncertain-thresholds models to each other: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt.
+We then compare two uncertain-thresholds models: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt.
 2b).
+In addition, we compare to baseline linear model that uses only the *predictive frequency* (no priors) to model endorsement.
 
@@
 In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
-By manipulating (rather than measuring) the referent frequency with which a person does an action, we showed how alternative models were insufficient to account for the gradience in endorsement.
-In particular, a fixed threshold model that has access to the same prior knowledge and uses the same information-theoretic decision rule as our uncertain-threshold model is unable to make different predictions for different frequencies.
+By manipulating (rather than measuring) the referent frequency, we showed how alternative models were unable to account for the gradience in endorsement.
+In particular, we show that prior knowledge in an information-theoretic, communicative model is not sufficient to produce gradience in endorsement: The fixed-threshold model, which has these components, does not make different predictions for different frequencies.
 Only our uncertain threshold model was able to precisely account for the wide range of endorsements.
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventative future occurrences of the action.
+In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and prevented future occurrences of the action.
 We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.

### 2018-02-22 paper/case3-causals.Rmd
address ellens inline comments in intro and expts

@@
 B: Prior elicitation task: Participants predict the results of the next 5 experiments.
-D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10}
+D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, cache=F}
 caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
@@
 
-```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
+```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
 figure.causals.endorsement <- bind_rows(
@@
 
-```{r figure-causals, fig.width=9, fig.height=4, cache = T, fig.cap="Endorsing generalizations about causes.
+```{r figure-causals, fig.width=9, fig.height=4, cache = F, fig.cap="Endorsing generalizations about causes.
 A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies.

### 2018-02-22 paper/comgen-paper.Rmd
address ellens inline comments in intro and expts

@@
 However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
-Instead, we posit that the cut-off is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment.
+Rather than throw-out the quantitative formalization of the threshold semantics, we posit that the threhsold is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment.
 <!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.

### 2018-02-28 paper/comgen-paper.Rmd
edits and comments on intro

@@
 
-Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models and none that have made precise, quantitative predictions that match human intuitions.
-The major challenge in formalizing generalization in language is determining what makes the statements true or false.
+Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models and none that have made precise, quantitative predictions that match human judgements.
+The major challenge in formalizing generalization in language is determining what makes the statements seem true or false.
 When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
@@
 These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not what makes generalization true or false.
-The predominantly studied generic statements are thought to refer to *kinds* [@Leslie2008] and thus may the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
+Generic statements are instead thought to refer to *kinds* [@Leslie2008] and thus may be the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
 <!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
@@
 To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
+Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication for the language of generalization.
+\ndg{cuttoff / threshold not mentioned before this, need to introduce...}
 However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
@@
 -->
-With these ideas, we create an endorsement model, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
-The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
+With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false.
+The assumptions of the theory and the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
+Our model is the first to make quantitative predictions about human endorsements of generalizations in language.
 
@@
 The paper is organized as follows. 
-In Section 1, we formalize the hypothesis that the core meaning of a generalization in language is a simple but underspecified threshold, articulate a theory of relevant background knowledge used to understand a generalization in context, and develop a computational model of endorsement around these components.
-The endorsement model's predictions depend upon the background knowledge and the prevalence communicated, which we demonstrate via simulation.
+In Section 1, we formalize the hypothesis that the core meaning of a generalization in language is a simple but underspecified threshold on a subjective probability, articulate a theory of relevant background knowledge used to understand a generalization in context, and use these components to develop a computational model of endorsement.
+The endorsement model's predictions depend upon relevant background knowledge and the prevalence communicated, which we demonstrate via simulation.
 Sections 2-4 present three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement. 
-While alternative models fall short, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements.
+Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement of generalization sentences. 
+We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, while alternative models fall short.
 This work opens the door to understanding generalizations in richer, pragmatic language contexts and building models that learn abstract knowledge from language.

### 2018-03-01 paper/comgen-paper.Rmd
address half of ellens comments in discussion

--- 2018-02-22 paper/comgen-paper.Rmd
@@
 
-It is a remarkable fact that so much is learned from ideas expressed vaguely in words.
+It is remarkable that so much is learned from ideas expressed vaguely in words.
 Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions is simple, but underspecified. 
-To our knowledge, this is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
-
-As a formal theory of the language of generalization, our framework aims to unify large swaths of language that are, on their surface, quite distinct from one another: "Birds lay eggs", "Sally smokes", "Herb X makes animals sleepy".
+We have argued that the core meaning of such linguistic expressions can be understood as simple but underspecified. 
+To our knowledge, ours is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
+
+As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types: "Robins lay eggs" (categories), "Sally smokes" (events), "Herb X makes animals sleepy" (causes).
+Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we take to mean *predictive probability* (as opposed to frequency).
+We test this theory by exploring its implications for *endorsement*, operationalized as a speaker's decision about whether or not to produce the generalization to naive listener. 
+Endorsement, we show, depends in systematic ways on the listener's prior beliefs about the prevalence.
 <!-- What these expressions have in common is not surface features but generalization (also referred to as *genericity*). -->
-We have formalized a unified, core meaning of generalization in language using the underlying scale of predictive probability or *prevalence*.
-We showed that endorsements of all three types of generalizations exhibit the same sensitivity to a background distribution comprised of other categories (Expt. 1, 2a \& 2b, 3).
-As well, our framework naturally accounts for a number of logically puzzling category generalizations (Expt.
-1) and provides an avenue for top-down moderators on language use, by elucidating the semantic scale as defined by a subjective, predictive probability, not mere frequency (Expt.
+This framework accounts for a number of philosophically puzzling generic statements (Expt.
+1), naturally extends to other domains of generalizations (habituals and causals; Expts.
+2 \& 3), and provides an avenue for top-down moderators on language use by way of *predictive* probability (Expt.
 2c).
-Finally, we have shown that listeners' prior knowledge about the prevalence of the feature in other categories is directly influences their endorsement of generalizations for the same category (Expt.
-3).
+We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
 <!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->
-
-In this paper, we proposed a model for interpreting and endorsing generalizations in language by formalizing a simple semantic theory in a communicative model with shared background knowledge.
-Our pair of models can be seen as a special case of a Rational Speech Act model, a rational framework of pragmatic language understanding [@Frank2012; @Goodman2016].
-The endorsement model, which we use to generate predictions for our three case studies, is a special case of a speaker model who can only produce one of two utterances: the generalization or silence. 
-The interpreter model is a "literal listener", who updates its beliefs by averaging over plausibly thresholds given prior knowledge and the simple truth-functional meaning.
 
@@
 <!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
-The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from background, world knowledge.
-This formal separation is a key advancement beyond previous accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data.
-That is, we provide a route for precise quantitative influence of conceptual knowledge on generic language by way of shared background knowledge between speakers and listeners.
-In the rest of this discussion, we elaborate some key features of the theory that warrant further investigation, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
+The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge.
+This formal separation is a key advancement beyond previous theoretical accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
+Our communicative framework also includes a model of a listener who interprets generalization.
+Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work. 
+In the rest of this discussion, we elaborate how our model relates to other problems in language understanding, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
+
+<!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->
 
@@
 
+<!-- ## Generic Identification -->
+
+<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
+<!-- The bare plural construction can also indicate a specific plural predication. -->
+<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
+<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
+-->
+
+<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences. -->
+<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
+-->
+<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
+<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
+<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
+
 ## Prior knowledge and kind representations
@@
 Previous psychological and philosophical work on generics has looked beyond prevalence and focused on kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Indeed, we see generics as describing kinds, but argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge, formalized with by prevalence prior.
-In the right situations, this shared background knowledge can presuppose beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
-In other situations, relevant background knowledge may be merely correlational in nature.
+Indeed, we see a core communicative function of generics as teaching properties of kinds to naive listeners.
+But we argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge; to interface with a truth-functional semantics, such background knowledge is represented in some capactiy in the form of a prevalence prior.
+There is nothing in our theory that rules out shared background knowledge presupposing beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
+Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
 
@@
 <!-- Our model of an interpreter, or naive listener, has access to implicit  -->
-statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(h)$.
+statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(p_{fk})$.
 We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
+In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(h)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(h \mid C)$.
+Thus, the prevalence prior $P(p_{fk})$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(p_{fk} \mid C)$.
 
@@
 
-Uncertainty about the comparison class adds yet more opportunity for miscommunication, deceit, or just faultless disagreement to the language of generalization.
-Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may disagree about the prevalences for other categories in the comparison class.
+Uncertainty about the comparison class adds yet more opportunity to the language of generalization for disagreement, miscommunication, or deceit.
+Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may fail to coordinate on the prevalences for other categories in the comparison class.
 That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis committing acts of terrorism).
-In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of a generalization.
-Understanding how knowledge of the comparison class influences language use is an exciting new area for future research in the language of generalizations.
+Understanding the contextual influence on the construction of comparison classes should provide insight into failures of communication.
+\mht{ellen: TRUE,  I AGREE WITH YOU AND THIS IS PROBABLY OKAY.
+BUT IT THINK IT WOULD BE BETTER TO SAY SOMETHING SUBSTANTIVE;  FOCUSSING ON HOW KNOWLEDGE OF THE COMPARISION CLASS SHOULD PROVIDE INSIGHTS INTO FAILURES TO COMMUNICATE SUCCESSFULLY.}
 
@@
 
+## Relationship to other semantic theories
+
+To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
+A number of other theories of genericity have been proposed in the formal semantics  literature.
+<!-- We now turn to situating our account with respect to these previous theories. -->
+<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
+-->
+These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
+Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
+
+The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
+We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
+Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
+For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
+We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
+
+<!-- ### Conceptual accounts -->
+
+<!-- Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
+-->
+<!-- These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties. -->
+<!-- That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
+-->
+
+<!-- If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar". -->
+
+<!-- The most influential conceptual account of generics is from @Leslie2007. -->
+<!-- For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
+-->
+<!-- Leslie's "default mode" comes equipped with the ability to single-out *striking properties* (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
+-->
+<!-- Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about. -->
+
+<!-- This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
+-->
+<!-- Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
+1 for naturalistic cases).
+-->
+<!-- In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
+3a), we have observed that the prior distribution over the prevalence $P(h)$ change when supplied information about the dangerousness of the feature.
+-->
+<!-- That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors.  -->
+<!-- Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features. -->
+<!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
+-->
+
+<!-- Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs"). -->
+<!-- Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young) -->
+<!-- The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist.  -->
+<!-- For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
+-->
+<!-- In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
+-->
+<!-- Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
+-->
+
+<!-- Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world.  -->
+<!-- "Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters. -->
+<!-- "Barns are red" because most barns are red. -->
+<!-- If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green". -->
+<!-- Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.  -->
+
+<!-- Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations. -->
+<!-- In the last fifteen years, there has been tremendous progress in formalizing  -->
+<!-- Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011].
+-->
+<!-- For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations). -->
+<!-- @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.  -->
+
+<!-- In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
+-->
+<!-- In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).   -->
+<!-- It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here. -->
+
+<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence across different categories. -->
+<!-- This minimally structured model  -->
+
+<!-- @Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts. -->
+<!-- Striking generics (e.g.
+\emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
+-->
+<!-- Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}). -->
+<!-- The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations. -->
+<!-- Statistical information takes a backseat to the conceptual structure. -->
+
+<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
+-->
+
+<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
+
+<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
+
+<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
+<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
+<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
+<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
+<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
+<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
+<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
+<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
+-->
+<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
+
+<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
+-->
+<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
+-->
+<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
+<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
+-->
+<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
+<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
+-->
+
+<!-- ### Statistical accounts -->
+
+### Relative and absolute generics
+
+Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
+Cohen treats generics as comprising two qualitatively different types: *relative* and *absolute* generics.
+<!-- For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means. -->
+*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
+That is, if a particular instance is more likely than not to have the feature, then the absolute generic is true. 
+By contrast, *relative generics* are true based on a comparison to an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
+"Mosquitos carry malaria" is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
+
+In our model, we do not draw a *relative* vs. *absolute* distinction, instead treating all generics as relative. 
+Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge.^[
+  For a related theory argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
+]
+Further, though Cohen's theory is framed in terms of probabilities, it is a fully semantic, fixed-threshold account which only makes deterministic predictions about what is true and what is false.
+In contrast, we posit an uncertain threshold which is resolved through a Bayesian interpretation model; our theory is a joint semantic--pragmatic theory.
+
+<!-- In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement. -->
+<!-- Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each. -->
+<!-- We used examples of both in our stimuli (Expt.
+1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".
+-->
+
+We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
+His theory posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
+For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
+"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+The inferential machinery behind Cohen's domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
+]
+However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
+
+<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
+
+### Generic as indexical
+
+@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analogous to *indexicals* (e.g., "this" or "I").
+Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999, and many others].
+Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive "quantificational force". 
+We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
+<!-- Finally, how the context-sensitivity of an indexical differs from the kind of context-sensitivity with an uncertain-threshold is an important question for future research. -->
+
+### "Normal" accounts
+
+A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
+For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
+However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
+Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
+<!-- We showed in Expt.
+2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations.
+-->
+<!-- Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.  -->
+
+### Underquantification
+
+A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
+In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
+The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
+This distinction is relevant for the acquisition of the language of generalizations; we do not take as primary the quantified relations (e.g., "Some", "All").
+<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
+-->
+Additionally, by using an underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
+
 ## Other philosophical puzzles
@@
 In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model vis-a-vis alternative models.
-In this section, we discuss how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
+We close by discussing how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
 We consider the five following examples:
 
-1. Mary handles the mail from Antarctica.
+1. Mary handles the mail from Antarctica (*yet has never had the opportunity*).
 2. Supreme Court Justices have even social security numbers.
@@
 
-## Relationship to other semantic theories
-
-To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the formal semantics  literature.
-<!-- We now turn to situating our account with respect to these previous theories. -->
-<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
--->
-These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
-We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
-Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
-
-<!-- ### Conceptual accounts -->
-
-<!-- Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
--->
-<!-- These accounts start with the perspective that generics express rich, conceptual relationships between kinds and properties. -->
-<!-- That is, "Bishops move diagonally" not because of a statistical relationship, but rather, because those are the rules of the game; if you start moving the bishop other ways besides diagonally, you cease to be playing chess.
--->
-
-<!-- If a lion lacked the capacity to roar, we might consider a less good example of being a lion because "lions roar". -->
-
-<!-- The most influential conceptual account of generics is from @Leslie2007. -->
-<!-- For Leslie, generics are tied to the cognitive system's "default mode of generalization", which infants seem ready to make use of by drawing strong generalizations from small amounts of data [e.g., @Baldwin1993].
--->
-<!-- Leslie's "default mode" comes equipped with the ability to single-out *striking properties* (e.g., properties which are dangerous or appalling) as particularly useful aspects of the world to know about.
--->
-<!-- Hence, "Mosquitos carry malaria" is true because malaria can kill you and is useful to know about. -->
-
-<!-- This accounts predicts that generics that convey striking properties should be endorsed even when they are relatively rare in the category (i.e., low referent-prevalence; e.g., "Sharks attack swimmers").
--->
-<!-- Indeed, naturalistic examples (e.g., "Sharks attack swimmers") and artificial examples (e.g., "Lorches have purple feathers")  supplemented with striking information (e.g.,"These feathers are as sharp as needles and can easily get lodged in you, causing massive bleeding") are endorsed when the prevalence is quite low (e.g., 30\% of lorches have purple feathers; @Cimpian2010; see Expt.
-1 for naturalistic cases).
--->
-<!-- In pilot work, using a paradigm similar to the prior manipulation paradigm employed in the causal language experiments (Expt.
-3a), we have observed that the prior distribution over the prevalence $P(h)$ change when supplied information about the dangerousness of the feature.
--->
-<!-- That is, our pilot work suggests that experiments that experimentally induce beliefs about the dangerousness of a feature also manipulate the prevalence priors.  -->
-<!-- Thus, our model would also predict these effects, but by way of the prevalence priors rather than some direct connection between generics and striking features. -->
-<!-- However, we do not dispute that extra-linguistic factors can play a role in endorsements of generalizations (e.g., a speaker may not *want* a hearer to believe the generalization, which she herself knows to be true, or visa versa; more on this below).
--->
-
-<!-- Of course, not all generics convey striking or appalling information (e.g., "Birds lay eggs"). -->
-<!-- Leslie's default mode, thus, also distinguishes *negative counter-instances* of a property (e.g., a bird that doesn't lay eggs, such as a male bird) from *positive counter-instances*  (e.g., a hypothetical bird that bears live young) -->
-<!-- The conceptual account argues that generics are much less reasonable when *positive* counter-instances exist.  -->
-<!-- For example, "Birds are female" seems weird because *being male* is a *positive* counter-instance of *being female*, but since there are no birds that bear live young (i.e., no *positive counter-instances*),  "Birds lay eggs" is fine.
--->
-<!-- In the current version of our theory, both kinds of counter-instances influence the referent-category feature-probabilities, though only positive counter-instances could impact the statistical details of the comparison class (in particular, when constructed with respect to the feature; see discussion about the Comparison Class).
--->
-<!-- Thus, the notion of *positive* and *negative* counter-instances may result from a particular way of looking at the constructs posited in our model, namely prevalences within- and across- categories or features.
--->
-
-<!-- Finally, generics are not limited to conveying rich, conceptual information; they are also used to describe facts of the world.  -->
-<!-- "Ravens are bigger than toasters" is a true statement, but not because of a rich relationship between ravens and toasters. -->
-<!-- "Barns are red" because most barns are red. -->
-<!-- If farmers around the world decided to paint their barns green, the things they would be painting would still be barns; in that world, we might say "Barns are green". -->
-<!-- Thus, conceptual accounts must be supplemented with the proviso that in ceratin situations, the statistics of the world are relevant.  -->
-
-<!-- Our view is that subjective probabilities can be formed either from worldly observations or because of the structure of people's mental representations. -->
-<!-- In the last fifteen years, there has been tremendous progress in formalizing  -->
-<!-- Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011].
--->
-<!-- For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations). -->
-<!-- @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.  -->
-
-<!-- In this paper, we take a minimalist approach to modeling conceptual structure, incorporating only what is necessary into the interpreter's background knowledge, the prior on prevalence $P(h)$.
--->
-<!-- In our Bayesian data analysis of background knowledge, we use a mixture model that reflects basic knowledge about kinds and properties (e.g., that most kinds don't have most properites).   -->
-<!-- It's plausible that more richly structured knowledge of the kind described by @Prasada2013 and @Leslie2007 can be incorporating into the general probabilsitic framework that we use here. -->
-
-<!-- In Expt. 1a, we discovered that a mixture model is necessary to account for intuitions about the prevalence across different categories. -->
-<!-- This minimally structured model  -->
-
-<!-- @Prasada2006 and later @Prasada2013 distinguish between \emph{principled}, \emph{statistical}, and \emph{causal} relations within concepts. -->
-<!-- Striking generics (e.g.
-\emph{Mosquitos carry malaria}) show characteristics of \emph{causal connections} (operationalized using the phrase \emph{There is something about Ks that cause them to F}).
--->
-<!-- Generics like \emph{Birds lay eggs} (in which only a minority have the property) exhibit *principled* connections (operationalized by endorsement of the phrase \emph{In general, Ks have F}). -->
-<!-- The fact that generics about different properties license different kinds of inferences is taken as evidence that the generics themselves represent different kinds of relations. -->
-<!-- Statistical information takes a backseat to the conceptual structure. -->
-
-<!-- It is also the first attempt in psychology to try to unify significant swaths of language that are seemingly quite different from one another: generalizations about events, causes, and categories.
--->
-
-<!-- -- Leslie (2008): Default inferences, could be similar to the cognitive model described, but we don't make strong metaphysical commitments (e.g., to "negative" properties) -->
-
-<!-- -- "default generalization" -- very close, the listener is doing a generalization, but not generalization based on evidence, but by reasoning about the threshold -->
-
-<!-- Generic language is the simple and ubiquitous way by which generalizations are conveyed between people. -->
-<!-- Yet the dramatic flexibility of generic language has confounded psychologists, linguists and philosophers who have tried to articulate what exactly generic statements mean.  -->
-<!-- We evaluated a theory of generic language derived from general principles of language understanding using a simple, but uncertain, basic meaning---a threshold on property prevalence. -->
-<!-- Our formal model is a minimal extension of the RSA theory of language understanding, together with an underspecified threshold semantics. -->
-<!-- The model was able to explain two major puzzles of generics: their extreme flexibility in truth conditions and the contrastingly strong interpretation of many novel generics. -->
-<!-- Both of these phenomena were revealed to depend in systematic ways on prior knowledge about properties. -->
-<!-- This prior knowledge was revealed through Bayesian model analysis to be structured, providing a promising bridge to conceptual accounts of generic language. -->
-<!-- To understand the nature of the underlying prevalence scale, we showed that generic language is about speakers' expectations of future prevalence, and not necessarily what the current state of the world is like.
--->
-<!-- Across all experiments, the formal model predicted the quantitative details of participants' judgments with high accuracy. -->
-
-<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013].
--->
-<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.
--->
-<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
-<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance.
--->
-<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
-<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior.
--->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences.  -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-<!-- ### Statistical accounts -->
-
-### Relative and absolute generics
-
-Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
-Cohen treats generics as comprising two qualitatively different types: *relative* and *absolute* generics.
-<!-- For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means. -->
-*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
-That is, if a particular instance is more likely than not to have the feature, then the absolute generic is true. 
-By contrast, *relative generics* are true based on a comparison to an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
-"Mosquitos carry malaria" is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
-
-In our model, we do not draw a *relative* vs. *absolute* distinction, instead treating all generics as relative. 
-Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge.^[
-  For a related theory argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
-]
-Further, though Cohen's theory is framed in terms of probabilities, it is a fully semantic, fixed-threshold account which only makes deterministic predictions about what is true and what is false.
-In contrast, we posit an uncertain threshold which is resolved through a Bayesian interpretation model; our theory is a joint semantic--pragmatic theory.
-
-<!-- In our theory, there is uncertainty about the core semantic meaning, and this uncertainty (though reduced in context) drives the model to make graded predictions about endorsement. -->
-<!-- Second, Cohen draws an *a priori* distinction between *Absolute* and *Relative* generics, and provides different mechanisms for each each. -->
-<!-- We used examples of both in our stimuli (Expt.
-1) and found that our single model handles both without any addition assumptions, casting doubt on the *a priori* distinction between "absolute" and "relative".
--->
-
-We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
-For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
-"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery behind Cohen's domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
-  However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
-]
-However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
-Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
-
-<!-- Of course, the inferential machinery behind this sort of domain restriction (i.e., what is $Alt(F)$?) requires further theorizing to explain.  -->
-
-### Generic as indexical
-
-@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analogous to *indexicals* (e.g., "this" or "I").
-Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999, and many others].
-Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive "quantificational force". 
-We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
-<!-- Finally, how the context-sensitivity of an indexical differs from the kind of context-sensitivity with an uncertain-threshold is an important question for future research. -->
-
-### "Normal" accounts
-
-A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
-For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
-However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
-Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
-<!-- We showed in Expt.
-2c that a speaker's beliefs about what is likely to be the case in the near future matters above and beyond what is currently true in the world for endorsing generalizations.
--->
-<!-- Our notion of prevalence is as a predictive probability, which incorporates background knowledge in order to make predictions about the future.  -->
-
-### Underquantification
-
-A proposal similar to our account concerning underspecification of generics has been made in the computational linguistics literature [so-called *underquantification*; @Herbelot2011].
-In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
-Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
-This distinction is relevant for the acquisition of the language of generalizations; we do not take as primary the quantified relations (e.g., "Some", "All").
-<!-- Formally, whereas the *underquantification* account posits that a generic is *ambiguous* between various meanings, we argue that the generic is *vague*, and has a continuum of possible meanings.
--->
-Additionally, by using an underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
-
 # Conclusion

### 2018-03-01 paper/case1-generics.Rmd

@@
            #aes( x = prevalence, color = src, lty = src))+
-    geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
+    geom_density(aes(y = ..scaled..), adjust = 0.5, size = 1)+
     #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
@@
     #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1)+
+    stat_ecdf(size = 1.3)+
     scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
@@
     facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 4, 3))+
+    scale_linetype_manual(values = c(1, 2, 3))+
     scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+

### 2018-03-01 paper/case2-habituals.Rmd

@@
                filter(gender == 'male', measurement == "% people who have done action before"), 
-            aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = MAP),
+            aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = 1 - MAP),
               fill = "#268bd2", 
@@
             aes(xmin = -4.25, xmax = -3.75,
-                                            ymin = 0, ymax = MAP),
+                                            ymin = 0, ymax = 1 - MAP),
             fill = "#cb4b16",
@@
 In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
-Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (same as the \\emph{proportion of people who have done action before} scatter-plot), reflecting the (inverse) rarity of the event across people.", cache = F}
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have NEVER done action before} scatter-plot), reflecting the rarity of the event across people.", cache = F}
 cowplot::plot_grid(

### 2018-03-01 paper/comgen-paper.Rmd
address em comment about acquisition problem

--- 2018-03-01 paper/comgen-paper.Rmd
@@
 However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
+Thus, under our framework, generalizations should not only be learned before, but also faciliate in learning, quantifiers.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
-This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
+<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
+-->
 

### 2018-03-01 paper/comgen-paper.Rmd
remove penultimate paragraph about deceit

@@
 
-In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
-The precise implementation of these hypotheses we leave for future work.
+In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework might well explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
 
@@
 
-The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong impression to a naive listener.
-Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
-Disagreements are also predicted when interlocutors fail to share background assumptions, which could manifest as differences in the prior distributions on prevalence or what goes into the comparison class.
-Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).
-This is an important area for future research.
+<!-- The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong impression to a naive listener.
+-->
+<!-- Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
+-->
+<!-- Disagreements are also predicted when interlocutors fail to share background assumptions, which could manifest as differences in the prior distributions on prevalence or what goes into the comparison class.
+-->
+<!-- Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).
+-->
+<!-- This is an important area for future research. -->
 

### 2018-03-14 paper/comgen-paper.Rmd
rewrite intro

@@
 abstract: > 
-    Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly").
-    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
-    Yet the meaning of these expressions is logically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    The major issue in formalizing generalization in language is determining which statements are true or which are false.
-    Using an information-theoretic probabilistic model, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
-    To test this theory, we examine endorsements of generalizations about three different domains: categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
-    Across these diverse domains, we find that our model explains the wide variance in human endorsements of language conveying generalization, while simpler models fall short.
-    Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization.
-    The results demonstrate that the context-sensitivity of such language emerges from the interaction of an underspecified meaning with diverse beliefs about properties.
+    Knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
+    Yet such knowledge can be difficult to extract from the environment. 
+    Fortunately, we are not limited to acquiring generalizations on our own; language allows us to communicate generalizations to each other (e.g., “Birds fly”, “John hikes”, “Drinking milk makes your bones strong").
+    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
+    Here we argue that three ingredients are necessary to formalize generalizations: Probability, vagueness, and context. 
+    We formalize these ingredients in an information-theoretic probabilistic model that makes quantitative predictions about human understanding of generalizations.
+    Across diverse domains, we find that the model explains the gradience in human endorsement, while simpler models fall short. 
+    This is the first formal theory that makes accurate and precise predictions about human understanding of generalizations in language and is the first step towards building models that can learn abstract knowledge from language.
 
@@
 
+<!-- Generalizations are central to human understanding and language provides simple ways to convey them (e.g., "Birds fly"). -->
+<!-- The language of generalization is ubiquitous in everyday discourse and child-directed speech.  -->
+<!-- The major issue in formalizing generalization in language is determining which statements are true or which are false. -->
+<!-- Using an information-theoretic probabilistic model, we explore the hypothesis that the meaning of these linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context.
+-->
+<!-- To test this theory, we examine endorsements of generalizations about three different domains: categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind").
+-->
+<!-- Across these diverse domains, we find that our model explains the wide variance in human endorsements of language conveying generalization, while simpler models fall short. -->
+<!-- Ours is the first formal theory that makes precise, quantitative predictions about human understanding of the language of generalization. -->
+<!-- The results demonstrate that the context-sensitivity of such language emerges from the interaction of an underspecified meaning with diverse beliefs about properties.  -->
+
+<!-- Knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world.
+Yet such knowledge can be difficult to extract from the environment.
+Fortunately, we are not limited to acquiring generalizations on our own; language allows us to communicate generalizations to each other (e.g., “Asparagus berries are poisonous”, “John hikes”, “Drinking milk makes your bones strong").
+In this talk, I’ll argue that three ingredients are necessary to understand generalizations: Probability, vagueness, and context.
+I formalize these ingredients in an information-theoretic probabilistic model that makes quantitative predictions about human understanding of generalizations.
+Across diverse domains, I find that the model explains the gradience in multiple dependent measures, while simpler models fall short.
+This is the first formal theory that makes accurate and precise predictions about human understanding of generalizations in language and is the first step towards building models that can learn abstract knowledge from language.
+-->
+
 # Introduction
@@
 By sharing generalizable knowledge, we flourish collectively without individually needing to taste potentially-poisonous plants or personally witness lightning strikes.
-Furthermore, flexibly communicating generalizations from one generation to the next is a mechanism by which culture can cumulatively evolve [@Tomasello1999; @Henrich2015].
+Being able to flexibly communicate generalizations from one generation to the next supports the faithful transmission of knowledge necessary for culture to cumulatively evolve [@Tomasello1999; @Henrich2015].
 
@@
 <!-- Language provides multiple, distinct ways of encoding generalizations. -->
-The *language of generalization* is most commonly studied with *generic language* (*generics*) or generalizations about categories [e.g., "Dogs are friendly"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008].
+The *language of generalization* covers a diverse swath of natural language expressions.^[
+  Some writers refer to the all of the *language of generalization* as "generic language".
+  In the literature, however, analysis and experiments are often limited to generalizations about categories. 
+  We use the more narrow-scoped terms (e.g., generics, habituals, and causals) to highlight the diversity of semantic types being predicated.
+]
+Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case in the language of generalization.
+In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
+Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs").
+Even events of complex inferential types such as actual causal events (e.g., "My grandpa drank moonshine and it made him blind") can be described in generalization (e.g., "Drinking moonshine makes you go blind").^[
+  Conceretely, we are generalizing over the causal relationship being realized in a particular instance, in this casea person.
+]
+
+The language of generalization is ubiquitous in everyday conversation and conveys rich meanings [@Orvell2017].
+It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context has implicated it as central to the growth of conceptual knowledge [@Gelman2004].
+It is believed every language can express generalization [@Behrens2005; @Carlson1995], and so understanding the language of generalization is a project with a far-reaching implications.
+
+<!-- Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
+-->
+
 <!-- Generics are ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].  -->
-In contrast to statements about concrete individuals or events (e.g., "Rufus is friendly"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the here and now, a fact which children as young as 2 appreciate [@Cimpian2008].
 <!-- Additionally, generics are the primary way by which speakers discuss social categories, and thus are key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
 -->
-Generics are just one case in the language of generalization, however; events can be described in generalization (*habitual language*; e.g., "Mary swims after work.") as well as causal relationships (*causal language*; e.g., "Staring at the sun makes you go blind.").
-It is believed every language can express generalization [@Behrens2005; @Carlson1995] and that such language is central to the growth of conceptual knowledge [@Gelman2004].
 <!-- Thus, an understanding of the language of generalization that extends to a wide variety of types (e.g., categories, events, causes)  -->
@@
 
-Despite its ubiquity and relative morphosyntactic simplicity, the language of generalization has been addressed by few formal models and none that have made precise, quantitative predictions that match human judgements.
-The major challenge in formalizing generalization in language is determining what makes the statements seem true or false.
-When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark".
-But the property does not apply to all dogs: Basenji dogs are barkless,
-<!-- ^[ -->
-<!-- http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html -->
-<!-- ],  -->
-for example.
-The generalization could signal something weaker like "Most dogs bark".
-However, *most* mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true.
+Despite its ability to convey abstract knowledge, its ubiquity in discourse, and its relative morphosyntactic simplicity, the language of generalization displays subtle context-sensitivities that make it difficult to formalize.
+"Robins lay eggs" sounds true and "Robins are female" does not. 
+Yet in each case, only 50% of the category have the property (i.e., only the females lay eggs). 
+"Mosquitos carry malaria" sounds true despite malaria being present in only a tiny fraction of mosquitos. 
+Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a bad sentence even if it were the case that on the current bench, nine out of nine justices have even social securtity numbers (i.e., when the sentence "All Supreme Court Justices have even social security numberes" is true).
+Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains 3 times last year, the habitual "Mary climbs mountain" seems well-supported. 
+Yet, if John went for a run 3 times in the last year, we probably shouldn't say that "John runs".
+
+<!-- When we hear "Dogs bark", it sounds like a universal statement, as in "All dogs bark". -->
+<!-- But the property does not apply to all dogs: Basenji dogs are barkless, for example. -->
+
+<!-- The generic could signal something weaker like "Most dogs bark". -->
+
+<!-- However, *most* mosquitos do not carry malaria (in fact, only a tiny fraction do), but "Mosquitos carry malaria" is intuitively true. -->
 <!-- *most mosquitos* do not carry malaria, while the statement "Mosquitos carry malaria" is intuitively true. -->
-The only *quantifier* that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria").
-But weakening the generalization to mean *some* is too permissive: Some robins are female (in fact, half of them are), but endorsing "Robins are female" seems odd.
-Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say.
-
-These observations have led some to conclude that the prevalence of the feature (or the probability of a member of the category having the property e.g.,  $P(x \text{ barks} \mid x \text{ is a dog})$) is not what makes generalization true or false.
-Generic statements are instead thought to refer to *kinds* [@Leslie2008] and thus may be the linguistic manifestation of special, kind--property relations [@Prasada2000; @Prasada2012]. 
+<!-- The only *quantifier* that would permit such a statement would be *some* (e.g., "Some mosquitos carry malaria"). -->
+<!-- But weakening the generalization to mean *some* is too permissive: Some robins are female (in fact, half of them are), but endorsing "Robins are female" seems odd. -->
+<!-- Even more perplexing: Those very same female robins lay eggs, and "Robins lay eggs" is a perfectly fine thing to say. -->
+
+These observations have led some to conclude that the literal meaning of a generic statement involves more than just the number of members of the category who have the property, referred to as the *prevalence* of the feature in the category.
+<!-- (or the probability of a member of the category having the property e.g.,  $P(x \text{ is friendly} \mid x \text{ is a dog})$) is not sufficient to make generalizations ("Dogs are friendly") true or false.
+-->
+Instead, generic statements are thought of semantically as a direct, linguistic manifestation of conceptual relations [@Leslie2008; @Prasada2000; @Prasada2012]. 
 <!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
 -->
-"Bishops move diagonally" or "The Speaker of the House succeeds the Vice President" are true statements not because of a tendency on behalf of the category to uphold the property.
-Rather, the utterances are believed to point out the existence of a conceptual structure (e.g., that bishops have a certain role in the game of chess).
-The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013].
+<!-- Indeed, generics can be true for a range of prevalence or frequency levels [@Khelmani2012; @Prasada2013]. -->
+For example, the statements "Bishops move diagonally" or "The Speaker of the House succeeds the Vice President" are true not because of a tendency on behalf of the category to uphold the property, but rather the existence of a conceptual relationship (e.g.,  what it means, in the game of chess, to be a bishop).
+True generics can be supported by different underlying types of category--property relations [e.g., principled vs.
+statistical connections; @Prasada2007], and thus support qualitatively different inferences [e.g., "Being striped is one aspect of being a tiger" is well supported while "Carrying malaria is one aspect of being a mosquito" is not not, still while "Tigers are striped" and "Mosquitos carry malaria" sound true; @Prasada2013].
+This theory has been influential in psychology, because it predicts several qualitative effects. 
+Still, the theory is not sufficiently precise to many any quanitative predictions.
+
+Insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
+In this paper, we propose such a semantic core.
+To do so, we draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] and truth-functional semantics [@Montague1973; @Cohen1999] to formalize the context-dependent aspects of language interpretation [@Frank2012] with the core semantic hypothesis: The meaning of an utterance conveying generalization is vague description of subjective, predictive probabilities.
+By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested.
+It is also the first theory to make quantitative predictions about human understanding of generalization in language.
+<!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
+<!-- Our model is the first to make quantitative predictions about human endorsements of generalizations in language. -->
+
+The paper is organized as follows. 
+In Section 1, we describe the computational model, which formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge can be described formally.
+Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgements about the truth or acceptibility of a sentence.
+The model as articulated predicts fine-grained, quantitative effects of background knowledge, which we both measure and manipulate across our three empirical case studies (Sections 2-4): generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*).
+We compare our model to two previously articulated quantitative models of generics as well as a lesioned-version of our model.
+In all cases, we find a very strong agreement of our model's predictions to human elicited endorsements, where the simpler models fall short.
+We conclude our paper with a discussion of open-questions for this approach, relation to linguistic and philosophical approaches to generics, and a few sketches of worked examples of other phenomenology in generics.
+
+<!-- This work opens the door to understanding generalizations in richer, pragmatic language contexts and building models that learn abstract knowledge from language. -->
+
+<!-- relevant background knowledge used to understand a generalization in context, and use these components to develop a computational model of endorsement. -->
+<!-- The endorsement model's predictions depend upon relevant background knowledge and the prevalence communicated, which we demonstrate via simulation. -->
+<!-- Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement of generalization sentences.  -->
+
+<!-- To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001]. -->
+<!-- Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication for the language of generalization. -->
+<!-- \ndg{cuttoff / threshold not mentioned before this, need to introduce...} -->
+<!-- However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female". -->
+<!-- Rather than throw-out the quantitative formalization of the threshold semantics, we posit that the threhsold is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment.
+-->
+
+<!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
+-->
+
 <!-- It's been suggested that the mind has cognitive primitives that directly dictate what generalizations are true or false. -->
@@
 
-Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015].
-Ravens and toasters have no privileged relationship to each other, but "Ravens are bigger than toasters" is still true.
-An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual statistics of the feature matters for making generalizations true.
-
-<!-- Furthermore, how conceptual accounts of the language of generalizations should extend beyond category generalizations (i.e., generics) is less clear.  -->
-<!-- "Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. -->
-
-What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
-But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
-In this paper, we propose such a semantic core for the language of generalization.
-To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
-Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication for the language of generalization.
-\ndg{cuttoff / threshold not mentioned before this, need to introduce...}
-However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
-Rather than throw-out the quantitative formalization of the threshold semantics, we posit that the threhsold is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment.
-<!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations.
--->
-With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false.
-The assumptions of the theory and the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
-Our model is the first to make quantitative predictions about human endorsements of generalizations in language.
-
 <!-- Specifically, we formalize an account where the core meaning of a generalization in language is a *simple but underspecfied* function of probability and where context helps resolve the underspecification.
@@
 
-The paper is organized as follows. 
-In Section 1, we formalize the hypothesis that the core meaning of a generalization in language is a simple but underspecified threshold on a subjective probability, articulate a theory of relevant background knowledge used to understand a generalization in context, and use these components to develop a computational model of endorsement.
-The endorsement model's predictions depend upon relevant background knowledge and the prevalence communicated, which we demonstrate via simulation.
-Sections 2-4 present three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
-Across these three case studies, we both measure and manipulate background knowledge and the prevalence communicated, measuring their effects on endorsement of generalization sentences. 
-We find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements, while alternative models fall short.
-This work opens the door to understanding generalizations in richer, pragmatic language contexts and building models that learn abstract knowledge from language.
-
 <!-- (cumulative $r^2(N) = 0.XX$). -->
@@
 
-Generalizations are used to make predictions about properties of instances or events that an agent has yet to experience [@HumeTHN].
-People readily predict that the next dog will have fur, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
+Generalizations are used to make predictions about events or properties of instances events that an agent has yet to experience [@HumeTHN].
+People readily predict that the next dog will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
 This prediction can be described by a conditional probability: $p(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence*.
-In particular, we define *prevalence* as a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+We identify *prevalence* as the latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
@@
 Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood as simple but underspecified. 
-To our knowledge, ours is the first formal theory of generalizations in language that makes precise quantitative predictions about human behavioral data.
+We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalizing by probability.
+Being able to precisely articulate the conditions under which a sentence is true lets you describe how an agent should update its beliefs based on that sentence. 
+Thus, in addition to providing a quantitative understanding of the phenomena, formalizing the language of generalizations opens up the possibility of building models that learn abstract, generalizable knowledge from language.
 
@@
 ## Relationship to other semantic theories
+
+<!-- The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013]. -->
+
+<!-- Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015]. -->
+<!-- <!-- "Cars have tape decks" is a generalization that was true about thirty years ago, but  --> -->
+<!-- <!-- Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. --> -->
+<!-- Ravens and toasters have no privileged relationship to each other and to assess if "Ravens are bigger than toasters", we should actually measure the distribution of sizes for ravens and toasters.
+-->
+<!-- An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual statistics of the feature matter for making generalizations true.
+-->
+
+<!-- <!-- Furthermore, how conceptual accounts of the language of generalizations should extend beyond category generalizations (i.e., generics) is less clear.  --> -->
+<!-- The alternative approach to generics is to try to rescue the notion the number of members of the category with the property (e.g., the number of robins that do indeed lay eggs). -->
 

### 2018-03-15 paper/comgen-paper.Rmd
light edits to model; replace p_fk with p

@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
-This prediction can be described by a conditional probability: $p(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence*.
-We identify *prevalence* as the latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$).
+which we will refer to as the *prevalence* and provide the notational simplification $p = p(f \mid k)$.
+Our *prevalence* $p$ is a *prevalence in the mind*, the latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
@@
 
+<!-- a useful representation  -->
 <!-- How do we come to know things?  -->
-How does one acquire inductive beliefs?
-If you *observe* wugs that have two legs, you might infer that all wugs have two legs.
+<!-- How does one acquire inductive beliefs? -->
+Probability is a useful representation for human generalization from observations [@Shepard1987].
+If you *observe* wugs (a novel category) that have two legs, you might infer that all wugs have two legs.
 But not all properties have such strong projectibility (prevalence).
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
-Abstract, potentially domain-specific, beliefs about properties can be represented by a probability distribution over the prevalence $P(p_{fk})$ [@Kemp2008].^[
-  We adopt the following notational simplification: $p_{fk} = p(f \mid k)$. 
+Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].^[
+  We adopt the following notational simplification. 
 ]
-Learning, then, can proceed via Bayes' Rule: $P(p_{fk} \mid d) \propto P(d \mid p_{fk}) \cdot P(p_{fk})$ given one's observational data $d$ and the observer's beliefs about the generative process that resulted in the observed data---the likelihood $P(d \mid p_{fk})$.
+Bayes Rule provides the mathematically correct way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---the likelihood $P(d \mid p)$ [@Tenenbaum2001].
+
+<!-- To do so, we look to probability, the universal currency of belief and  -->
+<!-- Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication for the language of generalization. -->
 
 <!-- But we do not always have access to  -->
-Observational data $d$ is not always available, however.
-Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*), events that are statistically unlikely (e.g., *lightning strikes tall objects*), or just aspects of the world that we have yet to experience.
+Observational data is not always available, however.
+Instead, we must listen to others to learn about properties that are costly to observe (e.g., *staring at the sun makes you go blind*), events that are statistically unlikely (e.g., *lightning strikes tall objects*), or any aspect of the world that we have yet to experience.
 Fortunately, language provides simple ways of communicating generalizations.
@@
 
-## The language of generalization
-
-The language of generalization is easy to spot when a property, that could project onto an individual, is predicated of a category (e.g., "Dogs are friendly"; *barks* could apply to an individual as in "This dog is friendly").
-This is often called *generic language* or *generics* [@Carlson1977].
-Generic statements can be contrasted with kind-denoting statements which use properties that can only apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* is not a property that could apply to an individual).
-Generalization can also manifest when describing an individual (*habitual language*; e.g., "John smokes").
-Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of a causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). ^[
-  We adopt this somewhat idiosyncratic categorization in order to emphasize the different semantic types predicated. 
-  Some authors refer to all of these types as *generics*.
-  Still, however, the primary "generics" investigated in the literature have been generalizations about categories ("Ks F").
-]
+## Communicating generalizations
+
+The language of generalization is easy to spot when a property, that could project onto an individual, is predicated of a category (e.g., "Dogs have four legs"; *has four legs* could apply to an individual as in "This dog has four legs").
+In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual).
+<!-- Dinosaurs are exctinct ~ John is a smoker? -->
+Generalization can also manifest when describing an instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2008].
+Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
 Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
-  We take up the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
+  We further distinguish the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
   Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
@@
 
-If generalization from observations can be described by a probability $p_{fk}$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
+If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
 The semantic tools of *truth values* provide a way to update a state of knowledge by relating the semantic quantity (probability) to  Boolean values [@Montague1973].
 The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-Thus, the simplest semantics for a generalization about category $k$ with property $f$ is a threshold on the *prevalence*: $\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}$.
+Thus, the simplest semantics for a generalization about category $k$ with property $f$ is a threshold on the *prevalence*: $\denote{generalization}(p, \theta) = \{p >\theta\}$.
 
@@
 
-<!-- We distinguish our proposal from previous ones by emphasizing the predictive nature of $p_{fk}$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
--->
-<!-- $p_{fk}$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->
+<!-- We distinguish our proposal from previous ones by emphasizing the predictive nature of $p$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
+-->
+<!-- $p$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->
 
@@
 
-The simplest semantics for a generalization is a threshold function: $\denote{gen}(p_{fk}, \theta) = \{p_{fk} >\theta\}$, but what threshold is appropriate?
-Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p_{fk}) = \{p_{fk} > 0\}$; $\denote{all} = \{p_{fk} = 1\}$.
+The simplest semantics for a generalization is a threshold function: $\denote{gen}(p, \theta) = \{p >\theta\}$, but what threshold is appropriate?
+Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p) = \{p > 0\}$; $\denote{all} = \{p = 1\}$.
 The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
@@
 We formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
-The model also has prior knowledge about the property $P(p_fk)$ and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
+The model also has prior knowledge about the property $P(p)$ and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
 
 \begin{eqnarray}
-Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{fk}, \theta)} \cdot P(p_{fk}) \cdot P(\theta)} \label{eq:L0}
+Lit(p, \theta \mid u) &\propto& {\delta_{\denote{u}(p, \theta)} \cdot P(p) \cdot P(\theta)} \label{eq:L0}
 \end{eqnarray}
 
-Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p_{fk}, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p_{fk} > \theta$) and $0$ otherwise.
+Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
 
 \begin{eqnarray}
-\delta_{\denote{u_{KF}}(p_{fk}, \theta)} &\propto  & \begin{cases}
-1 & \text{if } p_{fk} > \theta \\
+\delta_{\denote{u_{gen}}(p, \theta)} &\propto  & \begin{cases}
+1 & \text{if } p > \theta \\
 0 & \text{otherwise}
@@
 
-Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p_{fk})$.
+Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p)$.
 
@@
 
-Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
+Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is intuitively true or not?
 We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
-We formalize this by considering how well the generalization would convey the prevalence $p_{fk}$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
-  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p_{fk}$ that it wants to communicate.
-  Rather, the endorser may have a distribution over $p_{f}$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
+We formalize this by considering how well the generalization would convey the prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
+  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
+  Rather, the endorser may have a distribution over $p$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
   In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
-  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}$
+  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} Lit(p, \theta \mid u)} \diff \theta )}$
   For the empirical case studies described below, these two versions of the model make almost identical predictions.
@@
 \begin{equation} 
-S(u \mid p_{fk}) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)  \diff \theta } )}
+S(u \mid p) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p, \theta \mid u)  \diff \theta } )}
 \label{eq:S1}
@@
 
-The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p_{fk}, \theta \mid u)$.
+The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p, \theta \mid u)$.
 $S$ does not know $\theta$ and integrates over the interpreter's posterior beliefs about $\theta$.
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a mapping from a *referent-category prevalence* $p_{fk}$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{KF} \mid p_{fk})$.
+\ref{eq:S1}) provides a mapping from a *referent-category prevalence* $p$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{gen} \mid p)$.
 The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
@@
 The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p_{fk})$---with the underspecified semantics.
+\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p)$---with the underspecified semantics.
 Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence. 
-However, the interpretation model's prior beliefs $P(p_{fk})$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
+However, the interpretation model's prior beliefs $P(p)$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
 
 <!-- Our model makes context-sensitive predictions about endorsing generalizations based on two model components: The prevalence priors $P(p_fk)$ in Eq.
-\ref{eq:L0} and the referent-prevalence $p_{fk}$ in Eqs.
+\ref{eq:L0} and the referent-prevalence $p$ in Eqs.
 \ref{eq:S1} and \ref{eq:delta}.
@@
 Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
-In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p_{fk})]$.
+In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p' \cdot P(p')$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
 For a more detailed derivation of this relationship, see Appendix A.
@@
 -->
-<!-- In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p_{fk}$).
--->
-<!-- Thus, $P(p_{fk}) = P(k_{f})$. -->
+<!-- In the prevalence prior $P(p_f)$, a category is represented only by its corresponding prevalence (i.e., a sample from the prevalence prior can be thought of as a category $k$, with the only information available about the category being the prevalence of the feature in that category $p$).
+-->
+<!-- Thus, $P(p) = P(k_{f})$. -->
 
@@
 
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $p_{fk}$ in Eq.
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $p$ in Eq.
 \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(p_f)$ (Eq.
@@
 <!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
-<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p_{fk} \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
+<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
 -->
@@
 
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the referent-prevalence $p_{fk}$ communicated. 
+These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the referent-prevalence $p$ communicated. 
 We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
@@
 <!-- Our model of an interpreter, or naive listener, has access to implicit  -->
-statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(p_{fk})$.
+statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
 We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
@@
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(p_{fk})$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(p_{fk} \mid C)$.
+Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(p \mid C)$.
 

### 2018-03-15 paper/comgen-paper.Rmd
finish light edits to intro; tweak discussion on conceptual knowledge

@@
 <!-- Language provides multiple, distinct ways of encoding generalizations. -->
-The *language of generalization* covers a diverse swath of natural language expressions.^[
+The *language of generalization* covers a diverse swath of natural language expressions.
+Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case in the language of generalization.^[
   Some writers refer to the all of the *language of generalization* as "generic language".
@@
 ]
-Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case in the language of generalization.
 In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs").
-Even events of complex inferential types such as actual causal events (e.g., "My grandpa drank moonshine and it made him blind") can be described in generalization (e.g., "Drinking moonshine makes you go blind").^[
-  Conceretely, we are generalizing over the causal relationship being realized in a particular instance, in this casea person.
-]
-
-The language of generalization is ubiquitous in everyday conversation and conveys rich meanings [@Orvell2017].
-It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context has implicated it as central to the growth of conceptual knowledge [@Gelman2004].
-It is believed every language can express generalization [@Behrens2005; @Carlson1995], and so understanding the language of generalization is a project with a far-reaching implications.
+Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "My grandpa drank moonshine and it made him blind") can be described in generalization (e.g., "Drinking moonshine makes you go blind").
+
+Understanding the language of generalization is a project with far-reaching implications.
+The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], making meaning from experience [@Orvell2017].
+It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context suggests its centrality to the growth of conceptual knowledge [@Gelman2004].
+Finally, it is believed every language can express generalization [@Behrens2005; @Carlson1995].
 
@@
 "Mosquitos carry malaria" sounds true despite malaria being present in only a tiny fraction of mosquitos. 
-Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a bad sentence even if it were the case that on the current bench, nine out of nine justices have even social securtity numbers (i.e., when the sentence "All Supreme Court Justices have even social security numberes" is true).
+Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a bad sentence even if it were the case that on the current bench, nine out of nine justices have even social securtity numbers [i.e., when the sentence "All Supreme Court Justices have even social security numbers" is true; @Cohen1999].
 Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains 3 times last year, the habitual "Mary climbs mountain" seems well-supported. 
@@
 
-These observations have led some to conclude that the literal meaning of a generic statement involves more than just the number of members of the category who have the property, referred to as the *prevalence* of the feature in the category.
+These observations have led some to conclude that the literal meaning of a generic statement involves more than just the number of members of the category who have the property, otherwise known as the *prevalence* of the feature in the category.
 <!-- (or the probability of a member of the category having the property e.g.,  $P(x \text{ is friendly} \mid x \text{ is a dog})$) is not sufficient to make generalizations ("Dogs are friendly") true or false.
@@
 True generics can be supported by different underlying types of category--property relations [e.g., principled vs.
-statistical connections; @Prasada2007], and thus support qualitatively different inferences [e.g., "Being striped is one aspect of being a tiger" is well supported while "Carrying malaria is one aspect of being a mosquito" is not not, still while "Tigers are striped" and "Mosquitos carry malaria" sound true; @Prasada2013].
-This theory has been influential in psychology, because it predicts several qualitative effects. 
-Still, the theory is not sufficiently precise to many any quanitative predictions.
+statistical connections; @Prasada2006], and thus support qualitatively different inferences [e.g., "Being striped is one aspect of being a tiger" is endorsed while "Carrying malaria is one aspect of being a mosquito" is not, even while "Tigers are striped" and "Mosquitos carry malaria" sound true; @Prasada2013].
+This conceptual view of generics has been influential in psychology, because it predicts qualitative differences between different kinds of generics. 
+<!-- Still, the theory is not sufficiently precise to make any quantitative predictions. -->
 
@@
 In this paper, we propose such a semantic core.
-To do so, we draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] and truth-functional semantics [@Montague1973; @Cohen1999] to formalize the context-dependent aspects of language interpretation [@Frank2012] with the core semantic hypothesis: The meaning of an utterance conveying generalization is vague description of subjective, predictive probabilities.
+To do so, we draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] and truth-functional semantics [@Montague1973; @Cohen1999] to formalize the context-dependent aspects of language interpretation [@Frank2012] jointly with the core semantic hypothesis: The meaning of an utterance conveying generalization is a vague description of subjective, predictive probabilities.
 By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested.
@@
 The paper is organized as follows. 
-In Section 1, we describe the computational model, which formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge can be described formally.
-Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgements about the truth or acceptibility of a sentence.
+In Section 1, we describe the computational model, which formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge is formally described.
+Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgments about the truth or acceptibility of a sentence.
 The model as articulated predicts fine-grained, quantitative effects of background knowledge, which we both measure and manipulate across our three empirical case studies (Sections 2-4): generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*).
@@
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
-Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$).
-which we will refer to as the *prevalence* and provide the notational simplification $p = p(f \mid k)$.
-Our *prevalence* $p$ is a *prevalence in the mind*, the latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and provide the notational simplification $p = P(f \mid k)$.
+Our *prevalence* $p$ is a *prevalence in the mind*, a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
 The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
 The properties also vary (e.g., having fur, causing jitters, going to the gym).
-Yet the mathematical description of the inductive belief is always given by a probability $p(f \mid k)$.
+Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.
 
@@
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
-Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].^[
-  We adopt the following notational simplification. 
-]
+Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].
 Bayes Rule provides the mathematically correct way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---the likelihood $P(d \mid p)$ [@Tenenbaum2001].
@@
 The language of generalization is easy to spot when a property, that could project onto an individual, is predicated of a category (e.g., "Dogs have four legs"; *has four legs* could apply to an individual as in "This dog has four legs").
-In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual).
+In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
 <!-- Dinosaurs are exctinct ~ John is a smoker? -->
-Generalization can also manifest when describing an instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2008].
+Generalization can also manifest when describing an instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2005].
 Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
@@
 The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-Thus, the simplest semantics for a generalization about category $k$ with property $f$ is a threshold on the *prevalence*: $\denote{generalization}(p, \theta) = \{p >\theta\}$.
-
-Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has made precise, quantitative predictions about adult judgments.
-In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantics in order to update its beliefs from language.
-We then ask: When would a rational speaker choose to produce a generalization (vs. staying silent) to update the Bayesian model's state of knowledge?
+Thus, the simplest semantics for a generalization is a threshold on the prevalence: $\denote{generalization}(p, \theta) = \{p >\theta\}$.
+
+This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
+We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding this semantic hypothesis in a cognitive model in which relevant contextual knowledge can be formalized.
+By doing so, we thus provide an account of how context influences generic understanding and are able to make precise, quantitative predictions about human judgments.
+
+<!-- Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has made precise, quantitative predictions about adult judgments.
+-->
+<!-- In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantics in order to update its beliefs from language. -->
+<!-- We then ask: When would a rational speaker choose to produce a generalization (vs. staying silent) to update the Bayesian model's state of knowledge? -->
 
@@
 The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
-Rather than throw out the threshold-semantics, we posit this semantics is *underspecified*.
-We hypothesize that $\theta$ is determined by context in a way analogous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
 
@@
 
-We formalize this underspecified semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
-The model also has prior knowledge about the property $P(p)$ and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $u$:
+We formalize this underspecified (or, *vague*) semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013;   @Lassiter2015; cf., @Qing2014].^[
+  Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p)$.
+]
+The model also has prior knowledge about the property $P(p)$ (described in more detail below) and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $\delta_{\denote{u}(p, \theta)}$:
 
@@
 \end{eqnarray}
-
-Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p)$.
 
@@
 "disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [@Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$.^[
-  This "null" alternative to the generalization ("Ks F") can be realized in at least two other ways: the negation of the generalization (i.e., "It is not the case that Ks F") or the negative generalization (i.e., "Ks do not F").
+  This "null" alternative to the generalization can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
+  The latter is different because it creates a new threshold (analogous to how "short" and "tall" are modeled with different thresholds).
   All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity.
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a mapping from a *referent-category prevalence* $p$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{gen} \mid p)$.
+\ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{gen} \mid p)$.
 The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
@@
 
-Beliefs about properties result from internal conceptual models of the world. 
-Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among *different* categories.
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* $P(p_{barks})$ should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
+Beliefs about properties result from internal, conceptual models of the world. 
+We do not take up the task of formalizing particular conceptual models, but rather merely try to measure their implications on beliefs about prevalence. 
+Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among alternative categories.
+For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
 Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have some probability mass at relatively high prevalences, potentially with some uncertainty (Figure\ \@ref(fig:simulations); column 1).
@@
 
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $p$ in Eq.
-\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(p_f)$ (Eq.
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
+\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq.
 \ref{eq:L0}).
@@
 The endorsement model (Eq.
-\ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent-category prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
+\ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
 Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations).
@@
 
-These simulations show how the model predicted endorsement depends upon the background knowledge about the property $P(p_f)$ as well as the referent-prevalence $p$ communicated. 
+These simulations show how the model predicted endorsement depends upon the background knowledge of the interpreter about the property $P(p)$ as well as the referent-prevalence of the endorser $p$ communicated.
 We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
@@
 As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types: "Robins lay eggs" (categories), "Sally smokes" (events), "Herb X makes animals sleepy" (causes).
-Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we take to mean *predictive probability* (as opposed to frequency).
-We test this theory by exploring its implications for *endorsement*, operationalized as a speaker's decision about whether or not to produce the generalization to naive listener. 
+Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
+We test this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether or not to produce the generalization to naive listener. 
 Endorsement, we show, depends in systematic ways on the listener's prior beliefs about the prevalence.
@@
 1), naturally extends to other domains of generalizations (habituals and causals; Expts.
-2 \& 3), and provides an avenue for top-down moderators on language use by way of *predictive* probability (Expt.
+2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt.
 2c).
@@
 
-## Prior knowledge and kind representations
+## Prevalence priors and conceptual knowledge
 
@@
 
-Our theory assumes that listeners and speakers share relevant background knowledge (in the form of a *prevalence prior*) against which generalizations are interpreted.
-Given this representation of background knowledge (*prevalence prior*), language interfaces with conceptual knowledge via *prevalence*. 
-Previous psychological and philosophical work on generics has looked beyond prevalence and focused on kinds and their conceptual relations to properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Indeed, we see a core communicative function of generics as teaching properties of kinds to naive listeners.
-But we argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge; to interface with a truth-functional semantics, such background knowledge is represented in some capactiy in the form of a prevalence prior.
+Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
+Rather than have beliefs about prevalence *per se*, listeners are likely to have conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013] that gives rise to beliefs about prevalence.
+That is, the prevalence prior is a statistical layer that provides the glue between conceptual knowledge and natural language semantics.
+The truth conditions of generalizations depend only on prevalence.
+
+<!-- Given this minimal representation of background knowledge, language interfaces with conceptual knowledge via prevalence.  -->
+
+<!-- Previous psychological and philosophical work on generics has looked beyond prevalence and focused on kinds and their conceptual relations to properties  -->
+<!-- Indeed, we see a core communicative function of generics as teaching properties of kinds to naive listeners. -->
+<!-- But we argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge; to interface with a truth-functional semantics, such background knowledge must have a representation in the form of a prevalence prior.
+-->
+
 There is nothing in our theory that rules out shared background knowledge presupposing beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
 Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
-
 Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
 We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
-We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative theory.
+We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
 The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
-Thus, our theory provides a separation between background knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*. 
+Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*. 
 Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.

### 2018-03-18 paper/comgen-paper.Rmd
edits in model section

@@
 
-Generalizations are used to make predictions about events or properties of instances events that an agent has yet to experience [@HumeTHN].
+Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
 People readily predict that the next dog will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
-Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(f \mid k) = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and provide the notational simplification $p = P(f \mid k)$.
+Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
 Our *prevalence* $p$ is a *prevalence in the mind*, a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
@@
 Probability is a useful representation for human generalization from observations [@Shepard1987].
-If you *observe* wugs (a novel category) that have two legs, you might infer that all wugs have two legs.
-But not all properties have such strong projectibility (prevalence).
+If you *observe* several wugs (a novel category) that have two legs, you might infer that all wugs have two legs.
+But not all properties have such strong projectibility.
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
 Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].
-Bayes Rule provides the mathematically correct way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---the likelihood $P(d \mid p)$ [@Tenenbaum2001].
+Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].
 
@@
 
-The language of generalization is easy to spot when a property, that could project onto an individual, is predicated of a category (e.g., "Dogs have four legs"; *has four legs* could apply to an individual as in "This dog has four legs").
+The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs"; *has four legs* could apply to an individual as in "This dog has four legs").
 In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
 <!-- Dinosaurs are exctinct ~ John is a smoker? -->
-Generalization can also manifest when describing an instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2005].
+Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2005].
 Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
@@
 If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
-The semantic tools of *truth values* provide a way to update a state of knowledge by relating the semantic quantity (probability) to Boolean values [@Montague1973].
-The simplest way to relate a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-Thus, the simplest semantics for a generalization is a threshold on the prevalence: $\denote{generalization}(p, \theta) = \{p >\theta\}$.
+In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
+The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
+Thus, the simplest semantics for a generalization is a threshold on the prevalence: $\denote{gen}(p, \theta) = \{p >\theta\}$.
 
@@
 By doing so, we thus provide an account of how context influences generic understanding and are able to make precise, quantitative predictions about human judgments.
+/ndg{this paragraph belongs later, after the model has been finished.}
 
@@
 ]
-The model also has prior knowledge about the property $P(p)$ (described in more detail below) and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of utterance $\delta_{\denote{u}(p, \theta)}$:
+The model also has prior knowledge about the property $P(p)$ (described in more detail below) and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of the utterance $\delta_{\denote{u}(p, \theta)}$:
 
@@
 Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is intuitively true or not?
-We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey the appropriate information to the naive interpreter? 
-We formalize this by considering how well the generalization would convey the prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
+We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization statement convey the appropriate information to a naive interpreter? 
+We formalize this by considering how well the generalization would convey the target prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
@@
 \end{equation}
+\ndg{this eqn isn't well motivated. if we never use cost in this paper, then get rid of exp and ln and just have Lit to a power of lambda. also say why it's called S earlier?}
 
@@
 Following Bayesian decision theory, we assume the decision to endorse is approximately rational, with degree of rationality given by $\lambda$.
+\ndg{this doesn't make a ton of sense in this context, since we haven't set up S as a decision maker....}
 The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
@@
 \ref{eq:S1}).
-This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016] with only a single level of recursion and the space of possible utterances maximally constrained; the endorsement model is a "speaker", while the interpretation model is a "listener".
+This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016] with only a single level of recursion and the space of possible utterances maximally constrained; the endorsement model is a "speaker", while the interpretation model is a "listener", and we are interested in whether a reasonable speaker would bother to utter the generalization.
+\ndg{i wonder if the content of this paragrph should be earlier, to motivate the endorsement model?}
 
@@
 Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence. 
-However, the interpretation model's prior beliefs $P(p)$ must be considered before the endorsement model can say whether or not would it want to update those beliefs by endorsing the statement.
+However, the interpretation model's prior beliefs $P(p)$ will be constrain the interpretation and thus the endorsement.
 
@@
 
+\ndg{this paragraph should get moved elswhere. it is distracting here....}
 Beliefs about properties result from internal, conceptual models of the world. 
@@
 B: Full interpretation model marginalizes over possible thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
-C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
+C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.
+\ndg{say what P(p) is used here...}", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
 
@@
 
-These simulations show how the model predicted endorsement depends upon the background knowledge of the interpreter about the property $P(p)$ as well as the referent-prevalence of the endorser $p$ communicated.
+These simulations show how the model predicted endorsement depends upon the background knowledge of the interpreter about the property $P(p)$ as well as the referent-prevalence $p$ presented to the endorser.
 We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.

### 2018-03-18 paper/comgen-paper.Rmd
address comments up to prev prior subsec

@@
 Probability is a useful representation for human generalization from observations [@Shepard1987].
-If you *observe* several wugs (a novel category) that have two legs, you might infer that all wugs have two legs.
+If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
 But not all properties have such strong projectibility.
@@
 
-This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
-We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding this semantic hypothesis in a cognitive model in which relevant contextual knowledge can be formalized.
-By doing so, we thus provide an account of how context influences generic understanding and are able to make precise, quantitative predictions about human judgments.
-/ndg{this paragraph belongs later, after the model has been finished.}
-
 <!-- Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has made precise, quantitative predictions about adult judgments.
@@
 The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
-Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like "tall" have contextually-determined thresholds [e.g., what counts as "tall" for a four-year-old is different than what counts as "tall" for an adult; @Kennedy2007; @Lassiter2013].
+Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
 
@@
 
-Given the above model of literal interpretation, how do we decide when a statement conveying a generalization is intuitively true or not?
-We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization statement convey the appropriate information to a naive interpreter? 
-We formalize this by considering how well the generalization would convey the target prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}).^[
+In this paper, we are interested in explaining truth judgments (e.g., "Robins lay eggs" is intuitively true; "Robins are female" is not).
+If the interpreter is a kind of simple listener model, then we can ask whether an agent would bother to produce the generalization to this listener.
+The endorsement model then acts as a kind of speaker, reasoning about how the interpreter model (the listener) would understand the utterance.
+This kind of model formalizes the basic aspects of communicative reasoning and is called a Rational Speech Act model [@Frank2012; @Goodman2016].
+
+We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
+"disagree") as supplying two alternatives to the endorsement model: produce the generalization vs.
+some null alternative [@Franke2014cogsci; @Degen2014].
+For simplicity, we take the null alternative to be an information-less "silent" utterance: 
+$\denote{null}(x, \theta) = \text{True}$.^[
+  The null alternative can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
+  All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity.
+]
+
+The utterance encoding a generalization updates the interpreter model's beliefs about the prevalence of a feature in the category being referred to, which we refer to as the *referent prevalence*. 
+The endorsement model has a particular referent prevalence in mind and decides whether the generalization  (vs. the null alternative) is a good way to convey that to the interpreter. ^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
@@
 ]
-
+This endorsement model (called $S$ for speaker) does this by reasoning about the interpreter model $Lit$: 
 \begin{equation}
-S(u \mid p) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p, \theta \mid u)  \diff \theta } )}
+S(u \mid p) \propto (\int_{\theta} Lit(p, \theta \mid u)  \diff \theta)^\lambda
 \label{eq:S1}
 \end{equation}
-\ndg{this eqn isn't well motivated. if we never use cost in this paper, then get rid of exp and ln and just have Lit to a power of lambda. also say why it's called S earlier?}
-
-The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p, \theta \mid u)$.
-$S$ does not know $\theta$ and integrates over the interpreter's posterior beliefs about $\theta$.
-Following Bayesian decision theory, we assume the decision to endorse is approximately rational, with degree of rationality given by $\lambda$.
-\ndg{this doesn't make a ton of sense in this context, since we haven't set up S as a decision maker....}
-The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances. 
-We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [@Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$.^[
-  This "null" alternative to the generalization can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
-  The latter is different because it creates a new threshold (analogous to how "short" and "tall" are modeled with different thresholds).
-  All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity.
-]
+
+The informational content of the generalization is about the referent prevalence $p$.
+The semantic threshold $\theta$ is a nuisance parameter then; the endorsement model integrates over the interpreter's posterior beliefs about $\theta$.
+Finally, because the endorsement model must decide whether or not to endorse the generalization, we assume this model is an approximately rational decision-maker, with degree of rationality given by $\lambda$.
+This exponentiation step acts as a soft-max function on $S$'s posterior beliefs of which utterance is better.
+
+<!-- \ndg{this doesn't make a ton of sense in this context, since we haven't set up S as a decision maker....} -->
+
+<!-- We consider the notion of truth judgments or endorsement from the information-theoretic perspective: Would a generalization statement convey the appropriate information to a naive interpreter?
+-->
+
+<!-- We formalize this by considering how well the generalization would convey the referent prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}). -->
+
+<!-- \begin{equation}  -->
+<!-- S(u \mid p) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p, \theta \mid u)  \diff \theta } )} -->
+<!-- \label{eq:S1} -->
+<!-- \end{equation} -->
+<!-- \ndg{this eqn isn't well motivated. if we never use cost in this paper, then get rid of exp and ln and just have Lit to a power of lambda. also say why it's called S earlier?} -->
+
+<!-- The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p, \theta \mid u)$. -->
+<!-- The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances.  -->
+<!-- We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
+"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [@Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$.^[ -->
+<!--   This "null" alternative to the generalization can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
+-->
+<!--   The latter is different because it creates a new threshold (analogous to how "short" and "tall" are modeled with different thresholds). -->
+<!--   All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity. -->
+<!-- ] -->
 
@@
 \ref{eq:S1}).
-This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016] with only a single level of recursion and the space of possible utterances maximally constrained; the endorsement model is a "speaker", while the interpretation model is a "listener", and we are interested in whether a reasonable speaker would bother to utter the generalization.
-\ndg{i wonder if the content of this paragrph should be earlier, to motivate the endorsement model?}
+This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
+We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
+In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
+
+<!-- By doing so, we are able to describe how context influences generic understanding and are able to make precise, quantitative predictions about human judgments. -->
 

### 2018-03-18 paper/comgen-paper.Rmd
finish addressing comments in model sec, minor cleaning in model sec

@@
 The endorsement model then acts as a kind of speaker, reasoning about how the interpreter model (the listener) would understand the utterance.
-This kind of model formalizes the basic aspects of communicative reasoning and is called a Rational Speech Act model [@Frank2012; @Goodman2016].
+This kind of model formalizes the basic aspects of communicative reasoning and is the simplest instantiation of a Rational Speech Act model [@Frank2012; @Goodman2016].
 
@@
 "disagree") as supplying two alternatives to the endorsement model: produce the generalization vs.
-some null alternative [@Franke2014cogsci; @Degen2014].
-For simplicity, we take the null alternative to be an information-less "silent" utterance: 
+a null alternative [@Franke2014cogsci; @Degen2014].
+For simplicity, we take the null alternative to be an information-less "silent" utterance which is always true: 
 $\denote{null}(x, \theta) = \text{True}$.^[
@@
 
-The utterance encoding a generalization updates the interpreter model's beliefs about the prevalence of a feature in the category being referred to, which we refer to as the *referent prevalence*. 
-The endorsement model has a particular referent prevalence in mind and decides whether the generalization  (vs. the null alternative) is a good way to convey that to the interpreter. ^[
+The utterance encoding a generalization updates the interpreter model's beliefs about the prevalence of a feature in the category being referred to, which we call the *referent prevalence*. 
+The endorsement model has a particular referent prevalence in mind and decides if the generalization or the null alternative is better at conveying that to the interpreter. ^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
@@
 ]
-This endorsement model (called $S$ for speaker) does this by reasoning about the interpreter model $Lit$: 
+This endorsement model (called $S$ for speaker) does so by reasoning about the interpreter model $Lit$: 
 \begin{equation}
@@
 This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
-We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
+We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model $Lit$ in which relevant contextual knowledge can be formalized.
 In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
@@
 
-The uncertain, truth-conditional threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
-\ref{eq:L0}) by integrating the model's prior beliefs about the feature in question---the *prevalence prior* $P(p)$---with the underspecified semantics.
-Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence. 
-However, the interpretation model's prior beliefs $P(p)$ will be constrain the interpretation and thus the endorsement.
+The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question.
+This background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
+This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence.
+
+Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
+Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
+Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties.
+The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
+Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
+Cue validity operationalizes an alternative hypothesis about the interpretation of generic statements that the reading of statements like "Mosquitos carry malaria" is as "It is mosquitos that carry malaria", and empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
+Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
+Knowledge about other categories $k'$ enters in the denominator.
+Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
+Thus cue validity comes from a point estimate of the prevalence prior distribution.
+For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
+For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we will construct alternative models based on empirically-elicited cue validity.
+
+<!-- The prevalence priors represent abstract beliefs about the properties -->
+<!-- To reason through those questions, you may rely upon your intuitive theories of reproduction (e.g., only females lay eggs).  -->
+<!-- Each property has a prevalence  -->
+
+<!-- For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
+-->
+<!-- Furthermore, among the categories that do have individuals that bark (e.g., dogs, seals, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have some probability mass at relatively high prevalences, potentially with some uncertainty (Figure\ \@ref(fig:simulations); column 1).
+-->
+<!-- Abstract beliefs between different kinds of categories could manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations); column 4).
+-->
+
+<!-- The uncertain semantic threshold $\theta$ is resolved by the literal interpretation model $Lit$ (Eq.
+\ref{eq:L0}) the model's background knowledge about the feature in question---the *prevalence prior* $P(p)$---with the uncertain semantics.
+-->
+
+<!-- Because $P(\theta)$ is assumed to be a uniform distribution across all contexts, a generalization could in principle be felicitous with any referent-prevalence.  -->
+<!-- However, the interpretation model's prior beliefs $P(p)$ constrains possible interpretations of the statement, and thus the endorsement.  -->
 
@@
 <!-- These internal models may have domain-specific features but can be described by the domain-general currency of inductive belief: probability. -->
-
-\ndg{this paragraph should get moved elswhere. it is distracting here....}
-Beliefs about properties result from internal, conceptual models of the world. 
-We do not take up the task of formalizing particular conceptual models, but rather merely try to measure their implications on beliefs about prevalence. 
-Without appealing to domain specific knowledge, one can construct a prior distributions over prevalence by considering the prevalence of the feature among alternative categories.
-For example, many different kinds of animals *do not bark* (more precisely: have close to 0 exemplars who bark); thus, the prevalence prior for the feature *barks* should have substantial probability mass near 0, because one would expect a randomly-sampled category to have 0 or close to 0 exemplars that bark.
-Furthermore, among the categories that do have exemplars which bark (e.g., *dogs*, *seals*, ...), the probability is quite high that an exemplar will bark; thus, the corresponding prevalence prior would have some probability mass at relatively high prevalences, potentially with some uncertainty (Figure\ \@ref(fig:simulations); column 1).
-Abstract beliefs between different kinds of categories could manifest in these prevalence priors in the form of multi-modal distributions; for example, the prevalence prior for *lays eggs* should similarly have substantial probability mass near 0 (since many animal categories do not have egg-layers) but should have a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property (Figure\ \@ref(fig:simulations); column 4).
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability that an entity with a certain property $f$ is a member of kind $k$: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria), shown to be highly correlated with endorsements of generics [@Khemlani2012].
-*Cue validity* implicitly encodes knowledge of other categories $k'$ by averaging over those categories via the denominator in Bayes' Rule:
-$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
-Since cue validity is defined for a particular category--property pair, it can be seen as a point estimate of the prevalence prior distribution.
-In particular: The normalizing constant for calculating cue validity ($\sum_{k' \in K} p' \cdot P(p')$) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
-For a more detailed derivation of this relationship, see Appendix A.
 
@@
 
-```{r uniformPriorSimulation, fig.cap = "Computational model behavior.
+```{r uniformPriorSimulation, fig.cap = "Computational model behavior assuming a uniform prior over prevalence.
 A: Interpretation model posteriors assuming different fixed thresholds.
@@
 B: Full interpretation model marginalizes over possible thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
-C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.
-\ndg{say what P(p) is used here...}", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
+C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
 

### 2018-03-20 paper/case1-generics.Rmd
edits to case stufy 1

@@
 
-Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
+We first investgate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
 We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g.
@@
 1a).
-We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$ (Expt. 1b).
-This elicitation procedure includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq.
+We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$.
+The prevalence elicitation procedure (Expt.
+1b) includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq.
 \ref{eq:S1}) as well as for simpler, alternative models.
@@
 Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure) A.
+All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure)A.
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
@@
 As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
+indeterminate generics were agreed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
 
 In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
+\ndg{the letters after figures are often with a space..
+get rid of that?}
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
-We next measure the prevalence prior distribution and articulate a set of formal models that try to predict these endorsement data.
+We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict these endorsement data.
 
@@
 There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
-The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
+The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
 *Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
-This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.
+This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution
 
@@
 In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
-We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
+We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
   The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
@@
 blue lines).
-The *Single Beta* model does okay for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
+The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
 One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
@@
 ]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.
+A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. \ndg{but we don't use one because...?}
 
@@
 B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution.
-Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution.
+Distributions are the posterior predictive distributions for the models of the prior and the raw empirical distribution.
 A completely uniform distribution would be represented as the y = x line.", cache = F}
@@
 
-To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
+We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
+
+\ndg{next two paragraphs are redundant with subsections below. delete or merge into subsections.}
 As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
@@
 Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
-Such a model makes the wrong prediction for non-distinctive properties that in, absolute terms, have high prevalence but in relative terms, low prevalence (e.g., "Mosquitos don't carry malaria").
+Such a model makes the wrong prediction for non-distinctive properties that in absolute terms have high prevalence but in relative terms low prevalence (e.g., "Mosquitos don't carry malaria").
 A simple metric like cue validity is too blunt to capture these subtleties.
@@
 \ref{eq:L0}) conditioned on a particular referent-category prevalence $p_{fk'}$  (e.g.,  the percentage of robins that lay eggs).
-We use the empirically estimated referent-category prevalence (the same as used in the baseline regression model) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
-The empirically measured priors from Expt. 1b are used as the literal interpreter's prevalence prior $P(p_{fk})$.
+We use the empirically estimated referent-category prevalence (the same as used in the baseline regression models) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
+The empirical measurments of prevalence from Expt. 1b are used to constrain the literal interpreter's prevalence prior $P(p_{fk})$.
 
-To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt.
+We build a single Bayesian data analysis model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt.
 1b data), and the endorsement data (Expt.
 1a).
+\ndg{recal the mixture of betas model, and resuting params?}
 Modeling the data from both Expt.
-1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
-The endorsement model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
+1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix \ndg{which one?} and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
+The endorsement model in addition has optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
 To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burn-in.
@@
 
-To evaluate the fixed-threshold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
+To evaluate the fixed-threshold model, we examine model predictions as well as the posterior distribution over latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data.
 The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
@@
 Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers context-specific $\theta$'s.
-We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
+We use the same Bayesian data analysis approach; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
 Thus, this model has two *fewer* parameters than the fixed-threshold model above.
@@
 1b).
+\ndg{point to a figure or give some stat to back up thi claim?}
 This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
@@
 \ref{eq:S1} is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`].
+\ndg{this is just hanging out in space. add a sentence of interpretation, or burry it among other results.}
 
@@
 The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent prevalence*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure).
-It is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distribution. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
+The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure) ).
+This prior is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
+The red distribution shows the $L_0$ posterior upon hearing the generic utterance with an uncertain threshold-semantics. 
+The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own beliefs. 
+Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are useful things to say.
 "Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.
+"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's belief, despite the speaker believing that the prevalence is more than half.
 
@@
 Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
-Heretofore, however, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations, knowing when they are true and false.
-Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs.
-
+Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations: knowing when they are true and false.
+<!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->
 We have demonstrated that a semantics based on the probability of the feature is tenable in spite of alleged counterexamples.
-The key theoretical insight is that the truth-functional semantics is *underspecified* yet still is able to formalize, using recent developments in probabilistic modeling.
+The key theoretical insight is that the truth-functional semantics is *underspecified* but used precisiely in context by a process of probabiistic inference.
 Our model provides a clean delineation of world knowledge (formalized as a prior distribution) from the semantics of generalizations. 
@@
 However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.
-We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and prevalence priors (Case 3).
+We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case Study 2) and prevalence priors (Case Study 3).
 In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

### 2018-03-22 paper/case1-generics.Rmd
clean up case 1, still some outstanding comments

@@
 1a).
-We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$.
+We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p)$.
 The prevalence elicitation procedure (Expt.
-1b) includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq.
+1b) includes measurements of the referent-category feature-probabilities $p$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq.
 \ref{eq:S1}) as well as for simpler, alternative models.
@@
 Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure)A.
+All 30 generic sentences are shown in Figure\ \@ref(fig:generics-endorsement-figure)A.
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
@@
 
-In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
-\ndg{the letters after figures are often with a space..
-get rid of that?}
+In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
@@
 
-The prevalence prior $P(p_{fk})$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
+The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
 To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
@@
 
-This thought experiment decomposes the prevalence prior $P(p_{fk})$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p_{fk} \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(p_{fk}) = \int_{k} P(p_{fk} \mid k) \diff k$ and perform Bayesian data analysis to accurately reconstruct the prevalence prior.
+This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
+We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and perform Bayesian data analysis to accurately reconstruct the prevalence prior.
 We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure \ \@ref(fig:generics-prior-task) A).
+1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure\ \@ref(fig:generics-prior-task)A).
 A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure \ \@ref(fig:generics-prior-task) B).
+Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure\ \@ref(fig:generics-prior-task)B).
 Eight property--columns in total appeared in the table.
@@
 
-There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
+There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
 The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
@@
 
-The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs.
+The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure)B; red vs.
 blue lines).
@@
 
-\ndg{next two paragraphs are redundant with subsections below. delete or merge into subsections.}
-As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
-As a secondary alternative hypothesis, we explore whether referent prevalence and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
-We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.
-
-Our underspecified-threshold hypothesis models endorsement by considering how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p_{fk})$ (e.g., the prevalence of laying eggs among other animals) in line with the referent-category prevalence (e.g, the prevalence of laying eggs among robins).
-There are several substantive components to this hypothesis: (a) the prior distribution $P(p_{fk})$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
-not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
-As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
-This provides a strict test of the uncertain-threshold hypothesis (c).
-
 ```{r}
@@
 
+We present two baseline, quantitative models that have previously been used in the empirical literature on generic language.
+In addition to serving as alternatives, these regressions model help us understand the statistical properties of our thirty items. 
+First, we estimate how well referent prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
+Second, we include *cue validity*---the probability of a kind given the feature---as a second predictor in a linear model.
+We fit these models using standard maximum-likelihood techniques and model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.
+
 #### Referent prevalence
 
-From the prevalence prior data (Expt.
-1b), we estimate participants' beliefs about the probability of a feature for the referent categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
+From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
-The referent prevalence baseline is a decent model of these data because our stimulus set includes generics that are true with high prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*).
+Referent prevalence alone does okay at predicting these data because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").
 
-However, large deviations from an account based purely on referent prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent prevalence ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
+Large deviations from an account based purely on referent prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by referent prevalence ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).
 This includes generics that are judged true with relatively low referent prevalence (e.g., "Mosquitos carry malaria") and false with relatively high referent prevalence (e.g., "Sharks don't eat people").
@@
 
-##### Model specification
+<!-- ##### Model specification -->
 
-Cue validity is a metric of how diagnostic the feature is of the kind, and is given formally by the probability of a kind given the feature $P(k \mid f)$.
+Cue validity indexes the diagnosticity of the feature for a kind, given formally by the probability of a kind given the feature $P(k \mid f)$.
 As discussed in the Computational Model section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
-Cue validity can thus be seen as a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution.
+Cue validity thus is similar to a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution. 
+<!-- Comparison to a model based on cue validity thus  -->
 
-To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity.
-Though the cue validity of a particular category by a particular property can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity in various ways from empirical data about distinctiveness [@Cree2006; @Khemlani2012].
+<!-- To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity. -->
+Though the cue validity of a property for a category can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity from different empirical sources [@Cree2006; @Khemlani2012].
 In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs.
@@
 We thus used the data from the free production paradigm ($n = 100$) to estimate cue validity. 
-For a detailed analysis of the different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.
+For a detailed analysis of the different cue validity measurements and comparison to cue validity derived from the prevalence prior, see Appendix B.
 
@@
 
-##### Results
+<!-- ##### Results -->
 
@@
 "Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
-Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Fig.\ \@ref(fig:simulations)A bottom).
+Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Figure\ \@ref(fig:simulations)A bottom).
 Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
-Such a model makes the wrong prediction for non-distinctive properties that in absolute terms have high prevalence but in relative terms low prevalence (e.g., "Mosquitos don't carry malaria").
+Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
 A simple metric like cue validity is too blunt to capture these subtleties.
@@
 
-The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter.
-The endorsement model (Eq.
-\ref{eq:S1}) decides whether or not to assert the generalization to a naive interpreter (Eq.
-\ref{eq:L0}) conditioned on a particular referent-category prevalence $p_{fk'}$  (e.g.,  the percentage of robins that lay eggs).
-We use the empirically estimated referent-category prevalence (the same as used in the baseline regression models) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
-The empirical measurments of prevalence from Expt. 1b are used to constrain the literal interpreter's prevalence prior $P(p_{fk})$.
+Our underspecified-threshold model considers how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p)$ (Eq.
+\ref{eq:L0}; e.g., the prevalence of laying eggs among other animals) in line with the referent prevalence ($p$ in Eq.
+\ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
+There are several substantive components to this hypothesis: (a) the prior distribution $P(p)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
+As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
+This provides a strict test of the uncertain-threshold hypothesis (c).
 
-We build a single Bayesian data analysis model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt.
+<!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
+For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent-category prevalence $p$, prevalence priors $P(p)$ (both from Expt.
 1b data), and the endorsement data (Expt.
 1a).
-\ndg{recal the mixture of betas model, and resuting params?}
+Empirically elicited referent prevalence and prevalence prior data (Expt.
+1b) directly constrain their corresponding parameters in the model ($p$ in Eq.
+\ref{eq:S1} and $P(p)$ in Eq.
+\ref{eq:L0}, respectively).
+The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
+The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
 Modeling the data from both Expt.
-1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix \ndg{which one?} and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
-The endorsement model in addition has optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
-To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burn-in.
+1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
+To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.
 
-The number of parameters of this full data-analytic model is relatively large, and thus there is a concern that the parameters themselves (as opposed to the exact structure of our model) are doing the work.
-To address this concern, we construct a strong, alternative model that uses the same data analytic strategy and only differs in the uncertain semantic threshold $\theta$ is replaced with a fixed-threshold.
-To provide the strongest possible test, we make the fixed-threshold a parameter of the data-analytic model, to search for the best possible fixed-threshold. 
-Finally, a fixed-threshold model will have to accommodate responses that are inconsistent with the threshold (i.e., a participant endorsing the generalization when the referent prevalence is low); we thus outfit this model with an *additional* noise parameter, to allow for random guessing.
-Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p_{fk})$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
-This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
-We examine the predictions of this alternative model first.
+<!-- The number of parameters of this full data-analytic model is relatively large, and thus there is a concern that the parameters themselves (as opposed to the exact structure of our model) are doing the work.
+-->
+<!-- To address this concern, we construct a strong, alternative model that uses the same data analytic strategy and only differs in the uncertain semantic threshold $\theta$ is replaced with a fixed-threshold.
+-->
 
 #### Fixed-threshold with noise model
+
+To provide a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
+In addition, we make this fixed-threshold a parameter of the data-analysis model, to search for the best possible fixed-threshold. 
+Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional noise parameter, to allow for random guessing.
+Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
+This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
+<!-- We examine the predictions of this alternative model first. -->
 
@@
 We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-Figure \@ref(fig:generics-endorsement-figure) (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
+Figure\ \@ref(fig:generics-endorsement-figure) (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
 Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither. 
@@
 We use the same Bayesian data analysis approach; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
-Thus, this model has two *fewer* parameters than the fixed-threshold model above.
+Thus, this model has two fewer parameters than the fixed-threshold model above.
 
-We first examine the posterior predictive distribution on the prevalence prior and referent-prevalence data to ensure that the joint-inference model fits these data as well as the Bayesian model that modeled these data in isolation.
-This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters.
-Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
+We first examine the posterior predictive distribution on the prevalence prior and referent prevalence data to ensure that the joint-inference model does not distort these parameters at the service of predicting the endorsement data (e.g., such a distortion could manifest by the joint-inference model inferring that 100% of mosquitos carry malaria in order to predict that "Mosquitos carry malaria" is a good utterance).
+This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters (e.g., that not all mosquitos carry malaria).
+Importantly, the model recapitulates the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
 1b).
@@
 This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
+Finally, the inferred optimality parameter in the endorsement model (Eq.
+\ref{eq:S1}) is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`], a range consistent with the literature on similar models.
 
-The inferred optimality parameter in Eq.
-\ref{eq:S1} is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`].
-\ndg{this is just hanging out in space. add a sentence of interpretation, or burry it among other results.}
+As we see in Figure\ \@ref(fig:generics-endorsement-figure)(top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+To gain some intuition for why the model makes the predictions that it does, we can examine the relevant model components that give rise to these predictions (Figure \ref{fig:generics-endorsement-figure} bottom row).
+Recall that the prevalence prior (grey distribution) is also the interpreter model's posterior upon hearing the null, or silent, utterance, and that the endorsement model decides whether to produce the generic utterance or remain silent given some referent prevalence (blue distribution).
+The interpreter model's prevalence posterior upon hearing the generic utterance (red distribution) differs depending on the property being predicated (facets).
 
-As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
-The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent prevalence*).
-The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure) ).
-This prior is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
-The red distribution shows the $L_0$ posterior upon hearing the generic utterance with an uncertain threshold-semantics. 
-The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own beliefs. 
-Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are useful things to say.
-"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
-"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's belief, despite the speaker believing that the prevalence is more than half.
+The endorsement model decides if the generic utterance conveys information that would bring the interpreter's distribution more in line with the endorsement model's referent prevalence. 
+The model rates "Robins lay eggs" as a good utterance because the prevalence posterior implied by the generalization is similar to the referent prevalence. 
+The prevalence posterior for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad, endorsement around 0.5.
+"Mosquitos carry malaria" is an interesting case because the prevalence prior has high variance (i.e., participants are highly uncertain about the prevalence of carrying malaria among categories).
+As a result, the prevalence posterior also has high variance; still, the prevalence posterior is more consistent with the referent prevalence than the prevalence prior, and the endorsement model predicts "Mosquitos carry malaria" is a good utterance.
+Finally, an utterance with high referent prevalence, such as "Tigers don't eat people", is predicted to have low endorsement because the generic would be misleading; even if most tigers don't eat people, saying "Tigers don't eat people" implies that all don't eat people, which is too strong.
+
+<!-- The grey distribution shows the interpreter model's prevalence prior (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)).
+-->
+<!-- The prevalence prior is also the interpreter's prevalence posterior upon hearing the silent utterance $Int(p \mid u = null)$. -->
 
@@
 Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
-Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations: knowing when they are true and false.
+Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generics: knowing when they are true and false.
 <!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->
-We have demonstrated that a semantics based on the probability of the feature is tenable in spite of alleged counterexamples.
-The key theoretical insight is that the truth-functional semantics is *underspecified* but used precisiely in context by a process of probabiistic inference.
-Our model provides a clean delineation of world knowledge (formalized as a prior distribution) from the semantics of generalizations. 
+This empirical case study demonstrates that a semantics based on the prevalence of the feature is tenable despite of alleged counterexamples (e.g., "Robins lay eggs" vs. "Robins are female").
+The key theoretical insight is that the truth-functional semantics is underspecified, or vague, and resolved in context by a process of probabiistic inference.
+Our model provides a clear delineation of world knowledge (formalized as a prevalence prior) from the semantics of generics. 
 We return to this point, and its implications for theory-building, in the general discussion.
@@
 
-In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via our communicative model with prior knowledge about the distribution of prevalence (e.g., the prevalence of laying eggs for different kinds of animals).
-In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs.
-"...
-are female".
+In explaining the variable endorsements of generics, we related the referent prevalence (e.g., the percentage of robins that lay eggs) and the prevalence prior (e.g., the prevalence of laying eggs for different kinds of animals)  to the endorsement of the generalization (e.g., "Robins lay eggs") via an information-theoretic communicative model where the meaning of a generic is simple but underspecified.
+In this case study, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs.
+"Robins are female".
 However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.

### 2018-03-22 paper/case2-habituals.Rmd
small edits to habituals prose, redo hab priors figure

@@
 
-The event of Mary smoking at 2:30pm on January the 24th is an instance of a kind of event: *Mary smoking*. 
-Just as with categories, generalization can occur over events of a particular type.
-When expressed in language, these generalizations take the form of *habitual language*: "Mary smokes".
-
-Events are a broad class of entities. 
+As with categories, particular events like "Mary smoked yesterday" can be generalized into *habitual sentences*: "Mary smokes". 
+<!-- Events are a broad class of entities.  -->
 In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes").
@@
 To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
-We take event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).
-For the generalization "Mary smokes", instances of the category being generalized are *instances of Mary* and if for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
+We take event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).^[
+  Specifically, for the generalization "Mary smokes", the instances being generalized are *instances of Mary*, and for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
+]
 We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2a).
-We then measure endorsements of habitual statements while manipulating the *referent-prevalence*  (Expt. 2b), and use our computational model to predict habitual endorsements. 
+We then measure endorsements of habitual statements while manipulating the referent prevalence  (Expt. 2b), and use our computational model to predict habitual endorsements. 
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-By describing novel characters to participants, we are able to directly the manipulate the *referent-prevalence* (rate), which we were unable to do for generalizations about familiar categories.
+By describing novel characters to participants, we are able to directly the manipulate the referent prevalence, which we were unable to do for generalizations about familiar categories.
 <!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 
-Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely their observations. 
-Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
-Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
-We extend our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
+Finally, if habituals (and generics) are truly language for conveying generalizations, they should reflect speakers' expectations, not merely their observations. 
+Our computational model predicts endorsement rates given a referent prevalence $p$. 
+Does prevalence represent the actual, objective frequency in the world or the subjective, predictive belief in the head?
+We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
 We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
+
+<!-- (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)? -->
 
@@
 In order to generate model predictions for corresponding habitual statement, we first elicit the prior distributions over rates for different events.
-For language about the behaviors of people, $P(p_f)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
+For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
 We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1 .
@@
                        #"wears a suit", "wears a watch", "wears socks", 
-                       #"writes poems", 
-                       "goes to the movies"#, "plays the banjo"
+                       "writes poems", 
+                       "writes novels", 
+                       "goes to the movies", "plays the banjo"
                        )
@@
 
-figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
-       aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
-           y = empirical_mean, ymin = ci_lower, ymax = ci_upper, color = gender))+
-  facet_wrap(~measurement, scales = 'free', nrow = 2)+
+figure.habituals.priors.scatter <- 
+  rs.habituals.bda.posterior.predictive.measurementSpace %>%
+  select(-mean, -ci_lower, -ci_upper, -empirical_mean, -n, -cred_upper, -cred_lower) %>%
+  spread(measurement, MAP) %>%
+  ggplot(.,
+       aes(x = `% people who have done action before`, 
+           y = `Frequency of doing action (log scale)`, 
+           color = gender))+
   scale_color_solarized()+
   geom_point()+
-  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
-  geom_label_repel(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+  #geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+  geom_label_repel(data = . %>%
                     filter(item %in% example.habituals, gender == "female"), 
-                  inherit.aes =F, segment.alpha = 0.1,label.size = 0.15,
-                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 2)+
-  coord_fixed()+
-  xlab("Model posterior predictive")+
-  ylab("Empirical means")+
-  theme(legend.position = c(0.86, 0.09))
+                  inherit.aes =F, segment.alpha = 1,label.size = 0.25,
+                  segment.size = 5,
+                  aes(x = `% people who have done action before`, 
+           y = `Frequency of doing action (log scale)`, 
+           label = item), force = 1, size = 2)+
+  coord_fixed(1/7.5)+
+  #xlab("Model posterior predictive")+
+  #ylab("Empirical means")+
+  theme(legend.position = c(0.83, 0.16))+
+  scale_y_continuous(
+      limits = c(-1.5, 6),
+      breaks = c(0, 2.5, 4, 5.9),
+      labels = c( "annually", "monthly", "weekly", "daily")
+    )+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))
+
+# figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
+#        aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
+#            y = empirical_mean, ymin = ci_lower, ymax = ci_upper, color = gender))+
+#   facet_wrap(~measurement, scales = 'free', nrow = 2)+
+#   scale_color_solarized()+
+#   geom_point()+
+#   geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+#   geom_label_repel(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
+#                     filter(item %in% example.habituals, gender == "female"), 
+#                   inherit.aes =F, segment.alpha = 0.1,label.size = 0.15,
+#                   aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 2)+
+#   coord_fixed()+
+#   xlab("Model posterior predictive")+
+#   ylab("Empirical means")+
+#   theme(legend.position = c(0.86, 0.09))
 
@@
   scale_color_solarized()+
+  scale_linetype_manual(values = c(2, 1))+
   xlab("Frequency")+

### 2018-03-22 paper/appendix-habitualsItems.Rmd
add table of habituals items to appendix

# Appendix D: Habituals Items

```{r}
load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression

d.hab.predictive <- read.csv(paste(
  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))
```

```{r habitualItems, results="asis"}
habituals.predictive.items <- left_join(
  d.hab.predictive %>% 
    distinct(item, past_interval, condition),
  d.hab.predictive %>% 
    distinct(item, past_interval, condition, extra_sentence) %>%
    group_by(item, past_interval, condition) %>%
    top_n(1, extra_sentence)
) %>%
  spread(condition, extra_sentence) %>%
  select(-baseline)

habituals.items <- left_join(
  d.hab.endorse.regression %>%
    distinct(habitual, time_period),
  habituals.predictive.items %>% 
    select(item, past_interval) %>%
    rename(habitual = item, time_period = past_interval) %>%
    mutate(predictive = T)
  ) %>% 
  #rowwise() %>%
  mutate(predictive = ifelse(is.na(predictive), F, predictive),
         time_period = ifelse(predictive, 
                              paste(time_period , "*", sep = ""),
                              time_period)) %>%
  select(-predictive) %>%
  group_by(habitual) %>%
  summarize(`referent frequency` = paste(time_period, collapse = ", "))

habituals.tab.items <- left_join(habituals.items, 
          habituals.predictive.items %>%
            rename(habitual = item) %>%
            select(-past_interval)) %>% 
  mutate(enabling = ifelse(is.na(enabling), "", as.character(enabling)),
         preventative = ifelse(is.na(preventative), "",
                               as.character(preventative)))

# d.items <- d.items[with(d.items, order(positive)),] %>%
#   rename("Positive adjective" = positive, "Morphological antonym" = morphant,
#          "Lexical antonym" = lexant)

tab1 <- xtable::xtable(habituals.tab.items, 
                       #caption = "Items used in habituals experiments (Case Study 2)", 
                       align=c('p{1in}',' |p{1in}|', 'p{1.2in}| ','p{1.75in}|','p{1.75in} |'))

addtorow          <- list()
addtorow$pos      <- list()
addtorow$pos[[1]] <- c(0)
addtorow$command  <- c(paste("\\hline \n",
                             "\\endhead \n",
                             "\\hline \n",
                             "{\\footnotesize \\em{continued on next page}} \n",
                             "\\endfoot \n",
                             "\\endlastfoot \n",sep=""))

large <- function(x){ paste0('{\\Large ', x, '}')
}
bold <- function(x){
paste0('{\\bfseries ', x, '}') }

print(tab1, type="latex", 
      comment = F,
       #table.placement = "h", 
      tabular.environment = "longtable",
      hline.after=-1:nrow(tab1),
      size="\\fontsize{9pt}{10pt}\\selectfont", 
      include.rownames=FALSE,
      sanitize.colnames.function = bold
      #add.to.row = addtorow
      )
```

Items used in Case Study 2 (Habitual language). Referent frequency denotes the experimentally supplied time periods during which a person did an action 3 times (e.g., "In the past 5 years, John climbed mountains three times."; Expt. 2b). 
Enabling and preventative columns provide the causal manipulation sentences used in Expt. 3c in order to enable or prevent future instances of the action (blank entries mean that the item was not used in Expt. 2c).
Referent frequency with an asterisk denotes the time interval used in Expt. 2c.

### 2018-03-22 paper/appendix-bda.Rmd
edit prose in bda appendix

--- 2017-12-23 paper/appendix-bda.Rmd
@@
 In our three case studies, we compare an information-theoretic, computational model of endorsement to human endorsements of generalizations in language. 
-The model has a single free parameter: the optimality parameter in Eq. \ref{eq:S1}.
-Other model parameters (governing the prevalence prior $P(h)$ and the referent-prevalence $h'$) are estimated using additional behavioral data (e.g., prior elicitation tasks). 
-Througout the paper, we model all sources of data (prevalence prior data, endorsement data) using a single joint-inference Bayesian data analytic model.
+The model has a single free parameter: the optimality parameter $\lambda$ in Eq. \ref{eq:S1}.
+We analyze this model using a Bayesian data analytic approach, where we jointly infer this single model parameter $\lambda$ together with parameters that govern the prevalence priors $P(p)$ and referent prevalence $p$ for each item.
+To pin down the prevalence prior and referent prevalence parameters, we use additional data directly related to those parameters (e.g., prior elicitation data).
+Incorporating all data sources into a single Bayesian data analysis model is the appropriate way to track measurement uncertainty for all measurements.
+<!-- Other model parameters (governing the prevalence prior $P(p_{fk})$ and the referent-prevalence $P_{fk'}$) are estimated using additional behavioral data (e.g., prior elicitation tasks).  -->
+<!-- Througout the paper, we model all sources of data (prevalence prior data, endorsement data) using a single joint-inference Bayesian data analytic model. -->
 In this appendix, we describe this procedure in more detail for each case study.
@@
 
-In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence prior by asking about individual about the prevalence of features for individual categories.
+In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence prior by asking about the prevalence of features for individual categories.
 We performed an analagous elicitation in Case Study 3: Causal Language (Expt. 3a).
@@
 
-Participants' responses can be thought of as *samples* from the prevalence prior distribution. 
+Participants' responses in the prior elicitation task can be thought of as *samples* from the prevalence prior distribution. 
 Formally, we assume the prior data (analyzed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
-The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
+The "transient" distribution intuitively corresponds to categories that do not have the feature normally, but potentially could be caused by accidental forces (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
 We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
@@
 Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
+Adjusting 1 to $1- \epsilon$ leads to improper inferences for this simple 2-component model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$, forcing it to favor probabilities close to 1.
 This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
@@
 If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
-We construct a posterior predictive distribution by "forward sampling" the model.^[
-This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
+We construct a posterior predictive distribution by "forward sampling" the model (i.e., generating new data given the inferred parameter values).^[
+This forward sampling can be described by the following algorithm: First, flip a coin weighted by $\phi$.
 If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
@@
 In Case Study 2 (Expt.
-2a), we asked participants about parameters of this mixture model (by having participants answer questions abouut *different kinds of people*) rather than having participants give samples (e.g., by listing their friends and rating how often their friends did certain actions).
-In pilot testing, we found these different methodologies to give similar results.
-We made the decision to ask more abstract information about the events to get at participants' abstract beliefs about the property rather than their knowledge of true frequencies. 
-As well, by querying about abstract characters, we were able to include items that participants might not otherwise feel comfortable reporting off (e.g., how often their friends smoke marijuana).
-The questions used to elicit information about the parameters are described in the main text.
+2a), we asked participants about parameters of this mixture model (by having participants answer questions about different kinds of people) rather than having participants give samples (e.g., by listing their friends and family members, and rating how often they did certain actions).
+In pilot testing, we found these different methodologies to give comparable results and we opted to ask about hypothetical people to probing about potentially undesirable habits of participants' friends and familiy (e.g., how often they use cocaine).
+The questions used in this structured elicitation task are  described in the main text.
+
+<!-- We made the decision to ask more abstract information about the events to get at participants' abstract beliefs about the property rather than their knowledge of true frequencies.  -->
+<!-- As well, by querying about abstract characters, we were able to include items that participants might not otherwise feel comfortable reporting off (e.g., how often their friends smoke marijuana).
+-->
 
@@
 1b) and assumed those were generated from a single Beta distribution.
-We used the same priors as we did for the *stable cause* component of the prevalence prior:
+We assumed the following priors on the parameters:
 \begin{eqnarray*}
@@
 2c ("What is prevalence?"), we compared two endorsement models that differed in their representation of referent-prevalence.
-For one model (past frequency model), it was the frequency given to participants in the experimental prompt (same as in Expt.
-2b); for the other model (predictive frequency model), we used the mean elicited frequency from the *predictive frequency* condition (see main text).
+For one model (past frequency model), the actual frequency given to participants in the experimental prompt was assumed to the referent prevalence (same as in Expt.
+2b); for the other model (predictive frequency model), we used the mean elicited frequency from the *predictive frequency* condition (participants predictions about how often the person would do the action in the next time interval; see main text for details).
 In Case Study 3 (Causal endorsement), we used the proportion of successful causal events given to participants in the experimental prompt (e.g., 70 out of 100 uses of Herb C made animals sleepy).
@@
 
-To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the prevalence prior data (described above) to create a single, joint-inference model where the optimality parameter $\lambda_1$ (Eq.
-\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_f(h)$ for each property $f$) using data from Expt.
+To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the prevalence prior data (described above) to create a single, joint-inference model where the optimality parameter $\lambda$ (Eq.
+\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $p$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_(p)$ for each property $f$) using data from Expt.
 1a \& b (Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the prevalence prior distributions, we use the same priors described in Expt.
-1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
-We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
+For the parameters of the prevalence priors, we use the same priors described in Expt.
+1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda \sim \text{Uniform}(0,5)$.
+We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 150,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
+This algorithm is useful for models with many variables that only affect a subset of the model's predictions (e.g., in models with by-item or by-participant parameters, where those additional parameters only influence predictions for those items or participants).
 
-```{r genericsModelDiagram, fig.cap="Graphical model corresponding to the fully Bayesian data analysis of the RSA model.
+```{r genericsModelDiagram, fig.cap="Pseudo-graphical model corresponding to the fully Bayesian data analysis of the endorsement model.
 The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
 1a.
-The referent-category prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
-The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P_f(h)$, the referent-prevalence $h$, and a single speaker optimality parameter $\\lambda$ as input.
+The referent-prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
+The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P(p_{f})$, the referent-prevalence $p_{fk}$, and a single speaker optimality parameter $\\lambda$ as input.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
@@
 
+## Supplementary model criticism
+
 In addition to examining the posterior predictive distribution on endorsement judgments (presented in main text), we examined the marginal posteriors on parameters of the prevalence priors and referent-prevalence.
 These marginal distributions are important to examine to confirm that they have not changed significantly from the parameters inferred from their private data sources in isolation.
-For example, when modeling the referent-prevalence data in isolation, the model infers that roughly 50\% of robins lay eggs, as that is what participants tend to say in the prevalence elicitation task.^[
-  Some participants do report that 100\% of robins lay eggs so the average prevalence rating is closer to 65\%..
-].
-The question for this joint inference model is whether or not it still believes that roughly 50\% of robins lay eggs.
+For example, when modeling the referent-prevalence data in isolation, the model infers that roughly 65\% of robins lay eggs, as that is what participants on average produce in the prevalence elicitation task.^[
+  Most participants report that 50\% of robins lay eggs, while a minority respond 100\%.
+]
+The question for this joint inference model is whether or not it still believes that roughly 50\% of robins lay eggs after being forced to jointly predict endorsements for "Robins lay eggs".
+For example, a linear regression model based on referent-prevalence (of the kind presented in the main text) incorporated into this Bayesian analysis model will end up predicting high endorsement for "Robins lay eggs", but only does so by distorting the referent-prevalence data (inferring that 100\% of robins lay eggs); thus, the linear model sacrifices its goodness-of-fit to the referent-prevalence data in order to increase its goodness-of-fit to the endorsement data.
+Such a distortion would show manifest as a difference between the inferred parameters given only the referent-prevalence data and given the full joint model (all data sources modeled  simultaneously).
+
 We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only their data, suggesting that the modeling all three data sources together does not come at the cost of modeling any one of them accurately.

### 2018-03-22 analysis/case1-generics.Rmd
analysis and cached results for parameter comparison: prev only vs. joint inference"

@@
 
-# Experiment 1:a: Generic endorsements
+# Experiment 1a: Generic endorsements
 
@@
     rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper) %>%
-    select(-n, -empirical_mean)
+    select(-n, -empirical_stat)
 ) %>%
@@
 
-generics.endorsement.spectrum <- ggplot(
-    d.gen.endorse.bayes.prev, 
-    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
-  )+
-  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
-  geom_linerange(position = position_dodge(), size = 1)+
-  coord_flip()+
-  ylab("Human generic endorsement")+
-  xlab("")+
-  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
-  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  guides(color = guide_colorbar(title = 'Prevalence',
-                               ticks = F))+
-  theme(legend.position = 'bottom')
+# generics.endorsement.spectrum <- ggplot(
+#     d.gen.endorse.bayes.prev, 
+#     aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
+#   )+
+#   geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
+#   geom_linerange(position = position_dodge(), size = 1)+
+#   coord_flip()+
+#   ylab("Human generic endorsement")+
+#   xlab("")+
+#   scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
+#   scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
+#   guides(color = guide_colorbar(title = 'Prevalence',
+#                                ticks = F))+
+#   theme(legend.position = 'bottom')
 ```
@@
 
-save(d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes,
-     file = "../paper/cached_results/case1_endorseSummary_byItem.RData")
+# save(d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes,
+#      file = "../paper/cached_results/case1_endorseSummary_byItem.RData")
 
@@
 
-save(d.gen.endorse.regression.prevalence, 
-     d.gen.endorse.regression.prevalence.cuevalidity, 
-     d.gen.endorse.regression, file = "../paper/cached_results/case1_regressionResults.RData")
+# save(d.gen.endorse.regression.prevalence, 
+#      d.gen.endorse.regression.prevalence.cuevalidity, 
+#      d.gen.endorse.regression, file = "../paper/cached_results/case1_regressionResults.RData")
+load("../paper/cached_results/case1_regressionResults.RData")
 
@@
 
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
+// var statePrior = Infer({model: function(){
+//  var component = flip(mixture);
+//  return component ?
+//    categorical({
+//      vs: bins,
+//      ps: map(function(b) {
+//        return probability(Beta(priorParams), b) + Number.EPSILON
+//      }, bins )
+//    }) :
+//    categorical({
+//      vs: bins,
+//      ps: map(function(b) {
+//        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
+//      }, bins )
+//    })
+// }});
 '
@@
     return { state }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+ }, method: "forward", samples: 20000, verbose: T})}
+'
+
+no.utterance.model.3comp <- '
+var componentParams = [
+  {a: 1, b:100},
+  {a: priorParams.a1, b:priorParams.b1},
+  {a: priorParams.a2, b:priorParams.b2}
+]
+display(data.prior.mix)
+var noUtteranceInterpreter = function() {
+  Infer({model: function(){
+   var state = beta(componentParams[discrete(data.prior.mix)])
+    return {
+      state: state, 
+  }
+  }, method: "forward", samples: 20000, verbose: T})}
 '
@@
 
+uncertain.threshold.model.3comp <- '
+var componentParams = [
+  {a: 1, b:100},
+  {a: priorParams.a1, b:priorParams.b1},
+  {a: priorParams.a2, b:priorParams.b2}
+]
+display(data.prior.mix)
+display(JSON.stringify(componentParams))
+var uncertainThresholdInterpreter = function() {
+  Infer({model: function(){
+  var component = discrete(data.prior.mix)
+  // display(component)
+  // display(JSON.stringify(componentParams[component]))
+   var state = beta(componentParams[component])
+    factor( Math.log(state) )
+    return {
+      state: state, 
+  }
+  }, method: "rejection", samples: 20000, verbose: T})}
+'
+
 ```
@@
 
-n_chains <- 3
-n_samples <- 100000
+n_chains <- 2
+n_samples <- 60000
 burn <- n_samples / 2
-lg <- 20
-
-model_prefix <- "results-generics-jointModel-S1-smntcs_"
+lg <- 10
+
+#model_prefix <- "results-generics-jointModel-S1-smntcs_"
 #fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
-# m.samp <- data.frame()
+model_prefix <- "results-generics-jointModel-S1-smntcs_generic-3compPriors-2compRef-"
+m.samp <- data.frame()
 #m.samp.fixed <- data.frame()
-#for (i in seq(1, n_chains)){
-  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
+for (i in seq(1, n_chains)){
+  mi.gen <- read_csv(paste(project.path,  "models/generics/results/", model_prefix,
+                           n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
+  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
 
@@
 #   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-# }
+}
 # 
@@
 
-load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
-                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
-
-# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
+## MODEL RESULTS
+load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))
 
@@
     #filter(type == "withinKind") %>%
-    mutate(parameter = paste(param, property, category, sep = "_")) %>%
-    select(-param, -property, -category, -chain, -type) %>%
+    #mutate(parameter = paste(param, property, category, sep = "_")) %>%
+    mutate(parameter = paste(param, property, category, component, sep = "_")) %>%
+    select(-param, -property, -category, -chain, -type, -component) %>%
     #mutate(item = paste(parameter, property, sep = "_")) %>%
@@
     ungroup() %>%
-    separate(parameter, into = c("parameter", "property", "category"), sep= "_")
+    separate(parameter, into = c("parameter", "property", "category", "component"), sep= "_")
 
@@
     ungroup()
+
+m.samp.prevalence <- m.samp.prev.params %>%
+    mutate(parameter = paste(parameter, component, sep = "_")) %>%
+    select(-component) %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate( 
+      component = rbinom(n = 1, size = 1, p = mix_1),
+      a = ifelse(component == 1, mean_1*sampleSize_1,mean_2*sampleSize_2),
+      b = ifelse(component == 1, (1-mean_1)*sampleSize_1, (1-mean_1)*sampleSize_2),
+      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
+      ) %>%
+    ungroup()
+
+m.samp.prevalence %>% filter(property %in% c("are female", "lay eggs"),
+                             category == "Robins") %>%
+  ggplot(., aes( x= prevalence))+
+  geom_histogram()+
+  facet_wrap(~property)
 ```
@@
   guides(fill = F)
+generics.endorsement.models
 ```
@@
 ```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
+
+# m.gen.fullmodel.prior.parameters <- m.samp %>%
+#   filter(type == "prior", property %in% example.generics.properties) %>%
+#   group_by(param, property, category) %>%
+#   summarize(MAP = estimate_mode(val),
+#             cred_upper = hdi_upper(val),
+#             cred_lower = hdi_lower(val))
 
@@
   filter(type == "prior", property %in% example.generics.properties) %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
+  group_by(param, property, category, component) %>%
+  summarize(expval = mean(val),
+            MAP = estimate_mode(val),
             cred_upper = hdi_upper(val),
@@
 
+# m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
+#   ungroup() %>%
+#   select(param, property, category, MAP) %>%
+#   mutate(param = paste(param, category, sep = "_")) %>%
+#   select(-category) %>%
+#   spread(param, MAP) %>%
+#   rename(mix = mixture_NA, 
+#          stable_mean = stableFreq_mean, 
+#          stable_concentration = stableFreq_sampleSize) %>%
+#   mutate( a = stable_mean * stable_concentration, 
+#           b = (1 - stable_mean) * stable_concentration)
+
 m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
   ungroup() %>%
-  select(param, property, category, MAP) %>%
+  mutate(param = paste(param, component, sep = "_")) %>%
+  select(param, property, category, expval) %>%
   mutate(param = paste(param, category, sep = "_")) %>%
   select(-category) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
+  spread(param, expval) %>%
+  rename(mixture_0 = mixture_0_NA, 
+         mixture_1 = mixture_1_NA, 
+         mixture_2 = mixture_2_NA, 
+         stable_mean_1 = stableFreq_1_mean, 
+         stable_concentration_1 = stableFreq_1_sampleSize,
+         stable_mean_2 = stableFreq_2_mean, 
+         stable_concentration_2 = stableFreq_2_sampleSize
+         ) %>%
+  mutate( 
+    a_1 = stable_mean_1 * stable_concentration_1, 
+    b_1 = (1 - stable_mean_1) * stable_concentration_1,
+    a_2 = stable_mean_2 * stable_concentration_2, 
+    b_2 = (1 - stable_mean_2) * stable_concentration_2
+    )
 
@@
  priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
+ # inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
+ #                                                   b = priorParams[["b"]]),
+ #                               mix = priorParams[["mix"]]), 
+ #                  utt = "generic")
+  inputData = list(prior = list(params = data.frame(a1 = priorParams[["a_1"]],
+                                                   b1 = priorParams[["b_1"]],
+                                a2 = priorParams[["a_2"]],
+                                                   b2 = priorParams[["b_2"]]),
+                               mix = c(priorParams[["mixture_0"]],
+                                       priorParams[["mixture_1"]],
+                                       priorParams[["mixture_2"]])), 
                   utt = "generic")
- l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
- l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
+
+ l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model.3comp, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+ l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model.3comp, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
+
+# l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
+ #l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
  gen.listener.predictions <- bind_rows(
@@
 
-save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
-     generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
-     file = "../paper/cached_results/case1_modelPosteriors.RData")
+# save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
+#      generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
+#      file = "../paper/cached_results/case1_modelPosteriors.RData")
 
@@
                  color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
+  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
   facet_wrap(~property, nrow = 1)+
@@
     theme(legend.position = "bottom", legend.title = element_blank())
+
+generics.endorsement.insets
+```
+
+```{r}
+for (p in example.generics.properties){
+gen.inset.distributions.refactored %>%
+    filter(property == p) %>%
+
+    ggplot(. , aes( x = value, fill = Parameter, 
+                 color = Parameter, lty = Parameter, alpha = Parameter ))+
+  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+  theme_black()+
+  facet_wrap(~property, nrow = 1)+
+  geom_label_repel(data = category.text.labels %>%
+                     filter(property ==p),
+                  aes(label = category, x = x , y = y),
+                  inherit.aes = F, color = "#b2df8a", fill='black')+
+    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+    scale_fill_manual(values = c("white", "#fb9a99", "#b2df8a"))+
+    scale_color_manual(values = c("white", "#fb9a99", "#b2df8a"))+
+    scale_alpha_manual(values = c(0.8, 0.5, 0))+
+    #scale_linetype_manual(values = c(3, 4, 2, 1))+
+    scale_linetype_manual(values = c(3, 4, 1))+
+    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Prevalence") +
+    ylab("Scaled density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+  ggsave(paste(
+    "~/Documents/research/talks/generics/mit-bcs-2018-03/figs/generics-insets-",
+    p, ".pdf", sep = ""), width = 2.5, height = 2.5)
+}
+
 ```
@@
 
+```{r testingNewViz}
+
+d.prev.zeros <- d.prev %>%
+  mutate(nonZero = prevalence > 0) %>%
+  group_by(Property) %>%
+  tidyboot_mean(column = nonZero)
+
+d.prev.zeros %>% 
+  mutate(Property = factor(Property, levels = Property ))
+  ggplot(., aes( x = Property, y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_col()
+
+ggplot(d.prev %>%
+         filter(prevalence > 0), 
+           aes( x = prevalence))+
+           #aes( x = prevalence, color = src, lty = src))+
+    geom_density(aes(y = ..scaled..), adjust = 0.5, size = 1)+
+    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    #stat_ecdf(size = 1)+
+    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    facet_wrap(~Property)+
+    #scale_linetype_manual(values = c(1, 4, 3))+
+    scale_x_continuous(breaks = c(0, 100), limits= c(0, 100))+
+    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #coord_fixed()+
+    xlab("") +
+    ylab("Normalized probability density")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+```
+
 ```{r generic-endorsement-priors-model-run, eval = F}
 m.gen.endorse.priors.posteriorPredictive <- data.frame()
-n_samples <- 1000
+n_samples <- 20000
 lg = 0
-example.generics.prior.properties <- c(
-  "dont eat people", "have beautiful feathers",
-  "have wings", "are red",
-  "carry malaria", "lay eggs", 
-  "are female", "have spots"
-  )
-
-for (p in example.generics.prior.properties ) {
+# example.generics.prior.properties <- c(
+#   "dont eat people", "have beautiful feathers",
+#   "have wings", "are red",
+#   "carry malaria", "lay eggs", 
+#   "are female", "have spots"
+#   )
+
+for (p in levels(d.gen.endorse.priors$Property)) {
   priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
@@
 
-    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
-      group_by(Iteration, Chain) %>%
-      spread(Parameter, value) %>%
-      rowwise() %>%
-      mutate(
-        a = g*d,
-        b = (1-g)*d,
-        isPresent = rbinom(1, 1, prob = phi),
-        prevalence = ifelse(isPresent == 1, 
-                           rbeta(n = 1, 
-                                 shape1 = a,
-                                 shape2 = b),
-                           rbeta(n = 1,
-                                 shape1 = 1,
-                                 shape2 = 100)),
-        Property = p, src = "Structured"
-      ) %>% ungroup()
-
+        # m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
+    #   group_by(Iteration, Chain) %>%
+    #   spread(Parameter, value) %>%
+    #   rowwise() %>%
+    #   mutate(
+    #     a = g*d,
+    #     b = (1-g)*d,
+    #     isPresent = rbinom(1, 1, prob = phi),
+    #     prevalence = ifelse(isPresent == 1, 
+    #                        rbeta(n = 1, 
+    #                              shape1 = a,
+    #                              shape2 = b),
+    #                        rbeta(n = 1,
+    #                              shape1 = 1,
+    #                              shape2 = 100)),
+    #     Property = p, src = "Structured"
+    #   ) %>% ungroup()
+    # 
     m.gen.endorse.priors.unstructured <- webppl(
@@
 }
-save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-
-```
-
-```{r generic-endorsement-priors-figure2, eval = F}
-ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
-         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
-       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
-  geom_bar(stat = 'identity', position = position_dodge())+
-  geom_errorbar(position = position_dodge())+
-  coord_flip()+
-  ylab("MAP estimate and 95% HDI of Mixture parameter")
-```
+# save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
+
+```
+
+## Appendix C: Comparison of prior parameters inferred using only prior data and in joint-inference model
+```{r generic-priors-parameters, eval = F}
+m.gen.endorse.priors.posteriorPredictive <- data.frame()
+n_samples <- 20000
+lg = 0
+# example.generics.prior.properties <- c(
+#   "dont eat people", "have beautiful feathers",
+#   "have wings", "are red",
+#   "carry malaria", "lay eggs", 
+#   "are female", "have spots"
+#   )
+
+m.gen.endorse.priors.parameters <- data.frame()
+for (p in levels(d.gen.endorse.priors$Property)) {
+  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence
+
+    m.gen.endorse.priors.structured <- webppl(
+      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+m.gen.endorse.priors.structured.summary <- m.gen.endorse.priors.structured %>%
+  group_by(Parameter) %>%
+  summarize(MAP = estimate_mode(value),
+            cred_upper = hdi_upper(value),
+            cred_lower = hdi_lower(value))
+
+    m.gen.endorse.priors.parameters <- bind_rows(
+      m.gen.endorse.priors.parameters,
+      m.gen.endorse.priors.structured.summary %>%
+        mutate(Property = p)
+      )
+}
+
+# save(m.gen.endorse.priors.parameters, file = '../analysis/generics-priors-posteriorParameters.Rdata')
+```
+
+```{r}
+load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))
+
+m.gen.endorse.joint.prior.parameters <- m.samp %>%
+  filter(type %in% c("prior", "targetPrevalence")) %>%
+  group_by(property, category, type, param) %>%
+  summarize(MAP = estimate_mode(val),
+            cred_upper = hdi_upper(val),
+            cred_lower = hdi_lower(val))
+```
+
+```{r}
+left_join(
+  m.gen.endorse.priors.parameters,
+  m.gen.endorse.joint.prior.parameters %>%
+    filter(type == "prior") %>%
+    rowwise() %>%
+    mutate(Parameter = ifelse(param == "mixture", "phi",
+                              ifelse(category == "mean", "g", "d"))) %>%
+    ungroup() %>% 
+    select(property, Parameter, MAP, cred_upper, cred_lower) %>%
+    rename(Property = property,
+           MAP_joint = MAP,
+           cred_upper_joint = cred_upper,
+           cred_lower_joint = cred_lower)
+) %>%
+  mutate(Parameter = factor(Parameter,
+                            levels = c("phi", "g", "d"),
+                            labels = c(expression(paste("mixture parameter (", phi,")", sep = "")),
+                                       expression(paste("stable component: mean (", gamma,")", sep = "")),
+                                       expression(paste("stable component: concentration (", xi,")", sep = ""))))) %>%
+  ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                 y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
+  geom_point()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+  facet_wrap(~Parameter, scales = 'free', labeller = label_parsed)+
+  xlab("Inferred values with only prevalence data")+
+  ylab("Inferred values in joint-inference model")
+```

### 2018-03-23 paper/case2-habituals.Rmd
tweak notation in hab priors model
edits and comments in case stufy 2

@@
 Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].
-When children describe their lives to other, a surprisingly large amount of the language produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
+When children describe their lives to others, a surprisingly large amount of the language produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
 Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
+\ndg{save that last point for discussion?}
 
 To test the generality of our theory, we use the same computational model and follow the same general experimental structure as in the first case study. 
-We take event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).^[
-  Specifically, for the generalization "Mary smokes", the instances being generalized are *instances of Mary*, and for the instance to have the feature, it means the instance of Mary is one in which she is smoking.
+We take the event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).^[
+  Specifically, for the generalization "Mary smokes", the instances being generalized are *instances of Mary at different times*, and for an instance to have the feature, it means the instance of Mary is one in which she is smoking.
+\ndg{this footnote is confusing}
 ]
@@
 Does prevalence represent the actual, objective frequency in the world or the subjective, predictive belief in the head?
-We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
+We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt.
+2c).
+\ndg{give example of causal force intervening..}
 We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
+\ndg{possibly introduce this question briefly in intro, so readers are expecting it?}
 
@@
 For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
-We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1 .
-In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not.^[
-  In the case of event knowledge about people, we expect there to be several more than just these two possibilities represented in the prior, corresponding to individuals with different traits or demographics.
-  We assume here a simple structure so as to not make the specification of the prior overly complex.
+We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1.
+In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not do the action.^[
+  It is likely that more than just these two possibilities are represented in people's intuitive prior, corresponding to individuals with additional traits or demographics.
+  We assume here a simple two-component structure so as to not make the specification of the prior overly complex.
 ]
 With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
-We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people).
+We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people \ndg{huh?
+stable rate people?}).
 We will assume for simplicity that people who have never done the action before will rarely or never do the action.
@@
 For each event, participants were asked two questions, with different dependent measures. 
-These questions were designed to measure the two central components of the prevalence prior model.
+These questions were designed to measure the two components of the prevalence prior model.
 We anticipated there to be different beliefs about the rates and relative proportions of people depending on whether an actor is male or female, so we asked about both genders separately.
+The two questions were schematically:
 
@@
 Question 1 elicits the proportion of people who have done an action before. 
-We rescale this to be a number between 0 and 1, and assume it was generated from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma, \xi)$. 
+We rescale this to be a number between 0 and 1, and model it as generated from a Beta distribution: $d_{1} \sim \text{Beta}(\gamma, \xi)$. 
 Question 2 elicits the rate with which a person (who has done the action before) does the action.
@@
 
-The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter):
+The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter) \ndg{check fig ref}:
 We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2}(`r  n.items.habituals.prior.modeling`) = `r round(with(rs.habituals.bda.prior.summary.wide, cor(mix_mean, sfreq_mean)),2)`$).
@@
 \ref{eq:S1}) will endorse habitual sentences (e.g., \emph{Sam goes to the movies vs.
-the ballet.}) contingent on the shape of the prior distribution.
+the ballet.}) contingent on these details of the prior distribution.
 
@@
 \phi & \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1}) \nonumber \\ 
-\ln h & \sim \begin{cases}
+\ln p & \sim \begin{cases}
 		\text{Gaussian}(\mu_{Q2}, \sigma_{Q2}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
-				\text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
+				\text{Delta}(p=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
 		\end{cases}
@@
 \textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
+\ndg{describe the motivation and procedure more clearly.
+it sounds a little fishy this way, but actually it's great: we set out to test the predictions of the model by choosing the items predicted to have most variability....}
 For example, relatively high frequencies were chosen (e.g., three times every week vs.
@@
 In an exploratory analysis, we find no differences between endorsements of the habitual of characters with male and female names, and overall, the mean endorsements by gender are strongly correlated $r(`r n.habituals.gendered.analysis`) = `r r.habituals.gendered.analysis`$.
-Endorsements are even more highly correlated for the six events we anticipated differences by referent-gender:  $r(`r n.habituals.gendered.subset.analysis`) = `r r.habituals.gendered.subset.analysis`$
+Endorsements are even more highly correlated for the six events we anticipated differences by referent-gender:  $r(`r n.habituals.gendered.subset.analysis`) = `r r.habituals.gendered.subset.analysis`$.
 This lack of a difference may be because the felicity of habitual sentences depends on a comparison to individuals of both genders (i.e, in minimal contexts such as this, habituals are evaluated with respect to *other people*, not just other men or other women).
@@
 For all analyses, we collapse across gender of the referent character for endorsement judgments.
-Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold endorsement model.
+Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and a fixed-threshold alternative to our uncertain-threshold endorsement model.
 Analyses which use the rate prior distribution $P(p_f)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prior distribution.
@@
 The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because we designed the stimulus set to be critical of a referent-frequency model.
+\ndg{i think it's not so much that we designed the stimuli to be critical, as that we were able to independently manipulate the referent-frequency from the prior, which we couldn't do for generics?}
 <!-- An account purely based on the referent frequency does not explain endorsements in this data set. -->
@@
 
+\ndg{don't you want to report the posterior predictive correlation with data for this model?}
+
 <!-- That is, the best way this model has to deal with the endorsement data is to say there is some arbitrary threshold and a large percentage of deviations are due to noise.  -->
@@
 As shown in Figure \@ref(fig:habituals-endorsement-figure)B, the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
+
+\ndg{this part seems like discussion? also edit for grammar.}
 Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model achieves this. 
-An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is good statement to assert. 
+An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is a good statement to assert. 
 Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas someone who went to the movies 3 times last month more a person who "goes to the movies". 
@@
 We introduce these causal events into our endorsement paradigm to measure their influence on endorsement.
+\ndg{give examples}
 <!-- that either enable or prevent future actions. -->
@@
 2b).
-In addition, we compare to baseline linear model that uses only the *predictive frequency* (no priors) to model endorsement.
+In addition, we compare to a baseline linear model that uses only the *predictive frequency* (no priors) to model endorsement.
 
@@
 The experiment took on average `r round(ave.seconds.hab.pred/60,1)` minutes (*predictive frequency*) and `r round(ave.seconds.hab.pred.endorse / 60)` minutes (*sentence endorsement*).
+\ndg{fix missing (for me) numbers}
 Participants were compensated \$0.40.
@@
 Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2b), in equal proportions.
+\ndg{give examples?}
 
@@
 
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
+Figure \ref{fig:habituals-predictive-figure} (left) \ndg{check all subfig refs -- in many cases you say eg "left" when it shoulld be "a"..} shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given.
 We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r format(r.hab.pred.past.baseline.freq, digits = 3)`$). 
@@
 2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).
+Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} \ndg{fix ref} left; blue and green dots).
 
@@
 To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming our predictions, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
+Confirming that our manipulation worked as intended, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
 $\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
@@
 There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}B; green points).
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
 When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
@@
 `r round(d.hab.predictive.endorsment.preventative.summary[[1,"high"]], 2)`
-]
+].
+Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
 
@@
 We use our formal model to test whether past or predictive frequency matters for endorsement.
-To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p_{fk}$ that the endorsement model (Eq. \ref{eq:S1}) conditions on. 
+To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p_{fk}$ that the endorsement model (Eq. \ref{eq:S1}) aims to convey. 
 The past frequency model is constructed using the past frequency supplied to participants as the referent-prevalence.
@@
 We note that this kind of model is merely a re-description of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization.
+\ndg{this point is unclear.
+maybe save it for general discussion?}
 A theory of the semantics of a generalization must formalize the truth-conditions of the generalization as well as how those truth-conditions relate to endorsement. 
@@
 We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
-Predicted prevalence thus captures the influence of top-down moderators (e.g., intervening causal forces) on endorsement.
+That is, habitual language (and generalization language more generally) is fundementally about conveying people's predictive beliefs, not what has actually happened.
+
 <!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language.

### 2018-03-24 paper/case2-habituals.Rmd
address comments in case 2

@@
 We take the event analogue of prevalence to be the *rate* with which the event occurs (e.g., how often Mary smokes).^[
-  Specifically, for the generalization "Mary smokes", the instances being generalized are *instances of Mary at different times*, and for an instance to have the feature, it means the instance of Mary is one in which she is smoking.
-\ndg{this footnote is confusing}
+  Specifically, for the generalization "Mary smokes", the instances being generalized are *instances of Mary*.
 ]
@@
 Our computational model predicts endorsement rates given a referent prevalence $p$. 
-Does prevalence represent the actual, objective frequency in the world or the subjective, predictive belief in the head?
-We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt.
+Does prevalence represent the actual, objective frequency in the world (e.g., the rate at which a person has smoked cigarettes in the past) or a subjective, predictive belief in the head (e.g., the rate at which a person is expected to smoke in the future)?
+Such a distinction could explain why "Supreme Court Justices have even social security numbers" sounds strange even if nine out of the nine current justices have even social security numbers [@Cohen1999]: Our predictions about the evenness of the *next* justice's social security number are driven by strong prior beliefs that selection for the Supreme Court is uncorrelated from the numerical properties of one's social security number; the current observations are not enough in this case to sway those beliefs.
+<!-- not swayed by these observations due to -->
+We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (e.g., the person buys a pack of cigarettes; Expt.
 2c).
-\ndg{give example of causal force intervening..}
 We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
-\ndg{possibly introduce this question briefly in intro, so readers are expecting it?}
 
@@
 With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
-We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action (as a measure of the mean of stable-rate people \ndg{huh?
-stable rate people?}).
-We will assume for simplicity that people who have never done the action before will rarely or never do the action.
+We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action.
+We will assume for simplicity that people who have never done the action before will probably never do the action.
 
@@
 In total, thirty-one events were used.
-For a full list the stimulus set, see Appendix D.
+For a full list of the stimuli used in Expts. 2a-c, see Appendix D.
 
@@
 \begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
+\item ``How many \{men, women\} have *done action* before?'' \\
 
@@
 
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
+\item ``For a typical \{man, woman\} who has *done action*  before, how frequently does he or she \textsc{do action}?''\\
 
@@
 
-figure.habituals.priors.scatter <- 
-  rs.habituals.bda.posterior.predictive.measurementSpace %>%
+rs.habituals.bda.posterior.predictive.measurementSpace.wide <- rs.habituals.bda.posterior.predictive.measurementSpace %>%
   select(-mean, -ci_lower, -ci_upper, -empirical_mean, -n, -cred_upper, -cred_lower) %>%
-  spread(measurement, MAP) %>%
-  ggplot(.,
+  spread(measurement, MAP)
+
+figure.habituals.priors.scatter <- ggplot(
+  rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
+                    filter(item %in% example.habituals, gender == "female"),
        aes(x = `% people who have done action before`, 
            y = `Frequency of doing action (log scale)`, 
-           color = gender))+
+           color = gender, label = item))+
   scale_color_solarized()+
+  geom_point(data = rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
+                    filter(!(item %in% example.habituals) | gender == "male"),
+             inherit.aes = F, 
+             aes(
+               x = `% people who have done action before`, 
+               y = `Frequency of doing action (log scale)`, color = gender))+
   geom_point()+
+  geom_label_repel(segment.alpha = 1,label.size = 0.25,
+                   force = 10, size = 2, color = 'black')+
+
   #geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
-  geom_label_repel(data = . %>%
-                    filter(item %in% example.habituals, gender == "female"), 
-                  inherit.aes =F, segment.alpha = 1,label.size = 0.25,
-                  segment.size = 5,
-                  aes(x = `% people who have done action before`, 
-           y = `Frequency of doing action (log scale)`, 
-           label = item), force = 1, size = 2)+
   coord_fixed(1/7.5)+
@@
 2a).
-A: Mixture-model posterior predictions in comparison to the empirical mean responses for the two prior elicitation questions.
-Items cover the full spectrum of possible parameter values.
+A: Parameters of prevalence priors for the 31 items in Expt.
+2.
+Items cover much of the range of possible parameter values.
 B: Reconstructed prevalence priors.
 In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
-Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have NEVER done action before} scatter-plot), reflecting the rarity of the event across people.", cache = F}
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before} scatter-plot), reflecting the (inverse) popularity of the event across people.", cache = F}
 cowplot::plot_grid(
@@
 
-The priors elicited cover a range of possible parameter values as intended (Figure \@ref(fig:priorScatter), scatter) \ndg{check fig ref}:
+The priors elicited cover a range of possible parameter values as intended (Figure\ \@ref(fig:habituals-prior-figure)A):
 We observe a correlation in our items between the mean \% of Americans who have \textsc{done action} before (Question 1) and the mean log-frequency of action (Question 2) ($r_{1,2}(`r  n.items.habituals.prior.modeling`) = `r round(with(rs.habituals.bda.prior.summary.wide, cor(mix_mean, sfreq_mean)),2)`$).
@@
 
-Figure \@ref(fig:habituals-prior-figure) (right) shows example reconstructed priors.
+Figure\ \@ref(fig:habituals-prior-figure)B shows example reconstructed priors.
 In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties.
@@
                                           "MAP_h", "prediction")
-
 ```
@@
 
-Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
-Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
-\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
-\ndg{describe the motivation and procedure more clearly.
-it sounds a little fishy this way, but actually it's great: we set out to test the predictions of the model by choosing the items predicted to have most variability....}
-For example, relatively high frequencies were chosen (e.g., three times every week vs.
-2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs.
-2 years).
-In total, `r nrow(md.hab.long %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.
+Each event from Expt. 2a was then paired with between two to four frequencies, for which the habitual statement would be evaluated. 
+Frequencies were presented in terms of a character performing the action "three times in the past *time interval*".
+We chose to always have the character perform the action three times to provide a strong test of a baseline hypothesis that the habitual encodes the person has done the action multiple times in the past.
+
+Different time intervals were chosen for each event in order to maximize the variability of responses within each item. 
+Specifically, we used the endorsement model to generate predictions based on the prior elicitation data (Expt.
+2a) for each item, and chose between two and four time intervals across which maximal variability was predicted.
+For example, relatively high frequencies were chosen (e.g., time intervals of weeks and months) for items expected to occur rather often (e.g., *runs*); for an item was expected to occur infrequently (e.g., *climbs mountains*), lower frequencies were chosen (e.g., time intervals of years or longer) because the model predicted that much of the variability in endorsement would occur in that range.
+In total, `r nrow(m.hab.endorse.rsa %>% distinct(habitual, time_period))` unique items were created by pairing frequencies with events. 
+The full list of items and frequencies can be found in Appendix D.
 
@@
 
-On each trial, participants were presented with a \emph{past frequency statement} for a given event of the form: "In the past M \{weeks, months, years\}, \textsc{person} \textsc{did x} 3 times".
+On each trial, participants were presented with a *past frequency statement* for a given event of the form: "In the past \{week, 2 weeks, month, 5 years, ...\}, *Person did X* 3 times".
 For example, "In the past month, Bill smoked cigarettes 3 times".
-Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "\textsc{person does x}" (e.g.,"Bill smokes cigarettes.").
+Participants were asked whether they agreed or disagreed with the corresponding habitual sentence: "Person does X" (e.g.,"Bill smokes cigarettes.").
 Participants completed thirty-seven trials, which were composed of the thirty-one items from the prior elicitation task randomly paired with either a male or female character name.
@@
 When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance), reflecting the fact that these statements are not altogether *false* even though the action is done very rarely.
+In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree that people who wore a watch or wore a bra 3 times in the past week \emph{wears a watch} or \emph{wears a bra} habitually).
+In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the habitual utterances), reflecting the fact that these statements are not altogether *false* even though the action may be done very rarely.
 
@@
 Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and a fixed-threshold alternative to our uncertain-threshold endorsement model.
-Analyses which use the rate prior distribution $P(p_f)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prior distribution.
-To model the uncertainty in the input measurements, we bootstrap the data for the regression models and we construct joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-threshold).
+Analyses which use the prevalence prior distribution $P(p)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prevalence prior distribution.
+Parallel to our analysis of generics model, we model uncertainty in the input measurements by bootstrapping the data for the regression models and constructing joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-threshold).
 
@@
 runs".
-Some actions done with a relative high rate (e.g., 3 times in a month) do not receive full endorsement (e.g., *smokes cigarettes*; Figure \@ref(fig:habituals-endorsement-figure) A).
+Some actions done with a relative high rate (e.g., 3 times in a month) do not receive full endorsement (e.g., *smokes cigarettes*; Figure \@ref(fig:habituals-endorsement-figure)A).
 Overall, the referent-frequency (in log-scale) predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$).
 In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$).
-The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because we designed the stimulus set to be critical of a referent-frequency model.
-\ndg{i think it's not so much that we designed the stimuli to be critical, as that we were able to independently manipulate the referent-frequency from the prior, which we couldn't do for generics?}
+The prevalence baseline does appreciably worse in this data set in comparison to the generics data set (Case Study 1) because we were able to independently manipulate the referent-frequency separate from the prevalence priors, which we could not do for generics about familiar categories.
+
+<!-- designed the stimulus set to be critical of a referent-frequency model.
+\ndg{i think it's not so much that we designed the stimuli to be critical, as that we were able to independently manipulate the referent-frequency from the prior, which we couldn't do for generics?} -->
 <!-- An account purely based on the referent frequency does not explain endorsements in this data set. -->
@@
 
-In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)).
+In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)A x-axis).
 This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus is relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
@@
 This model is able to explain more of the variance in endorsements ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq.distinct`$; MSE=$`r mse.habituls.regression.freq.distinct`$). 
-It can differentiate events done with the same frequency (e.g., *writing poems* vs. *novels*, 3 times in the past 5 years), and increase endorsement of the more rare action (*novels*). 
-Still, this model fails to capture fine-grained details in endorsement.
-For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual $`r movies.year.data`$, while this regression model predicts quite lower judgments $`r movies.year.regression.distinct`$.
-On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants $`r banjo.2years.data`$.
-Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case $`r banjo.2years.regression.distinct`$.
+It can differentiate events done with the same frequency (e.g., *writing poems* vs. *novels*, 3 times in the past 5 years) by increasing endorsement of the more rare action (*novels*). 
+Still, this model fails to capture fine-grained differences in endorsement.
+For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual ($`r movies.year.data`$), while this regression model predicts quite lower judgments ($`r movies.year.regression.distinct`$).
+On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants ($`r banjo.2years.data`$).
+Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case ($`r banjo.2years.regression.distinct`$).
 
@@
 We next examine an information-theoretic endorsement model based on a fixed-threshold semantics.
-A fixed-threshold model commits the habitual to conveying that a person *does the action with some rate*, and the threshold on rates is common to all actions.
+A fixed-threshold model commits the habitual to conveying literally that a person *does the action with some non-zero frequency*, and the threshold on frequency is the same for all actions.
 As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data (for more details on model implementation, see Appendix C).
-We assume the referent-prevalence $p_{fk}$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
+We assume the referent-prevalence $p$ being conveyed by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in the past year).
 Additionally, to account for statements that would be literally false under this model (frequencies that fall below the fixed threshold), we include an additional noise parameter, as we did for the fixed-threshold model in Case Study 1.
@@
 
-The data analytic model infers that a low threshold is likely: the inferred threshold in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
+The data analytic model infers that a low threshold is likely: the Maximum A-Posteriori threshold and 95\% credible interval in units of number of times per year is `r round(exp(fixed.threshold.hab.posterior[[1,"MAP"]]), 2)` [`r round(exp(fixed.threshold.hab.posterior[[1,"cred_lower"]]), 2)`,
 `r round(exp(fixed.threshold.hab.posterior[[1,"cred_upper"]]), 2)`].
@@
 As a result, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
-The fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model.
-
-A fixed-threshold utterance updates the interpreter model's beliefs differentially depending on the item.
-For instance, it's highly unlikely that a random person *climbs mountains* with any non-zero rate; thus this model fully endorses "Mary climbs mountains" even with low-frequency (Figure \@ref(fig:habituals-endorsement-figure) A).
-However, the model doesn't differentiate doing the same action with different frequencies.
-It is equally true that a person does an action *with some frequency* for any frequency greater than zero, analogous to how "some Ks F" is equally true if 20\% or 50\% of Ks F.
-
-Finally, the data-analytic model infers that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
+The fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model (Figure\ \@ref(fig:habituals-endorsement-figure)B).
+
+The fixed-threshold habitual updates the interpreter model's prior beliefs differentially depending on the item.
+For instance, because of the distinctiveness of *climbs mountains*, the fixed-threshold endorsement model fully endorses the habitual ("Mary climbs mountains") even at a low frequency (Figure \@ref(fig:habituals-endorsement-figure)A).
+However, the model cannot differentiate among different frequencies of doing the same action.
+It is equally true that a person does an action with non-zero frequency for any frequency greater than zero, analogous to how "Some dogs are friendly" is equally true whether 20\% or 50\% or 80\% of dogs are friendly.
+
+Overall, the fixed-threshold model is able to predict only a fraction of the variance in human endorsements ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.fixed`$; MSE=$`r mse.habituals.rsa.fixed`$).
+The model does this by inferring that `r 100*round(fixed.noise.hab.posterior[[1,"MAP"]], 2)`% [`r 100*round(fixed.noise.hab.posterior[[1,"cred_lower"]], 2)`,
 `r 100*round(fixed.noise.hab.posterior[[1,"cred_upper"]], 2)`] of the data is noise and that the speaker optimality parameter is `r round(hab.fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(hab.fixed.threshold.s1opt[[1,"cred_lower"]], 2)`,
 `r round(hab.fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
-
-\ndg{don't you want to report the posterior predictive correlation with data for this model?}
 
@@
 Again, this model has two fewer parameters than the fixed-threshold model (no fixed-threshold parameter and no extrinsic noise process).
-As shown in Figure \@ref(fig:habituals-endorsement-figure)B, the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
-
-\ndg{this part seems like discussion? also edit for grammar.}
-Figure \@ref(fig:habituals-endorsement-figure)C provides insight into how the model achieves this. 
-An interpreter who hears a generalization interprets it relative the prior distribution over frequencies, which results in different points at which the generalization is a good statement to assert. 
-Someone who smoked cigarettes 3 times last month is not fully someone who "smokes cigarettes", whereas someone who went to the movies 3 times last month more a person who "goes to the movies". 
-Only the uncertain-threshold model is able to draw this fine distinction.
+As shown in Figure\ \@ref(fig:habituals-endorsement-figure)B, the uncertain-threshold endorsement model does a good job of accounting for the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituals.rsa.uncertain`$; MSE=$`r mse.habituals.rsa.uncertain`$), including actions done on the time scale of years or more  ($r^2(`r r2.hab.rsa.infrequent.n`) = `r r2.habituals.rsa.uncertain.infrequent`$; MSE=$`r mse.habituals.rsa.uncertain.infrequent`$).
 
@@
 The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in question.
+
+Figure\ \@ref(fig:habituals-endorsement-figure)C provides insight into how the uncertain-threshold model is able to match human judgments. 
+The endorsement model simulates how an interpreter would under the habitual sentence.
+A habitual is interpreted relative the prior distribution over frequencies, and the comparison between the frequency implied by the habitual vs.
+staying silent results in different frequencies at which the generalization is good to assert.
+Climbing mountains three times in the past year is good evidence that you *climb mountains*; going for a hike three times in the past year is less convincing that you *hike*; and if you went for a run three times in the past year, you not a person who *runs*.
+Only the uncertain-threshold model is able to draw these subtle distinctions.
 
@@
 On one hand, speakers can only be certain about what has happened in the past.
-On the other hand, it is important for speakers to be able to convey their predictions of what will be the case in the future.
-
-People can change their behavior abruptly due to a variety of decisions and outside events.
-We introduce these causal events into our endorsement paradigm to measure their influence on endorsement.
-\ndg{give examples}
-<!-- that either enable or prevent future actions. -->
+On the other hand, it is important for speakers to be able to convey their predictions of what they believe will be the case in the future.
+
+People can change their behavior abruptly due to a variety outside events (e.g., developing an allergy) or intend to do an action without actually completing it (e.g., by making a resolution). 
+We introduce these causal events into our experimental paradigm to measure their influence on endorsement.
 To provide the appropriate model-based analysis, participants in one condition make a prediction about the future (*predictive frequency*).
@@
 <!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
-We then compare two uncertain-thresholds models: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt.
+We then compare two uncertain-thresholds models: one which uses participants' ratings of *predictive frequency* as the referent prevalence and one which uses the *past frequency* (as was done for Expt.
 2b).
@@
 We recruited `r n.subj.hab.pred + n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
-`r n.subj.hab.pred` were assigned to the *predictive frequency* condition and `r n.subj.hab.pred.endorse` were assigned to the *sentence endorsement* condition.
-The experiment took on average `r round(ave.seconds.hab.pred/60,1)` minutes (*predictive frequency*) and `r round(ave.seconds.hab.pred.endorse / 60)` minutes (*sentence endorsement*).
-\ndg{fix missing (for me) numbers}
+`r n.subj.hab.pred` were assigned to the *predictive frequency* condition and `r n.subj.hab.pred.endorse` were assigned to the *habitual endorsement* condition.
+The experiment took on average `r round(ave.seconds.hab.pred$total/60,1)` minutes (*predictive frequency*) and `r round(ave.seconds.hab.pred.endorse$total / 60)` minutes (*habitual endorsement*).
 Participants were compensated \$0.40.
@@
 We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
-See Appendix D for a full list of the enabling and preventative information.
+See Appendix D for a full list of the items and frequencies used, as well as the enabling and preventative information.
 
@@
 Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2b), in equal proportions.
-\ndg{give examples?}
-
-In the *predictive frequency* condition, participants were asked ``In the next \textsc{time window}, how many times do you think \textsc{person} does \textsc{action}?'', where the \textsc{time window} was the same as given in the \emph{past frequency statement}.
-In the *sentence endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
+See Table 1 for example trials.
+
+```{r table-habitual-predictive-items, results="asis"}
+hab.pred.item.table <- xtable::xtable(data.frame(
+  Habitual = c("John smokes cigarettes.", "Tina volunteers at soup kitchens."),
+  Baseline = c("In the past month, John smoked cigarettes 3 times.",
+               "In the past five years, Tina volunteered for soup kitchens 3 times."),
+  Preventative = c("In the past month, John smoked cigarettes 3 times. Yesterday, John quit smoking cigarettes.",
+
+               "In the past five years, Tina volunteered for soup kitchens 3 times. Yesterday, Tina grew disillusioned with the soup kitchen system and wants nothing to do with it anymore."),
+  Enabling = c("In the past month, John smoked cigarettes 3 times. Yesterday, John wanted a smoke and bought a pack of cigarettes.",
+
+               "In the past five years, Tina volunteered for soup kitchens 3 times. Yesterday, Tina researched a new soup kitchen in the area and is going to volunteer with them.")
+), align=c('p{1in}',' |p{1in}|', 'p{1.75in}| ','p{1.75in}|','p{1.75in} |'),
+  caption = "Example stimuli used in Expt. 2c.")
+bold <- function(x){
+paste0('{\\bfseries ', x, '}') }
+
+print(hab.pred.item.table,
+    type="latex", 
+      comment = F,
+       #table.placement = "h", 
+      #tabular.environment = "longtable",
+      hline.after=-1:nrow(hab.pred.item.table),
+      size="\\fontsize{9pt}{10pt}\\selectfont", 
+      include.rownames=FALSE,
+      sanitize.colnames.function = bold
+      #add.to.row = addtorow
+      )
+```
+
+In the *predictive frequency* condition, participants were asked ``In the next *time interval*, how many times do you think *person does action*?'', where the *time interval* was the same as given in the past frequency statement.
+In the *habitual endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
 
@@
 
-Figure \ref{fig:habituals-predictive-figure} (left) \ndg{check all subfig refs -- in many cases you say eg "left" when it shoulld be "a"..} shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given.
+Figure \ref{fig:habituals-predictive-figure}B shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
 We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r format(r.hab.pred.past.baseline.freq, digits = 3)`$). 
@@
 2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
-Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} \ndg{fix ref} left; blue and green dots).
+Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-figure}B, yellow and purple dots).
 
@@
 
-#### Sentence endorsement
+#### Habitual endorsement
 
@@
 Figure \ref{fig:habituals-predictive-figure}C shows the resulting model predictions for the past frequency and the predictive frequency endorsement models. 
-Participants' judgments of the habitual statements was indeed influenced by the causal manipulations *in the way predicted* by the endorsement model that uses the predictive frequency as the object of communication ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
+Participants' judgments of the habitual statements was indeed influenced by the causal manipulations in the way predicted by the endorsement model that uses the predictive frequency as the referent prevalence ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.predictive`$; MSE = $`r mse.habituals.rsa.predictive`$).
 The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
@@
 
-A regression model that takes into the frequency and the *distinctiveness* of the action does a reasonable job at explaining the variance in this data.
-We note that this kind of model is merely a re-description of the data (and thus, the behavior of the uncertain threshold model), and does not represent a theory of the semantics of a generalization.
-\ndg{this point is unclear.
-maybe save it for general discussion?}
-A theory of the semantics of a generalization must formalize the truth-conditions of the generalization as well as how those truth-conditions relate to endorsement. 
-This is precisely what our information-theoretic models do (both fixed- and uncertain-threshold).
-
 <!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->

### 2018-03-24 paper/comgen-paper.Rmd
add table of habituals items to appendix
address comments in case 2

@@
 Understanding the language of generalization is a project with far-reaching implications.
-The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], making meaning from experience [@Orvell2017].
+The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], and making meaning from experience [@Orvell2017].
 It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context suggests its centrality to the growth of conceptual knowledge [@Gelman2004].
@@
 
+We note that regressions model that takes into account the referent prevalence and the distinctiveness of the feature do reasonable jobs at explaining some of the variance in the endorsement data.
+This kind of model, however, is merely a re-description of the data and does not represent a bonafide theory of the semantics of a generalization. 
+<!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
+A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement. 
+That is precisely what our information-theoretic model does.
+
 <!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
@@
 ```
+
+\newpage
+
+```{r child = 'appendix-habitualsItems.Rmd'}
+```

### 2018-03-24 paper/case3-causals.Rmd
minor edits to case 3, check formatting

@@
 
-Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or plants grow tall). 
+Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or make plants grow tall). 
 Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the property (e.g., a naturally occurring herb causing animals to be sleepy).
-The two cover stories can be seen in Table 1.
+The two cover stories can be seen in Table 2.
 
-Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure \@ref(figure-causals)B. 
-In two of the conditions, participants saw results that came from the same underlying distribution.
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the "common strong" condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the "common weak" condition).
+Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure 10B.
+In two of the conditions, participants saw results that came from a single underlying distribution.
+In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the *common strong* condition).
+In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the *common weak* condition).
 <!-- The results of the previous experiments were described verbally  -->
@@
 -->
-The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0s or 1s or 2s), and others that either had strong or weak effects as above.
-These are the "rare strong" and "rare weak" conditions.
+The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0, 1, or 2 successes), and others that either had strong or weak effects as above.
+These are the *rare strong* and *rare weak* conditions.
 <!-- These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect. -->
 
-\begin{table}[]
-\centering
-\label{tab:causalMaterials}
-\resizebox{\textwidth}{!}{
-\begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|}
-\hline
-                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline
-Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
+<!-- \begin{table}[] -->
+<!-- \centering -->
+<!-- \label{tab:causalMaterials} -->
+<!-- \resizebox{\textwidth}{!}{ -->
+<!-- \begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|} -->
+<!-- \hline -->
+<!--                    & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline -->
+<!-- Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
 Your team runs experiments trying to make feps grow tall with different fertilizers.
@@
 Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-\\ \hline
-Evidence statement & Your team gave fertilizer B to 100 different feps.
+\\ \hline -->
+<!-- Evidence statement & Your team gave fertilizer B to 100 different feps.
 Of those 100 treated, 2 feps grew tall.
@@
 Of those 100 treated, 98 cheebas were made sleepy.
-\\   \hline
-\end{tabular}
-}
-\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3}
-\end{table}
+\\   \hline                                                                                                                             -->
+<!-- \end{tabular} -->
+<!-- } -->
+<!-- \caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3} -->
+<!-- \end{table} -->
+
+```{r causalMaterials, results="asis"}
+causalMaterials <- xtable::xtable(data.frame(
+  "." = c("Cover story", "Evidence statement"),
+  Plants = c("On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
+Your team runs experiments trying to make feps grow tall with different fertilizers.",
+               "Your team gave fertilizer B to 100 different feps. Of those 100 treated, 2 feps grew tall."),
+  Animals = c("On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy.
+Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.",
+               "Your team gave herb C to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.")
+), align=c('p{1in}',' |p{1.75in}|', 'p{2in}|','p{2in} |'),
+  caption = "Cover stories and example evidence statements for the two sets of materials used in Expt. 3")
+bold <- function(x){
+paste0('{\\bfseries ', x, '}') }
+
+print(causalMaterials,
+    type="latex", 
+      comment = F,
+      hline.after=-1:nrow(causalMaterials),
+      size="\\fontsize{9pt}{10pt}\\selectfont", 
+      include.rownames=FALSE,
+      sanitize.colnames.function = bold
+      )
+```
 
@@
 
-Each participant saw only one cover story with one distribution of previous experiments (i.e., the experiment was a single trial).
+The experiment was a single trial: Each participant saw only one cover story with one distribution of previous experiments.
 <!-- In the first part of the trial, participants learned about different substances' ability to produce an effect ("previous experimental results"). -->
@@
 Experiment results appear one at a time (upon a click), and are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas.
-Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment).
-We described the results of these individual experiments using *token-level* causal language (e.g., "98 cheebas were made sleepy") to suggest that actual causation occurred in these cases.
+Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment; Figure \@ref(fig:causalExpt)A).
+We described the results of these individual experiments using token-level causal language (e.g., "98 cheebas were made sleepy") to imply that actual causation occurred in these cases.
 
-Participants see the results of eleven "experiments", though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
+Participants see the results of eleven experiments, though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
 (These lost results would be found in the *causal endorsement* task, Expt. 3b).
-After participants viewed the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing.
+After participants viewed the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing (Figure \@ref(fig:causalExpt)C).
 
 Upon clicking the continue button, the table of experiment results is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments.
-Participants were given 5 slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).
+Participants were asked to predict the results of the next 5 experiments (Figure \@ref(fig:causalExpt)D).
+Participants were given five slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).
 
 After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigated (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
-This attention check served to confirm that participants had encoded some part of both relevant aspects of the experiment (the domain and the frequencies).
+This attention check served to confirm that participants had encoded both relevant aspects of the experiment (the domain and the frequencies).
 
@@
 `r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
-The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure \ \@ref(fig:figure-causals).
+The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals).
 These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
@@
 
-The materials were the same as in Experiment 3a,
-The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)).
+The materials were the same as in Expt. 3a.
+The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)A-C).
 Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found.
 The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
-Participants saw 1 of 2 reported frequencies: 20\% or 70\% (randomized between-subjects).
-Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy"). 
-Participants responded by either clicking "Yes" or "No". 
+Participants saw one of two reported frequencies: 20\% or 70\% (randomized between-subjects).
+Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy") by either clicking "Yes" or "No" (Figure \@ref(fig:causalExpt)E). 
 After responding, participants completed the same attention check as Expt. 3a.
@@
 As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure \@ref(fig:causals-endorsement).
+These are shown for the different experimentally-manipulated priors and frequencies in Figure\ \@ref(fig:figure-causals)A.
 
 As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
-When many other causes produced the effect very reliably (*common deterministic* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure \ref{fig:figure-causals-endorsement; top, blue).
+When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure\ \@ref(fig:figure-causals)A).
 By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
@@
 In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
-In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(p_{fk})$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.
+In addition to further demonstrating the generality of this theory, these experiments show that the prevalence prior $P(p)$ is causally related to endorsements of generalizations in language.
+To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category.
 
 In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall. 
-We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it's plausible that there are herbs that only weakly make animals sleepy and it's also plausible that there are herbs that almost deterministically make animals sleepy).
+We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it is plausible that there are herbs that only weakly make animals sleepy and it is also plausible that there are herbs that almost deterministically make animals sleepy).
 These two features of the domains make them particularly amenable to manipulation.
-That is, people's abstract theories about these domains are flexible enough to permit such manipulations.
+<!-- Inituive theories about these domains are flexible enough to permit such manipulations. -->
 
-It's likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
+It is likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
 If this were happening in our domains, we would expect this to show up in the results of Expt.
@@
 ]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analogous to our "deterministic" priors conditions. 
-Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our "rare" prior conditions.
-Our theory would predict in these cases that differences in endorsement would be attributable to differences in the prevalence prior distribution (here: the belief distribution over causal power).
+For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analogous to our *strong* priors conditions. 
+Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our *rare* prior conditions.
+Our theory would predict that differences in endorsement in these cases would be mediated by differences in the corresponding prevalence prior distributions.

### 2018-03-26 analysis/case1-generics.Rmd
Finish scatterplot in appendix for parameter inference given different data sources

@@
          sentence = gsub('lyme', 'Lyme', sentence)) %>%
-  group_by(sentence) %>%
+  group_by(sentence, Property, Category) %>%
   summarize(k = sum(response), n = n()) %>%
@@
 ## Appendix C: Comparison of prior parameters inferred using only prior data and in joint-inference model
+
+### Prevalence prior parameters
+
 ```{r generic-priors-parameters, eval = F}
@@
 lg = 0
-# example.generics.prior.properties <- c(
-#   "dont eat people", "have beautiful feathers",
-#   "have wings", "are red",
-#   "carry malaria", "lay eggs", 
-#   "are female", "have spots"
-#   )
 
@@
 ```{r}
-left_join(
+load( file = '../analysis/generics-priors-posteriorParameters.Rdata')
+m.gen.endorse.priors.parameters <- left_join(
   m.gen.endorse.priors.parameters,
@@
            cred_lower_joint = cred_lower)
-) %>%
-  mutate(Parameter = factor(Parameter,
-                            levels = c("phi", "g", "d"),
-                            labels = c(expression(paste("mixture parameter (", phi,")", sep = "")),
-                                       expression(paste("stable component: mean (", gamma,")", sep = "")),
-                                       expression(paste("stable component: concentration (", xi,")", sep = ""))))) %>%
-  ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
+)
+
+ggplot(m.gen.endorse.priors.parameters, aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
@@
 ```
+
+### Referent prevalence parameters
+
+```{r generic-refprev-parameters, eval = F}
+m.gen.endorse.refprev.posteriorPredictive <- data.frame()
+n_samples <- 20000
+lg = 0
+
+m.gen.endorse.refprev.parameters <- data.frame()
+
+for (p in levels(d.gen.endorse.priors$Property)) {
+  categories <- d.gen.endorse.bayes %>% filter(Property == p) %>% distinct(Category)
+
+  for (k in categories$Category) {
+
+    priorData <- filter(d.gen.endorse.priors, Property == p, Category == k)$prevalence
+
+    m.gen.refprev <- webppl(
+      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
+                                 data = priorData, data_var = "data",
+                                 model_var = "model",
+                                 chains = 2,
+                                 cores = 2,
+                                 inference_opts =
+                                   list(method = "MCMC",
+                                        samples = n_samples,
+                                        burn = n_samples / 2,
+                                        lag = lg,
+                                        verbose = T))
+
+  m.gen.refprev.summary <- m.gen.refprev %>%
+    group_by(Parameter) %>%
+    summarize(MAP = estimate_mode(value),
+              cred_upper = hdi_upper(value),
+              cred_lower = hdi_lower(value))
+
+    m.gen.endorse.refprev.parameters <- bind_rows(
+      m.gen.endorse.refprev.parameters,
+      m.gen.refprev.summary %>%
+        mutate(Property = p, Category = k)
+      )
+    print(k)
+  }
+  print(p)
+}
+
+ #save(m.gen.endorse.refprev.parameters, file = '../analysis/generics-refprev-posteriorParameters.Rdata')
+```
+
+```{r}
+load(file = '../analysis/generics-refprev-posteriorParameters.Rdata')
+
+m.gen.endorse.refprev.parameters <- left_join(
+  m.gen.endorse.refprev.parameters,
+  m.gen.endorse.joint.prior.parameters %>%
+    filter(type == "targetPrevalence") %>%
+    rowwise() %>%
+    mutate(Parameter = ifelse(param == "mean", "g", "d")) %>%
+    ungroup() %>% 
+    select(property, category, Parameter, MAP, cred_upper, cred_lower) %>%
+    rename(Property = property,
+           Category = category,
+           MAP_joint = MAP,
+           cred_upper_joint = cred_upper,
+           cred_lower_joint = cred_lower)
+)
+
+ggplot(m.gen.endorse.refprev.parameters, aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                 y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
+  geom_point()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+  facet_wrap(~Parameter, scales = 'free', labeller = label_parsed)+
+  xlab("Inferred parameters using only prevalence data")+
+  ylab("Inferred parameters in joint-inference model")
+```
+
+```{r}
+save(m.gen.endorse.priors.parameters, m.gen.endorse.refprev.parameters,
+     file = "../paper/cached_results/case1_prevParamDistortion.RData")
+```

### 2018-03-26 paper/appendix-bda.Rmd
Finish scatterplot in appendix for parameter inference given different data sources

@@
 
-```{r genericsModelDiagram, fig.cap="Pseudo-graphical model corresponding to the fully Bayesian data analysis of the endorsement model.
+```{r genericsModelDiagram, fig.cap="Quasi-graphical model corresponding to the fully Bayesian data analysis of the endorsement model.
 The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
@@
 In addition to examining the posterior predictive distribution on endorsement judgments (presented in main text), we examined the marginal posteriors on parameters of the prevalence priors and referent-prevalence.
-These marginal distributions are important to examine to confirm that they have not changed significantly from the parameters inferred from their private data sources in isolation.
+These marginal distributions are important to confirm that they have not changed substantially from the parameters inferred from their primary data sources in isolation.
 For example, when modeling the referent-prevalence data in isolation, the model infers that roughly 65\% of robins lay eggs, as that is what participants on average produce in the prevalence elicitation task.^[
@@
 ]
-The question for this joint inference model is whether or not it still believes that roughly 50\% of robins lay eggs after being forced to jointly predict endorsements for "Robins lay eggs".
-For example, a linear regression model based on referent-prevalence (of the kind presented in the main text) incorporated into this Bayesian analysis model will end up predicting high endorsement for "Robins lay eggs", but only does so by distorting the referent-prevalence data (inferring that 100\% of robins lay eggs); thus, the linear model sacrifices its goodness-of-fit to the referent-prevalence data in order to increase its goodness-of-fit to the endorsement data.
-Such a distortion would show manifest as a difference between the inferred parameters given only the referent-prevalence data and given the full joint model (all data sources modeled  simultaneously).
+If the joint inference model (which models all data sources---referent prevalence, prevalence prior, and generic endorsement---simultaneously) infers something substantially different about referent-prevalence than a model of referent prevalence in isolation, that could into question the inferences we as scientists derive from the joint inference model.
+For example, incorporating a linear regression model (of the kinds presented as alterantive models in the main text) into this Bayesian joint-inference analysis model produces posterior predictions that match the generic endorsement data surprisingly well (e.g., that model predicts "Robins lay eggs" is true).
+Such a model is only able to do this by distorting the referent-prevalence data, inferring that 100\% of robins lay eggs; thus, the linear model in this joint-inference analysis framework sacrifices its goodness-of-fit to the referent-prevalence data in order to increase its goodness-of-fit to the endorsement data.
+^[
+  This distortion effect is why we accout for measurement uncertainty in the linear models by bootstrapping the data that forms their predictors.
+]
+Such a distortion manifests as a difference between the inferred parameters given only the referent-prevalence data and given the full joint model (all data sources simultaneously).
 
-We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only their data, suggesting that the modeling all three data sources together does not come at the cost of modeling any one of them accurately.
+```{r prevParamDistortion}
+load("cached_results/case1_prevParamDistortion.RData") #m.gen.endorse.priors.parameters, m.gen.endorse.refprev.parameters
+
+fig.distortion.prevpriors <- ggplot(
+  m.gen.endorse.priors.parameters %>%
+    mutate(Parameter = factor(Parameter,
+                            levels = c("phi", "g", "d"),
+                            labels = c(expression(paste("mixture parameter (", phi,")", sep = "")),
+                                       expression(atop("stable component",
+                                                  paste("mean (", gamma,")", sep = ""))),
+                                       expression(atop("stable component", 
+                                                  paste("concentration (", xi,")", sep = "")))))), 
+  aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                 y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
+  geom_point()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+  facet_wrap(~Parameter, scales = 'free', labeller = label_parsed)+
+  xlab("Prevalence prior model parameters")+
+  ylab("Joint-inference model parameters")
+
+fig.distortion.refprev <-ggplot(
+  m.gen.endorse.refprev.parameters %>%
+    mutate(Parameter = factor(Parameter,
+                            levels = c("g", "d"),
+                            labels = c(expression(atop("referent prevalence", 
+                                                       paste(" mean (", gamma,")", sep = ""))),
+                                       expression(atop("referent prevalence",
+                                                  paste("concentration (", xi,")", sep = "")))))), 
+  aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
+                 y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
+  geom_point()+
+  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
+  facet_wrap(~Parameter, scales = 'free', labeller = label_parsed)+
+  xlab("Referent prevalence model parameters")+
+  ylab("Joint-inference model parameters")
+```
+
+```{r distortion, fig.width=10, fig.asp = 0.29, out.width = "100%", fig.align = "center", cache = F, fig.cap="No evidence for parameter distortion caused by a joint-inference model.
+X-axis denotes Maximum A-Posteriori (MAP) estimates inferred using only a single data source (A: Prevalence prior data.
+B: Referent prevalence data).
+Y-axis denotes MAP estimates inferred using the joint-inference model which models all data sources simultaneously.
+Distortions would manifest by systematic deviations from the y=x line."}
+prow <- plot_grid( 
+  fig.distortion.prevpriors + theme(plot.margin = unit(c(6,6,0,6), "pt")) #+ ggtitle("prevalence priors")
+,
+  fig.distortion.refprev + theme(axis.title.y = element_blank(),
+                                 plot.margin = unit(c(6,0,0,0), "pt")),# + theme(legend.position="none"),
+   align = 'h',
+   labels = c("A", "B"),
+   #hjust = -1,
+   nrow = 1,
+  rel_widths = c(1, 0.7),
+  rel_heights = c(1, 0.7)
+  )
+
+prow
+```
+
+To investigate this distortion effect in the parameters, we compare the values inferred for the parameters governing the prevalence priors and referent prevalence variables before and after the joint-inference model sees the generic endorsement data.
+Specifically, we infer the parameters for prevalence priors and referent prevalence by constructing single models of these tasks and compare the inferred values to those that result from the joint-inference model.
+The inferred parameters for these two models are shown in Figure\ \@ref(fig:distortion).
+We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only the referent-prevalence and prevalence prior data, respectively.
+This results confirms that modeling all three data sources simultaneously does not distort some data sources (e.g., referent prevalence) in order to provide good fits for others (e.g., generic endorsement).

### 2018-03-26 paper/case1-generics.Rmd
Finish scatterplot in appendix for parameter inference given different data sources

@@
 We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
-  This assumption is similar in spirit that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
+  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
 ]
@@
 
+```{r distortionEffect}
+load("cached_results/case1_prevParamDistortion.RData") #m.gen.endorse.priors.parameters, m.gen.endorse.refprev.parameters
+
+r2.prevprior.distortion <- compute_r2(
+  m.gen.endorse.priors.parameters, 
+  "MAP", "MAP_joint", sigfigs = 4
+)
+
+r2.refprev.distortion <- compute_r2(
+  m.gen.endorse.refprev.parameters, 
+  "MAP", "MAP_joint", sigfigs = 4
+)
+```
+
 We first examine the posterior predictive distribution on the prevalence prior and referent prevalence data to ensure that the joint-inference model does not distort these parameters at the service of predicting the endorsement data (e.g., such a distortion could manifest by the joint-inference model inferring that 100% of mosquitos carry malaria in order to predict that "Mosquitos carry malaria" is a good utterance).
 This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters (e.g., that not all mosquitos carry malaria).
-Importantly, the model recapitulates the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt.
-1b).
-\ndg{point to a figure or give some stat to back up thi claim?}
+Importantly, the model recapitulates the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model ($r_{\text{prevalence prior parameters}}^2(`r length(m.gen.endorse.refprev.parameters[,"Parameter"])`) = `r r2.refprev.distortion`$; $r_{\text{referent prevalence parameters}}^2(`r length(m.gen.endorse.priors.parameters[,"Parameter"])`) = `r r2.prevprior.distortion`$; see Appendix D, Figure 14).
 This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).

### 2018-03-27 paper/case1-generics.Rmd
address lays eggs 3 component phenomenon

@@
 The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
-One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
-The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
-Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
-]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
-A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. \ndg{but we don't use one because...?}
+One property that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature *lays eggs*.
+The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%; a simple two-component mixture model has no way to account for such a tri-modal distribution.^[
+  The third mode at 100\% is not attributable to categories for which all members could be female (e.g., chickens).
+Instead, it appears that some participants are responding that 100\% of several different kinds of birds (e.g., robins) lay eggs.
+This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction* and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
+];
+A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. 
+Using a three-component model for this distribution does not change the resulting model predictions and we maintain the simpler two-component mixture for uniformity.
 

### 2018-03-27 paper/case1-generics.Rmd
add footnote about robins lay eggs in model results

@@
 We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
-Figure\ \@ref(fig:generics-endorsement-figure) (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
+Figure\ \@ref(fig:generics-endorsement-figure)B (top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
 Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither. 
@@
 
-As we see in Figure\ \@ref(fig:generics-endorsement-figure)(top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-To gain some intuition for why the model makes the predictions that it does, we can examine the relevant model components that give rise to these predictions (Figure \ref{fig:generics-endorsement-figure} bottom row).
+As we see in Figure\ \@ref(fig:generics-endorsement-figure)B (top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+To gain some intuition for why the model makes the predictions that it does, we can examine the relevant model components that give rise to these predictions (Figure \ref{fig:generics-endorsement-figure}C).
 Recall that the prevalence prior (grey distribution) is also the interpreter model's posterior upon hearing the null, or silent, utterance, and that the endorsement model decides whether to produce the generic utterance or remain silent given some referent prevalence (blue distribution).
@@
 The endorsement model decides if the generic utterance conveys information that would bring the interpreter's distribution more in line with the endorsement model's referent prevalence. 
-The model rates "Robins lay eggs" as a good utterance because the prevalence posterior implied by the generalization is similar to the referent prevalence. 
+The model rates "Robins lay eggs" as a good utterance because the prevalence posterior implied by the generalization is similar to the referent prevalence.^[
+  We again note that modeling the prevalence prior for *lays eggs* as a two-component mixture model, as we have assumed for all the prevalence priors, results in a distribution with a peak at 0\% and around 70\%.
+  This 70\% peak is a result of smoothing the underlying bimodal distribution at 50\% and 100\%. 
+  The same smoothing occurs for the referent-prevalence, as participants report as often that either 50\% or 100\% of robins lay eggs.
+  If instead, the prevalence prior is modeled as a tri-modal distribution and the referent-prevalence modeled as bi-modal (mainintaing the structure at 50\% and 100\%), the resulting interpretation (i.e., prevalance posterior given generalization) is that either 50\% or 100\% lay eggs.
+  This is precisely the bimodal referent-prevalence distribution for *robins lay eggs*, and so the endorsement model still predicts high endorsement. 
+  The fact that domain restriction enters in both the prevalence prior and the referent prevalence measurements, in effect, cancels one another out and has no effect on the resulting endorsement model predictions.
+]
 The prevalence posterior for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad, endorsement around 0.5.

### 2018-03-27 paper/case2-habituals.Rmd
minor edits to new aspects of discussion section

@@
 <!-- Events are a broad class of entities.  -->
-In our second case study, we focus on habituals about people's behaviors that take the form: \textsc{singular noun phrase} $+$ \textsc{present tense simple verb phrase} (e.g., "Mary smokes cigarettes").
+In our second case study, we focus on habituals about people's behaviors that take the form: *singular noun phrase* $+$ *present tense simple verb phrase* (e.g., "Mary smokes cigarettes"). 
 Learning about the behaviors of others is useful because they tell us about what that person is like more generally [e.g., @Repacholi1997; @Seiver2013].

### 2018-03-27 paper/comgen-paper.Rmd
minor edits to new aspects of discussion section

@@
 We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalizing by probability.
-Being able to precisely articulate the conditions under which a sentence is true lets you describe how an agent should update its beliefs based on that sentence. 
-Thus, in addition to providing a quantitative understanding of the phenomena, formalizing the language of generalizations opens up the possibility of building models that learn abstract, generalizable knowledge from language.
+By precisely articulating the conditions under which generalizations are true or false, we are able to describe how an agent should update its beliefs based on that sentence. 
+Thus, in addition to providing a quantitative understanding of the phenomena of the language of generalization, formalizing this language opens up the possibility of building models that learn abstract, generalizable knowledge from language.
 
@@
 
-We note that regressions model that takes into account the referent prevalence and the distinctiveness of the feature do reasonable jobs at explaining some of the variance in the endorsement data.
-This kind of model, however, is merely a re-description of the data and does not represent a bonafide theory of the semantics of a generalization. 
+We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
+These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data.
 <!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
@@
 Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
-Rather than have beliefs about prevalence *per se*, listeners are likely to have conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013] that gives rise to beliefs about prevalence.
-That is, the prevalence prior is a statistical layer that provides the glue between conceptual knowledge and natural language semantics.
-The truth conditions of generalizations depend only on prevalence.
+Beliefs about prevalence are often the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
+Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
+The prevalence prior is a common statistical layer that provides the glue between conceptual knowledge and natural language semantics.
+The truth conditions of generalizations depend only on prevalence, but prevalence depends upon conceptual knowledge.
 
@@
 
-There is nothing in our theory that rules out shared background knowledge presupposing beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
-Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
+<!-- There is nothing in our theory that rules out shared background knowledge presupposing beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
+-->
 Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
@@
 Actual conceptual knowledge against which generalizations are interpreted is most likely far-richer than simply a two-component mixture-model.
-We note, however, that a richer model of the prior is not necessary to account for the context-sensitive endorsement patterns we observe in our empirical data.
+We note, however, that a richer model of the prior was not necessary, at this point, to account for the context-sensitive endorsement patterns we observe in our empirical data.
 
@@
 This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-We distinguish this construct from other uses of *prevalence* in the literature, namely the usage as synonymous with frequency.
+We distinguish our construct from other uses of *prevalence* in the literature, often taken to be synonymous with observed frequency.
 <!-- the distinction that what is communicated is probability not frequency. -->
@@
 
-<!-- <!-- Furthermore, how conceptual accounts of the language of generalizations should extend beyond category generalizations (i.e., generics) is less clear.  --> -->
 <!-- The alternative approach to generics is to try to rescue the notion the number of members of the category with the property (e.g., the number of robins that do indeed lay eggs). -->
 
-To our knowledge, the present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
+The present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
 A number of other theories of genericity have been proposed in the formal semantics  literature.
@@
 For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this provides a more unifying view of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
+We believe this separation provides a more unifying view of the phenomena of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
+
+In addition, our model provides a path towards unifying conceptual and statistical approaches to generics. 
+Our semantic representation is inherently statistical: Natural language semantics only gets to operate on prevalence. 
+At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.
 
@@
 
-Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999 's theory of generics as a frequency adverb (e.g., "generally").
+Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999's theory of generics as a frequency adverb (e.g., "generally").
 Cohen treats generics as comprising two qualitatively different types: *relative* and *absolute* generics.

### 2018-03-30 paper/case2-habituals.Rmd
remove comment about trait language

@@
 When children describe their lives to others, a surprisingly large amount of the language produced concerns the actions of people close to them [e.g., "My brother works part-time at the restaurant"; @McGuire1986].
-Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
-\ndg{save that last point for discussion?}
+<!-- Habitual language about people may be a more conservative form of *trait language* (e.g., "Mary is a smoker.") and convey that behaviors are relatively enduring [@Gelman1999; @Gelman2004].
+\ndg{save that last point for discussion?} -->
 

### 2018-04-07 paper/case3-causals.Rmd
edits to case study 3

@@
 The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analogous to how "John smokes" relates to  "John smoked yesterday". 
+\ndg{"my grandpa's..." is itself a generic...
+is there a simple example to start with?
+e.g.
+"fire causes smoke" generalizes "this fire caused this smoke"?
+Also, somewhere (probably GD) we should discuss how many sentences have two ore more "dimensions of generalization".}
 We explore this hypothesis in our third case study: causal language or *causals* (e.g., "A causes B").
@@
 In this paper, we posit that prevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
-In this last set of experiments, we explicitly test the relationship between the prevalence priors and endorsements of generalizations about causes.
-Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.
+In this last set of experiments, we explicitly test the relationship between the prevalence priors and endorsements of generalizations about causes by manipulating the priors.
+
+<!--Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.-->
 
@@
 
-In this experiment, we manipulate and measure participants' background knowledge in order to check whether or not manipulation of participants' background knowledge was successful. 
-Experiment 3b (*causal endorsement*) will then follow a mostly-identical experimental procedure.
+In this experiment, we manipulate participants' background knowledge, measuring these beliefs in order to check whether the manipulation was successful. 
+Experiment 3b (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.
 
@@
 
-After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigated (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
+After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
 This attention check served to confirm that participants had encoded both relevant aspects of the experiment (the domain and the frequencies).
@@
 The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals).
+\ndg{its unclear in figure caption whether those are emprical, predicted, or bda priors.}
 These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
+\ndg{it'd be good to have some kid of stats here.
+maybe just show that empirical prealence distributions differ between conditions.
+also say how this matters: as before geeralization model predicts differences in endorsement for same target prevalence depending on priors.}
 We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
@@
 Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy") by either clicking "Yes" or "No" (Figure \@ref(fig:causalExpt)E). 
+This allows us to test whether endorsement of a causal sentence for a given actual frequency is affected by the causal priors induced by our manipulation.
 After responding, participants completed the same attention check as Expt. 3a.
@@
 
-As predicted by our model, endorsements for a causal statement were sensitive to the background distribution of other causes and the causal power of the target cause.
+\ndg{i'm not sure 10A is the best way to show this data, since the lines highlight the differences between causal powers (within conditions), while we care most about differences between conditions.}
+
+As predicted by our model, endorsements for a causal statement were sensitive to the causal power of the target cause and, critically, to the background distribution of other causes. 
 When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure\ \@ref(fig:figure-causals)A).
@@
 The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects again with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
+Our model predicted these effects with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
+
+\ndg{is it worth saying anything about the fact that the effect is even a bit bigger than predicted by the model?}
 
@@
 
-In our third case study, we applied our same model to generalizations about causal events.
+In our third case study, we applied our model to generalizations about causal events, without any changes.
 In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
@@
 To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category.
+\ndg{fix last sentence.
+is this about geeralization?
+didn't our last experiments show this?
+is it about causation?
+huh?}
 
 In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall.
+\ndg{which reminds me: need to say something above (3a) about (no) differences between the cover stories?}
 We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it is plausible that there are herbs that only weakly make animals sleepy and it is also plausible that there are herbs that almost deterministically make animals sleepy).

### 2018-04-10 paper/case3-causals.Rmd
refresh casauls figure, refactor causals code to analysis script, save cached results

@@
 # Case Study 3: Causal Language
+
+```{r load_causals_results}
+load(file = "cached_results/case3_endorsementDataModel.RData")
+#md.cas.fullmodel.endorsement,
+#      md.caus.endorse, 
+#      n.subj.cas.endorse, 
+#      ave.minutes.cas.endorse,
+#      n.subj.cas.endorse.failed,
+
+load(file = "cached_results/case3_priorRatings.RData")
+# d.cas.priors, 
+   #  n.subj.cas,
+  #   n.subj.cas.failed,
+ #    ave.minutes.cas,
+```
 
@@
 Language about causal relationships manifests in generalization.
-The utterance "Drinking moonshine makes you go blind" relates to "My grandpa's drinking moonshine made him go blind" in a way analogous to how "John smokes" relates to  "John smoked yesterday". 
-\ndg{"my grandpa's..." is itself a generic...
+The utterance "Fire causes smoke" relates to "This fire caused this smoke" in a way analogous to how "John runs" relates to  "John ran yesterday". 
+<!-- \ndg{"my grandpa's..." is itself a generic...
 is there a simple example to start with?
@@
 "fire causes smoke" generalizes "this fire caused this smoke"?
-Also, somewhere (probably GD) we should discuss how many sentences have two ore more "dimensions of generalization".}
+Also, somewhere (probably GD) we should discuss how many sentences have two ore more "dimensions of generalization".} -->
 We explore this hypothesis in our third case study: causal language or *causals* (e.g., "A causes B").
@@
 
-```{r}
-genericEndorsementPriorModelHelpers <- '
-var eps = 0.01;//Number.EPSILON;
-var log = function(x){ return Math.log(x) }
-var exp = function(x){ return Math.exp(x) }
-
-var avoidEndPoints = function(x){
-  x == 0 ? eps : 
-  x == 1 ? 1 - eps : 
-  x
-}
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var preprocessedResponses = map(function(d){
-  return avoidEndPoints(d / 100)
-}, data)
-'
-
-structuredPriorModel <- '
-var model = function(){
-  var phi = uniformDrift({a:0, b: 1, width:0.2});
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  var transientComponent = Beta({a:1, b:100})
-  mapData({data: preprocessedResponses}, function(d){
-    factor( log(
-      phi * exp(stableComponent.score(d)) +
-      (1 - phi) * exp(transientComponent.score(d))
-    ))
-  })
-  return {g, d, phi}
-}
-'
-
-unstructuredPriorModel <- '
-var model = function(){
-  var g = uniformDrift({a:0, b: 1, width:0.2});
-  var d = uniformDrift({a:0, b: 100, width:5});
-  var stableParams = betaShape({g, d})
-  var stableComponent = Beta(stableParams)
-  mapData({data: preprocessedResponses}, function(d){
-    factor(stableComponent.score(d))
-  })
-  return {g, d}
-}
-'
-genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
-```
-
-```{r rsaHelpers}
-rsaHelpers <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var round = function(x){
-  return Math.round(x*1000)/1000
-}
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
-// var thetaBins = [
-//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- // ]
-var thetaPrior = Infer({model: function(){
- return uniformDraw(thetaBins)
-}});
-
-var bins = map(round, _.range(0.01, 0.99, 0.01))
-
-// var bins = [
-  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-// ];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-
-var mixture = data.prior.mix[0];
-var priorParams = data.prior.params[0];
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-'
-```
-
-```{r rsaInterpretationModels}
-no.utterance.model <- '
-var noUtteranceInterpreter = function() {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    return { state }
- }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-'
-
-fixed.threshold.model <- '
-var fixedThresholdInterpreter = function(threshold) {
-  Infer({model: function(){
-  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-  var state = sample(statePrior)
-  condition( state > threshold)
-    return {
-      state: state
-  }
- // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
- }, method: "enumerate"})}
-'
-
-uncertain.threshold.model <- '
-var uncertainThresholdInterpreter = function() {
-  Infer({model: function(){
-   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
-    factor( Math.log(state) )
-    return {
-      state: state, 
-  }
-  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
-'
-
-```
-
-```{r simulationCalls}
-fixed.threshold.calls <- '
-_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
-'
-no.utterance.call <- ' 
-  noUtteranceInterpreter()
-'
-uncertain.threshold.call <- '
-  uncertainThresholdInterpreter()
-'
-```
-
 ### Method
-
-```{r causal-priors-data}
-d.cas.priors <- read.csv(paste(project.path,
-                           "data/causals/priors/causals-8-prior-trials.csv",
-                           sep= ""))
-
-d.cas.priors.catch <- read.csv(paste(project.path,
-                           "data/causals/priors/causals-8-prior-catch_trials.csv",
-                           sep= ""))
-
-# some participants were mischaracterized as failing the catch trial because they put something of the form "0/100" or "herb F: 19" 
-mischaracterized <- c( 24, 48, 62, 94, 106, 110, 111, 112, 113, 116, 125, 132, 145, 155, 158)
-
-d.cas.priors <- left_join(d.cas.priors, d.cas.priors.catch) %>%
-  mutate(pass_numeric = ifelse(workerid %in% mischaracterized, 1, pass_numeric),
-         passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-n.subj.cas <- length(unique(d.cas.priors$workerid))
-
-n.subj.cas.failed <- length(unique(filter(d.cas.priors, passBoth == 0)$workerid))
-
-d.cas.priors <- d.cas.priors %>% filter(passBoth == 1)
-
-ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-```
-
-```{r causal-priors-runModel, cache = T}
-causal.distributions <- levels(factor(d.cas.priors$distribution))
-p <- causal.distributions[1]
-m.cas.marginal.prevalence <- data.frame()
-m.cas.endorse.priors.summary <- data.frame()
-
-for (p in causal.distributions){
-  priorData <- 100*filter(d.cas.priors, distribution == p)$response
-
-  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
-         model_var = "model", inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T))
-
-  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
-    spread(Parameter, value) %>%
-    rowwise() %>%
-    mutate(
-      a = g * d,
-      b = (1 - g) * d,
-      stable = rbinom(n = 1, size = 1, prob = phi),
-      prevalence = ifelse(stable == 1, 
-                             rbeta(n = 1, shape1 = a, shape2 = b),
-                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
-      distribution = p
-    )
-  )
-
-  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
-                                            m.cas.endorse.priors %>% 
-                                              mutate(distribution = p) %>%
-                                              group_by(distribution, Parameter) %>%
-                                              summarize(MAP = estimate_mode(value),
-                                                        cred_upper = hdi_upper(value),
-                                                        cred_lower = hdi_lower(value))
-                                              )
-}
-
-```
 
@@
 
-Participants were then shown "previous experimental results", which followed one of four distributions, shown in Figure 10B.
-In two of the conditions, participants saw results that came from a single underlying distribution.
+Participants were then shown "previous experimental results", which followed one of four distributions.
+In two of the conditions, participants saw results that came from a single underlying distribution (*common* conditions).
 In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the *common strong* condition).
@@
 
-```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
-3 (stimuli) and priors reconstructed from participants' responses (model).
-", fig.width = 8, fig.height = 3, eval = F}
-sample.dists <- bind_rows(
-  data.frame(
-    dist = "rare weak",
-    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common weak",
-    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
-  ),
-  data.frame(
-    dist = "rare deterministic",
-    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
-          rbeta(n = 7000, shape1 = 2, shape2 = 50)
-          )
-  ),
-  data.frame(
-    dist = "common deterministic",
-    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
-  )
-) %>%
-    mutate(Distribution = factor(dist, 
-                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
-         labels = c("Common Deterministic", "Rare Deterministic",
-                    "Common Weak", "Rare Weak")))
-
-figure.causals.priors <- bind_rows(
-  sample.dists %>%
-    mutate(src = "stimuli") %>%
-    select(-dist),
-  m.cas.marginal.prevalence %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
-    mutate(Distribution = factor(distribution, 
-                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           labels = c("Common Deterministic", "Rare Deterministic",
-                      "Common Weak", "Rare Weak"))) %>%
-    select(Distribution, prevalence) %>%
-    mutate(src = 'model') %>%
-    rename(x = prevalence)
-) %>%
-  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
-  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
-                ))+ 
-  geom_density( adjust = 1.3, 
-               size = 1.2,
-               aes( y = ..scaled..))+ #
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
-  scale_fill_solarized()+scale_color_solarized()+
-  #scale_color_manual(values = c("#636363", "#d7191c"))+
-  scale_alpha_manual(values = c(0.1, 0.4))+
-  scale_linetype_manual(values = c(2, 1))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
-  guides(fill = F, color = F)+
-  theme(legend.position = 'bottom', legend.direction = 'horizontal')
-```
-
-```{r s1-model}
-s1.model <- '
-var probability = function(Dist, x) {
-    return Math.exp(Dist.score(x));
-}
-var targetUtterance = "generic";
-
-var utterancePrior = Infer({model: function(){
-  return uniformDraw([targetUtterance,"silence"])
-}});
-
-var betaShape = function(params){
-  return {
-      a: params.g * params.d,
-      b : (1-params.g) * params.d
-  }
-}
-
-var thetaPrior = Infer({model: function(){
- return uniformDraw([
-   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
- ])}
-});
-
-var bins = [
-  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
-  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
-];
-
-var meaning = function(utt,state, theta) {
-  return utt=="generic"? state > theta :
-         utt=="generic is false"? state<=theta :
-         utt=="silence"? true :
-         utt=="some"? state>0.01:
-         utt=="most"? state> 0.5:
-         utt=="all"? state >= 0.99:
-         true
-}
-var alpha = 2;
-var mixture = data.prior[0].phi;
-var priorParams = betaShape(data.prior[0]);
-
-var statePrior = Infer({model: function(){
-  var component = flip(mixture);
-  return component ?
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta(priorParams), b) + Number.EPSILON
-      }, bins )
-    }) :
-    categorical({
-      vs: bins,
-      ps: map(function(b) {
-        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
-      }, bins )
-    })
-}});
-
-var listener0 = cache(function(utterance) {
-  Infer({model: function(){
-    var state = sample(statePrior)
-    var theta = utterance == "generic" ? sample(thetaPrior) : -99
-    condition(meaning(utterance, state, theta))
-    return state
- }})}, 10000)
-
-var speaker1 = function(state) {
-  Infer({model: function(){
-    var utterance = sample(utterancePrior);
-    var listener_posterior = listener0(utterance);
-    factor(alpha * listener_posterior.score(state))
-    return utterance
-  }})
-}
-
-probability(speaker1(data.state[0]), "generic")
-'
-```
-
-```{r causal-endorsement-predictions, cache = T, eval = F}
-causal.priorParams <- m.cas.endorse.priors.summary %>%
-    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
-           Parameter != 'marginalPrevalence') %>%
-  select(distribution, Parameter, MAP) %>%
-  spread(Parameter, MAP)
-experimental.frequencies <- c(0.2, 0.7)
-causal.endorsement.predictions <- data.frame()
-for (p in causal.priorParams$distribution){
-  for (s in experimental.frequencies){
-
-    inputData = list(prior = filter(causal.priorParams, distribution == p), 
-                     state = s)
-
-    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")
-
-    causal.endorsement.predictions <- bind_rows(
-      causal.endorsement.predictions,
-      data.frame(state = s, distribution = p, prob = s1.rs)
-    )
-  }
-  print(p)
-}
-```
-
 <!-- #### Materials  -->
@@
 `r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
-The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals).
-\ndg{its unclear in figure caption whether those are emprical, predicted, or bda priors.}
-These distributions nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
-\ndg{it'd be good to have some kid of stats here.
+The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals)A.
+<!-- \ndg{its unclear in figure caption whether those are emprical, predicted, or bda priors.} -->
+As is visually apparent, the empirical prevalence distributions differ between conditions and nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition.
+This diversity is important because the model of generalizations predicts differences in endorsement---for the same referent prevalence---depending on these priors.
+<!-- \ndg{it'd be good to have some kid of stats here.
 maybe just show that empirical prealence distributions differ between conditions.
-also say how this matters: as before geeralization model predicts differences in endorsement for same target prevalence depending on priors.}
-We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected.
-
-```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 3a)."}
-d.cas.priors %>%
-  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
-      mutate(Distribution = factor(distribution, 
-                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
-         labels = c("Rare Deterministic",
-                    "Common Weak", "Rare Weak"))) %>% 
-ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
-  geom_density( adjust = 0.8, alpha =0.8, 
-               size = 1.2,
-               aes( y = ..scaled..))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
-  ylab("Scaled Prior Probability")+
-  xlab("Target probability")+
-  facet_wrap(~Distribution, scales = 'free')+
-  guides(fill = F, color = F)
-```
+also say how this matters: as before geeralization model predicts differences in endorsement for same target prevalence depending on priors.} -->
+<!-- We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected. -->
 
@@
 ### Method
-
-```{r causal-endorsement-data}
-d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-20-catch_trials.csv", sep = ""))
-
-d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
-                                       "data/causals/endorsement/",
-                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )
-
-d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)
-
-d.caus.endorse.catch <- d.caus.endorse.catch %>% 
-  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
-
-d.caus.endorse.20 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-20-trials.csv", sep = ""))
-
-d.caus.endorse.70 <- read.csv(paste(project.path, 
-                                "data/causals/endorsement/",
-                                "causals-8-70-trials.csv", sep = "")) %>%
-  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))
-
-d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)
-
-n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
-ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)
-
-n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)
-
-d.caus.endorse.summary <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1) %>%
-  group_by(distribution, frequency) %>%
-  summarize(k = sum(response), n = n()) %>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         low  = qbeta(.025, a, b),
-         high = qbeta(.975, a, b),
-         MAP_h = (a-1)/(a+b-2),
-         mean = a / (a + b))
-```
-
-```{r tests?}
-d.caus.endorse.passed <- left_join(
-  d.caus.endorse, 
-  d.caus.endorse.catch %>% select(workerid, passBoth)
-  ) %>%
-  filter(passBoth == 1)
-
-# str(d.caus.endorse.passed)
-# 
-# summary(glmer(response ~ frequency* across * within + (1 | story), family = 'binomial', data = d.caus.endorse.passed %>%
-#   separate(distribution, into =c("across", "within") ) %>%
-#     mutate(frequency = factor(frequency))))
-
-#str(d.caus.endorse.passed)  
-```
 
@@
 
-```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}
-
-ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
-                        group = distribution))+
-  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
-  theme(axis.text.x = element_text(angle = 0))+
-  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
-  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
-  scale_fill_solarized()+
-  xlab("Target frequency")+
-  ylab("Proportion Causal Endorsement")
-```
-
-```{r causals-fullmodel}
-n_chains <- 2
-n_samples <- 100000
-burn <- n_samples / 2
-lg <- 5
-i <- 1
-
-model_prefix <- "pilot-results-causals-jointModel-S1-"
-
-m.cas.samp <- data.frame()
-for (i in seq(1, n_chains)){
-  mi <- read_csv(paste(project.path,  "models/causals/results/", 
-                    model_prefix, "smntcs_causal-",
-                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
-}
-
-# n_chains <- 1
-# n_samples <- 1000
-# burn <- n_samples
-# lg <- 5
-# i <- 1
-# m.hab.fixed.samp <- data.frame()
-# for (i in seq(1, n_chains)){
-#   mi <- fread(paste(project.path,  "models/habituals/results/", 
-#                     model_prefix, "smtncs_some-",
-#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
-#   m.samp.i <- mi %>% mutate(chain = i)
-#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
-# }
-
-# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
-#   filter(type == 'predictive') %>%
-#   rename(habitual = B, time_period = D, binned_freq = E) %>%
-#   group_by(habitual, time_period, binned_freq) %>%
-#   summarize(MAP = estimate_mode(val),
-#             cred_upper = hdi_upper(val),
-#             cred_lower = hdi_lower(val))
-
-m.cas.fullmodel.endorsement <- m.cas.samp %>%
-  filter(type == 'predictive') %>%
-  group_by(dist, frequency) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-```
-
-```{r causal-model-insets, fig.width = 4, fig.height = 3.5, cache = T}
-m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
-  filter(type == "prior") %>%
-  rename(variable = item, parameter = roundedFreq) %>%
-  group_by(dist, variable, parameter) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-# use MAP estimates to generate L(h | causal) & L(h | silence) predictions
-
-m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
-  ungroup() %>%
-  select(dist, variable, parameter, MAP) %>%
-  mutate(param = paste(variable, parameter, sep = "_")) %>%
-  select(-variable, -parameter) %>%
-  spread(param, MAP) %>%
-  rename(mix = mixture_NA, 
-         stable_mean = stableFreq_mean, 
-         stable_concentration = stableFreq_sampleSize) %>%
-  mutate( a = stable_mean * stable_concentration, 
-          b = (1 - stable_mean) * stable_concentration)
-
-cas.listener.predictions <- data.frame()
-
-for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
- priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
- inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
-                                                   b = priorParams[["b"]]),
-                               mix = priorParams[["mix"]]), 
-                  utt = "generic")
- l0.rs <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
-  l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
- l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
- cas.listener.predictions <- bind_rows(
-   cas.listener.predictions, 
-      l0.rs.prior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Prior"),
-    l0.rs.posterior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Posterior")
-   )
-}
-
-#inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
-inset.color.order <- c("#859900","#d33682","#dc322f", "#268bd2")
-
-causals.endorsement.insets <- cas.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, 
-                              levels = c("state_Prior","state_Posterior"),
-                            labels = c("Prevalence prior (Expt. 3a)",
-                                       "Interpreter model posterior")),
-    Distribution = factor(distribution, 
-                               levels = c("rare_weak",  "common_weak", "rare_deterministic", "common_deterministic"),
-         labels = c("Weak, Rare", "Weak, Common", "Strong, Rare", "Strong, Common"))) %>%
-  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-  facet_wrap(~Distribution, nrow = 2)+
-  scale_fill_manual(values =inset.color.order )+
-  scale_color_manual(values = inset.color.order)+
-  geom_vline(xintercept = 0.2, lty = 3)+
-  geom_vline(xintercept = 0.7, lty = 3)+
-  scale_alpha_manual(values = c(0.8, 0.1))+
-  scale_linetype_manual(values = c(1, 2))+
-  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  xlab("Prevalence") +
-  ylab("Scaled probability density")+
-  theme(legend.position = "bottom", 
-        legend.direction = 'vertical',
-        legend.title = element_blank(),
-        plot.margin = unit(c(16,6,6,6), "pt"))+
-  guides(fill = F, color = F, alpha = F)
-
-#causals.endorsement.insets
-```
-
 ```{r}
-md.caus.endorse <- left_join(
-  m.cas.fullmodel.endorsement,
-    d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution)
-)
 
@@
 
+```{r figure-causals-priors}
+
+fig.causals.priors.data <- d.cas.priors %>%
+    select(distribution, response) %>%
+    rename(prevalence = response) %>%
+    mutate(distribution = factor(distribution, 
+           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
+           labels = c("Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))) %>%
+ggplot(.,
+       aes( x = prevalence , fill = distribution))+
+  geom_histogram(aes(
+    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
+    ),
+    bins = 20, color = 'black') + 
+    scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
+
+  #geom_bar(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
+  #geom_density(size = 0.4, aes( y = ..scaled.. ))+
+  #scale_fill_solarized()+
+  #scale_linetype_manual(values = c(2, 1))+
+  facet_wrap(~distribution, scales = 'free', nrow = 2)+
+  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  guides(fill = F)+
+  ylab("Proportion of responses")+
+  xlab("Prevalence rating")
+```
+
 ```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
-figure.causals.endorsement <- bind_rows(
-  m.cas.fullmodel.endorsement %>%
-    mutate(src = "model"),
-  d.caus.endorse.summary %>%
-    select(distribution, frequency, MAP_h, low, high) %>%
-    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
-    mutate(src = 'data')
-) %>%
-  ungroup() %>%
+figure.causals.endorsement <- md.cas.fullmodel.endorsement %>%
   mutate(
@@
            labels = c(
-                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))
-    ) %>%
-  ggplot(., aes( x = frequency, y = MAP, ymin = cred_lower, ymax = cred_upper, 
-                 color = dist, #linetype = dist, 
-                 shape = dist,
-                        group = dist#, 
+                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common")),
+    frequency = factor(frequency, 
+                       levels = c(20, 70),
+                       labels = c("Referent prevalence = 0.2",
+                                  "Referent prevalence = 0.7")
+    )) %>%
+  ggplot(., aes( x = src, y = MAP, ymin = cred_lower, ymax = cred_upper, 
+                 fill = dist #linetype = dist, 
+                 #shape = dist,
+                #        group = dist#, 
                  #alpha = src
                  ))+
-  #geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
-  geom_linerange(position = position_dodge(8), alpha = 1, alpha=0.8)+
-  geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
-  geom_point(position = position_dodge(8), size = 2.25)+
+  geom_bar(stat='identity', position = position_dodge(0.9), width = 0.9, color = 'black')+
+  geom_errorbar(position = position_dodge(0.9), width = 0.3,alpha = 0.8)+
+  #geom_linerange(position = position_dodge(), alpha=0.8)+
+  #geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
+  #geom_point(position = position_dodge(8), size = 2.25)+
   #theme(axis.text.x = element_text(angle = 90))+
@@
   scale_alpha_manual(values = c(1, 0.3))+
-  scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
+  #scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
   #scale_fill_solarized()+
-  scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
-  xlab("Referent prevalence")+
+  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
+  xlab("")+
   ylab("Causal Endorsement")+
-  facet_grid(.~src)+
+  facet_grid(.~frequency)+
   #coord_flip()+
-  coord_fixed(ratio = 90)+
+  #coord_fixed(ratio = 90)+
   #guides(fill = F)+
   guides(
-    shape=guide_legend(title="Background distribution"),
-    color=guide_legend(title="Background distribution")
+    #shape=guide_legend(title="Background distribution"),
+    fill=guide_legend(title="Background distribution")
     )+
   theme(
-    plot.margin = unit(c(0,6,0,6), "pt")
+    #plot.margin = unit(c(0,6,0,6), "pt")
     #legend.position = 'bottom', 
@@
 
-```{r figure-causals, fig.width=9, fig.height=4, cache = F, fig.cap="Endorsing generalizations about causes.
-A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies.
-B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors.
-Vertical lines denote referent-prevalence levels for the causal endorsement task.
-Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt.
-3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}
-
+```{r figure-causals, fig.width=9, cache = F, fig.asp = 0.4, fig.cap="Endorsing generalizations about causes.
+A: Empirical prevalence prior distributions elicited following prior manipulation cover story (Expt.
+3a).
+B: Endorsement model predictions (left) and human elicited endorsements (right) for four manipulated prevalence prior distributions and two referent prevalence levels."}
 prow <- plot_grid( 
+  fig.causals.priors.data,# + theme(legend.position="none"),
   figure.causals.endorsement + theme(legend.position="none"),
-  causals.endorsement.insets,# + theme(legend.position="none"),
-   align = 'h',
+   align = 'v',
    labels = c("A", "B"),
@@
    nrow = 1,
-  rel_widths = c(1, 0.7),
-  rel_heights = c(1, 0.7)
+  rel_widths = c(0.8, 1)
+  #rel_heights = c(1, 1)
   )
@@
 As in our other analyses of endorsement responses, we computed the Bayesian Maximum A-Posteriori (MAP) estimate and 95\% highest probability density interval of the true population probability of endorsing the statement, assuming a uniform prior.
-These are shown for the different experimentally-manipulated priors and frequencies in Figure\ \@ref(fig:figure-causals)A.
+These are shown for the different experimentally-manipulated priors and referent prevalences in Figure\ \@ref(fig:figure-causals)B.
 

### 2018-04-10 paper/comgen-paper.Rmd
add a note

@@
 In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "My grandpa drank moonshine and it made him blind") can be described in generalization (e.g., "Drinking moonshine makes you go blind").
+Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "This fire caused that smoke") can be described in generalization (e.g., "Fire causes smoke").
 
@@
 
+\mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)}
+
 It is remarkable that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
+Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
 We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalizing by probability.
@@
 
-As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types: "Robins lay eggs" (categories), "Sally smokes" (events), "Herb X makes animals sleepy" (causes).
+As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types: "Robins lay eggs" (categories), "Sally smokes" (events), "This herb makes zorbs sleepy" (causes).
 Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).

### 2018-04-13 paper/coverletter.tex
tweaks to cover letter

@@
 This paper explores the linguistic means by which generalizations are communicated.  
-We present a Bayesian model of endorsing generalizations and show that it predicts context-sensitive human judgments with high quantitative accuracy across diverse experimental contexts.
+We present a Bayesian model of understanding generalizations and show that it predicts context-sensitive human endorsement judgments with high quantitative accuracy across diverse experimental contexts.
 The theory suggests that the language of generalization can be understood in terms of a simple semantic theory that operates over beliefs, represented as probability.
@@
 Understanding how the world works requires learning generalizations. 
-The kinds of observations that would facilitate such learning may be rare, however (e.g., figuring out that lightning strikes tall objects) or costly (e.g., learning that certain plants are poisonous).
+The kinds of observations that would facilitate such learning, however, may be rare (e.g., figuring out that lightning strikes tall objects) or costly (e.g., learning that certain plants are poisonous).
 We do not need to need taste every plant to figure out which ones are poisonous, however.
@@
 The language of generalization is most commonly studied in predications of categories (e.g.,~``Birds fly.''), otherwise known as \emph{generic language}.
-But generalization exists beyond classically-defined natural and artifact kinds: Events are described in generalization (e.g.,~``Mary swims after work.''; \emph{habitual language}) as well as causal relationships (e.g.,~``Staring at the sun makes you go blind''; \emph{causal language}).
+But generalization exists beyond classically-defined natural and artifact kinds: Events are described in generalization (e.g.,~``Mary swims after work.''; \emph{habitual language}) as well as causal relationships (e.g.,~``Fire causes smoke''; \emph{causal language}).
 Generalizations are ubiquitous in everyday conversation (``Movie theaters are cold.''), the speech of young children (``Slides aren't for grown ups!''), child-directed speech (``Dogs are friendly.''), political and scientific discourse (``Politicians make promises.'', ``Psychology experiments don't replicate.''), motivation (``Big girls eat broccoli!''), stereotypes (``Boys are good at math.''), and many other facets of experience.
@@
 Habitual and causal language display similar context-sensitivities:
-``John smokes'' may be infelicitous if he does so only once a year, but ``Mary climbs mountains'' seemingly is fine with the same frequency.
-Both \emph{drinking moonshine}  and \emph{staring at the sun} will ``...make you go blind'', though the latter seems more dangerous than the former despite neither statement conveying precise risk information.
+``John smokes'' seems strange to say if he does so only once a year, but ``Mary climbs mountains'' seemingly is fine with the same frequency.
+Both \emph{drinking moonshine}  and \emph{staring at the sun} will ``...make you go blind'', but the latter seems more dangerous than the former despite neither statement conveying precise risk information.
 
@@
 %The dominant view in psychology has been to focus on special conceptual relations that supposedly determine what makes the language the generalization true or false.
-In this paper, we take seriously the context-sensitivity of such language and investigate the hypothesis that the meaning at the core of the language of generalization is \emph{simple but underspecified}.
-We formalize and embed this idea in a simple, rational model of communication and use it to address the fundamental outstanding question: What makes generalizations true or false?
-Our answer is that endorsement (a true or false judgment) is a speaker's decision about whether or not to say the \emph{simple but underspecified} generalization to a naive listener.
-Our model is the first formal model to make precise quantitative predictions about human understanding of generalizations in language.
+In this paper, we take seriously the idea that these statements convey generalization and look to \emph{probability}---the universal currency of belief---to formalize their meaning. 
+Rather than have a fixed-meaning (e.g., how the quantifier ``most'' always means \emph{more than half}), we hypothesize that the generalizations have an uncertain meaning that must be resolved in context.
+We formalize and embed this idea in a simple, rational model of communication and use it to address the fundamental outstanding question for the language of generalizations: What makes the sentences true or false?
+Our answer is that true or false judgments are speaker decisions about whether or not to produce the context-sensitive generalization to a naive listener.
+This is the first formal model to make precise quantitative predictions about human understanding of generalizations in language and we show how it is a sufficient general formulation to capture generalizations of diverse semantic types (categories, events, and causes).
 
@@
 Those reviews raised a number of points regarding the presentation and generality of our work at the time, and highlighted the need for comparison to other models. 
-The current manuscript differs from previous submissions in a number of important ways.
+The current manuscript differs from previous submissions in a number of substantial ways.
 First, we have completely re-written the paper for clarity and focus, especially simplifying and streamlining the modeling sections.
-Second, we have extended from generalizations about categories (or \emph{generic language}) to investigate three case studies: generalizations about categories, events, and causes.
-We are able to explain endorsements across these three domains with minimal domain-specific assumptions. 
-Furthermore, each case study naturally lends methodological advantages to provide further tests of our hypothesis/model (e.g., with causal generalizations, we are able to manipulate---rather than merely measure---prior knowledge).
+Second, we have extended the work substantially from concerning only generalizations about categories (\emph{generic language}) to addressing two other semantic types: generalizations events and causes.
+Across these three domains, we are able to explain endorsements with little-to-no domain-specific assumptions. 
+Furthermore, each case study naturally lends methodological advantages to provide strictiers tests of our hypothesis/model (e.g., with causal generalizations, we are able to manipulate---rather than merely measure---prior knowledge).
 %The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.
@@
 %With causal generalizations, we are able to \emph{manipulate} (rather than merely measure) prior knowledge, and show it is in fact causally related to endorsement. 
-Finally, we develop three alternative models: two linear models based on empirically-elicited statistical knowledge and one rich, cognitive model which lacks the \emph{underspecification of meaning} at the core of our hypothesis.
+Finally, we develop three alternative models: two linear models based on empirically-elicited statistical knowledge and one rich, cognitive model which lacks the uncertain meaning at the core of our hypothesis.
 These alternative models fail to account for key aspects of the context-sensitivity that is observed in the data and that our full model predicts.
@@
 Overall we feel that this paper represents a much improved, generalized and streamlined investigation of generalization in language, and a major breakthrough in computational modeling of language understanding.
-(We would be happy to provide detailed responses to previous reviewers; presently, we feel this would be of limited use given the major changes in content and presentation.)
+(We would be happy to provide detailed responses to previous reviewers, if it would be useful; presently, we feel this would be of limited use given the major changes in content and presentation.)
 

### 2018-04-19 paper/comgen-paper.Rmd
working on discussion

--- 2018-03-27 paper/comgen-paper.Rmd
@@
 
-It is remarkable that so much is learned from ideas expressed vaguely in words.
-Generalizations in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalizing by probability.
-By precisely articulating the conditions under which generalizations are true or false, we are able to describe how an agent should update its beliefs based on that sentence. 
-Thus, in addition to providing a quantitative understanding of the phenomena of the language of generalization, formalizing this language opens up the possibility of building models that learn abstract, generalizable knowledge from language.
-
-As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types: "Robins lay eggs" (categories), "Sally smokes" (events), "Herb X makes animals sleepy" (causes).
+The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to eachother succinctly in language.
+Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
+We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability.
+Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
+<!--
+formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
+As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.
 Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-We test this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether or not to produce the generalization to naive listener. 
-Endorsement, we show, depends in systematic ways on the listener's prior beliefs about the prevalence.
-<!-- What these expressions have in common is not surface features but generalization (also referred to as *genericity*). -->
+-->
+We tested this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether it would be useful to utter the generalization. 
+Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
 This framework accounts for a number of philosophically puzzling generic statements (Expt.
@@
 We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-<!-- In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below. -->
-
+In each case our model provided strong quantitative fit to human judgements.
+
+In the rest of this discussion, we elaborate how our model relates to language understanding more generally, sketch its application to several philosophical puzzles in genericity, and situate our theory with respect to extant theories of generic language.
+
+\ndg{
+[these paragraphs were out of place here. perhaps incorporate later...]
+By precisely articulating the conditions under which generalizations are true or false, we are able to describe how an agent should update its beliefs based on that sentence. 
+Thus, in addition to providing a quantitative understanding of the phenomena of the language of generalization, formalizing this language opens up the possibility of building models that learn abstract, generalizable knowledge from language.
+xx
 We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
@@
 That is precisely what our information-theoretic model does.
-
-<!-- The theory we present here goes beyond previous accounts in a number of useful ways. -->
-<!-- The foremost contribution of our theory is that it is accompanied by a formal model, which makes precise quantitative predictions about endorsments. -->
+xx
 The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge.
@@
 Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work. 
-In the rest of this discussion, we elaborate how our model relates to other problems in language understanding, sketch out arguments for other known philosophical puzzles in genericity, and situate our theory with respect to extant theories of genericity.
-
+}
 <!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->

### 2018-04-19 analysis/case3-causals.Rmd

---
title: "Analysis for Case 3 (causals)"
output: html_notebook
---

```{r libraries, cache = F}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
library(viridis)
library(tidyboot)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

compute_r2 <- function(df,v1, v2, sigfigs = 3){
  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
}

compute_mse <- function(df, v1, v2, sigfigs = 3){
  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
}

project.path <- "../"
options("scipen"=10) 
```

```{r}
genericEndorsementPriorModelHelpers <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)
'

structuredPriorModel <- '
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {g, d, phi}
}
'

unstructuredPriorModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  mapData({data: preprocessedResponses}, function(d){
    factor(stableComponent.score(d))
  })
  return {g, d}
}
'
genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
```

```{r rsaHelpers}
rsaHelpers <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var round = function(x){
  return Math.round(x*1000)/1000
}
var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
// var thetaBins = [
//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 // ]
var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var bins = map(round, _.range(0.01, 0.99, 0.01))

// var bins = [
  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
// ];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}

var mixture = data.prior.mix[0];
var priorParams = data.prior.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

fixed.threshold.model <- '
var fixedThresholdInterpreter = function(threshold) {
  Infer({model: function(){
  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
  var state = sample(statePrior)
  condition( state > threshold)
    return {
      state: state
  }
 // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
 }, method: "enumerate"})}
'

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

```

```{r simulationCalls}
fixed.threshold.calls <- '
_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
'
no.utterance.call <- ' 
  noUtteranceInterpreter()
'
uncertain.threshold.call <- '
  uncertainThresholdInterpreter()
'
```

```{r causal-priors-data}
d.cas.priors <- read.csv(paste(project.path,
                           "data/causals/priors/causals-8-prior-trials.csv",
                           sep= ""))

d.cas.priors.catch <- read.csv(paste(project.path,
                           "data/causals/priors/causals-8-prior-catch_trials.csv",
                           sep= ""))

# some participants were mischaracterized as failing the catch trial because they put something of the form "0/100" or "herb F: 19" 
mischaracterized <- c( 24, 48, 62, 94, 106, 110, 111, 112, 113, 116, 125, 132, 145, 155, 158)

d.cas.priors <- left_join(d.cas.priors, d.cas.priors.catch) %>%
  mutate(pass_numeric = ifelse(workerid %in% mischaracterized, 1, pass_numeric),
         passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))

n.subj.cas <- length(unique(d.cas.priors$workerid))

n.subj.cas.failed <- length(unique(filter(d.cas.priors, passBoth == 0)$workerid))

d.cas.priors <- d.cas.priors %>% filter(passBoth == 1)

ave.minutes.cas <- round(mean(unique(d.cas.priors %>% select(workerid, rt))$rt) / 1000 / 60, 1)
```

```{r causal-priors-runModel, cache = T}
causal.distributions <- levels(factor(d.cas.priors$distribution))
m.cas.marginal.prevalence <- data.frame()
m.cas.endorse.priors.summary <- data.frame()

for (p in causal.distributions){
  priorData <- 100*filter(d.cas.priors, distribution == p)$response

  m.cas.endorse.priors <- webppl(genericEndorsementPriorModel, data = priorData, data_var = "data",
         model_var = "model", 
         inference_opts = list(method = "MCMC", samples = 10000, burn = 5000, verbose = T))

  m.cas.marginal.prevalence <- bind_rows(m.cas.marginal.prevalence, m.cas.endorse.priors %>% 
    spread(Parameter, value) %>%
    rowwise() %>%
    mutate(
      a = g * d,
      b = (1 - g) * d,
      stable = rbinom(n = 1, size = 1, prob = phi),
      prevalence = ifelse(stable == 1, 
                             rbeta(n = 1, shape1 = a, shape2 = b),
                             rbeta(n = 1, shape1 = 1, shape2 = 100)),
      distribution = p
    )
  )

  m.cas.endorse.priors.summary <- bind_rows(m.cas.endorse.priors.summary,
                                            m.cas.endorse.priors %>% 
                                              mutate(distribution = p) %>%
                                              group_by(distribution, Parameter) %>%
                                              summarize(MAP = estimate_mode(value),
                                                        cred_upper = hdi_upper(value),
                                                        cred_lower = hdi_lower(value))
                                              )
}

```

```{r}

bind_rows(
  d.cas.priors %>%
    select(distribution, response) %>%
    rename(prevalence = response) %>%
    mutate(src = 'data'),
  m.cas.marginal.prevalence %>%
    select(distribution, prevalence) %>%
    mutate(src = 'model')
) %>%
  #mutate(src = factor(src, levels = c("model", "data")))
ggplot(.,
       aes( x = prevalence , color = distribution, linetype = src))+
  geom_density(size = 0.4, aes( y = ..scaled.. ))+
  scale_color_solarized()+
  scale_linetype_manual(values = c(2, 1))+
  facet_wrap(~distribution, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))

```

```{r}
n.subj.cas <- length(unique(d.cas.priors$workerid))

n.subj.cas.failed <- length(unique(filter(d.cas.priors, passBoth == 0)$workerid))

d.cas.priors <- d.cas.priors %>% filter(passBoth == 1)

save(d.cas.priors, 
     n.subj.cas,
     n.subj.cas.failed,
     ave.minutes.cas,
     file = "../paper/cached_results/case3_priorRatings.RData")

d.cas.priors %>%
    select(distribution, response) %>%
    rename(prevalence = response) %>%
ggplot(.,
       aes( x = prevalence , fill = distribution))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'black') + 
  #geom_bar(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  #geom_density(size = 0.4, aes( y = ..scaled.. ))+
  scale_fill_solarized()+
  #scale_linetype_manual(values = c(2, 1))+
  facet_wrap(~distribution, scales = 'free')+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses")+
  xlab("Prevalence rating")

```

# Endorsement

```{r causal-endorsement-data}
d.caus.endorse.catch.20 <- read.csv(paste(project.path, 
                                       "data/causals/endorsement/",
                                       "causals-8-20-catch_trials.csv", sep = ""))

d.caus.endorse.catch.70 <- read.csv(paste(project.path, 
                                       "data/causals/endorsement/",
                                       "causals-8-70-catch_trials.csv", sep = "")) %>%
  mutate(workerid = workerid + 1 +  max(d.caus.endorse.catch.20$workerid) )

d.caus.endorse.catch <- bind_rows(d.caus.endorse.catch.20, d.caus.endorse.catch.70)

d.caus.endorse.catch <- d.caus.endorse.catch %>% 
  mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))

d.caus.endorse.20 <- read.csv(paste(project.path, 
                                "data/causals/endorsement/",
                                "causals-8-20-trials.csv", sep = ""))

d.caus.endorse.70 <- read.csv(paste(project.path, 
                                "data/causals/endorsement/",
                                "causals-8-70-trials.csv", sep = "")) %>%
  mutate(workerid = workerid + 1 + max(d.caus.endorse.20$workerid))

d.caus.endorse <- bind_rows(d.caus.endorse.20, d.caus.endorse.70)

n.subj.cas.endorse <- length(unique(d.caus.endorse$workerid))
ave.minutes.cas.endorse <- round(mean(unique(d.caus.endorse %>% select(workerid, rt))$rt) / 1000 / 60, 1)

n.subj.cas.endorse.failed <- length(filter(d.caus.endorse.catch, passBoth == 0)$workerid)

d.caus.endorse.summary <- left_join(
  d.caus.endorse, 
  d.caus.endorse.catch %>% select(workerid, passBoth)
  ) %>%
  filter(passBoth == 1) %>%
  group_by(distribution, frequency) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))
```

```{r tests?}
d.caus.endorse.passed <- left_join(
  d.caus.endorse, 
  d.caus.endorse.catch %>% select(workerid, passBoth)
  ) %>%
  filter(passBoth == 1)

# str(d.caus.endorse.passed)
# 
# summary(glmer(response ~ frequency* across * within + (1 | story), family = 'binomial', data = d.caus.endorse.passed %>%
#   separate(distribution, into =c("across", "within") ) %>%
#     mutate(frequency = factor(frequency))))

#str(d.caus.endorse.passed)  
```

```{r causals-fullmodel}
n_chains <- 2
n_samples <- 100000
burn <- n_samples / 2
lg <- 5
i <- 1

model_prefix <- "pilot-results-causals-jointModel-S1-"

m.cas.samp <- data.frame()
for (i in seq(1, n_chains)){
  mi <- read_csv(paste(project.path,  "models/causals/results/", 
                    model_prefix, "smntcs_causal-",
                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  m.cas.samp <- bind_rows(m.cas.samp, mi %>% mutate(chain = i))
}

# n_chains <- 1
# n_samples <- 1000
# burn <- n_samples
# lg <- 5
# i <- 1
# m.hab.fixed.samp <- data.frame()
# for (i in seq(1, n_chains)){
#   mi <- fread(paste(project.path,  "models/habituals/results/", 
#                     model_prefix, "smtncs_some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.samp.i <- mi %>% mutate(chain = i)
#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
# }

# m.hab.somemodel.endorsement <- m.hab.fixed.samp %>%
#   filter(type == 'predictive') %>%
#   rename(habitual = B, time_period = D, binned_freq = E) %>%
#   group_by(habitual, time_period, binned_freq) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

m.cas.fullmodel.endorsement <- m.cas.samp %>%
  filter(type == 'predictive') %>%
  group_by(dist, frequency) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```

```{r}
md.caus.endorse <- left_join(
  m.cas.fullmodel.endorsement,
    d.caus.endorse.summary %>%
    select(distribution, frequency, MAP_h, low, high) %>%
    rename(dist = distribution)
)

n.caus.endorse <- length(md.caus.endorse$MAP_h)
r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")

```

```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
md.cas.fullmodel.endorsement <- bind_rows(
  m.cas.fullmodel.endorsement %>%
    mutate(src = "model"),
  d.caus.endorse.summary %>%
    select(distribution, frequency, MAP_h, low, high) %>%
    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
    mutate(src = 'data')
) %>%
  ungroup()

# save(md.cas.fullmodel.endorsement,
#      md.caus.endorse, 
#      n.subj.cas.endorse, 
#      ave.minutes.cas.endorse,
#      n.subj.cas.endorse.failed, 
#      file = "../paper/cached_results/case3_endorsementDataModel.RData")

figure.causals.endorsement <- md.cas.fullmodel.endorsement %>%
  mutate(
    src = factor(src, levels = c( "model", "data")),
    dist = factor(dist, 
           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
           labels = c(
                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))
    ) %>%
  ggplot(., aes( x = frequency, y = MAP, ymin = cred_lower, ymax = cred_upper, 
                 color = dist, #linetype = dist, 
                 shape = dist,
                        group = dist#, 
                 #alpha = src
                 ))+
  #geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
  geom_linerange(position = position_dodge(8), alpha=0.8)+
  geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
  geom_point(position = position_dodge(8), size = 2.25)+
  #theme(axis.text.x = element_text(angle = 90))+
  #geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_alpha_manual(values = c(1, 0.3))+
  scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
  #scale_fill_solarized()+
  scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
  xlab("Referent prevalence")+
  ylab("Causal Endorsement")+
  facet_grid(.~src)+
  #coord_flip()+
  coord_fixed(ratio = 90)+
  #guides(fill = F)+
  guides(
    shape=guide_legend(title="Background distribution"),
    color=guide_legend(title="Background distribution")
    )+
  theme(
    plot.margin = unit(c(0,6,0,6), "pt")
    #legend.position = 'bottom', 
    # legend.direction = 'horizontal', 
    # legend.title = element_blank()
  )
```

# Extra

```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt. 3 (stimuli) and priors reconstructed from participants' responses (model). ", fig.width = 8, fig.height = 3, eval = F}
sample.dists <- bind_rows(
  data.frame(
    dist = "rare weak",
    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
          rbeta(n = 7000, shape1 = 2, shape2 = 50)
          )
  ),
  data.frame(
    dist = "common weak",
    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
  ),
  data.frame(
    dist = "rare deterministic",
    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
          rbeta(n = 7000, shape1 = 2, shape2 = 50)
          )
  ),
  data.frame(
    dist = "common deterministic",
    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
  )
) %>%
    mutate(Distribution = factor(dist, 
                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
         labels = c("Common Deterministic", "Rare Deterministic",
                    "Common Weak", "Rare Weak")))

figure.causals.priors <- bind_rows(
  sample.dists %>%
    mutate(src = "stimuli") %>%
    select(-dist),
  m.cas.marginal.prevalence %>%
    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak")) %>%
    mutate(Distribution = factor(distribution, 
                                 levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
           labels = c("Common Deterministic", "Rare Deterministic",
                      "Common Weak", "Rare Weak"))) %>%
    select(Distribution, prevalence) %>%
    mutate(src = 'model') %>%
    rename(x = prevalence)
) %>%
  mutate(src = factor(src, levels = c("stimuli", "model"))) %>%
  ggplot(., aes(x = x, fill = Distribution, color = Distribution, alpha = src, lty = src
                ))+ 
  geom_density( adjust = 1.3, 
               size = 1.2,
               aes( y = ..scaled..))+ #
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_fill_solarized()+scale_color_solarized()+
  #scale_color_manual(values = c("#636363", "#d7191c"))+
  scale_alpha_manual(values = c(0.1, 0.4))+
  scale_linetype_manual(values = c(2, 1))+
  ylab("Scaled Prior Probability")+
  xlab("Target probability")+
  facet_wrap(~Distribution, scales = 'free', nrow = 1)+
  guides(fill = F, color = F)+
  theme(legend.position = 'bottom', legend.direction = 'horizontal')
```

```{r s1-model}
s1.model <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var betaShape = function(params){
  return {
      a: params.g * params.d,
      b : (1-params.g) * params.d
  }
}

var thetaPrior = Infer({model: function(){
 return uniformDraw([
   0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
   0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 ])}
});

var bins = [
  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}
var alpha = 2;
var mixture = data.prior[0].phi;
var priorParams = betaShape(data.prior[0]);

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:100}), b) + Number.EPSILON
      }, bins )
    })
}});

var listener0 = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return state
 }})}, 10000)

var speaker1 = function(state) {
  Infer({model: function(){
    var utterance = sample(utterancePrior);
    var listener_posterior = listener0(utterance);
    factor(alpha * listener_posterior.score(state))
    return utterance
  }})
}

probability(speaker1(data.state[0]), "generic")
'
```

```{r causal-endorsement-predictions, cache = T, eval = F}
causal.priorParams <- m.cas.endorse.priors.summary %>%
    filter(distribution %in% c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
           Parameter != 'marginalPrevalence') %>%
  select(distribution, Parameter, MAP) %>%
  spread(Parameter, MAP)
experimental.frequencies <- c(0.2, 0.7)
causal.endorsement.predictions <- data.frame()
for (p in causal.priorParams$distribution){
  for (s in experimental.frequencies){

    inputData = list(prior = filter(causal.priorParams, distribution == p), 
                     state = s)

    s1.rs <- webppl(s1.model, data = inputData, data_var = "data")

    causal.endorsement.predictions <- bind_rows(
      causal.endorsement.predictions,
      data.frame(state = s, distribution = p, prob = s1.rs)
    )
  }
  print(p)
}
```

```{r causal-model-insets, fig.width = 4, fig.height = 3.5, cache = T}
m.cas.fullmodel.prior.parameters <- m.cas.samp %>%
  filter(type == "prior") %>%
  rename(variable = item, parameter = roundedFreq) %>%
  group_by(dist, variable, parameter) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

# use MAP estimates to generate L(h | causal) & L(h | silence) predictions

m.cas.fullmodel.prior.parameters.tidy <- m.cas.fullmodel.prior.parameters %>%
  ungroup() %>%
  select(dist, variable, parameter, MAP) %>%
  mutate(param = paste(variable, parameter, sep = "_")) %>%
  select(-variable, -parameter) %>%
  spread(param, MAP) %>%
  rename(mix = mixture_NA, 
         stable_mean = stableFreq_mean, 
         stable_concentration = stableFreq_sampleSize) %>%
  mutate( a = stable_mean * stable_concentration, 
          b = (1 - stable_mean) * stable_concentration)

cas.listener.predictions <- data.frame()

for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
 priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
  l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 cas.listener.predictions <- bind_rows(
   cas.listener.predictions, 
      l0.rs.prior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Posterior")
   )
}

#inset.color.order <- c( "#268bd2", "#dc322f","#d33682","#859900")
inset.color.order <- c("#859900","#d33682","#dc322f", "#268bd2")

causals.endorsement.insets <- cas.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, 
                              levels = c("state_Prior","state_Posterior"),
                            labels = c("Prevalence prior (Expt. 3a)",
                                       "Interpreter model posterior")),
    Distribution = factor(distribution, 
                               levels = c("rare_weak",  "common_weak", "rare_deterministic", "common_deterministic"),
         labels = c("Weak, Rare", "Weak, Common", "Strong, Rare", "Strong, Common"))) %>%
  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~Distribution, nrow = 2)+
  scale_fill_manual(values =inset.color.order )+
  scale_color_manual(values = inset.color.order)+
  geom_vline(xintercept = 0.2, lty = 3)+
  geom_vline(xintercept = 0.7, lty = 3)+
  scale_alpha_manual(values = c(0.8, 0.1))+
  scale_linetype_manual(values = c(1, 2))+
  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Prevalence") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", 
        legend.direction = 'vertical',
        legend.title = element_blank(),
        plot.margin = unit(c(16,6,6,6), "pt"))+
  guides(fill = F, color = F, alpha = F)

#causals.endorsement.insets
```

```{r causals-endorsement-fig, fig.width = 4, fig.height = 3, eval = F}

ggplot(d.caus.endorse.summary, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
                        group = distribution))+
  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'black')+
  theme(axis.text.x = element_text(angle = 0))+
  geom_hline(yintercept = 0.5, lty = 3, color = 'black')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
  scale_fill_solarized()+
  xlab("Target frequency")+
  ylab("Proportion Causal Endorsement")
```

```{r empirical-causal-prior-densities, eval = F, fig.width = 5, fig.height = 3, fig.caption="Empirical densities from the prediction task in the prior manipulation experiment (Expt. 3a)."}
d.cas.priors %>%
  filter(distribution %in% c("common_weak", "rare_deterministic", "rare_weak")) %>%
      mutate(Distribution = factor(distribution, 
                               levels = c("rare_deterministic", "common_weak", "rare_weak"),
         labels = c("Rare Deterministic",
                    "Common Weak", "Rare Weak"))) %>% 
ggplot(., aes(x = response, fill = Distribution, color = Distribution))+ 
  geom_density( adjust = 0.8, alpha =0.8, 
               size = 1.2,
               aes( y = ..scaled..))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
  ylab("Scaled Prior Probability")+
  xlab("Target probability")+
  facet_wrap(~Distribution, scales = 'free')+
  guides(fill = F, color = F)
```

### 2018-04-19 paper/case3-causals.Rmd

@@
 `r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
+The empirically elicited distributions of responses were not appreciably different for our two cover stories (herbs making animals sleepy, fertilizer making plants grow tall) and thus we collapse the data across these two stories.
 The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals)A.
@@
 
-\ndg{i'm not sure 10A is the best way to show this data, since the lines highlight the differences between causal powers (within conditions), while we care most about differences between conditions.}
+<!-- \ndg{i'm not sure 10A is the best way to show this data, since the lines highlight the differences between causal powers (within conditions), while we care most about differences between conditions.} -->
 
@@
 The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
-Our model predicted these effects with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
+These effects were predicted by our model with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).
 
-\ndg{is it worth saying anything about the fact that the effect is even a bit bigger than predicted by the model?}
+<!-- \ndg{is it worth saying anything about the fact that the effect is even a bit bigger than predicted by the model?} -->
 
@@
 In addition to further demonstrating the generality of this theory, these experiments show that the prevalence prior $P(p)$ is causally related to endorsements of generalizations in language.
-To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category.
+<!-- To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category.
 \ndg{fix last sentence.
@@
 is it about causation?
-huh?}
+huh?} -->
 
 In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall.
-\ndg{which reminds me: need to say something above (3a) about (no) differences between the cover stories?}
+<!-- \ndg{which reminds me: need to say something above (3a) about (no) differences between the cover stories?} -->
 We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it is plausible that there are herbs that only weakly make animals sleepy and it is also plausible that there are herbs that almost deterministically make animals sleepy).

### 2018-04-19 paper/comgen-paper.Rmd

@@
 As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.
+
 Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
@@
 In the rest of this discussion, we elaborate how our model relates to language understanding more generally, sketch its application to several philosophical puzzles in genericity, and situate our theory with respect to extant theories of generic language.
+
+\mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)}
 
@@
 
+## Communicating predictive probabilities
+
+This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
+These predictive probabilities are fundementally mental representations, as opposed to observed frequency, which is often taken to be the object of statistical approaches to genericity.
+Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
+What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
+
+<!-- Expts.
+2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
+-->
+
+Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the numerical language used to convey explicit probabilities [cf., @Levinson1995].
+Rather than conveying probabilities *explicitly*, generalizations we argue convey them *implicitly*.
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the (historically quite recent) numerical language of probability [@Xu2008; @xu2009statistical].
+
+<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
+This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
+-->
+
+<!-- ### The Problems with Communicating Generalizations -->
+
+<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
+<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
+<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
+-->
+<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
+
+<!-- Generalizations can be made about almost anything. -->
+<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
+-->
+<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
+
+<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
+-->
+<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
+-->
+
+<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
+-->
+<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
+
+<!-- ### Statistical Accounts of Generics -->
+
+<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
+<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
+<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
+<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
+<!-- Let's first introduce some notation: -->
+
+<!-- ### Conceptual Accounts of Generics -->
+
 ## Prevalence priors and conceptual knowledge
 
-<!-- Though conceptual structure of kind discussed of the sort discussed by Leslie and Prasada are not explicitly formalized in our model, our general cognitive modeling framework provides natural avenues for future integration.
--->
+\ndg{this section is pretty critical, and needs work. or posisbly much of it belongs in the discussion of others sematic theoris?}
 
 Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
-Beliefs about prevalence are often the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
-The prevalence prior is a common statistical layer that provides the glue between conceptual knowledge and natural language semantics.
-The truth conditions of generalizations depend only on prevalence, but prevalence depends upon conceptual knowledge.
-
-<!-- Given this minimal representation of background knowledge, language interfaces with conceptual knowledge via prevalence.  -->
-
-<!-- Previous psychological and philosophical work on generics has looked beyond prevalence and focused on kinds and their conceptual relations to properties  -->
-<!-- Indeed, we see a core communicative function of generics as teaching properties of kinds to naive listeners. -->
-<!-- But we argue that the reason why particular generics are licensed in a context concerns the information conveyed to a listener relative to their background knowledge; to interface with a truth-functional semantics, such background knowledge must have a representation in the form of a prevalence prior.
--->
-
-<!-- There is nothing in our theory that rules out shared background knowledge presupposing beliefs about natural kinds and richly structured relations between categories and the properties [a la @Prasada2013].
--->
-Conceptual structure including higher-order abstractions can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components.
+Such a prior distribution implies a qualitative distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can brings about the target feature.
+Actual conceptual knowledge against which generalizations are interpreted is most likely richer than this.
+
+Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
 We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
@@
 
+Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
+Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
+The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
+The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
+
 <!-- Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations. -->
@@
 
-In our modeling work, we found that the empirical data which underlie the prevalence prior distributions are best modeled by a mixture-model with two mixture components.
-Such a prior distribution draws qualitative distinctions between different kinds of categories by virtue of the prevalence prior model representing multiple distinct components. 
-Actual conceptual knowledge against which generalizations are interpreted is most likely far-richer than simply a two-component mixture-model.
-We note, however, that a richer model of the prior was not necessary, at this point, to account for the context-sensitive endorsement patterns we observe in our empirical data.
-
+\ndg{ [why is this par here. and what does it mean??]
 The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
@@
 This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
+}
 
@@
 <!-- - essentialism: different generative models that imply the same statistics with different causal relations (but orthogonal) -->
-
-## Communicating predictive probabilities
-
-This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-We distinguish our construct from other uses of *prevalence* in the literature, often taken to be synonymous with observed frequency.
-<!-- the distinction that what is communicated is probability not frequency. -->
-<!-- In previous accounts, prevalence is treated as synonymous with the frequency of the feature in the category.  -->
-Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
-What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
-
-<!-- Expts.
-2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
--->
-
-Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the language used to convey explicit probabilities [cf., @Levinson1995].
-Rather than conveying *explicit probabilities*, generalizations we argue convey *implicit probabilities*.
-In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the actual language of probability [@Xu2008; @xu2009statistical].
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
 
@@
 An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
-
+\ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.}
+
+<!--
+[NDG: i cut this because it is unecassary speculation.]
 Uncertainty about the comparison class adds yet more opportunity to the language of generalization for disagreement, miscommunication, or deceit.
@@
 BUT IT THINK IT WOULD BE BETTER TO SAY SOMETHING SUBSTANTIVE;  FOCUSSING ON HOW KNOWLEDGE OF THE COMPARISION CLASS SHOULD PROVIDE INSIGHTS INTO FAILURES TO COMMUNICATE SUCCESSFULLY.}
-
-Finally, interlocutors may not only fail to coordinate on what categories are in the comparison class, the prevalences that may be assumed for the constituent categories of the comparison class, but the very nature of *how* the comparison class should be constructed.
-The comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
+-->
+
+Finally, the comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
+\ndg{Note QUD might not have been introduced, depending on where we move above floating paragraph..}
 Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
@@
 The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
+\ndg{mention that prosodic focus easily switches between these.}
 In this work, we focused on category-wise comparison classes purely for methodological convenience.
@@
 <!-- Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015]. -->
-<!-- <!-- "Cars have tape decks" is a generalization that was true about thirty years ago, but  --> -->
-<!-- <!-- Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. --> -->
+<!-- <!-- "Cars have tape decks" is a generalization that was true about thirty years ago, but  -->
+<!-- <!-- Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. --> 
 <!-- Ravens and toasters have no privileged relationship to each other and to assess if "Ravens are bigger than toasters", we should actually measure the distribution of sizes for ravens and toasters.

### 2018-04-19 paper/comgen-paper.Rmd
more work on discussion

@@
 The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
+\ndg{actually, i think it's better to have a specific section for these conceptual theories here.
+can leave a but of high-level discussion of prevalence priors in relation to bayesian intuitive theories above, and then talk about details of leslie and prasada here...}
 We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.

### 2018-04-20 paper/comgen-paper.Rmd
clean conceptual knoweldge subsec, streamline pred prob subsec

@@
 This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-These predictive probabilities are fundementally mental representations, as opposed to observed frequency, which is often taken to be the object of statistical approaches to genericity.
+These predictive probabilities are fundementally mental representations and not observable frequencies, the object of other statistical approaches to genericity.
 Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
@@
 Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the numerical language used to convey explicit probabilities [cf., @Levinson1995].
-Rather than conveying probabilities *explicitly*, generalizations we argue convey them *implicitly*.
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the numerical language used to convey explicit probabilities, a historically quite recent innovation [cf., @Levinson1995].
+Rather than conveying probabilities *explicitly*, generalizations convey them *implicitly*.
 In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
 The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the (historically quite recent) numerical language of probability [@Xu2008; @xu2009statistical].
+Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
 
@@
 
-\ndg{this section is pretty critical, and needs work. or posisbly much of it belongs in the discussion of others sematic theoris?}
+<!-- \ndg{this section is pretty critical, and needs work. or posisbly much of it belongs in the discussion of others sematic theoris?} -->
 
@@
 In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components.
-Such a prior distribution implies a qualitative distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can brings about the target feature.
-Actual conceptual knowledge against which generalizations are interpreted is most likely richer than this.
+Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
+Actual conceptual knowledge against which generalizations are interpreted is most likely richer than our simple two-component prevalence distributions.
 
@@
 We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
-The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each give rise to beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
+The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
 Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
-Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.
-
-Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
-The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
-The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
-
-<!-- Our approach makes the strong claim that predictive probabilities are the connective tissue between conceptual knowledge and the semantics of generalizations. -->
-<!-- That is, the effect of conceptually meaningful differences on generic language is predicted to be mediated by differences in corresponding speaker beliefs or listener prevalence distributions, which can occur for multiple reasons (e.g., by changing the comparison class).
--->
-<!-- We found in Expts. 1 \& 2 that conceptually different kinds of properties and events gave rise to quantitatively different prevalence priors, even while keeping the comparison class fixed.  -->
-<!-- In Expt. 3 we showed that these prevalence distributions are causally related to endorsement. -->
-
-\ndg{ [why is this par here. and what does it mean??]
-The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
-Our simple endorsement model assumes that the goal of communication is the prevalence (Eq.\ref{eq:S1}).
-In other words, the endorsement decision is computed with respect to the prevalence information conveyed to the listener.
-Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced.
-We note, however, that the endorsement model makes almost identical predictions for the data presented in this paper if the QUD is assumed to be about the abstract parameters of the background knowledge (e.g., which mixture component the referent is part of) as opposed to the prevalence itself.
-This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here.
-}
+
+The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
+Our model distinguishes the semantic contribution of an utterance from a speaker's utility in producing that utterance. 
+For simplicity, the mode presented here assumes these two are the same: they are both about prevalence. 
+However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions (i.e., if the communicative goal is less about prevalence and more about the kind of thing that the referent is).
+This behavior is promising for constructing models of generalizations that teach about the abstract relations present in intuitive theories of kinds and properties.
+
+<!-- The model, however, has the flexibility to address richer communicative goals [also known as the *Question Under Discussion* or QUD; @roberts1996qud]. -->
+
+<!-- Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.
+-->
+
+<!-- \ndg{ [why is this par here. and what does it mean??] -->
+<!-- The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
+-->
+<!-- Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced. -->
+<!-- This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here. -->
+<!-- } -->
 
@@
 Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
+
+### Conceptual accounts
+
+\mht{from above:
+Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
+Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
+The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
+The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
+}
 

### 2018-04-20 paper/comgen-paper.Rmd
edits to comparison class and acquisition subsecs

@@
 
-The probabilistic communicative model we introduce in this paper assumes shared background 
-<!-- Our model of an interpreter, or naive listener, has access to implicit  -->
-statistics of the event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
+The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
 We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
@@
 The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations explored in this paper.
+Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations highlighted in this paper.
 An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
-\ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.}
+Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
+In this paper, we do not include such a mechanism in our model, instead we made the comparison class clear to participants when possible in order to study the remaning context-sensitivity with generics.
+<!-- \ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.} -->
 
@@
 
-Finally, the comparison classes used in our case studies were with always respect to the *category* (*other animals*, *other people*, *other possible causes*); thus, our model addresses the implicit QUD of "*what* has feature?".
-\ndg{Note QUD might not have been introduced, depending on where we move above floating paragraph..}
-Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the *feature* (e.g., *other features*, *other actions*, *other effects*).
-It's long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine in a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what's morally right, ...)*" e.g., when said sardonically).
+Finally, the comparison classes used in our case studies were with always respect to the category (*other animals*, *other people*, *other possible causes*).
+Thus, our endorsement model assumes the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has feature?".
+Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
+It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
+The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*" e.g., when said sardonically).
+Prosodic focus easily gates between these interpretations (e.g., "[Lawyers] care about the law" vs. "Lawyers care about [the law]").
 \ndg{mention that prosodic focus easily switches between these.}
 In this work, we focused on category-wise comparison classes purely for methodological convenience.
-Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, and how the relevant comparison classes are constructed.
+Future work should investigate the factors that give rise to feature-wise interpretations of generalizations and how the relevant comparison classes are constructed.
 
@@
 <!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
-Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is in fact *easier* to formalize, but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
+Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, in fact, easier to formalize but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
 <!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) is inappropriate for generalizations  [@Leslie2008].
+This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generalizations [@Leslie2008].
 
 Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
-The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three distinct aspects of meaning: 
-(1) the *dimension* being described (i.e., probability $h$),
+With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning at least three distinct aspects of meaning:
+(1) the *dimension* being described (i.e., probability $p$),
 (2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
-(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
 Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
-Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
+Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
 However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
-Thus, under our framework, generalizations should not only be learned before, but also faciliate in learning, quantifiers.
+Thus, under our framework, generalizations should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
@@
 -->
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $h$: $\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h$
+Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$
 This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
-The difficulty in acquiring the meaning of quantifiers is then a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
+The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
 We leave for future work the precise implementation of the acquisition model we sketch out here.

### 2018-04-23 paper/comgen-paper.Rmd
talk some about leslie, strikingness, and principled connections

@@
 
-The present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the formal semantics  literature.
+The present paper presents the first formal theory of genericity in language that generates quantitative predictions about human behavioral data. 
+A number of other theories of genericity have been proposed in formal semantics and in psychology, which  posit different constructs or psychological mechanisms to account for the flexible truth conditions of generics.
+Thse accounts fall into two broad camps: Those that appeal to the quantification or the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations or abstract beliefs (e.g., *there is something about being K which causes it to F*).
+Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
+
+\mht{unsure about this paragraph...}
+<!-- Not all theories are created equal, however.  -->
+Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and further leave it to intuition to decide for a particular generic statement, what kind of generic it is.
+In this paper alone, our theory has made hundreds of predictions about the endorsement of individual generic statements, with high accuracy, derived from a general theory that we posit applies to all generic statements.
+In addition, previous accounts are rarely general enough to include generalizations of different semantic types (e.g., *habituals*) and deal only with generics.
+For these reasons alone, our account is novel. 
+As we describe below, it relates to extant theories in meaningful ways.
+
+<!-- By contrast, our theory has made hundreds of predictions about individual generic statements, derived from a general theory that we posit applies to all generic statements. -->
 <!-- We now turn to situating our account with respect to these previous theories. -->
@@
 -->
-These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
 
 ### Conceptual accounts
+
+Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
+
+The most influential account in psychology comes from @Leslie2008. 
+Leslie starts from the same point as our account: Generics express generalization. 
+She then turns her attention to the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child or adult to generalize the property to the kind.^[
+  Because the mechanism for understanding generics is innate, in her account, the learning puzzle (vis a vis quantifiers) immediately goes away.
+]
+Leslie describes the default generalization mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal) (ii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively)^[
+  This is a rather technical consideration used to account for the difference between "Birds lay eggs" and "Birds are female".
+For the latter, counterinstances (male birds) are positive because they have an alternative property (being male).
+For the former, counterinstances are negative because they simply lack the property (i.e., male birds do not reproduce by some other method).
+], and (iii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"). 
+On this account, generics are true if only some of Ks have F if all counterinstances are negative and the property is either characteristic or striking. 
+If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
+
+The evolutionary argument for accepting striking generics is straightforward: These are relevant properties to know about if you want to survive. 
+But there are two other factors that are confounded with striking properties that make it difficult to make a claim about strikingness *per se* leading to generic endorsement.
+The first is that striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
+Thus, the prevalence prior distributions of these features are hard to distinguish from properties that are just generally rare and distinctiveness (e.g., having extraordinarily beautiful feathers). 
+@Cimpian2010 (Expt.
+4) can be seen as evidence for this point: In that experiment, participants show a willingness to endorse both generics about striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
+This increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$  distributions for the two are similar. 
+Those experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prior distribution over the prevalence changes to resemble that of a distinctive property when supplied information about the dangerousness of the feature.
+
+The second factor confounded with striking properties, which Leslie herself uses as motivation for their distinction, is that striking properties are projected more strongly (i.e., generalized to more instances of the category) than neutral properties.
+Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral, statistically low-probability properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
+2 & 3].
+This provides evidence for the influence of strikingness on *predictive prevalence*, which we posit is the second intermediate representation between conceptual knowledge and generic endorsements.
+
+The notion of *characteristic* properties is the same as @Prasada2006's notion of a *k-property*, which is a property that bears a *principled connection* to the kind. 
+Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self locomotion; @Goodman1955; @Shipley1993].
 
@@
 We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
-Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
+
 For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
@@
 
-<!-- ### Statistical accounts -->
-
-### Relative and absolute generics
+### Statistical accounts
+
+#### Relative and absolute generics
 
@@
 
-### Generic as indexical
+#### Generic as indexical
 
@@
 
-### "Normal" accounts
+#### "Normal" accounts
 
@@
 
-### Underquantification
+#### Underquantification
 

### 2018-04-23 paper/comgen-paper.Rmd
finish drafting discussion of leslie and prasada

@@
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
-Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].
+Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007a].
 Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].
@@
 
+In our account, the core meaning of generics concerns probability (the currency of belief), which in many cases may be the byproduct of rich conceptual structure. 
+We believe this separation between conceptual structure (which exists in the head) and prevalence (a quantitative metric for natural language semantics) provides a more unifying view of the phenomena of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
+By formalizing how background knowledge influences generic understanding, our model provides a path towards unifying conceptual approaches to generics with inherently statistical natural language semantics.
+<!-- At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.  -->
+
 \mht{unsure about this paragraph...}
@@
 Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-
 The most influential account in psychology comes from @Leslie2008. 
-Leslie starts from the same point as our account: Generics express generalization. 
+Leslie takes the same starting point as our account: Generics express generalization. 
 She then turns her attention to the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child or adult to generalize the property to the kind.^[
@@
 ]
-Leslie describes the default generalization mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal) (ii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively)^[
-  This is a rather technical consideration used to account for the difference between "Birds lay eggs" and "Birds are female".
+Leslie describes the default generalization mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
+  This positive vs.
+negative counterinstance distinction is a rather technical consideration [though not without psychological foundation, see @Leslie2009 p.36] used to account for the difference between "Birds lay eggs" and "Birds are female".
   For the latter, counterinstances (male birds) are positive because they have an alternative property (being male). 
   For the former, counterinstances are negative because they simply lack the property (i.e., male birds do not reproduce by some other method).
-], and (iii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"). 
-On this account, generics are true if only some of Ks have F if all counterinstances are negative and the property is either characteristic or striking. 
+  We will not discuss this consideration any further other than to note that we explain the difference between "Birds lay eggs" and "Birds are female" by a different mechanism but that the notion of alternative features may come into play with feature-wise comparison classes (described above).
+]
+On this account, generics are true if only some Ks have F if all counterinstances are negative and the property is either characteristic or striking. 
 If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
 
+#### Striking generics
+
 The evolutionary argument for accepting striking generics is straightforward: These are relevant properties to know about if you want to survive. 
-But there are two other factors that are confounded with striking properties that make it difficult to make a claim about strikingness *per se* leading to generic endorsement.
+But there are two other factors that are confounded with striking properties that make it difficult to make a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
 The first is that striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
-Thus, the prevalence prior distributions of these features are hard to distinguish from properties that are just generally rare and distinctiveness (e.g., having extraordinarily beautiful feathers). 
+Thus, the prevalence prior distributions of these features are hard to distinguish from properties that are just generally rare and distinctiveness (e.g., having extraordinarily beautiful feathers; see also our Expt.
+2a, e.g., the distributions for *steals cars* vs.
+*climbs mountains*).
 @Cimpian2010 (Expt.
 4) can be seen as evidence for this point: In that experiment, participants show a willingness to endorse both generics about striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
-This increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$  distributions for the two are similar. 
-Those experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prior distribution over the prevalence changes to resemble that of a distinctive property when supplied information about the dangerousness of the feature.
-
-The second factor confounded with striking properties, which Leslie herself uses as motivation for their distinction, is that striking properties are projected more strongly (i.e., generalized to more instances of the category) than neutral properties.
-Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral, statistically low-probability properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
+This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$  distributions for the two are similar.
+Those experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prior distribution over the prevalence changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
+
+The second factor confounded with striking properties Leslie herself cites as motivation for their distinction.
+This factor is that striking properties are projected more strongly (i.e., generalized to more instances of the category) than neutral properties.
+Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
 2 & 3].
 This provides evidence for the influence of strikingness on *predictive prevalence*, which we posit is the second intermediate representation between conceptual knowledge and generic endorsements.
-
-The notion of *characteristic* properties is the same as @Prasada2006's notion of a *k-property*, which is a property that bears a *principled connection* to the kind. 
-Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self locomotion; @Goodman1955; @Shipley1993].
-
-\mht{from above:
-Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
-The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
-The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
-}
-
-The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
-\ndg{actually, i think it's better to have a specific section for these conceptual theories here.
-can leave a but of high-level discussion of prevalence priors in relation to bayesian intuitive theories above, and then talk about details of leslie and prasada here...}
-We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
-
-For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this separation provides a more unifying view of the phenomena of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
-
-In addition, our model provides a path towards unifying conceptual and statistical approaches to generics. 
-Our semantic representation is inherently statistical: Natural language semantics only gets to operate on prevalence. 
-At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.
+Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness above and beyond these mediating factors.
+
+#### Principled and statistical connections
+
+@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), which is a property that bears a *principled connection* to the kind. 
+A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
+"Ks, by virtue of being the kind of things that they are, F" (e.g., "Dogs, by virture of being the kind of things that they are, are four-legged"); if such a sentence is not endorsed (e.g., "Barns, by virture of being the kind of things that they are, are red") while the simple bare plural is endorsed (e.g., "Barns are red"), then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
+@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties displayed by a minority of the kind, striking properties, etc., see our Expt.
+1) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog"), and there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
+
+Where do principled connections come from? 
+Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic (or having a principled connection) if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self locomotion; @Goodman1955; @Shipley1993].
+Overhypotheses are naturally formalized as hierarchical Bayesian models, wherein a learner acquires knowledge at multiple levels of abstraction [e.g., learning from the same event about a particular dog, dogs in general, and animals in general; @Kemp2007a].
+Incorporating a hierarchical model of kinds and properties into our model of generic language is an intruiging direction towards understanding the computational underpinnings of principled connections.
+Furthermore, we find it an exciting possibility that different conceptual structures give rise to roughly the same distributions on prevalence, while nonetheless listeners draw different inferences from generic statements [a la the differences observed for "prevalence-matched items" in @Prasada2006].
+Such a result would not contradict our model, but which does require further elaboration of how those different conceptual structures relate to beliefs about prevalence.
+
+<!-- , and thus, even though the generic can imply the same prevalence, listeners have overall different inferences (e.g., about the *virtue of* sentence). -->
+
+<!-- The focus of this other empirical work is about highlighting the differences among generics, while our focus is to highlight what is common. -->
+
+<!-- Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011].
+-->
+<!-- For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations). -->
+<!-- @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.  -->
+
+<!-- our account is really about what is common among generics, and this is about what is differnet -->
+<!-- this is an interesting, albeit crude, result.
+if true, then this is really about different conceptual structures giving rise to roughly the same distributions on prevalence.
+even though the generic can imply the same prevalence, you have overall different inferences.
+our account is really about what is common among generics, and this is about what is differnet.
+-->
 

### 2018-04-24 paper/comgen-paper.Rmd
final edits throughout discussion, add alternative haslanger analysis, update bib

--- 2018-04-20 paper/comgen-paper.Rmd
@@
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
-Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].
+Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
 Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].
@@
 
-The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to eachother succinctly in language.
-Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
+The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly in language.
+Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
 We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability.
@@
 We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-In each case our model provided strong quantitative fit to human judgements.
+In each case, our model provided strong quantitative fit to human judgements while other models fall short.
+
+Ours is a psychological model that leverages the insights of truth-functional semantics to articulate how an agent should update their beliefs based on a generic sentence. 
+The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
+Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+Here, we demonstrate how the context-sensitivity of generics can emerges via the interplay of a stable (but vague) semantics and diverse background knowledge.
+
+\mht{unsure about this paragraph... a version of it may be better for the cover letter (if at all)}
+<!-- Not all theories are created equal, however.  -->
+Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and leave it to intuition to decide for a particular generic statement, what kind of generic it is.
+In this paper alone, our theory has made hundreds of predictions about the endorsement of individual generic statements, with high accuracy, derived from a general theory that we posit applies to all generic statements.
+In addition, previous accounts are rarely general enough to include generalizations of different semantic types (e.g., *habituals*) and deal only with generics.
+For these reasons alone, our account is novel.
 
@@
 
-\mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)}
-
-\ndg{
-[these paragraphs were out of place here. perhaps incorporate later...]
-By precisely articulating the conditions under which generalizations are true or false, we are able to describe how an agent should update its beliefs based on that sentence. 
-Thus, in addition to providing a quantitative understanding of the phenomena of the language of generalization, formalizing this language opens up the possibility of building models that learn abstract, generalizable knowledge from language.
-xx
-We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
-These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data.
-<!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
-A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement. 
-That is precisely what our information-theoretic model does.
-xx
-The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge.
-This formal separation is a key advancement beyond previous theoretical accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
-Our communicative framework also includes a model of a listener who interprets generalization.
-Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work. 
-}
+<!-- Thus, in addition to expressing a precise hypothesis about the truth conditions of generics, instantiating it in a cognitive model opens up the possibility of building more elaborate models that learn abstract, generalizable knowledge from language.
+-->
+
+<!-- We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
+-->
+<!-- These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data. -->
+<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} --> -->
+<!-- A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement.  -->
+<!-- That is precisely what our information-theoretic model does. -->
+<!-- xx -->
+<!-- The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge. -->
+
+<!-- That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
+-->
+<!-- Our communicative framework also includes a model of a listener who interprets generalization. -->
+<!-- Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work.  -->
+
+<!-- \mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)} -->
+
+<!-- \ndg{ -->
+<!-- [these paragraphs were out of place here. perhaps incorporate later...] -->
+<!-- } -->
 <!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->
@@
 This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-These predictive probabilities are fundementally mental representations and not observable frequencies, the object of other statistical approaches to genericity.
+These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
 Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
+Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
 What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
@@
 Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the numerical language used to convey explicit probabilities, a historically quite recent innovation [cf., @Levinson1995].
-Rather than conveying probabilities *explicitly*, generalizations convey them *implicitly*.
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
+Rather than conveying probabilities explicitly, generalizations convey them implicitly.
 In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
@@
 We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
-The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
+The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about prevalence), which language interfaces with via the tools of truth-functional semantics.
 Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
@@
 The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
-Our model distinguishes the semantic contribution of an utterance from a speaker's utility in producing that utterance. 
-For simplicity, the mode presented here assumes these two are the same: they are both about prevalence. 
-However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions (i.e., if the communicative goal is less about prevalence and more about the kind of thing that the referent is).
-This behavior is promising for constructing models of generalizations that teach about the abstract relations present in intuitive theories of kinds and properties.
+Not only does conceptual knowledge influence interpretation via prevalence priors, but it may very well be what the speaker intends to communicate.
+Like other probabilistic pragmatic models, our model distinguishes the semantic contribution of an utterance (what enters into the truth-functional semantics) from a speaker's utility in producing that utterance.
+For simplicity, the model presented here assumes these two are the same: the speaker's utility comes from conveying prevalence. 
+However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006].
+This result is promising for constructing models of speakers with the goal of teaching about the abstract relations between kinds and properties.
 
@@
 Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations highlighted in this paper.
-An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
-Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
-In this paper, we do not include such a mechanism in our model, instead we made the comparison class clear to participants when possible in order to study the remaning context-sensitivity with generics.
+An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
+Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the utterance in context [@Tessler2017].
+In this paper, we do not include such a mechanism in our model; instead, when possible, we make the comparison class clear to participants in order to study the remaning context-sensitivity with generics.
 <!-- \ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.} -->
@@
 
-Finally, the comparison classes used in our case studies were with always respect to the category (*other animals*, *other people*, *other possible causes*).
+Finally, the comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
 Thus, our endorsement model assumes the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has feature?".
@@
 It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
-The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*" e.g., when said sardonically).
-Prosodic focus easily gates between these interpretations (e.g., "[Lawyers] care about the law" vs. "Lawyers care about [the law]").
-\ndg{mention that prosodic focus easily switches between these.}
+Prosodic focus can gate between different interpretations: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
+Pragmatic reasoning is likely useful as well [cf., @Declerck1986; @Tessler2017].
 In this work, we focused on category-wise comparison classes purely for methodological convenience.
@@
 <!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
-Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, in fact, easier to formalize but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
+Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
 <!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generalizations [@Leslie2008].
+This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
 
 Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
-With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning at least three distinct aspects of meaning:
-(1) the *dimension* being described (i.e., probability $p$),
+With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning three distinct aspects of meaning:
+(1) the *dimension* being described (i.e., prevalence $p$),
 (2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
@@
 Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
-However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
-Thus, under our framework, generalizations should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
+However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
+Thus, under our framework, generics should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
@@
 -->
-Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$
+We have assumed the truth functional threshold $\theta$ comes from a uniform distribution over the unit interval $[0, 1]$, which is mathematically equivalent to a *continuously-valued* or *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$.
+The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $Lit(p \mid u) \propto p \cdot P(p)$
 This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
 The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-We leave for future work the precise implementation of the acquisition model we sketch out here.
+We leave for future work the precise implementation of the acquisition model sketched out here.
 
@@
 
-The present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in the formal semantics  literature.
+The present paper presents the first formal theory of genericity in language that generates quantitative predictions about human behavioral data. 
+A number of other theories of genericity have been proposed in formal semantics and in psychology, which posit different constructs or psychological mechanisms to account for the context-sensitivity of generics.
+These accounts fall into two broad camps: Those that appeal to quantification or the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations or abstract beliefs (e.g., *there is something about being K which causes it to F*).
+Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
+
+In our account, the core meaning of generics concerns probability (the currency of belief), which in many cases may be the byproduct of rich conceptual structure. 
+The separation between conceptual structure (which exists in the head) and prevalence (a quantitative metric for natural language semantics) provides a unified view of the phenomena of generics and a single answer to the semantic question: "what do generics mean?"
+By formalizing how background knowledge influences generic understanding, our model provides a path towards unifying conceptual approaches to generics with an inherently statistical natural language semantics.
+<!-- At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.  -->
+
+<!-- By contrast, our theory has made hundreds of predictions about individual generic statements, derived from a general theory that we posit applies to all generic statements. -->
 <!-- We now turn to situating our account with respect to these previous theories. -->
@@
 -->
-These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
 
@@
 
-\mht{from above:
-Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
-Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
-The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
-The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
-}
-
-The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
-\ndg{actually, i think it's better to have a specific section for these conceptual theories here.
-can leave a but of high-level discussion of prevalence priors in relation to bayesian intuitive theories above, and then talk about details of leslie and prasada here...}
-We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
 Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
-We believe this separation provides a more unifying view of the phenomena of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.
-
-In addition, our model provides a path towards unifying conceptual and statistical approaches to generics. 
-Our semantic representation is inherently statistical: Natural language semantics only gets to operate on prevalence. 
-At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.
+The most influential account in psychology comes from @Leslie2008. 
+Leslie uses the same starting point as our account: Generics express generalization. 
+She then turns her attention to the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.^[
+  Because the mechanism for understanding generics is innate, in her account, the learning puzzle (vis a vis quantifiers) immediately goes away.
+]
+Leslie describes the *default generalization* mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
+  This positive vs.
+negative counterinstance distinction is a rather technical consideration [though not without psychological foundation, see @Leslie2008, p.36] used to account for the difference between examples like "Birds lay eggs" vs.
+"Birds are female".
+  For the latter, male birds are positive counterinstances because they have an alternative property (being male). 
+  For the former, male birds are negative counterinstances because they simply lack the property (i.e., male birds do not reproduce by some other method).
+  We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by by a different mechanism (e.g., informativity with respect to a prevalence prior).
+  The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described above).
+]
+On this account, generics are true if *some* Ks have F when all counterinstances are negative and the property is either characteristic or striking. 
+If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
+
+#### Striking generics
+
+The evolutionary argument for accepting striking generics (e.g., "Tigers eat people") is straightforward: These are relevant properties to know about if you want to survive. 
+But there are two other factors that are confounded with striking properties that make it difficult to evaluate a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
+The first is that striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
+Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*; see also our Expt.
+2a, e.g., the distributions for *steals cars* vs.
+*climbs mountains* for an example with habituals).
+@Cimpian2010 (Expt.
+4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
+This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar.
+@Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
+
+The second factor confounded with striking properties is that striking properties may be projected more strongly (i.e., generalized to more instances of the category) than neutral properties.^[
+  This observation is also made by @Leslie2008 (p.42), who uses it as motivation for elevating striking properties to their special status in her theory.
+]
+Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
+2 & 3].
+Thus, there is evidence for the influence of strikingness on *predictive prevalence*, which we posit is an intermediate representation between conceptual knowledge and generic endorsements.
+Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
+
+#### Principled and statistical connections
+
+@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), which is a property that bears a *principled connection* to the kind. 
+A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
+"Ks, by virtue of being the kind of things that they are, F" (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged"); if such a sentence is not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple bare plural is endorsed (e.g., "Barns are red"), then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
+@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties with low prevalence, striking properties, etc., see our Expt.
+1) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
+Additionally, there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
+
+Where do principled connections come from? 
+Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic (or having a principled connection) if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self locomotion; @Goodman1955; @Shipley1993].
+Overhypotheses are naturally formalized as hierarchical Bayesian models, wherein a learner acquires knowledge at multiple levels of abstraction [e.g., learning from the same event about a particular dog, dogs in general, and animals in general; @Kemp2007].
+Incorporating a hierarchical model of kinds and properties into our model of generic language is a natural future direction towards understanding the computational underpinnings of principled connections.
+Furthermore, we find it an exciting possibility that different conceptual structures may give rise to roughly the same distributions on prevalence (and thus have the same implied prevalence interpretation from our model), while nonetheless human listeners draw different inferences from generic statements [a la the differences observed for "prevalence-matched items" in @Prasada2006].
+Such a result would not contradict our model, but would require further elaboration of how different conceptual structures relate to beliefs about prevalence.
+
+<!-- , and thus, even though the generic can imply the same prevalence, listeners have overall different inferences (e.g., about the *virtue of* sentence). -->
+
+<!-- The focus of this other empirical work is about highlighting the differences among generics, while our focus is to highlight what is common. -->
+
+<!-- Rich, structural mental representations can be formalized in probabilistic models, which can be used to derive quantitative predictions about inferences derived from that knowledge [@Tenenbaum2011].
+-->
+<!-- For example, @Kemp2008 introduced a model for learning different kinds of structural relationships between objects and properties (e.g., taxonomies, social cliques, dominance relations). -->
+<!-- @Goodmanconcepts argue that concepts and intuitive theories can be constructed from elementary random primitives using insights from *probabilistic programmming*.  -->
+
+<!-- our account is really about what is common among generics, and this is about what is differnet -->
+<!-- this is an interesting, albeit crude, result.
+if true, then this is really about different conceptual structures giving rise to roughly the same distributions on prevalence.
+even though the generic can imply the same prevalence, you have overall different inferences.
+our account is really about what is common among generics, and this is about what is differnet.
+-->
 
@@
 
-In our model, we do not draw a *relative* vs. *absolute* distinction, instead treating all generics as relative. 
-Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge.^[
-  For a related theory argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
+In our model, we treat all generics as relative. 
+Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge withour uncertain semantics.^[
+  For a related theoretical argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
 ]
 Further, though Cohen's theory is framed in terms of probabilities, it is a fully semantic, fixed-threshold account which only makes deterministic predictions about what is true and what is false.
-In contrast, we posit an uncertain threshold which is resolved through a Bayesian interpretation model; our theory is a joint semantic--pragmatic theory.
+In contrast, we posit an uncertain threshold which is resolved in context through Bayesian inference; our theory is a joint semantic--pragmatic theory.
 
@@
 
-We note additional machinery that Cohen's theory relies upon (and that is not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of *laying eggs* among *robins*?).
-His theory posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
-For example, the property "lays eggs" induces a set of alternatives that are associated with mechanisms of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
+We note an additional mechanisms that Cohen's and other statistical theories rely upon (and not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
+This mechanism is called *domain restriction*. 
+@Cohen1999 posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
+For example, the property "lays eggs" induces a set of alternatives that are associated with modes of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
 "Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery behind Cohen's domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+The inferential machinery domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
 ]
-However, we note that this mechanism may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+The mechanism of domain restriction may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
 Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
@@
 
-### Generic as indexical
-
-@Sterken2015 has proposed analyzing generic statements as inherently context-sensitive, analogous to *indexicals* (e.g., "this" or "I").
-Variability of endorsements is attributed by @Sterken2015 to context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999, and many others].
-Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive "quantificational force". 
+#### Generic as indexical
+
+@Sterken2015 takes a novel starting point for her analysis: Generics are inherently context-sensitive.
+To understand the properties of generics, she looks to another inherently context-sensitive part of language: *indexicals* (e.g., "this" or "I").
+@Sterken2015 posits a context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999 and others].
+Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive *quantificational force*. 
 We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
@@
 However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described above) and stereotyped language (e.g., "Boys are good at math”).
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described in more detail below) and stereotyped language (e.g., "Boys are good at math”).
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
@@
 The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
-Our semantic theory can be seen as a generalization of the *underquantification* to a continuous interval of possible meanings.
+Our semantic theory can be seen as a generalization of *underquantification* to a continuous interval of possible meanings.
 This distinction is relevant for the acquisition of the language of generalizations; we do not take as primary the quantified relations (e.g., "Some", "All").
@@
 
-In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted tests of our model vis-a-vis alternative models.
+In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
 We close by discussing how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
@@
 
-Our focus on predictive probability makes even novel predictions about some classic puzzles.
+Our focus on predictive probability even makes novel predictions about some classic puzzles.
 Sentence (2) is the conceptual opposite of sentence (1).
@@
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number*---the shear auspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
-That is, we predict there are situations where statements like (2) could be considered felicitous generalizations.
-
-Understanding how a semantic representation *composes* is another critical test for a theory of generalizations in language.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
+That is, our theory predicts there are situations where statements like (2) could be considered felicitous generalizations.
+
+Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
 @Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Statistical accounts of generalizations have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather not have to posit.
-This is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics (e.g., if the generic means *most*).
+Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
+However, such is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics, as posited in most statistical views of generics (e.g., if the generic means *most*).
 Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with prior knowledge pushing against the existence of *international elephants* and without any further semantic assumptions, our model can interpret Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
+In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
   An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
 ]
-Importantly, an incremental parsing of Sentence (3) leads our model to first believe that *most* elephants live in Africa (when it only hears that "Elephants live in Africa"), and then later believe that *some* elephants live in Africa (while others live in Asia) after hearing the end of the utterance ("...and Asia").
+Interestingly, an incremental parsing of Sentence (3) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia.
 Our model flexibly accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
@@
 Then, "is a paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
-  Note that this idea is related to @Cohen1999's notion of "Relative generics" (described more fully below), which have truth conditions that are determined by a comparison to an alternative set of Ks (his   Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an alternative set of Fs.
+  Note that this idea is related to @Cohen1999's notion of "Relative generics" (described above), which have truth conditions that are determined by a comparison to an alternative set of Ks which is composed of Ks that could satisfy some F in an alternative set of Fs.
 ]
@@
 
-Finally, a property can be widespread relative to other kinds or groups as well as being so systemic that we would predict it to be the case in the future, and speakers still might find it aversive to actually endorse the generalization.
-Such is the situation with Sentence (5) [@Haslanger2011]. 
-Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
+Finally, Sentence (5) suggests that a property can be widespread relative to other kinds or groups, as well as being so systemic that we would predict it to be the case in the future (high *predictive prevalence*), and speakers still might find it aversive to actually endorse the generalization [@Haslanger2011].
+<!-- Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
+-->
 In our **Model Simulations** section, we showed that the generalization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
@@
 This kind of extension to rational models of communication has already been used to account for a variety of phenomena in *polite language* use [@Yoon2016; @Yoon2017].
-We propose adopting such a value-based utility structure for states of the world for language about social categories: If the speaker found states of the world where the probability of the feature is high as undesirable (e.g., a world where many women were submissive), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
+Such a value-based utility structure for states of the world for language about social categories may capture intuitions like those about Sentence (5): If the speaker found states of the world where the probability of the feature is high as undesirable (e.g., a world where many women were submissive), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
+
+An alternative information-theoretic analysis of (5) could be made concerning the conceptual structure communicated by generalizations (see earlier discussion of *Prevalence Priors and Conceptual Structure*).
+Suppose there are two possible causes for a person to be submissive: Either it is in their DNA or the person was socialized in such a way as to be submissive. 
+Were either of these possible causes to exist for a particular group (e.g., women), then high prevalence of the property would be expected in that group. 
+A speaker may intend to communicate not the high prevalence, however, but what she believes is the generative cause of that high prevalence (i.e., either that there is an internal, DNA cause or an external, societal cause).
+Suppose the speaker wants to communicate that she believes an external, societal cause is leading to high prevalence of submissiveness.
+The decision to endorse (5) depends upon what the speaker believes her listener will infer. 
+If she is in a group of close friends discussing the ways in which society shapes behavior, the speaker may opt to endorse (5) because with high probability, she will be understood as endorsing the external, society cause.
+However, if she is worried that some might take her to mean that there's something about women that causes them to be submissive, the speaker may refrain from uttering (5).
+Such an explanation would be a purely information transmitting account that does not require any social utility to explain the behavior.
 

### 2018-04-24 paper/comgen-paper.Rmd
typo

@@
 <!-- These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data. -->
-<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} --> -->
+<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
 <!-- A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement.  -->

### 2018-05-08 paper/appendix-cueValidity.Rmd
refactor cue validity appendix to load rather than compute results

@@
-```{r echo = F}
-library(langcog)
-library(tidyverse)
-library(ggthemes)
-library(jsonlite)
-theme_set(theme_few())
-project.path <- "../"
-data.path <- "data/generics/endorsement/"
-substrRight <- function(x, n){
-  substr(x, nchar(x)-n+1, nchar(x))
-}
+```{r}
+fill.colors <- RColorBrewer::brewer.pal(3, "Set1")
 ```
@@
 
-```{r directQuestion, echo = F}
-d.cv.dq <- read.csv(paste(project.path, data.path, "cue-validity-1-trials.csv", sep = ""))
+```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, fig.cap="Top: Empirically measured cue validity for two different tasks.
+Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
+Dotted lines denote theoretical cue validity representing the desiderata (see text).
+Error bars denote bootstrapped 95% confidence intervals.
+Bottom left: Raw empirical distributions for direct question task.
+Bottom right: Correspondence between measured cue validity and prevalence prior derived cue validity."}
+load("cached_results/appendix_cueValidity_results.RData")
+# d.cv.bothtasks, d.cv.targets, undiagnostic.props
+# md.fp, md.dq
 
@@
 
-d.cv.targets <- left_join(
-  d.cv.dq %>%
-    mutate(property = gsub("&quotechar", "'", property), 
-         item = paste(category, property)),
-  target.items) %>%
-  filter(!is.na(type)) %>%
-  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))
-
-d.cv.summary <- d.cv.targets %>%
-  group_by(item, type) %>%
-  multi_boot_standard(col = "response")
-
-# ggplot(d.cv.summary, aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
-#   geom_bar(stat = 'identity', position = position_dodge())+
-#   geom_errorbar(position = position_dodge())+
-#   facet_wrap(~type, scales = 'free')+
-#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-#   theme(axis.text.x = element_text(angle = 90))+
-#   xlab("")+
-#   ylab("Probability rating of cue validity")+
-#   ggtitle("Direct question paradigm")
-
-```
-
-```{r freeProduction, echo = F}
-d.cv.fp <- read.csv(paste(project.path, 
-                          data.path, "cue-validity-2-freeProduction-trials-n100.csv", sep = ""))
-
-mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")
-
-d.cv.fp <- left_join(
-  d.cv.fp %>%
- # rename(property = category) %>%
-  mutate(response = tolower(response),
-         response = gsub(" ", "", response),
-         response = ifelse(substr(response, 1, 5) %in% mosquito.mispellings, "mosquito", response),
-         response = ifelse(response == "deertick", "tick", response),
-         response = ifelse(substrRight(response, 1) == "s",
-                           substr(response, 1, nchar(response)-1), response),
-         property = gsub("&quotechar", "'", property),
-         item = paste(response, property)),
-    target.items)
-
-d.cv.fp.summary <- left_join(
-  target.items,
-  d.cv.fp %>%
-    rename(category = response) %>%
-    group_by(property) %>%
-    mutate(n = n()) %>%
-    filter(!(is.na(type))) %>%
-    group_by(category, property, item) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials)
-  ) %>%
-  mutate(prop = ifelse(is.na(prop), 0.01, prop)) %>%
-  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))
-
-d.cv.bootstrapped <- data.frame()
-resample_n <- length(levels(factor(d.cv.fp$workerid)))
-for (i in 1:100){
-
-  d.cv.bsample <-left_join(
-    target.items,
-    d.cv.fp %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-    group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property))
-    ) %>%
-    group_by(category, property, item, type) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
-}
-
-empiricalLower = function(dist){
-  xi <- quantile(dist, 0.025)
-  return (xi[["2.5%"]])
-}
-empiricalUpper = function(dist){
-  xi <- quantile(dist, 0.975)
-  return (xi[["97.5%"]])
-}
-empiricalMean = function(dist){
-  xi <- quantile(dist, 0.5)
-  return (xi[["50%"]])
-}
-
-d.cv.fp.summary <- d.cv.bootstrapped %>%
-      group_by(item, type) %>%
-      summarize(mean = empiricalMean(prop),
-                ci_lower = empiricalLower(prop),
-                ci_upper = empiricalUpper(prop)) %>%
-  mutate(
-    ci_lower = ifelse(is.na(mean), 0.01, ci_lower),
-    ci_upper = ifelse(is.na(mean), 0.01, ci_upper),
-    mean = ifelse(is.na(mean), 0.01, mean)
-  )
-
-d.cv.bothtasks <- bind_rows(
-  d.cv.summary %>% mutate(task = 'direct question'),
-  d.cv.fp.summary %>% mutate(task = 'free production')
-)
-
 theoretical.cv <- data.frame(
@@
 
-```
-
-```{r}
 cv.bothquestions.bars <- d.cv.bothtasks %>%
@@
   guides(color = F)
-```
 
-```{r dq.histogram}
 dq.histograms <- ggplot(d.cv.targets %>%
@@
   ylab("Number of responses")
-```
 
-```{r}
-diagnostic.props <- data.frame(
+diagnostic.props2 <- data.frame(
   item = c("kangaroo has a pouch", "lion has a mane", 
@@
 
-undiagnostic.props <- data.frame(
+undiagnostic.props2 <- data.frame(
   item = c("leopard is juvenile", "lion is male", "robin is female", "swan is full-grown"),
@@
 
-false.props <- data.frame(
+false.props2 <- data.frame(
   item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
@@
 
-target.items2 <- bind_rows(diagnostic.props, undiagnostic.props, false.props)
-```
-
-```{r cv-fp-data-analyzeAll, cache = T}
-d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
-  mutate(
-    property = gsub("'", "", property),
-    Property = gsub("'", "", Property),
-    sentence = paste(Category, Property),
-    item = paste(category, property))
-
-d.cv.bootstrapped.all <- data.frame()
-resample_n <- length(levels(factor(d.cv.fp$workerid)))
-for (i in 1:1000){
-
-  d.cv.bsample <- d.cv.fp %>% 
-    select(workerid, property, response) %>% 
-    spread(property, response) %>% 
-    sample_n(resample_n, replace = TRUE) %>%
-    gather(property, category, -workerid) %>% 
-        group_by(property) %>%
-    mutate(n = n(),
-           item = paste(category, property)) %>%
-    filter(item %in% d.target.items$item) %>%
-    group_by(category, property) %>%
-    summarize(mentions = n(),
-              trials = mean(n), # mean(n) == n, because it's just the number of subjects
-              prop = mentions / trials,
-              prop = ifelse(is.na(prop), 0.01, prop),
-              iteration = i)
-
-  d.cv.bootstrapped.all <- bind_rows(d.cv.bootstrapped.all, d.cv.bsample)
-}
-
-d.gen.cv.all.summary <- left_join(
-    d.target.items %>% select(-sentence),
-    d.cv.bootstrapped.all %>%
-      group_by(category, property) %>%
-      summarize(cv_mean = empiricalMean(prop),
-                cv_ci_lower = empiricalLower(prop),
-                cv_ci_upper = empiricalUpper(prop))
-) %>%
-  mutate(
-    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
-    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
-    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
-  )
-
-```
-
-```{r cuevalidity-model-pk}
-wp.pkg.path <- paste(project.path, "models/generics/node_modules/utils/", sep = "")
-
-cueValidityModel1 <- '
-var cueValidity = function(){
-  var kind = uniformDraw(data.prior);
-  observe(Bernoulli({p: kind.prevalence/100}), true)
-  return kind.Category == data.kind[0]
-}
-
-expectation(Infer({model: cueValidity}))
-'
-
-d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
-                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-
-d.gen.endorse.priors <- read.csv(paste(project.path, 
-                                       "data/generics/endorsement/",
-                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
-gen.endorse.properties <- levels(d.gen.endorse.priors$Property)
-
-wp.cueValidity <- data.frame()
-for (p in gen.endorse.properties){
-  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
-  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)
-
-  for (catg in categories){
-
-    dataToPass <- list(
-      prior = prevPriorData,
-      kind = catg
-    )
-
-    wp.rs <- webppl(cueValidityModel1, 
-       data_var = "data",
-       data = dataToPass)
-
-    wp.cueValidity <- bind_rows(wp.cueValidity, 
-                                data.frame(Category = catg,
-                                           Property = p,
-                                           cv = wp.rs))
-
-  }
-  #print(p)
-}
-# save(wp.cueValidity, file =
-#        paste(project.path, model.path,
-#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
-# load(file = 
-#        paste(project.path, model.path, 
-#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
-```
-
-```{r}
-md.fp <- left_join(left_join(
-  d.gen.cv.all.summary,
-  wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
-  #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
-), target.items2) %>%
-  mutate(type = ifelse(is.na(type), "other", type),
-           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
-                       labels = c("diagnostic", "undiagnostic", "false", "other")))
-
-fill.colors <- RColorBrewer::brewer.pal(3, "Set1")
-
-# ggplot(md.fp, aes (x = prev_prior_derived_cv, y = cv_mean, ymin = cv_ci_lower, ymax = cv_ci_upper,
-#                    color = type))+
-#   #scale_alpha_manual(values = c(1,1,1,0.5))+
-#   geom_errorbar(alpha = 0.4)+
-#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-#   geom_point(data = md.fp %>% filter(type == "other"), size = 2)+
-#   geom_point(data = md.fp %>% filter(!(type == "other")), size = 2)+
-#   coord_fixed()+
-#   #scale_color_solarized()+
-#   scale_color_manual(values = c(fill.colors, "grey8"))+
-#   xlab("Prevalence Prior Derived Cue Validity")+
-#   ylab("Free Production Measured Cue Validity")+
-#   theme(legend.title = element_blank())
-
-r2.fp <- compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
-mse.fp <- compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
-n.fp <- length(md.fp$item)
-
-md.fp.desid <- md.fp %>%
-  filter(item %in% target.items2$item)
-
-r2.fp.desid <- compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
-mse.fp.desid <- compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
-n.fp.desid <- length(md.fp.desid$item)
-```
-
-```{r}
-d.cv.dq.all <- d.cv.dq %>%
-  mutate(property = gsub("&quotechar", "", property), 
-         item = paste(category, property)) %>%
-  group_by(category, property) %>%
-  multi_boot_standard(col = 'response')
-
-md.dq <-  left_join( left_join(
-    left_join(
-    d.gen.cv.all.summary %>% select(Category, Property, category, property, item),
-    d.cv.dq.all),
-    #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
-    wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
-  ), target.items2) %>%
-  mutate(type = ifelse(is.na(type), "other", type),
-           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
-                       labels = c("diagnostic", "undiagnostic", "false", "other")))
-
-# ggplot(md.dq, aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
-#                      color = type))+
-#   geom_errorbar(alpha = 0.4)+
-#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
-#   geom_point(data = md.dq %>% filter(type == "other"), size = 2)+
-#   geom_point(data = md.dq %>% filter(!(type == "other")), size = 2)+
-#   coord_fixed()+
-#   #scale_color_solarized()+
-#   scale_color_manual(values = c(fill.colors, "grey8"))+
-#   xlab("Prevalence Prior Derived Cue Validity")+
-#   ylab("Direct Question Measured Cue Validity")+
-#   theme(legend.title = element_blank())
-# 
-#   
-r2.dq <- compute_r2(md.dq, "mean", "prev_prior_derived_cv")
-mse.dq <- compute_mse(md.dq, "mean", "prev_prior_derived_cv")
-n.dq <- length(md.dq$item)
-
-md.dq.desid <- md.dq %>%
-  filter(item %in% target.items2$item)
-
-r2.dq.desid <- compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
-mse.dq.desid <- compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
-n.dq.desid <- length(md.dq.desid$item)
+target.items2 <- bind_rows(diagnostic.props2, undiagnostic.props2, false.props2)
 
@@
   facet_wrap(~src)
-```
 
-```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, fig.cap="Top: Empirically measured cue validity for two different tasks.
-Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
-Dotted lines denote theoretical cue validity representing the desiderata (see text).
-Error bars denote bootstrapped 95% confidence intervals.
-Bottom left: Raw empirical distributions for direct question task.
-Bottom right: Correspondence between measured cue validity and prevalence prior derived cue validity."}
 grid.arrange(cv.bothquestions.bars, 
@@
                                    ))
+
+```
+
+```{r}
+# d.cv.bothtasks, d.cv.targets, undiagnostic.props
+# md.fp, md.dq
+
+r2.fp <- compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
+mse.fp <- compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
+n.fp <- length(md.fp$item)
+
+md.fp.desid <- md.fp %>%
+  filter(item %in% target.items2$item)
+
+r2.fp.desid <- compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+mse.fp.desid <- compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
+n.fp.desid <- length(md.fp.desid$item)
+
+r2.dq <- compute_r2(md.dq, "mean", "prev_prior_derived_cv")
+mse.dq <- compute_mse(md.dq, "mean", "prev_prior_derived_cv")
+n.dq <- length(md.dq$item)
+
+md.dq.desid <- md.dq %>%
+  filter(item %in% target.items2$item)
+
+r2.dq.desid <- compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
+mse.dq.desid <- compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
+n.dq.desid <- length(md.dq.desid$item)
+
 ```
@@
 We conclude that researchers interested in generic truth conditions should use a free production paradigm for measuring cue validity.
-
-```{r cvModel-uniformPrior, eval = F}
-cueValidityModel2 <- '
-var cueValidity = function(){
-  var kind = uniformDraw(data.allKinds);
-  var responses = _.filter(data.prior, {Category: kind});
-  var response = _.isEmpty(responses) ? {prevalence: 0} : uniformDraw(responses);
-  observe(Bernoulli({p: response.prevalence/100}), true)
-  return kind == data.kind[0]
-}
-
-expectation(Infer({model: cueValidity}))
-'
-
-allKinds = levels(factor(d.gen.endorse.priors$Category))
-
-wp.cueValidity.uniform <- data.frame()
-for (p in gen.endorse.properties){
-  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
-  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)
-
-  for (catg in categories){
-
-    dataToPass <- list(
-      prior = prevPriorData,
-      kind = filter(prevPriorData, Category == catg)[1, "Category"],
-      allKinds = allKinds
-    )
-
-    wp.rs <- webppl(cueValidityModel2, data_var = "data", data = dataToPass)
-
-    wp.cueValidity.uniform <- bind_rows(wp.cueValidity.uniform, 
-                                data.frame(Category = catg,
-                                           Property = p,
-                                           cv = wp.rs))
-
-  }
-  print(p)
-}
-# save(wp.cueValidity, file = 
-#        paste(project.path, model.path, 
-#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
-# dataToPass %>% toJSON(.)
-# 
-# wp.rs
-
-```

### 2018-05-08 paper/comgen-paper.Rmd

@@
 
-The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly in language.
+The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to eachother succinctly using language.
 Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability.
+We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability or \emph{prevalence}.
 Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
@@
 -->
-We tested this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether it would be useful to utter the generalization. 
+We tested this theory by exploring its implications for truth judgments, modeled as a speaker's decision about whether it would be useful to utter the generalization. 
 Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
@@
 We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-In each case, our model provided strong quantitative fit to human judgements while other models fall short.
+In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
 
@@
 
+<!--
+NDG: i cut this from below...
+This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
+These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
+Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
+What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
+-->
+
+Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
+Rather than conveying probabilities explicitly, generalizations convey them implicitly.
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
+
+<!--
 \mht{unsure about this paragraph... a version of it may be better for the cover letter (if at all)}
-<!-- Not all theories are created equal, however.  -->
+\ndg{yeah, this is unecessarily inflamatory. ax it.}
 Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and leave it to intuition to decide for a particular generic statement, what kind of generic it is.
@@
 For these reasons alone, our account is novel. 
+-->
 
@@
 
-## Communicating predictive probabilities
-
-This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
-Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
-What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
-
 <!-- Expts.
@@
 -->
-
-Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
-Rather than conveying probabilities explicitly, generalizations convey them implicitly.
-In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
 
@@
 
-<!-- \ndg{this section is pretty critical, and needs work. or posisbly much of it belongs in the discussion of others sematic theoris?} -->
-
 Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
@@
 Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
-Actual conceptual knowledge against which generalizations are interpreted is most likely richer than our simple two-component prevalence distributions.
+Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions.
 
@@
 We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
-The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about prevalence), which language interfaces with via the tools of truth-functional semantics.
+The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
 Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
@@
 However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006].
-This result is promising for constructing models of speakers with the goal of teaching about the abstract relations between kinds and properties.
+This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.
 
@@
 The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations highlighted in this paper.
+Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
 An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
-Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the utterance in context [@Tessler2017].
-In this paper, we do not include such a mechanism in our model; instead, when possible, we make the comparison class clear to participants in order to study the remaning context-sensitivity with generics.
-<!-- \ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.} -->
+Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
+In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics.
 
@@
 
-Finally, the comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
-Thus, our endorsement model assumes the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has feature?".
+The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
+Thus, our endorsement model assumes that the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has this feature?".
 Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
 It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
-Prosodic focus can gate between different interpretations: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
-Pragmatic reasoning is likely useful as well [cf., @Declerck1986; @Tessler2017].
+Prosodic focus can change the interpretation: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
+Pragmatic reasoning is likely relevant here as well [cf., @Declerck1986; @Tessler2017].
 In this work, we focused on category-wise comparison classes purely for methodological convenience.
-Future work should investigate the factors that give rise to feature-wise interpretations of generalizations and how the relevant comparison classes are constructed.
+Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.
 
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
+This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., truth-functional notions) are inappropriate for generics [@Leslie2008].
 
@@
 The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-We leave for future work the precise implementation of the acquisition model sketched out here.
+We leave for future work the precise implementation of such an acquisition model.
 

### 2018-05-10 paper/comgen-paper.Rmd
some gd edits

@@
 The present paper presents the first formal theory of genericity in language that generates quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in formal semantics and in psychology, which posit different constructs or psychological mechanisms to account for the context-sensitivity of generics.
+A number of other theories of genericity have been proposed in formal semantics and in psychology, which posit different constructs or psychological mechanisms to account for the diversity of generics.
 These accounts fall into two broad camps: Those that appeal to quantification or the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations or abstract beliefs (e.g., *there is something about being K which causes it to F*).
@@
 
+\ndg{[this should go after other theories are introduced.]
 In our account, the core meaning of generics concerns probability (the currency of belief), which in many cases may be the byproduct of rich conceptual structure. 
@@
 By formalizing how background knowledge influences generic understanding, our model provides a path towards unifying conceptual approaches to generics with an inherently statistical natural language semantics.
+}
+
 <!-- At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.  -->
@@
 If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
+We believe that many of the key factors in this conceptual approach are compatible with our predictive probability approach: what is required is that the distinctions made by conceptual accounts influence predictive probability, which then mediates linguistic effects.
 
@@
 Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
+If there are none, then the effects of strikingness would be accounted for by our prevalence-mediated theory.
 
@@
 Overhypotheses are naturally formalized as hierarchical Bayesian models, wherein a learner acquires knowledge at multiple levels of abstraction [e.g., learning from the same event about a particular dog, dogs in general, and animals in general; @Kemp2007].
-Incorporating a hierarchical model of kinds and properties into our model of generic language is a natural future direction towards understanding the computational underpinnings of principled connections.
-Furthermore, we find it an exciting possibility that different conceptual structures may give rise to roughly the same distributions on prevalence (and thus have the same implied prevalence interpretation from our model), while nonetheless human listeners draw different inferences from generic statements [a la the differences observed for "prevalence-matched items" in @Prasada2006].
-Such a result would not contradict our model, but would require further elaboration of how different conceptual structures relate to beliefs about prevalence.
+These heirarchical models yield differences in predictive probability that are particularly robust.
+Integrating a hierarchical model of kinds and properties with our model of generic language is a natural future direction towards understanding the computational underpinnings of principled connections.
+Different conceptual structures may give rise to roughly the same distributions on prevalence and thus have similar endorsement profiles according to our model. 
+Yet the inferences that can be drawn from hearing these generics may differ, depeding on their interactions with the (possibly hierarchical) knowledge people bring to bear [a la the differences observed for "prevalence-matched items" in @Prasada2006].
+This is an intruiguing direction for future work.
 
@@
 In our model, we treat all generics as relative. 
-Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge withour uncertain semantics.^[
+Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge with our uncertain semantics.^[
   For a related theoretical argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
@@
 
-We note an additional mechanisms that Cohen's and other statistical theories rely upon (and not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
+Cohen's and other statistical theories rely upon an additional mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
 This mechanism is called *domain restriction*. 
@@
 "Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+The inferential machinery of domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.

### 2018-05-10 analysis/appendix-cueValidity.Rmd

---
title: "Analysis for cue validity appendix"
output: html_notebook
---

```{r echo = F}
library(tidyboot)
library(tidyverse)
library(ggthemes)
library(jsonlite)
library(rwebppl)
theme_set(theme_few())
project.path <- "../"
data.path <- "data/generics/endorsement/"
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
```

```{r directQuestion, echo = F}
d.cv.dq <- read.csv(paste(project.path, data.path, "cue-validity-1-trials.csv", sep = ""))

diagnostic.props <- data.frame(
  item = c("kangaroo has a pouch", "lion has a mane", 
           "mosquito carries malaria", "tick carries Lyme disease"),
  type = "diagnostic"
)

undiagnostic.props <- data.frame(
  item = c("kangaroo is juvenile", "lion is male", "robin is female", "leopard is full-grown"),
  type = "undiagnostic"
)

false.props <- data.frame(
  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
  type = "false"
)

target.items <- bind_rows(diagnostic.props, undiagnostic.props, false.props)

d.cv.targets <- left_join(
  d.cv.dq %>%
    mutate(property = gsub("&quotechar", "'", property), 
         item = paste(category, property)),
  target.items) %>%
  filter(!is.na(type)) %>%
  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))

d.cv.summary <- d.cv.targets %>%
  group_by(item, type) %>%
  tidyboot_mean(column = response)

# ggplot(d.cv.summary, aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
#   geom_bar(stat = 'identity', position = position_dodge())+
#   geom_errorbar(position = position_dodge())+
#   facet_wrap(~type, scales = 'free')+
#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
#   theme(axis.text.x = element_text(angle = 90))+
#   xlab("")+
#   ylab("Probability rating of cue validity")+
#   ggtitle("Direct question paradigm")

```

```{r freeProduction, echo = F}
d.cv.fp <- read.csv(paste(project.path, 
                          data.path, "cue-validity-2-freeProduction-trials-n100.csv", sep = ""))

mosquito.mispellings <- c("mosqu", "mesqu", "misqu", "mosiq")

d.cv.fp <- left_join(
  d.cv.fp %>%
 # rename(property = category) %>%
  mutate(response = tolower(response),
         response = gsub(" ", "", response),
         response = ifelse(substr(response, 1, 5) %in% mosquito.mispellings, "mosquito", response),
         response = ifelse(response == "deertick", "tick", response),
         response = ifelse(substrRight(response, 1) == "s",
                           substr(response, 1, nchar(response)-1), response),
         property = gsub("&quotechar", "'", property),
         item = paste(response, property)),
    target.items)

d.cv.fp.summary <- left_join(
  target.items,
  d.cv.fp %>%
    rename(category = response) %>%
    group_by(property) %>%
    mutate(n = n()) %>%
    filter(!(is.na(type))) %>%
    group_by(category, property, item) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials)
  ) %>%
  mutate(prop = ifelse(is.na(prop), 0.01, prop)) %>%
  mutate(type = factor(type, levels = c("diagnostic", "undiagnostic", "false")))

d.cv.bootstrapped <- data.frame()
resample_n <- length(levels(factor(d.cv.fp$workerid)))
for (i in 1:1000){

  d.cv.bsample <-left_join(
    target.items,
    d.cv.fp %>% 
    select(workerid, property, response) %>% 
    spread(property, response) %>% 
    sample_n(resample_n, replace = TRUE) %>%
    gather(property, category, -workerid) %>% 
    group_by(property) %>%
    mutate(n = n(),
           item = paste(category, property))
    ) %>%
    group_by(category, property, item, type) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials,
              prop = ifelse(is.na(prop), 0.01, prop),
              iteration = i)

  d.cv.bootstrapped <- bind_rows(d.cv.bootstrapped, d.cv.bsample)
}

empiricalLower = function(dist){
  xi <- quantile(dist, 0.025)
  return (xi[["2.5%"]])
}
empiricalUpper = function(dist){
  xi <- quantile(dist, 0.975)
  return (xi[["97.5%"]])
}
empiricalMean = function(dist){
  xi <- quantile(dist, 0.5)
  return (xi[["50%"]])
}

d.cv.fp.summary <- d.cv.bootstrapped %>%
      group_by(item, type) %>%
      summarize(mean = empiricalMean(prop),
                ci_lower = empiricalLower(prop),
                ci_upper = empiricalUpper(prop)) %>%
  mutate(
    ci_lower = ifelse(is.na(mean), 0.01, ci_lower),
    ci_upper = ifelse(is.na(mean), 0.01, ci_upper),
    mean = ifelse(is.na(mean), 0.01, mean)
  )

d.cv.bothtasks <- bind_rows(
  d.cv.summary %>% mutate(task = 'direct question'),
  d.cv.fp.summary %>% mutate(task = 'free production')
)

theoretical.cv <- data.frame(
  type = c( "false", "undiagnostic","diagnostic"),
  cv = c(0.05, 0.05, 0.95)
)

```

```{r}
cv.bothquestions.bars <- d.cv.bothtasks %>%
  ungroup() %>%
  mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
  ggplot(., aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge(0.5),
           width = 0.5, color = 'black', fill = 'white')+
  geom_errorbar(position = position_dodge(0.5), width = 0.3)+
  facet_grid(task~type, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  geom_hline(data = theoretical.cv, aes(yintercept = cv), lty = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        strip.text.y = element_text(angle = 0))+
  xlab("")+
  ylab("Cue validity")+
  guides(color = F)
```

```{r dq.histogram}
dq.histograms <- ggplot(d.cv.targets %>%
         filter(item %in% undiagnostic.props$item), aes( x = response ))+
  geom_histogram() + 
  facet_wrap(~item, nrow = 2) + 
  scale_x_continuous(breaks = c(0, 1))+
  scale_y_continuous(breaks = c(0, 10))+
  xlab("Direct question response")+
  ylab("Number of responses")
```

```{r}
diagnostic.props <- data.frame(
  item = c("kangaroo has a pouch", "lion has a mane", 
           "mosquito carries malaria", "tick carries Lyme disease"),
  type = "diagnostic"
)

undiagnostic.props <- data.frame(
  item = c("leopard is juvenile", "lion is male", "robin is female", "swan is full-grown"),
  type = "undiagnostic"
)

false.props <- data.frame(
  item = c("leopard has wings", "kangaroo has spots", "tiger has a pouch", "shark has a mane"),
  type = "false"
)

target.items2 <- bind_rows(diagnostic.props, undiagnostic.props, false.props)
```

```{r cv-fp-data-analyzeAll, cache = T}
d.target.items <- fromJSON(paste(project.path, "data/generics/endorsement/", "originalStims.json", sep = "")) %>%
  mutate(
    property = gsub("'", "", property),
    Property = gsub("'", "", Property),
    sentence = paste(Category, Property),
    item = paste(category, property))

d.cv.bootstrapped.all <- data.frame()
resample_n <- length(levels(factor(d.cv.fp$workerid)))
for (i in 1:1000){

  d.cv.bsample <- d.cv.fp %>% 
    select(workerid, property, response) %>% 
    spread(property, response) %>% 
    sample_n(resample_n, replace = TRUE) %>%
    gather(property, category, -workerid) %>% 
        group_by(property) %>%
    mutate(n = n(),
           item = paste(category, property)) %>%
    filter(item %in% d.target.items$item) %>%
    group_by(category, property) %>%
    summarize(mentions = n(),
              trials = mean(n), # mean(n) == n, because it's just the number of subjects
              prop = mentions / trials,
              prop = ifelse(is.na(prop), 0.01, prop),
              iteration = i)

  d.cv.bootstrapped.all <- bind_rows(d.cv.bootstrapped.all, d.cv.bsample)
}

d.gen.cv.all.summary <- left_join(
    d.target.items %>% select(-sentence),
    d.cv.bootstrapped.all %>%
      group_by(category, property) %>%
      summarize(cv_mean = empiricalMean(prop),
                cv_ci_lower = empiricalLower(prop),
                cv_ci_upper = empiricalUpper(prop))
) %>%
  mutate(
    cv_ci_lower = ifelse(is.na(cv_mean), 0.01, cv_ci_lower),
    cv_ci_upper = ifelse(is.na(cv_mean), 0.01, cv_ci_upper),
    cv_mean = ifelse(is.na(cv_mean), 0.01, cv_mean)
  )

```

```{r cuevalidity-model-pk}
wp.pkg.path <- paste(project.path, "models/generics/node_modules/utils/", sep = "")

cueValidityModel1 <- '
var cueValidity = function(){
  var kind = uniformDraw(data.prior);
  observe(Bernoulli({p: kind.prevalence/100}), true)
  return kind.Category == data.kind[0]
}

expectation(Infer({model: cueValidity}))
'

d.prev <- read.csv(paste(project.path, "data/generics/endorsement/",
                       "naturalGenerics-prior-trials-n57.csv", sep = ""))

d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

wp.cueValidity <- data.frame()
for (p in gen.endorse.properties){
  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)

  for (catg in categories){

    dataToPass <- list(
      prior = prevPriorData,
      kind = catg
    )

    wp.rs <- webppl(cueValidityModel1, 
       data_var = "data",
       data = dataToPass)

    wp.cueValidity <- bind_rows(wp.cueValidity, 
                                data.frame(Category = catg,
                                           Property = p,
                                           cv = wp.rs))

  }
  #print(p)
}
# save(wp.cueValidity, file =
#        paste(project.path, model.path,
#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
# load(file = 
#        paste(project.path, model.path, 
#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
```

```{r}
md.fp <- left_join(left_join(
  d.gen.cv.all.summary,
  wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
  #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
), target.items2) %>%
  mutate(type = ifelse(is.na(type), "other", type),
           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
                       labels = c("diagnostic", "undiagnostic", "false", "other")))

fill.colors <- RColorBrewer::brewer.pal(3, "Set1")

# ggplot(md.fp, aes (x = prev_prior_derived_cv, y = cv_mean, ymin = cv_ci_lower, ymax = cv_ci_upper,
#                    color = type))+
#   #scale_alpha_manual(values = c(1,1,1,0.5))+
#   geom_errorbar(alpha = 0.4)+
#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
#   geom_point(data = md.fp %>% filter(type == "other"), size = 2)+
#   geom_point(data = md.fp %>% filter(!(type == "other")), size = 2)+
#   coord_fixed()+
#   #scale_color_solarized()+
#   scale_color_manual(values = c(fill.colors, "grey8"))+
#   xlab("Prevalence Prior Derived Cue Validity")+
#   ylab("Free Production Measured Cue Validity")+
#   theme(legend.title = element_blank())

r2.fp <- compute_r2(md.fp, "cv_mean", "prev_prior_derived_cv")
mse.fp <- compute_mse(md.fp, "cv_mean", "prev_prior_derived_cv")
n.fp <- length(md.fp$item)

md.fp.desid <- md.fp %>%
  filter(item %in% target.items2$item)

r2.fp.desid <- compute_r2(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
mse.fp.desid <- compute_mse(md.fp.desid, "cv_mean", "prev_prior_derived_cv")
n.fp.desid <- length(md.fp.desid$item)
```

```{r}
d.cv.dq.all <- d.cv.dq %>%
  mutate(property = gsub("&quotechar", "", property), 
         item = paste(category, property)) %>%
  group_by(category, property) %>%
  tidyboot_mean(column = response)

md.dq <-  left_join( left_join(
    left_join(
    d.gen.cv.all.summary %>% select(Category, Property, category, property, item),
    d.cv.dq.all),
    #wp.cueValidity.uniform %>% rename(prev_prior_derived_cv = cv)
    wp.cueValidity %>% rename(prev_prior_derived_cv = cv)
  ), target.items2) %>%
  mutate(type = ifelse(is.na(type), "other", type),
           type = factor(type, levels = c("diagnostic", "undiagnostic", "false", "other"),
                       labels = c("diagnostic", "undiagnostic", "false", "other")))

# ggplot(md.dq, aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
#                      color = type))+
#   geom_errorbar(alpha = 0.4)+
#   scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
#   scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
#   geom_point(data = md.dq %>% filter(type == "other"), size = 2)+
#   geom_point(data = md.dq %>% filter(!(type == "other")), size = 2)+
#   coord_fixed()+
#   #scale_color_solarized()+
#   scale_color_manual(values = c(fill.colors, "grey8"))+
#   xlab("Prevalence Prior Derived Cue Validity")+
#   ylab("Direct Question Measured Cue Validity")+
#   theme(legend.title = element_blank())
# 
#   
r2.dq <- compute_r2(md.dq, "mean", "prev_prior_derived_cv")
mse.dq <- compute_mse(md.dq, "mean", "prev_prior_derived_cv")
n.dq <- length(md.dq$item)

md.dq.desid <- md.dq %>%
  filter(item %in% target.items2$item)

r2.dq.desid <- compute_r2(md.dq.desid, "mean", "prev_prior_derived_cv")
mse.dq.desid <- compute_mse(md.dq.desid, "mean", "prev_prior_derived_cv")
n.dq.desid <- length(md.dq.desid$item)

prevprior.cv.scatters <- bind_rows(
  md.fp %>%
    rename(mean = cv_mean, ci_lower = cv_ci_lower, ci_upper = cv_ci_upper) %>%
    mutate(src = "Free production"),
  md.dq %>%
    mutate(src = "Direct question")
) %>%
  ggplot(., aes (x = prev_prior_derived_cv, y = mean, ymin = ci_lower, ymax = ci_upper,
                     color = type))+
  geom_errorbar(alpha = 0.4)+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  geom_point(data = . %>% filter(type == "other"), size = 2)+
  geom_point(data = . %>% filter(!(type == "other")), size = 2)+
  coord_fixed()+
  #scale_color_solarized()+
  scale_color_manual(values = c(fill.colors, "grey8"))+
  xlab("Prevalence Prior Derived Cue Validity")+
  ylab("Measured Cue Validity")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.direction = 'horizontal')+
  facet_wrap(~src)
```

```{r}
# save(d.cv.bothtasks, d.cv.targets, md.fp, md.dq,
#      file = "../paper/cached_results/appendix_cueValidity_results.RData")
```

```{r cvModel-uniformPrior, eval = F}
cueValidityModel2 <- '
var cueValidity = function(){
  var kind = uniformDraw(data.allKinds);
  var responses = _.filter(data.prior, {Category: kind});
  var response = _.isEmpty(responses) ? {prevalence: 0} : uniformDraw(responses);
  observe(Bernoulli({p: response.prevalence/100}), true)
  return kind == data.kind[0]
}

expectation(Infer({model: cueValidity}))
'

allKinds = levels(factor(d.gen.endorse.priors$Category))

wp.cueValidity.uniform <- data.frame()
for (p in gen.endorse.properties){
  categories <- levels(factor(filter(d.gen.cv.all.summary, Property == p)$Category))
  prevPriorData = d.gen.endorse.priors %>% filter(Property == p)

  for (catg in categories){

    dataToPass <- list(
      prior = prevPriorData,
      kind = filter(prevPriorData, Category == catg)[1, "Category"],
      allKinds = allKinds
    )

    wp.rs <- webppl(cueValidityModel2, data_var = "data", data = dataToPass)

    wp.cueValidity.uniform <- bind_rows(wp.cueValidity.uniform, 
                                data.frame(Category = catg,
                                           Property = p,
                                           cv = wp.rs))

  }
  print(p)
}
# save(wp.cueValidity, file = 
#        paste(project.path, model.path, 
#              "results/prevPriorDerivedCueValidity.Rdata", sep = ""))
# dataToPass %>% toJSON(.)
# 
# wp.rs

```

### 2018-05-11 paper/comgen-paper.Rmd
final edits to GD and C

@@
 In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
-We close by discussing how a few other previously-discussed troubling examples of generalizations could be addressed in our communicative framework.
-We consider the five following examples:
-
-1. Mary handles the mail from Antarctica (*yet has never had the opportunity*).
-2. Supreme Court Justices have even social security numbers.
-3. Elephants live in Africa and Asia.
-4. Books are paperbacks.
-5. Women are submissive.
+We close by discussing how a three previously-discussed examples could be addressed in our communicative framework.
+
+**1. Mary handles the mail from Antarctica (*yet has never had the opportunity*).**
 
@@
 Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
-In our framework, we treat Sentence (1) is a boundary case of generalizations expressing predictive probabilities.
-In Expt.
-2c., we experimentally dissociated predictive probability from past frequency, and saw that only a model that took into account predictive probability could explain participants' endorsements of generalizations.
-We expect the same to be true with Mary, elucidated by the intuition that: were there to be any mail coming from Antarctica, Mary would handle it. 
-Past frequency or actual prevalence in the world often tracks predictive probabilities, but language users' internal models of how the world works can lead them in certain situations to expect something different in the future.
-
-Our focus on predictive probability even makes novel predictions about some classic puzzles.
-Sentence (2) is the conceptual opposite of sentence (1).
-Imagine that currently every Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (2) is still considered false, every though the property holds in exactly 100\% of the category [@Cohen1999].
-We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective probabilities.
+In our framework, Sentence (1) is a extreme case of generalizations expressing *predictive* probabilities.
+In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency.
+We expect the same to be true with Mary: any future mail coming from Antarctica will be handled by Mary. 
+Thus the predictive probability that Mary will handle Antactican mail, if there is any, is high.
+Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge.
+In this case our understanding of Mary's job leads to a strong preditcive probability in the absence of past frequency evidence.
+
+**2. Supreme Court Justices have even social security numbers.**
+
+Imagine that every current and past Supreme Court Justice has a social security number which is an *even number*. 
+Sentence (2) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
+We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
 That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
 Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated similarly by our model as "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
@@
 
+**3. Elephants live in Africa and Asia.**
+
 Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
@@
 Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
-However, such is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics, as posited in most statistical views of generics (e.g., if the generic means *most*).
+However, this is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics, as posited in most statistical views of generics (e.g., if the generic means *most*).
 Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
@@
 Interestingly, an incremental parsing of Sentence (3) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
-When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia.
-Our model flexibly accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia, but few in other places).
+The flexibly of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 
@@
 
+<!--
+**4. Books are paperbacks.**
+
 Sentence (4), strikes hearers as *odd* or perhaps *false*, despite the vast majority of books being paperback. 
 Why?
-We first observe that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset (i.e., "paperbacks", or "paperback books"). 
-We hypothesize that the strangeness of this example has to do an inflexible relationship between the comparison class and the referent-prevalence.
-Assume that the comparison class is constructed by considering the *predicability of the property* [in the sense of @Keil1979, originally from @Sommers1963].^[
+We first observe that the sentence is constructed by pairing a category ("Books") with a property that describes a strict subset (i.e., "paperbacks"). 
+We hypothesis that the starngeness of (4) has to do with the role of *predicability* [in the sense of @Keil1979, originally from @Sommers1963] in determining the comparison class.
+That is, assume that entities in the relevant comparison classes must be predicable of the property: each entity in each class must either have or not have the proprerty.^[
   Note that this assumption is consistent with the comparison classes we have assumed in our three case studies.
 ]
-Then, "is a paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
+Then, "is paperback" can only be informatively said of individual books, because these are the only objects that can plausibly have the property; that is, world knowledge gives us that an elephant cannot be predicated (either true or falsely) by the property "is a paperback".^[
   Note that this idea is related to @Cohen1999's notion of "Relative generics" (described above), which have truth conditions that are determined by a comparison to an alternative set of Ks which is composed of Ks that could satisfy some F in an alternative set of Fs.
@@
 
-Finally, Sentence (5) suggests that a property can be widespread relative to other kinds or groups, as well as being so systemic that we would predict it to be the case in the future (high *predictive prevalence*), and speakers still might find it aversive to actually endorse the generalization [@Haslanger2011].
-<!-- Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5).
--->
+**4. Women are submissive.**
+
+Finally, Sentence (4) suggests that a property can be widespread relative to other kinds or groups, as well as being so systemic that we would predict it to be the case in the future (high *predictive prevalence*), and speakers still might find it aversive to actually endorse the generalization [@Haslanger2011].
+( Due of a variety of socio-cultural reasons, @Haslanger2011 argues that women tend to be submissive (more so than men, and many other social categories), yet still cautions against asserting (5). )
 In our **Model Simulations** section, we showed that the generalization often implies the property is widespread, even with relatively uninformed prior beliefs about the property. 
@@
 This kind of extension to rational models of communication has already been used to account for a variety of phenomena in *polite language* use [@Yoon2016; @Yoon2017].
-Such a value-based utility structure for states of the world for language about social categories may capture intuitions like those about Sentence (5): If the speaker found states of the world where the probability of the feature is high as undesirable (e.g., a world where many women were submissive), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
-
-An alternative information-theoretic analysis of (5) could be made concerning the conceptual structure communicated by generalizations (see earlier discussion of *Prevalence Priors and Conceptual Structure*).
+Such a value-based utility structure for states of the world for language about social categories may capture intuitions like those about Sentence (4): If the speaker found states of the world where the probability of the feature is high as undesirable (e.g., a world where many women were submissive), then a speaker who considered both the informational content of the utterance and the utility in the states of the world implied by that utterance would too find it reprehensible to make such a generalization.
+
+An alternative information-theoretic analysis of (4) could be made concerning the conceptual structure communicated by generalizations (see earlier discussion of *Prevalence Priors and Conceptual Structure*).
 Suppose there are two possible causes for a person to be submissive: Either it is in their DNA or the person was socialized in such a way as to be submissive. 
@@
 Suppose the speaker wants to communicate that she believes an external, societal cause is leading to high prevalence of submissiveness.
-The decision to endorse (5) depends upon what the speaker believes her listener will infer. 
-If she is in a group of close friends discussing the ways in which society shapes behavior, the speaker may opt to endorse (5) because with high probability, she will be understood as endorsing the external, society cause.
-However, if she is worried that some might take her to mean that there's something about women that causes them to be submissive, the speaker may refrain from uttering (5).
+The decision to endorse (4) depends upon what the speaker believes her listener will infer. 
+If she is in a group of close friends discussing the ways in which society shapes behavior, the speaker may opt to endorse (4) because with high probability, she will be understood as endorsing the external, society cause.
+However, if she is worried that some might take her to mean that there's something about women that causes them to be submissive, the speaker may refrain from uttering (4).
 Such an explanation would be a purely information transmitting account that does not require any social utility to explain the behavior.
 
+-->
+
+<!--
 In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework might well explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
+-->
 
@@
 In our work, context takes the form of shared beliefs between speakers and listeners. 
-By leveraging this common ground, the language of generalizations provide a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
+By leveraging this common ground, the language of generalizations provides a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
 
@@
 -->
-The theory presented here provides the first computational perspective on how we communicate generalizations and how beliefs play a central role in the meaning of words.
+The theory presented here provides the first computational perspective on how we communicate generalizations, illustrating how beliefs play a central role in the meaning of words.
 

### 2018-05-11 paper/coverletter.tex
typo in cl

@@
 First, we have completely re-written the paper for clarity and focus, especially simplifying and streamlining the modeling sections.
-Second, we have extended the work substantially from concerning only generalizations about categories (\emph{generic language}) to addressing two other semantic types: generalizations events and causes.
+Second, we have extended the work substantially from concerning only generalizations about categories (\emph{generic language}) to addressing two other semantic types: generalizations  about events and causes.
 Across these three domains, we are able to explain endorsements with little-to-no domain-specific assumptions. 
-Furthermore, each case study naturally lends methodological advantages to provide strictiers tests of our hypothesis/model (e.g., with causal generalizations, we are able to manipulate---rather than merely measure---prior knowledge).
+Furthermore, each case study naturally lends methodological advantages to provide stricter tests of our hypothesis/model (e.g., with causal generalizations, we are able to manipulate---rather than merely measure---prior knowledge).
 %The empirical and much of the philosophical literatures have focused on generalizations about categories, or generic language.

### 2018-05-13 paper/comgen-paper.Rmd
final edits in abstract, intro, model, sims

@@
 abstract: > 
-    Knowledge that extends beyond the present context is crucial to thrive in our open-ended, dynamic world. 
-    Yet such knowledge can be difficult to extract from the environment. 
-    Fortunately, we are not limited to acquiring generalizations on our own; language allows us to communicate generalizations to each other (e.g., “Birds fly”, “John hikes”, “Drinking milk makes your bones strong").
-    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
-    Here we argue that three ingredients are necessary to formalize generalizations: Probability, vagueness, and context. 
-    We formalize these ingredients in an information-theoretic probabilistic model that makes quantitative predictions about human understanding of generalizations.
-    Across diverse domains, we find that the model explains the gradience in human endorsement, while simpler models fall short. 
-    This is the first formal theory that makes accurate and precise predictions about human understanding of generalizations in language and is the first step towards building models that can learn abstract knowledge from language.
-
-keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
+    Language provides simple ways of communicating generalizable knowledge to each other (e.g., "Birds fly", "John hikes", "Fire makes smoke").
+Though found in every language and emerging early in development, the language of generalization is philosphically puzzling and has resisted precise formalization.
+Here, we propose the first formal account of the language of generalization that makes quantitative predictions about human understanding.
+We test our model in three diverse domains: generalizations about categories (generic language), events (habitual language), and causes (causal language).
+The model explains the gradience in human endorsement through the interplay between a simple truth-conditional semantic theory and diverse beliefs about properties.
+This work opens the door to understanding precisely how abstract knowledge is learned from language.
+
+keywords          : "genericity, generalization, generics, pragmatics, semantics, Bayesian modeling"
 wordcount         : "20000"
@@
 lineno            : no
-toc               : yes
+toc               : no
 
@@
 Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case in the language of generalization.^[
-  Some writers refer to the all of the *language of generalization* as "generic language".
-  In the literature, however, analysis and experiments are often limited to generalizations about categories. 
+  Some writers refer to the all of the *language of generalization* as "generic language" or generics.
+  In both the empirical and theoretical literatures, however, analysis and experiments often focus only on generalizations about categories. 
   We use the more narrow-scoped terms (e.g., generics, habituals, and causals) to highlight the diversity of semantic types being predicated.
@@
 Understanding the language of generalization is a project with far-reaching implications.
-The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], and making meaning from experience [@Orvell2017].
+The language of generalization is ubiquitous in everyday conversation, is found in every language [@Behrens2005; @Carlson1995], and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], and making meaning from experience [@Orvell2017].
 It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context suggests its centrality to the growth of conceptual knowledge [@Gelman2004].
-Finally, it is believed every language can express generalization [@Behrens2005; @Carlson1995].
 
@@
 Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains 3 times last year, the habitual "Mary climbs mountain" seems well-supported. 
-Yet, if John went for a run 3 times in the last year, we probably shouldn't say that "John runs".
+Yet, if John went for a run 3 times in the last year, we probably should not say that "John runs".
 
@@
 True generics can be supported by different underlying types of category--property relations [e.g., principled vs.
-statistical connections; @Prasada2006], and thus support qualitatively different inferences [e.g., "Being striped is one aspect of being a tiger" is endorsed while "Carrying malaria is one aspect of being a mosquito" is not, even while "Tigers are striped" and "Mosquitos carry malaria" sound true; @Prasada2013].
+statistical connections; @Prasada2006], and thus support qualitatively different inferences [e.g., "Being striped is one aspect of being a tiger" is generally endorsed, while "Carrying malaria is one aspect of being a mosquito" is not, even while "Tigers are striped" and "Mosquitos carry malaria" are both intuitively true; @Prasada2013].
 This conceptual view of generics has been influential in psychology, because it predicts qualitative differences between different kinds of generics. 
@@
 Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that the next dog will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
+People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do.
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
-Probability is the universal currency of belief and this prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
+This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
 Our *prevalence* $p$ is a *prevalence in the mind*, a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
@@
 Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
-Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].
+By assuming some generative process that could produce one's observations $o$---the likelihood $P(o \mid p)$---Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations $o$: $P(o \mid d) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].
 
@@
 <!-- Dinosaurs are exctinct ~ John is a smoker? -->
-Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977, @Carlson2005].
+Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005].
 Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
@@
 
-We formalize this underspecified (or, *vague*) semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013;   @Lassiter2015; cf., @Qing2014].^[
+We formalize this underspecified, or vague, semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013;   @Lassiter2015; cf., @Qing2014].^[
   Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p)$.
@@
 \begin{eqnarray}
-Lit(p, \theta \mid u) &\propto& {\delta_{\denote{u}(p, \theta)} \cdot P(p) \cdot P(\theta)} \label{eq:L0}
+L(p, \theta \mid u) &\propto& {\delta_{\denote{u}(p, \theta)} \cdot P(p) \cdot P(\theta)} \label{eq:L0}
 \end{eqnarray}
 
+We denote this interpretation model by $L$ to indicate that it is modeling a listener, updating their beliefs according to the truth-functional meaning of an utterance.
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
@@
 
-We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives to the endorsement model: produce the generalization vs.
+We interpret the endorsement task (e.g., *true* vs.
+*false*; *agree* vs.
+*disagree*) as supplying two alternatives to the endorsement model: produce the generalization vs.
 a null alternative [@Franke2014cogsci; @Degen2014].
-For simplicity, we take the null alternative to be an information-less "silent" utterance which is always true: 
+For simplicity, we take the null alternative to be an informationless "silent" utterance which is always true: 
 $\denote{null}(x, \theta) = \text{True}$.^[
@@
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
-  Rather, the endorser may have a distribution over $p$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
+  Rather, the endorser may have a distribution over $p$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence of the property for the referent category. 
   In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
-  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} Lit(p, \theta \mid u)} \diff \theta )}$
+  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} L(p, \theta \mid u)} \diff \theta )}$
   For the empirical case studies described below, these two versions of the model make almost identical predictions.
 ]
-This endorsement model (called $S$ for speaker) does so by reasoning about the interpreter model $Lit$: 
+This endorsement model (called $S$ for speaker) does so by reasoning about the interpretation model $L$: 
 \begin{equation}
-S(u \mid p) \propto (\int_{\theta} Lit(p, \theta \mid u)  \diff \theta)^\lambda
+S(u \mid p) \propto (\int_{\theta} L(p, \theta \mid u)  \diff \theta)^\lambda
 \label{eq:S1}
@@
 
-The informational content of the generalization is about the referent prevalence $p$.
+The informational content of the generalization concerns the referent prevalence $p$.
 The semantic threshold $\theta$ is a nuisance parameter then; the endorsement model integrates over the interpreter's posterior beliefs about $\theta$.
@@
 This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
-We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model $Lit$ in which relevant contextual knowledge can be formalized.
+We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
 In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
@@
 By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-Cue validity operationalizes an alternative hypothesis about the interpretation of generic statements that the reading of statements like "Mosquitos carry malaria" is as "It is mosquitos that carry malaria", and empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
+The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
+In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
 Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
@@
 The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
-Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior. 
+Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior $P(p)$. 
 If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
-As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:simulations)A).
+As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:uniformPriorSimulation)A).
 Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
@@
 In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measuring and manipulating background knowledge and referent-prevalence and relate it to human elicited endorsements of generalizations.
+We do this by both measuring and manipulating background knowledge and referent-prevalence and predicting human endorsements of generalizations.
 

### 2018-05-14 paper/case1-generics.Rmd
final pass case 1; refresh fig caps

@@
 
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
+Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") are of substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
 In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
-However, intuitions and empirical data argue that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].
+However, intuitions and empirical data argue that generics simply do not reduce to quantified statements in a simple way [e.g., @Khemlani2012; @Prasada2013; @Cimpian2010].
 
@@
 The prevalence elicitation procedure (Expt.
-1b) includes measurements of the referent-category feature-probabilities $p$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq.
+1b) includes measurements of the referent-prevalence $p$ for different categories  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq.
 \ref{eq:S1}) as well as for simpler, alternative models.
@@
 Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
+They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Figure\ \@ref(fig:generics-endorsement-figure)A for the full list).
 The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
-Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
-All 30 generic sentences are shown in Figure\ \@ref(fig:generics-endorsement-figure)A.
+Approximately ten true, ten false, and ten uncertain truth-value generics were selected.
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
-4 participants were excluded for failing this trial.
+Four participants were excluded for failing this trial.
 
@@
 Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
-We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict these endorsement data.
+We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.
 
@@
 Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of^[
+That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of.^[
   The subjective probability may, in fact, be non-zero and small as opposed to 0. 
-  Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange   generic mutation or the interaction of dog genetics with a strange environment. 
-].
+  Non-zero probabilities allow for the intuitive possibility of a mammal animal that generally reproduces by giving live birth which in fact lays eggs, potentially explained by some strange generic mutation.
+]
 
 This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and perform Bayesian data analysis to accurately reconstruct the prevalence prior.
+We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and build a structured statistical model to accurately reconstruct the prevalence prior.
 We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
@@
 
-There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
+The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
 The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
 *Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
-This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution
+This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution.
 
@@
 <!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
-In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
+In order to integrate the results of this prior measurement task into our model of endorsement, we must build a statistical model of the prior elicitation data.
 We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
@@
 Instead, it appears that some participants are responding that 100\% of several different kinds of birds (e.g., robins) lay eggs.
-This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction* and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
-];
+This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction*, is posited in several theories of generics [e.g., @Cohen1999], and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
+]
 A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. 
@@
 
-We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
+We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, and our full endorsement model.
 
@@
 In addition to serving as alternatives, these regressions model help us understand the statistical properties of our thirty items. 
-First, we estimate how well referent prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
+First, we estimate how well referent prevalence itself predicts generic endorsement (e.g., does the fraction of robins that lay eggs predict the felicity of *Robins lay eggs*?).
 Second, we include *cue validity*---the probability of a kind given the feature---as a second predictor in a linear model.
@@
 
-From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}).
+From the prevalence prior data (Expt.
+1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}) and use it to predict endorsement.
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
@@
 `r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
-`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is judged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
+`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is misjudged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
 `r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
@@
 "Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
-"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
-Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Figure\ \@ref(fig:simulations)A bottom).
+*Lays eggs* is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like *robins*.
+Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
 Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
@@
 <!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
-For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent-category prevalence $p$, prevalence priors $P(p)$ (both from Expt.
+For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt.
 1b data), and the endorsement data (Expt.
@@
 Empirically elicited referent prevalence and prevalence prior data (Expt.
-1b) directly constrain their corresponding parameters in the model ($p$ in Eq.
+1b) directly constrain the parameters that generate those quantities in the model ($p$ in Eq.
 \ref{eq:S1} and $P(p)$ in Eq.
@@
 The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
-Modeling the data from both Expt.
+Predicting the data from both Expt.
 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
@@
 
-To provide a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
+For a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
 In addition, we make this fixed-threshold a parameter of the data-analysis model, to search for the best possible fixed-threshold. 
@@
 ```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories.
-Top left: Human elicited endorsements for thirty generic sentences reveal a continuuum of endorsements.
-Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right).
-Bottom: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence.
+A: Human elicited endorsements for thirty generic sentences reveal a continuum of endorsements.
+B: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right).
+C: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence.
 These distributions are inferred using all three data sources from Expt.
@@
 Generic language is the premier case study for generalizations in language. 
-Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
+Generics have been studied extensively in the cognitive and developmental psychological literatures and have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
 Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generics: knowing when they are true and false.
@@
 This empirical case study demonstrates that a semantics based on the prevalence of the feature is tenable despite of alleged counterexamples (e.g., "Robins lay eggs" vs. "Robins are female").
-The key theoretical insight is that the truth-functional semantics is underspecified, or vague, and resolved in context by a process of probabiistic inference.
+The key theoretical insight is that the truth-functional semantics is underspecified, or vague, and resolved in context by a process of probabilistic inference.
 Our model provides a clear delineation of world knowledge (formalized as a prevalence prior) from the semantics of generics. 

### 2018-05-14 paper/comgen-paper.Rmd
final pass case 1; refresh fig caps

@@
 ```{r uniformPriorSimulation, fig.cap = "Computational model behavior assuming a uniform prior over prevalence.
-A: Interpretation model posteriors assuming different fixed thresholds.
+A: Interpretation model posteriors assuming different fixed thresholds (facets).
 High thresholds rule out more world-states (prevalence levels), leaving fewer world-states among which to distribute the full probability mass.
-B: Full interpretation model marginalizes over possible thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
+B: Generic interpretation model averages over all thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
 C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.", fig.width = 13, fig.asp = 0.3, out.width = "100%", fig.align = "center", cache = F}
@@
 ```{r simulations, fig.cap = "Model simulations assuming different prevalence priors.
-Top: Prior distributions over the prevalence of a feature for 6 example features.
+Top: Prevalence priors for six example features.
 Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions.
-Arrows show intuitive referent-category prevalence for a target category.
-Bottom: The interpreter model posterior distributions over prevalence upon hearing a generalization about a novel category.
+Arrows show referent-prevalence for a target category.
+Bottom: Interpretation model posterior distributions over prevalence upon hearing a generalization about a novel category.
 Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for  the referent-category whose prevalence is shown in the top facets (e.g., \"Mosquitos carry malaria\").", fig.width = 9, fig.asp = 0.37, out.width = "100%", fig.align = "center", cache=F}

### 2018-05-14 paper/case1-generics.Rmd
fix legend title in gen endorse fig

@@
   scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
-  guides(color = guide_colorbar(title = 'Prevalence',
+  guides(fill = guide_colorbar(title = 'Referent prevalence',
                                ticks = F))+

### 2018-05-14 paper/case2-habituals.Rmd
upgrade hab pred fig

@@
   guides(fill=F, shape=F)+
-  scale_fill_viridis(discrete = T)+
+  scale_fill_brewer(type = "seq", palette = 2)+
   xlab("Past frequency")+
@@
                             "smokes marijuana","runs","watches space launches",
-                            "smokes cigarettes","drinks coffee")
+                            "smokes cigarettes","drinks coffee", "writes poems")
 
@@
   mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
-         src =factor(src , levels = c("human data","predictive_model", "regression_pastfreq",
-                                      "regression_futurefreq","past_model"),
-                     labels= c("Human data", "Uncertain semantics  \n(Predictive frequency)", "regression_pastfreq",
-                               "Regression              \n(Predictive frequency)", "Uncertain semantics\n(Past frequency)      ")),
+         # src =factor(src , 
+         #             levels = c("human data","predictive_model", "regression_pastfreq",
+         #                              "regression_futurefreq","past_model"),
+         #             labels= c("Human data", "Uncertain semantics  \n(Predictive frequency)", "regression_pastfreq",
+         #                       "Regression              \n(Predictive frequency)", "Uncertain semantics\n(Past frequency)      ")),
+         src =factor(src , 
+                     levels = c("regression_pastfreq",
+                                "regression_futurefreq",
+                                "past_model", 
+                                "predictive_model","human data"),
+                     labels= c(
+                               "Past frequency",
+                                "Predictive frequency",
+                                "Uncertain semantics\n(Past frequency)",
+                               "Uncertain semantics \n(Predictive frequency)", 
+                               "Human data")),
          hab_time = gsub("-","\n(", hab_time),
@@
          hab_time = factor(hab_time, 
-                           levels = c("climbs mountains\n(5 years)","steals cars\n(5 years)", "steals chewing gum\n(5 years)",
-                            "writes novels\n(5 years)", "watches space launches\n(2 years)", "hikes\n(year)","plays the banjo\n(year)",
-                            "smokes marijuana\n(year)","runs\n(2 months)","drinks coffee\n(month)",
-                            "smokes cigarettes\n(month)"))) %>%
-  filter(src != "regression_pastfreq",
-         item %in% pred.items.of.interest) %>%
+                           levels = c("climbs mountains\n(5 years)","hikes\n(year)","runs\n(2 months)",
+                            "watches space launches\n(2 years)", 
+                                      "steals cars\n(5 years)",
+                                      "steals chewing gum\n(5 years)",
+                            "writes novels\n(5 years)", 
+                            "writes poems\n(year)","plays the banjo\n(year)",
+                            "smokes marijuana\n(year)",
+                            "smokes cigarettes\n(month)",
+                            "drinks coffee\n(month)"))) %>%
+  filter(item %in% pred.items.of.interest) %>%
 ggplot(., 
        aes (y = MAP, ymin = cred_lower, ymax = cred_upper, 
-            x = hab_time, fill = condition))+
+            x = src, fill = condition))+
   #geom_abline(intercept = 0, slope = 1, lty = 3)+
@@
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_viridis(discrete = T)+
+  scale_fill_brewer(type = "seq", palette = 2)+
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
@@
   ylab("Habitual endorsement")+
-  xlab("Item (past frequency: 3 times per interval)")+
-  facet_grid(src~., scales = 'free')+
+  xlab("Model")+
+  #facet_grid(src~., scales = 'free')+
+  facet_wrap(~hab_time, nrow = 3)+
   theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
@@
                      labels= c("Human data","regression_pastfreq", 
-                                "Uncertain semantics (Past)", "Linear model (Predictive frequency)","Uncertain semantics (Predictive)"))) %>%
+                                "Uncertain semantics\n(Past)", "Linear model\n(Predictive frequency)","Uncertain semantics\n(Predictive)"))) %>%
   filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
@@
   xlab("Model prediction")+
-  facet_grid(.~src, scales = 'free')+
+  facet_grid(.~src)+
   theme(legend.position = "right")
@@
 
-```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline).
-Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation.
-Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 14,  fig.asp = 0.6, cache=F}
+```{r habituals-predictive-figure, fig.cap="A: Example empirical and predicted endorsements for habituals in three conditions.
+B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline).
+C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7, cache=F}
 plot_grid(
@@
     habituals.endorsement.pred.scatters +
-      theme(plot.margin = unit(c(0,0,12,12), "pt"),
-            legend.position = c(1.1,1.1)),
+      theme(plot.margin = unit(c(0,0,12,12), "pt")),
     labels = c("B", "C"),
-    nrow = 1,  axis = 'tblr', rel_widths = c(1, 1.8)), 
+    nrow = 1,  axis = 'tblr', rel_widths = c(1, 2.3)), 
   labels = c("A", ""), 
-  nrow = 2, align = 'v', axis = 'lr', rel_heights = c(3.1, 1.5))
+  nrow = 2, align = 'v', axis = 'lr', rel_heights = c(3.1, 2))
 ```

### 2018-05-15 paper/case2-habituals.Rmd
final edits to case study 2; refresh hab endorse fig

@@
 ]
-We test this by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2a).
+We test the model by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2a).
 We then measure endorsements of habitual statements while manipulating the referent prevalence  (Expt. 2b), and use our computational model to predict habitual endorsements. 
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
-By describing novel characters to participants, we are able to directly the manipulate the referent prevalence, which we were unable to do for generalizations about familiar categories.
+By describing novel characters to participants, we are able to directly the manipulate the referent prevalence, which we were unable to do for familiar categories in Case Study 1.
 <!-- In addition to directly manipulating the referent feature-probability, these experiments provide the first test of the generality of our theory: It can apply to generalizations about events as well as categories.
@@
 
-In order to generate model predictions for corresponding habitual statement, we first elicit the prior distributions over rates for different events.
+In order to generate model predictions for habitual endorsements, we first elicit the prior distributions over rates for different events.
 For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
@@
 In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not do the action.^[
-  It is likely that more than just these two possibilities are represented in people's intuitive prior, corresponding to individuals with additional traits or demographics.
+  It is likely that more than just these two possibilities are represented in people's intuitive theories, corresponding to individuals with additional traits or demographics.
   We assume here a simple two-component structure so as to not make the specification of the prior overly complex.
@@
 To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
-For each category, we created pairs or triplets of events that shared a superordinate actions (e.g. *writing* poems vs. novels).
+For each category, we created pairs or triplets of events that shared a superordinate action (e.g. *writing* poems vs. novels).
 The events were chosen to intuitively cover a range of likely frequencies.
@@
 For each event, participants were asked two questions, with different dependent measures. 
-These questions were designed to measure the two components of the prevalence prior model.
-We anticipated there to be different beliefs about the rates and relative proportions of people depending on whether an actor is male or female, so we asked about both genders separately.
-The two questions were schematically:
+These questions were designed to measure the two components of the prevalence prior distribution.
+We anticipated there to be different beliefs about the rates and relative proportions of men vs. women, so we asked about both genders separately. The two questions were schematically:
 
 \begin{enumerate}
-\item ``How many \{men, women\} have *done action* before?'' \\
+\item ``How many \{men, women\} have \emph{done action} before?'' \\
 
@@
 
-\item ``For a typical \{man, woman\} who has *done action*  before, how frequently does he or she \textsc{do action}?''\\
+\item ``For a typical \{man, woman\} who has \emph{done action}  before, how frequently does he or she \emph{do action}?''\\
 
@@
 In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
-Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before} scatter-plot), reflecting the (inverse) popularity of the event across people.", cache = F}
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache = F}
 cowplot::plot_grid(
@@
 Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis.
+Now that we have modeled the prevalence prior data, we see whether our endorsement model can accurately predict endorsement rates for habitual sentences about these actions.
 
@@
 
-Each event from Expt. 2a was then paired with between two to four frequencies, for which the habitual statement would be evaluated. 
+Each event from Expt. 2a was paired with between two to four frequencies, for which the habitual statement would be evaluated. 
 Frequencies were presented in terms of a character performing the action "three times in the past *time interval*".
-We chose to always have the character perform the action three times to provide a strong test of a baseline hypothesis that the habitual encodes the person has done the action multiple times in the past.
+We chose to always have the character perform the action three times to provide a strong test of a baseline hypothesis that the habitual encodes the person has done the action several (at least 3) times in the past.
 
@@
 2a) for each item, and chose between two and four time intervals across which maximal variability was predicted.
-For example, relatively high frequencies were chosen (e.g., time intervals of weeks and months) for items expected to occur rather often (e.g., *runs*); for an item was expected to occur infrequently (e.g., *climbs mountains*), lower frequencies were chosen (e.g., time intervals of years or longer) because the model predicted that much of the variability in endorsement would occur in that range.
+For example, relatively high frequencies were chosen (e.g., time intervals of weeks and months) for items expected to occur rather often (e.g., *runs*); for an item was expected to occur infrequently (e.g., *climbs mountains*), lower frequencies were chosen (e.g., time intervals of years or longer) because the model predicted that much of the variability in endorsement would occur in those respective ranges.
 In total, `r nrow(m.hab.endorse.rsa %>% distinct(habitual, time_period))` unique items were created by pairing frequencies with events. 
@@
 
-Habitual sentences were endorsed for a wide range of frequencies.
+The goal of this experiment was to elicit variability in habitual endorsements. 
+Consistent with this goal, we found habitual sentences were endorsed for a wide range of frequencies.
 When actions are very infrequent (3 times in a 5-year interval), habituals can receive strong agreement (e.g., \emph{writes novels}, \emph{climbs mountains}).
 When actions are relatively frequent (e.g., 3 times in a one month interval), habitual sentences can receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
-In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree that people who wore a watch or wore a bra 3 times in the past week \emph{wears a watch} or \emph{wears a bra} habitually).
-In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the habitual utterances), reflecting the fact that these statements are not altogether *false* even though the action may be done very rarely.
+In our data, actions completed with a relatively high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% disagree that people who wore a watch or wore a bra 3 times in the past week \emph{wear a watch} or \emph{wear a bra} habitually).
+Finally, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the habitual utterances), reflecting the fact that these statements are not altogether *false* even though the action may be done very rarely.
 
@@
                                        mutate(src = factor(src, levels = c(
-                                         "Human data", "Uncertain semantics",
-                                         "Fixed semantics", "Referent frequency",
-                                         "Distinctiveness +\n referent frequency"
+                                          "Referent frequency",
+                                         "Distinctiveness +\n referent frequency", 
+                                         "Fixed semantics",
+                                        "Uncertain semantics", "Human data"
+                                       )),
+                                       habitual = factor(habitual, levels = c( 
+                       "climbs mountains","hikes", "runs",
+                      "smokes cigarettes","drinks coffee",
+                      "goes to the movies", "watches space launches",
+                       "writes poems", "writes novels"
                        ))), aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
-                  x = time_period, fill = logAnnualRate))+
+                  x = src, fill = logAnnualRate, group = logAnnualRate))+
   #geom_abline(intercept = 0, slope = 1, lty = 3)+
   #geom_linerange(alpha = 0.15)+
-  geom_col(position = position_dodge(), color = 'black', width = 0.7)+
-  geom_errorbar(alpha = 0.7, width = 0.3)+
+  geom_col(position = position_dodge(), color = 'black'
+           #width = 0.7
+           )+
+  geom_errorbar(alpha = 0.7,
+                position = position_dodge())+
   #geom_point(shape = 21, size = 3)+
@@
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_viridis()+
+  scale_fill_viridis(
+      breaks = c(-0.5, 1.1, 3.5, 5),
+      labels = c("5 years", "year", "month", "week")
+  )+
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
@@
   ylab("Habitual endorsement")+
-  xlab("Frequency")+
-  facet_grid(src~habitual, scales = 'free')+
+  xlab("")+
+  #facet_grid(src~habitual, scales = 'free')+
+  facet_wrap(~habitual)+
+  guides(fill = F)+#guide_colorbar(ticks = F, title = "Time interval"))+
   theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
         axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45),
-        legend.position = "bottom") +
-   guides(fill = F)
+        legend.position = "right")
+
+#md.hab.long %>% distinct(logAnnualRate, time_period)
 ```
@@
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  scale_fill_viridis()+
-  coord_fixed()+
+  scale_fill_viridis(
+      breaks = c(-0.5, 1.1, 3.5, 5),
+      labels = c("5 years", "year", "month", "week")
+  )+  coord_fixed()+
   xlab("Model prediction")+
   ylab("Human endorsement")+
-  facet_wrap(~src, nrow = 1, strip.position = "top")+
-  guides(fill = guide_colorbar(title = 'log annual rate',
-                               ticks = F,
-                               title.position="top"))+ 
-  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
-        legend.direction = 'horizontal',
+  facet_wrap(~src, ncol = 2, strip.position = "top")+
+  guides(fill = guide_colorbar(ticks = F, title = "Time interval"))+
+  theme(strip.text.y = element_blank()#,# element_text(angle = 0, hjust= 0),
+        #legend.direction = 'horizontal',
         #legend.position = c(0.025,0.975),
         #legend.position =c(1,1),
-        legend.justification = c(1,1)
+        #legend.justification = c(1,1)
         )
@@
 
-```{r habituals-endorsement-figure, fig.width = 16, fig.height = 12.5, fig.cap="Endorsing generalizations about events.
+```{r habituals-endorsement-figure, fig.width = 15, fig.asp=0.5, fig.cap="Endorsing generalizations about events.
 A: Endorsements for nine events given different frequencies of action by human participants and four models.
@@
 
-hab.legend <- get_legend(habituals.endorsement.models)
+#hab.legend <- get_legend(habituals.endorsement.models)
 fig.hab.endorse.bars <- habituals.endorsement.bars +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) #+ ggtitle("prevalence priors")
+  theme(plot.margin = unit(c(16,6,6,6), "pt")) #+ ggtitle("prevalence priors")
 fig.hab.endorse.scatters <- habituals.endorsement.models +
-  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
+  theme(plot.margin = unit(c(0,6,6,6), "pt")) # + theme(legend.position="none") #+ ylab("")
 fig.hab.endorse.priors <- habituals.endorsement.insets +
-  theme(plot.margin = unit(c(18,2,6,6), "pt"))
-
-#+ 
-    #theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
-#p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))
-
-# fig.gen.endorse.toprow <- plot_grid(fig.gen.endorse.data,
-#                                      fig.gen.endorse.models, 
-#                                     # align = 'v',
-#                                     #  axis = 'l',
-#                                     labels = c("A", "B"),
-#                                     rel_widths = c(0.9, 1))
-
-#fig.hab.toprow <- 
-  plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters,
+  theme(plot.margin = unit(c(0,0,6,0), "pt"))
+
+  plot_grid(
+    plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters, nrow = 1, labels = c("A", "B"),
+              rel_widths = c(2, 1)),
                             # plot_grid(fig.hab.endorse.scatters,hab.legend, nrow = 1, rel_widths = c(0.6,4),
@@
                             fig.hab.endorse.priors,
-                            labels = c("A", "B", "C"), nrow = 3,
-                            axis = 'lr', 
-                        align = 'v', 
-                            rel_heights = c(3.1, 1.4, 1.2))
-
-# plot_grid(fig.hab.toprow,
-#           fig.hab.endorse.priors,
-#           labels = c("", "C"), nrow = 2, rel_heights = c(3, 1.3)
-#           )
-
-#plot_grid( prow, legend, rel_widths = c(3, .3))
-
-# grid.arrange(fig.habituals.endorsement.vs.freq, 
-#              habituals.endorsement.models,
-#              habituals.endorsement.insets, ncol = 2,
-#              layout_matrix = cbind(c(1,1,3), c(2,2,3)))
+                            labels = c("", "", "C"), nrow = 2,
+                            #axis = 'lr', 
+                        #align = 'v', 
+                            rel_heights = c(2, 1))
+
 ```
@@
 Analyses which use the prevalence prior distribution $P(p)$ (all models except "referent frequency" regression) use a 50\% mixture of the inferred priors for each gender to construct a single prevalence prior distribution.
-Parallel to our analysis of generics model, we model uncertainty in the input measurements by bootstrapping the data for the regression models and constructing joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-threshold).
+Parallel to our analysis in Case Study 1, we model uncertainty in the input measurements by bootstrapping the data for the regression models and constructing joint-inference, Bayesian data analytic models for the information-theoretic endorsement models (fixed-threshold and uncertain-threshold).
 
@@
 In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)A x-axis).
-This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus is relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
+This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
 Thus, we take this parameter as an index of the *distinctiveness* of the action, analogous to *cue validity* in the case study of generic language.
@@
 Still, this model fails to capture fine-grained differences in endorsement.
-For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual ($`r movies.year.data`$), while this regression model predicts quite lower judgments ($`r movies.year.regression.distinct`$).
+For example, going to the movies is a relatively nondistinctive action (many people do it) and going three times in a year is not very frequent, and yet people still strongly endorse the habitual (mean endorsement and 95\% CI: $`r movies.year.data`$), while this regression model predicts quite lower judgments ($`r movies.year.regression.distinct`$).
 On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants ($`r banjo.2years.data`$).
@@
 Figure\ \@ref(fig:habituals-endorsement-figure)C provides insight into how the uncertain-threshold model is able to match human judgments. 
-The endorsement model simulates how an interpreter would under the habitual sentence.
+The endorsement model simulates how an interpreter would understand the habitual sentence.
 A habitual is interpreted relative the prior distribution over frequencies, and the comparison between the frequency implied by the habitual vs.
 staying silent results in different frequencies at which the generalization is good to assert.
-Climbing mountains three times in the past year is good evidence that you *climb mountains*; going for a hike three times in the past year is less convincing that you *hike*; and if you went for a run three times in the past year, you not a person who *runs*.
+Climbing mountains three times in the past year is good evidence that you *climb mountains* because it is approximately the frequency that a listener would infer given the utterance; going for a hike three times in the past year is correspondingly less convincing that you *hike*; and if you went for a run three times in the past year, you not a person who *runs*.
 Only the uncertain-threshold model is able to draw these subtle distinctions.
@@
 
-There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}B; green points).
+There is a clear and consistent negative effect of preventative information on endorsements for the habitual sentence (Figure \ref{fig:habituals-predictive-figure}A; white bars).
 When collapsing across items, the Bayesian Maximum A-Posteriori estimate and 95\% highest probability density interval for the true endorsement probabilities per condition are: baseline = 
@@
 ].
-Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$).
+Still, frequency --- even predictive frequency --- does not perfectly explain the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.predictiveFreq`$; MSE = $`r mse.habituals.predictiveFreq`$; Figure \ref{fig:habituals-predictive-figure}B).
 
@@
 We use our formal model to test whether past or predictive frequency matters for endorsement.
-To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p_{fk}$ that the endorsement model (Eq. \ref{eq:S1}) aims to convey. 
+To formalize the predictive frequency speaker model, we use the mean predictive frequency as the referent-prevalence $p$ that the endorsement model (Eq. \ref{eq:S1}) aims to convey. 
 The past frequency model is constructed using the past frequency supplied to participants as the referent-prevalence.

### 2018-05-15 analysis/talk-figures.Rmd
script for black talk figures

---
title: "R Notebook"
output: html_notebook
---

# Preamble

```{r libraries, cache = F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
library(viridis)
fig.path <- "~/Documents/research/talks/defense/figs/"

theme_black <- function (base_size = 12, base_family = "") 
{
  rebase <- rebase <- ggthemes_data$solarized$base[c(paste0("base0", 3:0),
                                             paste0("base", 0:3))]
  names(rebase) <- paste0("rebase", c(paste0("0", 3:0), 0:3))
  theme_foundation(base_size = base_size, base_family = base_family) + 
     theme(text = element_text(color = 'white'), 
           title = element_text(color = 'white'), 
           line = element_line(color = rebase["rebase01"]), 
           rect = element_rect(fill = 'black', color = NA), 
           axis.ticks = element_line(color = 'white'), 
           axis.line = element_line(color = rebase["rebase01"],
                                    linetype = 1), axis.title.y = element_text(angle = 90), 
           legend.background = element_rect(fill = NULL, color = NA), 
           legend.key = element_rect(fill = NULL, colour = NULL, 
                                     linetype = 0), 
           panel.background = element_rect(fill = 'black', 
            colour = NA), 
           panel.grid = element_line(color = rebase["rebase03"]), 
           panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(),
           panel.border = element_rect(color = rebase["rebase01"]), 
           plot.background = element_rect(fill = NULL, 
            colour = NULL, linetype = 0))
}
theme_set(theme_black())

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r opts}
theme_set(theme_black())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

compute_r2 <- function(df,v1, v2, sigfigs = 3){
  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
}

compute_mse <- function(df, v1, v2, sigfigs = 3){
  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
}

project.path <- "../"
options("scipen"=10) 
```

```{r}
fig.path <- "~/Documents/research/talks/generics/mit-bcs-2018-03/figs/"
```

# Generics

### Endorsement data

```{r}
load("../paper/cached_results/case1_endorseSummary_byItem.RData") # d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes
ggplot(
    d.gen.endorse.bayes.prev %>%
      filter(!(sentence %in% c("Leopards have spots.", "Ducks have wings.",
                               "Tigers have pouches.","Kangaroos have spots.",
                               "Sharks have manes.", "Peacocks have beautiful feathers."))), 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='white',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1, color = 'white')+
  coord_flip()+
  ylab("Human endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1), option = "plasma")+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(fill = guide_colorbar(title = 'Referent Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')

ggsave(paste(fig.path, "generic-endorsement.pdf", sep = ""), 
       width = 7, height = 5)
```

### Priors

```{r}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

ggplot(m.gen.endorse.priors.posteriorPredictive %>%
         filter(src == 'Data'), 
           aes( x = prevalence))+
           #aes( x = prevalence, color = src, lty = src))+
    geom_density(aes(y = ..scaled..), adjust = 0.5, size = 1, color = 'white')+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #stat_ecdf(size = 1)+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    #scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("Human prevalence rating") +
    ylab("Normalized probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

ggsave(paste(fig.path, "generic-priors.pdf", sep = ""), 
       width = 6, height = 3.5)
```

Filtered out 0 responses

```{r}
ggplot(m.gen.endorse.priors.posteriorPredictive %>%
         filter(src == 'Data', prevalence > 0), 
           aes( x = prevalence))+
           #aes( x = prevalence, color = src, lty = src))+
    geom_density(aes(y = ..scaled..), adjust = 0.5, size = 1, color = 'white')+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #stat_ecdf(size = 1)+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    #scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("") +
    ylab("Normalized probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

ggsave(paste(fig.path, "generic-priors-nonZero.pdf", sep = ""), 
       width = 7, height = 4)
```

## Models

```{r}
load("../paper/cached_results/case1_regressionResults.RData") # d.gen.endorse.regression.prevalence, d.gen.endorse.regression.prevalence.cuevalidity, d.gen.endorse.regression,
r2.gen.n <- length(d.gen.endorse.bayes.prev$sentence)
r2.gen.regression.prev <- round(with(d.gen.endorse.regression.prevalence, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev <-  round(mean(d.gen.endorse.regression.prevalence$sqErr), 3)

r2.gen.regression.prev.cv <- round(with(d.gen.endorse.regression.prevalence.cuevalidity, cor(MAP_h, prediction_mean))^2, 3)
mse.gen.regression.prev.cv <- round(mean(d.gen.endorse.regression.prevalence.cuevalidity$sqErr), 3)

intermediate.prev.quantiles <-  quantile(d.gen.endorse.regression.prevalence$prev_mean, c(0.25, 0.76))

d.gen.endorse.regression.prevalence.intermediateprev <- d.gen.endorse.regression.prevalence %>%
  filter(
    (prev_mean > intermediate.prev.quantiles[["25%"]]) &
    (prev_mean < intermediate.prev.quantiles[["76%"]])
)
r2.gen.n.intermedprev <- length(d.gen.endorse.regression.prevalence.intermediateprev$sentence)

r2.gen.regression.prev.intermedprev <- round(with(d.gen.endorse.regression.prevalence.intermediateprev, cor(MAP_h, prediction_mean))^2,2)
mse.gen.regression.prev.intermedprev <-  round(mean(d.gen.endorse.regression.prevalence.intermediateprev$sqErr), 3)
```

```{r generic-model-scatters, cache = F}
load("../paper/cached_results/case1_modelPosteriors.RData")
#d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt

r2.gen.rsa.generics <- compute_r2(
  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
  "prediction_mean", "MAP_h", sigfigs = 4
)

r2.gen.rsa.fixed <- compute_r2(
  d.gen.endorse.rsa.regression %>% filter(src == "Fixed semantics model"),  
  "prediction_mean", "MAP_h", sigfigs = 4
)

mse.gen.rsa.generics <- compute_mse(
  d.gen.endorse.rsa.regression %>% filter(src == "Uncertain semantics model"), 
  "prediction_mean", "MAP_h", sigfigs = 5
)

mse.gen.rsa.fixed <- compute_mse(
  d.gen.endorse.rsa.regression %>% filter(src == "Fixed semantics model"),  
  "prediction_mean", "MAP_h", sigfigs = 5
)

for (s in levels(d.gen.endorse.rsa.regression$src)){
  ggplot(d.gen.endorse.rsa.regression %>% 
           filter(src == s), 
         aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4, color = 'grey90')+
  geom_errorbarh(alpha = 0.4, color = 'grey90')+
  geom_point(shape = 21, size = 3, color = 'grey90')+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_viridis(option = "plasma")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  guides(fill = F)

  ggsave(paste(fig.path, "generic-scatters", s, ".pdf", sep = ""), 
       width = 3, height = 3)

}

```

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}

category.text.labels <- data.frame(property = c("dont eat people", 
                      "carry malaria", "lay eggs",  "are female", "have spots"),
             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
            y = c(0.45, 0.5, 0.45, 0.5, 0.26))

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

# Habituals

### Priors

```{r}
load("~/Documents/research/habituals/writing/_cogsci2016/rdata/expt1-prior-stats.RData")

ggplot(prior.stats, aes(x = eMAP, y = fMAP, shape = Gender))+
  #geom_errorbar(aes(ymin = fcredLow, ymax = fcredHigh), alpha=0.5)+
  #geom_errorbarh(aes(xmin = ecredLow, xmax = ecredHigh),alpha=0.5)+
  geom_point(size=4, alpha = 0.9, color = 'white')+
  xlab("% done it before")+
  ylab("frequency (log scale)")+
  scale_shape_manual(values=c(21,22))+
  #theme_paper()+
  #scale_color_solarized()
  #scale_fill_brewer(palette='Set3')+
  coord_fixed(ratio = 1/8)+
  theme(legend.title = element_text(hjust=0))+
  scale_x_continuous(limits = c (0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(
      limits = c(0, 8),
      breaks = c(1.6, 4.1, 5.5, 7.5),
      labels = c("annually", "monthly", "weekly", "daily")
      )

  ggsave(paste(fig.path, "habituals-priors-scatter-legend2.pdf", sep = ""), 
       width = 4.5, height = 4.5)

```

```{r habituals-endorsement-gender-exploration}
load("../paper/cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
load("../paper/cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression
load("../paper/cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, md.hab, hab.listener.predictions

gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

r2.habituals.gendered <- compute_r2(d.hab.bayes.gendered.wide, "map_female", "map_male")
n.habituals.gendered.analysis <- length(d.hab.bayes.gendered.wide$habitual)
r.habituals.gendered.analysis <- round(with(d.hab.bayes.gendered.wide, cor(map_female, map_male)), 3)

n.habituals.gendered.subset.analysis <- length(d.hab.bayes.gendered.subset.wide$habitual)
r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, 
                                                   cor(map_female, map_male)), 3)
```

```{r habituals-regression-models}

r2.hab.n <- length(d.hab.endorse.regression.freq$MAP_h)

r2.habituls.regression.freq <- compute_r2(d.hab.endorse.regression.freq,
                                          "MAP_h", "prediction")

mse.habituls.regression.freq <- compute_mse(d.hab.endorse.regression.freq,
                                          "MAP_h", "prediction")

r2.habituls.regression.infrequent.freq <- d.hab.endorse.regression.freq %>%
  filter(logAnnualRate < 1.1)

r2.hab.infrequent.n <- length(r2.habituls.regression.infrequent.freq$MAP_h)

r2.habituls.infrequent.regression.freq <- compute_r2(r2.habituls.regression.infrequent.freq,
                                          "MAP_h", "prediction")

mse.habituls.infrequent.regression.freq <- compute_mse(r2.habituls.regression.infrequent.freq,
                                          "MAP_h", "prediction")

r2.habituls.regression.freq.distinct <- compute_r2(d.hab.endorse.regression.freq.mix,
                                          "MAP_h", "prediction")

mse.habituls.regression.freq.distinct <- compute_mse(d.hab.endorse.regression.freq.mix,
                                          "MAP_h", "prediction")

```

```{r habituals-rsamodels}

## model parameters
fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
hab.fixed.threshold.s1opt <- filter(fixed.hab.params.posterior, B == "speakerOptimality")

r2.habituals.rsa.fixed <- compute_r2(
  m.hab.endorse.rsa %>% filter(src == "some_model"),
                                          "MAP_h", "MAP")

mse.habituals.rsa.fixed <- compute_mse(
  m.hab.endorse.rsa %>% filter(src == "some_model"),
                                          "MAP_h", "MAP")

r2.habituals.rsa.uncertain <- compute_r2(
  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
                                          "MAP_h", "MAP")

mse.habituals.rsa.uncertain <- compute_mse(
  m.hab.endorse.rsa %>% filter(src == "habituals_model"),
                                          "MAP_h", "MAP")

habituals.rsa.uncertain.infrequent <- m.hab.endorse.rsa %>% filter(src == "habituals_model", logAnnualRate < 1.1)

r2.hab.rsa.infrequent.n <- length(habituals.rsa.uncertain.infrequent$MAP_h)

r2.habituals.rsa.uncertain.infrequent<- compute_r2(habituals.rsa.uncertain.infrequent,
                                          "MAP_h", "MAP")

mse.habituals.rsa.uncertain.infrequent <- compute_mse(habituals.rsa.uncertain.infrequent,
                                          "MAP_h", "MAP")

example.habituals <- c( 
                       #"wears a watch", "wears socks", 
                       "writes poems", "writes novels",
                      "goes to the movies", "watches space launches",
                      "smokes cigarettes","drinks coffee",
                       "climbs mountains","hikes", "runs"
                       )
```

```{r}
for (s in levels(factor(md.hab$src))){

md.hab %>% 
    filter(src == s) %>%
ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 2, color = 'grey60')+
  geom_linerange(alpha = 0.15, color = 'grey60')+
  geom_errorbarh(alpha = 0.15, color = 'grey60')+
  geom_point(shape = 21, size = 3, color = 'white')+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  #scale_fill_viridis(option = 'plasma')+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human endorsement")+
  guides(fill = guide_colorbar(title = 'log annual rate',
                               ticks = F,
                               title.position="top"))+ 
  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
        legend.direction = 'horizontal',
        #legend.position = c(0.025,0.975),
        #legend.position =c(1,1),
        legend.justification = c(1,1)
        )+
    guides(fill = F)

    ggsave(paste(fig.path, "habitual-scatters", s, ".pdf", sep = ""), 
       width = 3, height = 3)

}

```

## Predictive habituals

```{r loadCase2PredictiveData, cache =F}
load("../paper/cached_results/case2_predictive_data.RData")
#d.hab.predictive.endorsment.summary, d.hab.predictive.summary, n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse,n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, lmer.rs.hab.predictive.summary
```

```{r, cache = F}
r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)

r2.habituals.predictiveFreq <- compute_r2(d.hab.predictive.endorsment.summary,
                                          "logAnnualFutureRate", "MAP_h")
mse.habituals.predictiveFreq <- compute_mse(d.hab.predictive.endorsment.summary,
                                          "logAnnualFutureRate", "MAP_h")

d.hab.predictive.endorsment.baseline.summary <- d.hab.predictive.endorsment.condition.summary %>%
  filter(condition == 'baseline')

d.hab.predictive.endorsment.preventative.summary <- d.hab.predictive.endorsment.condition.summary %>%
  filter(condition == 'preventative')

d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
  filter(condition == 'enabling')
```

```{r fighabfreq_predictive_vs_past, cache = F}
fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary %>%
                                            ungroup() %>%
                                            mutate(condition = factor(condition,
                                                                      levels = c("preventative", "baseline", "enabling"))) %>%
                                            mutate(src = 'Manipulation check'),
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), size = 4,
              color = 'white')+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'white')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  facet_wrap(~src)+
  guides(fill=guide_legend(reverse = T), shape=guide_legend(reverse = T))+
  scale_fill_brewer(type = "seq", palette = 2)+
  xlab("Past frequency")+
  ylab("Predicted frequency")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(vjust = 1),
        axis.title.y = element_text(vjust = 1))

fig.hab.freq.predictive.vs.past

ggsave(fig.hab.freq.predictive.vs.past, 
       file = paste(fig.path, "habituals_predictives_manipCheck.pdf", sep =""),
       width = 6, height = 4)
```

```{r habituals-predictive-endorsement, cache = F, eval = F}

fig.hab.endorse.vs.predfreq <- d.hab.predictive.endorsment.summary %>%
  ggplot(., aes(x=logAnnualFutureRate, y=MAP_h, 
                 fill=condition, shape=condition,
                 xmin = future_lower, xmax=future_upper,
                 ymin=low, ymax = high))+
  geom_errorbar(alpha=0.8)+
  geom_errorbarh(alpha=0.8)+
  scale_shape_manual(values=c(21,22,23,24))+
  geom_point(alpha = 1, size = 4, color = 'white')+
  xlab("Predicted frequency (log scale)")+
  ylab("Human endorsement")+
  scale_x_continuous(limits = c(-4.2,7.2), 
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  coord_fixed(ratio=11.4)+
  scale_fill_brewer(type = "seq", palette = 2)+
  guides(fill = F, shape = F)+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position="bottom",
    legend.direction="horizontal"
    )

fig.hab.endorse.vs.predfreq

ggsave(fig.hab.freq.predictive.vs.past, 
       file = paste(fig.path, "habituals_predictives_prevEndorse.pdf", sep =""),
       width = 5, height = 3)
```

```{r habituals-predictive-rsa, cache = T, eval=T}
n_chains <- 3
# n_samples <- 500000
# burn <- n_samples / 2
# lg <- 150
model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
n_samples <- 100000
burn <- n_samples / 2
lg <- 50

m.hab.pred.samp <- data.frame()
m.hab.past.samp <- data.frame()

project.path <- "../"

load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-predictive-100000_burn50000_lag50_3chains.RData", sep = ""))

load(file = paste(project.path,  "models/habituals/results/results-habituals-predictive-jointModel-S1-smtncs_habitual-past-100000_burn50000_lag20_3chains.RData", sep = ""))

m.hab.pastmodel.endorsement <- m.hab.past.samp %>%
  filter(type == 'predictive', C == "endorsement") %>%
  rename(item = B, condition = D, binned_freq = E) %>%
  group_by(item, condition) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.predictive.endorsement <- m.hab.pred.samp %>%
  filter(type == 'predictive', C == "endorsement") %>%
  rename(item = B, condition = D, binned_freq = E) %>%
  group_by(item, condition) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.predictive.endorse.rsa <- bind_rows(
  left_join(
    d.hab.predictive.endorsment.summary,
    m.hab.predictive.endorsement
  ) %>%
    mutate(src = "predictive_model"),
  left_join(
    d.hab.predictive.endorsment.summary,
    m.hab.pastmodel.endorsement
  ) %>%
    mutate(src = "past_model")
)

r2.habituals.rsa.past <- compute_r2(
  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
                                          "MAP_h", "MAP")

mse.habituals.rsa.past <- compute_mse(
  m.hab.predictive.endorse.rsa %>% filter(src == "past_model"),
                                          "MAP_h", "MAP")

r2.habituals.rsa.predictive <- compute_r2(
  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
                                          "MAP_h", "MAP")

mse.habituals.rsa.predictive <- compute_mse(
  m.hab.predictive.endorse.rsa %>% filter(src == "predictive_model"),
                                          "MAP_h", "MAP")

r2.hab.rsa.predictive.n <- length(d.hab.predictive.endorsment.summary$MAP_h)
```
```{r}
View(m.hab.predictive.endorse.allModels)
```

```{r habituals-predictive-endorsement-bars}
pred.items.of.interest <- c("climbs mountains","steals cars", "steals chewing gum",
                            "writes novels", "hikes","plays the banjo",
                            "smokes marijuana","runs","watches space launches",
                            "smokes cigarettes","drinks coffee", "writes poems")

habituals.endorsement.pred.bars <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         # src =factor(src , 
         #             levels = c("human data","predictive_model", "regression_pastfreq",
         #                              "regression_futurefreq","past_model"),
         #             labels= c("Human data", "Uncertain semantics  \n(Predictive frequency)", "regression_pastfreq",
         #                       "Regression              \n(Predictive frequency)", "Uncertain semantics\n(Past frequency)      ")),
         src =factor(src , 
                     levels = c("regression_pastfreq",
                                "regression_futurefreq",
                                "past_model", 
                                "predictive_model","human data"),
                     labels= c(
                               "Past frequency",
                                "Predictive frequency",
                                "Uncertain semantics\n(Past frequency)",
                               "Uncertain semantics \n(Predictive frequency)", 
                               "Human data")),
         hab_time = gsub("-","\n(", hab_time),
         hab_time = paste(hab_time, ")", sep = "")) %>%
         # hab_time = factor(hab_time, 
         #                   levels = c("climbs mountains\n(5 years)","hikes\n(year)","runs\n(2 months)",
         #                    "watches space launches\n(2 years)", 
         #                              "steals cars\n(5 years)",
         #                              "steals chewing gum\n(5 years)",
         #                    "writes novels\n(5 years)", 
         #                    "writes poems\n(year)","plays the banjo\n(year)",
         #                    "smokes marijuana\n(year)",
         #                    "smokes cigarettes\n(month)",
         #                    "drinks coffee\n(month)"))) %>%
  # filter(#src != "regression_pastfreq",
  #        item %in% pred.items.of.interest) %>%
ggplot(., 
       aes (y = MAP, ymin = cred_lower, ymax = cred_upper, 
            x = src, fill = condition))+
  #geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  geom_col(position = position_dodge(0.7), color = 'white', width = 0.7)+
  geom_linerange(alpha = 0.8, size = 1, position = position_dodge(0.7),
                 color = 'white')+
  #geom_point(shape = 21, size = 3)+
  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_viridis(discrete = T)+
  scale_fill_brewer(type = "seq", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  #coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model")+
  #facet_grid(src~., scales = 'free')+
  facet_wrap(~hab_time)+
  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45,
                                   lineheight = 0.7),
        legend.position = "bottom")

habituals.endorsement.pred.bars
# 
ggsave(habituals.endorsement.pred.bars,
      file = paste(fig.path, "habituals_predictives_bars2_all.pdf", sep =""),
      width = 16, height = 12)
```

```{r habituals-predictive-endorsement-scatters, cache = F}
habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         src =factor(src , levels = c("human data", "regression_pastfreq",
                                     "past_model", "regression_futurefreq",
                                      "predictive_model"),
                     labels= c("Human data","regression_pastfreq", 
                                "Uncertain semantics (Past)", "Linear model (Predictive frequency)","Uncertain semantics (Predictive)"))) %>%
  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
ggplot(., 
       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
            y = MAP_h, ymin= low, ymax = high, fill = condition,
            shape = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3, color = 'white')+
  #geom_linerange(alpha = 0.15)+
  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
  geom_linerange(alpha = 0.5, size = 1, color = 'white')+
  geom_errorbarh(color = 'white', alpha = 0.5)+
  geom_point(size = 3, color ='white')+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_shape_manual(values=c(21,22,23))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_brewer(type = "seq", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model prediction")+
  facet_grid(.~src)+
  theme(legend.position = "right")

ggsave(habituals.endorsement.pred.scatters, 
       file = paste(fig.path, "habituals_predictive_modelScatters.pdf", sep =""),
       width = 10, height = 5)
```

# Causals

```{r load_causals_results}
load(file = "../paper/cached_results/case3_endorsementDataModel.RData")
#md.cas.fullmodel.endorsement,
#      md.caus.endorse, 
#      n.subj.cas.endorse, 
#      ave.minutes.cas.endorse,
#      n.subj.cas.endorse.failed,

load(file = "../paper/cached_results/case3_priorRatings.RData")
# d.cas.priors, 
   #  n.subj.cas,
  #   n.subj.cas.failed,
 #    ave.minutes.cas,
```

```{r}

n.caus.endorse <- length(md.caus.endorse$MAP_h)
r2.caus.rsa <- compute_r2(md.caus.endorse, "MAP_h", "MAP")
mse.caus.rsa <- compute_mse(md.caus.endorse, "MAP_h", "MAP")

```

```{r figure-causals-priors}

fig.causals.priors.data <- d.cas.priors %>%
    select(distribution, response) %>%
    rename(prevalence = response) %>%
    mutate(distribution = factor(distribution, 
           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
           labels = c("Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))) %>%
ggplot(.,
       aes( x = prevalence , fill = distribution))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'white') + 
    scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+

  #geom_bar(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  #geom_density(size = 0.4, aes( y = ..scaled.. ))+
  #scale_fill_solarized()+
  #scale_linetype_manual(values = c(2, 1))+
  facet_wrap(~distribution, scales = 'free', nrow = 2)+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))+
  guides(fill = F)+
  ylab("Proportion of responses")+
  xlab("Prevalence rating")

fig.causals.priors.data

ggsave(fig.causals.priors.data,
         file = paste(fig.path, "causals-priors.pdf", sep = ""), 
       width =6, height = 4.5)

```

```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
figure.causals.endorsement <- md.cas.fullmodel.endorsement %>%
  mutate(
    src = factor(src, levels = c( "model", "data")),
    dist = factor(dist, 
           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
           labels = c(
                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common")),
    frequency = factor(frequency, 
                       levels = c(20, 70),
                       labels = c("Referent prevalence = 0.2",
                                  "Referent prevalence = 0.7")
    )) %>%
  ggplot(., aes( x = src, y = MAP, ymin = cred_lower, ymax = cred_upper, 
                 fill = dist #linetype = dist, 
                 #shape = dist,
                #        group = dist#, 
                 #alpha = src
                 ))+
  geom_bar(stat='identity', position = position_dodge(0.9), width = 0.9, color = 'white')+
  geom_errorbar(position = position_dodge(0.9), width = 0.3,alpha = 0.8, color = 'white')+
  #geom_linerange(position = position_dodge(), alpha=0.8)+
  #geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
  #geom_point(position = position_dodge(8), size = 2.25)+
  #theme(axis.text.x = element_text(angle = 90))+
  #geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_alpha_manual(values = c(1, 0.3))+
  #scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
  #scale_fill_solarized()+
  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
  xlab("")+
  ylab("Causal Endorsement")+
  facet_grid(.~frequency)+
  #coord_flip()+
  #coord_fixed(ratio = 90)+
  #guides(fill = F)+
  guides(
    #shape=guide_legend(title="Background distribution"),
    fill=guide_legend(title="Background distribution")
    )+
  theme(
    #plot.margin = unit(c(0,6,0,6), "pt")
    #legend.position = 'bottom', 
    # legend.direction = 'horizontal', 
    # legend.title = element_blank()
  )

ggsave(figure.causals.endorsement,
         file = paste(fig.path, "causals-endorsements.pdf", sep = ""), 
       width =8, height = 4)
```

### 2018-05-24 paper/case2-habituals.Rmd
introduce idea that habituals should be like generics

@@
 As with categories, particular events like "Mary smoked yesterday" can be generalized into *habitual sentences*: "Mary smokes". 
+It is believed that an analysis of generics should lend itself naturally to be extended to an analysis of habituals [e.g., @Carlson2005; @Leslie2008].
 <!-- Events are a broad class of entities.  -->
@@
 Finally, if habituals (and generics) are truly language for conveying generalizations, they should reflect speakers' expectations, not merely their observations. 
+This intuition is sometimes expressed as an intensional meaning component of generics [@Dahl1975].
+For example, imagine a very small town where by total coincidence, all residents chew sugarless gum. 
+Endorsing the sentence "Residents of this town chew sugarless gum" seems to commit the speaker to believing that it is not sheer happenstance, but that there is some underlying cause that supports the counterfactual implication that were a new person to become a resident of the town, they too would likely chew sugarless gum.
+
 Our computational model predicts endorsement rates given a referent prevalence $p$. 
 Does prevalence represent the actual, objective frequency in the world (e.g., the rate at which a person has smoked cigarettes in the past) or a subjective, predictive belief in the head (e.g., the rate at which a person is expected to smoke in the future)?
-Such a distinction could explain why "Supreme Court Justices have even social security numbers" sounds strange even if nine out of the nine current justices have even social security numbers [@Cohen1999]: Our predictions about the evenness of the *next* justice's social security number are driven by strong prior beliefs that selection for the Supreme Court is uncorrelated from the numerical properties of one's social security number; the current observations are not enough in this case to sway those beliefs.
-<!-- not swayed by these observations due to -->
-We elucidate this aspect of our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (e.g., the person buys a pack of cigarettes; Expt.
-2c).
-We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.
+Such a distinction would support the intuitions about sugarless gum residents and could explain why "Supreme Court Justices have even social security numbers" sounds strange even if nine out of the nine current justices have even social security numbers [@Cohen1999]: Our predictions about the evenness of the *next* justice's social security number are driven by strong prior beliefs that selection for the Supreme Court is uncorrelated from the numerical properties of one's social security number; the current observations are not enough in this case to sway those beliefs.
+We examine this aspect of the theory by measuring endorsements of habituals when causal forces intervene on the world (e.g., the person buys a pack of cigarettes; Expt.
+2c) as well as participants' predictions about the likely frequency of the event in the future.
+We then construct generic endorsement models based on speakers aiming to convey the objective, past frequency or their subjective, future expectation to try to predict the habitual endorsement patterns.
 

### 2018-05-27 paper/case1-generics.Rmd
edits to causals; describe model in terms of ingredients; describe fixed threshold model as lesioned; begin edits in discussion

@@
 \ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
-There are several substantive components to this hypothesis: (a) the prior distribution $P(p)$ is relevant, (b) endorsement is a decision-theoretic process of uttering the generalization vs.
-not uttering it, and (c) the core semantics of a generalization is an uncertain threshold.
-As a control model, we assign a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keep the prior and the decision-theoretic architecture in place. 
-This provides a strict test of the uncertain-threshold hypothesis (c).
+There are several substantive components to this hypothesis: (a) context in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) vagueness in the semantics of a generalization.
+We construct an alternative, lesioned model by removing the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keeping the prior and the decision-theoretic architecture in place.
+There are no correspondingly simple ways to lesion the other two components (context or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.
 
@@
 
-#### Fixed-threshold with noise model
+#### Lesioned model (no vagueness)
 
 For a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
-In addition, we make this fixed-threshold a parameter of the data-analysis model, to search for the best possible fixed-threshold. 
-Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional noise parameter, to allow for random guessing.
+We make this the strongest, possible fixed-threshold model by searching for the best possible single, threshold that fits the data.
+Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional extrinsic noise parameter, to allow for random guessing.
 Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
@@
 
-generics.endorsement.models <- ggplot(d.gen.endorse.rsa.regression, 
+generics.endorsement.models <- d.gen.endorse.rsa.regression %>%
+  mutate(src = factor(src,
+                       levels = c("Prevalence",
+                                 "Uncertain semantics model",
+                                 "Cue validity + Prevalence",
+                                 "Fixed semantics model"
+                                 ),
+                       labels = c("Prevalence",
+                                 "Generic Endorsement model",
+                                 "Cue validity + Prevalence",
+                                  "Lesioned endorsement model\n(no vagueness)"
+                                 )
+                      )) %>%
+  ggplot(., 
          aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,

### 2018-05-27 paper/case2-habituals.Rmd
edits to causals; describe model in terms of ingredients; describe fixed threshold model as lesioned; begin edits in discussion

@@
                                       "regression_freq", 
+                                      "habituals_model",
                                       "regression_freq_distinct",
-                                      "some_model",
-                                      "habituals_model"
+                                      "some_model"
                                      ),
@@
                                  "Referent frequency", 
+                                 "Endorsement model",
                                  "Distinctiveness + \n referent frequency",
-                                 "Fixed semantics",
-                                 "Uncertain semantics"
+                                 "Lesioned model\n(no vagueness)"
                                  ) )) %>%
@@
 
-#### Fixed-threshold endorsement model
+#### Lesioned model (no vagueness)
 
 We next examine an information-theoretic endorsement model based on a fixed-threshold semantics.
-A fixed-threshold model commits the habitual to conveying literally that a person *does the action with some non-zero frequency*, and the threshold on frequency is the same for all actions.
+This model is identical to the full endorsement model, but is lesioned to not have vagueness, or uncertainty about the meaning.
+A fixed-threshold model commits the habitual to conveying literally that a person *does the action with some frequency*, and that threshold on frequency is the same for all actions.
 As in Case Study 1, we incorporate this model into a Bayesian joint-inference model to infer the fixed-threshold and simultaneously predict both the priors data and the endorsement data (for more details on model implementation, see Appendix C).
@@
 
-#### Uncertain-threshold endorsement model
+#### Uncertain threshold model
 

### 2018-05-27 paper/case3-causals.Rmd
edits to causals; describe model in terms of ingredients; describe fixed threshold model as lesioned; begin edits in discussion

@@
 Language about causal relationships manifests in generalization.
-The utterance "Fire causes smoke" relates to "This fire caused this smoke" in a way analogous to how "John runs" relates to  "John ran yesterday". 
+The utterance "Fire causes smoke" seemingly relates to "This fire caused this smoke" in a way analogous to how "John runs" relates to  "John ran yesterday". 
 <!-- \ndg{"my grandpa's..." is itself a generic...
@@
 
-In this experiment, we manipulate participants' background knowledge, measuring these beliefs in order to check whether the manipulation was successful. 
-Experiment 3b (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.
+In this experiment, we manipulate participants' background knowledge, and measure these beliefs in order to check whether the manipulation was successful. 
+Experiment 3b (*causal endorsement*) uses a very similar experimental procedure in exploring causal generalization language.
 
@@
 
-Participants were then shown "previous experimental results", which followed one of four distributions.
+Participants were then shown *previous experimental results*, which followed one of four distributions.
 In two of the conditions, participants saw results that came from a single underlying distribution (*common* conditions).
-In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the *common strong* condition).
-In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the *common weak* condition).
+In one of these conditions, all causes produced a strong effect (*common strong* condition; average efficacy approximately 98\%).
+In the second of these conditions, all causes produced a weak effect (*common weak* condition; average efficacy approximately 20\%).
 <!-- The results of the previous experiments were described verbally  -->
@@
 Participants are asked to review previous results once all displayed.
-B: Prior elicitation task: Participants predict the results of the next 5 experiments.
-D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, cache=F}
+D: Prior elicitation task: Participants predict the results of the next 5 experiments.
+E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, cache=F}
 caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
@@
 Participants were told that they were an astronaut-scientist on a distant planet trying to figure out how some system works (i.e., how to make a certain kind of animal sleepy with different herbs or how to make a plant grow tall with different fertilizers).
-The story for the "sleepy animals" condition read:
+The story for the *sleepy animals* condition read:
 
@@
 Participants were asked to predict the results of the next 5 experiments (Figure \@ref(fig:causalExpt)D).
-Participants were given five slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).
+Participants were given five slider bars ranging from 0 - 100, and asked to predict the outcomes for the next five substances (e.g., herbs M, N, P, Q, and R).
 
-After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
+After responding, participants then completed an attention check survey where they were asked the topic the team of scientists was investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
 This attention check served to confirm that participants had encoded both relevant aspects of the experiment (the domain and the frequencies).
@@
   #scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))+
   guides(fill = F)+

### 2018-05-27 paper/comgen-paper.Rmd
edits to causals; describe model in terms of ingredients; describe fixed threshold model as lesioned; begin edits in discussion

@@
 Insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
-In this paper, we propose such a semantic core.
-To do so, we draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] and truth-functional semantics [@Montague1973; @Cohen1999] to formalize the context-dependent aspects of language interpretation [@Frank2012] jointly with the core semantic hypothesis: The meaning of an utterance conveying generalization is a vague description of subjective, predictive probabilities.
+In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
+A semantics based on probability is not enough, however.
+We propose that the meaning of generalizations is underspecified or *vague* and that listeners derive a more precise interpretation in context.
+The fact that generics are vague, however, does not preclude them from being treated with formal models.
+We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
 By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested.
@@
 The paper is organized as follows. 
-In Section 1, we describe the computational model, which formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge is formally described.
+In Section 1, we describe the computational model of interpreting generalizations which has three components: Probability, vagueness, and context. 
+<!-- formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge is formally described.
+-->
 Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgments about the truth or acceptibility of a sentence.
@@
 
-If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization.
+If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
 In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
 The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-Thus, the simplest semantics for a generalization is a threshold on the prevalence: $\denote{gen}(p, \theta) = \{p >\theta\}$.
-
-<!-- Attempts of this kind have been made before in formal semantics [e.g., by positing that $\theta = 0.5$; @Cohen1999], but heretofore no model has made precise, quantitative predictions about adult judgments.
--->
-<!-- In addition to articulating an explicit semantic hypothesis, we present a Bayesian cognitive model that uses this semantics in order to update its beliefs from language. -->
-<!-- We then ask: When would a rational speaker choose to produce a generalization (vs. staying silent) to update the Bayesian model's state of knowledge? -->
-
-<!-- We distinguish our proposal from previous ones by emphasizing the predictive nature of $p$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.
--->
-<!-- $p$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief. -->
-
-<!-- We emphasize that this account is based on a probability $h$. -->
-<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the prevalence $h$.^[ -->
-<!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
-<!-- ] -->
-<!-- Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself.  -->
-<!-- Probability is a measure of belief.  -->
-
-### Literal interpretation model
-
-The simplest semantics for a generalization is a threshold function: $\denote{gen}(p, \theta) = \{p >\theta\}$, but what threshold is appropriate?
-Quantifier statements can be described using particular values of $\theta$: $\denote{some}(p) = \{p > 0\}$; $\denote{all} = \{p = 1\}$.
-The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
-Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
-
-<!-- So what threshold $\theta$? should be used for the generalizations?  -->
-<!-- Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$. -->
-
-We formalize this underspecified, or vague, semantics in a Bayesian cognitive model, where the threshold $\theta$ is sampled from a uniform prior distribution over possible thresholds $P(\theta)$ [@Lassiter2013;   @Lassiter2015; cf., @Qing2014].^[
-  Following @Lassiter2015, we defined $P(\theta)$ to be a uniform distribution over the support of $P(p)$.
-]
-The model also has prior knowledge about the property $P(p)$ (described in more detail below) and literal interpretation is given by updating these prior beliefs according the truth-functional meaning of the utterance $\delta_{\denote{u}(p, \theta)}$:
+For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) = \{p > 0\}$.
+"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) = \{p > 0.5\}$.
+Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) = \{p >\theta\}$.
+
+The obvious next question for such a representation concerns $\theta$: What threshold is appropriate?
+It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) = \{p > 0\}$; $\denote{most} = \{p > 0.5\}$.
+In a probabilistic representation, states of uncertainty are more fundamental than states of certainty (e.g., it is a special case when an agent with probabilistic beliefs is certain about something; the more typical case is that they are uncertain).
+Thus, if quantifiers have *certain* thresholds ("some": greater than 0; "most" greater than 0.5), then perhaps generics have *uncertain* thresholds.
+We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
+
+Finally, the meanings of linguistic expressions manifest in their capacity to convey information from speaker to hearer [@Grice1975; @Clark1996; @Levinson1995].
+Thus, the final ingredient to our model is *context* (Ingredient 3), which must be minimally formalized as a listener's prior knowledge about the property $P(p)$ and which we describe in more detail below.
+
+Putting these three ingredients (probability, vagueness, and context) together, we get the following model of generic interpretation:
 
 \begin{eqnarray}
-L(p, \theta \mid u) &\propto& {\delta_{\denote{u}(p, \theta)} \cdot P(p) \cdot P(\theta)} \label{eq:L0}
+L(p, \theta \mid u) &\propto& {\delta_{\denote{u}(p, \theta)}  \cdot P(\theta) \cdot P(p)} \label{eq:L0}
 \end{eqnarray}
 
-We denote this interpretation model by $L$ to indicate that it is modeling a listener, updating their beliefs according to the truth-functional meaning of an utterance.
+We denote this probabilistic generic interpretation model by $L$ to indicate that it is modeling a listener updating their beliefs according to the truth-functional meaning of an utterance.
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
@@
 \end{eqnarray}
+
+Following @Lassiter2015, we formalize the vagueness in the meaning of generics $P(\theta)$ as a uniform distribution over the support of $P(p)$.
+
+<!-- The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice.  -->
+<!-- Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
+-->
+
+<!-- So what threshold $\theta$? should be used for the generalizations?  -->
+<!-- Unlike quantified language which have fixed-thresholds, we posit that the language of generalizations is *underspecfied* with respect to the actual truth-functional threshold $\theta$. -->
 
@@
 
-The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to eachother succinctly using language.
+The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
 Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability or \emph{prevalence}.
+We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability or *prevalence*.
 Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
@@
 
-Ours is a psychological model that leverages the insights of truth-functional semantics to articulate how an agent should update their beliefs based on a generic sentence. 
+Our model leverages the insights of truth-functional semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
 The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
 Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-Here, we demonstrate how the context-sensitivity of generics can emerges via the interplay of a stable (but vague) semantics and diverse background knowledge.
+Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
 
@@
 
+#### Default generalizations
+
+Some might object at this point and argue it is not desirable to define generics in terms of quantifiers, because generics are in many ways *more fundamental* than quantifiers [@Leslie2008; @Gelman2009].
+For example, young children learn that meaning of generics far earlier than they know what quantified language means [@Gelman2015].
+Similiarly, if you tell adults novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later ask them to recall that information, they will tend to recall the information using generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
+Rather than the contradictory to the idea that prevalence is at core of
+
 #### Striking generics

### 2018-05-31 paper/appendix-cueValidity.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

@@
 
-```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, fig.cap="Top: Empirically measured cue validity for two different tasks.
+```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Top: Empirically measured cue validity for two different tasks.
 Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).

### 2018-05-31 paper/case1-generics.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

@@
 
-Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") are of substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
+Learning from generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") is believed to play a central role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
 In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
@@
 
-We first investgate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
+We first investigate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
 We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g.
@@
 Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Figure\ \@ref(fig:generics-endorsement-figure)A for the full list).
-The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
+They were asked to press one of two buttons (*P* or *Q*; randomized between-participants) to indicate whether they agreed or disagreed with the sentence (see Figure\ \@ref(fig:generics-endorsement-figure)A for the full list).
+The thirty sentences covered a range of conceptual categories described above.
 Approximately ten true, ten false, and ten uncertain truth-value generics were selected.
@@
 As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
-indeterminate generics were agreed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
+indeterminate generics were endorsed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).
 
@@
 
-```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties.
+```{r generic-endorsement-priors-figure, fig.width = 7, fig.asp = 0.9, out.width = "\\textwidth", fig.pos = "!h", fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties.
 B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution.
@@
 What do you think X is?"; @Cree2006].
-We found that these different ways of estimating cue validity diverge for a number of key cases, possibly due to an experimenter demand effect in the direct question paradigm.
-We thus used the data from the free production paradigm ($n = 100$) to estimate cue validity. 
+We found that these two ways of estimating cue validity diverge for a number of key cases (Appendix B).
+Most notably, undiagnostic features (e.g., *is female*), which in theory have a cue validity close to zero, were rated as having intermediate cue validity in the *direct question* paradigm. 
+In response to a direct question such as "There is an animal that is female.
+What is probability that it is a robin?", participants could be responding "I don't know" rather than reporting their intuitive base rate that a random animal would be a robin.
+The free production paradigm did not produce artifacts such as this one, and we chose to use it as the more veridical estimate of cue validity. 
 For a detailed analysis of the different cue validity measurements and comparison to cue validity derived from the prevalence prior, see Appendix B.
@@
 
-```{r generics-endorsement-figure, fig.width = 11, fig.height=8.5, fig.cap="Endorsing generalizations about categories.
+```{r generics-endorsement-figure, fig.width = 11, fig.asp = 0.8, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Endorsing generalizations about categories.
 A: Human elicited endorsements for thirty generic sentences reveal a continuum of endorsements.
@@
 This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters (e.g., that not all mosquitos carry malaria).
-Importantly, the model recapitulates the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model ($r_{\text{prevalence prior parameters}}^2(`r length(m.gen.endorse.refprev.parameters[,"Parameter"])`) = `r r2.refprev.distortion`$; $r_{\text{referent prevalence parameters}}^2(`r length(m.gen.endorse.priors.parameters[,"Parameter"])`) = `r r2.prevprior.distortion`$; see Appendix D, Figure 14).
+Importantly, the model captures the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model ($r_{\text{prevalence prior parameters}}^2(`r length(m.gen.endorse.refprev.parameters[,"Parameter"])`) = `r r2.refprev.distortion`$; $r_{\text{referent prevalence parameters}}^2(`r length(m.gen.endorse.priors.parameters[,"Parameter"])`) = `r r2.prevprior.distortion`$; see Appendix D, Figure 14).
 This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
@@
 Generics have been studied extensively in the cognitive and developmental psychological literatures and have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
-Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generics: knowing when they are true and false.
+Heretofore, no formal model has been able to pass the most basic empirical test for generics: knowing when they are true and false.
 <!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->

### 2018-05-31 paper/case2-habituals.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

@@
 In order to generate model predictions for habitual endorsements, we first elicit the prior distributions over rates for different events.
-For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people do a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
+For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people perform a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
 We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1.
-In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to do the action with a stable rate and those who do not do the action.^[
+In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to perform the action with a stable rate and those who do not perform the action.^[
   It is likely that more than just these two possibilities are represented in people's intuitive theories, corresponding to individuals with additional traits or demographics.
@@
 
-```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, fig.cap="Prevalence priors for events (Expt.
+```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt.
 2a).
@@
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
-  coord_fixed()+
+  #coord_fixed()+
   ylab("Habitual endorsement")+
@@
   guides(fill = guide_colorbar(ticks = F, title = "Time interval"))+
-  theme(strip.text.y = element_blank()#,# element_text(angle = 0, hjust= 0),
+  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
         #legend.direction = 'horizontal',
         #legend.position = c(0.025,0.975),
-        #legend.position =c(1,1),
+        legend.position ='bottom',
+        legend.text = element_text(angle = 45)
         #legend.justification = c(1,1)
@@
                                        "Posterior given Habitual")),
-         action = factor(action, levels = example.habituals)
+         action = factor(action, levels = c( 
+                       "climbs mountains","hikes", "runs",
+                      "smokes cigarettes","drinks coffee",
+                      "goes to the movies", "watches space launches",
+                       "writes poems", "writes novels"
+                       ))
                                 #"climbs mountains", "hikes", "runs",
@@
   geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-  facet_wrap(~action, nrow = 1)+
+  facet_wrap(~action, nrow = 2)+
   # geom_text_repel(data = category.text.labels,
@@
   ylab("Scaled probability density")+
-  theme(#legend.position = "bottom", 
+  theme(legend.position = c(0.9, 0), 
         legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1),
-        axis.title.y = element_text(hjust = 1))+
+        axis.text.x = element_text(angle = 90, vjust = 1))+
+        #axis.title.y = element_text(hjust = 1))+
   scale_x_continuous(limits = c(-5, 8), 
@@
 
-```{r habituals-endorsement-figure, fig.width = 15, fig.asp=0.5, fig.cap="Endorsing generalizations about events.
+```{r habituals-endorsement-figure, fig.width = 13, fig.asp=0.7, fig.cap="Endorsing generalizations about events.
 A: Endorsements for nine events given different frequencies of action by human participants and four models.
@@
 These distributions are inferred using both data sources from Expts.
-2a & 2b.", cache = F}
+2a and 2b.", out.width = "\\textwidth", fig.pos = "!h", cache = F}
 
@@
 fig.hab.endorse.bars <- habituals.endorsement.bars +
-  theme(plot.margin = unit(c(16,6,6,6), "pt")) #+ ggtitle("prevalence priors")
+  theme(plot.margin = unit(c(6,6,6,6), "pt")) #+ ggtitle("prevalence priors")
 fig.hab.endorse.scatters <- habituals.endorsement.models +
-  theme(plot.margin = unit(c(0,6,6,6), "pt")) # + theme(legend.position="none") #+ ylab("")
+  theme(plot.margin = unit(c(6,6,6,6), "pt")) # + theme(legend.position="none") #+ ylab("")
 fig.hab.endorse.priors <- habituals.endorsement.insets +
-  theme(plot.margin = unit(c(0,0,6,0), "pt"))
+  theme(plot.margin = unit(c(16,36,16,36), "pt"))
 
@@
               rel_widths = c(2, 1)),
-                            # plot_grid(fig.hab.endorse.scatters,hab.legend, nrow = 1, rel_widths = c(0.6,4),
-                            #                                 axis = 't', align = 'h'),
             fig.hab.endorse.priors,
-                            labels = c("", "", "C"), nrow = 2,
+                            labels = c("", "C"), nrow = 2,
                             #axis = 'lr', 
                         #align = 'v', 
-                            rel_heights = c(2, 1))
-
+                            rel_heights = c(1.7, 1))
+
+#fig.hab.endorse.priors
 ```
@@
 B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline).
-C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7, cache=F}
+C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7,out.width = "\\textwidth", fig.pos = "!h", cache=F}
 plot_grid(

### 2018-05-31 paper/case3-causals.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

--- 2018-04-19 paper/case3-causals.Rmd
@@
 Participants are asked to review previous results once all displayed.
-B: Prior elicitation task: Participants predict the results of the next 5 experiments.
-D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, cache=F}
+D: Prior elicitation task: Participants predict the results of the next 5 experiments.
+E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, out.width = "\\textwidth", fig.pos = "!h", cache=F}
 caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
@@
 
-```{r figure-causals, fig.width=9, cache = F, fig.asp = 0.4, fig.cap="Endorsing generalizations about causes.
+```{r figure-causals, fig.width=9, cache = F, fig.asp = 0.4, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Endorsing generalizations about causes.
 A: Empirical prevalence prior distributions elicited following prior manipulation cover story (Expt.

### 2018-05-31 paper/comgen-paper.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

@@
 In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
-A semantics based on probability is not enough, however.
-We propose that the meaning of generalizations is underspecified or *vague* and that listeners derive a more precise interpretation in context.
-The fact that generics are vague, however, does not preclude them from being treated with formal models.
+A semantics based on probability will not be enough, however.
+We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using world knowledge.
+
+The fact that generics are vague does not preclude them from being treated with formal models.
 We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
-By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested.
-It is also the first theory to make quantitative predictions about human understanding of generalization in language.
+The Bayesian model separates the semantics of an utterance conveying a generalization from the world knowledge a listener would use to interpret the utterance, a key theoretical advancement beyond previous accounts.
+<!-- By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested. -->
+This formal model is the first of its kind to make quantitative predictions about human understanding of generalization in language.
 <!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
@@
 This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
-Our *prevalence* $p$ is a *prevalence in the mind*, a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
-The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
+Our *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
 The properties also vary (e.g., having fur, causing jitters, going to the gym).
@@
 The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) = \{p > 0\}$.
-"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) = \{p > 0.5\}$.
-Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) = \{p >\theta\}$.
+For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) := p > 0$.
+"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.
+Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.
 
 The obvious next question for such a representation concerns $\theta$: What threshold is appropriate?
-It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) = \{p > 0\}$; $\denote{most} = \{p > 0.5\}$.
+It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) := p > 0$; $\denote{most} := p > 0.5$.
 In a probabilistic representation, states of uncertainty are more fundamental than states of certainty (e.g., it is a special case when an agent with probabilistic beliefs is certain about something; the more typical case is that they are uncertain).
@@
 Our endorsement model (Eq.
-\ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{gen} \mid p)$.
+\ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u \mid p)$.
 The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
@@
 
+<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
+
 Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
 Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
-Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties.
+Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
+  The Beta distribution is a distribution over numbers between 0 and 1. 
+  In other words, it is a probability distribution over probabilities, which is exactly how we are modeling prevalence. 
+]
 The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
@@
 Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability or *prevalence*.
-Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
+We have argued that the core meaning of such linguistic expressions can be understood by three ingredients: Probability, vagueness, and context. 
+Though generics are vague that does not preclude them from being treated by formal models. 
+A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.
+
 <!--
@@
 -->
-We tested this theory by exploring its implications for truth judgments, modeled as a speaker's decision about whether it would be useful to utter the generalization. 
+
+We tested this theory by exploring its implications for the simplest judgments a person could make: truth judgments.
+We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
 Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
@@
 
-Our model leverages the insights of truth-functional semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
+Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
 The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
@@
 Rather than conveying probabilities explicitly, generalizations convey them implicitly.
-In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
 The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
+Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
 
@@
 
-In the rest of this discussion, we elaborate how our model relates to language understanding more generally, sketch its application to several philosophical puzzles in genericity, and situate our theory with respect to extant theories of generic language.
+In the rest of this discussion, we elaborate how our model relates to language understanding more generally, situate our theory with respect to extant theories of generic language, and sketch applications to a few philosophical puzzles in genericity.
 
@@
 
-Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
-In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components.
-Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
-Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions.
-
-Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
-We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
-We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
-The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
-Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.
-
-The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
-Not only does conceptual knowledge influence interpretation via prevalence priors, but it may very well be what the speaker intends to communicate.
-Like other probabilistic pragmatic models, our model distinguishes the semantic contribution of an utterance (what enters into the truth-functional semantics) from a speaker's utility in producing that utterance.
-For simplicity, the model presented here assumes these two are the same: the speaker's utility comes from conveying prevalence. 
-However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006].
+Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
+It is this real-world knowledge (presently formalized in terms of a *prevalence prior*) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
+<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
+<!-- Instead,  -->
+We hypothesize that all of this knowledge feeds into participants' predictions (or, judgments about prevalence).
+<!-- which we model in a precise, quantitative manner. -->
+Thus, we bring precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
+Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
+Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.
+
+ <!-- You bring precision and clarity to the judgments by capturing the output of the cognitive processes that generate prevalence.
+But you tend to downplay or at least not emphasize that importance and sometime sounds as if you think you have an alternative view that argues against some of the other perspectives.
+I think this is worth clarifying.
+-->
+
+<!-- (at least in the form of a *prevalence prior*) against which generalizations are interpreted. -->
+<!-- In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components. -->
+<!-- Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
+-->
+<!-- Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions. -->
+
+<!-- Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+-->
+<!-- We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds and their properties [@Gelman2003; @Keil1992]. -->
+<!-- We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
+-->
+<!-- The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
+-->
+<!-- Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.  -->
+
+The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
+Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
+Like other models in the probabilistic pragmatic tradition, our model distinguishes the relevant variables for the truth-functional semantics from those that impact the speaker's utility in producing the utterance.
+A speaker's utility comes from addressing an implicit goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
+The separation of the QUD from the literal, truth-functional denotation of the utterance is an important theoretical distinction made explicit in our formal modeling approach [@Goodman2016]. 
+For simplicity, the model presented here assumes the QUD is about prevalence.
+However, the model makes nearly identical predictions if the QUD concerns the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
 This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.
@@
 The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
-We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
+We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
 In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(p \mid C)$.
-
-The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
-Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
-An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
-Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
-In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics.
+Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect to some comparison class $C$: $P(p \mid C)$.
+
+In this paper, we have assumed particular values of $C$ for our three case studies (*animals*, *people*, and *possible causes*, respectively).
+We think the choice of these classes is intuitive, but it is a limitation of this work that we do not derive these choices from more general information-theoretic considerations.
+The problem of choosing a comparison classes, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012].
+We have begun to explore how pragmatic reasoning and world knowledge can flexibly adjust the comparison class to appropriately suit the context [e.g., how a "short" basketball player is *short for a basketball player* while a "tall" basketball player is *tall for a person*; @Tessler2017].
+It remains to be seen how such principles could operate on richly structured, hierarchical knowledge about categories and properties that would be important for interpreting generic language.
+
+The employment of comparison classes in our model provides additional flexibility towards modeling different communicative goals.
+The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
+Thus, our endorsement model assumes that the QUD was "*what* has this feature?".
+Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
+It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
+<!-- "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
+-->
+Prosody provides a good cue towards resolving the comparison class, and pragmatic reasoning is likely relevant here as well [@Declerck1986; @Tessler2017].
+In this work, we focused on category-wise comparison classes purely for methodological convenience.
+Future work should investigate the factors that give rise to feature-wise interpretations of generalizations (e.g., "Dogs *have four legs*", as opposed to having other features), other QUDs generics can address, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.
+
+<!-- Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
+-->
+<!-- An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
+-->
+<!-- In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics. -->
 
@@
 
-The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
-Thus, our endorsement model assumes that the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has this feature?".
-Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
-It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
-Prosodic focus can change the interpretation: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
-Pragmatic reasoning is likely relevant here as well [cf., @Declerck1986; @Tessler2017].
-In this work, we focused on category-wise comparison classes purely for methodological convenience.
-Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.
-
 <!-- Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.  -->
@@
 <!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
-Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
+Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
 <!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
@@
 -->
-This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., truth-functional notions) are inappropriate for generics [@Leslie2008].
+The assumed complexity of a formal theory of generics and the simplicity with which young children acquire generics has led some to conclude that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
 
 Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
-With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning three distinct aspects of meaning:
+With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning:
 (1) the *dimension* being described (i.e., prevalence $p$),
@@
 However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
-Thus, under our framework, generics should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
+Thus, under our framework, generics should not only be learned before quantifiers but also facilitate the acquisition of quantifiers.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
@@
 
-<!-- The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013]. -->
-
-<!-- Yet, purely arbitrary relationships can also result in true generalizations [@Nickel2008; @Nickel2016; @Sterken2015]. -->
-<!-- <!-- "Cars have tape decks" is a generalization that was true about thirty years ago, but  -->
-<!-- <!-- Barns are red" because barn-owners tend to paint their barns red; were barn-owners to decide tomorrow to switch to blue, then "Barns are red" would be false. --> 
-<!-- Ravens and toasters have no privileged relationship to each other and to assess if "Ravens are bigger than toasters", we should actually measure the distribution of sizes for ravens and toasters.
--->
-<!-- An understanding of generalizations just in terms of conceptual relations must be supplemented with the proviso that, in some situations, the actual statistics of the feature matter for making generalizations true.
--->
-
-<!-- The alternative approach to generics is to try to rescue the notion the number of members of the category with the property (e.g., the number of robins that do indeed lay eggs). -->
-
-The present paper presents the first formal theory of genericity in language that generates quantitative predictions about human behavioral data. 
-A number of other theories of genericity have been proposed in formal semantics and in psychology, which posit different constructs or psychological mechanisms to account for the diversity of generics.
-These accounts fall into two broad camps: Those that appeal to quantification or the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations or abstract beliefs (e.g., *there is something about being K which causes it to F*).
-Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]
-
-\ndg{[this should go after other theories are introduced.]
-In our account, the core meaning of generics concerns probability (the currency of belief), which in many cases may be the byproduct of rich conceptual structure. 
-The separation between conceptual structure (which exists in the head) and prevalence (a quantitative metric for natural language semantics) provides a unified view of the phenomena of generics and a single answer to the semantic question: "what do generics mean?"
-By formalizing how background knowledge influences generic understanding, our model provides a path towards unifying conceptual approaches to generics with an inherently statistical natural language semantics.
-}
-
-<!-- At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.  -->
-
-<!-- By contrast, our theory has made hundreds of predictions about individual generic statements, derived from a general theory that we posit applies to all generic statements. -->
-<!-- We now turn to situating our account with respect to these previous theories. -->
-<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*.
--->
+The present paper presents the first formal theory of generalization in language that generates quantitative predictions about human behavioral data. 
+Our work builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
+The dominant approach from formal semantics tries to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
+These views are typically *statistical* and appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
+Theorists in philosophy and psychology have argued that what matters for producing and understanding generics is not the statistics of the world, but to mental representations or abstract beliefs in the head (e.g., *there is something about being a K which causes it to F*).
+Statistical and conceptual theories express the major contrasting views of generic language [@Carlson1995essay].^[
+  We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.
+]
 
@@
 Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-The most influential account in psychology comes from @Leslie2008. 
-Leslie uses the same starting point as our account: Generics express generalization. 
-She then turns her attention to the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.^[
-  Because the mechanism for understanding generics is innate, in her account, the learning puzzle (vis a vis quantifiers) immediately goes away.
+The most influential account in psychology comes from @Leslie2008, which has same starting point as our analysis: Generics express generalization. 
+This analysis draws upon insights from the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.^[
+  Because the mechanism for understanding generics is innate, in this account, the learning puzzle (vis a vis quantifiers) immediately goes away.
 ]
-Leslie describes the *default generalization* mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
+
+The *default generalization* mechanism has three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
   This positive vs.
@@
   For the former, male birds are negative counterinstances because they simply lack the property (i.e., male birds do not reproduce by some other method).
-  We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by by a different mechanism (e.g., informativity with respect to a prevalence prior).
+  We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by a different mechanism (e.g., informativity with respect to a prevalence prior).
   The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described above).
@@
 On this account, generics are true if *some* Ks have F when all counterinstances are negative and the property is either characteristic or striking. 
-If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
-We believe that many of the key factors in this conceptual approach are compatible with our predictive probability approach: what is required is that the distinctions made by conceptual accounts influence predictive probability, which then mediates linguistic effects.
+If the property is neither characteristic nor striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
+Many of the key factors in this conceptual approach are compatible with our predictive probability approach: What is required is that the distinctions made by conceptual accounts influence predictive probability, which mediates linguistic effects.
+Indeed, one version of this mechanism is already suggested by @Leslie2008, citing findings by @Rothbart1978, that a speaker’s perception of the prevalence of the feature can be altered by virtue of its dangerousness or distinctiveness.
 
@@
 
-Some might object at this point and argue it is not desirable to define generics in terms of quantifiers, because generics are in many ways *more fundamental* than quantifiers [@Leslie2008; @Gelman2009].
-For example, young children learn that meaning of generics far earlier than they know what quantified language means [@Gelman2015].
-Similiarly, if you tell adults novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later ask them to recall that information, they will tend to recall the information using generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
-Rather than the contradictory to the idea that prevalence is at core of
+The conceptual view of generics argues it is not desirable to define generics in the same terms as quantifiers (e.g., a truth-functional threshold on prevalence), because generics are in many ways *more fundamental* than quantifiers [@Leslie2008; @Gelman2009].
+For example, young children have a nearly adult-like understanding of generics far earlier than they do with quantified language [@Gelman2015].
+Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that information will tend to recall the information using generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
+As a result, generics are thought of as conveying *default generalizations*, whereas quantified language expresses more sophisticated and specific generalizations.
+
+Rather than be contradictory to a prevalence-based truth-functional semantics, these observations independently motivate our treatment of the semantics as *underspecified*.
+Probabilistic agents typically have uncertainty about variables of interest in their environment; having certainty about a random variable is a rare and special case.
+In a probabilistic representation, then, states of uncertainty are more fundamental than states of uncertainty.
+Therefore, if quantified language can be described with *certain* thresholds  (e.g., *some* means greater than *zero*, *most* means greater than *half*), then we would expect generics, as a more fundamental linguistic device, to have an *uncertain threshold*.
+Thus, in our framework, generics behave like a more fundamental (i.e., more uncertain) quantifier.
+One distinctive feature of generics that this informal analysis does not address is that generics are *intensional* (e.g., having to do with predictions are the future) whereas quantifiers tend to be *extensional* (i.e., concerned with the actual frequencies in the world).
+How and why the intensional/extensional distinction emerges between quantifiers and generics is an outstanding issue for a theory such as ours that tries to unify the linguistic analysis of these two kinds of expressions.
 
@@
 The evolutionary argument for accepting striking generics (e.g., "Tigers eat people") is straightforward: These are relevant properties to know about if you want to survive. 
-But there are two other factors that are confounded with striking properties that make it difficult to evaluate a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
-The first is that striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
+Our theory posits two mechanisms by which striking properties could influence generic endorsement.
+<!-- But there are two other factors that are confounded with striking properties that make it difficult to evaluate a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
+-->
+The first is the prevalence prior.
+Striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
 Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*; see also our Expt.
@@
 4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
-This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar.
+This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar to each other, and distinct from that of the neutral properties.
 @Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
 
-The second factor confounded with striking properties is that striking properties may be projected more strongly (i.e., generalized to more instances of the category) than neutral properties.^[
+The second mechanism by which strikingness could influence generic enodrsement is that striking properties may be projected more strongly (i.e., generalized to more instances of the category) than neutral properties.^[
   This observation is also made by @Leslie2008 (p.42), who uses it as motivation for elevating striking properties to their special status in her theory.
@@
 Different conceptual structures may give rise to roughly the same distributions on prevalence and thus have similar endorsement profiles according to our model. 
-Yet the inferences that can be drawn from hearing these generics may differ, depeding on their interactions with the (possibly hierarchical) knowledge people bring to bear [a la the differences observed for "prevalence-matched items" in @Prasada2006].
+Yet the inferences that can be drawn from hearing these generics may differ, depending on their interactions with the putative hierarchical knowledge people bring to bear [a la the differences observed for "prevalence-matched items" in @Prasada2006].
 This is an intruiguing direction for future work.
@@
 Our underspecified threshold model has clear antecedents in other statistical accounts, most notably @Cohen1999's theory of generics as a frequency adverb (e.g., "generally").
-Cohen treats generics as comprising two qualitatively different types: *relative* and *absolute* generics.
-<!-- For Cohen, the statement "Birds lay eggs" means "Generally, birds lay eggs", and then he takes up the task of explaining what "generally" means. -->
-*Absolute generics* use a fixed, 50\% threshold on prevalence: $P(F\mid K)>0.5$. 
-That is, if a particular instance is more likely than not to have the feature, then the absolute generic is true.
-By contrast, *relative generics* are true based on a comparison to an alternative set of kinds (his notation: $Alt(K)$), analogous to our comparison class.
+Cohen treats generics as a class comprising two qualitatively different types: *relative* and *absolute* generics.
+*Absolute generics* use a fixed, 50\% threshold on prevalence: $p>0.5$. 
+That is, if a particular instance is more likely than not to have the feature, then an absolute generic is true.
+By contrast, *relative generics* are true based on a comparison to an alternative set of kinds $Alt(K)$, analogous to our comparison class.
 "Mosquitos carry malaria" is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
@@
 In our model, we treat all generics as relative. 
-Attested differences in endorsement and interpretation, then, emerge through the interplay of prior knowledge with our uncertain semantics.^[
+Attested differences in endorsement, then, emerge through the interplay of prior knowledge with our uncertain semantics.^[
   For a related theoretical argument against the "relative" / "absolute" distinction for gradable adjectives, see @Lassiter2015.
 ]
-Further, though Cohen's theory is framed in terms of probabilities, it is a fully semantic, fixed-threshold account which only makes deterministic predictions about what is true and what is false.
+Further, though Cohen's theory is framed in terms of probabilities, it is a fully deterministic, fixed-threshold account which only makes qualitative predictions about what is true and what is false.
 In contrast, we posit an uncertain threshold which is resolved in context through Bayesian inference; our theory is a joint semantic--pragmatic theory.
@@
 
-Cohen's and other statistical theories rely upon an additional mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
+Cohen's and other statistical theories employ upon an additional mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
 This mechanism is called *domain restriction*. 
@@
 ]
-The mechanism of domain restriction may be implicit in our own theory: the prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
+The mechanism of domain restriction may be implicit in our own theory: The prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
 Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
@@
 @Sterken2015 takes a novel starting point for her analysis: Generics are inherently context-sensitive.
-To understand the properties of generics, she looks to another inherently context-sensitive part of language: *indexicals* (e.g., "this" or "I").
-@Sterken2015 posits a context-sensitive "quantificational force" as well as domain-restriction [of the kind used by @Cohen1999 and others].
-Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive *quantificational force*. 
+To understand the properties of generics, this analysis draws analogy to other, inherently context-sensitive linguistic expressions: *indexicals* (e.g., "this" or "I").
+@Sterken2015 uses this to motivate a context-sensitive *quantificational force* as well as mechanism of domain-restriction [of the kind used by @Cohen1999 and others].
+Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive quantificational force. 
 We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
@@
 
-A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008]. 
+A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008; @Nickel2016]. 
 For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
 However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described in more detail below) and stereotyped language (e.g., "Boys are good at math”).
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described in more detail below) and resisting stereotyped language (e.g., "Boys are good at math”).
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
@@
 
+### A unified perspective
+
+The statistical vs.
+conceptual distinction for theories of generics is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
+Truth conditions are unified criteria that all generics must satisfy in order to be true.
+*Genericity*, on the other hand, is thought to be a non-linguistic, psychological phenomenon previously explored either in terms of pragmatics [@Declerck1991] or meta-semantics [@Leslie2007; @Liebesman2011; @Sterken2015; @Nickel2016].
+A full account of generic language must include both a theory of generics (i.e., truth conditions) and a complementary theory of genericity [@Nickel2016].
+
+In our account, the truth conditions of generics concern the currency of belief, probability, and the relevant probabilities may be informed by rich conceptual structure.
+The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.
+We chart-out a single answer to the semantic question "what do generics mean?", while also formalizing how background knowledge influences generic understanding.
+That is, our approach provides both a theory of generics and genericity, and their interaction.
+This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
+
+<!-- Other theorists have focused on the diversity among generic statements and looked beyond the semantics to explain the variability between different kinds of generics. -->
+<!-- We take the distinction between generics and genericity as roughly coextensive with what has also been described as a statistical vs. conceptual distinction [@Carlson1995essay].^[ -->
+<!--   We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively. -->
+<!-- ] -->
+<!-- Conceptual theories often appeal to factors that have an explanatory component (e.g., why the property is present in an instance). ^[ -->
+<!--   Such factors are often thought of as outside the domain of truth conditions. -->
+<!--   For example, @Nickel2016 refers to genericity as a *semantic mechanism*, and one that could plausibly interact with other semantic mechanisms (e.g., gradability in predicates as in "Giraffes are tall").
+-->
+<!--   This interaction, @Nickel2016 argues, is analogous to how gold---a chemical element with certain defining properties---can be studied in isolation but may also interact with other metals to produce an alloy.
+-->
+<!--   We would not expect a theory of gold to be able to predict with high quantitative accuracy the properties of the alloy, without a theory of the other elements involved and their respective interactive effects.
+Thus, it is important to identify when one has a pure case of genericity on their hands as opposed to an alloy.
+-->
+<!-- ] -->
+
 ## Other philosophical puzzles
 
-In this paper, we aimed to balance two competing goals in designing our experimental stimuli: (1) including some familiar, philosophically puzzling examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
-We close by discussing how a three previously-discussed examples could be addressed in our communicative framework.
+In this paper, we aimed to balance two competing goals in our experimental case studies: (1) drawing upon familiar, philosophically interesting examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
+We close by discussing how three previously-discussed, philosophically interesting examples could be addressed in our communicative framework.
 
@@
 Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
-In our framework, Sentence (1) is a extreme case of generalizations expressing *predictive* probabilities.
+In our framework, Sentence (1) is an extreme case of generalizations expressing *predictive* probabilities.
 In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency.
-We expect the same to be true with Mary: any future mail coming from Antarctica will be handled by Mary. 
-Thus the predictive probability that Mary will handle Antactican mail, if there is any, is high.
+We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary. 
+Thus the predictive probability that Mary will handle Antarctican mail, if there is any, is high.
 Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
-In this case our understanding of Mary's job leads to a strong preditcive probability in the absence of past frequency evidence.
+In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
 
@@
 That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
-Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated similarly by our model as "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
 
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then accept the generic.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
 That is, our theory predicts there are situations where statements like (2) could be considered felicitous generalizations.
@@
 Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
-However, this is the only interpretation available if the generalization is given a fixed, majority based quantificational semantics, as posited in most statistical views of generics (e.g., if the generic means *most*).
+However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
 Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
@@
 In our work, context takes the form of shared beliefs between speakers and listeners. 
-By leveraging this common ground, the language of generalizations provides a powerful way to communicate and learn generalizations, which would otherwise be difficult or costly information to learn through direct experience.
+By leveraging this common ground, the language of generalizations provides a powerful way to communicate and learn abstract knowledge, which would otherwise be difficult or costly information to acquire through direct experience.
 
@@
 -->
-The theory presented here provides the first computational perspective on how we communicate generalizations, illustrating how beliefs play a central role in the meaning of words.
+The theory presented here provides the first computational perspective on how we communicate generalizations, illustrating how beliefs play a central role in understanding the meaning of words.
 

### 2018-06-05 paper/appendix-bda.Rmd
minor tweaks in model section; clean up appendices; update bib

@@
 The model has a single free parameter: the optimality parameter $\lambda$ in Eq. \ref{eq:S1}.
-We analyze this model using a Bayesian data analytic approach, where we jointly infer this single model parameter $\lambda$ together with parameters that govern the prevalence priors $P(p)$ and referent prevalence $p$ for each item.
+We analyze this model using a Bayesian data analytic approach, where we jointly infer this single model parameter $\lambda$ together with parameters that govern the prevalence priors $P(p)$ (Eq.
+\ref{eq:L0}) and referent prevalence $p$ (Eq.
+\ref{eq:S1}) for each item.
 To pin down the prevalence prior and referent prevalence parameters, we use additional data directly related to those parameters (e.g., prior elicitation data).
@@
 
-In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence prior by asking about the prevalence of features for individual categories.
-We performed an analagous elicitation in Case Study 3: Causal Language (Expt. 3a).
+In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence prior by asking participants about the prevalence of features for individual categories.
+We performed an analogous elicitation in Case Study 3: Causal Language (Expt. 3a).
 We describe the analysis using generics as our running example, but a parallel analysis was done for causals.
@@
 Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
-Adjusting 1 to $1- \epsilon$ leads to improper inferences for this simple 2-component model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$, forcing it to favor probabilities close to 1.
+Adjusting 1 to $1- \epsilon$ leads to improper inferences for this simple 2-component model, as $1 - \epsilon$ is only likely under a highly left-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$, forcing it to favor probabilities close to 1.
 This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
@@
 ]
+Representative posterior predictive results are shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)B (main text).
 
@@
 2a), we asked participants about parameters of this mixture model (by having participants answer questions about different kinds of people) rather than having participants give samples (e.g., by listing their friends and family members, and rating how often they did certain actions).
-In pilot testing, we found these different methodologies to give comparable results and we opted to ask about hypothetical people to probing about potentially undesirable habits of participants' friends and familiy (e.g., how often they use cocaine).
+In pilot testing, we found these different methodologies to give comparable results and we opted to ask about hypothetical people to probe about potentially undesirable habits of participants' friends and familiy (e.g., how often they use cocaine).
 The questions used in this structured elicitation task are  described in the main text.
@@
 2c ("What is prevalence?"), we compared two endorsement models that differed in their representation of referent-prevalence.
-For one model (past frequency model), the actual frequency given to participants in the experimental prompt was assumed to the referent prevalence (same as in Expt.
+For one model (past frequency model), the actual frequency given to participants in the experimental prompt was assumed to be the referent prevalence (same as in Expt.
 2b); for the other model (predictive frequency model), we used the mean elicited frequency from the *predictive frequency* condition (participants predictions about how often the person would do the action in the next time interval; see main text for details).
@@
 To fit the generic endorsement models, we incorporate them into the Bayesian data analytic model of the prevalence prior data (described above) to create a single, joint-inference model where the optimality parameter $\lambda$ (Eq.
-\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $p$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P_(p)$ for each property $f$) using data from Expt.
+\ref{eq:S1}) is inferred jointly with all the other latent parameters of the full model (the referent-prevalence $p$ for each category $k$ and property $f$ and the parameters of the prevalence priors $P(p)$ for each property $f$) using data from Expt.
 1a \& b (Figure \ref{fig:genericsModelDiagram}).
@@
 We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 150,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
-This algorithm is useful for models with many variables that only affect a subset of the model's predictions (e.g., in models with by-item or by-participant parameters, where those additional parameters only influence predictions for those items or participants).
+This algorithm is useful for models with many variables that only affect a subset of the full model's predictions (e.g., models with by-item or by-participant parameters, wherein those additional parameters only influence predictions for those items or participants).
 
@@
 The referent-prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
-The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P(p_{f})$, the referent-prevalence $p_{fk}$, and a single speaker optimality parameter $\\lambda$ as input.
+The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P(p)$, the referent-prevalence $p$, and a single speaker optimality parameter $\\lambda$ as input.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
@@
 ]
-If the joint inference model (which models all data sources---referent prevalence, prevalence prior, and generic endorsement---simultaneously) infers something substantially different about referent-prevalence than a model of referent prevalence in isolation, that could into question the inferences we as scientists derive from the joint inference model.
-For example, incorporating a linear regression model (of the kinds presented as alterantive models in the main text) into this Bayesian joint-inference analysis model produces posterior predictions that match the generic endorsement data surprisingly well (e.g., that model predicts "Robins lay eggs" is true).
-Such a model is only able to do this by distorting the referent-prevalence data, inferring that 100\% of robins lay eggs; thus, the linear model in this joint-inference analysis framework sacrifices its goodness-of-fit to the referent-prevalence data in order to increase its goodness-of-fit to the endorsement data.
+If the joint inference model (which models all data sources---referent prevalence, prevalence prior, and generic endorsement---simultaneously) infers referent-prevalence values substantially different from those inferred by a model of referent prevalence in isolation, that would suggest that the joint-model is distorting the prevalence parameters to accomodate the endorsement data.
+Such a result would call into question the inferences we as scientists derive from the joint inference model.
+For example, incorporating a linear regression model (of the kind presented as alterantive models in the main text) into this Bayesian joint-inference analysis model produces posterior predictions that match the generic endorsement data surprisingly well (e.g., that model predicts "Robins lay eggs" is true).
+Such a model is only able to do this, however, by distorting the referent-prevalence data, inferring that 100\% of robins lay eggs; thus, the linear model in this joint-inference analysis framework sacrifices its goodness-of-fit to the referent-prevalence data in order to increase its goodness-of-fit to the endorsement data.
 ^[
-  This distortion effect is why we accout for measurement uncertainty in the linear models by bootstrapping the data that forms their predictors.
+  This distortion effect is why we accout for measurement uncertainty in the linear models by bootstrapping the data that forms their predictors, rather than performing a Bayesian analysis.
 ]
@@
 The inferred parameters for these two models are shown in Figure\ \@ref(fig:distortion).
-We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only the referent-prevalence and prevalence prior data, respectively.
+We found that the referent-prevalences and prevalence priors inferred under the joint model were almost indistinguishable from those inferred using only the referent-prevalence and prevalence prior data, respectively (numerical results reported in main text).
 This results confirms that modeling all three data sources simultaneously does not distort some data sources (e.g., referent prevalence) in order to provide good fits for others (e.g., generic endorsement).

### 2018-06-05 paper/appendix-cueValidity.Rmd
minor tweaks in model section; clean up appendices; update bib

--- 2018-05-08 paper/appendix-cueValidity.Rmd
@@
 
-In Experiment 1, we articulated an alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a regression model.
+In Experiment 1, we articulated an alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a linear combination of these parameters.
 In a small review of the literature, we discovered different methods for measuring cue validity; in piloting, these different methods lead to different results. 
@@
 We describe two experiments that represent the primary methods for measuring cue validity and compare them with these desiderata in mind.
-Finally, we compare the cue validity measured using these different methods to cue validity derived from our prevalence prior elicitation task (Expt. 1a, main text).
+Finally, we compare the cue validity measured using these different methods to cue validity derived from our prevalence prior elicitation task (Expt. 1b, main text).
 
@@
 
-Measuring cue validity involves collecting participants' judgments that relate to the probability that an exemplar is a member of a kind given that is has a feature : $P(x \in k \mid x \in f)$.
+Measuring cue validity involves collecting participants' judgments that relate to the probability that an exemplar is a member of a kind given that it has a feature : $P(x \in k \mid x \in f)$.
 There are several ways one could measure cue validity. 
-Here we consider two measures: One that has participants estimate the probability $P(x \in k \mid x \in f)$ directly, a common technique in the literature on generic language [e.g., @Khemlani2012; @Prasada2013], and another that has participants freely produce categories given a feature [i.e., draw a sample from the conditional distribution on kinds given a feature; @Cree2006].
-We will the former the *direct question* method and the latter the *free production* method.
+Here we consider two measures: One has participants estimate the probability $P(x \in k \mid x \in f)$ directly, a common technique in the literature on generic language [e.g., @Khemlani2012; @Prasada2013], and another has participants freely produce categories given a feature [i.e., draw a sample from the conditional distribution on kinds given a feature; @Cree2006].
+We will refer to the former the *direct question* method and the latter the *free production* method.
 
@@
 There are infinite examples.
-The ones will use are \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger).
+The ones we will use are \emph{has wings} (leopard), \emph{has a mane} (shark), \emph{has spots} (kangaroo), \emph{has a pouch} (tiger).
 }
@@
 Materials were the same for both experiments.
-They were a collection of familiar properties and animal categories used in Expt. 1b (endorsement of generic statements) described in the main text.
+These were a collection of familiar properties and animal categories used in Expt. 1a (endorsement of generic statements) described in the main text.
 There were twenty-one properties in total.
@@
 
-Participants completed the thirty target trials (corresponding to the thirty generic statements used in Expt. 1b) in addition to ten filler trials (total number of trials = 40).
-The filler trials were made up of random category -- property pairings.
+Participants completed the thirty target trials (corresponding to the thirty generic statements used in Expt. 1a) in addition to ten filler trials (total number of trials = 40).
+The filler trials were made up of random category--property pairings.
 Trials were presented in a randomized order.
@@
 
-Participants responded by filling in a text box with their response.
-There were twenty-one trials in total, one for each property.
+Participants responded by filling in a text box with their response for twenty-one trials in total, one for each property.
 No filler trials were used.
@@
 We are interested in the results of each measure (direct question and free production) for the three conditions corresponding to the desiderata outlined above. 
-To evaluate each measure, we selected four example property--category pairs that we believe are unambiguously instances of the boundary conditions described above (these items are described above with the desiderata).
+To evaluate each measure, we selected four example property--category pairs that we believe are unambiguous instances of the boundary conditions described above (these items are described above with the desiderata).
 
-Figure \ref{fig:cv-bothquestions-barplots} (top) shows the results for the twelve items of interest for both measurements.
-We see that for the "false" features, both measures behave as desired (hypothsized results shown by the dotted line): The cue validity of a feature that is false is zero or near-zero.
-For "diagnostic" features, both measures also behave reasonably: Learning that an entity has malaria strongly implies that it is a mosquito. 
+Figure\ \@ref(fig:cvBothquestionsBarplots)A shows the results for the twelve items of interest for both measurements.
+We see that for the *false features*, both measures behave as desired (hypothesized results shown by the dotted line): The cue validity of a feature that is not present in the category is zero or near-zero.
+For *diagnostic features*, both measures also behave reasonably: Learning that an entity has malaria strongly implies that it is a mosquito. 
 However, there is some evidence that the free production measurement is more sensitive than the direct-question measure.
-"Having a mane" is strongly diagnostic for a "lion" but also for a "horse" (and so the overall cue validity for lion is around 0.5).
+"Having a mane" is strongly diagnostic for a "lion" but also for a "horse" (and so the overall cue validity of having a mane for a lion is around 0.5).
 "Carrying Lyme disease" is mostly diagnostic for a "tick" but also "deer" (and thus, the cue validity for tick is not maximal).
-These subtle differences among "diagnostic" features is picked up by the free-production measure but not by the direct-question measure.
+These subtle differences among diagnostic features are picked up by the free-production measure but not by the direct-question measure.
 
-The measures deviate most strongly, however, in their characterization of the undiagnostic features. 
-Learning that an entity is female should not strongly imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
-A similar phenomenon can be observed in direct question measure for the other undiagnostic features.
-Figure \ref{fig:cv-bothquestions-barplots} (bottom left) shows the raw empirical distributions of responses for the direct question measure. 
-We observe suggestive evidence that participants respond to this question for unidagnostic features in one of two ways: (i) reporting near-0 likelihood (accurate response) or (ii) reported near-0.5 likelihood.
-This latter response option may be a pragmatic effect of asking the direct question and/or participants "opting out" of a response. 
-For example, in response to the question "There is a thing that is female. What are the odds that it is a robin?", a reasonable human response may be "I don't know". 
+The free production and direct question measures deviate most strongly in their characterization of the undiagnostic features. 
+Learning that an entity is female should not imply that it is a robin, which is accurately reflected in the free production measure but not in the direct question measure.
+<!-- A similar phenomenon can be observed in direct question measure for the other undiagnostic features. -->
+Figure\ \@ref(fig:cvBothquestionsBarplots)B shows the raw empirical distributions of responses for the direct question measure for undiagnositic features. 
+We observe that participants respond to this question for undiagnostic features in one of two ways: (i) reporting near-0 likelihood (hypothesized response) or (ii) reported near-0.5 likelihood. 
+This latter response option may reflect participants "opting out" of a response (e.g., signalling "I don't know"). 
+For example, in response to the question "There is a thing that is female.
+What are the odds that it is a robin?", a person could say they have no evidence to suggest that it is, besides the very fact that the experimenter asked the question.
 Participants may cope with the awkwardness of the question by placing the slider bar in the middle of the scale.
 
-```{r cv-bothquestions-barplots, fig.height = 8, fig.width = 8, fig.cap="Top: Empirically measured cue validity for two different tasks.
+```{r cvBothquestionsBarplots, fig.width=10, fig.asp=0.7, fig.cap="A: Empirically measured cue validity for two different tasks.
 Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
 Dotted lines denote theoretical cue validity representing the desiderata (see text).
-Error bars denote bootstrapped 95% confidence intervals.
-Bottom left: Raw empirical distributions for direct question task.
-Bottom right: Correspondence between measured cue validity and prevalence prior derived cue validity."}
+B: Raw empirical distributions for direct question task.
+C: Correspondence between measured cue validity and prevalence prior derived cue validity.", out.width="\\textwidth", fig.pos="!h", cache = F}
 load("cached_results/appendix_cueValidity_results.RData")
@@
 
-grid.arrange(cv.bothquestions.bars, 
-             dq.histograms, 
-             prevprior.cv.scatters,
-             ncol = 4,
-             layout_matrix = cbind(c(1,1,2,2),
-                                   c(1,1,2,2),
-                                   c(1,1,3,3),
-                                   c(1,1,3,3)
-                                   ))
+cowplot::plot_grid(
+  cv.bothquestions.bars,
+  plot_grid(dq.histograms,  prevprior.cv.scatters, nrow = 1,
+            rel_widths = c(1,1), labels = c("B", "C")),
+  rel_heights = c(1.5,1),
+  nrow = 2,
+  labels = c("A", "")
+)
+# )
+# grid.arrange(cv.bothquestions.bars, 
+#              dq.histograms, 
+#              prevprior.cv.scatters,
+#              ncol = 4,
+#              layout_matrix = cbind(c(1,1,2,2),
+#                                    c(1,1,2,2),
+#                                    c(1,1,3,3),
+#                                    c(1,1,3,3)
+#                                    ))
 
@@
 
-To further understand these measures of cue validity, we compare them to cue validity derived from our prevalence prior elicitation task (Expt. 1a).
+To further understand these measures of cue validity, we compare them to cue validity derived from our prevalence prior elicitation task (Expt. 1b).
 Expt.
-1a is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated (the other half was freely generated by participants); including these supplied categories was important to measure referent-prevalence of interest (e.g., the percentage of mosquitos that carry malaria).
+1b is not perfectly designed for this comparison, as we supplied participants with half of the animal categories that they rated (the other half was freely generated by participants); including these supplied categories was important to measure the referent-prevalence of interest (e.g., the percentage of mosquitos that carry malaria).
 Including them in this analysis, however, potentially distorts the prior probability of categories $P(k)$.
 
-In this analysis, we treat each category entry from Expt. 1a (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
-This will result in the prevalence prior favoring kinds that are easy to produce (like dogs and cats, which is plausibly a good approximation for $P(k)$) as well as favoring the experimentally supplied kinds (like mosquitos and robins).
+In this analysis, we treat each category entry from Expt. 1b (participant free production or experimentally supplied category like mosquitos) as contributing to the prevalence prior.
+This results in the prevalence prior favoring kinds that are easy to produce (like dogs and cats; plausibly a good approximation for $P(k)$) as well as favoring the experimentally supplied kinds (like mosquitos and robins).
 
 We compute cue validity from the prevalence prior using Bayes' rule. 
-Figure \ref{fig:cv-bothquestions-barplots} (bottom right) shows the two measurements of cue validity as they relate to the prevalence prior derived cue validity. 
-The prevalence prior derived cue validity is highly associated with both measurements: $r_{direct}^2(`r n.dq`) = `r r2.dq`$; $MSE_{direct} = `r mse.dq`$ and $r_{free}^2(`r n.fp`) = `r r2.fp`$; $MSE_{free} = `r mse.fp`$.
+Figure\ \@ref(fig:cvBothquestionsBarplots)C shows the two measurements of cue validity as they relate to the prevalence prior derived cue validity. 
+Across the thirty property--category pairs, the prevalence prior derived cue validity is highly associated with both measurements: $r_{direct}^2(`r n.dq`) = `r r2.dq`$; $MSE_{direct} = `r mse.dq`$ and $r_{free}^2(`r n.fp`) = `r r2.fp`$; $MSE_{free} = `r mse.fp`$.
 Of primary interest is how the measurements behave for desiderata items. 
@@
 
-The points of largest deviation for the free-production measurement from the prevalence prior derived measurement occur where the prevalence prior derived measure rates the cue validity as relatively high when the free-production measure gives the item low cue validity (two black points in Fig.
-\ref{fig:cv-bothquestions-barplots} (right scatterplot) high X-value, low Y-value).
+The points of largest deviation for the free-production measurement from the prevalence prior derived measurement occur where the prevalence prior derived measure rates the cue validity as relatively high when the free-production measure gives the item low cue validity (two black points in Figure\ \@ref(fig:cvBothquestionsBarplots)C, high X-value, low Y-value).
 These two items are: ("is red", "cardinal") and ("is white", "swan").
-These items should have low relatively cue validity and are overestimated by the prevalence prior because of the prior on categoryies $P(k)$ (i.e., because they were supplied to every participant and thus get a higher weighted in the prior for deriving cue validity).
-In comparison, the direct question measurement consistently overestimates cue validity relative to the prevalence prior.
+These items should have relatively low cue validity and are overestimated by the prevalence prior because of the prior on categoryies $P(k)$ (i.e., because they were supplied to every participant and thus get a higher weighted in the prior for deriving cue validity).
+In comparison, the direct question measurement consistently overestimates cue validity relative to the cue validity derived from the prevalence prior for almost all of the items.
 
@@
 
-*Cue validity* is a commonly used measurement for understanding generic truth conditions. 
-Because we observe different measurements being used in the literature, we articulated three *a priori* desiderata to validate a measure of cue validity.
-We found that the "free production" measurement (i.e., having participants generate categories given a feature), and not the direct question measurement (i.e., asking participants a likelihood judgment of the category given the feature), satisfied all three boundary conditions.
-In addition, cue validity derived from our prevalence prior measurement (Expt. 1a) also satisfied these boundary conditions. 
-We conclude that researchers interested in generic truth conditions should use a free production paradigm for measuring cue validity.
+*Cue validity* is a commonly used measurement for understanding generic truth judgments [e.g., @Khemlani2012; @Prasada2013].
+We observed different measurements used in the literature and articulated three *a priori* desiderata to validate a measure of cue validity.
+We found that the "free production" measurement (i.e., participants freely produced categories given a feature), and not the direct question measurement (i.e., participants provide a likelihood judgment of a particular category given the feature), satisfied all three boundary conditions.
+In addition, cue validity derived from our prevalence prior measurement (Expt. 1b) also satisfied these boundary conditions. 
+We conclude that researchers interested in comparing cue validity to generic truth judgments should use a free production paradigm for measuring cue validity.

### 2018-06-05 paper/appendix-cvDerivation.Rmd
minor tweaks in model section; clean up appendices; update bib

@@
 Cue validity is defined for a particular category--property pair (e.g., *mosquitos* and *carry malaria*), and relates to referent-prevalence (e.g., how many mosquitos carry malaria) via the prevalence of *carrying malaria* in other categories $k'$ by Bayes' Rule:
-$$ p(k \mid f) = \frac{p(f \mid k) \cdot p(k)}{Z} $$
-where $Z =  \sum_{k' \in K} p( f \mid k') \cdot p( k')$
+$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{Z} $$
+where $Z =  \sum_{k' \in K} P( f \mid k') \cdot P( k')$
 
-The prevalence prior $P(p_f)$ (Eq. \ref{eq:L0}) is a probability distribution over prevalence for different categories $k'$.
-For ease of exposition, let $x = p_f = p(f \mid k)$; that is, $P(x) = P(p_f)$.
+The prevalence prior $P(p)$ (Eq. \ref{eq:L0}) is a probability distribution over prevalence for different categories $k'$.
+<!-- For ease of exposition, let $x = p = P(f \mid k)$; that is, $P(x) = P(p)$. -->
 
-\underline{Claim:} The normalizing constant for computing cue validity is equal to the expected value of the prevalence prior distribution: $\mathbb{E}[P(x)] = Z$
+\underline{Claim:} The normalizing constant for computing cue validity is equal to the expected value of the prevalence prior distribution: $\mathbb{E}[P(p)] = Z$
 
@@
 \begin{eqnarray} \label{eq:expectation}
-\mathbb{E}[P(x)] & = & \sum\limits_{x} x \cdot p(x) 
+\mathbb{E}[P(p)] & = & \sum\limits_{p} p \cdot P(p) 
 \end{eqnarray}
 
-The probability of a prevalence $x$ can be decomposed into the prior probability of a category $k$ and the likelihood of the prevalence $x$ given that category $k$: $p(x) = p(x \mid k) \cdot p(k)$. 
-We assume here, without loss of generality, that each category corresponds to one and only one prevalence $x$.
-Thus, $p(x \mid k) = 1$ if $k \in K_x$, a set of categories that have a given prevalence: $K_x = \{k' : p_{fk'} = x\}$. 
-Further,  e partition of the set of all categories $K$ into non-overlapping $K_x$s.
+The probability of a prevalence $p$ can be decomposed into the prior probability of a category $k$ and the likelihood of the prevalence $p$ given that category $k$: $P(p) = P(p \mid k) \cdot P(k)$. 
+We assume here, without loss of generality, that each category corresponds to one and only one prevalence $p$.
+Thus, $P(p \mid k) = 1$ if $k \in K_p$, a set of categories that have a given prevalence: $K_p = \{k' : p_{k'} = p\}$. 
+Then, consider the partition of the set of all categories $K$ into non-overlapping $K_p$.
 Thus:
@@
 \begin{eqnarray} \label{eq:prevToKinds}
-p(x) & = & \sum\limits_{k' \in K_x} p(x \mid k') \cdot p( k') \nonumber \\
-     & = & \sum\limits_{k' \in K_x} p(k')
+P(p) & = & \sum\limits_{k' \in K_p} P(p \mid k') \cdot P( k') \nonumber \\
+     & = & \sum\limits_{k' \in K_p} P(k')
 \end{eqnarray}
 
-since $\forall k' \in K_{x}:  p(x \mid k') = 1$.
+since $\forall k' \in K_{p}:  P(p \mid k') = 1$.
 Returning to Eq. \ref{eq:expectation}, we have:
@@
 \begin{eqnarray} \label{eq:eq3}
-\mathbb{E}[P(x)] & = & \sum\limits_{x} x \sum\limits_{k' \in K_x} p(k') \nonumber \\
-                  & = & \sum\limits_{x} \sum\limits_{k' \in K_x} x \cdot p(k')
+\mathbb{E}[P(p)] & = & \sum\limits_{p} p \sum\limits_{k' \in K_p} P(k') \nonumber \\
+                  & = & \sum\limits_{p} \sum\limits_{k' \in K_p} p \cdot P(k')
 \end{eqnarray}
 
-The set of all partitioned subsets $K_x$ is in a one-to-one correspondence with the set of all prevalences $x$. Thus, we have:
+The set of all partitioned subsets $K_p$ is in a one-to-one correspondence with the set of all prevalences $p$. Thus, we have:
 
 \begin{eqnarray} \label{eq:bijection}
-  & = & \sum\limits_{K_x} \sum\limits_{k' \in K_x} x \cdot p( k')
+  & = & \sum\limits_{K_p} \sum\limits_{k' \in K_p} p \cdot P( k')
 \end{eqnarray}
 
-Then, since $\cup_{x}{K_x} = K$, we have
+Then, since $\cup_{p}{K_p} = K$, we have
 
 \begin{eqnarray} \label{eq:partition}
-  & = & \sum\limits_{k' \in K} x \cdot p( k') \nonumber \\ 
-  & = & \sum\limits_{k' \in K} p(f \mid k') \cdot p( k') \nonumber \\ 
+  & = & \sum\limits_{k' \in K} p \cdot P( k') \nonumber \\ 
+  & = & \sum\limits_{k' \in K} P(f \mid k') \cdot P( k') \nonumber \\ 
   & = & Z

### 2018-06-05 paper/comgen-paper.Rmd
minor tweaks in model section; clean up appendices; update bib

@@
 
-The obvious next question for such a representation concerns $\theta$: What threshold is appropriate?
-It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) := p > 0$; $\denote{most} := p > 0.5$.
-In a probabilistic representation, states of uncertainty are more fundamental than states of certainty (e.g., it is a special case when an agent with probabilistic beliefs is certain about something; the more typical case is that they are uncertain).
-Thus, if quantifiers have *certain* thresholds ("some": greater than 0; "most" greater than 0.5), then perhaps generics have *uncertain* thresholds.
+The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
+Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
 We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
@@
 
-In our account, the truth conditions of generics concern the currency of belief, probability, and the relevant probabilities may be informed by rich conceptual structure.
+In our account, the truth conditions of generics are a function of beliefs formalized with probability, and the relevant probabilities may be informed by rich conceptual structure.
 The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.

### 2018-09-16 paper/response.tex
first draft of response letter

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
%\usepackage[urw-garamond]{mathdesign}
\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
%\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage{url}
% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter
\def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

%----------------------------------------------------------------------------------------
%	DOCUMENT MARGINS
%----------------------------------------------------------------------------------------

\textwidth 7in
\textheight 9.5in
\oddsidemargin -.25in
\evensidemargin -.25in
\topmargin -1in
\longindentation 0.50\textwidth
\parindent 0.4in

%----------------------------------------------------------------------------------------
%	SENDER INFORMATION
%----------------------------------------------------------------------------------------

\def\Who{} % Your name
\def\What{} % Your title
\def\Autha{Michael Henry Tessler} % Your name
\def\Authb{Noah D. Goodman} % Your name
\def\Where{Department of Psychology} % Your department/institution
\def\Address{450 Serra Mall, Bldg 420} % Your address
\def\CityZip{Stanford, CA 94305} % Your city, zip code, country, etc
\def\Email{E-mail: mtessler@stanford.edu} % Your email address
\def\TEL{Phone: (757) 561-7971} % Your phone number

%----------------------------------------------------------------------------------------
%	HEADER AND FROM ADDRESS STRUCTURE
%----------------------------------------------------------------------------------------

\address{
\includegraphics[width=0.8in]{logo-simple.pdf} % Include the logo of your institution
\hspace{5.1in} % Position of the institution logo, increase to move left, decrease to move right
\vskip -0.85in~\\ % Position of the text in relation to the institution logo, increase to move down, decrease to move up
\Large\hspace{1.5in}STANFORD UNIVERSITY \hfill %~\\[0.05in] % First line of institution name, adjust hspace if your logo is wide
%\hspace{1.5in}University 
\hfill 
\normalsize % Second line of institution name, adjust hspace if your logo is wide
\makebox[0ex][r]{\bf \Who \What }\hspace{0.08in} % Print your name and title with a little whitespace to the right
~\\[-0.11in] % Reduce the whitespace above the horizontal rule
\hspace{1.5in}\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
\hspace{\fill}\parbox[t]{2.85in}{ % Create a box for your details underneath the horizontal rule on the right
%\flushright 
\footnotesize % Use a smaller font size for the details
\flushright
%\Who \\  % Your name, all text after this will be italicized
\Autha\\
\Authb\\
\Where\\ % Your department
\Address\\ % Your address
\CityZip\\ % Your city and zip code
%\TEL\\ % Your phone number
%\Email\\ % Your email address
%\URL % Your URL
}
\hspace{0in} % Horizontal position of this block, increase to move left, decrease to move right
\vspace{-1in} % Move the letter content up for a more compact look
}

%----------------------------------------------------------------------------------------
%	TO ADDRESS STRUCTURE
%----------------------------------------------------------------------------------------

\def\opening#1{\thispagestyle{empty}
{\centering\fromaddress \vspace{0.6in} \\ % Print the header and from address here, add whitespace to move date down
\hspace*{\longindentation}\hspace*{\fill}\par} % Print today's date, remove \today to not display it
%{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{0.4in} % White space after the to address
\noindent #1 % Print the opening line
% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}
}

%----------------------------------------------------------------------------------------
%	SIGNATURE STRUCTURE
%----------------------------------------------------------------------------------------

\signature{\Autha \\ \Authb \What} % The signature is a combination of your name and title

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
\hspace*{\longindentation} % Move the signature right
\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.1in % Whitespace between the signature text and your name
\fromsig}} % Print your name and title

%----------------------------------------------------------------------------------------

\begin{document}

\begin{letter}

\opening{Dear Professor Saxe,}

Thank you for soliciting peer reviews for our manuscript \emph{The Language of Generalization}. We appreciate the time both you and the reviewers have devoted to commenting and critiquing our manuscript. We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
We have made a number of substantive changes in this version of the manuscript that we think will improve the readability of the paper.

We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments.
We hope this addresses R3's uncertainty about the relationship of our theories to extant theories. 
Our theory is, in R3's option-space, (e) an outright alternative to prior theories. 
Not explicitly the goal of this paper, however,  we also posit that our theory is (d), a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity. 
Finally, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison (in the hope of addressing R3's 2nd comment). 
The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our  model is not overparameterized and that the prior in our model is not doing all of the work. 
This also allows us to clarify the sense in which our model is unique (R3's 3rd comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).

We have taken inspiration of Reviewer 1's comments concerning the presentation of the various puzzles in a more accessible form. 
We have moved the General Discussion subsection ``Other philosophical puzzles'' to appear before the experiments and merged with the exposition about the model where we provide worked examples (e.g., \emph{birds lay eggs vs. are female}, \emph{mosquitos carry malaria}).
By moving these other philosophical puzzles to appear before the experiments, we are able to foreshadow the relevance of \emph{predictive probability} as central to our account (and motivate Expts. 2c \& d).
We have also added a table per R1's suggestion summarizing these linguistic examples we believe a theory of generics should be able to handle, including a high-level verbal description of how our model treats these examples.

We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
We have added a discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
We have taken a few paragraphs to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions. 
We note that this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity). 
We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson's (1994) empiricist view.

In addition to these broad theoretical points, we have clarified a number of smaller points brought up by Reviewer 1.
We have clarified our contrasts of generics from quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations of quantifiers. 
We are now explicit about our argument from analogy about how states of uncertainty are more fundamental than states of certainty motivates an uncertain threshold (for generics) as being more fundamental a certain, exact threshold (for quantifiers).

things i'm not sure about:
\begin{enumerate}
\item property theories of meaning (R1)
\item acquisition story and evidence of how difficulty with quantifiers comes from pragmatic considerations (Musolino \& Lidz, 2006)
\end{enumerate}

Finally we have gone through the manuscript and tried to make small changes to improve clarity and citations.

\closing{Sincerely yours,}

\end{letter}

\end{document}

### 2018-09-19 paper/response.tex
edits in response

@@
 
+\usepackage{color}
+\newcommand{\ndg}[1]{{\color{green}{[ndg: #1]}}}
+
 \begin{document}
@@
 We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments.
-We hope this addresses R3's uncertainty about the relationship of our theories to extant theories. 
-Our theory is, in R3's option-space, (e) an outright alternative to prior theories. 
-Not explicitly the goal of this paper, however,  we also posit that our theory is (d), a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
+We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theories to extant theories. 
+Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
+This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with ours.
+This is hopefully now more clearly articulated.
 Finally, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison (in the hope of addressing R3's 2nd comment).
@@
 
-We have taken inspiration of Reviewer 1's comments concerning the presentation of the various puzzles in a more accessible form. 
-We have moved the General Discussion subsection ``Other philosophical puzzles'' to appear before the experiments and merged with the exposition about the model where we provide worked examples (e.g., \emph{birds lay eggs vs.
+Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
+we have moved the General Discussion subsection ``Other philosophical puzzles'' to appear before the experiments and merged with the worked examples (e.g., \emph{birds lay eggs vs.
 are female}, \emph{mosquitos carry malaria}).
@@
 2c \& d).
-We have also added a table per R1's suggestion summarizing these linguistic examples we believe a theory of generics should be able to handle, including a high-level verbal description of how our model treats these examples.
+We have also added a table per R1's suggestion summarizing the examples we believe a theory of generics should be able to handle; in the corresponding section we have included a high-level verbal description of how our model treats these examples.
 
@@
 We note that this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity).
+We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
 We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson's (1994) empiricist view.
@@
 We are now explicit about our argument from analogy about how states of uncertainty are more fundamental than states of certainty motivates an uncertain threshold (for generics) as being more fundamental a certain, exact threshold (for quantifiers).
+\ndg{that last sentence confuses me.
+also see comment below about learning stuff.
+maybe tone this all down?}
 
@@
 \begin{enumerate}
-\item property theories of meaning (R1)
-\item acquisition story and evidence of how difficulty with quantifiers comes from pragmatic considerations (Musolino \& Lidz, 2006)
+\item property theories of meaning (R1) \ndg{they are alluding to theories of concepts -- conceptual role, feature-based, etc.
+i think we can add a few comments to the section on relation to conceptual theories of generics about this.
+basically we are not committed to any particular theory of concepts, as long as they are able to yield quantitative feature probabilities.}
+\item acquisition story and evidence of how difficulty with quantifiers comes from pragmatic considerations (Musolino \& Lidz, 2006) \ndg{we could remove this speculation, or town it down.
+we don't really want dig deeply into work on quantifier acquisition here....}
 \end{enumerate}

### 2018-09-20 paper/comgen-paper.Rmd
minor edits to intro and model; begin worked examples sec; move cue validity stuff to discussion subsec

@@
 author_note: >
-  This manuscript is currently in prep. Comments or suggestions should be directed to MHT.
+  This paper is currently under review. Comments or suggestions are appreciated and should be directed to MHT.
 
@@
 keywords          : "genericity, generalization, generics, pragmatics, semantics, Bayesian modeling"
-wordcount         : "20000"
+wordcount         : "25000"
 
@@
 In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
-Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "This fire caused that smoke") can be described in generalization (e.g., "Fire causes smoke").
+Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "The fire caused the smoke") can be described in generalization (e.g., "Fire causes smoke").
 
@@
 "Robins lay eggs" sounds true and "Robins are female" does not. 
-Yet in each case, only 50% of the category have the property (i.e., only the females lay eggs). 
+Yet in each case, only 50% of the category has the property (i.e., only the females lay eggs). 
 "Mosquitos carry malaria" sounds true despite malaria being present in only a tiny fraction of mosquitos. 
 Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a bad sentence even if it were the case that on the current bench, nine out of nine justices have even social securtity numbers [i.e., when the sentence "All Supreme Court Justices have even social security numbers" is true; @Cohen1999].
-Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains 3 times last year, the habitual "Mary climbs mountain" seems well-supported. 
-Yet, if John went for a run 3 times in the last year, we probably should not say that "John runs".
+Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains three times last year, the habitual "Mary climbs mountain" seems well-supported. 
+Yet, if John went for a run three times in the last year, we probably should not say that "John runs".
 
@@
 -->
-Instead, generic statements are thought of semantically as a direct, linguistic manifestation of conceptual relations [@Leslie2008; @Prasada2000; @Prasada2012]. 
+Instead, generic statements are thought of semantically as a direct, linguistic manifestation of abstract relations between kinds and properties [@Leslie2008; @Prasada2000; @Prasada2012]. 
 <!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
@@
 
-Insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
+Insofar as there is a single class of linguistic expressions that convey generalization, however, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
 In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
@@
 Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgments about the truth or acceptibility of a sentence.
+We sketch out a number of worked examples to qualitatively demonstrate the model's behavior and the describe the relation of our model to previous linguistic and philsophical approaches to generics.
 The model as articulated predicts fine-grained, quantitative effects of background knowledge, which we both measure and manipulate across our three empirical case studies (Sections 2-4): generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*).
@@
 In all cases, we find a very strong agreement of our model's predictions to human elicited endorsements, where the simpler models fall short.
-We conclude our paper with a discussion of open-questions for this approach, relation to linguistic and philosophical approaches to generics, and a few sketches of worked examples of other phenomenology in generics.
+We conclude our paper by clarifying some of the theoretical claims of the model and discuss open-questions for this approach.
 
@@
 Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
-People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do.
+People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find the people that we know doing what they habitually do.
 In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
@@
 The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
-The properties also vary (e.g., having fur, causing jitters, going to the gym).
+The properties also may vary (e.g., having fur, causing jitters, going to the gym).
 Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.
@@
 If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
-But not all properties have such strong projectibility.
+But not all properties have such strong projectibility:
 Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
 Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
-By assuming some generative process that could produce one's observations $o$---the likelihood $P(o \mid p)$---Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations $o$: $P(o \mid d) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].
+By assuming some generative process that could produce one's observations $o$ (i.e., a likelihood function $P(o \mid p)$), Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations $o$: $P(o \mid d) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].
 
@@
 The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) := p > 0$.
-"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.
+For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is greater than zero: $\denote{some}(p) := p > 0$.
+"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.
 Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.
@@
 
-We denote this probabilistic generic interpretation model by $L$ to indicate that it is modeling a listener updating their beliefs according to the truth-functional meaning of an utterance.
-Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
+We denote this probabilistic generic interpretation model by $L$ to indicate that it is modeling a listener updating their beliefs according to the truth-functional meaning of an utterance $u$.
+Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
 
@@
 For simplicity, we take the null alternative to be an informationless "silent" utterance which is always true: 
-$\denote{null}(x, \theta) = \text{True}$.^[
+$\denote{null}(p, \theta) = \text{True}$.^[
   The null alternative can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
@@
 The utterance encoding a generalization updates the interpreter model's beliefs about the prevalence of a feature in the category being referred to, which we call the *referent prevalence*. 
-The endorsement model has a particular referent prevalence in mind and decides if the generalization or the null alternative is better at conveying that to the interpreter. ^[
+The endorsement model has a particular referent prevalence in mind and decides if the generalization or the null alternative is better at conveying that to the interpreter.^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
@@
 
-The informational content of the generalization concerns the referent prevalence $p$.
+The informational content of the generalization is the prevalence in the referent category $p$.
 The semantic threshold $\theta$ is a nuisance parameter then; the endorsement model integrates over the interpreter's posterior beliefs about $\theta$.
@@
 In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
+In the next section, we work through different examples from the linguistics literature, describing how the prevalence prior and other relevant model components for each.
 
 <!-- By doing so, we are able to describe how context influences generic understanding and are able to make precise, quantitative predictions about human judgments. -->
-
-### Prevalence priors
-
-The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question.
-This background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
-This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence.
-
-<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
-
-Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
-Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
-Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
-  The Beta distribution is a distribution over numbers between 0 and 1. 
-  In other words, it is a probability distribution over probabilities, which is exactly how we are modeling prevalence. 
-]
-The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
-Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
-In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
-Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
-$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
-Knowledge about other categories $k'$ enters in the denominator.
-Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
-Thus cue validity comes from a point estimate of the prevalence prior distribution.
-For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
-For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we will construct alternative models based on empirically-elicited cue validity.
 
@@
 <!-- For example,   -->
-
-### Model simulations
-
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
-\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq.
-\ref{eq:L0}).
-We simulate how these two factors change both literal interpretation and endorsement using schematic parameter values based on intuition from classic examples in the literature on generic language.
-We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
 
@@
 
-The literal interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
+### Worked examples
+
+The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
+\ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq.
+\ref{eq:L0}).
+Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
+This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence. 
+We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
+We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
+All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+
 Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior $P(p)$. 
+The literal interpretation model (Eq. \ref{eq:L0}) computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
 If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
@@
 
-<!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
-<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
--->
-<!-- Higher thresholds  (e.g., $\theta = 0.75$) rule out many possibilities; an interpretation with this threshold has correspondingly less uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, right).
--->
-<!-- The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be, from an information-theoretic perspective, similar to staying silent (a posterior not very different from the prior).
--->
-<!-- Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
--->
-<!-- The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds. -->
-
+<!-- The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question. -->
+
+<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
 The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
+Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
+Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
+Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
+  The Beta distribution is a distribution over numbers between 0 and 1. 
+  In other words, it is a probability distribution over probabilities or prevalences.
+]
+The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
+Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
+
 Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
@@
 We do this by both measuring and manipulating background knowledge and referent-prevalence and predicting human endorsements of generalizations.
+
+<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
+<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
+\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
+\ref{eq:S1}).
+-->
+<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
+-->
+<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+-->
+
+<!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
+<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
+-->
+<!-- Higher thresholds  (e.g., $\theta = 0.75$) rule out many possibilities; an interpretation with this threshold has correspondingly less uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, right).
+-->
+<!-- The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be, from an information-theoretic perspective, similar to staying silent (a posterior not very different from the prior).
+-->
+<!-- Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
+-->
+<!-- The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds. -->
 
@@
 <!-- ### Conceptual Accounts of Generics -->
+
+## Prevalence priors and cue validity
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
+The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
+In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
+Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
+Knowledge about other categories $k'$ enters in the denominator.
+Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
+Thus cue validity comes from a point estimate of the prevalence prior distribution.
+For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
+For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we will construct alternative models based on empirically-elicited cue validity.
 

### 2018-09-22 paper/comgen-paper.Rmd
move philosophical puzzles to model section, begin working through examples, draft a table

@@
 
-### Worked examples
-
-The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
+### Model behavior
+
+The endorsement model defined in the previous section predicts that the variability in endorsements for generic statements and other sorts of generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
 \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq.
 \ref{eq:L0}).
+We explore the predictions of this model by varying each of these factors in the context of a few worked examples.
+These examples are taken from the linguistics literature on generics and are statements that any theory of generics should be able to correctly predict are either true, false, or somehow indeterminate.
+We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
+All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+
+<!-- Later we will test these predictions in a quantitative way using empirical data. -->
+<!-- We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
+-->
+First, we examine the model behavior assuming a uniform prevalence prior $P(p)$, representing a purely abstract property for which an interpreter has no substantive prior knowledge (Figure\ \@ref(fig:uniformPriorSimulation))
+The literal interpretation model (Eq. \ref{eq:L0}) computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
+If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
+As the threshold decreases, more and more prevalence levels become be compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
+Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior interpretation distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
+The endorsement model then inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
+
+<!-- The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question. -->
+<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
+
+The uncertain-threshold model's interpretations are highly sensitive to background knowledge.
 Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
 This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence. 
-We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
-We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
-
-Figure\ \@ref(fig:uniformPriorSimulation) shows different components of the model behavior assuming a uniform prevalence prior $P(p)$. 
-The literal interpretation model (Eq. \ref{eq:L0}) computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
-If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
-As the threshold decreases, more and more prevalence levels would be true  (Figure\ \@ref(fig:uniformPriorSimulation)A).
-Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
-The endorsement model inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
-
-<!-- The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question. -->
-
-<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
-The uncertain-threshold model's interpretations are highly sensitive to the shape of the prevalence priors (Figure\ \@ref(fig:simulations)).
-Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
+Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories (Figure\ \@ref(fig:simulations)).
 Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
@@
 
-Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity (column 1).
+```{r workedExamples, results="asis"}
+worked.examples <- data.frame(
+  example = c("1. Dogs bark",
+              "2. Kangaroos have spots",
+              "3. Sharks don't eat people",
+              "4. Robins lay eggs",
+              "5. Robins are female",
+              "6. Mosquitos carry malaria", 
+              "7. Mary handles the mail from Antarcita",
+              "8. Supreme Court Justices have even social security numbers",
+              "9. Elephants live in Africa and Asia"),
+  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "~50%/50%"),
+  `intuitive truth value` = c(
+    "T", "F", "F", "T", "U",
+    "T", "T", "F", "T" 
+  ),
+  `potential issue` = c(
+    "Not all dogs bark",
+    "Some kangaroos could have spots",
+    "Most sharks don't eat people",
+    "Only female (50%) of robins lay eggs",
+    "Roughly same number of robins that lay eggs are female",
+    "Very few mosquitos actually carry malaria",
+    "Hypothetically, there has never been any mail from Antarcita",
+    "Even if 100% have even social security numbers",
+    "Impossible for most to live in Africa and most to live in Asia"
+  )
+)
+
+examples <- xtable::xtable(worked.examples, 
+                       caption = "Example generalizations that a theory of generics should correctly predict.", 
+                       align=c('p{1.5in}', 'p{1.2in}| ',' |p{1in}|','p{1in}|','p{2in} |'))
+
+addtorow          <- list()
+addtorow$pos      <- list()
+addtorow$pos[[1]] <- c(0)
+addtorow$command  <- c(paste("\\hline \n",
+                             "\\endhead \n",
+                             "\\hline \n",
+                             "{\\footnotesize \\em{continued on next page}} \n",
+                             "\\endfoot \n",
+                             "\\endlastfoot \n",sep=""))
+
+large <- function(x){ paste0('{\\Large ', x, '}') }
+bold <- function(x){ paste0('{\\bfseries ', x, '}') }
+
+print(examples, 
+      type="latex", 
+      comment = F,
+       #table.placement = "h", 
+      tabular.environment = "longtable",
+      hline.after=-1:nrow(examples),
+      size="\\fontsize{9pt}{10pt}\\selectfont", 
+      include.rownames=FALSE,
+      sanitize.colnames.function = bold
+      #add.to.row = addtorow
+      )
+```
+
+#### Worked examples
+
+We are now ready to examine the endorsement model's predictions for different examples.
+These examples have historically proved challenging for prevalence-based approaches. 
+We describe how the uncertain-threshold model treats each in turn.
+
+**1. Dogs bark.**
+
+Often the first observation with generics is that they appear like *universal* quantifiers (e.g., "All") but permit exceptions. 
+That is, not all dogs bark, but still *Dogs bark* is true.
+The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which the generalization becomes true.
+Rather, listeners have uncertainty about the threshold *a priori* which leads to graded interpretations (e.g., *Dogs bark* meaning *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
+The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (shown with arrow in Figure\ \@ref(fig:simulations) row 2).
+
+**2. Kangaroos have spots.**
+
+A second observation regarding generics is that they cannot be so lenient so to always convey *existential* quantification (e.g., "Some").
+Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel the generalization "Kangaroos have spots" is too strong to assert.
+The model exhibits this same restraint, predicting a very low endorsement probability for this generic statement (Figure\ \@ref(fig:simulations); column 2).
+The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" is like "Dogs bark": it means *almost all* kangaroos have spots. 
+The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would mislead the listener.
+
+**3. Sharks don't eat people.**
+
+A similar logic can be applied to this example, which is the converse of the affirmative generalization "Sharks eat people", initially introduced by @Leslie2007. 
+Here, however, the prevalence of the feature for the referent category---the number of sharks that don't eat people---is very high: Almost all sharks don't eat people.
+Yet, intuitively, the generalization is again misleading. 
+Because for almost all animal categories, almost members of those categories don't eat people (i.e., the prevalence of the feature is almost 100% for all categories because very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people, which is too strong.
+It is interesting to note that the model is less certain of its decision, predicting an endorsement probability around 40%.
+We will test this quantitative prediction in one of our experiments.
+
+**4. and 5. Robins lay eggs vs. Robins are female**
+
+**6. Mosquitos carry malaria.**
+
+Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity.
 "Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
@@
 This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
+
+#### Other philosophical puzzles
+
+In this paper, we aimed to balance two competing goals in our experimental case studies: (1) drawing upon familiar, philosophically interesting examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
+We close by discussing how three previously-discussed, philosophically interesting examples could be addressed in our communicative framework.
+
+**7. Mary handles the mail from Antarctica (*yet has never had the opportunity*).**
+
+Imagine there is a job in the local bureaucrat's office to handle the mail from Antarctica and this job is assigned to Mary; to date, however, there has never been any mail from Antarctica [@Cohen1999].
+That is, the statement "Mary *has handled* mail from Antarctica" is false.
+Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
+In our framework, Sentence (1) is an extreme case of generalizations expressing *predictive* probabilities.
+In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency.
+We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary. 
+Thus the predictive probability that Mary will handle Antarctican mail, if there is any, is high.
+Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
+In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
+
+**8. Supreme Court Justices have even social security numbers.**
+
+Imagine that every current and past Supreme Court Justice has a social security number which is an *even number*. 
+Sentence (2) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
+We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
+That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
+Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+
+However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
+That is, our theory predicts there are situations where statements like (2) could be considered felicitous generalizations.
+
+**9. Elephants live in Africa and Asia.**
+
+Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
+@Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
+Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
+However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
+Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
+In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
+  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
+]
+Interestingly, an incremental parsing of Sentence (3) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia, but few in other places).
+The flexibly of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 
@@
 <!-- ] -->
-
-## Other philosophical puzzles
-
-In this paper, we aimed to balance two competing goals in our experimental case studies: (1) drawing upon familiar, philosophically interesting examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
-We close by discussing how three previously-discussed, philosophically interesting examples could be addressed in our communicative framework.
-
-**1. Mary handles the mail from Antarctica (*yet has never had the opportunity*).**
-
-Imagine there is a job in the local bureaucrat's office to handle the mail from Antarctica and this job is assigned to Mary; to date, however, there has never been any mail from Antarctica [@Cohen1999].
-That is, the statement "Mary *has handled* mail from Antarctica" is false.
-Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
-In our framework, Sentence (1) is an extreme case of generalizations expressing *predictive* probabilities.
-In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency.
-We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary. 
-Thus the predictive probability that Mary will handle Antarctican mail, if there is any, is high.
-Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
-In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
-
-**2. Supreme Court Justices have even social security numbers.**
-
-Imagine that every current and past Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (2) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
-We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
-That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
-Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
-
-However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
-That is, our theory predicts there are situations where statements like (2) could be considered felicitous generalizations.
-
-**3. Elephants live in Africa and Asia.**
-
-Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
-@Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
-However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
-Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
-  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-]
-Interestingly, an incremental parsing of Sentence (3) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
-When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia, but few in other places).
-The flexibly of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 

### 2018-09-23 paper/comgen-paper.Rmd
finish examples section; move alt theories to front and edit; discuss alternative models

@@
 
-<!-- Later we will test these predictions in a quantitative way using empirical data. -->
 <!-- We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
@@
 
+One of the most difficult examples for a theory of generics based on prevalence to handle is the intuitive difference in truth value between the statements "Robins lay eggs" and "Robins are female". 
+The former is intuitively true, even though only female robins could lay eggs (and hence, the prevalence is roughly 50%).
+However, the same implicit restriction to only females does not seem occur for the latter statement, as "Robins are female" strikes most as strange or false.
+Why is "Robins lay eggs" a reasonable utterance while "Robins are female" is not?
+
+The prior distributions over the prevalence of both features are shown in Figure\ \@ref(fig:simulations) (columns 5 and 6).
+As described above, the priors are different: Many animals have zero egg-layers (0% prevalence), while the vast majority of animal categories have female members in exactly the same proportion (50%).
+Interestingly, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes 50% have the property.^[
+  This behavior might suggest a future area for model revision. 
+  Intuitively, "Xs are female" should mean "All Xs are female".
+  In this paper, our empirical interest concerns endorsements or truth judgments; at this point, the interpretation model is only an intermediate representation useful for deriving predictions about endorsement.
+]
+However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would more aligned with the referent prevalence than if the endorsement model produced the null utterance, which would instead return the prior.
+In the case of "Robins lay eggs", the hypothetical generic utterance does not carry any information (the listener posterior is not different from the prior); in this case, however, the generic would not be misleading only uninformative, and hence the model predicts an endorsement probability of 0.5 (i.e., *neither true nor false*).
+
 **6. Mosquitos carry malaria.**
 
-Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity.
-"Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4).
-The interpretation model can also derive very weak interpretation, as shown in the  *carries malaria* distribution (column 6).
-
-The endorsement model (Eq.
+Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are malaria-free.
+The uncertain-threshold model comes to the same conclusion---endorsing a generic when the referent prevalence is very low---because the listener interpretation distribution would be more aligned with the referent prevalence than the prior.
+Intuitively, this is because not that many animals have malaria-carriers among them and so in a sense, having malaria is diagnostic for being a mosquito, an intuition that is often arrived at with this example.
+This example also highlights that the construct of *cue validity*---the probability of the feature given the category e.g., $P({is a mosquito} \mid \text{carries malaria})$---plays a role in our model.
+We return to this relationship in the General Discussion, and provide a precise mathematical derivation of the relationship between the prevalence prior and cue validity in Appendix A.
+
+<!-- Hearing "Ks bark" tells the literal interpreter that *almost all* Ks bark, though there is a good deal of uncertainty in the precise quantity. -->
+<!-- "Ks lay eggs" has a strikingly different interpretation: It means "Half of Ks lay eggs" (column 4). -->
+<!-- The interpretation model can also derive very weak interpretation, as shown in the  *carries malaria* distribution (column 6). -->
+<!-- The endorsement model (Eq.
 \ref{eq:S1}) predicts endorsement probabilities based on the literal interpretation of the utterance and the referent prevalence (e.g., how many robins lay eggs; shown in arrows in Figure\ \@ref(fig:simulations)A).
-Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations).
-In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
-Intriguingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false.
-To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs. bottom row).
-The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content.
-This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing).
-
-#### Other philosophical puzzles
-
-In this paper, we aimed to balance two competing goals in our experimental case studies: (1) drawing upon familiar, philosophically interesting examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
-We close by discussing how three previously-discussed, philosophically interesting examples could be addressed in our communicative framework.
+-->
+<!-- Predictions for a few examples are shown in the bottom row of Figure\ \@ref(fig:simulations). -->
+<!-- In accord with intuition, the endorsement model predicts "Dogs bark", "Robins lay eggs", and "Mosquitos carry malaria" are all true, despite the referent-prevalences varying substantially between these three examples.
+-->
+<!-- Intriguingly, the model predicts "Robins are female" (which has the same prevalence as "Robins lay eggs") should receive intermediate endorsement: It is neither true nor false. -->
+<!-- To understand this prediction, examine the interpretation distribution for the *are female* property: It is identical with the prior (Figure\ \@ref(fig:simulations); column 5; top vs.
+bottom row).
+-->
+<!-- The endorsement model decides that is neither better nor worse to produce the generalization than to stay silent, as they both carry the same information content. -->
+<!-- This example can be contrasted with cases such as "Sharks don't eat people" and "Kangaroos have spots", which the model thinks would be misleading to say (i.e., better to say nothing). -->
+
+<!-- #### Other philosophical puzzles -->
+
+<!-- In this paper, we aim to balance two competing goals in our experiments: (1) drawing upon familiar, philosophically interesting examples that have been discussed in the vast literature on generic language and (2) introducing novel stimuli that provide targeted quantitative tests of our model vis-a-vis alternative models.
+-->
+<!-- We close by discussing how three previously-discussed, philosophically interesting examples could be addressed in our communicative framework. -->
+
+\mht{do we want an example of a habitual or a minimal pair of habituals (e.g., sally hikes vs. climbs mountains)?}
 
@@
 That is, the statement "Mary *has handled* mail from Antarctica" is false.
-Sentence (1) is still thought to be intuitively true despite zero actual instances of the event.
-In our framework, Sentence (1) is an extreme case of generalizations expressing *predictive* probabilities.
-In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency.
-We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary. 
+Sentence (7) is still thought to be intuitively true despite zero actual instances of the event.
+This highlights an important ambiguity in the theoretical commitments of the uncertain threshold model: The endorsement model aims to communicate some referent prevalence $p$, but does the prevalence represent the actual, objective frequency in the world or a subjective, predictive degree of belief in the head?
+
+We posit that Sentence (7) is an extreme case of generalizations expressing *predictive* probabilities.
+We expect this context sets up the expectation that any future mail coming from Antarctica will be handled by Mary. 
+<!-- In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency. -->
+<!-- We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary.  -->
 Thus the predictive probability that Mary will handle Antarctican mail, if there is any, is high.
@@
 Imagine that every current and past Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (2) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
-We predict the rejection of Sentence (2) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
+Sentence (8) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
+We predict the rejection of Sentence (8) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
 That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
-Then, if we constructed the comparison class by considering other professionals, Sentence (2) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+Then, if we constructed the comparison class by considering other professionals, Sentence (8) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+
+\mht{this "surprising prediction" might set the reader up for the expectation that we are going to test this prediction..}
 
@@
 history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
-That is, our theory predicts there are situations where statements like (2) could be considered felicitous generalizations.
+That is, our theory predicts there are situations where statements like (8) could be considered felicitous generalizations.
 
@@
 
+\mht{both this and the "surprisng prediction" above are intutiions/examples we are not going to test empirically (however, here we at least give a model for it)...
+should these appear elsewhere, or somehow be marked upfront?}
+
 Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
-@Nickel2008 suggests Sentence (3) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
+@Nickel2008 suggests Sentence (9) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
 Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
@@
 Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (3) as meaning some elephants live in Africa and that different ones live in Asia.^[
+In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (9) as meaning some elephants live in Africa and that different ones live in Asia.^[
   An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
 ]
-Interestingly, an incremental parsing of Sentence (3) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
+Interestingly, an incremental parsing of Sentence (9) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
 When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia, but few in other places).
-The flexibly of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
-
-These simulations show how the model predicted endorsement depends upon the background knowledge of the interpreter about the property $P(p)$ as well as the referent-prevalence $p$ presented to the endorser.
-We chose schematic values for each of these, and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
-In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measuring and manipulating background knowledge and referent-prevalence and predicting human endorsements of generalizations.
-
-<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
-<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
-\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
-\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
-\ref{eq:S1}).
--->
-<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
--->
-<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
--->
-
-<!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
-<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
--->
-<!-- Higher thresholds  (e.g., $\theta = 0.75$) rule out many possibilities; an interpretation with this threshold has correspondingly less uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, right).
--->
-<!-- The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be, from an information-theoretic perspective, similar to staying silent (a posterior not very different from the prior).
--->
-<!-- Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
--->
-<!-- The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds. -->
-
-<!-- The literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") is given by Eq. \ref{eq:L0} and shown in  -->
-
-<!-- The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}.  -->
-<!-- For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
--->
-<!-- This would correspond to a rather strong interpretation (i.e., "Almost all feps bark"). -->
-<!-- This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green).  -->
-<!-- Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
--->
-<!-- The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple). -->
-<!-- Again, the literal interpretation depends upon the background knowledge in a deep way. -->
-
-<!-- The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right). -->
-<!-- Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
-\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
--->
-<!-- We see the model correctly  -->
-
-<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
-
-<!-- that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics. -->
-<!-- For these simulations, we had specify both the prevalence priors $P(h)$ and the referent prevalence $h'$.. -->
-<!-- In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes. -->
-
-<!-- These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row). -->
-<!-- The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior. -->
-<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[ -->
-<!-- The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities. -->
-<!-- If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold. -->
-<!-- If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower. -->
-<!-- As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it. -->
-<!-- When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model). -->
-<!-- The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*. -->
-<!-- ] -->
-
-<!-- Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements. -->
-<!-- The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$. -->
-<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
--->
-<!-- The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[ -->
-<!-- We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero.  -->
-<!-- The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
--->
-<!-- ] -->
-<!-- The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category. -->
-
-<!-- How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"? -->
-<!-- In each case, we must consider the prevalence prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
-<!-- For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
--->
-<!-- For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs. -->
-<!-- This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3). -->
-<!-- For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
--->
-<!-- The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case.
--->
-<!-- In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
--->
-<!-- "Robins lay eggs", however, has a lot of informational content. -->
-
-<!-- Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria". -->
-<!-- The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread. -->
-<!-- Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
--->
-<!-- Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria". -->
-
-```{r child = 'case1-generics.Rmd'}
-```
-
-```{r child = 'case2-habituals.Rmd'}
-```
-
-```{r child = 'case3-causals.Rmd'}
-```
-
-# General Discussion
-
-The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
-Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
-We have argued that the core meaning of such linguistic expressions can be understood by three ingredients: Probability, vagueness, and context. 
-Though generics are vague that does not preclude them from being treated by formal models. 
-A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.
-
-<!--
-formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.
-
-Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
--->
-
-We tested this theory by exploring its implications for the simplest judgments a person could make: truth judgments.
-We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
-Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
-This framework accounts for a number of philosophically puzzling generic statements (Expt.
-1), naturally extends to other domains of generalizations (habituals and causals; Expts.
-2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt.
-2c).
-We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
-
-Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
-The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
-Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
-
-<!--
-NDG: i cut this from below...
-This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
-Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
-Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
-What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
--->
-
-Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
-Rather than conveying probabilities explicitly, generalizations convey them implicitly.
-In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
-
-<!--
-\mht{unsure about this paragraph... a version of it may be better for the cover letter (if at all)}
-\ndg{yeah, this is unecessarily inflamatory. ax it.}
-Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and leave it to intuition to decide for a particular generic statement, what kind of generic it is.
-In this paper alone, our theory has made hundreds of predictions about the endorsement of individual generic statements, with high accuracy, derived from a general theory that we posit applies to all generic statements.
-In addition, previous accounts are rarely general enough to include generalizations of different semantic types (e.g., *habituals*) and deal only with generics.
-For these reasons alone, our account is novel. 
--->
-
-In the rest of this discussion, we elaborate how our model relates to language understanding more generally, situate our theory with respect to extant theories of generic language, and sketch applications to a few philosophical puzzles in genericity.
-
-<!-- Thus, in addition to expressing a precise hypothesis about the truth conditions of generics, instantiating it in a cognitive model opens up the possibility of building more elaborate models that learn abstract, generalizable knowledge from language.
--->
-
-<!-- We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
--->
-<!-- These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data. -->
-<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
-<!-- A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement.  -->
-<!-- That is precisely what our information-theoretic model does. -->
-<!-- xx -->
-<!-- The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge. -->
-
-<!-- That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
--->
-<!-- Our communicative framework also includes a model of a listener who interprets generalization. -->
-<!-- Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work.  -->
-
-<!-- \mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)} -->
-
-<!-- \ndg{ -->
-<!-- [these paragraphs were out of place here. perhaps incorporate later...] -->
-<!-- } -->
-<!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->
-
-<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
--->
-<!-- We do this without having to posit that conceptual structure and semantics are one in the same. -->
-<!-- This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
--->
-<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->
-
-<!-- @Nickel2016 notes that genericity is particularly challenging to study because it intersects with many other phenomena in natural language (e.g., gradable adjectives in "Giraffes are tall"). -->
-<!-- We agree, and add to this that genericity intersects with *world knowledge* in subtle ways, and it is critical to accurately describe and measure world knowledge before making claims about the semantics of a generalization.
--->
-<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
--->
-<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
-<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
-<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
-
-<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->
-
-<!-- Implicit aspects of language use: The comparison class and question under discussion -->
-
-<!-- to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task. -->
-<!-- The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.  -->
-
-<!-- ## Generic Identification -->
-
-<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
-<!-- The bare plural construction can also indicate a specific plural predication. -->
-<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
-<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
--->
-
-<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences. -->
-<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
--->
-<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
-<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
-<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
-
-<!-- Expts.
-2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
--->
-
-<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
-<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
-This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
--->
-
-<!-- ### The Problems with Communicating Generalizations -->
-
-<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
-<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
-<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
--->
-<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
-
-<!-- Generalizations can be made about almost anything. -->
-<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
--->
-<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
-
-<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
--->
-<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
--->
-
-<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
--->
-<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
-
-<!-- ### Statistical Accounts of Generics -->
-
-<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
-<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
-<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
-<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
-<!-- Let's first introduce some notation: -->
-
-<!-- ### Conceptual Accounts of Generics -->
-
-## Prevalence priors and cue validity
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
-In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
-Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
-$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
-Knowledge about other categories $k'$ enters in the denominator.
-Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
-Thus cue validity comes from a point estimate of the prevalence prior distribution.
-For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
-For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we will construct alternative models based on empirically-elicited cue validity.
-
-## Prevalence priors and conceptual knowledge
-
-Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
-It is this real-world knowledge (presently formalized in terms of a *prevalence prior*) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
-<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
-<!-- Instead,  -->
-We hypothesize that all of this knowledge feeds into participants' predictions (or, judgments about prevalence).
-<!-- which we model in a precise, quantitative manner. -->
-Thus, we bring precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
-Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
-Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.
-
- <!-- You bring precision and clarity to the judgments by capturing the output of the cognitive processes that generate prevalence.
-But you tend to downplay or at least not emphasize that importance and sometime sounds as if you think you have an alternative view that argues against some of the other perspectives.
-I think this is worth clarifying.
--->
-
-<!-- (at least in the form of a *prevalence prior*) against which generalizations are interpreted. -->
-<!-- In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components. -->
-<!-- Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
--->
-<!-- Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions. -->
-
-<!-- Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
--->
-<!-- We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds and their properties [@Gelman2003; @Keil1992]. -->
-<!-- We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
--->
-<!-- The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
--->
-<!-- Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.  -->
-
-The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
-Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
-Like other models in the probabilistic pragmatic tradition, our model distinguishes the relevant variables for the truth-functional semantics from those that impact the speaker's utility in producing the utterance.
-A speaker's utility comes from addressing an implicit goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
-The separation of the QUD from the literal, truth-functional denotation of the utterance is an important theoretical distinction made explicit in our formal modeling approach [@Goodman2016]. 
-For simplicity, the model presented here assumes the QUD is about prevalence.
-However, the model makes nearly identical predictions if the QUD concerns the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
-This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.
-
-<!-- The model, however, has the flexibility to address richer communicative goals [also known as the *Question Under Discussion* or QUD; @roberts1996qud]. -->
-
-<!-- Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.
--->
-
-<!-- \ndg{ [why is this par here. and what does it mean??] -->
-<!-- The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
--->
-<!-- Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced. -->
-<!-- This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here. -->
-<!-- } -->
-
-<!-- Primarily investigated through generic language (category generalizations), this perspective holds that generics are the linguistic outlet of the mind's default mode of representing kinds [@Leslie2007] and "...an adequate account of the meanings of generic sentences requires an understanding of the ways in which we represent connections between kinds and properties [p.406; @Prasada2013]." -->
-<!-- @Prasada2006 and later @Prasada2013 distinguish properties that have *principled connections* to kinds, *statistical connections*, and *causal connections*.  -->
-
-<!-- Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread. -->
-<!-- Prasada has argued that *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white") are  -->
-<!-- Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring.  -->
-<!-- Where in the probability-based semantics could such conceptual distinctions come into play? -->
-
-<!-- Inferential role semantics -->
-<!-- We take the view the causal relations only does anything because it implies statistical regularities, and these statistical regularities are what our linguistic model depends on. -->
-
-<!-- - what are habituals like under Leslie? -->
-
-<!-- probabilistic treatment of kinds vs. of causality -->
-<!-- conceptual representation vs. causal structure -->
-
-<!-- rational rules: concepts are relatively definitional (with some probabilistic structure on those definitions) -->
-<!-- - leslie: my kinds are your probabilistic concept representations -->
-<!-- - the reason why particular generics are licensed. not that there are kinds and that generics communicate about them. -->
-  <!-- - fundamentally communicative element to what the prevalence is and why a generic would sound good in a praticular case (information relative to the prevalence prior) -->
-
-<!-- - Ellen: causality implies a mechanism, not just a statistical relation. -->
-<!-- - are there parts of the  -->
-<!-- - essentialism: different generative models that imply the same statistics with different causal relations (but orthogonal) -->
-
-## The comparison class
-
-The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
-We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
-Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
-Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect to some comparison class $C$: $P(p \mid C)$.
-
-In this paper, we have assumed particular values of $C$ for our three case studies (*animals*, *people*, and *possible causes*, respectively).
-We think the choice of these classes is intuitive, but it is a limitation of this work that we do not derive these choices from more general information-theoretic considerations.
-The problem of choosing a comparison classes, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012].
-We have begun to explore how pragmatic reasoning and world knowledge can flexibly adjust the comparison class to appropriately suit the context [e.g., how a "short" basketball player is *short for a basketball player* while a "tall" basketball player is *tall for a person*; @Tessler2017].
-It remains to be seen how such principles could operate on richly structured, hierarchical knowledge about categories and properties that would be important for interpreting generic language.
-
-The employment of comparison classes in our model provides additional flexibility towards modeling different communicative goals.
-The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
-Thus, our endorsement model assumes that the QUD was "*what* has this feature?".
-Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
-It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
-<!-- "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
--->
-Prosody provides a good cue towards resolving the comparison class, and pragmatic reasoning is likely relevant here as well [@Declerck1986; @Tessler2017].
-In this work, we focused on category-wise comparison classes purely for methodological convenience.
-Future work should investigate the factors that give rise to feature-wise interpretations of generalizations (e.g., "Dogs *have four legs*", as opposed to having other features), other QUDs generics can address, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.
-
-<!-- Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
--->
-<!-- An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
--->
-<!-- In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics. -->
-
-<!--
-[NDG: i cut this because it is unecassary speculation.]
-Uncertainty about the comparison class adds yet more opportunity to the language of generalization for disagreement, miscommunication, or deceit.
-Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may fail to coordinate on the prevalences for other categories in the comparison class.
-That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis committing acts of terrorism).
-Understanding the contextual influence on the construction of comparison classes should provide insight into failures of communication.
-\mht{ellen: TRUE,  I AGREE WITH YOU AND THIS IS PROBABLY OKAY.
-BUT IT THINK IT WOULD BE BETTER TO SAY SOMETHING SUBSTANTIVE;  FOCUSSING ON HOW KNOWLEDGE OF THE COMPARISION CLASS SHOULD PROVIDE INSIGHTS INTO FAILURES TO COMMUNICATE SUCCESSFULLY.}
--->
-
-<!-- Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.  -->
-<!-- The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. -->
-<!-- Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object).  -->
-<!-- We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017]. -->
-
-<!-- ### Question under discussion -->
-
-<!-- However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD. -->
-<!-- The QUD is thus another layer of flexibility that makes understanding generalizations so challenging. -->
-<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
-<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
-<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->
-
-<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
-<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
--->
-<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
-<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
-<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
--->
-
-<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
-<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
-<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
--->
-<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
-<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
-<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
-<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
--->
-
-## Acquiring the language of generalization
-
-<!-- The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers. -->
-<!-- Generic language is one of the earliest emerging forms of complex, compositional language. -->
-<!-- Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008]. -->
-
-Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
-<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
-<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
-Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
-<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
-<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
-<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
--->
-The assumed complexity of a formal theory of generics and the simplicity with which young children acquire generics has led some to conclude that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
-
-Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
-With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning:
-(1) the *dimension* being described (i.e., prevalence $p$),
-(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
-(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
-Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
-However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
-Thus, under our framework, generics should not only be learned before quantifiers but also facilitate the acquisition of quantifiers.
-<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
-<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
--->
-
-There is a secondary argument for why our semantics presents an easy learning problem.
-<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
--->
-We have assumed the truth functional threshold $\theta$ comes from a uniform distribution over the unit interval $[0, 1]$, which is mathematically equivalent to a *continuously-valued* or *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$.
-The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $Lit(p \mid u) \propto p \cdot P(p)$
-This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
-The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
-We leave for future work the precise implementation of such an acquisition model.
+The flexibility of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
 
@@
 
-The present paper presents the first formal theory of generalization in language that generates quantitative predictions about human behavioral data. 
+The present paper presents the first formal theory of the language of generalization that generates quantitative predictions about human behavioral data. 
 Our work builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
-The dominant approach from formal semantics tries to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
-These views are typically *statistical* and appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
-Theorists in philosophy and psychology have argued that what matters for producing and understanding generics is not the statistics of the world, but to mental representations or abstract beliefs in the head (e.g., *there is something about being a K which causes it to F*).
+The main set of approaches from formal semantics try to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
+These views are typically *statistical* in nature in that they appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
+Many of these theories rely upon mechanisms outside of the truth conditions to make sense of the extreme flexibility exhibited by generics; unfortunately, these extra-semantic mechanisms are rarely described in any detail and never to the extent to make precise predictions.
+Other theorists, primarily in philosophy and psychology, have taken the extreme flexibility of generics to argue against a quantitative theory based on prevalence, instead arguing that abstract, mental representations are directly tied to semantics of generics (e.g., *there is something about being a K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of generic language [@Carlson1995essay].^[
@@
 The most influential account in psychology comes from @Leslie2008, which has same starting point as our analysis: Generics express generalization. 
-This analysis draws upon insights from the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.^[
-  Because the mechanism for understanding generics is innate, in this account, the learning puzzle (vis a vis quantifiers) immediately goes away.
-]
+This analysis draws upon insights from the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.
+<!-- ^[ -->
+<!--   Because the mechanism for understanding generics is innate, in this account, the learning puzzle (vis a vis quantifiers) immediately goes away. -->
+<!-- ] -->
 
@@
 If the property is neither characteristic nor striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
-Many of the key factors in this conceptual approach are compatible with our predictive probability approach: What is required is that the distinctions made by conceptual accounts influence predictive probability, which mediates linguistic effects.
+Many of the key factors in this conceptual approach are compatible with our view of prevalence as a predictive probability: What is required is that the distinctions made by conceptual accounts influence predictive probability, which mediates linguistic effects.
 Indeed, one version of this mechanism is already suggested by @Leslie2008, citing findings by @Rothbart1978, that a speaker’s perception of the prevalence of the feature can be altered by virtue of its dangerousness or distinctiveness.
@@
 
-The conceptual view of generics argues it is not desirable to define generics in the same terms as quantifiers (e.g., a truth-functional threshold on prevalence), because generics are in many ways *more fundamental* than quantifiers [@Leslie2008; @Gelman2009].
+The conceptual view of generics argues it is not desirable to define generics in the same terms as quantifiers (e.g., a truth-functional threshold on prevalence), because generics are more fundamental than quantifiers [@Leslie2008; @Gelman2009].
 For example, young children have a nearly adult-like understanding of generics far earlier than they do with quantified language [@Gelman2015].
-Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that information will tend to recall the information using generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
+Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that same information will tend to recall quantified information as generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
 As a result, generics are thought of as conveying *default generalizations*, whereas quantified language expresses more sophisticated and specific generalizations.
-
-Rather than be contradictory to a prevalence-based truth-functional semantics, these observations independently motivate our treatment of the semantics as *underspecified*.
-Probabilistic agents typically have uncertainty about variables of interest in their environment; having certainty about a random variable is a rare and special case.
-In a probabilistic representation, then, states of uncertainty are more fundamental than states of uncertainty.
-Therefore, if quantified language can be described with *certain* thresholds  (e.g., *some* means greater than *zero*, *most* means greater than *half*), then we would expect generics, as a more fundamental linguistic device, to have an *uncertain threshold*.
-Thus, in our framework, generics behave like a more fundamental (i.e., more uncertain) quantifier.
-One distinctive feature of generics that this informal analysis does not address is that generics are *intensional* (e.g., having to do with predictions are the future) whereas quantifiers tend to be *extensional* (i.e., concerned with the actual frequencies in the world).
-How and why the intensional/extensional distinction emerges between quantifiers and generics is an outstanding issue for a theory such as ours that tries to unify the linguistic analysis of these two kinds of expressions.
+The uncertain threshold model can be viewed as a way of formalizing what constitutes a default generalization.
+For this model, the default generalization is a Bayesian belief updating mechanism via a threshold function whose threshold value is uncertain.
+
+<!-- Rather than be contradictory to a prevalence-based truth-functional semantics, these observations independently motivate our treatment of the semantics as *underspecified*. -->
+<!-- From a probabilistic learning perspective, a child learning the semantics of generics (and quantifiers) need learn  -->
+<!-- Probabilistic agents typically have uncertainty about variables of interest in their environment; having certainty about a random variable is a rare and special case. -->
+<!-- In a probabilistic representation, then, states of uncertainty are more fundamental than states of uncertainty. -->
+<!-- Therefore, if quantified language can be described with *certain* thresholds  (e.g., *some* means greater than *zero*, *most* means greater than *half*), then we would expect generics, as a more fundamental linguistic device, to have an *uncertain threshold*.
+-->
+<!-- Thus, in our framework, generics behave like a more fundamental (i.e., more uncertain) quantifier. -->
+<!-- One distinctive feature of generics that this informal analysis does not address is that generics are *intensional* (e.g., having to do with predictions are the future) whereas quantifiers tend to be *extensional* (i.e., concerned with the actual frequencies in the world).
+-->
+<!-- How and why the intensional/extensional distinction emerges between quantifiers and generics is an outstanding issue for a theory such as ours that tries to unify the linguistic analysis of these two kinds of expressions.
+-->
 
@@
 Striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
-Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*; see also our Expt.
-2a, e.g., the distributions for *steals cars* vs.
-*climbs mountains* for an example with habituals).
+Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*).
+<!-- ; see also our Expt. 2a, e.g., the distributions for *steals cars* vs. *climbs mountains* for an example with habituals).  -->
 @Cimpian2010 (Expt.
 4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
-This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar to each other, and distinct from that of the neutral properties.
+This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar, and distinct from that of the neutral properties.
 @Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
@@
 ]
-Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
+Interestingly, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
 2 & 3].
@@
 
-@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), which is a property that bears a *principled connection* to the kind. 
+@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), a property that bears a *principled connection* to the kind. 
 A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
@@
 Cohen's and other statistical theories employ upon an additional mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
-This mechanism is called *domain restriction*. 
+This mechanism is called *domain restriction* and is a common feature in many theories of generics. 
 @Cohen1999 posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
@@
 ]
-The mechanism of domain restriction may be implicit in our own theory: The prior distribution over the prevalence of *lays eggs* presumably includes aspects of people's theories about reproduction (i.e., that only females lay eggs).
-Thus, there may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain restriction.
+The mechanism of domain restriction may be implicit in our own theory: The prior distribution over the prevalence of *lays eggs* relies upon aspects of an intuitive theory of reproduction (i.e., that only females lay eggs).
+There may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain of restriction.
 
@@
 
-A popular alternative view under the statistical banner draws on the intuition that generics express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008; @Nickel2016]. 
+A popular alternative view under the statistical banner draws on the intuition that generics often express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008; @Nickel2016]. 
 For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
 However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers"; described in more detail below) and resisting stereotyped language (e.g., "Boys are good at math”).
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers") and resisting stereotyped language (e.g., "Boys are good at math”).
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
@@
 
-### A unified perspective
+### A unified view
 
@@
 This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
+
+### Intermediate summary
+
+We have introduced the first quantitative theory of generic language and other sorts of generalizations in language, and discussed the relationship of this account to extant theories of generics.
+Above, we presented simulations showing how the model predicts endorsements depending upon the background knowledge about the property $P(p)$ as well as the referent prevalence $p$ believed to be true for the category.
+For each of these we chose schematic values for the parameters of the model (i.e., the prevalence priors and referent prevalence levels), and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
+In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
+We do this by both measuring and manipulating background knowledge and referent-prevalence and predicting human endorsements of generalizations.
+
+There are several theoretically-substantive components to our model: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) vagueness in the semantics of a generalization.
+Throughout our experiments, we compare the uncertain threshold model to an alternative, lesioned model by removing the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keeping the prior and the decision-theoretic architecture in place.
+There are no correspondingly simple ways to lesion the other two components (property knowledge or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.
+Furthermore, for comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we constructed alternative regression models based on empirically-elicited quantities. 
+In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our items. 
+These three alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions.
 
@@
 
+<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
+<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq.
+\ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq.
+\ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq.
+\ref{eq:S1}).
+-->
+<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
+-->
+<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).
+-->
+
+<!-- This reasoning process favors lower thresholds because they are consistent with more prevalences. -->
+<!-- Low thresholds (e.g., $\theta = 0.25$) rule out very few possibilities (only $p \leq 0.25$), and thus an interpretation with a low-threshold still has a lot of uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, left).
+-->
+<!-- Higher thresholds  (e.g., $\theta = 0.75$) rule out many possibilities; an interpretation with this threshold has correspondingly less uncertainty about the prevalence (Figure\ \@ref(fig:simulations)A, right).
+-->
+<!-- The flip-side of this is that the endorsement model is less likely to produce an utterance with a low-threshold in mind, because the end result would be, from an information-theoretic perspective, similar to staying silent (a posterior not very different from the prior).
+-->
+<!-- Higher thresholds (e.g., $\theta = 0.9$) rule out more possibilities and thus would be highly informative, but the interpretation model must balance this with the prior probabilities of the prevalences implied by the threshold (Figure\ \@ref(fig:simulations)A).
+-->
+<!-- The result of this reasoning process is a trade-off between highly informative thresholds and the prior probabilities of the prevalences implied by those thresholds. -->
+
+<!-- The literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") is given by Eq. \ref{eq:L0} and shown in  -->
+
+<!-- The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}.  -->
+<!-- For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
+-->
+<!-- This would correspond to a rather strong interpretation (i.e., "Almost all feps bark"). -->
+<!-- This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green).  -->
+<!-- Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
+-->
+<!-- The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple). -->
+<!-- Again, the literal interpretation depends upon the background knowledge in a deep way. -->
+
+<!-- The endorsement model's predictions for six generic sentences are shown in Figure\ \@ref(fig:simulations) (right). -->
+<!-- Given a referent-prevalence $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$; Fig.\ \@ref(fig:simulations) right x-axis) and the background knowledge of the interpreter (Fig.\ \@ref(fig:simulations) left), the endorsement model (Eq.
+\ref{eq:S1}) predicts an endorsement probability (Fig.\ \@ref(fig:simulations) right y-axis).
+-->
+<!-- We see the model correctly  -->
+
+<!-- \mht{For further discussion about the behavior of the model, and these six examples, see Appendix?} -->
+
+<!-- that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics. -->
+<!-- For these simulations, we had specify both the prevalence priors $P(h)$ and the referent prevalence $h'$.. -->
+<!-- In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes. -->
+
+<!-- These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row). -->
+<!-- The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior. -->
+<!-- The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[ -->
+<!-- The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities. -->
+<!-- If the threshold $\theta$ is very high, only the highest prevalence $h$ would pass the threshold. -->
+<!-- If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower. -->
+<!-- As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it. -->
+<!-- When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model). -->
+<!-- The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*. -->
+<!-- ] -->
+
+<!-- Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements. -->
+<!-- The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$. -->
+<!-- In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
+-->
+<!-- The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[ -->
+<!-- We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero.  -->
+<!-- The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
+-->
+<!-- ] -->
+<!-- The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category. -->
+
+<!-- How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"? -->
+<!-- In each case, we must consider the prevalence prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$. -->
+<!-- For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
+-->
+<!-- For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs. -->
+<!-- This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3). -->
+<!-- For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
+-->
+<!-- The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case.
+-->
+<!-- In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
+-->
+<!-- "Robins lay eggs", however, has a lot of informational content. -->
+
+<!-- Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria". -->
+<!-- The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread. -->
+<!-- Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4).
+-->
+<!-- Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria". -->
+
+```{r child = 'case1-generics.Rmd'}
+```
+
+```{r child = 'case2-habituals.Rmd'}
+```
+
+```{r child = 'case3-causals.Rmd'}
+```
+
+# General Discussion
+
+The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
+Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
+We have argued that the core meaning of such linguistic expressions can be understood by three ingredients: Probability, vagueness, and context. 
+Though generics are vague that does not preclude them from being treated by formal models. 
+A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.
+
+<!--
+formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
+As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.
+
+Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
+-->
+
+We tested this theory by exploring its implications for the simplest judgments a person could make: truth judgments.
+We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
+Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
+This framework accounts for a number of philosophically puzzling generic statements (Expt.
+1), naturally extends to other domains of generalizations (habituals and causals; Expts.
+2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt.
+2c).
+We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
+In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
+
+Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
+The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
+Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
+
+<!--
+NDG: i cut this from below...
+This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
+These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
+Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
+What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
+-->
+
+Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
+Rather than conveying probabilities explicitly, generalizations convey them implicitly.
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
+
+<!--
+\mht{unsure about this paragraph... a version of it may be better for the cover letter (if at all)}
+\ndg{yeah, this is unecessarily inflamatory. ax it.}
+Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and leave it to intuition to decide for a particular generic statement, what kind of generic it is.
+In this paper alone, our theory has made hundreds of predictions about the endorsement of individual generic statements, with high accuracy, derived from a general theory that we posit applies to all generic statements.
+In addition, previous accounts are rarely general enough to include generalizations of different semantic types (e.g., *habituals*) and deal only with generics.
+For these reasons alone, our account is novel. 
+-->
+
+<!-- In the rest of this discussion, we elaborate how our model relates to language understanding more generally, situate our theory with respect to extant theories of generic language, and sketch applications to a few philosophical puzzles in genericity.
+-->
+
+<!-- Thus, in addition to expressing a precise hypothesis about the truth conditions of generics, instantiating it in a cognitive model opens up the possibility of building more elaborate models that learn abstract, generalizable knowledge from language.
+-->
+
+<!-- We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
+-->
+<!-- These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data. -->
+<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
+<!-- A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement.  -->
+<!-- That is precisely what our information-theoretic model does. -->
+<!-- xx -->
+<!-- The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge. -->
+
+<!-- That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
+-->
+<!-- Our communicative framework also includes a model of a listener who interprets generalization. -->
+<!-- Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work.  -->
+
+<!-- \mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)} -->
+
+<!-- \ndg{ -->
+<!-- [these paragraphs were out of place here. perhaps incorporate later...] -->
+<!-- } -->
+<!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->
+
+<!-- Our separation of world knowledge from the semantics of generics provides a substantial, but well-circumscribed role for conceptual structure to influence generic production and comprehension.
+-->
+<!-- We do this without having to posit that conceptual structure and semantics are one in the same. -->
+<!-- This is makes it possible to connect with theories of formal semantics as well as applied Natural Language technologies that seeks to draw inferences from information conveyed in generalizations in text [e.g., @Herbelot2011].
+-->
+<!-- Statistical accounts in particular [@Cohen1999; @Nickel2008] -->
+
+<!-- @Nickel2016 notes that genericity is particularly challenging to study because it intersects with many other phenomena in natural language (e.g., gradable adjectives in "Giraffes are tall"). -->
+<!-- We agree, and add to this that genericity intersects with *world knowledge* in subtle ways, and it is critical to accurately describe and measure world knowledge before making claims about the semantics of a generalization.
+-->
+<!-- We used the most basic tests to validate our model: Production was examined in terms of *endorsement*, which can be seen as a special case of production when the only available alterantive utterances are the assertion or its negation.
+-->
+<!-- Comprehension was examined in terms of *implied prevalence*, which in our theory is most basic inference a hearer can make upon hearing a generalization. -->
+<!-- Though these are highly abstracted tests of the model, the modeling framework in principle allows for elaboration to a more complete production and comprehension model.  -->
+<!-- The model is a communicative model, which includes a component corresponding to *comprehension* of genericity (i.e., a listener model).  -->
+
+<!-- We conclude by sketching out arguments for other known philosophical puzzles in genericity. -->
+
+<!-- Implicit aspects of language use: The comparison class and question under discussion -->
+
+<!-- to explore when and how people choose to communicate their abstract knowledge when they have more options than in a two-alternative forced-choice task. -->
+<!-- The view of our endorsement model as a minimal communicative model highlights aspects of our modeling approach for further future development.  -->
+
+<!-- ## Generic Identification -->
+
+<!-- Throughout this paper we treated the bare plural construction as a generic utterance with a threshold semantics: $\denote{\text{K F}}(x, \theta)=x>\theta$. -->
+<!-- The bare plural construction can also indicate a specific plural predication. -->
+<!-- For example, "Dogs are on my lawn" picks out a specific group of dogs, while "Dogs have fur"  does not [@Carlson1977]. -->
+<!-- The problem of \emph{identifying} a generic meaning from a bare plural construction is itself a challenging problem because generic meaning can be signaled using a diverse array of morphosyntactic cues.
+-->
+
+<!-- @Declerck1991 suggests that generic and non-generic bare plurals can be treated in the same way, and that pragmatic considerations alone may resolve interpretative differences. -->
+<!-- Indeed it does appear that knowledge of the properties under discussion (e.g., the state of being on a front lawn; the state of having fur) could facilitate the generic identification process.
+-->
+<!-- Other pragmatic factors, like knowledge of the identity of the speaker (e.g., a teacher vs. a veterinarian), can also disambiguate generic and non-generic meaning [@Cimpian2008]. -->
+<!-- Recent work suggests that utterances that fail to refer to specific entities or events could pragmatically imply generic meaning [@Crone2016cogsci]. -->
+<!-- Incorporating these insights about generic identification into an information-theoretic, communicative perspective is a natural extension of this work. -->
+
+<!-- Expts.
+2c \& 2d that showed using participants' *predictions* about the future as the object of communication in our formal model perfectly tracked habitual endorsement, when the present frequency would make the wrong prediction.
+-->
+
+<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
+<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?".
+This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.
+-->
+
+<!-- ### The Problems with Communicating Generalizations -->
+
+<!-- Thus, in order to define a generalization about a category, there must be some corresponding concrete particular instance of that category from which the generalization is formed.  -->
+<!-- For example, if an agent observes $n$ instances of \textsc{dog} ($d_1, d_2, ..., d_n$) -->
+<!-- For example, if an observer forms a generalization about \textsc{dogs}, she must some way of determining when she is in an instance of the category \textsc{dogs}: She must be able to *individuate*.
+-->
+<!-- In Hume's words, generalizations are predictions about "instances of which we have had no experience resemble those of which we have had experience" [@HumeTHN]. -->
+
+<!-- Generalizations can be made about almost anything. -->
+<!-- Here, we restrict our focus to generalizations about categories (whose linguistic expression is known as *generic language*), which have been the primary focus of psychologists, linguists, and philosophers.
+-->
+<!-- We posit that our analysis should expect to generalizations about events (habitual language) as well as generalizations about causal forces (causal language). -->
+
+<!-- Generics express a relation between a kind K (e.g., \textsc{robins}) and a property F (e.g., \textsc{lays eggs}), such that the property can also be said to be applicable of an individual (i.e., the bird in my backyard lays eggs).
+-->
+<!-- Bare plural statements (e.g., \emph{Robins lay eggs}) tend strongly to yield a generic meaning [@Carlson1977], though other forms can express such a meaning sometimes (e.g., \emph{A mongoose eats snakes.}).
+-->
+
+<!-- Given that generics express a property that can be applied to individuals, it would seem intuitive that the number of individuals with the property would be what makes the statement true or false.
+-->
+<!-- Counter-examples like \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} v. \emph{Birds are female} stifle such intuition.  -->
+
+<!-- ### Statistical Accounts of Generics -->
+
+<!-- Statistical accounts take the \textbf{property prevalence} to be fundamental: \emph{Birds lay eggs} means \emph{Birds, in general, lay eggs}.  -->
+<!-- Of course, birds do not in general lay eggs (it's only the adult, female ones that do). -->
+<!-- The primary way of dealing with such issues is to posit domain restrictions ("implicitly, we are only talking about the females") when there are "salient partitions" [@Carlson1995]. -->
+<!-- The most fully-developed theory on this front is due to @Cohen1999.  -->
+<!-- Let's first introduce some notation: -->
+
+<!-- ### Conceptual Accounts of Generics -->
+
+## Prevalence priors and cue validity
+
+By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
+The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
+In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
+Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
+Knowledge about other categories $k'$ enters in the denominator.
+Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
+Thus cue validity comes from a point estimate of the prevalence prior distribution.
+For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
+For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we constructed alternative models based on empirically-elicited cue validity.
+These control models improved the quantitative fit to the endorsement data, but did not match the explanatory power of the uncertain threshold model.
+
+## Prevalence priors and conceptual knowledge
+
+Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
+It is this real-world knowledge (presently formalized in terms of a *prevalence prior*) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
+<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
+<!-- Instead,  -->
+We hypothesize that all of this knowledge feeds into participants' predictions (or, judgments about prevalence).
+<!-- which we model in a precise, quantitative manner. -->
+Thus, we bring precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
+Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
+Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.
+
+ <!-- You bring precision and clarity to the judgments by capturing the output of the cognitive processes that generate prevalence.
+But you tend to downplay or at least not emphasize that importance and sometime sounds as if you think you have an alternative view that argues against some of the other perspectives.
+I think this is worth clarifying.
+-->
+
+<!-- (at least in the form of a *prevalence prior*) against which generalizations are interpreted. -->
+<!-- In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components. -->
+<!-- Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
+-->
+<!-- Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions. -->
+
+<!-- Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
+-->
+<!-- We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds and their properties [@Gelman2003; @Keil1992]. -->
+<!-- We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.
+-->
+<!-- The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
+-->
+<!-- Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.  -->
+
+The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
+Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
+Like other models in the probabilistic pragmatic tradition, our model distinguishes the relevant variables for the truth-functional semantics from those that impact the speaker's utility in producing the utterance.
+A speaker's utility comes from addressing an implicit goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
+The separation of the QUD from the literal, truth-functional denotation of the utterance is an important theoretical distinction made explicit in our formal modeling approach [@Goodman2016]. 
+For simplicity, the model presented here assumes the QUD is about prevalence.
+However, the model makes nearly identical predictions if the QUD concerns the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
+This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.
+
+<!-- The model, however, has the flexibility to address richer communicative goals [also known as the *Question Under Discussion* or QUD; @roberts1996qud]. -->
+
+<!-- Future work should investigate formalizations of attested differences in background knowledge about properties [e.g., @Prasada2013's *principled*, *statistical*, and *causal* connections] and their corresponding influence on generic endorsement via prevalence priors.
+-->
+
+<!-- \ndg{ [why is this par here. and what does it mean??] -->
+<!-- The rational model of communication that we have developed in this paper makes explicit a speaker's assumptions about the goals of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
+-->
+<!-- Richer communicative contexts will surely need to elaborate the QUD to fit more appropriately with the informational goals of the context in which generalizations are produced. -->
+<!-- This observation is promising for the future goal of integrating communicative goals about kinds or conceptual structure into the information-theoretic communicative framework presented here. -->
+<!-- } -->
+
+<!-- Primarily investigated through generic language (category generalizations), this perspective holds that generics are the linguistic outlet of the mind's default mode of representing kinds [@Leslie2007] and "...an adequate account of the meanings of generic sentences requires an understanding of the ways in which we represent connections between kinds and properties [p.406; @Prasada2013]." -->
+<!-- @Prasada2006 and later @Prasada2013 distinguish properties that have *principled connections* to kinds, *statistical connections*, and *causal connections*.  -->
+
+<!-- Leslie suggests information that is striking (e.g., "Tigers eat people") is ecologically useful and thus permitted to be a generalization, even if the property is not widespread. -->
+<!-- Prasada has argued that *characteristic* properties (e.g., "Diapers are absorbent") and *statistical* properties (e.g., "Diapers are white") are  -->
+<!-- Gelman outlines how generics tend to express *essential* qualities that are relatively timeless and enduring.  -->
+<!-- Where in the probability-based semantics could such conceptual distinctions come into play? -->
+
+<!-- Inferential role semantics -->
+<!-- We take the view the causal relations only does anything because it implies statistical regularities, and these statistical regularities are what our linguistic model depends on. -->
+
+<!-- - what are habituals like under Leslie? -->
+
+<!-- probabilistic treatment of kinds vs. of causality -->
+<!-- conceptual representation vs. causal structure -->
+
+<!-- rational rules: concepts are relatively definitional (with some probabilistic structure on those definitions) -->
+<!-- - leslie: my kinds are your probabilistic concept representations -->
+<!-- - the reason why particular generics are licensed. not that there are kinds and that generics communicate about them. -->
+  <!-- - fundamentally communicative element to what the prevalence is and why a generic would sound good in a praticular case (information relative to the prevalence prior) -->
+
+<!-- - Ellen: causality implies a mechanism, not just a statistical relation. -->
+<!-- - are there parts of the  -->
+<!-- - essentialism: different generative models that imply the same statistics with different causal relations (but orthogonal) -->
+
+## The comparison class
+
+The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
+We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
+In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
+Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
+Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect to some comparison class $C$: $P(p \mid C)$.
+
+In this paper, we have assumed particular values of $C$ for our three case studies (*animals*, *people*, and *possible causes*, respectively).
+We think the choice of these classes is intuitive, but it is a limitation of this work that we do not derive these choices from more general information-theoretic considerations.
+The problem of choosing a comparison classes, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012].
+We have begun to explore how pragmatic reasoning and world knowledge can flexibly adjust the comparison class to appropriately suit the context [e.g., how a "short" basketball player is *short for a basketball player* while a "tall" basketball player is *tall for a person*; @Tessler2017].
+It remains to be seen how such principles could operate on richly structured, hierarchical knowledge about categories and properties that would be important for interpreting generic language.
+
+The employment of comparison classes in our model provides additional flexibility towards modeling different communicative goals.
+The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
+Thus, our endorsement model assumes that the QUD was "*what* has this feature?".
+Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
+It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
+<!-- "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
+-->
+Prosody provides a good cue towards resolving the comparison class, and pragmatic reasoning is likely relevant here as well [@Declerck1986; @Tessler2017].
+In this work, we focused on category-wise comparison classes purely for methodological convenience.
+Future work should investigate the factors that give rise to feature-wise interpretations of generalizations (e.g., "Dogs *have four legs*", as opposed to having other features), other QUDs generics can address, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.
+
+<!-- Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
+-->
+<!-- An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
+-->
+<!-- In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics. -->
+
+<!--
+[NDG: i cut this because it is unecassary speculation.]
+Uncertainty about the comparison class adds yet more opportunity to the language of generalization for disagreement, miscommunication, or deceit.
+Even if interlocutors roughly coordinate on a particular comparison class (e.g., agreeing that they are talking *relative to other animals*), they may fail to coordinate on the prevalences for other categories in the comparison class.
+That is, our model makes the prediction that the acceptance or rejection of controversial statements (e.g., "Muslims are terrorists") depends upon a speaker's beliefs about how often other categories exhibit the property (e.g., neo-nazis committing acts of terrorism).
+Understanding the contextual influence on the construction of comparison classes should provide insight into failures of communication.
+\mht{ellen: TRUE,  I AGREE WITH YOU AND THIS IS PROBABLY OKAY.
+BUT IT THINK IT WOULD BE BETTER TO SAY SOMETHING SUBSTANTIVE;  FOCUSSING ON HOW KNOWLEDGE OF THE COMPARISION CLASS SHOULD PROVIDE INSIGHTS INTO FAILURES TO COMMUNICATE SUCCESSFULLY.}
+-->
+
+<!-- Thus, we conclude generic, habitual, and causal language can be seen as a special case of *vague language*.  -->
+<!-- The construction of a comparison class adds another layer of flexibility into the use of generalizations in language. -->
+<!-- Objects can be conceptualized and categorized in multiple ways, giving rise to multiple, logically-possible comparison classes (e.g., a robin is a bird, is an animal, is an object).  -->
+<!-- We have begun doing work investigating how pragmatic reasoning can help constrain this open-ended problem [@Tessler2017]. -->
+
+<!-- ### Question under discussion -->
+
+<!-- However, the choice in constructing a comparison class can be thought of as the result of addressing a particular QUD. -->
+<!-- The QUD is thus another layer of flexibility that makes understanding generalizations so challenging. -->
+<!-- In the minimal contexts employed in our experiments, this is a reasonable assumption. -->
+<!-- There is a different assumption we could have made, however: Another clear way to construct the comparison class is with respect to other features.  -->
+<!-- This *feature-wise* comparison class would correspond to addressing the implicit QUDs: *what does \textsc{person} do?*, *what effects does \textsc{cause} bring about?*, and *what features does \textsc{kind} have?* -->
+
+<!-- Throughout our experiments in this work, we have focused on sentences about animals.  -->
+<!-- In addition to being the main focus of past theoretical and empirical work, focusing on animals is methodologically convenient as the comparison class for generics about animals is quite naturally \emph{animals}.
+-->
+<!-- When we look beyond generics about animals, deciding what goes into a comparison class becomes less clear. -->
+<!-- There are some hints that the comparison class can be derived with respect to the property [@Keil1979], but may involve pragmatic reasoning as well. -->
+<!-- For example, the statement "iPhones are useful" could be in comparison to other forms of technology (like a desktop computer), while "iPhones are heavy" could really only be informative relative to other handheld devices.
+-->
+
+<!-- The incorporation of a comparison class into the study of generic language might help elucidate other puzzles concerning generics. -->
+<!-- Recent work in philosophy and linguistics, for instance, suggest generic language is context-sensitive [@Nickel2008; Sterken2015]. -->
+<!-- @Nickel2008 points out that \emph{Dobermans have floppy ears} may be true in the context of a discussion of evolutionary biology but that \emph{Dobermans have pointy ears} is true in a discussion of dog breeding.
+-->
+<!-- Our theory provides a hint from where to begin to understand this context sensitivity: the comparison class. -->
+<!-- Different conversational contexts could bring to mind different comparison classes, in a way analogous to the context-sensitivity of  gradable adjectives (e.g., \emph{tall}).  -->
+<!-- Hearing that "Abigail is tall" means different things is Abigail is 20 years old or if she is 4.  -->
+<!-- Future work will be needed to explore whether a pragmatic inference approach is also relevant to establishing the comparison class, and what background knowledge about properties, categories, and context is relevant.
+-->
+
+## Acquiring the language of generalization
+
+<!-- The linguistic outlet for generalizations about categories---so called, *generic language*---has received tremendous attention from psychologists, linguists, and philosophers. -->
+<!-- Generic language is one of the earliest emerging forms of complex, compositional language. -->
+<!-- Somewhere between two and three years of age, children recognize that generics convey a generalization about a category, not directly tied to concrete instances in a scene [@Cimpian2008]. -->
+
+Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
+<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
+<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
+Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
+<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
+<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
+<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a].
+-->
+The assumed complexity of a formal theory of generics and the simplicity with which young children acquire generics has led some to conclude that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
+
+Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
+With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning:
+(1) the *dimension* being described (i.e., prevalence $p$),
+(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
+(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
+Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
+Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
+However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
+Thus, under our framework, generics should not only be learned before quantifiers but also facilitate the acquisition of quantifiers.
+<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
+<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.
+-->
+
+There is a secondary argument for why our semantics presents an easy learning problem.
+<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy.
+-->
+We have assumed the truth functional threshold $\theta$ comes from a uniform distribution over the unit interval $[0, 1]$, which is mathematically equivalent to a *continuously-valued* or *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$.
+The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $Lit(p \mid u) \propto p \cdot P(p)$
+This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
+The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
+We leave for future work the precise implementation of such an acquisition model.
+
 # Conclusion

### 2018-09-23 paper/comgen-paper.Rmd
discuss cue validity in common ground; vagueness; update acquisition story

@@
 For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is greater than zero: $\denote{some}(p) := p > 0$.
-"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.
+"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.^[
+  We note that we are describing the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
+]
 Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.
@@
 
+### Cue validity
+
+By encoding knowledge about other categories, the prevalence prior distributions in the uncertain threshold model are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
+Cue validity is believed to play a role in understanding generic language [@Leslie2007; @Khemlani2012; @Prasada2013], but the details remain obscure.
+The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
+Indeed, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
+
+Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
+$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
+Knowledge about other categories $k'$ enters in the denominator.
+Indeed this normalizing constant (the denominator) is equal to the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
+Thus cue validity comes from a point estimate of the prevalence prior distribution.
+For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
+We discuss the implications of this relationship in the General Discussion.
+For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we construct alternative quantitative models based on empirically-elicited cue validity.
+<!-- These control models improved the quantitative fit to the endorsement data, but did not match the explanatory power of the uncertain threshold model. -->
+
 ### A unified view
@@
 For each of these we chose schematic values for the parameters of the model (i.e., the prevalence priors and referent prevalence levels), and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
-In what follows, we test this theory for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
-We do this by both measuring and manipulating background knowledge and referent-prevalence and predicting human endorsements of generalizations.
+In what follows, we test this theory empirically for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
+We do this by both measuring and manipulating background knowledge and referent prevalence and predicting human endorsements of generalizations.
 
@@
 not uttering it, and (c) vagueness in the semantics of a generalization.
-Throughout our experiments, we compare the uncertain threshold model to an alternative, lesioned model by removing the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keeping the prior and the decision-theoretic architecture in place.
+Throughout our experiments, we compare the uncertain threshold model to an alternative, lesioned model which lacks the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to a quantified statement) but which has the same prevalence prior and the decision-theoretic architecture.
 There are no correspondingly simple ways to lesion the other two components (property knowledge or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.
-Furthermore, for comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we constructed alternative regression models based on empirically-elicited quantities. 
-In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our items. 
+Furthermore, for comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012], we construct alternative regression models based on empirically-elicited quantities (referent prevalence and *cue validity*, described below).
+In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our experimental materials. 
 These three alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions.
@@
 The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
-Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
+Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey rich meanings and display complex sensitivities to context.
 We have argued that the core meaning of such linguistic expressions can be understood by three ingredients: Probability, vagueness, and context. 
-Though generics are vague that does not preclude them from being treated by formal models. 
+That generics are vague does not preclude them from being treated by formal models. 
 A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.
@@
 
-We tested this theory by exploring its implications for the simplest judgments a person could make: truth judgments.
+We tested this theory by exploring its implications for the simplest judgments a person could make regarding a sentence: truth judgments.
 We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
@@
 
+The analogy of habituality (e.g., "John runs") and genericity (e.g., "Dogs have four legs") has typically been assumed in the literature after the original suggestion by @Carlson1977.
+The relationship has been never been empirically tested nor formally described.
+This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism explains judgments of both kinds of statements (Expts.
+1 & 2).
+
+\mht{should this be moved to the intro before other theories?}
 Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
 The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
-Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
 Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
@@
 
+In the rest of this discussion, we further discuss our model in relation to other constructs and theoretical positions, describe how our model relates to language understanding more generally including theories of vagueness, and sketch an argument for how our formal representation of the language of generalization could provide a relatively simple acquisition problem for a language learner.
+
 <!--
@@
 
-<!-- In the rest of this discussion, we elaborate how our model relates to language understanding more generally, situate our theory with respect to extant theories of generic language, and sketch applications to a few philosophical puzzles in genericity.
--->
-
 <!-- Thus, in addition to expressing a precise hypothesis about the truth conditions of generics, instantiating it in a cognitive model opens up the possibility of building more elaborate models that learn abstract, generalizable knowledge from language.
@@
 
-## Prevalence priors and cue validity
-
-By encoding knowledge about other categories, the prevalence prior distributions are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
-In fact, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
-Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
-$P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
-Knowledge about other categories $k'$ enters in the denominator.
-Indeed this normalizing constant (the denominator) is the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
-Thus cue validity comes from a point estimate of the prevalence prior distribution.
-For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
-For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we constructed alternative models based on empirically-elicited cue validity.
-These control models improved the quantitative fit to the endorsement data, but did not match the explanatory power of the uncertain threshold model.
-
-## Prevalence priors and conceptual knowledge
+## Prevalence priors, conceptual knowledge, and cue validity
 
@@
 <!-- Instead,  -->
-We hypothesize that all of this knowledge feeds into participants' predictions (or, judgments about prevalence).
+We hypothesize that all of this knowledge feeds into participants' predictions, or judgments about prevalence.
 <!-- which we model in a precise, quantitative manner. -->
-Thus, we bring precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
+This framework, thus, brings precision and clarity to the *output* of these cognitive processes and conceptual understanding: participants' intuitions about prevalence.
 Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
@@
 
+In our model, a generic statement or generalization updates a listener's *a priori* beliefs about the prevalence of the property for that category. 
+Since the prevalence prior includes the information necessary to compute *cue validity* (Appendix A), the cue validity of the feature for the new category is added to the common ground between interlocutors.
+Thus, given the knowledge represented in a prevalence prior, generics communicate information both about the prevalence of the feature in the new category (via the literal semantics) as well as the cue validity of the feature for the new category.
+To our knowledge, this is the first theory of generics that describes how the informational contribution of a generic relates to cue validity.^[
+  We are grateful to an anonymous reviewer for drawing our attention to this. 
+]
+This also means that our computational framework makes predictions about the cue validity implied by different generalizations, without any further assumptions.
+
 <!-- The model, however, has the flexibility to address richer communicative goals [also known as the *Question Under Discussion* or QUD; @roberts1996qud]. -->
@@
 
+## Genericity and vagueness
+
+We have argued that the language of generalizations are vague descriptions of prevalence or frequency in a way analagous to how gradable adjectives like "tall" are vague descriptions of some underlying degree scale (e.g., height).
+However, vague predicates like "tall" exhibit a number of additional phenomena that we do not suppose generics or generalizations would necessarily exhibit.
+For example, vague predicates admit borderline cases (e.g., a person who is neither tall nor not tall). 
+It is *a priori* unclear whether one could construct borderline cases with generics or habituals without sounding like a contradiction (e.g., "John both runs and doesn't run").
+Additionally, Sorites paradoxes can be constructed out of arguments using vague predicates, and it is not clear that generics or habituals could be used to construct such arguments.
+We note that no experimental data yet bears on these ideas and could be useful for understanding how far the relationship between generalizations and vague predicates goes.
+
+For now, we understand both genericity and vagueness as analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions (e.g., an uncertain threshold).
+We note that this sort of "lexical uncertainty" is kind of *parameter learning* problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a *structure learning* problem (e.g., lexical ambiguity).
+Further work should be done to better understand the kinds of context-sensitive linguistic phenomena that are modeled as parameter vs. structure learning problems.
+
+Our view of understanding generalizations involving reasoning about an uncertain threshold is reminiscent of @Williamson1994's epistemicist view on vagueness.
+This view holds that when a speaker utters a vague statement, there exists an objective set of criteria determining whether the entity in question satisfies the vague predicate.
+Vagueness emerges from uncertainty about the details of those objective criteria (e.g., the precise value of a threshold). 
+This uncertainty in turn could be the result of a population of speakers using slightly different criteria, thus shifting the criteria or threshold.
+Listeners then will not know exactly what kind of speaker they are dealing with *a priori* and normatively should maintain uncertainty about the truth conditions. 
+In our model, world knowledge and general communicative principles help a listener resolve the value of threshold.
+
 ## Acquiring the language of generalization
+
+\mht{added a footnote and tweaked paragraphs 1 and 2}
 
@@
 <!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
-Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
+Generics are often contrasted with quantifier language (e.g., "some", "most", "all"), whose truth conditions are easy to formalize but which pose difficulty for young children to acquire [@Brandone2014; @Gelman2015].
 <!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
@@
 -->
-The assumed complexity of a formal theory of generics and the simplicity with which young children acquire generics has led some to conclude that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics [@Leslie2008].
-
-Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
+@Leslie2008 argues that the necessary complexity of a formal account of generics and the simplicity with which young children acquire generics implies that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics.^[
+  This argument is a little too simplistic in that it ignores evidence that children's struggle with quantifiers stems from pragmatic issues [@Musolino2006].
+]
+
+Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater: In fact, our model of generics can be viewed as *simpler* from a learning perpsective than a model of quantifier semantics.
 With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning:
@@
 (2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
-(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
-Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
-Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
-However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
-Thus, under our framework, generics should not only be learned before quantifiers but also facilitate the acquisition of quantifiers.
+(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").^[
+  This particular framing of the acquisition process ignores the potentially different impact of pragmatic reasoning on generics vs. quantifiers. 
+]
+If a learner first acquires the dimension and the polarity (i.e., generics have to do with prevalence in some positive way), a rational learner should then represent uncertainty over possible thresholds $\theta$.
+For quantifier semantics, a learner would then need to learn the context-invariant value of the threshold $\theta$, but for generics, she could have an adult-like semantics for generics by maintaining uncertainty about the threshold.
+That is, the language of generalization is learned once aspects (1) and (2) are understood.
+Thus, under our framework, generics should not only be learned before quantifiers but could also facilitate the acquisition of quantifiers because of their shared logical form.
 <!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->

### 2018-09-24 paper/comgen-paper.Rmd
move prime numbered justices to gd

@@
 
-#### Worked examples
+### Worked examples
 
@@
 Then, if we constructed the comparison class by considering other professionals, Sentence (8) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
-
-\mht{this "surprising prediction" might set the reader up for the expectation that we are going to test this prediction..}
-
-However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
-That is, our theory predicts there are situations where statements like (8) could be considered felicitous generalizations.
 
@@
 
-### Cue validity
+#### Cue validity
 
@@
 The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
+In fact, we saw in Expt. 2c that it was participants predictions about the future that matter for the prevalence computation involved in endorsement.
+Intuitive theories guide these predictions, and might provide new insight into classic puzzles of generics.
+We described in the Worked Examples how our model treats "Supreme Court Justices have even social security numbers" as infelicitous even when 100% of justices have even SSNs, because a speaker's subjective probability that the *next justice* would have an even SSN is likely 50%.
+However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
+
 Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
@@
 
-Our view of understanding generalizations involving reasoning about an uncertain threshold is reminiscent of @Williamson1994's epistemicist view on vagueness.
+Our view of understanding generalizations involving reasoning about an uncertain threshold is reminiscent of @Williamson1992's epistemicist view on vagueness.
 This view holds that when a speaker utters a vague statement, there exists an objective set of criteria determining whether the entity in question satisfies the vague predicate.
@@
 @Leslie2008 argues that the necessary complexity of a formal account of generics and the simplicity with which young children acquire generics implies that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics.^[
-  This argument is a little too simplistic in that it ignores evidence that children's struggle with quantifiers stems from pragmatic issues [@Musolino2006].
+  This argument is simplistic in that it ignores evidence that children's struggle with quantifiers stems from pragmatic issues [@Musolino2006].
 ]

### 2018-09-24 paper/response.tex
edits to response letter

@@
 \newcommand{\ndg}[1]{{\color{green}{[ndg: #1]}}}
+\newcommand{\mht}[1]{{\color{blue}{[mht: #1]}}}
 
@@
 We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
-We have made a number of substantive changes in this version of the manuscript that we think will improve the readability of the paper.
+We have made a number of substantive changes in this version of the manuscript that we hope will improve the readability of the paper.
 
-We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments.
+Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
+we have merged the General Discussion subsection ``Other philosophical puzzles'' with the worked examples (e.g., \emph{birds lay eggs vs.
+are female}, \emph{mosquitos carry malaria}) that appeared before the experiments; now, both appear before the experiments.
+We describe why each example is interesting, how the model handles each case., and provide a summary in a table (per R1's suggestion).
+By moving these other philosophical puzzles to appear before the experiments, we are able to foreshadow the relevance of \emph{predictive probability} (and motivate Expt. 2c).
+
+We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments (after the model section and worked examples).
 We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theories to extant theories. 
@@
 
-Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
-we have moved the General Discussion subsection ``Other philosophical puzzles'' to appear before the experiments and merged with the worked examples (e.g., \emph{birds lay eggs vs.
-are female}, \emph{mosquitos carry malaria}).
-By moving these other philosophical puzzles to appear before the experiments, we are able to foreshadow the relevance of \emph{predictive probability} as central to our account (and motivate Expts.
-2c \& d).
-We have also added a table per R1's suggestion summarizing the examples we believe a theory of generics should be able to handle; in the corresponding section we have included a high-level verbal description of how our model treats these examples.
-
 We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
@@
 We have taken a few paragraphs to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions.
-We note that this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity).
-We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
-We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson's (1994) empiricist view.
+We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity).
+We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance Sorites sequences).
+We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson (1992)'s epistemicist view.\footnote{
+	R2 actually cited Williamson (1994).
+In our searches, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons.
+}
 
-In addition to these broad theoretical points, we have clarified a number of smaller points brought up by Reviewer 1.
-We have clarified our contrasts of generics from quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations of quantifiers. 
-We are now explicit about our argument from analogy about how states of uncertainty are more fundamental than states of certainty motivates an uncertain threshold (for generics) as being more fundamental a certain, exact threshold (for quantifiers).
-\ndg{that last sentence confuses me.
-also see comment below about learning stuff.
-maybe tone this all down?}
+In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
+We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
+We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainly.
+This point is a very particular one relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}.
+We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but generics are simpler because they lack a fixed threshold).
 
@@
 i think we can add a few comments to the section on relation to conceptual theories of generics about this.
-basically we are not committed to any particular theory of concepts, as long as they are able to yield quantitative feature probabilities.}
-\item acquisition story and evidence of how difficulty with quantifiers comes from pragmatic considerations (Musolino \& Lidz, 2006) \ndg{we could remove this speculation, or town it down.
-we don't really want dig deeply into work on quantifier acquisition here....}
+basically we are not committed to any particular theory of concepts, as long as they are able to yield quantitative feature probabilities.} \mht{i didn't feel completely confident writing about theories of concepts and don't have a sense of ``standard`` citations that would convey succinctly our point.
+can you add this?}
 \end{enumerate}

### 2018-09-26 paper/case1-generics.Rmd
clean up case 1; until rsa model results section

@@
 
-We first investigate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
+We first investigate how the *uncertain threshold* endorsement model predicts actual human endorsements of generic statements.
 We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g.
@@
 
-As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
+As a manipulation check, the first author assigned an \emph{a priori} truth judgment (true/false/indeterminate) to each stimulus item.
 As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
@@
 
-In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
+Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and the gradedness between the extremes.
+We observe gradedness among our thirty examples covering a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
 We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.
@@
 The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
-To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon).
-Ask yourself "is it female?" 
-Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). 
-Now, do you think it lays eggs? 
-Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young.
-That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of.^[
+To get an intuition for the kind of knowledge encoded in this belief distribution, imagine you are walking outside and come across an instance of your favorite kind of animal (e.g., a reindeer). 
+What is the chance it is female?
+Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female reindeer, approximately 50\%). 
+What is the chance that it lay eggs?
+Again, this depends upon the percentage of the category that you believe lays eggs, which then further depends on the particular kind of animal under consideration: If you're thinking of a reindeer, the answer is probably 0\%; if you're thinking of a peregrine falcon, the probability is similar to the being female probability (50%) because female peregrine falcons lay eggs.
+That is, the answer to how many of an arbitrary category is likely to lay eggs is either roughly 50\% or 0\%, depending on the kind of creature you may be thinking of.^[
   The subjective probability may, in fact, be non-zero and small as opposed to 0. 
-  Non-zero probabilities allow for the intuitive possibility of a mammal animal that generally reproduces by giving live birth which in fact lays eggs, potentially explained by some strange generic mutation.
+  Non-zero probabilities allow for the intuitive possibility of a reindeer that, by some terribly improbable set of circumstances such as a genetic mutation, lays eggs.
 ]
 
-This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
-We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and build a structured statistical model to accurately reconstruct the prevalence prior.
+The thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
+This decomposition can be used to measure the prevalence prior for familiar properties $P(p) = \int_{k} P(p \mid k) \diff k$ as a stand-in for a richer intuitive theory that could give rise to prevalence judgments.
 We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
-To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
+To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").^[
+  That is, we implicitly assume for these properties that logical negation tokenizes its own threshold instead of being derived compositionally via bivalent logical negation.
+For related empirical and modeling investigations regarding resolving compositional vs.
+non-compositional negation (in the context of gradable adjectives, e.g., "not happy" vs.
+"unhappy"), see @Tessler2018negant.
+]
 
@@
 Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
-1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure\ \@ref(fig:generics-prior-task)A).
+1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five animal kinds of their own (Figure\ \@ref(fig:generics-prior-task)A).
 A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
-Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure\ \@ref(fig:generics-prior-task)B).
+Participants were asked to fill in each cell with a with the percentage of members of each of the species that had the property (e.g., "50\%"; Figure\ \@ref(fig:generics-prior-task)B).
 Eight property--columns in total appeared in the table.
-
 This whole procedure was repeated two times (two trials).
@@
 
-The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
+The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Worked Examples* section (Figure\ \@ref(fig:simulations)A).
 The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions.
@@
 <!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
-In order to integrate the results of this prior measurement task into our model of endorsement, we must build a statistical model of the prior elicitation data.
+In order to incorporate the uncertainty in our measurement of the prevalence prior into the endorsement model's predictions, we build a Bayesian statistical model of the prior elicitation data.
 We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
@@
 ]
-This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
-The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
+This "null distribution" is potentially present for all features and acts in exactly the same way (i.e., the lack of producing the feature).
+The second distribution represents kinds of animals who *could* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
 The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
@@
 
-We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, and our full endorsement model.
+We can now compute the predictions of our endorsement model. 
+We describe first the behavior of a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, before proceeding to the results of the uncertain threshold endorsement model.
 
@@
 We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
-Referent prevalence alone does okay at predicting these data because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").
+Referent prevalence alone predicts a fair amount of variance because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").
 
@@
 Cue validity indexes the diagnosticity of the feature for a kind, given formally by the probability of a kind given the feature $P(k \mid f)$.
-As discussed in the Computational Model section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
-Cue validity thus is similar to a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution. 
+As discussed in the *Other Theories* section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
+Cue validity thus acts using a *point estimate* of the prevalence prior distribution, a single metric that summarizes the prior distribution. 
 <!-- Comparison to a model based on cue validity thus  -->
@@
 <!-- To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity. -->
-Though the cue validity of a property for a category can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity from different empirical sources [@Cree2006; @Khemlani2012].
+Though the cue validity of a property for a category can be derived from the prevalence prior distribution, previous empirical studies of generics have estimated cue validity from different empirical sources [@Cree2006; @Khemlani2012].
 In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs.
@@
 We found that these two ways of estimating cue validity diverge for a number of key cases (Appendix B).
-Most notably, undiagnostic features (e.g., *is female*), which in theory have a cue validity close to zero, were rated as having intermediate cue validity in the *direct question* paradigm. 
+Most notably, undiagnostic features (e.g., *is female*), which in theory have a cue validity close to zero, were rated as having intermediate cue validity (around 0.5) in the *direct question* paradigm, but not in the *free production* paradigm.
 In response to a direct question such as "There is an animal that is female.
-What is probability that it is a robin?", participants could be responding "I don't know" rather than reporting their intuitive base rate that a random animal would be a robin.
+What is probability that it is a robin?", participants seem to want to respond "I don't know" by placing the slider bar at the midpoint, rather than reporting their intuitive base rate that a random animal would be a robin.
 The free production paradigm did not produce artifacts such as this one, and we chose to use it as the more veridical estimate of cue validity. 
@@
 `r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
-`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
+`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (generic endorsement both $> 0.9$).
 Deviations, however, still remain.
@@
 Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
-Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
+Furthermore, cue validity cannot distinguish "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction); the cue validity can be zero or low for different reasons.
 Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
-A simple metric like cue validity is too blunt to capture these subtleties.
 
@@
 Our underspecified-threshold model considers how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p)$ (Eq.
-\ref{eq:L0}; e.g., the prevalence of laying eggs among other animals) in line with the referent prevalence ($p$ in Eq.
+\ref{eq:L0}; e.g., the prevalence of laying eggs among other animals) in line with the speaker's belief about the referent prevalence ($p$ in Eq.
 \ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
@@
 <!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
-For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt.
+For both the fixed-threshold and full uncertain-threshold endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt.
 1b data), and the endorsement data (Expt.
@@
 The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
-The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
+The endorsement data (Expt. 1a) is model by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
 Predicting the data from both Expt.
@@
 For a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
-We make this the strongest, possible fixed-threshold model by searching for the best possible single, threshold that fits the data.
-Finally, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional extrinsic noise parameter, to allow for random guessing.
-Thus, our fixed-threshold alternative model says that participants make an information-theoretic decision, taking into account the interpreter's prior distribution $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
+We make this the strongest, possible fixed-threshold model by searching for the best possible single threshold that fits the data.
+However, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional extrinsic noise parameter, to allow for random guessing.
+Thus, our fixed-threshold alternative model claims that participants make an information-theoretic decision, taking into account the interpreter's prior distribution on prevalence $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
 This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
@@
 
-Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers context-specific $\theta$'s.
+Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers property-specific $\theta$'s.
 We use the same Bayesian data analysis approach; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).

### 2018-09-26 paper/case1-generics.Rmd
finish edits with case 1

@@
 \ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
-There are several substantive components to this hypothesis: (a) context in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
+As described in the *Intermediate Summary*, there are several substantive components to this hypothesis: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
 not uttering it, and (c) vagueness in the semantics of a generalization.
@@
 1a).
+Predicting the data from both Expt.
+1a and 1b by a single, joint-inference model makes our assumptions explicit about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
 Empirically elicited referent prevalence and prevalence prior data (Expt.
@@
 The endorsement data (Expt. 1a) is model by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
-Predicting the data from both Expt.
-1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
 To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.
@@
 
-For a strong alternative model, we lesion our uncertain threshold model so that it has a fixed threshold $\theta$.
+For a strong alternative model, we lesion the uncertain threshold model so that it has a fixed threshold $\theta$.
 We make this the strongest, possible fixed-threshold model by searching for the best possible single threshold that fits the data.
 However, a fixed-threshold model will have to accommodate responses that are literally inconsistent with the threshold (i.e., a participant endorsing a generic when the referent prevalence is less than $\theta$); we thus outfit this model with an additional extrinsic noise parameter, to allow for random guessing.
-Thus, our fixed-threshold alternative model claims that participants make an information-theoretic decision, taking into account the interpreter's prior distribution on prevalence $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
+Thus, the fixed-threshold alternative model claims that participants make an information-theoretic decision, taking into account the interpreter's prior distribution on prevalence $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
 This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
@@
 
-To evaluate the fixed-threshold model, we examine model predictions as well as the posterior distribution over latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data.
-The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
-`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
-`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
-The inferred optimality parameter in Eq.
-\ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
-
 ```{r fixed-threshold-examples}
@@
 
-We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
+To evaluate the fixed-threshold model, we examine model predictions as well as the posterior distribution over latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data.
+The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
+`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
+`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
+The inferred optimality parameter in Eq.
+\ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
 Figure\ \@ref(fig:generics-endorsement-figure)B (top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
@@
 `r round(tigers.eat.people[[1,"prediction_ci_upper"]], 2)`]) as good a statement as "Peacocks have beautiful feathers" (`r round(peacocks.feathers[[1,"prediction_mean"]],2)` [`r round(peacocks.feathers[[1,"prediction_ci_lower"]], 2)`,
-`r round(peacocks.feathers[[1,"prediction_ci_upper"]], 2)`]), though participants seem to give a substantially weaker endorsement of the former ("Tigers eat people" = `r round(tigers.eat.people[[1,"MAP_h"]],2)` [`r round(tigers.eat.people[[1,"low"]], 2)`,
+`r round(peacocks.feathers[[1,"prediction_ci_upper"]], 2)`]), though participants give a substantially weaker endorsement of the former ("Tigers eat people" = `r round(tigers.eat.people[[1,"MAP_h"]],2)` [`r round(tigers.eat.people[[1,"low"]], 2)`,
 `r round(tigers.eat.people[[1,"high"]], 2)`]; "Peacocks have beautiful feathers" = `r round(peacocks.feathers[[1,"MAP_h"]],2)` [`r round(peacocks.feathers[[1,"low"]], 2)`,
@@
 `r round(mosquitos.attack.swimmers[[1,"high"]], 2)`]).
-This alternative model is unable to make these fine-grained distinctions because it must use the same semantic threshold in all contexts.
+The fixed-threshold alternative model is unable to make these fine-grained distinctions because it uses the same semantic threshold in all contexts.
 
@@
 Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers property-specific $\theta$'s.
-We use the same Bayesian data analysis approach; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
+We use the same Bayesian data analysis approach, dropping the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
 Thus, this model has two fewer parameters than the fixed-threshold model above.
@@
 We first examine the posterior predictive distribution on the prevalence prior and referent prevalence data to ensure that the joint-inference model does not distort these parameters at the service of predicting the endorsement data (e.g., such a distortion could manifest by the joint-inference model inferring that 100% of mosquitos carry malaria in order to predict that "Mosquitos carry malaria" is a good utterance).
-This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters (e.g., that not all mosquitos carry malaria).
-Importantly, the model captures the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when the Bayesian data analysis model only included these data and their associated model ($r_{\text{prevalence prior parameters}}^2(`r length(m.gen.endorse.refprev.parameters[,"Parameter"])`) = `r r2.refprev.distortion`$; $r_{\text{referent prevalence parameters}}^2(`r length(m.gen.endorse.priors.parameters[,"Parameter"])`) = `r r2.prevprior.distortion`$; see Appendix D, Figure 14).
+This is an important step in model validation because it tells whether the model's predictions are derived from intuitively plausible values of the parameters (e.g., that not all mosquitos carry malaria).
+Importantly, the joint-inference model captures the prior elicitation data (e.g., the probability of carry malaria among various species) and the referent prevalence data (e.g., the prevalence of carrying malaria among mosquitos) as well as it did when we analyzed these data in isolation (without conditioning on the endorsement data) ($r_{\text{prevalence prior parameters}}^2(`r length(m.gen.endorse.refprev.parameters[,"Parameter"])`) = `r r2.refprev.distortion`$; $r_{\text{referent prevalence parameters}}^2(`r length(m.gen.endorse.priors.parameters[,"Parameter"])`) = `r r2.prevprior.distortion`$; see Appendix D, Figure 14).
 This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).
@@
 
-As we see in Figure\ \@ref(fig:generics-endorsement-figure)B (top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
-To gain some intuition for why the model makes the predictions that it does, we can examine the relevant model components that give rise to these predictions (Figure \ref{fig:generics-endorsement-figure}C).
-Recall that the prevalence prior (grey distribution) is also the interpreter model's posterior upon hearing the null, or silent, utterance, and that the endorsement model decides whether to produce the generic utterance or remain silent given some referent prevalence (blue distribution).
-The interpreter model's prevalence posterior upon hearing the generic utterance (red distribution) differs depending on the property being predicated (facets).
-
-The endorsement model decides if the generic utterance conveys information that would bring the interpreter's distribution more in line with the endorsement model's referent prevalence. 
+As we see in Figure\ \@ref(fig:generics-endorsement-figure)B (top right subplot), the uncertain threshold endorsement model explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+Examining the relevant model components that give rise to these predictions further reveals the intuition for why the model makes the predictions that it does (Figure \ref{fig:generics-endorsement-figure}C).
+Because the endorsement model's alternative utterance is a null or silent utterance, the prevalence prior distributions is exactly what the interpreter model would believe if the speaker does not produce the generic.
+The endorsement model then decides whether maintaining the listener's prior or updating it with the uncertain threshold semantics would better get the listener to guess the correct prevalence for the category (correct in the mind of the speaker).
 The model rates "Robins lay eggs" as a good utterance because the prevalence posterior implied by the generalization is similar to the referent prevalence.^[
@@
 ]
-The prevalence posterior for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad, endorsement around 0.5.
+The prevalence posterior for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad, endorsement around 0.5, which is what is approximately the proportion of participants who endorse the statement.
 "Mosquitos carry malaria" is an interesting case because the prevalence prior has high variance (i.e., participants are highly uncertain about the prevalence of carrying malaria among categories).
@@
 Generics have been studied extensively in the cognitive and developmental psychological literatures and have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
-Heretofore, no formal model has been able to pass the most basic empirical test for generics: knowing when they are true and false.
+Heretofore, no models have been articulated with enough precision to make quantitative predictions about endorsement decisions, deciding whether a statement is true or false.
 <!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->

### 2018-10-01 paper/case1-generics.Rmd
clean up figures, table of exampels

@@
     #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    stat_ecdf(size = 1.3)+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    stat_ecdf(size = 0.7)+
+    scale_color_manual(values = c("black", "#d7191c", "#2b83ba"))+
+    scale_alpha_manual(values = c(1, 0.4, 0))+
     facet_wrap(~Property, nrow = 2)+
-    scale_linetype_manual(values = c(1, 2, 3))+
+    scale_linetype_manual(values = c(2, 1, 3))+
     scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
@@
 
-```{r}
+```{r regresion results}
 load("cached_results/case1_regressionResults.RData") # d.gen.endorse.regression.prevalence, d.gen.endorse.regression.prevalence.cuevalidity, d.gen.endorse.regression,
@@
 load("cached_results/case1_modelPosteriors.RData")
+#load("cached_results/case1_modelPosteriors_moreFlexiblePrior.RData")
 #d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt
@@
 
-```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
+```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5, cache=F}
 
@@
              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0.3, 0.3, 0.47, 0.05, 0.6),
-            y = c(0.45, 0.5, 0.45, 0.5, 0.26))
+             x = c(0, 0.3, 0, 0, 0.3),
+            y = c(3.8, 4, 4, 4, 4))
 
-generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
-                                      aes( x = value, fill = Parameter, 
-                 color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
+generics.endorsement.insets <- ggplot( gen.inset.distributions.refactored %>%
+         mutate(Parameter = factor(Parameter, levels = c("state_Prior", "state_Posterior", "speakerBeliefs"),
+                                   labels = c("Null interpretation\n(Prevalence prior)", "Generic interpretation\n(model)", 
+                                              "Referent prevalence")),
+                property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
+       aes(x = state, y = Parameter, group = Parameter ))+
+  scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
+  scale_x_continuous(expand = c(0, 0), limits = c(0, 1), breaks = c(0, 1))  +    # for both axes to remove unneeded padding
   facet_wrap(~property, nrow = 1)+
-  geom_label_repel(data = category.text.labels,
+  geom_text_repel(data = category.text.labels,
                   aes(label = category, x = x , y = y),
-                  inherit.aes = F, color = "#2b83ba")+
+                  inherit.aes = F)+
     #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
     #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+  ggridges::geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
@@
     scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
     xlab("Prevalence") +
-    ylab("Scaled probability density")+
+    ylab("")+
     theme(legend.position = "bottom", legend.title = element_blank())
@@
 1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
-
 fig.gen.endorse.data <- generics.endorsement.spectrum +

### 2018-10-01 paper/case2-habituals.Rmd
clean up figures, table of exampels

@@
   geom_label_repel(segment.alpha = 1,label.size = 0.25,
-                   force = 10, size = 2, color = 'black')+
+                   force = 10, size = 4, color = 'black')+
 
@@
   #ylab("Empirical means")+
-  theme(legend.position = c(0.83, 0.16))+
+  theme(legend.position = c(0.83, 0.16),
+        legend.text=element_text(size=16))+
   scale_y_continuous(
@@
 
-```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt.
+```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.7, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt.
 2a).
@@
 In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted.
-Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache = F}
-cowplot::plot_grid(
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache=F}
+plot_grid(
   figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
   figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
-  labels = c("A", "B"), #nrow = 1,
+  labels = c("A", "B"), nrow = 2,
   align = 'h',
-  rel_widths = c(1, 3)
+  rel_heights = c(1, 1)
   )
@@
 
-```{r habituals-endorsement-bars, fig.width = 8}
+```{r habituals-endorsement-bars, fig.width = 8,cache=F}
 habituals.endorsement.bars <- ggplot(md.hab.long %>%
@@
   theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45),
+        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 10),
         legend.position = "right")
@@
 
-```{r habitual-endorsment-scatters}
+```{r habitual-endorsment-scatters, cache=F}
 habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
@@
   facet_wrap(~src, ncol = 2, strip.position = "top")+
-  guides(fill = guide_colorbar(ticks = F, title = "Time interval"))+
+  guides(fill = guide_colorbar(ticks = T, title = "Time interval"))+
   theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
-        #legend.direction = 'horizontal',
+        legend.direction = 'horizontal',
         #legend.position = c(0.025,0.975),
         legend.position ='bottom',
-        legend.text = element_text(angle = 45)
+        legend.text = element_text(angle = 45, hjust = 0.5, vjust = 0.5)
         #legend.justification = c(1,1)
@@
 
-```{r habituals-model-insets, fig.width = 8, cache = T}
+```{r habituals-model-insets, fig.width = 8, cache=F}
 habituals.endorsement.insets <- hab.listener.predictions %>% 
-    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
-                                                  "state_Posterior"
+    mutate(Parameter = factor(Parameter, levels = c(                                                  "state_Posterior",
+"state_Prior"
                                                   ),
-                            labels = c("Prevalence Prior",
-                                       "Posterior given Habitual")),
+                            labels = c(
+                                       "Habitual Interpretation",
+                                       "Prevalence Prior")),
          action = factor(action, levels = c( 
@@
                               ) %>%
-  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
-  facet_wrap(~action, nrow = 2)+
+  ggplot(., aes( x = value, group = Parameter, y = Parameter ))+
+  #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+  ggridges::geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
+  facet_wrap(~action, nrow = 1)+
   # geom_text_repel(data = category.text.labels,
@@
   #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+  #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
   xlab("Frequency (log scale)") +
-  ylab("Scaled probability density")+
+  ylab("")+
   theme(legend.position = c(0.9, 0), 
         legend.title = element_blank(),
-        axis.text.x = element_text(angle = 90, vjust = 1))+
+        axis.text.x = element_text(angle = 90, vjust = 1),
+        axis.title.y =  element_blank())+
         #axis.title.y = element_text(hjust = 1))+
@@
 
-```{r habituals-endorsement-figure, fig.width = 13, fig.asp=0.7, fig.cap="Endorsing generalizations about events.
+```{r habituals-endorsement-figure, fig.width = 16, fig.asp=0.65, fig.cap="Endorsing generalizations about events.
 A: Endorsements for nine events given different frequencies of action by human participants and four models.
@@
 These distributions are inferred using both data sources from Expts.
-2a and 2b.", out.width = "\\textwidth", fig.pos = "!h", cache = F}
-
+2a and 2b.", out.width = "\\textwidth", fig.pos = "!h", cache=F}
 #hab.legend <- get_legend(habituals.endorsement.models)
 fig.hab.endorse.bars <- habituals.endorsement.bars +
-  theme(plot.margin = unit(c(6,6,6,6), "pt")) #+ ggtitle("prevalence priors")
+  theme(plot.margin = unit(c(6,0,6,12), "pt")) #+ ggtitle("prevalence priors")
 fig.hab.endorse.scatters <- habituals.endorsement.models +
-  theme(plot.margin = unit(c(6,6,6,6), "pt")) # + theme(legend.position="none") #+ ylab("")
+  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
 fig.hab.endorse.priors <- habituals.endorsement.insets +
-  theme(plot.margin = unit(c(16,36,16,36), "pt"))
+  theme(plot.margin = unit(c(16,0,0,0), "pt"))
 
 plot_grid(
-    plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters, nrow = 1, labels = c("A", "B"),
+    plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters, nrow = 1,
+              labels = c("A", "B"),
               rel_widths = c(2, 1)),
@@
                         #align = 'v',
-                            rel_heights = c(1.7, 1))
+                            rel_heights = c(1.6, 1))
 
@@
 
-```{r habituals-predictive-rsa, cache = T, eval=T}
+```{r habituals-predictive-rsa, eval=T}
 n_chains <- 3
@@
                      labels= c("Human data","regression_pastfreq", 
-                                "Uncertain semantics\n(Past)", "Linear model\n(Predictive frequency)","Uncertain semantics\n(Predictive)"))) %>%
+                                "Uncertain semantics\n(Past frequency)", "Linear model\n(Predictive frequency)","Uncertain semantics\n(Predictive frequency)"))) %>%
   filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
@@
   facet_grid(.~src)+
-  theme(legend.position = "right")
+  theme(legend.position = "top")
 ```
@@
 B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline).
-C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7,out.width = "\\textwidth", fig.pos = "!h", cache=F}
+C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7, out.width = "\\textwidth", fig.pos = "!h", cache=F}
 plot_grid(
@@
 habituals.endorsement.pred.scatters +
-      theme(plot.margin = unit(c(0,0,12,12), "pt")),
+       theme(plot.margin = unit(c(0,0,0,0), "pt")),
      labels = c("B", "C"),

### 2018-10-01 paper/comgen-paper.Rmd
clean up figures, table of exampels

@@
                       echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
-
 ```
 
-```{r libraries, cache = F}
+```{r libraries, cache=F}
 library(papaja)
@@
 worked.examples <- data.frame(
-  example = c("1. Dogs bark",
+  Example = c("1. Dogs bark",
               "2. Kangaroos have spots",
@@
               "9. Elephants live in Africa and Asia"),
-  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "~50%/50%"),
+  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "50%/50%"),
   `intuitive truth value` = c(
@@
     "Most sharks don't eat people",
-    "Only female (50%) of robins lay eggs",
-    "Roughly same number of robins that lay eggs are female",
+    "True, even though only female robins (50%) lay eggs",
+    "Not true, but same number that lay eggs (50%)",
     "Very few mosquitos actually carry malaria",
-    "Hypothetically, there has never been any mail from Antarcita",
-    "Even if 100% have even social security numbers",
+    "True even if there has never been any mail from Antarcita",
+    "False even if 100% have even social security numbers",
     "Impossible for most to live in Africa and most to live in Asia"
   )
-)
-
-examples <- xtable::xtable(worked.examples, 
+) %>%
+  rename("Referent prevalence" = referent.prevalence,
+         "Intuitive truth value" = intuitive.truth.value,
+         "Issue" = potential.issue)
+
+worked.examples.tab <- xtable::xtable(worked.examples, 
                        caption = "Example generalizations that a theory of generics should correctly predict.", 
-                       align=c('p{1.5in}', 'p{1.2in}| ',' |p{1in}|','p{1in}|','p{2in} |'))
+                       align=c('p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))
 
@@
 
-print(examples, 
+print(worked.examples.tab, 
       type="latex", 
@@
        #table.placement = "h", 
-      tabular.environment = "longtable",
-      hline.after=-1:nrow(examples),
+      #tabular.environment = "longtable",
+      hline.after=-1:nrow(worked.examples.tab),
       size="\\fontsize{9pt}{10pt}\\selectfont", 

### 2018-10-01 paper/case1-generics.Rmd
tweaks throughout, clean up figures

@@
              category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
-             x = c(0, 0.3, 0, 0, 0.3),
-            y = c(3.8, 4, 4, 4, 4))
+             x = c(0.5, 0.3, 0, 0, 0.3),
+            y = c(1.5, 1.5, 1.5, 1.5, 1.5))
 
 generics.endorsement.insets <- ggplot( gen.inset.distributions.refactored %>%
-         mutate(Parameter = factor(Parameter, levels = c("state_Prior", "state_Posterior", "speakerBeliefs"),
-                                   labels = c("Null interpretation\n(Prevalence prior)", "Generic interpretation\n(model)", 
-                                              "Referent prevalence")),
+         mutate(Parameter = factor(Parameter, levels = c("speakerBeliefs", "state_Posterior", "state_Prior"),
+                                   labels = c(
+                                              "Referent prevalence\n(Endorsement model input)",
+                                             "Generic interpretation\n(Interpretation model output)", 
+                                             "Prevalence prior\n(Null interpretation)")),
                 property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
-       aes(x = state, y = Parameter, group = Parameter ))+
+       aes(x = state, y = Parameter, group = Parameter, color = Parameter))+
   scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
@@
   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
-    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_color_manual(values = c("#2b83ba", "#636363","#636363"))+
     scale_alpha_manual(values = c(0.6, 0.4, 0))+
@@
     ylab("")+
-    theme(legend.position = "bottom", legend.title = element_blank())
+    theme(legend.position = "bottom", legend.title = element_blank())+
+  guides(color = F)
 ```

### 2018-10-01 paper/comgen-paper.Rmd
tweaks throughout, clean up figures

@@
 Finally, the meanings of linguistic expressions manifest in their capacity to convey information from speaker to hearer [@Grice1975; @Clark1996; @Levinson1995].
-Thus, the final ingredient to our model is *context* (Ingredient 3), which must be minimally formalized as a listener's prior knowledge about the property $P(p)$ and which we describe in more detail below.
+Thus, the final ingredient to our model is *context* (Ingredient 3), which must be minimally formalized as a listener's prior knowledge about the property $P(p)$ and which we describe in the *Worked Examples* section below.
 
@@
 
+With these ingredients, the literal interpretation model (Eq. \ref{eq:L0}) computes a posterior interpretation distribution on prevalence by considering different possible thresholds $\theta$.
+Figure\ \@ref(fig:uniformPriorSimulation) shows the model behavior assuming a uniform prevalence prior $P(p)$, perhaps representing a purely abstract property for which an interpreter has no substantive prior knowledge.
+If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance.
+As the threshold decreases, more and more prevalence levels become be compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
+The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution on prevalence that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
+This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise prevalence.
+
 <!-- The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice.  -->
@@
 In this paper, we are interested in explaining truth judgments (e.g., "Robins lay eggs" is intuitively true; "Robins are female" is not).
-If the interpreter is a kind of simple listener model, then we can ask whether an agent would bother to produce the generalization to this listener.
-The endorsement model then acts as a kind of speaker, reasoning about how the interpreter model (the listener) would understand the utterance.
-This kind of model formalizes the basic aspects of communicative reasoning and is the simplest instantiation of a Rational Speech Act model [@Frank2012; @Goodman2016].
-
-We interpret the endorsement task (e.g., *true* vs.
+We model the endorsement task (e.g., *true* vs.
 *false*; *agree* vs.
-*disagree*) as supplying two alternatives to the endorsement model: produce the generalization vs.
+*disagree*) as a *speaker decision* about whether or not to produce the generalization to a naive listener; thus, the endorsement model has two alternative utterances: produce the generalization vs.
 a null alternative [@Franke2014cogsci; @Degen2014].
@@
 ]
-
-The utterance encoding a generalization updates the interpreter model's beliefs about the prevalence of a feature in the category being referred to, which we call the *referent prevalence*. 
-The endorsement model has a particular referent prevalence in mind and decides if the generalization or the null alternative is better at conveying that to the interpreter.^[
+This kind of speaker model defined in terms of a listener model formalizes the basic aspects of communicative reasoning and is the simplest instantiation of a Rational Speech Act model [@Frank2012; @Goodman2016].
+
+<!-- If the interpreter is a kind of simple listener model, then we can ask whether an agent would bother to produce the generalization to this listener. -->
+<!-- The endorsement model then acts as a kind of speaker, reasoning about how the interpreter model (the listener) would understand the utterance. -->
+
+The endorsement model (called $S$ for speaker) decides whether or not to produce the generalization by reasoning about how the listener model ($L$; Eq. \ref{eq:L0}) would interpret it:
+\begin{equation}
+S(u \mid p) \propto (\int_{\theta} L(p, \theta \mid u)  \diff \theta)^\lambda
+\label{eq:S1}
+\end{equation}
+
+The goal of the endorsement model is to align the listener's beliefs about prevalence (given by the *prevalence prior*) with the speaker's beliefs about the prevalence of the feature in the category being referred to, which we call the *referent prevalence* ($p$; e.g., that 50% of robins lay eggs).
+^[
   A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
@@
 ]
-This endorsement model (called $S$ for speaker) does so by reasoning about the interpretation model $L$: 
-\begin{equation}
-S(u \mid p) \propto (\int_{\theta} L(p, \theta \mid u)  \diff \theta)^\lambda
-\label{eq:S1}
-\end{equation}
-
-The informational content of the generalization is the prevalence in the referent category $p$.
-The semantic threshold $\theta$ is a nuisance parameter then; the endorsement model integrates over the interpreter's posterior beliefs about $\theta$.
-Finally, because the endorsement model must decide whether or not to endorse the generalization, we assume this model is an approximately rational decision-maker, with degree of rationality given by $\lambda$.
+Thus, the communication-relevant content of the generalization is the prevalence in the referent category $p$.
+The semantic threshold $\theta$ is necessary for establishing the precise truth conditions (used in Eq. \ref{eq:L0}) but is otherwise a nuisance parameter, which the endorsement model integrates out.
+Finally, Eq. \ref{eq:S1} models an information-theoretic speaker's decision, which we assume is approximately rational, with degree of rationality given by $\lambda$.
 This exponentiation step acts as a soft-max function on $S$'s posterior beliefs of which utterance is better.
@@
 
+Given that the speaker only has two options (i.e., produce the generalization utterance or stay silent), the endorsement decision comes down to whether or not the *referent prevalence* is more likely under the prevalence prior distribution $P(p)$ or the listener interpretation distribution given by Eq.
+\ref{eq:L0} (Figure\ \@ref(fig:uniformPriorSimulation)C).
 Our endorsement model (Eq.
@@
 In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
-In the next section, we work through different examples from the linguistics literature, describing how the prevalence prior and other relevant model components for each.
+In the next section, we work through different examples from the linguistics literature, describing the prevalence prior and other relevant model components for each.
 
@@
 
-### Model behavior
+### Worked examples
 
@@
 
-<!-- We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
--->
-First, we examine the model behavior assuming a uniform prevalence prior $P(p)$, representing a purely abstract property for which an interpreter has no substantive prior knowledge (Figure\ \@ref(fig:uniformPriorSimulation))
-The literal interpretation model (Eq. \ref{eq:L0}) computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
-If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance (Figure\ \@ref(fig:uniformPriorSimulation)A, right).
-As the threshold decreases, more and more prevalence levels become be compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
-Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior interpretation distribution that favors higher prevalence levels because they are consistent with more thresholds (Figure\ \@ref(fig:uniformPriorSimulation)B).
-The endorsement model then inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases (Figure\ \@ref(fig:uniformPriorSimulation)C).
-
-<!-- The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question. -->
-<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
-
-The uncertain-threshold model's interpretations are highly sensitive to background knowledge.
-Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
-This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence. 
+The uncertain threshold model's interpretations are highly sensitive to background knowledge, formalized in simplest terms in terms of a *prevalence prior*.
 Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories (Figure\ \@ref(fig:simulations)).
-Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
+For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
 Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
@@
 Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
+Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
+This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence. 
+We explore the model's ability to account for intuitive truth judgments for different examples that have been historically challenging for prevalence-based approaches.
+
+<!-- We simulate how the prevalence priors change the literal interpretation and how they and the referent prevalence impact endorsement using schematic parameter values based on intuition from a few examples in the literature on generic language.
+-->
+
+<!-- The literal interpretation of a generalization (Eq. \ref{eq:L0}) reflects a balance between an uncertain threshold and shared background knowledge about the feature in question. -->
+<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->
 
@@
 
-### Worked examples
-
-We are now ready to examine the endorsement model's predictions for different examples.
-These examples have historically proved challenging for prevalence-based approaches. 
-We describe how the uncertain-threshold model treats each in turn.
-
 **1. Dogs bark.**
 
-Often the first observation with generics is that they appear like *universal* quantifiers (e.g., "All") but permit exceptions. 
+Often the first observation with generics is that they appear to behave like *universal* quantifiers (e.g., "All") that permit exceptions.
 That is, not all dogs bark, but still *Dogs bark* is true.
@@
 Rather, listeners have uncertainty about the threshold *a priori* which leads to graded interpretations (e.g., *Dogs bark* meaning *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
-The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (shown with arrow in Figure\ \@ref(fig:simulations) row 2).
+The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (*referent prevalence* of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
 
@@
 
-A second observation regarding generics is that they cannot be so lenient so to always convey *existential* quantification (e.g., "Some").
+A second observation regarding generics is that their truth conditions cannot be so lenient so to always convey *existential* quantification (e.g., "Some").
 Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel the generalization "Kangaroos have spots" is too strong to assert.
 The model exhibits this same restraint, predicting a very low endorsement probability for this generic statement (Figure\ \@ref(fig:simulations); column 2).
-The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" is like "Dogs bark": it means *almost all* kangaroos have spots. 
+The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean *almost all* kangaroos have spots.
 The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would mislead the listener.
@@
 
-A similar logic can be applied to this example, which is the converse of the affirmative generalization "Sharks eat people", initially introduced by @Leslie2007. 
-Here, however, the prevalence of the feature for the referent category---the number of sharks that don't eat people---is very high: Almost all sharks don't eat people.
+A similar logic can be applied to this example, which is the converse of the affirmative generalization "Sharks eat people", which is assumed true despite the low actual number of incidents involving sharks eating people [@Leslie2007].
+The referent prevalence---the number of sharks that don't eat people---is thus very high: Almost all sharks don't eat people.
 Yet, intuitively, the generalization is again misleading. 
 Because for almost all animal categories, almost members of those categories don't eat people (i.e., the prevalence of the feature is almost 100% for all categories because very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people, which is too strong.
-It is interesting to note that the model is less certain of its decision, predicting an endorsement probability around 40%.
+It is interesting to note that because of the high referent-prevalence, the model is less certain of its decision, predicting an endorsement probability around 40%.
 We will test this quantitative prediction in one of our experiments.
@@
 Interestingly, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes 50% have the property.^[
-  This behavior might suggest a future area for model revision. 
+  This behavior might suggest a potential area for model revision. 
   Intuitively, "Xs are female" should mean "All Xs are female".
@@
 
-Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are malaria-free.
+Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are actually malaria-free.
 The uncertain-threshold model comes to the same conclusion---endorsing a generic when the referent prevalence is very low---because the listener interpretation distribution would be more aligned with the referent prevalence than the prior.
@@
 This example also highlights that the construct of *cue validity*---the probability of the feature given the category e.g., $P({is a mosquito} \mid \text{carries malaria})$---plays a role in our model.
-We return to this relationship in the General Discussion, and provide a precise mathematical derivation of the relationship between the prevalence prior and cue validity in Appendix A.
+We return to this relationship in the next section, and provide a precise mathematical derivation of the relationship between the prevalence prior and cue validity in Appendix A.
 

### 2018-10-08 paper/case1-generics.Rmd
fix rendering

@@
                 property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
-       aes(x = state, y = Parameter, group = Parameter, color = Parameter))+
+       aes(x = value, y = Parameter, group = Parameter, color = Parameter))+
   scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
@@
 
-plot_grid(fig.gen.endorse.toprow,
+cowplot::plot_grid(fig.gen.endorse.toprow,
           fig.gen.endorse.priors,

### 2018-10-08 analysis/case1-generics.Rmd
update model results and analyses

@@
 # this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
-
 d.gen.endorse.priors <- read.csv(paste(project.path, 
@@
   )
+
 priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
@@
   }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
+
 '
@@
 '
-
 ```
@@
 
-n_chains <- 2
-n_samples <- 60000
+n_chains <- 4
+n_samples <- 100000
 burn <- n_samples / 2
-lg <- 10
+lg <- 20
 
@@
 #   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
-}
+
+}
+
 # 
@@
 ## MODEL RESULTS
-load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))
+#load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))
 
@@
 #save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
-#head(prevData)
-#n_samples
+
+load("../analysis/generics-priors-posteriorPredictives.Rdata")
 ```
@@
 
-```{r}
+```{r example generics}
 example.generics.properties <- c("dont eat people", 
@@
   theme(strip.text.y = element_text(angle = 0))
+
 ```
@@
 
+```{r generic-model-insets2, fig.width = 4.75, fig.height = 1.5}
+load('../analysis/generics-priors-posteriorPredictives.Rdata')
+lower_bins <-seq(0, 0.975, 0.025)
+upper_bins <- seq(0.025, 1, 0.025)
+mid_bins <- (upper_bins - lower_bins)/2 + lower_bins
+
+round_to_bin <- function(x){
+  index <- if (x==0){ 1 } else if (x ==1){ length(mid_bins)} else{
+    x <= upper_bins & x > lower_bins
+  }
+  #if (sum(index) > 1) { print (x) }
+  return (mid_bins[index])
+}
+
+m.gen.endorse.priors.binned.i <- m.gen.endorse.priors.posteriorPredictive %>% 
+  filter(src == "Data") %>%
+  #group_by(property) %>%
+  #sample_n(28, replace = TRUE) %>%
+  #gather(category, response, -workerid, -property) %>%
+  rowwise() %>%
+  mutate(binned_response = round_to_bin(prevalence)) %>%
+  group_by(Property, binned_response) %>%
+  count() %>%
+  ungroup() %>%
+  spread(binned_response, n)
+
+m.gen.endorse.priors.binned.i[is.na(m.gen.endorse.priors.binned.i)] <- 0
+
+m.gen.endorse.priors.binned <- m.gen.endorse.priors.binned.i %>%
+  gather(state, n, -Property) %>%
+  group_by(Property) %>%
+  mutate(prop = (n+1) / sum(n + 1),
+       prop = round(prop, 5))
+
+rsaHelpers2 <- '
+
+var roundTo3 = function(x){
+  return Math.round(x * 10000) / 10000
+}
+
+var probability = function(Dist, x) {
+    return Math.exp(Dist.score(x));
+}
+var targetUtterance = "generic";
+
+var round = function(x){
+  return Math.round(x*1000)/1000
+}
+var utterancePrior = Infer({model: function(){
+  return uniformDraw([targetUtterance,"silence"])
+}});
+
+var meaning = function(utt,state, theta) {
+  return utt=="generic"? state > theta :
+         utt=="generic is false"? state<=theta :
+         utt=="silence"? true :
+         utt=="some"? state>0.01:
+         utt=="most"? state> 0.5:
+         utt=="all"? state >= 0.99:
+         true
+}
+
+var bins = _.map(data.prior, "state");
+
+var thetaBins = map2(function(b1, b2){
+  return roundTo3((b2-b1)/2 + b1);
+}, bins.slice(0, bins.length-1), bins.slice(1))
+
+var priorProbs =  _.map(data.prior, "prop");
+
+var thetaPrior = Infer({model: function(){
+ return uniformDraw(thetaBins)
+}});
+
+var uncertainThresholdInterpreter = Infer({model: function(){
+   var state = categorical({vs: bins, ps: priorProbs})
+   factor( Math.log(state) )
+    return {
+      state: state, 
+  }
+  }, method: "enumerate"})
+
+var prior = Infer({model: function(){
+   var state = categorical({vs: bins, ps: priorProbs})
+    return {
+      state: state, 
+  }
+  }, method: "enumerate"})
+
+var returnVal = {uncertainThresholdInterpreter, prior}
+returnVal
+'
+
+properties <- unique(m.gen.endorse.priors.binned$Property)
+gen.listener.predictions <- data.frame()
+for (p in unique(m.gen.endorse.priors.binned$Property)){
+
+  priorProbs = m.gen.endorse.priors.binned %>% 
+    filter(Property == p) %>%
+    ungroup() %>%
+    select(state, prop) %>%
+    mutate(state = as.numeric(state))
+
+  wp.rs <- webppl(
+    program_code = rsaHelpers2, 
+    data = list(prior = priorProbs, 
+                utt = "generic") ,
+    data_var = "data"
+    )
+  wp.rs.generic <- get_samples(data.frame(wp.rs$uncertainThresholdInterpreter) %>%
+                                 rename(prob = probs), 10000)
+  wp.rs.prior <- get_samples(data.frame(wp.rs$prior) %>%
+                                 rename(prob = probs), 10000)
+
+  gen.listener.predictions <- bind_rows(
+   gen.listener.predictions, 
+    wp.rs.prior  %>% mutate(property = p, Parameter = "state_Prior"),
+    wp.rs.generic  %>% mutate(property = p, Parameter = "state_Posterior")
+   )
+}
+
+example.generics.properties
+
+example.generics <- c("Tigers dont eat people", 
+                      "Mosquitos carry malaria", 
+                      "Robins lay eggs", 
+                      "Robins are female",
+                      "Leopards have spots")
+
+gen.inset.distributions <- bind_rows(
+  gen.listener.predictions %>%
+    mutate(category = NA),
+  d.gen.endorse.priors %>% 
+    mutate(Sentence = paste(Category, Property)) %>%
+    filter(Sentence %in% example.generics) %>%
+    select(prevalence, Property, Category) %>%
+    rename(state = prevalence, property = Property, category = Category) %>%
+    mutate(Parameter = "speakerBeliefs",
+           state = state / 100)
+)
+
+category.text.labels <- data.frame(property = c("dont eat people", 
+                      "carry malaria", "lay eggs",  "are female", "have spots"),
+             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
+             x = c(0, 0.3, 0, 0, 0.3),
+            y = c(3.8, 4, 4, 4, 4))
+
+library(ggridges)
+gen.inset.distributions.refactored <- gen.inset.distributions %>% filter(property %in% category.text.labels$property)
+
+#save(gen.inset.distributions.refactored)
+ggplot( gen.inset.distributions.refactored %>%
+         mutate(Parameter = factor(Parameter, levels = c("state_Prior", "state_Posterior", "speakerBeliefs"),
+                                   labels = c("Null interpretation\n(Prevalence prior)", "Generic interpretation\n(model)", 
+                                              "Referent prevalence")),
+                property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
+       aes(x = state, y = Parameter, group = Parameter ))+
+  scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
+  scale_x_continuous(expand = c(0, 0), limits = c(0, 1), breaks = c(0, 1))  +    # for both axes to remove unneeded padding
+  facet_wrap(~property, nrow = 1)+
+  geom_text_repel(data = category.text.labels,
+                  aes(label = category, x = x , y = y),
+                  inherit.aes = F)+
+    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
+  geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
+  scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
+    scale_alpha_manual(values = c(0.6, 0.4, 0))+
+    #scale_linetype_manual(values = c(3, 4, 2, 1))+
+    scale_linetype_manual(values = c(3, 4, 1))+
+    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    xlab("Prevalence") +
+    ylab("")+
+    theme(legend.position = "bottom", legend.title = element_blank())
+
+```
+
 ```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
-
 # m.gen.fullmodel.prior.parameters <- m.samp %>%
@@
 
- l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model.3comp, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
- l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model.3comp, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
+ l0.rs.posterior <- webppl(paste(rsaHelpers, 
+                                 uncertain.threshold.model.3comp, 
+                                 uncertain.threshold.call, sep = '\n'), 
+                           data = inputData, data_var = "data")
+
+ l0.rs.prior <- webppl(paste(rsaHelpers, 
+                             no.utterance.model.3comp, 
+                             no.utterance.call, sep = '\n'), 
+                       data = inputData, data_var = "data")
 
@@
 
-m.gen.fullmodel.target.prevalence <- m.samp %>%
-  filter(type == "targetPrevalence") %>%
-  group_by(param, property, category) %>%
-  summarize(MAP = estimate_mode(val),
-            cred_upper = hdi_upper(val),
-            cred_lower = hdi_lower(val))
-
-m.gen.speakerBeliefs <- m.samp %>%
+# m.gen.fullmodel.target.prevalence <- m.samp %>%
+#   filter(type == "targetPrevalence") %>%
+#   group_by(param, property, category) %>%
+#   summarize(MAP = estimate_mode(val),
+#             cred_upper = hdi_upper(val),
+#             cred_lower = hdi_lower(val))
+
+# m.gen.speakerBeliefs <- m.samp %>%
+#   filter(type == "targetPrevalence") %>%
+#   mutate(Sentence = paste(category, property)) %>%
+#   filter(Sentence %in% example.generics) %>%
+#   mutate(property = factor(property))
+
+m.samp.i <- m.samp %>%
     filter(type == "targetPrevalence") %>%
@@
     filter(Sentence %in% example.generics) %>%
-  mutate(property = factor(property))
-
-# m.samp.prev.params <- m.samp %>%
-#     filter(type == "targetPrevalence") %>%
-#     mutate(Sentence = paste(category, property)) %>%
-#     filter(Sentence %in% example.generics) %>%
-#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
-#     select(-param, -property, -category, -chain, -type) %>%
-#     group_by(parameter) %>%
-#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
-#     ungroup() %>%
-#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
-#     group_by(category, property, iteration) %>%
-#     spread(parameter, val) %>%
-#     rowwise() %>%
-#     mutate(
-#       a = mean*sampleSize,
-#       b = (1-mean)*sampleSize,
-#       val = rbeta(n = 1, shape1 = a, shape2 = b)
-#       ) %>%
-#     ungroup()
+    mutate(parameter = paste(param, property, category, component, sep = "_")) %>%
+    select(-param, -property, -category, -component, -chain, -type) %>%
+    group_by(parameter) %>%
+    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
+    ungroup() %>%
+    separate(parameter, into = c("parameter", "property", "category", "component"), sep= "_") %>%
+    group_by(category, property, iteration) %>%
+    spread(parameter, val) %>%
+    rowwise() %>%
+    mutate(
+      a = mean*sampleSize,
+      b = (1-mean)*sampleSize,
+      val = rbeta(n = 1, shape1 = a, shape2 = b)
+      )
+
+m.samp.i.mixture <- m.samp.i %>% 
+    filter(component == 1) %>%
+    rowwise() %>%
+    mutate(c = rbinom(size = 1, n = 1, prob = mix))
+
+m.samp.ij <- left_join(
+  m.samp.i %>%
+    select(Sentence, property, category, iteration, component, val) %>%
+    spread(component, val),
+  m.samp.i.mixture %>% select(Sentence, property, category, iteration, c)
+) %>% rowwise() %>%
+  mutate(prev = ifelse(c == 1, `1`, `2`))
 
@@
     mutate(category = NA),
-  m.gen.speakerBeliefs %>%
-    select(property, val) %>%
-    rename(value = val) %>%
+  m.samp.ij %>%
+    select(property, prev) %>%
+    rename(value = prev) %>%
     mutate(Parameter = "speakerBeliefs")
@@
                                 "are female", "dont eat people") )
+```
+
+```{r vizualize insets, fig.width = 8, fig.height =4}
+load("../paper/cached_results/case1_modelPosteriors.RData")
 
@@
 #      generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
-#      file = "../paper/cached_results/case1_modelPosteriors.RData")
+#      file = "../paper/cached_results/case1_modelPosteriors_moreFlexiblePrior.RData")
+
+save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored,
+     generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
+     file = "../paper/cached_results/case1_modelPosteriors.RData")
+
+#load("../paper/cached_results/case1_modelPosteriors.RData")
 
@@
                  color = Parameter, lty = Parameter, alpha = Parameter ))+
-  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
+  geom_density(aes(y = ..scaled..), adjust = 1.5, size = 1)+
   facet_wrap(~property, nrow = 1)+
@@
     scale_linetype_manual(values = c(3, 4, 1))+
-    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
-    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
+    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
     xlab("Prevalence") +

### 2018-10-08 analysis/case2-habituals.Rmd
update model results and analyses

@@
      d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
-d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))
+d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character(response)))
 
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
-
-d.hab.predictive.summary
 ```
@@
   project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
-
-n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
-ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
-      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
-      summarize(total = mean(totalSec))
-
-d.hab.predictive.endorsment.condition.summary <- left_join(
+d.hab.predictive.endorsement.filtered <- left_join(
   d.hab.predictive.endorsment, 
@@
   mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
-  rename(item = habitual) %>%
+  rename(item = habitual)
+
+n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
+ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
+      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
+      summarize(total = mean(totalSec))
+
+d.hab.predictive.endorsment.condition.summary <- d.hab.predictive.endorsement.filtered %>%
   group_by(condition) %>%
@@
 ```{r}
+
+ m.hab.predictive.endorse.summarized <- m.hab.predictive.endorse.rsa %>%
+      select(-MAP, -cred_upper, -cred_lower, -src) %>% 
+      unique()
+
+d.hab.predictive.endorsement.filtered.logAnnualRates <- left_join(
+  d.hab.predictive.endorsement.filtered %>% 
+    select(-freqLevel, -past_logfreq, -future_logfreq),
+  m.hab.predictive.endorse.summarized %>%
+    select(item, condition, logAnnualPastRate, logAnnualFutureRate, future_lower, future_upper) 
+)
+
+```
+
+```{r}
+
+glm.hab.pred.endorse.pastfreq <- glm(response ~ logAnnualPastRate, 
+              data = d.hab.predictive.endorsement.filtered.logAnnualRates, family = 'binomial')
+
+glm.hab.pred.endorse.predfreq <- glm(response ~ logAnnualFutureRate, 
+              data = d.hab.predictive.endorsement.filtered.logAnnualRates, family = 'binomial')
+
+d.hab.predictive.endorsement.filtered.logAnnualRates.uniq <- unique(select(
+    d.hab.predictive.endorsement.filtered.logAnnualRates, item, logAnnualPastRate, logAnnualFutureRate, future_lower, future_upper, condition
+  ))
+
+m.hab.predictive.endorse.regPastFreq <- left_join(
+    m.hab.predictive.endorse.summarized,
+    m.hab.predictive.endorse.summarized %>%
+    mutate(
+      MAP = predict(glm.hab.pred.endorse.pastfreq, ., type = "response"), 
+      cred_upper = MAP,
+      cred_lower = MAP,
+      src = "regression_pastfreq"
+      )
+)
+
+m.hab.predictive.endorse.summarized.lower <- m.hab.predictive.endorse.summarized %>%
+  select(-logAnnualFutureRate) %>%
+  rename(logAnnualFutureRate = future_lower)
+
+m.hab.predictive.endorse.summarized.upper <- m.hab.predictive.endorse.summarized %>%
+  select(-logAnnualFutureRate) %>%
+  rename(logAnnualFutureRate = future_upper)
+
+m.hab.predictive.endorse.regPredFreq <- left_join(
+    m.hab.predictive.endorse.summarized,
+    m.hab.predictive.endorse.summarized %>%
+    mutate(
+      MAP = predict(glm.hab.pred.endorse.predfreq, ., type = "response"), 
+      cred_lower = predict(glm.hab.pred.endorse.predfreq, m.hab.predictive.endorse.summarized.lower, type = "response"),
+      cred_upper = predict(glm.hab.pred.endorse.predfreq, m.hab.predictive.endorse.summarized.upper, type = "response"),
+      src = "regression_futurefreq"
+      )
+)
+
+m.hab.predictive.endorse.allModels <- bind_rows(
+  m.hab.predictive.endorse.rsa,
+  m.hab.predictive.endorse.regPredFreq,
+  m.hab.predictive.endorse.regPastFreq,
+  m.hab.predictive.endorse.rsa %>%
+    select(-MAP, -cred_upper, -cred_lower, -src) %>%
+    unique() %>%
+    mutate(MAP = MAP_h, cred_lower = low,
+         cred_upper = high, src = "human data")
+)
+
+```
+
+```{r}
 save(d.hab.predictive.endorsment.summary, d.hab.predictive.summary, 
@@
      n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, 
-     lmer.rs.hab.predictive.summary,
+     lmer.rs.hab.predictive.summary, m.hab.predictive.endorse.allModels,
      file = "../paper/cached_results/case2_predictive_data.RData")
-```
+
+#m.hab.predictive.endorse.allModels
+```

### 2018-10-08 analysis/talk-figures.Rmd
update model results and analyses

@@
               color = 'white')+
-  scale_shape_manual(values=c(21,22,23))+
+  scale_shape_manual(values=c(21,21,21))+
   geom_abline(intercept = 0, slope = 1, lty =3, color = 'white')+
@@
   guides(fill=guide_legend(reverse = T), shape=guide_legend(reverse = T))+
-  scale_fill_brewer(type = "seq", palette = 2)+
+  scale_fill_brewer(type = "qual", palette = 2)+
   xlab("Past frequency")+
@@
        width = 6, height = 4)
+```
+```{r}
+d.hab.predictive.endorsment.condition.summary
+```
+
+```{r}
+d.hab.predictive.endorsment.condition.summary %>%
+    mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling"))) %>%
+    ggplot(., aes(x=condition, y=MAP_h, 
+                 fill=condition, shape=condition,
+                 ymin=low, ymax = high))+
+  geom_col(position = position_dodge(0.5), color = 'white', width = 0.5)+
+  geom_errorbar(alpha = 1, size = 0.5, position = position_dodge(0.3),
+                width = 0.2,
+                 color = 'white')+
+  #geom_point(shape = 21, size = 3)+
+  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
+  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
+  #scale_fill_viridis(discrete = T)+
+  scale_fill_brewer(type = "qual", palette = 2)+
+  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
+  #coord_fixed()+
+  ylab("Habitual endorsement")+
+  xlab("")+
+  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
+        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45,
+                                   lineheight = 0.7),
+        legend.position = "none")
+ggsave(file = paste(fig.path, "habituals_predictives_conditionEndorse.pdf", sep =""),
+       width = 3.5, height = 3)
 ```
@@
                      labels= c("Human data","regression_pastfreq", 
-                                "Uncertain semantics (Past)", "Linear model (Predictive frequency)","Uncertain semantics (Predictive)"))) %>%
+                              "Generics Model\n Past Frequency", 
+                              "Frequency alone\n Predictive Frequency",
+                              "Generics Mçodel\n Predictive Frequency"))) %>%
   filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
@@
   scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
-  scale_shape_manual(values=c(21,22,23))+
+  scale_shape_manual(values=c(21,21,21))+
   scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
-  scale_fill_brewer(type = "seq", palette = 2)+
+  scale_fill_brewer(type = "qual", palette = 2)+
   #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
@@
   xlab("Model prediction")+
-  facet_grid(.~src)+
+  facet_wrap(~src, nrow = 1)+
   theme(legend.position = "right")
+
+habituals.endorsement.pred.scatters
 
@@
        file = paste(fig.path, "habituals_predictive_modelScatters.pdf", sep =""),
-       width = 10, height = 5)
+       width = 8, height = 5)
 ```
@@
 ```
+
+```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt.
+3 (stimuli) and priors reconstructed from participants' responses (model).
+", fig.width = 8, fig.height = 3, eval = F}
+sample.dists <- bind_rows(
+  data.frame(
+    dist = "rare weak",
+    x = c(rbeta(n = 3000, shape1 = 20, shape2 = 100),
+          rbeta(n = 7000, shape1 = 1, shape2 = 100)
+          )
+  ),
+  data.frame(
+    dist = "common weak",
+    x = rbeta(n = 10000, shape1 = 20, shape2 = 100)
+  ),
+  data.frame(
+    dist = "rare deterministic",
+    x = c(rbeta(n = 3000, shape1 = 100, shape2 = 2),
+          rbeta(n = 7000, shape1 = 1, shape2 = 100)
+          )
+  ),
+  data.frame(
+    dist = "common deterministic",
+    x = rbeta(n = 10000, shape1 = 100, shape2 = 2)
+  )
+) %>%
+    mutate(Distribution = 
+        factor(dist, levels = c(  "rare weak", "common weak","rare deterministic","common deterministic"),
+         labels = c("Rare Weak", "Common Weak", "Rare Strong", "Common Strong")))
+
+figure.causals.priors <- sample.dists %>%
+  ggplot(., aes(x = x*100, fill = Distribution, color = Distribution))+ 
+  geom_density( adjust = 1.3, 
+               size = 1.2,
+               aes( y = ..scaled..), color = 'white')+ #
+  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100))+
+  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
+  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
+  #scale_color_manual(values = c("#636363", "#d7191c"))+
+  #scale_alpha_manual(values = c(0.1, 0.4))+
+  #scale_linetype_manual(values = c(2, 1))+
+  ylab("Scaled Prior Probability")+
+  xlab("Prevalence")+
+  facet_wrap(~Distribution, scales = 'free', nrow = 2)+
+  guides(fill = F, color = F)+
+  theme(legend.position = 'bottom', legend.direction = 'horizontal')
+
+ggsave(figure.causals.priors,
+         file = paste(fig.path, "causals-priors_stimuli.pdf", sep = ""), 
+       width =6, height = 4)
+```

### 2018-10-08 paper/comgen-paper.Rmd

@@
   - \usepackage{multirow}
+  - \usepackage{xcolor}
 
@@
 knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
+                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
 ```

### 2018-10-09 paper/comgen-paper.Rmd
incorporate ndg feedback into model section, beginning of worked examples

@@
 
-The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs"; *has four legs* could apply to an individual as in "This dog has four legs").
+The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "This dog has four legs").
 In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
 <!-- Dinosaurs are exctinct ~ John is a smoker? -->
-Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005].
+Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
 Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
@@
 ]
+We first describe a model for generics, before noting how the basic ideas generalize to habituals and causals.
 
@@
 The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is greater than zero: $\denote{some}(p) := p > 0$.
+For example, the literal meaning of the sentence "Some dogs have four legs" is that there is a non-zero chance that an individual dog will have four legs: $\denote{some}(p) := p > 0$.
 "Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.^[
-  We note that we are describing the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
+  We are describing the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
 ]
@@
 
-Putting these three ingredients (probability, vagueness, and context) together, we get the following model of generic interpretation:
+Putting these three ingredients (probability, vagueness, and context) together, we get the following model of interpreting generalizations in language:
 
@@
 
-We denote this probabilistic generic interpretation model by $L$ to indicate that it is modeling a listener updating their beliefs according to the truth-functional meaning of an utterance $u$.
+We denote this probabilistic interpretation model by $L$ to indicate that it is modeling a listener updating their beliefs according to the truth-functional meaning of an utterance $u$.
 Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(p, \theta)}$ that returns $1$ when the utterance is true (i.e., when $p > \theta$) and $0$ otherwise.
@@
 If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance.
-As the threshold decreases, more and more prevalence levels become be compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
+As the threshold decreases, more and more prevalence levels become compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
 The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution on prevalence that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
 This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise prevalence.
+
+The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics and, thus, naturally extends to generalizations of different semantic types.
+For example, if we take underlying semantic scale (formally, the support of $P(p)$) to be that of the temporal frequency of an event (e.g., how often we expect an event to occur), then Eq.
+\ref{eq:L0} describes a model of habitual interpretation (e.g., "John smokes").
+In this case, $p$ is naturally thought of as a rate (e.g., the frequency of an event within a certain time window).
 
@@
 ]
+Given that the speaker only has two options (i.e., produce the generalization utterance or stay silent), the endorsement decision comes down to whether or not the referent prevalence is more likely under the prevalence prior distribution $P(p)$ (i.e., the listener's posterior upon hearing silence) or the listener generic interpretation distribution given by Eq.
+\ref{eq:L0} (Figure\ \@ref(fig:uniformPriorSimulation)C).
 Thus, the communication-relevant content of the generalization is the prevalence in the referent category $p$.
-The semantic threshold $\theta$ is necessary for establishing the precise truth conditions (used in Eq. \ref{eq:L0}) but is otherwise a nuisance parameter, which the endorsement model integrates out.
-Finally, Eq. \ref{eq:S1} models an information-theoretic speaker's decision, which we assume is approximately rational, with degree of rationality given by $\lambda$.
-This exponentiation step acts as a soft-max function on $S$'s posterior beliefs of which utterance is better.
-
-<!-- \ndg{this doesn't make a ton of sense in this context, since we haven't set up S as a decision maker....} -->
-
-<!-- We consider the notion of truth judgments or endorsement from the information-theoretic perspective: Would a generalization statement convey the appropriate information to a naive interpreter?
--->
-
-<!-- We formalize this by considering how well the generalization would convey the referent prevalence $p$ to the $Lit$ model (Eq. \ref{eq:L0}). -->
-
-<!-- \begin{equation}  -->
-<!-- S(u \mid p) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p, \theta \mid u)  \diff \theta } )} -->
-<!-- \label{eq:S1} -->
-<!-- \end{equation} -->
-<!-- \ndg{this eqn isn't well motivated. if we never use cost in this paper, then get rid of exp and ln and just have Lit to a power of lambda. also say why it's called S earlier?} -->
-
-<!-- The endorsement model simulates what the interpretation model would believe upon hearing an utterance $u$: $Lit(p, \theta \mid u)$. -->
-<!-- The proportionality in Eq. \ref{eq:S1} implies normalization over a set of alternative utterances.  -->
-<!-- We interpret the endorsement task (e.g., "true" vs "false"; "agree" vs.
-"disagree") as supplying two alternatives: *endorse* or *not*, where *not* we take to be a silent utterance that conveys no information content [@Franke2014cogsci; @Degen2014]: $\denote{null}(x, \theta) = \text{True}$.^[ -->
-<!--   This "null" alternative to the generalization can be realized in at least two other ways: the negation of the generalization (e.g., "It is not the case that Robins lay eggs") or the negative generalization (i.e., "Robins do not lay eggs").
--->
-<!--   The latter is different because it creates a new threshold (analogous to how "short" and "tall" are modeled with different thresholds). -->
-<!--   All results reported are similar for these two alternatives, and we use the alternative of the "silent" utterance for simplicity. -->
-<!-- ] -->
-
-Given that the speaker only has two options (i.e., produce the generalization utterance or stay silent), the endorsement decision comes down to whether or not the *referent prevalence* is more likely under the prevalence prior distribution $P(p)$ or the listener interpretation distribution given by Eq.
-\ref{eq:L0} (Figure\ \@ref(fig:uniformPriorSimulation)C).
-Our endorsement model (Eq.
+The semantic threshold $\theta$ is necessary for establishing the precise truth conditions (used in Eq.
+\ref{eq:L0}) but is otherwise a nuisance parameter, which the endorsement model integrates out (note that there is no $\theta$ in the left-hand side of Eq.
+\ref{eq:S1}).
+Finally, because Eq.
+\ref{eq:S1} models an information-theoretic speaker's decision, $S_1$ computes a belief distribution and then produces utterances which are approximately rational according to that belief distribution, via a soft-max function with degree of rationality $\lambda$.
+\mht{better?}
+In the next section, we work through different examples from the linguistics literature, describing the prevalence prior and other relevant model components for each.
+
+<!-- Our endorsement model (Eq.
 \ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u \mid p)$.
-The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq.
-\ref{eq:S1}).
-This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
-We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
-In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.
-In the next section, we work through different examples from the linguistics literature, describing the prevalence prior and other relevant model components for each.
+-->
+<!-- This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973]. -->
+<!-- We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
+-->
+<!-- In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$. -->
 
@@
 
-### Worked examples
-
-The endorsement model defined in the previous section predicts that the variability in endorsements for generic statements and other sorts of generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
+# Worked examples
+
+<!-- The endorsement model defined in the previous section predicts that the variability in endorsements for generic statements and other sorts of generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq.
 \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq.
 \ref{eq:L0}).
-We explore the predictions of this model by varying each of these factors in the context of a few worked examples.
-These examples are taken from the linguistics literature on generics and are statements that any theory of generics should be able to correctly predict are either true, false, or somehow indeterminate.
+-->
+We explore the predictions of the endorsement model in the context of a few worked examples.
+These examples are taken from the linguistics literature on generics and are statements that have been historically challenging for prevalence-based approaches (see Table 1).
 We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
@@
 
-The uncertain threshold model's interpretations are highly sensitive to background knowledge, formalized in simplest terms in terms of a *prevalence prior*.
-Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories (Figure\ \@ref(fig:simulations)).
-For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
-Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
-  The Beta distribution is a distribution over numbers between 0 and 1. 
-  In other words, it is a probability distribution over probabilities or prevalences.
-]
-The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
+Model predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
+Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
+This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
+\ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below}
+\mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...}
+The prevalence prior can be thought of a distribution over the prevalence of a feature among alternative categories (Figure\ \@ref(fig:simulations)).
+<!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
+Figure\ \@ref(fig:simulations) (row 1) shows intuitive prevalence priors for six different properties (we introduce methods for empirically eliciting these priors in the experimental section).
+The *lay eggs* distribution is bimodal, with substantial probability mass near 0 (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
 Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
-Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
-This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence. 
-We explore the model's ability to account for intuitive truth judgments for different examples that have been historically challenging for prevalence-based approaches.
 
@@
 worked.examples.tab <- xtable::xtable(worked.examples, 
-                       caption = "Example generalizations that a theory of generics should correctly predict.", 
-                       align=c('p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))
+                       caption = "Example generalizations that a theory of generics should correctly predict. See details of each example in corresponding section.", 
+                       align=c('| p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))
 
@@
 
-Often the first observation with generics is that they appear to behave like *universal* quantifiers (e.g., "All") that permit exceptions.
-That is, not all dogs bark, but still *Dogs bark* is true.
+Often the first observation with generics is that they appear to behave like universal quantifiers (e.g., "All") that permit exceptions.
+That is, not all dogs bark, but still "Dogs bark" is true.
 The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which the generalization becomes true.
-Rather, listeners have uncertainty about the threshold *a priori* which leads to graded interpretations (e.g., *Dogs bark* meaning *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
-The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (*referent prevalence* of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
+Rather, listeners have uncertainty about the threshold *a priori* which leads to graded interpretations (e.g., "Dogs bark" meaning *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
+The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (referent prevalence of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
 

### 2018-10-10 paper/comgen-paper.Rmd
polish worked examples

@@
 
-Model predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
+Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
 Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
@@
 \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...}
-The prevalence prior can be thought of a distribution over the prevalence of a feature among alternative categories (Figure\ \@ref(fig:simulations)).
+The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).
 <!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
-Figure\ \@ref(fig:simulations) (row 1) shows intuitive prevalence priors for six different properties (we introduce methods for empirically eliciting these priors in the experimental section).
-The *lay eggs* distribution is bimodal, with substantial probability mass near 0 (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
+For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0 (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
 Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
+Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
+We now turn our attention to the endorsement model's predictions.
 
@@
               "2. Kangaroos have spots",
-              "3. Sharks don't eat people",
-              "4. Robins lay eggs",
-              "5. Robins are female",
-              "6. Mosquitos carry malaria", 
+              "3. Robins lay eggs",
+              "4. Robins are female",
+              "5. Mosquitos carry malaria", 
+              "6. Sharks don't eat people",
               "7. Mary handles the mail from Antarcita",
@@
               "9. Elephants live in Africa and Asia"),
-  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "50%/50%"),
+  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "85%", "0 times", "100%", "50%/50%"),
   `intuitive truth value` = c(
-    "T", "F", "F", "T", "U",
-    "T", "T", "F", "T" 
+    "T", "F",  "T", "U",
+    "T", "F","T", "F", "T" 
   ),
@@
     "Some kangaroos could have spots",
+    "Only female robins (50%) lay eggs",
+    "Same number that lay eggs (50%)",
+    "Very few mosquitos actually carry malaria",
     "Most sharks don't eat people",
-    "True, even though only female robins (50%) lay eggs",
-    "Not true, but same number that lay eggs (50%)",
-    "Very few mosquitos actually carry malaria",
-    "True even if there has never been any mail from Antarcita",
-    "False even if 100% have even social security numbers",
+    "Consider there has never been any mail from Antarcita",
+    "Consider 100% have even social security numbers",
     "Impossible for most to live in Africa and most to live in Asia"
@@
 
-Often the first observation with generics is that they appear to behave like universal quantifiers (e.g., "All") that permit exceptions.
-That is, not all dogs bark, but still "Dogs bark" is true.
-The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which the generalization becomes true.
-Rather, listeners have uncertainty about the threshold *a priori* which leads to graded interpretations (e.g., "Dogs bark" meaning *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
-The endorsement model then predicts this is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though not all dogs bark (referent prevalence of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
+Often the first observation with generics is that they appear to behave like universal quantifiers (e.g., "All") that permit exceptions: Not all dogs bark, but still "Dogs bark" is true.
+The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which a generic statement becomes true.
+Rather, listeners have uncertainty about the threshold which leads to graded interpretations (e.g., "Dogs bark" probably means *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
+The endorsement model predicts "Dogs bark" is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though there are exceptions to the universal generalization (referent prevalence of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
 
@@
 
-A second observation regarding generics is that their truth conditions cannot be so lenient so to always convey *existential* quantification (e.g., "Some").
-Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel the generalization "Kangaroos have spots" is too strong to assert.
-The model exhibits this same restraint, predicting a very low endorsement probability for this generic statement (Figure\ \@ref(fig:simulations); column 2).
+A second observation regarding generics is that their truth conditions cannot be so lenient so as to always convey *existential* quantification (e.g., "Some").
+Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel awkward to assert the generic "Kangaroos have spots".
+The model exhibits this same restraint, predicting a very low endorsement probability for this generic sentence (Figure\ \@ref(fig:simulations); column 2).
 The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean *almost all* kangaroos have spots.
-The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would mislead the listener.
-
-**3. Sharks don't eat people.**
-
-A similar logic can be applied to this example, which is the converse of the affirmative generalization "Sharks eat people", which is assumed true despite the low actual number of incidents involving sharks eating people [@Leslie2007].
-The referent prevalence---the number of sharks that don't eat people---is thus very high: Almost all sharks don't eat people.
-Yet, intuitively, the generalization is again misleading. 
-Because for almost all animal categories, almost members of those categories don't eat people (i.e., the prevalence of the feature is almost 100% for all categories because very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people, which is too strong.
-It is interesting to note that because of the high referent-prevalence, the model is less certain of its decision, predicting an endorsement probability around 40%.
-We will test this quantitative prediction in one of our experiments.
-
-**4. and 5. Robins lay eggs vs. Robins are female**
+The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it is too strong a statement and would mislead the listener.
+
+**3. and 4. Robins lay eggs vs. Robins are female**
 
@@
 As described above, the priors are different: Many animals have zero egg-layers (0% prevalence), while the vast majority of animal categories have female members in exactly the same proportion (50%).
-Interestingly, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes 50% have the property.^[
-  This behavior might suggest a potential area for model revision. 
-  Intuitively, "Xs are female" should mean "All Xs are female".
-  In this paper, our empirical interest concerns endorsements or truth judgments; at this point, the interpretation model is only an intermediate representation useful for deriving predictions about endorsement.
+Given this background knowledge, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes 50% have the property.
+However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would be more aligned with the referent prevalence than if the endorsement model produced the null utterance, which would instead return the prior.
+In contrast, "Robins are female" does not carry any information (the listener posterior is not different from the prior); here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5 (i.e., *neither true nor false*).
+Indeed, previous studies on generic endorsements have found "Robins are female" to receive an intermediate endorsement level [@Prasada2013].
+
+**5. Mosquitos carry malaria.**
+
+Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are actually malaria-free.
+The prevalence prior for "carries malaria" is highly skewed towards low prevalence levels: many animals do not have malaria-carriers among them and even for those that do, the prevalence is expected to be quite low.
+Then, carrying malaria is significantly more true of mosquitos than other animals, an intuition that is often arrived at with this example.
+This kind of behavior is related to the construct of *cue validity*---the probability of the feature given the category e.g., $P({is a mosquito} \mid \text{carries malaria})$---which we return to in the next section.
+The uncertain-threshold model displays a critical behavior: It can endorse generics when the referent prevalence is very low.
+
+<!-- and then point out that this is related to cue validity, as explored later. (or just wait to introduce cue validity until later.) -->
+<!-- ---because the listener interpretation distribution would be more aligned with the referent prevalence than the prior.  -->
+<!-- Intuitively, this is because many animals do not have malaria-carriers among them and so in a sense, having malaria is diagnostic for being a mosquito -->
+<!-- We return to this relationship in the next section, and provide a precise mathematical derivation of the relationship between the prevalence prior and cue validity in Appendix A. -->
+
+**6. Sharks don't eat people.**
+
+When the prevalence of the feature is very high, it is also not necessary for the model to endorse the generic.
+"Sharks don't eat people" is predicted to be a somewhat strange utterance, despite the fact that the vast majority of sharks do not eat people.^[
+ We create this example as the converse of the classic example "Sharks eat people", predicted to be *true* despite low prevalence [@Leslie2007].
+We reverse this example to show how the model deals with a high-prevalence feature that is predicted to be false or infelicitous.
 ] 
-However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would more aligned with the referent prevalence than if the endorsement model produced the null utterance, which would instead return the prior.
-In the case of "Robins lay eggs", the hypothetical generic utterance does not carry any information (the listener posterior is not different from the prior); in this case, however, the generic would not be misleading only uninformative, and hence the model predicts an endorsement probability of 0.5 (i.e., *neither true nor false*).
-
-**6. Mosquitos carry malaria.**
-
-Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are actually malaria-free.
-The uncertain-threshold model comes to the same conclusion---endorsing a generic when the referent prevalence is very low---because the listener interpretation distribution would be more aligned with the referent prevalence than the prior.
-Intuitively, this is because not that many animals have malaria-carriers among them and so in a sense, having malaria is diagnostic for being a mosquito, an intuition that is often arrived at with this example.
-This example also highlights that the construct of *cue validity*---the probability of the feature given the category e.g., $P({is a mosquito} \mid \text{carries malaria})$---plays a role in our model.
-We return to this relationship in the next section, and provide a precise mathematical derivation of the relationship between the prevalence prior and cue validity in Appendix A.
+<!-- Yet, intuitively, the generic would be misleading (similar in intuition to "Kangaroos have spots"). -->
+Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people, which is too strong.
+It is interesting to note that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 40% (i.e., somewhat false).
+We will test this quantitative prediction in Case Study 1 on generics.
 
@@
 
-Imagine there is a job in the local bureaucrat's office to handle the mail from Antarctica and this job is assigned to Mary; to date, however, there has never been any mail from Antarctica [@Cohen1999].
-That is, the statement "Mary *has handled* mail from Antarctica" is false.
-Sentence (7) is still thought to be intuitively true despite zero actual instances of the event.
-This highlights an important ambiguity in the theoretical commitments of the uncertain threshold model: The endorsement model aims to communicate some referent prevalence $p$, but does the prevalence represent the actual, objective frequency in the world or a subjective, predictive degree of belief in the head?
-
-We posit that Sentence (7) is an extreme case of generalizations expressing *predictive* probabilities.
+Imagine there is a job in the local bureaucrat's office to handle the mail from Antarctica and this job is assigned to Mary; to date, however, nobody has ever sent mail to the office from Antarctica [@Cohen1999].
+In other words, the statement "Mary has handled mail from Antarctica" is false.
+"Mary handles the mail from Antarctica" is still thought to be intuitively true despite zero actual instances of the event.
+This highlights an important ambiguity in the theoretical commitments of the uncertain threshold model: The endorsement model aims to communicate some referent prevalence $p$, but does the prevalence represent the actual, objective frequency in the world (e.g., the number of times Mary has handled mail in the past) or a subjective, predictive degree of belief in the head (e.g., our prediction that were the appropriate situation to arise, Mary would be handling the mail from Antarctica)?
+
+We posit that Mary the Antarctic mail handler is an extreme case of generalizations expressing *predictive* degrees of belief.
 We expect this context sets up the expectation that any future mail coming from Antarctica will be handled by Mary. 
@@
 In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
+We explore this question experimentally in Case Study 2 on habituals.
 
@@
 
-Imagine that every current and past Supreme Court Justice has a social security number which is an *even number*. 
-Sentence (8) is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
-We predict the rejection of Sentence (8) is the result of abstract, intuitive theories guiding our subjective predictive probabilities.
-That is, because observers strongly believe one's social security number does not influence selection for the Supreme Court, speakers would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
-Then, if we constructed the comparison class by considering other professionals, Sentence (8) would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+Imagine that every current and past Supreme Court Justice has had a social security number which was an *even number*. 
+"Supreme Court Justices have even social security numbers" is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
+We predict the rejection of even social security numbered Justices is the result of our intuitive theories guiding our subjective predictive probabilities, which feed into the endorsement model.
+That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
+Then, "Supreme Court Justices have even social security numbers" would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
+This example is thus the conceptual opposite of Mary the Antarctic mail handler, where our internal model of the world led us to a strong degree of belief in the property holding in the future; with the Supreme Court Justices, our internal models lead to to weak degree of belief in the property holding in the future.
 
@@
 
-\mht{both this and the "surprisng prediction" above are intutiions/examples we are not going to test empirically (however, here we at least give a model for it)...
-should these appear elsewhere, or somehow be marked upfront?}
+<!-- \mht{both this and the "surprisng prediction" above are intutiions/examples we are not going to test empirically (however, here we at least give a model for it)...
+should these appear elsewhere, or somehow be marked upfront?} -->
 
 Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
-@Nickel2008 suggests Sentence (9) is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Statistical accounts of generics have trouble with this kind of conjunction: It cannot be the case that *most* (more than half) elephants live in Africa and *most* (more than half) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which we would rather prefer not to posit.
-However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
-Our theory does not provide a fixed semantics for generalizations, but an uncertain one, which can be updated as more information comes in.
-In fact, with prior knowledge suggesting against the existence of international elephants and without any further semantic assumptions, our model interprets Sentence (9) as meaning some elephants live in Africa and that different ones live in Asia.^[
+@Nickel2008 suggests that "Elephants live in Africa and Asia" is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
+Statistical accounts of generics have trouble with this kind of conjunction because they historically have appealed to fixed, truth-conditional cutoffs for generics [e.g., generic means *more than half*; @Cohen1999].
+It cannot be the case that most (more than half of) elephants live in Africa and *most* (more than half of) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
+<!-- However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
+-->
+Our theory does not provide a fixed semantics for generics, but an uncertain one which can be updated as more information comes in.
+In fact, with prior knowledge suggesting against the existence of international elephants, our model interprets "Elephants live in Africa and Asia" as meaning that some elephants live in Africa and that different ones live in Asia.^[
   An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
 ]
-Interestingly, an incremental parsing of Sentence (9) (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
-When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa (and others in Asia, but few in other places).
+Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa and others in Asia (but few in other places).
 The flexibility of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
+We leave for future work the testing of quantitative predictions for this kind of example.
 
@@
 
+<!-- ^[ -->
+<!--   This behavior might suggest a potential area for model revision.  -->
+<!--   Intuitively, "Xs are female" should mean "All Xs are female". -->
+<!--   In this paper, our empirical interest concerns endorsements or truth judgments; at this point, the interpretation model is only an intermediate representation useful for deriving predictions about endorsement.
+-->
+<!-- ] -->
+
 The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.

### 2018-10-11 analysis/model-simulations.Rmd
add elephants model

@@
 
+## Elephants live in africa and asia
+
+```{r}
+elephants <- '
+var probability = function(Dist, x) {
+  return Math.exp(Dist.score(x));
+}
+
+var bins = [
+  0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+  0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
+];
+
+var theta = 1;
+var params75 = {a:45, b: 15};
+var params50 = {a:30, b: 30};
+var params25 = {a:15, b: 45};
+var params100 = {a:50, b: 1};
+
+var allComponents = [params25, params50, params75, params100]
+var nullParams = {a:1,b:2000};
+
+var makeComponent = function(params){
+  return Categorical({
+  vs: bins,
+  ps: map(function(b) {
+    probability(Beta(params), b) + Number.EPSILON
+  }, bins )
+})
+}
+
+var statePrior = Infer({model: function(){
+  var mainPlace = categorical({
+    ps:[1, 1, 1, 1],
+    vs:[
+      {asia: true, africa: false}, {asia: false, africa: true},
+      {asia: false, africa: false}, {asia: true, africa: true}
+    ]
+  });
+  return {
+    asia: sample(makeComponent(mainPlace.asia ? uniformDraw(allComponents) : nullParams)),
+    africa: sample(makeComponent(mainPlace.africa ? uniformDraw(allComponents) : nullParams))
+  }
+}})
+
+var thetaPrior = Infer({model: function(){
+  return {
+    asia: uniformDraw(
+      [0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+       0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95]
+    ),
+    africa: uniformDraw(
+      [0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
+       0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95]
+    )
+  }
+}});
+
+var meaning = function(utt, state, theta) {
+  state[utt] > theta[utt]
+}
+
+var listener0 = function(utterance, worldPriors, thresholdPriors) {
+  Infer({model: function(){
+    var state = sample(worldPriors)
+    var theta = sample(thresholdPriors)
+    var m = meaning(utterance, state, theta)
+    condition(m)
+    condition(state.africa + state.asia <= 1)
+    return {state, theta}
+  }})
+}
+
+var elephantsLiveInAsia = listener0("asia", statePrior, thetaPrior);
+var asiaStatePosterior = marginalize(elephantsLiveInAsia,"state");
+var asiaThresholdPosterior =  marginalize(elephantsLiveInAsia, "theta");
+
+var elephantsLiveinAfricaAndAsia = listener0("africa", asiaStatePosterior, asiaThresholdPosterior)
+
+var AfricaAndAsiaStatePosterior = marginalize(elephantsLiveinAfricaAndAsia, "state");
+
+var AfricaAndAsiaThresholdPosterior =  marginalize(elephantsLiveinAfricaAndAsia, "theta");
+
+var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior}
+x
+'
+```
+
+```{r}
+rs.eleph <- webppl(elephants)
+
+rs.asia <- as.data.frame(rs.eleph$asiaStatePosterior)
+rs.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)
+
+rs.asia.marignals <- bind_rows(
+  rs.asia %>%
+    rename(state = support.asia) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "asia"),
+  rs.asia %>%
+    rename(state = support.africa) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "africa")
+)
+
+ggplot(rs.asia.marignals, aes(x = state, y = prob))+
+  geom_col(position = position_dodge())+
+  facet_wrap(~marginal)
+```
+```{r}
+rs.asiaafrica.marignals <- bind_rows(
+  rs.asiaafrica %>%
+    rename(state = support.asia) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "asia"),
+  rs.asiaafrica %>%
+    rename(state = support.africa) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "africa")
+)
+
+ggplot(rs.asiaafrica.marignals, aes(x = state, y = prob))+
+  geom_col(position = position_dodge())+
+  facet_wrap(~marginal)
+```
+
 # Misc extra

### 2018-10-11 analysis/model-simulations.Rmd
elephants figure, edits to alternative theories

@@
 
-var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior}
+var x = {asiaStatePosterior, AfricaAndAsiaStatePosterior, statePrior}
 x
@@
 rs.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)
+rs.asiaafrica.prior <- as.data.frame(rs.eleph$statePrior)
 
@@
     summarize(prob = sum(probs)) %>%
-    mutate(marginal = "asia"),
+    mutate(marginal = "africa"),
   rs.asia %>%
@@
     summarize(prob = sum(probs)) %>%
-    mutate(marginal = "africa")
+    mutate(marginal = "asia")
 )
@@
   facet_wrap(~marginal)
-```
-```{r}
+
 rs.asiaafrica.marignals <- bind_rows(
@@
   facet_wrap(~marginal)
+
+rs.asiaafrica.priors <- bind_rows(
+  rs.asiaafrica.prior %>%
+    rename(state = support.asia) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "asia"),
+  rs.asiaafrica.prior %>%
+    rename(state = support.africa) %>%
+    group_by(state) %>%
+    summarize(prob = sum(probs)) %>%
+    mutate(marginal = "africa")
+)
+```
+
+```{r}
+
+save(rs.asia.marignals, rs.asiaafrica.marignals,rs.asiaafrica.priors,
+     file = "../paper/cached_results/modelSims-elephants.RData")
+
+fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 2, fill = 'grey', alpha = 0.3)+
+  facet_wrap(~marginal, ncol = 1)+
+  ggtitle('prevalence priors')+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("")+
+  ylab("Probability density")
+
+fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
+  facet_wrap(~marginal, ncol = 1)+
+  ggtitle('"Elephants live in Africa..."')+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("Prevalence")+
+  ylab("Probability density")+
+  theme(axis.title.y = element_blank())
+
+fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
+  facet_wrap(~marginal, ncol = 1)+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("")+
+  ggtitle('"...and Asia"')+
+  ylab("Probability density")+
+  theme(axis.title.y = element_blank())
+
+cowplot::plot_grid(
+  fig.eleph.0,
+  fig.eleph.1,
+  fig.eleph.2,
+  nrow = 1,
+  rel_widths =c(1,1, 1),
+  labels = c("A", "B","C")
+)
 ```

### 2018-10-11 paper/comgen-paper.Rmd
elephants figure, edits to alternative theories

@@
 knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
-                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
+                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
 ```
@@
 Our theory does not provide a fixed semantics for generics, but an uncertain one which can be updated as more information comes in.
-In fact, with prior knowledge suggesting against the existence of international elephants, our model interprets "Elephants live in Africa and Asia" as meaning that some elephants live in Africa and that different ones live in Asia.^[
-  An implementation of this example can be found: [http://forestdb.org/models/generics-conjunction.html](http://forestdb.org/models/generics-conjunction.html).
-]
-Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only the first part of the sentence that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa.
-When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa and others in Asia (but few in other places).
+In fact, with prior knowledge suggesting against the existence of international elephants (Figure\ \@ref(fig:elephants)A), our model interprets "Elephants live in Africa and Asia" as meaning that some elephants live in Africa and that different ones live in Asia (Figure\ \@ref(fig:elephants)C).
+Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa (Figure\ \@ref(fig:elephants)B).
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa and others in Asia (Figure\ \@ref(fig:elephants)C).
 The flexibility of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
@@
 
+```{r elephants, fig.cap="Model interpretation of a conjunctive generic (\"Elephants live in Africa and Asia\").
+A: Intuitive priors for marginal distributions of prevalence for living in Africa and living in Africa.
+B: Partial interpretation upon hearing utternace (\"Elephants live in Africa...\").
+C: Full interpretation upon hearing the end of the sentence (\"Elephants live in Africa and Asia\").
+Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.", fig.width = 8, fig.asp = 0.6, out.width = "100%", fig.align = "center", cache=F}
+load("cached_results/modelSims-elephants.RData")
+
+fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 2, fill = 'grey', alpha = 0.3, size = 1.5)+
+  facet_wrap(~marginal, ncol = 1)+
+  ggtitle('Prevalence priors')+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("")+
+  ylab("Probability density")+
+  theme(plot.title = element_text(size = 10, hjust = 0.5))
+
+fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
+  facet_wrap(~marginal, ncol = 1)+
+  ggtitle('"Elephants live in Africa..."')+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("Prevalence")+
+  ylab("Probability density")+
+  theme(axis.title.y = element_blank(),
+        plot.title = element_text(size = 10, hjust = 0.5))
+
+fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
+  facet_wrap(~marginal, ncol = 1)+
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  xlab("")+
+  ggtitle('"...and Asia"')+
+  ylab("Probability density")+
+  theme(axis.title.y = element_blank(),
+        plot.title = element_text(size = 10, hjust = 0.5))
+
+cowplot::plot_grid(
+  fig.eleph.0,
+  fig.eleph.1,
+  fig.eleph.2,
+  nrow = 1,
+  rel_widths =c(1,1, 1),
+  labels = c("A", "B","C")
+)
+```
+
 ## Relationship to other semantic theories
 
-The present paper presents the first formal theory of the language of generalization that generates quantitative predictions about human behavioral data. 
-Our work builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
-The main set of approaches from formal semantics try to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
+<!-- We presents the first formal theory of the language of generalization that generates quantitative predictions about human behavioral data.  -->
+Our formal theory builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
+The main approaches from formal semantics try to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
 These views are typically *statistical* in nature in that they appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
-Many of these theories rely upon mechanisms outside of the truth conditions to make sense of the extreme flexibility exhibited by generics; unfortunately, these extra-semantic mechanisms are rarely described in any detail and never to the extent to make precise predictions.
-Other theorists, primarily in philosophy and psychology, have taken the extreme flexibility of generics to argue against a quantitative theory based on prevalence, instead arguing that abstract, mental representations are directly tied to semantics of generics (e.g., *there is something about being a K which causes it to F*).
+Many of these theories rely upon mechanisms outside of the truth conditions to make sense of the extreme flexibility exhibited by generics; unfortunately, these extra-semantic mechanisms are not described in any detail to make precise, quantitative predictions.
+Other theorists, primarily in philosophy and psychology, have taken the extreme flexibility of generics to argue against a quantitative theory based on statistics, instead arguing that abstract, mental representations are directly tied to semantics of generics (e.g., *there is something about being a K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of generic language [@Carlson1995essay].^[
@@
 Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
-The most influential account in psychology comes from @Leslie2008, which has same starting point as our analysis: Generics express generalization. 
-This analysis draws upon insights from the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.
+The most influential account in psychology comes from @Leslie2008, which uses the same starting point as our analysis: Generics express generalization. 
+@Leslie2008's analysis draws upon insights from the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.
 <!-- ^[ -->
@@
   We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by a different mechanism (e.g., informativity with respect to a prevalence prior).
-  The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described above).
+  The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described in the General Discussion).
 ]
@@
 
-The conceptual view of generics argues it is not desirable to define generics in the same terms as quantifiers (e.g., a truth-functional threshold on prevalence), because generics are more fundamental than quantifiers [@Leslie2008; @Gelman2009].
-For example, young children have a nearly adult-like understanding of generics far earlier than they do with quantified language [@Gelman2015].
+The conceptual view of generics argues that it is not desirable to define generics in the same terms as quantifiers (e.g., a truth-functional threshold on prevalence), because generics are more basic or more fundamental than quantifiers [@Leslie2008; @Gelman2009].
+For example, according to certain measurements, young children have a nearly adult-like understanding of generics far earlier than they do with quantified language [@Gelman2015].
 Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that same information will tend to recall quantified information as generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
-As a result, generics are thought of as conveying *default generalizations*, whereas quantified language expresses more sophisticated and specific generalizations.
-The uncertain threshold model can be viewed as a way of formalizing what constitutes a default generalization.
-For this model, the default generalization is a Bayesian belief updating mechanism via a threshold function whose threshold value is uncertain.
+As a result, generics are thought of as conveying default generalizations, whereas quantified language expresses more sophisticated and specific generalizations.
+Our formalism provides a way of quantitatively testing potential alternative formulations of such a default generalization mechanism.
+The uncertain threshold model formalizes default generalization as Bayesian belief updating via a threshold function whose threshold value is uncertain and contextually-informed via prior knowledge about properties.
 
@@
 4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
-This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar, and distinct from that of the neutral properties.
+This similar increase in endorsement for striking and distinctive properties could be explained by the prevalence prior $P(p)$ distributions for the two being similar, and distinct from that of the neutral properties.
 @Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
 
-The second mechanism by which strikingness could influence generic enodrsement is that striking properties may be projected more strongly (i.e., generalized to more instances of the category) than neutral properties.^[
+The second mechanism by which strikingness could influence generic endorsement is that striking properties may be projected more strongly (i.e., higher predictive probability that future instances will have the property) than neutral properties.^[
   This observation is also made by @Leslie2008 (p.42), who uses it as motivation for elevating striking properties to their special status in her theory.
 ]
-Interestingly, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts.
+Interestingly, evidence suggests this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5", @Rothbart1978 Expts.
 2 & 3].
-Thus, there is evidence for the influence of strikingness on *predictive prevalence*, which we posit is an intermediate representation between conceptual knowledge and generic endorsements.
-Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
-If there are none, then the effects of strikingness would be accounted for by our prevalence-mediated theory.
+Thus, there is evidence for the influence of strikingness on predictive probability, which we posit is an intermediate representation between conceptual knowledge and generic endorsements.
+
+<!-- Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
+-->
+<!-- If there are none, then the effects of strikingness would be accounted for by our prevalence-mediated theory. -->
 
@@
 
-@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), a property that bears a *principled connection* to the kind. 
+@Leslie2008's notion of characteristic properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), a property that bears a *principled connection* to the kind. 
 A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
 "Ks, by virtue of being the kind of things that they are, F" (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged"); if such a sentence is not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple bare plural is endorsed (e.g., "Barns are red"), then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
-@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties with low prevalence, striking properties, etc., see our Expt.
-1) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
+@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties with low prevalence, striking properties) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
 Additionally, there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
 
-Where do principled connections come from? 
-Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic (or having a principled connection) if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self locomotion; @Goodman1955; @Shipley1993].
+<!-- Where do principled connections come from?  -->
+Both @Prasada2006 and @Leslie2008 surmise that a property may qualify as characteristic (or having a principled connection) if there exists an overhypothesis about that property for a relavant superordinate category [e.g., each kind of animal has a means for self-locomotion; @Goodman1955; @Shipley1993].
 Overhypotheses are naturally formalized as hierarchical Bayesian models, wherein a learner acquires knowledge at multiple levels of abstraction [e.g., learning from the same event about a particular dog, dogs in general, and animals in general; @Kemp2007].
-These heirarchical models yield differences in predictive probability that are particularly robust.
-Integrating a hierarchical model of kinds and properties with our model of generic language is a natural future direction towards understanding the computational underpinnings of principled connections.
+These Bayesian heirarchical models yield differences in predictive probability that are particularly robust.
+Integrating a hierarchical model of kinds and properties with our model of generic language is a natural direction to understanding the computational underpinnings of conceptual relations and generics.
 Different conceptual structures may give rise to roughly the same distributions on prevalence and thus have similar endorsement profiles according to our model. 
 Yet the inferences that can be drawn from hearing these generics may differ, depending on their interactions with the putative hierarchical knowledge people bring to bear [a la the differences observed for "prevalence-matched items" in @Prasada2006].
-This is an intruiguing direction for future work.
+Building hierarchical models of kinds and properties is a major undertaking in its own regard, but our formalism provides a way of connecting such a model with generic language.
 
@@
 
-Cohen's and other statistical theories employ upon an additional mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
-This mechanism is called *domain restriction* and is a common feature in many theories of generics. 
-@Cohen1999 posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features (so called $Alt(F)$).
-For example, the property "lays eggs" induces a set of alternatives that are associated with modes of reproduction (e.g., "gives birth to live young", "undergoes mitosis", ...).
-"Robins lay eggs" is evaluated as an *absolute generic* as only individuals that are female members of kinds are under consideration, because only the female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery of domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual information, but the details remain obscure [@Carlson1995essay].^[
+Cohen's and other statistical theories employ a *domain restriction* mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
+@Cohen1999 posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features $Alt(F)$.
+For example, the property *lays eggs* induces a set of alternatives that are associated with modes of reproduction (e.g., *gives birth to live young*, *undergoes mitosis*, ...).
+"Robins lay eggs" (an absolute generic for @Cohen1999) is evaluated by only considering female members of kinds, because only female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
+The inferential machinery of domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual knowledge, but the details remain obscure [@Carlson1995essay].^[
   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
 ]
-The mechanism of domain restriction may be implicit in our own theory: The prior distribution over the prevalence of *lays eggs* relies upon aspects of an intuitive theory of reproduction (i.e., that only females lay eggs).
+The uncertain threshold model can be seen as one particular mechanism by which the domain may be restricted: The structure of the prior distribution over the prevalence of *lays eggs* is a reflection of an intuitive theory of reproduction (i.e., that only females lay eggs) and the uncertain threshold model uses that background knowledge to derive a property-specific interpretation.
 There may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain of restriction.
@@
 
-@Sterken2015 takes a novel starting point for her analysis: Generics are inherently context-sensitive.
-To understand the properties of generics, this analysis draws analogy to other, inherently context-sensitive linguistic expressions: *indexicals* (e.g., "this" or "I").
+@Sterken2015 develops a novel analysis taking the context-sensitivity of generics as primary.
+This analysis draws analogy to other, inherently context-sensitive linguistic expressions: *indexicals* (e.g., "this" or "I").
 @Sterken2015 uses this to motivate a context-sensitive *quantificational force* as well as mechanism of domain-restriction [of the kind used by @Cohen1999 and others].
-Our uncertain-threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive quantificational force. 
+Our uncertain threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive quantificational force. 
 We have not had need for employing domain restriction on the categories, though as noted above, it is a potential avenue for future development.
@@
 A popular alternative view under the statistical banner draws on the intuition that generics often express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008; @Nickel2016]. 
-For example, "Dogs have four legs" is a good generalization even though, regrettably, not all dogs have four legs. 
-However, were the world to function *normally* (e.g., dogs would not be involved in freak-tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs. 
-The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generalizations (e.g., "Supreme Court justices have even social security numbers") and resisting stereotyped language (e.g., "Boys are good at math”).
+"Dogs have four legs" is then a good generic not because all dogs have four legs (regrettably, all do not) but were the world to function *normally* (e.g., dogs would not be involved in freak tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs.
+The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generics (e.g., "Supreme Court justices have even social security numbers") and resisting stereotyped language (e.g., "Boys are good at math”).
 Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
@@
 By encoding knowledge about other categories, the prevalence prior distributions in the uncertain threshold model are deeply connected to the construct of *cue validity*, or the probability of the kind given the feature: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not an entity is a mosquito, upon learning that it carries malaria).
-Cue validity is believed to play a role in understanding generic language [@Leslie2007; @Khemlani2012; @Prasada2013], but the details remain obscure.
-The strongest view of cue validity is that it operationalizes an alternative hypothesis about the interpretation of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria".
+Cue validity is believed to play a role in understanding generic language [@Leslie2007; @Khemlani2012; @Prasada2013], but the details remain underspecified.
+The strongest view of cue validity is that it operationalizes an alternative hypothesis about the meaning of generic statements: "Mosquitos carry malaria" means "It is mosquitos that carry malaria". 
 Indeed, empirically-elicited cue validity has been shown to be highly correlated with endorsements of generics [@Khemlani2012].
@@
 Thus cue validity comes from a point estimate of the prevalence prior distribution.
-For a more detailed derivation of this relationship between cue validity and prevalence priors, see Appendix A.
+For a more detailed derivation of the relationship between cue validity and prevalence priors, see Appendix A.
 We discuss the implications of this relationship in the General Discussion.
-For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we construct alternative quantitative models based on empirically-elicited cue validity.
+
+### Baseline models for quantitative comparisons
+
+There are several theoretically-substantive components to our model: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) vagueness in the semantics of a generalization.
+In our empirical studies, we compare the uncertain threshold model to an alternative, lesioned model which lacks the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to a quantified statement) but which has the same prevalence prior and the decision-theoretic architecture.
+There are no correspondingly simple ways to lesion the other two components (property knowledge or speaker decision) that still produces quantitative, context-sensitive predictions. 
+Furthermore, for comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012], we construct alternative regression models based on empirically-elicited quantities (referent prevalence and *cue validity*, described below).
+In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our experimental materials. 
+These three alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions.
+
+<!-- For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we construct alternative quantitative models based on empirically-elicited cue validity. -->
+
 <!-- These control models improved the quantitative fit to the endorsement data, but did not match the explanatory power of the uncertain threshold model. -->
-
-### A unified view
-
-The statistical vs.
-conceptual distinction for theories of generics is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
-Truth conditions are unified criteria that all generics must satisfy in order to be true.
-*Genericity*, on the other hand, is thought to be a non-linguistic, psychological phenomenon previously explored either in terms of pragmatics [@Declerck1991] or meta-semantics [@Leslie2007; @Liebesman2011; @Sterken2015; @Nickel2016].
-A full account of generic language must include both a theory of generics (i.e., truth conditions) and a complementary theory of genericity [@Nickel2016].
-
-In our account, the truth conditions of generics are a function of beliefs formalized with probability, and the relevant probabilities may be informed by rich conceptual structure.
-The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.
-We chart-out a single answer to the semantic question "what do generics mean?", while also formalizing how background knowledge influences generic understanding.
-That is, our approach provides both a theory of generics and genericity, and their interaction.
-This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
 
@@
 We do this by both measuring and manipulating background knowledge and referent prevalence and predicting human endorsements of generalizations.
-
-There are several theoretically-substantive components to our model: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
-not uttering it, and (c) vagueness in the semantics of a generalization.
-Throughout our experiments, we compare the uncertain threshold model to an alternative, lesioned model which lacks the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to a quantified statement) but which has the same prevalence prior and the decision-theoretic architecture.
-There are no correspondingly simple ways to lesion the other two components (property knowledge or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.
-Furthermore, for comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012], we construct alternative regression models based on empirically-elicited quantities (referent prevalence and *cue validity*, described below).
-In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our experimental materials. 
-These three alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions.
 
@@
 
-\mht{should this be moved to the intro before other theories?}
-Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
-The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
-Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
-
 <!--
@@
 In the rest of this discussion, we further discuss our model in relation to other constructs and theoretical positions, describe how our model relates to language understanding more generally including theories of vagueness, and sketch an argument for how our formal representation of the language of generalization could provide a relatively simple acquisition problem for a language learner.
+
+## A unified model
+
+The statistical vs.
+conceptual distinction for theories of generics is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
+Truth conditions are unified criteria that all generics must satisfy in order to be true.
+*Genericity*, on the other hand, is thought to be a non-linguistic, psychological phenomenon previously explored either in terms of pragmatics [@Declerck1991] or meta-semantics [@Leslie2007; @Liebesman2011; @Sterken2015; @Nickel2016].
+A full account of generic language must include both a theory of generics (i.e., truth conditions) and a complementary theory of genericity [@Nickel2016].
+
+In our account, the truth conditions of generics are a function of beliefs formalized with probability, and the relevant probabilities may be informed by rich conceptual structure.
+The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.
+We chart-out a single answer to the semantic question "what do generics mean?", while also formalizing how background knowledge influences generic understanding.
+That is, our approach provides both a theory of generics and genericity, and their interaction.
+This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
+
+Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
+The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
+Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
 
@@
 This also means that our computational framework makes predictions about the cue validity implied by different generalizations, without any further assumptions.
+
+### Strikingness
+
+Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
+If there are none, then the effects of strikingness would be accounted for by our prevalence-mediated theory.
 

### 2018-10-11 paper/comgen-paper.Rmd
begin editing gd

@@
 That generics are vague does not preclude them from being treated by formal models. 
-A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.
+A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability, leads to complex, quantitative interactions with background knowledge.
 
@@
 
-We tested this theory by exploring its implications for the simplest judgments a person could make regarding a sentence: truth judgments.
-We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
-Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
-This framework accounts for a number of philosophically puzzling generic statements (Expt.
+We tested this theory by exploring its implications for the simplest judgments a person can make about a sentence: endorsements or truth judgments.
+Truth judgments are the standard measurement for semantic theories, but are often limited to the intuitions of a single or a small handful of trained theorists, which often produced binary or ternary judgments: true, false, and possibly indeterminate.
+In this paper, we measured the truth judgments of naive language users, revealing whole continua of gradience. 
+These fine-grained, quantitative measurements pose real challenges for a complete theory of generics and other generalizations in language. 
+The framework we propose is sufficiently precise to predict such gradience, and we showed that the gradience in truth judgments depends in systematic ways on the listener's prior beliefs about prevalence.
+
+ already exhibit complex sensitivities to context for the language of generalizations.
+Rather than leave truth judgments to the i, we measured these empirically, revealing large amounts of gradience.
+
+The uncertain threshold semantics accounts for a number of philosophically puzzling generic statements (Expt.
 1), naturally extends to other domains of generalizations (habituals and causals; Expts.
@@
 2c).
+
+We measured and modeled truth judgments in order to 
+We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
+Endorsement, we have shown, 
 We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.

### 2018-10-11 paper/comgen-paper.Rmd
minor edit

@@
 The framework we propose is sufficiently precise to predict such gradience, and we showed that the gradience in truth judgments depends in systematic ways on the listener's prior beliefs about prevalence.
-
- already exhibit complex sensitivities to context for the language of generalizations.
-Rather than leave truth judgments to the i, we measured these empirically, revealing large amounts of gradience.
+We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
+In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
+In addition, the model accounts for standard linguistic intuitions about a number of philosophically puzzling generic statements (Worked Examples).
+
+The fact that our model applies equally as well to generic and habitual language sheds light on a long-attested analogy.
+The analogy of habituality (e.g., "John runs") and genericity (e.g., "Dogs have four legs") has typically been assumed in the literature after the original suggestion by @Carlson1977.
+The relationship has been never been empirically tested nor formally described.
+This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism explains judgments of both kinds of statements (Expts.
+1 & 2).
 
@@
 
-We measured and modeled truth judgments in order to 
-We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
-Endorsement, we have shown, 
-We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
-
-The analogy of habituality (e.g., "John runs") and genericity (e.g., "Dogs have four legs") has typically been assumed in the literature after the original suggestion by @Carlson1977.
-The relationship has been never been empirically tested nor formally described.
-This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism explains judgments of both kinds of statements (Expts.
-1 & 2).
+<!-- We measured and modeled truth judgments in order to  -->
+<!-- We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization.  -->
+<!-- Endorsement, we have shown,  -->
 

### 2018-10-11 paper/comgen-paper.Rmd
finish edits to gd

@@
 Our theory posits two mechanisms by which striking properties could influence generic endorsement.
-<!-- But there are two other factors that are confounded with striking properties that make it difficult to evaluate a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
--->
 The first is the prevalence prior.
@@
 @Cimpian2010 (Expt.
-4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
+4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and explicitly distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
 This similar increase in endorsement for striking and distinctive properties could be explained by the prevalence prior $P(p)$ distributions for the two being similar, and distinct from that of the neutral properties.
@@
 
-<!--
-formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.
-
-Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
--->
-
-We tested this theory by exploring its implications for the simplest judgments a person can make about a sentence: endorsements or truth judgments.
-Truth judgments are the standard measurement for semantic theories, but are often limited to the intuitions of a single or a small handful of trained theorists, which often produced binary or ternary judgments: true, false, and possibly indeterminate.
-In this paper, we measured the truth judgments of naive language users, revealing whole continua of gradience. 
-These fine-grained, quantitative measurements pose real challenges for a complete theory of generics and other generalizations in language. 
-The framework we propose is sufficiently precise to predict such gradience, and we showed that the gradience in truth judgments depends in systematic ways on the listener's prior beliefs about prevalence.
+We tested this theory by exploring its implications for the simplest judgments a person can make about a sentence: an endorsement or truth judgment.
+Truth judgments are the standard measurement for semantic theories, but are often limited to the intuitions of a single or a small handful of trained theorists, often producing only binary or ternary judgments (i.e., true, false, and possibly indeterminate).
+In this work, we measured the truth judgments of naive language users, revealing whole continua of gradience. 
+These fine-grained, quantitative measurements pose real challenges for verbal theories of generics, which can only predict qualitative differences.
+The framework we propose is sufficiently precise to predict quantitative gradience, and we showed that the gradience in truth judgments depends in systematic ways on an interpreter's prior beliefs about prevalence.
 We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
@@
 
-The fact that our model applies equally as well to generic and habitual language sheds light on a long-attested analogy.
-The analogy of habituality (e.g., "John runs") and genericity (e.g., "Dogs have four legs") has typically been assumed in the literature after the original suggestion by @Carlson1977.
-The relationship has been never been empirically tested nor formally described.
+The fact that our model applies equally as well to generic and habitual language sheds light on a long-attested relationship.
+The analogy of habituality (e.g., "John runs") and genericity (e.g., "Dogs have four legs") has typically been assumed in the literature following the original suggestion by @Carlson1977.
+The relationship, however, has been never been empirically tested nor formally described.
 This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism explains judgments of both kinds of statements (Expts.
@@
 
-The uncertain threshold semantics accounts for a number of philosophically puzzling generic statements (Expt.
-1), naturally extends to other domains of generalizations (habituals and causals; Expts.
-2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt.
-2c).
+In our model, a generic statement or other generalization updates a listener's *a priori* beliefs about the prevalence of the property for that category. 
+Since the prevalence prior includes the information necessary to compute cue validity (see Appendix A), the cue validity of the feature for the new category is added to the common ground between interlocutors.
+Thus, given the knowledge represented in a prevalence prior, generics communicate information both about the prevalence of the feature in the new category (via the literal semantics) as well as the cue validity of the feature for the new category.
+For example, if a listener hears "Alligators grow to be 10-feet long", they will update their personal beliefs both about the prevalence of 10-footedness among alligators as well as the probability that an animal is an alligator given that it is 10 feet long.
+To our knowledge, this is the first theory of generics that describes how the informational contribution of a generic relates to cue validity.^[
+  We are grateful to an anonymous reviewer for drawing our attention to this. 
+]
+This also means that our computational framework makes predictions about the cue validity implied by different generalizations, without any further assumptions.
+
+We propose that the language of generalization conveys predictive probabilities.
+Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
+Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
+Rather than conveying probabilities explicitly, the language of generalization conveys them implicitly.
+In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
+The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
+Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
+
+In the rest of this discussion, we further discuss the contribution of our modeling framework to empirical and theoretical work on the language of generalization, elaborate further on the role of conceptual knowledge in our modeling framework, describe how our model relates to language understanding more generally including theories of vagueness, and sketch an argument for how our formal representation of the language of generalization could provide a relatively simple acquisition problem for a language learner.
 
@@
 This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
-These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
-Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
+Prevalence in our model is not an observable frequency---the object of other statistical approaches to generics---but a mental representation.
+These probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
 Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
-What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.
--->
-
-Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
-Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995].
-Rather than conveying probabilities explicitly, generalizations convey them implicitly.
-In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
-The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
-Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].
-
-In the rest of this discussion, we further discuss our model in relation to other constructs and theoretical positions, describe how our model relates to language understanding more generally including theories of vagueness, and sketch an argument for how our formal representation of the language of generalization could provide a relatively simple acquisition problem for a language learner.
+What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability.
+-->
 
@@
 The statistical vs.
-conceptual distinction for theories of generics is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
+conceptual distinction for theories of generics, described earlier in this paper, is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
 Truth conditions are unified criteria that all generics must satisfy in order to be true.
-*Genericity*, on the other hand, is thought to be a non-linguistic, psychological phenomenon previously explored either in terms of pragmatics [@Declerck1991] or meta-semantics [@Leslie2007; @Liebesman2011; @Sterken2015; @Nickel2016].
+*Genericity*, on the other hand, is thought to be a non-linguistic, psychological phenomenon previously explained either in terms of pragmatics [@Declerck1991] or meta-semantics [@Leslie2007; @Liebesman2011; @Sterken2015; @Nickel2016].
 A full account of generic language must include both a theory of generics (i.e., truth conditions) and a complementary theory of genericity [@Nickel2016].
 
-In our account, the truth conditions of generics are a function of beliefs formalized with probability, and the relevant probabilities may be informed by rich conceptual structure.
-The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.
-We chart-out a single answer to the semantic question "what do generics mean?", while also formalizing how background knowledge influences generic understanding.
-That is, our approach provides both a theory of generics and genericity, and their interaction.
+Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
+The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold function) from world knowledge (represented by the prevalence prior).
+We, thus, chart-out a single answer to the semantic question "what do generics mean?", while also formalizing how background knowledge influences generic understanding (a question about genericity).
+Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
+The modeling approach we take here demonstrates how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
+<!-- That is, our framework provides both a theory of generics and genericity, and their interaction. -->
 This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
 
-Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
-The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
-Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
-Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.
+<!-- That is, the truth conditions of generics are a function of beliefs formalized with probability, and the relevant probabilities may be informed by rich conceptual structure. -->
+<!-- The separation between conceptual structure (which exists in the mind) and prevalence (a quantitative metric for natural language semantics) provides a unified view for the phenomenology of generics.
+-->
 
@@
 
-## Prevalence priors, conceptual knowledge, and cue validity
+## The role of conceptual knowledge
 
 Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
-It is this real-world knowledge (presently formalized in terms of a *prevalence prior*) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
+It is this real-world knowledge (presently formalized in terms of a prevalence prior) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
 <!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
 <!-- Instead,  -->
-We hypothesize that all of this knowledge feeds into participants' predictions, or judgments about prevalence.
+We hypothesize that all of this knowledge feeds into participants' predictions, measured through judgments about prevalence.
 <!-- which we model in a precise, quantitative manner. -->
-This framework, thus, brings precision and clarity to the *output* of these cognitive processes and conceptual understanding: participants' intuitions about prevalence.
+This framework, thus, brings precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
 Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
@@
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and then endorse the generic.
-
-Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
-Like other models in the probabilistic pragmatic tradition, our model distinguishes the relevant variables for the truth-functional semantics from those that impact the speaker's utility in producing the utterance.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compell an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and endorse such a generic.
+
+Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what a speaker intends to communicate.
+Like other models in the probabilistic pragmatics tradition, our model distinguishes the relevant variables for the truth-functional semantics (e.g., a threshold and a prevalence) from those that impact the speaker's utility in producing the utterance.
 A speaker's utility comes from addressing an implicit goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
@@
 For simplicity, the model presented here assumes the QUD is about prevalence.
-However, the model makes nearly identical predictions if the QUD concerns the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
-This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.
-
-In our model, a generic statement or generalization updates a listener's *a priori* beliefs about the prevalence of the property for that category. 
-Since the prevalence prior includes the information necessary to compute *cue validity* (Appendix A), the cue validity of the feature for the new category is added to the common ground between interlocutors.
-Thus, given the knowledge represented in a prevalence prior, generics communicate information both about the prevalence of the feature in the new category (via the literal semantics) as well as the cue validity of the feature for the new category.
-To our knowledge, this is the first theory of generics that describes how the informational contribution of a generic relates to cue validity.^[
-  We are grateful to an anonymous reviewer for drawing our attention to this. 
-]
-This also means that our computational framework makes predictions about the cue validity implied by different generalizations, without any further assumptions.
-
-### Strikingness
-
-Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
-If there are none, then the effects of strikingness would be accounted for by our prevalence-mediated theory.
+However, the model makes nearly identical predictions if the QUD concerns abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
+This observation may prove useful for constructing models of speakers whose goals are to convey abstract relations between kinds and properties.
+
+Conceptual knowledge concerning the strikingness or dangerousness of properties and their relation to generic language has been of particular interest to psychologists and philosophers since @Leslie2007.
+We described before that the strikingness of certain properties plausibly influences prevalence priors or a speaker's predictions about future prevalence.
+We have pilot data suggested these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
+More empirical work is needed to understand the conditions under which strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.
+<!-- If such effects exist, our modeling framework could be elaborated with a non-informational speaker utility [see e.g., @Yoon2016; @Yoon2017]. -->
 
@@
 Additionally, Sorites paradoxes can be constructed out of arguments using vague predicates, and it is not clear that generics or habituals could be used to construct such arguments.
-We note that no experimental data yet bears on these ideas and could be useful for understanding how far the relationship between generalizations and vague predicates goes.
+No experimental data yet bears on these ideas, but would be useful for further understanding the relationship between generalizations and vague predicates.
 
 For now, we understand both genericity and vagueness as analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions (e.g., an uncertain threshold).
-We note that this sort of "lexical uncertainty" is kind of *parameter learning* problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a *structure learning* problem (e.g., lexical ambiguity).
+We note that this sort of "lexical uncertainty" is a kind of *parameter learning* problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a *structure learning* problem (e.g., lexical ambiguity).
 Further work should be done to better understand the kinds of context-sensitive linguistic phenomena that are modeled as parameter vs. structure learning problems.
@@
 Listeners then will not know exactly what kind of speaker they are dealing with *a priori* and normatively should maintain uncertainty about the truth conditions. 
-In our model, world knowledge and general communicative principles help a listener resolve the value of threshold.
+In our model, world knowledge and general communicative principles help a listener resolve the value of threshold [see @Lassiter2015 for an extended discussion of resolving the value of a free semantic variable in context].
 
 ## Acquiring the language of generalization
-
-\mht{added a footnote and tweaked paragraphs 1 and 2}
 

### 2018-10-12 paper/comgen-paper.Rmd
tweaks to abstract, intro, model, habitual scale paragraph

@@
 Though found in every language and emerging early in development, the language of generalization is philosphically puzzling and has resisted precise formalization.
-Here, we propose the first formal account of the language of generalization that makes quantitative predictions about human understanding.
+Here, we propose the first formal account of generalizations conveyed with language that makes quantitative predictions about human understanding.
 We test our model in three diverse domains: generalizations about categories (generic language), events (habitual language), and causes (causal language).
-The model explains the gradience in human endorsement through the interplay between a simple truth-conditional semantic theory and diverse beliefs about properties.
+The model explains the gradience in human endorsement through the interplay between a simple truth-conditional semantic theory and diverse beliefs about properties, formalized in a probabilistic model of language understanding.
 This work opens the door to understanding precisely how abstract knowledge is learned from language.
@@
 The *language of generalization* covers a diverse swath of natural language expressions.
-Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case in the language of generalization.^[
+Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case generalizations in language.^[
   Some writers refer to the all of the *language of generalization* as "generic language" or generics.
@@
 "Mosquitos carry malaria" sounds true despite malaria being present in only a tiny fraction of mosquitos. 
-Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a bad sentence even if it were the case that on the current bench, nine out of nine justices have even social securtity numbers [i.e., when the sentence "All Supreme Court Justices have even social security numbers" is true; @Cohen1999].
-Similar context-sensitivity can be observed with habituals: Say Mary climbed mountains three times last year, the habitual "Mary climbs mountain" seems well-supported. 
-Yet, if John went for a run three times in the last year, we probably should not say that "John runs".
+Even more perplexing: "Supreme Court Justices have even social security numbers" is thought to be intuitively a false generalization even if it were the case that on the current bench, nine out of nine justices had even social securtity numbers [i.e., when the sentence "All Supreme Court Justices have even social security numbers" is true; @Cohen1999].
+Similar context-sensitivity can be observed with habituals: "Mary climbs mountains" could imply a few mountain climbs a year for Mary, but "John runs" would be infelicitious if John went for a run three times last year.
 
@@
 
-These observations have led some to conclude that the literal meaning of a generic statement involves more than just the number of members of the category who have the property, otherwise known as the *prevalence* of the feature in the category.
+These observations have led some to conclude that the literal meaning of a generic statement (and by analogy, other generalizations in language) involves more than just the number of members of the category who have the property, otherwise known as the *prevalence* of the feature in the category.
 <!-- (or the probability of a member of the category having the property e.g.,  $P(x \text{ is friendly} \mid x \text{ is a dog})$) is not sufficient to make generalizations ("Dogs are friendly") true or false.
 -->
-Instead, generic statements are thought of semantically as a direct, linguistic manifestation of abstract relations between kinds and properties [@Leslie2008; @Prasada2000; @Prasada2012]. 
+Instead, theorists have argued that generics are not treatable by the standard tools of truth-functional semantics [@Montague1973], but rather should be thought of semantically as a direct, linguistic manifestation of abstract relations between kinds and properties [@Leslie2008; @Prasada2000; @Prasada2012].
 <!-- Conceptual accounts of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012].
@@
 <!-- Indeed, generics can be true for a range of prevalence or frequency levels [@Khelmani2012; @Prasada2013]. -->
-For example, the statements "Bishops move diagonally" or "The Speaker of the House succeeds the Vice President" are true not because of a tendency on behalf of the category to uphold the property, but rather the existence of a conceptual relationship (e.g.,  what it means, in the game of chess, to be a bishop).
+For example, the statements "Bishops move diagonally" or "The Speaker of the House succeeds the Vice President" are true not because of a tendency on behalf of instances of a category to actually uphold the property, but rather the existence of a conceptual relationship (e.g.,  what it means, in the game of chess, to be a bishop).
 True generics can be supported by different underlying types of category--property relations [e.g., principled vs.
@@
 Insofar as there is a single class of linguistic expressions that convey generalization, however, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
-In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
-A semantics based on probability will not be enough, however.
+In this paper, we propose such a semantic core based on prevalence or probability and formalized using the tools of truth-functional semantics [@Montague1973; @Cohen1999].
+A semantics based on probability will not be enough to subtle sensitivities to context that the language of generalization exhibit.
 We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using world knowledge.
@@
 The paper is organized as follows. 
-In Section 1, we describe the computational model of interpreting generalizations which has three components: Probability, vagueness, and context. 
-<!-- formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge is formally described.
--->
-Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgments about the truth or acceptibility of a sentence.
-We sketch out a number of worked examples to qualitatively demonstrate the model's behavior and the describe the relation of our model to previous linguistic and philsophical approaches to generics.
-The model as articulated predicts fine-grained, quantitative effects of background knowledge, which we both measure and manipulate across our three empirical case studies (Sections 2-4): generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*).
+In the next section, we describe our computational framework for interpreting generalizations and our precise model for endorsing such statements (i.e., a model of truth judgments).
+To illustrate how the model works, we then work through a number of standard examples from the linguistics literature that any model of generics should be able to accomodate.
+The third section discusses the relationship of our model to previous accounts of generics from the linguistics and philosophical literatures. 
+These introductory sections are followed by three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+In the case study of generics, we use measure relevant background knowledge and prevalence to predict endorsements of familiar generic statements (e.g., "Robins lay eggs").
+In the study of habituals, we measure background knowledge but manipulate the prevalence or frequency of the event to predict endorsements of habitual statements about novel agents (e.g., "John runs" given that he's run a certain number of times in the past).
+In this case study, we also further examine the nature of the relevant probabilities for endorsing generalizations, asking whether it matters how often John has run in the past (past frequency) or how often a speaker expects him to run in the future (predictive probability).
+Finally, in our last case study, we manipulate background knowledge to show its causal influence on endorsing generalizations about novel causal events (e.g., "Herb X makes wugs sleepy"). 
 We compare our model to two previously articulated quantitative models of generics as well as a lesioned-version of our model.
@@
 We conclude our paper by clarifying some of the theoretical claims of the model and discuss open-questions for this approach.
+
+<!-- formalizes the hypothesis that the core meaning of a generalization in language is a vague probability and articulates it in a model of language understanding in which relevant background knowledge is formally described.
+-->
+<!-- Having defined a model of interpretation, we then describe an information-theoretic, communicative linking function from interpretation to judgments about the truth or acceptibility of a sentence.
+-->
+<!-- We sketch out a number of worked examples to qualitatively demonstrate the model's behavior and the describe the relation of our model to previous linguistic and philsophical approaches to generics.
+-->
+
+<!-- The model as articulated predicts fine-grained, quantitative effects of background knowledge, which we both measure and manipulate across our  -->
 
@@
 Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
-Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Staring at the sun makes you go blind"). 
+Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Fire causes smoke"). 
 Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
@@
 The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
-For example, the literal meaning of the sentence "Some dogs have four legs" is that there is a non-zero chance that an individual dog will have four legs: $\denote{some}(p) := p > 0$.
+For example, the literal meaning of the sentence "Some dogs have four legs" is that there is a non-zero chance that a given dog will have four legs: $\denote{some}(p) := p > 0$.
 "Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.^[
-  We are describing the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
+  These definitions concern the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
 ]
@@
 
-The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics and, thus, naturally extends to generalizations of different semantic types.
-For example, if we take underlying semantic scale (formally, the support of $P(p)$) to be that of the temporal frequency of an event (e.g., how often we expect an event to occur), then Eq.
-\ref{eq:L0} describes a model of habitual interpretation (e.g., "John smokes").
-In this case, $p$ is naturally thought of as a rate (e.g., the frequency of an event within a certain time window).
+The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics.
+The prevalence prior $P(p)$ is a distribution over probabilities $p$, which is be the output of a generative model of particular domain.
+For properties of objects, the generative model is naturally a Bernoulli model (e.g., flipping a coin) and thus the support of $P(p)$ is $[0, 1]$.
+For events, the implicit generative model is a Poisson model in which events occur randomly in time.
+The probability density of an event occurring at a particular time is governed by the rate parameter for the Poisson model. 
+Thus, Eq.
+\ref{eq:L0} becomes a model of habitual interpretation (e.g., "John runs") if we take the underlying semantic scale to be that of the temporal frequency of an event (e.g., how often we expect an event to occur); the support of $P(p)$ is this case would be $[0, \infty]$.
 
@@
 
-## Relationship to other semantic theories
+# Relationship to other semantic theories
 
@@
 
-### Conceptual accounts
+## Conceptual accounts
 
@@
 
-#### Default generalizations
+### Default generalizations
 
@@
 
-#### Striking generics
+### Striking generics
 
@@
 
-#### Principled and statistical connections
+### Principled and statistical connections
 
@@
 
-### Statistical accounts
-
-#### Relative and absolute generics
+## Statistical accounts
+
+### Relative and absolute generics
 
@@
 
-#### Cue validity
+### Cue validity
 
@@
 
-### Baseline models for quantitative comparisons
+## Baseline models for quantitative comparisons
 
@@
 
-### Intermediate summary
+## Intermediate summary
 

### 2018-10-13 paper/comgen-paper.Rmd
tweak final graf before examples

@@
 The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics.
-The prevalence prior $P(p)$ is a distribution over probabilities $p$, which is be the output of a generative model of particular domain.
+The prevalence prior $P(p)$ is a distribution over probabilities $p$, which represents the output of a generative model of particular domain.
 For properties of objects, the generative model is naturally a Bernoulli model (e.g., flipping a coin) and thus the support of $P(p)$ is $[0, 1]$.
@@
 
-The goal of the endorsement model is to align the listener's beliefs about prevalence (given by the *prevalence prior*) with the speaker's beliefs about the prevalence of the feature in the category being referred to, which we call the *referent prevalence* ($p$; e.g., that 50% of robins lay eggs).
+The goal of the endorsement model is to align the listener's *a priori* beliefs about prevalence (given by the prevalence prior) with the speaker's beliefs about the prevalence of the feature in the referent category $p$, the *referent prevalence* (e.g., that 50% of robins lay eggs).
 ^[
-  A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $p$ that it wants to communicate.
-  Rather, the endorser may have a distribution over $p$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence of the property for the referent category. 
+  A more general version of this model can relax the assumption that the endorser / speaker has access to a specific prevalence $p$ that it wants to communicate.
+  Rather, the endorser may have probabilistic beliefs about the prevalence of the property for the referent category $k$, which would be represented by a distribution over $p$: $P(p \mid k)$. 
   In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorsement model's belief distribution:
-  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} L(p, \theta \mid u)} \diff \theta )}$
+  $S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} L(p, \theta \mid u)} \diff \theta )}$.
   For the empirical case studies described below, these two versions of the model make almost identical predictions.
 ]
-Given that the speaker only has two options (i.e., produce the generalization utterance or stay silent), the endorsement decision comes down to whether or not the referent prevalence is more likely under the prevalence prior distribution $P(p)$ (i.e., the listener's posterior upon hearing silence) or the listener generic interpretation distribution given by Eq.
-\ref{eq:L0} (Figure\ \@ref(fig:uniformPriorSimulation)C).
-Thus, the communication-relevant content of the generalization is the prevalence in the referent category $p$.
-The semantic threshold $\theta$ is necessary for establishing the precise truth conditions (used in Eq.
+The endorsement model makes an approximately rational (with degree of rationality $\lambda$), information-theoretic decision based on its beliefs about which utterance would best achieve the goal of conveying the referent prevalence $p$.
+The semantic threshold $\theta$ is necessary for establishing the truth conditions and deriving an interpretation (used in Eq.
 \ref{eq:L0}) but is otherwise a nuisance parameter, which the endorsement model integrates out (note that there is no $\theta$ in the left-hand side of Eq.
 \ref{eq:S1}).
-Finally, because Eq.
-\ref{eq:S1} models an information-theoretic speaker's decision, $S_1$ computes a belief distribution and then produces utterances which are approximately rational according to that belief distribution, via a soft-max function with degree of rationality $\lambda$.
-\mht{better?}
+Given that the speaker only has two options (i.e., produce the generalization utterance or stay silent), the endorsement decision comes down to whether or not the referent prevalence is more likely under the prevalence prior distribution $P(p)$ (i.e., the listener's posterior upon hearing silence) or the listener generic interpretation distribution $L(p \mid u)$ given by Eq.
+\ref{eq:L0} (Figure\ \@ref(fig:uniformPriorSimulation)C).
 In the next section, we work through different examples from the linguistics literature, describing the prevalence prior and other relevant model components for each.

### 2018-10-13 paper/comgen-paper.Rmd
clean up worked examples

@@
 \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...}
-The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).
+The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
+  Alternatively, the prevalence prior can be conceptualized as one aspect of an intuitive theory of a domain. 
+]
 <!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
-For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0 (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
-Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.
+For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
+Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
 Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
@@
   `intuitive truth value` = c(
-    "T", "F",  "T", "U",
-    "T", "F","T", "F", "T" 
+    "True", "False",  "True", "False",
+    "True", "False","True", "False", "True" 
   ),
@@
 worked.examples.tab <- xtable::xtable(worked.examples, 
-                       caption = "Example generalizations that a theory of generics should correctly predict. See details of each example in corresponding section.", 
+                       caption = "Example sentences that a theory of generalizations should correctly predict. See details of each example in corresponding section.", 
                        align=c('| p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))
@@
 The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean *almost all* kangaroos have spots.
-The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it is too strong a statement and would mislead the listener.
+The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would lead to a too-strong interpretation and mislead the listener.
 
@@
 As described above, the priors are different: Many animals have zero egg-layers (0% prevalence), while the vast majority of animal categories have female members in exactly the same proportion (50%).
-Given this background knowledge, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes 50% have the property.
-However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would be more aligned with the referent prevalence than if the endorsement model produced the null utterance, which would instead return the prior.
-In contrast, "Robins are female" does not carry any information (the listener posterior is not different from the prior); here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5 (i.e., *neither true nor false*).
-Indeed, previous studies on generic endorsements have found "Robins are female" to receive an intermediate endorsement level [@Prasada2013].
+Given this background knowledge, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes roughly 50% have the property.
+However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would be more aligned with the referent prevalence in comparison to the interpretation of the null utterance, which is the prevalence prior.
+In contrast, the hypothetical generic interpretation of "Robins are female" is not different from the prevalence prior and hence the generic conveys no new information; here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5.
+Indeed, previous studies on generic endorsements have found "Robins are female" to not be rated as completely false but rather receive an intermediate endorsement level [i.e., *neither true nor false*; @Prasada2013].
 
@@
 
-Finally, the statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are actually malaria-free.
-The prevalence prior for "carries malaria" is highly skewed towards low prevalence levels: many animals do not have malaria-carriers among them and even for those that do, the prevalence is expected to be quite low.
+The statement "Mosquitos carry malaria" is intuitively true in spite of the fact that the vast majority of mosquitos are actually malaria-free.
+The prevalence prior for *carries malaria* is highly skewed towards low prevalence levels: many animals do not have malaria-carriers among them and even for those that do, the prevalence is expected to be quite low.
 Then, carrying malaria is significantly more true of mosquitos than other animals, an intuition that is often arrived at with this example.
@@
 
-When the prevalence of the feature is very high, it is also not necessary for the model to endorse the generic.
+When the prevalence of the feature is very high, it is not necessary for the model to endorse the generic.
 "Sharks don't eat people" is predicted to be a somewhat strange utterance, despite the fact that the vast majority of sharks do not eat people.^[
  We create this example as the converse of the classic example "Sharks eat people", predicted to be *true* despite low prevalence [@Leslie2007].
-We reverse this example to show how the model deals with a high-prevalence feature that is predicted to be false or infelicitous.
+We reverse this example to show how the model deals with a high-prevalence feature for which the generic is predicted to be false or infelicitous.
 ] 
 <!-- Yet, intuitively, the generic would be misleading (similar in intuition to "Kangaroos have spots"). -->
-Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people, which is too strong.
+Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that *no* sharks eat people (i.e., 100% don't eat people), which is too strong.
 It is interesting to note that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 40% (i.e., somewhat false).
-We will test this quantitative prediction in Case Study 1 on generics.
+We will test this quantitative prediction in Experiment 1 on generic language.
 
@@
 
-\mht{do we want an example of a habitual or a minimal pair of habituals (e.g., sally hikes vs. climbs mountains)?}
-
 **7. Mary handles the mail from Antarctica (*yet has never had the opportunity*).**
@@
 In other words, the statement "Mary has handled mail from Antarctica" is false.
-"Mary handles the mail from Antarctica" is still thought to be intuitively true despite zero actual instances of the event.
-This highlights an important ambiguity in the theoretical commitments of the uncertain threshold model: The endorsement model aims to communicate some referent prevalence $p$, but does the prevalence represent the actual, objective frequency in the world (e.g., the number of times Mary has handled mail in the past) or a subjective, predictive degree of belief in the head (e.g., our prediction that were the appropriate situation to arise, Mary would be handling the mail from Antarctica)?
+"Mary handles the mail from Antarctica", however, is still thought to be intuitively true despite zero actual instances of the event.
+This highlights an important ambiguity in the theoretical commitments of the uncertain threshold model: The endorsement model aims to communicate some referent prevalence $p$, but does the prevalence represent the actual, objective frequency in the world (e.g., the number of times in the past that Mary has handled mail from Antarctica) or a subjective, predictive degree of belief in the head (e.g., our prediction that were the appropriate situation to arise, Mary would be handling the mail from Antarctica)?
 
@@
 <!-- We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary.  -->
-Thus the predictive probability that Mary will handle Antarctican mail, if there is any, is high.
+Thus the predictive probability that Mary will handle Antarctican mail, should there be some, is high.
 Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
 In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
-We explore this question experimentally in Case Study 2 on habituals.
+We explore this question experimentally in Exerpiment 2 on habituals.
 
@@
 
-Imagine that every current and past Supreme Court Justice has had a social security number which was an *even number*. 
+Imagine that all current Supreme Court Justice has a social security number which was an *even number*. 
 "Supreme Court Justices have even social security numbers" is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
 We predict the rejection of even social security numbered Justices is the result of our intuitive theories guiding our subjective predictive probabilities, which feed into the endorsement model.
-That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability that the *next* justice would have an even social security number.
+That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability to the *next* justice having an even social security number.
 Then, "Supreme Court Justices have even social security numbers" would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
-This example is thus the conceptual opposite of Mary the Antarctic mail handler, where our internal model of the world led us to a strong degree of belief in the property holding in the future; with the Supreme Court Justices, our internal models lead to to weak degree of belief in the property holding in the future.
+This example is thus the conceptual opposite of Mary the Antarctic mail handler, where our internal model of the world led us to a strong degree of belief in the property holding in the future; with the Supreme Court Justices, our internal models lead to a relatively weak degree of belief in the property holding in the future.
 
@@
 Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
-@Nickel2008 suggests that "Elephants live in Africa and Asia" is semantically equivalent to: "Elephants live in Africa and elephants live in Asia".
-Statistical accounts of generics have trouble with this kind of conjunction because they historically have appealed to fixed, truth-conditional cutoffs for generics [e.g., generic means *more than half*; @Cohen1999].
+@Nickel2008 suggests that "Elephants live in Africa and Asia" is troubling for prevalence-based accounts [in particular, majority-quantificational accouts where the generic means *more than half*; @Cohen1999] because the statement should be semantically equivalent to "Elephants live in Africa and elephants live in Asia".
 It cannot be the case that most (more than half of) elephants live in Africa and *most* (more than half of) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
@@
 -->
+
 Our theory does not provide a fixed semantics for generics, but an uncertain one which can be updated as more information comes in.
 In fact, with prior knowledge suggesting against the existence of international elephants (Figure\ \@ref(fig:elephants)A), our model interprets "Elephants live in Africa and Asia" as meaning that some elephants live in Africa and that different ones live in Asia (Figure\ \@ref(fig:elephants)C).
-Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only that "Elephants live in Africa") leads our model to believe that *most* elephants live in Africa (Figure\ \@ref(fig:elephants)B).
+Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only that "Elephants live in Africa") leads our model to believe that *most*, possibly all, elephants live in Africa (Figure\ \@ref(fig:elephants)B).
 When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa and others in Asia (Figure\ \@ref(fig:elephants)C).
 The flexibility of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
-We leave for future work the testing of quantitative predictions for this kind of example.
+From a compositional perspective, this is highly desirable behavior but we leave the testing of quantitative predictions of this kind for future work.
 

### 2018-10-14 paper/comgen-paper.Rmd
clean up leslie sec

@@
 Our formal theory builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
-The main approaches from formal semantics try to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
-These views are typically *statistical* in nature in that they appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
-Many of these theories rely upon mechanisms outside of the truth conditions to make sense of the extreme flexibility exhibited by generics; unfortunately, these extra-semantic mechanisms are not described in any detail to make precise, quantitative predictions.
-Other theorists, primarily in philosophy and psychology, have taken the extreme flexibility of generics to argue against a quantitative theory based on statistics, instead arguing that abstract, mental representations are directly tied to semantics of generics (e.g., *there is something about being a K which causes it to F*).
+The dominant approaches from formal semantics try to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
+These views are typically *statistical* in nature in that they appeal to quantification or the statistics of the world (e.g., how many of the kind have the property) to define those unified, objective criteria.
+Many of these theories rely upon mechanisms outside of the truth conditions to make sense of the extreme flexibility exhibited by generics; unfortunately, these extra-semantic mechanisms are not described in sufficient detail to generate precise, quantitative predictions.
+Other theorists, primarily in philosophy and psychology, have taken the extreme flexibility of generics to argue against a quantitative theory based on statistics, instead suggesting that abstract, mental representations are directly tied to semantics of generics (e.g., *there is something about being a K which causes it to F*).
 Statistical and conceptual theories express the major contrasting views of generic language [@Carlson1995essay].^[
@@
 
-The *default generalization* mechanism has three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
+The *default generalization* mechanism has three components: the ability to (i) identify whether or not a feature is a *characteristic* property of a kind (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not a feature is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (instances of the kind which do not have the feature) into positive and negative counterinstances (i.e., instances of the kind which have some relevant alternative feature and instances of the kind which simply lack the feature, respectively).^[
   This positive vs.
-negative counterinstance distinction is a rather technical consideration [though not without psychological foundation, see @Leslie2008, p.36] used to account for the difference between examples like "Birds lay eggs" vs.
-"Birds are female".
-  For the latter, male birds are positive counterinstances because they have an alternative property (being male). 
-  For the former, male birds are negative counterinstances because they simply lack the property (i.e., male birds do not reproduce by some other method).
-  We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by a different mechanism (e.g., informativity with respect to a prevalence prior).
-  The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described in the General Discussion).
+negative counterinstance distinction is a rather technical consideration [though not without psychological foundation, see @Leslie2008, p.36] used to account for the difference between examples like "Robins lay eggs" vs.
+"Robins are female".
+  For "Robins are female", male robins are positive counterinstances because they have an alternative property (being male). 
+  For "Robins lay eggs", male robins are negative counterinstances because they simply lack the property (i.e., male robins do not reproduce by some other method).
+  We will not discuss this consideration any further other than to note that that the difference between "Robins lay eggs" and "Robins are female" can be explained by a different mechanism (e.g., informativity with respect to a prevalence prior).
+  The notion that alternative features may come into play in generic interpretation may also be addressed with prevalence priors constructed with respect to the feature (described in the General Discussion).
 ]
-On this account, generics are true if *some* Ks have F when all counterinstances are negative and the property is either characteristic or striking. 
-If the property is neither characteristic nor striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").
+On this account, generics are true if *some* instances of the kind have the feature when all counterinstances are negative counterinstances and the property is either characteristic or striking. 
+If the property is neither characteristic nor striking, then *almost all* instances of the kind must have the feature for the generic to be true (e.g., "Barns are red").
 Many of the key factors in this conceptual approach are compatible with our view of prevalence as a predictive probability: What is required is that the distinctions made by conceptual accounts influence predictive probability, which mediates linguistic effects.
@@
 As a result, generics are thought of as conveying default generalizations, whereas quantified language expresses more sophisticated and specific generalizations.
-Our formalism provides a way of quantitatively testing potential alternative formulations of such a default generalization mechanism.
-The uncertain threshold model formalizes default generalization as Bayesian belief updating via a threshold function whose threshold value is uncertain and contextually-informed via prior knowledge about properties.
+Rather than be contradictory, our model can be seen as formalizing a default generalization as Bayesian belief updating via a threshold function whose threshold value is uncertain and contextually-informed via prior knowledge about properties.
+Alternative formulations of such a default generalization mechanism could be proposed and quantitatively tested against our account.
 

### 2018-10-15 paper/comgen-paper.Rmd
finish polishing alt theories; expand interim summary to include overview of experiments

@@
 As a result, generics are thought of as conveying default generalizations, whereas quantified language expresses more sophisticated and specific generalizations.
-Rather than be contradictory, our model can be seen as formalizing a default generalization as Bayesian belief updating via a threshold function whose threshold value is uncertain and contextually-informed via prior knowledge about properties.
+Rather than be contradictory, our model can be seen as formalizing a default generalization as Bayesian belief updating via a threshold function whose threshold value is contextually-informed via knowledge about properties.
 Alternative formulations of such a default generalization mechanism could be proposed and quantitatively tested against our account.
@@
 
-The evolutionary argument for accepting striking generics (e.g., "Tigers eat people") is straightforward: These are relevant properties to know about if you want to survive. 
-Our theory posits two mechanisms by which striking properties could influence generic endorsement.
-The first is the prevalence prior.
-Striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
-Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*).
+@Leslie2008 posits a special mechanism to treat generics about striking properties (e.g., "Rottweilers maul children"), which seem to be acceptable even when the prevalence of the property is quite low (e.g., very few rottweilers maul children).
+Indeed, @Cimpian2010 found participants willing to endorse generics about striking properties (e.g., "Lorches have dangerous feathers") more so than that of neutral properties (e.g., "Lorches have purple feathers") at low levels of prevalence (e.g., when only 30% of the category had the property).
+@Leslie2008's argument for accepting striking generics is straightforward: These are relevant properties to know about if you want to survive. 
+Our theory posits two mechanisms by which striking properties could influence generic endorsement: the prevalence prior and the referent prevalence.
+
+The first observation is that striking properties are relatively rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
+Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive, as we have assumed in our worked example of "Mosquitos carry malaria".
 <!-- ; see also our Expt. 2a, e.g., the distributions for *steals cars* vs. *climbs mountains* for an example with habituals).  -->
-@Cimpian2010 (Expt.
-4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and explicitly distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
-This similar increase in endorsement for striking and distinctive properties could be explained by the prevalence prior $P(p)$ distributions for the two being similar, and distinct from that of the neutral properties.
 @Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.
 
-The second mechanism by which strikingness could influence generic endorsement is that striking properties may be projected more strongly (i.e., higher predictive probability that future instances will have the property) than neutral properties.^[
+The second mechanism by which strikingness could influence generic endorsement in our model is by speakers having a distorted perspective of how prevalent these features are within the referent category.
+That is, striking properties may be projected more strongly (i.e., higher predictive probability that future instances will have the property) than neutral properties.^[
   This observation is also made by @Leslie2008 (p.42), who uses it as motivation for elevating striking properties to their special status in her theory.
 ]
-Interestingly, evidence suggests this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5", @Rothbart1978 Expts.
+Interestingly, evidence suggests this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral, distinctive properties [e.g., people taller than 6'5", @Rothbart1978 Expts.
 2 & 3].
 Thus, there is evidence for the influence of strikingness on predictive probability, which we posit is an intermediate representation between conceptual knowledge and generic endorsements.
-
+It is beyond the scope of this paper to directly attempt to empirically distinguish these two potential mechanisms, though our experiments use a number of striking properties for which we measure the prevalence prior and referent prevalence.
+
+ <!-- (Expt. 4) -->
+<!-- and explicitly distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers").
+-->
+<!-- This similar increase in endorsement for striking and distinctive properties could be explained by the prevalence prior $P(p)$ distributions for the two being similar, and distinct from that of the neutral properties.
+-->
+<!-- The first is the prevalence prior. -->
 <!-- Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.
@@
 
-@Leslie2008's notion of characteristic properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), a property that bears a *principled connection* to the kind. 
-A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
-"Ks, by virtue of being the kind of things that they are, F" (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged"); if such a sentence is not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple bare plural is endorsed (e.g., "Barns are red"), then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
-@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties with low prevalence, striking properties) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
+@Leslie2008's construct of characteristic properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), a property that bears a *principled connection* to the kind. 
+A property bears a principled connection to the kind if a (generic) sentence that appeals to the kind to explain the existence of the property makes sense (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged").
+When such sentences are not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple generic (e.g., "Barns are red") is endorsed, then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
+@Prasada2013 showed that different kinds of generic statements (e.g., striking properties, characteristic properties with low prevalence) support different kinds of inferences in addition to the difference in endorsements for *by virtue of* statements (e.g., *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
 Additionally, there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
@@
 Integrating a hierarchical model of kinds and properties with our model of generic language is a natural direction to understanding the computational underpinnings of conceptual relations and generics.
-Different conceptual structures may give rise to roughly the same distributions on prevalence and thus have similar endorsement profiles according to our model. 
+Different conceptual structures may give rise to roughly the same distributions on prevalence and thus have similar generic endorsement profiles according to our model. 
 Yet the inferences that can be drawn from hearing these generics may differ, depending on their interactions with the putative hierarchical knowledge people bring to bear [a la the differences observed for "prevalence-matched items" in @Prasada2006].
@@
 That is, if a particular instance is more likely than not to have the feature, then an absolute generic is true.
-By contrast, *relative generics* are true based on a comparison to an alternative set of kinds $Alt(K)$, analogous to our comparison class.
+By contrast, *relative generics* are true based on a comparison to an alternative set of kinds $Alt(K)$, analogous to the categories that comprise the prevalence prior (the so-called *comparison class*, which we discuss further in the General Discussion).
 "Mosquitos carry malaria" is true because an arbitrary mosquito is more likely than an arbitrary member of an alternative kind to have the feature.
@@
 ]
-Further, though Cohen's theory is framed in terms of probabilities, it is a fully deterministic, fixed-threshold account which only makes qualitative predictions about what is true and what is false.
-In contrast, we posit an uncertain threshold which is resolved in context through Bayesian inference; our theory is a joint semantic--pragmatic theory.
+Further, though Cohen's theory is framed in terms of probabilities, it is a fully deterministic, fixed-threshold account which only makes qualitative predictions about what is true and what is false (i.e., it has a deterministic semantics).
+In contrast, we propose a fully probabilistic semantics embedded within a Bayesian model that describes how context resolves the uncertain threshold; our theory is a joint semantic--pragmatic theory.
 
@@
 
-Cohen's and other statistical theories employ a *domain restriction* mechanism (not currently required in our account) to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
+Cohen's and other statistical theories employ a mechanism (not currently required in our account) known as *domain restriction* to explain the context-sensitivity of generics: contextually restricting the entities that go into the computation of prevalence (i.e., which robins do we look at to compute the probability of laying eggs among robins?).
 @Cohen1999 posits that prevalence is calculated by only considering entities that *could have some feature* in a contextually-specified alternative set of features $Alt(F)$.
 For example, the property *lays eggs* induces a set of alternatives that are associated with modes of reproduction (e.g., *gives birth to live young*, *undergoes mitosis*, ...).
-"Robins lay eggs" (an absolute generic for @Cohen1999) is evaluated by only considering female members of kinds, because only female members can plausibly satisfy one of the other alternatives having to do with reproduction (i.e., the alternative features in $Alt(F)$).
-The inferential machinery of domain restriction (i.e., what comprises $Alt(F)$) relies upon conceptual knowledge, but the details remain obscure [@Carlson1995essay].^[
+"Robins lay eggs" [an absolute generic for @Cohen1999] is evaluated by only considering female members of kinds, because only female members can plausibly satisfy one of the other reproductive property alternatives (i.e., the alternative features in $Alt(F)$).
+The inferential machinery behind domain restriction ---how to determine $Alt(F)$---relies upon conceptual knowledge, but the details remain obscure [@Carlson1995essay].^[
   However, see @Cohen2004 for a discussion of how his semantic constraints relate to different kinds of generics and different kinds of conceptual representational frameworks used in cognitive science.
 ]
-The uncertain threshold model can be seen as one particular mechanism by which the domain may be restricted: The structure of the prior distribution over the prevalence of *lays eggs* is a reflection of an intuitive theory of reproduction (i.e., that only females lay eggs) and the uncertain threshold model uses that background knowledge to derive a property-specific interpretation.
+Our uncertain threshold model can be seen as one particular mechanism by which the domain may be restricted: The structure of the prior distribution over the prevalence of *lays eggs* is a reflection of an intuitive theory of reproduction (i.e., that only females lay eggs) and the uncertain threshold model uses that background knowledge to derive a property-specific interpretation.
 There may exist a refactorization of the uncertain threshold model to a fixed threshold where the listener has uncertainty about the relevant domain of restriction.
@@
 This analysis draws analogy to other, inherently context-sensitive linguistic expressions: *indexicals* (e.g., "this" or "I").
-@Sterken2015 uses this to motivate a context-sensitive *quantificational force* as well as mechanism of domain-restriction [of the kind used by @Cohen1999 and others].
+@Sterken2015 uses this analogy to motivate a context-sensitive *quantificational force* as well as mechanism of domain-restriction [of the kind used by @Cohen1999 and others].
 Our uncertain threshold semantics can be seen be a particular formalization of @Sterken2015's context-sensitive quantificational force. 
@@
 The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generics (e.g., "Supreme Court justices have even social security numbers") and resisting stereotyped language (e.g., "Boys are good at math”).
-Our theory does not directly formalize "what is normal", though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
+Our theory does not directly formalize what is *normal*, though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
 <!-- We showed in Expt.
@@
 In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-The task of the computational linguist, then, is to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+This proposal is used to then used to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
 Our semantic theory can be seen as a generalization of *underquantification* to a continuous interval of possible meanings.
@@
 -->
-Additionally, by using an underspecified threshold, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
+Additionally, by using an underspecified threshold on a scale of probability, our formulation naturally extends to other scales and other kinds of generalizations (e.g., habitual language), where quantified relations like "Most" or "All" are not directly applicable.
 
@@
 
-Cue validity is "inverse prevalence"; the two are related via Bayes' Rule:
+Cue validity is *inverse prevalence*; the two are related via Bayes' Rule:
 $P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.
-Knowledge about other categories $k'$ enters in the denominator.
+Knowledge about other categories $k'$ enters in the denominator to compute cue validity for prevalence.
 Indeed this normalizing constant (the denominator) is equal to the expected value (i.e., the mean) of the prevalence prior distribution: $\mathbb{E}[P(p)]$.
-Thus cue validity comes from a point estimate of the prevalence prior distribution.
-For a more detailed derivation of the relationship between cue validity and prevalence priors, see Appendix A.
-We discuss the implications of this relationship in the General Discussion.
+Thus cue validity comes from a point estimate of the prevalence prior distribution, and information about cue validity can be derived from the constructs posited in our model. 
+We return to the implications of this relationship in the General Discussion.
+For a more detailed, mathematical derivation of the relationship between cue validity and prevalence priors, see Appendix A.
 
@@
 
-There are several theoretically-substantive components to our model: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
-not uttering it, and (c) vagueness in the semantics of a generalization.
+In our empirical studies below, we compare our model to three alternatives.
+These alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions. 
+Instead, these models are designed to interrogate the theoretically-substantive components of our model. 
+There are three such components: (a) property knowledge in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs.
+not uttering it, and (c) vagueness in the semantics of a generalization (i.e., an uncertain threshold).
 In our empirical studies, we compare the uncertain threshold model to an alternative, lesioned model which lacks the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to a quantified statement) but which has the same prevalence prior and the decision-theoretic architecture.
 There are no correspondingly simple ways to lesion the other two components (property knowledge or speaker decision) that still produces quantitative, context-sensitive predictions.
-Furthermore, for comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012], we construct alternative regression models based on empirically-elicited quantities (referent prevalence and *cue validity*, described below).
-In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our experimental materials. 
-These three alternative models do not represent any of the extant theories of generics described above; no extant theory is sufficiently precise to yield quantitative predictions.
+Instead, we compare our model to two regression models based on empirically elicited referent prevalence and cue validity, which provides some interrogation of the necessity of property knowledge in the form of a full distribution on prevalence.
+<!-- Furthermore, for comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012], we construct alternative regression models based on empirically-elicited quantities (referent prevalence and *cue validity*, described below).
+-->
+In addition to serving as alternatives, these baseline regression models help us understand the statistical properties of our experimental materials and provide a comparison to standard methods in the psychological literature on generics [e.g., @Khemlani2012].
 
 <!-- For comparison to standard methods in the literature on generics [e.g., @Khemlani2012], we construct alternative quantitative models based on empirically-elicited cue validity. -->
-
 <!-- These control models improved the quantitative fit to the endorsement data, but did not match the explanatory power of the uncertain threshold model. -->
 
-## Intermediate summary
-
-We have introduced the first quantitative theory of generic language and other sorts of generalizations in language, and discussed the relationship of this account to extant theories of generics.
-Above, we presented simulations showing how the model predicts endorsements depending upon the background knowledge about the property $P(p)$ as well as the referent prevalence $p$ believed to be true for the category.
-For each of these we chose schematic values for the parameters of the model (i.e., the prevalence priors and referent prevalence levels), and saw that the endorsement model recovers standard intuitions about the truth or falsity of classic examples from the generics literature.
+# Interim summary and overview of experiments
+
+We have introduced the first quantitative theory of the language of generalization, and discussed the relationship of this account to extant theories of generics.
+Above, we presented simulations showing how the model predicts endorsements for classically puzzling generic statments.
+These predictions depended upon the background knowledge about the property $P(p)$ as well as the referent prevalence $p$ believed to be true for the category. 
+For each of these we chose intuitive values for the parameters of the model (i.e., the prevalence priors and referent prevalence levels).
 In what follows, we test this theory empirically for a wide range of generalizations, including generalizations of different types (categories, events, and causes).
 We do this by both measuring and manipulating background knowledge and referent prevalence and predicting human endorsements of generalizations.
+
+In Case Study 1, we examine generalizations about categories expressed in generic language. 
+We first measure endorsements for thirty generic statements about familiar categories, revealing an entire continuum of endorsements (Expt. 1a). 
+We then measure the corresponding prevalence priors and referent prevalence using a prevalence prior elicitation task (Expt. 1b).
+We compare the quantitative fits of our model to the three alternative models described above.
+This Case Study is an empirical version of several of the worked examples in the section above.
+
+In Case Study 2, we examine generalizations about events expressed in habitual language while manipulating the referent prevalence.
+We measure prevalence priors for events of people doing various actions (e.g., people running, hiking, climbing mountains; Expt. 2a).
+We then measure endorsements of habituals for statements about novel actors (e.g., "John runs") given referent prevalence information (e.g., "In the last two months, John ran three times."; Expt. 2b).
+Finally, we test whether referent prevalence in our model is best thought of as a past frequency (e.g., the number of times John has run in the past) or a prediction about the future (e.g., the number of times a speaker expects John to run in the future) by experimentally manipulating future predictions while keeping constant past frequency (Expt.
+2c).
+We answer this question by testing the quantitative fits of two versions of our model: one in which the speaker is conveying past frequency and one in which the speaker is conveying their predictions about the future.
+
+Case Study 3 experimentally manipulates the prevalence prior in the domain of causal language (e.g., "Herb X makes animals sleepy").
+Expt. 3a measures the (manipulated) prevalence prior, confirming that our manipulation influenced participants' beliefs about the prevalence of the feature across different categories.
+Expt. 3b measures the corresponding influence on causal endorsement, finding an effect of the manipulated background knowledge in the way predicted by the uncertain threshold model.
 

### 2018-10-16 paper/comgen-paper.Rmd
polish to gd

@@
 That generics are vague does not preclude them from being treated by formal models. 
-A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability, leads to complex, quantitative interactions with background knowledge.
+A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability, leads to complex, quantitative interactions with background knowledge, which closely tracks human judgments.
 
@@
 Truth judgments are the standard measurement for semantic theories, but are often limited to the intuitions of a single or a small handful of trained theorists, often producing only binary or ternary judgments (i.e., true, false, and possibly indeterminate).
-In this work, we measured the truth judgments of naive language users, revealing whole continua of gradience. 
+Our model accounted for these standard linguistic intuitions about a number of philosophically puzzling generic statements (Worked Examples).
+We went beyond intuitions, however, measuring truth judgments of naive language users, which revealed substantial gradience in endorsements.
 These fine-grained, quantitative measurements pose real challenges for verbal theories of generics, which can only predict qualitative differences.
 The framework we propose is sufficiently precise to predict quantitative gradience, and we showed that the gradience in truth judgments depends in systematic ways on an interpreter's prior beliefs about prevalence.
-We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
-In each case, our model provided a strong quantitative fit to human judgements while other models fall short.
-In addition, the model accounts for standard linguistic intuitions about a number of philosophically puzzling generic statements (Worked Examples).
+We provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
+In each case, our model provided a strong quantitative fit to human judgements while other models fell short.
 
@@
 The relationship, however, has been never been empirically tested nor formally described.
-This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism explains judgments of both kinds of statements (Expts.
+This paper presents the first empirical evidence that the reasoning involved in understanding generic and habitual sentences are similar: The same uncertain threshold mechanism operating over prior beliefs explains judgments of both kinds of statements (Expts.
 1 & 2).
 
-In our model, a generic statement or other generalization updates a listener's *a priori* beliefs about the prevalence of the property for that category. 
+In our model, an utterance conveying a generalization updates a listener's *a priori* beliefs about the prevalence of the property for that category. 
 Since the prevalence prior includes the information necessary to compute cue validity (see Appendix A), the cue validity of the feature for the new category is added to the common ground between interlocutors.
@@
 
-## A unified model
+## Generics and genericity
 
 The statistical vs.
-conceptual distinction for theories of generics, described earlier in this paper, is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
+conceptual distinction for theories of generics, described in detail earlier in this paper, is roughly co-extensive with the distinction between theories of the truth conditions of generics and the mental phenomenon of *genericity*, respectively [@Nickel2016].
 Truth conditions are unified criteria that all generics must satisfy in order to be true.
@@
 <!-- That is, our framework provides both a theory of generics and genericity, and their interaction. -->
-This model is thus the first step towards unifying conceptual approaches to generics with an inherently quantitative natural language semantics.
+This model is thus the first step towards unifying conceptual approaches to genericity with an inherently quantitative natural language semantics for generics.
 
@@
 The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
-In fact, we saw in Expt. 2c that it was participants predictions about the future that matter for the prevalence computation involved in endorsement.
+In fact, we saw in Expt. 2C that it was participants predictions about the future that led to the prevalence computation involved in the endorsement decision.
 Intuitive theories guide these predictions, and might provide new insight into classic puzzles of generics.
@@
 However, were we to learn much more surprising information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compell an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and endorse such a generic.
+history had a social security number which was a *prime number* (a much lower probability outcome)---the shear suspiciousness could compel an observer to revise their theory of the domain (appealing perhaps to a conspiracy), update their subjective probability of future instances, and endorse such a generic.
 
@@
 We have pilot data suggested these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
-More empirical work is needed to understand the conditions under which strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.
+More empirical work is needed to understand whether and how strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.
 <!-- If such effects exist, our modeling framework could be elaborated with a non-informational speaker utility [see e.g., @Yoon2016; @Yoon2017]. -->
@@
 
-The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
-We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
-In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
+The probabilistic communicative model we introduce in this paper assumes shared background knowledge about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
+We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect, respectively.
+In Expt. 3, we empirically demonstrated the influence of other categories on endorsements of generalizations.
 Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
@@
 We think the choice of these classes is intuitive, but it is a limitation of this work that we do not derive these choices from more general information-theoretic considerations.
-The problem of choosing a comparison classes, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012].
+The problem of choosing a comparison class, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012].
 We have begun to explore how pragmatic reasoning and world knowledge can flexibly adjust the comparison class to appropriately suit the context [e.g., how a "short" basketball player is *short for a basketball player* while a "tall" basketball player is *tall for a person*; @Tessler2017].
@@
 Thus, our endorsement model assumes that the QUD was "*what* has this feature?".
-Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
+Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to having four of other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
 It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
@@
 
-We have argued that the language of generalizations are vague descriptions of prevalence or frequency in a way analagous to how gradable adjectives like "tall" are vague descriptions of some underlying degree scale (e.g., height).
-However, vague predicates like "tall" exhibit a number of additional phenomena that we do not suppose generics or generalizations would necessarily exhibit.
+We have argued that the language of generalizations are vague descriptions of prevalence in a way analagous to how gradable adjectives like "tall" are vague descriptions of some underlying degree scale (e.g., height).
+Vague predicates like "tall", however, exhibit a number of additional phenomena that we do not suppose generics or generalizations would necessarily exhibit.
 For example, vague predicates admit borderline cases (e.g., a person who is neither tall nor not tall). 
-It is *a priori* unclear whether one could construct borderline cases with generics or habituals without sounding like a contradiction (e.g., "John both runs and doesn't run").
-Additionally, Sorites paradoxes can be constructed out of arguments using vague predicates, and it is not clear that generics or habituals could be used to construct such arguments.
+*A priori*, it is unclear whether one could construct borderline cases with generics or habituals without sounding like a contradiction (e.g., "John both runs and doesn't run").
+Additionally, sorites paradoxes can be constructed out of arguments using vague predicates, and it is not clear that generics or habituals could be used to construct such arguments.
 No experimental data yet bears on these ideas, but would be useful for further understanding the relationship between generalizations and vague predicates.
@@
 For now, we understand both genericity and vagueness as analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions (e.g., an uncertain threshold).
-We note that this sort of "lexical uncertainty" is a kind of *parameter learning* problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a *structure learning* problem (e.g., lexical ambiguity).
-Further work should be done to better understand the kinds of context-sensitive linguistic phenomena that are modeled as parameter vs. structure learning problems.
+This sort of "lexical uncertainty" is a kind of *parameter learning* problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a *structure learning* problem (e.g., lexical ambiguity).
+Further work should be done to better understand the kinds of context-sensitive linguistic phenomena that are modeled as parameter vs.
+structure learning problems to construct a richer typology of underspecified linguistic expressions.
 
 Our view of understanding generalizations involving reasoning about an uncertain threshold is reminiscent of @Williamson1992's epistemicist view on vagueness.
-This view holds that when a speaker utters a vague statement, there exists an objective set of criteria determining whether the entity in question satisfies the vague predicate.
+This view holds that when a speaker utters a vague statement, there exists an objective set of criteria determining whether the entity in question satisfies the vague predicate (i.e., whether or not the utterance is true).
 Vagueness emerges from uncertainty about the details of those objective criteria (e.g., the precise value of a threshold). 
-This uncertainty in turn could be the result of a population of speakers using slightly different criteria, thus shifting the criteria or threshold.
-Listeners then will not know exactly what kind of speaker they are dealing with *a priori* and normatively should maintain uncertainty about the truth conditions. 
-In our model, world knowledge and general communicative principles help a listener resolve the value of threshold [see @Lassiter2015 for an extended discussion of resolving the value of a free semantic variable in context].
+This uncertainty in turn could be the result of a population of speakers using slightly different criteria.
+Listeners then will not know exactly what kind of speaker they are dealing with *a priori* and normatively should maintain uncertainty about the truth conditions [see @Lassiter2015 for an extended discussion of vagueness involving resolving the value of a free semantic variable in context].
 
@@
 @Leslie2008 argues that the necessary complexity of a formal account of generics and the simplicity with which young children acquire generics implies that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics.^[
-  This argument is simplistic in that it ignores evidence that children's struggle with quantifiers stems from pragmatic issues [@Musolino2006].
+  This argument is a purely semantic argument which ignores evidence that children's difficulty with quantifiers stems from pragmatic issues [@Musolino2006].
 ]
 
-Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater: In fact, our model of generics can be viewed as *simpler* from a learning perpsective than a model of quantifier semantics.
+Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater: In fact, from a learning perspective, our semantics of generics can be viewed as *simpler* than that of quantifier semantics.
 With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning:
@@
 We have assumed the truth functional threshold $\theta$ comes from a uniform distribution over the unit interval $[0, 1]$, which is mathematically equivalent to a *continuously-valued* or *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$.
-The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $Lit(p \mid u) \propto p \cdot P(p)$
+The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $L(p \mid u) \propto p \cdot P(p)$
 This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.

### 2018-10-17 paper/case1-generics.Rmd
small edits to generics and habituals experiments

--- 2018-10-01 paper/case1-generics.Rmd
@@
 
-Learning from generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") is believed to play a central role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
+Learning from generic language (i.e., generalizations about categories; e.g., "Dogs bark.") is believed to play a central role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
 In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
@@
 
-We first investigate how the *uncertain threshold* endorsement model predicts actual human endorsements of generic statements.
-We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g.
+We first investigate how the uncertain threshold endorsement model predicts actual human endorsements of generic statements.
+We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are striking or dangerous (e.g.
 "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g.
 "Lions lay eggs.").
-We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt.
+We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: *true*, *false*, and *indeterminate*) for generics with properties of low, medium, and high referent-prevalence (Expt.
 1a).
@@
 
-In this experiment, we elicit human endorsements for generalizations about categories (*generics*) taken from the linguistic and psychological literature on generics [@Prasada2013].
-The goal of this study is to observe a range of endorsements for generic statements about animal categories.
+In this experiment, we elicit human endorsements for generic sentences taken from the linguistic and psychological literatures [@Prasada2013].
+The goal of this study is to elicit high variability of endorsements for generic statements about animal categories.
 
@@
 Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
-4 participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
-5 participants self-reported a native language other than English; removing their data has no effect on the results reported. 
+Four participants were excluded for failing to recall the button corresponding to *agreement* in the forced-choice task.
+Five participants self-reported a native language other than English; removing their data has no effect on the results reported. 
 The experiment took about 3 minutes and participants were compensated \$0.35.
@@
 The thirty sentences covered a range of conceptual categories described above.
-Approximately ten true, ten false, and ten uncertain truth-value generics were selected.
+Approximately ten true, ten false, and ten uncertain *a priori* truth-value generics were selected.
 As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
@@
 Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
-We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.
+We next measure the prevalence prior distributions and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.
 
@@
 What is the chance it is female?
-Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female reindeer, approximately 50\%). 
+Your answer will probably depend upon the percentage of the category that you believe to *be female* (e.g., the percentage of female reindeer, approximately 50\%). 
 What is the chance that it lay eggs?
-Again, this depends upon the percentage of the category that you believe lays eggs, which then further depends on the particular kind of animal under consideration: If you're thinking of a reindeer, the answer is probably 0\%; if you're thinking of a peregrine falcon, the probability is similar to the being female probability (50%) because female peregrine falcons lay eggs.
-That is, the answer to how many of an arbitrary category is likely to lay eggs is either roughly 50\% or 0\%, depending on the kind of creature you may be thinking of.^[
+Again, this depends upon the percentage of the category that you believe *lays eggs*, which then further depends on the particular kind of animal under consideration: If you're thinking of a reindeer, the answer is probably 0\%; if you're thinking of a peregrine falcon, the probability is similar to the *being female* probability (50%) because female peregrine falcons lay eggs.
+That is, the answer to how many of an arbitrary category is likely to lay eggs is either roughly 50\% or 0\%, depending on the kind of creature you may bring to mind.^[
   The subjective probability may, in fact, be non-zero and small as opposed to 0. 
@@
 To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").^[
-  That is, we implicitly assume for these properties that logical negation tokenizes its own threshold instead of being derived compositionally via bivalent logical negation.
+  This reverse-coding assumes for these properties that logical negation tokenizes its own threshold instead of being derived compositionally via bivalent logical negation.
 For related empirical and modeling investigations regarding resolving compositional vs.
@@
 We recruited 60 participants over Amazon MTurk.
-3 participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
-2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
+Three participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
+Two participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
 The experiment took about 10 minutes and participants were compensated \$1.00.
@@
 
-On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
+On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property (Figure\ \@ref(fig:generics-prior-task)). 
 Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt.
@@
 *Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
-This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution.
+This diversity is important because our endorsement model makes different predictions depending on the shape of these distrubutions.
 
-### Quantitative modeling
+### Modeling the prevalence priors
 
@@
 ] 
-We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
+We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.
+This *null distribution* is potentially present for all features and acts in exactly the same way (i.e., the lack of producing the feature).^[
   This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
 ]
-This "null distribution" is potentially present for all features and acts in exactly the same way (i.e., the lack of producing the feature).
-The second distribution represents kinds of animals who *could* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
-The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
+The second distribution represents kinds of animals who *could* have such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
+The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the null distribution (for example: we expect the null distribution to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
 To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
@@
 We can now compute the predictions of our endorsement model. 
-We describe first the behavior of a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, before proceeding to the results of the uncertain threshold endorsement model.
+We describe first the behavior of a set of alternatives models that have been previously proposed in the literature and an alternative form of our proposed endorsement model before proceeding to the results of the uncertain threshold endorsement model.
 
@@
 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}) and use it to predict endorsement.
-We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet).
+We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure)B upper-left facet).
 Referent prevalence alone predicts a fair amount of variance because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").
@@
 "Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
-*Lays eggs* is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like *robins*.
-Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
-Furthermore, cue validity cannot distinguish "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction); the cue validity can be zero or low for different reasons.
+*Lays eggs* is a somewhat diagnostic feature for birds, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like robins.
+Thus, the cue validity is low even though robins are in the distinctive part of the *lays eggs* prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
+Furthermore, cue validity cannot distinguish *undiagnostic* features (features present in almost every category; e.g., *not carrying malaria*) from *false* features (features that are absent a particular category; e.g., *lions* and *lay eggs*; see Appendix B for more discussion of this distinction); the cue validity can be near-zero for different reasons.
 Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
@@
 Thus, the fixed-threshold alternative model claims that participants make an information-theoretic decision, taking into account the interpreter's prior distribution on prevalence $P(p)$, using a fixed-threshold semantics, where deviations from a pure information-theoretic decision are accounted for by noise.
-This alternative model has 2 additional parameters to our uncertain threshold model (the fixed-threshold and the proportion of noise responses).
+This alternative model has 2 additional parameters to our uncertain threshold model (the value of the fixed-threshold and the proportion of noise responses).
 <!-- We examine the predictions of this alternative model first. -->
@@
 B: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right).
-C: Five example prevalence priors, listener posteriors upon hearing the generalization, and speaker belief distributions about the referent prevalence.
-These distributions are inferred using all three data sources from Expt.
-1 (see Figure \\ref{fig:genericsModelDiagram} for an overview of the Bayesian data analytic approach).", cache = F}
+C: Five example empirical prevalence priors, model-predicted generic interpretations, and empirical referent prevalence (speaker belief) distributions..", cache = F}
 fig.gen.endorse.data <- generics.endorsement.spectrum +
@@
 \ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].
-Figure\ \@ref(fig:generics-endorsement-figure)B (top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
-Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither. 
+Figure\ \@ref(fig:generics-endorsement-figure)B (bottom right subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
+Though the model is able to capture a lot of the variance, it only makes three kinds of judgments: true, false, or neither, similar to purely semantic accouts of generics. 
 It treats "Tigers eat people" (`r round(tigers.eat.people[[1,"prediction_mean"]],2)` [`r round(tigers.eat.people[[1,"prediction_ci_lower"]], 2)`,
@@
 `r round(peacocks.feathers[[1,"high"]], 2)`]).
-Similarly, "Lions lay eggs" is judged to be just as bad as "Mosquitos attack swimmers"(`r round(lions.lay.eggs[[1,"prediction_mean"]],2)` [`r round(lions.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
-`r round(lions.lay.eggs[[1,"prediction_ci_upper"]], 2)`, `r round(mosquitos.attack.swimmers[[1,"prediction_mean"]],2)` [`r round(mosquitos.attack.swimmers[[1,"prediction_ci_lower"]], 2)`,
-`r round(mosquitos.attack.swimmers[[1,"prediction_ci_upper"]], 2)`], respectively), though participants rate the former as completely false (`r round(lions.lay.eggs[[1,"MAP_h"]],2)` [`r round(lions.lay.eggs[[1,"low"]], 2)`,
+Similarly, "Lions lay eggs" (`r round(lions.lay.eggs[[1,"prediction_mean"]],2)` [`r round(lions.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
+`r round(lions.lay.eggs[[1,"prediction_ci_upper"]], 2)`]) is judged to be just as bad as "Mosquitos attack swimmers" (`r round(mosquitos.attack.swimmers[[1,"prediction_mean"]],2)` [`r round(mosquitos.attack.swimmers[[1,"prediction_ci_lower"]], 2)`,
+`r round(mosquitos.attack.swimmers[[1,"prediction_ci_upper"]], 2)`]), though participants rate the former as completely false (`r round(lions.lay.eggs[[1,"MAP_h"]],2)` [`r round(lions.lay.eggs[[1,"low"]], 2)`,
 `r round(lions.lay.eggs[[1,"high"]], 2)`]) while the latter is kind of true (`r round(mosquitos.attack.swimmers[[1,"MAP_h"]],2)` [`r round(mosquitos.attack.swimmers[[1,"low"]], 2)`,
@@
 
-As we see in Figure\ \@ref(fig:generics-endorsement-figure)B (top right subplot), the uncertain threshold endorsement model explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
+As we see in Figure\ \@ref(fig:generics-endorsement-figure)B (top right), the uncertain threshold endorsement model explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
 Examining the relevant model components that give rise to these predictions further reveals the intuition for why the model makes the predictions that it does (Figure \ref{fig:generics-endorsement-figure}C).
-Because the endorsement model's alternative utterance is a null or silent utterance, the prevalence prior distributions is exactly what the interpreter model would believe if the speaker does not produce the generic.
+Recall the endorsement model's alternative utterance is a null or silent utterance and thus, the prevalence prior distributions are exactly what the interpreter model would believe if the speaker does not produce the generic.
 The endorsement model then decides whether maintaining the listener's prior or updating it with the uncertain threshold semantics would better get the listener to guess the correct prevalence for the category (correct in the mind of the speaker).
 The model rates "Robins lay eggs" as a good utterance because the prevalence posterior implied by the generalization is similar to the referent prevalence.^[
-  We again note that modeling the prevalence prior for *lays eggs* as a two-component mixture model, as we have assumed for all the prevalence priors, results in a distribution with a peak at 0\% and around 70\%.
-  This 70\% peak is a result of smoothing the underlying bimodal distribution at 50\% and 100\%. 
-  The same smoothing occurs for the referent-prevalence, as participants report as often that either 50\% or 100\% of robins lay eggs.
-  If instead, the prevalence prior is modeled as a tri-modal distribution and the referent-prevalence modeled as bi-modal (mainintaing the structure at 50\% and 100\%), the resulting interpretation (i.e., prevalance posterior given generalization) is that either 50\% or 100\% lay eggs.
-  This is precisely the bimodal referent-prevalence distribution for *robins lay eggs*, and so the endorsement model still predicts high endorsement. 
-  The fact that domain restriction enters in both the prevalence prior and the referent prevalence measurements, in effect, cancels one another out and has no effect on the resulting endorsement model predictions.
+  We again note that the empirical prevalence prior for *lays eggs* is tri-model with peaks at 0\%, 50\%, and 100\%.
+  As a result, the generic interpretation is bi-modal: the listener is led to believe either 50\% or 100\% of robins lay eggs.
+  Interestingly, the endorsement model still makes the correct prediction because the referent-prevalence for laying eggs among robins is also bi-modal (peaks at 50\% and 100\%).
+  That is, domain-restriction (resulting in a response of 100\%) seemingly occurs for some participants for *both* the prevalence prior and referent prevalence measurements, and this allows the model to predict correctly that "Robins lay eggs" is a good generic utterance.
 ]
-The prevalence posterior for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad, endorsement around 0.5, which is what is approximately the proportion of participants who endorse the statement.
+The hypothetical interpretation for "Robins are female" is almost indistinguishable from the prevalence prior, because the prevalence prior has such low variance (almost all animals have female members in exactly the same proportion); the endorsement model then has no basis to prefer silence or the generic statement and the prediction is that the utterance should be neither good nor bad---endorsement around 0.5---which is what is approximately the proportion of participants who endorse the statement.
 "Mosquitos carry malaria" is an interesting case because the prevalence prior has high variance (i.e., participants are highly uncertain about the prevalence of carrying malaria among categories).
-As a result, the prevalence posterior also has high variance; still, the prevalence posterior is more consistent with the referent prevalence than the prevalence prior, and the endorsement model predicts "Mosquitos carry malaria" is a good utterance.
+As a result, the generic interpretation also has high variance; still, the generic interpretation is more consistent with the referent prevalence than the prevalence prior, and the endorsement model predicts "Mosquitos carry malaria" is a good utterance.
 Finally, an utterance with high referent prevalence, such as "Tigers don't eat people", is predicted to have low endorsement because the generic would be misleading; even if most tigers don't eat people, saying "Tigers don't eat people" implies that all don't eat people, which is too strong.

### 2018-10-17 paper/case2-habituals.Rmd
small edits to generics and habituals experiments

@@
 
-As with categories, particular events like "Mary smoked yesterday" can be generalized into *habitual sentences*: "Mary smokes". 
-It is believed that an analysis of generics should lend itself naturally to be extended to an analysis of habituals [e.g., @Carlson2005; @Leslie2008].
+As with instances of categories, particular events like "Mary smoked yesterday" can be generalized into *habitual sentences*: "Mary smokes". 
+It is believed that an analysis of generics should lend itself naturally to be extended to an analysis of habituals [e.g., @Carlson2005; @Leslie2008], but no such analysis or empirical data has directly connected the two.
 <!-- Events are a broad class of entities.  -->
@@
 ]
-We test the model by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2a).
-We then measure endorsements of habitual statements while manipulating the referent prevalence  (Expt. 2b), and use our computational model to predict habitual endorsements. 
+We test the model by first measuring the prevalence (rate) prior distribution for various actions (e.g., how often different people smoke cigarettes; Expt. 2A).
+We then measure endorsements of habitual statements while manipulating the referent prevalence  (Expt. 2B), and use our computational model to predict habitual endorsements. 
 <!-- We estimate the priors using a novel data-analytic approach that takes advantage of the mixture-model validated in Expt. 1b. -->
@@
 Our computational model predicts endorsement rates given a referent prevalence $p$. 
-Does prevalence represent the actual, objective frequency in the world (e.g., the rate at which a person has smoked cigarettes in the past) or a subjective, predictive belief in the head (e.g., the rate at which a person is expected to smoke in the future)?
+Using this model, we can ask quantitatively how well prevalence conveyed by a speaker represents the actual, objective frequency in the world (e.g., the rate at which a person has smoked cigarettes in the past) or a subjective, predictive belief in the head (e.g., the rate at which a person is expected to smoke in the future)?
 Such a distinction would support the intuitions about sugarless gum residents and could explain why "Supreme Court Justices have even social security numbers" sounds strange even if nine out of the nine current justices have even social security numbers [@Cohen1999]: Our predictions about the evenness of the *next* justice's social security number are driven by strong prior beliefs that selection for the Supreme Court is uncorrelated from the numerical properties of one's social security number; the current observations are not enough in this case to sway those beliefs.
 We examine this aspect of the theory by measuring endorsements of habituals when causal forces intervene on the world (e.g., the person buys a pack of cigarettes; Expt.
-2c) as well as participants' predictions about the likely frequency of the event in the future.
-We then construct generic endorsement models based on speakers aiming to convey the objective, past frequency or their subjective, future expectation to try to predict the habitual endorsement patterns.
+2C) as well as participants' predictions about the likely frequency of the event in the future.
+We then construct habitual endorsement models based on speakers aiming to convey the objective, past frequency or their subjective, future expectation to try to predict the habitual endorsement patterns.
 
@@
 
-## Experiment 2a: Measuring the prevalence prior for events
+## Experiment 2A: Measuring the prevalence prior for events
 
@@
 For language about the behaviors of people, $P(p)$ represents a language user's background knowledge about the rates with which people perform a behavior; this prior can be constructed as a distribution over *different people*, each of whom do the behavior with a different rate.
-We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Expt. 1.
-In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to perform the action with a stable rate and those who do not perform the action.^[
-  It is likely that more than just these two possibilities are represented in people's intuitive theories, corresponding to individuals with additional traits or demographics.
+We designed our elicitation task to take advantage of the mixture-model representation of the prevalence prior used in Case Study 1.
+In particular, we assume, to a first approximation, that the distribution over prevalence can be represented as a mixture of those who tend to perform the action with a stable rate and those who do not perform the action.
+With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
+We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the prevalence prior model) as well as the rate at which people (who have done the action before) do the action.
+We will assume for simplicity that people who have never done the action before will probably never do the action. ^[
+  It is likely that more than just these two possibilities are represented in people's intuitive theories, corresponding to individuals with additional traits or demographics, and plausibly influenced by the types of people a speaker knows and interacts with.
   We assume here a simple two-component structure so as to not make the specification of the prior overly complex.
 ]
-With the further assumption that, all else being equal, past is predictive of future behavior, we operationalize these two kinds of people as *people who have done the action before* and *people who have not the action before*.
-We design this experiment to measure participants' beliefs about the relative proportion of these two kinds of people (as a measure of the mixture parameter in the model) as well as the rate at which people (who have done the action before) do the action.
-We will assume for simplicity that people who have never done the action before will probably never do the action.
 
@@
 
-To construct our stimulus set, we choose actions from five categories of typical human behaviors: eating/consuming food and drug, work, wearing clothing, entertaining activities, and hobbies. 
+To construct our stimulus set, we choose actions from five categories of typical human behaviors having to do with food and drug, work, clothing, entertainment, and hobbies.
 For each category, we created pairs or triplets of events that shared a superordinate action (e.g. *writing* poems vs. novels).
@@
 In total, thirty-one events were used.
-For a full list of the stimuli used in Expts. 2a-c, see Appendix D.
+For a full list of the stimuli used in Expts. 2A-C, see Appendix D.
 
@@
   scale_color_solarized()+
+  geom_label_repel(segment.alpha = 1, label.size = 0.05,
+                   force = 10, size = 2.75, color = 'black')+
   geom_point(data = rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
@@
              inherit.aes = F, 
+             size = 1.5,
              aes(
@@
                y = `Frequency of doing action (log scale)`, color = gender))+
-  geom_point()+
-  geom_label_repel(segment.alpha = 1,label.size = 0.25,
-                   force = 10, size = 4, color = 'black')+
-
+  geom_point(size = 1.5)+
   #geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
@@
     )+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))
+  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
+  guides(color = F)
 
@@
 figure.habituals.priors.marginals <- ggplot(habituals.priors.marginals %>%
-  filter(val > -4.9) %>%
+  filter(val > -4.9, item != "wears a watch") %>%
   mutate(gender = factor(gender, levels = c("female", "male"))), 
@@
   geom_density(size = 0.4, aes( y = ..scaled.. ))+
-  facet_wrap(~item, nrow = 4)+
+  facet_wrap(~item, ncol = 5)+
   geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
-               filter(gender == 'male', measurement == "% people who have done action before"), 
+               filter(gender == 'male', measurement == "% people who have done action before", item != "wears a watch"), 
             aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = 1 - MAP),
@@
   geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
-               filter(gender == 'female', measurement == "% people who have done action before"), 
+               filter(gender == 'female', measurement == "% people who have done action before", item != "wears a watch"), 
             aes(xmin = -4.25, xmax = -3.75,
@@
   scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
-  theme(legend.position = c(0.93, -0.1),
+  theme(#legend.position = c(0.93, -0.1),
         legend.title = element_blank(),
-        legend.box = 'vertical',
+        legend.box = 'horizontal',
+        legend.direction = "vertical",
+        legend.position = "bottom",
         axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1),
@@
       labels = c("almost never", "annually", "monthly", "weekly", "daily")
-      )+
-  guides(color = F)
-```
-
-```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.7, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt.
+      )#+
+  #guides(color = F)
+```
+
+```{r habituals-prior-figure, fig.width = 11, fig.asp = 0.55, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt.
 2a).
@@
 Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache=F}
-plot_grid(
-  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
-  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
-  labels = c("A", "B"), nrow = 2,
+hab.prior.legend <- get_legend(figure.habituals.priors.marginals)
+
+cowplot::plot_grid(
+  plot_grid(figure.habituals.priors.scatter + theme(plot.margin = unit(c(0,6,0,0), "pt")),
+            hab.prior.legend, ncol = 1, rel_heights = c(1, 0.2)),
+  figure.habituals.priors.marginals + theme(plot.margin = unit(c(0,0,0,6), "pt"))+
+    guides(color = F, lty = F),
+  labels = c("A", "B"), nrow = 1,
   align = 'h',
-  rel_heights = c(1, 1)
+  rel_widths = c(0.5, 1)
   )
@@
 
-To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analogous to that used in Case Study 1 (Expt. 1b).
+To generate prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task, analogous to that used in Case Study 1 (Expt. 1A).
 The only difference is that we estimate the mixture component $\phi$ directly from responses to Question 1. 
@@
 
-In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigarettes") while manipulating the frequency with which the referent-event occurs (e.g., how often Mary smokes cigarettes).
+In this experiment, we elicit human endorsements for generalizations about events (*habituals*; e.g., "Mary smokes cigarettes") while manipulating the frequency with which the referent event occurs (e.g., how often Mary smokes cigarettes).
 
@@
 
-Each event from Expt. 2a was paired with between two to four frequencies, for which the habitual statement would be evaluated. 
+Each event from Expt. 2A was paired with between two to four frequencies, for which the habitual statement would be evaluated. 
 Frequencies were presented in terms of a character performing the action "three times in the past *time interval*".
@@
 Specifically, we used the endorsement model to generate predictions based on the prior elicitation data (Expt.
-2a) for each item, and chose between two and four time intervals across which maximal variability was predicted.
-For example, relatively high frequencies were chosen (e.g., time intervals of weeks and months) for items expected to occur rather often (e.g., *runs*); for an item was expected to occur infrequently (e.g., *climbs mountains*), lower frequencies were chosen (e.g., time intervals of years or longer) because the model predicted that much of the variability in endorsement would occur in those respective ranges.
+2A) for each item, and chose between two and four time intervals across which maximal variability was predicted.
+For example, relatively high frequencies were chosen (e.g., time intervals of weeks and months) for items expected to occur rather often (e.g., *runs*); for an item that was expected to occur infrequently (e.g., *climbs mountains*), lower frequencies were chosen (e.g., time intervals of years or longer) because the model predicted that much of the variability in endorsement would occur in those respective ranges.
 In total, `r nrow(m.hab.endorse.rsa %>% distinct(habitual, time_period))` unique items were created by pairing frequencies with events. 
@@
 
-In our empirically elicited priors, items differ the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)A x-axis).
-This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus relates to the *cue validity* of a particular feature for a particular individual (see Appendix A for a derivation of the relationship between the prevalence prior and cue validity).
-Thus, we take this parameter as an index of the *distinctiveness* of the action, analogous to *cue validity* in the case study of generic language.
-We construct a regression model that treats endorsement as a linear combination of frequency and distinctiveness information. 
-We use participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as well as frequency given to participants to predict habitual endorsement.
+In our empirically elicited priors, items differ in the proportion of people who have done the action before (the *mixture parameter* of the mixture model; Figure \@ref(fig:habituals-prior-figure)A x-axis).
+This mixture parameter is a major contributor to the mean of the prevalence prior distribution, and thus relates to the *cue validity* of a particular feature for a particular individual (Appendix A).
+Thus, we take this parameter as an index of the *distinctiveness* of the action, analogous to *cue validity* in the case of generic language.
+We construct a regression model that treats endorsement as a linear combination of the frequency given to participants and participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) as an index of distinctiveness.
 
@@
 On the other hand, playing the banjo three times in the past two years is not strong evidence for the habitual, according to participants ($`r banjo.2years.data`$).
-Nevertheless, because playing the banjo is a distinct skill, the regression model wants to endorse the habitual strongly in this case ($`r banjo.2years.regression.distinct`$).
+Nevertheless, because playing the banjo is a distinctive action, the regression model wants to endorse the habitual strongly in this case ($`r banjo.2years.regression.distinct`$).
 
@@
 As a result, the lowest endorsement this model can apply to an utterance is 0.5 (since both the habitual and silence are always true).
-The fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model (Figure\ \@ref(fig:habituals-endorsement-figure)B).
+As a result, the fixed-threshold model exhibits a small dynamic range of endorsements, similar to the referent-frequency model (Figure\ \@ref(fig:habituals-endorsement-figure)B).
 
@@
 For instance, because of the distinctiveness of *climbs mountains*, the fixed-threshold endorsement model fully endorses the habitual ("Mary climbs mountains") even at a low frequency (Figure \@ref(fig:habituals-endorsement-figure)A).
-However, the model cannot differentiate among different frequencies of doing the same action.
+However, the model cannot differentiate among different frequencies of doing the same action, because they are all above the truth-functional threshold.
 It is equally true that a person does an action with non-zero frequency for any frequency greater than zero, analogous to how "Some dogs are friendly" is equally true whether 20\% or 50\% or 80\% of dogs are friendly.
@@
 
-### Discussion
-
-Habitual language exhibits context-sensitivity directly parallel to that of generic language (Case Study 1).
-Habituals are endorsed for a wide range of frequencies, but show systematic patterns relative to the prior distribution of frequencies, as formalized by the uncertain-threshold model.
-Again, we articulated a number of alternative models and found that only the underspecified threshold model was able to explain the variability in endorsements.
-
-In this case study, we manipulated rather than measured the referent frequency (e.g., the frequency with which a person drinks coffee).
-By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model (and in a way that a fixed-threshold model cannot account for).
-The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in question.
-
 Figure\ \@ref(fig:habituals-endorsement-figure)C provides insight into how the uncertain-threshold model is able to match human judgments. 
@@
 
-In Expt. 2b, participants were given a statement about how often a person has done the action in the past and asked to judge the corresponding habitual statement.
+### Discussion
+
+Habitual language exhibits context-sensitivity directly parallel to that of generic language (Case Study 1).
+Habituals are endorsed for a wide range of frequencies, but show systematic patterns relative to the prior distribution of frequencies, as formalized by the uncertain-threshold model.
+Again, we articulated a number of alternative models and found that only the underspecified threshold model was able to explain the variability in endorsements.
+
+In this case study, we manipulated rather than measured the referent frequency (e.g., the frequency with which a person drinks coffee).
+By manipulating the target frequency, we have shown that it is causally related to habitual endorsements in the way predicted by our model (and in a way that a fixed-threshold model cannot account for).
+The relationship is not linear, however; habitual endorsements vary in complex ways that reflect interpreters' prior knowledge about the event in question.
+
+In Expt. 2B, participants were given a statement about how often a person has done the action in the past and asked to judge the corresponding habitual statement.
 This design potentially confounds an important distinction for the language of generalization: Does the prevalence communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
-In Expt. 2c, we investigate this question by teasing apart *past* from *predictive frequency* and measuring its influence on habitual endorsement.
+In Expt. 2C, we investigate this question by teasing apart *past* from *predictive frequency* and measuring its influence on habitual endorsement.
 
@@
 <!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
-We then compare two uncertain-thresholds models: one which uses participants' ratings of *predictive frequency* as the referent prevalence and one which uses the *past frequency* (as was done for Expt.
-2b).
+We then compare two uncertain-threshold models: one which uses participants' ratings of *predictive frequency* as the referent prevalence and one which uses the *past frequency* (as was done for Expt.
+2B).
 In addition, we compare to a baseline linear model that uses only the *predictive frequency* (no priors) to model endorsement.
@@
 
-The events used were a subset of those used in Expts. 2a \& b (21 of the original 31).
+The events used were a subset of those used in Expts. 2A \& B (21 of the original 31).
 In addition, we crafted statements that were intended to either increase the frequency (*enabling*; e.g., "Yesterday, Bill bought a pack of cigarettes.") or decrease the frequency (*preventative*; "Yesterday, Bill quit smoking.") of the event in the future.
 In order to increase the potential variability of responses across the experimental conditions, participants only saw the frequencies that led to the most intermediate endorsement of the habitual in Expt.
-2b.
-We did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.
+2B.
+We did not include separate trials for both male and female names for the select items we did in Expt. 2B, since we saw no differences in their endorsements of the habitual.
 See Appendix D for a full list of the items and frequencies used, as well as the enabling and preventative information.
@@
 
-The procedure was identical to Expt. 2b except for the inclusion of a second sentence on a subset of trials (*preventative* and *enabling* trials).
-On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2b).
-Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2b), in equal proportions.
-See Table 1 for example trials.
+The procedure was identical to Expt. 2B except for the inclusion of a second sentence on a subset of trials (*preventative* and *enabling* trials).
+On all trials, participants were presented with a \emph{past frequency sentence} (same as Expt. 2B).
+Additionally, trials either included \emph{preventative} information, \emph{enabling} information, or no additional information (identical to Expt. 2B), in equal proportions.
+See Table 2 for example trials.
 
@@
 In the *predictive frequency* condition, participants were asked ``In the next *time interval*, how many times do you think *person does action*?'', where the *time interval* was the same as given in the past frequency statement.
-In the *habitual endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
-
-### Results
+In the *habitual endorsement* condition, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2B).
 
@@
 
-#### Predictive frequency
-
-Figure \ref{fig:habituals-predictive-figure}B shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
+### Predictive frequency results
+
+Figure \ref{fig:habituals-predictive-figure}B shows the mean predicted future frequency as a function of the past frequency given to the participant and the type of causal information given. 
 We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r format(r.hab.pred.past.baseline.freq, digits = 3)`$). 
@@
 This result implies that our model makes identical predictions for Expt.
-2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
+2B whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to new data to distinguish these models).
 Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-figure}B, yellow and purple dots).
@@
 To account for participant and item variability in this analysis, we also include random effects of intercept and condition for both participants and items.
-Confirming that our manipulation worked as intended, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
+Confirming that our manipulation worked as intended, the preventative information led to significantly lower predictions for future frequency, relative to the baseline condition ($\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Estimate"],2)`$;
 $SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$
-).
-There was also tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionpreventative","t value"],2)`$).
+There was also a tendency for the enabling information to lead to higher predictions for future frequency, relative to baseline ($\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Estimate"],2)`$;
 $SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$
-).
-Finally, past frequency was a significant predictor of predicted future frequency (
-$\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["conditionenabling","t value"],2)`$).
+Finally, past frequency was a significant predictor of predicted future frequency ($\beta = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Estimate"],2)`$;
 $SE = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","Std. Error"],2)`;$
-$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$
-).
-
-#### Habitual endorsement
+$t = `r round(lmer.rs.hab.predictive.summary[["coefficients"]]["logAnnualPastRate","t value"],2)`$).
+
+### Habitual endorsement results
 
@@
 The model based on past frequency does not make different predictions for the different causal manipulation conditions and does a poor job at explaining the endorsements ($r^2(`r r2.hab.rsa.predictive.n`) = `r r2.habituals.rsa.past`$; MSE = $`r mse.habituals.rsa.past`$).
+This result strongly suggests that prevalence represents a predictive belief about the future.
 
@@
 Our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt.
-2a).
-Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b \& c).
-In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
+2A).
+Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2B \& C).
+In Expt. 2B, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
 By manipulating (rather than measuring) the referent frequency, we showed how alternative models were unable to account for the gradience in endorsement.
@@
 <!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
-In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and prevented future occurrences of the action.
+In Expt. 2C, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and prevented future occurrences of the action.
 We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
@@
 
-In these experiments, we introduced participants to novel actors and, by doing so, were able to directly manipulate the frequency of a person doing the action.
+In these experiments, we introduced participants to novel actors and, by doing so, were able to directly manipulate the referent frequency.
 The kinds of events we used were familiar to participants (e.g., *running*) and thus we measured the prevalence priors for those events.

### 2018-10-18 paper/response.tex
update response letter, emboldening parts for ndg approval

@@
 are female}, \emph{mosquitos carry malaria}) that appeared before the experiments; now, both appear before the experiments.
-We describe why each example is interesting, how the model handles each case., and provide a summary in a table (per R1's suggestion).
-By moving these other philosophical puzzles to appear before the experiments, we are able to foreshadow the relevance of \emph{predictive probability} (and motivate Expt. 2c).
+We describe why each example is interesting, how the model handles each case, and provide a summary in a table (per R1's suggestion).
+\textbf{We elaborated the puzzle of ``Elephants live in Africa and Asia'' by adding a figure of the model predictions for this example.
+We note in the worked examples when the relevant puzzle will be tested empirically (e.g., we now foreshadow the relevance of \emph{predictive probability} and motivate Expt.
+2C using ``Supreme Court Justices have even social security numbers'').}
 
@@
 Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
-This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with ours.
+This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with our model.
 This is hopefully now more clearly articulated.
-Finally, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison (in the hope of addressing R3's 2nd comment).
+
+In the hope of addressing Reviewer 3's second comment, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison.
 The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our model is not overparameterized and that the prior in our model is not doing all of the work.
-This also allows us to clarify the sense in which our model is unique (R3's 3rd comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).
+This also allows us to clarify the sense in which our model is unique (R3's third comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).
+
+\textbf{Reviewer 3 also made the more general comment that the presentation of material meanders in the paper. 
+We agree and have added a brief ``Intermediate summary'' section between the two halves of the paper (i.e., the model and related theories section vs. the experiments). 
+This section summarizes the model, worked examples, and related theories and provides an overview of the experiments and the utility of each.
+We hope this aids the readability.}
 
 We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
-We have added a discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
+We have added a paragraph to the introductory remarks of the General Discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
 We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
-We have taken a few paragraphs to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions.
-We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity).
-We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance Sorites sequences).
-We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson (1992)'s epistemicist view.\footnote{
+We have added a subsection to the General Discussion to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions.
+We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity), \textbf{which might point the way towards a more general information-theoretic typology of underspecification.
+}
+We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
+We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson and Simons (1992)'s epistemicist view.\footnote{
 	R2 actually cited Williamson (1994).
-In our searches, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons.
+In our literature search, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons.
 }
@@
 We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
-We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainly.
-This point is a very particular one relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}.
-We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but generics are simpler because they lack a fixed threshold).
+We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainty.
+That comment was meant in a very particular way relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}.
+We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
+\textbf{Reviewer 1 also brings to our attention property-based theories of concepts.
+We now note that we are not committed to any particular theory of concepts as long as they are able to generate quantitative feature probabilities (which could be brought about a number of different conceptual representations).
+We are now more explicit about this when discussing the role of conceptual knowledge in the General Discussion. }
 
-things i'm not sure about:
-\begin{enumerate}
-\item property theories of meaning (R1) \ndg{they are alluding to theories of concepts -- conceptual role, feature-based, etc.
+Finally we have gone through the manuscript and tried to make small changes to improve clarity and citations.
+
+%things i'm not sure about:
+%\begin{enumerate}
+%\item property theories of meaning (R1) \ndg{they are alluding to theories of concepts -- conceptual role, feature-based, etc.
 i think we can add a few comments to the section on relation to conceptual theories of generics about this.
@@
 can you add this?}
-\end{enumerate}
-
-Finally we have gone through the manuscript and tried to make small changes to improve clarity and citations.
+%\end{enumerate}
 

### 2018-10-19 analysis/model-simulations.Rmd
clean up elephants and causal task figures; final polish on case study 3

@@
 
-fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
+fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 50000) %>%
   ggplot(., aes(x = state))+
-  geom_density(adjust = 2, fill = 'grey', alpha = 0.3)+
+  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
   facet_wrap(~marginal, ncol = 1)+
   ggtitle('prevalence priors')+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
   xlab("")+
@@
 
-fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
+fig.eleph.1 <- get_samples(rs.asia.marignals, 50000) %>%
   ggplot(., aes(x = state))+
-  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
+  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3)+
   facet_wrap(~marginal, ncol = 1)+
   ggtitle('"Elephants live in Africa..."')+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
   xlab("Prevalence")+
@@
 
-fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
-  ggplot(., aes(x = state))+
+fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 50000) %>%
+  ggplot(., aes(aes(y = ..scaled..),x = state))+
   geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
   facet_wrap(~marginal, ncol = 1)+
-  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
   xlab("")+
@@
 )
+```
+
+```{r}
+get_samples(rs.asiaafrica.priors, 50000) %>%
+  ggplot(., aes(x = state))+
+  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
+  facet_wrap(~marginal, ncol = 1)+
+  ggtitle('prevalence priors')+
+  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
+  xlab("")+
+  ylab("Probability density")
 ```

### 2018-10-19 paper/case3-causals.Rmd
clean up elephants and causal task figures; final polish on case study 3

@@
 In this experiment, we manipulate participants' background knowledge, measuring these beliefs in order to check whether the manipulation was successful. 
-Experiment 3b (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.
+Experiment 3B (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.
 
@@
 Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the property (e.g., a naturally occurring herb causing animals to be sleepy).
-The two cover stories can be seen in Table 2.
+The two cover stories can be seen in Table 3.
 
-Participants were then shown "previous experimental results", which followed one of four distributions.
+Participants were then shown "previous experimental results", which followed one of four distributions represented as a table of numbers.
 In two of the conditions, participants saw results that came from a single underlying distribution (*common* conditions).
@@
 The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0, 1, or 2 successes), and others that either had strong or weak effects as above.
-These are the *rare strong* and *rare weak* conditions.
+These are the *rare strong* and *rare weak* distributions.
 <!-- These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect. -->
@@
 E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, out.width = "\\textwidth", fig.pos = "!h", cache=F}
-caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
+caus.exp.1 <- ggdraw() + draw_image("figs/causal-task/causal-task.001.png", scale = 1) +
   theme(plot.margin = unit(c(2,0,0,0), "pt")) 
-caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
+caus.exp.2 <- ggdraw() + draw_image("figs/causal-task/causal-task.002.png", scale = 1)+
   theme(plot.margin = unit(c(2,0,0,0), "pt")) 
-caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
+caus.exp.3 <- ggdraw() + draw_image("figs/causal-task/causal-task.003.png", scale = 1)+
   theme(plot.margin = unit(c(2,0,0,0), "pt")) 
-caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
-caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)
+caus.exp.4 <- ggdraw() + draw_image("figs/causal-task/causal-task.004.png", scale = 1)
+caus.exp.5 <- ggdraw() + draw_image("figs/causal-task/causal-task.005.png", scale = 1)
 
-caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh')
+caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh', rel_widths = c(1, 1.2, 2))
 
@@
   plot_grid(title, caus.exp.toprow, ncol=1, rel_heights=c(0.1, 1)),
-  plot_grid(add_sub(caus.exp.4, "Prior elicitation"), add_sub(caus.exp.5,"Causal endorsement"), labels = c("D", "E"), nrow = 1),
+  plot_grid(caus.exp.4,caus.exp.5, labels = c("D", "E"), nrow = 1, align = 'v'),
   nrow = 2)
@@
 
-Participants then click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas.
+Participants then clicked a button to show the results of the experiments, which appeared one at a time in a random order (following a particular distribution).
+Experimental results were also are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas.
 Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment; Figure \@ref(fig:causalExpt)A).
 We described the results of these individual experiments using token-level causal language (e.g., "98 cheebas were made sleepy") to imply that actual causation occurred in these cases.
+Participants see the results of eleven experiments, though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
+(These lost results would be found in the *causal endorsement* task, Expt. 3B).
+After participants viewed the results of the 10 experiments (and 1 missing experiment), they are told to review the results of the experiments before continuing (Figure \@ref(fig:causalExpt)C).
 
-Participants see the results of eleven experiments, though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
-(These lost results would be found in the *causal endorsement* task, Expt. 3b).
-After participants viewed the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing (Figure \@ref(fig:causalExpt)C).
-
-Upon clicking the continue button, the table of experiment results is removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5 experiments (Figure \@ref(fig:causalExpt)D).
-Participants were given five slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).
-
+Upon clicking the continue button, the table of experiment results is removed and participants are told that five more experiments were conducted that day and asked to predict the results of those experiments (Figure \@ref(fig:causalExpt)D).
+Participants were given five slider bars ranging from 0 - 100 to rate the number of predicted successes out of 100 attempts.
 After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen.
@@
 
-`r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
+`r n.subj.cas.failed` participants were excluded from the analysis for failing to answer at least one of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
 The empirically elicited distributions of responses were not appreciably different for our two cover stories (herbs making animals sleepy, fertilizer making plants grow tall) and thus we collapse the data across these two stories.
@@
 
-In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
-Most of the experimental design was identical to that of Experiment 3a.
+In this experiment, we tested whether the manipulated priors of Expt. 3A are causally related to the endorsement of causal statements.
+Most of the experimental design was identical to that of Expt. 3A.
 
@@
 
-The materials were the same as in Expt. 3a.
-The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)A-C).
-Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found.
+The materials were the same as in Expt. 3A.
+
+The first part of the experimental trial was the same as in Expt. 3A (the table of "previous experiments"; Figure \@ref(fig:causalExpt)A-C).
+Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found (the experiment with a "?" in the table).^[
+  We chose to have the scientists report on an earlier "lost experiment" to suggest a binomial generative process for the experiments wherein the scientists planned to perform 11 experiments, as opposed to alternative design wherein an 11th experiment is reported.
+Such a continuation of the series of experiments could imply a generative model following a geometric distribution where the scientists repeat the experiment until they reach one that is successful.
+]
 The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
@@
 
-As predicted by our model, endorsements for a causal statement were sensitive to the causal power of the target cause and, critically, to the background distribution of other causes. 
-When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure\ \@ref(fig:figure-causals)A).
-By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
+As predicted by our model, endorsements for a causal statement were sensitive to the referent prevalence of causal events and, critically, to the background distribution of other causes. 
+When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a causal frequency of 0.2, and were at chance when the causal frequency was 0.7 (Figure\ \@ref(fig:figure-causals), blue bars).
+By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal prevalence of 0.2, and were at ceiling when the prevalence was 0.7.
 The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
@@
 In our third case study, we applied our model to generalizations about causal events, without any changes.
-In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
+In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3A).
 This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
-In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
+In Expt. 3B, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
 In addition to further demonstrating the generality of this theory, these experiments show that the prevalence prior $P(p)$ is causally related to endorsements of generalizations in language.
@@
 <!-- Inituive theories about these domains are flexible enough to permit such manipulations. -->
-
 It is likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
 If this were happening in our domains, we would expect this to show up in the results of Expt.
-3a.
+3A.
 Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
 ]
-For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analogous to our *strong* priors conditions. 
+For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causality, analogous to our *strong* priors conditions. 
 Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our *rare* prior conditions.

### 2018-10-19 paper/comgen-paper.Rmd
clean up elephants and causal task figures; final polish on case study 3

@@
                   family = 'Palatino', fontface = 'bold', size = 3.2, inherit.aes =F, force = 15)+
-    ylab("Normalized probability density") +
+    ylab("Scaled probability density") +
     xlab("Prevalence")+
@@
 C: Full interpretation upon hearing the end of the sentence (\"Elephants live in Africa and Asia\").
-Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.", fig.width = 8, fig.asp = 0.6, out.width = "100%", fig.align = "center", cache=F}
+Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.", fig.width = 8, fig.asp = 0.6, out.width = "80%", fig.align = "center", cache=F}
 load("cached_results/modelSims-elephants.RData")
@@
   ggplot(., aes(x = state))+
-  geom_density(adjust = 2, fill = 'grey', alpha = 0.3, size = 1.5)+
+  geom_density(aes(y = ..scaled..), adjust = 2, fill = 'grey', alpha = 0.3, size = 1.25)+
   facet_wrap(~marginal, ncol = 1)+
@@
   xlab("")+
-  ylab("Probability density")+
+  ylab("Scaled probability density")+
+  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
   theme(plot.title = element_text(size = 10, hjust = 0.5))
@@
   ggplot(., aes(x = state))+
-  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
+  geom_density(aes(y = ..scaled..), adjust = 4, fill = 'grey', alpha = 0.3, size = 1.25)+
   facet_wrap(~marginal, ncol = 1)+
@@
   scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
   xlab("Prevalence")+
-  ylab("Probability density")+
+  ylab("Scaled probability density")+
   theme(axis.title.y = element_blank(),
@@
   ggplot(., aes(x = state))+
-  geom_density(adjust = 4, fill = 'grey', alpha = 0.3, size = 1.5)+
+  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3, size = 1.25)+
   facet_wrap(~marginal, ncol = 1)+
   scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
+  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
   xlab("")+
   ggtitle('"...and Asia"')+
-  ylab("Probability density")+
+  ylab("Scaled probability density")+
   theme(axis.title.y = element_blank(),
-        plot.title = element_text(size = 10, hjust = 0.5))
+        plot.title = element_text(size = 10, hjust = 0.5),
+        axis.ticks.y = element_blank())
 

### 2018-10-23 paper/response.tex
edits to response letter

@@
 We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
-\textbf{Reviewer 1 also brings to our attention property-based theories of concepts.
-We now note that we are not committed to any particular theory of concepts as long as they are able to generate quantitative feature probabilities (which could be brought about a number of different conceptual representations).
-We are now more explicit about this when discussing the role of conceptual knowledge in the General Discussion. }
+\textbf{Reviewer 1 also brings to our attention to property-based theories of concepts.
+We now are explicit---in the section on Intuitive Theories in the General Discussion---that the fact that our semantics is defined in terms of individual properties does not imply that the concepts involved in understanding generics are defined merely by their properties.
+Rather, complex intuitive theories, which can reflect conceptual role, produce prevalence priors which then yield generic judgments.}
 

### 2018-10-25 paper/response.tex
final revisions for resubmission

@@
 We appreciate the time both you and the reviewers have devoted to commenting and critiquing our manuscript.
+%We are greatly impressed by the depth and usefulness of all of the reviews.
 We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
@@
 
-Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
-we have merged the General Discussion subsection ``Other philosophical puzzles'' with the worked examples (e.g., \emph{birds lay eggs vs.
-are female}, \emph{mosquitos carry malaria}) that appeared before the experiments; now, both appear before the experiments.
+Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible, streamlined form,
+we have merged the General Discussion subsection ``Other philosophical puzzles'' (e.g., \emph{Mary handles the mail from Antarctica}) with the examples that appeared before the experiments (e.g., \emph{birds lay eggs vs.
+are female}, \emph{mosquitos carry malaria}); now, both appear before the experiments in a section titled \emph{Worked Examples}.
 We describe why each example is interesting, how the model handles each case, and provide a summary in a table (per R1's suggestion).
-\textbf{We elaborated the puzzle of ``Elephants live in Africa and Asia'' by adding a figure of the model predictions for this example.
+We elaborated the puzzle of ``Elephants live in Africa and Asia'' by adding a figure of the model predictions for this example.
 We note in the worked examples when the relevant puzzle will be tested empirically (e.g., we now foreshadow the relevance of \emph{predictive probability} and motivate Expt.
-2C using ``Supreme Court Justices have even social security numbers'').}
+2C using ``Supreme Court Justices have even social security numbers'').
 
-We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments (after the model section and worked examples).
-We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theories to extant theories. 
+We have taken Reviewers 1 and 3's suggestion of moving the \emph{Relationship to Other Semantic Theories} section to appear before the experiments (after the model section and worked examples).
+We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theory to extant theories. 
 Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
@@
 
-In the hope of addressing Reviewer 3's second comment, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison.
+In the hope of addressing Reviewer 3's second comment, we include an additional subsection in the \emph{Relationship to Other Semantic Theories} section describing the various alternative quantitative models we will use for model comparison.
 The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our model is not overparameterized and that the prior in our model is not doing all of the work.
-This also allows us to clarify the sense in which our model is unique (R3's third comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).
+This also allows us to clarify the sense in which our model is unique (R3's third comment): It is the first model of generics that makes quantitative predictions about human endorsements while connecting to a plausible truth-conditional semantic theory.
 
-\textbf{Reviewer 3 also made the more general comment that the presentation of material meanders in the paper. 
-We agree and have added a brief ``Intermediate summary'' section between the two halves of the paper (i.e., the model and related theories section vs. the experiments). 
+Reviewer 3 also made the more general comment that the presentation of material meanders in the paper. 
+We agree and have added a brief \emph{Interim Summary and Overview of Experiments} section between the two halves of the paper (i.e., the model and related theories section vs. the experiments). 
 This section summarizes the model, worked examples, and related theories and provides an overview of the experiments and the utility of each.
-We hope this aids the readability.}
+We also take Reviewer 1's criticism that the lay explanation of the model could be improved; we have added a short paragraph before the technical details of the model providing a high-level intuition for the model.
+We hope these changes aid the readability.
 
 We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
-We have added a paragraph to the introductory remarks of the General Discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
+We have added a paragraph to the introductory remarks of the General Discussion about how accepting a generic sentence adds information about cue validity to the common ground, which suggests other empirical tests of our account.
 We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
-We have added a subsection to the General Discussion to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions.
-We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity), \textbf{which might point the way towards a more general information-theoretic typology of underspecification.
-}
+We have added a subsection to the General Discussion to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertain as to the exact truth conditions.
+We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is a kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity), which might point the way towards a more general information-theoretic typology of underspecification.
 We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
@@
 In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
-We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
+We have been more explicit in our discussion of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations.
 We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainty.
-That comment was meant in a very particular way relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}.
+That comment was meant in a very particular way relating to Leslie (2007, 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}.
 We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
-\textbf{Reviewer 1 also brings to our attention to property-based theories of concepts.
+Reviewer 1 also brought our attention to property-based theories of concepts.
 We now are explicit---in the section on Intuitive Theories in the General Discussion---that the fact that our semantics is defined in terms of individual properties does not imply that the concepts involved in understanding generics are defined merely by their properties.
-Rather, complex intuitive theories, which can reflect conceptual role, produce prevalence priors which then yield generic judgments.}
+Rather, complex intuitive theories, which can reflect conceptual role, produce prevalence priors which then yield generic judgments.
 

### 2018-10-25 paper/comgen-paper.Rmd
final revisions for resubmission

@@
     address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
-    email         : "mhtessler@stanford.edu"
+    email         : "tessler@mit.edu"
   - name          : "Noah D. Goodman"
@@
 keywords          : "genericity, generalization, generics, pragmatics, semantics, Bayesian modeling"
-wordcount         : "25000"
+wordcount         : "27578"
 
@@
 lineno            : no
-toc               : no
 
@@
 The third section discusses the relationship of our model to previous accounts of generics from the linguistics and philosophical literatures. 
-These introductory sections are followed by three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
+These theoretical sections are followed by three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
 In the case study of generics, we use measure relevant background knowledge and prevalence to predict endorsements of familiar generic statements (e.g., "Robins lay eggs").
@@
 ]
-We first describe a model for generics, before noting how the basic ideas generalize to habituals and causals.
+
+The basic intuition behind our account is that before a listener hears a novel generalization such as "Alligators grow to be 10-feet long", they do not know how widely distributed the property to be in the category, including whether or not it is present at all.
+The utterance provides a vague sense of how strongly the generalization applies (e.g., how many alligators grow to be 10-feet long), which the listener derives from their knowledge of how the property (*growing to be 10-feet long*) is distributed among other categories (e.g., other animals).
+The decision of whether or not to endorse the generalization is that of a speaker reasoning about how well the utterance would align their interlocutor's beliefs about the prevalence of the feature in the category with those of their own.
+We formalize this intuition in a truth-conditional semantics incorporated into a Bayesian model of belief updating.
+<!-- We now the lay out the formal specification of this account along with theoretical justification. -->
+
+### Interpretation model
 
@@
 The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics.
-The prevalence prior $P(p)$ is a distribution over probabilities $p$, which represents the output of a generative model of particular domain.
-For properties of objects, the generative model is naturally a Bernoulli model (e.g., flipping a coin) and thus the support of $P(p)$ is $[0, 1]$.
-For events, the implicit generative model is a Poisson model in which events occur randomly in time.
-The probability density of an event occurring at a particular time is governed by the rate parameter for the Poisson model. 
-Thus, Eq.
+The semantic scale is determined by the prevalence prior $P(p)$.
+For generalizations about categories (i.e., generic statements), $P(p)$ ranges over $[0, 1]$; $p$ denotes the chance that an instance of a category has a Boolean property.
+To apply this same model to generalizations about events (i.e., habituals like “John runs”), we use a different, but related, scale: the frequency within a given time window (e.g., number of times John went for a run in the past week).^[
+  This measure is closely related to the instantaneous probability density of the event, as the time window gets infinitesimally small.
+]
+For events then, $p$ is a rate and $P(p)$ ranges over $[0, \infty)$.
+
+<!-- We thus define the scale for habituals to be over the probability density, or temporal frequency, of the event; the support of $P(p)$ would this case would be -->
+<!-- must compute a probability distribution from the occurrence of events (e.g., a person going for a run). -->
+<!-- One straightforward way is to compute the rate of the event with respect a certain time window (e.g., a day).  -->
+<!-- The probability density of the event occurring in the window is proportional to the rate of the event occurring (e.g., number of times per week).^[ -->
+<!-- For example, if John drinks tea on average four times a week and coffee seven times a week, the relative probability densities of him completing the actions on any given day is $\frac{4}{7}$ and 1, respectively.
+-->
+<!-- ] -->
+
+<!-- For events, the implicit generative model is a Poisson model in which events occur randomly in time. -->
+<!-- The probability density of an event occurring at a particular time is governed by the rate parameter for the Poisson model.  -->
+<!-- Thus, Eq.
 \ref{eq:L0} becomes a model of habitual interpretation (e.g., "John runs") if we take the underlying semantic scale to be that of the temporal frequency of an event (e.g., how often we expect an event to occur); the support of $P(p)$ is this case would be $[0, \infty]$.
+-->
 
@@
 We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
-All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.
+All models, analyses, data and links to experiments used in this paper can be found at \url{https://github.com/mhtess/genlang-paper}.
 
@@
 This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
-\ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below}
-\mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...}
+<!-- \ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below} -->
+<!-- \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...} -->
 The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
-  Alternatively, the prevalence prior can be conceptualized as one aspect of an intuitive theory of a domain. 
+  Alternatively, the prevalence prior can be conceptualized as a marginal distribution on prevalence derived from an intuitive theory formalized in a probabilistic language of thought [e.g., @Goodmanconcepts].
 ]
@@
     "Consider 100% have even social security numbers",
-    "Impossible for most to live in Africa and most to live in Asia"
+    "Impossible for most to live in Africa and most to live in Asia, and no individual elephant lives in both Africa and Asia"
   )
 ) %>%
-  rename("Referent prevalence" = referent.prevalence,
+  rename("Intuitive referent prevalence" = referent.prevalence,
          "Intuitive truth value" = intuitive.truth.value,
@@
 worked.examples.tab <- xtable::xtable(worked.examples, 
-                       caption = "Example sentences that a theory of generalizations should correctly predict. See details of each example in corresponding section.", 
+                       caption = "Example sentences that a theory of the language of generalizations should correctly predict. See details of each example in corresponding section.", 
                        align=c('| p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))
@@
 
-## The role of conceptual knowledge
+## Relation to intuitive theories
 
 Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
-It is this real-world knowledge (presently formalized in terms of a prevalence prior) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
+It is this real-world knowledge (presently formalized in terms of a prevalence prior) where issues about domain specific beliefs, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
 <!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
@@
 We hypothesize that all of this knowledge feeds into participants' predictions, measured through judgments about prevalence.
+That is, even though our underlying semantics is defined in terms prevalence of individual properties, this does not imply that the concepts involved in generic language understanding are defined merely by their properties.
+Instead, complex intuitive theories [that may reflect, for example conceptual role, see @Goodmanconcepts] give rise to prevalence priors, which then yield generic judgements.
 <!-- which we model in a precise, quantitative manner. -->
@@
 We described before that the strikingness of certain properties plausibly influences prevalence priors or a speaker's predictions about future prevalence.
-We have pilot data suggested these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
+We have collected pilot data suggesting these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
 More empirical work is needed to understand whether and how strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.

### 2018-10-25 paper/appendix-bda.Rmd
update model results and analyses
revisions to appendices

@@
 To pin down the prevalence prior and referent prevalence parameters, we use additional data directly related to those parameters (e.g., prior elicitation data).
-Incorporating all data sources into a single Bayesian data analysis model is the appropriate way to track measurement uncertainty for all measurements.
+Incorporating all data sources into a single Bayesian data analysis model is the appropriate way to track measurement uncertainty for all measurements simultaneously.
 <!-- Other model parameters (governing the prevalence prior $P(p_{fk})$ and the referent-prevalence $P_{fk'}$) are estimated using additional behavioral data (e.g., prior elicitation tasks).  -->
@@
 We performed an analogous elicitation in Case Study 3: Causal Language (Expt. 3a).
-We describe the analysis using generics as our running example, but a parallel analysis was done for causals.
+We describe the analysis using generics as our running example, but a parallel analysis was done for causal language.
 
-Participants' responses in the prior elicitation task can be thought of as *samples* from the prevalence prior distribution. 
-Formally, we assume the prior data (analyzed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
-The "transient" distribution intuitively corresponds to categories that do not have the feature normally, but potentially could be caused by accidental forces (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
+Participants' responses in the prior elicitation task can be thought of as samples from the prevalence prior distribution. 
+Formally, we assume the prior data (analyzed independently for each property) was generated from one of two underlying distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
+The "transient" distribution intuitively corresponds to categories that do not have the feature normally, but potentially could acquire the feature by accidental forces (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
 We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
@@
 
-In Case Study 2 (Expt.
+In Case Study 2 on habitual language (Expt.
 2a), we asked participants about parameters of this mixture model (by having participants answer questions about different kinds of people) rather than having participants give samples (e.g., by listing their friends and family members, and rating how often they did certain actions).
@@
 
-In Case Study 1, we used participants prevalence ratings for the category-of-interest in our generic sentences as the referent-prevalence that is used in the endorsement model (Eq. \ref{eq:S1}).
+In Case Study 1 (generics), we used participants prevalence ratings for the category-of-interest in our generic sentences as the referent-prevalence that is used in the endorsement model (Eq.
+\ref{eq:S1}).
 For a given generic sentence (e.g., "Robins lay eggs"), we took the prevalence ratings for the referent-category (e.g., the percentage of robins that lay eggs) from the prior elicitation task (Expt.
@@
 For the parameters of the prevalence priors, we use the same priors described in Expt.
-1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda \sim \text{Uniform}(0,5)$.
+1b; for the speaker optimality parameter, we use a prior with a range consistent with the previous literature that uses the same model class: $\lambda \sim \text{Uniform}(0,5)$.
 We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 150,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].
@@
 
-```{r genericsModelDiagram, fig.cap="Quasi-graphical model corresponding to the fully Bayesian data analysis of the endorsement model.
+```{r genericsModelDiagram, fig.cap="Quasi-graphical model corresponding to the fully Bayesian data analysis of the endorsement model for Case Study 1 (generic language).
 The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
-1a.
-The referent-prevalence $d^{pr}_{k,f}$ is generated from a latent prevalence $p_{fk}$.
-The fixed-threshold (control model) or uncertain-threshold model take the prevalence priors $P(p)$, the referent-prevalence $p$, and a single speaker optimality parameter $\\lambda$ as input.
+1a, which has three parameters: mean of the stable-cause distribution $\\gamma_{f}$ and concentration (inverse-variance) of the stable-cause distribution $\\xi{f}$ and the mixture parameter $\\phi_{f}$.
+The referent-prevalence $d^{pr}_{k,f}$ is generated from a Beta distribution with paramters: mean $\\gamma_{k,f}$ and concentration (inverse-variance) $\\xi{k,f}$.
+The posterior predictives of the prevalence prior $P(p_{fk'})$ and the referent prevalence $p_{fk}$ are then fed into the RSA speaker model $S$, which predicts the generic endorsement data $d^{end}_{k, f}$.
+The speaker model $S$ also takes in the single free parameter $\\lambda$ which operates as a soft-max function.
 This overall structured is repeated (except $\\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
-Note that S corresponds to a probabilistic *function* and not a *random variable* that is standard in graphical model notation; S cannot be represented by a graphical model because it has recursion.
-"}
+Note that $S$ corresponds to a probabilistic function and not a random variable that is standard in graphical model notation; $S$ cannot be represented by a graphical model because it has recursion.
+This entire BDA model is duplicated for the lesioned, fixed-threshold model (which only differs in the definition of $S$).
+The BDA model for habituals and causals mirrors this one, except they do not infer a referent prevalence $p_{fk}$ (they are assumed to be the same as those experimentally supplied to participants).", out.width = "0.8\\textwidth", fig.align="center"}
 knitr::include_graphics("figs/generics_bayesnetmodel.pdf", dpi = 108)
@@
 ]
-If the joint inference model (which models all data sources---referent prevalence, prevalence prior, and generic endorsement---simultaneously) infers referent-prevalence values substantially different from those inferred by a model of referent prevalence in isolation, that would suggest that the joint-model is distorting the prevalence parameters to accomodate the endorsement data.
+If the joint inference model (which models all data sources---referent prevalence, prevalence prior, and generic endorsement---simultaneously) infers referent-prevalence values substantially different from those inferred by a model of referent prevalence in isolation, that would suggest that the joint-model is distorting the prevalence parameters to accommodate the endorsement data.
 Such a result would call into question the inferences we as scientists derive from the joint inference model.

### 2018-10-25 paper/appendix-cueValidity.Rmd
revisions to appendices

@@
 In Experiment 1, we articulated an alternative model by measuring cue validity (and prevalence) and predicting generic endorsement from a linear combination of these parameters.
-In a small review of the literature, we discovered different methods for measuring cue validity; in piloting, these different methods lead to different results. 
+In a small review of the literature, we discovered different methods for measuring cue validity; in piloting, we found these different methods led to different results. 
 Therefore, we propose three *a priori* desiderata that a measurement of cue validity should satisfy.
@@
 
-Measuring cue validity involves collecting participants' judgments that relate to the probability that an exemplar is a member of a kind given that it has a feature : $P(x \in k \mid x \in f)$.
+Measuring cue validity involves collecting participants' judgments that relate to the probability that an exemplar is a member of a kind given that it has a feature: $P(x \in k \mid x \in f)$.
 There are several ways one could measure cue validity. 
-Here we consider two measures: One has participants estimate the probability $P(x \in k \mid x \in f)$ directly, a common technique in the literature on generic language [e.g., @Khemlani2012; @Prasada2013], and another has participants freely produce categories given a feature [i.e., draw a sample from the conditional distribution on kinds given a feature; @Cree2006].
+Here we consider two measures: The first has participants estimate the cue validity probability $P(x \in k \mid x \in f)$ directly, a common technique in the literature on generic language [e.g., @Khemlani2012; @Prasada2013], and another has participants freely produce categories given a feature [i.e., draw a sample from the conditional distribution on kinds given a feature; @Cree2006].
 We will refer to the former the *direct question* method and the latter the *free production* method.
@@
 Are the *direct question* and the *free productions* equally valid for measuring cue validity?
-We propose *a priori* three boundary conditions that the measurement should be able to satisfy.
+We propose *a priori* three boundary conditions that a measurement of cue validity should satisfy.
 For each case, we provide four examples from our larger stimulus set on generics (Case Study 1) which will be used to evaluate each measure.
@@
 \item{Completely undiagnostic features: A number of features are shared by almost every category.
+The cue validity of these features for particular categories should be extremely low or 0.
 The ones we will use are: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard).
-The cue validity of these features for particular categories should be extremely low or 0.
 Learning that an entity is female tells you almost nothing about what kind of animal it is.}
@@
 Of primary interest is the measurement for the desiderata items described above.
-Links to the experiments can be found on \url{https://mhtess.github.io}.
+Links to the experiments can be found on \url{https://github.com/mhtess/genlang-paper}.
 
@@
 
-To process the free production, we forced all characters in a repsonse to lower case, removed spaces, and made all terms into singular terms (e.g., "lions" --> "lion").
-As well, "mosquito" was a commonly mispelled label; we counted anything that started with "mosqu", "mesqu", "misqu", "mosiq" as "mosquito".
+To process the free production, we forced all characters in a response to lower case, removed spaces, and made all terms into singular terms (e.g., "lions" --> "lion").
+As well, "mosquito" was a commonly misspelled label; we counted anything that started with "mosqu", "mesqu", "misqu", "mosiq" as "mosquito".
 
@@
 Dotted lines denote theoretical cue validity representing the desiderata (see text).
-B: Raw empirical distributions for direct question task.
+B: Raw empirical distributions for the undiagnostic features in the direct question task.
 C: Correspondence between measured cue validity and prevalence prior derived cue validity.", out.width="\\textwidth", fig.pos="!h", cache = F}
@@
 These two items are: ("is red", "cardinal") and ("is white", "swan").
-These items should have relatively low cue validity and are overestimated by the prevalence prior because of the prior on categoryies $P(k)$ (i.e., because they were supplied to every participant and thus get a higher weighted in the prior for deriving cue validity).
-In comparison, the direct question measurement consistently overestimates cue validity relative to the cue validity derived from the prevalence prior for almost all of the items.
+These items should have relatively low cue validity and are overestimated by the prevalence prior because of the prior on categories $P(k)$ over-represents the categories that were supplied to every participant and thus get a higher weighted in the prior for deriving cue validity.^[
+  This deviation could be reduced in future experiments by performing a fully free production version of the prevalence prior task (i.e., without supplying the referent categories).
+]
+In comparison, the direct question measurement overestimates cue validity for almost all of the items relative to the cue validity derived from the prevalence prior.
 
@@
 In addition, cue validity derived from our prevalence prior measurement (Expt. 1b) also satisfied these boundary conditions. 
-We conclude that researchers interested in comparing cue validity to generic truth judgments should use a free production paradigm for measuring cue validity.
+Researchers interested in comparing cue validity to generic truth judgments should use a free production paradigm for measuring cue validity.

### 2018-10-25 paper/appendix-cvDerivation.Rmd
revisions to appendices

@@
 
-Cue validity is defined for a particular category--property pair (e.g., *mosquitos* and *carry malaria*), and relates to referent-prevalence (e.g., how many mosquitos carry malaria) via the prevalence of *carrying malaria* in other categories $k'$ by Bayes' Rule:
+Cue validity is defined for a particular category--property pair (e.g., *mosquitos* and *carry malaria*), and relates to the referent prevalence (e.g., how many mosquitos carry malaria) via Bayes' Rule:
 $$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{Z} $$
-where $Z =  \sum_{k' \in K} P( f \mid k') \cdot P( k')$
+where $Z =  \sum_{k' \in K} P( f \mid k') \cdot P( k')$, the average or marginal prevalence of the feature (e.g., *carrying malaria*) in other categories $k'$.
 
-The prevalence prior $P(p)$ (Eq. \ref{eq:L0}) is a probability distribution over prevalence for different categories $k'$.
+The prevalence prior $P(p)$ using the generic interpretation model (Eq. \ref{eq:L0}) is a probability distribution over prevalence for different categories $k'$.
 <!-- For ease of exposition, let $x = p = P(f \mid k)$; that is, $P(x) = P(p)$. -->

### 2018-10-26 paper/comgen-paper.tex
tweak wording in causal intro
update readme; remove packrat; update tex

@@
-\documentclass[english,floatsintext,man]{apa6}
-
+\documentclass[english,,man,floatsintext]{apa6}
+\usepackage{lmodern}
 \usepackage{amssymb,amsmath}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 % use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-
-% Table formatting
-\usepackage{longtable, booktabs}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-
-\newenvironment{lltable}
-  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
-  {\end{ThreePartTable}\end{center}\end{landscape}}
-
-% The following enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand\getlongtablewidth{%
- \begingroup
-  \ifcsname LT@\roman{LT@tables}\endcsname
-  \global\longtablewidth=0pt
-  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
-  \@nameuse{LT@\roman{LT@tables}}%
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={The Language of Generalization},
+            pdfauthor={Michael Henry Tessler~\& Noah D. Goodman},
+            pdfkeywords={genericity, generalization, generics, pragmatics, semantics, Bayesian
+modeling},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
 \fi
-\endgroup}
-
-  \usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
 \fi
-\hypersetup{breaklinks=true,
-            pdfauthor={},
-            pdftitle={The language of generalization: Probability, vagueness, and interaction},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setlength{\parindent}{0pt}
-%\setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-
-\ifxetex
-  \usepackage{polyglossia}
-  \setmainlanguage{}
-\else
-  \usepackage[english]{babel}
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
 
-% Manuscript styling
-\captionsetup{font=singlespacing,justification=justified}
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+  \title{The Language of Generalization}
+    \author{Michael Henry Tessler\textsuperscript{1}~\& Noah D.
+Goodman\textsuperscript{1}}
+    \date{}
+
+\shorttitle{The language of generalization}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Psychology, Stanford University}
+\keywords{genericity, generalization, generics, pragmatics, semantics, Bayesian modeling\newline\indent Word count: 27578}
 \usepackage{csquotes}
 \usepackage{upgreek}
-
-\usepackage{tikz} % Variable definition to generate author note
-
-% fix for \tightlist problem in pandoc 1.14
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Essential manuscript parts
-  \title{The language of generalization: Probability, vagueness, and interaction}
-
-  \shorttitle{The language of generalization}
-
-  \author{Michael Henry Tessler\textsuperscript{1}~\& Noah D. Goodman\textsuperscript{1}}
-
-  \def\affdep{{"", ""}}%
-  \def\affcity{{"", ""}}%
-
-  \affiliation{
-    \vspace{0.5cm}
-          \textsuperscript{1} Department of Psychology, Stanford University  }
-
-  \authornote{
-    \newcounter{author}
-    This manuscript is currently in prep. Comments or suggestions should be
-    directed to MHT.
-
-                      Correspondence concerning this article should be addressed to Michael Henry Tessler, 450 Serra Mall, Bldg.
-420, Rm.
-316, Stanford, CA 94305.
-E-mail: \href{mailto:mtessler@stanford.edu}{\nolinkurl{mtessler@stanford.edu}}
-                          }
-
-  \abstract{Generalizations are central to human understanding and language provides
-simple ways to convey them (e.g., ``Birds fly''). The language of
-generalization is ubiquitous in everyday discourse and child-directed
-speech. Yet the meaning of these expressions is logically puzzling
-(e.g., not all birds fly) and has resisted precise formalization. The
-major issue in formalizing generalization in language is determining
-which statements are true or which are false. Using an
-information-theoretic probabilistic model, we explore the hypothesis
-that the meaning of these linguistic expressions is \emph{simple but
-underspecified}, and that general communicative principles can be used
-to establish a more precise meaning in context. To test this theory, we
-examine endorsements of generalizations about three different domains:
-categories (\emph{generic language} e.g., ``Birds fly''), events
-(\emph{habitual language} e.g., ``John runs''), and causes (\emph{causal
-language} e.g., ``Staring at the sun makes you go blind''). Across these
-diverse domains, we find that our model explains the wide variance in
-human endorsements of language conveying generalization, while simpler
-models fall short. Ours is the first formal theory that makes precise,
-quantitative predictions about human understanding of the language of
-generalization. The results demonstrate that the context-sensitivity of
-such language emerges from the interaction of an underspecified meaning
-with diverse beliefs about properties.}
-  \keywords{genericity, generalization, generics, pragmatics, semantics, bayesian
-modeling \\
-
-    \indent Word count: 20000
-  }
-
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
 \usepackage{tabularx}
@@
 \usepackage{multirow}
+\usepackage{xcolor}
+
+\authornote{This paper is currently under review. Comments or
+suggestions are appreciated and should be directed to MHT.
+
+Correspondence concerning this article should be addressed to Michael
+Henry Tessler, 450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305.
+E-mail:
+\href{mailto:tessler@mit.edu}{\nolinkurl{tessler@mit.edu}}}
+
+\abstract{
+Language provides simple ways of communicating generalizable knowledge
+to each other (e.g., ``Birds fly'', ``John hikes'', ``Fire makes
+smoke''). Though found in every language and emerging early in
+development, the language of generalization is philosphically puzzling
+and has resisted precise formalization. Here, we propose the first
+formal account of generalizations conveyed with language that makes
+quantitative predictions about human understanding. We test our model in
+three diverse domains: generalizations about categories (generic
+language), events (habitual language), and causes (causal language). The
+model explains the gradience in human endorsement through the interplay
+between a simple truth-conditional semantic theory and diverse beliefs
+about properties, formalized in a probabilistic model of language
+understanding. This work opens the door to understanding precisely how
+abstract knowledge is learned from language.
+
+}
 
 \usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
 \theoremstyle{definition}
-\newtheorem{example}{Example}
+\newtheorem{example}{Example}[section]
 \theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
+\newtheorem{exercise}{Exercise}[section]
 \theoremstyle{remark}
@@
 \begin{document}
-
 \maketitle
-
-\setcounter{secnumdepth}{0}
 
@@
 \newcommand*\diff{\mathop{}\!\mathrm{d}}
-
-\definecolor{Red}{RGB}{255,0,0} \definecolor{Green}{RGB}{10,200,100}
+\definecolor{Red}{RGB}{255,0,0}
+\definecolor{Green}{RGB}{10,200,100}
 \definecolor{Blue}{RGB}{10,100,200}
@@
 
-\section{Introduction}\label{introduction}
-
-Learning that an object tends to have a property, an entity tends to
-exhibit a behavior, or a cause tends to produce an effect can be crucial
-to thrive in our open-ended world. Yet such knowledge can be difficult
-to acquire: Relevant observations may be costly (e.g., learning that a
-plant is poisonous) or rare (e.g., understanding that lightning strikes
-tall objects). It thus is important that language allow us to
-communicate such \emph{generalizations} to each other. By sharing
-generalizations, we flourish collectively without individually needing
-to taste potentially-poisonous plants or personally witness many
-lightning strikes. Flexibly communicating generalizations from one
-generation to the next may be a foundational mechanism behind the
-faithful transmission of knowledge necessary for cumulative cultural
-evolution (Henrich, 2015; Tomasello, 1999).
-
-The language of generalization is often studied via \emph{generic
-language} (or, \emph{generics}): simple statements predicating
-properties of categories (e.g., ``Dogs are friendly''; Carlson, 1977;
-Cohen, 1999; Leslie, 2007; Nickel, 2008). Generics are ubiquitous in
-everyday conversation as well as in child-directed speech (Gelman,
-Goetz, Sarnecka, \& Flukes, 2008). In contrast to \emph{particular
-statements} (e.g., \enquote{Rufus is friendly}) which describe
-individual entities or situations and can be verified through
-observation, generic statements refer to inherently unobservable
-categories (e.g., the category of \textsc{dogs}) and convey information
-that extends beyond the present context, a fact which children as young
-as 2 appreciate (Cimpian \& Markman, 2008). Generics are just one case
-in the language of generalization, however; events can be described in
-generalization (\emph{habitual language}; e.g., \enquote{Mary swims
-after work.}) as well as causal relationships (\emph{causal language};
-e.g., \enquote{Staring at the sun makes you go blind.}). Every language,
-it is believed, can express generalization (Behrens, 2005; Carlson \&
-Pelletier, 1995) and is central to the growth of conceptual knowledge
-(Gelman, 2004). Considering generalization as a singular phenomenon in
-language, thus, promises to provide understanding of a wide variety of
-linguistic expressions with powerful implications.
-
-Despite their ubiquity and relative simplicity, there have been few
-formal models of the language of generalization and none that have made
-precise, quantitative predictions to match human intuitions. The major
-challenge in formalization is determining \emph{what makes the
-statements true or false}. When we hear \enquote{Dogs bark}, it sounds
-like a universal statement, as in \enquote{All dogs bark}. But the
-property does not apply to all dogs: Basenji dogs are barkless\footnote{\url{http://strangesounds.org/2014/09/basenji-dogs-basenjis-dont-bark-howl.html}},
-for example. The generalization could signal something weaker like
-\enquote{Most dogs bark}. However, most mosquitos do not carry malaria
-(in fact, only a tiny fraction do), but \enquote{Mosquitos carry
-malaria} is intuitively true. The only quantifier that would permit such
-a statement would be \enquote{some} (e.g., \enquote{Some mosquitos carry
-malaria}). But weakening the generalization to mean \enquote{some} is
-too permissive: some robins are female (in fact, half of them are), but
-asserting \enquote{Robins are female} seems odd. Even more perplexing:
-Those very same female robins lay eggs, and \enquote{Robins lay eggs} is
-a perfectly fine thing to say.
-
-These observations have led to the conclusion that the prevalence of the
-feature (or the probability of a member of the category having the
-property e.g., \(P(x \text{ barks} \mid x \text{ is a dog})\)) is not
-the only parameter in the meaning of generalizations. Conceptual
-accounts of generics emphasize the structure of \emph{generic knowledge}
-(Prasada, 2000), and view generic utterances as the way of expressing
-special, mental relationships between kinds and properties (Leslie,
-2008; Prasada, Hennefield, \& Otap, 2012). \enquote{Bishops move
-diagonally} not because bishops tend to move diagonally but rather
-because those are the rules of the game. It's been suggested that the
-mind has cognitive primitives that directly dictate what generalizations
-are true or false. One such primitive is the ability to priviledge
-\emph{characteristic features}: For an animal, their mode of
-reproduction is a characteristic feature. Thus, whatever their mode of
-reproduction may be will make a true generic statement (e.g.,
-\enquote{Robins lay eggs}), regardless of the actual prevalence of the
-feature. \emph{Horrifying} or \emph{striking} information is also
-priviledged and creates true generics, which is why \enquote{Mosquitos
-carry malaria} is true
-
-Yet, generics convey more than just rich, conceptual relations (Nickel,
-2008, 2016; Sterken, 2015). Purely arbitrary relationships can result in
-true generics. \enquote{Barns are red} because barn-owners tend to paint
-their barns red; were barn-owners to decide tomorrow to switch to blue,
-then \enquote{Barns are red} would be false. Ravens and toasters have no
-priviledged relationship to each other, but the statement
-\enquote{Ravens are bigger than toasters} is still a true
-generalization. Conceptual accounts must be supplemented with the
-proviso that, in some situations, the actual prevalence of the feature
-matters for making generalizations true.
-
-What we are left with is hybrid theories, which try to classify
-different kinds of generalizations and the various inferences they
-support (e.g., Prasada, Khemlani, Leslie, \& Glucksberg, 2013). But
-insofar as there is a single class of linguistic expressions that convey
-generalization, there should be something common to them all: a general,
-unified semantic core. In this paper, we propose such a semantic core
-for the language of generalization. To do so, we look to probability,
-the universal currency of belief and a useful representation for human
-generalization from observations (Shepard, 1987; Tenenbaum \& Griffiths,
-2001). Given that certain probabilities are the result of inductive
-generalization, it would make sense that these are the object of
-communication in the language of generalization. To formalize a model of
-endorsement (i.e., what makes the statements true or false), we consider
-the information-theoretic function of a generalization by explicitly
-modeling the background knowledge a language interpreter would use when
-understanding such language. We create an endorsement model based on
-this interpretation hypothesis, providing the first formal theory that
-makes quantitative predictions about what makes generalizations in
-language true or false. The assumptions of the theory, and in turn, the
-conditions under which the theory may be meaningfully tested are made
-explicit by its instantiation in a formal model. Though concepts such as
-\emph{striking properties} are not explicitly formalized in our model,
-our general cognitive modeling framework provides natural avenues for
-future integration.
-
-The paper is organized as follows. In Section 1, we formalize the
-hypothesis that the core of meaning of a generalization in language is
-simple but \emph{underspecified}, articulate a thory of relevant
-background knowledge used to understand a generalization in language,
-and develop a computational model of endorsement around these
-components. The endorsement model's predictions depend upon the
-background knowledge and the probability communicated, which we
-demonstrate via simulation. Sections 2 - 4 present our three empirical
-case studies: generalizations about categories (\emph{generic
-language}), events (\emph{habitual language}), and causes (\emph{causal
-language}). Across these three case studies, we both measure and
-manipulate background knowledge and the probability communicated,
-measuring their effects on endorsement. We find a very strong agreement
-of our model's predictions to the full spectrum of human elicited
-endorsements, where alterantive models fall short. This work opens the
-door to understanding generalizations in pragmatic language
-understanding contexts and building models of learning from language.
-
-\section{Computational Framework}\label{computational-framework}
-
-Generalizations are used to make predictions about properties of
-instances that an agent has yet to experience (Hume, 1888). People
-readily predict that a new dog will have fur, drinking a new cup of
-coffee will cause jitters, and a new day will find certain people
-typing. In each case, we assign a specific exemplar \(x\) to a category
-\(k\), and make a prediction that it will have property \(f\). This
-prediction can be described by a conditional probability:
-\(p_{fk} = P(x \in f \mid x \in k)\), the probability that \(x\) will
-have \(f\) (formally, be in the set of things that have \(f\)) given
-that it is in \(k\), which we will refer to as the \textbf{prevalence}.
-The targets of our predictions can vary widely: They may be objects (a
-dog), events (a coffee drink), or more fine grained types (a person on a
-given day). The properties also vary (e.g., having fur, causing jitters,
-typing). Yet the mathematical description of the inductive inference is
-always given by the probability \(p_{fk}\).
-
-How does one acquire such an inductive belief? Observing instances of
-the category \(k\) and noting how many of them have \(f\) can support
-prediction to new instances when integrated with one's prior
-expectations about the property (cf., Gelman, 2003; Keil, 1992). For
-example, if you observe creatures that \textsc{have two legs}, you might
-infer that all creatures of that category have two legs. Observing new
-creatures with \textsc{broken wings}, however, leads to a much weaker
-prediction about other instances of the category having the property
-(Nisbett, Krantz, Jepson, \& Kunda, 1983). This kind of domain-specific
-knowledge about properties can be represented formally as a probability
-distribution over the prevalence \(p_{f}\): \(P(p_{f})\) (Kemp \&
-Tenenbaum, 2008), and observational data \(d\) can update one's beliefs
-via Bayes' Rule:
-\(P(p_{f} \mid d) \propto P(d \mid p_{f}) \cdot P(p_{f})\)
-
-Learning from observational evidence can only take you so far, though.
-To learn about properties that are costly to observe (e.g.,
-\emph{staring at the sun makes you go blind}) or events that are
-statistically rare (e.g., \emph{lightning strikes tall objects}), one
-would much rather learn from others. Fortunately, language has simple
-ways of encoding generalizations.
-
-\subsection{Generalization from
-language}\label{generalization-from-language}
-
-The language of generalization manifests when a property is predicated
-of a category: \enquote{Ks F} (e.g., \enquote{Dogs bark},
-\enquote{Staring at the sun makes you go blind}). Generalization from
-observations can be described as a predictive probability; it is
-intuitive then to posit that same quantity will be at the core of a
-semantic theory of the language of generalization. To connect to the
-semantic tools of \emph{truth values} (Montague, 1973), we must relate
-the scalar quantity of probability to a Boolean value. One simple way is
-with a \emph{threshold semantics}: An utterance is true if the relevant
-quantity is above a threshold. A threshold semantics for a
-generalization about category K with property F would then apply to the
-\emph{prevalence} \(p_{fk}\):
-\(\denote{K \text{ } F}(p_{fk}, \theta) = \{p_{fk} >\theta\}\)
-
-Various attempts of this kind have been made before (e.g., Cohen, 1999).
-We distinguish our proposal from previous ones by emphasizing the
-cognitive underpinnings of \(p_{fk}\), as well as the formalization into
-a model that makes precise, quantitative predictions about human
-endorsements. \(p_{fk}\) describes a latent belief and should not be
-confused with \emph{frequency}, which can inform a belief but is not
-itself the belief.
-
-\subsubsection{Literal interpretation
-model}\label{literal-interpretation-model}
-
-Quantifier statements can be described using a similar threshold
-semantics:
-\(\denote{some \text{ } K \text{ } F}(p_{fk}) = \{p_{fk} > 0\}; \denote{all \text{ } K \text{ } F} = \{p_{fk} = 1\}\).
-So what threshold \(\theta\)? should be used for the generalizations?
-Unlike quantified language which have fixed-thresholds, we posit that
-the language of generalizations is \emph{underspecfied} with respect to
-the actual truth-functional threshold \(\theta\). That is, we
-hypothesize that \(\theta\) is in part determined by contextual, in a
-way analagous to how gradable adjectives like \enquote{tall} have
-contextually-determined thresholds (e.g., what counts as ``tall'' for a
-four-year-old is different than what counts as ``tall'' for an adult;
-Kennedy, 2007; Lassiter \& Goodman, 2013).
-
-We formalize this underspecified semantics in a probabilistic model,
-where the underspecifed threshold \(\theta\) is sampled from a uniform
-prior distribution over possible thresholds \(P(\theta)\) (cf., Lassiter
-\& Goodman, 2013). After making explicit the relevant background
-knowledge about the property \(P(p_f)\), the model becomes:
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Knowledge that extends beyond the present context is crucial to thrive
+in our open-ended, dynamic world. Yet such knowledge can be difficult to
+extract from the environment: The relevant observations may be costly
+(e.g., learning that a plant is poisonous) or rare (e.g., understanding
+that lightning strikes tall objects). Fortunately, we are not limited to
+acquiring generalizations on our own; language allow us to communicate
+generalizations to each other. By sharing generalizable knowledge, we
+flourish collectively without individually needing to taste
+potentially-poisonous plants or personally witness lightning strikes.
+Being able to flexibly communicate generalizations from one generation
+to the next supports the faithful transmission of knowledge necessary
+for culture to cumulatively evolve (Henrich, 2015; Tomasello, 1999).
+
+The \emph{language of generalization} covers a diverse swath of natural
+language expressions. Generic language conveys generalizations about
+categories (e.g., ``Dogs have four legs''; Carlson, 1977; Cohen, 1999;
+Leslie, 2007; Nickel, 2008) and is the most well-studied case
+generalizations in language.\footnote{Some writers refer to the all of
+  the \emph{language of generalization} as \enquote{generic language} or
+  generics. In both the empirical and theoretical literatures, however,
+  analysis and experiments often focus only on generalizations about
+  categories. We use the more narrow-scoped terms (e.g., generics,
+  habituals, and causals) to highlight the diversity of semantic types
+  being predicated.} In contrast to statements about concrete
+individuals (e.g., \enquote{Rufus has four legs}), generic statements
+refer to inherently unobservable categories (e.g., the category of
+\textsc{dog}) and convey information that extends beyond the present
+context, a fact which children as young as 2 appreciate (Cimpian \&
+Markman, 2008). Simple events (e.g., \enquote{John ran yesterday}) can
+be generalized into habitual sentences (e.g., \enquote{John runs}), and
+even events of complex inferential types such as actual causal events
+(e.g., \enquote{The fire caused the smoke}) can be described in
+generalization (e.g., \enquote{Fire causes smoke}).
+
+Understanding the language of generalization is a project with
+far-reaching implications. The language of generalization is ubiquitous
+in everyday conversation, is found in every language (Behrens, 2005;
+Carlson \& Pelletier, 1995), and conveys rich meanings, impacting
+motivation (Cimpian, Arce, Dweck, \& Markman, 2007), transmitting
+stereotyped beliefs about social categories (Rhodes, Leslie, \& Tworek,
+2012), and making meaning from experience (Orvell, Kross, \& Gelman,
+2017). It is highly-prevalent in child-directed speech (Gelman, Goetz,
+Sarnecka, \& Flukes, 2008) and its ability to refer to abstractions
+beyond the present context suggests its centrality to the growth of
+conceptual knowledge (Gelman, 2004).
+
+Despite its ability to convey abstract knowledge, its ubiquity in
+discourse, and its relative morphosyntactic simplicity, the language of
+generalization displays subtle context-sensitivities that make it
+difficult to formalize. \enquote{Robins lay eggs} sounds true and
+\enquote{Robins are female} does not. Yet in each case, only 50\% of the
+category has the property (i.e., only the females lay eggs).
+\enquote{Mosquitos carry malaria} sounds true despite malaria being
+present in only a tiny fraction of mosquitos. Even more perplexing:
+\enquote{Supreme Court Justices have even social security numbers} is
+thought to be intuitively a false generalization even if it were the
+case that on the current bench, nine out of nine justices had even
+social securtity numbers (i.e., when the sentence ``All Supreme Court
+Justices have even social security numbers'' is true; Cohen, 1999).
+Similar context-sensitivity can be observed with habituals:
+\enquote{Mary climbs mountains} could imply a few mountain climbs a year
+for Mary, but \enquote{John runs} would be infelicitious if John went
+for a run three times last year.
+
+These observations have led some to conclude that the literal meaning of
+a generic statement (and by analogy, other generalizations in language)
+involves more than just the number of members of the category who have
+the property, otherwise known as the \emph{prevalence} of the feature in
+the category. Instead, theorists have argued that generics are not
+treatable by the standard tools of truth-functional semantics (Montague,
+1973), but rather should be thought of semantically as a direct,
+linguistic manifestation of abstract relations between kinds and
+properties (Leslie, 2008; Prasada, 2000; Prasada, Hennefield, \& Otap,
+2012). For example, the statements \enquote{Bishops move diagonally} or
+\enquote{The Speaker of the House succeeds the Vice President} are true
+not because of a tendency on behalf of instances of a category to
+actually uphold the property, but rather the existence of a conceptual
+relationship (e.g., what it means, in the game of chess, to be a
+bishop). True generics can be supported by different underlying types of
+category--property relations (e.g., principled vs.~statistical
+connections; Prasada \& Dillingham, 2006), and thus support
+qualitatively different inferences (e.g., ``Being striped is one aspect
+of being a tiger'' is generally endorsed, while ``Carrying malaria is
+one aspect of being a mosquito'' is not, even while ``Tigers are
+striped'' and ``Mosquitos carry malaria'' are both intuitively true;
+Prasada, Khemlani, Leslie, \& Glucksberg, 2013). This conceptual view of
+generics has been influential in psychology, because it predicts
+qualitative differences between different kinds of generics.
+
+Insofar as there is a single class of linguistic expressions that convey
+generalization, however, there should be something common to them all: a
+literal meaning that unifies generic, habitual, and causal language. In
+this paper, we propose such a semantic core based on prevalence or
+probability and formalized using the tools of truth-functional semantics
+(Cohen, 1999; Montague, 1973). A semantics based on probability will not
+be enough to subtle sensitivities to context that the language of
+generalization exhibit. We propose that the meaning of generalizations
+is underspecified or \emph{vague}, and that listeners derive a more
+precise interpretation in context using world knowledge.
+
+The fact that generics are vague does not preclude them from being
+treated with formal models. We draw upon the tools of Bayesian models of
+cognition (Tenenbaum, Kemp, Griffiths, \& Goodman, 2011) to formalize
+the vagueness and context-dependence of generic language (Frank \&
+Goodman, 2012; Goodman \& Lassiter, 2015). The Bayesian model separates
+the semantics of an utterance conveying a generalization from the world
+knowledge a listener would use to interpret the utterance, a key
+theoretical advancement beyond previous accounts. This formal model is
+the first of its kind to make quantitative predictions about human
+understanding of generalization in language.
+
+The paper is organized as follows. In the next section, we describe our
+computational framework for interpreting generalizations and our precise
+model for endorsing such statements (i.e., a model of truth judgments).
+To illustrate how the model works, we then work through a number of
+standard examples from the linguistics literature that any model of
+generics should be able to accomodate. The third section discusses the
+relationship of our model to previous accounts of generics from the
+linguistics and philosophical literatures. These theoretical sections
+are followed by three empirical case studies: generalizations about
+categories (\emph{generic language}), events (\emph{habitual language}),
+and causes (\emph{causal language}). In the case study of generics, we
+use measure relevant background knowledge and prevalence to predict
+endorsements of familiar generic statements (e.g., \enquote{Robins lay
+eggs}). In the study of habituals, we measure background knowledge but
+manipulate the prevalence or frequency of the event to predict
+endorsements of habitual statements about novel agents (e.g.,
+\enquote{John runs} given that he's run a certain number of times in the
+past). In this case study, we also further examine the nature of the
+relevant probabilities for endorsing generalizations, asking whether it
+matters how often John has run in the past (past frequency) or how often
+a speaker expects him to run in the future (predictive probability).
+Finally, in our last case study, we manipulate background knowledge to
+show its causal influence on endorsing generalizations about novel
+causal events (e.g., \enquote{Herb X makes wugs sleepy}). We compare our
+model to two previously articulated quantitative models of generics as
+well as a lesioned-version of our model. In all cases, we find a very
+strong agreement of our model's predictions to human elicited
+endorsements, where the simpler models fall short. We conclude our paper
+by clarifying some of the theoretical claims of the model and discuss
+open-questions for this approach.
+
+\hypertarget{computational-framework}{%
+\section{Computational Framework}\label{computational-framework}}
+
+Generalizations are used to make predictions about events or properties
+of instances that an agent has yet to experience (Hume, 1888). People
+readily predict that the next dog they encounter will have four legs,
+drinking another cup of coffee will cause jitters, and a new day will
+find the people that we know doing what they habitually do. In each
+case, we assign a specific exemplar \(x\) to a category \(k\), and make
+a prediction that it will have feature \(f\). This prediction can be
+described by a conditional probability: \(P(x \in f \mid x \in k)\), the
+probability that \(x\) will have \(f\) given that it is in \(k\)
+(formally, an instance of \(k\) will be in the set of things that have
+\(f\)), which we will refer to as the \emph{prevalence} and for
+convenience write as \(p = P(f \mid k)\). Our \emph{prevalence} \(p\) is
+a \emph{prevalence in the mind}, a latent belief that a future instance
+of a category would have a particular property; others might call this
+projectibility (Goodman, 1955). The targets of our predictions can vary
+widely: They may be objects (a dog), events (an instance of
+coffee-drinking), or more ad-hoc types (a person on a particular day).
+The properties also may vary (e.g., having fur, causing jitters, going
+to the gym). Yet the mathematical description of the inductive belief is
+always given by a probability \(P(f \mid k)\).
+
+Probability is a useful representation for human generalization from
+observations (Shepard, 1987). If you observe several \emph{wugs} (a
+novel category) that have two legs, you might infer that all wugs have
+two legs. But not all properties have such strong projectibility: Seeing
+a wug with broken wings tells you comparatively less about other wugs
+having broken wings (Nisbett, Krantz, Jepson, \& Kunda, 1983). Abstract,
+potentially domain-specific, beliefs about the projectibility of
+different properties can be represented by a probability distribution
+over the prevalence \(P(p)\) (Kemp, Perfors, \& Tenenbaum, 2007). By
+assuming some generative process that could produce one's observations
+\(o\) (i.e., a likelihood function \(P(o \mid p)\)), Bayes' Theorem
+provides the mathematically correct way to update one's prior beliefs
+from observations \(o\): \(P(o \mid d) \propto P(o \mid p) \cdot P(p)\)
+(Tenenbaum \& Griffiths, 2001).
+
+Observational data is not always available, however. Instead, we must
+listen to others to learn about properties that are costly to observe
+(e.g., \emph{staring at the sun makes you go blind}), events that are
+statistically unlikely (e.g., \emph{lightning strikes tall objects}), or
+any aspect of the world that we have yet to experience. Fortunately,
+language provides simple ways of communicating generalizations.
+
+\hypertarget{communicating-generalizations}{%
+\subsection{Communicating
+generalizations}\label{communicating-generalizations}}
+
+The language of generalization is easy to spot when a property, that
+could apply to an individual, is predicated of a category (e.g.,
+\enquote{Dogs have four legs}: \emph{has four legs} could apply to an
+individual as in \enquote{This dog has four legs}). In the semantics
+literature on generics, bare plural sentences of this kind are sometimes
+described as \emph{characterizing sentences} in contrast with
+\emph{kind-denoting} sentences where the property can only meaningfully
+apply to the category as a whole (e.g., \enquote{Dinosaurs are extinct};
+\emph{extinct} cannot apply to an individual dinosaur). Generalization
+can also manifest when describing instances of an individual
+(\emph{habitual language}; e.g., ``John smokes''; Carlson, 1977, 2005);
+in this case, the particular instance being generalized is an instance
+of an individual (e.g., John at a particular moment in time), which also
+permits predication (e.g., \enquote{John smoked yesterday after
+dinner}). Verbs like \emph{causes} or \emph{makes} also seem to convey
+generalization, in this case, about an instance of an actual causal
+event (\emph{causal language}; e.g., \enquote{Fire causes smoke}).
+Psychologists, linguists, and philosophers have long studied the
+language of generalization, as it appears very simple (e.g.,
+syntactically) yet its meaning is difficult to formalize.\footnote{We
+  further distinguish the problem of formalizing a \emph{meaning} for
+  the language of generalization as opposed to the problem of
+  \emph{identifying} generalizations. Syntax alone is neither necessary
+  nor sufficient for a listener to know that the sentence conveys a
+  generalization (e.g., indefinite singulars can encode generalizations:
+  \enquote{A dog has four legs} and bare plurals may not: \enquote{Dogs
+  are on my front lawn}). Our analysis thus begins once a sentence has
+  been disambiguated as conveying a generalization. }
+
+The basic intuition behind our account is that before a listener hears a
+novel generalization such as \enquote{Alligators grow to be 10-feet
+long}, they do not know how widely distributed the property to be in the
+category, including whether or not it is present at all. The utterance
+provides a vague sense of how strongly the generalization applies (e.g.,
+how many alligators grow to be 10-feet long), which the listener derives
+from their knowledge of how the property (\emph{growing to be 10-feet
+long}) is distributed among other categories (e.g., other animals). The
+decision of whether or not to endorse the generalization is that of a
+speaker reasoning about how well the utterance would align their
+interlocutor's beliefs about the prevalence of the feature in the
+category with those of their own. We formalize this intuition in a
+truth-conditional semantics incorporated into a Bayesian model of belief
+updating.
+
+\hypertarget{interpretation-model}{%
+\subsubsection{Interpretation model}\label{interpretation-model}}
+
+If generalization from observations can be described by a probability
+\(p\), it is natural to posit that same construct will be at the heart
+of a semantic theory of the language of generalization (Ingredient 1:
+Probability). In semantics, belief updating generally passes through
+Boolean \emph{truth values} (Montague, 1973). The simplest way to derive
+a Boolean from a scalar quantity like probability is via a
+\emph{threshold semantics}: The utterance is true if the relevant scalar
+value is above a threshold. For example, the literal meaning of the
+sentence \enquote{Some dogs have four legs} is that there is a non-zero
+chance that a given dog will have four legs:
+\(\mbox{ $[\![ some ]\!]$}(p) := p > 0\). \enquote{Most dogs have four
+legs} can also be described as a threshold on prevalence (e.g., the
+chance that a dog will have four legs is greater than 50\%):
+\(\mbox{ $[\![ most ]\!]$}(p) := p > 0.5\).\footnote{These definitions
+  concern the standard semantic truth conditions of quantifiers, not
+  their pragmatic interpretations (e.g., that \enquote{some} often
+  implies \enquote{not all}).} Thus, the simplest semantics for a
+generalization would also be a threshold on the prevalence:
+\(\mbox{ $[\![ gen ]\!]$}(p, \theta) := p >\theta\).
+
+The extreme flexibility of generalizations (e.g., \enquote{Mosquitos
+carry malaria}; \enquote{Birds lay eggs} vs. \enquote{Birds are female})
+suggests that no fixed threshold would suffice. Rather than throw out
+the threshold-semantics, we posit that the threshold is
+\emph{underspecified} in the literal meaning and is
+contextually-determined in a way analogous to how gradable adjectives
+like \emph{tall} have contextually-determined thresholds (e.g., what
+counts as tall for a four-year-old is different than what counts as tall
+for an adult; Kennedy, 2007; Lassiter \& Goodman, 2013). We formalize
+this underspecification of meaning (Ingredient 2: Vagueness) by putting
+a probability distribution over \(\theta\): \(P(\theta)\) (Lassiter \&
+Goodman, 2013, 2015; cf., Qing \& Franke, 2014).
+
+Finally, the meanings of linguistic expressions manifest in their
+capacity to convey information from speaker to hearer (Clark, 1996;
+Grice, 1975; Levinson, 1995). Thus, the final ingredient to our model is
+\emph{context} (Ingredient 3), which must be minimally formalized as a
+listener's prior knowledge about the property \(P(p)\) and which we
+describe in the \emph{Worked Examples} section below.
+
+Putting these three ingredients (probability, vagueness, and context)
+together, we get the following model of interpreting generalizations in
+language:
 
 \begin{eqnarray}
-Lit(p_{fk}, \theta \mid u) &\propto& {\delta_{\denote{u}(p_{f}, \theta)} \cdot P(p_{f}) \cdot P(\theta)} \label{eq:L0}
+L(p, \theta \mid u) &\propto& {\delta_{\mbox{ $[\![ u ]\!]$}(p, \theta)}  \cdot P(\theta) \cdot P(p)} \label{eq:L0}
 \end{eqnarray}
 
-Equation \ref{eq:L0} (\(Lit\)) is a literal interpretation model, that
-updates its beliefs about the prevalence of a feature in the category
-described \(p_{fk}\) according to the truth-functional meaning of the
-utterance \(u_{KF}\). Formally, the truth-functional meaning is
-represented by the Kronecker delta function
-\(\delta_{\denote{u}(p_{fk}, \theta)}\) that returns probabilities
-proportional to \(1\) when the utterance is true (i.e., when
-\(p_{fk} > \theta\)) and \(0\) otherwise.
+We denote this probabilistic interpretation model by \(L\) to indicate
+that it is modeling a listener updating their beliefs according to the
+truth-functional meaning of an utterance \(u\). Formally, the
+truth-functional meaning is represented by the Kronecker delta function
+\(\delta_{\mbox{ $[\![ u ]\!]$}(p, \theta)}\) that returns \(1\) when
+the utterance is true (i.e., when \(p > \theta\)) and \(0\) otherwise.
 
 \begin{eqnarray}
-\delta_{\denote{u_{KF}}(p_{fk}, \theta)} &\propto  & \begin{cases}
-1 & \text{if } p_{fk} > \theta \\
+\delta_{\mbox{ $[\![ u_{gen} ]\!]$}(p, \theta)} &\propto  & \begin{cases}
+1 & \text{if } p > \theta \\
 0 & \text{otherwise}
@@
 
-\subsubsection{Endorsement model}\label{endorsement-model}
-
-Given the minimal model of literal interpretation described above, how
-do we decide when a statement conveying a generalization is true or not?
-We consider the notion of felicity or endorsement from the
-information-theoretic perspective: Would a generalization convey
-sufficient information to warrant the cost of production? We formalize
-this by considering how well the generalization would convey the
-prevalence \(p_{fk}\) to the \(Lit\) model (Eq. \ref{eq:L0})\footnote{A
-  more general version of this model can relax the assumption that the
-  endorsement model has access to a specific prevalence \(p_{fk}\) that
-  it wants to communicate. Rather, the endorser may have a distribution
-  over \(p_{f}\) for the category \(k\), corresponding to the endorser's
-  uncertain beliefs about the prevalence. In this situation, we would
-  define the endorsement model decision to be with respect to the
+Following Lassiter and Goodman (2015), we formalize the vagueness in the
+meaning of generics \(P(\theta)\) as a uniform distribution over the
+support of \(P(p)\).
+
+With these ingredients, the literal interpretation model (Eq.
+\ref{eq:L0}) computes a posterior interpretation distribution on
+prevalence by considering different possible thresholds \(\theta\).
+Figure~\ref{fig:uniformPriorSimulation} shows the model behavior
+assuming a uniform prevalence prior \(P(p)\), perhaps representing a
+purely abstract property for which an interpreter has no substantive
+prior knowledge. If the threshold were to be very high (e.g.,
+\(\theta = 0.75\)), only the highest prevalence levels would be
+consistent with the utterance. As the threshold decreases, more and more
+prevalence levels become compatible with the threshold
+(Figure~\ref{fig:uniformPriorSimulation}A). The interpretation model
+weights the different thresholds by the probability that each is true,
+resulting in a posterior interpretation distribution on prevalence that
+favors higher prevalence levels
+(Figure~\ref{fig:uniformPriorSimulation}B). This interpretation
+distribution captures the intuition that generalizations imply high
+prevalence, though with substantial uncertainty about the precise
+prevalence.
+
+The model in Eq \ref{eq:L0} describes a general mechanism of
+belief-updating via an uncertain threshold semantics. The semantic scale
+is determined by the prevalence prior \(P(p)\). For generalizations
+about categories (i.e., generic statements), \(P(p)\) ranges over
+\([0, 1]\); \(p\) denotes the chance that an instance of a category has
+a Boolean property. To apply this same model to generalizations about
+events (i.e., habituals like \enquote{John runs}), we use a different,
+but related, scale: the frequency within a given time window (e.g.,
+number of times John went for a run in the past week).\footnote{This
+  measure is closely related to the instantaneous probability density of
+  the event, as the time window gets infinitesimally small.} For events
+then, \(p\) is a rate and \(P(p)\) ranges over \([0, \infty)\).
+
+\hypertarget{endorsement-model}{%
+\subsubsection{Endorsement model}\label{endorsement-model}}
+
+In this paper, we are interested in explaining truth judgments (e.g.,
+\enquote{Robins lay eggs} is intuitively true; \enquote{Robins are
+female} is not). We model the endorsement task (e.g., \emph{true} vs.
+\emph{false}; \emph{agree} vs. \emph{disagree}) as a \emph{speaker
+decision} about whether or not to produce the generalization to a naive
+listener; thus, the endorsement model has two alternative utterances:
+produce the generalization vs.~a null alternative (Degen \& Goodman,
+2014; Franke, 2014). For simplicity, we take the null alternative to be
+an informationless \enquote{silent} utterance which is always true:
+\(\mbox{ $[\![ null ]\!]$}(p, \theta) = \text{True}\).\footnote{The null
+  alternative can be realized in at least two other ways: the negation
+  of the generalization (e.g., \enquote{It is not the case that Robins
+  lay eggs}) or the negative generalization (i.e., \enquote{Robins do
+  not lay eggs}). All results reported are similar for these two
+  alternatives, and we use the alternative of the \enquote{silent}
+  utterance for simplicity.} This kind of speaker model defined in terms
+of a listener model formalizes the basic aspects of communicative
+reasoning and is the simplest instantiation of a Rational Speech Act
+model (Frank \& Goodman, 2012; Goodman \& Frank, 2016).
+
+The endorsement model (called \(S\) for speaker) decides whether or not
+to produce the generalization by reasoning about how the listener model
+(\(L\); Eq. \ref{eq:L0}) would interpret it: \begin{equation}
+S(u \mid p) \propto (\int_{\theta} L(p, \theta \mid u)  \mathop{}\!\mathrm{d}\theta)^\lambda
+\label{eq:S1}
+\end{equation}
+
+The goal of the endorsement model is to align the listener's \emph{a
+priori} beliefs about prevalence (given by the prevalence prior) with
+the speaker's beliefs about the prevalence of the feature in the
+referent category \(p\), the \emph{referent prevalence} (e.g., that 50\%
+of robins lay eggs).\footnote{A more general version of this model can
+  relax the assumption that the endorser / speaker has access to a
+  specific prevalence \(p\) that it wants to communicate. Rather, the
+  endorser may have probabilistic beliefs about the prevalence of the
+  property for the referent category \(k\), which would be represented
+  by a distribution over \(p\): \(P(p \mid k)\). In this situation, we
+  would define the endorsement model decision to be with respect to the
   expected value of the informativity, which integrates over the
   endorsement model's belief distribution:
-  \(S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p_{fk}\sim P_{k}} \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)} \diff \theta )}\)
+  \(S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{p\sim P_{k}} \ln{ \int_{\theta} L(p, \theta \mid u)} \mathop{}\!\mathrm{d}\theta )}\).
   For the empirical case studies described below, these two versions of
-  the model make almost identical predictions.}.
-
-\begin{equation} 
-S(u \mid p_{fk}) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} Lit(p_{fk}, \theta \mid u)  \diff \theta } )}
-\label{eq:S1}
-\end{equation}
-
-The endorsement model simulates what the interpretation model would
-believe upon hearing an utterance \(u\)):
-\(Lit(p_{fk}, \theta \mid u)\). \(S\) is not interested in communicating
-\(\theta\) (in fact, it does not know \(\theta\)), and so integrates
-over the values of \(\theta\). We assume the decision to endorse is an
-approximately rational one, with degree of rationality given by
-\(\lambda\). The proportionality in Eq. \ref{eq:S1} implies
-normalization over a set of alternative utterances. We interpret the
-endorsement task (e.g., \enquote{true} vs \enquote{false};
-\enquote{agree} vs. \enquote{disagree}) as supplying two alternatives:
-\emph{endorse} or \emph{not}, where \emph{not} we take to be a silent
-utterance that conveys no information content (Degen \& Goodman, 2014;
-cf., Franke, 2014): \(\denote{null}(x, \theta) = \text{True}\)\footnote{This
-  \enquote{null} alternative to the generalization (\enquote{Ks F}) can
-  be realized in at least two other ways: the negation of the
-  generalization (i.e., \enquote{It is not the case that Ks F}) or the
-  negative generalization (i.e., \enquote{Ks do not F}). All results
-  reported are similar for these two alternatives, and we use the
-  alternative of the \enquote{silent} utterance for simplicity.}
-
-Our endorsement model (Eq. \ref{eq:S1}) provides a straight-forward
-mapping from a \emph{referent-category prevalence} \(p_{fk}\) (e.g.,
-\(P(x \text{ lays eggs} \mid x \text{ is a robin})\)) to an endorsement
-probability for the corresponding generalization (e.g., \enquote{Robins
-lay eggs}): \(S(u = u_{KF} \mid p_{fk})\). The model assumes a threshold
-semantics based on probability (prevalence) but does not require
-specifying the threshold \emph{a priori} (note that there is no
-\(\theta\) in the left-hand side of Eq. \ref{eq:S1}). This model can be
-seen as a special case of a Rational Speech Act model (Frank \& Goodman,
-2012; Goodman \& Frank, 2016), where there is only a single level of
-recursion and the space of possible utterances is maximally constrained.
-
-\subsubsection{Prevalence priors and
-referent-prevalence}\label{prevalence-priors-and-referent-prevalence}
-
-Our model makes context-sensitive predictions about endorsing
-generalizations based on two model components: The prevalence priors
-\(P(p_f)\) in Eq. \ref{eq:L0} and the referent-prevalence \(p_{fk}\) in
-Eqs. \ref{eq:S1} and \ref{eq:delta}. Referent-prevalence is the
-probability that an individual \(x\) of the referent-category (e.g.,
-\enquote{Dogs}) will have the feature being predicated of the category
-(e.g., \enquote{\ldots{}barks}). We will return and refine this
-definition in Case Study 2, when considering generalizations about
-events. For now, the referent-prevalence is simply a probability that
-determines the truth-conditional semantics. Our hypothesis does not
-provide a mapping from the referent-prevalence directly to endorsement
-judgments, however, because \(\theta\) is underspecified.
-
-The uncertain, truth-conditional threshold \(\theta\) is resolved by the
-literal interpretation model \(Lit\) (Eq. \ref{eq:L0}) by integrating
-prior beliefs about the feature in question---the \emph{prevalence
-prior} \(P(p_f)\)---with the truth-functional semantics. Again,
-\(P(\theta)\) is set to be a uniform distribution across all contexts,
-and thus, the generalization could in principle be felicitious with
-potentially any referent-prevalence. However, interpretation model's
-\emph{a priori} beliefs \(P(p_f)\) must be considered before the
-endorsement model can say whether or not it would endorse the
-generalization.
-
-Beliefs about properties result from internal conceptual models of the
-world. These internal models have domain-specific features but should
-all give to the domain-general currency of inductive reasoning:
-probability. One way of constructing prior distributions over
-prevalence, without appealing directly to domain-specific conceptual
-knowledge, is by considering the prevalence of the feature among
-different categories. For example, many different kinds of animals
-\emph{do not bark} (more precisely: have close to 0 exemplars who bark);
-thus, the prevalence prior for the feature \emph{barks} \(P(p_{barks})\)
-should have substantial probability mass near 0, because what one would
-expect for a randomly-sampled category is that it has 0 or close to 0
-exemplars that bark. Furthermore, among the categories that do have
-exemplars which bark (e.g., \emph{dogs}, \emph{seals}, \ldots{}), the
-probability is quite high that an exemplar will bark; thus, the
-prevalence prior should have substantial mass at relatively high values,
-potentially with quite a bit of uncertainty;
-Figure~\ref{fig:simulations}A; first row). Conceptual differences can
-manifest in these prevalence priors in the form of multi-modal
-distributions; for example, the prevalence prior for \emph{lays eggs}
-should similiarly have substantial probability mass near 0 (since most
-animal categories do not have egg-layers) but should have a secondary
-component peaked around 0.5, because among the animals with egg-layers,
-only the female members of the category have the property
-(Figure~\ref{fig:simulations}A; bottom row).
+  the model make almost identical predictions.} The endorsement model
+makes an approximately rational (with degree of rationality
+\(\lambda\)), information-theoretic decision based on its beliefs about
+which utterance would best achieve the goal of conveying the referent
+prevalence \(p\). The semantic threshold \(\theta\) is necessary for
+establishing the truth conditions and deriving an interpretation (used
+in Eq. \ref{eq:L0}) but is otherwise a nuisance parameter, which the
+endorsement model integrates out (note that there is no \(\theta\) in
+the left-hand side of Eq. \ref{eq:S1}). Given that the speaker only has
+two options (i.e., produce the generalization utterance or stay silent),
+the endorsement decision comes down to whether or not the referent
+prevalence is more likely under the prevalence prior distribution
+\(P(p)\) (i.e., the listener's posterior upon hearing silence) or the
+listener generic interpretation distribution \(L(p \mid u)\) given by
+Eq. \ref{eq:L0} (Figure~\ref{fig:uniformPriorSimulation}C). In the next
+section, we work through different examples from the linguistics
+literature, describing the prevalence prior and other relevant model
+components for each.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figs/uniformPriorSimulation-1}
+
+}
+
+\caption{Computational model behavior assuming a uniform prior over prevalence.
+A: Interpretation model posteriors assuming different fixed thresholds (facets).
+High thresholds rule out more world-states (prevalence levels), leaving fewer world-states among which to distribute the full probability mass.
+B: Generic interpretation model averages over all thresholds to return a posterior distribution that favors higher prevalence levels in a graded manner.
+C: Endorsement model predicts higher rates of endorsemens as prevalence levels increase.}\label{fig:uniformPriorSimulation}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figs/simulations-1}
+
+}
+
+\caption{Model simulations assuming different prevalence priors.
+Top: Prevalence priors for six example features.
+Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions.
+Arrows show referent-prevalence for a target category.
+Bottom: Interpretation model posterior distributions over prevalence upon hearing a generalization about a novel category.
+Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for the referent-category whose prevalence is shown in the top facets (e.g., "Mosquitos carry malaria").}\label{fig:simulations}
+\end{figure}
+
+\hypertarget{worked-examples}{%
+\section{Worked examples}\label{worked-examples}}
+
+We explore the predictions of the endorsement model in the context of a
+few worked examples. These examples are taken from the linguistics
+literature on generics and are statements that have been historically
+challenging for prevalence-based approaches (see Table 1). We
+implemented these and all subsequent Bayesian models in the
+probabilistic programming language WebPPL (Goodman \& Stuhlmüller,
+2014). All models, analyses, data and links to experiments used in this
+paper can be found at \url{https://github.com/mhtess/genlang-paper}.
+
+Endorsement predictions depend upon the uncertain threshold model's
+interpretations, which are highly sensitive to background knowledge.
+Background knowledge may be richly structured, reflecting intuitive
+theories about the underlying causes of different kinds of properties
+(cf., Leslie, 2007). This model posits, however, that the only impact of
+structured knowledge on truth judgments is in their implications for
+beliefs about prevalence, formalized in terms of a prevalence prior
+\(P(p)\). The prevalence prior reflects a listener's beliefs about the
+prevalence of the feature in an unknown or unfamiliar category and be
+conceptualized in a theory-neutral way as a distribution over the
+prevalence among alternative categories
+(Figure~\ref{fig:simulations}).\footnote{Alternatively, the prevalence
+  prior can be conceptualized as a marginal distribution on prevalence
+  derived from an intuitive theory formalized in a probabilistic
+  language of thought (e.g., Goodman et al., 2015). } For example, the
+\emph{lay eggs} prevalence prior should be bimodal, with substantial
+probability mass near 0-prevalence (since many animal categories do not
+have egg-layers) and a secondary component peaked around 0.5 (because
+among the animals with egg-layers, only the female members of the
+category have the property). Conversely, the distribution over the
+prevalence of \emph{being female} is unimodal and centered at
+50\%-prevalence, because almost all animals have female members in that
+proportion. Figure~\ref{fig:simulations} (row 1) shows these and other
+intuitive prevalence priors for different properties (we introduce
+methods for empirically eliciting these priors in the experimental
+section). We now turn our attention to the endorsement model's
+predictions.
+
+\begin{table}[ht]
+\centering
+\begingroup\fontsize{9pt}{10pt}\selectfont
+\begin{tabular}{p{2in}|  |p{1.25in}|p{0.75in}|p{2in} |}
+  \hline
+{\bfseries Example} & {\bfseries Intuitive referent prevalence} & {\bfseries Intuitive truth value} & {\bfseries Issue} \\ 
+  \hline
+1. Dogs bark & 95\% & True & Not all dogs bark \\ 
+   \hline
+2. Kangaroos have spots & 5\% & False & Some kangaroos could have spots \\ 
+   \hline
+3. Robins lay eggs & 50\% & True & Only female robins (50\%) lay eggs \\ 
+   \hline
+4. Robins are female & 50\% & False & Same number that lay eggs (50\%) \\ 
+   \hline
+5. Mosquitos carry malaria & 5\% & True & Very few mosquitos actually carry malaria \\ 
+   \hline
+6. Sharks don't eat people & 85\% & False & Most sharks don't eat people \\ 
+   \hline
+7. Mary handles the mail from Antarcita & 0 times & True & Consider there has never been any mail from Antarcita \\ 
+   \hline
+8. Supreme Court Justices have even social security numbers & 100\% & False & Consider 100\% have even social security numbers \\ 
+   \hline
+9. Elephants live in Africa and Asia & 50\%/50\% & True & Impossible for most to live in Africa and most to live in Asia, and no individual elephant lives in both Africa and Asia \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Example sentences that a theory of the language of generalizations should correctly predict. See details of each example in corresponding section.} 
+\end{table}
+
+\textbf{1. Dogs bark.}
+
+Often the first observation with generics is that they appear to behave
+like universal quantifiers (e.g., \enquote{All}) that permit exceptions:
+Not all dogs bark, but still \enquote{Dogs bark} is true. The uncertain
+threshold account immediately accomodates this example because there is
+no single, fixed threshold beyond which a generic statement becomes
+true. Rather, listeners have uncertainty about the threshold which leads
+to graded interpretations (e.g., \enquote{Dogs bark} probably means
+\emph{almost all} dogs bark; Figure~\ref{fig:simulations}; column 1, row
+2). The endorsement model predicts \enquote{Dogs bark} is a rather good
+generic sentence (Figure~\ref{fig:simulations}, bottom row) even though
+there are exceptions to the universal generalization (referent
+prevalence of barking among dogs shown with arrow in
+Figure~\ref{fig:simulations} row 2).
+
+\textbf{2. Kangaroos have spots.}
+
+A second observation regarding generics is that their truth conditions
+cannot be so lenient so as to always convey \emph{existential}
+quantification (e.g., \enquote{Some}). Indeed, it's intuitively
+plausible that some kangaroos do have spots but a rational language user
+might feel awkward to assert the generic \enquote{Kangaroos have spots}.
+The model exhibits this same restraint, predicting a very low
+endorsement probability for this generic sentence
+(Figure~\ref{fig:simulations}; column 2). The reason is that, given the
+interpretation model's background knowledge about the property, the
+statement \enquote{Kangaroos have spots} will be interpreted like
+\enquote{Dogs bark}: it would mean \emph{almost all} kangaroos have
+spots. The endorsement model, which believes that very few kangaroos
+have spots, then would rather not endorse the statement because it would
+lead to a too-strong interpretation and mislead the listener.
+
+\textbf{3. and 4. Robins lay eggs vs.~Robins are female}
+
+One of the most difficult examples for a theory of generics based on
+prevalence to handle is the intuitive difference in truth value between
+the statements \enquote{Robins lay eggs} and \enquote{Robins are
+female}. The former is intuitively true, even though only female robins
+could lay eggs (and hence, the prevalence is roughly 50\%). However, the
+same implicit restriction to only females does not seem occur for the
+latter statement, as \enquote{Robins are female} strikes most as strange
+or false. Why is \enquote{Robins lay eggs} a reasonable utterance while
+\enquote{Robins are female} is not?
+
+The prior distributions over the prevalence of both features are shown
+in Figure~\ref{fig:simulations} (columns 5 and 6). As described above,
+the priors are different: Many animals have zero egg-layers (0\%
+prevalence), while the vast majority of animal categories have female
+members in exactly the same proportion (50\%). Given this background
+knowledge, the generic interpretation model returns roughly the same
+interpretation distribution for each hypothetical utterance: In each
+case, the model believes roughly 50\% have the property. However, only
+in the case of \enquote{Robins lay eggs} does the endorsement model
+actually assert the generic; it does so because the listener
+interpretation would be more aligned with the referent prevalence in
+comparison to the interpretation of the null utterance, which is the
+prevalence prior. In contrast, the hypothetical generic interpretation
+of \enquote{Robins are female} is not different from the prevalence
+prior and hence the generic conveys no new information; here, the
+generic would not be misleading but uninformative, and hence the model
+predicts an endorsement probability of 0.5. Indeed, previous studies on
+generic endorsements have found \enquote{Robins are female} to not be
+rated as completely false but rather receive an intermediate endorsement
+level (i.e., \emph{neither true nor false}; Prasada et al., 2013).
+
+\textbf{5. Mosquitos carry malaria.}
+
+The statement \enquote{Mosquitos carry malaria} is intuitively true in
+spite of the fact that the vast majority of mosquitos are actually
+malaria-free. The prevalence prior for \emph{carries malaria} is highly
+skewed towards low prevalence levels: many animals do not have
+malaria-carriers among them and even for those that do, the prevalence
+is expected to be quite low. Then, carrying malaria is significantly
+more true of mosquitos than other animals, an intuition that is often
+arrived at with this example. This kind of behavior is related to the
+construct of \emph{cue validity}---the probability of the feature given
+the category e.g.,
+\(P({is a mosquito} \mid \text{carries malaria})\)---which we return to
+in the next section. The uncertain-threshold model displays a critical
+behavior: It can endorse generics when the referent prevalence is very
+low.
+
+\textbf{6. Sharks don't eat people.}
+
+When the prevalence of the feature is very high, it is not necessary for
+the model to endorse the generic. \enquote{Sharks don't eat people} is
+predicted to be a somewhat strange utterance, despite the fact that the
+vast majority of sharks do not eat people.\footnote{We create this
+  example as the converse of the classic example \enquote{Sharks eat
+  people}, predicted to be \emph{true} despite low prevalence (Leslie,
+  2007). We reverse this example to show how the model deals with a
+  high-prevalence feature for which the generic is predicted to be false
+  or infelicitous.\\} Because for almost all animal categories, the
+prevalence of \emph{not eating people} is almost 100\% (very few things
+eat people), interpreting the statement \enquote{Sharks don't eat
+people} would lead one to believe that \emph{no} sharks eat people
+(i.e., 100\% don't eat people), which is too strong. It is interesting
+to note that because of the high referent prevalence, the model is less
+certain of its decision, predicting an endorsement probability around
+40\% (i.e., somewhat false). We will test this quantitative prediction
+in Experiment 1 on generic language.
+
+\textbf{7. Mary handles the mail from Antarctica (\emph{yet has never
+had the opportunity}).}
+
+Imagine there is a job in the local bureaucrat's office to handle the
+mail from Antarctica and this job is assigned to Mary; to date, however,
+nobody has ever sent mail to the office from Antarctica (Cohen, 1999).
+In other words, the statement \enquote{Mary has handled mail from
+Antarctica} is false. \enquote{Mary handles the mail from Antarctica},
+however, is still thought to be intuitively true despite zero actual
+instances of the event. This highlights an important ambiguity in the
+theoretical commitments of the uncertain threshold model: The
+endorsement model aims to communicate some referent prevalence \(p\),
+but does the prevalence represent the actual, objective frequency in the
+world (e.g., the number of times in the past that Mary has handled mail
+from Antarctica) or a subjective, predictive degree of belief in the
+head (e.g., our prediction that were the appropriate situation to arise,
+Mary would be handling the mail from Antarctica)?
+
+We posit that Mary the Antarctic mail handler is an extreme case of
+generalizations expressing \emph{predictive} degrees of belief. We
+expect this context sets up the expectation that any future mail coming
+from Antarctica will be handled by Mary. Thus the predictive probability
+that Mary will handle Antarctican mail, should there be some, is high.
+Predictive probabilities often track past frequency or actual prevalence
+in the world, but people's internal models of how the world works can
+lead them to diverge. In this case our understanding of Mary's job leads
+to a strong predictive probability in the absence of past frequency
+evidence. We explore this question experimentally in Exerpiment 2 on
+habituals.
+
+\textbf{8. Supreme Court Justices have even social security numbers.}
+
+Imagine that all current Supreme Court Justice has a social security
+number which was an \emph{even number}. \enquote{Supreme Court Justices
+have even social security numbers} is still considered false, even
+though the property holds for exactly 100\% of the category (Cohen,
+1999). We predict the rejection of even social security numbered
+Justices is the result of our intuitive theories guiding our subjective
+predictive probabilities, which feed into the endorsement model. That
+is, we predict observers strongly believe there is no causal relation
+between the evenness of one's social security number and selection for
+the Supreme Court, and thus would assign a roughly 50\% subjective
+probability to the \emph{next} justice having an even social security
+number. Then, \enquote{Supreme Court Justices have even social security
+numbers} would be rated by our model as similar to \enquote{Birds are
+female}, because all professions have roughly the same probability of
+having employees with even social security numbers. This example is thus
+the conceptual opposite of Mary the Antarctic mail handler, where our
+internal model of the world led us to a strong degree of belief in the
+property holding in the future; with the Supreme Court Justices, our
+internal models lead to a relatively weak degree of belief in the
+property holding in the future.
+
+\textbf{9. Elephants live in Africa and Asia.}
+
+Understanding how a semantic representation \emph{composes} is another
+important test for a theory of generalizations in language. Nickel
+(2008) suggests that \enquote{Elephants live in Africa and Asia} is
+troubling for prevalence-based accounts (in particular,
+majority-quantificational accouts where the generic means \emph{more
+than half}; Cohen, 1999) because the statement should be semantically
+equivalent to \enquote{Elephants live in Africa and elephants live in
+Asia}. It cannot be the case that most (more than half of) elephants
+live in Africa and \emph{most} (more than half of) elephants live in
+Asia, unless we are to posit \emph{international elephants} (i.e.,
+individual elephants who live part-time in Africa and part-time in
+Asia), which are intuitively implausible.
+
+Our theory does not provide a fixed semantics for generics, but an
+uncertain one which can be updated as more information comes in. In
+fact, with prior knowledge suggesting against the existence of
+international elephants (Figure~\ref{fig:elephants}A), our model
+interprets \enquote{Elephants live in Africa and Asia} as meaning that
+some elephants live in Africa and that different ones live in Asia
+(Figure~\ref{fig:elephants}C). Interestingly, an incremental parsing of
+the sentence (i.e., upon hearing only that \enquote{Elephants live in
+Africa}) leads our model to believe that \emph{most}, possibly all,
+elephants live in Africa (Figure~\ref{fig:elephants}B). When the
+sentence is completed (\enquote{\ldots{}and Asia}), the model
+non-monotonically updates its beliefs to something weaker: \emph{some}
+elephants live in Africa and others in Asia
+(Figure~\ref{fig:elephants}C). The flexibility of our model accommodates
+new evidence that might otherwise contradict previous utterances because
+it maintains uncertainty about the precise meaning of the utterance.
+From a compositional perspective, this is highly desirable behavior but
+we leave the testing of quantitative predictions of this kind for future
+work.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{figs/elephants-1}
+
+}
+
+\caption{Model interpretation of a conjunctive generic ("Elephants live in Africa and Asia").
+A: Intuitive priors for marginal distributions of prevalence for living in Africa and living in Africa.
+B: Partial interpretation upon hearing utternace ("Elephants live in Africa...").
+C: Full interpretation upon hearing the end of the sentence ("Elephants live in Africa and Asia").
+Uncertainty about the threshold for generic sentences allows the listener to non-monotonoically update its beliefs about the prevalence of the feature in categories.}\label{fig:elephants}
+\end{figure}
+
+\hypertarget{relationship-to-other-semantic-theories}{%
+\section{Relationship to other semantic
+theories}\label{relationship-to-other-semantic-theories}}
+
+Our formal theory builds on and relates to a number of extant theories
+of generics in both the formal semantics and psychological literatures.
+The dominant approaches from formal semantics try to describe unified,
+objective criteria by which to establish if a generic and other
+generalizations are true or false (i.e., generic \emph{truth
+conditions}). These views are typically \emph{statistical} in nature in
+that they appeal to quantification or the statistics of the world (e.g.,
+how many of the kind have the property) to define those unified,
+objective criteria. Many of these theories rely upon mechanisms outside
+of the truth conditions to make sense of the extreme flexibility
+exhibited by generics; unfortunately, these extra-semantic mechanisms
+are not described in sufficient detail to generate precise, quantitative
+predictions. Other theorists, primarily in philosophy and psychology,
+have taken the extreme flexibility of generics to argue against a
+quantitative theory based on statistics, instead suggesting that
+abstract, mental representations are directly tied to semantics of
+generics (e.g., \emph{there is something about being a K which causes it
+to F}). Statistical and conceptual theories express the major
+contrasting views of generic language (Carlson, 1995).\footnote{We use
+  the terms statistical and conceptual to refer to what Carlson (1995)
+  referred to as \enquote{inductive} and \enquote{rules and regulations}
+  views, respectively.}
+
+\hypertarget{conceptual-accounts}{%
+\subsection{Conceptual accounts}\label{conceptual-accounts}}
+
+Conceptual accounts try to identify the core meaning of a generalization
+directly with aspects of conceptual structure. The most influential
+account in psychology comes from Leslie (2008), which uses the same
+starting point as our analysis: Generics express generalization. Leslie
+(2008)'s analysis draws upon insights from the psychological literature
+on infant generalization to argue that generics tap into an innate,
+default mechanism that signals the child (or adult) to generalize the
+property to the kind.
+
+The \emph{default generalization} mechanism has three components: the
+ability to (i) identify whether or not a feature is a
+\emph{characteristic} property of a kind (e.g., one characteristic
+property for an animal would pertain to the mode of locomotion for the
+animal), (ii) identify whether or not a feature is \emph{striking}
+(e.g., can kill you; \enquote{Mosquitos carry the West Nile Virus}), and
+(iii) segment \emph{counterinstances} (instances of the kind which do
+not have the feature) into positive and negative counterinstances (i.e.,
+instances of the kind which have some relevant alternative feature and
+instances of the kind which simply lack the feature,
+respectively).\footnote{This positive vs.~negative counterinstance
+  distinction is a rather technical consideration (though not without
+  psychological foundation, see Leslie, 2008, p. 36) used to account for
+  the difference between examples like \enquote{Robins lay eggs} vs.
+  \enquote{Robins are female}. For \enquote{Robins are female}, male
+  robins are positive counterinstances because they have an alternative
+  property (being male). For \enquote{Robins lay eggs}, male robins are
+  negative counterinstances because they simply lack the property (i.e.,
+  male robins do not reproduce by some other method). We will not
+  discuss this consideration any further other than to note that that
+  the difference between \enquote{Robins lay eggs} and \enquote{Robins
+  are female} can be explained by a different mechanism (e.g.,
+  informativity with respect to a prevalence prior). The notion that
+  alternative features may come into play in generic interpretation may
+  also be addressed with prevalence priors constructed with respect to
+  the feature (described in the General Discussion).} On this account,
+generics are true if \emph{some} instances of the kind have the feature
+when all counterinstances are negative counterinstances and the property
+is either characteristic or striking. If the property is neither
+characteristic nor striking, then \emph{almost all} instances of the
+kind must have the feature for the generic to be true (e.g.,
+\enquote{Barns are red}). Many of the key factors in this conceptual
+approach are compatible with our view of prevalence as a predictive
+probability: What is required is that the distinctions made by
+conceptual accounts influence predictive probability, which mediates
+linguistic effects. Indeed, one version of this mechanism is already
+suggested by Leslie (2008), citing findings by Rothbart, Fulero, Jensen,
+Howard, and Birrell (1978), that a speaker's perception of the
+prevalence of the feature can be altered by virtue of its dangerousness
+or distinctiveness.
+
+\hypertarget{default-generalizations}{%
+\subsubsection{Default generalizations}\label{default-generalizations}}
+
+The conceptual view of generics argues that it is not desirable to
+define generics in the same terms as quantifiers (e.g., a
+truth-functional threshold on prevalence), because generics are more
+basic or more fundamental than quantifiers (Gelman, 2009; Leslie, 2008).
+For example, according to certain measurements, young children have a
+nearly adult-like understanding of generics far earlier than they do
+with quantified language (Gelman, Leslie, Was, \& Koch, 2015).
+Similarly, adults who are told novel information about categories using
+quantified language (e.g., \enquote{Most spiders shed their skin}) and
+later asked to recall that same information will tend to recall
+quantified information as generics (e.g., ``Spiders shed their skin'';
+Leslie \& Gelman, 2012), but not visa versa. As a result, generics are
+thought of as conveying default generalizations, whereas quantified
+language expresses more sophisticated and specific generalizations.
+Rather than be contradictory, our model can be seen as formalizing a
+default generalization as Bayesian belief updating via a threshold
+function whose threshold value is contextually-informed via knowledge
+about properties. Alternative formulations of such a default
+generalization mechanism could be proposed and quantitatively tested
+against our account.
+
+\hypertarget{striking-generics}{%
+\subsubsection{Striking generics}\label{striking-generics}}
+
+Leslie (2008) posits a special mechanism to treat generics about
+striking properties (e.g., \enquote{Rottweilers maul children}), which
+seem to be acceptable even when the prevalence of the property is quite
+low (e.g., very few rottweilers maul children). Indeed, Cimpian,
+Brandone, and Gelman (2010) found participants willing to endorse
+generics about striking properties (e.g., \enquote{Lorches have
+dangerous feathers}) more so than that of neutral properties (e.g.,
+\enquote{Lorches have purple feathers}) at low levels of prevalence
+(e.g., when only 30\% of the category had the property). Leslie (2008)'s
+argument for accepting striking generics is straightforward: These are
+relevant properties to know about if you want to survive. Our theory
+posits two mechanisms by which striking properties could influence
+generic endorsement: the prevalence prior and the referent prevalence.
+
+The first observation is that striking properties are relatively rare in
+the environment: Most animals do not maul children, eat swimmers, or
+carry malaria. Thus, the prevalence prior distributions of these
+features may be hard to distinguish from properties that are just
+generally rare and distinctive, as we have assumed in our worked example
+of \enquote{Mosquitos carry malaria}. Cimpian et al. (2010)'s
+experiments did not measure the prevalence prior distribution, but we
+have found in pilot work that the prevalence prior distribution changes
+to resemble that of a distinctive property when participants are
+supplied information about the dangerousness of a property.
+
+The second mechanism by which strikingness could influence generic
+endorsement in our model is by speakers having a distorted perspective
+of how prevalent these features are within the referent category. That
+is, striking properties may be projected more strongly (i.e., higher
+predictive probability that future instances will have the property)
+than neutral properties.\footnote{This observation is also made by
+  Leslie (2008) (p.42), who uses it as motivation for elevating striking
+  properties to their special status in her theory.} Interestingly,
+evidence suggests this enhanced projectibility holds for both dangerous
+properties (e.g., people doing criminal actions) as well as neutral,
+distinctive properties (e.g., people taller than 6'5", Rothbart et al.,
+1978 Expts. 2 \& 3). Thus, there is evidence for the influence of
+strikingness on predictive probability, which we posit is an
+intermediate representation between conceptual knowledge and generic
+endorsements. It is beyond the scope of this paper to directly attempt
+to empirically distinguish these two potential mechanisms, though our
+experiments use a number of striking properties for which we measure the
+prevalence prior and referent prevalence.
+
+\hypertarget{principled-and-statistical-connections}{%
+\subsubsection{Principled and statistical
+connections}\label{principled-and-statistical-connections}}
+
+Leslie (2008)'s construct of characteristic properties is similar to
+Prasada and Dillingham (2006)'s notion of a \emph{k-property} (\emph{k}
+for kind), a property that bears a \emph{principled connection} to the
+kind. A property bears a principled connection to the kind if a
+(generic) sentence that appeals to the kind to explain the existence of
+the property makes sense (e.g., \enquote{Dogs, by virtue of being the
+kind of things that they are, are four-legged}). When such sentences are
+not endorsed (e.g., \enquote{Barns, by virtue of being the kind of
+things that they are, are red}) while the simple generic (e.g.,
+\enquote{Barns are red}) is endorsed, then the property is thought to
+bear a \emph{statistical connection} to the kind (a so-called
+\emph{t-property}, for emphasizing that it is the \emph{tokens} having
+the property which matters for generic endorsement). Prasada et al.
+(2013) showed that different kinds of generic statements (e.g., striking
+properties, characteristic properties with low prevalence) support
+different kinds of inferences in addition to the difference in
+endorsements for \emph{by virtue of} statements (e.g., \emph{normative}:
+\enquote{Dogs are supposed to have four legs}, \emph{aspect}:
+\enquote{Having four legs is one aspect of being a dog}). Additionally,
+there is some evidence that the impact of principled connections on
+interpretations is separate from their influence on beliefs about
+prevalence (Prasada \& Dillingham, 2006).
+
+Both Prasada and Dillingham (2006) and Leslie (2008) surmise that a
+property may qualify as characteristic (or having a principled
+connection) if there exists an overhypothesis about that property for a
+relavant superordinate category (e.g., each kind of animal has a means
+for self-locomotion; Goodman, 1955; Shipley, 1993). Overhypotheses are
+naturally formalized as hierarchical Bayesian models, wherein a learner
+acquires knowledge at multiple levels of abstraction (e.g., learning
+from the same event about a particular dog, dogs in general, and animals
+in general; Kemp et al., 2007). These Bayesian heirarchical models yield
+differences in predictive probability that are particularly robust.
+Integrating a hierarchical model of kinds and properties with our model
+of generic language is a natural direction to understanding the
+computational underpinnings of conceptual relations and generics.
+Different conceptual structures may give rise to roughly the same
+distributions on prevalence and thus have similar generic endorsement
+profiles according to our model. Yet the inferences that can be drawn
+from hearing these generics may differ, depending on their interactions
+with the putative hierarchical knowledge people bring to bear (a la the
+differences observed for ``prevalence-matched items'' in Prasada \&
+Dillingham, 2006). Building hierarchical models of kinds and properties
+is a major undertaking in its own regard, but our formalism provides a
+way of connecting such a model with generic language.
+
+\hypertarget{statistical-accounts}{%
+\subsection{Statistical accounts}\label{statistical-accounts}}
+
+\hypertarget{relative-and-absolute-generics}{%
+\subsubsection{Relative and absolute
+generics}\label{relative-and-absolute-generics}}
+
+Our underspecified threshold model has clear antecedents in other
+statistical accounts, most notably Cohen (1999)'s theory of generics as
+a frequency adverb (e.g., \enquote{generally}). Cohen treats generics as
+a class comprising two qualitatively different types: \emph{relative}
+and \emph{absolute} generics. \emph{Absolute generics} use a fixed, 50\%
+threshold on prevalence: \(p>0.5\). That is, if a particular instance is
+more likely than not to have the feature, then an absolute generic is
+true. By contrast, \emph{relative generics} are true based on a
+comparison to an alternative set of kinds \(Alt(K)\), analogous to the
+categories that comprise the prevalence prior (the so-called
+\emph{comparison class}, which we discuss further in the General
+Discussion). \enquote{Mosquitos carry malaria} is true because an
+arbitrary mosquito is more likely than an arbitrary member of an
+alternative kind to have the feature.
+
+In our model, we treat all generics as relative. Attested differences in
+endorsement, then, emerge through the interplay of prior knowledge with
+our uncertain semantics.\footnote{For a related theoretical argument
+  against the \enquote{relative} / \enquote{absolute} distinction for
+  gradable adjectives, see Lassiter and Goodman (2015).} Further, though
+Cohen's theory is framed in terms of probabilities, it is a fully
+deterministic, fixed-threshold account which only makes qualitative
+predictions about what is true and what is false (i.e., it has a
+deterministic semantics). In contrast, we propose a fully probabilistic
+semantics embedded within a Bayesian model that describes how context
+resolves the uncertain threshold; our theory is a joint
+semantic--pragmatic theory.
+
+Cohen's and other statistical theories employ a mechanism (not currently
+required in our account) known as \emph{domain restriction} to explain
+the context-sensitivity of generics: contextually restricting the
+entities that go into the computation of prevalence (i.e., which robins
+do we look at to compute the probability of laying eggs among robins?).
+Cohen (1999) posits that prevalence is calculated by only considering
+entities that \emph{could have some feature} in a contextually-specified
+alternative set of features \(Alt(F)\). For example, the property
+\emph{lays eggs} induces a set of alternatives that are associated with
+modes of reproduction (e.g., \emph{gives birth to live young},
+\emph{undergoes mitosis}, \ldots{}). \enquote{Robins lay eggs} (an
+absolute generic for Cohen, 1999) is evaluated by only considering
+female members of kinds, because only female members can plausibly
+satisfy one of the other reproductive property alternatives (i.e., the
+alternative features in \(Alt(F)\)). The inferential machinery behind
+domain restriction ---how to determine \(Alt(F)\)---relies upon
+conceptual knowledge, but the details remain obscure (Carlson,
+1995).\footnote{However, see Cohen (2004) for a discussion of how his
+  semantic constraints relate to different kinds of generics and
+  different kinds of conceptual representational frameworks used in
+  cognitive science.} Our uncertain threshold model can be seen as one
+particular mechanism by which the domain may be restricted: The
+structure of the prior distribution over the prevalence of \emph{lays
+eggs} is a reflection of an intuitive theory of reproduction (i.e., that
+only females lay eggs) and the uncertain threshold model uses that
+background knowledge to derive a property-specific interpretation. There
+may exist a refactorization of the uncertain threshold model to a fixed
+threshold where the listener has uncertainty about the relevant domain
+of restriction.
+
+\hypertarget{generic-as-indexical}{%
+\subsubsection{Generic as indexical}\label{generic-as-indexical}}
+
+Sterken (2015) develops a novel analysis taking the context-sensitivity
+of generics as primary. This analysis draws analogy to other, inherently
+context-sensitive linguistic expressions: \emph{indexicals} (e.g.,
+\enquote{this} or \enquote{I}). Sterken (2015) uses this analogy to
+motivate a context-sensitive \emph{quantificational force} as well as
+mechanism of domain-restriction (of the kind used by Cohen, 1999 and
+others). Our uncertain threshold semantics can be seen be a particular
+formalization of Sterken (2015)'s context-sensitive quantificational
+force. We have not had need for employing domain restriction on the
+categories, though as noted above, it is a potential avenue for future
+development.
+
+\hypertarget{normal-accounts}{%
+\subsubsection{\texorpdfstring{\enquote{Normal}
+accounts}{``Normal'' accounts}}\label{normal-accounts}}
+
+A popular alternative view under the statistical banner draws on the
+intuition that generics often express something normative in the world
+(Asher \& Morreau, 1995; Nickel, 2008, 2016; Pelletier \& Asher, 1997).
+\enquote{Dogs have four legs} is then a good generic not because all
+dogs have four legs (regrettably, all do not) but were the world to
+function \emph{normally} (e.g., dogs would not be involved in freak
+tractor accidents or be born with strange genetic mutations), then
+\emph{all} dogs would have four legs. The idea that our beliefs about
+what is normal in the world influences our judgments about
+generalizations has intuitive appeal for rejecting accidentally true
+generics (e.g., \enquote{Supreme Court justices have even social
+security numbers}) and resisting stereotyped language (e.g.,
+\enquote{Boys are good at math}). Our theory does not directly formalize
+what is \emph{normal}, though we argue that a speaker's beliefs about
+what is \emph{probable} (which may relate to what is \emph{normal}; see
+Icard, Kominsky, \& Knobe, 2017) plays a role in endorsing and
+interpreting generalizations.
+
+\hypertarget{underquantification}{%
+\subsubsection{Underquantification}\label{underquantification}}
+
+A proposal similar to our account concerning underspecification of
+generics has been made in the computational linguistics literature
+(so-called \emph{underquantification}; Herbelot \& Copestake, 2011). In
+their model, generics express an explicit quantified relation,
+specifically either \enquote{Some}, \enquote{Most}, or \enquote{All}.
+This proposal is used to then used to construct a set of features that
+accurately predicts (relative to human judgments) the quantified
+relationship expressed by the generic (analogous to a quantifier version
+of the \emph{implied prevalence} task used in Gelman \& Raman, 2003;
+Cimpian et al., 2010). Our semantic theory can be seen as a
+generalization of \emph{underquantification} to a continuous interval of
+possible meanings. This distinction is relevant for the acquisition of
+the language of generalizations; we do not take as primary the
+quantified relations (e.g., \enquote{Some}, \enquote{All}).
+Additionally, by using an underspecified threshold on a scale of
+probability, our formulation naturally extends to other scales and other
+kinds of generalizations (e.g., habitual language), where quantified
+relations like \enquote{Most} or \enquote{All} are not directly
+applicable.
+
+\hypertarget{cue-validity}{%
+\subsubsection{Cue validity}\label{cue-validity}}
 
 By encoding knowledge about other categories, the prevalence prior
-distributions are deeply connected to the construct of \emph{cue
-validity}, or the probability that an entity with a certain property
-\(f\) is a member of kind \(k\): \(P(x \in k \mid x \in f)\) (e.g.,
-one's predictions about whether or not the entity is a robin, upon
-learning that it lays eggs). \emph{Cue validity} implicitly encodes
-knowledge of other categories and has been shown to be highly correlated
-with endorsing \emph{generic sentences}, or generalizations about
-categories (Khemlani, Leslie, \& Glucksberg, 2012). Cue validity is
-defined for a particular (category, property) pair (as is
-referent-prevalence), and relates to referent-prevalence by Bayes' Rule:
-
-\begin{equation}
-P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')} \label{eq:cuevalidity}
-\end{equation}
-
-Since \emph{cue validity} implicitly encodes knowledge of other
-categories (by summing over \(k'\)) and the prevalence prior explicitly
-encodes knowledge of other categories, how are these two constructs
-related? In the prevalence prior \(P(p_f)\), a category is represented
-only by its corresponding prevalence (i.e., a sample from the prevalence
-prior can be thought of as a category \(k\), with the only information
-available about the category being the prevalence of the feature in that
-category \(p_{fk}\)). Thus, \(P(p_{fk}) = P(k_{f})\). The denominator of
-Eq. \ref{eq:cuevalidity} (which encodes knowledge of other categories),
-then, is the expected value (i.e., the mean) of the prevalence prior
-distribution:
-\(\mathbb{E}[P(p_{f})] = \sum_{k' \in K} p_{fk'} \cdot P(p_{fk'} )\).
-For a more thorough derivation of this relationship, see Appendix A. The
-fact that the prevalence prior distribution relates only via its mean
-value to \emph{cue validity} reveals a potential shortcoming of cue
-validity: By reducing a distribution to a point estimate, the structure
-of the distribution is lost. This is particularly problematic for
-prevalence distributions that encode conceptual knowledge via multimodal
-distributions (e.g., Fig. \ref{fig:simulations}A; bottom row); the mean
-of a multimodal distribution is not a good representation of that
-distribution. We return to this point empirically in Case Study 1.
-
-\subsubsection{Model simulations}\label{model-simulations}
-
-The endorsement model defined in the previous section explicitly
-predicts that the variability in endorsements for generalizations in
-language can be explained by two factors: (i) the prevalence
-communicated in the category under discussion \(p_{fk}\) in Eq.
-\ref{eq:S1} (e.g., \(P(x \text{ lays eggs} \mid x \text{ is a robin})\))
-and (ii) the background knowledge about prevalences \(P(p_f)\) (Eq.
-\ref{eq:L0}). We simulate how these two factors change both literal
-interpretation and endorsement using schematic parameter values based on
-intuition from classic examples in the literature on generic language.
-We implemented these and all subsequent Bayesian models in the
-probabilistic programming language WebPPL (Goodman \& Stuhlmüller,
-2014). The following simulations were implemented using the R package
-RWebPPL in the RMarkdown document that generated this paper text and
-figures. That document, as well as all other models, analysis, data and
-links to experiments used in this paper can be found at
-\url{https://mhtess.github.io}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/simulations-1.pdf}
-\caption{\label{fig:simulations}Computational model behavior. A: Prior
-distributions over the prevalence of a feature in a category for 6
-example features B: Different fixed thresholds (columns) give rise to
-different partial interpretations. C: The interpreter model averages
-over all thresholds, producing posterior distributions that strongly
-depend upon the priors. D: Endorsement model predictions, assuming a
-particular referent-prevalence. Shapes of the priors were chosen to
-intuitivly correspond to properties labeling the distributions.}
-\end{figure}
-
-The literal interpretation model computes a posterior distribution on
-prevalence by considering different possible thresholds \(\theta\)
-(Figure~\ref{fig:simulations}B). Low thresholds (e.g., \(\theta = 0.1\))
-rule out very few possibilities (only \(p_{fk} \leq 0.1\)), and thus are
-quite likely given that its consistent with much of the prevalence
-prior. The flip-side of this is that the endorsement model is less
-likely to produce an utterance with a low-threshold in mind, because the
-end result would be similar to staying silent (a posterior not very
-different from the prior). Higher thresholds (e.g., \(\theta = 0.9\))
-rule out more possibilities and thus would be highly informative, but
-the interpretation model must balance this with the prior probabilities
-of the prevalences implied by the threshold
-(Figure~\ref{fig:simulations}A).
-
-The result of this reasoning process is a trade-off between highly
-informative thresholds and the prior probabilities of the prevalences
-implied by those thresholds. The prevalence-based interpretations of
-generalizations of novel categories are shown in
-Figure~\ref{fig:simulations}C. These interpretations depend heavily on
-the prevalence priors (different rows). Hearing \enquote{Ks bark} tells
-the literal interpretor that \emph{almost all} Ks bark, though there is
-a good deal of uncertainty in the precise quantity (top row; pink).
-\enquote{Ks lay eggs} has a strikingly different interpretation: It
-means \enquote{Half of Ks lay eggs} (4th row; green). The literal
-interpreter can also derive very weak interpretation, as shwon in the
-\textsc{carries malaria} distribution (bottom row, purple).
-
-The endorsement model (Eq. \ref{eq:S1}) predicts endorsement
-probabilities based on the literal interpretation of the utterance and
-the referent-category prevalence (e.g., how many robins lay eggs).
-Predictions for a few classic examples from the generics literature are
-shown in (Figure~\ref{fig:simulations}D). In accord with intuition, the
-endorsement model predicts \enquote{Dogs bark}, \enquote{Robins lay
-eggs}, and \enquote{Mosquitos carry malaria} are all true, despite the
-referent-prevalences varying substantially between these three examples.
-Intruigingly, the model predicts \enquote{Robins are female} (which has
-the same prevalence as \enquote{Robins lay eggs}) should receive
-intermediate endorsement: It is neither true nor false. To understand
-this prediction, examine the interpretation distribution for the
-\textsc{are female} distribution: It is identical with the prior
-(Figure~\ref{fig:simulations} A vs.~C; blue distributions). The
-endorsement model decides that is neither better nor worse to produce
-the generalization than to stay silent, as they both carry the same
-information content. This example can be contrasted with cases such as
-\enquote{Sharks don't eat people} and \enquote{Kangaroos have spots},
-which the model thinks would be misleading to say (i.e., better to say
-nothing).
-
-These simulations show how the model predicted endorsement depends upon
-the background knowledge about the property \(P(p_f)\) as well as the
-prevalence \(p_{fk}\) communicated. We chose schematic values for each
-of these, and saw that the endorsement model recapitulates standard
-intuitions about the truth or falsity of classic examples from the
-generics literature. In what follows, we test this theory for a wide
-range of generalizations, including generalizations of different types
-(categories, events, and causes). We do this by both measurning and
-manipulating background knowledge and referent-prevalence and relate it
-to human elicited endorsements of generalizations.
-
+distributions in the uncertain threshold model are deeply connected to
+the construct of \emph{cue validity}, or the probability of the kind
+given the feature: \(P(x \in k \mid x \in f)\) (e.g., one's predictions
+about whether or not an entity is a mosquito, upon learning that it
+carries malaria). Cue validity is believed to play a role in
+understanding generic language (Khemlani, Leslie, \& Glucksberg, 2012;
+Leslie, 2007; Prasada et al., 2013), but the details remain
+underspecified. The strongest view of cue validity is that it
+operationalizes an alternative hypothesis about the meaning of generic
+statements: \enquote{Mosquitos carry malaria} means \enquote{It is
+mosquitos that carry malaria}. Indeed, empirically-elicited cue validity
+has been shown to be highly correlated with endorsements of generics
+(Khemlani et al., 2012).
+
+Cue validity is \emph{inverse prevalence}; the two are related via
+Bayes' Rule:
+\(P( k \mid f) = \frac{P( f \mid k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}\).
+Knowledge about other categories \(k'\) enters in the denominator to
+compute cue validity for prevalence. Indeed this normalizing constant
+(the denominator) is equal to the expected value (i.e., the mean) of the
+prevalence prior distribution: \(\mathbb{E}[P(p)]\). Thus cue validity
+comes from a point estimate of the prevalence prior distribution, and
+information about cue validity can be derived from the constructs
+posited in our model. We return to the implications of this relationship
+in the General Discussion. For a more detailed, mathematical derivation
+of the relationship between cue validity and prevalence priors, see
+Appendix A.
+
+\hypertarget{baseline-models-for-quantitative-comparisons}{%
+\subsection{Baseline models for quantitative
+comparisons}\label{baseline-models-for-quantitative-comparisons}}
+
+In our empirical studies below, we compare our model to three
+alternatives. These alternative models do not represent any of the
+extant theories of generics described above; no extant theory is
+sufficiently precise to yield quantitative predictions. Instead, these
+models are designed to interrogate the theoretically-substantive
+components of our model. There are three such components: (a) property
+knowledge in the form of a prior distribution over prevalence \(P(p)\),
+(b) endorsement as a decision-theoretic process of uttering the
+generalization vs.~not uttering it, and (c) vagueness in the semantics
+of a generalization (i.e., an uncertain threshold). In our empirical
+studies, we compare the uncertain threshold model to an alternative,
+lesioned model which lacks the vagueness in meaning, assigning a fixed
+semantics to the generalization (i.e., analogous to a quantified
+statement) but which has the same prevalence prior and the
+decision-theoretic architecture. There are no correspondingly simple
+ways to lesion the other two components (property knowledge or speaker
+decision) that still produces quantitative, context-sensitive
+predictions. Instead, we compare our model to two regression models
+based on empirically elicited referent prevalence and cue validity,
+which provides some interrogation of the necessity of property knowledge
+in the form of a full distribution on prevalence. In addition to serving
+as alternatives, these baseline regression models help us understand the
+statistical properties of our experimental materials and provide a
+comparison to standard methods in the psychological literature on
+generics (e.g., Khemlani et al., 2012).
+
+\hypertarget{interim-summary-and-overview-of-experiments}{%
+\section{Interim summary and overview of
+experiments}\label{interim-summary-and-overview-of-experiments}}
+
+We have introduced the first quantitative theory of the language of
+generalization, and discussed the relationship of this account to extant
+theories of generics. Above, we presented simulations showing how the
+model predicts endorsements for classically puzzling generic statments.
+These predictions depended upon the background knowledge about the
+property \(P(p)\) as well as the referent prevalence \(p\) believed to
+be true for the category. For each of these we chose intuitive values
+for the parameters of the model (i.e., the prevalence priors and
+referent prevalence levels). In what follows, we test this theory
+empirically for a wide range of generalizations, including
+generalizations of different types (categories, events, and causes). We
+do this by both measuring and manipulating background knowledge and
+referent prevalence and predicting human endorsements of
+generalizations.
+
+In Case Study 1, we examine generalizations about categories expressed
+in generic language. We first measure endorsements for thirty generic
+statements about familiar categories, revealing an entire continuum of
+endorsements (Expt. 1a). We then measure the corresponding prevalence
+priors and referent prevalence using a prevalence prior elicitation task
+(Expt. 1b). We compare the quantitative fits of our model to the three
+alternative models described above. This Case Study is an empirical
+version of several of the worked examples in the section above.
+
+In Case Study 2, we examine generalizations about events expressed in
+habitual language while manipulating the referent prevalence. We measure
+prevalence priors for events of people doing various actions (e.g.,
+people running, hiking, climbing mountains; Expt. 2a). We then measure
+endorsements of habituals for statements about novel actors (e.g.,
+\enquote{John runs}) given referent prevalence information (e.g.,
+\enquote{In the last two months, John ran three times.}; Expt. 2b).
+Finally, we test whether referent prevalence in our model is best
+thought of as a past frequency (e.g., the number of times John has run
+in the past) or a prediction about the future (e.g., the number of times
+a speaker expects John to run in the future) by experimentally
+manipulating future predictions while keeping constant past frequency
+(Expt. 2c). We answer this question by testing the quantitative fits of
+two versions of our model: one in which the speaker is conveying past
+frequency and one in which the speaker is conveying their predictions
+about the future.
+
+Case Study 3 experimentally manipulates the prevalence prior in the
+domain of causal language (e.g., \enquote{Herb X makes animals sleepy}).
+Expt. 3a measures the (manipulated) prevalence prior, confirming that
+our manipulation influenced participants' beliefs about the prevalence
+of the feature across different categories. Expt. 3b measures the
+corresponding influence on causal endorsement, finding an effect of the
+manipulated background knowledge in the way predicted by the uncertain
+threshold model.
+
+\hypertarget{case-study-1-generic-language}{%
 \section{Case Study 1: Generic
-Language}\label{case-study-1-generic-language}
-
-Generalizations about categories (i.e., \emph{generic language}; e.g.,
-\enquote{Dogs bark.}) have received substantial interest in psychology
-for their role in concept and theory formation (e.g., Gelman, 2004),
-stereotype propogation (Rhodes, Leslie, \& Tworek, 2012), and motivation
-(Cimpian, Arce, Dweck, \& Markman, 2007), as well as many other facets
-of everyday reasoning. In addition, generics have been the case study of
-choice for the semantics of the language of generalization because of
-their vexing similarity to quantified statements (e.g., \enquote{Most
-dogs bark}). Time after time, psychologists have shown that generics
-simply do not reduce to quantified statements (e.g., Khemlani et al.,
-2012, Prasada et al. (2013), Cimpian, Brandone, and Gelman (2010)).
-
-Here, we take our first empirical look at how the \emph{underspecified
-threshold} endorsement model predicts actual human endorsements of
-generic statements. We measure endorsement for thirty generic sentences
-that cover a range of conceptual distinctions (Prasada et al., 2013):
-\emph{majority characteristic} (e.g., \enquote{Ducks have wings.}),
-\emph{minority characteristic} (e.g., \enquote{Robins lay eggs.}),
-\emph{striking} (e.g. \enquote{Mosquitos carry malaria.}), \emph{false
-generalization} (e.g., \enquote{Robins are female.}), and \emph{absent
-features} (e.g. \enquote{Lions lay eggs.}). We further craft sentences
-to elicit the full range of acceptability judgments (intuitively:
-\enquote{true}, \enquote{false}, and \enquote{indeterminate}) for
+Language}\label{case-study-1-generic-language}}
+
+Learning from generic language (i.e., generalizations about categories;
+e.g., \enquote{Dogs bark.}) is believed to play a central role in
+concept and theory formation (e.g., Gelman, 2004), stereotype
+propagation (Rhodes et al., 2012), motivation (Cimpian et al., 2007),
+and many other facets of everyday reasoning. In addition, generics have
+been the case study of choice for the semantics of the language of
+generalization because of their tantalizing similarity to quantified
+statements (e.g., \enquote{Most dogs bark}). However, intuitions and
+empirical data argue that generics simply do not reduce to quantified
+statements in a simple way (e.g., Khemlani et al., 2012; Cimpian et al.,
+2010; Prasada et al., 2013).
+
+We first investigate how the uncertain threshold endorsement model
+predicts actual human endorsements of generic statements. We measure
+endorsement for thirty generic sentences that cover a range of
+conceptual distinctions previously discussed in the empirical literature
+on generics (Prasada et al., 2013): characteristic features displayed by
+a majority (e.g., \enquote{Ducks have wings.}), characteristic features
+displayed by a minority (e.g., \enquote{Robins lay eggs.}), features
+that are striking or dangerous (e.g. \enquote{Mosquitos carry
+malaria.}), noncharacteristic features displayed by a minority (e.g.,
+\enquote{Robins are female.}), and features that are totally absent
+(e.g. \enquote{Lions lay eggs.}). We further craft sentences with the
+goal of eliciting the full range of acceptability judgments
+(intuitively: \emph{true}, \emph{false}, and \emph{indeterminate}) for
 generics with properties of low, medium, and high referent-prevalence
@@
 reliably measure the prior belief distribution over the prevalence of
-features \(P(h)\) (Expt. 1b). This elicitation procedure includes
-measurements of the referent-category feature-probabilties \(h'\)
-(e.g.,\(P(x \text{ lays eggs} \mid x \text{ is a robin})\)), allowing us
-to both generate predictions for the endorsement model (Eq. \ref{eq:S1})
-as well as for simpler, alternative models.
-
+features \(P(p)\). The prevalence elicitation procedure (Expt. 1b)
+includes measurements of the referent-prevalence \(p\) for different
+categories (e.g., \(P(x \text{ lays eggs} \mid x \text{ is a robin})\)),
+allowing us to generate predictions for the endorsement model (Eq.
+\ref{eq:S1}) as well as for simpler, alternative models.
+
+\hypertarget{experiment-1a-generic-endorsements}{%
 \subsection{Experiment 1a: Generic
-endorsements}\label{experiment-1a-generic-endorsements}
-
-In this experiment, we elicit human endorsements for generalizations
-about categories (\emph{generics}) taken from the linguistic and
-psychological literature on generics (Prasada et al., 2013). The goal of
-this study is to observe a range of endorsements for generic statements
-about animal categories.
-
-\subsubsection{Method}\label{method}
-
-\paragraph{Participants}\label{participants}
+endorsements}\label{experiment-1a-generic-endorsements}}
+
+In this experiment, we elicit human endorsements for generic sentences
+taken from the linguistic and psychological literatures (Prasada et al.,
+2013). The goal of this study is to elicit high variability of
+endorsements for generic statements about animal categories.
+
+\hypertarget{method}{%
+\subsubsection{Method}\label{method}}
+
+\hypertarget{participants}{%
+\paragraph{Participants}\label{participants}}
 
@@
 IP addresses and with at least a 95\% MTurk work approval rating (the
-same criteria apply to all experiments reported). 4 participants were
+same criteria apply to all experiments reported). Four participants were
 excluded for failing to recall the button corresponding to
-\emph{agreement} in the forced-choice task. 5 participants self-reported
-a native language other than English; removing their data has no effect
-on the results reported. The experiment took about 3 minutes and
-participants were compensated \$0.35.
-
-\paragraph{Procedure and materials}\label{procedure-and-materials}
+\emph{agreement} in the forced-choice task. Five participants
+self-reported a native language other than English; removing their data
+has no effect on the results reported. The experiment took about 3
+minutes and participants were compensated \$0.35.
+
+\hypertarget{procedure-and-materials}{%
+\paragraph{Procedure and materials}\label{procedure-and-materials}}
 
 Participants were shown thirty generic sentences in a randomized order.
-They were asked to press one of two buttons (randomized
-between-participants) to signify whether they agreed or disagreed with
-the sentence (see Table 2 in Appendix for complete list). The thirty
-sentences were presented in a random order between participants and
-covered a range of conceptual categories described above. Approximately
-10 true, 10 false, and 10 uncertain truth-value generics were selected.
-All 30 generic sentences are shown in Figure
-~\ref{fig:generics-endorsement-figure} A. As an attention check,
+They were asked to press one of two buttons (\emph{P} or \emph{Q};
+randomized between-participants) to indicate whether they agreed or
+disagreed with the sentence (see
+Figure~\ref{fig:generics-endorsement-figure}A for the full list). The
+thirty sentences covered a range of conceptual categories described
+above. Approximately ten true, ten false, and ten uncertain \emph{a
+priori} truth-value generics were selected. As an attention check,
 participants were asked at the end of the trials which button
-corresponded to \enquote{Agree}. 4 participants were excluded for
+corresponded to \enquote{Agree}. Four participants were excluded for
 failing this trial.
 
-\subsubsection{Results}\label{results}
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
 
 As a manipulation check, the first author assigned an \emph{a priori}
-truth-judgment (true/false/indeterminate) to each stimulus item. As one
+truth judgment (true/false/indeterminate) to each stimulus item. As one
 would expect, there were substantial differences in empirical
@@
 probability: \(0.93\) \([0.91, 0.94]\)); indeterminate generics were
-agreed with \emph{less} likely than chance (\(0.38\) \([0.35, 0.42])\))
-but substantially more than false generics (\(0.08\) \([0.06, 0.09])\)).
-
-In addition to these categorical differences between our thirty generic
-statements, we find a contiuum of endorsement values (Figure
-~\ref{fig:generics-endorsement-figure} A). Such a continuum of judgments
-is already evidence against any theory that only predicts categorically
-whether a generic statement is true or false. Ideally, a complete theory
-of genericity should be able to explain statements that are endorsed
-completely, unendorsed completely, and all shades in between. We next
-measure the prevalence prior distribution and articulate a set of formal
-models that try to predict these endorsement data.
-
+endorsed at a rate \emph{less} likely than chance (\(0.38\)
+\([0.35, 0.42])\)) but substantially more than false generics (\(0.08\)
+\([0.06, 0.09])\)).
+
+Ideally, a complete theory of genericity should be able to explain
+statements that are endorsed completely, rejected completely, and the
+gradedness between the extremes. We observe gradedness among our thirty
+examples covering a continuum of endorsement values
+(Figure~\ref{fig:generics-endorsement-figure}A). Such a continuum of
+judgments is already evidence against any theory that only predicts
+categorically whether a generic statement is true or false. We next
+measure the prevalence prior distributions and use them to articulate a
+set of quantitative models that try to predict this quantitative
+variability in endorsements.
+
+\hypertarget{experiment-1b-prevalence-prior-elicitation}{%
 \subsection{Experiment 1b: Prevalence prior
-elicitation}\label{experiment-1b-prevalence-prior-elicitation}
-
-The prevalence prior \(P(h)\) in Eq. \ref{eq:L0} describes the belief
+elicitation}\label{experiment-1b-prevalence-prior-elicitation}}
+
+The prevalence prior \(P(p)\) in Eq. \ref{eq:L0} describes the belief
 distribution on the probability of a given feature (e.g.,
 \textsc{lays eggs}) across relevant categories. To get an intuition for
-the kind of knowledge encoded in this belief distribution, consider the
-following thought experiment: You are walking around and you come across
-an instance of your favorite kind of animal from Earth (e.g., a
-peregrine falcon). Ask yourself \enquote{is it female?} Your answer will
-probably depend upon the percentage of the category that you believe to
-be female (e.g., the percentage of female peregrine falcons, i.e.,
-50\%). Now, do you think it lays eggs? Your answer to this question will
-likely depend upon on what animal you're thinking of: If you're thinking
-of a peregrine falcon, the probability is similar to that of being
-female (50\%) because female peregrine falcons lay eggs; if you're
-thinking of a mammal, it's likely that it won't lay eggs (0\%) because
-most mammals give birth to live young. That is, the answer is roughly
-either 50\% or 0\% depending on the kind of creature you are thinking
-of\footnote{The subjective probability may, in fact, be non-zero and
-  small as opposed to 0. Non-zero probabilities allow for the intuitive
-  possibility of a dog that lays eggs potentially due to some strange
-  generic mutation or the interaction of dog genetics with a strange
-  environment.}.
-
-This thought experiment decomposes the prevalence prior \(P(h)\) into a
+the kind of knowledge encoded in this belief distribution, imagine you
+are walking outside and come across an instance of your favorite kind of
+animal (e.g., a reindeer). What is the chance it is female? Your answer
+will probably depend upon the percentage of the category that you
+believe to \emph{be female} (e.g., the percentage of female reindeer,
+approximately 50\%). What is the chance that it lay eggs? Again, this
+depends upon the percentage of the category that you believe \emph{lays
+eggs}, which then further depends on the particular kind of animal under
+consideration: If you're thinking of a reindeer, the answer is probably
+0\%; if you're thinking of a peregrine falcon, the probability is
+similar to the \emph{being female} probability (50\%) because female
+peregrine falcons lay eggs. That is, the answer to how many of an
+arbitrary category is likely to lay eggs is either roughly 50\% or 0\%,
+depending on the kind of creature you may bring to mind.\footnote{The
+  subjective probability may, in fact, be non-zero and small as opposed
+  to 0. Non-zero probabilities allow for the intuitive possibility of a
+  reindeer that, by some terribly improbable set of circumstances such
+  as a genetic mutation, lays eggs.}
+
+The thought experiment decomposes the prevalence prior \(P(p)\) into a
 prior distribution on kinds \(P(k)\) and then a conditional probability
-of the prevalence given the kind \(P(h \mid k)\). We will use this
-decomposition to measure the prevalence prior
-\(P(h) = \int_{k} P(h \mid k) \diff k\) and perform Bayesian data
-analysis to accurately reconstruct the prevalence prior. We measured
-prior distributions empirically for the set of properties (e.g.,
-\textsc{lays eggs, carries malaria}; 21 in total) used in our generic
-sentences in Expt. 1a. To create a larger set of properties, we
+of the prevalence given the kind \(P(p \mid k)\). This decomposition can
+be used to measure the prevalence prior for familiar properties
+\(P(p) = \int_{k} P(p \mid k) \mathop{}\!\mathrm{d}k\) as a stand-in for
+a richer intuitive theory that could give rise to prevalence judgments.
+We measured prior distributions empirically for the set of properties
+(e.g., \emph{lays eggs, carries malaria}; 21 in total) used in our
+generic sentences in Expt. 1a. To create a larger set of properties, we
 reverse-code responses for five properties to create their corresponding
@@
 beautiful feathers} by subtracting from 100\% the responses for
-\enquote{has beautiful feathers}).
-
-\subsubsection{Method}\label{method-1}
-
-\paragraph{Participants}\label{participants-1}
-
-We recruited 60 participants over Amazon MTurk.\\
-3 participants were accidentally allowed to complete the experiment for
-a second time, so we excluded their second responses (resulting in
-\(n=57\)). 2 participants self-reported a native language other than
-English; removing their data (\(n=55\)) has no effect on the results
-reported. The experiment took about 10 minutes and participants were
-compensated \$1.00.
-
-\paragraph{Procedure and materials}\label{procedure-and-materials-1}
+\enquote{has beautiful feathers}).\footnote{This reverse-coding assumes
+  for these properties that logical negation tokenizes its own threshold
+  instead of being derived compositionally via bivalent logical
+  negation. For related empirical and modeling investigations regarding
+  resolving compositional vs.~non-compositional negation (in the context
+  of gradable adjectives, e.g., \enquote{not happy} vs.
+  \enquote{unhappy}), see Tessler and Franke (2018).}
+
+\hypertarget{method-1}{%
+\subsubsection{Method}\label{method-1}}
+
+\hypertarget{participants-1}{%
+\paragraph{Participants}\label{participants-1}}
+
+We recruited 60 participants over Amazon MTurk. Three participants were
+accidentally allowed to complete the experiment for a second time, so we
+excluded their second responses (resulting in \(n=57\)). Two
+participants self-reported a native language other than English;
+removing their data (\(n=55\)) has no effect on the results reported.
+The experiment took about 10 minutes and participants were compensated
+\$1.00.
+
+\hypertarget{procedure-and-materials-1}{%
+\paragraph{Procedure and materials}\label{procedure-and-materials-1}}
 
 On each trial of the experiment, participants filled out a table where
-each row was an animal category and each column was a property.
-Participants first were shown six animal categories randomly sampled
-from a set corresponding to referent-categories of the generic sentences
-used in Expt. 1a (e.g., \textsc{robins, mosquitos}) and were asked to
-generate five of their own (Figure ~\ref{fig:generics-prior-task} A). A
-column then appeared to the right of the animal names with a property
-label in the column header (e.g., \emph{lays eggs}). Participants were
-asked to fill in each row with the percentage of members of each of the
-species that had the property by giving a number (e.g., \enquote{50\%};
-Figure ~\ref{fig:generics-prior-task} B). Eight property--columns in
-total appeared in the table.
-
-This whole procedure was repeated two times (two trials). In total, each
-participant generated ten animal names and reported on the prevalence of
-sixteen properties for twenty-two animals (their own ten and the
-experimentally-supplied twelve).
-
-\begin{figure}[htbp]
+each row was an animal category and each column was a property
+(Figure~\ref{fig:generics-prior-task}). Participants first were shown
+six animal categories randomly sampled from a set corresponding to
+referent-categories of the generic sentences used in Expt. 1a (e.g.,
+\textsc{robins, mosquitos}) and were asked to generate five animal kinds
+of their own (Figure~\ref{fig:generics-prior-task}A). A column then
+appeared to the right of the animal names with a property label in the
+column header (e.g., \emph{lays eggs}). Participants were asked to fill
+in each cell with a with the percentage of members of each of the
+species that had the property (e.g., \enquote{50\%};
+Figure~\ref{fig:generics-prior-task}B). Eight property--columns in total
+appeared in the table. This whole procedure was repeated two times (two
+trials). In total, each participant generated ten animal names and
+reported on the prevalence of sixteen properties for twenty-two animals
+(their own ten and the experimentally-supplied twelve).
+
+\begin{figure}
 \centering
@@
 
-\subsubsection{Qualitative results}\label{qualitative-results}
-
-There is a lot of diversity in the shapes of the elicited prior
-distributions (8 examples shown in Figure~
-\ref{fig:generic-endorsement-priors-figure} A), which is roughly
-consistent with the schematic prior distributions used in the
-\emph{Model Simulations} section (Figure ~ \ref{fig:simulations} A). The
+\hypertarget{qualitative-results}{%
+\subsubsection{Qualitative results}\label{qualitative-results}}
+
+The elicited prior distributions have a diversity of shapes (8 examples
+shown in Figure~\ref{fig:generic-endorsement-priors-figure}A) that are
+roughly consistent with the schematic prior distributions used in the
+\emph{Worked Examples} section (Figure~\ref{fig:simulations}A). The
 property \emph{being female} is present in almost all categories in
-almost exactly the same proportion, where as properties such as
+almost exactly the same proportion, whereas properties such as
 \emph{laying eggs} or \emph{having spots} exhibit more structure
@@
 whereas \emph{carrying malaria} is really only present at low prevalence
-levels. This diversity is important because the endorsement model makes
-different predictions depending on the shape of the prior.
-
-\subsubsection{Quantitative modeling}\label{quantitative-modeling}
-
-In order to integrate the results of this prior measurement task into
-our model of endorsement, we must accurately model the prior elicitation
-data. We do this using a Bayesian mixture model, which assumes that the
-data generated for each property (e.g., \textsc{lay eggs}) comes from
-one of two underlying Beta distributions (\emph{Mixture of
-Betas}).\footnote{The Beta distribution is chosen because the support of
-  this distribution is numerical values between 0 - 1, exactly the form
-  of the response data in the prior elicitation task.} We specify one of
-these distributions \emph{a priori} to represent kinds of animals who
-\emph{do not have} a stable causal mechanism that could give rise to the
-property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in
-prevalence or prevalence values close to or equal to 0.\footnote{This
-  assumption is similar in spirit that employed by \emph{Hurdle Models}
-  of epidemiological data, where the observed count of zeros is often
-  substantially greater than one would expect from standard models, such
-  as the Poisson (e.g., when modeling adverse reactions to vaccines;
-  Rose, Martin, Wannemuehler, \& Plikaytis, 2006)} This \enquote{null
-distribution} is potentially present for all features in exactly the
-same way (i.e., the lack of producing the feature). The second
-distribution represents kinds of animals who \emph{do have} such a
-mechanism, and the two parameters of this distribution are not specified
-\emph{a priori} and are not the same for all properties, but are
-inferred on a property-wise basis from participants' responses. The
-\emph{Mixture of Betas} distribution has a third free parameter (for
-each property), the relative contribution of the \enquote{null
-distribution} (for example: we expect the \enquote{null distribution} to
-not contribute at all to properties like \emph{being female}, for which
-almost all categories have at least some members with the property). To
-ensure the \emph{Mixture of Betas} model of the prior is not overly
-complex, we fit an additional model that represents only a single
-underlying distribution (\emph{Single Beta}) for a comparison. For more
-details about model implementation and inference, see Appendix C.
+levels. This diversity is important because our endorsement model makes
+different predictions depending on the shape of these distrubutions.
+
+\hypertarget{modeling-the-prevalence-priors}{%
+\subsubsection{Modeling the prevalence
+priors}\label{modeling-the-prevalence-priors}}
+
+In order to incorporate the uncertainty in our measurement of the
+prevalence prior into the endorsement model's predictions, we build a
+Bayesian statistical model of the prior elicitation data. We approximate
+the prevalence distribution for each property (e.g., \textsc{lay eggs})
+with a Mixture of Betas model, which assumes that the data generated for
+each kind comes from one of two underlying Beta distributions.\footnote{The
+  Beta distribution is chosen because the support of this distribution
+  is numerical values between 0 - 1, exactly the form of the response
+  data in the prior elicitation task.} We specify one of these
+distributions \emph{a priori} to represent kinds of animals who \emph{do
+not have} a stable causal mechanism that could give rise to the property
+(e.g., \textsc{lions} and \textsc{lay eggs}), which results in
+prevalence or prevalence values close to or equal to 0. This \emph{null
+distribution} is potentially present for all features and acts in
+exactly the same way (i.e., the lack of producing the
+feature).\footnote{This assumption is similar in spirit to that employed
+  by \emph{Hurdle Models} of epidemiological data, where the observed
+  count of zeros is often substantially greater than one would expect
+  from standard models, such as the Poisson (e.g., when modeling adverse
+  reactions to vaccines; Rose, Martin, Wannemuehler, \& Plikaytis, 2006)}
+The second distribution represents kinds of animals who \emph{could}
+have such a mechanism, and the two parameters of this distribution are
+not specified \emph{a priori} and are not the same for all properties,
+but are inferred on a property-wise basis from participants' responses.
+The \emph{Mixture of Betas} distribution has a third free parameter (for
+each property), the relative contribution of the null distribution (for
+example: we expect the null distribution to not contribute at all to
+properties like \emph{being female}, for which almost all categories
+have at least some members with the property). To ensure the
+\emph{Mixture of Betas} model of the prior is not overly complex, we fit
+an additional model that represents only a single underlying
+distribution (\emph{Single Beta}) for a comparison. For more details
+about model implementation and inference, see Appendix C.
 
@@
 two Beta distributions and not as a single Beta distribution (Figure~
-\ref{fig:generic-endorsement-priors-figure} B; red vs.~blue lines). The
-\emph{Single Beta} model does okay for the \emph{being female}
+\ref{fig:generic-endorsement-priors-figure}B; red vs.~blue lines). The
+\emph{Single Beta} model provides a good fit for the \emph{being female}
 distribution, but overly smooths the other distributions, washing out
-the latent structure in participants' responses. One prior that the
+the latent structure in participants' responses. One property that the
 \emph{mixture of Betas} model does not perfectly capture is the prior
-distribution over the feature \textsc{lay eggs}. The empirical
-distribution is tri-modal, with reliable modes at 0\%, 50\%, and
-100\%\footnote{Similar phenomena have been observed in other prevalence
-  elicitation tasks when the referent-category is fixed (e.g.,
-  estimating only the percentage of \emph{robins} that \emph{lay eggs};
-  Prasada et al., 2013)}; a simple two-component mixture model has no
-way to account for such a tri-modal distribution. A more complex model
-(i.e., one with three mixture components) is necessary to perfectly
-account for this item.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/generic-endorsement-priors-figure-1.pdf}
-\caption{\label{fig:generic-endorsement-priors-figure}A: Empirically
-elicited prior distributions over prevalence for eight properties. B:
-Cumulative density plots reveal that a model of a mixture of two Beta
-distributions does substantially better at capturing the structure of
-the priors than a single Beta distribution. Distributions are the
-posterior predictive distributions for the models of the prio and the
-raw empirical distribution. A completely uniform distribution would be
-represented as the y = x line.}
+distribution over the feature \emph{lays eggs}. The empirical
+distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%;
+a simple two-component mixture model has no way to account for such a
+tri-modal distribution.\footnote{The third mode at 100\% is not
+  attributable to categories for which all members could be female
+  (e.g., chickens). Instead, it appears that some participants are
+  responding that 100\% of several different kinds of birds (e.g.,
+  robins) lay eggs. This may result from participants implicitly only
+  considering female members of the category as relevant to answer a
+  question about a reproductive capactiy like \emph{lays eggs}; this
+  restriction of what enters into the prevalence computation is known as
+  \emph{domain restriction}, is posited in several theories of generics
+  (e.g., Cohen, 1999), and has been observed in other prevalence
+  elicitation tasks (e.g., Prasada et al., 2013).} A more complex model
+(i.e., one with three mixture components) would be necessary to
+perfectly account for this item. Using a three-component model for this
+distribution does not change the resulting model predictions and we
+maintain the simpler two-component mixture for uniformity.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/generic-endorsement-priors-figure-1} \caption{A: Empirically elicited prior distributions over prevalence for eight properties.
+B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution.
+Distributions are the posterior predictive distributions for the models of the prior and the raw empirical distribution.
+A completely uniform distribution would be represented as the y = x line.}\label{fig:generic-endorsement-priors-figure}
 \end{figure}
 
+\hypertarget{endorsement-model-comparison}{%
 \subsection{Endorsement model
-comparison}\label{endorsement-model-comparison}
-
-To understand the generative process of generic endorsement, we
-articulate a set of formal models that have been previously-proposed in
-the literature, an alternative-form of our proposed endorsement model,
-and our full endorsement model. As the simplest baseline hypothesis, we
-first explore how well referent-category prevalence itself predicts
-generic endorsement (e.g., does the fraction of \textsc{robins} that
-\textsc{lay eggs} predict the felicity of \emph{Robins lay eggs}?). As a
-secondary alternative hypothesis, we explore whether referent prevalence
-and \emph{cue validity}---the probability of a kind given the feature
-(described in more detail below)---predicts the endorsement data. We fit
-these models using standard maximum-likelihood techniques; we model
+comparison}\label{endorsement-model-comparison}}
+
+We can now compute the predictions of our endorsement model. We describe
+first the behavior of a set of alternatives models that have been
+previously proposed in the literature and an alternative form of our
+proposed endorsement model before proceeding to the results of the
+uncertain threshold endorsement model.
+
+\hypertarget{baseline-models}{%
+\subsubsection{Baseline models}\label{baseline-models}}
+
+We present two baseline, quantitative models that have previously been
+used in the empirical literature on generic language. In addition to
+serving as alternatives, these regressions model help us understand the
+statistical properties of our thirty items. First, we estimate how well
+referent prevalence itself predicts generic endorsement (e.g., does the
+fraction of robins that lay eggs predict the felicity of \emph{Robins
+lay eggs}?). Second, we include \emph{cue validity}---the probability of
+a kind given the feature---as a second predictor in a linear model. We
+fit these models using standard maximum-likelihood techniques and model
 uncertainty in the input measurements (i.e., referent prevalence, cue
@@
 
-Our underspecified-threshold hypothesis models endorsement by
-considering how well the generalization would bring a naive
-interpreter's prior distribution on prevalence \(P(h)\) (e.g., the
-prevalence of laying eggs among other animals) in line with the
-referent-category prevalence (e.g, the prevalence of laying eggs among
-robins). There are several substantive components to this hypothesis:
-(a) the prior distribution \(P(h)\) is relevant, (b) endorsement is a
-decision-theoretic process of uttering the generalization vs.~not
-uttering it, and (c) the core semantics of a generalization is an
-uncertain threshold. As a control model, we assign a fixed semantics to
-the generalization (i.e., analogous to the quantified statements) but
-keep the prior and the decision-theoretic architecture in place. This
-provides a strict test of the uncertain-threshold hypothesis (c).
-
-\subsubsection{Baseline models}\label{baseline-models}
-
-\paragraph{Referent prevalence}\label{referent-prevalence}
+\hypertarget{referent-prevalence}{%
+\paragraph{Referent prevalence}\label{referent-prevalence}}
 
 From the prevalence prior data (Expt. 1b), we estimate participants'
-beliefs about the probability of a feature for the referent categories
-(e.g., the percentage of \textsc{robins} that \textsc{lay eggs}). We
-find a little over half of the variance in the endorsement data is
-explained this way (\(r^2(30) = 0.51\); MSE=\(0.08\); Figure ~
-\ref{fig:generic-endorsement-priors-figure}, upper-right: lower-left
-facet). The referent prevalence baseline is a decent model of these data
-because our stimulus set includes generics that are true with high
-prevalence properties (e.g., \emph{Leopards have spots.}) and generics
-that are false with low prevalence properties (e.g., \emph{Leopards have
+beliefs about the referent prevalence (e.g., the percentage of
+\textsc{robins} that \textsc{lay eggs}) and use it to predict
+endorsement. We find a little over half of the variance in the
+endorsement data is explained this way (\(r^2(30) = 0.51\);
+MSE=\(0.08\); Figure ~\ref{fig:generic-endorsement-priors-figure}B
+upper-left facet). Referent prevalence alone predicts a fair amount of
+variance because our stimulus set includes generics that are true with
+high prevalence properties (e.g., \enquote{Leopards have spots.}) and
+false with low prevalence properties (e.g., \enquote{Leopards have
 wings.}).
 
-However, large deviations from an account based purely on referent
-prevalence remain: Generics in which the referent-category has
-intermediate prevalence (prevalence quartiles 2 and 3:
+Large deviations from an account based purely on referent prevalence
+remain: Generics in which the referent-category has intermediate
+prevalence (prevalence quartiles 2 and 3:
 \(16\% < \text{prevalence} < 64\%\)), are not at all explained by
@@
 
+\hypertarget{cue-validity-and-referent-prevalence}{%
 \paragraph{Cue validity and referent
-prevalence}\label{cue-validity-and-referent-prevalence}
-
-\subparagraph{Model specification}\label{model-specification}
-
-Cue validity is linearly related to a point-estimate of the prevalence
-prior distribution (see Model section and Appendix A). It thus
-implicitly captures information about other categories, though cannot
-capture the structure that is present in the prevalence priors. To show
-that this structure is important, we explore a secondary baseline model
-based on prevalence and cue validity.
-
-Though the cue validity of a particular (category, property) pair can be
-derived from the prevalence prior distribution, previous empirical
-studies of generic language have not done this. Instead, these studies
-estimate cue validity by asking a separate group of participants about
-the distinctiveness of features for given animals (e.g., Khemlani et
-al., 2012), though different studies use different measurements.
-Preliminary analysis of these different measurements revealed that a
-\emph{free production} paradigm (Cree, McNorgan, \& McRae, 2006) is
-preferred. Participants (\(n = 100\)) were supplied with a feature
-(e.g., \enquote{X lays eggs}) and asked to generate a kind (e.g.,
-\enquote{what do you think X is ?}). For a detailed analysis of
-different cue validity measurements and comparison to \emph{prevalence
-prior derived cue validity}, see Appendix B.
-
-\subparagraph{Results}\label{results-1}
+prevalence}\label{cue-validity-and-referent-prevalence}}
+
+Cue validity indexes the diagnosticity of the feature for a kind, given
+formally by the probability of a kind given the feature \(P(k \mid f)\).
+As discussed in the \emph{Other Theories} section above, cue validity is
+linearly related to expected value of the prevalence prior distribution
+(see Appendix A for derivation). Cue validity thus acts using a
+\emph{point estimate} of the prevalence prior distribution, a single
+metric that summarizes the prior distribution.
+
+Though the cue validity of a property for a category can be derived from
+the prevalence prior distribution, previous empirical studies of
+generics have estimated cue validity from different empirical sources
+(Cree, McNorgan, \& McRae, 2006; Khemlani et al., 2012). In the
+empirical literature on generics, researchers often ask directly about
+the cue validity probability (e.g., ``There is an animal that lays eggs.
+What is the probability that it is a robin?''; Khemlani et al., 2012),
+though in the broader literature on semantic memory a \emph{free
+production} paradigm is often employed (e.g., ``X lays eggs. What do you
+think X is?''; Cree et al., 2006). We found that these two ways of
+estimating cue validity diverge for a number of key cases (Appendix B).
+Most notably, undiagnostic features (e.g., \emph{is female}), which in
+theory have a cue validity close to zero, were rated as having
+intermediate cue validity (around 0.5) in the \emph{direct question}
+paradigm, but not in the \emph{free production} paradigm. In response to
+a direct question such as \enquote{There is an animal that is female.
+What is probability that it is a robin?}, participants seem to want to
+respond \enquote{I don't know} by placing the slider bar at the
+midpoint, rather than reporting their intuitive base rate that a random
+animal would be a robin. The free production paradigm did not produce
+artifacts such as this one, and we chose to use it as the more veridical
+estimate of cue validity. For a detailed analysis of the different cue
+validity measurements and comparison to cue validity derived from the
+prevalence prior, see Appendix B.
 
 A linear model that uses predictors for both referent-prevalence and cue
-validity does a better job at explaning the endorsement data than just
+validity does a better job at explaining the endorsement data than just
 prevalence alone (\(r^2(30) = 0.73\); MSE=\(0.04\)). This model is able
@@
 carry malaria} (model endorsement and bootstrapped-95\% confidence
-interval = 0.84 {[}0.72, 0.92{]}) and \enquote{Lions have manes} (0.79
-{[}0.63, 0.88{]})), as these features are very diagnostic of the kind
-(human endorsement both \(> 0.9\)). Deviations, however, still remain.
+interval = 0.85 {[}0.72, 0.86{]}) and \enquote{Lions have manes} (0.79
+{[}0.61, 0.84{]})), as these features are very diagnostic of the kind
+(generic endorsement both \(> 0.9\)). Deviations, however, still remain.
 For example, \enquote{Robins lay eggs} still receives only intermediate
-endorsement by this model (0.68 {[}0.57, 0.79{]}; human endorsement =
+endorsement by this model (0.68 {[}0.56, 0.69{]}; human endorsement =
 0.94 {[}0.87, 0.97{]}), and \enquote{Mosquitos don't carry malaria} is
-judged to be a pretty good statement (0.57 {[}0.42, 0.71{]}; human
+misjudged to be a pretty good statement (0.58 {[}0.41, 0.58{]}; human
 endorsement = 0.07 {[}0.04, 0.14{]}).
@@
 highlight a shortcoming of reducing structured prevalence prior
-distributions to single point-estimates of cue validity. \enquote{Lays
-eggs} is a somewhat diagnostic feature for \emph{birds}, but there are
-many kinds of birds, and the feature is not itself diagnostic for a
-particular kind of bird like \enquote{Robins}. Thus, the cue validity is
-low even though robins are in the distinctive part of the \enquote{lays
-eggs} prevalence prior distribution (e.g., Fig.~\ref{fig:simulations}A
-bottom). Furthermore, cue validity glosses over the difference between
-\enquote{undiagnostic} features (features present in almost every
-category; e.g., \enquote{not carrying malaria}) and \enquote{false}
-features (features that are absent a particular category; e.g.,
-\enquote{lions} and \enquote{lay eggs}; see Appendix B for more
-discussion of this distinction). Such a model makes the wrong prediction
-for non-distinctive properties that in, absolute terms, have high
-prevalence but in relative terms, low prevalence (e.g.,
-\enquote{Mosquitos don't carry malaria}). A simple metric like cue
-validity is too blunt to capture these subtleties.
-
+distributions to single point-estimates of cue validity. \emph{Lays
+eggs} is a somewhat diagnostic feature for birds, but there are many
+kinds of birds, and the feature is not itself diagnostic for a
+particular kind of bird like robins. Thus, the cue validity is low even
+though robins are in the distinctive part of the \emph{lays eggs}
+prevalence prior distribution (Figure~\ref{fig:simulations}A bottom).
+Furthermore, cue validity cannot distinguish \emph{undiagnostic}
+features (features present in almost every category; e.g., \emph{not
+carrying malaria}) from \emph{false} features (features that are absent
+a particular category; e.g., \emph{lions} and \emph{lay eggs}; see
+Appendix B for more discussion of this distinction); the cue validity
+can be near-zero for different reasons. Such a model makes the wrong
+prediction for non-distinctive properties with high referent prevalence
+(e.g., \enquote{Mosquitos don't carry malaria}).
+
+\hypertarget{communicative-endorsement-models}{%
 \subsubsection{Communicative endorsement
-models}\label{communicative-endorsement-models}
-
-The model we propose for endorsing generalizations is a model of an
-agent that decides whether or not to say the generalization to a naive
-interpretor. The endorsement model (Eq. \ref{eq:S1}) decides whether or
-not to assert the generalization to a naive interpretor (Eq.
-\ref{eq:L0}) conditioned on a particular referent-category prevalence
-\(h'\) (e.g., the percentage of robins that lay eggs). We use the
-empirically estimated referent-category prevalence (the same as used in
-the baseline regression model) as the referent-category prevalence
-\(h'\) in the endorsement model. The empirically measured priors from
-Expt. 1b are used as the literal interpreter's prevalence prior
-\(P(h)\).
-
-To incorporate the measurements of these model components into our
-endorsement model, we build a single, Bayesian joint-inference model of
-the referent-category prevalence \(h'\), prevalence priors \(P(h)\)
-(both from Expt. 1b data), and the endorsement data (Expt. 1a). Modeling
-the data from both Expt. 1a and 1b by a single, joint-inference model
-simultaneously makes explicit our assumptions about how these data were
-generated and is the proper way to represent the uncertainty in our
-measurement of the prior elicitation data (see Appendix and Figure~
-\ref{fig:genericsModelDiagram} for further model specification details).
-The endorsement model is then fully specified after setting the single
-optimality parameter \(\lambda_1\) (in Eq. \ref{eq:S1}). To learn about
-the credible values of the parameters of the model and resulting model
-predictions, we ran an incrementalized version of MCMC (Ritchie,
-Stuhlmüller, \& Goodman, 2016) for 3 chains of 100,000 iterations,
-discarding the first 50,000 for burnin.
-
-The number of parameters of this full data-analytic model is relatively
-large, and thus there is a concern that the parameters themselves (as
-opposed to the exact structure of our model) are doing the work. To
-address this concern, we construct a strong, alternative model that uses
-the same data analytic strategy and only differs in the uncertain
-semantic threshold \(\theta\) is replaced with a fixed-threshold. To
-provide the strongest possible test, we make the fixed-threshold a
-parameter of the data-analytic model, to search for the best possible
-fixed-threshold. Finally, a fixed-threshold model will have to
-accomodate responses that are inconsistent with the threshold (i.e., a
-participant endorsing the generalization when the referent prevalence is
-low); we thus outfit this model with an \emph{additional} noise
-parameter, to allow for random guessing. Thus, our fixed-threshold
-alternative model says that participants make an information-theoretic
-decision, taking into account the interpreter's prior distribution
-\(P(h)\), using a fixed-threshold semantics, where deviations from a
-pure information-theoretic decision are accounted for by noise. This
+models}\label{communicative-endorsement-models}}
+
+Our underspecified-threshold model considers how well the generalization
+would bring a naive interpreter's prior distribution on prevalence
+\(P(p)\) (Eq. \ref{eq:L0}; e.g., the prevalence of laying eggs among
+other animals) in line with the speaker's belief about the referent
+prevalence (\(p\) in Eq. \ref{eq:S1}; e.g, the prevalence of laying eggs
+among robins). As described in the \emph{Intermediate Summary}, there
+are several substantive components to this hypothesis: (a) property
+knowledge in the form of a prior distribution over prevalence \(P(p)\),
+(b) endorsement as a decision-theoretic process of uttering the
+generalization vs.~not uttering it, and (c) vagueness in the semantics
+of a generalization. We construct an alternative, lesioned model by
+removing the vagueness in meaning, assigning a fixed semantics to the
+generalization (i.e., analogous to the quantified statements) but
+keeping the prior and the decision-theoretic architecture in place.
+There are no correspondingly simple ways to lesion the other two
+components (context or speaker decision) while still producing a model
+that makes quantitative, context-sensitive predictions.
+
+For both the fixed-threshold and full uncertain-threshold endorsement
+models, we build a joint Bayesian data analysis model of the referent
+prevalence \(p\), prevalence priors \(P(p)\) (both from Expt. 1b data),
+and the endorsement data (Expt. 1a). Predicting the data from both Expt.
+1a and 1b by a single, joint-inference model makes our assumptions
+explicit about how these data were generated and is the proper way to
+represent the uncertainty in our measurement of the prior elicitation
+data (see Appendix C and Figure~\ref{fig:genericsModelDiagram} for
+further model specification details). Empirically elicited referent
+prevalence and prevalence prior data (Expt. 1b) directly constrain the
+parameters that generate those quantities in the model (\(p\) in Eq.
+\ref{eq:S1} and \(P(p)\) in Eq. \ref{eq:L0}, respectively). The
+prevalence prior \(P(p)\) is modeled as a mixture of Betas while
+referent prevalence is modeled by a single Beta distribution. The
+endorsement data (Expt. 1a) is model by our endorsement model (Eq.
+\ref{eq:S1}), which has one free parameter \(\lambda\). To learn about
+the credible values of the parameters of the joint-inference model and
+resulting model predictions, we ran an incrementalized version of MCMC
+(Ritchie, Stuhlmüller, \& Goodman, 2016) for 3 chains of 150,000
+iterations, discarding the first 50,000 for burn-in.
+
+\hypertarget{lesioned-model-no-vagueness}{%
+\paragraph{Lesioned model (no
+vagueness)}\label{lesioned-model-no-vagueness}}
+
+For a strong alternative model, we lesion the uncertain threshold model
+so that it has a fixed threshold \(\theta\). We make this the strongest,
+possible fixed-threshold model by searching for the best possible single
+threshold that fits the data. However, a fixed-threshold model will have
+to accommodate responses that are literally inconsistent with the
+threshold (i.e., a participant endorsing a generic when the referent
+prevalence is less than \(\theta\)); we thus outfit this model with an
+additional extrinsic noise parameter, to allow for random guessing.
+Thus, the fixed-threshold alternative model claims that participants
+make an information-theoretic decision, taking into account the
+interpreter's prior distribution on prevalence \(P(p)\), using a
+fixed-threshold semantics, where deviations from a pure
+information-theoretic decision are accounted for by noise. This
 alternative model has 2 additional parameters to our uncertain threshold
-model (the fixed-threshold and the proportion of noise responses). We
-examine the predictions of this alternative model first.
-
-\paragraph{Fixed-threshold with noise
-model}\label{fixed-threshold-with-noise-model}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/generics-endorsement-figure-1.pdf}
-\caption{\label{fig:generics-endorsement-figure}Endorsing generalizations
-about categories. Top left: Human elicited endorsements for thirty
-generic sentences reveal a continuuum of endorsements. Top right: Model
-fits for the uncertain semantics speaker model (upper right), a fixed
-semantics speaker model (upper left), and regression models based on
-referent prevalence alone (lower left) and prevalence + cue validity
-(lower right). Bottom: Five example prevalence priors, listener
-posteriors upon hearing the generalization, and speaker belief
-distributions about the referent prevalence. These distributions are
-inferred using all three data sources from Expt. 1 (see Figure
-\ref{fig:genericsModelDiagram} for an overview of the Bayesian data
-analytic approach).}
+model (the value of the fixed-threshold and the proportion of noise
+responses).
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/generics-endorsement-figure-1} \caption{Endorsing generalizations about categories.
+A: Human elicited endorsements for thirty generic sentences reveal a continuum of endorsements.
+B: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent prevalence alone (lower left) and prevalence + cue validity (lower right).
+C: Five example empirical prevalence priors, model-predicted generic interpretations, and empirical referent prevalence (speaker belief) distributions..}\label{fig:generics-endorsement-figure}
 \end{figure}
 
-To evaluate the fixed-threhsold model, we examine the posterior
-distribution which represents what we should believe about the latent
-parameters of the model (referent prevalence, prevalence priors, the
-optimality, fixed-threshold, and noise parameters) given the observed
-data, as well as what predictions of the model given these parameter
-values. The Maximum A-Posteriori value and 95\% highest probability
-density interval for the inferred (fixed) threshold and noise parameters
-are 0.34 {[}0.25, 0.37{]} and 0.20 {[}0.18, 0.22{]}, respectively. The
-inferred optimality parameter in Eq. \ref{eq:S1} is 0.34 {[}0.25,
-0.37{]}.
-
-We compare the fixed-threshold model's posterior predictive distribution
-of generic endorsement to the empirical truth judgments. Figure
-\ref{fig:generics-endorsement-figure} (top right; top left subplot)
+To evaluate the fixed-threshold model, we examine model predictions as
+well as the posterior distribution over latent parameters of the model
+(referent prevalence, prevalence priors, the optimality,
+fixed-threshold, and noise parameters) given the observed data. The
+Maximum A-Posteriori value and 95\% highest probability density interval
+for the inferred (fixed) threshold and noise parameters are 0.34
+{[}0.25, 0.37{]} and 0.20 {[}0.18, 0.22{]}, respectively. The inferred
+optimality parameter in Eq. \ref{eq:S1} is 0.34 {[}0.25, 0.37{]}.
+Figure~\ref{fig:generics-endorsement-figure}B (bottom right subplot)
 shows the fixed-threshold model's ability to predict the generic
@@
 model is able to capture a lot of the variance, it only makes three
-kinds of judgments: true, false, or neither. It treats \enquote{Tigers
-eat people} (0.90 {[}0.85, 0.91{]}) as good a statement as
-\enquote{Peacocks have beautiful feathers} (0.88 {[}0.85, 0.91{]}),
-though participants seem to give a substantially weaker endorsement of
-the former (\enquote{Tigers eat people} = 0.69 {[}0.59, 0.77{]};
-\enquote{Peacocks have beautiful feathers} = 0.99 {[}0.94, 1{]}).
-Similarly, \enquote{Lions lay eggs} is judged to be just as bad as
-\enquote{Mosquitos attack swimmers}(0.10 {[}0.09, 0.15, 0.10 {[}0.09,
-0.15{]}, respectively), though participants rate the former as
-completely false (0.01 {[}0, 0.06{]}) while the latter is kind of true
-(0.38 {[}0.28, 0.48{]}). This alternative model is unable to make these
-fine-grained distinctions because it must use the same semantic
-threshold in all contexts.
-
-\paragraph{Uncertain threshold model}\label{uncertain-threshold-model}
+kinds of judgments: true, false, or neither, similar to purely semantic
+accouts of generics. It treats \enquote{Tigers eat people} (0.90
+{[}0.89, 0.91{]}) as good a statement as \enquote{Peacocks have
+beautiful feathers} (0.90 {[}0.89, 0.91{]}), though participants give a
+substantially weaker endorsement of the former (\enquote{Tigers eat
+people} = 0.69 {[}0.59, 0.77{]}; \enquote{Peacocks have beautiful
+feathers} = 0.99 {[}0.94, 1{]}). Similarly, \enquote{Lions lay eggs}
+(0.10 {[}0.09, 0.11{]}) is judged to be just as bad as
+\enquote{Mosquitos attack swimmers} (0.10 {[}0.09, 0.11{]}), though
+participants rate the former as completely false (0.01 {[}0, 0.06{]})
+while the latter is kind of true (0.38 {[}0.28, 0.48{]}). The
+fixed-threshold alternative model is unable to make these fine-grained
+distinctions because it uses the same semantic threshold in all
+contexts.
+
+\hypertarget{uncertain-threshold-model}{%
+\paragraph{Uncertain threshold model}\label{uncertain-threshold-model}}
 
@@
 model, except that rather than having a fixed \(\theta\) for all
-contexts, the model infers context-specific \(\theta\)'s. We construct
-the same joint-inference Bayesian data analytic model as we did for the
-fixed-threshold analysis; however, we are able to drop the additional
-parameters required for the fixed-threshold model (the fixed-threshold
-and noise parameters). Thus, this model has two \emph{fewer} parameters
-than the fixed-threshold model above.
+contexts, the model infers property-specific \(\theta\)'s. We use the
+same Bayesian data analysis approach, dropping the additional parameters
+required for the fixed-threshold model (the fixed-threshold and noise
+parameters). Thus, this model has two fewer parameters than the
+fixed-threshold model above.
 
 We first examine the posterior predictive distribution on the prevalence
-prior and referent-prevalence data to ensure that the joint-inference
-model fits these data as well as the Bayesian model that modeled these
-data in isolation. This is an important step in model validation because
-it tells us that our model's predictions are derived from reasonable
-values of the parameters. Importantly, the model recapitulates the prior
-elicitation data (e.g., the probability of laying eggs among various
-species) and the referent-category prevalence data (e.g., the
-probability of laying eggs among robins) as it did when the Bayesian
-data analysis model only included these data and their associated model
-(results section of Expt. 1b). This result confirms that the
+prior and referent prevalence data to ensure that the joint-inference
+model does not distort these parameters at the service of predicting the
+endorsement data (e.g., such a distortion could manifest by the
+joint-inference model inferring that 100\% of mosquitos carry malaria in
+order to predict that \enquote{Mosquitos carry malaria} is a good
+utterance). This is an important step in model validation because it
+tells whether the model's predictions are derived from intuitively
+plausible values of the parameters (e.g., that not all mosquitos carry
+malaria). Importantly, the joint-inference model captures the prior
+elicitation data (e.g., the probability of carry malaria among various
+species) and the referent prevalence data (e.g., the prevalence of
+carrying malaria among mosquitos) as well as it did when we analyzed
+these data in isolation (without conditioning on the endorsement data)
+(\(r_{\text{prevalence prior parameters}}^2(60) = 0.9997\);
+\(r_{\text{referent prevalence parameters}}^2(63) = 0.9989\); see
+Appendix D, Figure 14). This result confirms that the
 theoretically-interesting predictions of this model --- predictions of
 generic endorsement --- are based on intuitively meaningful model
-components (i.e., the shapes of the prevalence distributions).
-
-The inferred optimality parameter in Eq. \ref{eq:S1} is 0.34 {[}0.25,
-0.37{]}.
-
-As we see in Figure ~\ref{fig:generics-endorsement-figure} (top right,
-top right subplot), the endorsement model that uses an
-uncertain-threshold semantics explains nearly all of the variance in
-human endorsements (\(r^2(30) = 0.9978\); MSE = \(0.00035185\)). To gain
-some intuition for why that is the case, examine the bottom row of
-Figure \ref{fig:generics-endorsement-figure}. The blue, solid lined
-distribution corresponds to the speaker's beliefs about the probability
-of the feature for the referent-category (i.e., \emph{referent
-prevalence}). The grey distribution shows the listener's prior
-distribution over probabilities of the feature (these are the
-corresponding Probability Density Functions of the Cumulative Density
-Functions shown in Figure ~\ref{fig:generic-endorsement-priors-figure}.
-It is also the listener \(L_0\)'s posterior on referent prevalence upon
-hearing the silent utterance. The red distribution shows the \(L_0\)
-posterior upon hearing the generic utterance that corresponding to an
-uncertain threshold-semantics. The speaker model decides when the
-generic utterance conveys information that would bring the listener's
-distribution more in line with the speaker's own distrubtion. Thus, it
-finds that \enquote{Leopards have spots}, \enquote{Robins lay eggs}, and
-\enquote{Mosquitos carry malaria} are also useful things to say.
-\enquote{Robins are female} is neither good nor bad, as the
-information-content of the utterance is very small relative to silence.
-\enquote{Tigers don't eat people} is rather misleading, however; it
-doesn't bring the listener closer to the speaker's distribution, despite
-the speaker believing that the prevalence is more than half.
-
-\subsection{Discussion}\label{discussion}
+components (i.e., the shapes of the prevalence distributions). Finally,
+the inferred optimality parameter in the endorsement model (Eq.
+\ref{eq:S1}) is 2.47 {[}2.18, 2.75{]}, a range consistent with the
+literature on similar models.
+
+As we see in Figure~\ref{fig:generics-endorsement-figure}B (top right),
+the uncertain threshold endorsement model explains nearly all of the
+variance in human endorsements (\(r^2(30) = 0.9978\); MSE =
+\(0.00035185\)). Examining the relevant model components that give rise
+to these predictions further reveals the intuition for why the model
+makes the predictions that it does (Figure
+\ref{fig:generics-endorsement-figure}C). Recall the endorsement model's
+alternative utterance is a null or silent utterance and thus, the
+prevalence prior distributions are exactly what the interpreter model
+would believe if the speaker does not produce the generic. The
+endorsement model then decides whether maintaining the listener's prior
+or updating it with the uncertain threshold semantics would better get
+the listener to guess the correct prevalence for the category (correct
+in the mind of the speaker). The model rates \enquote{Robins lay eggs}
+as a good utterance because the prevalence posterior implied by the
+generalization is similar to the referent prevalence.\footnote{We again
+  note that the empirical prevalence prior for \emph{lays eggs} is
+  tri-model with peaks at 0\%, 50\%, and 100\%. As a result, the generic
+  interpretation is bi-modal: the listener is led to believe either 50\%
+  or 100\% of robins lay eggs. Interestingly, the endorsement model
+  still makes the correct prediction because the referent-prevalence for
+  laying eggs among robins is also bi-modal (peaks at 50\% and 100\%).
+  That is, domain-restriction (resulting in a response of 100\%)
+  seemingly occurs for some participants for \emph{both} the prevalence
+  prior and referent prevalence measurements, and this allows the model
+  to predict correctly that \enquote{Robins lay eggs} is a good generic
+  utterance.} The hypothetical interpretation for \enquote{Robins are
+female} is almost indistinguishable from the prevalence prior, because
+the prevalence prior has such low variance (almost all animals have
+female members in exactly the same proportion); the endorsement model
+then has no basis to prefer silence or the generic statement and the
+prediction is that the utterance should be neither good nor
+bad---endorsement around 0.5---which is what is approximately the
+proportion of participants who endorse the statement. \enquote{Mosquitos
+carry malaria} is an interesting case because the prevalence prior has
+high variance (i.e., participants are highly uncertain about the
+prevalence of carrying malaria among categories). As a result, the
+generic interpretation also has high variance; still, the generic
+interpretation is more consistent with the referent prevalence than the
+prevalence prior, and the endorsement model predicts \enquote{Mosquitos
+carry malaria} is a good utterance. Finally, an utterance with high
+referent prevalence, such as \enquote{Tigers don't eat people}, is
+predicted to have low endorsement because the generic would be
+misleading; even if most tigers don't eat people, saying \enquote{Tigers
+don't eat people} implies that all don't eat people, which is too
+strong.
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
@@
 language. Generics have been studied extensively in the cognitive and
-developmental psychological literatures and shown to have deep
-implications for wide ranging phenomena from stereotype propogation
-(Rhodes et al., 2012) to motivation (Cimpian et al., 2007). Heretofore,
-however, no formal model has been able to pass the most basic
-truth-functional tests of the semantics of generalizations, knowing when
-they are true and false. Determining the truth conditions is the first
-step towards articulating a formal theory of how the language updates
-beliefs.
-
-We have demonstrated that a semantics based on the probability of the
-feature is tenable in spite of alleged counterexamples. The key
-theoretical insight is that the truth-functional semantics is
-\emph{underspecified} yet still is able to formalize, using recent
-developments in probabilistic modeling. Our model provides a clean
-delineation of world knowledge (formalized as a prior distribution) from
-the semantics of generalizations. We return to this point, and its
-implications for theory-building, in the general discussion.
+developmental psychological literatures and have deep implications for
+wide ranging phenomena from stereotype propagation (Rhodes et al., 2012)
+to motivation (Cimpian et al., 2007). Heretofore, no models have been
+articulated with enough precision to make quantitative predictions about
+endorsement decisions, deciding whether a statement is true or false.
+This empirical case study demonstrates that a semantics based on the
+prevalence of the feature is tenable despite of alleged counterexamples
+(e.g., \enquote{Robins lay eggs} vs. \enquote{Robins are female}). The
+key theoretical insight is that the truth-functional semantics is
+underspecified, or vague, and resolved in context by a process of
+probabilistic inference. Our model provides a clear delineation of world
+knowledge (formalized as a prevalence prior) from the semantics of
+generics. We return to this point, and its implications for
+theory-building, in the general discussion.
 
 In explaining the variable endorsements of generics, we related the
-referent-category prevalence (e.g., the percentage of robins that lay
-eggs) to the endorsement of the generalization (e.g., \enquote{Robins
-lay eggs}) via the prevalence priors (e.g., the percentage of different
-kinds of animals that lay eggs). In doing so, we used generic statements
-about familiar animal categories, which has long been the cleanest
-domain for testing semantic theories of generics by providing minimal
-comparison like \enquote{Robins lay eggs} vs. \enquote{\ldots{} are
-female}. To model statements about familiar categories, we were forced
-to \emph{measure} the relevant quantities in the model (i.e., the
-referent prevalence and the prevalence priors), which people have access
-to via their mental representations of the category. We now seek to
-demonstrate how these quantities are causally related to endorsement, by
-manipulating referent prevalence (Case 2) and feature-probabilitiy
-priors (Case 3). In addition, we take this opportunty to highlight the
-generality of the theory, by performing these additional empirical tests
-in different domains for generalization: events and causes.
-
+referent prevalence (e.g., the percentage of robins that lay eggs) and
+the prevalence prior (e.g., the prevalence of laying eggs for different
+kinds of animals) to the endorsement of the generalization (e.g.,
+\enquote{Robins lay eggs}) via an information-theoretic communicative
+model where the meaning of a generic is simple but underspecified. In
+this case study, we used generic statements about familiar animal
+categories, which has long been the cleanest domain for testing semantic
+theories of generics by providing minimal comparison like
+\enquote{Robins lay eggs} vs. \enquote{Robins are female}. However,
+modeling familiar category generics is a correlational analysis: The
+relevant quantities in the model were measured rather than manipulated.
+We now seek to demonstrate how these quantities are causally related to
+endorsement, by manipulating referent prevalence (Case Study 2) and
+prevalence priors (Case Study 3). In addition, we take this opportunity
+to highlight the generality of the theory, by performing these
+additional empirical tests in different domains for generalization:
+events and causes.
+
+\hypertarget{case-study-2-habitual-language}{%
 \section{Case Study 2: Habitual
-Language}\label{case-study-2-habitual-language}
-
-The event of Mary smoking at 2:30pm on January the 24th is an instance
-of a kind of event: \emph{Mary smoking}. Just as with categories,
-generalization can occur over events of a particular type. When
-expressed in language, these generalizations take the form of
-\emph{habitual language}: \enquote{Mary smokes}.
-
-Events are a broad class of entities. In our second case study, we focus
-on habituals about people's behaviors that take the form:
-\textsc{singular noun phrase} \(+\)
-\textsc{present tense simple verb phrase} (e.g., \enquote{Mary smokes
-cigarettes}). Learning about the behaviors of others is useful because
-they tell us about what that person is like more generally (e.g.,
-Repacholi \& Gopnik, 1997; Seiver, Gopnik, \& Goodman, 2013). When
-children describe their lives to other, a surprisingly large amount of
-the langauge produced concerns the actions of people close to them
-(e.g., ``My brother works part-time at the restaurant''; W. J. McGuire
-\& McGuire, 1986). Habitual language about people may be a more
-conservative form of \emph{trait language} (e.g., \enquote{Mary is a
-smoker.}) and convey that behaviors are relatively enduring (Gelman,
-2004; Gelman \& Heyman, 1999).
+Language}\label{case-study-2-habitual-language}}
+
+As with instances of categories, particular events like \enquote{Mary
+smoked yesterday} can be generalized into \emph{habitual sentences}:
+\enquote{Mary smokes}. It is believed that an analysis of generics
+should lend itself naturally to be extended to an analysis of habituals
+(e.g., Carlson, 2005; Leslie, 2008), but no such analysis or empirical
+data has directly connected the two. In our second case study, we focus
+on habituals about people's behaviors that take the form: \emph{singular
+noun phrase} \(+\) \emph{present tense simple verb phrase} (e.g.,
+\enquote{Mary smokes cigarettes}). Learning about the behaviors of
+others is useful because they tell us about what that person is like
+more generally (e.g., Repacholi \& Gopnik, 1997; Seiver, Gopnik, \&
+Goodman, 2013). When children describe their lives to others, a
+surprisingly large amount of the language produced concerns the actions
+of people close to them (e.g., ``My brother works part-time at the
+restaurant''; McGuire \& McGuire, 1986).
 
@@
 model and follow the same general experimental structure as in the first
-case study. We take event analogue of prevalence to be the \emph{rate}
-with which the event occurs (e.g., how often Mary smokes). For the
-generalization \enquote{Mary smokes}, instances of the category being
-generalized are \emph{instances of Mary} and if for the instance to have
-the feature, it means the instance of Mary is one in which she is
-smoking. We test this by first measuring the prevalence (rate) prior
+case study. We take the event analogue of prevalence to be the
+\emph{rate} with which the event occurs (e.g., how often Mary
+smokes).\footnote{Specifically, for the generalization \enquote{Mary
+  smokes}, the instances being generalized are \emph{instances of Mary}.}
+We test the model by first measuring the prevalence (rate) prior
 distribution for various actions (e.g., how often different people smoke
-cigarttes; Expt. 2a). We then measure endorsements of habitual
-statements while manipulating the \emph{referent-prevalence} (Expt. 2b),
-and use our computational model to predict habitual endorsements. By
+cigarettes; Expt. 2A). We then measure endorsements of habitual
+statements while manipulating the referent prevalence (Expt. 2B), and
+use our computational model to predict habitual endorsements. By
 describing novel characters to participants, we are able to directly the
-manipulate the \emph{referent-prevalence} (rate), which we were unable
-to do for generalizations about familiar categories.
+manipulate the referent prevalence, which we were unable to do for
+familiar categories in Case Study 1.
 
 Finally, if habituals (and generics) are truly language for conveying
-generalizations, it would be useful for them to reflect a speaker's
-expectations, not merely her observations. Our computational model
-predicts endorsement rates given a referent-prevalence \(p_{fk}\). Does
-prevalence represent the actual, past frequency of the event (e.g., how
-often Mary has actually smoked in the past month) or the predictive
-probability of the event in the near future (e.g., how often we should
-expect Mary to smoke next week)? We extend our theory by measuring
-participants' predictions about future rates and endorsements of
-habituals when causal forces intervene on the world (Expt. 2c). We then
-use our model to test whether habitual endorsements are based on past
-frequencies or future expectations.
-
-\subsection{Experiment 2a: Measuring the prevalence prior for
-events}\label{experiment-2a-measuring-the-prevalence-prior-for-events}
-
-In order to generate model predictions for corresponding habitual
-statement, we first elicit the prior distributions over rates for
-different events. For language about the behaviors of people, \(P(p_f)\)
-represents a language user's background knowledge about the rates with
-which people do a behavior; this prior can be constructed as a
-distribution over \emph{different people}, each of whom do the behavior
-with a different rate. We designed our elicitation task to take
-advantage of the mixture-model representation of the prevalence prior
-used in Expt. 1 . In particular, we assume, to a first approximation,
-that the distribution over prevalence can be represented as a mixture of
-those who tend to do the action with a stable rate and those who do
-not.\footnote{In the case of event knowledge about people, we expect
-  there to be several more than just these two possibilities represented
-  in the prior, corresponding to individuals with different traits or
-  demographics. We assume here a simple structure so as to not make the
-  specification of the prior overly complex.} With the further
-assumption that, all else being equal, past is predictive of future
-behavior, we operationalize these two kinds of people as \emph{people
-who have done the action before} and \emph{people who have not the
-action before}. We design this experiment to measure participants'
-beliefs about the relative proportion of these two kinds of people (as a
-measure of the mixture parameter in the model) as well as the rate at
-which people (who have done the action before) do the action (as a
-measure of the mean of stable-rate people). We will aassume for
-simplicity that people who have never done the action before will rarely
-or never do the action.
-
-\subsubsection{Method}\label{method-2}
-
-\paragraph{Participants}\label{participants-2}
+generalizations, they should reflect speakers' expectations, not merely
+their observations. This intuition is sometimes expressed as an
+intensional meaning component of generics (Dahl, 1975). For example,
+imagine a very small town where by total coincidence, all residents chew
+sugarless gum. Endorsing the sentence \enquote{Residents of this town
+chew sugarless gum} seems to commit the speaker to believing that it is
+not sheer happenstance, but that there is some underlying cause that
+supports the counterfactual implication that were a new person to become
+a resident of the town, they too would likely chew sugarless gum.
+
+Our computational model predicts endorsement rates given a referent
+prevalence \(p\). Using this model, we can ask quantitatively how well
+prevalence conveyed by a speaker represents the actual, objective
+frequency in the world (e.g., the rate at which a person has smoked
+cigarettes in the past) or a subjective, predictive belief in the head
+(e.g., the rate at which a person is expected to smoke in the future)?
+Such a distinction would support the intuitions about sugarless gum
+residents and could explain why \enquote{Supreme Court Justices have
+even social security numbers} sounds strange even if nine out of the
+nine current justices have even social security numbers (Cohen, 1999):
+Our predictions about the evenness of the \emph{next} justice's social
+security number are driven by strong prior beliefs that selection for
+the Supreme Court is uncorrelated from the numerical properties of one's
+social security number; the current observations are not enough in this
+case to sway those beliefs. We examine this aspect of the theory by
+measuring endorsements of habituals when causal forces intervene on the
+world (e.g., the person buys a pack of cigarettes; Expt. 2C) as well as
+participants' predictions about the likely frequency of the event in the
+future. We then construct habitual endorsement models based on speakers
+aiming to convey the objective, past frequency or their subjective,
+future expectation to try to predict the habitual endorsement patterns.
+
+\hypertarget{experiment-2a-measuring-the-prevalence-prior-for-events}{%
+\subsection{Experiment 2A: Measuring the prevalence prior for
+events}\label{experiment-2a-measuring-the-prevalence-prior-for-events}}
+
+In order to generate model predictions for habitual endorsements, we
+first elicit the prior distributions over rates for different events.
+For language about the behaviors of people, \(P(p)\) represents a
+language user's background knowledge about the rates with which people
+perform a behavior; this prior can be constructed as a distribution over
+\emph{different people}, each of whom do the behavior with a different
+rate. We designed our elicitation task to take advantage of the
+mixture-model representation of the prevalence prior used in Case Study
+1. In particular, we assume, to a first approximation, that the
+distribution over prevalence can be represented as a mixture of those
+who tend to perform the action with a stable rate and those who do not
+perform the action. With the further assumption that, all else being
+equal, past is predictive of future behavior, we operationalize these
+two kinds of people as \emph{people who have done the action before} and
+\emph{people who have not the action before}. We design this experiment
+to measure participants' beliefs about the relative proportion of these
+two kinds of people (as a measure of the mixture parameter in the
+prevalence prior model) as well as the rate at which people (who have
+done the action before) do the action. We will assume for simplicity
+that people who have never done the action before will probably never do
+the action.\footnote{It is likely that more than just these two
+  possibilities are represented in people's intuitive theories,
+  corresponding to individuals with additional traits or demographics,
+  and plausibly influenced by the types of people a speaker knows and
+  interacts with. We assume here a simple two-component structure so as
+  to not make the specification of the prior overly complex.}
+
+\hypertarget{method-2}{%
+\subsubsection{Method}\label{method-2}}
+
+\hypertarget{participants-2}{%
+\paragraph{Participants}\label{participants-2}}
 
@@
 
-\paragraph{Materials}\label{materials}
+\hypertarget{materials}{%
+\paragraph{Materials}\label{materials}}
 
 To construct our stimulus set, we choose actions from five categories of
-typical human behaviors: eating/consuming food and drug, work, wearing
-clothing, entertaining activities, and hobbies. For each category, we
-created pairs or triplets of events that shared a superordinate actions
-(e.g. \emph{writing} poems vs.~novels). The events were chosen to
-intuitively cover a range of likely frequencies. In total, thirty-one
-events were used. For a full list the stimulus set, see Appendix D.
-
-\paragraph{Procedure}\label{procedure}
+typical human behaviors having to do with food and drug, work, clothing,
+entertainment, and hobbies. For each category, we created pairs or
+triplets of events that shared a superordinate action (e.g.
+\emph{writing} poems vs.~novels). The events were chosen to intuitively
+cover a range of likely frequencies. In total, thirty-one events were
+used. For a full list of the stimuli used in Expts. 2A-C, see Appendix
+D.
+
+\hypertarget{procedure}{%
+\paragraph{Procedure}\label{procedure}}
 
@@
 dependent measures. These questions were designed to measure the two
-central components of the prevalence prior model. We anticipated there
-to be different beliefs about the rates and relative proportions of
-peopel depending on whether an actor is male or female, so we asked
-about both genders separately.
+components of the prevalence prior distribution. We anticipated there to
+be different beliefs about the rates and relative proportions of men
+vs.~women, so we asked about both genders separately. The two questions
+were schematically:
 
 \begin{enumerate}
-\item ``How many \{men, women\} have \textsc{done action} before?'' \\
+\item ``How many \{men, women\} have \emph{done action} before?'' \\
 
@@
 
-\item ``For a typical \{man, woman\} who has \textsc{done action}  before, how frequently does he or she \textsc{do action}?''\\
+\item ``For a typical \{man, woman\} who has \emph{done action}  before, how frequently does he or she \emph{do action}?''\\
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/habituals-prior-figure-1.pdf}
-\caption{\label{fig:habituals-prior-figure}Prevalence priors for events
-(Expt. 2a). Left: Mean mixture parameter and mean stable frequency
-parameter for 31 events. Right: Inferred priors on frequencies from the
-structured, prior elicitation task. Priors are reconstructed by forward
-sampling using the inferred parameters in the prior mixture model.}
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/habituals-prior-figure-1} \caption{Prevalence priors for events (Expt.
+2a).
+A: Parameters of prevalence priors for the 31 items in Expt.
+2.
+Items cover much of the range of possible parameter values.
+B: Reconstructed prevalence priors.
+In order to show frequencies for events that are very rare across people (e.g., "writes novels"), extremely low frequencies (\emph{almost never}) are omitted.
+Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.}\label{fig:habituals-prior-figure}
 \end{figure}
 
+\hypertarget{data-analysis-and-results}{%
 \subsubsection{Data analysis and
-results}\label{data-analysis-and-results}
+results}\label{data-analysis-and-results}}
 
@@
 elicits the proportion of people who have done an action before. We
-rescale this to be a number between 0 and 1, and assume it was generated
+rescale this to be a number between 0 and 1, and model it as generated
 from a Beta distribution: \(d_{1} \sim \text{Beta}(\gamma, \xi)\).
@@
 values of the parameters by running MCMC for 100,000 iterations,
-discarding the first 50,000 for burnin.
+discarding the first 50,000 for burn-in.
 
 The priors elicited cover a range of possible parameter values as
-intended (Figure \ref{fig:priorScatter}, scatter): We observe a
+intended (Figure~\ref{fig:habituals-prior-figure}A): We observe a
 correlation in our items between the mean \% of Americans who have
@@
 sentences (e.g., \emph{Sam goes to the movies vs. the ballet.})
-contingent on the shape of the prior distribution.
+contingent on these details of the prior distribution.
 
 To generate prevalence prior distributions, we built a Bayesian
-mixture-model for this prior elicitation task, analagous to that used in
-Case Study 1 (Expt. 1b). The only difference is that we estimate the
+mixture-model for this prior elicitation task, analogous to that used in
+Case Study 1 (Expt. 1A). The only difference is that we estimate the
 mixture component \(\phi\) directly from responses to Question 1. We
@@
 \phi & \sim \text{Beta}(\gamma_{Q1}, \xi_{Q1}) \nonumber \\ 
-\ln h & \sim \begin{cases}
+\ln p & \sim \begin{cases}
         \text{Gaussian}(\mu_{Q2}, \sigma_{Q2}) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
-                \text{Delta}(h=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
+                \text{Delta}(p=0.01) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
         \end{cases}
@@
 
-Figure \ref{fig:habituals-prior-figure} (right) shows example
-reconstructed priors. In addition to specifying the correct way to
-combine our two prior-elicitation questions, using this inferred prior
-resolves two technical difficulties. First, it smooths effects that are
-clearly results of the response format. For example, a very common
-rating for certain events is \emph{1 time per year}. Presumably
-participants would be just as happy reporting \emph{approximately} 1
-time per year (e.g., on average, 1.2 times per year); the raw data does
-not reflect this due to demands of the dependent measure. Second, this
-methodology better captures the tails of the prior distribution (i.e.,
-very frequent or very infrequent rates) which have relatively little
-data and need to be regularized by the analysis.
-
+Figure~\ref{fig:habituals-prior-figure}B shows example reconstructed
+priors. In addition to specifying the correct way to combine our two
+prior-elicitation questions, using this inferred prior resolves two
+technical difficulties. First, it smooths effects that are clearly
+results of the response format. For example, a very common rating for
+certain events is \emph{1 time per year}. Presumably participants would
+be just as happy reporting \emph{approximately} 1 time per year (e.g.,
+on average, 1.2 times per year); the raw data does not reflect this due
+to demands of the dependent measure. Second, this methodology better
+captures the tails of the prior distribution (i.e., very frequent or
+very infrequent rates) which have relatively little data and need to be
+regularized by the analysis. Now that we have modeled the prevalence
+prior data, we see whether our endorsement model can accurately predict
+endorsement rates for habitual sentences about these actions.
+
+\hypertarget{experiment-2b-habitual-endorsements}{%
 \subsection{Experiment 2b: Habitual
-endorsements}\label{experiment-2b-habitual-endorsements}
+endorsements}\label{experiment-2b-habitual-endorsements}}
 
 In this experiment, we elicit human endorsements for generalizations
-about events (\emph{habituals}; e.g., \enquote{Mary smokes cigaerettes})
-while manipulating the frequency with which the referent-event occurs
+about events (\emph{habituals}; e.g., \enquote{Mary smokes cigarettes})
+while manipulating the frequency with which the referent event occurs
 (e.g., how often Mary smokes cigarettes).
 
-\subsubsection{Method}\label{method-3}
-
-\paragraph{Participants}\label{participants-3}
+\hypertarget{method-3}{%
+\subsubsection{Method}\label{method-3}}
+
+\hypertarget{participants-3}{%
+\paragraph{Participants}\label{participants-3}}
 
@@
 
-\paragraph{Materials}\label{materials-1}
-
-Each event from Expt. 2a was then paired with between 2 - 4 frequencies,
-for which the habitual statement would be evaluated. Frequencies were
-always \enquote{3 times every \textsc{time period}} so that the referent
-character had always completed the event multiple times.
-\textsc{time period}s were chosen specific to each event by simulating
-predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of
-maximizing the variability in endorsements across items. For example,
-relatively high frequencies were chosen (e.g., three times every week
-vs.~2 months) for an item that was expected to occur rather often (e.g.,
-\enquote{runs}) because the model predicted that much of the variability
-in endorsement would occur in this range; for an item was expected to
-occur infrequently (e.g., \enquote{climbs mountains}), lower frequencies
-were chosen (e.g., three times every 5 years vs.~2 years). In total, 93
-unique items were created by pairing frequencies with events.
-
-\paragraph{Procedure}\label{procedure-1}
-
-On each trial, participants were presented with a
-\emph{past frequency statement} for a given event of the form:
-\enquote{In the past M \{weeks, months, years\}, \textsc{person}
-\textsc{did x} 3 times}. For example, \enquote{In the past month, Bill
-smoked cigarettes 3 times}. Participants were asked whether they agreed
-or disagreed with the corresponding habitual sentence:
-\enquote{\textsc{person does x}} (e.g.,\enquote{Bill smokes
-cigarettes.}). Participants completed thirty-seven trials, which were
-composed of the thirty-one items from the prior elicitation task
-randomly paired with either a male or female character name. Six of
-these items were then also paired with a name of the opposite gender
-(e.g., participants rated both a female character and a male character
-who drank beer). These were used for an exploratory analysis on
-differences in endorsements by gender of the target character.
-
-\subsubsection{Results}\label{results-2}
-
-Habitual sentences were endorsed for a wide range of frequencies. When
-actions are very infrequent (3 times in a 5-year interval), habituals
-can receive strong agreement (e.g., \emph{writes novels},
-\emph{climbs mountains}). When actions are relatively frequent (e.g., 3
-times in a one month interval), habitual sentences can receive less than
-full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). In
-our data, actions completed with a high frequency (3 times in a one week
+\hypertarget{materials-1}{%
+\paragraph{Materials}\label{materials-1}}
+
+Each event from Expt. 2A was paired with between two to four
+frequencies, for which the habitual statement would be evaluated.
+Frequencies were presented in terms of a character performing the action
+\enquote{three times in the past \emph{time interval}}. We chose to
+always have the character perform the action three times to provide a
+strong test of a baseline hypothesis that the habitual encodes the
+person has done the action several (at least 3) times in the past.
+
+Different time intervals were chosen for each event in order to maximize
+the variability of responses within each item. Specifically, we used the
+endorsement model to generate predictions based on the prior elicitation
+data (Expt. 2A) for each item, and chose between two and four time
+intervals across which maximal variability was predicted. For example,
+relatively high frequencies were chosen (e.g., time intervals of weeks
+and months) for items expected to occur rather often (e.g.,
+\emph{runs}); for an item that was expected to occur infrequently (e.g.,
+\emph{climbs mountains}), lower frequencies were chosen (e.g., time
+intervals of years or longer) because the model predicted that much of
+the variability in endorsement would occur in those respective ranges.
+In total, 93 unique items were created by pairing frequencies with
+events. The full list of items and frequencies can be found in Appendix
+D.
+
+\hypertarget{procedure-1}{%
+\paragraph{Procedure}\label{procedure-1}}
+
+On each trial, participants were presented with a \emph{past frequency
+statement} for a given event of the form: \enquote{In the past \{week, 2
+weeks, month, 5 years, \ldots{}\}, \emph{Person did X} 3 times}. For
+example, \enquote{In the past month, Bill smoked cigarettes 3 times}.
+Participants were asked whether they agreed or disagreed with the
+corresponding habitual sentence: \enquote{Person does X}
+(e.g.,\enquote{Bill smokes cigarettes.}). Participants completed
+thirty-seven trials, which were composed of the thirty-one items from
+the prior elicitation task randomly paired with either a male or female
+character name. Six of these items were then also paired with a name of
+the opposite gender (e.g., participants rated both a female character
+and a male character who drank beer). These were used for an exploratory
+analysis on differences in endorsements by gender of the target
+character.
+
+\hypertarget{results-1}{%
+\subsubsection{Results}\label{results-1}}
+
+The goal of this experiment was to elicit variability in habitual
+endorsements. Consistent with this goal, we found habitual sentences
+were endorsed for a wide range of frequencies. When actions are very
+infrequent (3 times in a 5-year interval), habituals can receive strong
+agreement (e.g., \emph{writes novels}, \emph{climbs mountains}). When
+actions are relatively frequent (e.g., 3 times in a one month interval),
+habitual sentences can receive less than full endorsement (e.g.,
+\emph{wears socks}, \emph{drinks coffee}). In our data, actions
+completed with a relatively high frequency (3 times in a one week
 interval) receive at a minimum 75\% endorsement, though there is still
-variability among them (e.g., between 10-25\% of people disagree with
-\emph{wears a watch} and \emph{wears a bra}). In addition, we observe
-that none of our items receive less than 25\% endorsement (i.e., a
-maximum of about 75\% of participants disagree with the felicity of the
-utterance), reflecting the fact that these statements are not altogether
-\emph{false} even though the action is done very rarely.
-
+variability among them (e.g., between 10-25\% disagree that people who
+wore a watch or wore a bra 3 times in the past week \emph{wear a watch}
+or \emph{wear a bra} habitually). Finally, we observe that none of our
+items receive less than 25\% endorsement (i.e., a maximum of about 75\%
+of participants disagree with the habitual utterances), reflecting the
+fact that these statements are not altogether \emph{false} even though
+the action may be done very rarely.
+
+\hypertarget{endorsement-model-comparison-1}{%
 \subsubsection{Endorsement model
-comparison}\label{endorsement-model-comparison-1}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/habituals-endorsement-figure-1.pdf}
-\caption{\label{fig:habituals-endorsement-figure}Endorsing generalizations
-about events. A: Endorsements for nine events given different
-frequencies of action by human participants and four models. B: Human
-elicited endorsements for ninety-three habitual sentences as a function
-of the referent (log) frequency of action. Top right: Model fits for all
-ninety-three habitual sentences by each model. C: Nine example frequency
-priors and posteriors upon hearing the generalization. These
-distributions are inferred using both data sources from Expts. 2a \&
-2b.}
+comparison}\label{endorsement-model-comparison-1}}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/habituals-endorsement-figure-1} \caption{Endorsing generalizations about events.
+A: Endorsements for nine events given different frequencies of action by human participants and four models.
+B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action.
+Top right: Model fits for all ninety-three habitual sentences by each model.
+C: Nine example frequency priors and posteriors upon hearing the generalization.
+These distributions are inferred using both data sources from Expts.
+2a and 2b.}\label{fig:habituals-endorsement-figure}
 \end{figure}
@@
 six events we anticipated differences by referent-gender:
-\(r(21) = 0.97\) This lack of a difference may be because the felicity
+\(r(21) = 0.97\). This lack of a difference may be because the felicity
 of habitual sentences depends on a comparison to individuals of both
@@
 judgments. Parallel to our analysis of generic language endorsements, we
-articulate a set of simple regression models and an alternative to our
-uncertain-threshold endorsement model. Analyses which use the rate prior
-distribution \(P(p_f)\) (all models except \enquote{referent frequency}
-regression) use a 50\% mixture of the inferred priors for each gender to
-construct a single prior distribution. To model the uncertainty in the
-input measurements, we bootstrap the data for the regression models and
-we construct joint-inference, Bayesian data analytic models for the
-information-theoretic endorsement models (fixed-threshold and
-uncertain-thresold).
-
-\paragraph{Referent frequency}\label{referent-frequency}
+articulate a set of simple regression models and a fixed-threshold
+alternative to our uncertain-threshold endorsement model. Analyses which
+use the prevalence prior distribution \(P(p)\) (all models except
+\enquote{referent frequency} regression) use a 50\% mixture of the
+inferred priors for each gender to construct a single prevalence prior
+distribution. Parallel to our analysis in Case Study 1, we model
+uncertainty in the input measurements by bootstrapping the data for the
+regression models and constructing joint-inference, Bayesian data
+analytic models for the information-theoretic endorsement models
+(fixed-threshold and uncertain-threshold).
+
+\hypertarget{referent-frequency}{%
+\paragraph{Referent frequency}\label{referent-frequency}}
 
@@
 (e.g., 3 times in a month) do not receive full endorsement (e.g.,
-\emph{smokes cigarettes}; Figure \ref{fig:habituals-endorsement-figure}
-A). Overall, the referent-frequency (in log-scale) predicts only a
-fraction of the variability in responses (\(r^2(93) = 0.325\);
-MSE=\(0.0355\)). In addition, for actions that are done on the time
-scale of years or longer (lower median of frequency), referent frequency
-no longer explains endorsements (\(r^2(50) = 0.0662\); MSE =\(0.0477\)).
-The prevalence baseline does appreciably worse in this data set in
-comparison to the generics data set (Case Study 1) because we designed
-the stimulus set to be critical of a referent-frequency model.
-
+\emph{smokes cigarettes}; Figure
+\ref{fig:habituals-endorsement-figure}A). Overall, the
+referent-frequency (in log-scale) predicts only a fraction of the
+variability in responses (\(r^2(93) = 0.325\); MSE=\(0.0355\)). In
+addition, for actions that are done on the time scale of years or longer
+(lower median of frequency), referent frequency no longer explains
+endorsements (\(r^2(50) = 0.0662\); MSE =\(0.0477\)). The prevalence
+baseline does appreciably worse in this data set in comparison to the
+generics data set (Case Study 1) because we were able to independently
+manipulate the referent-frequency separate from the prevalence priors,
+which we could not do for generics about familiar categories.
+
+\hypertarget{distinctiveness-and-referent-frequency}{%
 \paragraph{Distinctiveness and referent
-frequency}\label{distinctiveness-and-referent-frequency}
-
-In our empirically elicited priors, items differ the proportion of
+frequency}\label{distinctiveness-and-referent-frequency}}
+
+In our empirically elicited priors, items differ in the proportion of
 people who have done the action before (the \emph{mixture parameter} of
-the mixture model; Figure \ref{fig:habituals-prior-figure}). This
-mixture parameter is a major contributor to the mean of the prevalence
-prior distribution, and thus is relates to the \emph{cue validity} of a
-particular feature for a particular individual (see Appendix A for a
-derivation of the relationship between the prevalence prior and cue
-validity). Thus, we take this parameter as an index of the
-\emph{distinctiveness} of the action, analagous to \emph{cue validity}
-in the case study of generic langauge. We construct a regression model
-that treats endorsement as a linear combination of frequency and
-distinctiveness information. We use participants' responses to the
-question about the mixture parameter \(\phi\) (i.e., the proportion of
-people who have done the action before) as well as frequency given to
-participants to predict habitual endorsement.
+the mixture model; Figure \ref{fig:habituals-prior-figure}A x-axis).
+This mixture parameter is a major contributor to the mean of the
+prevalence prior distribution, and thus relates to the \emph{cue
+validity} of a particular feature for a particular individual (Appendix
+A). Thus, we take this parameter as an index of the
+\emph{distinctiveness} of the action, analogous to \emph{cue validity}
+in the case of generic language. We construct a regression model that
+treats endorsement as a linear combination of the frequency given to
+participants and participants' responses to the question about the
+mixture parameter \(\phi\) (i.e., the proportion of people who have done
+the action before) as an index of distinctiveness.
 
 This model is able to explain more of the variance in endorsements
-(\(r^2(93) = 0.583\); MSE=\(0.0219\)). It can differentiate events done
+(\(r^2(93) = 0.583\); MSE=\(0.022\)). It can differentiate events done
 with the same frequency (e.g., \emph{writing poems} vs. \emph{novels}, 3
-times in the past 5 years), and increase endorsement of the more rare
+times in the past 5 years) by increasing endorsement of the more rare
 action (\emph{novels}). Still, this model fails to capture fine-grained
-details in endorsment. For example, going to the movies is a relatively
-nondistinctive action (many people do it) and going three times in a
-year is not very frequent, and yet people still strongly endorse the
-habitual \(0.81 [0.69, 0.89]\), while this regression model predicts
-quite lower judgments \(0.41 [0.38, 0.43]\). On the other hand, playing
-the banjo three times in the past two years is not strong evidence for
-the habitual, according to participants \(0.45 [0.33, 0.59]\).
-Nevertheless, because playing the banjo is a distinct skill, the
+differences in endorsement. For example, going to the movies is a
+relatively nondistinctive action (many people do it) and going three
+times in a year is not very frequent, and yet people still strongly
+endorse the habitual (mean endorsement and 95\% CI:
+\(0.81 [0.69, 0.89]\)), while this regression model predicts quite lower
+judgments (\(0.41 [0.41, 0.43]\)). On the other hand, playing the banjo
+three times in the past two years is not strong evidence for the
+habitual, according to participants (\(0.45 [0.33, 0.59]\)).
+Nevertheless, because playing the banjo is a distinctive action, the
 regression model wants to endorse the habitual strongly in this case
-\(0.75 [0.74, 0.76]\).
-
-\paragraph{Fixed-threshold endorsement
-model}\label{fixed-threshold-endorsement-model}
+(\(0.75 [0.75, 0.76]\)).
+
+\hypertarget{lesioned-model-no-vagueness-1}{%
+\paragraph{Lesioned model (no
+vagueness)}\label{lesioned-model-no-vagueness-1}}
 
 We next examine an information-theoretic endorsement model based on a
-fixed-threshold semantics. A fixed-threshold model commits the habitual
-to conveying that a person \emph{does the action with some rate}, and
-the threshold on rates is common to all actions. As in Case Study 1, we
-incorporate this model into a Bayesian joint-inference model to infer
-the fixed-threshold and simultaneously predict both the priors data and
-the endorsement data (for more details on model implementation, see
-Appendix C). We assume the referent-prevalence \(p_{fk}\) being conveyed
-by the endorsement model (Eq. \ref{eq:S1}) is the frequency provided to
-participants (e.g., 3 times in the past year). Additionally, to account
-for statements that would be literally false under this model
-(frequencies that fall below the fixed threshold), we include an
-additional noise parameter, as we did for the fixed-threshold model in
-Case Study 1. To learn about the credible values of the model's
-parameters and generate predictions given those inferred parameter
-values, we collected 2 MCMC chains of 100,000 iterations, discarding the
-first 50,000 iterations for burn in.
+fixed-threshold semantics. This model is identical to the full
+endorsement model, but is lesioned to not have vagueness, or uncertainty
+about the meaning. A fixed-threshold model commits the habitual to
+conveying literally that a person \emph{does the action with some
+frequency}, and that threshold on frequency is the same for all actions.
+As in Case Study 1, we incorporate this model into a Bayesian
+joint-inference model to infer the fixed-threshold and simultaneously
+predict both the priors data and the endorsement data (for more details
+on model implementation, see Appendix C). We assume the
+referent-prevalence \(p\) being conveyed by the endorsement model (Eq.
+\ref{eq:S1}) is the frequency provided to participants (e.g., 3 times in
+the past year). Additionally, to account for statements that would be
+literally false under this model (frequencies that fall below the fixed
+threshold), we include an additional noise parameter, as we did for the
+fixed-threshold model in Case Study 1. To learn about the credible
+values of the model's parameters and generate predictions given those
+inferred parameter values, we collected 2 MCMC chains of 100,000
+iterations, discarding the first 50,000 iterations for burn in.
 
 The data analytic model infers that a low threshold is likely: the
-inferred threshold in units of number of times per year is 0.01 {[}0.01,
-0.37{]}. Compare this with the lowest referent-frequency used in our
-data set: \(0.6\) times per year (3 times every 5 years). Thus, all of
-the utterances evaluated under this fixed-threshold model were literally
-true. As a result, the lowest endorsement this model can apply to an
-utterance is 0.5 (since both the habitual and silence are always true).
-The fixed-threshold model exhibits a small dynamic range of
-endorsements, similar to the referent-frequency model.
-
-A fixed-threshold utterance updates the interpreter model's beliefs
-differentially depending on the item. For instance, it's highly unlikely
-that a random person \emph{climbs mountains} with any non-zero rate;
-thus this model fully endorses \enquote{Mary climbs mountains} even with
-low-frequency (Figure \ref{fig:habituals-endorsement-figure} A).
-However, the model doesn't differentiate doing the same action with
-different frequencies. It is equally true that a person does an action
-\emph{with some frequency} for any frequency greater than zero,
-analogous to how \enquote{some Ks F} is equally true if 20\% or 50\% of
-Ks F.
-
-Finally, the data-analytic model infers that 10\% {[}1, 19{]} of the
-data is noise and that the speaker optimality parameter is 0.77 {[}0.70,
-1.25{]}.
-
-\paragraph{Uncertain-threshold endorsement
-model}\label{uncertain-threshold-endorsement-model}
+Maximum A-Posteriori threshold and 95\% credible interval in units of
+number of times per year is 0.01 {[}0.01, 0.37{]}. Compare this with the
+lowest referent-frequency used in our data set: \(0.6\) times per year
+(3 times every 5 years). Thus, all of the utterances evaluated under
+this fixed-threshold model were literally true. As a result, the lowest
+endorsement this model can apply to an utterance is 0.5 (since both the
+habitual and silence are always true). As a result, the fixed-threshold
+model exhibits a small dynamic range of endorsements, similar to the
+referent-frequency model
+(Figure~\ref{fig:habituals-endorsement-figure}B).
+
+The fixed-threshold habitual updates the interpreter model's prior
+beliefs differentially depending on the item. For instance, because of
+the distinctiveness of \emph{climbs mountains}, the fixed-threshold
+endorsement model fully endorses the habitual (\enquote{Mary climbs
+mountains}) even at a low frequency (Figure
+\ref{fig:habituals-endorsement-figure}A). However, the model cannot
+differentiate among different frequencies of doing the same action,
+because they are all above the truth-functional threshold. It is equally
+true that a person does an action with non-zero frequency for any
+frequency greater than zero, analogous to how \enquote{Some dogs are
+friendly} is equally true whether 20\% or 50\% or 80\% of dogs are
+friendly.
+
+Overall, the fixed-threshold model is able to predict only a fraction of
+the variance in human endorsements (\(r^2(93) = 0.299\);
+MSE=\(0.0369\)). The model does this by inferring that 10\% {[}1, 19{]}
+of the data is noise and that the speaker optimality parameter is 0.77
+{[}0.70, 1.25{]}.
+
+\hypertarget{uncertain-threshold-model-1}{%
+\paragraph{Uncertain threshold
+model}\label{uncertain-threshold-model-1}}
 
@@
 fixed-threshold parameter and no extrinsic noise process). As shown in
-Figure \ref{fig:habituals-endorsement-figure}B, the uncertain-threshold
+Figure~\ref{fig:habituals-endorsement-figure}B, the uncertain-threshold
 endorsement model does a good job of accounting for the variability in
@@
 on the time scale of years or more (\(r^2(50) = 0.903\);
-MSE=\(0.00617\)). Figure \ref{fig:habituals-endorsement-figure}C
-provides insight into how the model achieves this. An interpreter who
-hears a generalization interprets it relative the prior distribution
-over frequencies, which results in different points at which the
-generalization is good statement to assert. Someone who smoked
-cigarettes 3 times last month is not fully someone who \enquote{smokes
-cigarettes}, whereas someone who went to the movies 3 times last month
-more a person who \enquote{goes to the movies}. Only the
-uncertain-threshold model is able to draw this fine distinction.
-
-\subsubsection{Discussion}\label{discussion-1}
+MSE=\(0.00617\)).
+
+Figure~\ref{fig:habituals-endorsement-figure}C provides insight into how
+the uncertain-threshold model is able to match human judgments. The
+endorsement model simulates how an interpreter would understand the
+habitual sentence. A habitual is interpreted relative the prior
+distribution over frequencies, and the comparison between the frequency
+implied by the habitual vs.~staying silent results in different
+frequencies at which the generalization is good to assert. Climbing
+mountains three times in the past year is good evidence that you
+\emph{climb mountains} because it is approximately the frequency that a
+listener would infer given the utterance; going for a hike three times
+in the past year is correspondingly less convincing that you
+\emph{hike}; and if you went for a run three times in the past year, you
+not a person who \emph{runs}. Only the uncertain-threshold model is able
+to draw these subtle distinctions.
+
+\hypertarget{discussion-1}{%
+\subsubsection{Discussion}\label{discussion-1}}
 
@@
 in a way that a fixed-threshold model cannot account for). The
-relationship is not linear (or log-linear), however; habitual
-endorsements vary in complex ways that reflect interpreters' prior
-knowledge about the event in question.
-
-In Expt. 2b, participants were given a statement about how often a
+relationship is not linear, however; habitual endorsements vary in
+complex ways that reflect interpreters' prior knowledge about the event
+in question.
+
+In Expt. 2B, participants were given a statement about how often a
 person has done the action in the past and asked to judge the
@@
 prevalence communicated by a generalization indicate an objective, past
-frequency or a subjective, future expectation? In Expt. 2c, we
+frequency or a subjective, future expectation? In Expt. 2C, we
 investigate this question by teasing apart \emph{past} from
@@
 
+\hypertarget{experiment-2c-what-is-prevalence}{%
 \subsection{Experiment 2c: What is
-prevalence?}\label{experiment-2c-what-is-prevalence}
+prevalence?}\label{experiment-2c-what-is-prevalence}}
 
@@
 expectations? On one hand, speakers can only be certain about what has
-happened in the past. On the other hand, language has a communicative
-function, and it would be useful for speakers to convey their
-predictions of what will be the case in the future.
-
-People can change their behavior abruptly due to a variety of decisions
-and outside events. We introduce these causal events into our minimal
-endorsement paradigm and measure their influence on endorsement. To
-provide the appropriate model-based analysis, participants in one
-condition make a prediction about what will be the case in the future
-(\emph{predictive frequency}). In another condition, participants decide
-whether or not to endorse the habitual sentence (as in Expt. 2b). We
-then compare two uncertain-thresholds models to each other: one which
-uses participants' ratings of \emph{predictive frequency} as the object
-of communication and one which uses the \emph{past frequency} (as was
-done for Expt. 2b).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/habituals-predictive-figure-1.pdf}
-\caption{\label{fig:habituals-predictive-figure}Top left: Predicted
-frequency of event (log-scale) as a function of (log) past frequency and
-condition manipulation (enabling, preventative, and baseline). Top
-right: Human endorsement of habitual sentences as a function of log
-predicted frequency and condition manipulation. Bottom row: Endorsement
-models based on past frequency (left) and measured predictive frequency
-(row).}
+happened in the past. On the other hand, it is important for speakers to
+be able to convey their predictions of what they believe will be the
+case in the future.
+
+People can change their behavior abruptly due to a variety outside
+events (e.g., developing an allergy) or intend to do an action without
+actually completing it (e.g., by making a resolution). We introduce
+these causal events into our experimental paradigm to measure their
+influence on endorsement. To provide the appropriate model-based
+analysis, participants in one condition make a prediction about the
+future (\emph{predictive frequency}). In another condition, participants
+decide whether or not to endorse the habitual sentence (as in Expt. 2b).
+We then compare two uncertain-threshold models: one which uses
+participants' ratings of \emph{predictive frequency} as the referent
+prevalence and one which uses the \emph{past frequency} (as was done for
+Expt. 2B). In addition, we compare to a baseline linear model that uses
+only the \emph{predictive frequency} (no priors) to model endorsement.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/habituals-predictive-figure-1} \caption{A: Example empirical and predicted endorsements for habituals in three conditions.
+B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline).
+C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.}\label{fig:habituals-predictive-figure}
 \end{figure}
 
-\subsubsection{Method}\label{method-4}
-
-\paragraph{Participants}\label{participants-4}
+\hypertarget{method-4}{%
+\subsubsection{Method}\label{method-4}}
+
+\hypertarget{participants-4}{%
+\paragraph{Participants}\label{participants-4}}
 
@@
 Expt. 2b. 120 were assigned to the \emph{predictive frequency} condition
-and 150 were assigned to the \emph{sentence endorsement} condition. The
-experiment took on average minutes (\emph{predictive frequency}) and
-minutes (\emph{sentence endorsement}). Participants were compensated
-\$0.40.
-
-\paragraph{Materials}\label{materials-2}
-
-The events used were a subset of those used in Expts. 2a \& b (21 of the
+and 150 were assigned to the \emph{habitual endorsement} condition. The
+experiment took on average 3.50 minutes (\emph{predictive frequency})
+and 2 minutes (\emph{habitual endorsement}). Participants were
+compensated \$0.40.
+
+\hypertarget{materials-2}{%
+\paragraph{Materials}\label{materials-2}}
+
+The events used were a subset of those used in Expts. 2A \& B (21 of the
 original 31). In addition, we crafted statements that were intended to
@@
 participants only saw the frequencies that led to the most intermediate
-endorsement of the habitual in Expt. 2b. We did not include separate
+endorsement of the habitual in Expt. 2B. We did not include separate
 trials for both male and female names for the select items we did in
-Expt. 2b, since we saw no differences in their endorsements of the
-habitual. See Appendix D for a full list of the enabling and
-preventative information.
-
-\paragraph{Procedure}\label{procedure-2}
-
-The procedure was identical to Expt. 2b except for the inclusion of a
+Expt. 2B, since we saw no differences in their endorsements of the
+habitual. See Appendix D for a full list of the items and frequencies
+used, as well as the enabling and preventative information.
+
+\hypertarget{procedure-2}{%
+\paragraph{Procedure}\label{procedure-2}}
+
+The procedure was identical to Expt. 2B except for the inclusion of a
 second sentence on a subset of trials (\emph{preventative} and
 \emph{enabling} trials). On all trials, participants were presented with
-a \emph{past frequency sentence} (same as Expt. 2b). Additionally,
+a \emph{past frequency sentence} (same as Expt. 2B). Additionally,
 trials either included \emph{preventative} information, \emph{enabling}
-information, or no additional information (identical to Expt. 2b), in
-equal proportions.
+information, or no additional information (identical to Expt. 2B), in
+equal proportions. See Table 2 for example trials.
+
+\begin{table}[ht]
+\centering
+\begingroup\fontsize{9pt}{10pt}\selectfont
+\begin{tabular}{ |p{1in}|p{1.75in}| p{1.75in}|p{1.75in} |}
+  \hline
+{\bfseries Habitual} & {\bfseries Baseline} & {\bfseries Preventative} & {\bfseries Enabling} \\ 
+  \hline
+John smokes cigarettes.
+& In the past month, John smoked cigarettes 3 times.
+& In the past month, John smoked cigarettes 3 times.
+Yesterday, John quit smoking cigarettes.
+& In the past month, John smoked cigarettes 3 times.
+Yesterday, John wanted a smoke and bought a pack of cigarettes.
+\\
+   \hline
+Tina volunteers at soup kitchens.
+& In the past five years, Tina volunteered for soup kitchens 3 times.
+& In the past five years, Tina volunteered for soup kitchens 3 times.
+Yesterday, Tina grew disillusioned with the soup kitchen system and wants nothing to do with it anymore.
+& In the past five years, Tina volunteered for soup kitchens 3 times.
+Yesterday, Tina researched a new soup kitchen in the area and is going to volunteer with them.
+\\
+   \hline
+\end{tabular}
+\endgroup
+\caption{Example stimuli used in Expt. 2c.} 
+\end{table}
 
 In the \emph{predictive frequency} condition, participants were asked
-``In the next \textsc{time window}, how many times do you think
-\textsc{person} does \textsc{action}?'', where the \textsc{time window}
-was the same as given in the \emph{past frequency statement}. In the
-\emph{sentence endorsement} condition, participants were asked if they
-agreed or disagreed with the corresponding habitual sentence (as in
-Expt. 2b).
-
-\subsubsection{Results}\label{results-3}
-
-\paragraph{Predictive frequency}\label{predictive-frequency}
-
-Figure \ref{fig:habituals-predictive-figure} (left) shows the mean
-predicted future rate as a function of the past rate given to the
+``In the next \emph{time interval}, how many times do you think
+\emph{person does action}?'', where the \emph{time interval} was the
+same as given in the past frequency statement. In the \emph{habitual
+endorsement} condition, participants were asked if they agreed or
+disagreed with the corresponding habitual sentence (as in Expt. 2B).
+
+\hypertarget{predictive-frequency-results}{%
+\subsubsection{Predictive frequency
+results}\label{predictive-frequency-results}}
+
+Figure \ref{fig:habituals-predictive-figure}B shows the mean predicted
+future frequency as a function of the past frequency given to the
 participant and the type of causal information given. We observe in the
 baseline condition that future frequency perfectly tracks past frequency
-(\(r(21) = 0.99\)). That is, participants believe if a person smoked
+(\(r(21) = 0.994\)). That is, participants believe if a person smoked
 cigarettes 3 times last month, they will smoke cigarettes 3 times next
 month. This result implies that our model makes identical predictions
-for Expt. 2b whether the referent is past frequency or expected future
-frequency (indicating, as expected, that we must look to the new data to
+for Expt. 2B whether the referent is past frequency or expected future
+frequency (indicating, as expected, that we must look to new data to
 distinguish these models). Critically, we observe the preventative
@@
 increases predicted frequency (Figure
-\ref{fig:habituals-predictive-elicitation} left; blue and green dots).
+\ref{fig:habituals-predictive-figure}B, yellow and purple dots).
 
 We confirm these observations using a linear mixed-effects model,
-predicting the log-transformed responses from the log-transormed past
+predicting the log-transformed responses from the log-transformed past
 frequency and the experimental condition (baseline, preventative,
@@
 analysis, we also include random effects of intercept and condition for
-both participants and items. Confirming our predictions, the
-preventative information led to significantly lower predictions for
-future frequency, relative to the baseline condition (
-\(\beta = -3.18\); \(SE = 0.27;\) \(t = -11.96\) ). There was also
+both participants and items. Confirming that our manipulation worked as
+intended, the preventative information led to significantly lower
+predictions for future frequency, relative to the baseline condition
+(\(\beta = -3.18\); \(SE = 0.27;\) \(t = -11.96\)). There was also a
 tendency for the enabling information to lead to higher predictions for
-future frequency, relative to baseline ( \(\beta = 0.96\);
-\(SE = 0.11;\) \(t = 8.54\) ). Finally, past frequency was a significant
-predictor of predicted future frequency ( \(\beta = 1.01\);
-\(SE = 0.02;\) \(t = 40.80\) ).
-
-\paragraph{Sentence endorsement}\label{sentence-endorsement}
+future frequency, relative to baseline (\(\beta = 0.96\); \(SE = 0.11;\)
+\(t = 8.54\)). Finally, past frequency was a significant predictor of
+predicted future frequency (\(\beta = 1.01\); \(SE = 0.02;\)
+\(t = 40.80\)).
+
+\hypertarget{habitual-endorsement-results}{%
+\subsubsection{Habitual endorsement
+results}\label{habitual-endorsement-results}}
 
@@
 information on endorsements for the habitual sentence (Figure
-\ref{fig:habituals-predictive-figure}B; green points). Still, frequency
---- even predictive frequency --- does not perfectly explain the
-endorsements (\(r^2(63) = 0.518\); MSE = \(4.3\)). When collapsing
+\ref{fig:habituals-predictive-figure}A; white bars). When collapsing
 across items, the Bayesian Maximum A-Posteriori estimate and 95\%
@@
 probabilities per condition are: baseline = 0.85 {[}0.83, 0.87{]},
-enabling = 0.90 {[}0.88, 0.92{]}, preventative = 0.29 {[}0.26, 0.32{]}
+enabling = 0.90 {[}0.88, 0.92{]}, preventative = 0.29 {[}0.26, 0.32{]}.
+Still, frequency --- even predictive frequency --- does not perfectly
+explain the endorsements (\(r^2(63) = 0.518\); MSE = \(4.29\); Figure
+\ref{fig:habituals-predictive-figure}B).
 
@@
 model, we use the mean predictive frequency as the referent-prevalence
-\(p_{fk}\) that the endorsement model (Eq. \ref{eq:S1}) conditions on.
-The past frequency model is constructed using the past frequency
-supplied to participants as the referent-prevalence. We analyze this
-model in the same Bayesian data analysis regime as for our previous
-models. We use the same priors over the parameters as before and learn
-about the posterior distribution by collecting three independent MCMC
-chains of 100,000 iterations (removing the first 50,000 for burn-in).
-Figure \ref{fig:habituals-predictive-figure}C shows the resulting model
+\(p\) that the endorsement model (Eq. \ref{eq:S1}) aims to convey. The
+past frequency model is constructed using the past frequency supplied to
+participants as the referent-prevalence. We analyze this model in the
+same Bayesian data analysis regime as for our previous models. We use
+the same priors over the parameters as before and learn about the
+posterior distribution by collecting three independent MCMC chains of
+100,000 iterations (removing the first 50,000 for burn-in). Figure
+\ref{fig:habituals-predictive-figure}C shows the resulting model
 predictions for the past frequency and the predictive frequency
 endorsement models. Participants' judgments of the habitual statements
-was indeed influenced by the causal manipulations \emph{in the way
-predicted} by the endorsement model that uses the predictive frequency
-as the object of communication (\(r^2(63) = 0.931\); MSE = \(0.00594\)).
-The model based on past frequency does not make different predictions
-for the different causal manipulation conditions and does a poor job at
+was indeed influenced by the causal manipulations in the way predicted
+by the endorsement model that uses the predictive frequency as the
+referent prevalence (\(r^2(63) = 0.931\); MSE = \(0.00594\)). The model
+based on past frequency does not make different predictions for the
+different causal manipulation conditions and does a poor job at
 explaining the endorsements (\(r^2(63) = 0.0334\); MSE = \(0.0833\)).
-
-\subsection{Discussion}\label{discussion-2}
+This result strongly suggests that prevalence represents a predictive
+belief about the future.
+
+\hypertarget{discussion-2}{%
+\subsection{Discussion}\label{discussion-2}}
 
@@
 the rate at which a person does an action, taking into account a naive
-interpreter's prior beliefs about the event (measured in Expt. 2a). Our
+interpreter's prior beliefs about the event (measured in Expt. 2A). Our
 computational model endorses statements that communicate generalizations
 about events with the same sensitivity to context and frequency that
-people exhibit (Expt. 2b \& c). In Expt. 2b, we varied the type of event
+people exhibit (Expt. 2B \& C). In Expt. 2B, we varied the type of event
 and the past frequency with which the person did the action, and found
 graded endorsements of the corresponding habitual sentences. By
-manipulating (rather than measuring) the referent frequency with which a
-person does an action, we showed how alternative models were
-insufficient to account for the gradience in endorsement. In particular,
-a fixed threshold model that has access to the same prior knowledge and
-uses the same information-theoretic decision rule as our
-uncertain-threshold model is unable to make different predictions for
-different frequencies. Only our uncertain threshold model was able to
-precisely account for the wide range of endorsements.
-
-A regression model that takes into the frequency and the
-\emph{distinctiveness} of the action does a reasonable job at explaining
-the variance in this data. We note that this kind of model is merely a
-re-decription of the data (and thus, the behavior of the uncertain
-threshold model), and does not represent a theory of the semantics of a
-generalization. A theory of the semantics of a generalization must
-formalize the truth-conditions of the generalization as well as how
-those truth-conditions relate to endorsement. This is precisely what our
-information-theoretic models do (both fixed- and uncertain-threshold).
-
-In Expt. 2c, we further investigated the nature of the underlying
+manipulating (rather than measuring) the referent frequency, we showed
+how alternative models were unable to account for the gradience in
+endorsement. In particular, we show that prior knowledge in an
+information-theoretic, communicative model is not sufficient to produce
+gradience in endorsement: The fixed-threshold model, which has these
+components, does not make different predictions for different
+frequencies. Only our uncertain threshold model was able to precisely
+account for the wide range of endorsements.
+
+In Expt. 2C, we further investigated the nature of the underlying
 prevalence scale by introducing causal information that enabled and
-preventated future occurences of the action. We used the
+prevented future occurrences of the action. We used the
 empirically-measured predicted future frequency as the object of
@@
 observations) is a better model of habitual endorsements under these
-situations. Predicted prevalence thus captures the infleunce of top-down
-moderators (e.g., intervening causal forces) on endorsement.
+situations. That is, habitual language (and generalization language more
+generally) is fundementally about conveying people's predictive beliefs,
+not what has actually happened.
 
 In these experiments, we introduced participants to novel actors and, by
-doing so, were able to directly manipulate the frequency of a person
-doing the action. The kinds of events we used were familiar to
-participants (e.g., \emph{running}) and thus we measured the prevalence
-priors for those events. In our final case study, we experimentally
-manipulate the prevalence priors, testing their causal influence over
-endorsements. In addition, we further we extend our theory to the
-language of causal relationships.
-
+doing so, were able to directly manipulate the referent frequency. The
+kinds of events we used were familiar to participants (e.g.,
+\emph{running}) and thus we measured the prevalence priors for those
+events. In our final case study, we experimentally manipulate the
+prevalence priors, testing their causal influence over endorsements. In
+addition, we further we extend our theory to the language of causal
+relationships.
+
+\hypertarget{case-study-3-causal-language}{%
 \section{Case Study 3: Causal
-Language}\label{case-study-3-causal-language}
+Language}\label{case-study-3-causal-language}}
 
 Language about causal relationships manifests in generalization. The
-utterance \enquote{Drinking moonshine makes you go blind} relates to
-\enquote{My grandpa's drinking moonshine made him go blind} in a way
-analagous to how \enquote{John smokes} relates to \enquote{John smoked
-yesterday}. We explore this hypothesis in our third case study: causal
-language or \emph{causals} (e.g., \enquote{A causes B}).
+utterance \enquote{Fire causes smoke} relates to \enquote{This fire
+caused this smoke} in a way analogous to how \enquote{John runs} relates
+to \enquote{John ran yesterday}. We explore this hypothesis in our third
+case study: causal language or \emph{causals} (e.g., \enquote{A causes
+B}).
 
 The problem of \emph{causal induction}---knowing that one thing causes
-another----has been studied extensively in human psychology (Cheng,
-1997; Cheng \& Npvick, 1992; Griffiths \& Tenenbaum, 2005, 2009).
-Classically, this is cast as a problem of inducing an unobservable
-relation (\emph{type causation}) from observable events or contingency
-data. We take a different approaching, examining \emph{type causation}
-by the language used to describe it (e.g., \enquote{A causes B}). We
-assume that such language conveys a generalization about \emph{token} or
-\emph{actual causation} (e.g., \enquote{A caused B, in this instance})
-and that our theory of the language of generalizations extends in a
-natural way to describe \emph{causal language}. Ascribing causation to
-an individual event (\emph{token or actual causation}) is itself a
-complex, inferential process (e.g., depending on counterfactual
-reasoning; T. Gerstenberg, Goodman, Lagnado, \& Tenenbaum, 2015), which
-we do not try to model here.
-
-In this paper, we posit thatprevalence priors are a mediating
+another---has been studied extensively in human psychology (Cheng, 1997;
+Cheng \& Npvick, 1992; Griffiths \& Tenenbaum, 2005, 2009). Classically,
+this is cast as a problem of inducing an unobservable relation
+(\emph{type causation}) from observable events or contingency data. We
+take a different approaching, examining \emph{type causation} by the
+language used to describe it (e.g., \enquote{A causes B}). We explore
+the idea that such language conveys a generalization about \emph{token}
+or \emph{actual causation} (e.g., \enquote{A caused B, in this
+instance}) and that our theory of the language of generalizations
+extends in a natural way to describe \emph{causal language}. Ascribing
+causation to an individual event (\emph{token or actual causation}) is
+itself a complex, inferential process (e.g., depending on counterfactual
+reasoning; Gerstenberg, Goodman, Lagnado, \& Tenenbaum, 2015), which we
+do not try to model here.
+
+In this paper, we posit that prevalence priors are a mediating
 representation between abstract conceptual structure and generalizations
@@
 relationship between the prevalence priors and endorsements of
-generalizations about causes. Also, by designing the experiments in the
-domain of causal language, we further demonstrate the generality of our
-theory of communicating generalizations.
-
+generalizations about causes by manipulating the priors.
+
+\hypertarget{experiment-3a-manipulating-prevalence-priors}{%
 \subsection{Experiment 3a: Manipulating prevalence
-priors}\label{experiment-3a-manipulating-prevalence-priors}
-
-In this experiment, we manipulate and measure participants' background
-knowledge in order to check whether or not manipulation of participants'
-background knowledge was successful. Experiment 3b (\emph{causal
-endorsement}) will then follow a mostly-identical experimental
-procedure.
-
-\subsubsection{Method}\label{method-5}
-
-\paragraph{Participants}\label{participants-5}
+priors}\label{experiment-3a-manipulating-prevalence-priors}}
+
+In this experiment, we manipulate participants' background knowledge,
+measuring these beliefs in order to check whether the manipulation was
+successful. Experiment 3B (\emph{causal endorsement}) will then use a
+very similar experimental procedure in exploring causal generalization
+language.
+
+\hypertarget{method-5}{%
+\subsubsection{Method}\label{method-5}}
+
+\hypertarget{participants-5}{%
+\paragraph{Participants}\label{participants-5}}
 
@@
 
-\paragraph{Materials}\label{materials-3}
+\hypertarget{materials-3}{%
+\paragraph{Materials}\label{materials-3}}
 
@@
 different substances to produce an effect (either to make animals sleepy
-or plants grow tall). Our cover stories were constructed so that the
-potential cause could have some plausible intuitive mechanism that could
-give rise to the proprety (e.g., a naturally occurring herb causing
-animals to be sleepy). The two cover stories can be seen in Table
-\ref{tab:causalItems}.
+or make plants grow tall). Our cover stories were constructed so that
+the potential cause could have some plausible intuitive mechanism that
+could give rise to the property (e.g., a naturally occurring herb
+causing animals to be sleepy). The two cover stories can be seen in
+Table 3.
 
 Participants were then shown \enquote{previous experimental results},
-which followed one of four distributions, shown in Figure
-\ref{fig:causals-conditions}. In two of the conditions, participants saw
-results that came from the same underlying distribution. In one of these
-conditions, all causes produced a strong effect (average efficacy
-approximately 98\%; the \enquote{common strong} condition). In the
+which followed one of four distributions represented as a table of
+numbers. In two of the conditions, participants saw results that came
+from a single underlying distribution (\emph{common} conditions). In one
+of these conditions, all causes produced a strong effect (average
+efficacy approximately 98\%; the \emph{common strong} condition). In the
 second of these conditions, all causes produced a weak effect (average
-efficacy approximately 20\%; the \enquote{common weak} condition). The
-two other conditions used distributions in which some experiments
-resulted in either no or very few succeses (i.e., produced 0s or 1s or
-2s), and others that either had strong or weak effects as above. These
-are the \enquote{rare strong} and \enquote{rare weak} conditions.
-
-\begin{table}[]
+efficacy approximately 20\%; the \emph{common weak} condition). The two
+other conditions used distributions in which some experiments resulted
+in either no or very few successes (i.e., produced 0, 1, or 2
+successes), and others that either had strong or weak effects as above.
+These are the \emph{rare strong} and \emph{rare weak} distributions.
+
+\begin{table}[ht]
 \centering
-\label{tab:causalMaterials}
-\resizebox{\textwidth}{!}{
-\begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|}
-\hline
-                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline
+\begingroup\fontsize{9pt}{10pt}\selectfont
+\begin{tabular}{ |p{1.75in}|p{2in}|p{2in} |}
+  \hline
+{\bfseries .} & {\bfseries Plants} & {\bfseries Animals} \\ 
+  \hline
 Cover story & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall.
@@
 Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs.
-\\ \hline
+\\
+   \hline
 Evidence statement & Your team gave fertilizer B to 100 different feps.
@@
 Of those 100 treated, 98 cheebas were made sleepy.
-\\   \hline
+\\
+   \hline
 \end{tabular}
-}
-\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
+\endgroup
+\caption{Cover stories and example evidence statements for the two sets of materials used in Expt. 3} 
 \end{table}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/causalExpt-1.pdf}
-\caption{\label{fig:causalExpt}Overview of Experiment 3. A-C: Results of
-previous experiments are shown one at a time, described in text and
-displayed in a table. One of the results was lost. Participants are
-asked to review previous results once all displayed. B: Prior
-elicitation task: Participants predict the results of the next 5
-experiments. D: Causal endorsement task: Results of previously lost
-experiment are found and participants are asked to evaluate the causal
-generalization.}
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/causalExpt-1} \caption{Overview of Experiment 3.
+A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table.
+One of the results was lost.
+Participants are asked to review previous results once all displayed.
+D: Prior elicitation task: Participants predict the results of the next 5 experiments.
+E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.}\label{fig:causalExpt}
 \end{figure}
 
-\paragraph{Procedure}\label{procedure-3}
-
-Each participant saw only one cover story with one distribution of
-previous experiments (i.e., the experiment was a single trial).
-Participants were told that they were an astronaut-scientist on a
-distant planet trying to figure out how some system works (i.e., how to
-make a certain kind of animal sleepy with different herbs or how to make
-a plant grow tall with different fertilizers). The story for the
-\enquote{sleepy animals} condition read:
+\hypertarget{procedure-3}{%
+\paragraph{Procedure}\label{procedure-3}}
+
+The experiment was a single trial: Each participant saw only one cover
+story with one distribution of previous experiments. Participants were
+told that they were an astronaut-scientist on a distant planet trying to
+figure out how some system works (i.e., how to make a certain kind of
+animal sleepy with different herbs or how to make a plant grow tall with
+different fertilizers). The story for the \emph{sleepy animals}
+condition read:
 
@@
 
-Participants then click a button to show the results of the experiments.
-Experiment results appear one at a time (upon a click), and are
-described in an \emph{evidence statement} (e.g., \enquote{Your team gave
-herb A to 100 different cheebas. Of those 100 treated, 98 cheebas were
-made sleepy.}) as well as displayed in a table showing the number of
+Participants then clicked a button to show the results of the
+experiments, which appeared one at a time in a random order (following a
+particular distribution). Experimental results were also are described
+in an \emph{evidence statement} (e.g., \enquote{Your team gave herb A to
+100 different cheebas. Of those 100 treated, 98 cheebas were made
+sleepy.}) as well as displayed in a table showing the number of
 successes (e.g., \enquote{animals made sleepy}) per number of attempts
-(always 100 per experiment). We described the results of these
-individual experiments using \emph{token-level} causal language (e.g.,
-\enquote{98 cheebas were made sleepy}) to suggest that actual causation
-occurred in these cases.
-
-Participants see the results of eleven \enquote{experiments}, though
-they are told the results of one experiment were lost and a \enquote{?}
-was placed in the table (Figure \ref{fig:causalExpt}). (These lost
-results would be found in the \emph{causal endorsement} task, Expt. 3b).
-After participants viewed the results of the 10 \enquote{experiments}
-(and 1 missing experiment), they are told to review the results of the
-experiments before continuing.
+(always 100 per experiment; Figure \ref{fig:causalExpt}A). We described
+the results of these individual experiments using token-level causal
+language (e.g., \enquote{98 cheebas were made sleepy}) to imply that
+actual causation occurred in these cases. Participants see the results
+of eleven experiments, though they are told the results of one
+experiment were lost and a \enquote{?} was placed in the table (Figure
+\ref{fig:causalExpt}B). (These lost results would be found in the
+\emph{causal endorsement} task, Expt. 3B). After participants viewed the
+results of the 10 experiments (and 1 missing experiment), they are told
+to review the results of the experiments before continuing (Figure
+\ref{fig:causalExpt}C).
 
 Upon clicking the continue button, the table of experiment results is
-removed and participants are told more experiments were conducted.
-Participants were asked to predict the results of the next 5
-experiments. Participants were given 5 slider bars ranging from 0 - 100,
-and asked to predict the next five substances (e.g., herbs M, N, P, Q,
-and R).
-
-After responding, participants then completed an attention check survey
-where they were asked what the team of scientists were investigated
-(choosing a response from a drop-down menu with 12 options) and to input
-one of the numerical results they saw on the previous screen. This
-attention check served to confirm that participants had encoded some
-part of both relevant aspects of the experiment (the domain and the
-frequencies).
-
-\subsubsection{Results}\label{results-4}
-
-20 participants were excluded from the analysis for failing to answer
-both of the attention check questions correctly, leaving a total of 140
-responses for analysis. The distributions that resulted from
-participants predicting the causal efficacy of the new substances are
-shown in Figure \ref{fig:figure-causals}. These distributions nicely
-recapitulate the distributions supplied in the different experimental
-conditions, suggesting that the manipulation does indeed change
-participants' representations of what probabilities are likely to occur
-in each experimental condition. We hypothesize that with the
-distributions altered, endorsements of generalizations will similarly be
-affected.
-
+removed and participants are told that five more experiments were
+conducted that day and asked to predict the results of those experiments
+(Figure \ref{fig:causalExpt}D). Participants were given five slider bars
+ranging from 0 - 100 to rate the number of predicted successes out of
+100 attempts. After responding, participants then completed an attention
+check survey where they were asked what the team of scientists were
+investigating (choosing a response from a drop-down menu with 12
+options) and to input one of the numerical results they saw on the
+previous screen. This attention check served to confirm that
+participants had encoded both relevant aspects of the experiment (the
+domain and the frequencies).
+
+\hypertarget{results-2}{%
+\subsubsection{Results}\label{results-2}}
+
+20 participants were excluded from the analysis for failing to answer at
+least one of the attention check questions correctly, leaving a total of
+140 responses for analysis. The empirically elicited distributions of
+responses were not appreciably different for our two cover stories
+(herbs making animals sleepy, fertilizer making plants grow tall) and
+thus we collapse the data across these two stories. The distributions
+that resulted from participants predicting the causal efficacy of the
+new substances are shown in Figure~\ref{fig:figure-causals}A. As is
+visually apparent, the empirical prevalence distributions differ between
+conditions and nicely recapitulate the distributions supplied in the
+different experimental conditions, suggesting that the manipulation does
+indeed change participants' representations of what probabilities are
+likely to occur in each experimental condition. This diversity is
+important because the model of generalizations predicts differences in
+endorsement---for the same referent prevalence---depending on these
+priors.
+
+\hypertarget{experiment-3b-causal-endorsements}{%
 \subsection{Experiment 3b: Causal
-Endorsements}\label{experiment-3b-causal-endorsements}
-
-In this experiment, we tested whether the manipulated priors of Expt. 3a
+Endorsements}\label{experiment-3b-causal-endorsements}}
+
+In this experiment, we tested whether the manipulated priors of Expt. 3A
 are causally related to the endorsement of causal statements. Most of
-the experimental deisgn was identical to that of Experiment 3a.
-
-\subsubsection{Method}\label{method-6}
-
-\paragraph{Participants}\label{participants-6}
+the experimental design was identical to that of Expt. 3A.
+
+\hypertarget{method-6}{%
+\subsubsection{Method}\label{method-6}}
+
+\hypertarget{participants-6}{%
+\paragraph{Participants}\label{participants-6}}
 
@@
 
-\paragraph{Procedure and materials}\label{procedure-and-materials-2}
-
-The materials were the same as in Experiment 3a, The first part of the
-experimental trial was the same as in Expt. 3a (the table of
-\enquote{previous experiments}; Figure \ref{fig:causalExpt}). Upon
-continuing beyond the first part of the trial, the table of results and
-background story were removed from the screen and the participant is
-told that the results of the \enquote{lost experiment} were found. The
-results are reported to the participant in terms of how many out of 100
-of the attempts were successful. Participants saw 1 of 2 reported
-frequencies: 20\% or 70\% (randomized between-subjects). Participants
-were then asked to judge the causal sentence (e.g., \enquote{Herb X
-makes the animals sleepy}). Partipants responded by either clicking
-\enquote{Yes} or \enquote{No}. After responding, participants completed
-the same attention check as Expt. 3a.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/figure-causals-1.pdf}
-\caption{\label{fig:figure-causals}Endorsing generalizations about causes.
-A: Endorsement model predictions (left) and human elicited endorsements
-(right) for four background distributions and two observed frequencies.
-B: Prevalence prior distributions and interpreter model posteriors upon
-hearing a causal generalization, for the experimentally manipulated
-priors. Vertical lines denote referent-prevalence levels for the causal
-endorsement task. Endorsement mode predictions, interpreter model
-posteriors, and prevalence priors are inferred using both Expt. 3a and
-3b data, following the same Bayesian data analytic approach outlined in
-Appendix C.}
+\hypertarget{procedure-and-materials-2}{%
+\paragraph{Procedure and materials}\label{procedure-and-materials-2}}
+
+The materials were the same as in Expt. 3A.
+
+The first part of the experimental trial was the same as in Expt. 3A
+(the table of \enquote{previous experiments}; Figure
+\ref{fig:causalExpt}A-C). Upon continuing beyond the first part of the
+trial, the table of results and background story were removed from the
+screen and the participant is told that the results of the \enquote{lost
+experiment} were found (the experiment with a \enquote{?} in the
+table).\footnote{We chose to have the scientists report on an earlier
+  \enquote{lost experiment} to suggest a binomial generative process for
+  the experiments wherein the scientists planned to perform 11
+  experiments, as opposed to alternative design wherein an 11th
+  experiment is reported. Such a continuation of the series of
+  experiments could imply a generative model following a geometric
+  distribution where the scientists repeat the experiment until they
+  reach one that is successful.} The results are reported to the
+participant in terms of how many out of 100 of the attempts were
+successful. Participants saw one of two reported frequencies: 20\% or
+70\% (randomized between-subjects). Participants were then asked to
+judge the causal sentence (e.g., \enquote{Herb X makes the animals
+sleepy}) by either clicking \enquote{Yes} or \enquote{No} (Figure
+\ref{fig:causalExpt}E). This allows us to test whether endorsement of a
+causal sentence for a given actual frequency is affected by the causal
+priors induced by our manipulation. After responding, participants
+completed the same attention check as Expt. 3a.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/figure-causals-1} \caption{Endorsing generalizations about causes.
+A: Empirical prevalence prior distributions elicited following prior manipulation cover story (Expt.
+3a).
+B: Endorsement model predictions (left) and human elicited endorsements (right) for four manipulated prevalence prior distributions and two referent prevalence levels.}\label{fig:figure-causals}
 \end{figure}
 
-\subsubsection{Results}\label{results-5}
+\hypertarget{results-3}{%
+\subsubsection{Results}\label{results-3}}
 
@@
 are shown for the different experimentally-manipulated priors and
-frequencies in Figure \ref{fig:causals-endorsement}.
+referent prevalences in Figure~\ref{fig:figure-causals}B.
 
 As predicted by our model, endorsements for a causal statement were
-sensitive to the background distribution of other causes and the causal
-power of the target cause. When many other causes produced the effect
-very reliably (\emph{common deterministic} condition), very few
-participants endorsed the causal statement for a cause with causal power
-of 0.2, and were at chance when the causal power was 0.7 (Figure
-\textbackslash{}ref\{fig:figure-causals-endorsement; top, blue). By
-contrast, when many other causes failed to produce the effect and those
-that did were not very reliable (\emph{rare weak} condition; green in
-figure), at least half of participants endorsed the causal statement for
-a cause with causal power of 0.2, and were at ceiling when the causal
-power was 0.7. The other two conditions (\emph{rare deterministic} and
+sensitive to the referent prevalence of causal events and, critically,
+to the background distribution of other causes. When many other causes
+produced the effect very reliably (\emph{common strong} condition), very
+few participants endorsed the causal statement for a causal frequency of
+0.2, and were at chance when the causal frequency was 0.7
+(Figure~\ref{fig:figure-causals}, blue bars). By contrast, when many
+other causes failed to produce the effect and those that did were not
+very reliable (\emph{rare weak} condition; green in figure), at least
+half of participants endorsed the causal statement for a cause with
+causal prevalence of 0.2, and were at ceiling when the prevalence was
+0.7. The other two conditions (\emph{rare deterministic} and
 \emph{common weak}) led to endorsements intermediate between these two
-conditions. Our model predicted these effects again with strong
+conditions. These effects were predicted by our model with strong
 quantitative accuracy (\(r^2(8) = 0.835\); MSE = \(0.0123\)).
 
-\subsection{Discussion}\label{discussion-3}
-
-In our third case study, we applied our same model to generalizations
-about causal events. In this domain, we succesfully manipulated
-participants' beliefs about the expected prevalence of a causal
-relationship in a domain (Expt. 3a). This was done using both unimodal
-(\emph{common weak}, \emph{common strong}) and bimodal (\emph{rare
-weak}, \emph{rare strong}) distributions. In Expt. 3b, we showed that
-these manipulated priors influenced endorsements of the corresponding
-causal statements. In addition to further demonstrating the generality
-of this theory, these experiments show that the \emph{prevalence prior}
-\(P(h)\) is causally related to endorsements of generalizations in
-language. To our knowledge, these are the first experiments to
-demonstrate how the probabilities of other categories having a feature
-can influence endorsing a generalization about a different category.
+\hypertarget{discussion-3}{%
+\subsection{Discussion}\label{discussion-3}}
+
+In our third case study, we applied our model to generalizations about
+causal events, without any changes. In this domain, we successfully
+manipulated participants' beliefs about the expected prevalence of a
+causal relationship in a domain (Expt. 3A). This was done using both
+unimodal (\emph{common weak}, \emph{common strong}) and bimodal
+(\emph{rare weak}, \emph{rare strong}) distributions. In Expt. 3B, we
+showed that these manipulated priors influenced endorsements of the
+corresponding causal statements. In addition to further demonstrating
+the generality of this theory, these experiments show that the
+prevalence prior \(P(p)\) is causally related to endorsements of
+generalizations in language.
 
@@
 mechanism that could give rise to the property and these causal events
-could have ambiguous causal power associated with them (e.g., it's
+could have ambiguous causal power associated with them (e.g., it is
 plausible that there are herbs that only weakly make animals sleepy and
-it's also plausible that there are herbs that almost deterministically
+it is also plausible that there are herbs that almost deterministically
 make animals sleepy). These two features of the domains make them
-particularly amenable to manipulation. That is, people's abstract
-theories about these domains are flexible enough to permit such
-manipulations.
-
-It's likely that other domain knowledge would interact with the
-experimentally-supplied \enquote{experimental data} to form a hybrid
-belief distribution.\footnote{If this were happening in our domains, we
-  would expect this to show up in the results of Expt. 3a. Participants'
+particularly amenable to manipulation. It is likely that other domain
+knowledge would interact with the experimentally-supplied
+\enquote{experimental data} to form a hybrid belief
+distribution.\footnote{If this were happening in our domains, we would
+  expect this to show up in the results of Expt. 3A. Participants'
   predictions about the likely causal power of new causes would be
@@
 systems (e.g., billiard balls hitting each other) could strongly induce
-near-deterministic notions of causal power, analagous to our
-\enquote{deterministic} priors conditions. Causal systems that
-demonstrate surprising or \emph{a priori} unlikely effects (e.g.,
-liquids melting concrete) could induce rarity about the existence of a
-non-zero causal power, analgous to our \enquote{rare} prior conditions.
-Our theory would predict in these cases that differences in endorsement
-would be attributable to differences in the prevalence prior
-distribution (here: the belief distribution over causal power).
-
-\section{General Discussion}\label{general-discussion}
-
-It is a remarkable fact that so much is learned from ideas expressed
-vaguely in words. Generalizations in language (e.g., \enquote{John
-runs.}, \enquote{Dogs are friendly.}, \enquote{Staring at the sun makes
-you go blind.}) are a premier example of how simple
-statements---statements understood by even the youngest language
-users---can display complex sensitivities to context. We have argued
-that the core meaning of such linguistic expressions is, in fact,
-simple, but underspecified. To our knowledge, this is the first formal
-theory of generalizations in language that makes precise quantitative
-predictions about human behavioral data.
-
-As a formal theory of generalizations in language, we aim to unify
-significant swaths of language that are, on their surface, quite
-different from one another: generalizations about categories, events,
-and causes. We have been able to formalize a unified, core meaning using
-the underlying scale of \emph{prevalence}. We showed that all three
-kinds of generalizations exhibit the same kind of sensitivity to context
-(Expt. 1, 2a \& 2b, 3). Our framework naturally accounts for a number of
-classic examples from the semantics of \emph{generic language} (Expt.
-1). We provide an avenue for top-down moderators on language use, by
-elucidating the scale as defined by a subjective, predictive
-probability, not mere frequency (Expts. 2c \& 2d). Finally, we have
-shown that listeners' prior knowledge about the prevalence of the
-feature in a category is causally related to their endorsement of
-statements of genericity (Expt. 3). In addition to unifying seemingly
-disparate parts of language, this paper provides a theoretical framework
-for asking further questions about genericity, which we outline below
-
-The foremost contribution of our theory is that it is accompanied by a
-formal model, which makes precise quantitative predictions about
-endorsments. The formal Bayesian model provides a clean separation of
-the semantics of a generalization (operationalized in terms of the
-likelihood function) from background, world knowledge (operationalized
-in terms of the prior). This formal separation is key improvement beyond
-previous accounts. Previous accounts have either tried to account for
-context-sensitivity by baking it into the semantics (e.g., Cohen, 1999)
-or positing a semantics that cannot be separated from world knowledge
-(e.g., Leslie, 2008). Our model formalizes both the semantics of
-generalizations and the structure of world knowledge; this separation
-allows us to articulate a route for precise quantitative inlfuence of
-conceptual structure on generic language (c.f., Leslie, 2008). We do
-this without having to posit that conceptual structure and semantics are
-one in the same. This is makes it possible to connect with theories of
-formal semantics as well as applied Natural Language technologies that
-seeks to draw inferences from information conveyed in generalizations in
-text (e.g., Herbelot \& Copestake, 2011).
-
-In the rest of this discussion, we elaborate some key features of the
-theory that warrant future investigation, sketch out arguments for other
-known philosophical puzzles in genericity, and situate our theory with
-respect to extant theories of genericity.
-
-\subsection{A step towards communicating
-generalizations}\label{a-step-towards-communicating-generalizations}
-
-In this paper, we proposed a model for interpreting and endorsing
-generalizations in language by formalizing a simple semantic theory in a
-probabilistic model with structured, prior knowledge. Our pair of models
-can be seen as a special case of a Rational Speech Act model, a rational
-framework of pragmatic language understanding (Frank \& Goodman, 2012;
-Goodman \& Frank, 2016). Our endorsement model, which we use to generate
-predictions for our three case studies, can be seen as a special case of
-a speaker model who can only produce one of two utterances: the
-generalization or silence. Our interpreter model can be seen as a kind
-of \enquote{literal listener}, who does not do any sort of pragmatic or
-communicative reasoning. Our modeling framework could thus naturally be
-extended to more faithful models of pragamtic communication of
-generalizations, to explore when and how people choose to communicate
-their abstract knowledge when they have more options than in a
-two-alternative forced-choice task. The view of our endorsement model as
-a minimal communicative model highlights aspects of our modeling
-approach for further future development.
-
-\subsubsection{The comparison class}\label{the-comparison-class}
-
-Our model of an interpreter, or naive listener, has access to implicit
-statistics of the event or property in question, represented by the
-prior belief distribution over the prevalence \(P(h)\). The prevalence
-priors for a property, event, or cause are constructed by considering
-\emph{other possible} categories having the property, people doing the
-action, or causes producing the effect. Collectively, these other kinds,
-people, or causes form \emph{comparison classes} against which the
-referent-category is evaluated. Thus, the prevalence prior \(P(h)\) is
-constructed with respect \emph{the comparison class} \(C\): \(P_C(h)\).
-
-The existence of comparison classes is uncontroversial in the study of
-\emph{vague} or \emph{underspecified} language (e.g., gradable
-adjectives like \emph{tall} and vague quantifiers like \emph{many};
-Bale, 2011; Solt, 2009). Adult judgments of the felicity of gradable
-adjectives like \emph{tall} or \emph{dark} depend upon fine-grained
-details of the statistics of the comparison class (Qing \& Franke, 2014;
-Schmidt, Goodman, Barner, \& Tenenbaum, 2009; Solt \& Gotzner, 2012) in
-ways directly analagous to the context-sensitivity of the language of
-generalizations explored in this paper. Thus, we conclude generic,
-habitual, and causal language can be seen as a special case of
-\emph{vague language}.
-
-The construction of a comparison class adds another layer of flexibility
-into the use of generalizations in language. Objects can be
-conceptualized and categorized in multiple ways, giving rise to
-multiple, logically-possible comparison classes (e.g., a robin is a
-bird, is an animal, is an object). We have begun doing work
-investigating how pragmatic reasoning can help constrain this open-ended
-problem (Tessler, Lopez-Brau, \& Goodman, 2017). Even if interlocutors
-coordinate on a particular comparison class, they may disagree about the
-prevalences for other \emph{other categories} in the class. That is, our
-model makes the prediction that the acceptance or rejection of the
-statement \enquote{Humans cause global warming} or \enquote{Muslims are
-terrorists} depends upon a speaker's beliefs about how \emph{other
-forces} (e.g., plate tectonics) influence the climate or how often other
-social categories (e.g., neo-nazis) commit acts of terrorism. Indeed, we
-saw in Expt. 3 how the statistics of other causes can influence the
-endorsement of a single generalization (e.g., \enquote{Herb C makes
-animals sleepy}). Understanding how knowledge of the comparison class
-influences language use is an exciting new area for future research in
-the language of generalizations.
-
-\subsubsection{Question under
-discussion}\label{question-under-discussion}
-
-Rational models of communication, of the kind we have developed in this
-paper, are required to make explicit a speaker's assumptions about the
-goal of communication, otherwise known as the Question Under Discussion
-or QUD (Roberts, 1996). We have made a very minimalist assumption, that
-the goal of communication (at least, for purposes of endorsement) is the
-prevalence. However, the choice in constructing a comparison class can
-be thought of as the result of addressing a particular QUD. For example,
-the comparison classes used in our case studies were with respect to the
-target category (\emph{other animals}, \emph{other people}, \emph{other
-possible causes}); thus, our model addresses the implicit QUDs of
-\enquote{\emph{what} has feature?}, \enquote{\emph{who} does action?},
-or \enquote{\emph{what} causes effect?}. Were the QUDs to be reversed
-(e.g., \enquote{what features does category have?}, \enquote{what does
-person do?}, \enquote{what effects does cause bring about?}), the
-comparison classes would need to be constructed with respect to the
-feature (e.g., \emph{other features}, \emph{other actions}, \emph{other
-effects}).
-
-The QUD is thus another layer of flexibility that makes understanding
-generalizations so challenging. The same sentence can be used to address
-multiple QUDs (Krifka, 1995). The statement \enquote{Lawyers care about
-the law.} can be interpreted with a category-wise comparison class
-(i.e., \enquote{Lawyers \emph{(as opposed to doctors, firefighters,
-\ldots{})} care about the law.}; imagine in a pedagogical context) or a
-feature-wise comparison class (i.e., \enquote{Lawyers care about the law
-\emph{(as opposed to justice, doing what's morally right, \ldots{})}}
-e.g., when said sardonically). In this work, we focused on category-wise
-comparison classes for methodological convenience. Future work should
-investigate the feature-wise reading of generalizations, and explore
-what cues listeners adopt for one or the other interpretation.
-
-\subsection{Structured prior
-knowledge}\label{structured-prior-knowledge}
-
-Previous psychological and philosophical work on generics has looked
-beyond prevalence and focused on conceptual distinctions and relations
-(Gelman, 2003; Leslie, 2007, 2008; Prasada et al., 2013). Prasada has
-argued for a distinction between \emph{characteristic} properties (e.g.,
-\enquote{Diapers are absorbent}) and \emph{statistical} properties
-(e.g., \enquote{Diapers are white}). Leslie suggests information that is
-striking (e.g., \enquote{Tigers eat people}) is ecologically useful and
-thus permitted to be a generic. Gelman outlines how generics tend to
-express \emph{essential} qualities that are relatively timeless and
-enduring. Where in the probability-based semantics could such conceptual
-distinctions come into play?
-
-Our approach makes the strong claim that beliefs about predicted
-prevalence are the connective tissue between conceptual knowledge and
-the semantics of generic language. That is, the effect of conceptually
-meaningful differences on generic language is predicted to be mediated
-by differences in corresponding prevalence distributions. Modulations of
-prevalence distributions can occur for multiple reasons (e.g., by
-changing the comparison class) as described in the previous section. We
-found in Expts. 1 \& 2 that conceptually different kinds of properties
-and events gave rise to quantitatively different prevalence priors, even
-while keeping the comparison class fixed. In Expt. 3 we showed that
-these prevalence distributions are causally related to endorsement.
-
-It is natural to ask how prevalence might reflect conceptual knowledge.
-We found that empirical prevalence distributions are structured in a
-mixture-model that plausibly reflects intuitions about causal mechanisms
-underlying different properties; the differences in shape of these
-distributions in turn led to variable endorsements of generalizations.
-It is plausible that richer conceptual knowledge also influences these
-distributions, such as higher-order conceptual knowledge about the
-nature of properties and categories (Gelman, 2003; Keil, 1992). Indeed,
-conceptual structure in general, including higher-order abstractions,
-can be captured by probabilisitic causal models (Gopnik, 2003; Pearl,
-1988) and their generalization in probabilistic programs (Goodman,
-Tenenbaum, \& Gerstenberg, 2015). Future work will be needed to explore
-whether probabilistic representations of conceptual knowledge can
-capture the relations identified in other accounts of generics (such as
-principled, essential, and striking properties), and whether the effect
-of these relations can then be adequately described via their impact on
-prevalence priors.
-
-\subsection{Communicating predictive
-probabilities}\label{communicating-predictive-probabilities}
-
-This paper puts forth the theory that the language of generalization
-communicates predictive probabilities from speaker to hearer. In
-previous accounts, prevalence is treated as synonymous with the
-frequency of the feature in the category. We make the important
-distinction that probability can be more general than frequency, and in
-our account, underlies speakers' subjective, predictions about the
-future and is subject to top-down moderator. Expts. 2c \& 2d that showed
-using participants' \emph{predictions} about the future as the object of
-communication in our formal model perfectly tracked habitual
-endorsement, when the present frequency would make the wrong prediction.
-
-Communicating probabilities might seem contrary to a basic tenet in
-cognitive psychology, that human cognition falls short when reasoning
-about probabilities (Tversky \& Kahneman, 1974). Our theory suggests
-that the problems with understanding probabilities observed in classic,
-cognitive psychology paradigms are a problem in understanding the
-\emph{language used} to convey \emph{explicit probabilties} (cf.,
-Levinson, 1995). Rather than conveying \emph{explicit probabilities},
-generalizations we argue convey \emph{implicit probabilities}, which are
-easier to understand and quite useful for statistical reasoning. Given
-the relationship to \emph{vague language} (described above), we argue
-that the utterance \enquote{70\% of birds fly} is analagous to saying
-that \enquote{John is 6'3}\enquote{, while saying}Birds fly" is more
-similar to saying \enquote{John is tall}. The latter statements are
-easier to process, understood at an earlier age, and may be more useful
-for human reasoning. Indeed, young children are actually quite good
-about reasoning about probabilities, but in ways that are not explicit
-or tied to language (Dewar \& Xu, 2010; Gweon, Tenenbaum, \& Schulz,
-2010).
-
+near-deterministic notions of causality, analogous to our \emph{strong}
+priors conditions. Causal systems that demonstrate surprising or \emph{a
+priori} unlikely effects (e.g., liquids melting concrete) could induce
+rarity about the existence of a non-zero causal power, analogous to our
+\emph{rare} prior conditions. Our theory would predict that differences
+in endorsement in these cases would be mediated by differences in the
+corresponding prevalence prior distributions.
+
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
+
+The human species is remarkable not only because we can extract useful
+generalizations from observations of the world, but because we can
+convey these generalizations to each other succinctly using language.
+Generalizations expressed in language (e.g., \enquote{John runs.},
+\enquote{Dogs are friendly.}, \enquote{Fire causes smoke.}) are a
+premier example of how simple statements---statements understood by even
+the youngest language users---can convey rich meanings and display
+complex sensitivities to context. We have argued that the core meaning
+of such linguistic expressions can be understood by three ingredients:
+Probability, vagueness, and context. That generics are vague does not
+preclude them from being treated by formal models. A vague threshold
+meaning operating over a speaker's inductive beliefs, formalized by
+predictive probability, leads to complex, quantitative interactions with
+background knowledge, which closely tracks human judgments.
+
+We tested this theory by exploring its implications for the simplest
+judgments a person can make about a sentence: an endorsement or truth
+judgment. Truth judgments are the standard measurement for semantic
+theories, but are often limited to the intuitions of a single or a small
+handful of trained theorists, often producing only binary or ternary
+judgments (i.e., true, false, and possibly indeterminate). Our model
+accounted for these standard linguistic intuitions about a number of
+philosophically puzzling generic statements (Worked Examples). We went
+beyond intuitions, however, measuring truth judgments of naive language
+users, which revealed substantial gradience in endorsements. These
+fine-grained, quantitative measurements pose real challenges for verbal
+theories of generics, which can only predict qualitative differences.
+The framework we propose is sufficiently precise to predict quantitative
+gradience, and we showed that the gradience in truth judgments depends
+in systematic ways on an interpreter's prior beliefs about prevalence.
+We provided strict tests of our formal model by both measuring and
+manipulating listeners' background knowledge as well as comparing our
+model to a number of alternatives. In each case, our model provided a
+strong quantitative fit to human judgements while other models fell
+short.
+
+The fact that our model applies equally as well to generic and habitual
+language sheds light on a long-attested relationship. The analogy of
+habituality (e.g., \enquote{John runs}) and genericity (e.g.,
+\enquote{Dogs have four legs}) has typically been assumed in the
+literature following the original suggestion by Carlson (1977). The
+relationship, however, has been never been empirically tested nor
+formally described. This paper presents the first empirical evidence
+that the reasoning involved in understanding generic and habitual
+sentences are similar: The same uncertain threshold mechanism operating
+over prior beliefs explains judgments of both kinds of statements
+(Expts. 1 \& 2).
+
+In our model, an utterance conveying a generalization updates a
+listener's \emph{a priori} beliefs about the prevalence of the property
+for that category. Since the prevalence prior includes the information
+necessary to compute cue validity (see Appendix A), the cue validity of
+the feature for the new category is added to the common ground between
+interlocutors. Thus, given the knowledge represented in a prevalence
+prior, generics communicate information both about the prevalence of the
+feature in the new category (via the literal semantics) as well as the
+cue validity of the feature for the new category. For example, if a
+listener hears \enquote{Alligators grow to be 10-feet long}, they will
+update their personal beliefs both about the prevalence of 10-footedness
+among alligators as well as the probability that an animal is an
+alligator given that it is 10 feet long. To our knowledge, this is the
+first theory of generics that describes how the informational
+contribution of a generic relates to cue validity.\footnote{We are
+  grateful to an anonymous reviewer for drawing our attention to this. }
+This also means that our computational framework makes predictions about
+the cue validity implied by different generalizations, without any
+further assumptions.
+
+We propose that the language of generalization conveys predictive
+probabilities. Communicating probabilities might seem contrary to the
+long attested failures in reasoning about probability (Tversky \&
+Kahneman, 1974). Our theory suggests that the problems with
+understanding probabilities observed in classic, cognitive psychology
+paradigms are a problem in understanding explicit probabilities
+expressed using \emph{numerical language}, a historically quite recent
+innovation (cf., Levinson, 1995). Rather than conveying probabilities
+explicitly, the language of generalization conveys them implicitly. In
+other words, we argue that the utterance \enquote{70\% of birds fly} is
+a precise statement about how many birds fly in the way that
+\enquote{John is 6'3}" is a precise statement about the height of John,
+whereas \enquote{Birds fly} is a vague statement more akin to the
+utterance \enquote{John is tall}. The latter statements are easier to
+process, understood at an earlier age, and may be more useful for human
+reasoning. Indeed, even infants are actually quite good with reasoning
+about probabilities, but in ways that are not explicit or tied to the
+numerical language of probability (Xu \& Denison, 2009; Xu \& Garcia,
+2008).
+
+In the rest of this discussion, we further discuss the contribution of
+our modeling framework to empirical and theoretical work on the language
+of generalization, elaborate further on the role of conceptual knowledge
+in our modeling framework, describe how our model relates to language
+understanding more generally including theories of vagueness, and sketch
+an argument for how our formal representation of the language of
+generalization could provide a relatively simple acquisition problem for
+a language learner.
+
+\hypertarget{generics-and-genericity}{%
+\subsection{Generics and genericity}\label{generics-and-genericity}}
+
+The statistical vs.~conceptual distinction for theories of generics,
+described in detail earlier in this paper, is roughly co-extensive with
+the distinction between theories of the truth conditions of generics and
+the mental phenomenon of \emph{genericity}, respectively (Nickel, 2016).
+Truth conditions are unified criteria that all generics must satisfy in
+order to be true. \emph{Genericity}, on the other hand, is thought to be
+a non-linguistic, psychological phenomenon previously explained either
+in terms of pragmatics (Declerck, 1991) or meta-semantics (Leslie, 2007;
+Liebesman, 2011; Nickel, 2016; Sterken, 2015). A full account of generic
+language must include both a theory of generics (i.e., truth conditions)
+and a complementary theory of genericity (Nickel, 2016).
+
+Our model leverages the insights of formal semantics and computational
+cognitive modeling to articulate how an agent should update their
+beliefs based on a generic sentence. The Bayesian model provides a clean
+separation of the semantics of a generalization (represented formally by
+a threshold function) from world knowledge (represented by the
+prevalence prior). We, thus, chart-out a single answer to the semantic
+question \enquote{what do generics mean?}, while also formalizing how
+background knowledge influences generic understanding (a question about
+genericity). Previous theoretical accounts have either aimed to account
+for the context-sensitivity of generics by positing distinct semantic
+constructs (e.g., \emph{relative} vs \emph{absolute} generics; Cohen,
+1999) or positing a semantics that cannot be separated from world
+knowledge (Leslie, 2008). The modeling approach we take here
+demonstrates how the context-sensitivity of generics can emerge via the
+interplay of a stable (but vague) semantics and diverse background
+knowledge. This model is thus the first step towards unifying conceptual
+approaches to genericity with an inherently quantitative natural
+language semantics for generics.
+
+\hypertarget{relation-to-intuitive-theories}{%
+\subsection{Relation to intuitive
+theories}\label{relation-to-intuitive-theories}}
+
+Our theory assumes that listeners and speakers employ real-world
+knowledge of objects and events in order to use and interpret
+generalizations. It is this real-world knowledge (presently formalized
+in terms of a prevalence prior) where issues about domain specific
+beliefs, interpretation of properties (Prasada \& Dillingham, 2006),
+over-hypotheses (Leslie, 2008), and essentialism (Gelman, 2003) can all
+play a role. We hypothesize that all of this knowledge feeds into
+participants' predictions, measured through judgments about prevalence.
+That is, even though our underlying semantics is defined in terms
+prevalence of individual properties, this does not imply that the
+concepts involved in generic language understanding are defined merely
+by their properties. Instead, complex intuitive theories (that may
+reflect, for example conceptual role, see Goodman et al., 2015) give
+rise to prevalence priors, which then yield generic judgements. This
+framework, thus, brings precision and clarity to the \emph{output} of
+these cognitive processes and conceptual understanding: intuitions about
+prevalence. Applying the same precision and clarity to the more abstract
+aspects of conceptual knowledge including property knowledge,
+essentialism, etc. is an important next step for this line of work.
+Probabilistic causal models (Gopnik, 2003; Pearl, 1988) and their
+generalization in probabilistic programs (Goodman et al., 2015) are
+obvious starting places to look for such a formalism for conceptual
+structure and higher-order abstractions.
+
+The fact that conceptual knowledge is not a part of our formal semantics
+does not imply that such knowledge is unrelated to communicating
+generalizations. In fact, we saw in Expt. 2C that it was participants
+predictions about the future that led to the prevalence computation
+involved in the endorsement decision. Intuitive theories guide these
+predictions, and might provide new insight into classic puzzles of
+generics. We described in the Worked Examples how our model treats
+\enquote{Supreme Court Justices have even social security numbers} as
+infelicitous even when 100\% of justices have even SSNs, because a
+speaker's subjective probability that the \emph{next justice} would have
+an even SSN is likely 50\%. However, were we to learn much more
+surprising information---for instance, if every Supreme Court Justice in
+U.S. history had a social security number which was a \emph{prime
+number} (a much lower probability outcome)---the shear suspiciousness
+could compel an observer to revise their theory of the domain (appealing
+perhaps to a conspiracy), update their subjective probability of future
+instances, and endorse such a generic.
+
+Not only does conceptual knowledge influence interpretation via beliefs
+about prevalence, but conceptual knowledge may very well be what a
+speaker intends to communicate. Like other models in the probabilistic
+pragmatics tradition, our model distinguishes the relevant variables for
+the truth-functional semantics (e.g., a threshold and a prevalence) from
+those that impact the speaker's utility in producing the utterance. A
+speaker's utility comes from addressing an implicit goal of
+communication, sometimes referred to as the \emph{Question Under
+Discussion} or QUD (Roberts, 1996). The separation of the QUD from the
+literal, truth-functional denotation of the utterance is an important
+theoretical distinction made explicit in our formal modeling approach
+(Goodman \& Frank, 2016). For simplicity, the model presented here
+assumes the QUD is about prevalence. However, the model makes nearly
+identical predictions if the QUD concerns abstract parameters of the
+prevalence distributions (e.g., if the speaker intends to convey that
+``K is the kind of thing that Fs''; cf., Prasada \& Dillingham, 2006),
+something much closer to communicating conceptual understanding. This
+observation may prove useful for constructing models of speakers whose
+goals are to convey abstract relations between kinds and properties.
+
+Conceptual knowledge concerning the strikingness or dangerousness of
+properties and their relation to generic language has been of particular
+interest to psychologists and philosophers since Leslie (2007). We
+described before that the strikingness of certain properties plausibly
+influences prevalence priors or a speaker's predictions about future
+prevalence. We have collected pilot data suggesting these constructs are
+indeed altered as a result of introducing information about the
+dangerousness of features to participants (e.g., as in Cimpian et al.,
+2010). More empirical work is needed to understand whether and how
+strikingness influences generic understanding above and beyond the
+probabilistic constructs we have posited in our theory.
+
+\hypertarget{the-comparison-class}{%
+\subsection{The comparison class}\label{the-comparison-class}}
+
+The probabilistic communicative model we introduce in this paper assumes
+shared background knowledge about the statistics of an event or property
+in question, represented by the prior belief distribution over the
+prevalence \(P(p)\). We constructed prevalence priors for a property,
+event, or cause by considering other possible categories having the
+property, people doing the action, or causes producing the effect,
+respectively. In Expt. 3, we empirically demonstrated the influence of
+other categories on endorsements of generalizations. Collectively, these
+other kinds, people, or causes form \emph{comparison classes} against
+which the referent-category is evaluated. Thus, the prevalence prior
+\(P(p)\) is actually a conditional distribution constructed with respect
+to some comparison class \(C\): \(P(p \mid C)\).
+
+In this paper, we have assumed particular values of \(C\) for our three
+case studies (\emph{animals}, \emph{people}, and \emph{possible causes},
+respectively). We think the choice of these classes is intuitive, but it
+is a limitation of this work that we do not derive these choices from
+more general information-theoretic considerations. The problem of
+choosing a comparison class, however, is not unique to the language of
+generalization, but is a problem for any theory of \emph{vague} or
+\emph{underspecified} language (e.g., gradable adjectives like
+\emph{tall} and vague quantifiers like \emph{many}; Bale, 2011; Qing \&
+Franke, 2014; Schmidt, Goodman, Barner, \& Tenenbaum, 2009; Solt, 2009;
+Solt \& Gotzner, 2012). We have begun to explore how pragmatic reasoning
+and world knowledge can flexibly adjust the comparison class to
+appropriately suit the context (e.g., how a ``short'' basketball player
+is \emph{short for a basketball player} while a ``tall'' basketball
+player is \emph{tall for a person}; Tessler, Lopez-Brau, \& Goodman,
+2017). It remains to be seen how such principles could operate on richly
+structured, hierarchical knowledge about categories and properties that
+would be important for interpreting generic language.
+
+The employment of comparison classes in our model provides additional
+flexibility towards modeling different communicative goals. The
+comparison classes used in our case studies were constructed with
+respect to the category (\emph{other animals}, \emph{other people},
+\emph{other possible causes}). Thus, our endorsement model assumes that
+the QUD was \enquote{\emph{what} has this feature?}. Any part of a
+sentence, however, can be brought into focus (e.g., by prosody) and
+turned into an answer to a QUD: \enquote{\emph{Dogs} have four legs} (as
+opposed to other animals), \enquote{Dogs \emph{have} four legs} (as
+opposed to eating or doing other things with four legs), \enquote{Dogs
+have \emph{four} legs} (as opposed to two legs, three legs, six legs),
+\enquote{Dogs have four \emph{legs}} (as opposed to having four of other
+limbs/body parts), \enquote{Dogs \emph{have four legs}} (as opposed to
+having other features). It has long been noted that the same
+generalization can be used to address multiple QUDs (Krifka, 1995), and
+we posit that differences in interpretation are the result of multiple
+distinct comparison classes competing for influence. Prosody provides a
+good cue towards resolving the comparison class, and pragmatic reasoning
+is likely relevant here as well (Declerck, 1986; Tessler et al., 2017).
+In this work, we focused on category-wise comparison classes purely for
+methodological convenience. Future work should investigate the factors
+that give rise to feature-wise interpretations of generalizations (e.g.,
+\enquote{Dogs \emph{have four legs}}, as opposed to having other
+features), other QUDs generics can address, how the relevant comparison
+classes are constructed, and how these inferences interact with
+threshold inference.
+
+\hypertarget{genericity-and-vagueness}{%
+\subsection{Genericity and vagueness}\label{genericity-and-vagueness}}
+
+We have argued that the language of generalizations are vague
+descriptions of prevalence in a way analagous to how gradable adjectives
+like \enquote{tall} are vague descriptions of some underlying degree
+scale (e.g., height). Vague predicates like \enquote{tall}, however,
+exhibit a number of additional phenomena that we do not suppose generics
+or generalizations would necessarily exhibit. For example, vague
+predicates admit borderline cases (e.g., a person who is neither tall
+nor not tall). \emph{A priori}, it is unclear whether one could
+construct borderline cases with generics or habituals without sounding
+like a contradiction (e.g., \enquote{John both runs and doesn't run}).
+Additionally, sorites paradoxes can be constructed out of arguments
+using vague predicates, and it is not clear that generics or habituals
+could be used to construct such arguments. No experimental data yet
+bears on these ideas, but would be useful for further understanding the
+relationship between generalizations and vague predicates.
+
+For now, we understand both genericity and vagueness as analogous
+linguistic phenomena insofar as they can both be thought of as the
+result of a listener being uncertainty as to the exact truth conditions
+(e.g., an uncertain threshold). This sort of \enquote{lexical
+uncertainty} is a kind of \emph{parameter learning} problem (e.g., the
+listener knows the form of the truth conditions, but not the values of
+some variables) which can be formally distinguished from other sorts of
+uncertain truth conditions better modeled as a \emph{structure learning}
+problem (e.g., lexical ambiguity). Further work should be done to better
+understand the kinds of context-sensitive linguistic phenomena that are
+modeled as parameter vs.~structure learning problems to construct a
+richer typology of underspecified linguistic expressions.
+
+Our view of understanding generalizations involving reasoning about an
+uncertain threshold is reminiscent of Williamson and Simons (1992)'s
+epistemicist view on vagueness. This view holds that when a speaker
+utters a vague statement, there exists an objective set of criteria
+determining whether the entity in question satisfies the vague predicate
+(i.e., whether or not the utterance is true). Vagueness emerges from
+uncertainty about the details of those objective criteria (e.g., the
+precise value of a threshold). This uncertainty in turn could be the
+result of a population of speakers using slightly different criteria.
+Listeners then will not know exactly what kind of speaker they are
+dealing with \emph{a priori} and normatively should maintain uncertainty
+about the truth conditions (see Lassiter \& Goodman, 2015 for an
+extended discussion of vagueness involving resolving the value of a free
+semantic variable in context).
+
+\hypertarget{acquiring-the-language-of-generalization}{%
 \subsection{Acquiring the language of
-generalizations}\label{acquiring-the-language-of-generalizations}
-
-The linguistic outlet for generalizations about categories---so called,
-\emph{generic language}---has received tremendous attention from
-psychologists, linguists, and philosophers. Generic language is one of
-the earliest emerging forms of complex, compositional language.
-Somewhere between two and three years of age, children recognize that
-generics convey a generalization about a category, not directly tied to
-concrete instances in a scene (Cimpian \& Markman, 2008). Generics are
-common in child-directed and child-produced speech (Gelman, Coley,
-Rosengren, Hartman, \& Pappas, 1998; Gelman, Taylor, Nguyen, Leaper, \&
-Bigler, 2004) and are believed to be central to the growth of conceptual
-knowledge (Gelman, 2004),
-
-What is perhaps surprising from a formal perspective is that generic
-language is far from trivial to characterize. If generics convey
-something about the probabilty of a feature, we would expect them to be
-in some way comparable to quantifier statments (e.g., \enquote{some},
-\enquote{most}, \enquote{all}, \ldots{}). The extreme flexibility of
-generic meaning (e.g., \enquote{Birds lay eggs} vs. \enquote{Birds are
-female}) stands in stark contrast to its early emergence in development.
-In fact, quantified statements, whose formal meaning is much more
-straight-forward (e.g., \enquote{Some} means more than zero), emerge
-\emph{later} in development (Brandone, Gelman, \& Hedglen, 2014; Gelman,
-Leslie, Was, \& Koch, 2015), and are often confused for generic
-statements (Leslie \& Gelman, 2012). This has led some to conclude that
+generalization}\label{acquiring-the-language-of-generalization}}
+
+Perhaps the most surprising aspect of the language of generalization is
+how difficult it is to formalize, given how common it is in
+child-directed and child-produced speech (Gelman, Coley, Rosengren,
+Hartman, \& Pappas, 1998; Gelman et al., 2004). Generics are often
+contrasted with quantifier language (e.g., \enquote{some},
+\enquote{most}, \enquote{all}), whose truth conditions are easy to
+formalize but which pose difficulty for young children to acquire
+(Brandone, Gelman, \& Hedglen, 2014; Gelman et al., 2015). Leslie (2008)
+argues that the necessary complexity of a formal account of generics and
+the simplicity with which young children acquire generics implies that
 the normal tools for describing the semantics of quantified utterances
-(i.e., a truth-functional threshold) is not approrpriate for generic
-language (Leslie, 2008).
-
-We think rejecting the normal tools of truth-functional semantics for
-generics would be throwing out the baby with the bathwater. When we
-consider the acquisition problem, there are three aspects of meaning
-that a child must acquire for a truth-functional quantifier semantics
-\(\denote{u}(h, \theta) = \{h :h > \theta\}\): (1) the dimension being
-described (i.e., the probability \(h\)), (2) the polarity of the
-relation (i.e., \(>\) vs. \(<\)), and (3) the value of the threshold
-(e.g., \(\theta = 0\) for \enquote{some}, \(\theta = 0.5\) for
-\enquote{most}). Upon learning the meaning has to do with probability
-and that it stands in a positive relation to some standard \(\theta\), a
-rational learner would adopt a prior distribution over possible
-thresholds \(\theta\), as a form of \emph{lexical uncertainty} (Bergen,
-Levy, \& Goodman, To appear). This prior could then be updated with more
-data to acquire a fixed meaning. However, for the generic statement, the
-language learner is done once she acquires aspects (1) and (2). In our
-model, \(\theta\) is left underspecified in the semantics and is
-inferred in context. Thus, in this sketch of an acquisition model, a
-child would first acquire generic language, and from that, carve out
-more precise meanings for quantified language.
-
-The uniform prior over the threshold \(\theta\) in the truth-functional
-threshold semantics (as we have assumed in our model) provides a
-secondary argument for why acquiring our semantics for generics should
-be easy. Uniform uncertainty over values in the unit interval \([0, 1]\)
-for threshold \(\theta\) in a threshold-function is mathematically
-equivalent to a \emph{soft semantics} wherein the degree to which the
-utterance is true is proportional to the prevalence \(h\) \emph{itself}:
-
-\[
-\int_{0}^{1} \delta_{h > \theta} \diff \theta =  h
-\] This \emph{soft semantics} (corresponding intuitively to a meaning
-like \enquote{the higher the probability, the better the utterance}, or
-simply \enquote{more is better}) is perhaps the simplest semantics one
-could imagine. The difficulty in acquiring the meaning of quantifiers is
-then a difficulty in recognizing a fixed-threshold semantics as a
-special case of this \emph{more is better} semantics. We leave for
-future work the precise implementation of the acquisition model we
-sketch out here.
-
-\subsection{Other philosophical
-puzzles}\label{other-philosophical-puzzles}
-
-In our experiments, we have tried to include classic, philosophically
-puzzling examples of generalizations in language in addition to crafting
-novel stimuli that provide stricter tests of the main hypothesis. In
-this section, we consider some other previously-discussed troubling
-examples of generalizations and sketch out arguments rooted in our
-theoretical framework to demonstrate how our theory could account for
-these cases. We consider the five following examples:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Books are paperbacks.
-\item
-  Mary handles the mail from Antarctica.
-\item
-  Supreme Court Justices have even social security numbers.
-\item
-  Elephants live in Africa and Asia.
-\item
-  Women are submissive.
-\end{enumerate}
-
-Sentence (1), strikes hearers as \emph{odd} or perhaps \emph{false},
-despite the vast majority of books being paperback. Why? A first
-observation is that the sentence is constructed by pairing a category
-(\enquote{Books}) with a property that describes a strict subset
-(\enquote{paperbacks} is short-hand for \enquote{paperback books}). We
-expect intuitions about this statement to generalize to other examples
-expressing an analogous relation (e.g., \enquote{Pastas are spaghetti},
-\enquote{Animals are humans}). We hypothesize that the strangeness of
-these examples has to do an inflexible relationship between the
-comparison class and the referent-prevalence. Assume that the comparison
-class is constructed by considering the \emph{predicability} of the
-property (in the sense of Keil, 1979, originally from Sommers
-(1963)).\footnote{Note that this assumption is consistent with the
-  comparison classes we have assumed in our three case studies.} Then,
-\enquote{is a paperback} can only be informatively said of individual
-books, because these are the only objects that can plausibly have the
-property; that is, world knowledge gives us that an elephant cannot be
-predicated (either true or falsely) by the property \enquote{is a
-paperback.}\footnote{Note that this idea is similar to Cohen (1999)'s
-  notion of \enquote{Relative generics}, which have truth conditions
-  that are determined by a comparison to an alternative set of Ks (his
-  Alt(K), our comparison class) which is composed of Ks that could
-  satisfy some F in an an alternative set of Fs.} The relevant
-aggregations of entities, then, are collection of books, potentially
-including books of different genres or publication eras among other such
-sub-categories. Then, given that \enquote{books} is the superordinate
-category of \enquote{kinds of books}, the referent-category prevalence
-cannot be different from the mean of the prevalence prior. Finally,
-given this prevalence prior and the referent-prevalence, our endorsement
-model would predict \enquote{Books are paperbacks} is neither true nor
-untrue, in the a way analogous to \enquote{Robins are female}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/books-paperbacks.pdf}
-\caption{\label{fig:booksArePaperbacks}Sketch of an argument for why
-\enquote{Books are paperbacks} sounds odd. The feature \enquote{is
-paperback} can only be predicated (in the sense of Keil (1979)) of
-individual books, which are organized into collections (here, by genre).
-The prevalence prior is constructed by aggregating these collections of
-books. Then the prevalence of \enquote{is paperbook} for the category of
-\enquote{books} can never be higher than the mean of the prior
-distribution. The endorsement model would give this sentence a rating of
-0.5, corresponding to neither true nor false.}
-\end{figure}
-
-Imagine there is a job in the local beaurocrat's office to handle the
-mail from Antarctica and this job is assigned to Mary; to date, however,
-there has never been any mail from Antarctica (Cohen, 1999). That is,
-the statement \enquote{Mary has handled mail from Antarctica} is false.
-Sentence (2) is still thought to be true despite zero actual instances
-of the event. We think (2) is a boundary case of generalizations
-expressing predictive probabilities, which we elucidated in Expt. 2c. In
-in that study, we experimentally dissociated predictive probability from
-past frequency, and saw that only a model that took into account
-predictive probability could explain participants' endorsements of
-generalizations. We expect the same to be true here, elucidated by the
-intuition that: were there to be any mail coming from Antarctica, Mary
-would handle it. Past frequency or actual prevalence in the world often
-tracks predictive probabilities, but language users' internal models of
-how the world works can lead them in certain situations to expect
-something different in the future.
-
-Our focus on predictive probability makes even new prediction about some
-classic puzzles. Sentence (3) is the conceptual opposite of sentence
-(2). Imagine that currently every Supreme Court Justice has a social
-security number which is an \emph{even number}. Sentence (3) is still
-considered false, every though the property holds in 100\% of the
-category (Cohen, 1999). We predict this phenomenon is the result of
-abstract, intuitive theories guiding us to reject observed frequencies
-in forming our subjective probabilities. That is, because observers
-strongly believe selection for the Supreme Court is not influenced by
-one's social security number, speakers would assign a roughly 50\%
-subjective probability that the \emph{next} justice would have an even
-social security number. Then, given that the all professions would have
-roughly the same probability of having employees with even social
-security numbers, Sentence (3) is again similar to \enquote{Birds are
-female}. However, were we to learn much more surprising
-information---for instance, if every Supreme Court Justice in U.S.
-history had a social security number which was a \emph{prime
-number}---the shear suspiciousness could compel an observer to revise
-their theory of the domain (appealing perhaps to a conspiracy), update
-their subjective probability of future instances, and then accept the
-generic. That is, we predict there are situations where statements like
-(3) could be considered felicitious generalizations.
-
-Understanding how a semantic representation \emph{composes} is another
-critical test for a theory of generalizations in language. Nickel (2008)
-suggests Sentence (4) is semantically equivalent to: \enquote{Elephants
-live in Africa and elephants live in Asia}. Stastistical account of
-generalizations have trouble with this kind of conjunction: It cannot be
-the case that \emph{most} (more than half) elephants live in Africa and
-\emph{most} (more than half) elephants live in Asia, unless we are to
-posit \emph{international elephants} (i.e., individual elephants who
-live part-time in Africa and part-time in Asia), which we would rather
-not have to posit. However, this is the only interpretation if the
-generalization is given a fixed, majority based quantificational account
-(e.g., if the generic means \emph{most}). Our theory does not provide a
-fixed semantics for the generalizations, but an uncertain one, which can
-be updated as more information comes in. In fact, with a strong
-constraint against the existence of \emph{international elephants} but
-with any further semantic assumptions, our model infers that some
-elephants live in Africa and other lives in Asia.\footnote{An
-  implementation of this example can be found:
-  \url{http://forestdb.org/models/generics-conjunction.html}.}
-Importantly, the model believes that most lives in Africa, when it only
-hears that \enquote{Elephants live in Africa}, and only later revises
-it's beliefs to a weaker \enquote{some}-like interpretation after
-hearing they live in Asia as well. Our model flexibly accomodates new
-evidence that might otherwise contradict previous utterances because it
-maintains uncertainty about the precise interpretation of single
-utterances.
-
-Finally, sometimes a property is widespread relative to other kinds or
-groups, and it might be so systemic that we would believe it to be the
-case in the future, but speakers still might find it avertise to
-actually endorse the generalization. Such is the situation with Sentence
-(5) (Haslanger, 2011). Due of a variety of socio-cultural reasons,
-Haslanger (2011) argues that women tend to be submissive (more so than
-men, and many other social categories), yet still cautions against
-asserting (5). In our \textbf{Model Simulations} section, we showed that
-the genearlization often implies the property is widespread, even with
-relatively uninformed prior beliefs about the property. If the generic
-conveys the property is in fact more widespread than the speaker herself
-might believe, this can lead to a distortion of the truth..\footnote{Note
-  that this can straight-forwardly capture the central phenomena of
-  Cimpian et al. (2010).} The current formulation of the model is
-relatively ambivalent about the deviations of the listener's beliefs
-from the speaker's belief (i.e., the speaker doesn't mind that the
-prevalence that she believes to be true will be exaggerated in the mind
-of the listener). However, if states of the world (or, listener's
-beliefs about states of the world) correspond to different subjective
-values, speakers who take into the account the subjective utilities of
-the listener may produce language that deviates from what a pure
-informational transmission speaker might say. This kind of extension to
-rational models of communication has already been used to account for a
-variety of phenomena in \emph{polite language} use (Yoon, Tessler,
-Goodman, \& Frank, 2016, 2017). We propose adopting such a value-based
-utility structure for states of the world for language about social
-categories: If the speaker found states of the world where the
-probability of the feature is high (e.g., a world where many women were
-submissive) as undesirable, then a speaker who considered both the
-informational content of the utterance and the utility in the states of
-the world implied by that utterance would too find it reprehensible to
-make such a generalization. We find this possibilitity intruiging and
-leave it for future work.
-
-In sum, we've tried to argue that our information-theoretic
-communicative model couched in general cognitive framework can be used
-to explain a number of interesting and heretofore puzzling phenomena in
-genericity as well as make novel predictions about a wider range of
-language. The precise implementation of these hypotheses we leave for
-future work.
-
-\subsection{Relationship to other
-theories}\label{relationship-to-other-theories}
-
-To our knowledge, the present papaer presents the first formal theory of
-genericity in language that makes accurate and precise quantitative
-predictions about human behavioral data. A number of other theories of
-genericity have been proposed in the linguistics and psychological
-literatures. We now turn to situating our account with respect to these
-previous theories. Semantic theories fall into one of two broad camps:
-Those that appeal to the statistics of the world (e.g., how many Ks have
-F) and those that appeal to structured, conceptual representations
-(e.g., \emph{there is something about being K which causes it to F}).
-Statistical and conceptual theories express the major contrasting views
-of the truth conditions of generic statements (Carlson, 1995).\footnote{We
-  use the terms statistical and conceptual to refer to what Carlson
-  (1995) referred to as \enquote{inductive} and \enquote{rules and
-  regulations} views, respectively.}
-
-\subsubsection{Statistical accounts}\label{statistical-accounts}
-
-\paragraph{Relative and absolute
-generics}\label{relative-and-absolute-generics}
-
-Our underspecified threshold model has clear antecedents in other
-statistical accounts, most notably Cohen (1999) 's theory of generics as
-a frequency adverb (e.g., \enquote{generally}). For Cohen, the statement
-\enquote{Birds lay eggs} means \enquote{Generally, birds lay eggs}, and
-then he takes up the task of explaining what \enquote{generally} means.
-He partitions generics into two types: \emph{absolute} and
-\emph{relative} generics. \emph{Absolute generics} use a fixed, 50\%
-threshold on prevalence: \(P(F\mid K)>0.5\). Roughly speaking,
-\enquote{Dogs have four legs} is true because a given dog is more likely
-than not to have four legs. \emph{Relative generics} depend upon an
-alternative set of kinds (his notation: \(Alt(K)\)), analogous to our
-comparison class. \enquote{Mosquitos carry malaria} is a relative
-generic: it is true because an arbitrary mosquito is more likely than an
-arbitrary member of an alternative kind to have the feature.
-
-Our uncertain-threshold model deviates from Cohen's account in two
-primary ways. First, though his theory is framed in terms of
-probabilities, it still utilities a fixed threshold semantics and thus
-is only able to make predictions about what is \enquote{true} and what
-is \enquote{false}. In our theory, there is uncertainty about the core
-semantic meaning, and this uncertainty (though reduced in context)
-drives the model to make graded predictions about endorsement. Second,
-Cohen draws an \emph{a priori} distinction between \emph{Absolute} and
-\emph{Relative} generics, and provides different mechanisms for each
-each. We used examples of both in our stimuli (Expt. 1) and found that
-our single model handles both without any addition assumptions, casting
-doubt on the \emph{a priori} distinction between \enquote{absolute} and
-\enquote{relative.}\footnote{For a related theory that aims to do away
-  with the distinction between \enquote{absolute} and \enquote{relative}
-  adjectives, see Lassiter and Goodman (2015).}
-
-We note additional machinery that Cohen's theory relies upon (and that
-is not currently required in our account) to explain the
-context-sensitivity of generics: contextually restricting the entities
-that go into the computation of prevalence (i.e., which robins do we
-look at to compute the probability of \emph{laying eggs} among
-\emph{robins}?). His theory posits that prevalence is calculuated by
-only considering entities that \emph{could have some feature} in a
-contextually-specified alternative set of features (so called
-\(Alt(F)\)). For example, the property \enquote{lays eggs} induces a set
-of alternatives that are associated with mechanisms of reproduction
-(e.g., \enquote{gives birth to live young}, \enquote{undergoes mitosis},
-\ldots{}). Therefore, \enquote{Robins lay eggs} is evaluated as an
-\emph{absolute generic} because only individuals that are female members
-of kinds are under consideration, because only the female members can
-plausibly satisfy one of the other aternatives having to do with
-reproduction (i.e., the alternative features in \(Alt(F)\)). The
-inferential machinery behind Cohen's domain restriction (i.e., what
-comrpises \(Alt(F)\)?) relies upon conceptual information, but the
-details remain obscure (Carlson, 1995).\footnote{However, see Cohen
-  (2004) for a discussion of how his semantic constraints relate to
-  different kinds of generics and different kinds of conceptual
-  representational frameworks found in cognitive science.} However, we
-note that this mechanism may be implicit in our own theory: the prior
-distribution over the prevalence of \emph{lays eggs} presumably includes
-aspects of people's theories about reproduction (i.e., that only females
-lay eggs). Thus, there may exist a refactorization of the uncertain
-threshold model to a fixed threshold where the listener has uncertainty
-about the relevant domain restriction.
-
-\paragraph{\texorpdfstring{\enquote{Normal}
-accounts}{Normal accounts}}\label{normal-accounts}
-
-The primary alternative view under the statistical banner draws on the
-intuition that generics express something normative in the world (Asher
-\& Morreau, 1995; Nickel, 2008; F. J. Pelletier \& Asher, 1997). For
-example, \enquote{Dogs have four legs} is a good generalization even
-though, regrettably, not all dogs have four legs. However, were the
-world to function \emph{normally} (e.g., dogs would not be involved in
-freak-tractor accidents or be born with strange genetic mutations), then
-\emph{all} dogs would have four legs. The idea that our beliefs about
-what is normal in the world influences our judgments about
-generalizations has intuitive appeal for rejecting accidentally true
-generalizations (e.g., \enquote{Supreme Court justices have even social
-security numbers}; described above) and stereotyped language (e.g.,
-\enquote{Boys are good at math}). Our theory does not directly formalize
-\enquote{what is normal}, though we argue that a speaker's beliefs about
-what is \emph{probable} (which may relate to what is \emph{normal}; see
-Icard, Kominsky, \& Knobe, 2017) plays a role in endorsing and
-interpreting generalizations. We showed in Expt. 2c that a speaker's
-beliefs about what is likely to be the case in the near future matters
-above and beyond what is currently true in the world for endorsing
-generalizations. Our notion of prevalence is as a predictive
-probability, which incorporates background knowledge in order to make
-predictions about the future.
-
-\paragraph{Underquantification}\label{underquantification}
-
-A proposal similar to our account concerning underspecification of
-generics has been made in the computational linguistics literature
-(so-called \emph{underquantification}; Herbelot \& Copestake, 2011). In
-their model, generics express an explicit quantified relation,
-specifically either \enquote{Some}, \enquote{Most}, or \enquote{All}.
-The task of the computational linguist, then, is to construct a set of
-features that accurately predicts (relative to human judgments) the
-quantified relationship expressed by the generic (Cimpian et al., 2010;
-analagous to a quantifier version of the \emph{implied prevalence} task
-used in Gelman \& Raman, 2003). Our semantic theory can be seen as a
-generalization of the \emph{underquantification} to a continuous
-interval of possible meanings. This distinction is relevant for the
-acquisition of the language of generalizations; we do not think that
-quantified relations (e.g., \enquote{Some}, \enquote{All}) are in any
-way primary or special. Additionally, by using a vague, underspecified
-threshold, our formulation naturally extends to other scales and other
-kinds of generalizations (e.g., habitual language), where quantified
-relations like \enquote{Most} or \enquote{All} are not directly
-applicable.
-
-\paragraph{Generic as indexical}\label{generic-as-indexical}
-
-Sterken (2015) has recently proposed an intruiging account of the
-context-sensitive of generic language by treating generics as a kind of
-\emph{indexical} (e.g., \enquote{this} or \enquote{I}). The variability
-of endorsements is then attributed to mechanisms of domain restriction
-(described above with Cohen (1999)) and context-sensitive
-\enquote{quantificational force}. Our uncertain-threshold semantics may
-be a precise formalization of Sterken (2015)'s \enquote{quantificational
-force} (and a generalization of \emph{underquantification}, see above),
-and we have argued above that domain restriction is not a necessary
-mechanisms for the cases considered in this paper. We leave for future
-work exploring how the context-sensitivity of an indexical may differ
-from the kind of context-sensitivity in our model.
-
-\subsubsection{Conceptual accounts}\label{conceptual-accounts}
-
-Conceptual accounts of generics emphasize the structure of generic
-knowledge (Prasada, 2000), and view generic utterances as the way of
-expressing special mental relationships between kinds and properties
-(Leslie, 2008; Prasada et al., 2012). These accounts start with the
-perspective that generics express rich, conceptual relationships between
-kinds and properties. That is, \enquote{Bishops move diagonally} not
-because of a statistical relationship, but rather, because those are the
-rules of the game; if you start moving the bishop other ways besides
-diagonally, you cease to be playing chess. If a lion lacked the capacity
-to roar, we might consider a less good example of being a lion because
-\enquote{lions roar}.
-
-The most influential conceptual account of generics is from Leslie
-(2007). For Leslie, generics are tied to the cognitive system's
-\enquote{default mode of generalization}, which infants seem ready to
-make use of by drawing strong generalizations from small amounts of data
-(e.g., Baldwin, Markman, \& Melartin, 1993). Leslie's \enquote{default
-mode} comes equipped with the ability to single-out
-\emph{striking properties} (e.g., properties which are dangerous or
-appalling) as particularly useful aspects of the world to know about.
-Hence, \enquote{Mosquitos carry malaria} is true because malaria can
-kill you and is useful to know about.
-
-This accounts predicts that generics that convey striking properties
-should be endorsed even when they are relatively rare in the category
-(i.e., low referent-prevalence; e.g., \enquote{Sharks attack swimmers}).
-Indeed, naturalistic examples (e.g., \enquote{Sharks attack swimmers})
-and artificial examples (e.g., \enquote{Lorches have purple feathers})
-supplemented with striking information (e.g.,\enquote{These feathers are
-as sharp as needles and can easily get lodged in you, causing massive
-bleeding}) are endorsed when the prevalence is quite low (e.g., 30\% of
-lorches have purple feathers; Cimpian et al. (2010); see Expt. 1 for
-naturalistic cases). In pilot work, using a paradigm similar to the
-prior manipulation paradigm employed in the causal language experiments
-(Expt. 3a), we have observed that the prior distribution over the
-prevalence \(P(h)\) change when supplied information about the
-dangerousness of the feature. That is, our pilot work suggests that
-experiments that experimentally induce beliefs about the dangerousness
-of a feature also manipulate the prevalence priors. Thus, our model
-would also predict these effects, but by way of the prevalence priors
-rather than some direct connection between generics and striking
-features.
-
-Of course, not all generics convey striking or appalling information
-(e.g., \enquote{Birds lay eggs}). Leslie's default mode, thus, also
-distinguishes \emph{negative counter-instances} of a property (e.g., a
-bird that doesn't lay eggs, such as a male bird) from \emph{positive
-counter-instances} (e.g., a hypothetical bird that bears live young) The
-conceptual account argues that generics are much less reasonable when
-\emph{positive} counter-instances exist. For example, \enquote{Birds are
-female} seems weird because \emph{being male} is a \emph{positive}
-counter-instance of \emph{being female}, but since there are no birds
-that bear live young (i.e., no \emph{positive counter-instances}),
-\enquote{Birds lay eggs} is fine. In the current version of our theory,
-both kinds of counter-instances influence the referent-category
-feature-probabilities, though only positive counter-instances could
-impact the statistical details of the comparison class (in particular,
-when constructed with respect to the feature; see discussion about the
-Comparison Class). Thus, the notion of \emph{positive} and
-\emph{negative} counter-instances may result from a particular way of
-looking at the constructs posited in our model, namely prevalences
-within- and across- categories or features.
-
-Finally, generics are not limited to conveying rich, conceptual
-information; they are also used to describe facts of the world.
-\enquote{Ravens are bigger than toasters} is a true statement, but not
-because of a rich relationship between ravens and toasters.
-\enquote{Barns are red} because most barns are red. If farmers around
-the world decided to paint their barns green, the things they would be
-painting would still be barns; in that world, we might say
-\enquote{Barns are green}. Thus, conceptual accounts must be
-supplemented with the proviso that in ceratin situations, the statistics
-of the world are relevant.
-
-Our view is that subjective probabilities can be formed either from
-worldly observations or because of the structure of people's mental
-representations. In the last fifteen years, there has been tremendous
-progress in formalizing Rich, structural mental representations can be
-formalized in probabilistic models, which can be used to derive
-quantitative predictions about inferences derived from that knowledge
-(Tenenbaum, Kemp, Griffiths, \& Goodman, 2011). For example, Kemp and
-Tenenbaum (2008) introduced a model for learning different kinds of
-structural relationships between objects and properties (e.g.,
-taxonomies, social cliques, dominance relations). Goodman et al. (2015)
-argue that concepts and intuitive theories can be constructed from
-elementary random primitives using insights from \emph{probabilistic
-programmming}.
-
-In this paper, we take a minimalist approach to modeling conceptual
-structure, incorporating only what is necessary into the interpreter's
-background knowledge, the prior on prevalence \(P(h)\). In our Bayesian
-data analysis of background knowledge, we use a mixture model that
-reflects basic knowledge about kinds and properties (e.g., that most
-kinds don't have most properites).\\
-It's plausible that more richly structured knowledge of the kind
-described by Prasada et al. (2013) and Leslie (2007) can be
-incorporating into the general probabilsitic framework that we use here.
-
-The key point of divergence then between the conceptual accounts and our
-view concerns the core, semantic meaning of a generic statement.
-Conceptual accounts try to identify the core meaning of a generalization
-directly with aspects of conceptual structure. For us, the semantics
-concerns a probability, which is the byproduct of a conceptual
-structure, but it is not the conceptual structure itself. We believe
-this provides a more unifying view of generics, giving a single metric
-as the basic currency of generic meaning: probability.
-
-\section{Conclusion}\label{conclusion}
+(e.g., a truth-functional threshold) are inappropriate for
+generics.\footnote{This argument is a purely semantic argument which
+  ignores evidence that children's difficulty with quantifiers stems
+  from pragmatic issues (Musolino \& Lidz, 2006).}
+
+Rejecting the tools of truth-functional semantics for generalizations
+would be throwing the baby out with the bathwater: In fact, from a
+learning perspective, our semantics of generics can be viewed as
+\emph{simpler} than that of quantifier semantics. With some reasonable
+assumptions about the hypothesis space of semantic meanings, the
+acquisition of a threshold-based truth-functional meaning
+\(\mbox{ $[\![ u ]\!]$}(p, \theta) := p > \theta\) requires learning
+three distinct aspects of meaning: (1) the \emph{dimension} being
+described (i.e., prevalence \(p\)), (2) the \emph{polarity} of the
+relation (i.e., \(>\) vs. \(<\)), and (3) the value of the
+\emph{threshold} (e.g., \(\theta = 0\) for \enquote{some},
+\(\theta = 0.5\) for \enquote{most}).\footnote{This particular framing
+  of the acquisition process ignores the potentially different impact of
+  pragmatic reasoning on generics vs.~quantifiers. } If a learner first
+acquires the dimension and the polarity (i.e., generics have to do with
+prevalence in some positive way), a rational learner should then
+represent uncertainty over possible thresholds \(\theta\). For
+quantifier semantics, a learner would then need to learn the
+context-invariant value of the threshold \(\theta\), but for generics,
+she could have an adult-like semantics for generics by maintaining
+uncertainty about the threshold. That is, the language of generalization
+is learned once aspects (1) and (2) are understood. Thus, under our
+framework, generics should not only be learned before quantifiers but
+could also facilitate the acquisition of quantifiers because of their
+shared logical form.
+
+There is a secondary argument for why our semantics presents an easy
+learning problem. We have assumed the truth functional threshold
+\(\theta\) comes from a uniform distribution over the unit interval
+\([0, 1]\), which is mathematically equivalent to a
+\emph{continuously-valued} or \emph{soft semantics} wherein the degree
+to which the utterance is true is proportional to the degree itself, in
+this case prevalence \(p\):
+\(\int_{0}^{1} \delta_{p > \theta} \mathop{}\!\mathrm{d}\theta = p\).
+The model for generic interpretation (Eq. \ref{eq:L0}) then becomes:
+\(L(p \mid u) \propto p \cdot P(p)\) This \emph{soft semantics}
+(corresponding intuitively to a meaning like \enquote{the higher the
+probability, the better}, or simply \enquote{more is better}) is perhaps
+the simplest quantitative semantics one could posit. The difficulty in
+acquiring the meaning of quantifiers, then, is a difficulty in
+recognizing a fixed-threshold semantics as a special case of this
+\emph{more is better} semantics. We leave for future work the precise
+implementation of such an acquisition model.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 possible? To the contrary, underspecification can be efficient, given
-that context can be used to resolve uncertainty in meaning (Piantadosi,
-Tily, \& Gibson, 2012). In our work, context takes the form of shared
-beliefs about the property in question. By leveraging this common
-ground, genericity provide a powerful way to communicate and learn
-generalizations, which would otherwise be difficult or costly
-information to learn through direct experience.
-
-The dark side of this flexibility is the potential for miscommunication
-or deceit: A speaker might assert a generalization that she herself
-would not accept, conveying a too-strong generalization to a naive
-listener. Our model predicts this potential particularly for properties
-which, when present, are widespread in a category; biological properties
-are believed to have this distribution, but many properties of social
-categories may as well (Cimpian \& Markman, 2011; Cimpian, Mu, \&
-Erickson, 2012; Rhodes et al., 2012). Disagreements are also predicted
-when interlocutors fail to share background assumptions, which could be
-differences in the prior distributions on prevalence or the comparison
-class. Core aspects of political disagreement then (e.g., as to whether
-\enquote{Humans cause global warming}) could be derived from differences
-in the estimated causal responsibility of the category in question
-(e.g., what impacts humans are having), of \emph{other forces} (e.g.,
-plate tectonics), as well as the comparison class of other forces (e.g.,
-what are the alternative causes?). This is a promising area for future
-research.
+that context can be relied upon to resolve uncertainty in the moment
+(Piantadosi, Tily, \& Gibson, 2012). In our work, context takes the form
+of shared beliefs between speakers and listeners. By leveraging this
+common ground, the language of generalizations provides a powerful way
+to communicate and learn abstract knowledge, which would otherwise be
+difficult or costly information to acquire through direct experience.
 
@@
 the first computational perspective on how we communicate
-generalizations and how beliefs play a central role in the meaning of
-words.
+generalizations, illustrating how beliefs play a central role in
+understanding the meaning of words.
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \hypertarget{refs}{}
-\hypertarget{ref-Asher1995}{}
+\leavevmode\hypertarget{ref-Asher1995}{}%
 Asher, N., \& Morreau, M. (1995). What some generic sentences mean.
@@
 
-\hypertarget{ref-Baldwin1993}{}
-Baldwin, D. A., Markman, E. M., \& Melartin, R. L. (1993). Infants '
-Ability to Draw Inferences about Nonobvious Object Properties: Evidence
-from Exploratory Play. \emph{Child Development}, \emph{64}(3), 711--728.
-
-\hypertarget{ref-Bale2011}{}
+\leavevmode\hypertarget{ref-Bale2011}{}%
 Bale, A. C. (2011). Scales and comparison classes. \emph{Natural
@@
 
-\hypertarget{ref-Behrens2005}{}
+\leavevmode\hypertarget{ref-Behrens2005}{}%
 Behrens, L. (2005). Genericity from a cross-linguistic perspective.
@@
 
-\hypertarget{ref-Bergen2016}{}
-Bergen, L., Levy, R., \& Goodman, N. D. (To appear). Pragmatic reasoning
-through semantic inference. \emph{Semantics and Pragmatics}.
-
-\hypertarget{ref-Brandone2014}{}
+\leavevmode\hypertarget{ref-Brandone2014}{}%
 Brandone, A. C., Gelman, S. A., \& Hedglen, J. (2014). Children's
@@
 
-\hypertarget{ref-Carlson1977}{}
+\leavevmode\hypertarget{ref-Carlson1977}{}%
 Carlson, G. N. (1977). \emph{Reference to kinds in english}
@@
 
-\hypertarget{ref-Carlson1995essay}{}
+\leavevmode\hypertarget{ref-Carlson1995essay}{}%
 Carlson, G. N. (1995). Truth conditions of generic sentences: Two
@@
 
-\hypertarget{ref-Carlson1995}{}
+\leavevmode\hypertarget{ref-Carlson2005}{}%
+Carlson, G. N. (2005). Generics, Habituals and Iteratives. In \emph{The
+encyclopedia of language and linguistics} (2nd ed.). Elsevier.
+doi:\href{https://doi.org/10.1007/s13398-014-0173-7.2}{10.1007/s13398-014-0173-7.2}
+
+\leavevmode\hypertarget{ref-Carlson1995}{}%
 Carlson, G. N., \& Pelletier, F. J. (1995). \emph{The generic book.}
@@
 
-\hypertarget{ref-Cheng1997}{}
+\leavevmode\hypertarget{ref-Cheng1997}{}%
 Cheng, P. W. (1997). From Covariation to Causation: A Causal Power
@@
 
-\hypertarget{ref-Cheng1992}{}
+\leavevmode\hypertarget{ref-Cheng1992}{}%
 Cheng, P. W., \& Npvick, L. R. (1992). Covariation in Natural Causal
@@
 
-\hypertarget{ref-Cimpian2008}{}
+\leavevmode\hypertarget{ref-Cimpian2007}{}%
+Cimpian, A., Arce, H.-M. C., Dweck, C. S., \& Markman, E. M. (2007).
+Subtle Linguistic Cues Affect Children's Motivation. \emph{Psychological
+Science}, \emph{18}(4), 314--316.
+
+\leavevmode\hypertarget{ref-Cimpian2010}{}%
+Cimpian, A., Brandone, A. C., \& Gelman, S. A. (2010). Generic
+statements require little evidence for acceptance but have powerful
+implications. \emph{Cognitive Science}, \emph{34}(8), 1452--1482.
+
+\leavevmode\hypertarget{ref-Cimpian2008}{}%
 Cimpian, A., \& Markman, E. M. (2008). Preschool children's use of cues
@@
 
-\hypertarget{ref-Cimpian2011a}{}
-Cimpian, A., \& Markman, E. M. (2011). The Generic/Nongeneric
-Distinction Influences How Children Interpret New Information About
-Social Others. \emph{Child Development}, \emph{82}(2), 471--492.
-doi:\href{https://doi.org/10.1111/j.1467-8624.2010.01525.x}{10.1111/j.1467-8624.2010.01525.x}
-
-\hypertarget{ref-Cimpian2007}{}
-Cimpian, A., Arce, H.-M. C., Dweck, C. S., \& Markman, E. M. (2007).
-Subtle Linguistic Cues Affect Children's Motivation. \emph{Psychological
-Science}, \emph{18}(4), 314--316.
-
-\hypertarget{ref-Cimpian2010}{}
-Cimpian, A., Brandone, A. C., \& Gelman, S. A. (2010). Generic
-statements require little evidence for acceptance but have powerful
-implications. \emph{Cognitive Science}, \emph{34}(8), 1452--1482.
-
-\hypertarget{ref-Cimpian2012b}{}
-Cimpian, A., Mu, Y., \& Erickson, L. C. (2012). Who Is Good at This
-Game? Linking an Activity to a Social Category Undermines Children's
-Achievement. \emph{Psychological Science}, \emph{23}(5), 533--541.
-doi:\href{https://doi.org/10.1177/0956797611429803}{10.1177/0956797611429803}
-
-\hypertarget{ref-Cohen1999}{}
+\leavevmode\hypertarget{ref-Clark1996}{}%
+Clark, H. H. (1996). \emph{Using language}. Cambridge University Press.
+
+\leavevmode\hypertarget{ref-Cohen1999}{}%
 Cohen, A. (1999). Generics, Frequency Adverbs, and Probability.
@@
 
-\hypertarget{ref-Cohen2004}{}
+\leavevmode\hypertarget{ref-Cohen2004}{}%
 Cohen, A. (2004). Generics and Mental Representations. \emph{Linguistics
@@
 
-\hypertarget{ref-Cree2006}{}
+\leavevmode\hypertarget{ref-Cree2006}{}%
 Cree, G. S., McNorgan, C., \& McRae, K. (2006). Distinctive features
@@
 
-\hypertarget{ref-Degen2014}{}
+\leavevmode\hypertarget{ref-Dahl1975}{}%
+Dahl, Ö. (1975). On generics. In E. Keenan (Ed.), \emph{Formal semantics
+of natural language} (pp. 99--111). Cambridge: Cambridge University
+Press.
+
+\leavevmode\hypertarget{ref-Declerck1986}{}%
+Declerck, R. (1986). The manifold interpretations of generic sentences.
+\emph{Lingua}, \emph{68}, 149--188.
+
+\leavevmode\hypertarget{ref-Declerck1991}{}%
+Declerck, R. (1991). The origins of genericity. \emph{Linguistics},
+\emph{29}, 79--102.
+
+\leavevmode\hypertarget{ref-Degen2014}{}%
 Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
@@
 
-\hypertarget{ref-Dewar2010}{}
-Dewar, K. M., \& Xu, F. (2010). Induction, overhypothesis, and the
-origin of abstract knowledge: Evidence from 9-month-old infants.
-\emph{Psychological Science}, \emph{21}, 1871--1877.
-doi:\href{https://doi.org/10.1177/0956797610388810}{10.1177/0956797610388810}
-
-\hypertarget{ref-Frank2012}{}
+\leavevmode\hypertarget{ref-Frank2012}{}%
 Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
@@
 
-\hypertarget{ref-Franke2014cogsci}{}
+\leavevmode\hypertarget{ref-Franke2014cogsci}{}%
 Franke, M. (2014). Typical use of quantifiers: A probabilistic speaker
@@
 
-\hypertarget{ref-Gelman2003}{}
+\leavevmode\hypertarget{ref-Gelman2003}{}%
 Gelman, S. A. (2003). \emph{Essential child: Origins of
@@
 
-\hypertarget{ref-Gelman2004}{}
+\leavevmode\hypertarget{ref-Gelman2004}{}%
 Gelman, S. A. (2004). Learning words for kinds: Generic noun phrases in
@@
 
-\hypertarget{ref-Gelman1999}{}
-Gelman, S. A., \& Heyman, G. D. (1999). Carrot-Eaters and
-Creature-Believers: The Effects of Lexicalization on Children's
-Inferences About Social Categories. \emph{Psychological Science},
-\emph{10}(6), 489--493.
-doi:\href{https://doi.org/10.1111/1467-9280.00194}{10.1111/1467-9280.00194}
-
-\hypertarget{ref-Gelman2003b}{}
-Gelman, S. A., \& Raman, L. (2003). Preschool children use linguistic
-form class and pragmatic cues to interpret generics. \emph{Child
-Development}, \emph{74}(1), 308--325.
-
-\hypertarget{ref-Gelman1998}{}
+\leavevmode\hypertarget{ref-Gelman2009}{}%
+Gelman, S. A. (2009). Learning from others: Children's construction of
+concepts. \emph{Annual Review of Psychology}, \emph{60}, 115--140.
+doi:\href{https://doi.org/10.1146/annurev.psych.59.103006.093659.LEARNING}{10.1146/annurev.psych.59.103006.093659.LEARNING}
+
+\leavevmode\hypertarget{ref-Gelman1998}{}%
 Gelman, S. A., Coley, J. D., Rosengren, K. S., Hartman, E., \& Pappas,
@@
 
-\hypertarget{ref-Gelman2008}{}
+\leavevmode\hypertarget{ref-Gelman2008}{}%
 Gelman, S. A., Goetz, P. J., Sarnecka, B. W., \& Flukes, J. (2008).
@@
 
-\hypertarget{ref-Gelman2015}{}
+\leavevmode\hypertarget{ref-Gelman2015}{}%
 Gelman, S. A., Leslie, S.-J., Was, A. M., \& Koch, C. M. (2015).
@@
 
-\hypertarget{ref-GelmanEtAl2004}{}
+\leavevmode\hypertarget{ref-Gelman2003b}{}%
+Gelman, S. A., \& Raman, L. (2003). Preschool children use linguistic
+form class and pragmatic cues to interpret generics. \emph{Child
+Development}, \emph{74}(1), 308--325.
+
+\leavevmode\hypertarget{ref-GelmanEtAl2004}{}%
 Gelman, S. A., Taylor, M. G., Nguyen, S. P., Leaper, C., \& Bigler, R.
@@
 
-\hypertarget{ref-Gerstenberg2015how}{}
+\leavevmode\hypertarget{ref-Gerstenberg2015how}{}%
 Gerstenberg, T., Goodman, N. D., Lagnado, D. A., \& Tenenbaum, J. B.
@@
 
-\hypertarget{ref-Goodman2016}{}
+\leavevmode\hypertarget{ref-Goodman1955}{}%
+Goodman, N. (1955). \emph{Fact, fiction, and forecast}. Harvard
+University Press.
+
+\leavevmode\hypertarget{ref-Goodman2016}{}%
 Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language
@@
 
-\hypertarget{ref-dippl}{}
+\leavevmode\hypertarget{ref-GoodmanLassiter}{}%
+Goodman, N. D., \& Lassiter, D. (2015). Probabilistic semantics and
+pragmatics: Uncertainty in language and thought. In S. Lappin \& C. Fox
+(Eds.), \emph{The handbook of contemporary semantic theory, 2nd
+edition}. Wiley-Blackwell.
+
+\leavevmode\hypertarget{ref-dippl}{}%
 Goodman, N. D., \& Stuhlmüller, A. (2014). The Design and Implementation
@@
 
-\hypertarget{ref-Goodmanconcepts}{}
+\leavevmode\hypertarget{ref-Goodmanconcepts}{}%
 Goodman, N. D., Tenenbaum, J. B., \& Gerstenberg, T. (2015). Concepts in
@@
 
-\hypertarget{ref-Gopnik2003theory}{}
+\leavevmode\hypertarget{ref-Gopnik2003theory}{}%
 Gopnik, A. (2003). The theory theory as an alternative to the innateness
@@
 
-\hypertarget{ref-Griffiths2005}{}
+\leavevmode\hypertarget{ref-Grice1975}{}%
+Grice, H. P. (1975). Logic and conversation. In \emph{Readings in
+language and mind}. Blackwell.
+
+\leavevmode\hypertarget{ref-Griffiths2005}{}%
 Griffiths, T. L., \& Tenenbaum, J. B. (2005). Structure and strength in
@@
 
-\hypertarget{ref-Griffiths2009}{}
+\leavevmode\hypertarget{ref-Griffiths2009}{}%
 Griffiths, T. L., \& Tenenbaum, J. B. (2009). Theory-Based Causal
@@
 
-\hypertarget{ref-Gweon2010}{}
-Gweon, H., Tenenbaum, J. B., \& Schulz, L. E. (2010). Infants consider
-both the sample and the sampling process in inductive generalization.
-\emph{Proceedings of the National Academy of Sciences of the United
-States of America}, \emph{107}(20), 9066--71.
-doi:\href{https://doi.org/10.1073/pnas.1003095107}{10.1073/pnas.1003095107}
-
-\hypertarget{ref-Haslanger2011}{}
-Haslanger, S. (2011). Ideology, generics, and common ground. In
-\emph{Feminist metaphysics} (pp. 179--207). Springer.
-
-\hypertarget{ref-Henrich2015}{}
+\leavevmode\hypertarget{ref-Henrich2015}{}%
 Henrich, J. (2015). \emph{The secret of our success: how culture is
@@
 
-\hypertarget{ref-Herbelot2011}{}
+\leavevmode\hypertarget{ref-Herbelot2011}{}%
 Herbelot, A., \& Copestake, A. (2011). Formalising and specifying
@@
 
-\hypertarget{ref-HumeTHN}{}
+\leavevmode\hypertarget{ref-HumeTHN}{}%
 Hume, D. (1888). (L. A. Selby Bigge, Ed.). Oxford, Clarendon Press.
 
-\hypertarget{ref-Icard2017}{}
+\leavevmode\hypertarget{ref-Icard2017}{}%
 Icard, T. F., Kominsky, J. F., \& Knobe, J. (2017). Normality and actual
@@
 
-\hypertarget{ref-Keil1979}{}
-Keil, F. C. (1979). \emph{Semantic and conceptual development.} Harvard
-University Press.
-
-\hypertarget{ref-Keil1992}{}
-Keil, F. C. (1992). \emph{Concepts, kind, and cognitive development.}
-MIT Press.
-
-\hypertarget{ref-Kemp2008}{}
-Kemp, C., \& Tenenbaum, J. B. (2008). The discovery of structural form.
-\emph{Proceedings of the National Academy of Sciences of the United
-States of America}, \emph{105}(31), 10687--10692.
-doi:\href{https://doi.org/10.1073/pnas.0802631105}{10.1073/pnas.0802631105}
-
-\hypertarget{ref-Kennedy2007}{}
+\leavevmode\hypertarget{ref-Kemp2007}{}%
+Kemp, C., Perfors, A., \& Tenenbaum, J. B. (2007). Learning
+overhypotheses with hierarchical Bayesian models. \emph{Developmental
+Science}, \emph{10}(3), 307--21.
+doi:\href{https://doi.org/10.1111/j.1467-7687.2007.00585.x}{10.1111/j.1467-7687.2007.00585.x}
+
+\leavevmode\hypertarget{ref-Kennedy2007}{}%
 Kennedy, C. (2007). Vagueness and grammar: the semantics of relative and
@@
 
-\hypertarget{ref-Khemlani2012}{}
+\leavevmode\hypertarget{ref-Khemlani2012}{}%
 Khemlani, S., Leslie, S.-J., \& Glucksberg, S. (2012). Inferences about
@@
 
-\hypertarget{ref-KrifkaGenericBookFocus}{}
+\leavevmode\hypertarget{ref-KrifkaGenericBookFocus}{}%
 Krifka, M. (1995). Focus and the interpretation of generic sentences. In
@@
 
-\hypertarget{ref-Lassiter2013}{}
+\leavevmode\hypertarget{ref-Lassiter2013}{}%
 Lassiter, D., \& Goodman, N. D. (2013). Context, scale structure, and
@@
 
-\hypertarget{ref-Lassiter2015}{}
+\leavevmode\hypertarget{ref-Lassiter2015}{}%
 Lassiter, D., \& Goodman, N. D. (2015). Adjectival vagueness in a
@@
 
-\hypertarget{ref-Leslie2007}{}
+\leavevmode\hypertarget{ref-Leslie2007}{}%
 Leslie, S.-J. (2007). Generics and the Structure of the Mind.
@@
 
-\hypertarget{ref-Leslie2008}{}
+\leavevmode\hypertarget{ref-Leslie2008}{}%
 Leslie, S.-J. (2008). Generics: Cognition and acquisition.
@@
 
-\hypertarget{ref-Leslie2012a}{}
+\leavevmode\hypertarget{ref-Leslie2012}{}%
 Leslie, S.-J., \& Gelman, S. A. (2012). Quantified statements are
-recalled as generics: Evidence from preschool children and adults.
+recalled as generics: evidence from preschool children and adults.
 \emph{Cognitive Psychology}, \emph{64}(3), 186--214.
@@
 
-\hypertarget{ref-Levinson1995}{}
+\leavevmode\hypertarget{ref-Levinson1995}{}%
 Levinson, S. C. (1995). Interactional biases in human thinking. In E. N.
@@
 
-\hypertarget{ref-McGuire1986}{}
+\leavevmode\hypertarget{ref-Liebesman2011}{}%
+Liebesman, D. (2011). Simple generics. \emph{Noûs}, \emph{45}(3),
+409--442.
+
+\leavevmode\hypertarget{ref-McGuire1986}{}%
 McGuire, W. J., \& McGuire, C. V. (1986). Differences in conceptualizing
@@
 
-\hypertarget{ref-Montague1973}{}
+\leavevmode\hypertarget{ref-Montague1973}{}%
 Montague, R. (1973). The Proper Treatment of Quantification in Ordinary
@@
 
-\hypertarget{ref-Nickel2008}{}
+\leavevmode\hypertarget{ref-Musolino2006}{}%
+Musolino, J., \& Lidz, J. (2006). Why children aren't universally
+successful with quantification. \emph{Linguistics}, \emph{44}(4),
+817--852.
+
+\leavevmode\hypertarget{ref-Nickel2008}{}%
 Nickel, B. (2008). Generics and the ways of normality. \emph{Linguistics
@@
 
-\hypertarget{ref-Nickel2016}{}
+\leavevmode\hypertarget{ref-Nickel2016}{}%
 Nickel, B. (2016). \emph{Between logic and the world}. Oxford: Oxford
@@
 
-\hypertarget{ref-Nisbett1983}{}
+\leavevmode\hypertarget{ref-Nisbett1983}{}%
 Nisbett, R. E., Krantz, D. H., Jepson, C., \& Kunda, Z. (1983). The use
@@
 
-\hypertarget{ref-pearl1988probabilistic}{}
+\leavevmode\hypertarget{ref-Orvell2017}{}%
+Orvell, A., Kross, E., \& Gelman, S. A. (2017). How ``you'' makes
+meaning. \emph{Science}, \emph{355}(6331). Retrieved from
+\url{http://science.sciencemag.org/content/355/6331/1299.full}
+
+\leavevmode\hypertarget{ref-pearl1988probabilistic}{}%
 Pearl, J. (1988). Probabilistic reasoning in intelligent systems:
@@
 
-\hypertarget{ref-Pelletier1997}{}
-Pelletier, F. J., \& Asher, N. (1997). Generics and defaults. handbook
-of logic and language, ed. by j. van benthem and alice gb ter meulen,
-1125--1177. Cambridge: The MIT Press.
-
-\hypertarget{ref-Piantadosi2012}{}
+\leavevmode\hypertarget{ref-Pelletier1997}{}%
+Pelletier, F. J., \& Asher, N. (1997). Generics and defaults. In J. van
+Benthem \& A. Ter Meulen (Eds.), \emph{Handbook of logic and language}
+(pp. 1125--1177). Cambridge: The MIT Press.
+
+\leavevmode\hypertarget{ref-Piantadosi2012}{}%
 Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
@@
 
-\hypertarget{ref-Prasada2000}{}
+\leavevmode\hypertarget{ref-Prasada2000}{}%
 Prasada, S. (2000). Acquiring generic knowledge. \emph{Trends in
@@
 
-\hypertarget{ref-Prasada2012}{}
+\leavevmode\hypertarget{ref-Prasada2006}{}%
+Prasada, S., \& Dillingham, E. M. (2006). Principled and statistical
+connections in common sense conception. \emph{Cognition}, \emph{99}(1),
+73--112.
+doi:\href{https://doi.org/10.1016/j.cognition.2005.01.003}{10.1016/j.cognition.2005.01.003}
+
+\leavevmode\hypertarget{ref-Prasada2012}{}%
 Prasada, S., Hennefield, L., \& Otap, D. (2012). Conceptual and
@@
 
-\hypertarget{ref-Prasada2013}{}
+\leavevmode\hypertarget{ref-Prasada2013}{}%
 Prasada, S., Khemlani, S., Leslie, S.-J., \& Glucksberg, S. (2013).
@@
 
-\hypertarget{ref-Qing2014}{}
+\leavevmode\hypertarget{ref-Qing2014}{}%
 Qing, C., \& Franke, M. (2014). Gradable adjectives, vagueness, and
@@
 
-\hypertarget{ref-Repacholi1997}{}
+\leavevmode\hypertarget{ref-Repacholi1997}{}%
 Repacholi, B. M., \& Gopnik, A. (1997). Early reasoning about desires:
@@
 
-\hypertarget{ref-Rhodes2012}{}
+\leavevmode\hypertarget{ref-Rhodes2012}{}%
 Rhodes, M., Leslie, S.-J., \& Tworek, C. M. (2012). Cultural
@@
 
-\hypertarget{ref-Ritchie2016}{}
+\leavevmode\hypertarget{ref-Ritchie2016}{}%
 Ritchie, D., Stuhlmüller, A., \& Goodman, N. D. (2016). C3: Lightweight
@@
 
-\hypertarget{ref-roberts1996qud}{}
+\leavevmode\hypertarget{ref-roberts1996qud}{}%
 Roberts, C. (1996). Information structure in discourse: Towards an
@@
 
-\hypertarget{ref-hurdleModels}{}
+\leavevmode\hypertarget{ref-hurdleModels}{}%
 Rose, C. E., Martin, S. W., Wannemuehler, K. A., \& Plikaytis, B. D.
@@
 
-\hypertarget{ref-Schmidt2009}{}
+\leavevmode\hypertarget{ref-Rothbart1978}{}%
+Rothbart, M., Fulero, S., Jensen, C., Howard, J., \& Birrell, P. (1978).
+From individual to group impressions: Availability heuristics in
+stereotype formation. \emph{Journal of Experimental Social Psychology},
+\emph{14}(3), 237--255.
+doi:\href{https://doi.org/10.1016/0022-1031(78)90013-6}{10.1016/0022-1031(78)90013-6}
+
+\leavevmode\hypertarget{ref-Schmidt2009}{}%
 Schmidt, L. A., Goodman, N. D., Barner, D., \& Tenenbaum, J. B. (2009).
@@
 
-\hypertarget{ref-Seiver2013}{}
+\leavevmode\hypertarget{ref-Seiver2013}{}%
 Seiver, E., Gopnik, A., \& Goodman, N. D. (2013). Did She Jump Because
@@
 
-\hypertarget{ref-Shepard1987}{}
+\leavevmode\hypertarget{ref-Shepard1987}{}%
 Shepard, R. N. (1987). Toward a universal law of generalization for
@@
 
-\hypertarget{ref-Solt2009}{}
+\leavevmode\hypertarget{ref-Shipley1993}{}%
+Shipley, E. F. (1993). Categories, hierarchies, and induction. \emph{The
+Psychology of Learning and Motivation}, \emph{30}, 265--301.
+
+\leavevmode\hypertarget{ref-Solt2009}{}%
 Solt, S. (2009). Notes on the Comparison Class. In \emph{International
@@
 
-\hypertarget{ref-Solt2012}{}
+\leavevmode\hypertarget{ref-Solt2012}{}%
 Solt, S., \& Gotzner, N. (2012). Experimenting with degree.
@@
 
-\hypertarget{ref-Sommers1963}{}
-Sommers, F. (1963). Types and ontology. \emph{The Philosophical Review},
-327--363.
-
-\hypertarget{ref-Sterken2015}{}
+\leavevmode\hypertarget{ref-Sterken2015}{}%
 Sterken, R. K. (2015). Generics in Context. \emph{Philosophers'
@@
 
-\hypertarget{ref-Tenenbaum2001}{}
+\leavevmode\hypertarget{ref-Tenenbaum2001}{}%
 Tenenbaum, J. B., \& Griffiths, T. L. (2001). Generalization, similarity
@@
 
-\hypertarget{ref-Tenenbaum2011}{}
+\leavevmode\hypertarget{ref-Tenenbaum2011}{}%
 Tenenbaum, J. B., Kemp, C., Griffiths, T. L., \& Goodman, N. D. (2011).
@@
 
-\hypertarget{ref-Tessler2017}{}
+\leavevmode\hypertarget{ref-Tessler2018negant}{}%
+Tessler, M. H., \& Franke, M. (2018). Not unreasonable: Carving vague
+dimensions with contraries and contradictions.
+
+\leavevmode\hypertarget{ref-Tessler2017}{}%
 Tessler, M. H., Lopez-Brau, M., \& Goodman, N. D. (2017). Warm (for
@@
 
-\hypertarget{ref-Tomasello1999}{}
+\leavevmode\hypertarget{ref-Tomasello1999}{}%
 Tomasello, M. (1999). \emph{The cultural origins of human cognition}.
@@
 
-\hypertarget{ref-Tversky1974}{}
+\leavevmode\hypertarget{ref-Tversky1974}{}%
 Tversky, A., \& Kahneman, D. (1974). Judgment under Uncertainty:
@@
 
-\hypertarget{ref-Yoon2016}{}
-Yoon, E. J., Tessler, M. H., Goodman, N. D., \& Frank, M. C. (2016).
-Talking with tact: Polite language as a balance between kindness and
-informativity. In \emph{Proceedings of the thirty-eighth annual
-conference of the cognitive science society}.
-
-\hypertarget{ref-Yoon2017}{}
-Yoon, E. J., Tessler, M. H., Goodman, N. D., \& Frank, M. C. (2017). ``I
-won't lie, it wasn't amazing'': Modeling polite indirect speech.
+\leavevmode\hypertarget{ref-Williamson1992}{}%
+Williamson, T., \& Simons, P. (1992). Vagueness and ignorance.
+\emph{Proceedings of the Aristotelian Society, Supplementary Volumes},
+\emph{66}, 145--177.
+
+\leavevmode\hypertarget{ref-xu2009statistical}{}%
+Xu, F., \& Denison, S. (2009). Statistical inference and sensitivity to
+sampling in 11-month-old infants. \emph{Cognition}, \emph{112}(1),
+97--104.
+
+\leavevmode\hypertarget{ref-Xu2008}{}%
+Xu, F., \& Garcia, V. (2008). Intuitive statistics by 8-month-old
+infants. \emph{Proceedings of the National Academy of Sciences of the
+United States of America}, \emph{105}(13), 5012--5.
+doi:\href{https://doi.org/10.1073/pnas.0704450105}{10.1073/pnas.0704450105}
 
@@
 
+\hypertarget{appendix-a-the-relationship-between-the-prevalence-prior-and-cue-validity}{%
 \section{Appendix A: The Relationship between the Prevalence Prior and
 Cue
-Validity}\label{appendix-a-the-relationship-between-the-prevalence-prior-and-cue-validity}
+Validity}\label{appendix-a-the-relationship-between-the-prevalence-prior-and-cue-validity}}
 
 Cue validity is defined for a particular category--property pair (e.g.,
-\emph{mosquitos} and \emph{carry malaria}), and relates to
-referent-prevalence (e.g., how many mosquitos carry malaria) via the
-prevalence of \emph{carrying malaria} in other categories \(k'\) by
-Bayes' Rule: \[ p(k \mid f) = \frac{p(f \mid k) \cdot p(k)}{Z} \] where
-\(Z = \sum_{k' \in K} p( f \mid k') \cdot p( k')\)
-
-The prevalence prior \(P(p_f)\) (Eq. \ref{eq:L0}) is a probability
-distribution over prevalence for different categories \(k'\). For ease
-of exposition, let \(x = p_f = p(f \mid k)\); that is,
-\(P(x) = P(p_f)\).
+\emph{mosquitos} and \emph{carry malaria}), and relates to the referent
+prevalence (e.g., how many mosquitos carry malaria) via Bayes' Rule:
+\[ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{Z} \] where
+\(Z = \sum_{k' \in K} P( f \mid k') \cdot P( k')\), the average or
+marginal prevalence of the feature (e.g., \emph{carrying malaria}) in
+other categories \(k'\).
+
+The prevalence prior \(P(p)\) using the generic interpretation model
+(Eq. \ref{eq:L0}) is a probability distribution over prevalence for
+different categories \(k'\).
 
@@
 is equal to the expected value of the prevalence prior distribution:
-\(\mathbb{E}[P(x)] = Z\)
+\(\mathbb{E}[P(p)] = Z\)
 
@@
 \begin{eqnarray} \label{eq:expectation}
-\mathbb{E}[P(x)] & = & \sum\limits_{x} x \cdot p(x) 
+\mathbb{E}[P(p)] & = & \sum\limits_{p} p \cdot P(p) 
 \end{eqnarray}
 
-The probability of a prevalence \(x\) can be decomposed into the prior
+The probability of a prevalence \(p\) can be decomposed into the prior
 probability of a category \(k\) and the likelihood of the prevalence
-\(x\) given that category \(k\): \(p(x) = p(x \mid k) \cdot p(k)\). We
+\(p\) given that category \(k\): \(P(p) = P(p \mid k) \cdot P(k)\). We
 assume here, without loss of generality, that each category corresponds
-to one and only one prevalence \(x\). Thus, \(p(x \mid k) = 1\) if
-\(k \in K_x\), a set of categories that have a given prevalence:
-\(K_x = \{k' : p_{fk'} = x\}\). Further, e partition of the set of all
-categories \(K\) into non-overlapping \(K_x\)s. Thus:
+to one and only one prevalence \(p\). Thus, \(P(p \mid k) = 1\) if
+\(k \in K_p\), a set of categories that have a given prevalence:
+\(K_p = \{k' : p_{k'} = p\}\). Then, consider the partition of the set
+of all categories \(K\) into non-overlapping \(K_p\). Thus:
 
 \begin{eqnarray} \label{eq:prevToKinds}
-p(x) & = & \sum\limits_{k' \in K_x} p(x \mid k') \cdot p( k') \nonumber \\
-     & = & \sum\limits_{k' \in K_x} p(k')
+P(p) & = & \sum\limits_{k' \in K_p} P(p \mid k') \cdot P( k') \nonumber \\
+     & = & \sum\limits_{k' \in K_p} P(k')
 \end{eqnarray}
 
-since \(\forall k' \in K_{x}: p(x \mid k') = 1\). Returning to Eq.
+since \(\forall k' \in K_{p}: P(p \mid k') = 1\). Returning to Eq.
 \ref{eq:expectation}, we have:
@@
 \begin{eqnarray} \label{eq:eq3}
-\mathbb{E}[P(x)] & = & \sum\limits_{x} x \sum\limits_{k' \in K_x} p(k') \nonumber \\
-                  & = & \sum\limits_{x} \sum\limits_{k' \in K_x} x \cdot p(k')
+\mathbb{E}[P(p)] & = & \sum\limits_{p} p \sum\limits_{k' \in K_p} P(k') \nonumber \\
+                  & = & \sum\limits_{p} \sum\limits_{k' \in K_p} p \cdot P(k')
 \end{eqnarray}
 
-The set of all partitioned subsets \(K_x\) is in a one-to-one
-correspondence with the set of all prevalences \(x\). Thus, we have:
+The set of all partitioned subsets \(K_p\) is in a one-to-one
+correspondence with the set of all prevalences \(p\). Thus, we have:
 
 \begin{eqnarray} \label{eq:bijection}
-  & = & \sum\limits_{K_x} \sum\limits_{k' \in K_x} x \cdot p( k')
+  & = & \sum\limits_{K_p} \sum\limits_{k' \in K_p} p \cdot P( k')
 \end{eqnarray}
 
-Then, since \(\cup_{x}{K_x} = K\), we have
+Then, since \(\cup_{p}{K_p} = K\), we have
 
 \begin{eqnarray} \label{eq:partition}
-  & = & \sum\limits_{k' \in K} x \cdot p( k') \nonumber \\ 
-  & = & \sum\limits_{k' \in K} p(f \mid k') \cdot p( k') \nonumber \\ 
+  & = & \sum\limits_{k' \in K} p \cdot P( k') \nonumber \\ 
+  & = & \sum\limits_{k' \in K} P(f \mid k') \cdot P( k') \nonumber \\ 
   & = & Z
@@
 
+\hypertarget{appendix-b-measuring-cue-validity}{%
 \section{Appendix B: Measuring Cue
-Validity}\label{appendix-b-measuring-cue-validity}
+Validity}\label{appendix-b-measuring-cue-validity}}
 
@@
 validity (and prevalence) and predicting generic endorsement from a
-regression model. In a small review of the literature, we discovered
-different methods for measuring cue validity; in piloting, these
-different methods lead to different results. Therefore, we propose three
-\emph{a priori} desiderata that a measurement of cue validity should
-satisfy. We describe two experiments that represent the primary methods
-for measuring cue validity and compare them with these desiderata in
-mind. Finally, we compare the cue validity measured using these
-different methods to cue validity derived from our prevalence prior
-elicitation task (Expt. 1a, main text).
-
-\subsection{Desiderata}\label{desiderata}
+linear combination of these parameters. In a small review of the
+literature, we discovered different methods for measuring cue validity;
+in piloting, we found these different methods led to different results.
+Therefore, we propose three \emph{a priori} desiderata that a
+measurement of cue validity should satisfy. We describe two experiments
+that represent the primary methods for measuring cue validity and
+compare them with these desiderata in mind. Finally, we compare the cue
+validity measured using these different methods to cue validity derived
+from our prevalence prior elicitation task (Expt. 1b, main text).
+
+\hypertarget{desiderata}{%
+\subsection{Desiderata}\label{desiderata}}
 
@@
 relate to the probability that an exemplar is a member of a kind given
-that is has a feature : \(P(x \in k \mid x \in f)\). There are several
-ways one could measure cue validity. Here we consider two measures: One
-that has participants estimate the probability
+that it has a feature: \(P(x \in k \mid x \in f)\). There are several
+ways one could measure cue validity. Here we consider two measures: The
+first has participants estimate the cue validity probability
 \(P(x \in k \mid x \in f)\) directly, a common technique in the
 literature on generic language (e.g., Khemlani et al., 2012; Prasada et
-al., 2013), and another that has participants freely produce categories
-given a feature (i.e., draw a sample from the conditional distribution
-on kinds given a feature; Cree et al., 2006). We will the former the
-\emph{direct question} method and the latter the \emph{free production}
-method.
+al., 2013), and another has participants freely produce categories given
+a feature (i.e., draw a sample from the conditional distribution on
+kinds given a feature; Cree et al., 2006). We will refer to the former
+the \emph{direct question} method and the latter the \emph{free
+production} method.
 
@@
 valid for measuring cue validity? We propose \emph{a priori} three
-boundary conditions that the measurement should be able to satisfy. For
-each case, we provide four examples from our larger stimulus set on
+boundary conditions that a measurement of cue validity should satisfy.
+For each case, we provide four examples from our larger stimulus set on
 generics (Case Study 1) which will be used to evaluate each measure.
@@
 There are infinite examples.
-The ones will use are \emph{has wings} (leopard), \emph{has a mane} (shark), *has spots* (kangaroo), *has a pouch* (tiger).
+The ones we will use are \emph{has wings} (leopard), \emph{has a mane} (shark), \emph{has spots} (kangaroo), \emph{has a pouch} (tiger).
 }
 \item{Completely undiagnostic features: A number of features are shared by almost every category.
+The cue validity of these features for particular categories should be extremely low or 0.
 The ones we will use are: \emph{is female} (robin), \emph{is male} (lion), \emph{is juvenile} (kangaroo), \emph{is full-grown} (leopard).
-The cue validity of these features for particular categories should be extremely low or 0.
 Learning that an entity is female tells you almost nothing about what kind of animal it is.}
@@
 items described above. Links to the experiments can be found on
-\url{https://mhtess.github.io}.
-
-\subsection{Experimental materials}\label{experimental-materials}
-
-Materials were the same for both experiments. They were a collection of
-familiar properties and animal categories used in Expt. 1b (endorsement
+\url{https://github.com/mhtess/genlang-paper}.
+
+\hypertarget{experimental-materials}{%
+\subsection{Experimental materials}\label{experimental-materials}}
+
+Materials were the same for both experiments. These were a collection of
+familiar properties and animal categories used in Expt. 1a (endorsement
 of generic statements) described in the main text. There were twenty-one
@@
 
+\hypertarget{direct-question-experiment}{%
 \subsection{Direct question
-experiment}\label{direct-question-experiment}
-
-\subsubsection{Method}\label{method-7}
-
-\paragraph{Participants}\label{participants-7}
+experiment}\label{direct-question-experiment}}
+
+\hypertarget{method-7}{%
+\subsubsection{Method}\label{method-7}}
+
+\hypertarget{participants-7}{%
+\paragraph{Participants}\label{participants-7}}
 
@@
 
-\paragraph{Procedure}\label{procedure-4}
+\hypertarget{procedure-4}{%
+\paragraph{Procedure}\label{procedure-4}}
 
@@
 Participants completed the thirty target trials (corresponding to the
-thirty generic statements used in Expt. 1b) in addition to ten filler
+thirty generic statements used in Expt. 1a) in addition to ten filler
 trials (total number of trials = 40). The filler trials were made up of
-random category -- property pairings. Trials were presented in a
+random category--property pairings. Trials were presented in a
 randomized order.
 
+\hypertarget{free-production-experiment}{%
 \subsection{Free production
-experiment}\label{free-production-experiment}
-
-\subsubsection{Method}\label{method-8}
-
-\paragraph{Participants}\label{participants-8}
+experiment}\label{free-production-experiment}}
+
+\hypertarget{method-8}{%
+\subsubsection{Method}\label{method-8}}
+
+\hypertarget{participants-8}{%
+\paragraph{Participants}\label{participants-8}}
 
@@
 
-\paragraph{Procedure}\label{procedure-5}
+\hypertarget{procedure-5}{%
+\paragraph{Procedure}\label{procedure-5}}
 
@@
 
-Participants responded by filling in a text box with their response.
-There were twenty-one trials in total, one for each property. No filler
-trials were used. Trials were presented in a randomized order.
-
+Participants responded by filling in a text box with their response for
+twenty-one trials in total, one for each property. No filler trials were
+used. Trials were presented in a randomized order.
+
+\hypertarget{free-production-data-processing}{%
 \subsubsection{Free production data
-processing}\label{free-production-data-processing}
-
-To process the free production, we forced all characters in a repsonse
+processing}\label{free-production-data-processing}}
+
+To process the free production, we forced all characters in a response
 to lower case, removed spaces, and made all terms into singular terms
 (e.g., \enquote{lions} --\textgreater{} \enquote{lion}). As well,
-\enquote{mosquito} was a commonly mispelled label; we counted anything
+\enquote{mosquito} was a commonly misspelled label; we counted anything
 that started with \enquote{mosqu}, \enquote{mesqu}, \enquote{misqu},
@@
 
-\subsection{Results and Evaluation}\label{results-and-evaluation}
+\hypertarget{results-and-evaluation}{%
+\subsection{Results and Evaluation}\label{results-and-evaluation}}
 
@@
 desiderata outlined above. To evaluate each measure, we selected four
-example property--category pairs that we believe are unambiguously
+example property--category pairs that we believe are unambiguous
 instances of the boundary conditions described above (these items are
@@
 
-Figure \ref{fig:cv-bothquestions-barplots} (top) shows the results for
-the twelve items of interest for both measurements. We see that for the
-\enquote{false} features, both measures behave as desired (hypothsized
+Figure~\ref{fig:cvBothquestionsBarplots}A shows the results for the
+twelve items of interest for both measurements. We see that for the
+\emph{false features}, both measures behave as desired (hypothesized
 results shown by the dotted line): The cue validity of a feature that is
-false is zero or near-zero. For \enquote{diagnostic} features, both
-measures also behave reasonably: Learning that an entity has malaria
-strongly implies that it is a mosquito. However, there is some evidence
-that the free production measurement is more sensitive than the
-direct-question measure. \enquote{Having a mane} is strongly diagnostic
-for a \enquote{lion} but also for a \enquote{horse} (and so the overall
-cue validity for lion is around 0.5). \enquote{Carrying Lyme disease} is
-mostly diagnostic for a \enquote{tick} but also \enquote{deer} (and
-thus, the cue validity for tick is not maximal). These subtle
-differences among \enquote{diagnostic} features is picked up by the
-free-production measure but not by the direct-question measure.
-
-The measures deviate most strongly, however, in their characterization
-of the undiagnostic features. Learning that an entity is female should
-not strongly imply that it is a robin, which is accurately reflected in
-the free production measure but not in the direct question measure. A
-similar phenomenon can be observed in direct question measure for the
-other undiagnostic features. Figure \ref{fig:cv-bothquestions-barplots}
-(bottom left) shows the raw empirical distributions of responses for the
-direct question measure. We observe suggestive evidence that
-participants respond to this question for unidagnostic features in one
-of two ways: (i) reporting near-0 likelihood (accurate response) or (ii)
-reported near-0.5 likelihood. This latter response option may be a
-pragmatic effect of asking the direct question and/or participants
-\enquote{opting out} of a response. For example, in response to the
-question \enquote{There is a thing that is female. What are the odds
-that it is a robin?}, a reasonable human response may be \enquote{I
-don't know}. Participants may cope with the awkwardness of the question
-by placing the slider bar in the middle of the scale.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/cv-bothquestions-barplots-1.pdf}
-\caption{\label{fig:cv-bothquestions-barplots}Top: Empirically measured cue
-validity for two different tasks. Items are grouped by whether the
-property is never present in the category (false), the property is
-always present in the category and every other category (undiagnostic),
-or present in the category and absent from most other categories
-(diagnostic). Dotted lines denote theoretical cue validity representing
-the desiderata (see text). Error bars denote bootstrapped 95\%
-confidence intervals. Bottom left: Raw empirical distributions for
-direct question task. Bottom right: Correspondence between measured cue
-validity and prevalence prior derived cue validity.}
+not present in the category is zero or near-zero. For \emph{diagnostic
+features}, both measures also behave reasonably: Learning that an entity
+has malaria strongly implies that it is a mosquito. However, there is
+some evidence that the free production measurement is more sensitive
+than the direct-question measure. \enquote{Having a mane} is strongly
+diagnostic for a \enquote{lion} but also for a \enquote{horse} (and so
+the overall cue validity of having a mane for a lion is around 0.5).
+\enquote{Carrying Lyme disease} is mostly diagnostic for a
+\enquote{tick} but also \enquote{deer} (and thus, the cue validity for
+tick is not maximal). These subtle differences among diagnostic features
+are picked up by the free-production measure but not by the
+direct-question measure.
+
+The free production and direct question measures deviate most strongly
+in their characterization of the undiagnostic features. Learning that an
+entity is female should not imply that it is a robin, which is
+accurately reflected in the free production measure but not in the
+direct question measure. Figure~\ref{fig:cvBothquestionsBarplots}B shows
+the raw empirical distributions of responses for the direct question
+measure for undiagnositic features. We observe that participants respond
+to this question for undiagnostic features in one of two ways: (i)
+reporting near-0 likelihood (hypothesized response) or (ii) reported
+near-0.5 likelihood. This latter response option may reflect
+participants \enquote{opting out} of a response (e.g., signalling
+\enquote{I don't know}). For example, in response to the question
+\enquote{There is a thing that is female. What are the odds that it is a
+robin?}, a person could say they have no evidence to suggest that it is,
+besides the very fact that the experimenter asked the question.
+Participants may cope with the awkwardness of the question by placing
+the slider bar in the middle of the scale.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{figs/cvBothquestionsBarplots-1} \caption{A: Empirically measured cue validity for two different tasks.
+Items are grouped by whether the property is never present in the category (false), the property is always present in the category and every other category (undiagnostic), or present in the category and absent from most other categories (diagnostic).
+Dotted lines denote theoretical cue validity representing the desiderata (see text).
+B: Raw empirical distributions for the undiagnostic features in the direct question task.
+C: Correspondence between measured cue validity and prevalence prior derived cue validity.}\label{fig:cvBothquestionsBarplots}
 \end{figure}
 
+\hypertarget{comparison-with-prevalence-prior-derived-cue-validity}{%
 \subsection{Comparison with prevalence prior derived cue
-validity}\label{comparison-with-prevalence-prior-derived-cue-validity}
+validity}\label{comparison-with-prevalence-prior-derived-cue-validity}}
 
@@
 cue validity derived from our prevalence prior elicitation task (Expt.
-1a). Expt. 1a is not perfectly designed for this comparison, as we
+1b). Expt. 1b is not perfectly designed for this comparison, as we
 supplied participants with half of the animal categories that they rated
 (the other half was freely generated by participants); including these
-supplied categories was important to measure referent-prevalence of
+supplied categories was important to measure the referent-prevalence of
 interest (e.g., the percentage of mosquitos that carry malaria).
@@
 
-In this analysis, we treat each category entry from Expt. 1a
+In this analysis, we treat each category entry from Expt. 1b
 (participant free production or experimentally supplied category like
-mosquitos) as contributing to the prevalence prior. This will result in
-the prevalence prior favoring kinds that are easy to produce (like dogs
-and cats, which is plausibly a good approximation for \(P(k)\)) as well
-as favoring the experimentally supplied kinds (like mosquitos and
-robins).
+mosquitos) as contributing to the prevalence prior. This results in the
+prevalence prior favoring kinds that are easy to produce (like dogs and
+cats; plausibly a good approximation for \(P(k)\)) as well as favoring
+the experimentally supplied kinds (like mosquitos and robins).
 
 We compute cue validity from the prevalence prior using Bayes' rule.
-Figure \ref{fig:cv-bothquestions-barplots} (bottom right) shows the two
-measurements of cue validity as they relate to the prevalence prior
-derived cue validity. The prevalence prior derived cue validity is
-highly associated with both measurements: \(r_{direct}^2(30) = 0.781\);
-\(MSE_{direct} = 0.0482\) and \(r_{free}^2(30) = 0.728\);
-\(MSE_{free} = 0.0265\). Of primary interest is how the measurements
-behave for desiderata items. We see that the prevalence prior derived
-cue validity converges with the free production measurement for the
-desiderata items (\(r_{free}^2(12) = 0.957\); \(MSE_{free} = 0.00778\)),
-whereas the direct question measurement overestimates the cue validity
-of undiagnositic features (\(r_{direct}^2(12) = 0.776\);
-\(MSE_{direct} = 0.0567\)).
+Figure~\ref{fig:cvBothquestionsBarplots}C shows the two measurements of
+cue validity as they relate to the prevalence prior derived cue
+validity. Across the thirty property--category pairs, the prevalence
+prior derived cue validity is highly associated with both measurements:
+\(r_{direct}^2(30) = 0.782\); \(MSE_{direct} = 0.0481\) and
+\(r_{free}^2(30) = 0.739\); \(MSE_{free} = 0.0244\). Of primary interest
+is how the measurements behave for desiderata items. We see that the
+prevalence prior derived cue validity converges with the free production
+measurement for the desiderata items (\(r_{free}^2(12) = 0.947\);
+\(MSE_{free} = 0.00822\)), whereas the direct question measurement
+overestimates the cue validity of undiagnositic features
+(\(r_{direct}^2(12) = 0.779\); \(MSE_{direct} = 0.0561\)).
 
@@
 free-production measure gives the item low cue validity (two black
-points in Fig. \ref{fig:cv-bothquestions-barplots} (right scatterplot)
-high X-value, low Y-value). These two items are: (\enquote{is red},
-\enquote{cardinal}) and (\enquote{is white}, \enquote{swan}). These
-items should have low relatively cue validity and are overestimated by
-the prevalence prior because of the prior on categoryies \(P(k)\) (i.e.,
-because they were supplied to every participant and thus get a higher
-weighted in the prior for deriving cue validity). In comparison, the
-direct question measurement consistently overestimates cue validity
-relative to the prevalence prior.
-
-\subsection{Summary}\label{summary}
+points in Figure~\ref{fig:cvBothquestionsBarplots}C, high X-value, low
+Y-value). These two items are: (\enquote{is red}, \enquote{cardinal})
+and (\enquote{is white}, \enquote{swan}). These items should have
+relatively low cue validity and are overestimated by the prevalence
+prior because of the prior on categories \(P(k)\) over-represents the
+categories that were supplied to every participant and thus get a higher
+weighted in the prior for deriving cue validity.\footnote{This deviation
+  could be reduced in future experiments by performing a fully free
+  production version of the prevalence prior task (i.e., without
+  supplying the referent categories).} In comparison, the direct
+question measurement overestimates cue validity for almost all of the
+items relative to the cue validity derived from the prevalence prior.
+
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
 
 \emph{Cue validity} is a commonly used measurement for understanding
-generic truth conditions. Because we observe different measurements
-being used in the literature, we articulated three \emph{a priori}
-desiderata to validate a measure of cue validity. We found that the
-\enquote{free production} measurement (i.e., having participants
-generate categories given a feature), and not the direct question
-measurement (i.e., asking participants a likelihood judgment of the
-category given the feature), satisfied all three boundary conditions. In
-addition, cue validity derived from our prevalence prior measurement
-(Expt. 1a) also satisfied these boundary conditions. We conclude that
-researchers interested in generic truth conditions should use a free
-production paradigm for measuring cue validity.
+generic truth judgments (e.g., Khemlani et al., 2012; Prasada et al.,
+2013). We observed different measurements used in the literature and
+articulated three \emph{a priori} desiderata to validate a measure of
+cue validity. We found that the \enquote{free production} measurement
+(i.e., participants freely produced categories given a feature), and not
+the direct question measurement (i.e., participants provide a likelihood
+judgment of a particular category given the feature), satisfied all
+three boundary conditions. In addition, cue validity derived from our
+prevalence prior measurement (Expt. 1b) also satisfied these boundary
+conditions. Researchers interested in comparing cue validity to generic
+truth judgments should use a free production paradigm for measuring cue
+validity.
 
@@
 
+\hypertarget{appendix-c-bayesian-data-analysis}{%
 \section{Appendix C: Bayesian Data
-Analysis}\label{appendix-c-bayesian-data-analysis}
+Analysis}\label{appendix-c-bayesian-data-analysis}}
 
@@
 generalizations in language. The model has a single free parameter: the
-optimality parameter in Eq. \ref{eq:S1}. Other model parameters
-(governing the prevalence prior \(P(h)\) and the referent-prevalence
-\(h'\)) are estimated using additional behavioral data (e.g., prior
-elicitation tasks). Througout the paper, we model all sources of data
-(prevalence prior data, endorsement data) using a single joint-inference
-Bayesian data analytic model. In this appendix, we describe this
+optimality parameter \(\lambda\) in Eq. \ref{eq:S1}. We analyze this
+model using a Bayesian data analytic approach, where we jointly infer
+this single model parameter \(\lambda\) together with parameters that
+govern the prevalence priors \(P(p)\) (Eq. \ref{eq:L0}) and referent
+prevalence \(p\) (Eq. \ref{eq:S1}) for each item. To pin down the
+prevalence prior and referent prevalence parameters, we use additional
+data directly related to those parameters (e.g., prior elicitation
+data). Incorporating all data sources into a single Bayesian data
+analysis model is the appropriate way to track measurement uncertainty
+for all measurements simultaneously. In this appendix, we describe this
 procedure in more detail for each case study.
 
+\hypertarget{modeling-prevalence-priors}{%
 \subsection{Modeling prevalence
-priors}\label{modeling-prevalence-priors}
+priors}\label{modeling-prevalence-priors}}
 
 In Case Study 1: Generic Language (Expt. 1b), we elicited the prevalence
-prior by asking about individual about the prevalence of features for
-individual categories. We performed an analagous elicitation in Case
+prior by asking participants about the prevalence of features for
+individual categories. We performed an analogous elicitation in Case
 Study 3: Causal Language (Expt. 3a). We describe the analysis using
 generics as our running example, but a parallel analysis was done for
-causals.
-
-Participants' responses can be thought of as \emph{samples} from the
-prevalence prior distribution. Formally, we assume the prior data
-(analyzed independently for each property) was generated from one of two
-distributions: a distribution corresponding to those kinds with a stable
-causal mechanism that \emph{could} give rise to the property
-(\(\mathcal{D}_{stable}\)) and a \enquote{transient cause} distribution
-corresponding to those kinds without a stable mechanism
-(\(\mathcal{D}_{transient}\)). The \enquote{transient} distribution
-intuitively corresponds to accidental causes of the feature (e.g., a
-lion, who through some genetic mutation, reproduces by laying eggs). We
-model this distribution as a Beta distribuition that heavily favors
-probabilities near 0:
+causal language.
+
+Participants' responses in the prior elicitation task can be thought of
+as samples from the prevalence prior distribution. Formally, we assume
+the prior data (analyzed independently for each property) was generated
+from one of two underlying distributions: a distribution corresponding
+to those kinds with a stable causal mechanism that \emph{could} give
+rise to the property (\(\mathcal{D}_{stable}\)) and a \enquote{transient
+cause} distribution corresponding to those kinds without a stable
+mechanism (\(\mathcal{D}_{transient}\)). The \enquote{transient}
+distribution intuitively corresponds to categories that do not have the
+feature normally, but potentially could acquire the feature by
+accidental forces (e.g., a lion, who through some genetic mutation,
+reproduces by laying eggs). We model this distribution as a Beta
+distribuition that heavily favors probabilities near 0:
 \(\text{Beta}(\gamma = 0.01, \delta = 100)\).\footnote{Note that we use
@@
   Adjusting 1 to \(1- \epsilon\) leads to improper inferences for this
-  model, as \(1 - \epsilon\) is only likely under a highly right-skewed
-  distribution; treating 1 as \(1- \epsilon\) disproportionately
-  influences the shape of \(\mathcal{D}_{stable}\) relative to other
-  responses. This problem does not appear for 0 being adjusted to
-  \(\epsilon\) because the \enquote{transient} distribution already
-  expects such low values.} Finally, we assume that these two components
-combine with mixture weighting \(\phi\) such that the data we observe is
+  simple 2-component model, as \(1 - \epsilon\) is only likely under a
+  highly left-skewed distribution; treating 1 as \(1- \epsilon\)
+  disproportionately influences the shape of \(\mathcal{D}_{stable}\),
+  forcing it to favor probabilities close to 1. This problem does not
+  appear for 0 being adjusted to \(\epsilon\) because the
+  \enquote{transient} distribution already expects such low values.}
+Finally, we assume that these two components combine with mixture
+weighting \(\phi\) such that the data we observe is
 \[P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) \].
 We put the following priors over the latent parameters of the model:
-
 \begin{eqnarray*}
@@
 \xi_i & \sim & \text{Uniform}(0, 100)
-\end{eqnarray*}
-
-where \(i\) ranges over the different properties (e.g., \emph{lays
-eggs}, \emph{carries malaria}).
+\end{eqnarray*} where \(i\) ranges over the different properties (e.g.,
+\emph{lays eggs}, \emph{carries malaria}).
 
@@
 data. We construct a posterior predictive distribution by
-\enquote{forward sampling} the model.\footnote{This can be described by
-  the following algorithm: First, flip a coin weighted by \(\phi\). If
-  it comes up heads, we then sample from the \enquote{stable} component:
-  \(\text{Beta}(\gamma, \xi)\). If it comes up tails, we sample from the
-  \enquote{transient} component: \(\text{Beta}(0.01, 100)\). We do this
-  many times using the posterior distibution to generate a distribution
-  over predicted prevalence ratings.}
-
-In Case Study 2 (Expt. 2a), we asked participants about parameters of
-this mixture model (by having participants answer questions abouut
-\emph{different kinds of people}) rather than having participants give
-samples (e.g., by listing their friends and rating how often their
-friends did certain actions). In pilot testing, we found these different
-methodologies to give similar results. We made the decision to ask more
-abstract information about the events to get at participants' abstract
-beliefs about the property rather than their knowledge of true
-frequencies. As well, by querying about abstract characters, we were
-able to include items that participants might not otherwise feel
-comfortable reporting off (e.g., how often their friends smoke
-marijuana). The questions used to elicit information about the
-parameters are described in the main text.
-
+\enquote{forward sampling} the model (i.e., generating new data given
+the inferred parameter values).\footnote{This forward sampling can be
+  described by the following algorithm: First, flip a coin weighted by
+  \(\phi\). If it comes up heads, we then sample from the
+  \enquote{stable} component: \(\text{Beta}(\gamma, \xi)\). If it comes
+  up tails, we sample from the \enquote{transient} component:
+  \(\text{Beta}(0.01, 100)\). We do this many times using the posterior
+  distibution to generate a distribution over predicted prevalence
+  ratings.} Representative posterior predictive results are shown in
+Figure~\ref{fig:generic-endorsement-priors-figure}B (main text).
+
+In Case Study 2 on habitual language (Expt. 2a), we asked participants
+about parameters of this mixture model (by having participants answer
+questions about different kinds of people) rather than having
+participants give samples (e.g., by listing their friends and family
+members, and rating how often they did certain actions). In pilot
+testing, we found these different methodologies to give comparable
+results and we opted to ask about hypothetical people to probe about
+potentially undesirable habits of participants' friends and familiy
+(e.g., how often they use cocaine). The questions used in this
+structured elicitation task are described in the main text.
+
+\hypertarget{modeling-referent-prevalence}{%
 \subsection{Modeling
-referent-prevalence}\label{modeling-referent-prevalence}
-
-In Case Study 1, we used participants prevalence ratings for the
-category-of-interest in our generic sentences as the referent-prevalence
-that is used in the endorsement model (Eq. \ref{eq:S1}). For a given
-generic sentence (e.g., \enquote{Robins lay eggs}), we took the
-prevalence ratings for the referent-category (e.g., the percentage of
-robins that lay eggs) from the prior elicitation task (Expt. 1b) and
-assumed those were generated from a single Beta distribution. We used
-the same priors as we did for the \emph{stable cause} component of the
-prevalence prior:
-
+referent-prevalence}\label{modeling-referent-prevalence}}
+
+In Case Study 1 (generics), we used participants prevalence ratings for
+the category-of-interest in our generic sentences as the
+referent-prevalence that is used in the endorsement model (Eq.
+\ref{eq:S1}). For a given generic sentence (e.g., \enquote{Robins lay
+eggs}), we took the prevalence ratings for the referent-category (e.g.,
+the percentage of robins that lay eggs) from the prior elicitation task
+(Expt. 1b) and assumed those were generated from a single Beta
+distribution. We assumed the following priors on the parameters:
 \begin{eqnarray*}
@@
 \xi_i & \sim & \text{Uniform}(0, 100)
-\end{eqnarray*}
-
-We took samples from the posterior predictive of this Beta distribution
-(i.e., reconstructed prevalence ratings) as the
+\end{eqnarray*} We took samples from the posterior predictive of this
+Beta distribution (i.e., reconstructed prevalence ratings) as the
 \emph{referent-prevalence} used in the model.
@@
 we compared two endorsement models that differed in their representation
-of referent-prevalence. For one model (past frequency model), it was the
-frequency given to participants in the experimental prompt (same as in
-Expt. 2b); for the other model (predictive frequency model), we used the
-mean elicited frequency from the \emph{predictive frequency} condition
-(see main text). In Case Study 3 (Causal endorsement), we used the
-proportion of successful causal events given to participants in the
-experimental prompt (e.g., 70 out of 100 uses of Herb C made animals
-sleepy).
-
+of referent-prevalence. For one model (past frequency model), the actual
+frequency given to participants in the experimental prompt was assumed
+to be the referent prevalence (same as in Expt. 2b); for the other model
+(predictive frequency model), we used the mean elicited frequency from
+the \emph{predictive frequency} condition (participants predictions
+about how often the person would do the action in the next time
+interval; see main text for details). In Case Study 3 (Causal
+endorsement), we used the proportion of successful causal events given
+to participants in the experimental prompt (e.g., 70 out of 100 uses of
+Herb C made animals sleepy).
+
+\hypertarget{jointly-modeling-referent-prevalence-prevalence-priors-and-generic-endorsements}{%
 \subsection{Jointly modeling referent-prevalence, prevalence priors, and
 generic
-endorsements}\label{jointly-modeling-referent-prevalence-prevalence-priors-and-generic-endorsements}
+endorsements}\label{jointly-modeling-referent-prevalence-prevalence-priors-and-generic-endorsements}}
 
@@
 above) to create a single, joint-inference model where the optimality
-parameter \(\lambda_1\) (Eq. \ref{eq:S1}) is inferred jointly with all
-the other latent parameters of the full model (the referent-prevalence
-\(h'_{k, f}\) for each category \(k\) and property \(f\) and the
-parameters of the prevalence priors \(P_f(h)\) for each property \(f\))
-using data from Expt. 1a \& b (Figure \ref{fig:genericsModelDiagram}).
-For the parameters of the prevalence prior distributions, we use the
-same priors described in Expt. 1b; for the speaker optimality parameter,
-we use a prior with a range consistent with previous literature using
-the same model class: \(\lambda_1 \sim \text{Uniform}(0,5)\). We learn
-about the \emph{a posteriori} credible values of the joint inference
-models by collecting samples from 3 MCMC chains of 100,000 iterations
-removing the first 50,000 iterations for burn-in, using an
-incrementalized version of the Metropolis-Hastings algorithm (Ritchie et
-al., 2016).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figs/generics_bayesnetmodel.pdf}
-\caption{\label{fig:genericsModelDiagram}Graphical model corresponding to
-the fully Bayesian data analysis of the RSA model. The prevalence prior
-data \(d^{pr}_{f}\) is assumed to be generated from the mixture model
-validated in Expt. 1a. The referent-category prevalence \(d^{pr}_{k,f}\)
-is generated from a latent prevalence \(p_{fk}\). The fixed-threshold
-(control model) or uncertain-threshold model take the prevalence priors
-\(P_f(h)\), the referent-prevalence \(h\), and a single speaker
-optimality parameter \(\lambda\) as input. This overall structured is
-repeated (except \(\lambda\)) for each of the unique properties \(f\)
-and categories \(k\) that correspond to the generic sentences in our
-stimulus set. Note that S corresponds to a probabilistic \emph{function}
-and not a \emph{random variable} that is standard in graphical model
-notation; S cannot be represented by a graphical model because it has
-recursion.}
+parameter \(\lambda\) (Eq. \ref{eq:S1}) is inferred jointly with all the
+other latent parameters of the full model (the referent-prevalence \(p\)
+for each category \(k\) and property \(f\) and the parameters of the
+prevalence priors \(P(p)\) for each property \(f\)) using data from
+Expt. 1a \& b (Figure \ref{fig:genericsModelDiagram}). For the
+parameters of the prevalence priors, we use the same priors described in
+Expt. 1b; for the speaker optimality parameter, we use a prior with a
+range consistent with the previous literature that uses the same model
+class: \(\lambda \sim \text{Uniform}(0,5)\). We learn about the
+\emph{a posteriori} credible values of the joint inference models by
+collecting samples from 3 MCMC chains of 150,000 iterations removing the
+first 50,000 iterations for burn-in, using an incrementalized version of
+the Metropolis-Hastings algorithm (Ritchie et al., 2016). This algorithm
+is useful for models with many variables that only affect a subset of
+the full model's predictions (e.g., models with by-item or
+by-participant parameters, wherein those additional parameters only
+influence predictions for those items or participants).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\textwidth]{figs/generics_bayesnetmodel}
+
+}
+
+\caption{Quasi-graphical model corresponding to the fully Bayesian data analysis of the endorsement model for Case Study 1 (generic language).
+The prevalence prior data $d^{pr}_{f}$ is assumed to be generated from the mixture model validated in Expt.
+1a, which has three parameters: mean of the stable-cause distribution $\gamma_{f}$ and concentration (inverse-variance) of the stable-cause distribution $\xi{f}$ and the mixture parameter $\phi_{f}$.
+The referent-prevalence $d^{pr}_{k,f}$ is generated from a Beta distribution with paramters: mean $\gamma_{k,f}$ and concentration (inverse-variance) $\xi{k,f}$.
+The posterior predictives of the prevalence prior $P(p_{fk'})$ and the referent prevalence $p_{fk}$ are then fed into the RSA speaker model $S$, which predicts the generic endorsement data $d^{end}_{k, f}$.
+The speaker model $S$ also takes in the single free parameter $\lambda$ which operates as a soft-max function.
+This overall structured is repeated (except $\lambda$) for each of the unique properties $f$ and categories $k$ that correspond to the generic sentences in our stimulus set.
+Note that $S$ corresponds to a probabilistic function and not a random variable that is standard in graphical model notation; $S$ cannot be represented by a graphical model because it has recursion.
+This entire BDA model is duplicated for the lesioned, fixed-threshold model (which only differs in the definition of $S$).
+The BDA model for habituals and causals mirrors this one, except they do not infer a referent prevalence $p_{fk}$ (they are assumed to be the same as those experimentally supplied to participants).}\label{fig:genericsModelDiagram}
 \end{figure}
+
+\hypertarget{supplementary-model-criticism}{%
+\subsection{Supplementary model
+criticism}\label{supplementary-model-criticism}}
 
@@
 referent-prevalence. These marginal distributions are important to
-examine to confirm that they have not changed significantly from the
-parameters inferred from their private data sources in isolation. For
-example, when modeling the referent-prevalence data in isolation, the
-model infers that roughly 50\% of robins lay eggs, as that is what
-participants tend to say in the prevalence elicitation task.\footnote{Some
-  participants do report that 100\% of robins lay eggs so the average
-  prevalence rating is closer to 65\%..}. The question for this joint
-inference model is whether or not it still believes that roughly 50\% of
-robins lay eggs. We found that the referent-prevalences and prevalence
-priors inferred under the joint model were almost indistinguishable from
-those inferred using only their data, suggesting that the modeling all
-three data sources together does not come at the cost of modeling any
-one of them accurately.
+confirm that they have not changed substantially from the parameters
+inferred from their primary data sources in isolation. For example, when
+modeling the referent-prevalence data in isolation, the model infers
+that roughly 65\% of robins lay eggs, as that is what participants on
+average produce in the prevalence elicitation task.\footnote{Most
+  participants report that 50\% of robins lay eggs, while a minority
+  respond 100\%.} If the joint inference model (which models all data
+sources---referent prevalence, prevalence prior, and generic
+endorsement---simultaneously) infers referent-prevalence values
+substantially different from those inferred by a model of referent
+prevalence in isolation, that would suggest that the joint-model is
+distorting the prevalence parameters to accommodate the endorsement
+data. Such a result would call into question the inferences we as
+scientists derive from the joint inference model. For example,
+incorporating a linear regression model (of the kind presented as
+alterantive models in the main text) into this Bayesian joint-inference
+analysis model produces posterior predictions that match the generic
+endorsement data surprisingly well (e.g., that model predicts
+\enquote{Robins lay eggs} is true). Such a model is only able to do
+this, however, by distorting the referent-prevalence data, inferring
+that 100\% of robins lay eggs; thus, the linear model in this
+joint-inference analysis framework sacrifices its goodness-of-fit to the
+referent-prevalence data in order to increase its goodness-of-fit to the
+endorsement data.\footnote{This distortion effect is why we accout for
+  measurement uncertainty in the linear models by bootstrapping the data
+  that forms their predictors, rather than performing a Bayesian
+  analysis.} Such a distortion manifests as a difference between the
+inferred parameters given only the referent-prevalence data and given
+the full joint model (all data sources simultaneously).
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figs/distortion-1}
+
+}
+
+\caption{No evidence for parameter distortion caused by a joint-inference model.
+X-axis denotes Maximum A-Posteriori (MAP) estimates inferred using only a single data source (A: Prevalence prior data.
+B: Referent prevalence data).
+Y-axis denotes MAP estimates inferred using the joint-inference model which models all data sources simultaneously.
+Distortions would manifest by systematic deviations from the y=x line.}\label{fig:distortion}
+\end{figure}
+
+To investigate this distortion effect in the parameters, we compare the
+values inferred for the parameters governing the prevalence priors and
+referent prevalence variables before and after the joint-inference model
+sees the generic endorsement data. Specifically, we infer the parameters
+for prevalence priors and referent prevalence by constructing single
+models of these tasks and compare the inferred values to those that
+result from the joint-inference model. The inferred parameters for these
+two models are shown in Figure~\ref{fig:distortion}. We found that the
+referent-prevalences and prevalence priors inferred under the joint
+model were almost indistinguishable from those inferred using only the
+referent-prevalence and prevalence prior data, respectively (numerical
+results reported in main text). This results confirms that modeling all
+three data sources simultaneously does not distort some data sources
+(e.g., referent prevalence) in order to provide good fits for others
+(e.g., generic endorsement).
+
+\newpage
+
+\hypertarget{appendix-d-habituals-items}{%
+\section{Appendix D: Habituals Items}\label{appendix-d-habituals-items}}
+
+\begingroup\fontsize{9pt}{10pt}\selectfont
+\begin{longtable}{ |p{1in}|p{1.2in}| p{1.75in}|p{1.75in} |}
+  \hline
+{\bfseries habitual} & {\bfseries referent frequency} & {\bfseries enabling} & {\bfseries preventative} \\ 
+  \hline
+climbs mountains & 5 years*, 2 years, year & Yesterday, William remembered how much fun that was bought a lot of new mountain climbing gear.
+& Yesterday, William turned 80 and gave up all strenuous physical exercise because his doctor said it would be deadly.
+\\
+   \hline
+does cocaine & 5 years, year*, month, week & Yesterday, Tim wanted to get high and bought some cocaine. & Yesterday, William realized he is severely allergic to cocaine and will no longer do it. \\ 
+   \hline
+drinks beer & year, month*, 2 weeks, week & Yesterday, Tim wanted to get tipsy and bought a six-pack of beer. & Yesterday, William gave up alcohol and entered into Alcoholics Anonymous. \\ 
+   \hline
+drinks coffee & year, month*, 2 weeks, week & Yesterday, William wanted a morning jolt and bought a pound of fresh roasted coffee.
+& Yesterday, Veronica developed a caffeine allergy and decided to give up all caffeine.
+\\
+   \hline
+eats caviar & 5 years*, year, month & Yesterday, William learned about the dietary benefits of eating caviar and bought a jar at the supermaket. & Yesterday, Tina developed a seafood allergy. \\ 
+   \hline
+eats peanut butter & 5 years, year*, month & Yesterday, Veronica learned about the dietary benefits of eating peanut butter and bought a jar at the supermaket.
+& Yesterday, Ted developed a peanut allergy.
+\\
+   \hline
+goes to the ballet & 2 years, year, month &  &  \\ 
+   \hline
+goes to the movies & 2 years, year, month &  &  \\ 
+   \hline
+hikes & 2 years, year*, 2 months, week & Yesterday, William remembered how much fun those times were and bought a lot of new hiking gear.
+& Yesterday, Vince was in a motorcycle accident and will never walk again.
+\\
+   \hline
+listens to live music & year, month, week &  &  \\ 
+   \hline
+listens to Pandora & year, month, week &  &  \\ 
+   \hline
+plays tennis & 5 years, 2 years, year* & Yesterday, Tim remembered how much fun that was and bought a new tennis racket.
+& Yesterday, William developed crippling arthritis in both elbows and can only move his arms extremely slowly.
+\\
+   \hline
+plays the banjo & 5 years, 2 years, year* & Yesterday, William remembered how much fun that was and joined his friend\&quotechars band as the banjoist.
+& Yesterday, William developed crippling arthritis in his hands and no longer can play musical instruments.
+\\
+   \hline
+runs & 2 years, year, 2 months*, week & Yesterday, Vince remembered how much fun those times were and bought a new pair of running shoes.
+& Yesterday, Veronica was in a car accident and became permanently paralyzed from the waist down.
+\\
+   \hline
+sells companies & 5 years, year &  &  \\ 
+   \hline
+sells things on eBay & 5 years, year &  &  \\ 
+   \hline
+smokes cigarettes & year, month*, week & Yesterday, Tina wanted a smoke and bought a pack of cigarettes. & Yesterday, Vince quit smoking cigarettes. \\ 
+   \hline
+smokes marijuana & 5 years, year*, month, week & Yesterday, William wanted to get high and bought some marijuana.
+& Yesterday, Vince realized he is severely allergic to marijuana and will no longer smoke it.
+\\
+   \hline
+steals cars & 5 years*, year, month & Yesterday, William learned a new technique for breaking into cars.
+& Yesterday, Tina got caught and went through a radical transformation, vowing to never break the law again.
+\\
+   \hline
+steals chewing gum & 5 years*, year, month & Yesterday, Vince learned a new trick to distract shopkeepers. & Yesterday, William got caught and vowed to never break the law again. \\ 
+   \hline
+volunteers for political campaigns & 5 years*, year & Yesterday, Vince researched a new political candidate in the area and is going to volunteer with them.
+& Yesterday, Vince grew disillusioned with the political system and wants nothing to do with it anymore.
+\\
+   \hline
+volunteers for soup kitchens & 5 years*, year & Yesterday, Vince researched a new soup kitchen in the area and is going to volunteer with them.
+& Yesterday, Tom grew disillusioned with the soup kitchen system and wants nothing to do with it anymore.
+\\
+   \hline
+watches professional football & 2 years, year*, month & Yesterday, William remembered how much enjoyable that was and upgraded his cable to have access to all professional football games.
+& Yesterday, Veronica learned about all the corruption in professional sports and no longer can watch it.
+\\
+   \hline
+watches space launches & 2 years*, year, month & Yesterday, William remembered how much enjoyable that was and researched all of the space launches in the next year within driving distance.
+& Yesterday, William went through a radical transformation and now it is against his belief to witness anything relating to space travel.
+\\
+   \hline
+wears a bra & 6 months, month, week &  &  \\ 
+   \hline
+wears a suit & 6 months, month*, week & Yesterday, Vince got a high paying job on Wall Street. & Yesterday, Veronica got fired from her job on Wall Street and now works in a pizza parlor. \\ 
+   \hline
+wears a watch & 6 months, month, week &  &  \\ 
+   \hline
+wears slacks & 6 months, month, week &  &  \\ 
+   \hline
+wears socks & 6 months, month, week &  &  \\ 
+   \hline
+writes novels & 5 years*, year & Yesterday, William finished an MFA program and quit his other job to focus on writing novels.
+& Yesterday, William became fed up with the literary world and decided to never write anything again.
+\\
+   \hline
+writes poems & 5 years, year* & Yesterday, William finished an MFA program and quit his other job to focus on writing poems.
+& Yesterday, Veronica became fed up with the poetry world and decided to never write poems again.
+\\
+   \hline
+\hline
+\end{longtable}
+\endgroup
+
+Items used in Case Study 2 (Habitual language). Referent frequency
+denotes the experimentally supplied time periods during which a person
+did an action 3 times (e.g., \enquote{In the past 5 years, John climbed
+mountains three times.}; Expt. 2b). Enabling and preventative columns
+provide the causal manipulation sentences used in Expt. 2c in order to
+enable or prevent future instances of the action (blank entries indicate
+that the item was not used in Expt. 2c). Referent frequency with an
+asterisk denotes the time interval used in Expt. 2c.
 

### 2018-12-11 experiments/causals/js/causals-1.js
update readme, gitignore, add expts

@@ -1,0 +1,353 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past)
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+
+      // show prior questions and responses
+      $(".question0").show();
+      $("#slider_table0").show();
+      $(".question1").show();
+      $("#slider_table1").show();
+      $("#prior_number").show();
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+
+      // which half of trial we're in
+      this.switch = true;
+      this.stim = stim;
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
+      this.startTime = Date.now();
+
+      // replace CATEGORY, EXEMPLAR, TREATMENT, PAST from stimuli
+      var story = replaceTerms(stim, "storyline")
+
+      var existential_question = replaceTerms(stim, "existentialQuestion")
+
+      var prevalence_question = replaceTerms(stim, "prevalenceQuestion")
+
+
[…]

### 2018-12-11 experiments/causals/js/causals-2.js

@@ -1,0 +1,403 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      // $("#speaker_choices").hide();
+      // $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+
+      // which half of trial we're in
+      // this.switch = true;
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
+      this.startTime = Date.now();
+
+      // replace CATEGORY, EXEMPLAR, TREATMENT, PAST from stimuli
+      var story = replaceTerms(stim, "storyline")
+
[…]

### 2018-12-11 experiments/causals/js/causals-3.js

@@ -1,0 +1,395 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      this.count = 0;
+      // which half of trial we're in
+      // this.switch = true;
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
+      this.startTime = Date.now();
+
[…]

### 2018-12-11 experiments/causals/js/causals-4.js

@@ -1,0 +1,413 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
+      // this.switch = true;
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
+      this.startTime = Date.now();
+
[…]

### 2018-12-11 experiments/causals/js/causals-5.js

@@ -1,0 +1,461 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+      $("#multi_slider_table").hide();
+      $(".left").hide()
+      $(".right").hide()
+
+
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
+      // this.switch = true;
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
[…]

### 2018-12-11 experiments/causals/js/causals-6.js

@@ -1,0 +1,540 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+      $("#multi_slider_table").hide();
+      $(".left").hide()
+      $(".right").hide()
+
+
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      $("#nextExptButton").html("Look at results of next experiment");
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
+      // this.switch = true;
[…]

### 2018-12-11 experiments/causals/js/causals-7-endorsement.js

@@ -1,0 +1,566 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+      $("#multi_slider_table").hide();
+      $(".left").hide()
+      $(".right").hide()
+
+
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      $("#nextExptButton").html("Look at results of next experiment");
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
[…]

### 2018-12-11 experiments/causals/js/causals-7-interpretation.js

@@ -1,0 +1,566 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+      $("#multi_slider_table").hide();
+      $(".left").hide()
+      $(".right").hide()
+
+
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      $("#nextExptButton").html("Look at results of next experiment");
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
[…]

### 2018-12-11 experiments/causals/js/causals-7-prior.js

@@ -1,0 +1,566 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+    button : function() {
+        exp.go();
+    }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
+      $("#prior_number").hide();
+      $("#multi_slider_table").hide();
+      $(".left").hide()
+      $(".right").hide()
+
+
+
+      $(".data").show();
+
+      // hide listener/speaker question
+      $(".question2").hide();
+      $(".task_prompt").hide();
+      // hide listener task responses
+      $("#listener_number").hide();
+      $("#slider_table2").hide();
+      // hide speaker task responses
+      $("#speaker_choices").hide();
+      $('input[name="speaker"]').prop('checked', false);
+
+      $(".err").hide();
+      $("#continueButton").hide()
+      $("#evidenceDescription").hide();
+      $("#nextExptButton").show()
+
+      $("#nextExptButton").html("Look at results of next experiment");
+
+      this.count = 0;
+      this.waitFlag = 1;
+      // which half of trial we're in
[…]

### 2018-12-11 experiments/causals/js/causals-8-prior.js

@@ -1,0 +1,594 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+     button : function() {
+         exp.go();
+     }
+  });
+
+  slides.debrief = slide({
+    name : "debrief",
+    start: function() {
+      $(".err").hide();
+     },
+     button : function() {
+       var response = $("#catch").val()
+       var numericResponse = $("#resultRetrieval").val();
+       var passNumeric = parseInt(numericResponse) ?
+          exp.stimscopy[0].data.indexOf(parseInt(numericResponse)) != -1 ? 1 : 0 :0
+       if ( (response == 99) || numericResponse == "") {
+         $(".err").show();
+       } else {
+         var passStory = (response == exp.stimscopy[0].story) ?  1 : 0;
+         // var passNumeric = exp.stimscopy[0].data.indexOf(numericResponse) != -1 ? 1 : 0;
+         exp.catch_trials.push({
+           response_story: response,
+           actual_story: exp.stimscopy[0].story,
+           response_data: numericResponse,
+           pass_story: passStory,
+           pass_numeric: passNumeric
+         })
+         exp.go();
+       }
+     }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
[…]

### 2018-12-11 experiments/causals/js/causals-8.js

@@ -1,0 +1,594 @@
+var replaceTerms = function(stim, label){
+  var prompt = stim[label];
+  return prompt.replace(/CATEGORY/g,
+     stim.category).replace(/EXEMPLAR/g,
+       stim.exemplar).replace(/TREATMENT/g,
+         stim.treatment).replace(/TARGET/g,
+           stim.target).replace(/QUERY/g,
+             stim.query).replace(/UNIT/g,
+               stim.unit).replace(/PAST/g,
+                 stim.past).replace(/SPECIAL/g,
+                 stim.targetTreatment)
+};
+
+var jsUcfirst = function(string) {
+    return string.charAt(0).toUpperCase() + string.slice(1);
+};
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+      $(".err").hide();
+      $("#total-num").html(exp.nTrials);
+     },
+     button : function() {
+         exp.go();
+     }
+  });
+
+  slides.debrief = slide({
+    name : "debrief",
+    start: function() {
+      $(".err").hide();
+     },
+     button : function() {
+       var response = $("#catch").val()
+       var numericResponse = parseInt($("#resultRetrieval").val())
+       if ( (response == 99) || numericResponse == "") {
+         $(".err").show();
+       } else {
+         var passStory = (response == exp.stimscopy[0].story) ?  1 : 0;
+         var passNumeric = exp.stimscopy[0].data.indexOf(numericResponse) != -1 ? 1 : 0;
+         exp.catch_trials.push({
+           response_story: response,
+           actual_story: exp.stimscopy[0].story,
+           response_data: numericResponse,
+           pass_story: passStory,
+           pass_numeric: passNumeric
+         })
+         exp.go();
+       }
+     }
+  });
+
+  slides.prior_elicitation = slide({
+    name: "prior_elicitation",
+
+   // present : _.shuffle(_.range(numTrials)),
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      var prompt, utt;
+      console.log(stim)
+      // show prior questions and responses
+      $(".question0").hide();
+      $("#slider_table0").hide();
+      // $(".question1").show();
+      $("#slider_table1").hide();
[…]

### 2018-12-11 experiments/causals/js/gaussian.js

@@ -1,0 +1,113 @@
+(function(exports) {
+
+  // Complementary error function
+  // From Numerical Recipes in C 2e p221
+  var erfc = function(x) {
+    var z = Math.abs(x);
+    var t = 1 / (1 + z / 2);
+    var r = t * Math.exp(-z * z - 1.26551223 + t * (1.00002368 +
+            t * (0.37409196 + t * (0.09678418 + t * (-0.18628806 +
+            t * (0.27886807 + t * (-1.13520398 + t * (1.48851587 +
+            t * (-0.82215223 + t * 0.17087277)))))))))
+    return x >= 0 ? r : 2 - r;
+  };
+
+  // Inverse complementary error function
+  // From Numerical Recipes 3e p265
+  var ierfc = function(x) {
+    if (x >= 2) { return -100; }
+    if (x <= 0) { return 100; }
+
+    var xx = (x < 1) ? x : 2 - x;
+    var t = Math.sqrt(-2 * Math.log(xx / 2));
+
+    var r = -0.70711 * ((2.30753 + t * 0.27061) /
+            (1 + t * (0.99229 + t * 0.04481)) - t);
+
+    for (var j = 0; j < 2; j++) {
+      var err = erfc(r) - xx;
+      r += err / (1.12837916709551257 * Math.exp(-(r * r)) - r * err);
+    }
+
+    return (x < 1) ? r : -r;
+  };
+
+  // Models the normal distribution
+  var Gaussian = function(mean, variance) {
+    if (variance <= 0) {
+      throw new Error('Variance must be > 0 (but was ' + variance + ')');
+    }
+    this.mean = mean;
+    this.variance = variance;
+    this.standardDeviation = Math.sqrt(variance);
+  }
+
+  // Probability density function
+  Gaussian.prototype.pdf = function(x) {
+    var m = this.standardDeviation * Math.sqrt(2 * Math.PI);
+    var e = Math.exp(-Math.pow(x - this.mean, 2) / (2 * this.variance));
+    return e / m;
+  };
+
+  // Cumulative density function
+  Gaussian.prototype.cdf = function(x) {
+    return 0.5 * erfc(-(x - this.mean) / (this.standardDeviation * Math.sqrt(2)));
+  };
+
+  // Percent point function
+  Gaussian.prototype.ppf = function(x) {
+    return this.mean - this.standardDeviation * Math.sqrt(2) * ierfc(2 * x);
+  };
+
[…]

### 2018-12-11 experiments/causals/js/stims-2.js

@@ -1,0 +1,128 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [10, 30, 50, 70],//, 90],
+    prompt: "The experiment with SPECIAL has just finished.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The experiment with SPECIAL has just finished.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think were successfully PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare",
+    data: [0, 10, 0, 0, 0, 15, 0, 0, 0, 0]
+  },
+  {
+    distribution: "gendered",
+    data:[0, 0, 50, 0, 0, 50, 0, 0, 0, 0]
+  },
+  {
+    distribution: "female",
+    data: [50, 50, 50, 50, 50, 50, 50, 50, 50, 50]
+  },
+  {
+    distribution: "biological",
+    data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  },
+  {
+    distribution: "accidental",
+    data: [5, 15, 10, 5, 10, 15, 5, 5, 10, 15, 15]
+  },
+  {
+    distribution: "prevalent",
+    data: [75, 60, 65, 75, 80, 40, 80, 75, 80, 90]
+  }
+]
+
+var stories = [
+  {
+    story: "plants",
+    storyline:  "On this planet, there is an edible plant called CATEGORY and your team has to figure out how CATEGORY grow. Your team runs experiments trying to grow CATEGORY with different chemical compounds.",
+    existentialQuestion: "How likely do you think it is that SPECIAL will grow <emph>at least 1</emph> EXEMPLAR?",
+    prevalenceQuestion: "We know now that at least 1 EXEMPLAR plant was successfully grown with SPECIAL.<br> How many of the remaining 99 do you think will successfully grow?\n",
+    treatment: "compound",
+    target: "makes the plants grow",
+    query: "make the plants grow",
+    past: "grown",
+    unit: "plants"
+  },
+  {
+    story: "bread",
[…]

### 2018-12-11 experiments/causals/js/stims-3.js

@@ -1,0 +1,181 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [20],//, 90],
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "Your team treated 100 CATEGORY with SPECIAL."
+    //" The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The experiment with SPECIAL has just finished.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think were successfully PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare",
+    data: [0, 10, 0, 0, 0, 15, 0, 0, 0, 0]
+  },
+  // {
+  //   distribution: "gendered",
+  //   data:[0, 0, 50, 0, 0, 50, 0, 0, 0, 0]
+  // },
+  // {
+  //   distribution: "female",
+  //   data: [50, 50, 50, 50, 50, 50, 50, 50, 50, 50]
+  // },
+  // {
+  //   distribution: "biological",
+  //   data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  // },
+  {
+    distribution: "accidental",
+    data: [5, 15, 10, 5, 10, 15, 5, 5, 10, 15, 15]
+  },
+  {
+    distribution: "prevalent",
+    data: [75, 60, 65, 75, 80, 40, 80, 75, 80, 90]
+  }
+]
+
+var stories = [
+  // {
+  //   story: "happy animals",
+  //   storyline:  "On this planet, there are animals called CATEGORY and your team wants to figure out what makes CATEGORY happy. Your team runs experiments trying to make CATEGORY happy with different chemical compounds.",
+  //   treatment: "compound",
+  //   target: "makes the animals happy",
+  //   query: "make the animals happy",
+  //   evidence: " were happy",
+  //   past: "happy",
+  //   unit: "animals"
+  // },
+  // {
+  //   story: "wagging tails",
[…]

### 2018-12-11 experiments/causals/js/stims-4.js

@@ -1,0 +1,201 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [20],//, 90],
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "Your team treated 100 CATEGORY with SPECIAL."
+    //" The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The experiment with SPECIAL has just finished.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think were successfully PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare",
+    data: [0, 10, 0, 0, 0, 15, 0, 0, 0, 0]
+  },
+  // {
+  //   distribution: "gendered",
+  //   data:[0, 0, 50, 0, 0, 50, 0, 0, 0, 0]
+  // },
+  // {
+  //   distribution: "female",
+  //   data: [50, 50, 50, 50, 50, 50, 50, 50, 50, 50]
+  // },
+  // {
+  //   distribution: "biological",
+  //   data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  // },
+  {
+    distribution: "accidental",
+    data: [5, 15, 10, 5, 10, 15, 5, 5, 10, 15, 15]
+  }//,
+  // {
+  //   distribution: "prevalent",
+  //   data: [75, 60, 65, 75, 80, 40, 80, 75, 80, 90]
+  // }
+]
+
+var stories = [
+  // {
+  //   story: "happy animals",
+  //   storyline:  "On this planet, there are animals called CATEGORY and your team wants to figure out what makes CATEGORY happy. Your team runs experiments trying to make CATEGORY happy with different chemical compounds.",
+  //   treatment: "compound",
+  //   target: "makes the animals happy",
+  //   query: "make the animals happy",
+  //   evidence: " were happy",
+  //   past: "happy",
+  //   unit: "animals"
+  // },
+  // {
+  //   story: "wagging tails",
[…]

### 2018-12-11 experiments/causals/js/stims-6.js

@@ -1,0 +1,286 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [20],//, 90],
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "Your team treated 100 CATEGORY with SPECIAL."
+    //" The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The experiment with SPECIAL has just finished.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think were successfully PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare",
+    data: [0, 10, 0, 15, 0, 10,0, 0, 0, 0]
+  },
+  // {
+  //   distribution: "gendered",
+  //   data:[0, 0, 50, 50, 0,  50,  0, 0, 0, 0]
+  // },
+  // {
+  //   distribution: "female",
+  //   data: [50, 50, 50, 50, 50, 50, 50, 50, 50, 50]
+  // },
+  // {
+  //   distribution: "deterministic",
+  //   data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  // },
+  // {
+  //   distribution: "accidental",
+  //   data: [5, 15, 10, 5, 10, 15, 5, 5, 10, 15, 15]
+  // }
+  // {
+  //   distribution: "prevalent",
+  //   data: [75, 60, 65, 75, 80, 40, 80, 75, 80, 90]
+  // }
+]
+
+
+var stories = [
+  // {
+  //   story: "batteries",
+  //   storyline:  "You are an astronaut-scientist exploring a distant planet. On this planet, there are aliens and they have electronic devices called CATEGORY and your team of scientists wants to figure out what kind of battery makes CATEGORY work. Your team runs experiments trying to make CATEGORY work with different batteries.",
+  //   treatment: "battery",
+  //   target: "makes the device work",
+  //   query: "make the devices work",
+  //   past: "worked",
+  //   evidence: "had worked",
+  //   unit: "devices"
+  // },
+  {
+    story: "artifact play music",
[…]

### 2018-12-11 experiments/causals/js/stims-7.js

@@ -1,0 +1,293 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [20, 60],
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "Your team treated 100 CATEGORY with SPECIAL."
+    //" The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare_weak",
+    data: [0, 20, 0, 10, 0, 0, 15, 0, 20, 0]
+  },
+  {
+    distribution: "common_weak",
+    data: [10, 20, 15, 10, 15, 20, 10, 10, 15, 20, 20]
+  },
+  {
+    distribution: "rare_strong",
+    data: [75, 0, 65, 0, 80, 90, 0, 0, 80, 90]
+  },
+  {
+    distribution: "common_strong",
+    data: [75, 65, 65, 75, 80, 90, 80, 75, 80, 90]
+  },
+  {
+    distribution: "rare_deterministic",
+    data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  },
+  // {
+  //   distribution: "common_deterministic",
+  //   data: [100, 100, 100, 100, 100, 100, 100, 100, 100, 100, 100]
+  // },
+  {
+    distribution: "weak_or_strong",
+    data: [85, 75, 15, 75, 10, 90, 90, 80, 10, 20]
+  }
+]
+
+
+var stories = [
+  // {
+  //   story: "batteries",
+  //   storyline:  "You are an astronaut-scientist exploring a distant planet. On this planet, there are aliens and they have electronic devices called CATEGORY and your team of scientists wants to figure out what kind of battery makes CATEGORY work. Your team runs experiments trying to make CATEGORY work with different batteries.",
+  //   treatment: "battery",
+  //   target: "makes the device work",
+  //   query: "make the devices work",
+  //   past: "worked",
+  //   evidence: "had worked",
[…]

### 2018-12-11 experiments/causals/js/stims-8.js

@@ -1,0 +1,345 @@
+var preamble = "The results are shown below:"
+
+var tasks = {
+  speaker: {
+    frequencies: [20, 70],
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "Does SPECIAL QUERY?",
+    frequencyStatement: "Your team treated 100 CATEGORY with SPECIAL."
+    //" The number of CATEGORY that were successfully PAST (out of 100) with SPECIAL was:"
+  },
+  listener: {
+    prompt: "The results of the experiment with SPECIAL were found.",
+    utterance: "SPECIAL TARGET.",
+    question: "How many out of 100 UNIT do you think PAST?"
+  }
+}
+
+var rarity = 3; // (how many out of 10 will have it?)
+
+var zeroDist = gaussian(0, 1.2);
+var sampleNull = function(){
+  var s = zeroDist.ppf(Math.random())
+  var si = s > 0 ? s : 0
+  return Math.round(si)
+}
+
+var deterministic = gaussian(100, 3);
+var sampleDeterministic = function(){
+  var s = deterministic.ppf(Math.random())
+  var si = s < 100 ? s : 100
+  return Math.round(si)
+}
+
+var weak = gaussian(20, 2);
+var strong = gaussian(80, 5);
+
+var rare_weak_samples = [], common_weak_samples = [];
+var rare_strong_samples = [], common_strong_samples = [];
+var rare_deterministic_samples = [], common_deterministic_samples = [];
+
+// rare weak distribution
+for (var i=0; i<10; i++){
+  if (i < rarity) {
+    var s = weak.ppf(Math.random())
+    rare_weak_samples.push(Math.round(s));
+  } else {
+    rare_weak_samples.push(sampleNull());
+  }
+}
+
+// common weak
+for (var i=0; i<10; i++){
+  var s = weak.ppf(Math.random())
+  common_weak_samples.push(Math.round(s));
+}
+
+
+// common determinsitic
+for (var i=0; i<10; i++){
+  common_deterministic_samples.push(sampleDeterministic());
+}
+for (var i=0; i<10; i++){
+  if (i < rarity) {
+    rare_deterministic_samples.push(sampleDeterministic());
+  } else {
+    rare_deterministic_samples.push(sampleNull());
+  }
+}
+
+
+// console.log(rare_weak_samples)
+
+var distributions = [
+  {
[…]

### 2018-12-11 experiments/causals/js/stims.js

@@ -1,0 +1,128 @@
+// all of the causes are desirable... what if they are undesirable? (e.g., chemicals killing babies)
+
+var preamble = "The number of UNIT that were successfully PAST (out of 100) are:"
+
+var tasks = {
+  speaker: {
+    frequencies: [10, 30, 50, 70],//, 90],
+    prompt: "The final experiment has finished.",
+    utterance: "It TARGET.",
+    question: "Does it QUERY?",
+    frequencyStatement: "The number of CATEGORY that were successfully PAST (out of 100) with the final TREATMENT were:"
+  },
+  listener: {
+    prompt: "The final experiment has finished.",
+    utterance: "It TARGET.",
+    question: "How many out of 100 UNIT do you think were successfully PAST?"
+  }
+}
+
+
+var distributions = [
+  {
+    distribution: "rare",
+    data: [0, 10, 0, 0, 0, 15, 0, 0, 0, 0]
+  },
+  {
+    distribution: "gendered",
+    data:[0, 0, 50, 0, 0, 50, 0, 0, 0, 0]
+  },
+  {
+    distribution: "female",
+    data: [50, 50, 50, 50, 50, 50, 50, 50, 50, 50]
+  },
+  {
+    distribution: "biological",
+    data: [0, 0, 100, 100, 0, 0, 100, 0, 0, 100, 0]
+  },
+  {
+    distribution: "accidental",
+    data: [5, 15, 10, 5, 10, 15, 5, 5, 10, 15, 15]
+  },
+  {
+    distribution: "prevalent",
+    data: [75, 60, 65, 75, 80, 40, 80, 75, 80, 90]
+  }
+]
+
+var stories = [
+  {
+    story: "plants",
+    storyline:  "On this planet, there is an edible plant called CATEGORY and your team has to figure out how CATEGORY grow. Your team runs 11 experiments, trying to grow CATEGORY with 11 different chemical compounds. In each experiment, your team fed 100 of the plants with 1 of the compounds and recorded how many grew.",
+    existentialQuestion: "How likely do you think it is that the chemical used in this experiment will grow <emph>at least 1</emph> EXEMPLAR?",
+    prevalenceQuestion: "We know now that at least 1 EXEMPLAR plant was successfully grown with this compound.<br> How many of the remaining 99 do you think will successfully grow?\n",
+    treatment: "compound",
+    target: "makes the plants grow",
+    query: "make the plants grow",
+    past: "grown",
+    unit: "plants"
+  },
+  {
+    story: "bread",
[…]

### 2018-12-11 experiments/generics/js/cue-validity-1.js

@@ -1,0 +1,177 @@
+function make_slides(f) {
+  var   slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+     $("#ntrials").html(exp.n_trials)
+   },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.one_slider = slide({
+    name : "one_slider",
+    present : exp.stimuli,
+    present_handle : function(stim) {
+      $(".err").hide();
+      this.startTime = Date.now();
+      this.stim = stim;
+
+      $(".prompt").html(
+        "Imagine you come across a thing that <strong>" + stim.property +
+        "</strong>.<br> What are the odds that it is a <strong>" + stim.category + "</strong>?"
+      );
+      this.init_sliders();
+      exp.sliderPost = null; //erase current slider value
+    },
+
+    button : function() {
+      if (exp.sliderPost == null) {
+        $(".err").show();
+      } else {
+        this.rt = Date.now() - this.startTime;
+        this.log_responses();
+        _stream.apply(this);
+      }
+    },
+
+    init_sliders : function() {
+      utils.make_slider("#single_slider", function(event, ui) {
+        exp.sliderPost = ui.value;
+      });
+    },
+
+    log_responses : function() {
+      exp.data_trials.push({
+        "trial_type" : "cue_validity",
+        "trial_num": exp.fixedStims.indexOf(this.stim) + 1,
+        "category": this.stim.category,
+        "property": this.stim.property,
+        "response": exp.sliderPost,
+        "rt": this.rt
+      });
+    }
+  });
+
+  slides.subj_info =  slide({
+    name : "subj_info",
+    submit : function(e){
+      //if (e.preventDefault) e.preventDefault(); // I don't know what this means.
+      exp.subj_data = {
+        language : $("#language").val(),
+        enjoyment : $("#enjoyment").val(),
+        asses : $('input[name="assess"]:checked').val(),
+        age : $("#age").val(),
+        gender : $("#gender").val(),
+        education : $("#education").val(),
+        comments : $("#comments").val(),
+        fairprice: $("#fairprice").val(),
+        problems: $("#problems").val()
[…]

### 2018-12-11 experiments/generics/js/cue-validity-2-freeProduction.js

@@ -1,0 +1,212 @@
+function make_slides(f) {
+  var   slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    start: function() {
+     $("#ntrials").html(exp.n_trials)
+   },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+
+  slides.free_production = slide({
+    name: "free_production",
+    present : exp.stimuli,
+    present_handle : function(property) {
+      $(".err").hide();
+      $("#text_response").val('')
+      this.startTime = Date.now();
+      this.property = property;
+      $(".prompt").html(
+        "Imagine you come across a thing (animal or insect) that <strong>" +  property +
+        "</strong>.<br> What do you think it is?"
+      );
+    },
+    button : function() {
+      response = $("#text_response").val();
+      if (response.length == 0) {
+        $(".err").show();
+      } else {
+        this.rt = Date.now() - this.startTime;
+        this.log_responses();
+        _stream.apply(this);
+      }
+    },
+    log_responses : function() {
+      exp.data_trials.push({
+        "trial_type" : "free_production",
+        "trial_num": exp.fixedStims.indexOf(this.property) + 1,
+        "category": this.property,
+        "response": $("#text_response").val(),
+        "rt": this.rt
+      });
+    }
+  });
+
+  // slides.one_slider = slide({
+  //   name : "one_slider",
+  //   present : exp.stimuli,
+  //   present_handle : function(stim) {
+  //     $(".err").hide();
+  //     this.startTime = Date.now();
+  //     this.stim = stim;
+  //
+  //     $(".prompt").html(
+  //       "Imagine you come across a thing that <strong>" + stim.property +
+  //       "</strong>.<br> What are the odds that it is a <strong>" + stim.category + "</strong>?"
+  //     );
+  //     this.init_sliders();
+  //     exp.sliderPost = null; //erase current slider value
+  //   },
+  //
+  //   button : function() {
+  //     if (exp.sliderPost == null) {
+  //       $(".err").show();
+  //     } else {
+  //       this.rt = Date.now() - this.startTime;
+  //       this.log_responses();
+  //       _stream.apply(this);
[…]

### 2018-12-11 experiments/generics/js/fingerprinter.js

@@ -1,0 +1,35 @@
+/* global turk, store, location */
+
+var fingerprint;
+
+function setGeo(data) {
+  fingerprint.ip = data.ip;
+  fingerprint.geo = data; 
+}
+
+(function() {
+  
+  fingerprint = {
+    browser: navigator.userAgent,
+    screenWidth: screen.width,
+    screenHeight: screen.height,
+    colorDepth: screen.colorDepth,
+    ip: "",
+    geo: "",
+    timezone: new Date().getTimezoneOffset(),
+    plugins: Array.prototype.slice.call(navigator.plugins).map(function(x) { return {filename: x.filename, description: x.description}})
+  }
+
+
+  var isLocal = /file/.test(location.protocol);
+  
+  // inject a call to a json service that will give us geolocation information 
+  var protocol = isLocal ? "http://" : "//";
+  var src = protocol + "freegeoip.net/json/?callback=setGeo";
+
+  var scriptEl = document.createElement('script');
+  scriptEl.src = protocol + "freegeoip.net/json/?callback=setGeo";
+  
+  document.body.appendChild(scriptEl);
+
+})()

### 2018-12-11 experiments/generics/js/prior-1.js

@@ -1,0 +1,353 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $("#total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.instructions2 = slide({
+    name : "instructions2",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+    slides.instructions3 = slide({
+    name : "instructions3",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.priors = slide({
+    name: "priors",
+
+    present : _.zip(_.flatten(["",exp.columnNames]),
+                    _.flatten(["animal",exp.properties])),
+    //this gets run only at the beginning of the block
+
+    present_handle : function(stim) {
+
+      $(".err").hide();
+
+      console.log(stim);
+
+      // hide columns
+      this.col = stim[0]
+      this.property = stim[1]
+
+      this.col!='' ? 
+      _.map(exp.columnNames.slice(exp.columnNames.indexOf(this.col)),
+            function(x){
+        $(".prop"+x).hide();
+      }) :  _.map(exp.columnNames,
+            function(x){
+        $(".prop"+x).hide()})
+
+
+      $(".prop"+this.col).show();
+
+
+      // fix certain animal names in the table
+      _.map(_.range(exp.numberOfGivenAnimals),
+        function(x){
+          $("#text_response"+x).val(exp.animals[x]);
+          document.getElementById('text_response'+x).disabled=true;})
+
+
+
+      this.startTime = Date.now();
+
+      $("#head" + this.col).html(this.property);
+
+      this.col ==''?
+        $(".query").html("Listed below are 5 kinds of animals. Add 5 of your own to the list.") :
+        $(".query").html("For each kind of animal, what percentage of the species do you think " + this.property + "?")
+
+
+      // load column names into page
+      // _.zip(this.properties,this.columns).map(function(x){
+      //   $("#head" + x[1]).html(x[0]);
+      // })
+
+    },
+
+    button : function() {
+
+
+      var isComplete = function(lst){
[…]

### 2018-12-11 experiments/generics/js/prior-2.js

@@ -1,0 +1,420 @@
+// so called elicitation task...
+// same as experiment-11, 6 kinds / page
+
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $("#total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.instructions2 = slide({
+    name : "instructions2",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+    slides.instructions3 = slide({
+    name : "instructions3",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.priors = slide({
+    name: "priors",
+
+    present :exp.stims.shift(),
+    //this gets run only at the beginning of the block
+
+    present_handle : function(stim) {
+
+      $(".err").hide();
+
+      console.log(stim);
+
+      // hide columns
+      this.col = stim[0]
+      this.property = stim[1]
+      this.animals = stim[2]
+
+      // first trial? hide the rest of the columns : otherwise, hide all of them
+      this.col!='' ? 
+      _.map(exp.columnNames.slice(exp.columnNames.indexOf(this.col)),
+            function(x){
+        $(".prop"+x).hide();
+      }) :  _.map(exp.columnNames,
+            function(x){
+        $(".prop"+x).hide()})
+
+      //erase current columns enetries
+
+      var column = this.col
+      _.map([0,1,2,3,4,5,6,7,8,9,10], 
+                  function(y){return $("#text_response"+y+column.toLowerCase()).val("")
+                });
+
+      $(".prop"+this.col).show();
+
+
+      // fix certain animal names in the table
+      this.col == '' ? 
+      _.map(_.zip(_.range(exp.numberOfGivenAnimals), this.animals),
+        function(x){
+          $("#text_response"+x[0]).val(
+            x[1]
+            );
+          document.getElementById('text_response'+x[0]).disabled=true;}) : null
+
+      this.col == '' ? 
+      _.map([6,7,8,9,10],
+        function(x){
+          document.getElementById('text_response'+x).disabled=false;
+                  $("#text_response"+x).val("");
+                }) : null
+
+      this.startTime = Date.now();
+
[…]

### 2018-12-11 experiments/generics/js/stimuli.js

@@ -1,0 +1,152 @@
+var stims = [
+  {"Ducks":"have wings"},
+  {"Leopards":"have spots"},
+  {"Swans":"are white"},
+  {"Cardinals":"are red"},
+  {"Kangaroos":"have pouches"},
+  {"Robins":"lay eggs"},
+  {"Lions":"have manes"},
+  {"Mosquitos":"carry malaria"},
+  {"Sharks":"attacks swimmers"},
+  {"Ticks":"carry Lyme disease"},
+  {"Tigers":"eat people"},
+  {"Peacocks":"have beautiful feathers"}
+]
+
+
+var otherStims = [
+  [
+    {"Leopards":"are full-grown"},
+    {"Kangaroos":"are juvenile"}
+  ],
+  [
+    {"Lions":"are male"},
+    {"Robins":"are female"}
+  ]
+];
+
+var properties = [
+  {
+    property: "have spots", category: "physical"
+  },
+  {
+    property: "have brown fur", category: "physical"
+  },
+  {
+    property: "have white fur", category: "physical"
+  },
+  {
+    property: "have a good sense of smell", category: "physical"
+  },
+  {
+    property: "are afraid of loud noises", category: "psychological"
+  },
+  {
+    property: "are afraid of dogs", category: "psychological"
+  },
+  {
+    property: "are intelligent", category: "psychological"
+  },
+  {
+    property: "eat garbage", category: "diet"
+  },
+  {
+    property: "eat grass", category: "diet"
+  },
+  {
+    property: "eat meat", category: "diet"
+  },
+  {
+    property: "eat insects", category: "diet"
+  },
+  {
+    property: "eat people", category: "diet"
+  },
+  {
+    property: "live in trees", category: "habitat"
+  },
+  {
+    property: "live in zoos", category: "habitat"
+  },
+  {
+    property: "live in Africa", category: "habitat"
+  },
+  {
+    property: "hunt other animals", category: "behavior"
+  }
+]
+
+var animals = [
+  "Cows", "Whales", "Dogs", "Cats", "Rabbits",
+  "Raccoons", "Pigs", "Chickens", "Pandas",
+  "Tigers", "Turtles", "Dolphins", "Penguins",
+  "Mountain lions", "Bears", "Ants"
+]
+
+
+var originalProperties = [
+  "has wings",
+  "has spots",
+  "is white",
+  "is red",
+  "has a pouch",
+  "lays eggs",
+  "has a mane",
[…]

### 2018-12-11 experiments/generics/js/truthjudge-1.js

@@ -1,0 +1,221 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $(".total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+     start: function() {
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+key).html(val);
+      });
+      $(".total-num").html(exp.numTrials);  
+    },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.truthJudge = slide({
+    name: "truthJudge",
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+
+       var keyDictionary = 
+            {"agree-key": "Agree",
+            "disagree-key": "Disagree"}
+
+
+      this.startTime = Date.now();
+      this.stim = stim 
+      $(".generic").html(this.stim);
+
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+val+"key-reminder").html(keyDictionary[key]);
+      });
+
+      $(document).one("keydown", _s.keyPressHandler);
+    },
+
+    keyPressHandler : function(event) {
+      var keyCode = event.which;
+      if (keyCode != 81 && keyCode != 80) {
+        // If a key that we don't care about is pressed, re-attach the handler (see the end of this script for more info)
+        $(document).one("keydown", _s.keyPressHandler);
+      } else {
+        // If a valid key is pressed (code 80 is p, 81 is q),
+          _s.rt = Date.now() - _s.startTime;
+          _s.log_responses(keyCode);
+          /* use _stream.apply(this); if and only if there is
+          "present" data. (and only *after* responses are logged) */
+         setTimeout(function(){_stream.apply(_s)}, 500);
+      }
+
+    },
+
+    log_responses : function(keyCode) {
+      var response = _.invert(exp.judgeButtons)[exp.buttonCodes[keyCode]]
+      exp.data_trials.push({
+        "trial_type" : "truthJudge",
+        "sentence":_s.stim,
+        "response" : response,
+        "rt":_s.rt,
+      });
+    }
+  });
+
+  slides.check = slide({
+     name : "check",
+     start: function() {
+      this.startTime = Date.now();
+            $(".err").hide();
+
+     },
+    button : function() {
[…]

### 2018-12-11 experiments/habituals/priors/js/predictive-1.js

@@ -1,0 +1,254 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      $("#n_trials").html(exp.n_trials);
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+
+  slides.catch = slide({
+     name : "catch",
+     start: function() {
+      this.startTime = Date.now();
+            $(".err").hide();
+     },
+    button : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      if ((response1 == -1) || (response2 == -1)) {
+        $(".err").show();
+      } else {
+        this.rt = Date.now() - this.startTime;
+        this.log_responses();
+        exp.go();
+      }
+    },
+    log_responses : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      exp.catch_trials.push({
+        "trial_type" : "catch",
+        "response1" : response1,
+        "response2" : response2,
+        "pass": (response1 == 1 && response2==1)? 1 : 0,
+        "rt":this.rt
+      });
+    }
+  });
+
+  slides.single_trial = slide({
+    name: "single_trial",
+
+    present: exp.stims,
+
+    present_handle : function(stim0) {
+
+      var condition = stim0[0]
+      var stim = stim0[1]
+      this.startTime = Date.now()
+      this.stim =  stim;
+      this.trialNum = exp.stimscopy.indexOf(stim0);
+
+      //$("#text_response").val('')
+      //Instead of text_response now using time_frequency and time_comparison
+      $("#time_frequency").val('')
+      $("#time_comparison").val('')
+      $(".err").hide();
+
+
+      this.condition = condition
+
+      var freq = stim.prevent_test_freq[0]
+
+      this.stim.freq = "3"
+      this.stim.interval = freq
+
+      $(".frequency").html("In the <strong>past " + freq + "</strong>, " +
+         stim.character.name  + " " + stim.past + " <em>3 times</em>.");
+
+      var possessive = condition == "baseline"? "" : stim[condition]["requires"] == "possessive" ?
+        stim.character.gender == "male" ? "his " :
+                                          "her " :
[…]

### 2018-12-11 experiments/habituals/priors/js/predictive-stims-1.js

@@ -1,0 +1,1024 @@
+// same as /backfiring-words/experiments/priors/stims-2.js
+
+var stimuli = [
+{
+	habitual: "hikes",
+	past: "went on a hike",
+	category: "hobby",
+	verb: "go on a hike",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a motorcycle accident and",
+		obj: "will never walk again"
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a lot of new hiking gear"
+	},
+	filler: {
+		verb: "was in a motorcycle accident and got",
+		obj: "license suspended",
+		requires:"possessive"
+	},
+	prevent_test_freq: ["year"],
+	predict_test_freq: "week"
+	// prevent_test_freq: ["2 years", "2 months"]
+},
+{
+	habitual: "runs",
+	past: "went for a run",
+	category: "hobby",
+	verb: "go for a run",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a car accident and",
+		obj: "became permanently paralyzed from the waist down",
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a new pair of running shoes"
+	},
+	filler: {
+		verb: "was in a car accident and",
+		obj: "has to go to driving school",
+		// requires: "possessive"
+	},
+	prevent_test_freq: ["2 months"],
+	predict_test_freq: "week"
+},
+{
+	habitual: "plays the banjo",
+	past: "played the banjo",
+	category: "hobby",
+	verb:"play the banjo",
+	frequency: ["5 years","2 years","year"],
+	preventative: {
+		verb: "developed crippling arthritis in",
+		obj: "hands and no longer can play musical instruments",
+		requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun that was and joined",
+		obj: "friend's band as the banjoist",
+		requires: "possessive"
+	},
+	filler: {
+		verb: "developed a rash on",
+		obj: "leg and has to put ointment on it",
+		requires: "possessive"
+	},
+	prevent_test_freq: ["year"],
+	predict_test_freq: "week"
+	// enabling: "really enjoys playing the banjo"
+},
+{
+	habitual: "plays tennis",
+	past: "played tennis",
+	category: "hobby",
+	verb:"play tennis",
[…]

### 2018-12-11 experiments/habituals/priors/js/priors-1.js

@@ -1,0 +1,182 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      $("#n_trials").html(exp.n_trials);
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+
+  slides.catch = slide({
+     name : "catch",
+     start: function() {
+      this.startTime = Date.now();
+            $(".err").hide();
+     },
+    button : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      if ((response1 == -1) || (response2 == -1)) {
+        $(".err").show();
+      } else {
+        this.rt = Date.now() - this.startTime;
+        this.log_responses();
+        exp.go();
+      }
+    },
+    log_responses : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      exp.catch_trials.push({
+        "trial_type" : "catch",
+        "response1" : response1,
+        "response2" : response2,
+        "pass": (response1 == 1 && response2==1)? 1 : 0,
+        "rt":this.rt
+      });
+    }
+  });
+
+  slides.single_trial = slide({
+    name: "single_trial",
+    
+    present: exp.stimuli,
+
+    present_handle : function(stim) {
+      this.startTime = Date.now()
+      this.stim =  stim; 
+      this.trialNum = exp.stimscopy.indexOf(stim);
+      $("#text_response").val('')
+      $("#frequency").val('')
+      $(".err").hide();
+      $(".question1").html("What percentage of the U.S. population do you believe has " + stim.past + " before?<br>");
+      $(".question2").html("For a typical person who has " + stim.past + 
+            " before, how frequently does he or she " + stim.present + "?");
+      this.init_sliders();
+      $(".slider_number").html("---")
+      exp.sliderPost = null; //erase current slider value
+    },
+
+    init_sliders : function() {
+      utils.make_slider("#single_slider", function(event, ui) {
+        exp.sliderPost = ui.value;
+        $(".slider_number").html(Math.round(exp.sliderPost*1000)/10+"%")
+      }, "horizontal", 0.001, 600);
+    },
+
+    button : function() {
+      response = $("#text_response").val();
[…]

### 2018-12-11 experiments/habituals/priors/js/priors-2.js

@@ -1,0 +1,236 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      $("#n_trials").html(exp.n_trials);
+      exp.startT = Date.now();
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+
+  slides.catch = slide({
+     name : "catch",
+     start: function() {
+      this.startTime = Date.now();
+            $(".err").hide();
+     },
+    button : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      if ((response1 == -1) || (response2 == -1)) {
+        $(".err").show();
+      } else {
+        this.rt = Date.now() - this.startTime;
+        this.log_responses();
+        exp.go();
+      }
+    },
+    log_responses : function() {
+      var response1 = $("#catch1").val()
+      var response2 = $("#catch2").val()
+      exp.catch_trials.push({
+        "trial_type" : "catch",
+        "response1" : response1,
+        "response2" : response2,
+        "pass": (response1 == 1 && response2==1)? 1 : 0,
+        "rt":this.rt
+      });
+    }
+  });
+
+  slides.single_trial = slide({
+    name: "single_trial",
+    
+    present: exp.stimuli,
+
+    present_handle : function(stim) {
+      this.startTime = Date.now()
+      this.stim =  stim; 
+      this.trialNum = exp.stimscopy.indexOf(stim);
+
+      $("#n_people_a").val('')
+      $("#n_people_b").val('')
+
+      $("#comparison_a").val('1000')
+      $("#comparison_b").val('1000')
+
+      $("#text_response_a").val('')
+      $("#text_response_b").val('')
+
+      $("#frequency_a").val('year')
+      $("#frequency_b").val('year')
+
+      $(".err").hide();
+
+      var menQ = "How many American men do you think have <strong>" + stim.past + "</strong> before?<br>"
+      var womenQ =  "How many American women do you think have <strong> " + stim.past + "</strong> before?<br>"
+      var menQ2 = "For a typical man who has " + stim.past + " before, how frequently does he <strong>" + stim.present + "</strong>?"
[…]

### 2018-12-11 experiments/habituals/priors/js/stims-2.js

@@ -1,0 +1,697 @@
+var stimuli = [
+{
+	habitual: "hikes",
+	present : "hike",
+	past: "hiked",
+	category: "hobby",
+	frequency: ["year","month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "runs",
+	present: "run",
+	past: "run",
+	category: "hobby",
+	frequency: ["year","month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "plays the banjo",
+	present: "play the banjo",
+	past: "played the banjo",
+	category: "hobby",
+	frequency: ["year"," month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "plays tennis",
+	present: "play tennis",
+	past: "played tennis",
+	category: "hobby",
+	frequency: ["year","month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "climbs mountains",
+	present: "climb mountains",
+	past: "climbed mountains",
+	category: "hobby",
+	frequency: ["5 years", "year","month"],
+	defaultFreq: "year"
+},
+{
+	habitual: "wears a suit",
+	present: "wear a suit",
+	past: "worn a suit",
+	category: "clothing",
+	frequency: ["year","month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "wears a bra",
+	present: "wear a bra",
+	past: "worn a bra",
+	category: "clothing",
+	frequency: ["year", "month","week"],
+	defaultFreq: "year"
+},
+{
+	habitual: "wears slacks",
+	present: "wear slacks",
+	past: "worn slacks",
+	category: "clothing",
+	frequency: ["year", "month","week"],
+	defaultFreq:  "year"
+},
+{
+	habitual: "wears socks",
+	present: "wear socks",
+	past: "worn socks",
+	category: "clothing",
+	frequency: ["month","week"],
+	defaultFreq: "year"
+},
+// {
+// 	habitual: "wears a hat",
+// 	present: "wear a hat",
+// 	past: "wore a hat",
+// 	category: "clothing",
+// 	frequency: ["month","week"]	
+// },
+// {
+// 	habitual: "wears gloves",
+// 	past: "wore gloves",
+// 	category: "clothing",
+// 	frequency: ["month","week"]
+// },
+// {
+// 	habitual: "wears sweaters",
[…]

### 2018-12-11 experiments/habituals/priors/js/stims-3.js

@@ -1,0 +1,1024 @@
+// same as /backfiring-words/experiments/priors/stims-2.js
+
+var stimuli = [
+{
+	habitual: "hikes",
+	past: "went on a hike",
+	category: "hobby",
+	verb: "go on a hike",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a motorcycle accident and",
+		obj: "will never walk again"
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a lot of new hiking gear"
+	},
+	filler: {
+		verb: "was in a motorcycle accident and got",
+		obj: "license suspended",
+		requires:"possessive"
+	},
+	prevent_test_freq: ["year"],
+	predict_test_freq: "week"
+	// prevent_test_freq: ["2 years", "2 months"]
+},
+{
+	habitual: "runs",
+	past: "went for a run",
+	category: "hobby",
+	verb: "go for a run",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a car accident and",
+		obj: "became permanently paralyzed from the waist down",
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a new pair of running shoes"
+	},
+	filler: {
+		verb: "was in a car accident and",
+		obj: "has to go to driving school",
+		// requires: "possessive"
+	},
+	prevent_test_freq: ["2 months"],
+	predict_test_freq: "week"
+},
+{
+	habitual: "plays the banjo",
+	past: "played the banjo",
+	category: "hobby",
+	verb:"play the banjo",
+	frequency: ["5 years","2 years","year"],
+	preventative: {
+		verb: "developed crippling arthritis in",
+		obj: "hands and no longer can play musical instruments",
+		requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun that was and joined",
+		obj: "friend's band as the banjoist",
+		requires: "possessive"
+	},
+	filler: {
+		verb: "developed a rash on",
+		obj: "leg and has to put ointment on it",
+		requires: "possessive"
+	},
+	prevent_test_freq: ["year"],
+	predict_test_freq: "week"
+	// enabling: "really enjoys playing the banjo"
+},
+{
+	habitual: "plays tennis",
+	past: "played tennis",
+	category: "hobby",
+	verb:"play tennis",
[…]

### 2018-12-11 experiments/habituals/priors/js/stims.js

@@ -1,0 +1,146 @@
+var stimuli = [
+{
+	item: "eats granola for breakfast",
+	present: "eat granola for breakfast",
+	past: "eaten granola for breakfast",
+	type: "food"
+},
+{
+	item: "eats meals with no meat",
+	present: "eat meals with no meat",
+	past: "eaten a meal with no meat",
+	type: "food"
+},
+// {
+// 	item: "drinks fancy coffee",
+// 	present: "drink fancy coffee",
+// 	past: "drunk fancy coffee",
+// 	type: "food"
+// },
+{
+	item: "drinks beer",
+	present: "drink beer",
+	past: "drank a beer",
+	type: "food"
+},
+{
+	item: "drinks wine with dinner",
+	present: "drink wine with dinner",
+	past: "drank wine with dinner",
+	type: "food"
+},
+{
+	item: "smokes",
+	present: "smoke",
+	past: "smoked",
+	type: "food"
+},
+{
+	item: "runs",
+	present: "run",
+	past: "run",
+	type: "sports"
+},
+{
+	item: "hikes",
+	present: "hike",
+	past: "hiked",
+	type: "sports"
+},
+{
+	item: "runs the mile in under four minutes",
+	present: "run the mile in under four minutes",
+	past: "run the mile in under four minutes",
+	type: "sports"
+},
+// {
+// 	item: "swims",
+// 	present: "swim",
+// 	past: "swum",
+// 	type: "sports"
+// },
+{
+	item: "plays computer games",
+	present: "play computer games",
+	past: "played a computer game",
+	type: "games"
+},
+// {
+// 	item: "plays poker",
+// 	present: "play poker",
+// 	past: "played poker",
+// 	type: "games"
+// },
+{
+	item: "writes novels",
+	present: "write novels",
+	past: "written a novel",
+	type: "occupation"
+},
+{
+	item: "writes poems",
+	present: "write poems",
+	past: "written a poem",
+	type: "occupation"
+},
+{
+	item: "drives to work",
+	present: "drive to work",
+	past: "driven to work",
+	type: "commute"
+},
+{
+	item: "bikes to work",
+	present: "bike to work",
+	past: "biked to work",
+	type: "commute"
+},
+{
+	item: "walks to work",
+	present: "walk to work",
+	past: "walked to work",
+	type: "commute"
+},
+{
+	item: "steals cars",
+	present: "steal cars",
+	past: "stolen a car",
+	type: "illicit"
+},
+{
+	item: "murders people",
[…]

### 2018-12-11 experiments/habituals/truth-judgments/js/stims-2.js

@@ -1,0 +1,959 @@
+var stimuli = [
+{
+	habitual: "hikes",
+	past: "hiked",
+	category: "hobby",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a motorcycle accident and",
+		obj: "will never walk again"
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a lot of new hiking gear"
+	},
+	filler: {
+		verb: "was in a motorcycle accident and got",
+		obj: "license suspended",
+		requires:"possessive"
+	},
+	prevent_test_freq: ["year"]
+	// prevent_test_freq: ["2 years", "2 months"]
+},
+{
+	habitual: "runs",
+	past: "ran",
+	category: "hobby",
+	frequency: ["2 years","year","2 months","week"],
+	preventative: {
+		verb: "was in a car accident and",
+		obj: "became permanently paralyzed from the waist down",
+		// requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun those times were",
+		obj: "and bought a new pair of running shoes"
+	},
+	filler: {
+		verb: "was in a car accident and",
+		obj: "has to go to driving school",
+		// requires: "possessive"
+	},
+	prevent_test_freq: ["2 months"]
+},
+{
+	habitual: "plays the banjo",
+	past: "played the banjo",
+	category: "hobby",
+	frequency: ["5 years","2 years","year"],
+	preventative: {
+		verb: "developed crippling arthritis in",
+		obj: "hands and no longer can play musical instruments",
+		requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun that was and joined",
+		obj: "friend's band as the banjoist",
+		requires: "possessive"
+	},
+	filler: {
+		verb: "developed a rash on",
+		obj: "leg and has to put ointment on it",
+		requires: "possessive"
+	},
+	prevent_test_freq: ["year"]
+	// enabling: "really enjoys playing the banjo"
+},
+{
+	habitual: "plays tennis",
+	past: "played tennis",
+	category: "hobby",
+	frequency: ["5 years","2 years","year"],
+	preventative: {
+		verb: "developed crippling arthritis in both elbows and can only move",
+		obj: "arms extremely slowly",
+		requires: "possessive"
+	},
+	enabling: {
+		verb: "remembered how much fun that was",
[…]

### 2018-12-11 experiments/habituals/truth-judgments/js/stims.js

@@ -1,0 +1,269 @@
+var stimuli = [
+{
+	habitual: "hikes",
+	25: {hab: "once a year", 
+		past: {tense: "hiked", instances: "1 time", pastTimeWindow: "year"}
+	},
+	50: {hab: "every couple months",
+		past: {tense: "hiked", instances: "4 times", pastTimeWindow: "year"}
+	},
+	75: {hab: "once a month",
+		past: {tense: "hiked", instances: "12 times", pastTimeWindow: "year"}
+	}
+},{
+	habitual: "runs",
+	25: {hab: "three times a year",
+		past: {tense: "ran", instances: "3 times", pastTimeWindow: "year"}
+	},
+	50: {hab: "twice a month",
+		past: {tense: "ran", instances: "25 times", pastTimeWindow: "year"}
+	},
+	75: {hab: "twice a week",
+		past: {tense: "ran", instances: "120 times", pastTimeWindow: "year"}
+	}
+},{
+	habitual: "smokes",
+	25: {hab: "once a week",
+		past: {tense: "smoked", instances: "1 time", pastTimeWindow: "week"}
+	},
+	50: {hab: "once a day",
+		past: {tense: "smoked", instances: "7 times", pastTimeWindow: "week"}
+	},
+	75: {hab: "ten times a day",
+		past: {tense: "smoked", instances: "70 times", pastTimeWindow: "week"}
+	}
+},{
+	habitual:"drives to work",
+	25: {hab: "3 times a week",
+		past: {tense: "drove to work", instances: "3 times", pastTimeWindow: "week"}
+	},
+	50: {hab: "4 times a week",
+		past: {tense: "drove to work", instances: "4 times", pastTimeWindow: "week"}
+	},
+	75: {hab: "5 times a week",
+		past: {tense: "drove to work", instances: "5 times", pastTimeWindow: "week"}
+	}
+},{
+	habitual:"bikes to work",
+	25: {hab: "once or twice a month",
+		past: {tense: "biked to work", instances: "2 times", pastTimeWindow: "month"}
+	},
+	50: {hab: "once or twice a week",
+		past: {tense: "biked to work", instances: "6 times", pastTimeWindow: "month"}
+	},
+	75: {hab: "six times a week",
+		past: {tense: "biked to work", instances: "24 times", pastTimeWindow: "month"}
+	}
+},{
+	habitual:"vacations in Switzerland",
[…]

### 2018-12-11 experiments/habituals/truth-judgments/js/tj-1.js

@@ -1,0 +1,232 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $(".total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+     start: function() {
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+key).html(val);
+      });
+      $(".total-num").html(exp.numTrials);  
+    },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.truthJudge = slide({
+    name: "truthJudge",
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      // debugger;
+      this.startTime = Date.now();
+
+      this.stim = stim 
+      var habit = this.stim[0]
+      var charName = this.stim[1]
+      // debugger;
+  // 25: {hab: "once a year", 
+  //   past: {tense: "hiked", instances: "1 time", pastTimeWindow: "year"}
+  // },
+  // 50: {hab: "every couple months",
+  //   past: {tense: "hiked", instances: "4 times", pastTimeWindow: "year"}
+  // },
+  // 75: {hab: "once a month",
+  //   past: {tense: "hiked", instances: "12 times", pastTimeWindow: "year"}
+  // }
+
+      var freq = _.omit(habit, "habitual")
+
+      this.stim.freq = _.keys(freq)[0]
+      var description = _.values(freq)[0]
+      this.stim.description = description
+
+      var keyDictionary = {
+        "agree-key": "Yes",
+        "disagree-key": "No"
+      }
+
+      $(".frequency").html("In the past <strong>" + description.past.pastTimeWindow + "</strong>, " +
+         charName.name  + " " + description.past.tense + " <em>" + description.past.instances+ "</em>.");
+      // $(".frequency").html("Suppose: " + charName.name  + " " + habit.habitual + " <em>" + _.values(freq)[0] + "</em>.");
+
+      $(".habitual").html('"' + charName.name  + ' ' + habit.habitual + '."');
+
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+val+"key-reminder").html(keyDictionary[key]);
+      });
+
+      $(document).one("keydown", _s.keyPressHandler);
+    },
+
+    keyPressHandler : function(event) {
[…]

### 2018-12-11 experiments/habituals/truth-judgments/js/tj-2.js

@@ -1,0 +1,283 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $(".total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+     start: function() {
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+key).html(val);
+      });
+      $(".total-num").html(exp.numTrials);  
+    },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.truthJudge = slide({
+    name: "truthJudge",
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim) {
+      // debugger;
+      // console.log(stim)
+      this.startTime = Date.now();
+
+      this.stim = stim 
+      // var habit = this.stim[0]
+      // var charName = this.stim[1]
+      // debugger;
+
+      var freq = _.sample(stim.frequency)//_.omit(habit, "habitual")
+
+      this.stim.freq = "3"
+      this.stim.interval = freq
+      // var description = stim.condition
+      // this.stim.description = description
+
+      var keyDictionary = {
+        "agree-key": "Agree",
+        "disagree-key": "Disagree"
+      }
+
+      $(".frequency").html("In the past <strong>" + freq + "</strong>, " +
+         stim.character.name  + " " + stim.past + " <em>3 times</em>.");
+      // $(".frequency").html("Suppose: " + charName.name  + " " + habit.habitual + " <em>" + _.values(freq)[0] + "</em>.");
+
+      $(".habitual").html('"' + stim.character.name  + ' ' + stim.habitual + '."');
+
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+val+"key-reminder").html(keyDictionary[key]);
+      });
+
+      $(document).one("keydown", _s.keyPressHandler);
+    },
+
+    keyPressHandler : function(event) {
+      var keyCode = event.which;
+      if (keyCode != 81 && keyCode != 80) {
+        // If a key that we don't care about is pressed, re-attach the handler (see the end of this script for more info)
+        $(document).one("keydown", _s.keyPressHandler);
+      } else {
[…]

### 2018-12-11 experiments/habituals/truth-judgments/js/tj-3-preventatives.js

@@ -1,0 +1,344 @@
+function make_slides(f) {
+  var slides = {};
+
+  slides.i0 = slide({
+     name : "i0",
+     start: function() {
+      exp.startT = Date.now();
+      $(".total-num").html(exp.numTrials);  
+     }
+  });
+
+  slides.instructions = slide({
+    name : "instructions",
+     start: function() {
+      _.mapObject(exp.judgeButtons, function(val,key){
+        $("#"+key).html(val);
+      });
+      $(".total-num").html(exp.numTrials);  
+    },
+    button : function() {
+      exp.go(); //use exp.go() if and only if there is no "present" data.
+    }
+  });
+
+  slides.truthJudge = slide({
+    name: "truthJudge",
+    present : exp.stims,
+    //this gets run only at the beginning of the block
+    present_handle : function(stim0) {
+      // for testing
+
+
+      var condition = stim0[0]
+      var stim = stim0[1]
+      // debugger;
+      // console.log(stim)
+      this.startTime = Date.now();
+
+      // for production
+      this.stim = stim 
+      this.condition = condition
+      // var condition = _.sample(["preventative","enabling","filler", null])
+      
+      // for testing purposes
+      // var condition = stim[0]
+      // this.stim = stim[1]
+
+      // var habit = this.stim[0]
+      // var charName = this.stim[1]
+      // debugger;
+      // debugger;
+      // var condition = 
+
+      // for null condition, sample both hi and lo frquency
+      // otherwise, do a mismatch
+      // var freq = condition == null ?  _.sample([_.last(stim.frequency), _.first(stim.frequency)]) :
+      //           condition == "preventative" ? _.last(stim.frequency) : 
+      //                                          _.first(stim.frequency)
+
+      // var freq = _.sample([_.last(stim.frequency), _.first(stim.frequency)])
+
+      var freq = stim.prevent_test_freq[0]
+
+      // var freq = _.last(stim.frequency)
+      this.stim.freq = "3"
+      this.stim.interval = freq
+      // var description = stim.condition
+      // this.stim.description = description
+
+      var keyDictionary = {
+        "agree-key": "Agree",
+        "disagree-key": "Disagree"
+      }
+
+      $(".frequency").html("In the past <strong>" + freq + "</strong>, " +
[…]

### 2018-12-12 paper/comgen-paper.Rmd
reorganize data folder, proof edits to ms

@@
 author_note: >
-  This paper is currently under review. Comments or suggestions are appreciated and should be directed to MHT.
+  This paper is based on a Ph.D.
+dissertation submitted to Stanford University.
+The research was supported by National Science Foundation Graduate Research Fellowship DGE-114747 awarded to MHT and DARPA PPAML grant FA8750-14-2-0009 to NDG.
+A portion of this paper (Case Study 2) appeared in the proceedings of the 38th Annual Meeting of the Cognitive Science Society, Philadelphia, 2016.
+We are deeply grateful to Ellen Markman, Gregory Scontras, Thomas Icard, Michael C.
+Frank, Michael Franke, and Sophie Bridgers for extensive conversations about and support for this work.
+In addition, the work was greatly improved through countless discussions with members of the Computation and Cognition Lab and the Language and Cognition Lab at Stanford, as well as the participants of *A Generic Workshop* at the Center for the Study of Language and Information (CSLI) at Stanford in May 2017.
+Finally, we thank two anonymous reviewers and Joshua Hartshorne for helping us clarify our main arguments and improving the quality of the manuscript.
+All models, analyses, data, and links to experiments used in this article can be found at https://github.com/mhtess/genlang-paper
 
@@
 The *language of generalization* covers a diverse swath of natural language expressions.
-Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case generalizations in language.^[
+Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case of generalizations in language.^[
   Some writers refer to the all of the *language of generalization* as "generic language" or generics.
@@
 Insofar as there is a single class of linguistic expressions that convey generalization, however, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
-In this paper, we propose such a semantic core based on prevalence or probability and formalized using the tools of truth-functional semantics [@Montague1973; @Cohen1999].
-A semantics based on probability will not be enough to subtle sensitivities to context that the language of generalization exhibit.
-We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using world knowledge.
+In this paper, we propose such a semantic core based on prevalence and formalized using the tools of truth-functional semantics [@Montague1973; @Cohen1999].
+A semantics based on prevalence will not be enough to capture subtle sensitivities to context that the language of generalization exhibit.
+We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using probabilistic world knowledge.
 
@@
 <!-- By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested. -->
-This formal model is the first of its kind to make quantitative predictions about human understanding of generalization in language.
+This formal model is the first of its kind to make quantitative predictions about human understanding of the l anguage of generalization.
 <!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
@@
 This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
-Our *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
+The *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
 The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
@@
 Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
-By assuming some generative process that could produce one's observations $o$ (i.e., a likelihood function $P(o \mid p)$), Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations $o$: $P(o \mid d) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].
+By assuming some generative process that could produce one's observations $o$---a likelihood function $P(o \mid p)$---Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations: $P(p \mid o) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].
 
@@
 
-The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "This dog has four legs").
+The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "Rufus has four legs").
 In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
@@
 Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
-  We further distinguish the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
+  We further distinguish the problem of formalizing a *meaning* for the language of generalization from the problem of *identifying* generalizations. 
   Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
@@
 
+Our model of interpreting the language of generalizations has three conceptual components: Probability, vagueness, and context.
 If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
@@
 The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
-Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
+Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a person is different than what counts as tall for a building; @Kennedy2007; @Lassiter2013].
 We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].
@@
 
-Following @Lassiter2015, we formalize the vagueness in the meaning of generics $P(\theta)$ as a uniform distribution over the support of $P(p)$.
+Following @Lassiter2015, we formalize the vagueness in the meaning of generalizations $P(\theta)$ as a uniform distribution over the support of $P(p)$.
 
 With these ingredients, the literal interpretation model (Eq. \ref{eq:L0}) computes a posterior interpretation distribution on prevalence by considering different possible thresholds $\theta$.
-Figure\ \@ref(fig:uniformPriorSimulation) shows the model behavior assuming a uniform prevalence prior $P(p)$, perhaps representing a purely abstract property for which an interpreter has no substantive prior knowledge.
+Figure\ \@ref(fig:uniformPriorSimulation) shows the model behavior assuming a uniform prevalence prior $P(p)$, representing a purely abstract property for which an interpreter has no substantive prior knowledge.
 If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance.
 As the threshold decreases, more and more prevalence levels become compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
-The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution on prevalence that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
-This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise prevalence.
+The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
+This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise quantity.
 
@@
 
-# Worked examples
+## Worked examples
 
@@
 
-Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
+Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to the interpretation model's background knowledge.
 Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
-This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
+Our model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
 <!-- \ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below} -->
@@
 <!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
-For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
+For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 50% (because among the animals with egg-layers, only the female members of the category have the property).
 Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
@@
               "9. Elephants live in Africa and Asia"),
-  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "85%", "0 times", "100%", "50%/50%"),
+  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "95%", "0 times", "100%", "50%/50%"),
   `intuitive truth value` = c(
@@
 The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which a generic statement becomes true.
-Rather, listeners have uncertainty about the threshold which leads to graded interpretations (e.g., "Dogs bark" probably means *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
-The endorsement model predicts "Dogs bark" is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though there are exceptions to the universal generalization (referent prevalence of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).
+Rather, listeners have uncertainty about the threshold which leads to graded interpretations (e.g., "Dogs bark" means almost all dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
+The endorsement model then predicts "Dogs bark" is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though there are exceptions to the universal generalization (referent prevalence of barking among dogs roughly 95%, shown with arrow in Figure\ \@ref(fig:simulations) row 2).
 
@@
 
-A second observation regarding generics is that their truth conditions cannot be so lenient so as to always convey *existential* quantification (e.g., "Some").
+A second observation regarding generics is that their truth conditions cannot be so lenient so as to always convey existential quantification (e.g., "Some").
 Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel awkward to assert the generic "Kangaroos have spots".
 The model exhibits this same restraint, predicting a very low endorsement probability for this generic sentence (Figure\ \@ref(fig:simulations); column 2).
-The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean *almost all* kangaroos have spots.
+The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean almost all kangaroos have spots.
 The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would lead to a too-strong interpretation and mislead the listener.
@@
 In contrast, the hypothetical generic interpretation of "Robins are female" is not different from the prevalence prior and hence the generic conveys no new information; here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5.
-Indeed, previous studies on generic endorsements have found "Robins are female" to not be rated as completely false but rather receive an intermediate endorsement level [i.e., *neither true nor false*; @Prasada2013].
+Indeed, previous studies on generic endorsements have found "Robins are female" to not be rated as completely false but rather receive an intermediate endorsement level [i.e., neither true nor false; @Prasada2013].
 
@@
 <!-- Yet, intuitively, the generic would be misleading (similar in intuition to "Kangaroos have spots"). -->
-Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that *no* sharks eat people (i.e., 100% don't eat people), which is too strong.
-It is interesting to note that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 40% (i.e., somewhat false).
+Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people (i.e., 100% don't eat people), which is too strong.
+It is interesting that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 0.4 (i.e., somewhat false).
 We will test this quantitative prediction in Experiment 1 on generic language.
@@
 <!-- We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary.  -->
-Thus the predictive probability that Mary will handle Antarctican mail, should there be some, is high.
-Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
+Thus the predictive probability that Mary will handle Antarctic mail, should there be some, is high.
+Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead the two to diverge. 
 In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
@@
 
-Imagine that all current Supreme Court Justice has a social security number which was an *even number*. 
+Imagine that all current Supreme Court Justice has a social security number which was an even number.
 "Supreme Court Justices have even social security numbers" is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
-We predict the rejection of even social security numbered Justices is the result of our intuitive theories guiding our subjective predictive probabilities, which feed into the endorsement model.
-That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability to the *next* justice having an even social security number.
+We predict the rejection of even social security numbered Justices is the result of people's intuitive theories guiding their subjective predictive probabilities, which feed into the endorsement model.
+That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability to the next justice having an even social security number.
 Then, "Supreme Court Justices have even social security numbers" would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
@@
 
-Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
+Understanding how a semantic representation composes is another important test for a theory of the language of generalization.
 @Nickel2008 suggests that "Elephants live in Africa and Asia" is troubling for prevalence-based accounts [in particular, majority-quantificational accouts where the generic means *more than half*; @Cohen1999] because the statement should be semantically equivalent to "Elephants live in Africa and elephants live in Asia".
-It cannot be the case that most (more than half of) elephants live in Africa and *most* (more than half of) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
+It cannot be the case that most (more than half of) elephants live in Africa and most (more than half of) elephants live in Asia, unless we are to posit international elephants (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
 <!-- However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999].
@@
 In fact, with prior knowledge suggesting against the existence of international elephants (Figure\ \@ref(fig:elephants)A), our model interprets "Elephants live in Africa and Asia" as meaning that some elephants live in Africa and that different ones live in Asia (Figure\ \@ref(fig:elephants)C).
-Interestingly, an incremental parsing of the sentence  (i.e., upon hearing only that "Elephants live in Africa") leads our model to believe that *most*, possibly all, elephants live in Africa (Figure\ \@ref(fig:elephants)B).
-When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: *some* elephants live in Africa and others in Asia (Figure\ \@ref(fig:elephants)C).
+Of theoretical interest, an incremental parsing of the sentence  (i.e., upon hearing only that "Elephants live in Africa") leads our model to believe that most, possibly all, elephants live in Africa (Figure\ \@ref(fig:elephants)B).
+When the sentence is completed ("...and Asia"), the model non-monotonically updates its beliefs to something weaker: some elephants live in Africa and others in Asia (Figure\ \@ref(fig:elephants)C).
 The flexibility of our model accommodates new evidence that might otherwise contradict previous utterances because it maintains uncertainty about the precise meaning of the utterance.
@@
 ]
-On this account, generics are true if *some* instances of the kind have the feature when all counterinstances are negative counterinstances and the property is either characteristic or striking. 
-If the property is neither characteristic nor striking, then *almost all* instances of the kind must have the feature for the generic to be true (e.g., "Barns are red").
+On this account, generics are true if some instances of the kind have the feature when all counterinstances are negative counterinstances and the property is either characteristic or striking. 
+If the property is neither characteristic nor striking, then almost all instances of the kind must have the feature for the generic to be true (e.g., "Barns are red").
 Many of the key factors in this conceptual approach are compatible with our view of prevalence as a predictive probability: What is required is that the distinctions made by conceptual accounts influence predictive probability, which mediates linguistic effects.
@@
 For example, according to certain measurements, young children have a nearly adult-like understanding of generics far earlier than they do with quantified language [@Gelman2015].
-Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that same information will tend to recall quantified information as generics [e.g., "Spiders shed their skin"; @Leslie2012], but not visa versa.
+Similarly, adults who are told novel information about categories using quantified language (e.g., "Most spiders shed their skin") and later asked to recall that same information will tend to recall quantified information as generics (e.g., "Spiders shed their skin"), but not visa versa [@Leslie2012].
 As a result, generics are thought of as conveying default generalizations, whereas quantified language expresses more sophisticated and specific generalizations.
-Rather than be contradictory, our model can be seen as formalizing a default generalization as Bayesian belief updating via a threshold function whose threshold value is contextually-informed via knowledge about properties.
+Rather than be contradictory, our model can be seen as formalizing a default generalization as Bayesian belief updating via a threshold function whose threshold value is contextually-informed by knowledge about properties.
 Alternative formulations of such a default generalization mechanism could be proposed and quantitatively tested against our account.
@@
 A property bears a principled connection to the kind if a (generic) sentence that appeals to the kind to explain the existence of the property makes sense (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged").
-When such sentences are not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple generic (e.g., "Barns are red") is endorsed, then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
-@Prasada2013 showed that different kinds of generic statements (e.g., striking properties, characteristic properties with low prevalence) support different kinds of inferences in addition to the difference in endorsements for *by virtue of* statements (e.g., *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
+When such sentences are not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple generic (e.g., "Barns are red") is endorsed, then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the tokens having the property which matters for generic endorsement).
+In addition to the difference in endorsements for *by virtue of* statements, @Prasada2013 showed that different kinds of generic statements (e.g., striking properties, characteristic properties with low prevalence) support different kinds of inferences (e.g., *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
 Additionally, there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
@@
 A popular alternative view under the statistical banner draws on the intuition that generics often express something normative in the world [@Asher1995; @Pelletier1997; @Nickel2008; @Nickel2016]. 
-"Dogs have four legs" is then a good generic not because all dogs have four legs (regrettably, all do not) but were the world to function *normally* (e.g., dogs would not be involved in freak tractor accidents or be born with strange genetic mutations), then *all* dogs would have four legs.
+"Dogs have four legs" is then a good generic not because all dogs have four legs (regrettably, all do not) but were the world to function normally (e.g., dogs would not be involved in freak tractor accidents or be born with strange genetic mutations), then all dogs would have four legs.
 The idea that our beliefs about what is normal in the world influences our judgments about generalizations has intuitive appeal for rejecting accidentally true generics (e.g., "Supreme Court justices have even social security numbers") and resisting stereotyped language (e.g., "Boys are good at math”).
-Our theory does not directly formalize what is *normal*, though we argue that a speaker's beliefs about what is *probable* [which may relate to what is *normal*; see @Icard2017] plays a role in endorsing and interpreting generalizations.
+Our theory does not directly formalize what is *normal*, though we argue that a speaker's beliefs about what is probable [which may relate to what is normal; see @Icard2017] plays a role in endorsing and interpreting generalizations.
 <!-- We showed in Expt.
@@
 In their model, generics express an explicit quantified relation, specifically either "Some", "Most", or "All".
-This proposal is used to then used to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
+This proposal is used to construct a set of features that accurately predicts (relative to human judgments) the quantified relationship expressed by the generic [analogous to a quantifier version of the *implied prevalence* task used in @Gelman2003b; @Cimpian2010].
 Our semantic theory can be seen as a generalization of *underquantification* to a continuous interval of possible meanings.
@@
 
-Cue validity is *inverse prevalence*; the two are related via Bayes' Rule:
+Cue validity is inverse prevalence; the two are related via Bayes' Rule:
 $P( k \mid  f) = \frac{P( f \mid  k) \cdot P( k)}{\sum\limits_{k' \in K} P( f \mid k') \cdot P( k')}$.

### 2018-12-12 paper/comgen-paper.tex
reorganize data folder, proof edits to ms

@@
 
-\authornote{This paper is currently under review. Comments or
-suggestions are appreciated and should be directed to MHT.
+\authornote{This paper is based on a Ph.D.~dissertation
+submitted to Stanford University. The research was supported by National
+Science Foundation Graduate Research Fellowship DGE-114747 awarded to
+MHT and DARPA PPAML grant FA8750-14-2-0009 to NDG. A portion of this
+paper (Case Study 2) appeared in the proceedings of the 38th Annual
+Meeting of the Cognitive Science Society, Philadelphia, 2016. We are
+deeply grateful to Ellen Markman, Gregory Scontras, Thomas Icard,
+Michael C. Frank, and Sophie Bridgers for extensive conversations and
+support for this work. In addition, the work was greatly improved
+through countless discussions with members of the Computation and
+Cognition Lab and the Language and Cognition Lab at Stanford, as well as
+the participants of \emph{A Generic Workshop} at the Center for the
+Study of Language and Information (CSLI) at Stanford in May 2017.
+Finally, we thank two anonymous reviewers and Joshua Hartshorne for
+helping us clarify our main arguments and improving the quality of the
+manuscript.
 

### 2018-12-12 experiments/_shared/js/ecosystem.js
fix paths for expts

@@ -133,6 +133,18 @@ var Ecosystem = {
         var tar1 = properties["tar1"]==null ? Ecosystem.randBoul() : properties["tar1"];
         var tar2 = properties["tar2"]==null ? Ecosystem.randBoul() : properties["tar2"];
 
+        var drawOnly = properties["drawOnly"]==null ? [] : properties["drawOnly"];
+
+        // if we say "draw only tar1" and tar2 is not also in drawOnly, tar2 is false
+        if ( (drawOnly.indexOf("tar1") > -1) & (drawOnly.indexOf("tar2") == -1) ) {
+            tar2 = false;
+        }
+        // and vice versa
+        if ( (drawOnly.indexOf("tar2") > -1) & (drawOnly.indexOf("tar1") == -1) ) {
+            tar1 = false;
+        }
+
+
         if (paperlabel != null) {
 
             //for rescaling
@@ -150,11 +162,20 @@ var Ecosystem = {
 
             var pathlabels = Object.keys(ends["00"]);
 
+            // figure out which paths to draw
+            // debugger;
+            var drawBody = ((drawOnly.indexOf("tar1") == -1) &
+                             (drawOnly.indexOf("tar2") == -1))
+            var drawTar1 = (drawOnly.indexOf("tar1") > -1) | tar1;
+            var drawTar2 = (drawOnly.indexOf("tar2") > -1) | tar2;
+
+            // for each path, figure out if it should be drawn and if so draw it
             for (var i=0; i<pathlabels.length; i++) {
                 var pathlabel = pathlabels[i];
-                if ( (pathlabel != "target1" && pathlabel != "target2") ||
-                        (pathlabel == "target1" && tar1) ||
-                        (pathlabel == "target2" && tar2)) {
+                var isTar1 = pathlabel == "target1";
+                var isTar2 = pathlabel == "target2";
+                var isBody = (pathlabel != "target1" && pathlabel != "target2");
+                if ( (isTar1 & drawTar1) | (isTar2 & drawTar2) | (isBody & drawBody) ) {
                     var pathstring = Ecosystem.intermediate2d(ends, pathlabel, prop1, prop2);
                     var path = paper.path(pathstring);
                     Ecosystem.stroke(path, ends["colors"][pathlabel]);
@@ -385,9 +406,12 @@ var Ecosystem = {
 	                			this.propsAndParams[property]["var"]
 	                		);
 	                		break;
+                        case "drawOnl":
[…]

### 2018-12-12 experiments/_shared/js/exp-V2.js

@@ -17,11 +17,16 @@ make_exp = function() {
    * in exp.structure
    */
   f.go = function(num_slides_to_skip) {
-    /* previously: we first called end of whatever slide we _were_ on 
-        this was redundent with what was done in _stream */
+    /* first call end of whatever slide we _were_ on */
+//      debugger;
 
-    /* figure out what slide to go to next */
+    // if (typeof _s !== 'undefined' && _s.end) {
+    //     _s.end();
+    // } // duplicated w/ what's in _stream
+
+    /* then figure out what slide to go to next */
     this.slideIndex++;
+
     if (this.slideIndex < this.structure.length) {
       /*
        * in the original, there's an option to do different versions of the

### 2018-12-12 experiments/_shared/js/stream-V2.js

@@ -20,6 +20,7 @@ var _stream = function() {
   if (exp.nQs) {
     //if number of total questions is defined, then show progress bar
     $('.bar').css('width', ( (exp.phase / exp.nQs)*100 + "%"));
+    // $('.bar-text').html((exp.phase + "/"+ exp.nQs));
   } else {
     $(".progress").hide();
   }
@@ -31,8 +32,10 @@ var _stream = function() {
 
     if (presented_stims.length === 0) {
       //done with slide
-      if (this.end) {this.end();};
+      //debugger;
+      if (this.end) {this.end();}; // try if else
       this.callback();
+      //this.end ? this.end() : this.callback();
     } else if (this.present_handle) {
       exp.phase++;
       var stim = presented_stims.shift();

### 2018-12-12 experiments/_shared/js/uniqueturker.js

@@ -1,14 +1,14 @@
 // Source: https://s3.amazonaws.com/mturk-public/externalHIT_v1.js
-function turkGetParam( name, defaultValue ) {
-    var regexS = "[\?&]"+name+"=([^&#]*)";
-    var regex = new RegExp( regexS );
-    var tmpURL = window.location.href;
-    var results = regex.exec( tmpURL );
-    if( results == null ) {
-        return defaultValue;
-    } else {
-        return results[1];
-    }
+function turkGetParam( name, defaultValue ) { 
+    var regexS = "[\?&]"+name+"=([^&#]*)"; 
+    var regex = new RegExp( regexS ); 
+    var tmpURL = window.location.href; 
+    var results = regex.exec( tmpURL ); 
+    if( results == null ) { 
+        return defaultValue; 
+    } else { 
+        return results[1];    
+    } 
 }
 
 function UTWorkerLimitReached(ut_id, workerId, assignmentId) {

### 2018-12-12 experiments/_shared/js/utils.js

@@ -1,13 +1,67 @@
 var utils = {
 
-	fillArray: function(value, len) {
-		var arr = [];
-		for (var i = 0; i < len; i++) {
-			arr.push(value);
-		}
-		return arr;
+	intermediatePath: function(from, to, pos) {
+	    var fromCurve = Raphael.path2curve(from);
+	    var toCurve = Raphael.path2curve(to);
+	    var diff = [];
+	    var attr = "path";
+	    //compute difference between paths and store in diff
+	    for (i = 0, ii = fromCurve.length; i < ii; i++) {
+	      diff[i] = [0];
+	      for (var j = 1, jj = fromCurve[i].length; j < jj; j++) {
+	        diff[i][j] = (toCurve[i][j] - fromCurve[i][j]);
+	      }
+	    }
+	    var S = " ";
+	    now = [];
+	    //compute new path string for intermediate image
+	    for (var i = 0, ii = fromCurve.length; i < ii; i++) {
+	      now[i] = [fromCurve[i][0]];
+	      for (var j = 1, jj = fromCurve[i].length; j < jj; j++) {
+	        now[i][j] = +fromCurve[i][j] + pos * diff[i][j];
+	      }
+	      now[i] = now[i].join(S);
+	    }
+	    return now.join(S);
+	},
+
+ 	intermediate2dPath: function(ends, pathlabel, prop1, prop2) {
+        //interpolate the proper amount along one dimension:
+        var dim2as0 = Ecosystem.intermediate(ends["00"][pathlabel], ends["10"][pathlabel], prop1);
+        var dim2as1 = Ecosystem.intermediate(ends["01"][pathlabel], ends["11"][pathlabel], prop1);
+        //interpolate the proper amount along the other dimension:
+        return Ecosystem.intermediate(dim2as0, dim2as1, prop2);
+    },
+
+	upperCaseFirst: function(str){
+		return str.replace(/\w\S*/g, function(txt){return txt.charAt(0).toUpperCase() + txt.substr(1).toLowerCase();});
+	},
+
+	isNumeric: function(val){
+		var intRegex = /^\d+$/;
+		var floatRegex = /^((\d+(\.\d *)?)|((\d*\.)?\d+))$/;
+		return (intRegex.test(val) || floatRegex.test(val))
 	},
 	
+	fillArray: function(value, len) {
+	  var arr = [];
+	  for (var i = 0; i < len; i++) {
+	    arr.push(value);
+	  }
+	  return arr;
+	},
+
+	flatten: function(array) {
[…]

### 2018-12-12 experiments/habituals/truth-judgments/js/tj-2.js

@@ -5,7 +5,7 @@ function make_slides(f) {
      name : "i0",
      start: function() {
       exp.startT = Date.now();
-      $(".total-num").html(exp.numTrials);  
+      $(".total-num").html(exp.numTrials);
      }
   });
 
@@ -15,7 +15,7 @@ function make_slides(f) {
       _.mapObject(exp.judgeButtons, function(val,key){
         $("#"+key).html(val);
       });
-      $(".total-num").html(exp.numTrials);  
+      $(".total-num").html(exp.numTrials);
     },
     button : function() {
       exp.go(); //use exp.go() if and only if there is no "present" data.
@@ -31,7 +31,7 @@ function make_slides(f) {
       // console.log(stim)
       this.startTime = Date.now();
 
-      this.stim = stim 
+      this.stim = stim
       // var habit = this.stim[0]
       // var charName = this.stim[1]
       // debugger;
@@ -196,10 +196,10 @@ function init() {
     return utils.fillArray(c, stimuli.length/timeConditions.length)
   }))
 
-  var bothGenders = ["drinks beer","drinks coffee", 
+  var bothGenders = ["drinks beer","drinks coffee",
                       "wears socks","wears a bra",
                       "wears a suit", "does cocaine"]
-                      
+
   // debugger;
   var nBothGender = _.filter(stimuli, function(s){return _.contains(bothGenders,s.habitual)}).length
 
@@ -213,9 +213,9 @@ function init() {
 
   var stimsWNames =  _.flatten(_.map(stimuli, function(s){
     var newObj = jQuery.extend(true, {}, s);
-    return !(_.contains(bothGenders,s.habitual)) ? 
+    return !(_.contains(bothGenders,s.habitual)) ?
     _.extend(s, {character: allGenders.pop()}) :
-      [_.extendOwn(s, {character: someMen.pop()}), 
+      [_.extendOwn(s, {character: someMen.pop()}),
       _.extendOwn(newObj, {character: someWomen.pop()})]
   }), true)
 
@@ -224,12 +224,12 @@ function init() {
   // var conditionsBothGenders = [conditions, conditions]
 
   // var stimsUnpacked1 = _.shuffle(_.map(
-  //   _.zip(stimuli, _.shuffle(conditions)), 
+  //   _.zip(stimuli, _.shuffle(conditions)),
   //   function(s){return _.extend(s[0], {"condition": s[1]})})
   // )
[…]
